### 2024-04-27 main.tex
Update on Overleaf.

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{graphicx}

% Title, authors, and affiliations
\title{Poincar\'e--Friedrichs constants over triangulated domains}
\author{TCF, MWL, MV}

% Theorem environments

\begin{document}

\maketitle

\begin{abstract}
    We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
    These include the Poincar\'e, Maxwell, and Friedrichs constants as special cases. 
    The main application that we envision concern computable estimates over finite element patches. 
\end{abstract}

\section{Introduction}
\cite{ern2021finite}

% Verfurth, Veeser & Verfurth 
% ...

\section{Triangulations and polytopal shellings}
\section{Constructive estimate of $p$-Poincar\'e constants}
\section{Lebesgue de Rham complexes and examples}
\section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}

\section*{Acknowledgments}

\bibliographystyle{plain}
\bibliography{library}

\end{document}

### 2024-04-27 main.tex
first material

@@
 \usepackage{fullpage}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{graphicx}
+\input{header}
 
@@
 
+% introductory paragraph
+
+% Estimates for Poincare constants 
+% \cite{bebendorf2003note}
+% \cite{vohralik2005discrete}
+% \cite{farwig2016note}
 % Verfurth, Veeser & Verfurth 
@@
 
+% Estimates for Friedrichs constants (if any)
+
+% Estimates for Maxwell constants (if any)
+
+While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
+we are not aware of computable estimates. 
+Clearly, not all local patches describe convex subdomains. 
+An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
+Indeed, finite element patches of Lipschitz satisfy that condition. 
+Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation.
+However, the interior ball can be abstrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity.
+Some interesting limit cases include the slit domain and the crossed bricks domain,
+for which some finite element patches are not star-shaped with respect to any ball. 
+\color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
+
 \section{Triangulations and polytopal shellings}
+
+We gather notions of simplicial meshes for the subsequent discussion.
+
+A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these the \emph{vertices} of the simplex $T$. 
+If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
+then we call $S$ a subsimplex of $T$ and we call $T$ a supersimplex of $S$.
+
+A family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if its member simplices satisfy the following condition: 
+(i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
+The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
+We say that $\calT$ has dimension $n$ if it contains an $n$-dimensional simplex as a supersimplex for each simplex within it.
+
+Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
+More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
+Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
+We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
+Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
+Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces of the triangulation.
+
+When $\calT$ is a triangulation and $T \in \calT$, then $\calT(T)$ denotes the \emph{local patch} of $T$, which is the smallest simplicial subcomplex of $\calT$ that contains all supersimplices of $T$.
+Formally,
+\begin{gather*}
+    \calT(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
+\end{gather*}
+A crucial observation is this: 
+given $T, T' \in \calT$, the intersection $\calT(T) \cap \calT(T')$ is either empty or the convex closure of $T$ and $T'$ is a simplex $S \in \calT$ such that $\calT(T) \cap \calT(T') = \calT(S)$. 
+\color{red}Probably needs a proof\color{black}
+
 \section{Constructive estimate of $p$-Poincar\'e constants}
+
+% either proceeding simplex by simplex, matching along faces 
+% or proceeding patch by patch, matching over intersections
+
 \section{Lebesgue de Rham complexes and examples}

### 2024-04-29 main.tex
Update on Overleaf.

@@
 \input{header}
+\usepackage{amscd}
+\usepackage{tikz-cd}
+\newtheorem{remark}{Remark}
 
@@
 
+\begin{remark}
+    Suppose that $\calT$ is a simplicial complex and that $T$ is a simplex, $T \notin \calT$, such that $\calS := T \cap |\calT|$ is a subcomplex of $\partial T$. 
+    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
+    \begin{align*}
+        \begin{CD}
+            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
+        \end{CD}
+    \end{align*}
+    We notice that $\calS$, $\calT$, $T$ and $\calT \cup T$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
+    By the nature of the mappings in the Mayer-Vietoris sequence, we see that 
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0 
+        \end{CD}
+    \end{align*}
+    is an exact sequence. 
+    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
+    the Mayer-Vietoris sequence includes the exact sequence 
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow 0 
+        \end{CD}
+    \end{align*}
+    and we conclude that $H_{k}(\calT) = 0$ for $1 \leq k \leq n-1$.
+    Finally, the Mayer-Vietoris sequence includes the exact sequences 
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT \cup T) \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT \cup T) \longrightarrow 0
+        \end{CD}
+    \end{align*}
+    Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT \cup T)$.
+    % We know that  $H_{0}(\calT \cup T) \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
+    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
+    % one easily sees that $H_{0}(\calT \cup T) \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
+    If $\calS$ is isomorphic to disk,
+    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
+    If instead $\calS$ is isomorphic to a sphere, 
+    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
+    % Moreover, Thus $H_{n}(\calT \cup T) = H_{n}(\calT) \oplus H_{n}(\calS)$.
+    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
+    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT \cup T) \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0
+        \end{CD}
+    \end{align*}
+\end{remark}
+
+A simplicial $n$-dimensional complex $\calT$ is called shellable if its $n$-simplices can be arranged in linear order $T_0, T_1, \dots$ in such a way that the subcomplex $( \cup_{i=0}^{k-1} T_i ) \cap T_k$ has dimension $n-1$ for all $k > 0$.
+
 \bibliographystyle{plain}

### 2024-04-30 main.tex
some progress on the combinatorics

--- 2024-04-27 main.tex
@@
 
+It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
+In particular, this enables the inductive method of proof.
+
+Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres.
+However, these estimates are important partial results.
+Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+l
+
 \section{Triangulations and polytopal shellings}
+
+% 1. Develop some notation
 
@@
 \end{gather*}
-A crucial observation is this: 
-given $T, T' \in \calT$, the intersection $\calT(T) \cap \calT(T')$ is either empty or the convex closure of $T$ and $T'$ is a simplex $S \in \calT$ such that $\calT(T) \cap \calT(T') = \calT(S)$. 
-\color{red}Probably needs a proof\color{black}
+A crucial observation is the following.
+
+\begin{lemma}
+ Let $\calT$ be an $n$-dimensional simplicial complex and let $T,T' \in \calT$.
+ Then either $\calT_{n}(T) \cap \calT_{n}(T') = \emptyset$ or there exists $S \in \calT$
+ such that $\calT_{n}(T) \cap \calT_{n}(T') = \calT_{n}(S)$ with $T, T' \subseteq S$.
+\end{lemma}
+\begin{proof}
+ Let $F \in \calT$ be $n$-dimensional.
+ We have $F \in \calT(T )$ if and only if all vertices of $T $ are vertices of $F$.
+ We have $F \in \calT(T')$ if and only if all vertices of $T'$ are vertices of $F$.
+ Consequently, $F \in \calT(T) \cap \calT(T)$ if and only if $F \in \calT(S)$,
+ where $S \in \calT$ and $S$ is the convex closure of $F$ and $F'$.
+\end{proof}
+
+% 2. Develop manifold-like complexes and characterize them
+
+An $n$-dimensional simplicial complex is called \emph{manifold-like} if for every $x \in \bigcup \calT$
+we have one of the following two conditions:
+\begin{itemize}
+ \item 
+ there exists $\epsilon > 0$ 
+ and a homeomorphism 
+ \begin{align*}
+    \phi : \Ball_\epsilon(x) \cap \bigcup\calT  
+    \rightarrow 
+    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1 \right\}
+ \end{align*}
+ such that $\phi(x) = 0$,
+ \item 
+ there exists $\epsilon > 0$ and a homeomorphism 
+ \begin{align*}
+    \phi : \Ball_\epsilon(x) \cap \bigcup\calT 
+    \rightarrow 
+    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1, x_n \leq 0 \right\}
+ \end{align*}
+ such that $\phi(x) = 0$.
+\end{itemize}
+This characterizes the union of the simplicial complex $\calT$ as a topological manifold with boundary.
+
+We would like to have a purely combinatorial and computable criterion that characterizes manifold-like simplicial complexes. A first step in that direction is the following result.
+
+\begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
+    Let $\calT$ be an $n$-dimensional simplicial complex. The following are equivalent:
+    \begin{itemize}
+     \item $\calT$ is manifold-like
+     \item $\calT(V)$ is the triangulation of a ball for all $V \in \Vertices(\calT)$
+     \item $\calT(V)$ is manifold-like for all $V \in \Vertices(\calT)$
+     \item $\calT(S)$ is the triangulation of a ball for all $S \in \calT$
+     \item $\calT(S)$ is manifold-like for all $S \in \calT$
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    \color{red} TODO
+\end{proof}
+
+\begin{remark}
+    Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
+    Conversely, for each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. % TODO: are these compact?
+    % TODO There are computational limits to algorithmically deciding whether a simplicial complex represents a manifold. 
+\end{remark}
+
+% 3. Develop construction of complexes via adding patches
+
+We are interested in exhausting a simplicial complex in a controlled manner. 
+Suppose that $\calT$ is a manifold-like $n$-dimensional simplicial complex. 
+We call $n$-simplices $S,T \in \calT$ \emph{face-connected} if there exists a sequence $S_0=S,S_1,\dots,T=S_m$ such that $S_{i} \cap S_{i-1}$ is a face for all $1 \leq i \leq m$.
+Clearly, face-connected is an equivalence relation.
+A \emph{connected component} of $\calT$ is an equivalence class under the face-connected relation, and we call $\calT$ connected if all its $n$-simplices are face-connected.
+In a manifold-like simplicial complex, two $n$-simplices have non-empty intersection if and only if they are face-connected.
+
+It is a consequence of Lemma~\ref{lemma:characterizationofmanifoldcomplexes} that,
+if $\calT$ is a manifold-like simplicial complex, then $\calT(S)$ is connected for all $S \in \calT$.
+Moreover, a manifold-like simplicial complex $\calT$ is connected if and only if $\bigcup\calT$ is a connected topological space.
+
+We let \emph{$k$-patching} refer to enumerations $S_1, S_2, \dots$ of $\subsimplex_{k}(\calT)$
+such that for any $0 \leq m$, the union 
+$\calU_{m} := \calT(S_0) \cup \calT(S_1) \cup \calT(S_2) \cup \dots \cup \calT(S_m)$
+shares an $n$-simplex with the patch $\calT(S_{m+1})$.
+We call the $k$-patching \emph{manifold-like} if $\calU_{m}$ is manifold-like for all $0 \leq m$.
+Clearly, a $k$-patching only exists if $k < n$ and if $\calT$ is connected. 
+We refer the reader to Figure~\ref{figure:illustrationpatching} for an illustration.
+
+\begin{lemma}
+    A connected manifold-like $n$-dimensional simplicial complex $\calT$ admits a $k$-patching for any $k < n$.
+\end{lemma}
+\begin{proof}
+    We define an undirected graph by letting $\subsimplex_{k}(\calT)$ be the set of nodes 
+    and connecting any $S, S' \in \subsimplex_{k}(\calT)$ if there exists $T \in \subsimplex_{k+1}(\calT)$ with $S, S' \subseteq T$. 
+    Note that in this case $\calT(S) \cap \calT(S') = \calT(T)$. 
+    Since $\calT$ is connected, the graph $\calG$ is connected.
+
+    We let $S_0, S_1, S_2, \dots$ be an enumeration of the $k$-simplices generated by a breadth-first traversal of the graph $\calG$,
+    starting at some arbitrary but fixed $S_0 \in \calT$. 
+    Since $\calG$ is locally finite and connected, 
+    this breadth-first traversal includes all $k$-simplices of $\calT$.
+
+    Let $m \in \bbZ$ with $m \geq 1$. If $S_m$ has distance $d \in \bbN$ from $S_1$ in the graph $\calG$,
+    then there exists $0 \leq l \leq m$ such that $S_l$ has distance $d-1$ from $S_1$ and is connected to $S_m$. 
+    It follows that the sequence $S_0, S_1, S_2, \dots$ is a $k$-patching of $\calT$. 
+\end{proof}
+
+The preceding lemma is generally not true when the $k$-patching is required to be manifold-like,
+as can be verified from some simple examples;~see Figure~\ref{figure:annuluscounterexample}.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
+        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}
+    \begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
+        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}
+    \begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
+        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}
+    \begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
+        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}
+    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation.
+(1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
+(2) The new edge patch already be a subset of the subtriangulation (3) An inadmissible choice because new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like (4) An inadmissible choice because new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}[scale=0.5]
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
+        \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
+        \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
+        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+        \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
+        \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
+        \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
+        \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
+        \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
+        \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
+        \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
+    \end{tikzpicture}
+    \begin{tikzpicture}[scale=0.5]
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
+        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
+        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
+        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+        \draw (O) -- (A);
+        \draw (O) -- (B);
+        \draw (O) -- (C);
+        \draw (O) -- (X);
+        \draw (O) -- (Y);
+        \draw (O) -- (Z);
+        %
+    \end{tikzpicture}
+    \begin{tikzpicture}[scale=0.5] 
+        \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
+        % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
+
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
+        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
+        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
+        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+        \coordinate (T) at ({0}, {0}, {3});
+
+        \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
+        \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
+        \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
+        \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
+        \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
+        \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
+
+    \end{tikzpicture}
+
+    \caption{Example of a connected $2$-dimensional manifold-like simplicial complex, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
+\end{figure}
+
+% \color{red}
+% \begin{proposition}
+%     Suppose that $\calT$ is a connected $n$-dimensional simplicial complex. Then the following are equivalent:
+%     \begin{itemize}
+%      \item $\calT$ is manifold-like
+%      \item $\calT$ has a manifold-like $0$-patching
+%      % \item There exists $1 \leq k \leq n$ such that $\calT$ has a $k$-patching
+%     \end{itemize}
+% \end{proposition}
+% \color{black}
+
+% 4. Shellability
+
+We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
+Given an $n$-dimensional simplicial complex $\calT$, a \emph{shelling} is an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$ such that $( \calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m}) ) \cap \calT(T_{m+1})$ is a simplicial complex of dimension $n-1$.
+Notice that the last intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$, and is thus manifold like.
+
+% \begin{lemma}
+%     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
+%     In particular, $\calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m})$ is manifold-like for every $m \geq 0$.
+% \end{lemma}
+% \begin{proof}    
+% \end{proof}
+
+We notion of shelling is taken from Ziegler's book~\cite{}
+
+% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars
+
+%
 
@@
 
-\section{Lebesgue de Rham complexes and examples}
 \section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}
+% Repeat for H(curl), H(div), and differential forms
 

### 2024-04-30 main.tex
spellcheck

@@
 \input{header}
-\usepackage{amscd}
-\usepackage{tikz-cd}
-\newtheorem{remark}{Remark}
 
@@
 Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation.
-However, the interior ball can be abstrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity.
+However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity.
 Some interesting limit cases include the slit domain and the crossed bricks domain,

### 2024-04-30 main.tex
Update on Overleaf.

--- 2024-04-30 main.tex
@@
-\documentclass[a4paper]{article}
+\documentclass[a4paper]{amsart}
 \usepackage[utf8]{inputenc}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 \input{header}
@@
 \section{Introduction}
-\cite{ern2021finite}
 
@@
 Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-l
+
+\cite{ern2021finite}
 
@@
 
+We gather notions of simplicial meshes for the subsequent discussion. 
+Apart from basic definitions and notational conventions, we pay special attention to the question of when a simplicial complex is a triangulation of a manifold. 
+A particularly important class of simplicial complexes are so-called \emph{shellable} complexes.
+Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner.
+While shellable complexes are a very special class of complexes, they faciliate achieving the main goal of our exposition.
+Our main references on simplicial complexes and shellability are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}.
+
 % 1. Develop some notation
 
-We gather notions of simplicial meshes for the subsequent discussion.
+\subsection{Basic notions}
 
@@
 
-When $\calT$ is a triangulation and $T \in \calT$, then $\calT(T)$ denotes the \emph{local patch} of $T$, which is the smallest simplicial subcomplex of $\calT$ that contains all supersimplices of $T$.
+When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} of $T$, which is the smallest simplicial subcomplex of $\calT$ that contains all supersimplices of $T$.
 Formally,
 \begin{gather*}
-    \calT(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
+    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
 \end{gather*}
@@
  Let $F \in \calT$ be $n$-dimensional.
- We have $F \in \calT(T )$ if and only if all vertices of $T $ are vertices of $F$.
- We have $F \in \calT(T')$ if and only if all vertices of $T'$ are vertices of $F$.
- Consequently, $F \in \calT(T) \cap \calT(T)$ if and only if $F \in \calT(S)$,
+ We have $F \in \patch_{\calT}(T )$ if and only if all vertices of $T $ are vertices of $F$.
+ We have $F \in \patch_{\calT}(T')$ if and only if all vertices of $T'$ are vertices of $F$.
+ Consequently, $F \in \patch_{\calT}(T) \cap \patch_{\calT}(T)$ if and only if $F \in \patch_{\calT}(S)$,
  where $S \in \calT$ and $S$ is the convex closure of $F$ and $F'$.
@@
 % 2. Develop manifold-like complexes and characterize them 
+\subsection{Triangulations of manifolds}
+
+We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$.
+We call those $F \in \calT$ of dimension $n-1$ contained within only one parent a \emph{boundary face}.
+We write $\partial\calT$ for the simplicial subcomplex of $\calT$ of dimension $n-1$ 
+whose full-dimensional members are exactly the boundary faces of $\calT$.
 
@@
      \item $\calT$ is manifold-like
-     \item $\calT(V)$ is the triangulation of a ball for all $V \in \Vertices(\calT)$
-     \item $\calT(V)$ is manifold-like for all $V \in \Vertices(\calT)$
-     \item $\calT(S)$ is the triangulation of a ball for all $S \in \calT$
-     \item $\calT(S)$ is manifold-like for all $S \in \calT$
+     \item $\patch_{\calT}(V)$ is the triangulation of a ball for all $V \in \Vertices(\calT)$
+     \item $\patch_{\calT}(V)$ is manifold-like for all $V \in \Vertices(\calT)$
+     \item $\patch_{\calT}(S)$ is the triangulation of a ball for all $S \in \calT$
+     \item $\patch_{\calT}(S)$ is manifold-like for all $S \in \calT$
     \end{itemize}
@@
 \end{remark}
-
-% 3. Develop construction of complexes via adding patches
-
-We are interested in exhausting a simplicial complex in a controlled manner. 
-Suppose that $\calT$ is a manifold-like $n$-dimensional simplicial complex. 
-We call $n$-simplices $S,T \in \calT$ \emph{face-connected} if there exists a sequence $S_0=S,S_1,\dots,T=S_m$ such that $S_{i} \cap S_{i-1}$ is a face for all $1 \leq i \leq m$.
-Clearly, face-connected is an equivalence relation.
-A \emph{connected component} of $\calT$ is an equivalence class under the face-connected relation, and we call $\calT$ connected if all its $n$-simplices are face-connected.
-In a manifold-like simplicial complex, two $n$-simplices have non-empty intersection if and only if they are face-connected.
-
-It is a consequence of Lemma~\ref{lemma:characterizationofmanifoldcomplexes} that,
-if $\calT$ is a manifold-like simplicial complex, then $\calT(S)$ is connected for all $S \in \calT$.
-Moreover, a manifold-like simplicial complex $\calT$ is connected if and only if $\bigcup\calT$ is a connected topological space.
-
-We let \emph{$k$-patching} refer to enumerations $S_1, S_2, \dots$ of $\subsimplex_{k}(\calT)$
-such that for any $0 \leq m$, the union 
-$\calU_{m} := \calT(S_0) \cup \calT(S_1) \cup \calT(S_2) \cup \dots \cup \calT(S_m)$
-shares an $n$-simplex with the patch $\calT(S_{m+1})$.
-We call the $k$-patching \emph{manifold-like} if $\calU_{m}$ is manifold-like for all $0 \leq m$.
-Clearly, a $k$-patching only exists if $k < n$ and if $\calT$ is connected. 
-We refer the reader to Figure~\ref{figure:illustrationpatching} for an illustration.
-
-\begin{lemma}
-    A connected manifold-like $n$-dimensional simplicial complex $\calT$ admits a $k$-patching for any $k < n$.
-\end{lemma}
-\begin{proof}
-    We define an undirected graph by letting $\subsimplex_{k}(\calT)$ be the set of nodes 
-    and connecting any $S, S' \in \subsimplex_{k}(\calT)$ if there exists $T \in \subsimplex_{k+1}(\calT)$ with $S, S' \subseteq T$. 
-    Note that in this case $\calT(S) \cap \calT(S') = \calT(T)$. 
-    Since $\calT$ is connected, the graph $\calG$ is connected.
-
-    We let $S_0, S_1, S_2, \dots$ be an enumeration of the $k$-simplices generated by a breadth-first traversal of the graph $\calG$,
-    starting at some arbitrary but fixed $S_0 \in \calT$. 
-    Since $\calG$ is locally finite and connected, 
-    this breadth-first traversal includes all $k$-simplices of $\calT$.
-
-    Let $m \in \bbZ$ with $m \geq 1$. If $S_m$ has distance $d \in \bbN$ from $S_1$ in the graph $\calG$,
-    then there exists $0 \leq l \leq m$ such that $S_l$ has distance $d-1$ from $S_1$ and is connected to $S_m$. 
-    It follows that the sequence $S_0, S_1, S_2, \dots$ is a $k$-patching of $\calT$. 
-\end{proof}
-
-The preceding lemma is generally not true when the $k$-patching is required to be manifold-like,
-as can be verified from some simple examples;~see Figure~\ref{figure:annuluscounterexample}.
 
@@
 
-% 4. Shellability
+% 3. Shellability 
+\subsection{Shellable simplicial complexes}
 
 We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-Given an $n$-dimensional simplicial complex $\calT$, a \emph{shelling} is an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$ such that $( \calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m}) ) \cap \calT(T_{m+1})$ is a simplicial complex of dimension $n-1$.
+Given an $n$-dimensional simplicial complex $\calT$, a \emph{shelling} is an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$ such that $( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) ) \cap \patch_{\calT}(T_{m+1})$ is a simplicial complex of dimension $n-1$.
 Notice that the last intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$, and is thus manifold like.
@@
 %     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
-%     In particular, $\calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m})$ is manifold-like for every $m \geq 0$.
+%     In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is manifold-like for every $m \geq 0$.
 % \end{lemma}
@@
 
-We notion of shelling is taken from Ziegler's book~\cite{}
+We notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
 
@@
 %
+
+A simplicial $n$-dimensional complex $\calT$ is called shellable if its $n$-simplices can be arranged in linear order $T_0, T_1, \dots$ in such a way that the subcomplex $( \cup_{i=0}^{k-1} T_i ) \cap T_k$ has dimension $n-1$ for all $k > 0$.
+
+\begin{remark}
+    A shellable simplicial complex that triangulates a manifold has a very restricted topology. 
+    The Mayer-Vietoris theorem implies restrictions on the homology groups of simplicial complexes iteratively constructed via shelling.
+
+    Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold, and suppose that its boundary complex $\partial\calT$ is either empty or strongly connected.
+    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$.
+In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$.
+We write $\calT'$ be the  simplicial complex that contains $\calT \cup T$.
+    We exclude that case $n \leq 1$ since otherwise the discussion is trivial.
+
+    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
+    \begin{align*}
+        \begin{CD}
+            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
+        \end{CD}
+    \end{align*}
+    We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
+    By the nature of the mappings in the Mayer-Vietoris sequence, 
+    \color{red}which uses some specific knowledge about the arrows\color{black}, 
+    we see that 
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0 
+        \end{CD}
+    \end{align*}
+    is an exact sequence. 
+    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
+    the Mayer-Vietoris sequence includes the exact sequence 
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow 0 
+        \end{CD}
+    \end{align*}
+    and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
+    Finally, the Mayer-Vietoris sequence includes the exact sequences 
+    \begin{align*}
+        \begin{CD}
+            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT') \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT') \longrightarrow 0
+        \end{CD}
+    \end{align*}
+    % Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
+    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
+    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+    % one easily sees that $H_{0}(\calT') \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+    Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
+    In the case that $\calS$ is isomorphic to disk,
+    then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ are trivial and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
+    Consider now the case that $\calS$ is isomorphic to a sphere.
+    Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
+Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq \bbZ$.
+    \color{red}By some handwaving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
+    Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
+
+    We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
+    \[
+        H_0(\calT) \simeq \bbZ, 
+        \quad 
+        H_1(\calT) \simeq \dots \simeq H_{n-1}(\calT) \simeq 0.
+    \]
+    Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
+
+    % then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
+    % Moreover, Thus $H_{n}(\calT') = H_{n}(\calT) \oplus H_{n}(\calS)$.
+    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
+    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
+    % \begin{align*}
+    %     \begin{CD}
+    %         0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT') \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0
+    %     \end{CD}
+    % \end{align*}
+\end{remark}
 

### 2024-05-01 main.tex
more material on poincare inequality

--- 2024-04-30 main.tex
@@
 
+Let us assume that $p \in [1,\infty]$ and that $\Omega \subseteq \bbR^{n}$ is an open set. 
+We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the Poincar\'e--Friedrichs inequality with exponent $p \in [1,\infty]$
+if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
+for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:inequalitypf:gradient}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm PF},\nabla,\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+We call $C_{{\rm PF},\Omega,p}$ the Poincar\'e--Friedrichs constant. 
+This inequality implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+
+\begin{remark}
+    Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.
+
+    Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
+    we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
+    if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
+    for all $u \in W^{1,p}(\Omega)$
+    \begin{align}
+        \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+        \leq 
+        C_{\varnothing,\Omega,p} 
+        \| \nabla u \|_{L^{p}(\Omega)}
+        ,
+    \end{align}
+    where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
+    \begin{align*}
+        u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
+    \end{align*}
+    Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
+    Towards a converse inequality, 
+    let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+    \begin{align*}
+        \| v_\Omega \|_{L^{p}(\Omega)}^{p}
+        = 
+        \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
+        \leq 
+        \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
+        = 
+        \| v \|_{L^{p}(\Omega)}^{p}
+        .
+    \end{align*}
+    Here, we have used Jensen's inequality. 
+    In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
+    We therefore combine 
+    \begin{align*}
+        \| v - v_\Omega \|_{L^{p}(\Omega)} 
+        \leq
+        2
+        \| v \|_{L^{p}(\Omega)},
+        \quad 
+        v \in L^{p}(\Omega)
+        .
+    \end{align*}
+    \begin{align*}
+        \color{Emerald}
+        \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+        \leq 
+        2^{p-1} 
+        \| u \|_{L^{p}(\Omega)}^{p}
+        +
+        2^{p-1} 
+        \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+        \leq 
+        2^{p} 
+        \| u \|_{L^{p}(\Omega)}^{p}
+        .
+    \end{align*}
+    We conclude that the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$. 
+    In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
+    and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
+    \color{red} Question: can we modify the preceding discussion for general $p$ so that this special inequality for $p=2$ emerges as a limit case?
+Then we get stronger results for $p \approx 2$.
+Stern's paper?
+\color{black}
+
+    The Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+    The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
+    When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
+    which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
+    \color{red} Make this last paragraph for concise.
+\end{remark}
+
 % either proceeding simplex by simplex, matching along faces 
 % or proceeding patch by patch, matching over intersections
+\begin{theorem}
+    \color{red}Precise form of the inequality yet to be discussed, though the construction is clear.
+\end{theorem}
+
+\begin{proof}
+ Let $u \in W^{1,p}(\Omega)$. 
+ For each $F \in \calT$ of dimension $n-1$, 
+ we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F} \| \nabla u_F \|_{L^{p}(U_F)}$.
+
+ Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j < m$ such that $F_m := T_m \cap T_j$ is a face of dimension $n-1$.
+We write $\Omega_m := \cup_{j=0}^{m} T_m$.
+Hence $\Omega = \Omega_M$.
+
+%  We let $T \in \calT$ be the first $n$-simplex. 
+%  There exists We already have
+
+ Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$.
+Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
+ By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j}$. 
+ Since $\nabla u_{F_{m}|T_j} = \nabla w_{m-1|T_j}$,
+ there exists a constant $c_{m} := w_{m-1|T_j} - u_{F_{m}|T_j}$.
+ We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
+ By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_j} = w_{m-1|T_j}$. 
+ But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
+ As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
+ Moreover, 
+ \begin{gather*}
+    \| u'_{F_m} \|_{L^{p}(T_m)}
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
+    +
+    \| c_{m} \|_{L^{p}(T_m)},
+    \qquad 
+    \| c_{m} \|_{L^{p}(T_m)}
+    \leq 
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| c_{m} \|_{L^{p}(T_j)},
+    \\ 
+    \| c_{m} \|_{L^{p}(T_j)}
+    \leq 
+    \| w_{m-1}\|_{L^{p}(T_j)} + \| u_{F_{m}} \|_{L^{p}(T_j)} 
+    .
+ \end{gather*}
+ In particular,
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| u_{F_{m}} \|_{L^{p}(T_j)}
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_j)}
+    .
+ \end{align*}
+ In the special case $p < \infty$, we also find 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq 
+    3^{p-1}
+    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+    +
+    3^{p-1}
+    \frac{ \vol(T_m) }{ \vol(T_j) }
+    \| u_{F_{m}} \|_{L^{p}(T_j)}^{p}
+    +
+    3^{p-1}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
+    \\&\leq 
+    3^{p-1}
+    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_j) } \right)
+    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
+    +
+    3^{p-1}
+    \frac{ \vol(T_m) }{ \vol(T_j) }
+    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
+    .
+ \end{align*}
+ Recursive application provides the desired result. 
+\end{proof}
+
+\begin{remark}
+    The previous result depends on only a few parameters of the triangulation:
+    the length of any traversal from the root simplex,
+    the ratios of the volumes of adjacent simplices,
+    the Poincar\'e constants on each face patch, and the Poincar\'e constant of the initial simplex. 
+    The aforementioned local Poincar\'e constants can generally be estimated in terms of shape-parameters. 
+    If the face patches of the triangulation are convex, then better estimates are possible. 
+\end{remark}
 

### 2024-05-01 draft.tex

--- 2024-04-30 main.tex
@@
-\documentclass[a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{fullpage}
-\input{header}
-
-% Title, authors, and affiliations
-\title{Poincar\'e--Friedrichs constants over triangulated domains}
-\author{TCF, MWL, MV}
-
-% Theorem environments
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-    We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    These include the Poincar\'e, Maxwell, and Friedrichs constants as special cases. 
-    The main application that we envision concern computable estimates over finite element patches. 
-\end{abstract}
-
-\section{Introduction}
-\cite{ern2021finite}
-
-% introductory paragraph
-
-% Estimates for Poincare constants 
-% \cite{bebendorf2003note}
-% \cite{vohralik2005discrete}
-% \cite{farwig2016note}
-% Verfurth, Veeser & Verfurth 
-% ...
-
-% Estimates for Friedrichs constants (if any)
-
-% Estimates for Maxwell constants (if any)
-
-While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
-we are not aware of computable estimates. 
-Clearly, not all local patches describe convex subdomains. 
-An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
-Indeed, finite element patches of Lipschitz satisfy that condition. 
-Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation.
-However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity.
-Some interesting limit cases include the slit domain and the crossed bricks domain,
-for which some finite element patches are not star-shaped with respect to any ball. 
-\color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
-
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
-In particular, this enables the inductive method of proof.
-
-Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-l
-
-\section{Triangulations and polytopal shellings}
-
-% 1. Develop some notation
-
-We gather notions of simplicial meshes for the subsequent discussion.
-
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these the \emph{vertices} of the simplex $T$. 
-If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a subsimplex of $T$ and we call $T$ a supersimplex of $S$.
-
-A family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if its member simplices satisfy the following condition: 
-(i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-We say that $\calT$ has dimension $n$ if it contains an $n$-dimensional simplex as a supersimplex for each simplex within it.
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
-More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
-We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
-Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
-Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces of the triangulation.
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\calT(T)$ denotes the \emph{local patch} of $T$, which is the smallest simplicial subcomplex of $\calT$ that contains all supersimplices of $T$.
-Formally,
-\begin{gather*}
-    \calT(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
-\end{gather*}
-A crucial observation is the following.
-
-\begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $T,T' \in \calT$.
- Then either $\calT_{n}(T) \cap \calT_{n}(T') = \emptyset$ or there exists $S \in \calT$
- such that $\calT_{n}(T) \cap \calT_{n}(T') = \calT_{n}(S)$ with $T, T' \subseteq S$.
-\end{lemma}
-\begin{proof}
- Let $F \in \calT$ be $n$-dimensional.
- We have $F \in \calT(T )$ if and only if all vertices of $T $ are vertices of $F$.
- We have $F \in \calT(T')$ if and only if all vertices of $T'$ are vertices of $F$.
- Consequently, $F \in \calT(T) \cap \calT(T)$ if and only if $F \in \calT(S)$,
- where $S \in \calT$ and $S$ is the convex closure of $F$ and $F'$.
-\end{proof}
-
-% 2. Develop manifold-like complexes and characterize them
-
-An $n$-dimensional simplicial complex is called \emph{manifold-like} if for every $x \in \bigcup \calT$
-we have one of the following two conditions:
-\begin{itemize}
- \item 
- there exists $\epsilon > 0$ 
- and a homeomorphism 
- \begin{align*}
-    \phi : \Ball_\epsilon(x) \cap \bigcup\calT  
-    \rightarrow 
-    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1 \right\}
- \end{align*}
- such that $\phi(x) = 0$,
- \item 
- there exists $\epsilon > 0$ and a homeomorphism 
- \begin{align*}
-    \phi : \Ball_\epsilon(x) \cap \bigcup\calT 
-    \rightarrow 
-    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1, x_n \leq 0 \right\}
- \end{align*}
- such that $\phi(x) = 0$.
-\end{itemize}
-This characterizes the union of the simplicial complex $\calT$ as a topological manifold with boundary.
-
-We would like to have a purely combinatorial and computable criterion that characterizes manifold-like simplicial complexes. A first step in that direction is the following result.
-
-\begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
-    Let $\calT$ be an $n$-dimensional simplicial complex. The following are equivalent:
-    \begin{itemize}
-     \item $\calT$ is manifold-like
-     \item $\calT(V)$ is the triangulation of a ball for all $V \in \Vertices(\calT)$
-     \item $\calT(V)$ is manifold-like for all $V \in \Vertices(\calT)$
-     \item $\calT(S)$ is the triangulation of a ball for all $S \in \calT$
-     \item $\calT(S)$ is manifold-like for all $S \in \calT$
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    \color{red} TODO
-\end{proof}
-
-\begin{remark}
-    Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    Conversely, for each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. % TODO: are these compact?
-    % TODO There are computational limits to algorithmically deciding whether a simplicial complex represents a manifold. 
-\end{remark}
-
-% 3. Develop construction of complexes via adding patches
+% Develop construction of complexes via adding patches 
+\subsection{Patch coverings}
 
@@
 It is a consequence of Lemma~\ref{lemma:characterizationofmanifoldcomplexes} that,
-if $\calT$ is a manifold-like simplicial complex, then $\calT(S)$ is connected for all $S \in \calT$.
+if $\calT$ is a manifold-like simplicial complex, then $\patch_{\calT}(S)$ is connected for all $S \in \calT$.
 Moreover, a manifold-like simplicial complex $\calT$ is connected if and only if $\bigcup\calT$ is a connected topological space.
@@
 such that for any $0 \leq m$, the union 
-$\calU_{m} := \calT(S_0) \cup \calT(S_1) \cup \calT(S_2) \cup \dots \cup \calT(S_m)$
-shares an $n$-simplex with the patch $\calT(S_{m+1})$.
+$\calU_{m} := \patch_{\calT}(S_0) \cup \patch_{\calT}(S_1) \cup \patch_{\calT}(S_2) \cup \dots \cup \patch_{\calT}(S_m)$
+shares an $n$-simplex with the patch $\patch_{\calT}(S_{m+1})$.
 We call the $k$-patching \emph{manifold-like} if $\calU_{m}$ is manifold-like for all $0 \leq m$.
@@
     and connecting any $S, S' \in \subsimplex_{k}(\calT)$ if there exists $T \in \subsimplex_{k+1}(\calT)$ with $S, S' \subseteq T$. 
-    Note that in this case $\calT(S) \cap \calT(S') = \calT(T)$. 
+    Note that in this case $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(T)$. 
     Since $\calT$ is connected, the graph $\calG$ is connected.
@@
 as can be verified from some simple examples;~see Figure~\ref{figure:annuluscounterexample}.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation.
-(1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
-(2) The new edge patch already be a subset of the subtriangulation (3) An inadmissible choice because new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like (4) An inadmissible choice because new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=0.5]
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
-        \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
-        \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
-        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-        \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
-        \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
-        \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
-        \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
-        \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
-        \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
-        \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
-    \end{tikzpicture}
-    \begin{tikzpicture}[scale=0.5]
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-        \draw (O) -- (A);
-        \draw (O) -- (B);
-        \draw (O) -- (C);
-        \draw (O) -- (X);
-        \draw (O) -- (Y);
-        \draw (O) -- (Z);
-        %
-    \end{tikzpicture}
-    \begin{tikzpicture}[scale=0.5] 
-        \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
-        % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
-
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-        \coordinate (T) at ({0}, {0}, {3});
-
-        \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
-
-    \end{tikzpicture}
-
-    \caption{Example of a connected $2$-dimensional manifold-like simplicial complex, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
-\end{figure}
-
-% \color{red}
-% \begin{proposition}
-%     Suppose that $\calT$ is a connected $n$-dimensional simplicial complex. Then the following are equivalent:
-%     \begin{itemize}
-%      \item $\calT$ is manifold-like
-%      \item $\calT$ has a manifold-like $0$-patching
-%      % \item There exists $1 \leq k \leq n$ such that $\calT$ has a $k$-patching
-%     \end{itemize}
-% \end{proposition}
-% \color{black}
-
-% 4. Shellability
-
-We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-Given an $n$-dimensional simplicial complex $\calT$, a \emph{shelling} is an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$ such that $( \calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m}) ) \cap \calT(T_{m+1})$ is a simplicial complex of dimension $n-1$.
-Notice that the last intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$, and is thus manifold like.
-
-% \begin{lemma}
-%     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
-%     In particular, $\calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m})$ is manifold-like for every $m \geq 0$.
-% \end{lemma}
-% \begin{proof}    
-% \end{proof}
-
-We notion of shelling is taken from Ziegler's book~\cite{}
-
-% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars
-
-%
-
-\section{Constructive estimate of $p$-Poincar\'e constants}
-
-% either proceeding simplex by simplex, matching along faces 
-% or proceeding patch by patch, matching over intersections
-
-\section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}
-% Repeat for H(curl), H(div), and differential forms
-
-\section*{Acknowledgments}
-
-\begin{remark}
-    Suppose that $\calT$ is a simplicial complex and that $T$ is a simplex, $T \notin \calT$, such that $\calS := T \cap |\calT|$ is a subcomplex of $\partial T$. 
-    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
-    \begin{align*}
-        \begin{CD}
-            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
-        \end{CD}
-    \end{align*}
-    We notice that $\calS$, $\calT$, $T$ and $\calT \cup T$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
-    By the nature of the mappings in the Mayer-Vietoris sequence, we see that 
-    \begin{align*}
-        \begin{CD}
-            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0 
-        \end{CD}
-    \end{align*}
-    is an exact sequence. 
-    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
-    the Mayer-Vietoris sequence includes the exact sequence 
-    \begin{align*}
-        \begin{CD}
-            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow 0 
-        \end{CD}
-    \end{align*}
-    and we conclude that $H_{k}(\calT) = 0$ for $1 \leq k \leq n-1$.
-    Finally, the Mayer-Vietoris sequence includes the exact sequences 
-    \begin{align*}
-        \begin{CD}
-            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT \cup T) \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT \cup T) \longrightarrow 0
-        \end{CD}
-    \end{align*}
-    Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT \cup T)$.
-    % We know that  $H_{0}(\calT \cup T) \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
-    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
-    % one easily sees that $H_{0}(\calT \cup T) \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
-    If $\calS$ is isomorphic to disk,
-    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
-    If instead $\calS$ is isomorphic to a sphere, 
-    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
-    % Moreover, Thus $H_{n}(\calT \cup T) = H_{n}(\calT) \oplus H_{n}(\calS)$.
-    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
-    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
-    \begin{align*}
-        \begin{CD}
-            0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT \cup T) \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0
-        \end{CD}
-    \end{align*}
-\end{remark}
-
-A simplicial $n$-dimensional complex $\calT$ is called shellable if its $n$-simplices can be arranged in linear order $T_0, T_1, \dots$ in such a way that the subcomplex $( \cup_{i=0}^{k-1} T_i ) \cap T_k$ has dimension $n-1$ for all $k > 0$.
-
-\bibliographystyle{plain}
-\bibliography{library}
-
-\end{document}

### 2024-05-01 main.tex
Update on Overleaf.

@@
 \usepackage[utf8]{inputenc}
-% \usepackage{fullpage}
+\usepackage{fullpage}
 \input{header}
@@
 
-\maketitle
-
 \begin{abstract}
@@
 \end{abstract}
+
+\maketitle
 
@@
 
-\section{Triangulations and polytopal shellings}
+\section{Basic notions of triangulations and polytopal shellings}
 
@@
 \end{proof}
+
+Given an $n$-dimensional simplicial complex $\calT$, 
+we call $n$-simplices $S,T \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,T=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+Clearly, strongly connected in $\calT$ is an equivalence relation.
+A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, and we call $\calT$ strongly connected if it has only one strongly connected component.
 
@@
 
-Let us assume that $p \in [1,\infty]$ and that $\Omega \subseteq \bbR^{n}$ is an open set. 
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the Poincar\'e--Friedrichs inequality with exponent $p \in [1,\infty]$
+Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
+Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^n$ for the corresponding Lebesgue space of vector fields.
+We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
 if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
@@
     \leq 
-    C_{{\rm PF},\nabla,\Omega,p} 
+    C_{{\rm PF},\Omega,p} 
     \| \bff \|_{L^{p}(\Omega)}
@@
 \end{align}
-We call $C_{{\rm PF},\Omega,p}$ the Poincar\'e--Friedrichs constant. 
-This inequality implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+Equivalently, for all $u \in W^{1,p}(\Omega)$ we have 
+\begin{align}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm PF},\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)}
+    .
+\end{align}
+We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+The main interest in this inequality is that it implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+\\
 
-\begin{remark}
 Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.
-
 Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
@@
 \end{align*}
+% \begin{align*}
+%     \color{Emerald}
+%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p-1} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     +
+%     2^{p-1} 
+%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     .
+% \end{align*}
+Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.
+
+In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
+and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
+This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+We use a generalization of the projection estimate that was studied by Stern~\cite{stern2015banach} to obtain improved estimates for all $L^p$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
 \begin{align*}
-        \color{Emerald}
-        \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+    \| v - v_\Omega \|_{L^{p}(\Omega)}
     \leq 
-        2^{p-1} 
-        \| u \|_{L^{p}(\Omega)}^{p}
-        +
-        2^{p-1} 
-        \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-        \leq 
-        2^{p} 
-        \| u \|_{L^{p}(\Omega)}^{p}
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| v \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| v \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    v \in L^p(\Omega)
     .
 \end{align*}
-    We conclude that the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$. 
-    In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
-    and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
-    \color{red} Question: can we modify the preceding discussion for general $p$ so that this special inequality for $p=2$ emerges as a limit case?
-Then we get stronger results for $p \approx 2$.
-Stern's paper?
-\color{black}
+We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
+The main consequence for us is the estimate 
+$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
+\color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}
 
-    The Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-    The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-    \color{red} Make this last paragraph for concise.
+We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
+Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+
+\begin{remark}
+    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality suits our discussion better than the Poincar\'e inequality. 
+    We want to generalize the discussion to the curl and divergence operators. 
+    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
+    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
+    Hence, it is not clear a priori whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
+    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
+    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
+    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
 \end{remark}
+
+% See the collection at Lemma 3.24
+% https://hal.science/hal-03226049/file/volI_hal.pdf
+
+We now collect examples for Poincar\'e--Friedrich inequalities for important special cases. Over convex bounded domains, it is known~\cite{bebendorf2003note} that 
+\begin{align}
+    \| u - u_{\Omega} \|_{L^{2}(\Omega)}
+    \leq 
+    \frac{d}{\pi}
+    \| \nabla u \|_{L^{2}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,2}(\Omega)
+    .
+\end{align}
+More generally~\cite[Theorem~1]{esposito2013poincare}, when $2 \leq p < \infty$, one can show that 
+\begin{align}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    \frac{d}{\sqrt[p]{\pi_p}}
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where 
+\begin{align}
+    \pi_p
+    :=
+    2\pi \frac{ \sqrt[p]{p-1} }{ p \sin(\pi/p) }
+    .
+\end{align}
+Moreover, we are aware of~\cite{chua2006estimates}, who estimate when $1 < p < \infty$,
+\begin{align}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm CW},p}
+    d
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where, 
+\begin{align}
+    C_{{\rm CW},p} 
+    := 
+    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
+    \frac{ 
+        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
+    }{ 
+        \| \nabla v \|_{L^{p}([0,1])} 
+    }
+    \leq 
+    \sqrt[p]{p} 2^{1-\frac 1 p}
+    .
+\end{align}
+
+% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
+% d/2 in the case $p = 1$ over convex domains
+
+% https://academic.oup.com/plms/article/93/1/197/1462187
+% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?
 
@@
 \begin{theorem}
-    \color{red}Precise form of the inequality yet to be discussed, though the construction is clear.
+    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
 \end{theorem}
@@
 
+% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
+% Lemma 5.5
+
 \section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}

### 2024-05-01 main.tex
update on poincare constants

@@
 Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-\cite{ern2021finite}
 
@@
 
-We now collect examples for Poincar\'e--Friedrich inequalities for important special cases. Over convex bounded domains, it is known~\cite{bebendorf2003note} that 
-\begin{align}
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)}
+We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite{ern2021finite} for a short overview.
+Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that
+\begin{align}\label{math:acostaduran}
+    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
     \leq 
-    \frac{d}{\pi}
+    \frac{\diam(\Omega)}{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,2}(\Omega)
+    ,
+    \\
+    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
+    \leq 
+    \frac{\diam(\Omega)}{\pi}
     \| \nabla u \|_{L^{2}(\Omega)}
@@
 \end{align}
-More generally~\cite[Theorem~1]{esposito2013poincare}, when $2 \leq p < \infty$, one can show that 
-\begin{align}
+These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
+Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
+\begin{align}\label{math:chuawheeden}
     \| u - u_{\Omega} \|_{L^{p}(\Omega)}
     \leq 
-    \frac{d}{\sqrt[p]{\pi_p}}
+    C_{{\rm CW},p}
+    \diam(\Omega)
     \| \nabla u \|_{L^{p}(\Omega)}
@@
 where 
-\begin{align}
-    \pi_p
-    :=
-    2\pi \frac{ \sqrt[p]{p-1} }{ p \sin(\pi/p) }
-    .
-\end{align}
-Moreover, we are aware of~\cite{chua2006estimates}, who estimate when $1 < p < \infty$,
-\begin{align}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm CW},p}
-    d
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where, 
 \begin{align}
@@
     \sqrt[p]{p} 2^{1-\frac 1 p}
+    =
+    2
+    \left( \frac p 2 \right)^{\frac 1 p}
     .
 \end{align}
+In addition to that,
+according to~\cite[Theorem~1]{esposito2013poincare}, when $2 \leq p < \infty$, one can show that 
+\begin{align}\label{math:esposito:pf}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\rm{ENT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where 
+\begin{align}
+    C_{\rm{ENT},p}
+    :=
+    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
+    .
+\end{align}
+The constant $C_{\rm{ENT},p}$ is the best possible. 
+Note that the last inequalities imply, again when $2 \leq p < \infty$, the Poincar\'e inequalities
+\begin{align}\label{math:esposito:poincare}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    2^{1-\frac 2 p}C_{\rm{ENT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}
+The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.
+
+\begin{remark}
+    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
+    We observe 
+    \begin{align*}
+        2^{1-\frac 2 p}
+        C_{\rm{ENT},p}
+        =
+        2 
+        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
+        =
+        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
+        \leq 
+        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
+        \leq 
+        \frac{1}{ 4^{\frac 1 p} }
+        .
+    \end{align*}
+    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden}.
+    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
+    \begin{align*}
+        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
+        \leq 
+        \diam(\Omega)
+        \| \nabla u \|_{L^{\infty}(\Omega)}
+        ,
+        \quad
+        u \in W^{1,\infty}(\Omega)
+        %
+    \end{align*}
+    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
+    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
+%     Taking the \emph{informal} limit also suggest the inequality 
+%     \begin{align*}
+%         \min\limits_{ c \in \bbR }
+%         \| u - c \|_{L^{\infty}(\Omega)}
+%         \leq 
+%         \frac{d}{2}
+%         \| \nabla u \|_{L^{\infty}(\Omega)}
+%         ,
+%         \quad
+%         u \in W^{1,\infty}(\Omega)
+%         ,
+%     \end{align*}
+%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
+\end{remark}
 

### 2024-05-01 main.tex
Update on Overleaf.

@@
 
+\section{Constructive estimate of Poincar\'e constants}
+
+In this section we address the stepwise computable estimate of Poincar\'e constants of triangulated domains.
+As a preparatory step, we survey variations of the Poincar\'e inequality over convex domains.
+These results, the exposition of which we believe to be of value on its own, will serve as a building block in constructing inequalities over triangulated domains.
+
+Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
+Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^n$ for the corresponding Lebesgue space of vector fields.
+We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
+if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
+for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:inequalitypf:gradient}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm PF},\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+Equivalently, for all $u \in W^{1,p}(\Omega)$ we have 
+\begin{align}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm PF},\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)}
+    .
+\end{align}
+We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+The main interest in this inequality is that it implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+\\
+
+Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
+we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
+if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
+for all $u \in W^{1,p}(\Omega)$
+\begin{align}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\varnothing,\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+\end{align}
+where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
+\begin{align*}
+    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
+\end{align*}
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
+Towards a converse inequality, 
+let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align*}
+    \| v_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
+    \leq 
+    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
+    = 
+    \| v \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align*}
+Here, we have used Jensen's inequality. 
+In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
+We therefore combine 
+\begin{align*}
+    \| v - v_\Omega \|_{L^{p}(\Omega)} 
+    \leq
+    2
+    \| v \|_{L^{p}(\Omega)},
+    \quad 
+    v \in L^{p}(\Omega)
+    .
+\end{align*}
+% \begin{align*}
+%     \color{Emerald}
+%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p-1} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     +
+%     2^{p-1} 
+%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     .
+% \end{align*}
+Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.
+
+In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
+and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
+This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+We use a generalization of the projection estimate that was studied by Stern~\cite{stern2015banach} to obtain improved estimates for all $L^p$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+\begin{align*}
+    \| v - v_\Omega \|_{L^{p}(\Omega)}
+    \leq 
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| v \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| v \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    v \in L^p(\Omega)
+    .
+\end{align*}
+We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
+The main consequence for us is the estimate 
+$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
+\color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}
+
+We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
+Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+
+\begin{remark}
+    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality suits our discussion better than the Poincar\'e inequality. 
+    We want to generalize the discussion to the curl and divergence operators. 
+    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
+    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
+    Hence, it is not clear a priori whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
+    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
+    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
+    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
+\end{remark}
+
+\subsection{Poincar\'e inequalities over convex domains}
+% See the collection at Lemma 3.24
+% https://hal.science/hal-03226049/file/volI_hal.pdf
+
+We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview.
+Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that
+\begin{align}\label{math:acostaduran}
+    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
+    \leq 
+    \frac{\diam(\Omega)}{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,2}(\Omega)
+    ,
+    \\
+    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
+    \leq 
+    \frac{\diam(\Omega)}{\pi}
+    \| \nabla u \|_{L^{2}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,2}(\Omega)
+    .
+\end{align}
+These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
+Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
+\begin{align}\label{math:chuawheeden}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm CW},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where 
+\begin{align}
+    C_{{\rm CW},p} 
+    := 
+    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
+    \frac{ 
+        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
+    }{ 
+        \| \nabla v \|_{L^{p}([0,1])} 
+    }
+    \leq 
+    \sqrt[p]{p} 2^{1-\frac 1 p}
+    =
+    2
+    \left( \frac p 2 \right)^{\frac 1 p}
+    .
+\end{align}
+In addition to that,
+according to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
+\begin{align}\label{math:esposito:pf}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\rm{ENT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where 
+\begin{align}
+    C_{\rm{ENT},p}
+    :=
+    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
+    .
+\end{align}
+The constant $C_{\rm{ENT},p}$ is the best possible. 
+Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+\begin{align}\label{math:esposito:poincare}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    2^{1-\frac 2 p}C_{\rm{ENT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}
+The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.
+
+\begin{remark}
+    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
+    We observe 
+    \begin{align*}
+        2^{1-\frac 2 p}
+        C_{\rm{ENT},p}
+        =
+        2 
+        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
+        =
+        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
+        \leq 
+        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
+        \leq 
+        \frac{1}{ 4^{\frac 1 p} }
+        .
+    \end{align*}
+    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $p \geq 2$.
+    In the limit as $p$ goes to $1$, \eqref{math:esposito:poincare} recovers \eqref{math:acostaduran}. 
+    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
+    \begin{align*}
+        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
+        \leq 
+        \diam(\Omega)
+        \| \nabla u \|_{L^{\infty}(\Omega)}
+        ,
+        \quad
+        u \in W^{1,\infty}(\Omega)
+        %
+    \end{align*}
+    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
+    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
+%     Taking the \emph{informal} limit also suggest the inequality 
+%     \begin{align*}
+%         \min\limits_{ c \in \bbR }
+%         \| u - c \|_{L^{\infty}(\Omega)}
+%         \leq 
+%         \frac{d}{2}
+%         \| \nabla u \|_{L^{\infty}(\Omega)}
+%         ,
+%         \quad
+%         u \in W^{1,\infty}(\Omega)
+%         ,
+%     \end{align*}
+%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
+\end{remark}
+
+\begin{align}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    % 2^{ - \frac{p-1}{p}}
+    %2^{ - 1 + \frac{1}{p}}
+    \frac{1}{ 2^{ 1 - \frac{1}{p} } }
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
+% d/2 in the case $p = 1$ over convex domains
+
+% https://academic.oup.com/plms/article/93/1/197/1462187
+% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?
+
+\begin{proof}
+    Given $z \in \Omega$, we define 
+    \[
+        u_z(x) := \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
+    \]
+\end{proof}
+
+\subsection{Poincar\'e inequalities over triangulated domains}
+
+% either proceeding simplex by simplex, matching along faces 
+% or proceeding patch by patch, matching over intersections
+\begin{theorem}
+    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
+\end{theorem}
+
+\begin{proof}
+ Let $u \in W^{1,p}(\Omega)$. 
+ For each $F \in \calT$ of dimension $n-1$, 
+ we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F} \| \nabla u_F \|_{L^{p}(U_F)}$.
+
+ Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j < m$ such that $F_m := T_m \cap T_j$ is a face of dimension $n-1$.
+We write $\Omega_m := \cup_{j=0}^{m} T_m$.
+Hence $\Omega = \Omega_M$.
+
+%  We let $T \in \calT$ be the first $n$-simplex. 
+%  There exists We already have
+
+ Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$.
+Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
+ By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j}$. 
+ Since $\nabla u_{F_{m}|T_j} = \nabla w_{m-1|T_j}$,
+ there exists a constant $c_{m} := w_{m-1|T_j} - u_{F_{m}|T_j}$.
+ We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
+ By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_j} = w_{m-1|T_j}$. 
+ But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
+ As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
+ Moreover, 
+ \begin{gather*}
+    \| u'_{F_m} \|_{L^{p}(T_m)}
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
+    +
+    \| c_{m} \|_{L^{p}(T_m)},
+    \qquad 
+    \| c_{m} \|_{L^{p}(T_m)}
+    \leq 
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| c_{m} \|_{L^{p}(T_j)},
+    \\ 
+    \| c_{m} \|_{L^{p}(T_j)}
+    \leq 
+    \| w_{m-1}\|_{L^{p}(T_j)} + \| u_{F_{m}} \|_{L^{p}(T_j)} 
+    .
+ \end{gather*}
+ In particular,
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| u_{F_{m}} \|_{L^{p}(T_j)}
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_j)}
+    .
+ \end{align*}
+ In the special case $p < \infty$, we also find 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq 
+    3^{p-1}
+    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+    +
+    3^{p-1}
+    \frac{ \vol(T_m) }{ \vol(T_j) }
+    \| u_{F_{m}} \|_{L^{p}(T_j)}^{p}
+    +
+    3^{p-1}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
+    \\&\leq 
+    3^{p-1}
+    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_j) } \right)
+    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
+    +
+    3^{p-1}
+    \frac{ \vol(T_m) }{ \vol(T_j) }
+    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
+    .
+ \end{align*}
+ Recursive application provides the desired result. 
+\end{proof}
+
+\begin{remark}
+    The previous result depends on only a few parameters of the triangulation:
+    the length of any traversal from the root simplex,
+    the ratios of the volumes of adjacent simplices,
+    the Poincar\'e constants on each face patch, and the Poincar\'e constant of the initial simplex. 
+    The aforementioned local Poincar\'e constants can generally be estimated in terms of shape-parameters. 
+    If the face patches of the triangulation are convex, then better estimates are possible. 
+\end{remark}
+
+% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
+% Lemma 5.5
+
+\section{Shellable triangulated domains}
+
 % 2. Develop manifold-like complexes and characterize them 
-\subsection{Triangulations of manifolds}
-
 We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$.
@@
 
-\section{Constructive estimate of $p$-Poincar\'e constants}
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
-Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^n$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm PF},\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Equivalently, for all $u \in W^{1,p}(\Omega)$ we have 
-\begin{align}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm PF},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    .
-\end{align}
-We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The main interest in this inequality is that it implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-\\
-
-Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
-for all $u \in W^{1,p}(\Omega)$
-\begin{align}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\varnothing,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-\end{align}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
-Towards a converse inequality, 
-let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
-    \| v_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
-    \leq 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
-    = 
-    \| v \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-Here, we have used Jensen's inequality. 
-In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
-We therefore combine 
-\begin{align*}
-    \| v - v_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| v \|_{L^{p}(\Omega)},
-    \quad 
-    v \in L^{p}(\Omega)
-    .
-\end{align*}
-% \begin{align*}
-%     \color{Emerald}
-%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p-1} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     +
-%     2^{p-1} 
-%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     .
-% \end{align*}
-Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.
-
-In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
-and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
-This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-We use a generalization of the projection estimate that was studied by Stern~\cite{stern2015banach} to obtain improved estimates for all $L^p$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-\begin{align*}
-    \| v - v_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| v \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| v \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    v \in L^p(\Omega)
-    .
-\end{align*}
-We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
-The main consequence for us is the estimate 
-$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
-\color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}
-
-We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
-Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not clear a priori whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% See the collection at Lemma 3.24
-% https://hal.science/hal-03226049/file/volI_hal.pdf
-
-We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite{ern2021finite} for a short overview.
-Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that
-\begin{align}\label{math:acostaduran}
-    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{\diam(\Omega)}{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,2}(\Omega)
-    ,
-    \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
-    \leq 
-    \frac{\diam(\Omega)}{\pi}
-    \| \nabla u \|_{L^{2}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,2}(\Omega)
-    .
-\end{align}
-These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
-\begin{align}\label{math:chuawheeden}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm CW},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where 
-\begin{align}
-    C_{{\rm CW},p} 
-    := 
-    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
-    \frac{ 
-        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
-    }{ 
-        \| \nabla v \|_{L^{p}([0,1])} 
-    }
-    \leq 
-    \sqrt[p]{p} 2^{1-\frac 1 p}
-    =
-    2
-    \left( \frac p 2 \right)^{\frac 1 p}
-    .
-\end{align}
-In addition to that,
-according to~\cite[Theorem~1]{esposito2013poincare}, when $2 \leq p < \infty$, one can show that 
-\begin{align}\label{math:esposito:pf}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\rm{ENT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where 
-\begin{align}
-    C_{\rm{ENT},p}
-    :=
-    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
-    .
-\end{align}
-The constant $C_{\rm{ENT},p}$ is the best possible. 
-Note that the last inequalities imply, again when $2 \leq p < \infty$, the Poincar\'e inequalities
-\begin{align}\label{math:esposito:poincare}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    2^{1-\frac 2 p}C_{\rm{ENT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.
-
-\begin{remark}
-    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
-    We observe 
-    \begin{align*}
-        2^{1-\frac 2 p}
-        C_{\rm{ENT},p}
-        =
-        2 
-        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
-        =
-        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
-        \leq 
-        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
-        \leq 
-        \frac{1}{ 4^{\frac 1 p} }
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden}.
-    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
-    \begin{align*}
-        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-        \leq 
-        \diam(\Omega)
-        \| \nabla u \|_{L^{\infty}(\Omega)}
-        ,
-        \quad
-        u \in W^{1,\infty}(\Omega)
-        %
-    \end{align*}
-    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
-    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
-%     Taking the \emph{informal} limit also suggest the inequality 
-%     \begin{align*}
-%         \min\limits_{ c \in \bbR }
-%         \| u - c \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \frac{d}{2}
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         u \in W^{1,\infty}(\Omega)
-%         ,
-%     \end{align*}
-%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
-\end{remark}
-
-% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
-% d/2 in the case $p = 1$ over convex domains
-
-% https://academic.oup.com/plms/article/93/1/197/1462187
-% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?
-
-% either proceeding simplex by simplex, matching along faces 
-% or proceeding patch by patch, matching over intersections
-\begin{theorem}
-    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
-\end{theorem}
-
-\begin{proof}
- Let $u \in W^{1,p}(\Omega)$. 
- For each $F \in \calT$ of dimension $n-1$, 
- we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F} \| \nabla u_F \|_{L^{p}(U_F)}$.
-
- Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j < m$ such that $F_m := T_m \cap T_j$ is a face of dimension $n-1$.
-We write $\Omega_m := \cup_{j=0}^{m} T_m$.
-Hence $\Omega = \Omega_M$.
-
-%  We let $T \in \calT$ be the first $n$-simplex. 
-%  There exists We already have
-
- Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$.
-Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
- By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j}$. 
- Since $\nabla u_{F_{m}|T_j} = \nabla w_{m-1|T_j}$,
- there exists a constant $c_{m} := w_{m-1|T_j} - u_{F_{m}|T_j}$.
- We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_j} = w_{m-1|T_j}$. 
- But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
- As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
- Moreover, 
- \begin{gather*}
-    \| u'_{F_m} \|_{L^{p}(T_m)}
-    \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
-    +
-    \| c_{m} \|_{L^{p}(T_m)},
-    \qquad 
-    \| c_{m} \|_{L^{p}(T_m)}
-    \leq 
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| c_{m} \|_{L^{p}(T_j)},
-    \\ 
-    \| c_{m} \|_{L^{p}(T_j)}
-    \leq 
-    \| w_{m-1}\|_{L^{p}(T_j)} + \| u_{F_{m}} \|_{L^{p}(T_j)} 
-    .
- \end{gather*}
- In particular,
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| u_{F_{m}} \|_{L^{p}(T_j)}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_j)}
-    .
- \end{align*}
- In the special case $p < \infty$, we also find 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}^{p}
-    &\leq 
-    3^{p-1}
-    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
-    +
-    3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_j) }
-    \| u_{F_{m}} \|_{L^{p}(T_j)}^{p}
-    +
-    3^{p-1}
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
-    \\&\leq 
-    3^{p-1}
-    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_j) } \right)
-    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
-    +
-    3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_j) }
-    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
-    .
- \end{align*}
- Recursive application provides the desired result. 
-\end{proof}
-
-\begin{remark}
-    The previous result depends on only a few parameters of the triangulation:
-    the length of any traversal from the root simplex,
-    the ratios of the volumes of adjacent simplices,
-    the Poincar\'e constants on each face patch, and the Poincar\'e constant of the initial simplex. 
-    The aforementioned local Poincar\'e constants can generally be estimated in terms of shape-parameters. 
-    If the face patches of the triangulation are convex, then better estimates are possible. 
-\end{remark}
-
-% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
-% Lemma 5.5
-
-\section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}
 % Repeat for H(curl), H(div), and differential forms

### 2024-05-02 main.tex
more updates

@@
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner.
-While shellable complexes are a very special class of complexes, they faciliate achieving the main goal of our exposition.
+While shellable complexes are a very special class of complexes, they facilitate achieving the main goal of our exposition.
 Our main references on simplicial complexes and shellability are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}.
@@
 
-We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview.
+We now collect examples for Poincar\'e--Friedrichs inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview.
 Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that
@@
     \leq 
-    2^{1-\frac 2 p}C_{\rm{ENT},p}
+    2^{|1-\frac 2 p|}C_{\rm{ENT},p}
     \diam(\Omega)
@@
 \begin{remark}
-    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
-    We observe 
+    Let us compare the different estimates for the Poincar\'e inequality.
+    In the case $2 \leq p$, 
     \begin{align*}
@@
         =
-        2 
-        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
+        \frac{ 2^{1-\frac 2 p} }{2}
+        \frac{ \sin(\pi/p) }{ \pi/p }
+        \frac{ 1 }{ \sqrt[p]{p-1} }
         =
-        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
+        4^{-\frac 1 p}
         \leq
-        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
-        \leq 
-        \frac{1}{ 4^{\frac 1 p} }
+        C_{{\rm CW},p} 
         .
     \end{align*}
-    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $p \geq 2$.
+    In the case $2 \geq p$, 
+    \begin{align*}
+        2^{\frac 2 p - 1}
+        C_{\rm{ENT},p}
+        =
+        \frac{ 2^{\frac 2 p - 1} }{2}
+        \frac{ \sin(\pi/p) }{ \pi/p }
+        \frac{ 1 }{ \sqrt[p]{p-1} }
+        \leq
+        \frac{ 2^{\frac 2 p-1} }{2}
+        =
+        2^{\frac 2 p - 2}
+        =
+        4^{\frac 1 p - 1}
+        \leq
+        C_{{\rm CW},p} 
+%         % 
+%         .
+%         4^{\frac 1 p}
+%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
+%         =
+%         4^{\frac 1 p}
+%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
+%         \leq 
+%         \frac 1 2
+        .
+    \end{align*}
+    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
     In the limit as $p$ goes to $1$, \eqref{math:esposito:poincare} recovers \eqref{math:acostaduran}. 
@@
 
+% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
+% d/2 in the case $p = 1$ over convex domains
+
+% https://academic.oup.com/plms/article/93/1/197/1462187
+% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?
+
+\color{Emerald}
 \begin{align}
@@
 \end{align}
-% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
-% d/2 in the case $p = 1$ over convex domains
-
-% https://academic.oup.com/plms/article/93/1/197/1462187
-% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?
 
@@
     \[
-        u_z(x) := \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
+        w(x,z) 
+        := 
+        \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
+        =
+        u(x) - u(z)
+        .
     \]
+    Subsequently,
+    \begin{align*}
+        w(x) = |\Omega|^{-1} \int_{\Omega} w(x,z) dz.
+    \end{align*}
+    Clearly, $\nabla_{x} u(x) = \nabla_{x} w(x,z) = \nabla_{x} w(x)$.
+    Next, 
+    \begin{align*}
+        \int_{\Omega} | w(x) |^{p} dx
+        &\leq 
+        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} | w(x,z) |^{p} dz dx
+        \\&\leq 
+        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} \int_0^1 | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
+        \\&= 
+        |\Omega|^{-1} \int_{\Omega} \int_{\Omega} \int_0^{D/|x-z|} | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
+        .
+    \end{align*}
+
 \end{proof}
+\color{black}
 
@@
 % or proceeding patch by patch, matching over intersections
-\begin{theorem}
+
+\begin{lemma}
+    Let $T_1$ and $T_{2}$ be two $n$-simplices such that $F = T_1 \cap T_2$ is a common subsimplex of dimension $n-1$. Then 
+    \color{red} Here we estimate the Poincar\'e constant over a face patch.
+\end{lemma}
+\begin{proof}
+    \color{red}
+    Possible approaches: 
+    \begin{itemize}
+     \item Take the trace jump (requires trace inequality with explicit constant) and extend the resulting constant function
+     \item The union is star-shaped with respect to some (hopefully large) convex set, then use inequality for that situation (available in literature)
+     \item Reflection trick
+     \item Paper by Veeser and Verfuerth?
+    \end{itemize}
+    Most importantly, all constants must be explicitly computable!
+    We can do all these methods and compare the results. 
+    \color{black}
+    We write $U := T_1 \cup T_2$. Let $u \in W^{1,p}(U)$.
+    Suppose $u_1 \in W^{1,p}(T_1)$ and $u_2 \in W^{1,p}(T_2)$
+    satisfy $\nabla u_1 = \nabla u_{|T_1}$ and $\nabla u_2 = \nabla u_{|T_2}$.
+    Then there exists a constant $c \in \bbR$ such that $c = \trace_{T_1,F} u_1 - \trace_{T_1,F} u_2$.
+    Consequently, if we define 
+    \color{red} yet to be completed.
+\end{proof}
+
+The following result by Veeser and Verfürth~\cite[Lemma 2.8]{veeser} is important in this context.
+
+\begin{lemma}\label{lemma:traceinequality}
+    Let $p \in [1,\infty)$ and let $T$ be an $n$-dimensional simplex with a face $F$. Then 
+    \begin{align*}
+        |F|^{-1} \| u \|_{L^{p}(F)}^{p}
+        \leq 
+        |T|^{-1} \| u \|_{L^{p}(T)}^{p}
+        +
+        p \cdot \diam(T) |T|^{-1} 
+        \| u \|_{L^{p}(T)}^{p-1}
+        \| \nabla u \|_{\bfL^{p}(T)}
+        .
+    \end{align*}
+\end{lemma}
+
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
@@
 
- Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j < m$ such that $F_m := T_m \cap T_j$ is a face of dimension $n-1$.
+ Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
 We write $\Omega_m := \cup_{j=0}^{m} T_m$.
@@
 Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
- By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j}$. 
- Since $\nabla u_{F_{m}|T_j} = \nabla w_{m-1|T_j}$,
- there exists a constant $c_{m} := w_{m-1|T_j} - u_{F_{m}|T_j}$.
+ By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
+ Since $\nabla u_{F_{m}|T_{j(m)}} = \nabla w_{m-1|T_{j(m)}}$,
+ there exists a constant $c_{m} := w_{m-1|T_{j(m)}} - u_{F_{m}|T_{j(m)}}$.
  We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_j} = w_{m-1|T_j}$. 
+ By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_{j(m)}} = w_{m-1|T_{j(m)}}$. 
  But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
@@
     \leq 
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| c_{m} \|_{L^{p}(T_j)},
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+    \| c_{m} \|_{L^{p}(T_{j(m)})},
     \\ 
-    \| c_{m} \|_{L^{p}(T_j)}
+    \| c_{m} \|_{L^{p}(T_{j(m)})}
     \leq 
-    \| w_{m-1}\|_{L^{p}(T_j)} + \| u_{F_{m}} \|_{L^{p}(T_j)} 
+    \| w_{m-1}\|_{L^{p}(T_{j(m)})} + \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
     .
@@
     +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| u_{F_{m}} \|_{L^{p}(T_j)}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}
     +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_j)}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
     .
  \end{align*}
- In the special case $p < \infty$, we also find 
+ In the special case $p=1$,
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    \leq 
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    +
+    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
+    .
+ \end{align*}
+ In the special case $p=\infty$, we get 
+ \begin{align*}
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    \leq 
+    2
+    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+    +
+    \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    .
+ \end{align*}
+ In particular, letting $q$ be the complementary exponent, 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    \leq 
+    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+    \right)^{\frac 1 p}
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
+    .
+ \end{align*}
+
+ \color{red}We want to summarize the Lp norms so that the Poincare inequality over $U_F$ is applied only once.
+In the special cases $p=1$ and $p=\infty$, this works as above.
+Do we have a formula for general $p$ that contains these as limit cases?
+\color{black}
+ In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
  \begin{align*}
@@
     3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_j) }
-    \| u_{F_{m}} \|_{L^{p}(T_j)}^{p}
+    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
     +
     3^{p-1}
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
+    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
     \\&\leq 
     3^{p-1}
-    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_j) } \right)
+    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
     \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
@@
     3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_j) }
-    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
+    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    ,
+ \end{align*}
+ and therefore
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    &\leq 
+    3^{\frac{p-1}{p}}
+    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)^{\frac 1 p}
+    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
+    +
+    3^{\frac{p-1}{p}}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
     .
  \end{align*}
- Recursive application provides the desired result. 
+ \color{blue}
+ In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq 
+    \left( 
+        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
+    \right)^{ p-1 }
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    ,
+ \end{align*}
+ and therefore
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    &\leq 
+    \left( 
+        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
+    \right)^{ \frac{p-1}{p} }
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)} 
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
+    \right)
+    .
+ \end{align*}
+ \color{black}
+ Recursive application provides the following estimate:
+ if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
+ such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
+ then 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    &\leq 
+    \sum_{t=1}^{m} 
+    \left( 
+        \prod_{t < l \leq m} 
+        3^{\frac{p-1}{p}}
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{j(l)})^{\frac 1 p} }
+    \right)
+    \max\left( 1, \frac{ \vol(T_t) }{ \vol(T_{j(t)}) } \right)^{\frac 1 p}
+    \| u_{F_t} \|_{L^{p}(U_{F_t})}
+    \\&\quad \quad \quad 
+    +
+    \left( 
+        \prod_{t < l \leq m} 
+        3^{\frac{p-1}{p}}
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{j(l)})^{\frac 1 p} }
+    \right)
+    \| u_{T_0}\|_{L^{p}(T_{0})}
+    .
+ \end{align*}
+
 \end{proof}
@@
 % Lemma 5.5
+
+\begin{figure}
+\begin{tikzpicture}
+    % Define the vertices of the triangles
+    \coordinate (A) at (0,0);
+    \coordinate (B) at (2,0);
+    \coordinate (C) at (1,1.5);
+    \coordinate (D) at (3,1.5); % Extra vertex for the second triangle
+    \coordinate (E) at (3,2.5); % Extra vertex for the second triangle
+    \coordinate (F) at (4,0.25); % Extra vertex for the second triangle
+    \coordinate (X) at (1,-1.5);
+    \coordinate (Y) at (3,-1.5); % Extra vertex for the second triangle
+
+    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
+    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
+    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
+    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
+    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
+    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
+    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
+
+    % Draw triangles
+    \draw[fill=gray!20] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!30] (B) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!30] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=gray!30] (B) -- (D) -- (F) -- cycle; 
+    \draw[fill=gray!20] (A) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!20] (Y) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!20] (Y) -- (B) -- (F) -- cycle;
+
+    % Draw arrows between triangle centroids
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY);
+
+    % Labels for vertices (optional)
+    \node at (A) [below left] {$A$};
+    \node at (B) [below right] {$B$};
+    \node at (C) [above] {$C$};
+    \node at (D) [above right] {$D$};
+\end{tikzpicture}
+\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+\end{figure}
+
+\newpage
 

### 2024-05-03 draft.tex
Update on Overleaf.

@@
 as can be verified from some simple examples;~see Figure~\ref{figure:annuluscounterexample}.
+
+\color{Emerald}
+\begin{align}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    % 2^{ - \frac{p-1}{p}}
+    %2^{ - 1 + \frac{1}{p}}
+    \frac{1}{ 2^{ 1 - \frac{1}{p} } }
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+
+\begin{proof}
+    Given $z \in \Omega$, we define 
+    \[
+        w(x,z) 
+        := 
+        \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
+        =
+        u(x) - u(z)
+        .
+    \]
+    Subsequently,
+    \begin{align*}
+        w(x) = |\Omega|^{-1} \int_{\Omega} w(x,z) dz.
+    \end{align*}
+    Clearly, $\nabla_{x} u(x) = \nabla_{x} w(x,z) = \nabla_{x} w(x)$.
+    Next, 
+    \begin{align*}
+        \int_{\Omega} | w(x) |^{p} dx
+        &\leq 
+        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} | w(x,z) |^{p} dz dx
+        \\&\leq 
+        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} \int_0^1 | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
+        \\&= 
+        |\Omega|^{-1} \int_{\Omega} \int_{\Omega} \int_0^{D/|x-z|} | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
+        .
+    \end{align*}
+
+\end{proof}
+\color{black}
+
+\begin{lemma}
+    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
+    \begin{align*}
+        \| u - u_{\Omega} \|_{L^p(\Omega)} 
+        &
+        \leq 
+        \frac{2}{((n-1)!)^n }
+        \left( \frac{\diam(T)^n}{\vol(T)} \right)^n
+        \left( \frac{\diam(T')^n}{n! \vol(T')} \right)^n
+        \diam(\Omega)
+        \| \nabla u \|_{L^p(\Omega)} 
+    \end{align*}
+    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty)$.
+\end{lemma}
+\begin{proof}
+    Suppose a tetrahedron $T$ has vertices $v_0,v_1,\dots,v_n$ and let $F_0,F_1\dots,F_n$ be the faces opposite to those vertices. 
+    The height $h(T,k)$ of the vertex $v_k$ in $T$ equals 
+    \[
+        h(T,k) := n \frac{\vol(T)}{\vol(F_k)}
+    \]
+    A lower bound for the height in terms of the volume and diameter of $T$ is 
+    \[
+        h(T,k) 
+        = 
+        n \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        \frac{\diam(T)^n}{\vol(F_k)}
+        \geq 
+        n \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        (n-1)! \frac{\diam(T)^n}{\diam(T)^{n-1}}
+        \geq 
+        \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        n! \diam(T) 
+        .
+    \]
+    Any subsimplex $S$ of $T$ adjacent to $v_k$ thus satisfies 
+    \[
+        \diam(S)
+        \geq 
+        \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        n! \diam(T) 
+        .
+    \]
+    We let $w \in F_0$ be the barycenter in the face opposite to $v_0$. 
+    Then the convex combination of $w$ and any of the faces $F_1,\dots,F_n$ defines simplices $S_1,\dots,S_n$ which satisfy 
+    \[
+        \vol(S_1) = \dots = \vol(S_n) = \frac{\vol(T)}{n}
+        .
+    \]
+    Consequently, 
+    the height $h_k := $ of the vertex $w$ in $S_k$ equals 
+    \[
+        h_k := n \frac{\vol(S_k)}{\vol(F_k)} = \frac{\vol(T)}{\vol(F_k)}
+    \]
+    It follows that $T$ is star-shaped with respect to the intersection of $T$
+    with the ball around $w$ of radius $h$, where $h := \min_{1 \leq k \leq n} h_k$.
+    A lower bound for height in terms of the volume and diameter of $T$ is 
+    \[
+        h_k 
+        = 
+        \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        \frac{\diam(T)^n}{\vol(F_k)}
+        \geq 
+        \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        (n-1)! \frac{\diam(T)^n}{\diam(T)^{n-1}}
+        \geq 
+        \frac{\vol(T)}{\diam(T)^n}
+        \cdot 
+        (n-1)! \diam(T) 
+        .
+    \]
+    Let now $T'$ be another $n$-simplex with vertices $v_0',v_1,\dots,v_n$.
+    We construct $h'$ analogous to above and $h'' := \min(h,h')$. 
+    Hence $\Omega := T \cup T'$ is star-shaped with respect to a ball around $w$ of radius $h''$.
+    Using a result by Farweg and Rosteck,
+    \begin{align*}
+        \| u - u_{\Omega} \|_{L^p(\Omega)} 
+        &
+        \leq 
+        2 \diam(\Omega)^n
+        \omega_n^{ 1 - \frac 1 n }
+        \frac{|\Omega|^{\frac{1}{n}}}{|\Ball(w,h'')|}
+        \| \nabla u \|_{L^p(\Omega)} 
+        \\&
+        \leq 
+        2 \diam(\Omega)^n
+        \omega_n^{ - \frac 1 n }
+        \frac{|\Omega|^{\frac{1}{n}}}{(h'')^n}
+        \| \nabla u \|_{L^p(\Omega)} 
+        .
+    \end{align*}
+    Without loss of generality, $\diam(T) \leq \diam(T')$. Now, 
+    \begin{align*}
+        \| u - u_{\Omega} \|_{L^p(\Omega)} 
+        &
+        \leq 
+        \left( \frac{\diam(T)^n}{\vol(T)} \right)^n
+        2 \diam(\Omega)^n
+        \omega_n^{ - \frac 1 n }
+        \frac{|\Omega|^{\frac{1}{n}}}{((n-1)!)^n \diam(T)^n }
+        \| \nabla u \|_{L^p(\Omega)} 
+        \\&
+        \leq 
+        \frac{2}{((n-1)!)^n }
+        \left( \frac{\diam(T)^n}{\vol(T)} \right)^n
+        \frac{ \diam(T')^n }{ \diam(T)^n }
+        \diam(T')
+        \| \nabla u \|_{L^p(\Omega)} 
+        .
+    \end{align*}
+    We know that 
+    \begin{align*}
+        \diam(T')
+        \leq 
+        \frac{\diam(T')^n}{n! \vol(T')}
+        \diam(F)
+        \leq 
+        \frac{\diam(T')^n}{n! \vol(T')}
+        \diam(T)
+        .
+    \end{align*}
+    The final estimate is
+    \begin{align*}
+        \| u - u_{\Omega} \|_{L^p(\Omega)} 
+        &
+        \leq 
+        \frac{2}{((n-1)!)^n }
+        \left( \frac{\diam(T)^n}{\vol(T)} \right)^n
+        \left( \frac{\diam(T')^n}{n! \vol(T')} \right)^n
+        \diam(\Omega)
+        \| \nabla u \|_{L^p(\Omega)} 
+        .
+    \end{align*}
+    This finishes the proof. 
+\end{proof}
+
+We use the following trace inequality, which can be found in the literature.
+
+\begin{lemma}\label{lemma:traceinequality}
+    Let $p \in [1,\infty)$ and let $T$ be an $n$-dimensional simplex with a face $F$. Then 
+    \begin{align*}
+        \| u \|_{L^{p}(F)}^{p}
+        \leq 
+        \frac{|F|}{|T|} 
+        \| u \|_{L^{p}(T)}^{p}
+        +
+        p \cdot \diam(T) 
+        \frac{|F|}{|T|} 
+        \| u \|_{L^{p}(T)}^{p-1}
+        \| \nabla u \|_{\bfL^{p}(T)}
+        .
+    \end{align*}
+    for all $u \in W^{1,p}(T)$. Moreover, 
+    \begin{align*}
+        \| u \|_{L^{\infty}(F)}
+        \leq 
+        \| u \|_{L^{\infty}(T)}
+        .
+    \end{align*}
+    for all $u \in W^{1,\infty}(T)$. \qed
+\end{lemma}
+
+\begin{remark}
+    Lemma~\cite{veeser2012poincare} has been stated by Veeser and Verfürth~\cite[Lemma 2.8]{veeser2012poincare} when $1 \leq p < \infty$. 
+    The case $p = \infty$ is obvious because functions in $W^{1,\infty}(T)$ are already Lipschitz. 
+    \color{red}\textbf{The following is probably wrong} 
+    However, note that for any $p \in [1,\infty)$ and $u \in W^{1,p}(T)$ we have 
+    \begin{align*}
+        \| u \|_{L^{p}(F)}
+        &\leq 
+        \| u \|_{L^{p}(T)}^{\frac{p-1}{p}}
+        \left(
+            \frac{|F|}{|T|}
+            \| u \|_{L^{p}(T)}
+            +
+            p \cdot \diam(T)
+            \frac{|F|}{|T|}
+            \| \nabla u \|_{\bfL^{p}(T)}
+        \right)^{\frac{1}{p}}
+        \\&\leq 
+        \| u \|_{L^{p}(T)}^{\frac{p-1}{p}}
+        \left( \frac{|F|}{|T|} \right)^{\frac 1 p}
+        \left(
+            \| u \|_{L^{p}(T)}^{\frac{1}{p}}
+            +
+            \sqrt[p]{p} \cdot \diam(T)^{\frac 1 p} 
+            \| \nabla u \|_{\bfL^{p}(T)}^{\frac 1 p} 
+        \right)
+        .
+    \end{align*}
+    The limit as $p$ goes to infinity leads to the inequality as stated in the preceding lemma,
+    which is therefore the natural limit case of the aforementioned trace inequality.
+\end{remark}
+
+\begin{lemma}
+    Let $T_1$ and $T_{2}$ be two $n$-simplices such that $F = T_1 \cap T_2$ is a common subsimplex of dimension $n-1$. Then 
+    \color{red} Here we estimate the Poincar\'e constant over a face patch.
+\end{lemma}
+
+\color{red}
+Possible approaches: 
+\begin{itemize}
+ \item Take the trace jump (requires trace inequality with explicit constant) and extend the resulting constant function
+ \item The union is star-shaped with respect to some (hopefully large) convex set, then use inequality for that situation (available in literature)
+ \item Reflection trick
+ \item Paper by Veeser and Verfuerth?
+\end{itemize}
+Most importantly, all constants must be explicitly computable!
+We can do all these methods and compare the results. 
+\color{black}
+
+\begin{proof}
+    We write $U := T_1 \cup T_2$. Let $u \in W^{1,p}(U)$.
+    Suppose $u_1 \in W^{1,p}(T_1)$ and $u_2 \in W^{1,p}(T_2)$
+    satisfy $\nabla u_1 = \nabla u_{|T_1}$ and $\nabla u_2 = \nabla u_{|T_2}$.
+    Then there exists a constant $c \in \bbR$ such that $c = \trace_{T_1,F} u_1 - \trace_{T_1,F} u_2$.
+    Consequently, if we define $u_2' = u_2 + c$, then we obtain a function $u = u_1 \cup u_2' \in W^{1,p}(T)$. 
+    Notice that 
+    \begin{align*}
+        \| u \|_{L^{p}(U)}^{p}
+        &\leq 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        \| u'_2 \|_{L^{p}(T_2)}^{p}
+        \\
+        &\leq 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        \left( 
+            \| u_2 \|_{L^{p}(T_2)}
+            +
+            \left(\frac{|T_2|}{|F|}\right)^{\frac 1 p}
+            \| c \|_{L^{p}(F)}
+        \right)^{p}
+    \end{align*}
+    \begin{align*}
+        \color{red}
+        \| u'_2 \|_{L^{p}(T_2)}
+        \leq 
+        \| u_2 \|_{L^{p}(T_2)}
+        +
+        \| c \|_{L^{p}(T_2)}
+        = 
+        \| u_2 \|_{L^{p}(T_2)}
+        +
+        \left(\frac{|T_2|}{|F|}\right)^{\frac 1 p}
+        \| c \|_{L^{p}(F)}
+        .
+    \end{align*}
+    Recall that 
+    \begin{align*}
+        \| v \|_{L^{p}(F)}^{p}
+        \leq 
+        \frac{|F|}{|T|} 
+        \| v \|_{L^{p}(T)}^{p}
+        +
+        p \cdot \diam(T) 
+        \frac{|F|}{|T|} 
+        \| v \|_{L^{p}(T)}^{p-1}
+        \| \nabla v \|_{\bfL^{p}(T)}
+        ,
+        \quad 
+        v \in W^{1,p}(T)
+        .
+    \end{align*}
+    Now 
+    \begin{align*}
+        \| c \|_{L^{p}(F)}^{p}
+        &\leq 
+        2^{p-1}
+        \| u_1 \|_{L^{p}(F)}^{p}
+        +
+        2^{p-1}
+        \| u_2 \|_{L^{p}(F)}^{p}
+    \end{align*}
+    We thus proceed with 
+    \begin{align*}
+        \| u_1 \|_{L^{p}(F)}^{p}
+        +
+        \| u_2 \|_{L^{p}(F)}^{p}
+        &
+        \leq 
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        p \cdot \diam(T_1) 
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p-1}
+        \| \nabla u_1 \|_{\bfL^{p}(T_1)}
+        \\&\quad\quad
+        +
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        p \cdot \diam(T_2) 
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{p}(T_2)}^{p-1}
+        \| \nabla u_2 \|_{\bfL^{p}(T_2)}
+    \end{align*}
+    If $p = 1$, then we summarize this as 
+    \begin{align*}
+        \| u \|_{L^{1}(U)} 
+        &\leq 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \| u'_2 \|_{L^{1}(T_2)} 
+        \\
+        &\leq 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \| u_2 \|_{L^{1}(T_2)}
+        +
+        \left(\frac{|T_2|}{|F|}\right)
+        \| c \|_{L^{1}(F)}
+        \\
+        &\leq 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \| u_2 \|_{L^{1}(T_2)}
+        +
+        \left(\frac{|T_2|}{|F|}\right)
+        \| u_1 \|_{L^{1}(F)} 
+        +
+        \left(\frac{|T_2|}{|F|}\right)
+        \| u_2 \|_{L^{1}(F)} 
+        \\
+        &\leq 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \| u_2 \|_{L^{1}(T_2)}
+        \\&\qquad 
+        +
+        \left(\frac{|T_2|}{|F|}\right)
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \diam(T_1) 
+        \left(\frac{|T_2|}{|F|}\right)
+        \frac{|F|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{1}(T_1)}
+        \\&\quad\quad
+        +
+        \left(\frac{|T_2|}{|F|}\right)
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{1}(T_2)} 
+        +
+        \diam(T_2) 
+        \left(\frac{|T_2|}{|F|}\right)
+        \frac{|F|}{|T_2|} 
+        \| \nabla u_2 \|_{\bfL^{1}(T_2)}
+        \\
+        &\leq 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \| u_2 \|_{L^{1}(T_2)}
+        \\&\qquad 
+        +
+        \frac{|T_2|}{|T_1|} 
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        \diam(T_1) 
+        \frac{|T_2|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{1}(T_1)}
+        \\&\quad\quad
+        +
+        \| u_2 \|_{L^{1}(T_2)} 
+        +
+        \diam(T_2) 
+        \| \nabla u_2 \|_{\bfL^{1}(T_2)}
+        \\
+        &\leq 
+        \left( 1 + \frac{|T_2|}{|T_1|} \right)
+        \| u_1 \|_{L^{1}(T_1)} 
+        +
+        2
+        \| u_2 \|_{L^{1}(T_2)}
+        +
+        \diam(T_1) 
+        \frac{|T_2|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{1}(T_1)}
+        +
+        \diam(T_2) 
+        \| \nabla u_2 \|_{\bfL^{1}(T_2)}
+        .
+    \end{align*}
+    When $1 < p < \infty$, then Young's inequality implies 
+    \begin{align*}
+        \| u_1 \|_{L^{p}(F)}^{p}
+        +
+        \| u_2 \|_{L^{p}(F)}^{p}
+        &
+        \leq 
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{q(p-1)}
+        +
+        \frac p q \cdot \diam(T_1)^{p}
+        \frac{|F|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{p}(T_1)}^{p}
+        \\&\quad\quad
+        +
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{p}(T_2)}^{q(p-1)}
+        +
+        \frac p q \cdot \diam(T_2)^{p} 
+        \frac{|F|}{|T_2|} 
+        \| \nabla u_2 \|_{\bfL^{p}(T_2)}^{p}
+        \\
+        &
+        \leq 
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        \frac{|F|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        (p-1) \cdot \diam(T_1)^{p} 
+        \frac{|F|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{p}(T_1)}^{p}
+        \\&\quad\quad
+        +
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        \frac{|F|}{|T_2|} 
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        (p-1) \cdot \diam(T_2)^{p} 
+        \frac{|F|}{|T_2|} 
+        \| \nabla u_2 \|_{\bfL^{p}(T_2)}^{p}
+        .
+    \end{align*}
+    \color{red}The last terms vanish in the limit $p \rightarrow 1$. 
+    It is not clear whether $p=1$ emerges as a limit case: 
+    we have gained an additional $p$-norm of $u$ but applying the Poincare inequality introduces the Poincare constant, 
+    whereas there is no such dependence on the Poincare constant in the case $p=1$ above. 
+    \color{black}
+    In summary, 
+    \begin{align*}
+        2^{1-p}
+        \left(\frac{|T_2|}{|F|}\right)
+        \| c \|_{L^{p}(F)}^{p}
+        &
+        \leq 
+        2
+        \frac{|T_2|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        (p-1) \cdot \diam(T_1)^{p} 
+        \frac{|T_2|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{p}(T_1)}^{p}
+        \\&\quad\quad\quad\quad
+        +
+        2
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        (p-1) \cdot \diam(T_2)^{p} 
+        \| \nabla u_2 \|_{\bfL^{p}(T_2)}^{p}
+        .
+    \end{align*}
+    We thus find 
+    %{\tiny
+    \begin{align*}
+        \| u \|_{L^{p}(U)}^{p}
+        &\leq 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        \| u'_2 \|_{L^{p}(T_2)}^{p}
+        \\
+        &\leq 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        \left( 
+            \| u_2 \|_{L^{p}(T_2)}
+            +
+            \left(\frac{|T_2|}{|F|}\right)^{\frac 1 p}
+            \| c \|_{L^{p}(F)}
+        \right)^{p}
+        \\
+        &\leq 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        2^{p-1}
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        2^{p-1}
+        \left(\frac{|T_2|}{|F|}\right)
+        \| c \|_{L^{p}(F)}^{p}
+        \\
+        % &\leq 
+        % \| u_1 \|_{L^{p}(T_1)}^{p}
+        % +
+        % 2^{p-1}
+        % \| u_2 \|_{L^{p}(T_2)}^{p}
+        % +
+        % 4^{p-1}
+        % \left( 
+        %     2 \max\left( 
+        %         \frac{|T_2|}{|T_1|} 
+        %         ,
+        %         1
+        %     \right)
+        %     \| u_1 \cup u_2 \|_{L^{p}(U)}^{p}
+        %     +
+        %     (p-1) \cdot 
+        %     \max\left( 
+        %         \diam(T_1)^p \frac{|T_2|}{|T_1|} 
+        %         ,
+        %         \diam(T_2)^p 
+        %         %
+        %     \right) 
+        %     \| \nabla u_1 \cup \nabla u_2 \|_{\bfL^{p}(U)}^{p}
+        % \right)
+        % \\
+        &\leq 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        2^{p-1}
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        \\&\quad\quad\quad\quad
+        +
+        4^{p-1}
+        2
+        \frac{|T_2|}{|T_1|} 
+        \| u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        4^{p-1}
+        (p-1) \cdot \diam(T_1)^{p} 
+        \frac{|T_2|}{|T_1|} 
+        \| \nabla u_1 \|_{\bfL^{p}(T_1)}^{p}
+        \\&\quad\quad\quad\quad
+        +
+        4^{p-1}
+        2
+        \| u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        4^{p-1}
+        (p-1) \cdot \diam(T_2)^{p} 
+        \| \nabla u_2 \|_{\bfL^{p}(T_2)}^{p}
+    \end{align*}
+    %}
+    We can now apply the Poincar\'e--Friedrichs inequality over each simplex. Hence,
+    \begin{align*}
+        \| u \|_{L^{p}(U)}^{p}
+        &\leq 
+        C_1 D^{p} \| \nabla u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        2^{p-1}
+        C_2 D^{p} \| \nabla u_2 \|_{L^{p}(T_2)}^{p}
+        \\&\quad\quad\quad\quad
+        +
+        4^{p-1}
+        2
+        Q
+        C_1 D^{p} \| \nabla u_1 \|_{L^{p}(T_1)}^{p}
+        +
+        4^{p-1}
+        (p-1) \cdot D^{p} 
+        Q
+        \| \nabla u_1 \|_{\bfL^{p}(T_1)}^{p}
+        \\&\quad\quad\quad\quad
+        +
+        4^{p-1}
+        2
+        C_2 D^{p} \| \nabla u_2 \|_{L^{p}(T_2)}^{p}
+        +
+        4^{p-1}
+        (p-1) \cdot D^{p} 
+        \| \nabla u_2 \|_{\bfL^{p}(T_2)}^{p}
+        \\
+        &\leq 
+        \left( 
+            C_1 
+            +
+            4^{p-1}
+            2
+            Q
+            C_1 
+            +
+            4^{p-1}
+            (p-1)
+            Q
+        \right) 
+        D^{p}
+        \| \nabla u_1 \|_{L^{p}(T_1)}^{p}
+        \\&\quad\quad\quad\quad
+        +
+        \left( 
+        2^{p-1}
+        C_2 
+        +
+        4^{p-1}
+        2
+        C_2 
+        +
+        4^{p-1}
+        (p-1)
+        \right) 
+        D^{p}
+        \| \nabla u_2 \|_{L^{p}(T_2)}^{p}
+        \\
+        &\leq 
+        \left( 
+            2^{p-1}
+            C  
+            +
+            4^{p-1}
+            2
+            Q'
+            C_1 
+            +
+            4^{p-1}
+            (p-1)
+            Q'
+        \right) 
+        D^{p} 
+        \| \nabla u \|_{L^{p}(U)}^{p}
+        .
+    \end{align*}
+
+    \color{red} Possibly the estimate can be tweaked to obtain nicer constants.
+\end{proof}

### 2024-05-03 main.tex
Update on Overleaf.

@@
 
+We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
+Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
+we search for a constant $C > 0$ such that
+
 % Estimates for Poincare constants 
@@
 % \cite{vohralik2005discrete}
-% \cite{farwig2016note}
 % Verfurth, Veeser & Verfurth 
@@
 As a preparatory step, we survey variations of the Poincar\'e inequality over convex domains.
-These results, the exposition of which we believe to be of value on its own, will serve as a building block in constructing inequalities over triangulated domains.
+These results, the exposition of which we believe to be of value on its own, will serve as a building block in constructing inequalities over local patches and then triangulated domains.
+\\
 
@@
 We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$.
-The main interest in this inequality is that it implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-\\
-
-Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.
+
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature.
 Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
@@
 In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
-We therefore combine 
+It follows that 
 \begin{align*}
@@
 In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
-and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
+and therefore even $C_{\varnothing,\Omega,2} = C_{{\rm PF},\Omega,2}$. 
 This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-We use a generalization of the projection estimate that was studied by Stern~\cite{stern2015banach} to obtain improved estimates for all $L^p$ spaces with $1 \leq p \leq \infty$:
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).\footnote{\color{red}Is there a better name for this than Xu-Zikatanov estimate?}
+Stern~\cite{stern2015banach} provided a generalization of the projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
 since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
@@
 $C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
+We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
 \color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}
 
-We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
-Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
+We define the potential 
+\[
+    \Phi( \bff ) := \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \nabla v = \bff } } \| v \|_{L^{p}(\Omega)},
+    \quad 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\]
+Clearly, 
+\[
+    \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
+\]
+and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
+Consequently, any linear potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
+satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
+\[
+    C_{{\rm PF},\Omega,p} 
+    \leq 
+    \argmin\limits_{ v \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi(\nabla v) \|_{L^p(\Omega)} }{ \| \nabla v \|_{L^p(\Omega)} }
+    .
+\]
+A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
+\[
+    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
+    \quad 
+    u \in W^{1,p}(\Omega)
+    .
+\]
+Its operator norm is just the smallest Poincar\'e constant $C_{\varnothing,\Omega,p}$.
+
+In the light of these musings, we can clarify that our objective is the construction of linear potential operators for the gradient and later for the curl and divergence operators. 
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+The potential reconstruction is the natural approach towards the topic when addressing the curl and divergence operators.
 
@@
 \end{remark}
+
+% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
 
@@
     \leq 
-    C_{\rm{ENT},p}
+    C_{\rm{EFNT},p}
     \diam(\Omega)
@@
 \begin{align}
-    C_{\rm{ENT},p}
+    C_{\rm{EFNT},p}
     :=
@@
 \end{align}
-The constant $C_{\rm{ENT},p}$ is the best possible. 
+The constant $C_{\rm{EFNT},p}$ is the best possible. 
 Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
@@
     \leq 
-    2^{|1-\frac 2 p|}C_{\rm{ENT},p}
+    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
     \diam(\Omega)
@@
 The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
+Finally,
+since convex domains are Lipschitz domains, we may estimate 
+\begin{align}\label{math:lipschitzestimate}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{\infty}(\Omega)}
+    \leq 
+    \diam(\Omega)
+    \| \nabla u \|_{L^{\infty}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,\infty}(\Omega)
+    .
+\end{align}
 
@@
         2^{1-\frac 2 p}
-        C_{\rm{ENT},p}
+        C_{\rm{EFNT},p}
         =
@@
         2^{\frac 2 p - 1}
-        C_{\rm{ENT},p}
+        C_{\rm{EFNT},p}
         =
@@
     Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
+    Notably, it is much less clear whether \eqref{math:esposito:pf} implies a limit case for Lipschitz functions. 
 %     Taking the \emph{informal} limit also suggest the inequality 
@@
 
-\color{Emerald}
-\begin{align}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    % 2^{ - \frac{p-1}{p}}
-    %2^{ - 1 + \frac{1}{p}}
-    \frac{1}{ 2^{ 1 - \frac{1}{p} } }
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-
-\begin{proof}
-    Given $z \in \Omega$, we define 
+\subsection{Poincar\'e inequalities over triangulated domains}
+
+Given a gradient vector field, we can reconstructed the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
+This defines a scalar potential.
+This shall be our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials. 
+After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
+This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being contructed so far.
+Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion.
+
+We have already seen a survey of Poincar\'e inequalities over convex domains. 
+Slightly more generally, we are interested in such inequalities over face patches within simplicial triangulations. 
+We state a geometric auxiliary lemma and an estimate of Poincar\'e--Friedrichs constants over face patches 
+that captures the correct asymptotic behavior as $p$ grows to infinity.
+
+\begin{lemma}\label{lemma:volumecomparison}
+    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
     \[
-        w(x,z) 
-        := 
-        \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
-        =
-        u(x) - u(z)
+        \frac{ \vol(T_1) }{ \vol(T_2) }
+        \leq 
+        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
+        \cdot 
+        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
         .
     \]
-    Subsequently,
-    \begin{align*}
-        w(x) = |\Omega|^{-1} \int_{\Omega} w(x,z) dz.
-    \end{align*}
-    Clearly, $\nabla_{x} u(x) = \nabla_{x} w(x,z) = \nabla_{x} w(x)$.
-    Next, 
-    \begin{align*}
-        \int_{\Omega} | w(x) |^{p} dx
-        &\leq 
-        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} | w(x,z) |^{p} dz dx
-        \\&\leq 
-        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} \int_0^1 | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
-        \\&= 
-        |\Omega|^{-1} \int_{\Omega} \int_{\Omega} \int_0^{D/|x-z|} | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
-        .
-    \end{align*}
-
-\end{proof}
-\color{black}
-
-\subsection{Poincar\'e inequalities over triangulated domains}
-
-% either proceeding simplex by simplex, matching along faces 
-% or proceeding patch by patch, matching over intersections
-
-\begin{lemma}
-    Let $T_1$ and $T_{2}$ be two $n$-simplices such that $F = T_1 \cap T_2$ is a common subsimplex of dimension $n-1$. Then 
-    \color{red} Here we estimate the Poincar\'e constant over a face patch.
 \end{lemma}
 \begin{proof}
-    \color{red}
-    Possible approaches: 
-    \begin{itemize}
-     \item Take the trace jump (requires trace inequality with explicit constant) and extend the resulting constant function
-     \item The union is star-shaped with respect to some (hopefully large) convex set, then use inequality for that situation (available in literature)
-     \item Reflection trick
-     \item Paper by Veeser and Verfuerth?
-    \end{itemize}
-    Most importantly, all constants must be explicitly computable!
-    We can do all these methods and compare the results. 
-    \color{black}
-    We write $U := T_1 \cup T_2$. Let $u \in W^{1,p}(U)$.
-    Suppose $u_1 \in W^{1,p}(T_1)$ and $u_2 \in W^{1,p}(T_2)$
-    satisfy $\nabla u_1 = \nabla u_{|T_1}$ and $\nabla u_2 = \nabla u_{|T_2}$.
-    Then there exists a constant $c \in \bbR$ such that $c = \trace_{T_1,F} u_1 - \trace_{T_1,F} u_2$.
-    Consequently, if we define 
-    \color{red} yet to be completed.
+    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
+    Then $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
+    We estimate 
+    \begin{align*}
+        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
+        \\
+        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
+        .
+    \end{align*}
+    The desired estimate follows. 
+    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
+    % \begin{align*}
+    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
+    %     \leq 
+    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
+    %     \cdot 
+    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
+    %     .
+    % \end{align*}
 \end{proof}
 
-The following result by Veeser and Verfürth~\cite[Lemma 2.8]{veeser} is important in this context.
-
-\begin{lemma}\label{lemma:traceinequality}
-    Let $p \in [1,\infty)$ and let $T$ be an $n$-dimensional simplex with a face $F$. Then 
-    \begin{align*}
-        |F|^{-1} \| u \|_{L^{p}(F)}^{p}
-        \leq 
-        |T|^{-1} \| u \|_{L^{p}(T)}^{p}
+\begin{remark}
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}. 
+    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
+    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
+    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
+    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
+    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
+\end{remark}
+
+\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
+    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
+    \begin{align*}
+        \min\limits_{ c \in \bbR }
+        \| u - c \|_{L^{p}(U)}
+        &
+        \leq 
+        2 C_{\rm{EFNT},p}
+        \max\left( 
+            \frac{ \vol(T_1) }{ \vol(T_2) }
+            ,
+            \frac{ \vol(T_2) }{ \vol(T_1) }
+        \right)^{\frac 1 p}
+        \max\left( \diam(T_1), \diam(T_2) \right)
+        \| \nabla u \|_{L^{p}(U)}
+        \\&
+        \leq 
+        2 C_{\rm{EFNT},p}
+        \left( 
+            \frac{\diam(T_1)^n}{n! \vol(T_1)} 
+            \frac{\diam(T_2)^n}{n! \vol(T_2)} 
+        \right)^{\frac 1 p}
+        \max\left( \diam(T_1), \diam(T_2) \right)
+        \| \nabla u \|_{L^{p}(U)}
+        .
+    \end{align*}
+    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
+\end{lemma}
+
+\begin{proof}
+    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
+    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
+    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
+    We fix affine homeomorphisms $\Phi_1 : \hat T_1 \rightarrow T_1$ and $\Phi_2 : \hat T_2 \rightarrow T_2$
+    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
+    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.
+
+    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \Phi \in W^{1,p}(\hat U)$. 
+    We observe 
+    \begin{align*}
+        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
+        &=
+        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
         +
-        p \cdot \diam(T) |T|^{-1} 
-        \| u \|_{L^{p}(T)}^{p-1}
-        \| \nabla u \|_{\bfL^{p}(T)}
-        .
-    \end{align*}
-\end{lemma}
+        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
+        \\&
+        \leq 
+        |\det(\Dif \Phi_1)|
+        \cdot \| \Dif \Phi_1 \|^{p}
+        \cdot 
+        \| \nabla u \|_{L^{p}(T_1)}^{p}
+        +
+        |\det(\Dif \Phi_2)|
+        \cdot \| \Dif \Phi_2 \|^{p}
+        \cdot 
+        \| \nabla u \|_{L^{p}(T_2)}^{p}
+        \\&
+        \leq 
+        \max\left( 
+            |\det(\Dif \Phi_1)|^{-1} \cdot \| \Dif \Phi_1 \|^{p}
+            ,
+            |\det(\Dif \Phi_2)|^{-1} \cdot \| \Dif \Phi_2 \|^{p}
+        \right)
+        \| \nabla u \|_{L^{p}(U)}^{p}
+        .
+    \end{align*}
+    Hence 
+    \begin{align*}
+        \| \nabla \hat u \|_{L^{p}(\hat U)}
+        &\leq 
+        \max\left( 
+            |\det(\Dif \Phi_1)|^{-\frac 1 p} \cdot \| \Dif \Phi_1 \|
+            ,
+            |\det(\Dif \Phi_2)|^{-\frac 1 p} \cdot \| \Dif \Phi_2 \|
+        \right)
+        \| \nabla u \|_{L^{p}(U)}
+        .
+    \end{align*}
+    There exists $\hat w \in W^{1,p}(U)$ such that $\nabla \hat w = \nabla \hat u$ and 
+    \begin{align*}
+        \| \hat w \|_{L^{p}(\hat U)}
+        \leq 
+        2 C_{\rm{EFNT},p}
+        \| \nabla \hat u \|_{L^{p}(\hat U)}
+        .
+    \end{align*}
+    Next, setting $w = \hat w \circ \Phi^{-1}$, we find $\nabla w = \nabla u$ and 
+    \begin{align*}
+        \| w \|_{L^{p}(U)}
+        \leq 
+        \max\left( 
+            |\det(\Dif \Phi_1)|
+            ,
+            |\det(\Dif \Phi_2)|
+        \right)^{\frac 1 p}
+        \| \hat w \|_{L^{p}(\hat U)}
+        .
+    \end{align*}
+    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
+    \begin{align*}
+        \| w \|_{L^{p}(U)}
+        &\leq 
+        2 C_{\rm{EFNT},p}
+        \max\left( 
+            |\det(\Dif \Phi_1)|
+            ,
+            |\det(\Dif \Phi_2)|
+        \right)^{\frac 1 p}
+        \max\left( 
+            |\det(\Dif \Phi_1)|^{-\frac 1 p} 
+            ,
+            |\det(\Dif \Phi_2)|^{-\frac 1 p} 
+        \right)
+        D
+        \| \nabla u \|_{L^{p}(U)}
+        \\&
+        \leq 
+        2 C_{\rm{EFNT},p}
+        \max\left( 
+            |\det(\Dif \Phi_1)|
+            ,
+            |\det(\Dif \Phi_2)|
+        \right)^{\frac 1 p}
+        \min\left( 
+            |\det(\Dif \Phi_1)|
+            ,
+            |\det(\Dif \Phi_2)| 
+        \right)^{-\frac 1 p} 
+        D
+        \| \nabla u \|_{L^{p}(U)}
+        \\&
+        \leq 
+        2 C_{\rm{EFNT},p}
+        \max\left( 
+            \frac{ |\det(\Dif \Phi_1)| }{ |\det(\Dif \Phi_2)| }
+            ,
+            \frac{ |\det(\Dif \Phi_2)| }{ |\det(\Dif \Phi_1)| }
+        \right)^{\frac 1 p}
+        D
+        \| \nabla u \|_{L^{p}(U)}
+        \\&
+        \leq 
+        2 C_{\rm{EFNT},p}
+        \max\left( 
+            \frac{ \vol(T_1) }{ \vol(T_2) }
+            ,
+            \frac{ \vol(T_2) }{ \vol(T_1) }
+        \right)^{\frac 1 p}
+        D
+        \| \nabla u \|_{L^{p}(U)}
+        .
+    \end{align*}
+    This gives the desired result.
+
+\end{proof}
+
+\begin{figure}[t]
+\begin{tikzpicture}
+    % Define the vertices of the triangles
+    \coordinate (A) at (0,0);
+    \coordinate (B) at (2,0);
+    \coordinate (C) at (1,1.5);
+    \coordinate (D) at (3,1.5); % Extra vertex for the second triangle
+    \coordinate (E) at (3,2.5); % Extra vertex for the second triangle
+    \coordinate (F) at (4,0.25); % Extra vertex for the second triangle
+    \coordinate (X) at (1,-1.5);
+    \coordinate (Y) at (3,-1.5); % Extra vertex for the second triangle
+
+    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
+    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
+    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
+    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
+    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
+    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
+    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
+
+    % Draw triangles
+    \draw[fill=gray!20] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!30] (B) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!30] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=gray!30] (B) -- (D) -- (F) -- cycle; 
+    \draw[fill=gray!20] (A) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!20] (Y) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!20] (Y) -- (B) -- (F) -- cycle;
+
+    % Draw arrows between triangle centroids
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY);
+
+    % Labels for vertices (optional)
+    \node at (A) [below left] {$A$};
+    \node at (B) [below right] {$B$};
+    \node at (C) [above] {$C$};
+    \node at (D) [above right] {$D$};
+\end{tikzpicture}
+\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+\end{figure}
 
@@
  \end{align*}
+ We want to summarize the two integrals of $u_{F_m}$. 
  In the special case $p=1$,
@@
  \end{align*}
- In the special case $p=\infty$, we get 
+ In the special case $p=\infty$, 
  \begin{align*}
@@
  \end{align*}
- In particular, letting $q$ be the complementary exponent, 
+ When $1 < p < \infty$, letting $q$ be the complementary exponent, we observe 
  \begin{align*}
     \| w_{m} \|_{L^{p}(T_m)}
-    \leq 
+    &\leq 
     \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
@@
     \| w_{m-1}\|_{L^{p}(T_{j(m)})}
-    .
- \end{align*}
-
- \color{red}We want to summarize the Lp norms so that the Poincare inequality over $U_F$ is applied only once.
-In the special cases $p=1$ and $p=\infty$, this works as above.
-Do we have a formula for general $p$ that contains these as limit cases?
-\color{black}
- In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}^{p}
-    &\leq 
-    3^{p-1}
-    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
-    +
-    3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
-    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
-    +
-    3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
-    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
     \\&\leq 
-    3^{p-1}
-    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
-    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
-    +
-    3^{p-1}
-    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
-    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
-    ,
- \end{align*}
- and therefore
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &\leq 
-    3^{\frac{p-1}{p}}
-    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)^{\frac 1 p}
+    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
     \| u_{F_m} \|_{L^{p}(U_{F_m})} 
     +
-    3^{\frac{p-1}{p}}
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
@@
  \end{align*}
- \color{blue}
- In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}^{p}
-    &\leq 
-    \left( 
-        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
-    \right)^{ p-1 }
-    \left( 
-        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
-        +
-        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
-        +
-        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
-    \right)
-    ,
- \end{align*}
- and therefore
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &\leq 
-    \left( 
-        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
-    \right)^{ \frac{p-1}{p} }
-    \left( 
-        \| u_{F_m} \|_{L^{p}(T_m)} 
-        +
-        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
-        +
-        \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
-    \right)
-    .
- \end{align*}
- \color{black}
  Recursive application provides the following estimate:
@@
         \prod_{t < l \leq m} 
-        3^{\frac{p-1}{p}}
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{j(l)})^{\frac 1 p} }
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
     \right)
-    \max\left( 1, \frac{ \vol(T_t) }{ \vol(T_{j(t)}) } \right)^{\frac 1 p}
+    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
     \| u_{F_t} \|_{L^{p}(U_{F_t})}
@@
     \left( 
-        \prod_{t < l \leq m} 
-        3^{\frac{p-1}{p}}
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{j(l)})^{\frac 1 p} }
+        \prod_{0 < l \leq m} 
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
     \right)
@@
  \end{align*}
-
+ %  
+ % \color{red}We want to summarize the Lp norms so that the Poincare inequality over $U_F$ is applied only once.
+In the special cases $p=1$ and $p=\infty$, this works as above.
+Do we have a formula for general $p$ that contains these as limit cases?
+\color{black}
+ % In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}^{p}
+ %    &\leq 
+ %    3^{p-1}
+ %    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+ %    +
+ %    3^{p-1}
+ %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+ %    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+ %    +
+ %    3^{p-1}
+ %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+ %    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+ %    \\&\leq 
+ %    3^{p-1}
+ %    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+ %    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
+ %    +
+ %    3^{p-1}
+ %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+ %    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+ %    ,
+ % \end{align*}
+ % and therefore
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}
+ %    &\leq 
+ %    3^{\frac{p-1}{p}}
+ %    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)^{\frac 1 p}
+ %    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
+ %    +
+ %    3^{\frac{p-1}{p}}
+ %    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+ %    \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
+ %    .
+ % \end{align*}
+ % \color{blue}
+ % In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}^{p}
+ %    &\leq 
+ %    \left( 
+ %        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
+ %    \right)^{ p-1 }
+ %    \left( 
+ %        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+ %        +
+ %        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+ %        +
+ %        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+ %    \right)
+ %    ,
+ % \end{align*}
+ % and therefore
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}
+ %    &\leq 
+ %    \left( 
+ %        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
+ %    \right)^{ \frac{p-1}{p} }
+ %    \left( 
+ %        \| u_{F_m} \|_{L^{p}(T_m)} 
+ %        +
+ %        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
+ %        +
+ %        \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
+ %    \right)
+ %    .
+ % \end{align*}
+ % \color{black}
 \end{proof}
@@
 % Lemma 5.5
-
-\begin{figure}
-\begin{tikzpicture}
-    % Define the vertices of the triangles
-    \coordinate (A) at (0,0);
-    \coordinate (B) at (2,0);
-    \coordinate (C) at (1,1.5);
-    \coordinate (D) at (3,1.5); % Extra vertex for the second triangle
-    \coordinate (E) at (3,2.5); % Extra vertex for the second triangle
-    \coordinate (F) at (4,0.25); % Extra vertex for the second triangle
-    \coordinate (X) at (1,-1.5);
-    \coordinate (Y) at (3,-1.5); % Extra vertex for the second triangle
-
-    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
-    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
-    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
-    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
-    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
-
-    % Draw triangles
-    \draw[fill=gray!20] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!30] (B) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!30] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!30] (B) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!20] (A) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!20] (Y) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!20] (Y) -- (B) -- (F) -- cycle;
-
-    % Draw arrows between triangle centroids
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY);
-
-    % Labels for vertices (optional)
-    \node at (A) [below left] {$A$};
-    \node at (B) [below right] {$B$};
-    \node at (C) [above] {$C$};
-    \node at (D) [above right] {$D$};
-\end{tikzpicture}
-\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-\end{figure}
 
@@
 (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
-(2) The new edge patch already be a subset of the subtriangulation (3) An inadmissible choice because new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like (4) An inadmissible choice because new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
+(2) The new edge patch may already be a subset of the subtriangulation (3) An inadmissible choice because new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like (4) An inadmissible choice because new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
 \end{figure}

### 2024-05-03 main.tex
add makefile; extensions and polishment

@@
     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    These include the Poincar\'e, Maxwell, and Friedrichs constants as special cases. 
-    The main application that we envision concern computable estimates over finite element patches. 
+    These includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
+    The main application that we envision are computable estimates over finite element patches. 
 \end{abstract}
@@
 
-% introductory paragraph
-
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
-Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
-we search for a constant $C > 0$ such that
-
-% Estimates for Poincare constants 
-% \cite{bebendorf2003note}
-% \cite{vohralik2005discrete}
-% Verfurth, Veeser & Verfurth 
-% ...
-
-% Estimates for Friedrichs constants (if any)
-
-% Estimates for Maxwell constants (if any)
+{\color{red}This introduction is a very rough draft, including snippets}
+
+We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains.
+The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry.
+In particular, this yields computable upper bounds for Poincar\'e--Friedrichs inequalities. 
+For example, if $\bff \in \bfL^{p}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
+we want to bound the $L^p$ norm of the potential
+\begin{align*}
+    \argmin\limits_{ \substack{ \bfv \in \bfL^{p}(\curl) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\curl}
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
+We address this topic in the special case where $\Omega$ admits a shellable triangulation.
+While this constraints us to the class of {\color{red}contractible} domains, 
+having computable upper bounds for such domains is an important step stone towards the more general case. 
+For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.
 
@@
 for which some finite element patches are not star-shaped with respect to any ball.
+
+We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
+Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
+we search for a constant $C > 0$ such that 
+\begin{align*}
+    \min\limits_{c\in\bbR}
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad} \| \nabla u \|_{L^p(\Omega)},
+    \quad 
+    u \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*}
+Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
+The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
+Even though the existence of such a bounded linear potential construction is not evident a priori, 
+picking the average-free potential 
+\begin{align*}
+    \Phi_{\grad}( \bff ) 
+    := 
+    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
+    \quad 
+    \bff \in \nabla W^{1,p}(\Omega)
+\end{align*}
+is known to be a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
+\begin{align*}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_\Omega$ denotes the average of $u$.
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities. 
+The optimal values for all $1 \leq p < \infty$ are known when the domain is convex.
+
+The situation is less clear cut when we try to find try the curl or divergence operators
+\begin{align*}
+    \curl : \bfW^{p}(\curl) \rightarrow \bfL^{p}(\curl),
+    \quad 
+    \divergence : \bfW^{p}(\divergence) \rightarrow L^{p}(\curl),
+\end{align*}
+where we use the function spaces
+\begin{align*}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
+    .
+\end{align*}
+The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
+The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. 
+In the Banach space case, it is not immediately evident the kernels of these operators are complemented.
+We are interested in constants for inequalities such as 
+\begin{align*}
+    \argmin\limits_{ \substack{ v \in W^{p}(\curl) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)},
+    \leq 
+    C_{\curl}
+    \| \bff \|_{L^{p}(\Omega)}
+    \\
+    \argmin\limits_{ \substack{ v \in W^{p}(\divergence) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)},
+    \leq 
+    C_{\divergence}
+    \| f \|_{L^{p}(\Omega)}
+    ,
+\end{align*}
+and whether these constants can be estimated by the operator norm of linear potential operators 
+\begin{align*}
+    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
+    \quad 
+    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega).
+\end{align*}
+We notice that not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs for the curl and divergence operators, even if the domain is convex, which is in sharp contrast to the study of the gradient operator.
+In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
+\\
+
+The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence satisfying explicitly computable upper bounds.
+This is achieved for a special class of triangulated domains,
+namely domains with so-called \emph{shellable} triangulations. 
+Formally, a simplicial complex is shellable if its full-dimensional simplices can be ordered in a sequence such that each such simplex in the sequence intersects the union of the previously listed simplices in a codimension one simplicial complex in the boundary of the new facet being added.
+Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
+by successively glueing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
+the gluing interface is a triangulated submanifold of the boundary. 
+This forces the intermediate triangulations to be particularly well-shaped.
+
+\color{red}Do Ern and Guermond construct a potential for the gradient over triangulations? What exactly is their approach\color{black}
+\nocite{gross2004electromagnetic,hiptmair2002finite}
+
+As a necessary subcomponent, we need to apply local Poincar\'e inequalities to select potentials. 
+Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients. 
+We construct gradient potentials locally over convex domains or face patches. 
+We can access a considerable body of literature for gradient Poincar\'e inequalities over convex domains~\cite{bebendorf2003note}.
+In fact, optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known over convex domains.
+
+By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
+The literature is much scarcer when it comes to this. 
+We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
+By duality, that implies lower bounds for the case of full boundary conditions.
+We remark that their work also shows that over convex domains in 3D:
+\begin{align*}
+    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
+\end{align*}
+But we need to find potentials over a simplex subject to partial boundary conditions 
+and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
+The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
+Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
+has no estimates in the literature.
+
+We fix this problem in two steps. 
+First, we construct an auxiliary problem subject to full boundary conditions.
+Second, we develop explicit estimates for the regularized Bogovski operator.
+
+% Estimates for Poincare constants 
+% \cite{bebendorf2003note}
+% \cite{vohralik2005discrete}
+% Verfurth, Veeser & Verfurth 
+% ...
+
+% Estimates for divergence constants (if any)
+
+% Estimates for curl constants (if any)
+
+\color{blue}
+
+The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
+Furthermore, their constants enter the stability and convergence theory of finite element methods.
+Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
+\\
+
 \color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
+\\
 
@@
 In particular, this enables the inductive method of proof.
+\\
 
@@
 
-\section{Basic notions of triangulations and polytopal shellings}
+\begin{remark}
+    The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
+    Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
+    In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
+    It also enters the a~priori error analysis. 
+\end{remark}
+
+\begin{remark}
+ For reference, how the extension should work:
+ suppose that $u \in H(\Omega)$ and let $f = du$.
+ Suppose we have $u_1 \in H(T_1)$ with $du_1 = du$ over $T_1$. 
+ We built $u'_2 \in H(T_2)$ such that 
+ \begin{align*}
+    \trace_F u_1 = \trace_F u'_2
+ \end{align*}
+ We let $u''_2 \in H(T_2)$ such that 
+ \begin{align*}
+    d u''_2 = f - d u'_2, \quad \trace_F u''_2 = 0
+ \end{align*}
+ Such $u''_2$ exists because 
+ \begin{align*}
+  \trace_F( f_2 - d u'_2 ) 
+  &= 
+  \trace_F f_1 - \trace_F d u'_2
+  \\&= 
+  \trace_F f_1 - \trace_F d u'_2
+  \\&= 
+  \trace_F d u_1 - \trace_F d u'_2
+  \\&= 
+  d \trace_F u_1 - d \trace_F u'_2
+  \\&= 
+  d \trace_F u_1 - d \trace_F u_1
+  = 0
+  .
+ \end{align*}
+ Setting $u_2 = u'_2 + u''_2$, we find 
+ \begin{align*}
+    d u_2 = d u'_2 + d u''_2 = d u'_2 + f - d u'_2 = f,
+    \\
+    \trace_F u_2 = \trace_F u'_2 = \trace_F u_1.
+ \end{align*}
+ That requires an extension from given partial boundary data. 
+ Possible approaches:
+ \begin{itemize}
+  \item Reflect a neighborhood and multiply with cut-off function.
+  \item Take traces from patch and extend onto new simplex. 
+ \end{itemize}
+
+\end{remark}
+
+\section{Basic notions of triangulations}
 
@@
 Our main references on simplicial complexes and shellability are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}.
-
-% 1. Develop some notation
 
@@
 We define the potential 
-\[
+\begin{align*}
     \Phi( \bff ) := \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \nabla v = \bff } } \| v \|_{L^{p}(\Omega)},
@@
     .
-\]
+\end{align*}
 Clearly, 
-\[
+\begin{align*}
     \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
-\]
+\end{align*}
 and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
@@
 satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\[
+\begin{align*}
     C_{{\rm PF},\Omega,p} 
@@
     .
-\]
+\end{align*}
 A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
-\[
+\begin{align*}
     \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
@@
     .
-\]
+\end{align*}
 Its operator norm is just the smallest Poincar\'e constant $C_{\varnothing,\Omega,p}$.
@@
 \subsection{Poincar\'e inequalities over convex domains}
-% See the collection at Lemma 3.24
-% https://hal.science/hal-03226049/file/volI_hal.pdf
+% See the collection at Lemma 3.24 : https://hal.science/hal-03226049/file/volI_hal.pdf
 
@@
 After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being contructed so far.
+This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed so far.
 Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion.
@@
     Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \[
+    \begin{align*}
         \frac{ \vol(T_1) }{ \vol(T_2) }
@@
         .
-    \]
+    \end{align*}
 \end{lemma}
@@
 \begin{tikzpicture}
-    % Define the vertices of the triangles
     \coordinate (A) at (0,0);
@@
     \coordinate (C) at (1,1.5);
-    \coordinate (D) at (3,1.5); % Extra vertex for the second triangle
-    \coordinate (E) at (3,2.5); % Extra vertex for the second triangle
-    \coordinate (F) at (4,0.25); % Extra vertex for the second triangle
+    \coordinate (D) at (3,1.5); 
+    \coordinate (E) at (3,3); 
+    \coordinate (F) at (4,0.25); 
     \coordinate (X) at (1,-1.5);
-    \coordinate (Y) at (3,-1.5); % Extra vertex for the second triangle
+    \coordinate (Y) at (3,-1.5); 
+    \coordinate (T) at (5,2);
 
@@
     \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
-
-    % Draw triangles
-    \draw[fill=gray!20] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!30] (B) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!30] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!30] (B) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!20] (A) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!20] (Y) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!20] (Y) -- (B) -- (F) -- cycle;
-
-    % Draw arrows between triangle centroids
+    \coordinate (CentroidDFT) at ($(D)!0.3333!(F)!0.3333!(T)$);
+    \coordinate (CentroidDET) at ($(D)!0.3333!(E)!0.3333!(T)$);
+
+    \draw[fill=gray!10] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!10] (B) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!10] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=gray!10] (B) -- (D) -- (F) -- cycle; 
+    \draw[fill=gray!10] (A) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!10] (Y) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!10] (Y) -- (B) -- (F) -- cycle; 
+    \draw[fill=gray!10] (T) -- (D) -- (F) -- cycle; 
+    \draw[fill=gray!10] (T) -- (D) -- (E) -- cycle;
+
     \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
@@
     \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
-
-    % Labels for vertices (optional)
-    \node at (A) [below left] {$A$};
-    \node at (B) [below right] {$B$};
-    \node at (C) [above] {$C$};
-    \node at (D) [above right] {$D$};
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
+    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET);
+
+%     \node at (A) [below left] {$A$};
+%     \node at (B) [below right] {$B$};
+%     \node at (C) [above] {$C$};
+%     \node at (D) [above right] {$D$};
+%     \node at (T) [above right] {$T$};
 \end{tikzpicture}
@@
     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
+    For any $u \in W^{1,p}(\Omega)$ there exists $w \in W^{1,p}(\Omega)$
+    with $\nabla u = \nabla w$ and such that for all $T \in \calT$:
+    \begin{align*}
+        ...
+    \end{align*}
 \end{theorem}
@@
  \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
+    \| w_{m} \|_{L^{p}(S_m)}
     &\leq 
@@
         \prod_{t < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
     \right)
-    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
+    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{\frac 1 q}
     \| u_{F_t} \|_{L^{p}(U_{F_t})}
@@
         \prod_{0 < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
     \right)
-    \| u_{T_0}\|_{L^{p}(T_{0})}
-    .
- \end{align*}
- %  
- % \color{red}We want to summarize the Lp norms so that the Poincare inequality over $U_F$ is applied only once.
-In the special cases $p=1$ and $p=\infty$, this works as above.
-Do we have a formula for general $p$ that contains these as limit cases?
-\color{black}
- % In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
- % \begin{align*}
- %    \| w_{m} \|_{L^{p}(T_m)}^{p}
- %    &\leq 
- %    3^{p-1}
- %    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
- %    +
- %    3^{p-1}
- %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
- %    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
- %    +
- %    3^{p-1}
- %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
- %    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
- %    \\&\leq 
- %    3^{p-1}
- %    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
- %    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
- %    +
- %    3^{p-1}
- %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
- %    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
- %    ,
- % \end{align*}
- % and therefore
- % \begin{align*}
- %    \| w_{m} \|_{L^{p}(T_m)}
- %    &\leq 
- %    3^{\frac{p-1}{p}}
- %    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)^{\frac 1 p}
- %    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
- %    +
- %    3^{\frac{p-1}{p}}
- %    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
- %    \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
- %    .
- % \end{align*}
- % \color{blue}
- % In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
- % \begin{align*}
- %    \| w_{m} \|_{L^{p}(T_m)}^{p}
- %    &\leq 
- %    \left( 
- %        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
- %    \right)^{ p-1 }
- %    \left( 
- %        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
- %        +
- %        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
- %        +
- %        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
- %    \right)
- %    ,
- % \end{align*}
- % and therefore
- % \begin{align*}
- %    \| w_{m} \|_{L^{p}(T_m)}
- %    &\leq 
- %    \left( 
- %        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
- %    \right)^{ \frac{p-1}{p} }
- %    \left( 
- %        \| u_{F_m} \|_{L^{p}(T_m)} 
- %        +
- %        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
- %        +
- %        \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
- %    \right)
- %    .
- % \end{align*}
- % \color{black}
+    \| u_{S_0}\|_{L^{p}(S_{0})}
+    .
+ \end{align*}
+ It follows that
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(S_m)}^{p}
+    &\leq 
+    (m+1)^{p-1}
+    \sum_{t=1}^{m} 
+    \left( 
+        \prod_{t < l \leq m} 
+        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
+    \right)
+    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{p/q}
+    \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
+    \\&\quad \quad \quad 
+    +
+    (m+1)^{p-1}
+    \left( 
+        \prod_{0 < l \leq m} 
+        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
+    \right)
+    \| u_{S_0}\|_{L^{p}(S_{0})}^{p}
+    .
+ \end{align*}
+ Notice that $p/q = p - 1$.
 \end{proof}
@@
 Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq \bbZ$.
-    \color{red}By some handwaving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
+    \color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
     Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
@@
     We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
-    \[
+    \begin{align*}
         H_0(\calT) \simeq \bbZ, 
@@
         H_1(\calT) \simeq \dots \simeq H_{n-1}(\calT) \simeq 0.
-    \]
+    \end{align*}
     Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
@@
 
+\section{Extension operator on finite element stars}
+
 \section{Constructive estimate of Poincar\'e--Friedrichs constants}
-% Repeat for H(curl), H(div), and differential forms
+
+\subsection{Inequalities for partial boundary conditions on a single simplex}
+
+\subsection{Constructions over shellable triangulations}
 

### 2024-06-09 main.tex
Update on Overleaf.

@@
 
-We gather notions of simplicial meshes for the subsequent discussion. 
-Apart from basic definitions and notational conventions, we pay special attention to the question of when a simplicial complex is a triangulation of a manifold. 
-A particularly important class of simplicial complexes are so-called \emph{shellable} complexes.
-Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner.
-While shellable complexes are a very special class of complexes, they facilitate achieving the main goal of our exposition.
-Our main references on simplicial complexes and shellability are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}.
-
-\subsection{Basic notions}
+We gather basic notions and definitions concerning simplicial meshes.
 
@@
 If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a subsimplex of $T$ and we call $T$ a supersimplex of $S$.
-
-A family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if its member simplices satisfy the following condition: 
-(i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
+then we call $S$ a \textit{subsimplex} of $T$ and we call $T$ a \textit{supersimplex} of $S$.
+
+The strictly positive convex combinations of the simplex' vertices are the \textit{interior} of the simplex,
+and its remaining points constitute the \textit{boundary} of the simplex.
+\\
+
+A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if it satisfies the following conditions: 
+(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
+% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
 The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-We say that $\calT$ has dimension $n$ if it contains an $n$-dimensional simplex as a supersimplex for each simplex within it.
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{We warn the reader that simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes.}
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
+\[
+    \underlying{\calT} := \bigcup_{ T \in \calT } T
+    .
+\]
+We call a set \textit{triangulable} if it is the underlying set of some triangulation.
+
+\begin{remark}
+    Our main interest in this manuscript are finite triangulations of compact sets. 
+    There is another reason why we insist on the triangulation being finite: 
+    if we do not require our simplicial complexes to be finite,
+    then our definition would be considerably more permissive than the typical definitions in topology. 
+    % 
+    For example, if we allowed simplicial complex to be infinite, 
+    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
+    %
+    A more interesting such example is this:
+    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
+    that underlies an ``infinite $0$-dimensional simplicial complex''.
+    If we place $\calC$ on the x-axis of a 2D coordinate system 
+    and connect each member of $\calC$ to $(0,1)$ via a straight line segment, 
+    then the resulting set is still compact, even path-connected,  
+    but has an ``infinite $1$-dimensional triangulation''.
+    % 
+    However, none of these infinite families are simplicial complexes in the sense of topology~\cite{spanier1966homology}. 
+\end{remark}
 
@@
 Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
-Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces of the triangulation.
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} of $T$, which is the smallest simplicial subcomplex of $\calT$ that contains all supersimplices of $T$.
-Formally,
+Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.
+
+\begin{remark}
+    Our use of the term \textit{face} as is common in the finite element literature
+    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.
+    Notably, this terminology difers from the uses \textit{face} and \textit{facet} in the theory of polyhedra. 
+\end{remark}
+
+When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{star} of $T$, 
+which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. Formally,
 \begin{gather*}
@@
 \begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $T,T' \in \calT$.
- Then either $\calT_{n}(T) \cap \calT_{n}(T') = \emptyset$ or there exists $S \in \calT$
- such that $\calT_{n}(T) \cap \calT_{n}(T') = \calT_{n}(S)$ with $T, T' \subseteq S$.
+ Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
+ Then either $\calT_{n}(S) \cap \calT_{n}(S') = \emptyset$ or there exists $S'' \in \calT$
+ such that $\calT_{n}(S) \cap \calT_{n}(S') = \calT_{n}(S'')$ with $S, S' \subseteq S''$.
 \end{lemma}
 \begin{proof}
- Let $F \in \calT$ be $n$-dimensional.
- We have $F \in \patch_{\calT}(T )$ if and only if all vertices of $T $ are vertices of $F$.
- We have $F \in \patch_{\calT}(T')$ if and only if all vertices of $T'$ are vertices of $F$.
- Consequently, $F \in \patch_{\calT}(T) \cap \patch_{\calT}(T)$ if and only if $F \in \patch_{\calT}(S)$,
- where $S \in \calT$ and $S$ is the convex closure of $F$ and $F'$.
+ Let $T \in \calT$ be $n$-dimensional.
+ We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
+ We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
+ Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
+ where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
 \end{proof}
 
+We will use a specific notion of connectivity. 
 Given an $n$-dimensional simplicial complex $\calT$, 
-we call $n$-simplices $S,T \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,T=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
 Clearly, strongly connected in $\calT$ is an equivalence relation.
@@
 
-\section{Shellable triangulated domains}
-
-% 2. Develop manifold-like complexes and characterize them 
-We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$.
-We call those $F \in \calT$ of dimension $n-1$ contained within only one parent a \emph{boundary face}.
-We write $\partial\calT$ for the simplicial subcomplex of $\calT$ of dimension $n-1$ 
-whose full-dimensional members are exactly the boundary faces of $\calT$.
-
-An $n$-dimensional simplicial complex is called \emph{manifold-like} if for every $x \in \bigcup \calT$
-we have one of the following two conditions:
-\begin{itemize}
- \item 
- there exists $\epsilon > 0$ 
- and a homeomorphism 
- \begin{align*}
-    \phi : \Ball_\epsilon(x) \cap \bigcup\calT  
-    \rightarrow 
-    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1 \right\}
- \end{align*}
- such that $\phi(x) = 0$,
- \item 
- there exists $\epsilon > 0$ and a homeomorphism 
- \begin{align*}
-    \phi : \Ball_\epsilon(x) \cap \bigcup\calT 
-    \rightarrow 
-    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1, x_n \leq 0 \right\}
- \end{align*}
- such that $\phi(x) = 0$.
-\end{itemize}
-This characterizes the union of the simplicial complex $\calT$ as a topological manifold with boundary.
-
-We would like to have a purely combinatorial and computable criterion that characterizes manifold-like simplicial complexes. A first step in that direction is the following result.
+\section{Shellable triangulations}
+
+We return to the theory of triangulations,
+as our main objective requires some further concepts.
+We are interested in simplicial complexes that triangulated manifolds. 
+We put particular focus on \emph{shellable} simplicial complexes as a particularly important class of complexes.
+Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner.
+Patches within triangulations are examples of such shellable complexes.
+Our main references for this section are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}. 
+\\
+
+\subsection{Triangulations of manifolds}
+
+We define an $n$-dimensional simplicial complex to be a \emph{simplicial manifold} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
+We recall that this means that for every $x \in \underlying{\calT}$
+there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^n$
+such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^n \suchthat |x| \leq 1 \}$
+or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
+Note than any simplicial complex that triangulates an $n$-dimensional manifold must be an $n$-dimensional simplicial complex.
+
+The following special cases receive particular interest:
+a \textit{simplicial $n$-ball} is any triangulation of a topological (closed) $n$-ball,
+and we sometimes call this a simplicial \textit{$n$-disk}.
+A \textit{simplicial $n$-sphere} is any triangulation of a topological $n$-sphere.
+
+We now gather a few helpful properties of simplicial manifolds,
+which we state without proof.
 
 \begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
-    Let $\calT$ be an $n$-dimensional simplicial complex. The following are equivalent:
-    \begin{itemize}
-     \item $\calT$ is manifold-like
-     \item $\patch_{\calT}(V)$ is the triangulation of a ball for all $V \in \Vertices(\calT)$
-     \item $\patch_{\calT}(V)$ is manifold-like for all $V \in \Vertices(\calT)$
-     \item $\patch_{\calT}(S)$ is the triangulation of a ball for all $S \in \calT$
-     \item $\patch_{\calT}(S)$ is manifold-like for all $S \in \calT$
-    \end{itemize}
+    Let $\calT$ be a finite $n$-dimensional simplicial manifold. 
+    \begin{enumerate}
+        \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
+        \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
+        % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
+        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
+        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
+        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
+    \end{enumerate}
 \end{lemma}
 \begin{proof}
-    \color{red} TODO
+    % Faces have at most two parents TODO must be more careful here 
+    Let $F \in \Faces(T)$ and let $z_F \in F$ be its midpoint. 
+    Let $B_F$ be a ball around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$.
+    Suppose there were distinct $n$-simplices $T_1, T_2, T_3$ that contain $z_F$. The intersection of any two of them is $F$, and their interiors are disjoint. 
+    It follows that $B_F \setminus F$ has at least $3$ connected components, though $B_F \setminus F$ has at most two components. 
+    We conclude that each face is in at most two $n$-simplices.
+
+    % TODO inner/boundary faces
+
+    % TODO structure of stars around simplices
+
+    % TODO
+
+    % TODO stars are strongly connected 
+    We show that each vertex star is strongly connected via a short induction argument.
+    Clearly, any simplicial $1$-ball and simplicial $1$-sphere is strongly connected. 
+    Now, if $n \geq 1$, then any vertex star in an $(n+1)$-dimensional simplicial manifold is strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
+    The induction argument implies that each vertex star in $\calT$ is strongly connected.
+
+    % strongly connected
+    If the underlying space is connected, then we easily see that the underlying space of the $1$-skeleton is path-connected.
+    Given $n$-simplices $S,S' \in \calT$, 
+    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$.
+    We also notice that each vertex star is strongly connected. 
+    We can thus construct change the first sequence to another $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
+    such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
 \end{proof}
+
+Suppose that $\calT$ is an $n$-dimensional simplicial manifold. 
+The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
+If $S$ lies in the boundary of the underlying set, then it lies within some boundary face, % TODO
+and so we conclude that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
+Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
+Definitions imply that the boundary complex is a simplicial manifold of dimension $n-1$.
+
+The boundary simplices of a simplicial manifold of dimension $n$ constitute a simplicial manifold themselves, of dimension $n-1$, which triangulate the boundary of the underlying space.
+
+% We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$.
+
+% TODO: https://arxiv.org/html/1607.08163v3
+% https://mathoverflow.net/questions/403415/properties-a-triangulation-must-have-in-order-to-describe-a-manifold
 
@@
 \end{remark}
+\begin{remark}
+    Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. 
+    For that reason, there is no easy combinatorial property that indicates whether a simplicial complex triangulates a manifold.
+\end{remark}
+
+% TODO: the following lemma needs only be as strong as it aids the subsequent discussion
 
@@
 
-    \caption{Example of a connected $2$-dimensional manifold-like simplicial complex, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
+    \caption{Example of a connected $2$-dimensional simplicial manifold, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
 \end{figure}
@@
 We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-Given an $n$-dimensional simplicial complex $\calT$, a \emph{shelling} is an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$ such that $( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) ) \cap \patch_{\calT}(T_{m+1})$ is a simplicial complex of dimension $n-1$.
-Notice that the last intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$, and is thus manifold like.
-
-% \begin{lemma}
-%     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
-%     In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is manifold-like for every $m \geq 0$.
-% \end{lemma}
-% \begin{proof}    
-% \end{proof}
-
-We notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
+We build upon the notion of shelling, as introduced in~\cite[Definition 8.1]{ziegler2012lectures}.
+Our definition of shelling is equivalent to the notion of the shellings of simplicial complexes in the aforementioned reference; see also~\cite[Remark~8.3]{ziegler2012lectures}.
+
+Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
+For any enumeration, we call 
+\[
+    I_m := ( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) ) \cap \patch_{\calT}(T_{m+1})
+\]
+be the $m$-th \textit{interface complex}. Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
+We call the enumeration a \emph{shelling} if each interface $I_m$ is a simplicial complex of dimension $n-1$.
+
+\begin{remark}
+    We interpret a shelling as the construction of a triangulation 
+    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
+    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
+\end{remark}
+
+\begin{example}
+    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
+    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
+\end{example}
+\begin{example}
+    The standard triangulation of the $n$-dimensional cube, the Kuhn triangulation, is shellable. 
+\end{example}
+\begin{example}
+    Not all triangulable sets admit a triangulation that is also shellable. 
+    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
+    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
+\end{example}
+
+Our main interest are the local patches or stars within triangulations. 
+It turns out that those are shellable.
+
+\begin{lemma}
+    Any simplicial $2$-disk is shellable.
+    Any simplicial $2$-sphere is shellable. 
+\end{lemma}
+\begin{proof}
+    Let $\calT$ be a simplicial $2$-disk. 
+    If $\calT$ contains only one triangle, then there is nothing to show. 
+    Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges {\color{red}Needs proof}. 
+    Letting $\calT'$ be the triangulation obtained by removing $T$,
+    we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
+    Repeating this procedure yields an enumeration of the triangles of $\calT$,
+    whose reverse is a shelling.
+
+    Now let $\calS$ be any simplicial $2$-sphere. 
+    By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
+    Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+\end{proof}
+
+\begin{lemma}
+    Let $\calT$ be a $n$-dimensional simplicial manifold and $V \in \Vertices(\calT)$ be an inner vertex.
+    Then $\patch_{\calT}(V)$ is shellable. 
+\end{lemma}
+\begin{proof}
+    Without loss of generality, $V$ is the origin. 
+    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
+    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
+    which does not affect shellability. 
+    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
+    and is thus shellable~\cite{ziegler2012lectures}. % TODO: cite exactly 
+\end{proof}
+
+\begin{lemma}
+    Let $\calT$ be a $3$-dimensional simplicial manifold and $S \in \calT$.
+    Then $\patch_{\calT}(S)$ is shellable. 
+\end{lemma}
+\begin{proof}
+    The statement is clear if $S$ is an inner or boundary face of $\calT$. 
+    The statement is also easily verified if $S$ is an inner or boundary edge of $\calT$.
+    When $S$ is an inner vertex, then we apply the preceding lemma.
+
+    It remains to consider the case where $S$ is a boundary vertex. 
+    Then the triangles of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-disk {\color{red}Needs proof},
+    which is shellable,
+    and any such shelling can be extended to a shelling of $\patch_{\calT}(S)$.
+\end{proof}
+
+\begin{remark}
+    Patches around boundary simplices are not necessarily shellable when the dimension exceeds $3$.
+    For example, there exists a non-shellable triangulation of a tetrahedron. 
+    If we extend this triangulation to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, 
+    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
+\end{remark}
+
+The reason of our interest in shellable simplicial complexes is that they can be constructed by successive adhesion of simplices to intermediate complexes, 
+such that the interface is well-behaved: it is a simplicial disk or a simplicial sphere. 
+That has the following important consequence.
+
+% TODO: we only need some basic properties, namely that the construction maintains manifolds with boundary.
+% TODO: copy and adapt the content of Ziegler and Kozlov as necessary
+
+\begin{lemma}
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is a simplicial manifold.
+    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is a simplicial manifold for every $m \geq 0$.
+\end{lemma}
+\begin{proof}    
+\end{proof}
 
@@
 
-%
-
-A simplicial $n$-dimensional complex $\calT$ is called shellable if its $n$-simplices can be arranged in linear order $T_0, T_1, \dots$ in such a way that the subcomplex $( \cup_{i=0}^{k-1} T_i ) \cap T_k$ has dimension $n-1$ for all $k > 0$.
-
 \begin{remark}
+    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possibly enumerations.
+    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
+    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
+\end{remark}
+
+\subsection{On the topology of shellable triangulations}
+
 A shellable simplicial complex that triangulates a manifold has a very restricted topology. 
@@
 % \end{align*}
-\end{remark}
 

### 2024-06-10 main.tex
work on Poincare

--- 2024-05-03 main.tex
@@
 
-\section{Introduction}
+\section{Introduction}\label{section:intro}
 
@@
 In particular, this yields computable upper bounds for Poincar\'e--Friedrichs inequalities. 
-For example, if $\bff \in \bfL^{p}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
-we want to bound the $L^p$ norm of the potential
-\begin{align*}
-    \argmin\limits_{ \substack{ \bfv \in \bfL^{p}(\curl) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{p}(\Omega)}
+For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
+we want to bound the $\bfL^2$ norm of the potential
+\begin{align*}
+    \argmin\limits_{ \substack{ \bfv \in \bfL^{2} \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
+    \leq 
+    C_{\curl}
+    \| \bff \|_{\bfL^{2}(\Omega)}
+    .
+\end{align*}
+Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
+We address this topic in the special case where $\Omega$ admits a shellable triangulation.
+Even though only contractible domains can admit a shellable triangulation, 
+having computable upper bounds for such domains is an important step stone towards the more general case. 
+For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.
+
+We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
+Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
+we search for a constant $C > 0$ such that 
+\begin{align*}
+    \min\limits_{c\in\bbR}
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
+    \quad 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
+The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
+Even though the existence of such a bounded linear potential construction is not evident a priori, 
+picking the average-free potential 
+\begin{align*}
+    \Phi_{\grad}( \bff ) 
+    := 
+    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
+    \quad 
+    \bff \in \nabla W^{1,p}(\Omega)
+\end{align*}
+is a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
+\begin{align*}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
+    \quad 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_\Omega$ denotes the average of $u$.
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.
+
+The situation is less clear cut when we study the curl or divergence operators
+\begin{align*}
+    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\curl,\Omega),
+    \qquad 
+    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
+\end{align*}
+where we use the function spaces
+\begin{align*}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
+    .
+\end{align*}
+The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
+{\color{red}The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. }
+In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
+We are interested in constants for inequalities such as 
+\begin{align*}
+    \argmin\limits_{ \substack{ v \in W^{p}(\curl,\Omega) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)}
     \leq 
@@
     \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-We address this topic in the special case where $\Omega$ admits a shellable triangulation.
-While this constraints us to the class of {\color{red}contractible} domains, 
-having computable upper bounds for such domains is an important step stone towards the more general case. 
-For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.
+    ,
+    \qquad 
+    \argmin\limits_{ \substack{ v \in W^{p}(\divergence,\Omega) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\divergence}
+    \| f \|_{L^{p}(\Omega)}
+    ,
+\end{align*}
+and whether these constants can be estimated by the operator norm of linear potential operators 
+\begin{align*}
+    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \quad 
+    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
+\end{align*}
+We remark that seemingly not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators, 
+% even if the domain is convex, 
+which is in sharp contrast to the study of the gradient operator.
+
+We explore formulate our main results in the framework of exterior calculus.
+The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
+%
+It is used ubiquitiously in physics and engineering. 
+%
+For the purpose of our discussion, this formalisms allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
+\\
+
+Before we outline the main results of this exposition in more details, 
+we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains.
+
+% Convex domains
+
+% Domains starshaped wrt ball
+
+% Limitations
+
+Most research on optimal constants has addressed the case of convex domains. 
+Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
+Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.
+
+In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
+\\
 
@@
 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
-Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
-we search for a constant $C > 0$ such that 
-\begin{align*}
-    \min\limits_{c\in\bbR}
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad} \| \nabla u \|_{L^p(\Omega)},
-    \quad 
-    u \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
-The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
-Even though the existence of such a bounded linear potential construction is not evident a priori, 
-picking the average-free potential 
-\begin{align*}
-    \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
-    \quad 
-    \bff \in \nabla W^{1,p}(\Omega)
-\end{align*}
-is known to be a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
-\begin{align*}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
-    \quad 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities. 
-The optimal values for all $1 \leq p < \infty$ are known when the domain is convex.
-
-The situation is less clear cut when we try to find try the curl or divergence operators
-\begin{align*}
-    \curl : \bfW^{p}(\curl) \rightarrow \bfL^{p}(\curl),
-    \quad 
-    \divergence : \bfW^{p}(\divergence) \rightarrow L^{p}(\curl),
-\end{align*}
-where we use the function spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
-    .
-\end{align*}
-The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. 
-In the Banach space case, it is not immediately evident the kernels of these operators are complemented.
-We are interested in constants for inequalities such as 
-\begin{align*}
-    \argmin\limits_{ \substack{ v \in W^{p}(\curl) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)},
-    \leq 
-    C_{\curl}
-    \| \bff \|_{L^{p}(\Omega)}
-    \\
-    \argmin\limits_{ \substack{ v \in W^{p}(\divergence) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)},
-    \leq 
-    C_{\divergence}
-    \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
-and whether these constants can be estimated by the operator norm of linear potential operators 
-\begin{align*}
-    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
-    \quad 
-    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega).
-\end{align*}
-We notice that not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs for the curl and divergence operators, even if the domain is convex, which is in sharp contrast to the study of the gradient operator.
-In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
-\\
-
 The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence satisfying explicitly computable upper bounds.
@@
 \begin{align*}
-    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
+    C_{\grad,p} \geq C_{\curl} \geq C_{\divergence}.
 \end{align*}
@@
 has no estimates in the literature.
+
+An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
+We refer to \cite{hurri1988poincare} for that perspective.
 
@@
 
-\section{Basic notions of triangulations}
+The remainder of this manuscript is structured as follows.
+We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants over triangulated domains in Section~\ref{section:poincare}.
+We then review the notion of shellable triangulation in Section~\ref{section:shellable}.
+We construct an important geometric reflection operator in Section~\ref{section:extension}
+and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+
+\section{Basic notions of triangulations}\label{section:triangulations}
 
@@
 
-\section{Constructive estimate of Poincar\'e constants}
+\section{Constructive estimate of Poincar\'e constants}\label{section:poincare}
 
@@
 
-\section{Shellable triangulated domains}
+\section{Shellable triangulated domains}\label{section:shellable}
 
@@
 
-% \begin{lemma}
-%     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
-%     In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is manifold-like for every $m \geq 0$.
-% \end{lemma}
-% \begin{proof}    
-% \end{proof}
-
-We notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
+\begin{lemma}
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
+    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ triangulates a manifold for all $m \geq 0$.
+\end{lemma}
+\begin{proof}    
+\end{proof}
+
+The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
 
@@
 
-    Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold, and suppose that its boundary complex $\partial\calT$ is either empty or strongly connected.
-    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$.
+    Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold.
+    Suppose that its boundary complex $\partial\calT$ is not empty and strongly connected.  
+    We exclude the case $n \leq 1$ since otherwise the discussion is trivial.
+
+    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, 
+    whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$. 
     In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$. 
-We write $\calT'$ be the  simplicial complex that contains $\calT \cup T$.
-    We exclude that case $n \leq 1$ since otherwise the discussion is trivial.
-
+    We write $\calT'$ for the  simplicial complex that contains $\calT \cup T$.
     According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
@@
     \end{align*}
-    We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
+    We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to ${G}$. 
     By the nature of the mappings in the Mayer-Vietoris sequence, 
@@
     is an exact sequence. 
-    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
+    Moreover, $H_{k}(\calS) = H_{k}(T) = 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
     the Mayer-Vietoris sequence includes the exact sequence 
@@
     and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
-    Finally, the Mayer-Vietoris sequence includes the exact sequences 
+    Finally, the Mayer-Vietoris sequence includes the exact sequence 
     \begin{align*}
@@
     % Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
-    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
+    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq {G}$ because the respective simplicial complexes are path-connected. 
     % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
-    % one easily sees that $H_{0}(\calT') \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+    % one easily sees that $H_{0}(\calT') \simeq {G}$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
     Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
-    In the case that $\calS$ is isomorphic to disk,
-    then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ are trivial and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
+    In the case that $\calS$ is isomorphic to disk, we have $H_{n-1}(\calS) = 0$,
+    and then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T) = 0$ are trivial 
+    and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
     Consider now the case that $\calS$ is isomorphic to a sphere.
     Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
-Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq \bbZ$.
+Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq {G}$.
     \color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
@@
     \begin{align*}
-        H_0(\calT) \simeq \bbZ, 
+        H_0(\calT) \simeq {G}, 
         \quad 
@@
     \end{align*}
-    Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
+    Moreover, $H_n(\calT) \simeq {G}$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
 
@@
 
-\section{Extension operator on finite element stars}
-
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}
+\section{Extension operator on finite element stars}\label{section:extension}
+
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
 

### 2024-06-11 main.tex

--- 2024-06-09 main.tex
@@
     \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-We address this topic in the special case where $\Omega$ admits a shellable triangulation.
-While this constraints us to the class of {\color{red}contractible} domains, 
-having computable upper bounds for such domains is an important step stone towards the more general case. 
-For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.
+    ,
+    \qquad 
+    \argmin\limits_{ \substack{ v \in W^{p}(\divergence,\Omega) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\divergence}
+    \| f \|_{L^{p}(\Omega)}
+    ,
+\end{align*}
+and whether these constants can be estimated by the operator norm of linear potential operators 
+\begin{align*}
+    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \quad 
+    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
+\end{align*}
+We remark that seemingly not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators, 
+% even if the domain is convex, 
+which is in sharp contrast to the study of the gradient operator.
+
+We explore formulate our main results in the framework of exterior calculus.
+The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
+%
+It is used ubiquitously in physics and engineering. 
+%
+For the purpose of our discussion, this formalisms allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
+\\
+
+Before we outline the main results of this exposition in more details, 
+we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains.
+
+% Convex domains
+
+% Domains starshaped wrt ball
+
+% Limitations
+
+Most research on optimal constants has addressed the case of convex domains. 
+Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
+Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.
+
+In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
+\\
 
@@
     and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.
-    Notably, this terminology difers from the uses \textit{face} and \textit{facet} in the theory of polyhedra. 
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra. 
 \end{remark}
@@
 
-We now gather a few helpful properties of simplicial manifolds,
-which we state without proof.
+We gather a few helpful properties of simplicial manifolds.
 
@@
     Let $\calT$ be a finite $n$-dimensional simplicial manifold. 
-    \begin{enumerate}
+    \begin{itemize}
         \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
         \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
+        \item The simplices contained in the boundary constitute a triangulation of the boundary.
         % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
@@
         \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
-    \end{enumerate}
+    \end{itemize}
 \end{lemma}
 \begin{proof}
-    % Faces have at most two parents TODO must be more careful here 
+    \begin{enumerate}
+    \item 
+    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial M$, then all inner points of $S$ are on $\partial M$. 
+    Since the boundary is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior of the manifold.
+
+    \item
     Let $F \in \Faces(T)$ and let $z_F \in F$ be its midpoint. 
-    Let $B_F$ be a ball around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$.
-    Suppose there were distinct $n$-simplices $T_1, T_2, T_3$ that contain $z_F$. The intersection of any two of them is $F$, and their interiors are disjoint. 
-    It follows that $B_F \setminus F$ has at least $3$ connected components, though $B_F \setminus F$ has at most two components. 
-    We conclude that each face is in at most two $n$-simplices.
-
-    % TODO inner/boundary faces
-
+    Let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
+    Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
+    The intersection of any two of them is $F$, and their interiors are disjoint.
+
+    If $z_F$ is an interior point of $M$, 
+    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere $S$ of dimension $n-1$. 
+    At the same time, $X = F \subseteq \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere $S' \subseteq S$ of dimension $n-2$. 
+    We see that $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
+    But by construction $\partial \mathring B_F \setminus X$ is homeomorphic to $S \setminus S'$,
+    which has exactly two distinct connected components according to the Jordan-Brouwer separation theorem.
+    We conclude that $F$ is contained in two $n$-simplices of $\calT$.
+    If an inner face $F$ were contained in only one $n$-simplex,
+    then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
+    So each inner face is contained in exactly two $n$-simplices.
+
+    If $F$ is contained in only one $n$-simplex, then it must be a boundary face. 
+    If a boundary face $F$ were contained in at least two $n$-simplices,
+    then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
+    So each boundary face is contained in exactly one $n$-simplex.
+
+    \item
+    Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
+    If $x \in \partial M$ is a boundary simplex, then it is an inner point of some simplex $S \in \calT$.
+    But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial M$.
+
+    \item 
     % TODO structure of stars around simplices 
-
-    % TODO
+    Let $S$ be any simplex with midpoint $z_F$. 
+    For $\delta > 0$ small enough, 
+    \begin{align*}
+        B_{\delta}(z_F) = \left\{ x \in M \suchthat d(x,z_F) \leq \delta \right\},
+        \quad 
+        S_{\delta}(z_F) = \left\{ x \in M \suchthat d(x,z_F) = \delta \right\},
+    \end{align*}
+    are subsets of $\patch_{\calT}(S)$.
+%     For any $K \in \patch_{\calT}(S)$ that contains $S$, 
+%     we can easily find a homeomorphism
+
+%     Then $\patch_{\calT}(S)$ is star-shaped with respect to $z_F$. 
+%     We let $B$
+%     Any half-ray starting at $z_F$ intersects at most one vertex in $\patch_{\calT}(S)$ other than $z_F$. 
+%
 
     % TODO stars are strongly connected 
+    \item 
     We show that each vertex star is strongly connected via a short induction argument.
@@
     % strongly connected
+    \item 
     If the underlying space is connected, then we easily see that the underlying space of the $1$-skeleton is path-connected.
@@
     such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+    \end{enumerate}
 \end{proof}
@@
 \begin{lemma}    
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
+    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ triangulates a manifold for all $m \geq 0$.
+\end{lemma}
+\begin{proof}    
+\end{proof}
+
+The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
+\begin{lemma}    
     Any simplicial $2$-disk is shellable.
@@
 
+    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, 
+    whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$. 
+    In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$. 
+    We write $\calT'$ for the  simplicial complex that contains $\calT \cup T$.
+
 Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold, and suppose that its boundary complex $\partial\calT$ is either empty or strongly connected.
@@
 We write $\calT'$ be the  simplicial complex that contains $\calT \cup T$.
-We exclude that case $n \leq 1$ since otherwise the discussion is trivial.
+We exclude the case $n \leq 1$ since otherwise the discussion is trivial.
 
@@
 \end{align*}
-We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
+We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to ${G}$. 
 By the nature of the mappings in the Mayer-Vietoris sequence, 
@@
 is an exact sequence. 
-Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
+Moreover, $H_{k}(\calS) = H_{k}(T) = 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
 the Mayer-Vietoris sequence includes the exact sequence 
@@
 and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
-Finally, the Mayer-Vietoris sequence includes the exact sequences 
+Finally, the Mayer-Vietoris sequence includes the exact sequence 
 \begin{align*}
@@
 \end{align*}
+
 % Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
@@
 Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
-In the case that $\calS$ is isomorphic to disk,
 then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ are trivial and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
@@
 
+In the case that $\calS$ is isomorphic to a disk, we have $H_{n-1}(\calS) = 0$,
+and then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T) = 0$ are trivial 
+and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
+Consider now the case that $\calS$ is isomorphic to a sphere.
+Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
+Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq {G}$.
+\color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
+Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
+
 We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
@@
 \end{align*}
+Moreover, $H_n(\calT) \simeq {G}$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise. 
 Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
@@
 
+\begin{remark}    
+    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq {G}$ because the respective simplicial complexes are path-connected. 
+    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+    % one easily sees that $H_{0}(\calT') \simeq {G}$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$.
+
+    % then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
+    % Moreover, Thus $H_{n}(\calT') = H_{n}(\calT) \oplus H_{n}(\calS)$.
+    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
+    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
+    % \begin{align*}
+    %     \begin{CD}
+    %         0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT') \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0
+    %     \end{CD}
+    % \end{align*}
+\end{remark}
+
 \section{Extension operator on finite element stars}
 
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}
+\section{Extension operator on finite element stars}\label{section:extension}
+
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
 

### 2024-06-14 main.tex
manifold discussion

@@
 
-% Domains starshaped wrt ball
+% Domains star-shaped with respect to a ball
 
@@
 \]
-We call a set \textit{triangulable} if it is the underlying set of some triangulation.
+We call a set \textit{trianguable} if it is the underlying set of some triangulation.
 
@@
 Patches within triangulations are examples of such shellable complexes.
-Our main references for this section are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}. 
+Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}. 
 \\
@@
 
-We define an $n$-dimensional simplicial complex to be a \emph{simplicial manifold} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
+We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
 We recall that this means that for every $x \in \underlying{\calT}$
@@
 or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
-Note than any simplicial complex that triangulates an $n$-dimensional manifold must be an $n$-dimensional simplicial complex.
+Any simplicial complex that triangulates an $n$-dimensional manifold must be an $n$-dimensional simplicial complex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO: integrate into narrative 
+Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
+All other simplices of the manifold triangulation are called \emph{inner simplices}. 
+We will show soon that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
+% 
+%
+Suppose that $\calT$ is an $n$-dimensional manifold triangulation. 
+The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
+If $S$ lies in the boundary of the underlying set, then it lies within some boundary face.
+and so we conclude that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
+Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
+Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
+% 
+%
+The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 The following special cases receive particular interest:
-a \textit{simplicial $n$-ball} is any triangulation of a topological (closed) $n$-ball,
-and we sometimes call this a simplicial \textit{$n$-disk}.
-A \textit{simplicial $n$-sphere} is any triangulation of a topological $n$-sphere.
-
-We gather a few helpful properties of simplicial manifolds.
+a \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball,
+and we sometimes call this a \textit{$n$-disk} triangulation.
+An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
+
+We gather a few helpful properties of manifold triangulations. 
+While the reader might deem them obvious, we nevertheless include proofs.
 
 \begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
-    Let $\calT$ be a finite $n$-dimensional simplicial manifold. 
+    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
     \begin{itemize}
@@
     \item 
-    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial M$, then all inner points of $S$ are on $\partial M$. 
-    Since the boundary is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior of the manifold.
+    We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
+    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$. 
+    Since the boundary is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
 
@@
 
-    If $z_F$ is an interior point of $M$, 
+    If $z_F$ is an interior point of $\calM$, 
     then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere $S$ of dimension $n-1$. 
@@
 
-    If $F$ is contained in only one $n$-simplex, then it must be a boundary face. 
-    If a boundary face $F$ were contained in at least two $n$-simplices,
+    If $F$ is contained in only one $n$-simplex, then it must be a face in the boundary of $\calM$. 
+    If $F$ were contained in at least two $n$-simplices,
     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-    So each boundary face is contained in exactly one $n$-simplex.
+    So each face within $\partial \calM$ is contained in exactly one $n$-simplex.
 
@@
     Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
-    If $x \in \partial M$ is a boundary simplex, then it is an inner point of some simplex $S \in \calT$.
-    But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial M$.
+    If $x \in \partial \calM$ is a boundary simplex, then it is an inner point of some simplex $S \in \calT$.
+    But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial \calM$.
 
     \item 
-    % TODO structure of stars around simplices 
-    Let $S$ be any simplex with midpoint $z_F$. 
+    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint $z_F$, and dimension $k$.
+    Let $\calS := \patch_{\calT}(S)$ be its star. 
+    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
+    has vertices $v_0, v_1, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$. 
+    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
+    \begin{align*}
+        v_0, \dots, v_{i-1}, z_F, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
+    \end{align*}
+    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
+    that triangulates the same underlying set as $\calS$.
+    Moreover, $\calS' = \patch_{\calS'}(z_F)$. 
+    In particular, $z_F$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$.
+
+    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
     For $\delta > 0$ small enough, 
     \begin{align*}
-        B_{\delta}(z_F) = \left\{ x \in M \suchthat d(x,z_F) \leq \delta \right\},
+        B_{\delta}(z) = \left\{ x \in M \suchthat d(x,z) \leq \delta \right\},
         \quad 
-        S_{\delta}(z_F) = \left\{ x \in M \suchthat d(x,z_F) = \delta \right\},
+        S_{\delta}(z) = \left\{ x \in M \suchthat d(x,z) = \delta \right\},
     \end{align*}
     are subsets of $\patch_{\calT}(S)$.
-%     For any $K \in \patch_{\calT}(S)$ that contains $S$, 
-%     we can easily find a homeomorphism
-
-%     Then $\patch_{\calT}(S)$ is star-shaped with respect to $z_F$. 
-%     We let $B$
-%     Any half-ray starting at $z_F$ intersects at most one vertex in $\patch_{\calT}(S)$ other than $z_F$. 
-%
-
-    % TODO stars are strongly connected 
+    For each $K \in \patch_{\calT}(S)$ that contains $S$ and which has the complementary simplex $F_S$, 
+    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
+    such that 
+    $\phi_{K|S}$ is the identity,
+    such that 
+    $\phi_{K}(S_F) = S_{\delta}(z)$,
+    and such that 
+    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$.
+
+    If $z$ is an inner vertex of $\calS'$, 
+    then the boundary simplices of $\calS'$,
+    which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
+    If $z$ is a boundary vertex of $\calS'$,
+    which is the case if and only if $S$ is a boundary simplex, 
+    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
+    which is a topological ball of dimension $n-1$.
+
     \item 
@@
     Clearly, any simplicial $1$-ball and simplicial $1$-sphere is strongly connected. 
-    Now, if $n \geq 1$, then any vertex star in an $(n+1)$-dimensional simplicial manifold is strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
+    Now, if $n \geq 1$, then any vertex star in an $(n+1)$-dimensional manifold triangulation is strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
     The induction argument implies that each vertex star in $\calT$ is strongly connected.
 
-    % strongly connected
     \item 
@@
     \end{enumerate}
+    All relevant results are proven. 
 \end{proof}
-
-Suppose that $\calT$ is an $n$-dimensional simplicial manifold. 
-The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
-If $S$ lies in the boundary of the underlying set, then it lies within some boundary face, % TODO
-and so we conclude that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
-Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
-Definitions imply that the boundary complex is a simplicial manifold of dimension $n-1$.
-
-The boundary simplices of a simplicial manifold of dimension $n$ constitute a simplicial manifold themselves, of dimension $n-1$, which triangulate the boundary of the underlying space.
-
-% We call an $n$-dimensional simplicial complex $\calT$ \emph{non-branching} if every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$.
 
@@
     Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    Conversely, for each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. % TODO: are these compact?
-    % TODO There are computational limits to algorithmically deciding whether a simplicial complex represents a manifold. 
+    Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. 
+    We therefore are not in pursuit of any easy combinatorial property that indicates whether a simplicial complex (without any further specific assumptions) triangulates a manifold.
+
+    Conversely, not all topological manifolds, even if compact, can be described as a triangulation. 
+    Such manifolds appear in dimension four and higher:
+    one example is the E8 manifold, which is a compact simply-connected topological $4$-manifold that is homeomorphic to the underlying set of any simplicial complex.
+The construction of such counterexamples typically involves an infinite procedure.
+%     For each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. 
 \end{remark}
-\begin{remark}
-    Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. 
-    For that reason, there is no easy combinatorial property that indicates whether a simplicial complex triangulates a manifold.
-\end{remark}
-
-% TODO: the following lemma needs only be as strong as it aids the subsequent discussion
 
@@
 
-    \caption{Example of a connected $2$-dimensional simplicial manifold, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
+    \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
 \end{figure}
-
-% \color{red}
-% \begin{proposition}
-%     Suppose that $\calT$ is a connected $n$-dimensional simplicial complex. Then the following are equivalent:
-%     \begin{itemize}
-%      \item $\calT$ is manifold-like
-%      \item $\calT$ has a manifold-like $0$-patching
-%      % \item There exists $1 \leq k \leq n$ such that $\calT$ has a $k$-patching
-%     \end{itemize}
-% \end{proposition}
-% \color{black}
 
@@
 \[
-    I_m := ( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) ) \cap \patch_{\calT}(T_{m+1})
+    I_m 
+    := 
+    \big( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) \big) 
+    \cap 
+    \patch_{\calT}(T_{m+1})
 \]
@@
 \begin{example}
-    Not all triangulable sets admit a triangulation that is also shellable. 
+    Not all trianguable sets admit a triangulation that is also shellable. 
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
@@
 \begin{lemma}
-    Let $\calT$ be a $n$-dimensional simplicial manifold and $V \in \Vertices(\calT)$ be an inner vertex.
+    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
     Then $\patch_{\calT}(V)$ is shellable. 
@@
 \begin{lemma}
-    Let $\calT$ be a $3$-dimensional simplicial manifold and $S \in \calT$.
+    Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
     Then $\patch_{\calT}(S)$ is shellable. 
@@
 \begin{lemma}
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is a simplicial manifold.
-    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is a simplicial manifold for every $m \geq 0$.
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is a manifold triangulation.
+    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is a manifold triangulation for every $m \geq 0$.
 \end{lemma}
@@
 
+\subsection{Numerical examples}
+
+% Square 
+% L-shaped 
+% Slit
+% Cube 
+% Fechera
+% Crossed bricks
+
 \section*{Acknowledgments}

### 2024-06-15 main.tex
more theory

@@
-\documentclass[a4paper]{amsart}
+\documentclass[a4paper]{article}
 \usepackage[utf8]{inputenc}
@@
 Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
+In practice, we not always distinguish between points and singleton simplices. % TODO: see whether being formally correct iis possible 
 Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.
@@
 Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}.
-\\
 
@@
 or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
-Any simplicial complex that triangulates an $n$-dimensional manifold must be an $n$-dimensional simplicial complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO: integrate into narrative 
-Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
-All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We will show soon that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
-% 
-%
-Suppose that $\calT$ is an $n$-dimensional manifold triangulation. 
-The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
-If $S$ lies in the boundary of the underlying set, then it lies within some boundary face.
-and so we conclude that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
-Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
-Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
-% 
-%
-The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional.
+
+We know that any manifold $\calM$ has a got a topological boundary $\partial\calM$, possibly empty. 
+If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$.
 
@@
 While the reader might deem them obvious, we nevertheless include proofs. 
-
-\begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
+We begin with the boundary.
+
+\begin{lemma}\label{lemma:boundarysimplices}
     Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
@@
         % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
-        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
-        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
-        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
     \end{itemize}
@@
 \begin{proof}
+    We prove these statements in several steps.
     \begin{enumerate}
@@
     But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial \calM$.
-
+    \end{enumerate}
+    All relevant results are proven. 
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO: integrate into narrative 
+Suppose that $\calT$ is an $n$-dimensional simplicial complex that triangulates a manifold. 
+Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
+% The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
+All other simplices of the manifold triangulation are called \emph{inner simplices}.
+
+We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
+We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
+% We see that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
+% Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
+% Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
+% The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\
+
+We continue with a few more observations about manifold triangulations.
+
+\begin{lemma}\label{lemma:startopology}
+    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
+    \begin{itemize}
+        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
+        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
+        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    We prove these statements in several steps.
+    \begin{enumerate}
     \item 
@@
     \begin{align*}
-        B_{\delta}(z) = \left\{ x \in M \suchthat d(x,z) \leq \delta \right\},
+        B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
         \quad 
-        S_{\delta}(z) = \left\{ x \in M \suchthat d(x,z) = \delta \right\},
+        S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
     \end{align*}
@@
     which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
+
     If $z$ is a boundary vertex of $\calS'$,
@@
     then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
-    which is a topological ball of dimension $n-1$.
+    which is a topological ball of dimension $n-1$. % TODO: explain why
 
@@
     := 
-    \big( \patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m}) \big) 
+    \big( 
+        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
+    \big) 
     \cap 
-    \patch_{\calT}(T_{m+1})
+    T_{m+1}
 \]
-be the $m$-th \textit{interface complex}. Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface $I_m$ is a simplicial complex of dimension $n-1$.
+be the $m$-th \textit{interface set}. 
+% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
+We call the enumeration a \emph{shelling} if each interface $I_m$ is a manifold of dimension $n-1$.
 
@@
 \end{remark}
+\begin{remark}
+    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possibly enumerations.
+    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
+    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
+\end{remark}
+
+We collect important examples of shellable triangulations.
+Our main interest are local patches or stars within triangulations.
 
@@
     The standard triangulation of the $n$-dimensional cube, the Kuhn triangulation, is shellable. 
+    % https://scholar.google.de/scholar?hl=de&as_sdt=0%2C5&q=kuhn+triangulation+shelling&btnG=
 \end{example}
-\begin{example}
-    Not all trianguable sets admit a triangulation that is also shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
-\end{example}
-
-Our main interest are the local patches or stars within triangulations. 
-It turns out that those are shellable.
-
-\begin{lemma}    
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
-    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ triangulates a manifold for all $m \geq 0$.
-\end{lemma}
-\begin{proof}    
-\end{proof}
-
-The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
+
 \begin{lemma}    
@@
     If $\calT$ contains only one triangle, then there is nothing to show. 
-    Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges {\color{red}Needs proof}. 
+    Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
+    {\color{red}Needs proof}. 
     Letting $\calT'$ be the triangulation obtained by removing $T$,
@@
 \end{proof}
+
+% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars
 
@@
     It remains to consider the case where $S$ is a boundary vertex. 
-    Then the triangles of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-disk {\color{red}Needs proof},
+    Then the triangles of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-disk 
+    {\color{red}Needs proof},
     which is shellable,
@@
 
+\begin{example}
+    Not all trianguable sets admit a triangulation that is also shellable. 
+    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
+    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
+\end{example}
 \begin{remark}
@@
 
-% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars
-
-\begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possibly enumerations.
-    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
-    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
-\end{remark}
+\begin{lemma}    
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
+    In particular, $T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a manifold with boundary for all $m \geq 0$.
+\end{lemma}
+\begin{proof}    
+\end{proof}
+
+% The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
 
@@
 % Cube 
-% Fechera
+% Fichera
 % Crossed bricks

### 2024-06-15 draft.tex
add makefile; extensions and polishment
work on combinatorics

@@
 \end{proof}
+
+%  
+ % \color{red}We want to summarize the Lp norms so that the Poincare inequality over $U_F$ is applied only once.
+In the special cases $p=1$ and $p=\infty$, this works as above.
+Do we have a formula for general $p$ that contains these as limit cases?
+\color{black}
+ % In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}^{p}
+ %    &\leq 
+ %    3^{p-1}
+ %    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+ %    +
+ %    3^{p-1}
+ %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+ %    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+ %    +
+ %    3^{p-1}
+ %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+ %    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+ %    \\&\leq 
+ %    3^{p-1}
+ %    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+ %    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
+ %    +
+ %    3^{p-1}
+ %    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+ %    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+ %    ,
+ % \end{align*}
+ % and therefore
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}
+ %    &\leq 
+ %    3^{\frac{p-1}{p}}
+ %    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)^{\frac 1 p}
+ %    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
+ %    +
+ %    3^{\frac{p-1}{p}}
+ %    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
+ %    \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
+ %    .
+ % \end{align*}
+ % \color{blue}
+ % In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}^{p}
+ %    &\leq 
+ %    \left( 
+ %        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
+ %    \right)^{ p-1 }
+ %    \left( 
+ %        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+ %        +
+ %        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+ %        +
+ %        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+ %    \right)
+ %    ,
+ % \end{align*}
+ % and therefore
+ % \begin{align*}
+ %    \| w_{m} \|_{L^{p}(T_m)}
+ %    &\leq 
+ %    \left( 
+ %        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
+ %    \right)^{ \frac{p-1}{p} }
+ %    \left( 
+ %        \| u_{F_m} \|_{L^{p}(T_m)} 
+ %        +
+ %        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
+ %        +
+ %        \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
+ %    \right)
+ %    .
+ % \end{align*}
+ % \color{black}
+
+we have any of the following two conditions:
+\begin{itemize}
+ \item 
+ there exists $\epsilon > 0$ 
+ and a homeomorphism 
+ \begin{align*}
+    \phi : \Ball_\epsilon(x) \cap \underlying{\calT}  
+    \rightarrow 
+    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1 \right\}
+ \end{align*}
+ such that $\phi(x) = 0$,
+ \item 
+ there exists $\epsilon > 0$ and a homeomorphism 
+ \begin{align*}
+    \phi : \Ball_\epsilon(x) \cap \underlying{\calT} 
+    \rightarrow 
+    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1, x_n \leq 0 \right\}
+ \end{align*}
+ such that $\phi(x) = 0$.
+\end{itemize}
+This characterizes the union of the simplicial complex $\calT$ as a topological manifold with boundary.
+
+\subsection{On the topology of shellable triangulations}
+
+A shellable simplicial complex that triangulates a manifold has a very restricted topology. 
+The Mayer-Vietoris theorem implies restrictions on the homology groups of simplicial complexes iteratively constructed via shelling.
+
+    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, 
+    whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$. 
+    In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$. 
+    We write $\calT'$ for the  simplicial complex that contains $\calT \cup T$.
+
+Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold, and suppose that its boundary complex $\partial\calT$ is either empty or strongly connected.
+Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$.
+In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$.
+We write $\calT'$ be the  simplicial complex that contains $\calT \cup T$.
+We exclude the case $n \leq 1$ since otherwise the discussion is trivial.
+
+According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
+\begin{align*}
+    \begin{CD}
+        \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
+    \end{CD}
+\end{align*}
+We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to ${G}$. 
+By the nature of the mappings in the Mayer-Vietoris sequence, 
+\color{red}which uses some specific knowledge about the arrows\color{black}, 
+we see that 
+\begin{align*}
+    \begin{CD}
+        0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0 
+    \end{CD}
+\end{align*}
+is an exact sequence. 
+Moreover, $H_{k}(\calS) = H_{k}(T) = 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
+the Mayer-Vietoris sequence includes the exact sequence 
+\begin{align*}
+    \begin{CD}
+        0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow 0 
+    \end{CD}
+\end{align*}
+and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
+Finally, the Mayer-Vietoris sequence includes the exact sequence 
+\begin{align*}
+    \begin{CD}
+        0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT') \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT') \longrightarrow 0 
+    \end{CD}
+\end{align*}
+
+% Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
+% % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
+% Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+% one easily sees that $H_{0}(\calT') \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
+then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ are trivial and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
+Consider now the case that $\calS$ is isomorphic to a sphere.
+Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
+Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq \bbZ$.
+\color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
+Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
+
+In the case that $\calS$ is isomorphic to a disk, we have $H_{n-1}(\calS) = 0$,
+and then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T) = 0$ are trivial 
+and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
+Consider now the case that $\calS$ is isomorphic to a sphere.
+Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
+Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq {G}$.
+\color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
+Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
+
+We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
+\begin{align*}
+    H_0(\calT) \simeq \bbZ, 
+    \quad 
+    H_1(\calT) \simeq \dots \simeq H_{n-1}(\calT) \simeq 0.
+\end{align*}
+Moreover, $H_n(\calT) \simeq {G}$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise. 
+Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
+
+% then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
+% Moreover, Thus $H_{n}(\calT') = H_{n}(\calT) \oplus H_{n}(\calS)$.
+% We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
+% NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
+% \begin{align*}
+%     \begin{CD}
+%         0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT') \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0
+%     \end{CD}
+% \end{align*}
+
+\begin{remark}    
+    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq {G}$ because the respective simplicial complexes are path-connected. 
+    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
+    % one easily sees that $H_{0}(\calT') \simeq {G}$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$.
+
+    % then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
+    % Moreover, Thus $H_{n}(\calT') = H_{n}(\calT) \oplus H_{n}(\calS)$.
+    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
+    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
+    % \begin{align*}
+    %     \begin{CD}
+    %         0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT') \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0
+    %     \end{CD}
+    % \end{align*}
+\end{remark}

### 2024-06-15 main.tex
work on combinatorics

@@
 Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
-In practice, we not always distinguish between points and singleton simplices. % TODO: see whether being formally correct iis possible 
+In practice, we not always distinguish between points and singleton simplices. % TODO: see whether being formally correct is possible 
 Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.
@@
 
+The reason of our interest in shellable simplicial complexes is that they can be constructed by successive adhesion of simplices to intermediate complexes, 
+such that the interface is well-behaved: it is a simplicial disk or a simplicial sphere. 
+That leads to the following important consequence.
+
+% TODO: we only need some basic properties, namely that the construction maintains manifolds with boundary.
+% TODO: copy and adapt the content of Ziegler and Kozlov as necessary
+% The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
+
+\begin{lemma}    
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, 
+    then
+    $$
+        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}
+    $$ 
+    is a manifold with boundary for all $0 \leq m \geq M$.
+    % 
+    In particular, $X_{m}$ is a topological $n$-ball when $m < M$, 
+    and 
+    $X_{M}$ is either a topological $n$-ball or topological $n$-sphere. 
+\end{lemma}
+\begin{proof}  
+    We prove this claim by induction. 
+    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. 
+    Suppose that $X_m := T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a topological $n$-ball and that $T_{m+1}$ is the next $n$-simplex in the shelling.
+    By definition, $I_{m+1} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
+    and it is triangulated by some faces of $T_{m+1}$ and their subsimplices.
+
+    Let $F$ be such a face. 
+    By assumption, $F$ must be contained in exactly one $n$-simplex of $T_{0}, T_{1}, \dots, T_{m}$,
+    and $F$ is in the boundary of $X_{m}$. We conclude that $I_{m}$ triangulates a submanifold of the boundary of $X_{m}$.
+
+    On the one hand, 
+    if $I_{m+1}$ is the entire boundary of $T_{m+1}$, 
+    then it must also be the boundary of the topological $n$-ball $X_{m}$. 
+    Hence $X_{m} \cup T_{m+1}$ must be a topological $n$-sphere and thus a manifold without boundary, which requires $m = M$.
+    On the other hand, 
+    if $I_{m+1}$ is a proper subset of the entire boundary of $T_{m+1}$, 
+    then $X_{m} \cup T_{m+1}$ is still a topological $n$-ball.
+\end{proof}
+
 We collect important examples of shellable triangulations.
@@
 \begin{proof}
-    Let $\calT$ be a simplicial $2$-disk. 
-    If $\calT$ contains only one triangle, then there is nothing to show. 
-    Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
-    {\color{red}Needs proof}. 
+    First, 
+    let $\calS$ be any triangulation of a $2$-sphere. 
+    By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-disk.
+    Any shelling of that disk can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    So it remains to show that any triangulation $\calT$ of the two-dimensional disk is shellable. 
+    We will construct the shelling in reverse.
+
+    Write $M = |\calT|$. 
+    We call a triangle $T \in \calT$ \emph{good} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
+    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk contains a good triangle. 
+    Clearly, this is the case if the triangulation contains only one triangle. 
+    Now suppose the induction claim is true when the triangulation includes $N$ triangles,
+    and assume that $\calT$ includes $N+1$ triangles. 
+    There exists a triangle $T' \in \calT$ with at least one edge in the boundary. 
+    If $T'$ is good, then we are already done. 
+    Otherwise, $T'$ intersects the boundary at one edge and its opposing vertex.
+    Removing $T'$ splits the manifold into two pieces, each of which is a topological $2$-disk.
+    By the induction assumption, they contain a good triangle.
+
+    Since $\calT$ triangulates a $2$-disk,
+    it contains a good triangle $T$. 
+    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
+    If $T$ intersects with the boundary in exactly one or two edges, 
+    then $\overline{M \setminus T}$ is still a topological $2$-disk.
     Letting $\calT'$ be the triangulation obtained by removing $T$,
     we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
-    Repeating this procedure yields an enumeration of the triangles of $\calT$,
-    whose reverse is a shelling.
-
-    Now let $\calS$ be any simplicial $2$-sphere. 
-    By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
-    Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
+%     Let $\calT$ be a simplicial $2$-disk. 
+%     If $\calT$ contains only one triangle, then there is nothing to show. 
+%     Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
+%     {\color{red}Needs proof}.
+
+%     Now let $\calS$ be any simplicial $2$-sphere. 
+%     By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
+%     Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
 \end{proof}
@@
     Then the triangles of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-disk 
-    {\color{red}Needs proof},
     which is shellable,
@@
     We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
-\end{example}
-\begin{remark}
-    Patches around boundary simplices are not necessarily shellable when the dimension exceeds $3$.
+
     For example, there exists a non-shellable triangulation of a tetrahedron. 
@@
     then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-\end{remark}
-
-The reason of our interest in shellable simplicial complexes is that they can be constructed by successive adhesion of simplices to intermediate complexes, 
-such that the interface is well-behaved: it is a simplicial disk or a simplicial sphere. 
-That has the following important consequence.
-
-% TODO: we only need some basic properties, namely that the construction maintains manifolds with boundary.
-% TODO: copy and adapt the content of Ziegler and Kozlov as necessary
-
-\begin{lemma}
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is a manifold triangulation.
-    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is a manifold triangulation for every $m \geq 0$.
-\end{lemma}
-\begin{proof}    
-\end{proof}
-
-\begin{lemma}    
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
-    In particular, $T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a manifold with boundary for all $m \geq 0$.
-\end{lemma}
-\begin{proof}    
-\end{proof}
-
-% The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
-
-\subsection{On the topology of shellable triangulations}
-
-A shellable simplicial complex that triangulates a manifold has a very restricted topology. 
-The Mayer-Vietoris theorem implies restrictions on the homology groups of simplicial complexes iteratively constructed via shelling.
-
-    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, 
-    whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$. 
-    In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$. 
-    We write $\calT'$ for the  simplicial complex that contains $\calT \cup T$.
-
-Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold, and suppose that its boundary complex $\partial\calT$ is either empty or strongly connected.
-Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$.
-In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$.
-We write $\calT'$ be the  simplicial complex that contains $\calT \cup T$.
-We exclude the case $n \leq 1$ since otherwise the discussion is trivial.
-
-According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
-\begin{align*}
-    \begin{CD}
-        \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
-    \end{CD}
-\end{align*}
-We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to ${G}$. 
-By the nature of the mappings in the Mayer-Vietoris sequence, 
-\color{red}which uses some specific knowledge about the arrows\color{black}, 
-we see that 
-\begin{align*}
-    \begin{CD}
-        0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0 
-    \end{CD}
-\end{align*}
-is an exact sequence. 
-Moreover, $H_{k}(\calS) = H_{k}(T) = 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
-the Mayer-Vietoris sequence includes the exact sequence 
-\begin{align*}
-    \begin{CD}
-        0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow 0 
-    \end{CD}
-\end{align*}
-and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
-Finally, the Mayer-Vietoris sequence includes the exact sequence 
-\begin{align*}
-    \begin{CD}
-        0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT') \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT') \longrightarrow 0 
-    \end{CD}
-\end{align*}
-
-% Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
-% % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
-% Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
-% one easily sees that $H_{0}(\calT') \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
-Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
-then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ are trivial and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
-Consider now the case that $\calS$ is isomorphic to a sphere.
-Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
-Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq \bbZ$.
-\color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
-Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
-
-In the case that $\calS$ is isomorphic to a disk, we have $H_{n-1}(\calS) = 0$,
-and then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T) = 0$ are trivial 
-and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
-Consider now the case that $\calS$ is isomorphic to a sphere.
-Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$.
-Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq {G}$.
-\color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
-Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.
-
-We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
-\begin{align*}
-    H_0(\calT) \simeq \bbZ, 
-    \quad 
-    H_1(\calT) \simeq \dots \simeq H_{n-1}(\calT) \simeq 0.
-\end{align*}
-Moreover, $H_n(\calT) \simeq {G}$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise. 
-Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.
-
-% then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
-% Moreover, Thus $H_{n}(\calT') = H_{n}(\calT) \oplus H_{n}(\calS)$.
-% We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
-% NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
-% \begin{align*}
-%     \begin{CD}
-%         0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT') \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0
-%     \end{CD}
-% \end{align*}
-
-\begin{remark}    
-    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq {G}$ because the respective simplicial complexes are path-connected. 
-    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
-    % one easily sees that $H_{0}(\calT') \simeq {G}$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$.
-
-    % then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
-    % Moreover, Thus $H_{n}(\calT') = H_{n}(\calT) \oplus H_{n}(\calS)$.
-    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
-    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
-    % \begin{align*}
-    %     \begin{CD}
-    %         0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT') \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0
-    %     \end{CD}
-    % \end{align*}
+    This demonstrates that patches around boundary simplices are not necessarily shellable when the dimension exceeds $3$.
 \end{remark}

### 2024-06-18 draft.tex
some improvements

@@
 \end{remark}
+
+\section*{Theorem 8.1}
+
+\noindent \textbf{Theorem 8.1 (Discrete Poincaré inequality).} There holds
+\begin{align*}
+    \|g\|^2_{0,\Omega} 
+    \leq 
+    C_P |g|^2_{1,T} 
+    + 
+    \frac{4}{|\Omega|} \left( \int_{\Omega} g(x) \, dx \right)^2
+        \quad 
+    \forall g \in W(T_h), \forall h > 0
+\end{align*}
+with
+\begin{align*}
+C_P = 4C_d C_\Omega \frac{C_{d,T}}{\kappa_T} [\text{diam}(\Omega)]^2 + 8c_d h^2,
+\end{align*}
+where \(C_\Omega\) is given by (27) when \(\Omega\) is convex and by (28) otherwise, \(C_{d,T}\) is given by (12) when Assumption (B) is satisfied and by (15) in the general case, \(c_d\) is given by (22), and \(C_d\) is given by (26).
+\\
+
+\noindent Obviously
+\begin{align*}
+    \|g\|_{0,\Omega} 
+    \leq 
+    \|g - I(g)\|_{0,\Omega} + \|I(g)\|^2_{0,\Omega}
+    ,
+\end{align*}
+\begin{align*}
+    \|g\|^2_{0,\Omega} 
+    &\leq 
+    2\|g - I(g)\|^2_{0,\Omega} + 2\|I(g)\|^2_{0,\Omega} 
+    ,
+    \|g\|_{0,\Omega} 
+    &\leq
+    \sqrt{2}
+    \sqrt{ \|g - I(g)\|^2_{0,\Omega} + 2\|I(g)\|^2_{0,\Omega} }
+    .
+\end{align*}
+We apply the cellwise local approximation estimate, which coincides with the cellwise Poincare inequality:
+\begin{align*}
+    \|g - I(g)\|_{0,\Omega}
+    &\leq 
+    \frac{ h_T }{\pi}
+    \| \nabla_\calT g \|_{0,\Omega}
+    ,
+    \|g - I(g)\|_{0,\Omega}
+    &\leq 
+    \frac{ h_T }{\pi}
+    \| \nabla_\calT g \|_{0,\Omega}
+    .
+\end{align*}

### 2024-06-18 main.tex
fixes
some improvements

@@
 \title{Poincar\'e--Friedrichs constants over triangulated domains}
-\author{TCF, MWL, MV}
+\author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
 
@@
 \begin{document}
+
+\maketitle
 
@@
 \end{abstract}
-
-\maketitle
 
@@
 We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
-\[
+\begin{align*}
     \underlying{\calT} := \bigcup_{ T \in \calT } T
     .
-\]
+\end{align*}
 We call a set \textit{trianguable} if it is the underlying set of some triangulation.
@@
 For any enumeration, we call 
-\[
+\begin{align*}
     I_m 
@@
     T_{m+1}
-\]
+\end{align*}
 be the $m$-th \textit{interface set}. 
@@
 %     {\color{red}Needs proof}. 
-
+%   
 %     Now let $\calS$ be any simplicial $2$-sphere. 
@@
 
-\begin{example}
+\begin{remark}
     Not all trianguable sets admit a triangulation that is also shellable. 

### 2024-06-19 main.tex
Update on Overleaf.

--- 2024-06-15 main.tex
@@
 We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants over triangulated domains in Section~\ref{section:poincare}.
-We then review the notion of shellable triangulation in Section~\ref{section:shellable}.
+We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
 We construct an important geometric reflection operator in Section~\ref{section:extension}
@@
 we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-Clearly, strongly connected in $\calT$ is an equivalence relation.
-A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, and we call $\calT$ strongly connected if it has only one strongly connected component.
+We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
+Clearly, strongly connected in $\calT$ is an equivalence relation. A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
+and we call $\calT$ strongly connected if it has only one strongly connected component.
 
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
+    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
+    there exists a strong path $T_0, T_1, \dots, T_m = T$.
+    Then for any $u \in W^{1,p}(\Omega)$ 
+    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
+    and such that for all $T \in \calT$:
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}^{p}
+        &\leq 
+        (m+1)^{p-1}
+        \sum_{t=1}^{m} 
+        \left( 
+            \prod_{t < l \leq m} 
+            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
+        \right)
+        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
+        C_{p,T_{t} \cup T_{t+1}}
+        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
+        \\&\quad \quad \quad 
+        +
+        (m+1)^{p-1}
+        \left( 
+            \prod_{0 < l \leq m} 
+            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
+        \right)
+        C_{p,T_{0}}
+        \| \nabla u \|_{L^{p}(T_{0})}^{p}
+        .
+    \end{align*}
     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
-    For any $u \in W^{1,p}(\Omega)$ there exists $w \in W^{1,p}(\Omega)$
-    with $\nabla u = \nabla w$ and such that for all $T \in \calT$:
-    \begin{align*}
-        ...
-    \end{align*}
 \end{theorem}
@@
 
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
+    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
+    there exists a strong path $T_0, T_1, \dots, T_m = T$.
+    Then for any $u \in W^{1,p}(\Omega)$ 
+    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
+    and such that for all $T \in \calT$:
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}^{p}
+        &\leq 
+        (m+1)^{p-1}
+        \sum_{t=1}^{m} 
+        \left( 
+            \prod_{t < l \leq m} 
+            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
+        \right)
+        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
+        C_{p,T_{t} \cup T_{t+1}}
+        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
+        \\&\quad \quad \quad 
+        +
+        (m+1)^{p-1}
+        \left( 
+            \prod_{0 < l \leq m} 
+            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
+        \right)
+        C_{p,T_{0}}
+        \| \nabla u \|_{L^{p}(T_{0})}^{p}
+        .
+    \end{align*}
+    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
+\end{theorem}
+
+\begin{proof}
+    Let $u \in W^{1,p}(\Omega)$. 
+    Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
+We write $\Omega_m := \cup_{j=0}^{m} T_m$.
+Hence $\Omega = \Omega_M$.
+
+    Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$.
+Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
+    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$.
+
+    Let $\hat T$ be the reference simplex.
+    We fix affine homeomorphisms $\Phi_1 : \hat T \rightarrow T_1$ and $\Phi_2 : \hat T \rightarrow T_2$
+    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
+    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.
+
+    We define $u'_{m+1} := u_{{m}} \circ \Phi_1 \circ \Phi_2^{-1} \in W^{1,p}(T_{m+1})$. 
+    In particular, $u'_{m+1} \in W^{1,p}(T_{m+1})$ such that 
+    \begin{align*}
+        \trace_F u_{m} = \trace_F u'_{m+1}
+    \end{align*}
+    We will also use the bound 
+    \begin{align*}
+        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
+        &\leq 
+        |\det(\Dif \Phi_1)|^{-\frac 1 p} \cdot \| \Dif \Phi_1 \|
+        \cdot 
+        |\det(\Dif \Phi_2)|^{-\frac 1 p} \cdot \| \Dif \Phi_2 \|
+        \| \nabla u_{m} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Suppose that $u''_{m+1} \in W^{1,p}(T_{m+1})$ with 
+    \begin{align*}
+        \nabla u''_{m+1} = \nabla u - \nabla u'_{m+1}, 
+        \quad 
+        \trace_{F_{m}} u''_{m+1} = 0
+    \end{align*}
+    Such $u''_{m+1}$ exists because 
+    \begin{align*}
+        \trace_{F_{m}}( \nabla u - \nabla u'_{m+1} ) 
+        &= 
+        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla u'_{m+1}
+        \\&= 
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} u'_{m+1}
+        = 
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} u_{|m}
+        = 0
+        .
+    \end{align*}
+    Setting $u_{m+1} = u_{m}$ over $\Omega_{m}$ and $u_{m+1} = u'_{m+1} + u''_{m+1}$ over $T_{m+1}$, 
+    we find 
+    \begin{gather*}
+        \nabla u_{m+1} = \nabla u'_{m+1} + \nabla u''_{m+1} = \nabla u'_{m+1} + \nabla u - \nabla u'_{m+1} = \nabla u,
+        % \end{gather*}
+        \\
+        % \begin{gather*}
+        \trace_{F_{m}} u_{m+1} = \trace_{F_{m}} u'_{m+1} = \trace_{F_{m}} u_1.
+    \end{gather*}
+    We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
+    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi - u'_{m+1} \circ \Psi )$. 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$,
+    and extend that $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction, $\hat g$ is the gradient of a unique function in $w \in W^{1,p}$ that vanishes at the boundary of $\hat U$,
+    which satisfies Friedrichs inequality. In total, we utilize 
+    \begin{gather*}
+        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
+        \| w \|_{L^{p}(\hat T)}
+        ,
+        \qquad 
+        \| w \|_{L^{p}(\hat U)} 
+        \leq 
+        2 
+        \| \hat g \|_{\bfL^{p}(\hat U)}
+        ,
+        \\
+        \| \hat g \|_{\bfL^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{\bfL^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Dif \Psi_1)|^{-\frac 1 p} \cdot \| \Dif \Psi_1 \|
+        \| \nabla u - \nabla u'_{m+1} \|_{\bfL^{p}(T)}
+        .
+    \end{gather*}
+    We thus have
+    \begin{align*}
+        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
+        &
+        \leq 
+        \| \nabla u \|_{L^{p}(T_{m+1})} 
+        + 
+        2^{1+\frac n p}
+        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
+        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
+        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
+        \\&
+        \leq 
+        \| \nabla u \|_{L^{p}(T_{m+1})} 
+        + 
+        2^{1+\frac n p}
+        \| \Dif \Psi \|
+        \| \Dif \Psi \|
+        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
+        .
+    \end{align*}
+
+\end{proof}
+
 \begin{remark}
@@
 
-\section{Shellable triangulations}
+\section{Shellable triangulations}\label{section:advancedtriangulations}
 

### 2024-06-20 main.tex
some notes

@@
  We want to summarize the two integrals of $u_{F_m}$.
+
+ \newpage\color{red}
+ We want 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    \leq
+    \left( 
+        1 
+        + 
+        2
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$,
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    +
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq
+    \left( 
+        1 
+        + 
+        2
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \right)
+    \left( 
+        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
+        +
+        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
+        +
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    .
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{orange}
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    \leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$, 
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    +
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \right) 
+    \left( 
+        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
+        +
+        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{JungleGreen}
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq
+    \left( 
+        3
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    \\&
+    \leq
+    \left( 
+        3
+    \right)^{p/q}
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$, ????
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})}^{1}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{1}(T_{j(m)})}^{1}
+    \right)
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq
+    3
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{MidnightBlue}
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    \\&
+    \leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$, ????
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})} 
+        +
+        \| w_{m-1}\|_{L^{1}(T_{j(m)})} 
+    \right)
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq 
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \right) 
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
+        +
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{black}
  In the special case $p=1$,

### 2024-06-20 main.tex
Update on Overleaf.

--- 2024-06-19 main.tex
@@
 
+Upper bound for the classical Poincar\'e inequality over a simplex is easily found. 
+We can use it to compute an upper bound for the Poincar\'e--Friedrichs inequality 
+when homogeneous boundary conditions are imposed on a single face of the boundary.
+
+\begin{lemma}
+    Let $T$ be an $n$-simplex and with a face $F$. 
+    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
+    \begin{align*}
+        \| u \|_{L^{p}(T)}
+        &
+        \leq 
+        C_{\partial,p}
+        \diam(T) \| \nabla u \|_{L^{p}(T)}
+    \end{align*}
+    where 
+    \begin{align*}
+        C_{\partial,p}
+        \leq 
+        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
+        .
+    \end{align*}
+    % \begin{align*}
+    %     \| u \|_{L^{p}(T)}
+    %     &
+    %     \leq 
+    %     C_{?} \diam(T)
+    %     \| \nabla w \|_{\bfL^{p}(T)}
+    %     +
+    %     \| \gamma \|_{\bfL^{p}(T)}
+    %     \\&
+    %     \leq 
+    %     C_{?} \diam(T)
+    %     \| \nabla u \|_{\bfL^{p}(T)}
+    %     +
+    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
+    %     \diam(T)
+    %     \| \nabla w \|_{L^{p}(T)}
+    %     \\&
+    %     \leq 
+    %     C_{?} 
+    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
+    %     +
+    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
+    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
+    %     \\&
+    %     \leq 
+    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
+    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
+    %     .
+    % \end{align*}
+\end{lemma}
+\begin{proof}
+    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
+    \[
+        \| w \|_{L^{p}(T)}
+        \leq 
+        C_{?}
+        \| \nabla w \|_{\bfL^{p}(T)}
+        .
+    \]
+    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
+    We use that 
+    \[
+        \| \gamma \|_{L^{p}(T)}
+        =
+        \gamma \vol(T)^\frac{1}{p}
+        =
+        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
+        \cdot 
+        \gamma 
+        \vol(F)^\frac{1}{p}
+        \leq 
+        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
+        \| \gamma \|_{L^{p}(F)}
+        .
+    \]
+    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
+    \begin{align*}
+        \| \gamma \|_{L^{p}(F)}^{p}
+        &
+        \leq 
+        \frac{ \vol(F) }{ \vol(T) }
+        \| w \|_{L^{p}(T)}^{p}
+        +
+        p
+        \cdot 
+        \diam(T)
+        \frac{ \vol(F) }{ \vol(T) }
+        \| w \|_{L^{p}(T)}^{p-1}
+        \| \nabla w \|_{L^{p}(T)}
+        \\&
+        \leq 
+        \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right) 
+        \diam(T)^{p}
+        \left( \frac{ \vol(F) }{ \vol(T) } \right)
+        \| \nabla w \|_{L^{p}(T)}^{p}
+        .
+    \end{align*}
+    Recall that $u = w - \gamma$. The desired result follows. 
+\end{proof}
+
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
@@
     Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
-We write $\Omega_m := \cup_{j=0}^{m} T_m$.
-Hence $\Omega = \Omega_M$.
-
-    Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$.
-Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
+    We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.
+
+    First, there exists $w_0 \in W^{1,p}(T_{0})$ such that $\nabla w_{0} = \nabla u$ over $\Omega_0$. 
+    Suppose that $0 \leq m < M$ such that there exists $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_m$. 
+    Hence $w_{m} - u_{|\Omega_{m}}$ is a constant.
+
     By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
-
     Let $\hat T$ be the reference simplex.
-    We fix affine homeomorphisms $\Phi_1 : \hat T \rightarrow T_1$ and $\Phi_2 : \hat T \rightarrow T_2$
-    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
-    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.
-
-    We define $u'_{m+1} := u_{{m}} \circ \Phi_1 \circ \Phi_2^{-1} \in W^{1,p}(T_{m+1})$. 
-    In particular, $u'_{m+1} \in W^{1,p}(T_{m+1})$ such that 
-    \begin{align*}
-        \trace_F u_{m} = \trace_F u'_{m+1}
-    \end{align*}
-    We will also use the bound 
-    \begin{align*}
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
-        &\leq 
-        |\det(\Dif \Phi_1)|^{-\frac 1 p} \cdot \| \Dif \Phi_1 \|
-        \cdot 
-        |\det(\Dif \Phi_2)|^{-\frac 1 p} \cdot \| \Dif \Phi_2 \|
-        \| \nabla u_{m} \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Suppose that $u''_{m+1} \in W^{1,p}(T_{m+1})$ with 
-    \begin{align*}
-        \nabla u''_{m+1} = \nabla u - \nabla u'_{m+1}, 
+    We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
+    each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
+    We define $w'_{m+1} := w_{{m}} \circ \Phi \circ \Theta^{-1} \in W^{1,p}(T_{m+1})$. 
+    %
+    {\color{blue}We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
+    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. }
+    %
+    By construction, $w'_{m+1} \in W^{1,p}(T_{m+1})$ with 
+    \begin{align*}
+        \trace_F w_{m} = \trace_F w'_{m+1}
+        .
+    \end{align*}
+    Suppose that $w''_{m+1} = u - w'_{m+1} \in W^{1,p}(T_{m+1})$.
+    It satisfies 
+    \begin{align*}
+        \nabla w''_{m+1} = \nabla u - \nabla w'_{m+1}, 
         \quad 
-        \trace_{F_{m}} u''_{m+1} = 0
-    \end{align*}
-    Such $u''_{m+1}$ exists because 
-    \begin{align*}
-        \trace_{F_{m}}( \nabla u - \nabla u'_{m+1} ) 
+        \trace_{F_{m}} w''_{m+1} = 0.
+    \end{align*}
+    The trace condition holds because 
+    \begin{align*}
+        \trace_{F_{m}}( \nabla u - \nabla w'_{m+1} ) 
         &= 
-        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla u'_{m+1}
+        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m+1}
         \\&= 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} u'_{m+1}
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m+1}
         = 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} u_{|m}
-        = 0
-        .
-    \end{align*}
-    Setting $u_{m+1} = u_{m}$ over $\Omega_{m}$ and $u_{m+1} = u'_{m+1} + u''_{m+1}$ over $T_{m+1}$, 
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m}
+        = 
+        0
+        .
+    \end{align*}
+    Setting $w_{m+1} := w_{m}$ over $\Omega_{m}$ and $w_{m+1} := w'_{m+1} + w''_{m+1}$ over $T_{m+1}$, 
     we find 
     \begin{gather*}
-        \nabla u_{m+1} = \nabla u'_{m+1} + \nabla u''_{m+1} = \nabla u'_{m+1} + \nabla u - \nabla u'_{m+1} = \nabla u,
+        \nabla w_{m+1} = \nabla w'_{m+1} + \nabla w''_{m+1} = \nabla w'_{m+1} + \nabla u - \nabla w'_{m+1} = \nabla u,
         % \end{gather*}
@@
         % \begin{gather*}
-        \trace_{F_{m}} u_{m+1} = \trace_{F_{m}} u'_{m+1} = \trace_{F_{m}} u_1.
+        \trace_{F_{m}} w_{m+1} = \trace_{F_{m}} w'_{m+1} = \trace_{F_{m}} w_{m}.
     \end{gather*}
+    That means that $w_{m+1} \in W^{1,p}(\Omega_{m+1})$ with $\nabla w_{m+1} = \nabla u$ over $\Omega_{m+1}$. 
+    As we will show soon, there exists $D_{m+1} > 0$ such that 
+    \begin{gather*}
+        \| u''_{m+1} \|_{L^{p}(T_{m+1})} 
+        \leq 
+        D_{m+1} \diam(T_{m+1}) \cdot \| \nabla u - \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}.
+    \end{gather*}
+    Therefore, 
+    \begin{align*}
+        \| u''_{m+1} \|_{L^{p}(T_{m+1})}  
+        &
+        \leq 
+        D_{m+1} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
+        + 
+        D_{m+1} \diam(T_{m+1}) \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})} 
+        .
+    \end{align*}
+    We use also the inequality 
+    \begin{align*}
+        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
+        &\leq 
+        |\det(\Dif \Phi  )|^{-\frac 1 p} \cdot \| \Dif \Phi   \|
+        \cdot 
+        |\det(\Dif \Theta)|^{ \frac 1 p} \cdot \| \Dif \Theta^{-1} \|
+        \| \nabla u_{m} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Putting this all together, 
+    \begin{align*}
+        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
+        &\leq 
+        \frac{ \vol(T_{m+1})^{\frac 1 p} }{ \vol(T_{m})^{\frac 1 p} } 
+        \cdot 
+        \| \Dif \Phi   \|
+        \cdot 
+        \| \Dif \Theta^{-1} \|
+        \| \nabla u_{m} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    % TODO: Finish the recursion
+
     We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
@@
     \end{align*}
-
+    We will also use the bound.  
 \end{proof}

### 2024-06-21 main.tex
improved inequality

@@
     \end{align*}
-    where 
+    where $C_{\partial,p} > 0$ is a constant such that 
     \begin{align*}
@@
         \leq 
-        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
+        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right),
+        \quad 
+        C_{\partial,p}
+        \leq 
+        2^{\frac n p}
         .
@@
     \end{align*}
-    Recall that $u = w - \gamma$. The desired result follows. 
+    Recall that $u = w - \gamma$. The first inequality follows.
+
+    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \Psi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi )$. 
+    Then $\nabla \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordiante axes.
+    We define $\tilde g = \nabla \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\hat U)} 
+        \leq 
+        2 
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        .
+    \end{gather*}
+    In addition to that, 
+    \begin{gather*}
+        \| u \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Dif \Psi)|^{\frac 1 p} 
+        \| \hat u \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Dif \Psi)|^{\frac 1 p} 
+        \| \tilde u \|_{L^{p}(\hat U)}
+        ,
+        \\
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{\bfL^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Dif \Psi_1)|^{-\frac 1 p} \| \Dif \Psi \| \cdot 
+        \| \nabla u \|_{\bfL^{p}(T)}
+        .
+    \end{gather*}
+    The second inequality follows.
 \end{proof}
@@
 
-    We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
-    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi - u'_{m+1} \circ \Psi )$. 
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$,
-    and extend that $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction, $\hat g$ is the gradient of a unique function in $w \in W^{1,p}$ that vanishes at the boundary of $\hat U$,
-    which satisfies Friedrichs inequality. In total, we utilize 
-    \begin{gather*}
-        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
-        \| w \|_{L^{p}(\hat T)}
-        ,
-        \qquad 
-        \| w \|_{L^{p}(\hat U)} 
-        \leq 
-        2 
-        \| \hat g \|_{\bfL^{p}(\hat U)}
-        ,
-        \\
-        \| \hat g \|_{\bfL^{p}(\hat U)}
-        \leq 
-        2^{\frac n p}
-        \| \hat g \|_{\bfL^{p}(\hat T)}
-        \leq 
-        2^{\frac n p}
-        |\det(\Dif \Psi_1)|^{-\frac 1 p} \cdot \| \Dif \Psi_1 \|
-        \| \nabla u - \nabla u'_{m+1} \|_{\bfL^{p}(T)}
-        .
-    \end{gather*}
-    We thus have
-    \begin{align*}
-        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
-        &
-        \leq 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
-        + 
-        2^{1+\frac n p}
-        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
-        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
-        \\&
-        \leq 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
-        + 
-        2^{1+\frac n p}
-        \| \Dif \Psi \|
-        \| \Dif \Psi \|
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
-        .
-    \end{align*}
-    We will also use the bound.  
 \end{proof}

### 2024-06-21 main.tex
Update on Overleaf.

--- 2024-06-20 main.tex
@@
     if we do not require our simplicial complexes to be finite,
-    then our definition would be considerably more permissive than the typical definitions in topology. 
+    then a reasonable definition of simplicial complex would need additional topological conditions. 
     % 
-    For example, if we allowed simplicial complex to be infinite, 
+    For example, if we modify our definition of simplicial complex to be infinite, 
     then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
@@
     % 
-    However, none of these infinite families are simplicial complexes in the sense of topology~\cite{spanier1966homology}. 
+    However, none of these infinite families are infinite simplicial complexes in the sense of topology~\cite{spanier1966homology}. 
 \end{remark}
@@
 We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
-\color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}
 
@@
 However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any linear potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
+Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
 satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
@@
 
-In the light of these musings, we can clarify that our objective is the construction of linear potential operators for the gradient and later for the curl and divergence operators. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+In the light of these musings, we clarify that our objective is the construction of linear potential operators for the gradient and later for the curl and divergence operators,
+which is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
 The potential reconstruction is the natural approach towards the topic when addressing the curl and divergence operators.
@@
 We now collect examples for Poincar\'e--Friedrichs inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
-Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
 \begin{align}\label{math:acostaduran}
@@
     \quad 
-    u \in W^{1,2}(\Omega)
+    u \in W^{1,1}(\Omega)
     ,
@@
 These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
+Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite{chua2006estimates}:
 \begin{align}\label{math:chuawheeden}
@@
 \end{align}
-In addition to that,
-according to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
+The literature knows optimal Poincar\'e--Friedrichs constants over convex domains. 
+According to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
 \begin{align}\label{math:esposito:pf}
@@
 \end{align}
-where 
+where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
 \begin{align}
@@
 \end{align}
-The constant $C_{\rm{EFNT},p}$ is the best possible. 
 Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
@@
 The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-Finally,
-since convex domains are Lipschitz domains, we may estimate 
+Finally, since convex domains are Lipschitz domains: 
 \begin{align}\label{math:lipschitzestimate}
@@
 
-Given a gradient vector field, we can reconstructed the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
+Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
 This defines a scalar potential.
@@
 After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed so far.
+This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed in intermediate steps.
 Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion. 
-
-We have already seen a survey of Poincar\'e inequalities over convex domains. 
-Slightly more generally, we are interested in such inequalities over face patches within simplicial triangulations. 
-We state a geometric auxiliary lemma and an estimate of Poincar\'e--Friedrichs constants over face patches 
-that captures the correct asymptotic behavior as $p$ grows to infinity.
+\\
+
+We achieve this goal via several auxiliary results. 
+We start with a few geometric observations that pertain to the mesh regularity. 
+Whenever $T$ is an $n$-dimensional simplex, we define the quantity 
+\begin{align*}
+    \mu(T)
+    := 
+    \frac{ \diam(T)^n }{ n! \vol(T) }
+    .
+\end{align*}
+Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
+\begin{align*}
+    \mu(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \mu(T),
+    \qquad 
+    \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
+    \qquad 
+    \kappa(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
+\end{align*}
+
+\begin{lemma}\label{lemma:affinetransform}
+    Let $T$ be an $n$-simplex and let $\Psi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
+    \begin{align*}
+        \| \Jacobian \Psi \|
+        \leq 
+        \sqrt{n} \cdot \diam(T)
+        ,
+        \qquad 
+        \| \Jacobian \Psi^{-1} \|
+        \leq 
+        \sqrt{2n^n} 
+        % \frac{ n! \vol(T) } { \diam(T)^n }
+        \mu(T)^{-1}
+        \diam(T)^{-1}
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Psi$ in descending order.
+    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Psi)$. Hence 
+    \[
+        \diam(T) 
+        \leq 
+        \sqrt{2} \sigma_1 
+        \leq 
+        \sqrt{2} 
+        \frac{ \sigma_1^n }{ \det(\Jacobian\Psi) } 
+        \sigma_n
+        \leq 
+        \sqrt{2n^n} 
+        \frac{ \diam(T)^n }{ n! \vol(T) } 
+        \sigma_n
+        .
+    \]
+    The desired result is thus evident. 
+\end{proof}
 
@@
         \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
+        &\leq 
         \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
@@
         \frac{\diam(T_2)^n}{n! \vol(T_2)} 
+        \leq 
+        \mu(T_1) \mu(T_2)
+        ,
+        \\
+        \diam(T_1)
+        &\leq 
+        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
+        \diam(F)
+        \leq 
+        \mu(T_1)
+        \diam(F)
+        .
+    \end{align*}
+    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
+    \begin{align*}
+        \| \Jacobian \Xi \|
+        \leq 
+        \sqrt{2n^{n+1}} 
+        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
+        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
+        \leq 
+        \sqrt{2n^{n+1}} 
+        \frac{ \mu(T_1) }{ \mu(T_2) }
         .
@@
     Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    Then $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
+    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
     We estimate 
@@
     \end{align*}
-    The desired estimate follows. 
+    The first estimate follows. 
+    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
+    \begin{align*}
+        \diam(F)
+        \geq 
+        h
+        =
+        n!
+        \frac{ \vol(T_1) }{ \vol(F') }
+        \geq 
+        \frac{ n! \vol(T_1) }{ \diam(T_1)^n }
+        \cdot 
+        \diam(T_1)
+        .
+    \end{align*}
+    That shows the second estimate. 
+    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
+    \begin{align*}
+        \| \Jacobian \Xi \|
+        &
+        \leq 
+        \sqrt{n} 
+        \cdot 
+        \diam(T_1)
+        \sqrt{2n^n} 
+        \frac{ n! \vol(T_2) } {\diam(T_2)^n } 
+        \diam(T_2)^{-1}
+        \\&
+        \leq 
+        \sqrt{n} 
+        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
+        \diam(F)
+        \sqrt{2n^n} \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
+        \diam(F)^{-1}
+        \leq 
+        \sqrt{2n^{n+1}}
+        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
+        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
+        .
+    \end{align*}
+    All the desired results thus follow. 
     % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
@@
 \begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}. 
+    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\mu(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    In our convention, the reference simplex has unit shape measure.
     This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
@@
 \end{remark}
+
+We have already seen a survey of Poincar\'e inequalities over convex domains. 
+Slightly more generally, we are interested in such inequalities over face patches within simplicial triangulations. 
+We state a geometric auxiliary lemma and an estimate of Poincar\'e--Friedrichs constants over face patches 
+that captures the correct asymptotic behavior as $p$ grows to infinity.
 
@@
 \end{lemma}
-
 \begin{proof}
@@
     This gives the desired result. 
-
 \end{proof}
@@
 \begin{figure}[t]
+\begin{center}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+\end{center}
 \caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
@@
     \end{align*}
-    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
 \end{theorem}
@@
 
-Upper bound for the classical Poincar\'e inequality over a simplex is easily found. 
-We can use it to compute an upper bound for the Poincar\'e--Friedrichs inequality 
+We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains,
+While the underlying idea remains the same, the construction of the potential is slightly different. 
+As an auxiliary result with independent relevance, we compute an upper bound for the Poincar\'e--Friedrichs inequality 
 when homogeneous boundary conditions are imposed on a single face of the boundary. 
-
-\begin{lemma}
+% Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.
+
+\begin{lemma}\label{lemma:mixedbconsimplex}
     Let $T$ be an $n$-simplex and with a face $F$. 
@@
         \leq 
+        C_{{\rm PF},T,F,p} \diam(T) \| \nabla u \|_{L^{p}(T)}
+    \end{align*}
+    where 
+    \begin{align*}
         C_{\partial,p}
-        \diam(T) \| \nabla u \|_{L^{p}(T)}
-    \end{align*}
-    where 
-    \begin{align*}
-        C_{\partial,p}
-        \leq 
-        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
+        \leq 
+        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right) 
         .
@@
         \leq 
-        C_{?}
+        C_{{\rm PF},T,p} 
         \| \nabla w \|_{\bfL^{p}(T)}
@@
         \leq 
-        \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right) 
+        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
         \diam(T)^{p}
@@
 \end{proof}
+
+The following potential construction and upper bound for the Poincar\'e--Friedrichs constant 
+serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
 
@@
         \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
-        C_{p,T_{t} \cup T_{t+1}}
+        C_{{\rm PF},T_{t} \cup T_{t+1},p}
         \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
@@
         \right)
-        C_{p,T_{0}}
+        C_{{\rm PF},T_{0},p}
         \| \nabla u \|_{L^{p}(T_{0})}^{p}
@@
     Let $\hat T$ be the reference simplex.
-    We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
-    each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
-    We define $w'_{m+1} := w_{{m}} \circ \Phi \circ \Theta^{-1} \in W^{1,p}(T_{m+1})$. 
+    % We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
+    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
     %
-    {\color{blue}We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
-    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. }
+    We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
+    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. 
     %
@@
     That means that $w_{m+1} \in W^{1,p}(\Omega_{m+1})$ with $\nabla w_{m+1} = \nabla u$ over $\Omega_{m+1}$. 
-    As we will show soon, there exists $D_{m+1} > 0$ such that 
-    \begin{gather*}
-        \| u''_{m+1} \|_{L^{p}(T_{m+1})} 
-        \leq 
-        D_{m+1} \diam(T_{m+1}) \cdot \| \nabla u - \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}.
-    \end{gather*}
-    Therefore, 
-    \begin{align*}
-        \| u''_{m+1} \|_{L^{p}(T_{m+1})}  
+    Lemma~\ref{lemma:mixedbconsimplex} gives 
+    \begin{align*}
+        \| w''_{m+1} \|_{L^{p}(T_{m+1})} 
         &
         \leq 
-        D_{m+1} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
-        + 
-        D_{m+1} \diam(T_{m+1}) \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})} 
-        .
-    \end{align*}
-    We use also the inequality 
-    \begin{align*}
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u - \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}.
+        \\&
+        \leq 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
+        + 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
+        .
+    \end{align*}
+    We use also employ Lemma~\ref{lemma:volumecomparison} to find 
+    \begin{align*}
+        \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}
         &\leq 
-        |\det(\Dif \Phi  )|^{-\frac 1 p} \cdot \| \Dif \Phi   \|
+        |\det(\Dif \Xi  )|^{-\frac 1 p} 
+        \| \Dif \Xi   \|
         \cdot 
-        |\det(\Dif \Theta)|^{ \frac 1 p} \cdot \| \Dif \Theta^{-1} \|
-        \| \nabla u_{m} \|_{L^{p}(T_{m})}
+        \| \nabla w_{m} \|_{L^{p}(T_{m})}
+        \\&\leq 
+        \kappa(\calT)^{1+\frac 1 p} 
+        \sqrt{2n^{n+1}} 
+        \cdot 
+        \| \nabla w_{m} \|_{L^{p}(T_{m})}
         .
@@
     \begin{align*}
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
-        &\leq 
-        \frac{ \vol(T_{m+1})^{\frac 1 p} }{ \vol(T_{m})^{\frac 1 p} } 
+        &
+        \| w_{m+1} \|_{L^{p}(T_{m+1})}
+        \\&
+        \leq  
+        \| w'_{m+1} \|_{L^{p}(T_{m+1})}
+        + 
+        \| w''_{m+1} \|_{L^{p}(T_{m+1})}
+        \\&
+        \leq  
+        \kappa(\calT) 
+        \| w_{m} \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \| \nabla u \|_{L^{p}(T_{m+1})} 
+        + 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
+        \\&
+        \leq  
+        \kappa(\calT) 
+        \| w_{m} \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \| \nabla u \|_{L^{p}(T_{m+1})} 
+        + 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \kappa(\calT)^{1+\frac 1 p} 
+        \sqrt{2n^{n+1}} 
         \cdot 
-        \| \Dif \Phi   \|
-        \cdot 
-        \| \Dif \Theta^{-1} \|
-        \| \nabla u_{m} \|_{L^{p}(T_{m})}
+        \| \nabla w_{m} \|_{L^{p}(T_{m})} 
+        \\&
+        \leq  
+        \kappa(\calT) 
+        \| w_{m} \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \left( 1 + \kappa(\calT)^{1+\frac 1 p} \sqrt{2n^{n+1}} \right) 
+        \| \nabla u \|_{L^{p}(T_{m+1})} 
         .
@@
     % TODO: Finish the recursion 
-
-    We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
-    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi - u'_{m+1} \circ \Psi )$. 
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$,
-    and extend that $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction, $\hat g$ is the gradient of a unique function in $w \in W^{1,p}$ that vanishes at the boundary of $\hat U$,
-    which satisfies Friedrichs inequality. In total, we utilize 
-    \begin{gather*}
-        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
-        \| w \|_{L^{p}(\hat T)}
-        ,
-        \qquad 
-        \| w \|_{L^{p}(\hat U)} 
-        \leq 
-        2 
-        \| \hat g \|_{\bfL^{p}(\hat U)}
-        ,
-        \\
-        \| \hat g \|_{\bfL^{p}(\hat U)}
-        \leq 
-        2^{\frac n p}
-        \| \hat g \|_{\bfL^{p}(\hat T)}
-        \leq 
-        2^{\frac n p}
-        |\det(\Dif \Psi_1)|^{-\frac 1 p} \cdot \| \Dif \Psi_1 \|
-        \| \nabla u - \nabla u'_{m+1} \|_{\bfL^{p}(T)}
-        .
-    \end{gather*}
-    We thus have
-    \begin{align*}
-        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
-        &
-        \leq 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
-        + 
-        2^{1+\frac n p}
-        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
-        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
-        \\&
-        \leq 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
-        + 
-        2^{1+\frac n p}
-        \| \Dif \Psi \|
-        \| \Dif \Psi \|
-        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
-        .
-    \end{align*}
     We will also use the bound.  
@@
 \begin{remark}
-    The previous result depends on only a few parameters of the triangulation:
-    the length of any traversal from the root simplex,
-    the ratios of the volumes of adjacent simplices,
+    The previous theorems, Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} and Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} 
+    depend on only a few parameters of the triangulation:
+    the length of any traversal from the root simplex, the ratios of the volumes of adjacent simplices,
     the Poincar\'e constants on each face patch, and the Poincar\'e constant of the initial simplex. 

### 2024-06-21 main.tex

@@
         \leq 
-        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right) 
+        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right),  
+        \quad 
+        C_{\partial,p}
+        \leq 
+        2^{\frac n p}
         .
@@
     \end{align*}
-    We use also employ Lemma~\ref{lemma:volumecomparison} to find 
+    We also employ Lemma~\ref{lemma:volumecomparison} to find 
     \begin{align*}
@@
         \| \nabla w_{m} \|_{L^{p}(T_{m})}
-        \\&\leq 
-        \kappa(\calT)^{1+\frac 1 p} 
-        \sqrt{2n^{n+1}} 
+        \leq 
+        \kappa(\calT)^{\frac 1 p} \xi(\calT)
         \cdot 
@@
         \leq  
-        \kappa(\calT) 
+        \kappa(\calT)^{\frac 1 p} 
         \| w_{m} \|_{L^{p}(T_{m})} 
@@
         C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \left( 
             \| \nabla u \|_{L^{p}(T_{m+1})} 
             + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
             \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
+        \right) 
         \\&
         \leq  
-        \kappa(\calT) 
+        \kappa(\calT)^{\frac 1 p} 
         \| w_{m} \|_{L^{p}(T_{m})} 
         + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        C_{{\rm PF},T,F,p} 
+        \left( 1 + \kappa(\calT)^{\frac 1 p} \xi(\calT) \right) 
+        \diam(T_{m+1}) 
         \| \nabla u \|_{L^{p}(T_{m+1})} 
-        + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
-        \kappa(\calT)^{1+\frac 1 p} 
-        \sqrt{2n^{n+1}} 
-        \cdot 
-        \| \nabla w_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \kappa(\calT) 
-        \| w_{m} \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
-        \left( 1 + \kappa(\calT)^{1+\frac 1 p} \sqrt{2n^{n+1}} \right) 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
         .
@@
     % TODO: Finish the recursion 
-    We will also use the bound.  
 \end{proof}

### 2024-06-22 main.tex
some progress

--- 2024-06-21 main.tex
@@
 
-We achieve this goal via several auxiliary results. 
-We start with a few geometric observations that pertain to the mesh regularity. 
-Whenever $T$ is an $n$-dimensional simplex, we define the quantity 
-\begin{align*}
-    \mu(T)
+Towards this goal, we introduce quantitative measures for the geometric quality of triangulations,
+which give an indication of the regularity of simplex shapes. 
+Most of such \emph{shape measures} in the literature are based on geometric features, 
+but we consider indicators based on affine transformations associated with the mesh;
+this is because the properties of these transformations are what shows up in our estimates.
+
+Whenever $T$ is an $n$-dimensional simplex 
+\begin{align*}
+    \kappa(T)
     := 
@@
 \begin{align*}
-    \mu(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \mu(T),
+    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
+%     \qquad 
+%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
     \qquad 
-    \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
+    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
+\end{align*}
+Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
+that preserves $F$. We define 
+\begin{align*}
+    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
+\end{align*}
+This indicator quantifies how much reflection across the shared face distorts the goemetry.
+
+% and $\Phi : \Delta^n \rightarrow T$ is an affine diffeomorphism from the reference simplex,
+% we define the quantity 
+% \begin{align*}
+%     \kappa(T)
+%     := 
+%     \frac{ \diam(T)^n }{ n! \vol(T) }
+%     .
+% \end{align*}
+
+\begin{lemma}\label{lemma:affinetransform}
+    Let $T$ be an $n$-simplex and let $\Phi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
+    \begin{align*}
+        \| \Jacobian \Phi \|
+        \leq 
+        \sqrt{n} \cdot \diam(T)
+        ,
         \qquad 
-    \kappa(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
-\end{align*}
-
-\begin{lemma}\label{lemma:affinetransform}
-    Let $T$ be an $n$-simplex and let $\Psi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
-    \begin{align*}
-        \| \Jacobian \Psi \|
-        \leq 
-        \sqrt{n} \cdot \diam(T)
-        ,
-        \qquad 
-        \| \Jacobian \Psi^{-1} \|
+        \| \Jacobian \Phi^{-1} \|
         \leq 
@@
         % \frac{ n! \vol(T) } { \diam(T)^n }
-        \mu(T)^{-1}
+        \kappa(T)^{-1}
         \diam(T)^{-1}
@@
 \begin{proof}
-    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Psi$ in descending order.
-    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Psi)$. Hence 
+    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
+    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Phi)$. Hence 
     \[
@@
         \sqrt{2} 
-        \frac{ \sigma_1^n }{ \det(\Jacobian\Psi) } 
+        \frac{ \sigma_1^n }{ \det(\Jacobian\Phi) } 
         \sigma_n
@@
         \leq 
-        \mu(T_1) \mu(T_2)
+        \kappa(T_1) \kappa(T_2)
         ,
@@
         \leq 
-        \mu(T_1)
+        \kappa(T_1)
         \diam(F)
@@
         \sqrt{2n^{n+1}} 
-        \frac{ \mu(T_1) }{ \mu(T_2) }
+        \frac{ \kappa(T_1) }{ \kappa(T_2) }
         .
@@
     % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\mu(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
     In our convention, the reference simplex has unit shape measure.
@@
         2 C_{\rm{EFNT},p}
-        \left( 
-            \frac{\diam(T_1)^n}{n! \vol(T_1)} 
-            \frac{\diam(T_2)^n}{n! \vol(T_2)} 
-        \right)^{\frac 1 p}
+        \rho(\calT)^{\frac 1 p}
         \max\left( \diam(T_1), \diam(T_2) \right)
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
     Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    there exists a strong path $T_0, T_1, \dots, T_m = T$.
+    we fix a strong path $T_0, T_1, \dots, T_m = T$.
     Then for any $u \in W^{1,p}(\Omega)$ 
@@
  \end{align*}
- We want to summarize the two integrals of $u_{F_m}$. 
+ We summarize the two integrals of $u_{F_m}$. 
+ % 
  In the special case $p=1$,
@@
         \leq 
-        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right) 
-        .
-    \end{align*}
-    % \begin{align*}
-    %     \| u \|_{L^{p}(T)}
-    %     &
-    %     \leq 
-    %     C_{?} \diam(T)
-    %     \| \nabla w \|_{\bfL^{p}(T)}
-    %     +
-    %     \| \gamma \|_{\bfL^{p}(T)}
-    %     \\&
-    %     \leq 
-    %     C_{?} \diam(T)
-    %     \| \nabla u \|_{\bfL^{p}(T)}
-    %     +
-    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
-    %     \diam(T)
-    %     \| \nabla w \|_{L^{p}(T)}
-    %     \\&
-    %     \leq 
-    %     C_{?} 
-    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
-    %     +
-    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
-    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
-    %     \\&
-    %     \leq 
-    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
-    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
-    %     .
-    % \end{align*}
+        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right),  
+        \quad 
+        C_{\partial,p}
+        \leq 
+        2^{\frac n p}
+        .
+    \end{align*}
 \end{lemma}
@@
     \end{align*}
-    Recall that $u = w - \gamma$. The desired result follows. 
+    Recall that $u = w - \gamma$. The first inequality follows.
+
+    There exists $\Phi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \Phi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Phi )$. 
+    Then $\nabla \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    We define $\tilde g = \nabla \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\hat U)} 
+        \leq 
+        2 
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        .
+    \end{gather*}
+    In addition to that, 
+    \begin{gather*}
+        \| u \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Dif \Phi)|^{\frac 1 p} 
+        \| \hat u \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Dif \Phi)|^{\frac 1 p} 
+        \| \tilde u \|_{L^{p}(\hat U)}
+        ,
+        \\
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{\bfL^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Dif \Phi_1)|^{-\frac 1 p} \| \Dif \Phi \| \cdot 
+        \| \nabla u \|_{\bfL^{p}(T)}
+        .
+    \end{gather*}
+    The second inequality follows.
 \end{proof}
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly connected finite triangulation $\calT$.
     Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    there exists a strong path $T_0, T_1, \dots, T_m = T$.
+    we fix a strong path $T_0, T_1, \dots, T_m = T$.
     Then for any $u \in W^{1,p}(\Omega)$ 
@@
     \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}^{p}
+        \| w_{m} \|_{L^{p}(T_m)}
         &\leq 
-        (m+1)^{p-1}
-        \sum_{t=1}^{m} 
-        \left( 
-            \prod_{t < l \leq m} 
-            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
-        \right)
-        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
-        C_{{\rm PF},T_{t} \cup T_{t+1},p}
-        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
-        \\&\quad \quad \quad 
+        \sum_{l=1}^{m} 
+        \rho(\calT)^{\frac{m-l}{p}}
+        C_{{\rm PF},T,p} \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) \diam(T_{0})
+        \| \nabla u \|_{L^{p}( T_{l} )}
         +
-        (m+1)^{p-1}
-        \left( 
-            \prod_{0 < l \leq m} 
-            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
-        \right)
-        C_{{\rm PF},T_{0},p}
-        \| \nabla u \|_{L^{p}(T_{0})}^{p}
+        \rho(\calT)^{\frac m p}
+        C_{{\rm PF},T_{0},p} \diam(T_{0})
+        \| \nabla u \|_{L^{p}( T_{0} )}
         .
@@
         \| \nabla w_{m} \|_{L^{p}(T_{m})}
-        \\&\leq 
-        \kappa(\calT)^{1+\frac 1 p} 
-        \sqrt{2n^{n+1}} 
+        \leq 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
         \cdot 
@@
         \leq  
-        \kappa(\calT) 
+        \rho(\calT)^{\frac 1 p} 
         \| w_{m} \|_{L^{p}(T_{m})} 
@@
         C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \left( 
             \| \nabla u \|_{L^{p}(T_{m+1})} 
             + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
             \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
+        \right) 
         \\&
         \leq  
-        \kappa(\calT) 
+        \rho(\calT)^{\frac 1 p} 
         \| w_{m} \|_{L^{p}(T_{m})} 
         + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        C_{{\rm PF},T,F,p} 
+        \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+        \diam(T_{m+1}) 
         \| \nabla u \|_{L^{p}(T_{m+1})} 
-        + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
-        \kappa(\calT)^{1+\frac 1 p} 
-        \sqrt{2n^{n+1}} 
-        \cdot 
-        \| \nabla w_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \kappa(\calT) 
-        \| w_{m} \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
-        \left( 1 + \kappa(\calT)^{1+\frac 1 p} \sqrt{2n^{n+1}} \right) 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
-        .
-    \end{align*}
-    % TODO: Finish the recursion 
-    We will also use the bound.  
+        .
+    \end{align*}
+    The recursive estimate follows. 
 \end{proof}
@@
 % Lemma 5.5
-
-\newpage
 
@@
 
-\section{Extension operator on finite element stars}
+\newpage
 

### 2024-06-22 main.tex
vector calculus

@@
  For each $F \in \calT$ of dimension $n-1$, 
- we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F} \| \nabla u_F \|_{L^{p}(U_F)}$.
-
- Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
+ we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F,p} \| \nabla u_F \|_{L^{p}(U_F)}$.
+
+ There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+ \[
+    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{P}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+ \]
+ In particular, $c_{\star} := u - w_0$ is a constant function. 
+ Now, let $T \in \calT$ be any $n$-simplex. 
+ By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
+ For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{j(m)}$ be a face of dimension $n-1$. 
+ We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated \textbf{domain}. % TODO: technical stuff
+
+%  Since $\calT$ is strongly connected, there exists an enumersation of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
 We write $\Omega_m := \cup_{j=0}^{m} T_m$.
@@
 
-%  We let $T \in \calT$ be the first $n$-simplex. 
-%  There exists We already have
-
- Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$.
-Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant.
- By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
- Since $\nabla u_{F_{m}|T_{j(m)}} = \nabla w_{m-1|T_{j(m)}}$,
- there exists a constant $c_{m} := w_{m-1|T_{j(m)}} - u_{F_{m}|T_{j(m)}}$.
- We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_{j(m)}} = w_{m-1|T_{j(m)}}$. 
- But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
- As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
- Moreover, 
+ Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
+ such that $c_{\star} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
+ Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. 
+ By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
+ Since $\nabla u_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}}$,
+ there exists a constant $c_{m} := w_{m-1|T_{{m-1}}} - u_{F_{m}|T_{{m-1}}}$.
+ We define $w'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
+ By construction, $\nabla w'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ 
+ and 
+ $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
+ But that already implies $w'_{F_m} = u_{|F_m} - c_{\star}$. 
+ We define a measurable function $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$.
+ We have $c_{\star} = w_{m} - u_{|\Omega_{m}}$.
+
+ We assess the norm of this potential. We observe 
  \begin{gather*}
@@
     \leq 
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
-    \| c_{m} \|_{L^{p}(T_{j(m)})},
-    \\ 
-    \| c_{m} \|_{L^{p}(T_{j(m)})}
-    \leq 
-    \| w_{m-1}\|_{L^{p}(T_{j(m)})} + \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| c_{m} \|_{L^{p}(T_{{m-1}})},
+    \\ 
+    \| c_{m} \|_{L^{p}(T_{{m-1}})}
+    \leq 
+    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
     .
@@
     +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
-    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
     +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
     .
@@
     \max\left(
-        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
     \right)
@@
     +
-    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
-    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
+    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
+    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
     .
@@
     +
-    \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
     .
@@
     &\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
+    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
     \left( 
@@
         +
-        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
     \right)^{\frac 1 p}
     +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
     \\&\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
+    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
     \| u_{F_m} \|_{L^{p}(U_{F_m})} 
     +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
     .
@@
  Notice that $p/q = p - 1$.
+
+ Repeating this argument produces $w \in L^{p}(\Omega)$ 
+ such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{\star}$.
+ In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
 \end{proof}
@@
 \section{Extension operator on finite element stars}\label{section:extension}
+% Only define the geometric mapping and its important quantities
+% Leave the function spaces etc. for later
 
 \section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
+
+Recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
+and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^n$ for vector-valued functions with each component in $L^{p}(\Omega)$.
+
+In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
+$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
+\[
+    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+\]
+The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
+and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
+\[
+    W^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
+    \quad 
+    W^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
+\]
+More generally, ...
+\\
+
+We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
+Suppose that $U,V \subset \mathbb{R}^3$ are open sets and suppose that $\phi: U \to V$ is a bi-Lipschitz mapping.
+The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
+$\phi^{\grad}: L^{p}(V) \to L^{p}(U)$,
+$\phi^{\curl}: \bfL^{p}(V) \to \bfL^{p}(U)$, 
+and
+$\phi^{\divergence}: \bfL^{p}(V) \to \bfL^{p}(U)$. 
+and
+$\phi^{\rm b}: L^{p}(V) \to L^{p}(U)$. 
+They are defined by % TODO: change inverse convention from here on 
+\begin{equation}\label{eq_definition_piola}
+\begin{aligned}
+    \phi^{\grad}(v) &= v \circ \phi, \\
+    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
+    \phi^{\divergence}(\bfw) &= \left( \frac{ \Jacobian\phi^{-1} }{\det\Jacobian\phi^{-1}} \bfw \right)  \circ \phi, \\
+    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
+\end{aligned}
+\end{equation}
+where $v \in L^{p}(V)$ and $\bfw \in \bfL^{p}(V)$, 
+and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$
+These mappings are invertible. 
+%
+% trace properties 
+%
+The commutativity properties
+\begin{equation}\label{eq_piola_commute}
+\begin{aligned}
+    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
+    \\
+    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
+    % TODO: watch the sign 
+    \\
+    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
+\end{aligned}
+\end{equation}
+for $v \in W^{p}(\grad,U)$, $\bfv \in W^{p}(\curl,U)$, and $\bfw \in W^{p}(\divergence,U)$.  
+%
+
+\subsection{Exterior Algebra}
+
+In mathematics, Euclidean space, denoted \(\mathbb{R}^n\), is a fundamental concept representing the \(n\)-dimensional generalization of the familiar 2D and 3D spaces.
+Multilinear forms are scalar-valued functions that take multiple vectors as input and return a scalar and which are linear in each argument.
+This leads us to the study of alternating algebra, which focuses on antisymmetric multilinear forms.
+Alternating algebra plays a crucial role in various areas of mathematics, including geometry and physics.
+\\
+
+Let $V$ be a real vector space. 
+Given an integer $k \geq 0$, We let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
+Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
+if 
+\[ 
+    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
+    = 
+    \text{sign}(\pi) 
+    u( v_1, v_2, \ldots, v_k ) 
+\]
+for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
+By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
+Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
+
+The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra.
+Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) altand \( u_2 \in \Alt^{l}(V) \), their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
+defined by the formula 
+\[
+    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
+    = 
+    \frac{1}{k! l!} 
+    \sum_{ \sigma \in S_{p+q}} 
+    \mathrm{sgn}(\sigma) 
+    u_1( v_{\sigma(  1)}, \ldots, v_{\sigma(k  )} ) 
+    u_2( v_{\sigma(k+1)}, \ldots, v_{\sigma(k+l)} ),
+\]
+for any \( v_1, v_2, \ldots, v_{p+q} \in V \).
+Here, \( S_{p+q} \) denotes the symmetric group on \( p+q \) elements, \( \mathrm{sgn}(\sigma) \) is the sign of the permutation \( \sigma \).
+The exterior product is bilinear and associative, and satisfies
+\begin{align*}
+    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
+    \quad 
+    u_1 \in \Alt^{k}(V),
+    \quad 
+    u_2 \in \Alt^{l}(V).
+\end{align*}
+We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
+Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
+Moreover, this particular setting comes with a canonical basis. 
+We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^n\}\) be the canonical basis dual to the standard unit vectors.
+This is a basis of $\Alt^{1}(\bbR^{n})$. 
+The set 
+\begin{align*}
+    \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n), % TODO: define sigma 
+\end{align*}
+is the canonical basis of $\Alt^{k}(\bbR^{n})$. Note that 
+\begin{align*}
+    \dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}. 
+\end{align*}
+In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
+% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).
+
+We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
+which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
+The exterior derivative \( d \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
+to a \((k+1)\)-form \( d\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
+Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
+\[
+    \omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \omega_{\sigma} \, 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
+\]
+where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
+The exterior derivative \( d\omega \) is defined by
+\[
+    d\omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \sum_{j=1}^{n} 
+    \frac{\partial \omega_{\sigma}}{\partial x^j} 
+    \, \cartanx^j \wedge 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
+\]
+The exterior derivative is linear and nilpotent, which means 
+\( d(d\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
+Moreover, it satisfies the Leibniz rule:
+\[ 
+    d(\omega \wedge \eta) 
+    = 
+    d\omega \wedge \eta + (-1)^{k} \omega \wedge d\eta, 
+    \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
+    \qquad \eta \in C^{\infty}\Alt^{l}(\Omega).
+\]
+These properties ensure that the exterior derivative is a crucial tool in differential geometry and calculus on manifolds.
+
+\begin{remark}
+    In three dimensions, 
+    the calculus of differential forms can be translted into classical vector calculus. 
+    This is expressed formally as the commuting diagram 
+    \[
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) @>{d}>> C^\infty\Alt^3(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        @VV{\varpi^{3}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
+    \end{CD}
+    \]
+    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
+    \begin{align*}
+     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
+     = 
+     \left( u_1, u_2, u_3 \right), 
+     \quad 
+     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
+     = 
+     \left( u_{23}, - u_{13}, u_{12} \right).
+     .
+    \end{align*}
+    In two dimensions, 
+    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
+    To the authors' best knowledge, neither convention is dominant in the literature.
+    On the one hand, we have a commuting diagram 
+    \[
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
+    \end{CD}
+    \]
+    where the the middle vertical arrow is the isomorphism that satisfies 
+    \begin{align*}
+        \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right)
+        =
+        \left( u_1, u_2 \right),
+    \end{align*}
+    and the other vertical arrows are the identity. 
+    Alternatively, we may use the commuting diagram 
+    \[
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega)
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        \\
+        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
+    \end{CD}
+    \]
+    where the the middle vertical arrow is the isomorphism that satisfies 
+    \begin{align*}
+        \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right)
+        =
+        \left( u_2, -u_1 \right),
+    \end{align*}
+    and the other vertical arrows are the identity. 
+    The utility of exterior calculus is that the doperators of vector calculus can be translated into a common framework that does not depend on the dimension.
+\end{remark}
+
+In physics, alternating algebra is crucial in the formulation of theories such as electromagnetism and general relativity.
+For example, in electromagnetism, the electromagnetic field tensor is an alternating 2-form, and its properties are naturally described using the language of exterior algebra.
+
+- Spivak, Michael. *Calculus on Manifolds*. W. A. Benjamin, 1965.
+- Lee, John M. *Introduction to Smooth Manifolds*. Springer, 2012.
+- Greub, Werner H. *Multilinear Algebra*. Springer, 1978.
+- Bott, Raoul, and Loring W. Tu. *Differential Forms in Algebraic Topology*. Springer, 1982.
+
+These references provide a deeper understanding of the concepts discussed and offer additional insights into the applications and further study of alternating algebra.
 

### 2024-06-22 main.tex
some improvements

@@
 We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
-Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
+Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
 we search for a constant $C > 0$ such that 
@@
 Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
-Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^n$ for the corresponding Lebesgue space of vector fields.
+Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
 We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
@@
     := 
-    \frac{ \diam(T)^n }{ n! \vol(T) }
+    \frac{ \diam(T)^{n} }{ n! \vol(T) }
     .
@@
 \end{align*}
-This indicator quantifies how much reflection across the shared face distorts the goemetry.
-
-% and $\Phi : \Delta^n \rightarrow T$ is an affine diffeomorphism from the reference simplex,
+This indicator quantifies how much reflection across the shared face distorts the geometry.
+
+% and $\Phi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
 % we define the quantity 
@@
 %     := 
-%     \frac{ \diam(T)^n }{ n! \vol(T) }
+%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
 %     .
@@
 \begin{lemma}\label{lemma:affinetransform}
-    Let $T$ be an $n$-simplex and let $\Phi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
+    Let $T$ be an $n$-simplex and let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
     \begin{align*}
@@
         \leq 
-        \sqrt{2n^n} 
-        % \frac{ n! \vol(T) } { \diam(T)^n }
+        \sqrt{2n^{n}} 
+        % \frac{ n! \vol(T) } { \diam(T)^{n} }
         \kappa(T)^{-1}
@@
     We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
-    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Phi)$. Hence 
+    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\Phi)$. Hence 
     \[
@@
         \sqrt{2} 
-        \frac{ \sigma_1^n }{ \det(\Jacobian\Phi) } 
+        \frac{ \sigma_1^{n} }{ \det(\Jacobian\Phi) } 
         \sigma_n
         \leq 
-        \sqrt{2n^n} 
-        \frac{ \diam(T)^n }{ n! \vol(T) } 
+        \sqrt{2n^{n}} 
+        \frac{ \diam(T)^{n} }{ n! \vol(T) } 
         \sigma_n
@@
         &\leq 
-        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
+        \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
         \cdot 
-        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
+        \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
         \leq 
@@
         &\leq 
-        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
+        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
         \diam(F)
@@
         \sqrt{2n^{n+1}} 
-        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
-        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
+        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
         \leq 
@@
     \begin{align*}
-        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
-        \\
-        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
+        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
+        \\
+        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
         .
@@
         \geq 
-        \frac{ n! \vol(T_1) }{ \diam(T_1)^n }
+        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
         \cdot 
@@
         \diam(T_1)
-        \sqrt{2n^n} 
-        \frac{ n! \vol(T_2) } {\diam(T_2)^n } 
+        \sqrt{2n^{n}} 
+        \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } 
         \diam(T_2)^{-1}
@@
         \sqrt{n} 
-        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
+        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
         \diam(F)
-        \sqrt{2n^n} \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
+        \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
         \diam(F)^{-1}
@@
         \sqrt{2n^{n+1}}
-        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
-        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
+        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
         .
@@
     %     \leq 
-    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
+    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
     %     \cdot 
-    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
+    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
     %     .
@@
 \begin{remark}
-    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
     % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
@@
 
-%  Since $\calT$ is strongly connected, there exists an enumersation of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
+%  Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
 We write $\Omega_m := \cup_{j=0}^{m} T_m$.
@@
 We recall that this means that for every $x \in \underlying{\calT}$
-there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^n$
-such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^n \suchthat |x| \leq 1 \}$
+there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
+such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| \leq 1 \}$
 or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
@@
 
-Recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^n$ for vector-valued functions with each component in $L^{p}(\Omega)$.
-
+\subsection{Review of vector calculus}
+
+We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
+Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
+First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
+and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
 In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
@@
 \[
-    W^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
+    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
     \quad 
-    W^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
+    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
 \]
-More generally, ...
-\\
-
 We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
-Suppose that $U,V \subset \mathbb{R}^3$ are open sets and suppose that $\phi: U \to V$ is a bi-Lipschitz mapping.
+Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
 The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
-$\phi^{\grad}: L^{p}(V) \to L^{p}(U)$,
-$\phi^{\curl}: \bfL^{p}(V) \to \bfL^{p}(U)$, 
+$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
+$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
+$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
 and
-$\phi^{\divergence}: \bfL^{p}(V) \to \bfL^{p}(U)$. 
-and
-$\phi^{\rm b}: L^{p}(V) \to L^{p}(U)$. 
-They are defined by % TODO: change inverse convention from here on 
-\begin{equation}\label{eq_definition_piola}
-\begin{aligned}
+$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
+They are defined by 
+\begin{subequations}\label{eq_definition_piola}
+\begin{align}
     \phi^{\grad}(v) &= v \circ \phi, \\
@@
     \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
-\end{aligned}
-\end{equation}
-where $v \in L^{p}(V)$ and $\bfw \in \bfL^{p}(V)$, 
-and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$
+\end{align}
+\end{subequations}
+where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
+and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
 These mappings are invertible. 
+%
+% TODO: bounds
+%
+We use the commutativity relations 
+\begin{subequations}\label{eq_piola_commute}
+\begin{align}
+    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
+    \\
+    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
+    % TODO: watch the sign 
+    \\
+    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
+\end{align}
+\end{subequations}
+for $v \in W^{p}(\grad,\Omega)$, $\bfv \in W^{p}(\curl,\Omega)$, and $\bfw \in W^{p}(\divergence,\Omega)$.  
+We summarize this as a commuting diagram:
+\begin{align*}
+    \begin{CD}
+        W^{1,p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
+        \\
+        @VV{\phi^{\grad}}V 
+        @VV{\phi^{\curl}}V 
+        @VV{\phi^{\divergence}}V 
+        @VV{\phi^{\rm b}}V 
+        \\
+        W^{1,p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
+    \end{CD}
+\end{align*}
+
+\begin{remark}
+    Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
+    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega'$.
+    This is in accordance with the notion of pullback, that we will review shortly. 
+    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
+\end{remark}
+
+%
+
 %
@@
 %
-The commutativity properties
-\begin{equation}\label{eq_piola_commute}
-\begin{aligned}
-    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
-    % TODO: watch the sign 
-    \\
-    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
-\end{aligned}
-\end{equation}
-for $v \in W^{p}(\grad,U)$, $\bfv \in W^{p}(\curl,U)$, and $\bfw \in W^{p}(\divergence,U)$.  
-%
-
-\subsection{Exterior Algebra}
-
-In mathematics, Euclidean space, denoted \(\mathbb{R}^n\), is a fundamental concept representing the \(n\)-dimensional generalization of the familiar 2D and 3D spaces.
-Multilinear forms are scalar-valued functions that take multiple vectors as input and return a scalar and which are linear in each argument.
-This leads us to the study of alternating algebra, which focuses on antisymmetric multilinear forms.
-Alternating algebra plays a crucial role in various areas of mathematics, including geometry and physics.
-\\
-
+
+\subsection{Review of exterior calculus}
+
+We also investigate this from the perspective of exterior calculus. 
+We give a brief introduction into this topic. 
 Let $V$ be a real vector space. 
@@
 The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) altand \( u_2 \in \Alt^{l}(V) \), their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
+Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
+their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
 defined by the formula 
@@
     \frac{1}{k! l!} 
-    \sum_{ \sigma \in S_{p+q}} 
-    \mathrm{sgn}(\sigma) 
+    \sum_{ \sigma \in S_{k+l}} 
+    \signum(\sigma) 
     u_1( v_{\sigma(  1)}, \ldots, v_{\sigma(k  )} ) 
@@
 \]
-for any \( v_1, v_2, \ldots, v_{p+q} \in V \).
-Here, \( S_{p+q} \) denotes the symmetric group on \( p+q \) elements, \( \mathrm{sgn}(\sigma) \) is the sign of the permutation \( \sigma \).
+for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
+Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\sigma) \) is the sign of the permutation \( \sigma \).
 The exterior product is bilinear and associative, and satisfies
@@
 Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^n\}\) be the canonical basis dual to the standard unit vectors.
-This is a basis of $\Alt^{1}(\bbR^{n})$. 
-The set 
-\begin{align*}
-    \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n), % TODO: define sigma 
-\end{align*}
-is the canonical basis of $\Alt^{k}(\bbR^{n})$. Note that 
-\begin{align*}
-    \dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}. 
-\end{align*}
+We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the canonical basis dual to the standard unit vectors.
+This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
+To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
+we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
+and introduce the basic $k$-alternators 
+\begin{align*}
+    \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
+\end{align*}
+These define a basis of $\Alt^{k}(\bbR^{n})$.
+Note that 
+$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
 In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
 % The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).
+
+We notice that the standard scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
+which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
+The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
 
@@
 \]
-These properties ensure that the exterior derivative is a crucial tool in differential geometry and calculus on manifolds.
+Let u now turn our attention to Sobolev spaces of differential forms. 
+Since $\Alt^{k}(\Omega)$ is a normed space, we can consider the pointwise norms of differential $k$-forms. 
+% First, we notice that the % TODO: introduce a norm 
+We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
+such that its pointwise norm is $p$-integrable. 
+The exterior derivative is defined in the sense of distributions and we introduce 
+\[
+    W^p\Alt^{k}(\Omega) = \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
+\]
+We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
+Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+The pullback of $u \in W^p\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
+\[ 
+    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
+    = 
+    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
+\]
+for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.
 
@@
     In three dimensions, 
-    the calculus of differential forms can be translted into classical vector calculus. 
+    the calculus of differential forms can be translated into classical vector calculus. 
     This is expressed formally as the commuting diagram 
@@
      \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     = 
+     &= 
      \left( u_1, u_2, u_3 \right), 
-     \quad 
+     \\
      \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     = 
+     &= 
      \left( u_{23}, - u_{13}, u_{12} \right).   
-     .
     \end{align*}
@@
     and the other vertical arrows are the identity. 
-    The utility of exterior calculus is that the doperators of vector calculus can be translated into a common framework that does not depend on the dimension.
+    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
 \end{remark}
 
-In physics, alternating algebra is crucial in the formulation of theories such as electromagnetism and general relativity.
-For example, in electromagnetism, the electromagnetic field tensor is an alternating 2-form, and its properties are naturally described using the language of exterior algebra.
-
-- Spivak, Michael. *Calculus on Manifolds*. W. A. Benjamin, 1965.
-- Lee, John M. *Introduction to Smooth Manifolds*. Springer, 2012.
-- Greub, Werner H. *Multilinear Algebra*. Springer, 1978.
-- Bott, Raoul, and Loring W. Tu. *Differential Forms in Algebraic Topology*. Springer, 1982.
-
-These references provide a deeper understanding of the concepts discussed and offer additional insights into the applications and further study of alternating algebra.
-
 \subsection{Inequalities for partial boundary conditions on a single simplex}
+
+We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+Let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+that maps the faces $F_{0}, F_{1}, \dots, F_{l}$ onto the boundary patch $\Gamma$. 
+We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
+% Copied from McIntosh paper 
+Rewriting $B^{k}$ in the same way, we get
+\begin{equation}\label{eq:Bogo}
+    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da\;.
+\end{equation}
+If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
+one sees that $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$, 
+and that $B^{k} u(x) = 0$ unless $x \in \Omega$. 
+Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
+Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
+The fact that $B^{k}$ indeed maps 
+$C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
 
@@
 % Slit
+
 % Cube 

### 2024-06-24 main.tex
bogovskii operator

@@
     \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
-    \phi^{\divergence}(\bfw) &= \left( \frac{ \Jacobian\phi^{-1} }{\det\Jacobian\phi^{-1}} \bfw \right)  \circ \phi, \\
+    \phi^{\divergence}(\bfw) &= \left( \det(\Jacobian\phi) \Jacobian\phi^{-1} \bfw \right)  \circ \phi, \\
     \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
@@
 % Copied from McIntosh paper 
-Rewriting $B^{k}$ in the same way, we get
-\begin{equation}\label{eq:Bogo}
-    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da\;.
+We begin with introducing the Costabel-McIntosh-Bogovski\u{\i} kernel.
+For $\ell\in\{0,\dotsc,n\}$, we define the kernel $G_\ell : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
+\begin{equation}
+\label{eq:Gl}
+  G_\ell(x,y) = 
+  \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
 \end{equation}
-If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
-one sees that $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$, 
-and that $B^{k} u(x) = 0$ unless $x \in \Omega$. 
-Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
-Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
-The fact that $B^{k}$ indeed maps 
-$C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
+Given a differential form $u \in {C^\infty}_0(\bbR^n,\Alt^\ell)$, \(1\leq \ell \leq n\), 
+we then define the integral operators
+\begin{align}
+  T_\ell u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+\end{align}
+We call $T_\ell$ a Bogovski\u{\i}-type operator.
+
+In order to see that the integrals in the definition of $T_\ell$ exist, 
+we first rewrite the kernel $G_\ell$:
+\begin{align*}
+    G_\ell(x,y) 
+    &= 
+    \int_0^\infty \tau^{n-\ell} (\tau+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+\tau(x-y) \right)\,d\tau
+    \\
+    &= 
+    \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
+    \int_0^\infty \tau^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+\tau(x-y) \right)\,d\tau 
+    \\
+    &= 
+    |\Omega|^{-1}\sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \,
+    |x-y|^{k-n} \int_0^\infty r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr \;
+    .
+\end{align*}
+We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
+\begin{align*}
+    G_\ell(x,y) 
+    &\leq 
+    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr \;.
+    \\
+    &= 
+    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
+\end{align*}
+We pointwise estimate $B_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| B_{\ell} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+    \\&\leq 
+    \left| 
+        \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \right| 
+    \\&\leq 
+    \left| 
+        \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
+    \right| 
+    .
+\end{align*}
+We recall the radial integrals 
+\begin{align*}
+    \int_{B_D(0)} |z|^{k+1-n} dz
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k} dr
+    =
+    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
+    .
+\end{align*}
+We compute 
+\begin{align*}
+    &
+    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
+    \\&
+    =
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
+    .
+\end{align*}
+So the convolution of $u$ is taken against an integrable function. 
+Taylor's inequality now implies: 
+\begin{align*}
+    \| B_{\ell} u \|_{L^{p}(\Omega)}
+    &\leq 
+    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
+    D
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+In particular, we have a bounded operator $B_{\ell} : L^{p}(\bbR^n,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1})$ for any $1 \leq p \leq \infty$.
+
+\newpage 
+In order to see other properties of the operators, we apply a different change of variables. 
+Let us write this in detail for the operator $R_\ell$. 
+We substitute $y$ by the new variable $a=y+t(x-y)$.
+Whence $da = (1-t)^n dy$ and $t(x-y) = a-y$ and $x-y = (a-y)/t$ and $x - (a-x)/t = y$
+\begin{align*}
+    T_\ell u(x) 
+    &= 
+    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(y+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\&= 
+    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\&= 
+    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &= 
+    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
+    \chi_{\Omega}\left(a\right) 
+    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
+\end{align*}
+Then we substitute $1-s = 1/(t+1)$, that is, $s = t/(t+1)$:
+Whence $t = \left( 1/s-1 \right)^{-1}$.
+\begin{align*}
+    T_\ell u(x) 
+    &= 
+    \int \int_1^\infty (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
+    \chi_{\Omega}\left(a\right) 
+    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
+    \\
+    &= 
+    .
+\end{align*}
+
+Then we substitute $s = (t-1)/t$:
+\begin{align*}
+    &= 
+    \int \int_1^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
+    \chi_{\Omega}\left(a\right)
+    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
+    \\
+    &= 
+    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
+    .
+\end{align*}
+Then we substitute $s = (t-1)/t$:
+\begin{align*}
+    T_\ell u(x) 
+    &= 
+    \int \int_1^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
+    \\
+    &= 
+    - \int \int_1^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
+    \\
+    &=
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    .
+\end{align*}
+We copy a statement by McIntosh and Costabel, who are too fucking lazy to write down their goddamn substititions for fucks sake, stupid assholes:
+\begin{align*}
+    T_\ell u(x) 
+    = 
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    .
+\end{align*}
+From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $T_\ell u(x)$ is smooth with support contained in $\overline\Omega$ as well.
+
+We compute the exterior derivative of this potential:
+\begin{align*}
+    T_{\ell,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)}
+    \int_1^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_1^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
+    .
+\end{align*}
+\begin{align*}
+    \cartan T_{\ell,a} u(x) 
+    &= 
+    k
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_1^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_1^\infty 
+    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    .
+\end{align*}
+When we calculate the exterior derivative of $u$, we find 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \partial_{j} u(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
+    .
+\end{align*}
+The potential operator, applied to this result, gives 
+\begin{align*}
+    T_{\ell+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    \cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Applying cancelations, we find 
+\begin{align*}
+    &
+    \cartan T_{\ell,a} u(x)
+    +
+    T_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    k
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_1^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_1^\infty 
+    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_1^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_1^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    \int_1^\infty \partial_{t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    u_{\sigma}\left(x)\right) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+
+From this form of $T_\ell$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $T_\ell$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
+But if $u\in{C^\infty}_0(\bbR^n,\Alt^\ell)$, one sees that $T_\ell u$ is ${C^\infty}$ on 
+$\bbR^n\setminus\supp\chi_{\Omega}$, and that 
+$T_\ell u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
+Thus if $\Omega$ is open and starlike with respect to $B$, then   
+$u\in{C^\infty}_0(\Omega,\Alt^\ell)$ implies $\supp T_\ell u \subset\Omega$, and, if $\Omega$ is bounded, then
+$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp T_\ell u \subset\overline\Omega$. 
+The fact that $T_\ell$ indeed maps 
+${C^\infty}_0(\bbR^n,\Alt^\ell)$ to ${C^\infty}_0(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.
+
+\subsection{Homotopy relations}
+
+Cartan's formula for the Lie derivative of a differential form with respect to a vector field can be written as
+$$
+  \frac{d}{dt}F^*_t u = F^*_t \left(d(X_t\lrcorner u) + X_t\lrcorner du\right)\;,
+$$
+where $F^*_t$ denotes the pull-back by the flow $F_t$ associated with the vector field $X_t$. Here we consider the special case of the dilation flow with center $a$
+$$
+  F_t(x) = a+t(x-a) \quad\text{ with vector field } X_t=x-a\;,
+$$
+which gives a pull-back of
+$$
+  F^*_t u(x) = t^\ell \,u\left(a+t(x-a)\right) \quad \text{for an $\ell$-form } u \;.
+$$
+This leads to the formula
+\begin{equation}
+\label{eq:Cartan}
+ \frac{d}{dt}(t^\ell u\left(a+t(x-a)\right) =
+    d\Bigl(t^{\ell-1}(x-a)\lrcorner u\left(a+t(x-a)\right)\Bigr) +
+    t^{\ell}(x-a)\lrcorner du\left(a+t(x-a)\right)
+\end{equation}
+which can also be verified elementarily from the formulas we gave in Section~\ref{S:notation}.
+
+Integrating \eqref{eq:Cartan} from $0$ to $1$ and comparing with \eqref{eq:regPoincare}, 
+we find the homotopy relations, valid for all $u\in{C^\infty}_0(\bbR^n,\Alt^\ell)$ 
+\begin{equation}
+\begin{aligned}
+\label{eq:dR+Rd=1}
+ dR_\ell u + R_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
+ R_1 du &= u - \left(\chi_{\Omega},u\right)\; &&(\ell=0)\;;\\
+ dR_nu &=u &&(\ell=n)\;.
+\end{aligned}
+\end{equation}
+One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $T_\ell$ directly.
+The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutation relations for $T_\ell$ from the relations \eqref{eq:dR+Rd=1} which are already proved.
+Here is what one obtains for $u\in{C^\infty}_0(\bbR^n,\Alt^\ell)$:
+\begin{equation}
+\begin{aligned}
+\label{eq:dT+Td=1}
+  dT_\ell u + T_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
+  T_1 du &= u \; &&(\ell=0)\;;\\
+ dT_n u &=u - (\int\! u)\star\chi_{\Omega}&&(\ell=n)\;.
+\end{aligned}
+\end{equation}
+Here we consider $\chi_{\Omega}$ as an element of ${C^\infty}_0(\bbR^n,\Alt^0)$, so that for another $0$-form $u$ we have the $L^2$ scalar product $\left(\chi_{\Omega},u\right)=\int\chi_{\Omega}(a)u(a)da$, and $\star\chi_{\Omega}$ is the $n$-form $\chi_{\Omega}(x)dx_1\wedge\dots\wedge dx_n$.
+
+The formulas for the endpoints $\ell=0$ and $\ell=n$ correspond to the two extended de Rham complexes without boundary conditions and with compact support, see \eqref{eq:edRwobc} and \eqref{eq:edRwcs}.
+To see this, let us extend the definition of the exterior derivative by writing $\overline d$ for all the mappings of the complex
+$$
+ 0 \to\bbR\to^\iota{C^\infty}(\overline\Omega,\Alt^0) \to^d {C^\infty}(\overline\Omega,\Alt^1)
+ \to^d\cdots \to^d {C^\infty}(\overline\Omega,\Alt^n) \to 0
+$$ 
+and $\underline d$ for all the mappings of the complex
+$$
+ 0 \to {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^0) \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^1) \to^d\cdots
+ \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^n) \to^{\iota^*} \bbR \to 0
+$$
+where $\iota$ is the inclusion mapping for constant functions and 
+$\iota^*=(\star\iota)'$ denotes the integral $u\mapsto\int\!u$ for $n$-forms.
+
+If we correspondingly extend the definitions of $R_\ell$ and $T_\ell$ by
+$$
+\begin{aligned}
+  R_0u &:=\left(\chi_{\Omega},u\right)\,\text{ for $0$-forms }u\,, &
+  R_{n+1} &:=0\,,\\
+  T_{n+1}u &:= \star(u\chi_{\Omega}) \,\text{ for }u\in\bbR\,,  &
+  T_0 &:= 0\,,
+\end{aligned}
+$$
+then we can write the relations \eqref{eq:dR+Rd=1} and \eqref{eq:dT+Td=1} simply as
+\begin{equation}\label{eq:R&T&d}
+ \overline d\,R_\ell u + R_{\ell+1} \,\overline d u  = u
+ \quad \text{ and }\quad
+ \underline d\,T_\ell u + T_{\ell+1} \,\underline du = u\quad \text{ for all }\;
+  0\le\ell\le n.
+\end{equation}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. Then 
+    \begin{align*}
+        \| \vec u \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \vec u \|_{L^{2}(\Omega)}.
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
+    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
+    with smallest singular value $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
+    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
+    which has the same smallest singular value. 
+\end{proof}
 

### 2024-06-24 draft.tex
some progress
gather material on potential reconstruction

@@
 
+\newpage\color{red}
+ We want 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    \leq
+    \left( 
+        1 
+        + 
+        2
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$,
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    +
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq
+    \left( 
+        1 
+        + 
+        2
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \right)
+    \left( 
+        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
+        +
+        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
+        +
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    .
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{orange}
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    \leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$, 
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    +
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
+    \right)
+    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \right) 
+    \left( 
+        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
+        +
+        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{JungleGreen}
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq
+    \left( 
+        3
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    \\&
+    \leq
+    \left( 
+        3
+    \right)^{p/q}
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$, ????
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})}^{1}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{1}(T_{j(m)})}^{1}
+    \right)
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq
+    3
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+ \color{MidnightBlue}
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}^{p}
+    &\leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    \\&
+    \leq
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
+    \right)^{p/q}
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
+        +
+        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
+    \right)
+    .
+ \end{align*}
+ In the special case $p=1$ and $p=\infty$, ????
+ \begin{align*}
+    \| w_{m} \|_{L^{1}(T_m)}
+    &\leq 
+    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})} 
+        +
+        \| w_{m-1}\|_{L^{1}(T_{j(m)})} 
+    \right)
+    .
+    \\
+    \| w_{m} \|_{L^{2}(T_m)}^{2}
+    &\leq 
+    \left( 
+        2 
+        + 
+        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
+    \right) 
+    \left( 
+        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
+        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
+        +
+        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
+    \right)
+    \\
+    \| w_{m} \|_{L^{\infty}(T_m)}
+    &\leq 
+    3
+    \max\left( 
+        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+        ,
+        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
+    \right)
+    .
+ \end{align*}
+
+ We introduce the operator $B^{k}$, which can be written in several alternative forms
+\begin{align*}
+    B^{k} u(x) 
+    &= 
+    - |\Omega|^{-1}
+    \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da
+    \\&= 
+    |\Omega|^{-1}
+    \int_{\Omega} \,(x-a) \lrcorner \int_0^1 t^{-{k}-1}\,u\left( a+(x-a)/s \right) \,ds\,da
+    .
+\end{align*}
+If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
+then $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$ and $B^{k} u(x) = 0$ when $x \notin \Omega$. 
+Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
+Since $\Omega$ is bounded, $\supp u \subseteq \overline\Omega$ implies $\supp B^{k} u \subset\overline\Omega$. 
+% The fact that $B^{k}$ indeed maps 
+% $C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
+
+\begin{align*}
+    \int_{\Omega}
+    \left| B^{k} u(x) \right|^{p}
+    dx
+    &
+    = 
+    |\Omega|^{-1}
+    \int_{\Omega}
+    \int_{\Omega} 
+    \int_0^1
+    s^{(-{k}-1)p}\, |x-a|^{p} \left| u\left( a+(x-a)/s \right) \right|^{p} \,ds\,da
+    dx
+    \\&
+    = 
+    |\Omega|^{-1}
+    \int_{\Omega}
+    \int_{\Omega-a} 
+    \int_{|z|/D}^{1}
+    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( a+z/s \right) \right|^{p} \,ds\,da
+    dz
+    \\&
+    = 
+    |\Omega|^{-1}
+    \int_{\Omega}
+    \int_{2\Omega} 
+    \int_{|z|/D}^{1}
+    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( a+z/s \right) \right|^{p} \,ds\,da
+    dz
+    \\&
+    = 
+    |\Omega|^{-1}
+    \int_{\Omega + z/s}
+    \int_{2\Omega} 
+    \int_{|z|/D}^{1} % y = a + z/s
+    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( y \right) \right|^{p} \,ds\,dy
+    dz
+    \\&
+    = 
+    |\Omega|^{-1}
+    \int_{2\Omega}
+    \int_{2\Omega} 
+    \int_{|z|/D}^{1} % y = a + z/s
+    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( y \right) \right|^{p} \,ds\,dy
+    dz
+    .
+\end{align*}
+
+\begin{align*}
+    G_\ell(x,y) 
+    &\leq 
+    \int_{0}^{\frac{D}{|x-y|}} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
+    \\
+    &\leq 
+    \frac{|x-y|}{D}
+    \int_{0}^{\frac{D}{|x-y|}} \frac{D}{|x-y|} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
+    .
+\end{align*}
+\begin{align*}
+    G_\ell(x,y)^{p} 
+    &\leq 
+    \frac{|x-y|}{D}
+    \int_{0}^{\frac{D}{|x-y|}} \frac{D^{p}}{|x-y|^{p}} \tau^{pn-p\ell} (\tau+1)^{p\ell-p} \,d\tau
+    \\&\leq 
+    \frac{|x-y|}{D}
+    \frac{D^{p}}{|x-y|^{p}} \int_{0}^{\frac{D}{|x-y|}} (\tau+1)^{pn-p} \,d\tau
+    \\&\leq 
+    \frac{D^{p-1}}{|x-y|^{p-1}} \left( \left( \frac{D}{|x-y|} + 1 \right)^{pn-p+1} - 1 \right)
+    \\&\leq 
+    \frac{D^{p-1}}{|x-y|^{p-1}} \left( 2^{pn-p+1} \left( \frac{D}{|x-y|} \right)^{pn-p+1} - 1 \right)
+    \\&\leq 
+    2^{pn-p+1} \frac{D^{pn}}{|x-y|^{pn}} - \frac{D^{p-1}}{|x-y|^{p-1}}
+    .
+\end{align}
+
+Moreover,  
+\begin{align*}
+    \int_{\Omega} \left| B_{\ell} u(x) \right|^{p} dx
+    &=
+    |\Omega|^{-1} 
+    \int_{\Omega} 
+    \int_{\Omega} 
+    \left( 2^{pn-p+1} \frac{D^{pn}}{|x-y|^{pn}} - \frac{D^{p-1}}{|x-y|^{p-1}} \right)
+    \left| (x-y)\lrcorner u(y) \right|^{p} 
+    dy dx
+    \\&=
+    |\Omega|^{-1} 
+    \int_{\Omega} 
+    \int_{\Omega} \left( 2^{pn-p+1} D^{pn} |x-y|^{-pn+p} - D^{p-1} |x-y| \right) dx
+    \left| u(y) \right|^{p} 
+    dy
+    .
+\end{align*}
+
+We use the radial integrals
+\begin{align*}
+    \int_{B_D(0)} |z|^{m} dz
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{m} r^{n-1} dr
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{m+n-1} dr
+    =
+    \vol_{n-1}(S_1) \frac{D^{m+n}}{m+n}
+    .
+\end{align*}
+
 \section*{Theorem 8.1}

### 2024-06-24 main.tex
gather material on potential reconstruction

@@
 
-\subsection{Inequalities for partial boundary conditions on a single simplex}
-
-We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-Let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-that maps the faces $F_{0}, F_{1}, \dots, F_{l}$ onto the boundary patch $\Gamma$. 
-We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-% Copied from McIntosh paper 
+\subsection{Bogovski\u{\i}-type operators}
 We begin with introducing the Costabel-McIntosh-Bogovski\u{\i} kernel.
@@
     \| u \|_{L^{p}(\Omega)}
+    \leq 
+    n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    D
+    \| u \|_{L^{p}(\Omega)}
     .
@@
 \end{align*}
+$a = y + t(x-y)$
+$s = \frac{t}{t-1}$
 From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $T_\ell u(x)$ is smooth with support contained in $\overline\Omega$ as well.
@@
 
+\subsection{Inequalities for partial boundary conditions on a single simplex}
+We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+Let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+that maps the faces $F_{0}, F_{1}, \dots, F_{l}$ onto the boundary patch $\Gamma$. 
+We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
 \subsection{Constructions over shellable triangulations}

### 2024-06-25 main.tex
Update on Overleaf.

--- 2024-06-22 main.tex
@@
 
-% Copied from McIntosh paper 
-Rewriting $B^{k}$ in the same way, we get
-\begin{equation}\label{eq:Bogo}
-    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da\;.
+We introduce the operator $B^{k}$, which is
+\begin{equation}\label{eq:Bogo} % TODO: rewrite 
+    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da.
 \end{equation}
 If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
-one sees that $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$, 
-and that $B^{k} u(x) = 0$ unless $x \in \Omega$. 
+then $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$ and $B^{k} u(x) = 0$ when $x \notin \Omega$. 
 Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
 Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
-The fact that $B^{k}$ indeed maps 
-$C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
+% The fact that $B^{k}$ indeed maps C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
 
@@
 
+\begin{align}
+    v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
+    \\
+    \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
+    \\
+    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
+    \\
+    v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
+    \\
+    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
+\end{align}
+\begin{align}
+    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+    +
+    \sum_{i=1}^{k} \lambda_{i} v_i 
+    +
+    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+    -
+    \sum_{i=k+1}^{n-1} \lambda_{i} v_i
+\end{align}
+\begin{align}
+    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+    +
+    \sum_{i=1}^{k} \lambda_{i} v_i 
+    +
+    \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i
+    +
+    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+\end{align}
+
 \section*{Acknowledgments}

### 2024-06-25 draft.tex
write up

@@
 
+In order to see other properties of the operators, we apply a different change of variables. 
+Let us write this in detail for the operator $R_{\ell}$. 
+We substitute $y$ by the new variable $a=y+t(x-y)$.
+Whence $da = (1-t)^n dy$ and $t(x-y) = a-y$ and $x-y = (a-y)/t$ and $x - (a-x)/t = y$
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    &= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(y+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\&= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\&= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
+    \chi_{\Omega}\left(a\right) 
+    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
+\end{align*}
+Then we substitute $1-s = 1/(t+1)$, that is, $s = t/(t+1)$:
+Whence $t = \left( 1/s-1 \right)^{-1}$.
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    &= 
+    \int \int_{1}^\infty (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
+    \chi_{\Omega}\left(a\right) 
+    \frac{ x-a }{t+1}\lrcorner u( x + (a-x)/(t+1) ) \,dt\,dy 
+    \\
+    &= 
+    .
+\end{align*}
+
+Then we substitute $s = (t-1)/t$:
+\begin{align*}
+    &= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
+    \chi_{\Omega}\left(a\right)
+    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
+    \\
+    &= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
+    .
+\end{align*}
+Then we substitute $s = (t-1)/t$:
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    &= 
+    \int \int_{1}^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
+    \\
+    &= 
+    - \int \int_{1}^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
+    \\
+    &=
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    .
+\end{align*}
+We copy a statement by McIntosh and Costabel:
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    = 
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    .
+\end{align*}
+$a = y + t(x-y)$
+$s = \frac{t}{t-1}$
+From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $\Bogov_{\ell} u(x)$ is smooth with support contained in $\overline\Omega$ as well.
+
+From this form of $\Bogov_{\ell}$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $\Bogov_{\ell}$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
+But if $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$, one sees that $\Bogov_{\ell} u$ is ${C^\infty}$ on 
+$\bbR^n\setminus\supp\chi_{\Omega}$, and that 
+$\Bogov_{\ell} u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
+Thus if $\Omega$ is open and starlike with respect to $B$, then   
+$u\in{C^\infty_c}(\Omega,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\Omega$, and, if $\Omega$ is bounded, then
+$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\overline\Omega$. 
+The fact that $\Bogov_{\ell}$ indeed maps 
+${C^\infty_c}(\bbR^n,\Alt^\ell)$ to ${C^\infty_c}(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.
+
+\subsection{Homotopy relations}
+
+Cartan's formula for the Lie derivative of a differential form with respect to a vector field can be written as
+$$
+  \frac{d}{dt}F^*_t u = F^*_t \left(d(X_t\lrcorner u) + X_t\lrcorner du\right)\;,
+$$
+where $F^*_t$ denotes the pull-back by the flow $F_t$ associated with the vector field $X_t$. Here we consider the special case of the dilation flow with center $a$
+$$
+  F_t(x) = a+t(x-a) \quad\text{ with vector field } X_t=x-a\;,
+$$
+which gives a pull-back of
+$$
+  F^*_t u(x) = t^\ell \,u\left(a+t(x-a)\right) \quad \text{for an $\ell$-form } u \;.
+$$
+This leads to the formula
+\begin{equation}
+\label{eq:Cartan}
+ \frac{d}{dt}(t^\ell u\left(a+t(x-a)\right) =
+    d\Bigl(t^{\ell-1}(x-a)\lrcorner u\left(a+t(x-a)\right)\Bigr) +
+    t^{\ell}(x-a)\lrcorner du\left(a+t(x-a)\right)
+\end{equation}
+which can also be verified elementarily from the formulas we gave in Section~\ref{S:notation}.
+
+Integrating \eqref{eq:Cartan} from $0$ to $1$ and comparing with \eqref{eq:regPoincare}, 
+we find the homotopy relations, valid for all $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$ 
+\begin{equation}
+\begin{aligned}
+\label{eq:dR+Rd=1}
+ dR_{\ell} u + R_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
+ R_1 du &= u - \left(\chi_{\Omega},u\right)\; &&(\ell=0)\;;\\
+ dR_nu &=u &&(\ell=n)\;.
+\end{aligned}
+\end{equation}
+One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $\Bogov_{\ell}$ directly.
+The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutativity relations for $\Bogov_{\ell}$ from the relations \eqref{eq:dR+Rd=1} which are already proved.
+Here is what one obtains for $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$:
+\begin{equation}
+\begin{aligned}
+\label{eq:dT+Td=1}
+  d\Bogov_{\ell} u + T_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
+  T_1 du &= u \; &&(\ell=0)\;;\\
+ dT_n u &=u - (\int\! u)\star\chi_{\Omega}&&(\ell=n)\;.
+\end{aligned}
+\end{equation}
+Here we consider $\chi_{\Omega}$ as an element of ${C^\infty_c}(\bbR^n,\Alt^0)$, so that for another $0$-form $u$ we have the $L^2$ scalar product $\left(\chi_{\Omega},u\right)=\int\chi_{\Omega}(a)u(a)da$, and $\star\chi_{\Omega}$ is the $n$-form $\chi_{\Omega}(x)dx_1\wedge\dots\wedge dx_n$.
+
+The formulas for the endpoints $\ell=0$ and $\ell=n$ correspond to the two extended de Rham complexes without boundary conditions and with compact support, see \eqref{eq:edRwobc} and \eqref{eq:edRwcs}.
+To see this, let us extend the definition of the exterior derivative by writing $\overline d$ for all the mappings of the complex
+$$
+ 0 \to\bbR\to^\iota{C^\infty}(\overline\Omega,\Alt^0) \to^d {C^\infty}(\overline\Omega,\Alt^1)
+ \to^d\cdots \to^d {C^\infty}(\overline\Omega,\Alt^n) \to 0
+$$ 
+and $\underline d$ for all the mappings of the complex
+$$
+ 0 \to {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^0) \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^1) \to^d\cdots
+ \to^d {C^\infty}_{\overline\Omega}(\bbR^n,\Alt^n) \to^{\iota^*} \bbR \to 0
+$$
+where $\iota$ is the inclusion mapping for constant functions and 
+$\iota^*=(\star\iota)'$ denotes the integral $u\mapsto\int\!u$ for $n$-forms.
+
+If we correspondingly extend the definitions of $R_{\ell}$ and $\Bogov_{\ell}$ by
+$$
+\begin{aligned}
+  R_0u &:=\left(\chi_{\Omega},u\right)\,\text{ for $0$-forms }u\,, &
+  R_{n+1} &:=0\,,\\
+  T_{n+1}u &:= \star(u\chi_{\Omega}) \,\text{ for }u\in\bbR\,,  &
+  T_0 &:= 0\,,
+\end{aligned}
+$$
+then we can write the relations \eqref{eq:dR+Rd=1} and \eqref{eq:dT+Td=1} simply as
+\begin{equation}\label{eq:R&T&d}
+ \overline d\,R_{\ell} u + R_{\ell+1} \,\overline d u  = u
+ \quad \text{ and }\quad
+ \underline d\,\Bogov_{\ell} u + T_{\ell+1} \,\underline du = u\quad \text{ for all }\;
+  0\le\ell\le n.
+\end{equation}
+
 \section*{Theorem 8.1}

### 2024-06-25 main.tex
write up

@@
 We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
+We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
+Bogovski\u{\i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
 We construct an important geometric reflection operator in Section~\ref{section:extension}
@@
 
-\section{Extension operator on finite element stars}\label{section:extension}
-% Only define the geometric mapping and its important quantities
-% Leave the function spaces etc. for later
-
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-\subsection{Review of vector calculus}
+\section{Review of vector calculus and exterior calculus}
 
@@
 
-\subsection{Review of exterior calculus}
-
-We also investigate this from the perspective of exterior calculus. 
+%\section{Review of exterior calculus}
+
+We also assume the perspective of exterior calculus. 
 We give a brief introduction into this topic. 
@@
 
+\section{Bogovski\u{\i}-type operators over convex sets}\label{section:bogovskii}
+
+We use potential operators for the exterior derivative over convex domains that respect boundary conditions. 
+These are known as Bogovski\u{\i}-type operators.
+They were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics.~\cite{bogovskii} 
+The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel},
+on whose work the following presentation is based. 
+In contrast to the aforementioned reference, the goal of our discussion is more modest:
+we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
+However, we derive explicit bounds for the operator norms, which are of independent interest.
+
+We begin with introducing the Costabel-McIntosh kernel.
+For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
+\begin{equation}\label{eq:Gl}
+  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
+\end{equation}
+Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
+we then define the integral operators
+\begin{align}
+  \Bogov_{\ell} u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+\end{align}
+We call $\Bogov_{\ell}$ a Bogovski\u{\i}-type operator.
+
+We show that the integrals in the definition of $\Bogov_{\ell}$ actually exist. 
+we first rewrite the kernel $G_{\ell}$:
+\begin{align*}
+    G_{\ell}(x,y) 
+    &= 
+    \int_0^\infty \tau^{n-\ell} (\tau+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+\tau(x-y) \right)\,d\tau
+    \\
+    &= 
+    \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
+    \int_0^\infty \tau^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+\tau(x-y) \right)\,d\tau 
+    \\
+    &= 
+    |\Omega|^{-1}\sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \,
+    |x-y|^{k-n} \int_0^\infty r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    .
+\end{align*}
+We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
+\begin{align*}
+    G_{\ell}(x,y) 
+    &\leq 
+    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr 
+    \\
+    &= 
+    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
+\end{align*}
+We pointwise estimate $\Bogov_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| \Bogov_{\ell} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+    \\&\leq 
+    \left| 
+        \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \right| 
+    \\&\leq 
+    \left| 
+        \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
+    \right| 
+    .
+\end{align*}
+We recall the radial integrals 
+\begin{align*}
+    \int_{B_D(0)} |z|^{k+1-n} dz
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k} dr
+    =
+    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
+    .
+\end{align*}
+We compute 
+\begin{align*}
+    &
+    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
+    \\&
+    =
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
+    .
+\end{align*}
+Here, $A(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
+and which is bounded by $2^{\ell-1}$. 
+So the convolution of $u$ is taken against an integrable function. 
+Taylor's convolution inequality now implies: 
+\begin{align*}
+    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
+    &\leq 
+    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
+    D
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    D
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+In particular, for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\[
+    \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+\]
+This follows from a density argument.
+
+Additional properties of these operators become apparent after a change of variables. 
+We write down the full definition of these operators and perform two substutions:
+first, we substitute $a = y + t(x-y)$ and then we substitute $s = \frac{t}{t-1}$,
+leading to 
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    &= 
+    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(y+t(x-y)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    .
+\end{align*}
+We first discuss the support properties of this operator. 
+Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ satisfies $\supp u \subseteq \overline\Omega$.
+Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
+meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
+
+We study the interaction of this potential operator with the exterior derivative.
+Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ with $\supp u \subseteq \overline\Omega$.
+We rewrite the potential,
+\begin{align*}
+    T_{\ell,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan T_{\ell,a} u(x) 
+    &= 
+    k
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \partial_{j} u(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
+    .
+\end{align*}
+The potential operator, applied to this result, gives 
+\begin{align*}
+    T_{\ell+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    \cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan T_{\ell,a} u(x)
+    +
+    T_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    k
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    \int_{1}^\infty \partial_{t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    u_{\sigma}\left(x)\right) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan T_{\ell,a} u = u$.
+
+For full technical clarify, we show we have a bounded operator 
+\[
+    \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+    .
+\]
+% - Rewrite kernel
+% - Show the support property
+% - Assess that it is Lp bounded for compactly supported forms; density argument
+% - Conclude that it is absolutely convergent. Do one (!) derivative
+% - Poincare lemma for smooth forms : needs smoothness, but that's a simple calculation 
+% - prove duality via some density argument and the extension of smooth forms outside of Lipschitz domains
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$. There exists a bounded mapping 
+    \begin{align*}
+     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+    \end{align*}
+    such that 
+    \begin{align*}
+        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
+    \end{align*}
+    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
+\end{lemma}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. Then 
+    \begin{align*}
+        \| \vec u \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \vec u \|_{L^{2}(\Omega)}.
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
+    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
+    with smallest singular value $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
+    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
+    which has the same smallest singular value. 
+\end{proof}
+
+\section{Extension operator on finite element stars}\label{section:extension}
+% Only define the geometric mapping and its important quantities
+% Leave the function spaces etc. for later
+
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
+
 \subsection{Inequalities for partial boundary conditions on a single simplex}
-
 We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
@@
 Let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-that maps the faces $F_{0}, F_{1}, \dots, F_{l}$ onto the boundary patch $\Gamma$. 
+that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
 We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
@@
 
-We introduce the operator $B^{k}$, which is
-\begin{equation}\label{eq:Bogo} % TODO: rewrite 
-    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da.
-\end{equation}
-If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
-then $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$ and $B^{k} u(x) = 0$ when $x \notin \Omega$. 
-Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
-Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
-% The fact that $B^{k}$ indeed maps C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
+Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
+We set $\hat f := \Phi^{\ast} f$ and $\hat u = \Phi^{\ast} u$, 
+so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
+
+We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
+Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
+
+The operator norm bound of the potential operator shows 
+\begin{align*}
+    \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+    &\leq 
+    n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
+    \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+    \\&
+    2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
+    \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+    .
+\end{align*}
+We use the pullback estimates 
+\begin{align*}
+    \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+    &\leq 
+    .
+    \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+    .
+\end{align*}
+\begin{align*}
+    \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
+    &\leq 
+    2^{n-l}
+    \| \hat f \|_{L^{p}(\Upsilon^{n})} 
+    \leq 
+    2^{n-l}
+    \Phi
+    \| f \|_{L^{p}(\Upsilon^{n})} 
+    .
+\end{align*}
+
+Let $\Upsilon^{n}$ is convex with diameter $2$.
 
@@
 
-\begin{align}
-    v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
-    \\
-    \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
-    \\
-    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
-    \\
-    v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
-    \\
-    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
-\end{align}
-\begin{align}
-    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
-    +
-    \sum_{i=1}^{k} \lambda_{i} v_i 
-    +
-    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
-    -
-    \sum_{i=k+1}^{n-1} \lambda_{i} v_i
-\end{align}
-\begin{align}
-    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
-    +
-    \sum_{i=1}^{k} \lambda_{i} v_i 
-    +
-    \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i
-    +
-    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
-\end{align}
-
 \section*{Acknowledgments}

### 2024-06-25 draft.tex

@@
 
+We introduce the operator $B^{k}$, which is
+\begin{equation}\label{eq:Bogo} % TODO: rewrite 
+    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da.
+\end{equation}
+If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
+then $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$ and $B^{k} u(x) = 0$ when $x \notin \Omega$. 
+Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
+Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
+% The fact that $B^{k}$ indeed maps C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.
+
 \section*{Theorem 8.1}

### 2024-06-25 main.tex
corrections

@@
 
+\usepackage{hyperref}         % For hypertext links
+
 % Title, authors, and affiliations
-\title{Poincar\'e--Friedrichs constants over triangulated domains}
-\author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
+% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
+% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
+
+\title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
+\author{
+    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
+    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{email2@example.com}} \and
+    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
+}
 
@@
 %
-For the purpose of our discussion, this formalisms allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
+For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
 \\
@@
 Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation.
-However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity.
+However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape-regularity.
 Some interesting limit cases include the slit domain and the crossed bricks domain,
@@
 Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively glueing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
+by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
 the gluing interface is a triangulated submanifold of the boundary. 
 This forces the intermediate triangulations to be particularly well-shaped.
-
-\color{red}Do Ern and Guermond construct a potential for the gradient over triangulations? What exactly is their approach\color{black}
-\nocite{gross2004electromagnetic,hiptmair2002finite}
 
@@
 Second, we develop explicit estimates for the regularized Bogovski operator. 
+\nocite{gross2004electromagnetic,hiptmair2002finite}
 
@@
 
-\color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
+\color{red}Our upper bounds do not depend on the angles of such re-entrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
 \\
@@
     It also enters the a~priori error analysis. 
-\end{remark}
-
-\begin{remark}
- For reference, how the extension should work:
- suppose that $u \in H(\Omega)$ and let $f = du$.
- Suppose we have $u_1 \in H(T_1)$ with $du_1 = du$ over $T_1$. 
- We built $u'_2 \in H(T_2)$ such that 
- \begin{align*}
-    \trace_F u_1 = \trace_F u'_2
- \end{align*}
- We let $u''_2 \in H(T_2)$ such that 
- \begin{align*}
-    d u''_2 = f - d u'_2, \quad \trace_F u''_2 = 0
- \end{align*}
- Such $u''_2$ exists because 
- \begin{align*}
-  \trace_F( f_2 - d u'_2 ) 
-  &= 
-  \trace_F f_1 - \trace_F d u'_2
-  \\&= 
-  \trace_F f_1 - \trace_F d u'_2
-  \\&= 
-  \trace_F d u_1 - \trace_F d u'_2
-  \\&= 
-  d \trace_F u_1 - d \trace_F u'_2
-  \\&= 
-  d \trace_F u_1 - d \trace_F u_1
-  = 0
-  .
- \end{align*}
- Setting $u_2 = u'_2 + u''_2$, we find 
- \begin{align*}
-    d u_2 = d u'_2 + d u''_2 = d u'_2 + f - d u'_2 = f,
-    \\
-    \trace_F u_2 = \trace_F u'_2 = \trace_F u_1.
- \end{align*}
- That requires an extension from given partial boundary data. 
- Possible approaches:
- \begin{itemize}
-  \item Reflect a neighborhood and multiply with cut-off function.
-  \item Take traces from patch and extend onto new simplex. 
- \end{itemize}
-
 \end{remark}
@@
 These are known as Bogovski\u{\i}-type operators.
-They were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics.~\cite{bogovskii} 
-The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel},
+They were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics.~\cite{bogovskii1979solution} 
+The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel2010bogovskiui},
 on whose work the following presentation is based. 
@@
 We show that the integrals in the definition of $\Bogov_{\ell}$ actually exist. 
-we first rewrite the kernel $G_{\ell}$:
+In order to understand the properties of the operator $\Bogov_{\ell}$,
+including the convergence of the integral, we first rewrite the Costabel-McIntosh kernel $G_{\ell}$:
 \begin{align*}
@@
 \end{align*}
-We pointwise estimate $\Bogov_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
+We can now analyze the potential operator $\Bogov_{\ell}$. 
+Suppose that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$ and that $x \in \bbR^{n}$.
+First, if $x \notin \overline\Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t \geq 1$.
+Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
+More generally, we pointwise estimate $\Bogov_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
 \begin{align*}
@@
     \\&\leq 
-    \left| 
     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
-    \right| 
     \\&\leq 
-    \left| 
     \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
-    \right| 
     .
@@
 and which is bounded by $2^{\ell-1}$. 
+In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
 So the convolution of $u$ is taken against an integrable function. 
@@
 \end{align*}
-In particular, for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+We have assumed so far that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$. 
+Since that space is dense in the Lebesgue spaces, a density argument provides gives the following: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
 \[
@@
 \]
-This follows from a density argument.
+Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
+that is, the reconstructed potential has support contained within $\overline\Omega$.
 
 Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substutions:
-first, we substitute $a = y + t(x-y)$ and then we substitute $s = \frac{t}{t-1}$,
+We write down the full definition of these operators and perform two substitutions:
+first, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
 leading to 
@@
 \end{align*}
-We first discuss the support properties of this operator. 
-Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ satisfies $\supp u \subseteq \overline\Omega$.
-Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
-meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
-
-We study the interaction of this potential operator with the exterior derivative.
-Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ with $\supp u \subseteq \overline\Omega$.
+% We first discuss the support properties of this operator. 
+% Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ satisfies $\supp u \subseteq \overline\Omega$.
+% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
+% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
+% 
+Given $a \in \Omega$, we introduce the potential operator 
+\begin{align*}
+    \Bogov_{\ell,a} u(x) 
+    &:= 
+    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
+    .
+\end{align*}
+By definition,
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    =
+    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da\;
+    .
+\end{align*}
+We study the interaction of the potential operator with the exterior derivative in more detail.
+Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$ with $\supp u \subseteq \overline\Omega$.
 We rewrite the potential,
@@
     \int_{1}^\infty 
-    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
     .
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \partial_{j} u(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
-    .
-\end{align*}
-The potential operator, applied to this result, gives 
+    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
+    ,
+\end{align*}
+and apply the potential operator to this result, which gives 
 \begin{align*}
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
-    \cartanx^{j} \wedge \cartanx^{\sigma}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    \;\cartanx^{j} \wedge \cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \;\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan T_{\ell,a} u(x)
+    +
+    T_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
     \cartanx^{\sigma}
@@
     (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
     (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan T_{\ell,a} u(x)
-    +
-    T_{\ell+1,a} \cartan u(x)
     \\&
     =
-    k
     \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
     \\&\qquad
     +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \partial_{j} u_{\sigma}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
     \cartanx^{\sigma}
@@
     \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{1}^\infty \partial_{t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}\left(x)\right) \cartanx^{\sigma}
+    u_{\sigma}(x) \cartanx^{\sigma}
     =
@@
 \subsection{Inequalities for partial boundary conditions on a single simplex}
+
+\begin{lemma}
+    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    Then 
+    \begin{align*}
+        \| u \| \leq 
+    \end{align*}
+\end{lemma}
+\begin{proof}
     We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
@@
         &\leq 
-    .
+        ....
         \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
@@
         2^{n-l}
-    \Phi
+        ....
         \| f \|_{L^{p}(\Upsilon^{n})} 
@@
     \end{align*}
-
-Let $\Upsilon^{n}$ is convex with diameter $2$.
+\end{proof}
 
@@
 
+\begin{align}
+    v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
+    \\
+    \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
+    \\
+    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
+    \\
+    v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
+    \\
+    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
+\end{align}
+\begin{align}
+    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+    +
+    \sum_{i=1}^{k} \lambda_{i} v_i 
+    +
+    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+    -
+    \sum_{i=k+1}^{n-1} \lambda_{i} v_i
+\end{align}
+\begin{align}
+    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+    +
+    \sum_{i=1}^{k} \lambda_{i} v_i 
+    +
+    \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i
+    +
+    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+\end{align}
+
+\begin{remark}
+    For reference, how the extension should work:
+    suppose that $u \in H(\Omega)$ and let $f = du$.
+    Suppose we have $u_1 \in H(T_1)$ with $du_1 = du$ over $T_1$. 
+    We built $u'_2 \in H(T_2)$ such that 
+    \begin{align*}
+    \trace_F u_1 = \trace_F u'_2
+    \end{align*}
+    We let $u''_2 \in H(T_2)$ such that 
+    \begin{align*}
+    d u''_2 = f - d u'_2, \quad \trace_F u''_2 = 0
+    \end{align*}
+    Such $u''_2$ exists because 
+    \begin{align*}
+    \trace_F( f_2 - d u'_2 ) 
+    &= 
+    \trace_F f_1 - \trace_F d u'_2
+    \\&= 
+    \trace_F f_1 - \trace_F d u'_2
+    \\&= 
+    \trace_F d u_1 - \trace_F d u'_2
+    \\&= 
+    d \trace_F u_1 - d \trace_F u'_2
+    \\&= 
+    d \trace_F u_1 - d \trace_F u_1
+    = 0
+    .
+    \end{align*}
+    Setting $u_2 = u'_2 + u''_2$, we find 
+    \begin{align*}
+    d u_2 = d u'_2 + d u''_2 = d u'_2 + f - d u'_2 = f,
+    \\
+    \trace_F u_2 = \trace_F u'_2 = \trace_F u_1.
+    \end{align*}
+    That requires an extension from given partial boundary data. 
+    Possible approaches:
+    \begin{itemize}
+        \item Reflect a neighborhood and multiply with cut-off function.
+        \item Take traces from patch and extend onto new simplex. 
+    \end{itemize}
+\end{remark}
+
 \section*{Acknowledgments}

### 2024-06-25 main.tex
Update on Overleaf.

@@
 
-{\color{red}This introduction is a very rough draft, including snippets}
-
+\paragraph{Motivation}
 We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains.
 The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry.
-In particular, this yields computable upper bounds for Poincar\'e--Friedrichs inequalities. 
+In particular, these bounds on the operator norms yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
+Equivalently, this gives lower bounds for the eigenvalues of several vector Laplacians.
+
 For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
-we want to bound the $\bfL^2$ norm of the potential
-\begin{align*}
-    \argmin\limits_{ \substack{ \bfv \in \bfL^{2} \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
+we want to find a potential $\bfu \in \bfH(\curl,\Omega)$ under the curl operator whose $\bfL^2$ norm is bounded in terms of the source field.
+This is expressed via the Poincar\'e--Friedrichs inequality
+\begin{align*}
+    \min\limits_{ \substack{ \bfv \in \bfL^{2} \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
     \leq 
@@
 \end{align*}
+The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. Any upper bound for it corresponds to a lower bound for the Maxwell eigenvalues.
+
 Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
 We address this topic in the special case where $\Omega$ admits a shellable triangulation.
-Even though only contractible domains can admit a shellable triangulation, 
+Even though only contractible domains can ever admit a shellable triangulation, 
 having computable upper bounds for such domains is an important step stone towards the more general case. 
-For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.
+For example, local patches around a simplex within a larger triangulation are shellable.
+\\
+
+\color{blue}
+The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
+Furthermore, their constants enter the stability and convergence theory of finite element methods.
+Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
+\color{black}
+\\
+\color{red}
+The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
+Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
+In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
+It also enters the a~priori error analysis. 
+\color{black}
+
+\color{red}Our upper bounds do not depend on the angles of such re-entrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
+\\
+
+\paragraph{Background and literature review}
 
@@
 The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
+In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
 {\color{red}The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. }
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
 We are interested in constants for inequalities such as 
@@
 
+\paragraph{Review literature}
 Before we outline the main results of this exposition in more details, 
@@
 
+An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
+We refer to \cite{hurri1988poincare} for that perspective.
+
+The literature is much scarcer when it comes to this. 
+We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
+By duality, that implies lower bounds for the case of full boundary conditions.
+We remark that their work also shows that over convex domains in 3D:
+\begin{align*}
+    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
+\end{align*}
+But we need to find potentials over a simplex subject to partial boundary conditions 
+and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
+The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
+
+\paragraph{Actual content of the paper}
 The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence satisfying explicitly computable upper bounds.
@@
 
+It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
+In particular, this enables the inductive method of proof.
+
 As a necessary subcomponent, we need to apply local Poincar\'e inequalities to select potentials. 
@@
 By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
-The literature is much scarcer when it comes to this. 
-We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
-By duality, that implies lower bounds for the case of full boundary conditions.
-We remark that their work also shows that over convex domains in 3D:
-\begin{align*}
-    C_{\grad,p} \geq C_{\curl} \geq C_{\divergence}.
-\end{align*}
-But we need to find potentials over a simplex subject to partial boundary conditions 
-and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
-The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
+
 Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
 has no estimates in the literature.
-
-An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
-We refer to \cite{hurri1988poincare} for that perspective.
 
@@
 
-\color{blue}
-
-The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
-Furthermore, their constants enter the stability and convergence theory of finite element methods.
-Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
-\\
-
-\color{red}Our upper bounds do not depend on the angles of such re-entrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
-\\
-
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
-In particular, this enables the inductive method of proof.
-\\
-
+\paragraph{Future work}
 Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres.
+In particular, domains with shellable triangulations are contractible.
 However, these estimates are important partial results.
 Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-\begin{remark}
-    The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
-    Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
-    In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
-    It also enters the a~priori error analysis. 
-\end{remark}
 
@@
 This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).\footnote{\color{red}Is there a better name for this than Xu-Zikatanov estimate?}
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+%\footnote{\color{red}Is there a better name for this than Xu-Zikatanov estimate?}
 Stern~\cite{stern2015banach} provided a generalization of the projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
@@
 
-\section{Review of vector calculus and exterior calculus}
+\section{Review of vector calculus and exterior calculus}\label{section:calculus}
 
@@
     To the authors' best knowledge, neither convention is dominant in the literature.
-    On the one hand, we have a commuting diagram 
+    We summarize the situation in the following commuting diagram: 
     \[
     \begin{CD}
+        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
+        \\
+        @AA{\varkappa^{0}}A 
+        @AA{\varkappa^{1}}A 
+        @AA{\varkappa^{2}}A 
+        \\
         C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) 
@@
     \]
-    where the the middle vertical arrow is the isomorphism that satisfies 
-    \begin{align*}
-        \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right)
-        =
-        \left( u_1, u_2 \right),
-    \end{align*}
-    and the other vertical arrows are the identity. 
-    Alternatively, we may use the commuting diagram 
-    \[
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega)
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \]
-    where the the middle vertical arrow is the isomorphism that satisfies 
-    \begin{align*}
-        \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right)
-        =
-        \left( u_2, -u_1 \right),
-    \end{align*}
-    and the other vertical arrows are the identity. 
+    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
+We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
+    The other vertical arrows are the identity. 
     The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
@@
         &\leq 
-        ....
+        \| \Jacobian\Phi \|_{\infty}^{k}
+        |\det\Phi^{-\frac{1}{p}}|
+        \cdot 
         \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
@@
         2^{n-l}
-        \| \hat f \|_{L^{p}(\Upsilon^{n})} 
+        \| \hat f \|_{L^{p}(\hat T)} 
         \leq 
         2^{n-l}
-        ....
-        \| f \|_{L^{p}(\Upsilon^{n})} 
+        \| \Jacobian\Phi^{-1} \|_{\infty}^{k+1}
+        |\det\Phi^{\frac{1}{p}}|
+        \cdot 
+        \| f \|_{L^{p}(T)} 
         .

### 2024-06-26 main.tex
Update on Overleaf.

@@
     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    These includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
+    This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
     The main application that we envision are computable estimates over finite element patches. 
@@
 We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains.
-The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry.
+The potential operators satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry.
 In particular, these bounds on the operator norms yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
@@
 
-For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
+For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
 we want to find a potential $\bfu \in \bfH(\curl,\Omega)$ under the curl operator whose $\bfL^2$ norm is bounded in terms of the source field.
@@
 
-Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
+Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
 We address this topic in the special case where $\Omega$ admits a shellable triangulation.
@@
 We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Bogovski\u{\i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
+Bogovski\u{i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
 We construct an important geometric reflection operator in Section~\ref{section:extension}
 and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+
+One component of our efforts are estimates for Bogovski\u{i}-type potential operators over convex domains, seen as operators between Lebesgue spaces. 
+This follows closely the discussions in the literature~\cite{costabel2010bogovskiui} but no operator norm estimates are given in the literature, to the best of our best knowledge.
+The Bogovski\u{i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
+It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
+Our variant of the Bogovski\u{i} potential operator is simplified in comparison earlier discussions:
+we only view it over convex domains and use simpler (that is, constant) weight function. 
+The resulting operator has generally lower regularity properties in comparison to the regularized potential in the literature but the regularity is sufficient for our purposes and the operator norms are easily computed.
+We consider this outcome to be of independent interest.
+
+The Bogovski\u{i} potential operator is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to boundary conditions.
+For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential.
+We achieve by constructing an auxiliary problem subject to full boundary conditions.
+
+This construction of potentials requires triangulations with special conditions: 
+we assemble the triangulation sequentially, adding one simplex after the other, such that the interface between new previous intermediate triangulation and the next simplex is always a boundary submanifold of either of them.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Such triangulations are also known as shellable.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D are shellable.
+
+Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus.
+Exterior calculus has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,arnold2006finite}.
+Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
+The formalism is independent of the dimension and highlights structures commmon to the gradient, curl, and divergence operators.
+It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
+
+\cite{vohralik2005discrete}
 
@@
 
-The strictly positive convex combinations of the simplex' vertices are the \textit{interior} of the simplex,
+The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
 and its remaining points constitute the \textit{boundary} of the simplex.
@@
 
+Let $T$ be an $n$-dimensional simplex with some subsimplex $F$ We show that there exists a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is only on one side of the hyperplane.
+
+\begin{lemma}\label{lemma:oppositesubsimplex}
+    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
+    Let $F, F'$ be the two subsimplices of $T$ with respective sets of vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
+    Then $T$ lies on one side of the affine subspace
+    \[
+        A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
+    \]
+    Moreover, $F = T \cap A$.
+\end{lemma}
+\begin{proof}
+    Evidently, $A$ has dimension $n-1$ and $F \cap A \cap T$.
+    Let us now suppose that $x \in A \cap T$.
+    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
     \begin{align}
-    v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
-    \\
-    \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
-    \\
-    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
-    \\
-    v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
-    \\
-    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
-\end{align}
-\begin{align}
-    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+        x 
+        &
+        = 
+        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
+        \\&
+        = 
+        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
         + 
-    \sum_{i=1}^{k} \lambda_{i} v_i 
+        \sum_{i=1  }^{k  } \lambda_{i} v_i 
         + 
-    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
-    -
-    \sum_{i=k+1}^{n-1} \lambda_{i} v_i
-\end{align}
-\begin{align}
-    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
-    +
-    \sum_{i=1}^{k} \lambda_{i} v_i 
+        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
         + 
         \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
-    +
-    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+        .
     \end{align}
+    We know $x$ can be written as a unique convex combination of the vertices of $T$.
+    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive. 
+    If $x \notin F$, then at least one of these coefficients must be negative. 
+    But then their sum must be negative, which is a contradiction. 
+    The desired statement follows.         
+\end{proof}
 

### 2024-06-26 main.tex
clean up

--- 2024-06-25 main.tex
@@
 
-\paragraph{Motivation}
 We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains.
@@
 having computable upper bounds for such domains is an important step stone towards the more general case. 
-For example, local patches around a simplex within a larger triangulation are shellable.
-\\
-
-\color{blue}
-The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
-Furthermore, their constants enter the stability and convergence theory of finite element methods.
-Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
-\color{black}
-\\
-\color{red}
-The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
-Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
-In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
-It also enters the a~priori error analysis. 
-\color{black}
-
-\color{red}Our upper bounds do not depend on the angles of such re-entrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
-\\
-
-\paragraph{Background and literature review}
-
+For example, local patches around a simplex within a larger 2D or 3D triangulation are shellable.
+We express all our main results in the calculus of differential forms, also known as exterior calculus, 
+and state the instances of the curl and divergence operator as special cases. 
+\\
+
+Before we outline the main results of this exposition in more details, 
+we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
 We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
@@
 picking the average-free potential 
+One example for a bounded linear operator is the average-free potential:
 \begin{align*}
@@
     \bff \in \nabla W^{1,p}(\Omega)
-\end{align*}
-is a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
+    .
+\end{align*}
+Its operator norm is the constant in the Poincar\'e inequality 
 \begin{align*}
@@
 
-The situation is less clear cut when we study the curl or divergence operators
+Most research on optimal constants has addressed the case of convex domains. 
+Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
+Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.
+When the domain is not convex but star-shaped with respect to a ball,
+then a Poincar\'e inequality is already implicit in polynomial interpolation estimates that are known to the mathematical community~\cite{...}. 
+An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
+We refer to \cite{hurri1988poincare} for that perspective.
+
+The situation is less clear cut when we study the curl or divergence operators in vector calculus.
+Here, we use the function spaces
+\begin{align*}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
+    .
+\end{align*}
+Their members are vector fields whose distributional partial derivatives satisfy certain cancellation properties. 
+Our objective is to find bounded potentials for the operators 
 \begin{align*}
@@
 \end{align*}
-where we use the function spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
-    .
-\end{align*}
 The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
 In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-{\color{red}The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. }
+The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
 We are interested in constants for inequalities such as 
@@
 \end{align*}
-We remark that seemingly not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators, 
+Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
 % even if the domain is convex, 
-which is in sharp contrast to the study of the gradient operator.
-
-We explore formulate our main results in the framework of exterior calculus.
-The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
-%
-It is used ubiquitously in physics and engineering. 
-%
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-\paragraph{Review literature}
-Before we outline the main results of this exposition in more details, 
-we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains.
-
-% Convex domains
-
-% Domains star-shaped with respect to a ball
-
-% Limitations
-
-Most research on optimal constants has addressed the case of convex domains. 
-Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.
-
-In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
+This sharply contrasts to the study of the gradient operator.
+
+The literature is much scarcer when it comes to this. 
+We can access some estimates from the literature in the formalism of exterior calculus. 
+We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$ and no boundary conditions are imposed. 
+In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator over convex domains.
+This implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
+By duality, that implies lower bounds for the case of full boundary conditions.
+We remark that their work also shows that over convex domains in 3D:
+\begin{align*}
+    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
+\end{align*}
+% TODO: summarize 
+When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constant 
+follow from bounds on the operator norm of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
+as mapping between Lebesgue spaces,
+though these estimates have not been made explicit in the literature yet.
 \\
@@
 While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
-we are not aware of computable estimates. 
+we are not aware of computable estimates for the case of $\bfH(\curl)$ and $\bfH(\divergence)$. % TODO
 Clearly, not all local patches describe convex subdomains. 
-An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
-Indeed, finite element patches of Lipschitz satisfy that condition. 
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that stars in triangulations are often star-shaped with respect to a ball. 
 Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. 
 However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape-regularity. 
+Estimates that rely on this geometric condition deteriorate when the aforementioned ball has small radius,
+and that is inevitable when the domain has a bad geometry. 
 Some interesting limit cases include the slit domain and the crossed bricks domain,
@@
 
-An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
-We refer to \cite{hurri1988poincare} for that perspective.
-
-The literature is much scarcer when it comes to this. 
-We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
-By duality, that implies lower bounds for the case of full boundary conditions.
-We remark that their work also shows that over convex domains in 3D:
-\begin{align*}
-    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
-\end{align*}
-But we need to find potentials over a simplex subject to partial boundary conditions 
-and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
-The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
+Veeser and Verfürth have provided computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over finite element stars~\cite{veeser2000}.
+
+% TODO:V&V seems to be the only reference for stars .... 
+General results of this type for a class containing the finite element stars are not known to us. 
+In particular and as will be illustrated in a moment, 
+Poincaré constants of stars and thus of star-shaped domains may be arbitrarily large. 
+Consequently, corresponding bounds have to incorporate some quantity that is sensible to the possible lack of
+convexity.
+
+There is a popular avenue towards estimates that is able to circumvent the effect of low boundary regularity. 
+A common principle of many proofs is to construct a potential step-by-step: 
+starting with a single triangle, the potential is constructed over an increasing subdomain, until the entire domain is complete.
+That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest.
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed. 
+That difference can easily be removed. 
+...
+Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
+% TODO: list literature
+% TODO: details 
+\\
 
@@
 In particular, this enables the inductive method of proof.
+% 
+We explore formulate our main results in the framework of exterior calculus.
+The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
+%
+It is used ubiquitously in physics and engineering. 
+%
+For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis.
+
+But we need to find potentials over a simplex subject to partial boundary conditions 
+and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
+The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
+
+The regularized Bogovskii potential operator was studied extensively by Costabel and McIntosh.
+These operators are defiend over sets star-shaeped with respect to a ball. 
+Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. 
+We study a variation of this potential operator over convex sets.
+We simply use a constant averaging over the entire domain. 
+While the resulting Bogovskii-type potential has more moderate regularity properties, 
+this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms.
 
@@
 Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+
+\color{blue}
+The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
+Furthermore, their constants enter the stability and convergence theory of finite element methods.
+Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
+\color{black}
+\\
+\color{red}
+The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
+Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
+In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
+It also enters the a~priori error analysis. 
+\color{black}
+
+\color{red}Our upper bounds do not depend on the angles of such re-entrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
+\\
 
@@
 Whenever $T$ is an $n$-dimensional simplex 
-\begin{align*}
+\begin{align}\label{math:geometricshapemeasure}
     \kappa(T)
@@
     .
-\end{align*}
+\end{align}
 Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
-\begin{align*}
+\begin{align}\label{math:moremeasures}
     \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
@@
     \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
-\end{align*}
+\end{align}
 Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
 that preserves $F$. We define 
-\begin{align*}
+\begin{align}\label{math:reflectionmeasure}
     \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
-\end{align*}
+\end{align}
 This indicator quantifies how much reflection across the shared face distorts the geometry.
 
-% and $\Phi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
+% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
 % we define the quantity 
@@
 \begin{lemma}\label{lemma:affinetransform}
-    Let $T$ be an $n$-simplex and let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
-    \begin{align*}
-        \| \Jacobian \Phi \|
+    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
+    \begin{align*}
+        \| \Jacobian \varphi \|
         \leq 
@@
         \qquad 
-        \| \Jacobian \Phi^{-1} \|
+        \| \Jacobian \varphi^{-1} \|
         \leq 
@@
 \begin{proof}
-    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
-    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\Phi)$. Hence 
+    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\varphi$ in descending order.
+    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\varphi)$. Hence 
     \[
@@
         \sqrt{2} 
-        \frac{ \sigma_1^{n} }{ \det(\Jacobian\Phi) } 
+        \frac{ \sigma_1^{n} }{ \det(\Jacobian\varphi) } 
         \sigma_n
@@
     Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
-    We fix affine homeomorphisms $\Phi_1 : \hat T_1 \rightarrow T_1$ and $\Phi_2 : \hat T_2 \rightarrow T_2$
+    We fix affine homeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
     which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
-    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.
-
-    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \Phi \in W^{1,p}(\hat U)$. 
+    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
+
+    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
     We observe 
@@
         \leq 
-        |\det(\Dif \Phi_1)|
-        \cdot \| \Dif \Phi_1 \|^{p}
+        |\det(\Dif \varphi_1)|
+        \cdot \| \Dif \varphi_1 \|^{p}
         \cdot 
@@
         +
-        |\det(\Dif \Phi_2)|
-        \cdot \| \Dif \Phi_2 \|^{p}
+        |\det(\Dif \varphi_2)|
+        \cdot \| \Dif \varphi_2 \|^{p}
         \cdot 
@@
         \max\left( 
-            |\det(\Dif \Phi_1)|^{-1} \cdot \| \Dif \Phi_1 \|^{p}
-            ,
-            |\det(\Dif \Phi_2)|^{-1} \cdot \| \Dif \Phi_2 \|^{p}
+            |\det(\Dif \varphi_1)|^{-1} \cdot \| \Dif \varphi_1 \|^{p}
+            ,
+            |\det(\Dif \varphi_2)|^{-1} \cdot \| \Dif \varphi_2 \|^{p}
         \right)
@@
         \max\left( 
-            |\det(\Dif \Phi_1)|^{-\frac 1 p} \cdot \| \Dif \Phi_1 \|
-            ,
-            |\det(\Dif \Phi_2)|^{-\frac 1 p} \cdot \| \Dif \Phi_2 \|
+            |\det(\Dif \varphi_1)|^{-\frac 1 p} \cdot \| \Dif \varphi_1 \|
+            ,
+            |\det(\Dif \varphi_2)|^{-\frac 1 p} \cdot \| \Dif \varphi_2 \|
         \right)
@@
     \end{align*}
-    Next, setting $w = \hat w \circ \Phi^{-1}$, we find $\nabla w = \nabla u$ and 
+    Next, setting $w = \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
     \begin{align*}
@@
         \max\left( 
-            |\det(\Dif \Phi_1)|
-            ,
-            |\det(\Dif \Phi_2)|
+            |\det(\Dif \varphi_1)|
+            ,
+            |\det(\Dif \varphi_2)|
         \right)^{\frac 1 p}
@@
         \max\left( 
-            |\det(\Dif \Phi_1)|
-            ,
-            |\det(\Dif \Phi_2)|
+            |\det(\Dif \varphi_1)|
+            ,
+            |\det(\Dif \varphi_2)|
         \right)^{\frac 1 p}
         \max\left( 
-            |\det(\Dif \Phi_1)|^{-\frac 1 p} 
-            ,
-            |\det(\Dif \Phi_2)|^{-\frac 1 p} 
+            |\det(\Dif \varphi_1)|^{-\frac 1 p} 
+            ,
+            |\det(\Dif \varphi_2)|^{-\frac 1 p} 
         \right)
@@
         \max\left( 
-            |\det(\Dif \Phi_1)|
-            ,
-            |\det(\Dif \Phi_2)|
+            |\det(\Dif \varphi_1)|
+            ,
+            |\det(\Dif \varphi_2)|
         \right)^{\frac 1 p}
         \min\left( 
-            |\det(\Dif \Phi_1)|
-            ,
-            |\det(\Dif \Phi_2)| 
+            |\det(\Dif \varphi_1)|
+            ,
+            |\det(\Dif \varphi_2)| 
         \right)^{-\frac 1 p} 
@@
         \max\left( 
-            \frac{ |\det(\Dif \Phi_1)| }{ |\det(\Dif \Phi_2)| }
-            ,
-            \frac{ |\det(\Dif \Phi_2)| }{ |\det(\Dif \Phi_1)| }
+            \frac{ |\det(\Dif \varphi_1)| }{ |\det(\Dif \varphi_2)| }
+            ,
+            \frac{ |\det(\Dif \varphi_2)| }{ |\det(\Dif \varphi_1)| }
         \right)^{\frac 1 p}
@@
  For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{j(m)}$ be a face of dimension $n-1$. 
- We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated \textbf{domain}. % TODO: technical stuff
+ We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
 
@@
     \begin{align*}
-        C_{\partial,p}
-        \leq 
-        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right),  
+        C_{{\rm PF},T,F,p}
+        \leq 
+        \left( C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p} \right),  
         \quad 
-        C_{\partial,p}
+        C_{{\rm PF},T,F,p}
         \leq 
@@
 
-    There exists $\Phi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \Phi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Phi )$. 
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \varphi )$. 
     Then $\nabla \hat u = \hat g$. 
@@
         \leq 
-        |\det(\Dif \Phi)|^{\frac 1 p} 
+        |\det(\Dif \varphi)|^{\frac 1 p} 
         \| \hat u \|_{L^{p}(\hat T)}
         \leq 
-        |\det(\Dif \Phi)|^{\frac 1 p} 
+        |\det(\Dif \varphi)|^{\frac 1 p} 
         \| \tilde u \|_{L^{p}(\hat U)}
@@
         2^{\frac n p}
-        |\det(\Dif \Phi_1)|^{-\frac 1 p} \| \Dif \Phi \| \cdot 
+        |\det(\Dif \varphi_1)|^{-\frac 1 p} \| \Dif \varphi \| \cdot 
         \| \nabla u \|_{\bfL^{p}(T)}
@@
     Let $\hat T$ be the reference simplex.
-    % We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
+    % We fix affine homeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
     % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
@@
 
-    Let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
     that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
@@
     Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
-    We set $\hat f := \Phi^{\ast} f$ and $\hat u = \Phi^{\ast} u$, 
+    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
     so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
@@
         &\leq 
-        \| \Jacobian\Phi \|_{\infty}^{k}
-        |\det\Phi^{-\frac{1}{p}}|
+        \| \Jacobian\varphi \|_{\infty}^{k}
+        |\det\varphi^{-\frac{1}{p}}|
         \cdot 
@@
         2^{n-l}
-        \| \Jacobian\Phi^{-1} \|_{\infty}^{k+1}
-        |\det\Phi^{\frac{1}{p}}|
+        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
+        |\det\varphi^{\frac{1}{p}}|
         \cdot 

### 2024-06-26 main.tex

@@
 We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
-The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry.
+The potential operators satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry. 
 In particular, these bounds on the operator norms yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
@@
 
-Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-We address this topic in the special case where $\Omega$ admits a shellable triangulation.
+Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
+We accomplish our results for a special class of triangulations, so-called shellable triangulations.
+We address this topic in the special case where $\Omega$ admits special triangulations, 
+namely the class of so-called \emph{shellable} triangulations. 
 Even though only contractible domains can ever admit a shellable triangulation, 
@@
 Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
-we search for a constant $C > 0$ such that 
+we search for a constant $C_{\grad,p} > 0$ such that 
 \begin{align*}
@@
 The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
-Even though the existence of such a bounded linear potential construction is not evident a priori, 
-picking the average-free potential 
+% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
 One example for a bounded linear operator is the average-free potential:
@@
 When the domain is not convex but star-shaped with respect to a ball,
-then a Poincar\'e inequality is already implicit in polynomial interpolation estimates that are known to the mathematical community~\cite{...}. 
+then polynomial interpolation estimates already provide the Poincar\'e inequality~\cite{ern2021finite}. 
 An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
@@
 \begin{align*}
-    \argmin\limits_{ \substack{ v \in W^{p}(\curl,\Omega) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)}
+    \argmin\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
+    \| \bfv \|_{\bfL^{p}(\Omega)}
     \leq 
     C_{\curl}
-    \| \bff \|_{L^{p}(\Omega)}
+    \| \bff \|_{\bfL^{p}(\Omega)}
     ,
     \qquad 
-    \argmin\limits_{ \substack{ v \in W^{p}(\divergence,\Omega) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)}
+    \argmin\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
+    \| \bfv \|_{\bfL^{p}(\Omega)}
     \leq 
@@
 We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$ and no boundary conditions are imposed. 
-In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator over convex domains.
+We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue}, who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$.
+The provide lower bounds for the spectrum of the Hodge--Laplace operator over convex domains.
 This implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
 By duality, that implies lower bounds for the case of full boundary conditions.
-We remark that their work also shows that over convex domains in 3D:
+Their work also includes the following sequence of inequalities,
+valid over convex domains in 3D:
 \begin{align*}
@@
 \end{align*}
-% TODO: summarize 
 When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constant 
@@
 
-While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
-we are not aware of computable estimates for the case of $\bfH(\curl)$ and $\bfH(\divergence)$. % TODO
 Clearly, not all local patches describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that stars in triangulations are often star-shaped with respect to a ball. 
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local patchess in triangulations are often star-shaped with respect to a ball. 
 Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. 
@@
 and that is inevitable when the domain has a bad geometry. 
-Some interesting limit cases include the slit domain and the crossed bricks domain,
+Some illustrative limit cases include the slit domain and the crossed bricks domain,
 for which some finite element patches are not star-shaped with respect to any ball.
 
-Veeser and Verfürth have provided computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over finite element stars~\cite{veeser2000}.
-
-% TODO:V&V seems to be the only reference for stars .... 
-General results of this type for a class containing the finite element stars are not known to us. 
-In particular and as will be illustrated in a moment, 
-Poincaré constants of stars and thus of star-shaped domains may be arbitrarily large. 
-Consequently, corresponding bounds have to incorporate some quantity that is sensible to the possible lack of
-convexity.
-
-There is a popular avenue towards estimates that is able to circumvent the effect of low boundary regularity. 
+Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
+However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
+We review some of the main outcomes. 
+% TODO: wait for answer to email 
+Veeser and Verfürth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
+Naturally, their estimate deteriorates when the shape regularity of the mesh deteriotates.
+% 
+There is a popular avenue towards Poincar\'e--Friedrichs constants, which can circumvent the effect of low boundary regularity, 
+and which has been published in different variations~\cite{vohralik2005discrete,ern2021finite}. 
 A common principle of many proofs is to construct a potential step-by-step: 
@@
 and that difference can easily be removed. 
-That difference can easily be removed. 
-...
-Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
-% TODO: list literature
-% TODO: details 
+% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
+
+While we know Poincar\'e--Friedrichs constants over finite element patches for scalar-valued Sobolev spaces, 
+we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
+In the Hilbert space setting, with $p=2$, the Friedrichs inequality over the Sobolev space with Dirichlet boundary conditions implies, via duality, the Poincar\'e--Friedrichs for the divergence operator.
+However, that method seems restricted to the Hilbert space case $p=2$.
+We are not aware of more general estimates for the curl operator, even in the Hilbert space situation. 
 \\
@@
 The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence satisfying explicitly computable upper bounds.
-This is achieved for a special class of triangulated domains,
-namely domains with so-called \emph{shellable} triangulations. 
-Formally, a simplicial complex is shellable if its full-dimensional simplices can be ordered in a sequence such that each such simplex in the sequence intersects the union of the previously listed simplices in a codimension one simplicial complex in the boundary of the new facet being added.
-Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-the gluing interface is a triangulated submanifold of the boundary. 
-This forces the intermediate triangulations to be particularly well-shaped.
-
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
-In particular, this enables the inductive method of proof.
-% 
+We follow closely the philosophy of the aforementioned sequential approach.
+The transition to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
+\\
+
+% Exterior calculus 
+Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus.
+Exterior calculus has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,arnold2006finite}.
+Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
+The formalism is independent of the dimension and highlights structures commmon to the gradient, curl, and divergence operators.
+It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
+
 We explore formulate our main results in the framework of exterior calculus.
@@
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-
+\\
+
+We fix this problem in two steps.
+First, we construct an auxiliary problem subject to full boundary conditions.
+Second, we develop explicit estimates for the regularized Bogovski operator.
+\nocite{gross2004electromagnetic,hiptmair2002finite}
+\\
+
+% General outline 
+% TODO: outline of the construction; mention why shellable is important; mixed BC
+This construction of potentials requires triangulations with special conditions: 
+we assemble the triangulation sequentially, adding one simplex after the other, such that the interface between new previous intermediate triangulation and the next simplex is always a boundary submanifold of either of them.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Such triangulations are also known as shellable.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D are shellable.
+
+As a necessary subcomponent, we need to apply local Poincar\'e inequalities to select potentials. 
+Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients. 
+We construct gradient potentials locally over convex domains or face patches. 
+We can access a considerable body of literature for gradient Poincar\'e inequalities over convex domains~\cite{bebendorf2003note}.
+In fact, optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known over convex domains.
+By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
+\\
+
+% Shellable 
+Formally, a simplicial complex is shellable if its full-dimensional simplices can be ordered in a sequence such that each such simplex in the sequence intersects the union of the previously listed simplices in a codimension one simplicial complex in the boundary of the new facet being added.
+Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
+by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
+the gluing interface is a triangulated submanifold of the boundary. 
+This forces the intermediate triangulations to be particularly well-shaped.
+
+It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
+In particular, this enables the inductive method of proof.
+\\
+
+% Mixed BC
 But we need to find potentials over a simplex subject to partial boundary conditions 
@@
 The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
+
+Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
+has no estimates in the literature.
+
+One component of our efforts are estimates for Bogovski\u{i}-type potential operators over convex domains, seen as operators between Lebesgue spaces. 
+This follows closely the discussions in the literature~\cite{costabel2010bogovskiui} but no operator norm estimates are given in the literature, to the best of our best knowledge.
+The Bogovski\u{i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
+It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
+Our variant of the Bogovski\u{i} potential operator is simplified in comparison earlier discussions:
+we only view it over convex domains and use simpler (that is, constant) weight function. 
+The resulting operator has generally lower regularity properties in comparison to the regularized potential in the literature but the regularity is sufficient for our purposes and the operator norms are easily computed.
+We consider this outcome to be of independent interest.
+
+The Bogovski\u{i} potential operator is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to boundary conditions.
+For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential.
+We achieve by constructing an auxiliary problem subject to full boundary conditions.
 
@@
 
-As a necessary subcomponent, we need to apply local Poincar\'e inequalities to select potentials. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients. 
-We construct gradient potentials locally over convex domains or face patches. 
-We can access a considerable body of literature for gradient Poincar\'e inequalities over convex domains~\cite{bebendorf2003note}.
-In fact, optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known over convex domains.
-
-By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
-
-Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
-has no estimates in the literature.
-
-We fix this problem in two steps. 
-First, we construct an auxiliary problem subject to full boundary conditions.
-Second, we develop explicit estimates for the regularized Bogovski operator. 
-\nocite{gross2004electromagnetic,hiptmair2002finite}
+\paragraph{Future work}
+The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
+Furthermore, their constants enter the stability and convergence theory of finite element methods.
+Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
+
+The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
+Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
+In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
+It also enters the a~priori error analysis.
+
+Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres.
+In particular, domains with shellable triangulations are contractible.
+However, these estimates are important partial results.
+Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+
+The remainder of this manuscript is structured as follows.
+We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants over triangulated domains in Section~\ref{section:poincare}.
+We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
+We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
+Bogovski\u{i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
+We construct an important geometric reflection operator in Section~\ref{section:extension}
+and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+
+% % TODO:V&V seems to be the only reference for stars ....
+General results of this type for a class containing the finite element stars are not known to us.
+In particular and as will be illustrated in a moment, Poincar\'e constants of stars and thus of star-shaped domains may be arbitrarily large.
+Consequently, corresponding bounds have to incorporate some quantity that perceives the possible lack of convexity.
+% TODO: \cite{vohralik2005discrete}
 
@@
 
-% Estimates for divergence constants (if any)
-
-% Estimates for curl constants (if any)
-
-\paragraph{Future work}
-Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres.
-In particular, domains with shellable triangulations are contractible.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-\color{blue}
-The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
-Furthermore, their constants enter the stability and convergence theory of finite element methods.
-Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
-\color{black}
-\\
-\color{red}
-The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
-Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
-In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
-It also enters the a~priori error analysis. 
-\color{black}
-
-\color{red}Our upper bounds do not depend on the angles of such re-entrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}
-\\
-
-The remainder of this manuscript is structured as follows.
-We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants over triangulated domains in Section~\ref{section:poincare}.
-We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
-We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Bogovski\u{\i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
-We construct an important geometric reflection operator in Section~\ref{section:extension}
-and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-
 \section{Basic notions of triangulations}\label{section:triangulations}

### 2024-06-26 main.tex
spellcheck

@@
 Clearly, not all local patches describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local patchess in triangulations are often star-shaped with respect to a ball. 
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local patches in triangulations are often star-shaped with respect to a ball. 
 Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. 
@@
 Veeser and Verfürth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriotates.
+Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
 % 
@@
 Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights structures commmon to the gradient, curl, and divergence operators.
+The formalism is independent of the dimension and highlights structures common to the gradient, curl, and divergence operators.
 It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
@@
 First, we construct an auxiliary problem subject to full boundary conditions.
-Second, we develop explicit estimates for the regularized Bogovski operator.
+Second, we develop explicit estimates for the regularized Bogovski\u{\i} operator.
 \nocite{gross2004electromagnetic,hiptmair2002finite}
@@
 
-One component of our efforts are estimates for Bogovski\u{i}-type potential operators over convex domains, seen as operators between Lebesgue spaces. 
+One component of our efforts are estimates for Bogovski\u{\i}-type potential operators over convex domains, seen as operators between Lebesgue spaces. 
 This follows closely the discussions in the literature~\cite{costabel2010bogovskiui} but no operator norm estimates are given in the literature, to the best of our best knowledge.
-The Bogovski\u{i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
+The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
 It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
-Our variant of the Bogovski\u{i} potential operator is simplified in comparison earlier discussions:
+Our variant of the Bogovski\u{\i} potential operator is simplified in comparison earlier discussions:
 we only view it over convex domains and use simpler (that is, constant) weight function. 
@@
 
-The Bogovski\u{i} potential operator is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to boundary conditions.
+The Bogovski\u{\i} potential operator is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to boundary conditions.
 For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential.
@@
 
-The regularized Bogovskii potential operator was studied extensively by Costabel and McIntosh.
-These operators are defiend over sets star-shaeped with respect to a ball. 
+The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
+These operators are defined over sets star-shaped with respect to a ball. 
 Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. 
@@
 We simply use a constant averaging over the entire domain. 
-While the resulting Bogovskii-type potential has more moderate regularity properties, 
+While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
 this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms.
@@
 We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Bogovski\u{i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
+Bogovski\u{\i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
 We construct an important geometric reflection operator in Section~\ref{section:extension}

### 2024-06-27 main.tex
Update on Overleaf.

@@
 We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
-The potential operators satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry. 
-In particular, these bounds on the operator norms yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
+The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
+In particular, these operator norm bounds yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
 Equivalently, this gives lower bounds for the eigenvalues of several vector Laplacians.
@@
 For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfH(\curl,\Omega)$ under the curl operator whose $\bfL^2$ norm is bounded in terms of the source field.
-This is expressed via the Poincar\'e--Friedrichs inequality
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2} \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
+we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator whose $\bfL^2$ norm is bounded in terms of the source field. This is expressed via the Poincar\'e--Friedrichs inequality 
+\begin{align*}
+    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
     \leq 
@@
 Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-We accomplish our results for a special class of triangulations, so-called shellable triangulations.
-We address this topic in the special case where $\Omega$ admits special triangulations, 
-namely the class of so-called \emph{shellable} triangulations. 
+% We accomplish our results for a special class of triangulations, so-called shellable triangulations.
+We accomplish this undertaking in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
 Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important step stone towards the more general case. 
+having computable upper bounds for such domains is an important stepping stone towards the more general case. 
 For example, local patches around a simplex within a larger 2D or 3D triangulation are shellable.
 We express all our main results in the calculus of differential forms, also known as exterior calculus, 
-and state the instances of the curl and divergence operator as special cases. 
+and treat the curl and divergence operator as its particular instances. 
 \\
@@
 \end{align*}
-Its operator norm is the constant in the Poincar\'e inequality 
+Its operator norm is the constant $C_{\rm P,p} > 0$ in the Poincar\'e inequality 
 \begin{align*}
@@
     \leq 
-    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
+    C_{\rm P,p} \| \nabla u \|_{L^p(\Omega)},
     \quad 
@@
 Most research on optimal constants has addressed the case of convex domains. 
-Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.
+% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
+Notably, the optimal constants $C_{\grad,p}$ for any $1 \leq p < \infty$ that depends only on the domain diameter is known when the domain is convex.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
 When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already provide the Poincar\'e inequality~\cite{ern2021finite}. 
-An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
-We refer to \cite{hurri1988poincare} for that perspective.
+then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{ern2021finite}. 
+An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain,
+implying Poincar\'e inequalities on star-shaped open sets~\cite{hurri1988poincare}.
 
 The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-Here, we use the function spaces
+We use the vector field spaces
 \begin{align*}
@@
     \leq 
-    C_{\curl}
+    C_{\curl,p}
     \| \bff \|_{\bfL^{p}(\Omega)}
@@
     \leq 
-    C_{\divergence}
+    C_{\divergence,p}
     \| f \|_{L^{p}(\Omega)}
@@
 \end{align*}
-and whether these constants can be estimated by the operator norm of linear potential operators 
+and whether these constants can be estimated by the operator norms of linear potential operators 
 \begin{align*}
@@
 We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue}, who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$.
-The provide lower bounds for the spectrum of the Hodge--Laplace operator over convex domains.
+They provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains.
 This implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
@@
 valid over convex domains in 3D:
-\begin{align*}
-    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
-\end{align*}
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constant 
-follow from bounds on the operator norm of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mapping between Lebesgue spaces,
-though these estimates have not been made explicit in the literature yet.
+\begin{align}\label{math:intro:guerinisavo}
+    C_{\grad,2} \geq C_{\curl,2} \geq C_{\divergence,2}.
+\end{align}
+When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
+follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
+as mappings between Lebesgue spaces, though these estimates have not been made explicit in the literature yet.
 \\
@@
 One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local patches in triangulations are often star-shaped with respect to a ball. 
-Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. 
-However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape-regularity. 
+Over patches around interior subsimplices, the size of the interior ball only depends on the shape regularity of the triangulation. 
+However, that interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape regularity. 
 Estimates that rely on this geometric condition deteriorate when the aforementioned ball has small radius,
-and that is inevitable when the domain has a bad geometry. 
-Some illustrative limit cases include the slit domain and the crossed bricks domain,
+and that is inevitable when the domain has an unfortunate geometry. 
+Some illustrative limit cases include the slit domain and the crossed bricks domain~\cite{licht2019smoothed},
 for which some finite element patches are not star-shaped with respect to any ball.
@@
 % TODO: wait for answer to email 
-Veeser and Verfürth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
+Veeser and Verfürth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
 Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
 % 
-There is a popular avenue towards Poincar\'e--Friedrichs constants, which can circumvent the effect of low boundary regularity, 
-and which has been published in different variations~\cite{vohralik2005discrete,ern2021finite}. 
-A common principle of many proofs is to construct a potential step-by-step: 
-starting with a single triangle, the potential is constructed over an increasing subdomain, until the entire domain is complete.
+The literature knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that can circumvent the effect of low boundary regularity~\cite{vohralik2005discrete,ern2021finite}.
+These potentials share being constructed step-by-step: 
+starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is complete.
 That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest.
@@
 Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed. 
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface. 
 % Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
@@
 we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality over the Sobolev space with Dirichlet boundary conditions implies, via duality, the Poincar\'e--Friedrichs for the divergence operator.
-However, that method seems restricted to the Hilbert space case $p=2$.
-We are not aware of more general estimates for the curl operator, even in the Hilbert space situation. 
-\\
-
-\paragraph{Actual content of the paper}
-The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence satisfying explicitly computable upper bounds.
+In the Hilbert space setting, with $p=2$, the Friedrichs inequality over the Sobolev space with Dirichlet boundary conditions implies, 
+via duality, the Poincar\'e--Friedrichs for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
+We are not aware of any estimates for the curl operator, even in the Hilbert space situation. 
+\\
+
+The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence, satisfying explicitly computable upper bounds.
 We follow closely the philosophy of the aforementioned sequential approach.
-The transition to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
+Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
 
@@
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus.
-Exterior calculus has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,arnold2006finite}.
+Exterior calculus is used ubiquitously in physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite}.
 Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
@@
 It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
-
-We explore formulate our main results in the framework of exterior calculus.
-The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
-%
-It is used ubiquitously in physics and engineering. 
-%
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis.
@@
 
-We fix this problem in two steps.
-First, we construct an auxiliary problem subject to full boundary conditions.
-Second, we develop explicit estimates for the regularized Bogovski\u{\i} operator.
-\nocite{gross2004electromagnetic,hiptmair2002finite}
-\\
-
 % General outline 
-% TODO: outline of the construction; mention why shellable is important; mixed BC
+We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
+The basic inductive strategy remains the same.
+We start by constructing, say, a curl potential, over a single simplex.
+Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
+The two potentials will not have the same tangential trace along the interface between the subtriangulation and the new simplex.
+
+To ensure the correct continuity properties, we require triangulations with stronger structures than in the case of gradient potentials.
+We need to ensure that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Under those conditions, which are met by \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
+Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+\\
+
+% Shellable 
 This construction of potentials requires triangulations with special conditions: 
-we assemble the triangulation sequentially, adding one simplex after the other, such that the interface between new previous intermediate triangulation and the next simplex is always a boundary submanifold of either of them.
+we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
 Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Such triangulations are also known as shellable.
+Such triangulations are called \textit{shellable}.
 Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D are shellable.
-
-As a necessary subcomponent, we need to apply local Poincar\'e inequalities to select potentials. 
+In particular, local stars in 2D and 3D triangulations are shellable. 
+\\
+
+% auxiliary problems 
+% We construct gradient potentials locally over convex domains or face patches. 
+Estimating the norm of local potential operators over convex domains is an important subcomponent of this endeavor. 
 Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients. 
-We construct gradient potentials locally over convex domains or face patches. 
-We can access a considerable body of literature for gradient Poincar\'e inequalities over convex domains~\cite{bebendorf2003note}.
-In fact, optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known over convex domains.
-By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
-\\
-
-% Shellable 
-Formally, a simplicial complex is shellable if its full-dimensional simplices can be ordered in a sequence such that each such simplex in the sequence intersects the union of the previously listed simplices in a codimension one simplicial complex in the boundary of the new facet being added.
-Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-the gluing interface is a triangulated submanifold of the boundary. 
-This forces the intermediate triangulations to be particularly well-shaped.
-
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
-In particular, this enables the inductive method of proof.
-\\
-
-% Mixed BC
-But we need to find potentials over a simplex subject to partial boundary conditions 
-and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
-The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
-
-Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
-has no estimates in the literature.
-
-One component of our efforts are estimates for Bogovski\u{\i}-type potential operators over convex domains, seen as operators between Lebesgue spaces. 
-This follows closely the discussions in the literature~\cite{costabel2010bogovskiui} but no operator norm estimates are given in the literature, to the best of our best knowledge.
-The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
-It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
-Our variant of the Bogovski\u{\i} potential operator is simplified in comparison earlier discussions:
-we only view it over convex domains and use simpler (that is, constant) weight function. 
-The resulting operator has generally lower regularity properties in comparison to the regularized potential in the literature but the regularity is sufficient for our purposes and the operator norms are easily computed.
-We consider this outcome to be of independent interest.
-
-The Bogovski\u{\i} potential operator is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to boundary conditions.
+While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
+the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
+
+In the Hilbert space case, $p=2$, the work of Guerini and Savo shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex Lipschitz domains.
+% TODO: double check
+
+No such results are known for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
+We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
+In comparison to their exposition, our variants of the regularized potential operators are simplified:
+we only study them over convex domains and use simpler (that is, constant) weight functions. 
+The resulting operator has generally lower regularity properties in comparison to the regularized potential in the literature;
+however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
+We consider the latter outcome to be of independent interest.
+
+In addition to that, we need to find potentials over a simplex subject to partial boundary conditions,
+Again, we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
+The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
 For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential.
-We achieve by constructing an auxiliary problem subject to full boundary conditions.
-
-The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
-These operators are defined over sets star-shaped with respect to a ball. 
-Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. 
-We study a variation of this potential operator over convex sets.
-We simply use a constant averaging over the entire domain. 
-While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
-this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms.
-
-\paragraph{Future work}
-The Poincar\'e--Friedrichs inequalities are crucial in the stability analysis of partial differential equations of vector analysis.
+We achieve this by constructing an auxiliary problem subject to full boundary conditions.
+\\
+
+% Future work 
+Computable reliable estimates for the Poincar\'e--Friedrichs constant are important: 
+they quantify the fundamental stability properties of partial differential equations in vector analysis,
+such as the Hodge Laplace equation. 
+Upper bounds correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
 Furthermore, their constants enter the stability and convergence theory of finite element methods. 
-Computable and reliable estimates are a cornerstone in rigorous a~priori and a~posteriori error analysis.
-
-The Poincar\'e--Friedrichs constant describes the fundamental stability properties of the partial differential equation. 
-Conversely, it also implies a the lower bound for the non-zero eigenvalues of the scalar and vector Laplacian.
-In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enable bound for the spectrum of stiffness matrices. 
-It also enters the a~priori error analysis.
-
-Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres.
+In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
+and they lead to lower bounds for the spectrum of finite element matrices.
+
+Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
 In particular, domains with shellable triangulations are contractible.
@@
 Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+
+We have also identified that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularlized potential operators.
+It is of interest whether the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
+These topics remain for future research.
+\\
 
@@
 We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Bogovski\u{\i}-type integral operators over convex sets are discussed in Section~\ref{section:bogovskii}.
+Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
 We construct an important geometric reflection operator in Section~\ref{section:extension}
@@
 Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}.
+
+\begin{remark}
+It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. In particular, this enables the inductive method of proof.
+Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation.
+Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
+by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
+the gluing interface is a triangulated submanifold of the boundary. 
+This forces the intermediate triangulations to be particularly well-shaped. 
+\end{remark}
 
@@
 
-\section{Bogovski\u{\i}-type operators over convex sets}\label{section:bogovskii}
+\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
 
@@
 
+\begin{remark}
+It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
+The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
+The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
+These operators are defined over sets star-shaped with respect to a ball. 
+Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis.
+However, no operator norm estimates are given in the literature, to the best of our best knowledge.
+We study a variation of this potential operator over convex sets.
+We simply use a constant averaging over the entire domain. 
+While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
+this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms. 
+\end{remark}
+
 We begin with introducing the Costabel-McIntosh kernel.
@@
 \begin{align}
+  \Poinc_{\ell} u(x) &= \int G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy
+  \\
   \Bogov_{\ell} u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
@@
 In order to understand the properties of the operator $\Bogov_{\ell}$,
-including the convergence of the integral, we first rewrite the Costabel-McIntosh kernel $G_{\ell}$:
+including the convergence of the integral, we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
+Letting $x,y \in \bbR^n$ with at least one $x$ or $y$ contained in $\Omega$, we deduce 
 \begin{align*}
@@
 
-For full technical clarify, we show we have a bounded operator 
+For full technical clarity, we show we have a bounded operator 
 \[

### 2024-06-28 main.tex
some clean up

--- 2024-06-26 main.tex
@@
 In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
+$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
 \[
@@
 \]
-The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
+The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
 and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
@@
 \end{subequations}
-for $v \in W^{p}(\grad,\Omega)$, $\bfv \in W^{p}(\curl,\Omega)$, and $\bfw \in W^{p}(\divergence,\Omega)$.  
+for $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
 We summarize this as a commuting diagram:
@@
     \begin{CD}
-        W^{1,p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
+        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
         \\
@@
         \\
-        W^{1,p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
+        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
     \end{CD}
@@
 \begin{remark}
-    Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega'$.
-    This is in accordance with the notion of pullback, that we will review shortly. 
+    The Piola transform goes int the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
+    This definition is in accordance with the notion of pullback, which we will review shortly. 
     One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
+    The literature also knows the Piola transform in the direction of the original mapping. 
 \end{remark}
-
-%
 
@@
 
-We also assume the perspective of exterior calculus. 
-We give a brief introduction into this topic. 
+Having discussed vector analysis, we review exterior calculus. 
+We give a brief introduction into this topic, and refer to the literature for further background~\cite{...}. 
 Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, We let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
+Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
 Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
@@
     \frac{1}{k! l!} 
-    \sum_{ \sigma \in S_{k+l}} 
-    \signum(\sigma) 
-    u_1( v_{\sigma(  1)}, \ldots, v_{\sigma(k  )} ) 
-    u_2( v_{\sigma(k+1)}, \ldots, v_{\sigma(k+l)} ),
+    % \sum_{ \pi \in S_{k+l}} 
+    \sum_{ \pi } 
+    \signum(\pi) 
+    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
+    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
 \]
 for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\sigma) \) is the sign of the permutation \( \sigma \).
+Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
+% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
 The exterior product is bilinear and associative, and satisfies 
@@
 \begin{align*}
-    \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
+    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
 \end{align*}
@@
 which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( d \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( d\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
+The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
+to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
 Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
@@
 where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( d\omega \) is defined by
+The exterior derivative \( \cartan\omega \) is defined by
 \[
-    d\omega = 
+    \cartan\omega = 
     \sum_{ \sigma \in \Sigma(k,n) } 
@@
 The exterior derivative is linear and nilpotent, which means 
-\( d(d\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
+\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
 Moreover, it satisfies the Leibniz rule:
 \[ 
-    d(\omega \wedge \eta) 
-    = 
-    d\omega \wedge \eta + (-1)^{k} \omega \wedge d\eta, 
+    \cartan(\omega \wedge \eta) 
+    = 
+    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
     \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
@@
 \]
-Let u now turn our attention to Sobolev spaces of differential forms. 
+Let us now turn our attention to Sobolev spaces of differential forms. 
 Since $\Alt^{k}(\Omega)$ is a normed space, we can consider the pointwise norms of differential $k$-forms. 
@@
 
+% TODO: transformationssatz
+
 \begin{remark}
@@
     \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) @>{d}>> C^\infty\Alt^3(\Omega) 
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
         \\
@@
     We summarize the situation in the following commuting diagram: 
-    \[
+    \[ % TODO: what is the convention for the curl and rotation ? look up in the textbooks?
     \begin{CD}
@@
         \\
-        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) 
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
         \\
@@
 \end{remark}
+
+% TODO: spaces with boundary conditions: grad, curl, divergence, exterior derivative; approximation properties
 
@@
 \begin{align*}
-    T_{\ell,a} u(x) 
+    \Bogov_{\ell,a} u(x) 
     &= 
@@
 \begin{align*}
-    \cartan T_{\ell,a} u(x) 
+    \cartan \Bogov_{\ell,a} u(x) 
     &= 
-    k
+    \ell 
     \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
@@
 \begin{align*}
-    T_{\ell+1,a} \cartan u(x)
+    \Bogov_{\ell+1,a} \cartan u(x)
     &=
@@
     &
-    \cartan T_{\ell,a} u(x)
+    \cartan \Bogov_{\ell,a} u(x)
     +
-    T_{\ell+1,a} \cartan u(x)
+    \Bogov_{\ell+1,a} \cartan u(x)
     \\&
@@
 \end{align*}
-In particular, if $\cartan u = 0$, then $\cartan T_{\ell,a} u = u$.
+In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell,a} u = u$.
 

### 2024-06-28 draft.tex
Update on Overleaf.

@@
+\documentclass[a4paper]{article}
+\usepackage[utf8]{inputenc}
+\usepackage{fullpage}
+\usepackage{hyperref}         % For hypertext links
+
+\input{header}
+
+\begin{document}
+
+Given $a \in \Omega$, we introduce the potential operator 
+\begin{align*}
+    \Poinc_{\ell,a} u(x) 
+    &:= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
+    .
+\end{align*}
+By definition,
+\begin{align*}
+    \Poinc_{\ell} u(x) 
+    =
+    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;
+    .
+\end{align*}
+We study the interaction of the potential operator with the exterior derivative in more detail.
+Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$ with $\supp u \subseteq \overline\Omega$.
+We rewrite the potential,
+\begin{align*}
+    \Poinc_{\ell,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Poinc_{\ell,a} u(x) 
+    &= 
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
+    ,
+\end{align*}
+and apply the potential operator to this result, which gives 
+\begin{align*}
+    \Poinc_{\ell+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    \;\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \;\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Poinc_{\ell,a} u(x)
+    +
+    \Poinc_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
+    \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    u_{\sigma}(x) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell,a} u = u$.
+
 % Develop construction of complexes via adding patches 
@@
  \end{align*}
+ \color{black}
 
@@
     .
-\end{align}
+\end{align*}
 
@@
 \begin{align*}
-    \Bogov_{\ell} u(x) 
+    \Poinc_{\ell} u(x) 
     &= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} 
     \chi_{\Omega}\left(y+t(y-x)\right) 
@@
     \\&= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} 
     \chi_{\Omega}\left(y+(x-y)-(x-y)+t(y-x)\right) 
@@
     \\&= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} 
     \chi_{\Omega}\left(x+(t+1)(y-x)\right) 
@@
     &= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
+    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1} (t+1)^{n}
     \chi_{\Omega}\left(a\right) 
@@
 \begin{align*}
-    \Bogov_{\ell} u(x) 
+    \Poinc_{\ell} u(x) 
     &= 
-    \int \int_{1}^\infty (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
+    \int \int_{0}^{1} (t-1)^{n-\ell} \left( 1/s-1 \right)^{\ell-1} (t+1)^{n}
     \chi_{\Omega}\left(a\right) 
@@
     &= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
+    \int \int_{0}^{1} (t-1)^{n-\ell}t^{-n+\ell-1} 
     \chi_{\Omega}\left(a\right)
@@
     &= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
+    \int \int_{0}^{1} (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
     .
@@
 \begin{align*}
-    \Bogov_{\ell} u(x) 
+    \Poinc_{\ell} u(x) 
     &= 
-    \int \int_{1}^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
+    \int \int_{0}^{1} s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
     \\
     &= 
-    - \int \int_{1}^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
+    - \int \int_{0}^{1} s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
     \\
     &=
-    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
     .
@@
 \begin{align*}
-    \Bogov_{\ell} u(x) 
-    = 
-    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \Poinc_{\ell} u(x) 
+    = 
+    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
     .
@@
 $s = \frac{t}{t-1}$
-From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $\Bogov_{\ell} u(x)$ is smooth with support contained in $\overline\Omega$ as well.
-
-From this form of $\Bogov_{\ell}$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $\Bogov_{\ell}$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
-But if $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$, one sees that $\Bogov_{\ell} u$ is ${C^\infty}$ on 
+From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $\Poinc_{\ell} u(x)$ is smooth with support contained in $\overline\Omega$ as well.
+
+From this form of $\Poinc_{\ell}$, because of the unbounded interval of integration in $t$, one cannot immediately conclude that $\Poinc_{\ell}$ maps ${C^\infty}$ functions to ${C^\infty}$ functions.
+But if $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$, one sees that $\Poinc_{\ell} u$ is ${C^\infty}$ on 
 $\bbR^n\setminus\supp\chi_{\Omega}$, and that 
-$\Bogov_{\ell} u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
+$\Poinc_{\ell} u(x)=0$ unless $x$ lies in the starlike hull of $\supp u$ with respect to $B$. 
 Thus if $\Omega$ is open and starlike with respect to $B$, then   
-$u\in{C^\infty_c}(\Omega,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\Omega$, and, if $\Omega$ is bounded, then
-$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp \Bogov_{\ell} u \subset\overline\Omega$. 
-The fact that $\Bogov_{\ell}$ indeed maps 
+$u\in{C^\infty_c}(\Omega,\Alt^\ell)$ implies $\supp \Poinc_{\ell} u \subset\Omega$, and, if $\Omega$ is bounded, then
+$u\in{C^\infty}_{\overline\Omega}(\bbR^n,\Alt^\ell)$ implies $\supp \Poinc_{\ell} u \subset\overline\Omega$. 
+The fact that $\Poinc_{\ell}$ indeed maps 
 ${C^\infty_c}(\bbR^n,\Alt^\ell)$ to ${C^\infty_c}(\bbR^n,\Alt^{\ell-1})$ will be a consequence of Theorem~\ref{T:pseudo} below.
@@
 \end{equation}
-One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $\Bogov_{\ell}$ directly.
-The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutativity relations for $\Bogov_{\ell}$ from the relations \eqref{eq:dR+Rd=1} which are already proved.
+One could be tempted to integrate Cartan's formula from $1$ to $\infty$ and compare with \eqref{eq:Bogo}, thus formally obtaining a similar homotopy relation for $\Poinc_{\ell}$ directly.
+The result is indeed true except for $\ell=n$, but for a rigorous proof we prefer to use the duality relation \eqref{eq:dualRT} to deduce corresponding anticommutativity relations for $\Poinc_{\ell}$ from the relations \eqref{eq:dR+Rd=1} which are already proved.
 Here is what one obtains for $u\in{C^\infty_c}(\bbR^n,\Alt^\ell)$:
@@
 \label{eq:dT+Td=1}
-  d\Bogov_{\ell} u + T_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
+  d\Poinc_{\ell} u + \Poinc_{\ell+1} du &= u\; &&(1\le\ell\le n-1)\;;\\
   T_1 du &= u \; &&(\ell=0)\;;\\
@@
 
-If we correspondingly extend the definitions of $R_{\ell}$ and $\Bogov_{\ell}$ by
+If we correspondingly extend the definitions of $R_{\ell}$ and $\Poinc_{\ell}$ by
 $$
@@
  \quad \text{ and }\quad
- \underline d\,\Bogov_{\ell} u + T_{\ell+1} \,\underline du = u\quad \text{ for all }\;
+ \underline d\,\Poinc_{\ell} u + \Poinc_{\ell+1} \,\underline du = u\quad \text{ for all }\;
   0\le\ell\le n.
@@
 \end{align*}
+
+\begin{align}
+        v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
+        \\
+        \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
+        \\
+        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
+        \\
+        v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
+        \\
+        x = v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
+    \end{align}
+    \begin{align}
+        v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+        +
+        \sum_{i=1}^{k} \lambda_{i} v_i 
+        +
+        \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+        -
+        \sum_{i=k+1}^{n-1} \lambda_{i} v_i
+    \end{align}
+    \begin{align}
+        v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
+        +
+        \sum_{i=1}^{k} \lambda_{i} v_i 
+        +
+        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i
+        +
+        \sum_{i=k+1}^{n-1} \lambda_{i} v_n
+    \end{align}
+
+\end{document}

### 2024-06-28 draft.tex
additional work on potentials

@@
 
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$. There exists a bounded mapping 
+    \begin{align*}
+     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+    \end{align*}
+    such that 
+    \begin{align*}
+        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
+    \end{align*}
+    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
+\end{lemma}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$. There exists a bounded mapping 
+    \begin{align*}
+     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+    \end{align*}
+    such that 
+    \begin{align*}
+        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
+    \end{align*}
+    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
+\end{lemma}
+
+There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}(\Omega,\Alt^{\ell})$
+and which satisfies $\cartan u_{i} = 0$. Let $w \in L^{p}(\Omega,\Alt^{\ell-1})$ be the limit of $\Poinc_{\ell} u_{i}$.
+We know that $\Poinc_{\ell} u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell-1})$. 
+Given any $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
+\begin{align*}
+    \int_{\Omega} w \wedge \cartan v
+    &=
+    \lim_{i} \int_{\Omega} \Poinc_{\ell} u_{i} \wedge \cartan v
+    \\&=
+    \lim_{i} \int_{\Omega} \cartan \Poinc_{\ell} u_{i} \wedge v
+    \\&=
+    \lim_{i} \int_{\Omega} u_{i} \wedge v
+    =
+    \int_{\Omega} u \wedge v
+    .
+\end{align*}
+That means $w \in W^{p}(\Omega,\Alt^{\ell-1})$ with $\cartan w = u$.
+
 \section*{Theorem 8.1}
@@
 
+    Bogovskii was the first establish the 
+    on whose work the following presentation is based. 
+    In contrast to the aforementioned reference, the goal of our discussion is more modest:
+    we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
+    However, we derive explicit bounds for the operator norms, which are of independent interest.
+
+    It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
+    The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
+    The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
+    These operators are defined over sets star-shaped with respect to a ball.
+
+    The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+    on whose work the following presentation is based. 
+    In contrast to the aforementioned reference, the goal of our discussion is more modest:
+    we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
+    However, we derive explicit bounds for the operator norms, which are of independent interest.
+
+    Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis.
+However, no operator norm estimates are given in the literature, to the best of our best knowledge.
+    We study a variation of this potential operator over convex sets.
+    We simply use a constant averaging over the entire domain. 
+    While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
+    this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms. 
 \end{document}

### 2024-06-28 main.tex
additional work on potentials

@@
     The main application that we envision are computable estimates over finite element patches. 
+    %
+    As a result with independent standing, we establishes Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
+    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators. 
 \end{abstract}
@@
 % TODO: wait for answer to email 
-Veeser and Verfürth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
+Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
 Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
@@
 We have also identified that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularlized potential operators.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
 It is of interest whether the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
@@
 \begin{remark}
-    The Piola transform goes int the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
     scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
@@
 
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable. 
+    Then $u_\epsilon \rightarrow u$ almost everywhere. 
+    If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$. 
+\end{lemma}
+
+\begin{lemma} % TODO: possibly useful
+    Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
+\end{lemma}
+
+\begin{lemma}
+    Smooth forms are dense in $\bfW^{p}\Lambda^{k}$.
+\end{lemma}
+
 \section{Regularized potential operators over convex sets}\label{section:potentialoperator}
 
-We use potential operators for the exterior derivative over convex domains that respect boundary conditions. 
-These are known as Bogovski\u{\i}-type operators.
-They were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics.~\cite{bogovskii1979solution} 
-The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-on whose work the following presentation is based. 
-In contrast to the aforementioned reference, the goal of our discussion is more modest:
-we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
-However, we derive explicit bounds for the operator norms, which are of independent interest.
-
-\begin{remark}
-It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
-The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
-The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
-These operators are defined over sets star-shaped with respect to a ball. 
-Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis.
-However, no operator norm estimates are given in the literature, to the best of our best knowledge.
-We study a variation of this potential operator over convex sets.
-We simply use a constant averaging over the entire domain. 
-While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
-this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms. 
-\end{remark}
+We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
+We already know the optimal constants for the gradient operator over convex domains,
+and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
+We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
+
+For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
+We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
+and the $L^{p}$ de~Rham with full boundary conditions. 
+The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
+% 
+In comparison to their work, our discussion is more modest:
+we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+However, our explicit purpose are explicit bounds for the operator norms, which are of independent interest. 
+\\
 
@@
 \end{align}
-We call $\Bogov_{\ell}$ a Bogovski\u{\i}-type operator.
-
-We show that the integrals in the definition of $\Bogov_{\ell}$ actually exist. 
-In order to understand the properties of the operator $\Bogov_{\ell}$,
-including the convergence of the integral, we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
-Letting $x,y \in \bbR^n$ with at least one $x$ or $y$ contained in $\Omega$, we deduce 
+We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
+\\
+
+We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
+In order to analyze the properties of the potential operators,
+we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
+Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
 \begin{align*}
@@
 \end{align*}
-We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
 \begin{align*}
@@
 \end{align*}
-We can now analyze the potential operator $\Bogov_{\ell}$. 
+We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
+
+We begin with the Poincar\'e operator. 
+Suppose that $u \in C^{\infty}(\Omega,\Alt^{\ell})$ with $1 \leq \ell \leq n$.
+We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| \Poinc_{\ell} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+%     \\&\leq 
+%     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
+    .
+\end{align*}
+We recall the radial integrals 
+\begin{align*}
+    \int_{B_D(0)} |z|^{k+1-n} dz
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k} dr
+    =
+    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
+    .
+\end{align*}
+We compute 
+\begin{align*}
+    &
+    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
+    \\&
+    =
+    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
+    .
+\end{align*}
+Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
+and which is bounded by $2^{n-\ell}$. 
+In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
+    &\leq 
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
+    D
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    D
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u \in C^{\infty}(\Omega,\Alt^{\ell})$. 
+Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\[
+    \Poinc_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+\]
+Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$.
+
+We analyze the Bogovski\u{\i} potential operator with similar means. 
 Suppose that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$ and that $x \in \bbR^{n}$.
-First, if $x \notin \overline\Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t \geq 1$.
-Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
-More generally, we pointwise estimate $\Bogov_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
+First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
+Consider now the case $x \in \overline\Omega$. 
+We estimate $\Bogov_{\ell} u(x)$ pointwise by 
 \begin{align*}
@@
 \end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_D(0)} |z|^{k+1-n} dz
-    =
-    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
-    =
-    \vol_{n-1}(S_1) \int_0^D r^{k} dr
-    =
-    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-    .
-\end{align*}
-We compute 
+Using once more the radial integrals discussed above, we compute 
+% We recall the radial integrals 
+% \begin{align*}
+%     \int_{B_D(0)} |z|^{k+1-n} dz
+%     =
+%     \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
+%     =
+%     \vol_{n-1}(S_1) \int_0^D r^{k} dr
+%     =
+%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
+%     .
+% \end{align*}
+% We compute 
 \begin{align*}
@@
     =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
-    .
-\end{align*}
-Here, $A(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
+    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
+    .
+\end{align*}
+Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
 and which is bounded by $2^{\ell-1}$. 
@@
 So the convolution of $u$ is taken against an integrable function. 
-Taylor's convolution inequality now implies: 
+Young's convolution inequality now implies: 
 \begin{align*}
@@
     \leq 
-    n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
     D
@@
 We have assumed so far that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$. 
-Since that space is dense in the Lebesgue spaces, a density argument provides gives the following: 
+Since that space is dense in the Lebesgue spaces, a density argument yields: 
 for any $1 \leq p \leq \infty$ we have a bounded linear operator 
@@
 \]
+Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
 Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
 that is, the reconstructed potential has support contained within $\overline\Omega$. 
+\\
 
 Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions:
-first, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+We write down the full definition of these operators and perform two substitutions.
+For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
+leading to 
+\begin{align*}
+    \Poinc_{\ell} u(x) 
+    &= 
+    \int \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
+    \chi_{\Omega}\left(x+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    .
+\end{align*}
+For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
 leading to 
@@
 % 
-Given $a \in \Omega$, we introduce the potential operator 
-\begin{align*}
+Given $a \in \Omega$, we introduce the potential operators 
+\begin{align*}
+    \Poinc_{\ell,a} u(x) 
+    &:= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
+    ,
+    \\
     \Bogov_{\ell,a} u(x) 
@@
 \begin{align*}
+    \Poinc_{\ell} u(x) 
+    =
+    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;,
+    \quad 
     \Bogov_{\ell} u(x) 
@@
 \end{align*}
-We study the interaction of the potential operator with the exterior derivative in more detail.
+We study the interaction of these potential operator with the exterior derivative in more detail.
+
+The following discussion is classical and establishes the exactness of several de~Rham complexes. 
+We recapitulate these arguments since our variants of the regularized potential operators 
+are not yet included in the published literature.
+
+Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$.
+We rewrite the Poincar\'e potential,
+\begin{align*}
+    \Poinc_{\ell,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Poinc_{\ell,a} u(x) 
+    &= 
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
+    ,
+\end{align*}
+and apply the Poincar\'e potential operator to this result, which gives 
+\begin{align*}
+    \Poinc_{\ell+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    \;\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \;\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Poinc_{\ell,a} u(x)
+    +
+    \Poinc_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
+    \cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
+    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
+    \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    u_{\sigma}(x) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell,a} u = u$.
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be convex.
+    If $1 \leq p < \infty$ and $u \in C^{\infty}\Lambda^{k}(\Omega)$ with $\cartan u = 0$,
+    then there exists $u_{n} \in C^{\infty}\Lambda^{k}(\Omega)$ with $\cartan u_{n} = 0$ that converges to $u$ in $L^{p}$.
+\end{lemma}
+\begin{proof}
+    % TODO
+\end{proof}
+
+The discussion for the Bogovski\u{\i} operator is almost analogous. 
 Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the potential,
+We rewrite the Bogovski\u{\i} potential,
 \begin{align*}
@@
 \end{align*}
-and apply the potential operator to this result, which gives 
+and apply the Bogovski\u{\i} potential operator to this result, which gives 
 \begin{align*}
@@
 
-For full technical clarity, we show we have a bounded operator 
-\[
+The main results of this section are summarized as follows.
+These results also imply the Poincar\'--Friedrichs inequalities that we have been looking for. 
+These constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the dimension and the form degree enters the estimate.
+
+\begin{theorem}
+    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
+    We have bounded operators 
+    \begin{align*}
+        \Poinc_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+        ,
+        \qquad 
         \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
         .
-\]
-% - Rewrite kernel
-% - Show the support property
-% - Assess that it is Lp bounded for compactly supported forms; density argument
-% - Conclude that it is absolutely convergent. Do one (!) derivative
-% - Poincare lemma for smooth forms : needs smoothness, but that's a simple calculation 
-% - prove duality via some density argument and the extension of smooth forms outside of Lipschitz domains
+    \end{align*}
+    They satisfy the operator norm bounds 
+    \begin{align*}
+        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+        D
+        \| u \|_{L^{p}(\Omega)}
+        ,
+        \\
+        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+        D
+        \| u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    If $u \in \bfW^{p}    (\Omega,\Alt^{\ell})$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
+    If $u \in \bfW^{p}_{0}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$ with $u = \cartan \Bogov_{\ell} u$.
+\end{theorem}
+\begin{proof}
+    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}(\Omega,\Alt^{\ell})$.
+
+    Consider now $u \in W^{p}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$. 
+    We write $w := \Poinc_{\ell  } u$. 
+    There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}(\Omega,\Alt^{\ell})$. 
+    For any test form $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
+        +
+        (-1)^{k(n-k-1)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{k(n-k-1)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}(\Omega,\Alt^{\ell-1})$ with $\cartan w = u$.
+
+    Analogously, suppose that $u \in W^{p}_{0}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$. 
+    We write $w := \Bogov_{\ell} u$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}(\Omega,\Alt^{\ell})$. 
+    For any test form $v \in C^{\infty}(\Omega,\Alt^{n-\ell-1})$, 
+    which is the restriction of some member of $C^{\infty}(\bbR^{n},\Alt^{n-\ell-1})$, 
+    it holds that 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
+        +
+        (-1)^{k(n-k-1)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{k(n-k-1)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}_{0}(\Omega,\Alt^{\ell-1})$ with $\cartan w = u$.
+    % TODO: definition of weak derivative + definition of boundary condition 
+    % 
+    This completes the proof. 
+\end{proof}
+
+% TODO: Density of C infty mit oder ohne c. 
+% TODO: Density im kernel 
+% TODO: lrcorner
+
+\begin{remark}
+    The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
+    while they are increasing for the Bogovski\u{\i} operator.
+    This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over convex domains~\cite{guerini2004eigenvalue}.
+\end{remark}
+
+\begin{remark}
+    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+    To the best of our knowledge, the work of Costabel and McIntosh was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    These potentials enable the analysis of de~Rham complexes without boundary conditions.
+    % 
+    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+    Their generalization to differential forms was first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
+    % 
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they study domains star-shaped with respect to a ball. 
+    Instead, we average over the entire domain, which requires a convex geometry. 
+    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
+    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
+\end{remark}
+
+\section{Extension operator on finite element stars}\label{section:extension}
+% Only define the geometric mapping and its important quantities
+% Leave the function spaces etc. for later
+
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
+
+\subsection{Inequalities for partial boundary conditions on a single simplex}
 
 \begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$. There exists a bounded mapping 
-    \begin{align*}
-     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
-    \end{align*}
-    such that 
-    \begin{align*}
-        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
-    \end{align*}
-    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
+    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    Then 
+    \begin{align*}
+        \| u \| \leq 
+    \end{align*}
 \end{lemma}
+\begin{proof}
+    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+    such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
+    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
+    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
+    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
+    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
+
+    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
+    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
+
+    The operator norm bound of the potential operator shows 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        \\&
+        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        .
+    \end{align*}
+    We use the pullback estimates 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        \| \Jacobian\varphi \|_{\infty}^{k}
+        |\det\varphi^{-\frac{1}{p}}|
+        \cdot 
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        .
+    \end{align*}
+    \begin{align*}
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        2^{n-l}
+        \| \hat f \|_{L^{p}(\hat T)} 
+        \leq 
+        2^{n-l}
+        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
+        |\det\varphi^{\frac{1}{p}}|
+        \cdot 
+        \| f \|_{L^{p}(T)} 
+        .
+    \end{align*}
+\end{proof}
+
+\subsection{Constructions over shellable triangulations}
 
@@
 \end{proof}
-
-\section{Extension operator on finite element stars}\label{section:extension}
-% Only define the geometric mapping and its important quantities
-% Leave the function spaces etc. for later
-
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-\subsection{Inequalities for partial boundary conditions on a single simplex}
-
-\begin{lemma}
-    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
-    Then 
-    \begin{align*}
-        \| u \| \leq 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-    such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
-    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
-    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
-
-    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
-    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
-
-    The operator norm bound of the potential operator shows 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        \\&
-        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        .
-    \end{align*}
-    We use the pullback estimates 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        \| \Jacobian\varphi \|_{\infty}^{k}
-        |\det\varphi^{-\frac{1}{p}}|
-        \cdot 
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        .
-    \end{align*}
-    \begin{align*}
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        2^{n-l}
-        \| \hat f \|_{L^{p}(\hat T)} 
-        \leq 
-        2^{n-l}
-        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
-        |\det\varphi^{\frac{1}{p}}|
-        \cdot 
-        \| f \|_{L^{p}(T)} 
-        .
-    \end{align*}
-\end{proof}
-
-\subsection{Constructions over shellable triangulations}
 

### 2024-06-28 main.tex
rewriting

@@
 \]
+We observe that $u \in L^p\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^p\Alt^{k+1}(\Omega)$
+if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
+\begin{align*}
+    \int_{\Omega} \cartan v \wedge u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{\Omega} v \wedge f 
+    .
+\end{align*}
 We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
@@
 We begin with the Poincar\'e operator. 
-Suppose that $u \in C^{\infty}(\Omega,\Alt^{\ell})$ with $1 \leq \ell \leq n$.
+Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
 We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
@@
 \end{align*}
-We have assumed so far that $u \in C^{\infty}(\Omega,\Alt^{\ell})$. 
+We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
 Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
@@
 \[
-    \Poinc_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
 \]
-Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$.
-
+% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
+% 
 We analyze the Bogovski\u{\i} potential operator with similar means. 
-Suppose that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$ and that $x \in \bbR^{n}$.
+Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
 First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
@@
 \end{align*}
-We have assumed so far that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$. 
+We have assumed so far that $u$ is essentially bounded.
 Since that space is dense in the Lebesgue spaces, a density argument yields: 
@@
 \[
-    \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
 \]
-Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
+% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
 Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
@@
 We study the interaction of these potential operator with the exterior derivative in more detail.
-
-The following discussion is classical and establishes the exactness of several de~Rham complexes. 
+% 
+That discussion is classical and establishes the exactness of several de~Rham complexes. 
 We recapitulate these arguments since our variants of the regularized potential operators 
@@
 
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be convex.
-    If $1 \leq p < \infty$ and $u \in C^{\infty}\Lambda^{k}(\Omega)$ with $\cartan u = 0$,
-    then there exists $u_{n} \in C^{\infty}\Lambda^{k}(\Omega)$ with $\cartan u_{n} = 0$ that converges to $u$ in $L^{p}$.
-\end{lemma}
-\begin{proof}
-    % TODO
-\end{proof}
+% TODO: averaging
 
@@
 In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell,a} u = u$.
-
-The main results of this section are summarized as follows.
-These results also imply the Poincar\'--Friedrichs inequalities that we have been looking for. 
-These constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+\\
+
+% TODO: averaging
+
+We are in the position to establish the main results of this section.
+This includes upper bounds for the Poincar\'--Friedrichs inequalities that we have been looking for. 
+Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
 though the dimension and the form degree enters the estimate.
@@
     \begin{align*}
-        \Poinc_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
         ,
         \qquad 
-        \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
         .
@@
     \end{align*}
-    If $u \in \bfW^{p}    (\Omega,\Alt^{\ell})$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
-    If $u \in \bfW^{p}_{0}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$ with $u = \cartan \Bogov_{\ell} u$.
+    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
+    If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
 \end{theorem}
 \begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}(\Omega,\Alt^{\ell})$.
-
-    Consider now $u \in W^{p}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$. 
+    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.
+
+    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
     We write $w := \Poinc_{\ell  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}(\Omega,\Alt^{\ell})$. 
+    There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
     For any test form $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
@@
         +
-        (-1)^{k(n-k-1)+1}
+        (-1)^{k(n-k)+1}
         \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
@@
         &=
-        (-1)^{k(n-k-1)+1}
+        (-1)^{k(n-k)+1}
         \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
@@
     \end{align*}
-    By definition, $w \in W^{p}(\Omega,\Alt^{\ell-1})$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$. 
+    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
+
+    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
     We write $w := \Bogov_{\ell} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}(\Omega,\Alt^{\ell})$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
     For any test form $v \in C^{\infty}(\Omega,\Alt^{n-\ell-1})$, 
@@
         +
-        (-1)^{k(n-k-1)+1}
+        (-1)^{k(n-k)+1}
         \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
@@
         &=
-        (-1)^{k(n-k-1)+1}
+        (-1)^{k(n-k)+1}
         \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
@@
     \end{align*}
-    By definition, $w \in W^{p}_{0}(\Omega,\Alt^{\ell-1})$ with $\cartan w = u$.
+    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
     % TODO: definition of weak derivative + definition of boundary condition 

### 2024-06-28 draft.tex
rename variables; Gradient section

@@
 \begin{document}
+
+\begin{lemma}\label{lemma:mixedbconsimplex}
+    Let $T$ be an $n$-simplex and with a face $F$. 
+    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
+    \begin{align*}
+        \| u \|_{L^{p}(T)}
+        &
+        \leq 
+        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
+    \end{align*}
+    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},T,F,p}
+        \leq 
+        \left( C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p} \right),  
+        \quad 
+        C_{{\rm PF},T,F,p}
+        \leq 
+        \diam(T)
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
+    \[
+        \| w \|_{L^{p}(T)}
+        \leq 
+        C_{{\rm PF},T,p} 
+        \| \nabla w \|_{\bfL^{p}(T)}
+        .
+    \]
+    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
+    We use that 
+    \[
+        \| \gamma \|_{L^{p}(T)}
+        =
+        \gamma \vol(T)^\frac{1}{p}
+        =
+        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
+        \cdot 
+        \gamma 
+        \vol(F)^\frac{1}{p}
+        \leq 
+        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
+        \| \gamma \|_{L^{p}(F)}
+        .
+    \]
+    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
+    \begin{align*}
+        \| \gamma \|_{L^{p}(F)}^{p}
+        &
+        \leq 
+        \frac{ \vol(F) }{ \vol(T) }
+        \| w \|_{L^{p}(T)}^{p}
+        +
+        p
+        \cdot 
+        \diam(T)
+        \frac{ \vol(F) }{ \vol(T) }
+        \| w \|_{L^{p}(T)}^{p-1}
+        \| \nabla w \|_{L^{p}(T)}
+        \\&
+        \leq 
+        \left( \frac{ \vol(F) }{ \vol(T) } \right)
+        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
+        \diam(T)^{p}
+        \| \nabla w \|_{L^{p}(T)}^{p}
+        \\&
+        \leq 
+        \left( \frac{ \vol(F) }{ \vol(T) } \right)
+        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
+        %\diam(T)^{p}
+        \| \nabla w \|_{L^{p}(T)}^{p}
+        .
+    \end{align*}
+    Recall that $u = w - \gamma$. The first inequality follows.
+
+    The second inequality follows from Rademachers theorem when $p = \infty$.
+    Let assume that $1 \leq p < \infty$. 
+    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
+    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and the $n$-th coordinate is non-negative over $T$. 
+    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $u$ outside of $T$.
+    With the fundamental theorem of calculus and H\"olders inequality: 
+    \begin{align*}
+        &
+        \int_{\Omega} |u(x_{1},\dots,x_{n-1},x_{n})|^{p} dx_1 \dots dx_{n-1} dx_{n}
+        \\&
+        \leq
+        \int_{\Omega} \left| \int_{0}^{x_n} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{n}
+        \\&
+        \leq
+        \int_{\Omega} \int_{0}^{x_n} x_{n}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+        \\&
+        \leq
+        \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+        \leq 
+        D^{p} 
+        \int_{\Omega} |\nabla u|^{p} dx
+        .
+    \end{align*}
+    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
+
+    Very briefly verify that density argument: 
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \varphi )$. 
+    Then $\nabla \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    We define $\tilde g = \nabla \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$,
+    and we approximate $\tilde u$ in $W^{1,p}(\hat U)$ via a sequence in $C^{\infty}_{c}(\hat U)$.
+
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \varphi )$. 
+    Then $\nabla \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    We define $\tilde g = \nabla \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\hat U)} 
+        \leq 
+        2 
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        .
+    \end{gather*}
+    In addition to that, 
+    \begin{gather*}
+        \| u \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Dif \varphi)|^{\frac 1 p} 
+        \| \hat u \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Dif \varphi)|^{\frac 1 p} 
+        \| \tilde u \|_{L^{p}(\hat U)}
+        ,
+        \\
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{\bfL^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Dif \varphi_1)|^{-\frac 1 p} \| \Dif \varphi \| \cdot 
+        \| \nabla u \|_{\bfL^{p}(T)}
+        .
+    \end{gather*}
+    The second inequality follows.
+\end{proof}
 

### 2024-06-28 main.tex
rename variables; Gradient section

@@
 
-\title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
+\title{Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over domains with shellable triangulations}
 \author{
@@
 Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
+The majority of estimates in the literature address only gradient potentials. 
 % We accomplish our results for a special class of triangulations, so-called shellable triangulations.
@@
 
-\section{Constructive estimate of Poincar\'e constants}\label{section:poincare}
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincare}
 
@@
 
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
+Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
 Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
@@
 \end{align}
-Equivalently, for all $u \in W^{1,p}(\Omega)$ we have 
+Under the condition that $\Omega$ is connected, this is equivalent to  
 \begin{align}
@@
     C_{{\rm PF},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
+    \| \nabla u \|_{L^{p}(\Omega)},
+    \quad 
+    u \in W^{1,p}(\Omega)
     .
@@
 We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+\\
 
@@
 Towards a converse inequality, 
-let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
-    \| v_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
-    \leq 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
-    = 
-    \| v \|_{L^{p}(\Omega)}^{p}
+let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align*}
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \right)^{p}
+    \leq 
+    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \right)
+    = 
+    \| u \|_{L^{p}(\Omega)}^{p}
     .
@@
 Here, we have used Jensen's inequality. 
-In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
 It follows that 
 \begin{align*}
-    \| v - v_\Omega \|_{L^{p}(\Omega)} 
+    \| u - u_\Omega \|_{L^{p}(\Omega)} 
     \leq
     2
-    \| v \|_{L^{p}(\Omega)},
+    \| u \|_{L^{p}(\Omega)},
     \quad 
-    v \in L^{p}(\Omega)
+    u \in L^{p}(\Omega)
     .
@@
 % \end{align*}
-Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.
-
-In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
+Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}.
+\end{align*}
+In the special case $p=2$, this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$,
 and therefore even $C_{\varnothing,\Omega,2} = C_{{\rm PF},\Omega,2}$. 
-This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
+This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
 and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-%\footnote{\color{red}Is there a better name for this than Xu-Zikatanov estimate?}
-Stern~\cite{stern2015banach} provided a generalization of the projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
+Stern~\cite{stern2015banach} provides a generalized projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
 since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
 \begin{align*}
-    \| v - v_\Omega \|_{L^{p}(\Omega)}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}
     \leq 
     \min\left( 2, 2^{|2/p-1|} \right)
-    \| v \|_{L^{p}(\Omega)}
+    \| u \|_{L^{p}(\Omega)}
     = 
     2^{|2/p-1|} 
-    \| v \|_{L^{p}(\Omega)}
+    \| u \|_{L^{p}(\Omega)}
     ,
     \quad 
-    v \in L^p(\Omega)
+    u \in L^p(\Omega)
     .
@@
 We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
-The main consequence for us is the estimate 
-$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
-We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
+We thus conclude 
+\begin{align*}
+    C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}.
+\end{align*}
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
+\\
 
@@
 \begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \nabla v = \bff } } \| v \|_{L^{p}(\Omega)},
+    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
     \quad 
@@
     \leq 
-    \argmin\limits_{ v \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla v) \|_{L^p(\Omega)} }{ \| \nabla v \|_{L^p(\Omega)} }
+    \argmin\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
     .
@@
 Its operator norm is just the smallest Poincar\'e constant $C_{\varnothing,\Omega,p}$.
-
-In the light of these musings, we clarify that our objective is the construction of linear potential operators for the gradient and later for the curl and divergence operators,
-which is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
+\\
+
+In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient and later for the curl and divergence operators.
+This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
@@
 \begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality suits our discussion better than the Poincar\'e inequality. 
+    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
     We want to generalize the discussion to the curl and divergence operators. 
@@
 
-\subsection{Poincar\'e inequalities over convex domains}
+\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
 % See the collection at Lemma 3.24 : https://hal.science/hal-03226049/file/volI_hal.pdf
 
-We now collect examples for Poincar\'e--Friedrichs inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
+see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
 Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
@@
 \end{align}
-These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
+These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
 Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite{chua2006estimates}:
@@
 \end{align}
-The literature knows optimal Poincar\'e--Friedrichs constants over convex domains. 
-According to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
+These Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
+
+We know optimal Poincar\'e--Friedrichs constants over convex domains~\cite{ferone2012remark,esposito2013poincare}: 
+when $1 < p < \infty$, one can show that 
 \begin{align}\label{math:esposito:pf}
@@
 \end{align}
-Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+% TODO: double check what is known in the literature 
+Note that the last inequalities imply, again when $1 \leq p < \infty$, the Poincar\'e inequalities
 \begin{align}\label{math:esposito:poincare}
@@
 \end{align}
-The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
 Finally, since convex domains are Lipschitz domains: 
@@
 \begin{remark}
+    The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
     Let us compare the different estimates for the Poincar\'e inequality.
@@
     Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
-    Notably, it is much less clear whether \eqref{math:esposito:pf} implies a limit case for Lipschitz functions. 
+    Notably, it is much less clear whether \eqref{math:esposito:pf} implies a limit case Poincar\'e--Friedrichs inequality for Lipschitz functions. 
 %     Taking the \emph{informal} limit also suggest the inequality 
@@
 
+\begin{remark}
+    The optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    but individual convex domains may allow for better constants.
+    We refer to \cite{matculevich2016explicit} for an overview. 
+    For example, triangles allow the reduction of the constant by 20\%.
+\end{remark}
+
 % https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
@@
 
-\subsection{Poincar\'e inequalities over triangulated domains}
+\subsection{Poincar\'e--Friedrichs inequalities over triangulated domains}
 
@@
     Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
-    We fix affine homeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
+    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
     which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
@@
     we fix a strong path $T_0, T_1, \dots, T_m = T$.
+    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
     Then for any $u \in W^{1,p}(\Omega)$ 
@@
     \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}^{p}
+        % \color{red}
+        \| w \|_{L^{p}(T_m)}
         &\leq 
-        (m+1)^{p-1}
+        \left( 1 + \rho(\calT)^{\frac q p} \right)^{\frac 1 q}
         \sum_{t=1}^{m}
-        \left( 
-            \prod_{t < l \leq m} 
-            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
-        \right)
-        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
-        C_{p,T_{t} \cup T_{t+1}}
-        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
+        \rho(\calT)^{\frac{m-t}{p}}
+        C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
+        % 2 C_{\rm{EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
+        \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
         \\&\quad \quad \quad 
         +
-        (m+1)^{p-1}
-        \left( 
-            \prod_{0 < l \leq m} 
-            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
-        \right)
-        C_{p,T_{0}}
-        \| \nabla u \|_{L^{p}(T_{0})}^{p}
+        \rho(\calT)^{\frac{m-1}{p}}
+        % C_{\rm{EFNT},p} \diam(T_0)
+        C_{{\rm{PF}},T_{0},p}
+        \| \nabla u \|_{L^{p}(T_{0})}
         .
@@
  For each $F \in \calT$ of dimension $n-1$, 
- we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F,p} \| \nabla u_F \|_{L^{p}(U_F)}$.
+ we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla u_F \|_{L^{p}(U_F)}$.
 
@@
  \[
-    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{P}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
  \]
- In particular, $c_{\star} := u - w_0$ is a constant function. 
+ In particular, $c_{0} := u - w_0$ is a constant function. 
  Now, let $T \in \calT$ be any $n$-simplex. 
  By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
- For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{j(m)}$ be a face of dimension $n-1$. 
+ For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
  We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
@@
  Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
- such that $c_{\star} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
+ such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
  Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. 
@@
  $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
- But that already implies $w'_{F_m} = u_{|F_m} - c_{\star}$. 
+ But that already implies $w'_{F_m} = u_{|F_m} - c_{0}$. 
  We define a measurable function $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$.
- We have $c_{\star} = w_{m} - u_{|\Omega_{m}}$.
+ We have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
 
@@
  \end{align*}
- When $1 < p < \infty$, letting $q$ be the complementary exponent, we observe 
+ % 1/q = 1 - 1/p = (p-1)/p 
+ When $1 < p < \infty$, letting $q := p/(p-1) \in [1,\infty]$ be the complementary exponent, we observe 
  \begin{align*}
@@
  Recursive application provides the following estimate:
- if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
- such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
- then 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(S_m)}
+%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
+%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
+%  then 
+ \begin{align*}
+    \| w_{m} \|_{L^{p}(T_m)}
     &\leq 
@@
         \prod_{t < l \leq m} 
-        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
     \right)
-    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{\frac 1 q}
+    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
     \| u_{F_t} \|_{L^{p}(U_{F_t})}
@@
         \prod_{0 < l \leq m} 
-        \frac{ \vol(S_l)^{\frac 1 p} }{ \vol(S_{l-1})^{\frac 1 p} } 
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
     \right)
-    \| u_{S_0}\|_{L^{p}(S_{0})}
-    .
- \end{align*}
- It follows that
- \begin{align*}
-    \| w_{m} \|_{L^{p}(S_m)}^{p}
-    &\leq 
-    (m+1)^{p-1}
-    \sum_{t=1}^{m} 
-    \left( 
-        \prod_{t < l \leq m} 
-        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
-    \right)
-    \left( 1 + \frac{ \vol(S_t)^{\frac q p} }{ \vol(S_{t-1})^{\frac q p} } \right)^{p/q}
-    \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
-    \\&\quad \quad \quad 
-    +
-    (m+1)^{p-1}
-    \left( 
-        \prod_{0 < l \leq m} 
-        \frac{ \vol(S_l) }{ \vol(S_{l-1}) } 
-    \right)
-    \| u_{S_0}\|_{L^{p}(S_{0})}^{p}
-    .
- \end{align*}
- Notice that $p/q = p - 1$.
-
+    \| u_{T_0}\|_{L^{p}(T_{0})}
+    .
+ \end{align*}
+ We use Definition~\eqref{math:moremeasures} to prove the desired inequality.
+%  \begin{align*}
+%     \| w_{m} \|_{L^{p}(T_m)}^{p}
+%     &\leq 
+%     (m+1)^{p-1}
+%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
+%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
+%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
+%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
+%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
+%     \\&\quad \quad \quad 
+%     +
+%     (m+1)^{p-1}
+%     \rho(\calT)^{m-1}
+%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
+%     .
+%  \end{align*}
+%  Notice that $p/q = p - 1$.
+ % 
  Repeating this argument produces $w \in L^{p}(\Omega)$ 
- such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{\star}$.
+ such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
  In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
@@
         \leq 
-        C_{{\rm PF},T,F,p} \diam(T) \| \nabla u \|_{L^{p}(T)}
-    \end{align*}
-    where $C_{\partial,p} > 0$ is a constant such that 
+        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
+    \end{align*}
+    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
     \begin{align*}
@@
         \leq 
-        \left( C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p} \right),  
+        \left( C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p} \right),  
         \quad 
@@
         \leq 
-        2^{\frac n p}
+        \diam(T)
         .
@@
         \leq 
+        \left( \frac{ \vol(F) }{ \vol(T) } \right)
         \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
         \diam(T)^{p}
+        \| \nabla w \|_{L^{p}(T)}^{p}
+        \\&
+        \leq 
         \left( \frac{ \vol(F) }{ \vol(T) } \right)
+        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
+        %\diam(T)^{p}
         \| \nabla w \|_{L^{p}(T)}^{p}
@@
 
+    The second inequality follows from Rademachers theorem when $p = \infty$.
+    Let assume that $1 \leq p < \infty$. 
+    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
+    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and the $n$-th coordinate is non-negative over $T$. 
+    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $u$ outside of $T$.
+    With the fundamental theorem of calculus and H\"olders inequality: 
+    \begin{align*}
+        &
+        \int_{\Omega} |u(x_{1},\dots,x_{n-1},x_{n})|^{p} dx_1 \dots dx_{n-1} dx_{n}
+        \\&
+        \leq
+        \int_{\Omega} \left| \int_{0}^{x_n} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{n}
+        \\&
+        \leq
+        \int_{\Omega} \int_{0}^{x_n} x_{n}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+        \\&
+        \leq
+        \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+        \leq 
+        D^{p} 
+        \int_{\Omega} |\nabla u|^{p} dx
+        .
+    \end{align*}
+    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
+
+    Very briefly verify that density argument: 
     There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \varphi )$. 
-    Then $\nabla \hat u = \hat g$. 
-    % 
+    We let $\hat u := u \circ \varphi$.
     Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
     We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    We define $\tilde g = \nabla \tilde u$
-    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
-    \begin{gather*}
-        \| \tilde u \|_{L^{p}(\hat U)} 
-        \leq 
-        2 
-        \| \tilde g \|_{\bfL^{p}(\hat U)}
-        .
-    \end{gather*}
-    In addition to that, 
-    \begin{gather*}
-        \| u \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Dif \varphi)|^{\frac 1 p} 
-        \| \hat u \|_{L^{p}(\hat T)}
-        \leq 
-        |\det(\Dif \varphi)|^{\frac 1 p} 
-        \| \tilde u \|_{L^{p}(\hat U)}
-        ,
-        \\
-        \| \tilde g \|_{\bfL^{p}(\hat U)}
-        \leq 
-        2^{\frac n p}
-        \| \hat g \|_{\bfL^{p}(\hat T)}
-        \leq 
-        2^{\frac n p}
-        |\det(\Dif \varphi_1)|^{-\frac 1 p} \| \Dif \varphi \| \cdot 
-        \| \nabla u \|_{\bfL^{p}(T)}
-        .
-    \end{gather*}
-    The second inequality follows.
+    Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
+    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ is the desired sequence that approximates $u$. 
 \end{proof}
@@
     we fix a strong path $T_0, T_1, \dots, T_m = T$.
+    For any $1 \leq l \leq m$, let $F_{l} = T_{l} \cap T_{l-1}$.
     Then for any $u \in W^{1,p}(\Omega)$ 
@@
         \| w_{m} \|_{L^{p}(T_m)}
+%         &\leq 
+%         \rho(\calT)^{\frac m p}
+%         C_{{\rm PF},T_{0},p} 
+%         \| \nabla u \|_{L^{p}( T_{0} )}
+%         +
+%         \sum_{l=1}^{m} 
+%         \rho(\calT)^{\frac {m-l} p}
+%         C_{{\rm PF},T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l})} 
+%         \\&\qquad 
+%         +
+%         \sum_{l=1}^{m} 
+%         \rho(\calT)^{\frac {m-l} p} \xi(\calT)
+%         C_{{\rm PF},T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l-1})} 
+%         \\
         &\leq 
+        \rho(\calT)^{\frac m p}
+        C_{{\rm PF},T_{0},p} 
+        \| \nabla u \|_{L^{p}( T_{0} )}
+        \\&\qquad 
+        +
         \sum_{l=1}^{m} 
-        \rho(\calT)^{\frac{m-l}{p}}
-        C_{{\rm PF},T,p} \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) \diam(T_{0})
-        \| \nabla u \|_{L^{p}( T_{l} )}
-        +
-        \rho(\calT)^{\frac m p}
-        C_{{\rm PF},T_{0},p} \diam(T_{0})
-        \| \nabla u \|_{L^{p}( T_{0} )}
-        .
-    \end{align*}
-    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
+        \rho(\calT)^{\frac {m-l} p}
+        C_{{\rm PF},T_{l},F_{l},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{l})} 
+            +
+            \rho(\calT)^{\frac {1} p}
+            \xi(\calT)
+            \| \nabla u \|_{L^{p}(T_{l-1})} 
+        \right)
+        .
+    \end{align*}
+%     \begin{align*}
+%         \| w_{m} \|_{L^{p}(T_m)}
+%         &\leq 
+%         \sum_{l=1}^{m} 
+%         \rho(\calT)^{\frac{m-l}{p}}
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{{\rm PF},T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}( T_{l} )}
+%         +
+%         \rho(\calT)^{\frac m p}
+%         C_{{\rm PF},T_{0},p} 
+%         \| \nabla u \|_{L^{p}( T_{0} )}
+%         .
+%     \end{align*}
+%     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
 \end{theorem}
@@
     Let $u \in W^{1,p}(\Omega)$. 
-    Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.
-
-    First, there exists $w_0 \in W^{1,p}(T_{0})$ such that $\nabla w_{0} = \nabla u$ over $\Omega_0$. 
-    Suppose that $0 \leq m < M$ such that there exists $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_m$. 
-    Hence $w_{m} - u_{|\Omega_{m}}$ is a constant.
-
-    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
-    Let $\hat T$ be the reference simplex.
-    % We fix affine homeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
+    First, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+    \[
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+    \]
+    In particular, $c_{0} := u - w_0$ is a constant function.
+
+    Now, let $T \in \calT$ be any $n$-simplex. 
+    By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
+    For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
+    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+
+    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $c_{0} = u - w_{m-1}$.
+    In particular, $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
+    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{m-1}$. 
+    % Let $\hat T$ be the reference simplex.
+    % We fix affine diffeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
     % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
     %
-    We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
-    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. 
+    We define $w'_{m} := w_{m-1} \circ \Xi \in W^{1,p}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
     %
-    By construction, $w'_{m+1} \in W^{1,p}(T_{m+1})$ with 
-    \begin{align*}
-        \trace_F w_{m} = \trace_F w'_{m+1}
-        .
-    \end{align*}
-    Suppose that $w''_{m+1} = u - w'_{m+1} \in W^{1,p}(T_{m+1})$.
-    It satisfies 
-    \begin{align*}
-        \nabla w''_{m+1} = \nabla u - \nabla w'_{m+1}, 
+    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
+    \begin{align*}
+        \trace_F w_{m-1} = \trace_F w'_{m}
+        .
+    \end{align*}
+    Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
+    \begin{align*}
+        \nabla w''_{m} = \nabla u - \nabla w'_{m}, 
         \quad 
-        \trace_{F_{m}} w''_{m+1} = 0.
+        \trace_{F_{m}} w''_{m} = 0.
     \end{align*}
@@
     \begin{align*}
-        \trace_{F_{m}}( \nabla u - \nabla w'_{m+1} ) 
+        \trace_{F_{m}}( \nabla u - \nabla w'_{m} ) 
         &= 
-        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m+1}
+        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m}
         \\&= 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m+1}
-        = 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m}
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m}
+        = 
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m-1}
         = 
@@
     \end{align*}
-    Setting $w_{m+1} := w_{m}$ over $\Omega_{m}$ and $w_{m+1} := w'_{m+1} + w''_{m+1}$ over $T_{m+1}$, 
+    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
     we find 
     \begin{gather*}
-        \nabla w_{m+1} = \nabla w'_{m+1} + \nabla w''_{m+1} = \nabla w'_{m+1} + \nabla u - \nabla w'_{m+1} = \nabla u,
+        \nabla w_{m} = \nabla w'_{m} + \nabla w''_{m} = \nabla w'_{m} + \nabla u - \nabla w'_{m} = \nabla u,
         % \end{gather*}
@@
         % \begin{gather*}
-        \trace_{F_{m}} w_{m+1} = \trace_{F_{m}} w'_{m+1} = \trace_{F_{m}} w_{m}.
+        \trace_{F_{m}} w_{m} = \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{m-1}.
     \end{gather*}
-    That means that $w_{m+1} \in W^{1,p}(\Omega_{m+1})$ with $\nabla w_{m+1} = \nabla u$ over $\Omega_{m+1}$. 
+    That means that $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_{m}$. 
+    In particular, $c_{0} = u - w_{m}$. 
     Lemma~\ref{lemma:mixedbconsimplex} gives 
     \begin{align*}
-        \| w''_{m+1} \|_{L^{p}(T_{m+1})} 
+        \| w''_{m} \|_{L^{p}(T_{m})} 
         &
         \leq 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u - \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}.
-        \\&
-        \leq 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
-        + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
+        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
+        \\&
+        \leq 
+        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
         .
@@
     \begin{align*}
-        \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}
+        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
         &\leq 
@@
         \cdot 
-        \| \nabla w_{m} \|_{L^{p}(T_{m})}
+        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
         \leq 
@@
         \cdot 
-        \| \nabla w_{m} \|_{L^{p}(T_{m})}
+        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
         .
@@
         &
-        \| w_{m+1} \|_{L^{p}(T_{m+1})}
-        \\&
-        \leq  
-        \| w'_{m+1} \|_{L^{p}(T_{m+1})}
-        + 
-        \| w''_{m+1} \|_{L^{p}(T_{m+1})}
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
         \\&
@@
         \rho(\calT)^{\frac 1 p} 
-        \| w_{m} \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
+        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},F_{m},p} 
         \left( 
-            \| \nabla u \|_{L^{p}(T_{m+1})} 
-            + 
-            \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
+            \| \nabla u \|_{L^{p}(T_{m})} 
+            + 
+            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
         \right) 
@@
         \rho(\calT)^{\frac 1 p} 
-        \| w_{m} \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T,F,p} 
-        \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-        \diam(T_{m+1}) 
-        \| \nabla u \|_{L^{p}(T_{m+1})} 
-        .
-    \end{align*}
-    The recursive estimate follows. 
+        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},F_{m},p} 
+        \| \nabla u \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},F_{m},p} 
+        \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},F_{m},p} 
+        \| \nabla u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},F_{m},p} 
+        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},F_{m},p} 
+        \| \nabla u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},F_{m},p} 
+        \| \nabla u \|_{L^{p}(T_{m-1})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         + 
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla u \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    The existence of $w \in W^{1,p}(\Omega)$ satisfying the recursive estimate follows. 
 \end{proof}
@@
 \begin{remark}
-    The previous theorems, Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} and Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} 
+    The previous theorems, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} 
     depend on only a few parameters of the triangulation:
     the length of any traversal from the root simplex, the ratios of the volumes of adjacent simplices,
-    the Poincar\'e constants on each face patch, and the Poincar\'e constant of the initial simplex. 
-    The aforementioned local Poincar\'e constants can generally be estimated in terms of shape-parameters. 
+    the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex. 
+    The aforementioned local Poincar\'e--Friedrichs constants can generally be estimated in terms of shape-parameters. 
     If the face patches of the triangulation are convex, then better estimates are possible. 
@@
 \end{align*}
+We let $W^p_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^p\Alt^{k}(\Omega)$ 
+for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^p\Alt^{k}(\bbR^{n})$. 
+The space $W^p_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.
+
+Lastly, we are also interested in differential forms whose trace vanishes along only a part of the boundary. 
+Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
+We say that $u \in W^p\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
+such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+\begin{align*}
+    \int_{B_r(x)} \cartan v \wedge \tilde u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
+    .
+\end{align*}
+
 We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
@@
 
+Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
+Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
+
 \begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable. 
-    Then $u_\epsilon \rightarrow u$ almost everywhere. 
-    If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$. 
+%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
+%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
+%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    If $u \in L^{p}(\Omega)$, then $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
 \end{lemma}
 
-\begin{lemma} % TODO: possibly useful
-    Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
+% \begin{lemma} % TODO: possibly useful
+%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
+% \end{lemma}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    Smooth forms are dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
+    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}_{0}\Lambda^{k}(\Omega)$.
 \end{lemma}
-
-\begin{lemma}
-    Smooth forms are dense in $\bfW^{p}\Lambda^{k}$.
-\end{lemma}
+\begin{proof}
+    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
+    By the dominated convergence theorem and because $u$ has a weak derivative,
+    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
+    \begin{align*}
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v
+        &= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x)
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x)
+        \\&= 
+        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x)
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x)
+        = 
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v
+        .
+    \end{align*}
+    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
+
+    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
+    Let $u \in \bfW^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
+    Define $\varphi_t(x) = tx$ for $t > 1$. 
+    Then $\varphi_{t}^{\ast} u \in \bfW^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
+    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
+    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
+    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
+    The desired result follows. 
+\end{proof}
 
@@
     &= 
-    \int_0^\infty \tau^{n-\ell} (\tau+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+\tau(x-y) \right)\,d\tau
+    \int_0^\infty t^{n-\ell} (t+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
@@
     \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
-    \int_0^\infty \tau^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+\tau(x-y) \right)\,d\tau 
+    \int_0^\infty t^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
     \\
@@
 \end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives
 \begin{align*}
     G_{\ell}(x,y) 
-    &\leq 
+    &= 
     |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr 
@@
 \[
-    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
 \]
@@
 \[
-    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
 \]
@@
 % We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ satisfies $\supp u \subseteq \overline\Omega$.
+% Suppose that $u \in C^{\infty}\Alt^{\ell-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
 % Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
@@
 
-Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$.
+Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$.
 We rewrite the Poincar\'e potential,
@@
 \end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell,a} u = u$.
-
-% TODO: averaging
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x)
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell} u = u$.
 
 The discussion for the Bogovski\u{\i} operator is almost analogous. 
-Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$ with $\supp u \subseteq \overline\Omega$.
+Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
 We rewrite the Bogovski\u{\i} potential,
@@
 \end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell,a} u = u$.
-\\
-
-% TODO: averaging
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Bogov_{\ell} u(x) + \Bogov_{\ell+1} \cartan u(x)
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell} u = u$.
+\\
 
@@
     \end{align*}
-    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
+    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
     If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
@@
     We write $w := \Poinc_{\ell  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\ell-1}(\Omega)$, we verify 
     \begin{align*}
@@
     We write $w := \Bogov_{\ell} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}(\Omega,\Alt^{n-\ell-1})$, 
-    which is the restriction of some member of $C^{\infty}(\bbR^{n},\Alt^{n-\ell-1})$, 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
+    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
     it holds that 

### 2024-06-30 draft.tex
numerous updates

@@
 \begin{document}
+
+\begin{remark}
+    For reference, how the extension should work:
+    suppose that $u \in H(\Omega)$ and let $f = du$.
+    Suppose we have $u_1 \in H(T_1)$ with $du_1 = du$ over $T_1$. 
+    We built $u'_2 \in H(T_2)$ such that 
+    \begin{align*}
+        \trace_F u_1 = \trace_F u'_2
+    \end{align*}
+    We let $u''_2 \in H(T_2)$ such that 
+    \begin{align*}
+        d u''_2 = f - d u'_2, \quad \trace_F u''_2 = 0
+    \end{align*}
+    Such $u''_2$ exists because 
+    \begin{align*}
+        \trace_F( f_2 - d u'_2 ) 
+        &= 
+        \trace_F f_1 - \trace_F d u'_2
+        \\&= 
+        \trace_F f_1 - \trace_F d u'_2
+        \\&= 
+        \trace_F d u_1 - \trace_F d u'_2
+        \\&= 
+        d \trace_F u_1 - d \trace_F u'_2
+        \\&= 
+        d \trace_F u_1 - d \trace_F u_1
+        = 0
+        .
+    \end{align*}
+    Setting $u_2 = u'_2 + u''_2$, we find 
+    \begin{align*}
+        d u_2 = d u'_2 + d u''_2 = d u'_2 + f - d u'_2 = f,
+        \\
+        \trace_F u_2 = \trace_F u'_2 = \trace_F u_1.
+    \end{align*}
+    That requires an extension from given partial boundary data. 
+    Possible approaches:
+    \begin{itemize}
+        \item Reflect a neighborhood and multiply with cut-off function.
+        \item Take traces from patch and extend onto new simplex. 
+    \end{itemize}
+\end{remark}
 

### 2024-06-30 main.tex
numerous updates

@@
-\documentclass[a4paper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
@@
 
-\title{Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over domains with shellable triangulations}
+\title{Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations}
 \author{
@@
 We review some of the main outcomes. 
-% TODO: wait for answer to email 
 Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
@@
 % Exterior calculus 
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus.
-Exterior calculus is used ubiquitously in physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite}.
+Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
+Exterior calculus is used ubiquitously in physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,}.
 Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
@@
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis.
-\\
+\\ % hu2019structure
 
@@
 These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex Lipschitz domains.
-% TODO: double check
 
@@
 and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-
-% % TODO:V&V seems to be the only reference for stars ....
-General results of this type for a class containing the finite element stars are not known to us.
-In particular and as will be illustrated in a moment, Poincar\'e constants of stars and thus of star-shaped domains may be arbitrarily large.
-Consequently, corresponding bounds have to incorporate some quantity that perceives the possible lack of convexity.
-% TODO: \cite{vohralik2005discrete}
-
-% Estimates for Poincare constants 
-% \cite{bebendorf2003note}
-% \cite{vohralik2005discrete}
-% Verfurth, Veeser & Verfurth 
-% ...
 
@@
 Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
-In practice, we not always distinguish between points and singleton simplices. % TODO: see whether being formally correct is possible 
+In practice, we not always distinguish between points and singleton simplices. 
 Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.
@@
 \end{align}
-% TODO: double check what is known in the literature 
 Note that the last inequalities imply, again when $1 \leq p < \infty$, the Poincar\'e inequalities
@@
 when homogeneous boundary conditions are imposed on a single face of the boundary. 
+We present this result with two different techniques. 
+While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains. 
 % Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.
@@
         \leq 
-        \left( C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p} \right),  
+        C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
         \quad 
@@
         \leq
+        \frac{1}{\sqrt[p]{p}}
         \diam(T)
@@
 
-    The second inequality follows from Rademachers theorem when $p = \infty$.
+    The second inequality follows from Rademacher's theorem when $p = \infty$.
     Let assume that $1 \leq p < \infty$. 
     Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
-    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and the $n$-th coordinate is non-negative over $T$. 
-    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $u$ outside of $T$.
-    With the fundamental theorem of calculus and H\"olders inequality: 
-    \begin{align*}
-        &
-        \int_{\Omega} |u(x_{1},\dots,x_{n-1},x_{n})|^{p} dx_1 \dots dx_{n-1} dx_{n}
-        \\&
-        \leq
-        \int_{\Omega} \left| \int_{0}^{x_n} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{n}
-        \\&
-        \leq
-        \int_{\Omega} \int_{0}^{x_n} x_{n}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
-        \\&
-        \leq
-        \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
-        \leq 
-        D^{p} 
-        \int_{\Omega} |\nabla u|^{p} dx
-        .
+    Without loss of generality, 
+    the segment from to the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
+    and the minimal first coordinate among all the points of $F$ equals $0$. 
+    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $\nabla u$ outside of $T$.
+    %With the fundamental theorem of calculus and H\"olders inequality: 
+    \begin{align*}
+        \int_{\Omega} |u(x)|^{p} dx
+        &\leq
+        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} dx_{1} d\overline{x}
+        \\&
+        \leq
+        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| dy \right|^{p} dx_{1} d\overline{x}
+        \\&
+        \leq
+        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} dx_{1}
+        \\&
+        \leq
+        \int_{0}^{D} x_{1}^{p-1} dx_1 \cdot \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} 
+        \leq
+        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} dx
+        %
+%         \leq
+%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} dx_1 \dots dx_{n-1} dx_{1}
+%         \\&
+%         \leq
+%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{1}
+%         \\&
+%         \leq
+%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+%         \\&
+%         \leq
+%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+%         \leq 
+%         D^{p} 
+%         \int_{\Omega} |\nabla u|^{p} dx
+%         .
     \end{align*}
@@
 \end{proof}
-
-% TODO: https://arxiv.org/html/1607.08163v3
-% https://mathoverflow.net/questions/403415/properties-a-triangulation-must-have-in-order-to-describe-a-manifold
 
@@
 
-% TODO: we only need some basic properties, namely that the construction maintains manifolds with boundary.
-% TODO: copy and adapt the content of Ziegler and Kozlov as necessary
-% The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}
-
 \begin{lemma}    
@@
 
-% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars
-
 \begin{lemma}
@@
 \section{Review of vector calculus and exterior calculus}\label{section:calculus}
+
+We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
+Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
 
@@
 %
-% TODO: bounds
+% TODO: bounds on the Jacobian transform 
 %
@@
     u_2 \in \Alt^{l}(V).
+\end{align*}
+We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined as 
+\begin{align*}
+    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
+    \quad 
+    v_1, v_2, \ldots, v_{k-1} \in V.
 \end{align*}
@@
 Let us now turn our attention to Sobolev spaces of differential forms. 
-Since $\Alt^{k}(\Omega)$ is a normed space, we can consider the pointwise norms of differential $k$-forms. 
+Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a canonical norm, we can consider the pointwise norms of differential $k$-forms. 
 % First, we notice that the % TODO: introduce a norm 
@@
 \begin{align}
-  \Poinc_{\ell} u(x) &= \int G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy
-  \\
-  \Bogov_{\ell} u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy
+  \\
+  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
 \end{align}
@@
     &= 
-    \int_0^\infty t^{n-\ell} (t+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
-    \int_0^\infty t^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    |\Omega|^{-1}\sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \,
-    |x-y|^{k-n} \int_0^\infty r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \\
+    &= 
+    |\Omega|^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
     .
@@
     &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr 
+    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
     \\
@@
     =
-    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
-    =
-    \vol_{n-1}(S_1) \int_0^D r^{k} dr
+    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
+    =
+    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
     =
@@
 %     =
-%     \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
+%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
 %     =
-%     \vol_{n-1}(S_1) \int_0^D r^{k} dr
+%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
 %     =
@@
     &= 
-    \int \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
     \chi_{\Omega}\left(x+t(y-x)\right) 
@@
     &=
-    \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
     .
@@
     &= 
-    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
     \chi_{\Omega}\left(y+t(x-y)\right) 
@@
     &=
-    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
     .
@@
 
-% TODO: Density of C infty mit oder ohne c. 
-% TODO: Density im kernel 
-% TODO: lrcorner
+% DONE: Density of C infty mit oder ohne c.
 
@@
 
+\begin{proposition}\label{proposition:guerinisavo}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
+    Moreover, 
+    \begin{align*}
+        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
+    \end{align*}
+\end{proposition}
+\begin{proof}
+    The result is true if $\Omega$ has a smooth boundary. 
+    Now suppose that $\Omega$ is a Lipschitz domain. 
+\end{proof}
+
 \subsection{Inequalities for partial boundary conditions on a single simplex}
@@
     which has the same smallest singular value. 
+\end{proof}
+
+\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
+    Let $T$ be an $n$-simplex and with a face $F$. 
+    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
+    \begin{align*}
+        \| u \|_{L^{p}(T)}
+        &
+        \leq 
+        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
+    \end{align*}
+    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},T,F,k,p}
+        \leq 
+        \diam(T)
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    Then $\cartan \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    We define $\tilde g = \cartan \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\hat U)} 
+        \leq 
+        C_{???} 
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        .
+    \end{gather*}
+    In addition to that, 
+    \begin{gather*}
+        \| u \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Dif \varphi)|^{\frac 1 p} 
+        \| \hat u \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Dif \varphi)|^{\frac 1 p} 
+        \| \tilde u \|_{L^{p}(\hat U)}
+        ,
+        \\
+        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{\bfL^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Dif \varphi_1)|^{-\frac 1 p} \| \Dif \varphi \| \cdot 
+        \| \cartan u \|_{\bfL^{p}(T)}
+        .
+    \end{gather*}
+    The second inequality follows.
+\end{proof}
+
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
+    and such that for all $T \in \calT$:
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}
+    \end{align*}
+\end{theorem}
+
+\begin{proof}
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
+    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+
+    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    \[
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \]
+    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
+    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
+    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
+    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
+
+    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
+    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
+    \begin{align*}
+        \trace_F w_{m-1} = \trace_F w'_{m}
+        .
+    \end{align*}
+    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
+    \begin{align*}
+        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
+        \quad 
+        \trace_{\Gamma_{m}} w''_{m} = 0.
+    \end{align*}
+    Indeed, such $w''_{m}$ exists because 
+    \begin{align*}
+        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
+        &= 
+        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
+        \\&= 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
+        = 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
+        = 
+        0
+        .
+    \end{align*}
+    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
+    we find 
+    \begin{gather*}
+        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
+        \\
+        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
+    \end{gather*}
+    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
+
+    We want to estimate norms. 
+    Lemma~\ref{lemma:} gives 
+    \begin{align*}
+        \| w''_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
+        \\&
+        \leq 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    We also employ Lemma~\ref{lemma:volumecomparison} to find 
+    \begin{align*}
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Dif \Xi  )|^{-\frac 1 p} 
+        \| \Dif \Xi   \|
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        \leq 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        .
+    \end{align*}
+    Putting this all together, 
+    \begin{align*}
+        &
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \left( 
+            \| \cartan u \|_{L^{p}(T_{m})} 
+            + 
+            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        \right) 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(U_{m-1})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+%         + 
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
+%         \| \cartan u \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
 \end{proof}
@@
 
-\begin{remark}
-    For reference, how the extension should work:
-    suppose that $u \in H(\Omega)$ and let $f = du$.
-    Suppose we have $u_1 \in H(T_1)$ with $du_1 = du$ over $T_1$. 
-    We built $u'_2 \in H(T_2)$ such that 
-    \begin{align*}
-        \trace_F u_1 = \trace_F u'_2
-    \end{align*}
-    We let $u''_2 \in H(T_2)$ such that 
-    \begin{align*}
-        d u''_2 = f - d u'_2, \quad \trace_F u''_2 = 0
-    \end{align*}
-    Such $u''_2$ exists because 
-    \begin{align*}
-        \trace_F( f_2 - d u'_2 ) 
-        &= 
-        \trace_F f_1 - \trace_F d u'_2
-        \\&= 
-        \trace_F f_1 - \trace_F d u'_2
-        \\&= 
-        \trace_F d u_1 - \trace_F d u'_2
-        \\&= 
-        d \trace_F u_1 - d \trace_F u'_2
-        \\&= 
-        d \trace_F u_1 - d \trace_F u_1
-        = 0
-        .
-    \end{align*}
-    Setting $u_2 = u'_2 + u''_2$, we find 
-    \begin{align*}
-        d u_2 = d u'_2 + d u''_2 = d u'_2 + f - d u'_2 = f,
-        \\
-        \trace_F u_2 = \trace_F u'_2 = \trace_F u_1.
-    \end{align*}
-    That requires an extension from given partial boundary data. 
-    Possible approaches:
-    \begin{itemize}
-        \item Reflect a neighborhood and multiply with cut-off function.
-        \item Take traces from patch and extend onto new simplex. 
-    \end{itemize}
-\end{remark}
+\begin{proof}
+    The desired results are known for smoothly bounded domains;
+    see Theorem~2.6 of \cite{guerini2004eigenvalue} for % decay in k
+    see \cite[Theorem~1.3]{guerini2004spectre} for
+    \begin{align*}
+        C \diam(\Omega)^{-2} 
+        \leq 
+        \lambda_{k},
+        \qquad 
+        C := 
+        \left\{\begin{array}{ll}
+            \frac{n-1}{ne^{3}} & \text{ if } k=0
+            \\
+            \frac{k(n-k)}{ne^{3}} & \text{ if } 1 \leq k \leq n-1
+            \\
+            \lambda_{1,0}(B) & \text{ if } k = n % Dirichlet eigenvalue over a ball
+        \end{array}\right. 
+        % \frac{\max_{k(n-k),n-1}}{ne^{3}} \diam(\Omega)^{-2}        
+    \end{align*}
+    see \cite{savo} for $n \geq 3$, 
+    \begin{align*}
+        \frac{4}{n^{2} \tbinom{n}{k-1} \diam(\Omega)^{2} } \leq \lambda_{k}
+    \end{align*}
+
+    We use a technical argument
+    to generalize them to our situation.
+
+    There exists a bi-Lipschitz mapping $\varphi : \overline{B_1(0)} \rightarrow \Omega$. 
+    We let $\varphi_{\eps} : \overline{B_1(0)} \rightarrow \bbR^{n}$ be smooth,
+    uniformly bounded, and pointwise converging to $\varphi$ in the norm of $W^{1,\infty}$. 
+    For $\epsilon > 0$ small enough, 
+    the range $\Omega_{\eps}$ of each $\varphi_{\eps}$ is a smoothly bounded domain,
+    and $\varphi_{\epsilon} : \overline{B_1(0)} \rightarrow \Omega_{\eps}$ is a diffeomorphism.
+    The diameters of $\Omega_{\eps}$ converge to the diameter of $\Omega$.
+    The desired claim now follows by the dominated convergence theorem % Given $u \in W^{2}\Lambda^{k}(\Omega)$
+
+\end{proof}
+
+% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
+% https://eudml.org/doc/258483
+
+\begin{lemma}
+    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
+    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
+    \begin{align*}
+        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R^{2}/r % euclidean 
+    \end{align*}
+    If $K$ is convex, then 
+    \begin{align*}
+        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
+        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
+    \end{align*}
+
+\end{lemma}
 

### 2024-06-30 plotconstant.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def EFNT(p):
+    return (p * np.sin(np.pi / p)) / (2 * np.pi * ((p - 1) ** (1 / p)) )
+    
+    
+# Define the function f(p)
+def f(p):
+    return EFNT(p) + ( EFNT(p) ** p + p * EFNT(p) ** (p-1) ) ** (1/p)  - (1/p) ** (1/p)
+
+# Generate p values from 1 to 100
+ps = np.linspace(1.01, 100, 1000)
+ys = f(ps)
+
+print(ps)
+print(ys)
+
+# Plot the function
+plt.plot( ps, ys, label='f(p)')
+plt.xlabel('p')
+plt.ylabel('f(p)')
+plt.title('Plot of f(p) from 1 to 100')
+plt.legend()
+plt.grid(True)
+plt.show()
+
+

### 2024-07-04 main.tex
Update on Overleaf.

--- 2024-06-28 main.tex
@@
     The main application that we envision are computable estimates over finite element patches. 
-    %
-    As a result with independent standing, we establishes Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators. 
 \end{abstract}
@@
 \end{align*}
-The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. Any upper bound for it corresponds to a lower bound for the Maxwell eigenvalues.
+The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.
 
@@
 % We accomplish our results for a special class of triangulations, so-called shellable triangulations.
-We accomplish this undertaking in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
+We accomplish this task in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
 Even though only contractible domains can ever admit a shellable triangulation, 
@@
 When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{ern2021finite}. 
+then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008finite,ern2021finite}. 
 An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain,
@@
 \end{align*}
-Their members are vector fields whose distributional partial derivatives satisfy certain cancellation properties. 
+Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
+This only requires that certain linear combinations of distributional partial derivatives are measurable, 
+and in particular these spaces are not classical Sobolev spaces of vector fields. 
 Our objective is to find bounded potentials for the operators 
 \begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\curl,\Omega),
+    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
     \qquad 
@@
 
-The literature is much scarcer when it comes to this. 
+The literature in functional analysis is much scarcer when it comes to this. 
 We can access some estimates from the literature in the formalism of exterior calculus. 
@@
 However, that interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape regularity. 
-Estimates that rely on this geometric condition deteriorate when the aforementioned ball has small radius,
+Estimates that rely on this geometric condition thus deteriorate when the aforementioned ball has small radius,
 and that is inevitable when the domain has an unfortunate geometry. 
@@
 % TODO: wait for answer to email 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
+Veeser and Verfürth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
 Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
@@
 we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
+In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
+via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
+We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
+which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
+However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as finite element stars.
 We are not aware of any estimates for the curl operator, even in the Hilbert space situation. 
@@
 
-The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence, satisfying explicitly computable upper bounds.
+The main objective of the present exposition is the construction of linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds.
 We follow closely the philosophy of the aforementioned sequential approach.
@@
 
-In addition to that, we need to find potentials over a simplex subject to partial boundary conditions,
+In addition to that, we need to find potentials over a simplex subject to partial boundary conditions. 
 Again, we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
@@
 Upper bounds correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
-Furthermore, their constants enter the stability and convergence theory of finite element methods. 
+% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
 In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
@@
 We have also identified that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularlized potential operators.
 It is of interest whether the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
@@
 % (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
+% The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
 We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{We warn the reader that simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes.}
@@
  Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\calT_{n}(S) \cap \calT_{n}(S') = \emptyset$ or there exists $S'' \in \calT$
- such that $\calT_{n}(S) \cap \calT_{n}(S') = \calT_{n}(S'')$ with $S, S' \subseteq S''$.
+ Then either $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \emptyset$ or there exists $S'' \in \calT$
+ such that $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \calT_{n}(S'')$ with $S, S' \subseteq S''$.
 \end{lemma}
@@
 % \end{align*}
-Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.
+Via an application of the triangle inequality, 
+the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.
 
@@
 Stern~\cite{stern2015banach} provided a generalization of the projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that % TODO: cite specific results of Ari 
 \begin{align*}
@@
 \end{align}
+% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity paremeter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
 Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
@@
 \end{align}
-Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
+Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
 that preserves $F$. We define 
@@
 This indicator quantifies how much reflection across the shared face distorts the geometry. 
+% TODO: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
 
@@
         \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        \leq 
+        = 
         \kappa(T_1) \kappa(T_2)
@@
         \diam(F)
-        \leq 
+        = 
         \kappa(T_1)
@@
         \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        \leq 
+        =  
         \sqrt{2n^{n+1}} 
@@
     We estimate 
+    % TODO: I am not 100% sure what that means.
+Is really the heights of F?
+I imagine this is rather the heights of simplices T_1 and T_2, isn't?
+Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
+(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
+    % TODO: clarify the following inequalities
     \begin{align*}
@@
 \begin{lemma}\label{lemma:mixedbconsimplex}
-    Let $T$ be an $n$-simplex and with a face $F$. 
+    Let $T$ be an $n$-simplex with a face $F$. 
     If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
@@
         C_{{\rm PF},T,p} 
-        \| \nabla w \|_{\bfL^{p}(T)}
+        \| \nabla w \|_{\bfL^{p}(T)} % TODO: bold face or no boldface? No bold face 
         .
@@
 
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    There exists $\varphi : \hat T \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
     We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \varphi )$. 
@@
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner.
-Patches within triangulations are examples of such shellable complexes.
+Patches within triangulations of dimension two and three are examples of such shellable complexes.
 Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}.
@@
 
-We know that any manifold $\calM$ has a got a topological boundary $\partial\calM$, possibly empty. 
+We know that any manifold $\calM$ has got a topological boundary $\partial\calM$, possibly empty. 
 If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$.
@@
     then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere $S$ of dimension $n-1$. 
-    At the same time, $X = F \subseteq \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere $S' \subseteq S$ of dimension $n-2$. 
+    At the same time, $X = F \cap \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere $S' \subseteq S$ of dimension $n-2$. % TODO: proofread
     We see that $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
@@
         \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. % TODO: Define this macro 
         \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
@@
     \item 
-    If the underlying space is connected, then we easily see that the underlying space of the $1$-skeleton is path-connected.
+    If the underlying space is connected, then we easily see that the union of the $1$-simplices is path-connected.
     Given $n$-simplices $S,S' \in \calT$, 
@@
     We also notice that each vertex star is strongly connected. 
-    We can thus construct change the first sequence to another $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
+    We can thus change the first sequence to another $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
     such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
@@
     Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. 
+    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
+    Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
+    % Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. ~\cite{todo}
     We therefore are not in pursuit of any easy combinatorial property that indicates whether a simplicial complex (without any further specific assumptions) triangulates a manifold.
@@
 \begin{lemma}    
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, 
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, % TODO: what is non-brnaching?
     then
@@
     $$ 
-    is a manifold with boundary for all $0 \leq m \geq M$.
+    is a manifold with boundary for all $0 \leq m \leq M$.
     % 
@@
     We call a triangle $T \in \calT$ \emph{good} if it intersects the boundary $\partial M$ in a non-empty union of edges.
+% TODO: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
     We show by an induction argument over the number of triangles that every triangulation of a $2$-disk contains a good triangle. 
@@
 In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
+$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
 \[
@@
 \]
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
+The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
 and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
@@
 \end{subequations}
-for $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
+for $v \in W^{p}(\grad,\Omega)$, $\bfv \in W^{p}(\curl,\Omega)$, and $\bfw \in W^{p}(\divergence,\Omega)$.  
 We summarize this as a commuting diagram:
@@
     \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
+        W^{1,p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
         \\
@@
         \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
+        W^{1,p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
     \end{CD}
@@
 \begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
     scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
+    This is in accordance with the notion of pullback, that we will review shortly. 
     One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
 \end{remark}
+
+%
 
@@
 
-Having discussed vector analysis, we review exterior calculus. 
-We give a brief introduction into this topic, and refer to the literature for further background~\cite{...}. 
+We also assume the perspective of exterior calculus. 
+We give a brief introduction into this topic. 
 Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
+Given an integer $k \geq 0$, We let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
 Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
@@
     \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
+    \sum_{ \sigma \in S_{k+l}} 
+    \signum(\sigma) 
+    u_1( v_{\sigma(  1)}, \ldots, v_{\sigma(k  )} ) 
+    u_2( v_{\sigma(k+1)}, \ldots, v_{\sigma(k+l)} ),
 \]
 for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
+Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\sigma) \) is the sign of the permutation \( \sigma \).
 The exterior product is bilinear and associative, and satisfies
@@
 \begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
+    \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
 \end{align*}
@@
 which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
+The exterior derivative \( d \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
+to a \((k+1)\)-form \( d\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
 Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
@@
 where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
+The exterior derivative \( d\omega \) is defined by
 \[
-    \cartan\omega = 
+    d\omega = 
     \sum_{ \sigma \in \Sigma(k,n) } 
@@
 The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
+\( d(d\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
 Moreover, it satisfies the Leibniz rule:
 \[ 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
+    d(\omega \wedge \eta) 
+    = 
+    d\omega \wedge \eta + (-1)^{k} \omega \wedge d\eta, 
     \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
@@
 \]
-Let us now turn our attention to Sobolev spaces of differential forms. 
+Let u now turn our attention to Sobolev spaces of differential forms. 
 Since $\Alt^{k}(\Omega)$ is a normed space, we can consider the pointwise norms of differential $k$-forms. 
@@
 \]
-We observe that $u \in L^p\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^p\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
 We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
@@
 for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.
-
-% TODO: transformationssatz
 
@@
     \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
+        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) @>{d}>> C^\infty\Alt^3(\Omega) 
         \\
@@
     We summarize the situation in the following commuting diagram: 
-    \[ % TODO: what is the convention for the curl and rotation ? look up in the textbooks?
+    \[
     \begin{CD}
@@
         \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
+        C^\infty\Alt^0(\Omega) @>{d}>> C^\infty\Alt^1(\Omega) @>{d}>> C^\infty\Alt^2(\Omega) 
         \\
@@
 
-% TODO: spaces with boundary conditions: grad, curl, divergence, exterior derivative; approximation properties
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable. 
-    Then $u_\epsilon \rightarrow u$ almost everywhere. 
-    If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$. 
-\end{lemma}
-
-\begin{lemma} % TODO: possibly useful
-    Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-\end{lemma}
-
-\begin{lemma}
-    Smooth forms are dense in $\bfW^{p}\Lambda^{k}$.
-\end{lemma}
-
 \section{Regularized potential operators over convex sets}\label{section:potentialoperator}
 
-We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-We already know the optimal constants for the gradient operator over convex domains,
-and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
-
-For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
-and the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our explicit purpose are explicit bounds for the operator norms, which are of independent interest. 
-\\
+We use potential operators for the exterior derivative over convex domains that respect boundary conditions. 
+These are known as Bogovski\u{\i}-type operators.
+They were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics.~\cite{bogovskii1979solution} 
+The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+on whose work the following presentation is based. 
+In contrast to the aforementioned reference, the goal of our discussion is more modest:
+we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
+However, we derive explicit bounds for the operator norms, which are of independent interest.
+
+\begin{remark}
+It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
+The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
+The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
+These operators are defined over sets star-shaped with respect to a ball. 
+Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis.
+However, no operator norm estimates are given in the literature, to the best of our best knowledge.
+We study a variation of this potential operator over convex sets.
+We simply use a constant averaging over the entire domain. 
+While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
+this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms. 
+\end{remark}
 
@@
 \end{align}
-We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
-\\
-
-We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
+We call $\Bogov_{\ell}$ a Bogovski\u{\i}-type operator.
+
+We show that the integrals in the definition of $\Bogov_{\ell}$ actually exist. 
+In order to understand the properties of the operator $\Bogov_{\ell}$,
+including the convergence of the integral, we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
+Letting $x,y \in \bbR^n$ with at least one $x$ or $y$ contained in $\Omega$, we deduce 
 \begin{align*}
@@
 \end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
+We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus % TODO: define D
 \begin{align*}
@@
 \end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-We begin with the Poincar\'e operator. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
-We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\ell} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_D(0)} |z|^{k+1-n} dz
-    =
-    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
-    =
-    \vol_{n-1}(S_1) \int_0^D r^{k} dr
-    =
-    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-    .
-\end{align*}
-We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
-    \\&
-    =
-    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
-    .
-\end{align*}
-Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{n-\ell}$. 
-In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-    &\leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\[
-    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
-\]
-% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
-% 
-We analyze the Bogovski\u{\i} potential operator with similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\ell} u(x)$ pointwise by 
+We can now analyze the potential operator $\Bogov_{\ell}$. 
+Suppose that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$ and that $x \in \bbR^{n}$.
+First, if $x \notin \overline\Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t \geq 1$.
+Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
+More generally, we pointwise estimate $\Bogov_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
 \begin{align*}
@@
 \end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_D(0)} |z|^{k+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_0^D r^{k} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-%     .
-% \end{align*}
-% We compute 
+We recall the radial integrals 
+\begin{align*}
+    \int_{B_D(0)} |z|^{k+1-n} dz
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
+    =
+    \vol_{n-1}(S_1) \int_0^D r^{k} dr
+    =
+    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
+    .
+\end{align*}
+We compute 
 \begin{align*}
@@
     =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
+    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
+    .
+\end{align*}
+Here, $A(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
 and which is bounded by $2^{\ell-1}$. 
@@
 So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
+Taylor's convolution inequality now implies: 
 \begin{align*}
@@
     \leq 
-    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
     D
@@
 \end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
+We have assumed so far that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$. 
+Since that space is dense in the Lebesgue spaces, a density argument provides gives the following: 
 for any $1 \leq p \leq \infty$ we have a bounded linear operator 
 \[
-    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
+    \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
 \]
-% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
 Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
 that is, the reconstructed potential has support contained within $\overline\Omega$.
-\\
 
 Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\ell} u(x) 
-    &= 
-    \int \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+We write down the full definition of these operators and perform two substitutions:
+first, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
 leading to 
@@
 % 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\ell,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
-    ,
-    \\
+Given $a \in \Omega$, we introduce the potential operator 
+\begin{align*}
     \Bogov_{\ell,a} u(x) 
@@
 \begin{align*}
-    \Poinc_{\ell} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;,
-    \quad 
     \Bogov_{\ell} u(x) 
@@
 \end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-That discussion is classical and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators 
-are not yet included in the published literature.
-
-Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\ell,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\ell,a} u(x) 
-    &= 
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
-    ,
-\end{align*}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\ell+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    \;\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \;\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Poinc_{\ell,a} u(x)
-    +
-    \Poinc_{\ell+1,a} \cartan u(x)
-    \\&
-    =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
-    \cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell,a} u = u$.
-
-% TODO: averaging
-
-The discussion for the Bogovski\u{\i} operator is almost analogous. 
+We study the interaction of the potential operator with the exterior derivative in more detail.
 Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell})$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \Bogov_{\ell,a} u(x) 
+We rewrite the potential,
+\begin{align*}
+    T_{\ell,a} u(x) 
     &= 
@@
 \begin{align*}
-    \cartan \Bogov_{\ell,a} u(x) 
+    \cartan T_{\ell,a} u(x) 
     &= 
-    \ell 
+    k
     \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
@@
 \end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \Bogov_{\ell+1,a} \cartan u(x)
+and apply the potential operator to this result, which gives 
+\begin{align*}
+    T_{\ell+1,a} \cartan u(x)
     &=
@@
     &
-    \cartan \Bogov_{\ell,a} u(x)
+    \cartan T_{\ell,a} u(x)
     +
-    \Bogov_{\ell+1,a} \cartan u(x)
+    T_{\ell+1,a} \cartan u(x)
     \\&
@@
 \end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell,a} u = u$.
-\\
-
-% TODO: averaging
-
-We are in the position to establish the main results of this section.
-This includes upper bounds for the Poincar\'--Friedrichs inequalities that we have been looking for. 
-Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.
-
-\begin{theorem}
-    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-        D
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-        D
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
-    If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
-\end{theorem}
-\begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Poinc_{\ell  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\ell} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}(\Omega,\Alt^{n-\ell-1})$, 
-    which is the restriction of some member of $C^{\infty}(\bbR^{n},\Alt^{n-\ell-1})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-    % TODO: definition of weak derivative + definition of boundary condition 
-    % 
-    This completes the proof. 
-\end{proof}
-
-% TODO: Density of C infty mit oder ohne c. 
-% TODO: Density im kernel 
-% TODO: lrcorner
-
-\begin{remark}
-    The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-    while they are increasing for the Bogovski\u{\i} operator.
-    This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over convex domains~\cite{guerini2004eigenvalue}.
-\end{remark}
-
-\begin{remark}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % 
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-\end{remark}
-
-\section{Extension operator on finite element stars}\label{section:extension}
-% Only define the geometric mapping and its important quantities
-% Leave the function spaces etc. for later
-
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-\subsection{Inequalities for partial boundary conditions on a single simplex}
+In particular, if $\cartan u = 0$, then $\cartan T_{\ell,a} u = u$.
+
+For full technical clarity, we show we have a bounded operator 
+\[
+    \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+    .
+\]
+% - Rewrite kernel
+% - Show the support property
+% - Assess that it is Lp bounded for compactly supported forms; density argument
+% - Conclude that it is absolutely convergent. Do one (!) derivative
+% - Poincare lemma for smooth forms : needs smoothness, but that's a simple calculation 
+% - prove duality via some density argument and the extension of smooth forms outside of Lipschitz domains
 
 \begin{lemma}
-    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
-    Then 
-    \begin{align*}
-        \| u \| \leq 
-    \end{align*}
+    Let $\Omega \subseteq \bbR^{n}$ be convex. There exists a bounded mapping 
+    \begin{align*}
+     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
+    \end{align*}
+    such that 
+    \begin{align*}
+        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
+    \end{align*}
+    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
 \end{lemma}
-\begin{proof}
-    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-    such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
-    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
-    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
-
-    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
-    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
-
-    The operator norm bound of the potential operator shows 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        \\&
-        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        .
-    \end{align*}
-    We use the pullback estimates 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        \| \Jacobian\varphi \|_{\infty}^{k}
-        |\det\varphi^{-\frac{1}{p}}|
-        \cdot 
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        .
-    \end{align*}
-    \begin{align*}
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        2^{n-l}
-        \| \hat f \|_{L^{p}(\hat T)} 
-        \leq 
-        2^{n-l}
-        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
-        |\det\varphi^{\frac{1}{p}}|
-        \cdot 
-        \| f \|_{L^{p}(T)} 
-        .
-    \end{align*}
-\end{proof}
-
-\subsection{Constructions over shellable triangulations}
 
@@
     \begin{align*}
-        \| \vec u \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \vec u \|_{L^{2}(\Omega)}.
+        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)},
+        \qquad 
+        \bfu \in \bfH(\divergence,\Omega)
+        .
     \end{align*}
@@
 \end{proof}
+
+\section{Extension operator on finite element stars}\label{section:extension}
+% Only define the geometric mapping and its important quantities
+% Leave the function spaces etc. for later
+
+\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
+
+\subsection{Inequalities for partial boundary conditions on a single simplex}
+
+\begin{lemma}
+    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    Then 
+    \begin{align*}
+        \| u \| \leq 
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+    such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
+    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
+    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
+    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
+    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
+
+    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
+    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
+
+    The operator norm bound of the potential operator shows 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        \\&
+        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        .
+    \end{align*}
+    We use the pullback estimates 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        \| \Jacobian\varphi \|_{\infty}^{k}
+        |\det\varphi^{-\frac{1}{p}}|
+        \cdot 
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        .
+    \end{align*}
+    \begin{align*}
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        2^{n-l}
+        \| \hat f \|_{L^{p}(\hat T)} 
+        \leq 
+        2^{n-l}
+        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
+        |\det\varphi^{\frac{1}{p}}|
+        \cdot 
+        \| f \|_{L^{p}(T)} 
+        .
+    \end{align*}
+\end{proof}
+
+\subsection{Constructions over shellable triangulations}
 

### 2024-07-04 main.tex
more stuff

--- 2024-06-30 main.tex
@@
 
-    We use a technical argument
-    to generalize them to our situation.
-
-    There exists a bi-Lipschitz mapping $\varphi : \overline{B_1(0)} \rightarrow \Omega$. 
-    We let $\varphi_{\eps} : \overline{B_1(0)} \rightarrow \bbR^{n}$ be smooth,
-    uniformly bounded, and pointwise converging to $\varphi$ in the norm of $W^{1,\infty}$. 
-    For $\epsilon > 0$ small enough, 
-    the range $\Omega_{\eps}$ of each $\varphi_{\eps}$ is a smoothly bounded domain,
-    and $\varphi_{\epsilon} : \overline{B_1(0)} \rightarrow \Omega_{\eps}$ is a diffeomorphism.
-    The diameters of $\Omega_{\eps}$ converge to the diameter of $\Omega$.
-    The desired claim now follows by the dominated convergence theorem % Given $u \in W^{2}\Lambda^{k}(\Omega)$
-
+    For each $0 \leq k \leq n$ we let $\mu_{k}$ be the smallest non-zero eigenvalue of the Hodge-Laplace operator acting on $k$-forms.
+For each $0 \leq k \leq n-1$, we let $\sigma_{k}$ be the smallest non-zero singular value of the exterior derivative $\cartan : L^{2}\Lambda^{k}(\Omega) \rightarrow L^{2}\Lambda^{k+1}(\Omega)$.
+We have the relation
+    \begin{align*}
+        \mu_{k} = \min( \sigma_{k}, \sigma_{k-1} )^{2}.
+    \end{align*}
+    We first consider the case where $\Omega$ is strictly convex with smooth boundary. 
+    According to Theorem~2.6 of \cite{guerini2004eigenvalue},
+    \begin{align*}
+        \mu_{0} = \mu_{1} < \dots < \mu_{n}.
+    \end{align*}
+    By definition, we have $\mu_{n} = \sigma_{n-1}^{2}$. 
+    Suppose that we know $\mu_{k} = \sigma_{k-1}^{2}$ for some $2 \leq k \leq n$. Then 
+    \begin{align*}
+        \sigma_{k-1}^{2} = \mu_{k} > \mu_{k-1} = \min( \sigma_{k-1}, \sigma_{k-2} )^{2}
+    \end{align*}
+    implies $\mu_{k-1} = \sigma_{k-2}^{2}$. 
+    Iterating this, we find 
+    \begin{align*}
+        \sigma_{0} < \sigma_{1} < \dots < \sigma_{n-1}.
+    \end{align*}
+    We have shown this when $\Omega$ is strictly convex with smooth boundary.
+
+    We now address the case where $\Omega$ is merely convex. 
+    According to Theorem~A of \cite{blocki1997smooth}, 
+    there exists a continuous convex function $\beta : \overline\Omega \rightarrow \bbR$ that equals zero along $\partial\Omega$, which is negative over $\Omega$, and whose Hessian over $\Omega$ has positive determinant.
+    This already implies that the Hessian of $\beta$ over $\Omega$ is always positive-definite, and so $\beta : \Omega \rightarrow \bbR$ is strictly convex.
+
+    For $\epsilon > 0$ small enough, the sublevel sets 
+    \begin{align*}
+        \Omega_{\epsilon} := \left\{ x \in \Omega \suchthat \beta(x) < -\epsilon \right\}
+    \end{align*}
+    are strictly convex smoothly bounded open sets compactly contained in $\Omega$. 
+    For convenience, we also write $\Omega_{0} := \Omega$.
+
+    We first show that for each $\rho > 0$ there exists $\epsilon > 0$ such that $\Omega \setminus \Omega_{\epsilon} \subseteq \partial\Omega + B_{\rho}(0)$. 
+    Indeed, if that were not the case, then there would exist $\rho > 0$ such that for any $\epsilon > 0$ we can find $x_{\epsilon}$ with $\beta(x_{\epsilon}) > -\epsilon$ but distance at least $\rho$ from $\partial\Omega$.
+We could then pick a subsequence converging to a point $x \in \Omega$ with $\beta(x) = 0$, which is a contradiction.
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%
+    % TODO: from here on 
+    For $\rho > 0$ small enough, the mapping 
+    \begin{align*}
+        A : \partial\Omega \times [0,\rho] \rightarrow \bbR^{n}, \quad (x,s) \mapsto x - \frac{s}{|x|} x
+    \end{align*}
+    is bijective. It satisfies the bounds 
+    \begin{align*}
+        ..
+    \end{align*}
+    and 
+    \begin{align*}
+        ..
+    \end{align*}
+    % TODO:
+    Consequently, there exists $L > 0$ such that for all $\epsilon > 0$ small enough 
+    there exists $B_{\epsilon} : \Omega \rightarrow \Omega_{\epsilon}$ bi-Lipschitz with
+    \begin{align*}
+        \| \Id - B_{\epsilon} \|_{L^{\infty}(\Omega)} < L \epsilon,
+        \quad 
+        \| \Id - \Jacobian B_{\epsilon} \|_{L^{\infty}(\Omega)} < L \epsilon.
+    \end{align*}
+    %%%%%%%%%%%%%%%%%%%%%%%%%
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%
+    For any $\epsilon \geq 0$, we let $X^{k}_{\epsilon} := H\Lambda^{k}(\Omega) \cap \ker\cartan$. 
+    Notice that $B_{\epsilon}^{\ast} X^{k}_{\epsilon} = X^{k}_{0}$. 
+    %
+    Consider any $0 \leq k \leq n-1$. 
+    Let $f \in H\Lambda^{k+1}(\Omega)$ with $\cartan f = 0$.
+    There exists $u_\star \in H\Lambda^{k}(\Omega)$ with $\cartan u = f$ 
+    because $\Omega$ is convex and thus contractible. % TODO: theorem 
+    Notice that $B_{\epsilon}^{-\ast} u_0 \in H\Lambda^{k}(\Omega_{\epsilon})$ 
+    with $\cartan B_{\epsilon}^{-\ast} u_\star = B_{\epsilon}^{-\ast} f$ over $\Omega_{\epsilon}$.
+    % 
+    \begin{align*}
+        ..
+    \end{align*}
+    % TODO
+    We conclude that $P^{k}_{\epsilon} \rightarrow P^{k}_{0}$ in the operator norm. 
+    In particular, the operator norms converge. 
+    %%%%%%%%%%%%%%%%%%%%%%%%%
+
+    For any $0 \leq k \leq n-2$ and $\epsilon > 0$ we have $\| P^{k}_{\epsilon} \| < \| P^{k+1}_{\epsilon} \|$,
+    so that $\| P^{k}_{0} \| \leq \| P^{k+1}_{0} \|$.
+    This had to be shown.
+%     
+%     There exists a bi-Lipschitz mapping $\varphi : \overline{B_1(0)} \rightarrow \Omega$. 
+%     We let $\varphi_{\eps} : \overline{B_1(0)} \rightarrow \bbR^{n}$ be smooth,
+%     uniformly bounded, and pointwise converging to $\varphi$ in the norm of $W^{1,\infty}$. 
+%     For $\epsilon > 0$ small enough, 
+%     the range $\Omega_{\eps}$ of each $\varphi_{\eps}$ is a smoothly bounded domain,
+%     and $\varphi_{\epsilon} : \overline{B_1(0)} \rightarrow \Omega_{\eps}$ is a diffeomorphism.
+%     The diameters of $\Omega_{\eps}$ converge to the diameter of $\Omega$.
+%     The desired claim now follows by the dominated convergence theorem % Given $u \in W^{2}\Lambda^{k}(\Omega)$
+    % TODO: show that the trafo converges to identity.
+    % Write the trafo as perturbation of the identity.
 \end{proof}
@@
 % https://eudml.org/doc/258483
-
+% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
+% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
 \begin{lemma}
@@
         R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
+        \\
         \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
     \end{align*}
-
+\end{lemma}
+
+\begin{lemma}
+    .
 \end{lemma}

### 2024-07-04 main.tex

@@
-\documentclass[10pt,a4paper]{article}
+\documentclass[12pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
@@
     %
-    As a result with independent standing, we establishes Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
+    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
     This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
+    We express all our main results in the calculus of differential forms and treat the curl and divergence operator as its particular instances. 
 \end{abstract}
@@
 The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
-In particular, these operator norm bounds yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
-Equivalently, this gives lower bounds for the eigenvalues of several vector Laplacians.
+In particular, such operator norm bounds yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
 
@@
 For example, local patches around a simplex within a larger 2D or 3D triangulation are shellable.
-We express all our main results in the calculus of differential forms, also known as exterior calculus, 
-and treat the curl and divergence operator as its particular instances. 
 \\
@@
 we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
+We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
 Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
@@
     .
-\end{align*}
+\end{align*} % TODO: use same notation as later 
 Its operator norm is the constant $C_{\rm P,p} > 0$ in the Poincar\'e inequality 
@@
 \end{align*}
-Their members are vector fields whose distributional partial derivatives satisfy certain cancellation properties. 
+Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
+This only requires that certain linear combinations of distributional partial derivatives are integrable, 
+and hence these spaces are not classical Sobolev spaces of vector fields. 
 Our objective is to find bounded potentials for the operators 
 \begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\curl,\Omega),
+    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
     \qquad 
@@
 \begin{align*}
-    \argmin\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
+    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
     \| \bfv \|_{\bfL^{p}(\Omega)}
@@
     \qquad 
-    \argmin\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
+    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
     \| \bfv \|_{\bfL^{p}(\Omega)}
@@
 
-The literature is much scarcer when it comes to this. 
+The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
 We can access some estimates from the literature in the formalism of exterior calculus. 
@@
 By duality, that implies lower bounds for the case of full boundary conditions.
-Their work also includes the following sequence of inequalities,
-valid over convex domains in 3D:
+Their study also implies sequences of inequalities, such as the following in 3D convex domains:
 \begin{align}\label{math:intro:guerinisavo}
@@
 
+The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local patches within triangulated domains. 
 Clearly, not all local patches describe convex subdomains. 
@@
 % 
-The literature knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that can circumvent the effect of low boundary regularity~\cite{vohralik2005discrete,ern2021finite}.
-These potentials share being constructed step-by-step: 
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is complete.
+The literature~\cite{vohralik2005discrete,ern2021finite} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
+starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted.
 That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest.
@@
 
-While we know Poincar\'e--Friedrichs constants over finite element patches for scalar-valued Sobolev spaces, 
+While we know Poincar\'e--Friedrichs constants over local patches for scalar-valued Sobolev spaces, 
 we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
+In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
+via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
+We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
+which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
+However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local patches.
 We are not aware of any estimates for the curl operator, even in the Hilbert space situation. 
@@
 
-The main objective of the present exposition is the construction of linear potential operators the gradient, curl, and divergence, satisfying explicitly computable upper bounds.
-We follow closely the philosophy of the aforementioned sequential approach.
+Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we follow closely the philosophy of the aforementioned sequential approach.
 Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
@@
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,}.
+Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,}.
 Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights structures common to the gradient, curl, and divergence operators.
-It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
+The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
+%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\ % hu2019structure
+\\ % TODO hu2019structure
 
@@
 Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-The two potentials will not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-
-To ensure the correct continuity properties, we require triangulations with stronger structures than in the case of gradient potentials.
-We need to ensure that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
+
+To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
+We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
 Under those conditions, which are met by \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
@@
 
-% Shellable 
+% TODO: compare with previous paragraphs 
 This construction of potentials requires triangulations with special conditions: 
@@
 % We construct gradient potentials locally over convex domains or face patches. 
-Estimating the norm of local potential operators over convex domains is an important subcomponent of this endeavor. 
+Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
 Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
+% TODO: cite VVVV
 While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
@@
 
+% TODO: cite VVVV
 In the Hilbert space case, $p=2$, the work of Guerini and Savo shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
@@
 
-No such results are known for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
+But no such results are known for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
 We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator has generally lower regularity properties in comparison to the regularized potential in the literature;
+The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
 however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
@@
 
-In addition to that, we need to find potentials over a simplex subject to partial boundary conditions,
-Again, we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
+In addition to that, we need to find potentials over a simplex subject to partial boundary conditions. 
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
 We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
@@
 
-We have also identified that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
+We conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
 We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-It is of interest whether the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
 On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
@@
 % \end{align*}
-Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+Via an application of the triangle inequality, 
+the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
 \begin{align*}
@@
 and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern~\cite{stern2015banach} provides a generalized projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+Stern's generalized projection estimate~\cite{stern2015banach} implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that % TODO: cite specific results of Ari 
 \begin{align*}
@@
     The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
     scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
@@
 \end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives % TODO: define D
 \begin{align*}
@@
     Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
+    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
     The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,

### 2024-07-04 main.tex

@@
 Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,p} > 0$ such that 
+we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
 \begin{align*}
@@
     \leq 
-    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
+    C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
     \quad 
@@
     .
-\end{align*} % TODO: use same notation as later 
-Its operator norm is the constant $C_{\rm P,p} > 0$ in the Poincar\'e inequality 
+\end{align*} 
+Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
 \begin{align*}
@@
     \leq 
-    C_{\rm P,p} \| \nabla u \|_{L^p(\Omega)},
+    C_{\varnothing,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
     \quad 
@@
 % The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, the optimal constants $C_{\grad,p}$ for any $1 \leq p < \infty$ that depends only on the domain diameter is known when the domain is convex.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+Notably, the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ that depends only on the domain diameter is known when the domain is convex.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
 When the domain is not convex but star-shaped with respect to a ball,
@@
     \leq 
-    C_{\curl,p}
+    C_{\curl,\Omega,p}
     \| \bff \|_{\bfL^{p}(\Omega)}
@@
     \leq 
-    C_{\divergence,p}
+    C_{\divergence,\Omega,p}
     \| f \|_{L^{p}(\Omega)}
@@
 \begin{align}\label{math:intro:guerinisavo}
-    C_{\grad,2} \geq C_{\curl,2} \geq C_{\divergence,2}.
+    C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
 \end{align}
@@
 We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
 Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
@@
 
-% TODO: compare with previous paragraphs 
-This construction of potentials requires triangulations with special conditions: 
-we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Shellable triangulations are defined by a special constructive property:
+we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D triangulations are shellable. 
+\\
+
+% This construction of potentials requires triangulations with special conditions: 
+% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
 Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
@@
 Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable. 
-\\
+% In particular, local stars in 2D and 3D triangulations are shellable. 
+% \\
 
@@
     If we place $\calC$ on the x-axis of a 2D coordinate system 
-    and connect each member of $\calC$ to $(0,1)$ via a straight line segment, 
+    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
     then the resulting set is still compact, even path-connected,  
@@
 In practice, we not always distinguish between points and singleton simplices. 
-Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.
-
-\begin{remark}
+Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
+% \begin{remark}
     Our use of the term \textit{face} as is common in the finite element literature
     and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra. 
-\end{remark}
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{star} of $T$, 
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra. %
+% \end{remark}
+}
+
+When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
 which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. Formally,
@@
  Then either $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \emptyset$ or there exists $S'' \in \calT$
- such that $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \calT_{n}(S'')$ with $S, S' \subseteq S''$.
+ such that $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S'')$ with $S, S' \subseteq S''$.
 \end{lemma}
@@
 
-We will use a specific notion of connectivity. 
+We introduce a specific notion of connectivity. 
 Given an $n$-dimensional simplicial complex $\calT$, 
@@
 Clearly, strongly connected in $\calT$ is an equivalence relation. A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ strongly connected if it has only one strongly connected component.
+and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component.
 
@@
 \end{align}
-% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity paremeter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
+% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
 Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
@@
 \begin{lemma}    
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, % TODO: what is non-brnaching?
+    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, % TODO: what is non-branching?
     then

### 2024-07-04 main.tex
Update on Overleaf.

@@
 \subsection{Poincar\'e--Friedrichs inequalities over convex domains}
-% See the collection at Lemma 3.24 : https://hal.science/hal-03226049/file/volI_hal.pdf
 
@@
 This defines a scalar potential.
-This shall be our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials. 
-After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed in intermediate steps.
-Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion. 
-\\
-
-Towards this goal, we introduce quantitative measures for the geometric quality of triangulations,
-which give an indication of the regularity of simplex shapes. 
+This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
+after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
+\\
+
+Towards this goal, we introduce quantitative measures for the geometric quality of triangulations. 
+These indicate of the regularity of simplex shapes. 
 Most of such \emph{shape measures} in the literature are based on geometric features, 
-but we consider indicators based on affine transformations associated with the mesh;
+but we also consider indicators based on affine transformations associated with the mesh;
 this is because the properties of these transformations are what shows up in our estimates.
 
-Whenever $T$ is an $n$-dimensional simplex 
+We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
 \begin{align}\label{math:geometricshapemeasure}
@@
 \end{align}
+Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
 Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
@@
 This indicator quantifies how much reflection across the shared face distorts the geometry.
-% TODO: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
+
+For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.
+
+% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
 
@@
 % \end{align*}
-
-\begin{lemma}\label{lemma:affinetransform}
-    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
-    \begin{align*}
-        \| \Jacobian \varphi \|
-        \leq 
-        \sqrt{n} \cdot \diam(T)
-        ,
-        \qquad 
-        \| \Jacobian \varphi^{-1} \|
-        \leq 
-        \sqrt{2n^{n}} 
-        % \frac{ n! \vol(T) } { \diam(T)^{n} }
-        \kappa(T)^{-1}
-        \diam(T)^{-1}
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\varphi$ in descending order.
-    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\varphi)$. Hence 
-    \[
-        \diam(T) 
-        \leq 
-        \sqrt{2} \sigma_1 
-        \leq 
-        \sqrt{2} 
-        \frac{ \sigma_1^{n} }{ \det(\Jacobian\varphi) } 
-        \sigma_n
-        \leq 
-        \sqrt{2n^{n}} 
-        \frac{ \diam(T)^{n} }{ n! \vol(T) } 
-        \sigma_n
-        .
-    \]
-    The desired result is thus evident. 
-\end{proof}
-
-\begin{lemma}\label{lemma:volumecomparison}
-    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \begin{align*}
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        &\leq 
-        \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-        \cdot 
-        \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        = 
-        \kappa(T_1) \kappa(T_2)
-        ,
-        \\
-        \diam(T_1)
-        &\leq 
-        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        \diam(F)
-        = 
-        \kappa(T_1)
-        \diam(F)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        \leq 
-        \sqrt{2n^{n+1}} 
-        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        =  
-        \sqrt{2n^{n+1}} 
-        \frac{ \kappa(T_1) }{ \kappa(T_2) }
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
-    We estimate 
-    % TODO: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-    % TODO: clarify the following inequalities
-    \begin{align*}
-        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
-        \\
-        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        .
-    \end{align*}
-    The first estimate follows. 
-    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-    \begin{align*}
-        \diam(F)
-        \geq 
-        h
-        =
-        n!
-        \frac{ \vol(T_1) }{ \vol(F') }
-        \geq 
-        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
-        \cdot 
-        \diam(T_1)
-        .
-    \end{align*}
-    That shows the second estimate. 
-    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        &
-        \leq 
-        \sqrt{n} 
-        \cdot 
-        \diam(T_1)
-        \sqrt{2n^{n}} 
-        \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } 
-        \diam(T_2)^{-1}
-        \\&
-        \leq 
-        \sqrt{n} 
-        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        \diam(F)
-        \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        \diam(F)^{-1}
-        \leq 
-        \sqrt{2n^{n+1}}
-        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        .
-    \end{align*}
-    All the desired results thus follow. 
-    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
-    % \begin{align*}
-    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
-    %     \leq 
-    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-    %     \cdot 
-    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-    %     .
-    % \end{align*}
-\end{proof}
 
@@
 \end{remark}
+
+\begin{lemma}\label{lemma:affinetransform}
+    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
+    \begin{align*}
+        \| \Jacobian \varphi \|
+        \leq 
+        \sqrt{n} \cdot \diam(T)
+        ,
+        \qquad 
+        \| \Jacobian \varphi^{-1} \|
+        \leq 
+        \sqrt{2n} 
+        % \frac{ n! \vol(T) } { \diam(T)^{n} }
+        \kappa(T)^{\frac 1 n}
+        \diam(T)^{-1}
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    We easily verify the first inequality.
+To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
+    The Jacobian determinant is the product of these singular values. 
+    Thus, $\sigma_1/\sigma_n \leq \sigma_1 / \sqrt[n]{ \det(\Jacobian\varphi) }$ and 
+    \[
+        \diam(T) 
+        \leq 
+        \sqrt{2} \sigma_1 
+        \leq 
+        \sqrt{2} 
+        \frac{ \sigma_1 }{ \sqrt[n]{ \det(\Jacobian\varphi) } } 
+        \sigma_n
+        \leq 
+        \sqrt{2n} 
+        \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)^{\frac 1 n}
+        \sigma_n
+        .
+    \]
+    The desired result is thus evident. 
+\end{proof}
+
+\begin{lemma}\label{lemma:volumecomparison}
+    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
+    \begin{align*}
+        \frac{ \vol(T_1) }{ \vol(T_2) }
+        \leq 
+        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
+        % \cdot 
+        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
+        % = 
+        \kappa(T_1) \kappa(T_2)
+        ,
+        \qquad 
+        \diam(T_1)
+        \leq 
+        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        % \diam(F)
+        % = 
+        \kappa(T_1)
+        \diam(F)
+        .
+    \end{align*}
+    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
+    \begin{align*}
+        \| \Jacobian \Xi \|
+        \leq 
+        \sqrt{2n^{n+1}} 
+        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
+        =  
+        \sqrt{2n^{n+1}} 
+        \frac{ \kappa(T_1) }{ \kappa(T_2) }
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
+    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
+    We estimate 
+    % TODO: I am not 100% sure what that means.
+Is really the heights of F?
+I imagine this is rather the heights of simplices T_1 and T_2, isn't?
+Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
+(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
+    % TODO: clarify the first of the following inequalities
+    \begin{align*}
+        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
+        \\
+        h_2 &= n! \frac{\vol(T_2)}{\vol(F)} \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
+        .
+    \end{align*}
+    The first estimate follows. 
+    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
+    \begin{align*}
+        \diam(F)
+        \geq 
+        h
+        =
+        n!
+        \frac{ \vol(T_1) }{ \vol(F') }
+        \geq 
+        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
+        \cdot 
+        \diam(T_1)
+        .
+    \end{align*}
+    That shows the second estimate. 
+    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
+    \begin{align*}
+        \| \Jacobian \Xi \|
+        &
+        \leq 
+        \sqrt{n} 
+        \cdot 
+        \diam(T_1)
+        %
+        % \sqrt{2n} \left( \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } \right)^{\frac 1 n}
+        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
+        \diam(T_2)^{-1}
+        \\&
+        \leq 
+        \sqrt{n} 
+        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        \diam(F)
+        % \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
+        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
+        \diam(F)^{-1}
+        \leq 
+        n\sqrt{2}
+        \kappa(T_1)
+        \kappa(T_2)^{\frac 1 n}
+        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        % \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
+        .
+    \end{align*}
+    All the desired results thus follow. % TODO: improve these results 
+    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
+    % \begin{align*}
+    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
+    %     \leq 
+    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
+    %     \cdot 
+    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
+    %     .
+    % \end{align*}
+\end{proof}
 
@@
 \begin{example}
-    The standard triangulation of the $n$-dimensional cube, the Kuhn triangulation, is shellable. 
-    % https://scholar.google.de/scholar?hl=de&as_sdt=0%2C5&q=kuhn+triangulation+shelling&btnG=
+    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.~\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
 \end{example}
@@
     The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
-    and is thus shellable~\cite{ziegler2012lectures}. % TODO: cite exactly 
+    and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
 \end{proof}
@@
 Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the canonical basis dual to the standard unit vectors.
+We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
 This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
@@
 
-We notice that the standard scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
+We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
 which induces a scalar product on $\Alt^{k}(\bbR^{n})$.

### 2024-07-04 main.tex
corrections

--- 2024-07-04 main.tex
@@
 \end{align*} 
-Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
+Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
 \begin{align*}
@@
     \leq 
-    C_{\varnothing,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
+    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^p(\Omega)},
     \quad 
@@
 
-In this section we address the stepwise computable estimate of Poincar\'e constants of triangulated domains.
-As a preparatory step, we survey variations of the Poincar\'e inequality over convex domains.
-These results, the exposition of which we believe to be of value on its own, will serve as a building block in constructing inequalities over local patches and then triangulated domains.
+In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
+As a preparatory step, we survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities over convex domains.
+This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
 \\
@@
 \end{align}
-Under the condition that $\Omega$ is connected, this is equivalent to  
+Since $\Omega$ is connected, this is equivalent to  
 \begin{align}
@@
 We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, % TODO: cite AAAA
 we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
+if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
 for all $u \in W^{1,p}(\Omega)$
@@
     \leq 
-    C_{\varnothing,\Omega,p} 
+    C_{{\rm P},\Omega,p} 
     \| \nabla u \|_{L^{p}(\Omega)}
@@
 \end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
 Towards a converse inequality, 
@@
 In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+We conclude that taking the average is a projection within Lebegue spaces with unit norm. 
 It follows that 
@@
 \begin{align*}
-    C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}.
-\end{align*}
-In the special case $p=2$, this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$,
-and therefore even $C_{\varnothing,\Omega,2} = C_{{\rm PF},\Omega,2}$. 
+    C_{{\rm P},\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}.
+\end{align*}
+In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$,
+and therefore even $C_{{\rm P},\Omega,2} = C_{{\rm PF},\Omega,2}$. 
 This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
 and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite{stern2015banach} implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that % TODO: cite specific results of Ari 
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
 \begin{align*}
@@
 We thus conclude 
-\begin{align*}
-    C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}.
-\end{align*}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
+\begin{align}\label{math:p_vs_pf}
+    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}.
+\end{align}
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor of at most two that only depends on $1 \leq p \leq \infty$.
 \\
@@
 \end{align*}
-Clearly, 
+If there is a Poincar\'e--Friedrichs constant, then by definition
 \begin{align*}
@@
 \begin{align*}
-    C_{{\rm PF},\Omega,p} 
-    \leq 
-    \argmin\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \min\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
+    \leq 
+    \min\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
     \frac{ \| \overline\Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
@@
 \end{align*}
-A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
+A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
+\begin{align*}
+    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
     \quad 
@@
 \end{align*}
-Its operator norm is just the smallest Poincar\'e constant $C_{\varnothing,\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient and later for the curl and divergence operators.
+Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
+\\
+
+In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
 This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-The potential reconstruction is the natural approach towards the topic when addressing the curl and divergence operators.
+We will extend the potential reconstruction when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
 
@@
     By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not clear a priori whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
+    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
     % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
@@
 These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite{chua2006estimates}:
+Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem 1.1]{chua2006estimates}:
 \begin{align}\label{math:chuawheeden}
@@
 \end{align}
-These Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
-
-We know optimal Poincar\'e--Friedrichs constants over convex domains~\cite{ferone2012remark,esposito2013poincare}: 
+As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
+
+We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
 when $1 < p < \infty$, one can show that 
@@
 \end{align}
-Note that the last inequalities imply, again when $1 \leq p < \infty$, the Poincar\'e inequalities
+Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
 \begin{align}\label{math:esposito:poincare}
@@
 \end{align}
+In the limit case $p=1$, the optimal Poincar\'e constant $1/2$ also coincides with the optimal Poincar\'e--Friedrichs constant, as can verified with some one-dimensional example.
+% TODO Acosta-Duran %\footnote{In the case $p=1$, the optimal Poincar\'e constant $1/2$ is an upper bound for the optimal Poincar\'e--Friedrichs constant.
+When $\Omega = (0,1)$, then $u(x) = x - 0.5$ is }
 Finally, since convex domains are Lipschitz domains: 
@@
 \begin{remark}
-    The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
+    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
+    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
     Let us compare the different estimates for the Poincar\'e inequality. 
@@
     It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    In the limit as $p$ goes to $1$, \eqref{math:esposito:poincare} recovers \eqref{math:acostaduran}. 
-    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
+    % TODO: 
+    In the limit as $p$ goes to $1$, the factor $C_{\rm{EFNT},p}$ converges to $1/2$,
+    which is the optimal Poincar\'e--Friedrichs constant and also the factor in Inequality \eqref{math:acostaduran}. 
+    In the limit as $p$ goes to infinity, the factor $C_{\rm{EFNT},p}$ converges to $1/2$, 
+    which implies the Poincar\'e inequality 
     \begin{align*}
@@
     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
-    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
-    Notably, it is much less clear whether \eqref{math:esposito:pf} implies a limit case Poincar\'e--Friedrichs inequality for Lipschitz functions. 
-%     Taking the \emph{informal} limit also suggest the inequality 
-%     \begin{align*}
-%         \min\limits_{ c \in \bbR }
-%         \| u - c \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \frac{d}{2}
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         u \in W^{1,\infty}(\Omega)
-%         ,
-%     \end{align*}
-%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
 \end{remark}
@@
 \begin{remark}
-    The optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
     but individual convex domains may allow for better constants.
-    We refer to \cite{matculevich2016explicit} for an overview. 
-    For example, triangles allow the reduction of the constant by 20\%.
+    We refer to \cite{matculevich2016explicit} for an overview;
+    for example, triangles allow the reduction of the constant by 20\%.
 \end{remark}
-
-% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
-% d/2 in the case $p = 1$ over convex domains
-
-% https://academic.oup.com/plms/article/93/1/197/1462187
-% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?
 

### 2024-07-04 main.tex
Update on Overleaf.

@@
 \end{align}
-In the limit case $p=1$, the optimal Poincar\'e constant $1/2$ also coincides with the optimal Poincar\'e--Friedrichs constant, as can verified with some one-dimensional example.
-% TODO Acosta-Duran %\footnote{In the case $p=1$, the optimal Poincar\'e constant $1/2$ is an upper bound for the optimal Poincar\'e--Friedrichs constant.
-When $\Omega = (0,1)$, then $u(x) = x - 0.5$ is }
-Finally, since convex domains are Lipschitz domains: 
+In the limit case $p=1$, the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
+\begin{align}\label{math:l1estimate}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{1}(\Omega)}
+    \leq 
+    \frac{ \diam(\Omega) }{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    u \in W^{1,1}(\Omega)
+    .
+\end{align}
+In the limit case $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
 \begin{align}\label{math:lipschitzestimate}
@@
 \end{align}
+
+\begin{example}
+    Let $\Omega = (-1,1)$ and consider the family of odd function $u_{t} : \Omega \rightarrow \bbR$ for $t \in (0,1)$ 
+    that satisfy $u_{t}(0)=0$, $u_{t}(t) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
+    Obviously,
+    \begin{align}
+        \| u_{t} \|_{L^{1}(\Omega)} = 2 - t,
+        \qquad 
+        \| u'_{t} \|_{L^{1}(\Omega)} = 2t \frac{2}{2t} = 2.
+        ,
+    \end{align}
+    and $\Omega$ has diameter $2$. As $u_t$ has average zero, this example shows that \eqref{math:acostaduran} is optimal. 
+    At the same time, for any constant $c \in \bbR$ we have $\| u_t - c \|_{L^1(\Omega)} = \| u_t + c \|_{L^1(\Omega)}$.
+    Since norms are convex, it follows that $u_t$ is the potential with minimal $L^1$ norm. 
+\end{example}
 

### 2024-07-05 draft.tex
Update on Overleaf.

@@
 \end{document}
+
+For jede Matrix $M \in \mathbb R^{n \times n}$ schreiben wir die Reihen als $r_1, r_2, \dots, r_n \in \bbR^{n}$.
+Die maximale Euklidische Norm der Reihenvektoren
+\begin{align*}
+    \| M \|_{\star} := \max\limits_{1 \leq i \leq n} \| r_i \|_{2}
+\end{align*}
+defininiert eine Norm auf den $n \times n$ Matrizen.
+
+I am looking for the smallest constant $C > 0$ such that 
+\begin{align*}
+    \| M \|_{2} \leq C \| M \|_{\star}.
+\end{align*}
+Es ist bekannt dass die Frobenius norm eine obere Schranke ist:
+\begin{align*}
+    \| M \|_{2} = \sigma_{1}(M) \leq \sum_{i=1}^{n} \sigma_{i}(M) = \| M \|_{F}
+\end{align*}
+wo $\sigma_{1}(M) \geq \dots \geq \sigma_{n}(M)$ die Singularwerte darstellen. Folglich,
+\begin{align*}
+    \| M \|_{F} = \sqrt{\sum_{i=1}^{n} \| r_i \|_{2} } \leq \sqrt{n} \max\limits_{1 \leq i \leq n} \| r_i \|_{2}
+\end{align*}
+Kann die Konstante $\sqrt{n}$ noch verbessert werden?

### 2024-07-07 main.tex
revision of literature, introduction (partially)

@@
 
-\title{Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations}
 \author{
@@
     This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
-    We express all our main results in the calculus of differential forms and treat the curl and divergence operator as its particular instances. 
+    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
 \end{abstract}
@@
 
+% TODO: MV : this first paragraph is a better abstract 
 We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
 The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
-In particular, such operator norm bounds yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
-
+In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
+
+% TODO : MV : remove 'For example' 
 For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator whose $\bfL^2$ norm is bounded in terms of the source field. This is expressed via the Poincar\'e--Friedrichs inequality 
+we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
+This is expressed via the Poincar\'e--Friedrichs inequality
 \begin{align*}
@@
 having computable upper bounds for such domains is an important stepping stone towards the more general case. 
-For example, local patches around a simplex within a larger 2D or 3D triangulation are shellable.
+For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
 \\
@@
 We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
+% TODO: MV : Be more didactical: write following as the existence of a potential. 
+Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
 we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
-\begin{align*}
+\begin{align}\label{math:intro:poincarefriedrichs:grad}
     \min\limits_{c\in\bbR}
@@
     \quad 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
+    u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
+    .\tag{PF} % TODO Decide later to keep the tags
+\end{align}
 Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
@@
 Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
-\begin{align*}
+\begin{align}\label{math:intro:poincare:grad}
     \| u - u_{\Omega} \|_{L^{p}(\Omega)}
@@
     u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
+    , \tag{P} % TODO: tag poincare inequality 
+\end{align}
 where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
 
@@
 % The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ that depends only on the domain diameter is known when the domain is convex.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+Notably, the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ that depend only on the domain diameter are known when the domain is convex.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
 When the domain is not convex but star-shaped with respect to a ball,
 then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008finite,ern2021finite}. 
-An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain,
-implying Poincar\'e inequalities on star-shaped open sets~\cite{hurri1988poincare}.
+An open set star-shaped with respect to a internal point satisfies Poincar\'e inequalities~\cite[Theorem~3.1]{hurri1988poincare}.
 
@@
 \end{align*}
-The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
+The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
 In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
@@
 \end{align*}
+
 Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
@@
 This sharply contrasts to the study of the gradient operator. 
-
-The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
+%
+% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
 We can access some estimates from the literature in the formalism of exterior calculus. 
@@
 follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces, though these estimates have not been made explicit in the literature yet.
-\\
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local patches within triangulated domains. 
-Clearly, not all local patches describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local patches in triangulations are often star-shaped with respect to a ball. 
+as mappings between Lebesgue spaces. 
+We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation},
+but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+\\
+% DONE: cite Guzman and Salgado in a reasonable manner
+
+The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
+Clearly, not all local stars describe convex subdomains. 
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball. 
 Over patches around interior subsimplices, the size of the interior ball only depends on the shape regularity of the triangulation. 
@@
 and that is inevitable when the domain has an unfortunate geometry. 
-Some illustrative limit cases include the slit domain and the crossed bricks domain~\cite{licht2019smoothed},
-for which some finite element patches are not star-shaped with respect to any ball.
+Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfuhrt and veeser
+which contain finite element patches are not star-shaped with respect to any ball.
 
@@
 % 
-The literature~\cite{vohralik2005discrete,ern2021finite} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
+The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
 starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted.
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest.
+That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here.
 The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
@@
 
-While we know Poincar\'e--Friedrichs constants over local patches for scalar-valued Sobolev spaces, 
+While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
 we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
@@
 which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local patches.
+However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
 We are not aware of any estimates for the curl operator, even in the Hilbert space situation. 
@@
 
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we follow closely the philosophy of the aforementioned sequential approach.
+Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
 Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
@@
 
-% Exterior calculus 
+% Exterior calculus % TODO: MV recommends moving this down to finish the current line of thoughts 
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
@@
 However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-
+% 
 To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
@@
 The remainder of this manuscript is structured as follows.
-We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants over triangulated domains in Section~\ref{section:poincare}.
+We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants for the gradient over convex and triangulated domains in Section~\ref{section:poincare}.
 We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
@@
 We construct an important geometric reflection operator in Section~\ref{section:extension}
-and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
 
@@
 
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these the \emph{vertices} of the simplex $T$. 
+A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
+We call these points the \emph{vertices} of the simplex $T$.
 If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
@@
 % The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{We warn the reader that simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes.}
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
 We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
@@
     % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of topology~\cite{spanier1966homology}. 
+    However, none of these infinite families are infinite simplicial complexes in the sense of topology~\cite{spanier1995algebraic}. 
 \end{remark}
@@
 
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincare}
+\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincare}
 
@@
 We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+% TODO: MV move this part to the introduction, as an alternative the first few paragraphs
 
@@
 \end{align*}
-Here, we have used Jensen's inequality. 
+Here, we have used H\"older's or Jensen's inequality. 
 In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
 We conclude that taking the average is a projection within Lebegue spaces with unit norm. 
-It follows that 
+The triangle inequality now shows that 
 \begin{align*}
@@
 \end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$,
-and therefore even $C_{{\rm P},\Omega,2} = C_{{\rm PF},\Omega,2}$. 
+In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
+Hence $C_{{\rm P},\Omega,2} = C_{{\rm PF},\Omega,2}$.
 This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
@@
 \end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor of at most two that only depends on $1 \leq p \leq \infty$.
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
 \\
@@
 \begin{align*}
-    \min\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
     \frac{ \| \Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
     \leq 
-    \min\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
     \frac{ \| \overline\Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
@@
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend the potential reconstruction when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
 
@@
         \frac{ 1 }{ \sqrt[p]{p-1} }
-        =
+        \leq 
         4^{-\frac 1 p}
@@
     \end{align*}
-    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+    It follows that \eqref{math:esposito:poincare} is a possibly tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
     % TODO: 
@@
     \end{align*}
-    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
+    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % TODO: cite 
+    % TODO: review this entire result 
 \end{remark}
@@
 
+% TODO: as for instance recently used in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
+
 Towards this goal, we introduce quantitative measures for the geometric quality of triangulations. 
@@
 \end{align}
+% 
+% 
+% TODO: Note that \kappa(T)=1 whenever T is a line segment, an isosceles right-angled triangle, or their generalizations to higher dimensions (multiples of a reference simplex).
+\kappa(T) is slightly bigger than one for equilateral simplices and blows up with distortion.
+% 
+%
+
 % TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
@@
         \leq 
-        \sqrt{n} \cdot \diam(T)
+        \sqrt{n} \cdot \diam(T) % TODO: can this improved?
         ,
@@
     \]
-    The desired result is thus evident. 
+    The desired result is thus evident. % TODO: this is incorrect. Find a better explanation. 
 \end{proof}
@@
 We collect important examples of shellable triangulations.
-Our main interest are local patches or stars within triangulations.
+Our main interest are local stars or stars within triangulations.
 
@@
     We want to estimate norms. 
-    Lemma~\ref{lemma:} gives 
+    Lemma~\ref{lemma:todo} gives 
     \begin{align*}
@@
     \end{align*}
-    see \cite{savo} for $n \geq 3$, 
+    see \cite{guerini2004eigenvalue} for $n \geq 3$, 
     \begin{align*}

### 2024-07-12 main.tex
Sections 1-3

@@
 
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations}
 \author{
@@
 
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+
 \begin{document}
@@
 \begin{abstract}
-    We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
-    The main application that we envision are computable estimates over finite element patches. 
+    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulatons.
+This class of triangulations includes local stars in dimension two and three.
+    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
+    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
+    % 
+    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
+    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
+    %     The main application that we envision are computable estimates over finite element patches. 
     %
@@
 
-% TODO: MV : this first paragraph is a better abstract 
-We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
-The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
-In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
-
-% TODO : MV : remove 'For example' 
-For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
+% DONE \todo{Reformulate the first paragraph. } % 
+Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
+The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
+which quantify the fundamental stability features of a variety of partial differential equations.
+% which serve a variety of purposes:
+% these constants quantify the fundamental stability properties of partial differential equations, imply lower bounds for the spectra of vector and Hodge Laplacians, and they . 
+However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
+% We study potential operators in the special class of domains with shellable triangulations,
+% which include local stars in 2D and 3D. 
+% We bound the operator norms of our operators in terms of the shape regularity of the triangulation.
+
+% We contribute to the construction of potential operators in vector analysis and exterior calculus over triangulated domains. 
+% We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
+% The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
+% In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
+
+% DONE : MV : remove 'For example' 
+We illustrate the subject of our discussion with the curl operator. 
+% One example application concerns the curl operator. 
+If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
 we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$. 
-This is expressed via the Poincar\'e--Friedrichs inequality
+This boundedness is expressed via the Poincar\'e--Friedrichs inequality 
 \begin{align*}
@@
 % We accomplish our results for a special class of triangulations, so-called shellable triangulations.
-We accomplish this task in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
+% We accomplish this task in 
+We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
 Even though only contractible domains can ever admit a shellable triangulation, 
@@
 For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
+Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
 \\
@@
 We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-% TODO: MV : Be more didactical: write following as the existence of a potential. 
+
+% DONE: MV : Be more didactical: write following as the existence of a potential. 
 Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
+we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
+for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:intro:inequalitypf:gradient}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+The different scalar potentials only differ by a constant. 
+Therefore, %when the domain is connected, then 
+this inequality is equivalent to the following statement: 
 \begin{align}\label{math:intro:poincarefriedrichs:grad}
@@
     \quad 
+    \forall
     u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
-    .\tag{PF} % TODO Decide later to keep the tags
+    .\tag{PF} 
 \end{align}
+% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
+% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
+% \begin{align}\label{math:intro:poincarefriedrichs:grad}
+%     \min\limits_{c\in\bbR}
+%     \| u - c \|_{L^{p}(\Omega)}
+%     \leq 
+%     C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
+%     \quad 
+%     u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
+%     .\tag{PF} 
+% \end{align}
 Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
@@
     \quad 
+    \forall 
     \bff \in \nabla W^{1,p}(\Omega)
@@
     \quad 
+    \forall 
     u \in W^{1,p}(\Omega)
-    , \tag{P} % TODO: tag poincare inequality 
+    , \tag{P} % DONE: tag poincare inequality 
 \end{align}
@@
 % The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ that depend only on the domain diameter are known when the domain is convex.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
 When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008finite,ern2021finite}. 
+then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
 An open set star-shaped with respect to a internal point satisfies Poincar\'e inequalities~\cite[Theorem~3.1]{hurri1988poincare}.
@@
 Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain linear combinations of distributional partial derivatives are integrable, 
+This only requires that certain sums of distributional partial derivatives are integrable, 
 and hence these spaces are not classical Sobolev spaces of vector fields. 
@@
 Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball. 
-Over patches around interior subsimplices, the size of the interior ball only depends on the shape regularity of the triangulation. 
-However, that interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape regularity. 
-Estimates that rely on this geometric condition thus deteriorate when the aforementioned ball has small radius,
-and that is inevitable when the domain has an unfortunate geometry. 
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfuhrt and veeser
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
+which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators. 
+However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
+This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfuhrt and veeser
 which contain finite element patches are not star-shaped with respect to any ball.
@@
 We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-\\
 
@@
 We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-
-% Exterior calculus % TODO: MV recommends moving this down to finish the current line of thoughts 
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\ % TODO hu2019structure
+\\
 
@@
 Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-% TODO: cite VVVV
+% DONT: cite VVVV
 While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
@@
 
-% TODO: cite VVVV
-In the Hilbert space case, $p=2$, the work of Guerini and Savo shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+% DONE: cite VVVV
+In the Hilbert space case, $p=2$, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
 By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
@@
 
-In addition to that, we need to find potentials over a simplex subject to partial boundary conditions. 
+In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
 Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
@@
 We achieve this by constructing an auxiliary problem subject to full boundary conditions.
+\\
+
+% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
+Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
+Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
+Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
+The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
+%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
+For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
 \\
@@
 The remainder of this manuscript is structured as follows.
-We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants for the gradient over convex and triangulated domains in Section~\ref{section:poincare}.
+We review basic notions of triangulations in Section~\ref{section:triangulations}.
+We review Poincar\'e constants for the gradient over convex domains in~\ref{section:poincare}.
+We develop computable upper bounds for Poincar\'e--Friedrichs constants for the gradient over triangulated domains in Section~\ref{section:gradient}.
 We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
@@
 % (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-% The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that complex.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
 We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
@@
     % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of topology~\cite{spanier1995algebraic}. 
+    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{spanier1995algebraic}. 
 \end{remark}
@@
 We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
+The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
 Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
@@
 % \begin{remark}
-    Our use of the term \textit{face} as is common in the finite element literature
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra. %
+    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
+    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.~\cite{schrijver1998theory}
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra.~\cite{ziegler2012lectures}
 % \end{remark}
@@
 We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
-Clearly, strongly connected in $\calT$ is an equivalence relation. A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
+Clearly, strongly connected in $\calT$ is an equivalence relation among simplices. 
+A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
 and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component.
 
-\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
-As a preparatory step, we survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities over convex domains.
+\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+
+We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
+We take the opportunity to discuss convex domains as a preparatory special case.
 This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
@@
 
-% TODO: MV move this part to the introduction, as an alternative the first few paragraphs
+% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
 
@@
     \quad 
+    \forall 
     u \in W^{1,p}(\Omega)
@@
 We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, % TODO: cite AAAA
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, % TODO: cite AAAA somebody, such as Alexandre
 we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
 if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-for all $u \in W^{1,p}(\Omega)$
+% for all $u \in W^{1,p}(\Omega)$
 \begin{align}
@@
     \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall u \in W^{1,p}(\Omega)
     ,
@@
     \quad 
+    \forall
     u \in L^{p}(\Omega)
@@
     \quad 
+    \forall 
     u \in L^p(\Omega)
@@
 
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
 see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
@@
     \quad 
+    \forall 
     u \in W^{1,1}(\Omega)
@@
     \quad 
+    \forall 
     u \in W^{1,2}(\Omega)
@@
 These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem 1.1]{chua2006estimates}:
+Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
 \begin{align}\label{math:chuawheeden}
@@
 \end{align}
-where 
+where we use an upper bound by Chua and Wheeden:
 \begin{align}
@@
 \end{align}
+Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
 As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
@@
     \leq 
-    C_{\rm{EFNT},p}
+    C_{{\rm EFNT},p}
     \diam(\Omega)
@@
 \end{align}
-where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
+where $C_{{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
 \begin{align}
-    C_{\rm{EFNT},p}
+    C_{{\rm EFNT},p}
     :=
@@
     \leq 
-    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
+    2^{|1-\frac 2 p|}C_{{\rm EFNT},p}
     \diam(\Omega)
@@
 \end{align}
-In the limit case $p=1$, the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
+When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
 \begin{align}\label{math:l1estimate}
@@
 \end{align}
-In the limit case $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
+When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
 \begin{align}\label{math:lipschitzestimate}
@@
     \quad 
+    \forall 
     u \in W^{1,\infty}(\Omega)
@@
 
-\begin{example}
-    Let $\Omega = (-1,1)$ and consider the family of odd function $u_{t} : \Omega \rightarrow \bbR$ for $t \in (0,1)$ 
-    that satisfy $u_{t}(0)=0$, $u_{t}(t) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
-    Obviously,
-    \begin{align}
-        \| u_{t} \|_{L^{1}(\Omega)} = 2 - t,
-        \qquad 
-        \| u'_{t} \|_{L^{1}(\Omega)} = 2t \frac{2}{2t} = 2.
-        ,
-    \end{align}
-    and $\Omega$ has diameter $2$. As $u_t$ has average zero, this example shows that \eqref{math:acostaduran} is optimal. 
-    At the same time, for any constant $c \in \bbR$ we have $\| u_t - c \|_{L^1(\Omega)} = \| u_t + c \|_{L^1(\Omega)}$.
-    Since norms are convex, it follows that $u_t$ is the potential with minimal $L^1$ norm. 
-\end{example}
+% TODO: Keep ?
+% \begin{example}
+%     We explain why \eqref{math:l1estimate} is optimal. 
+%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
+%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
+%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
+%     and $\Omega$ has diameter $2$. 
+%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
+%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
+%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
+% \end{example}
 
@@
     Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
-    Let us compare the different estimates for the Poincar\'e inequality. 
+    Let us compare the estimate $C_{{\rm CW},p}$ for the Poincar\'e constant
+    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm EFNT},p}$. 
     In the case $2 \leq p$, 
@@
         2^{1-\frac 2 p}
-        C_{\rm{EFNT},p}
+        C_{{\rm EFNT},p}
         =
@@
         2^{\frac 2 p - 1}
-        C_{\rm{EFNT},p}
+        C_{{\rm EFNT},p}
         =
@@
     \end{align*}
-    It follows that \eqref{math:esposito:poincare} is a possibly tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    % TODO: 
-    In the limit as $p$ goes to $1$, the factor $C_{\rm{EFNT},p}$ converges to $1/2$,
-    which is the optimal Poincar\'e--Friedrichs constant and also the factor in Inequality \eqref{math:acostaduran}. 
-    In the limit as $p$ goes to infinity, the factor $C_{\rm{EFNT},p}$ converges to $1/2$, 
-    which implies the Poincar\'e inequality 
-    \begin{align*}
-        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-        \leq 
-        \diam(\Omega)
-        \| \nabla u \|_{L^{\infty}(\Omega)}
-        ,
-        \quad
-        u \in W^{1,\infty}(\Omega)
-        %
-    \end{align*}
-    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % TODO: cite 
-    % TODO: review this entire result 
+    It follows that \eqref{math:esposito:poincare} is generally tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
+    % DONT: insert the original inequality by chua and Wheeden
+    % DONE: chua wheeden upper bound is not optimal!
+    % DONE: Theorem 1.2 in Chua Wheeden 
+% TODO: Keep ?
+%     In the limit as $p$ goes to $1$, the factor $C_{{\rm EFNT},p}$ converges to $1/2$,
+%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
+%     \begin{align*}
+%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
+%         \leq 
+%         \frac{1}{2}
+%         \diam(\Omega)
+%         \| \nabla u \|_{L^{1}(\Omega)}
+%         ,
+%         \quad
+%         \forall 
+%         u \in W^{1,1}(\Omega)
+%         .
+%     \end{align*}
+%     In the limit as $p$ goes to infinity, the factor $C_{{\rm EFNT},p}$ converges to $1/2$, 
+%     which implies the Poincar\'e inequality 
+%     \begin{align*}
+%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
+%         \leq 
+%         \diam(\Omega)
+%         \| \nabla u \|_{L^{\infty}(\Omega)}
+%         ,
+%         \quad
+%         \forall 
+%         u \in W^{1,\infty}(\Omega)
+%         %
+%     \end{align*}
+%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % TODO: cite 
+%     % TODO: review this entire result 
 \end{remark}
+
+\todo{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
 
@@
 
-\subsection{Poincar\'e--Friedrichs inequalities over triangulated domains}
-
+\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
+
+In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. As a preparatory step, 
 Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
@@
 
+% TODO: INTRODuce a reference simplex 
+% TODO: DEFINE THE JACOBIAN
+
 \begin{lemma}\label{lemma:affinetransform}
@@
 
+% TODO: REMOVE THE \cdot 
 \begin{lemma}\label{lemma:volumecomparison}
@@
 \end{lemma}
+
+% TODO: REMOVE THE FACTORIAL?
+
 \begin{proof}
@@
     \end{align*}
-    All the desired results thus follow. % TODO: improve these results 
+    All the desired results thus follow. % TODO: improve these results, explain in more detail  
     % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
@@
 \begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
-    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
+    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
+    Let $U := T_1 \cup T_2$. 
+    Then 
     \begin{align*}
@@
         \leq 
-        2 C_{\rm{EFNT},p}
+        2 C_{{\rm EFNT},p}
         \max\left( 
@@
         \leq 
-        2 C_{\rm{EFNT},p}
+        2 C_{{\rm EFNT},p}
         \rho(\calT)^{\frac 1 p}
@@
 \end{lemma}
+\begin{remark}
+    The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
+\end{remark}
 \begin{proof}
-    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
+    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
     We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
-    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
+    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
     We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
@@
         \leq 
-        |\det(\Dif \varphi_1)|
+        |\det(\Dif \varphi_1^{-1})|
         \cdot \| \Dif \varphi_1 \|^{p}
@@
         +
-        |\det(\Dif \varphi_2)|
+        |\det(\Dif \varphi_2^{-1})|
         \cdot \| \Dif \varphi_2 \|^{p}
@@
     \end{align*}
-    There exists $\hat w \in W^{1,p}(U)$ such that $\nabla \hat w = \nabla \hat u$ and 
+    Notice that $\hat U$ has diameter $2$. 
+    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
     \begin{align*}
@@
         \leq 
-        2 C_{\rm{EFNT},p}
+        2 C_{{\rm EFNT},p}
         \| \nabla \hat u \|_{L^{p}(\hat U)}
@@
     \end{align*}
-    Next, setting $w = \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
+    Next, setting $w := \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
     \begin{align*}
@@
     \end{align*}
+    % TODO: that abbreviation is to close to the Jacobian / total derivative 
     Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
@@
         &\leq 
-        2 C_{\rm{EFNT},p}
+        2 C_{{\rm EFNT},p}
         \max\left( 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
@@
     and such that for all $T \in \calT$:
-    \begin{align*}
+    \begin{align*} % TODO: UNIFY NOTATION FOR THE CONSTANTS 
         % \color{red}
@@
         C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{\rm{EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
+        % 2 C_{{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
         \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
@@
         \rho(\calT)^{\frac{m-1}{p}}
-        % C_{\rm{EFNT},p} \diam(T_0)
+        % C_{{\rm EFNT},p} \diam(T_0)
         C_{{\rm{PF}},T_{0},p}
@@
  For each $F \in \calT$ of dimension $n-1$, 
- we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla u_F \|_{L^{p}(U_F)}$.
-
+ we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that 
+ \begin{align*}
+    \| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla u_F \|_{L^{p}(U_F)},
+ \end{align*}
+ where the computable constant $C$ is given by ... % TODO
  There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
@@
     \begin{align*}
-        \int_{\Omega} |u(x)|^{p} dx
+        \int_{\Omega} |u(x)|^{p} \diff x dx
         &\leq
@@
 
-\section{Shellable triangulations}\label{section:advancedtriangulations}
+\section{Shellable triangulations of manifolds}\label{section:advancedtriangulations}
 
@@
     then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the dimension exceeds $3$.
+    This demonstrates that patches around boundary simplices are not necessarily shellable when the dimension is larger than the three.
 \end{remark}
-
-\newpage
 
@@
 $\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-They are defined by 
+We define them 
+for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
 \begin{subequations}\label{eq_definition_piola}
@@
     \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
-    \phi^{\divergence}(\bfw) &= \left( \det(\Jacobian\phi) \Jacobian\phi^{-1} \bfw \right)  \circ \phi, \\
-    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
+    \phi^{\divergence}(\bfw) &= \left( \adj(\Jacobian\phi) \bfw \right)  \circ \phi, \\
+    \phi^{\rm b}(v) &= \left( \det(\Jacobian\phi) v \right)  \circ \phi,
 \end{align}
 \end{subequations}
-where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
 and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
@@
 
-\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
+\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
 
@@
 
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
     Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.

### 2024-07-14 main.tex
Section 4

@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulatons.
+    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations.
 This class of triangulations includes local stars in dimension two and three.
@@
     \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
-    \| \bfv \|_{\bfL^{p}(\Omega)}
+    \| \bfv \|_{L^{p}(\Omega)}
     \leq 
     C_{\curl,\Omega,p}
-    \| \bff \|_{\bfL^{p}(\Omega)}
+    \| \bff \|_{L^{p}(\Omega)}
     ,
@@
     \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
-    \| \bfv \|_{\bfL^{p}(\Omega)}
+    \| \bfv \|_{L^{p}(\Omega)}
     \leq 
@@
 \end{gather*}
+We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
 A crucial observation is the following.
@@
 In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebegue spaces with unit norm. 
+We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
 The triangle inequality now shows that 
@@
 
+% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
+
 \section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
@@
 after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
-\\
-
-% TODO: as for instance recently used in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
+The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
+\\
 
@@
 
+For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.
+
 We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
@@
 \end{align}
-% 
-% 
-% TODO: Note that \kappa(T)=1 whenever T is a line segment, an isosceles right-angled triangle, or their generalizations to higher dimensions (multiples of a reference simplex).
-\kappa(T) is slightly bigger than one for equilateral simplices and blows up with distortion.
-% 
-%
-
-% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
+
+\begin{remark}
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    In our convention, the reference simplex has unit shape measure.
+    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
+$\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
+
+% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
+    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
+    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
+    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
+    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
+    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
+\end{remark}
+
+% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
 Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
@@
 \begin{align}\label{math:reflectionmeasure}
-    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
+    \xi(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
+    \| \Jacobian \Xi_{S,T} \|
 \end{align}
+to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
 This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.
-
-% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
 
@@
 
-\begin{remark}
-    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-% TODO: INTRODuce a reference simplex 
-% TODO: DEFINE THE JACOBIAN
+% DONE: INTRODuce a reference simplex 
+% DONE: DEFINE THE JACOBIAN 
+\todo{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}
 
@@
         \leq 
-        \sqrt{n} \cdot \diam(T) % TODO: can this improved?
+        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
         ,
@@
         \leq 
-        \sqrt{2n} 
-        % \frac{ n! \vol(T) } { \diam(T)^{n} }
-        \kappa(T)^{\frac 1 n}
+        \Czwei{n} \cdot 
+        \kappa(T) 
         \diam(T)^{-1}
@@
     \end{align*}
+    Here, $\Ceins{n} \leq \sqrt{n}$ and $\Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} }$. 
 \end{lemma}
@@
     The Jacobian determinant is the product of these singular values. 
-    Thus, $\sigma_1/\sigma_n \leq \sigma_1 / \sqrt[n]{ \det(\Jacobian\varphi) }$ and 
-    \[
-        \diam(T) 
-        \leq 
-        \sqrt{2} \sigma_1 
-        \leq 
-        \sqrt{2} 
-        \frac{ \sigma_1 }{ \sqrt[n]{ \det(\Jacobian\varphi) } } 
-        \sigma_n
-        \leq 
-        \sqrt{2n} 
-        \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)^{\frac 1 n}
-        \sigma_n
-        .
-    \]
-    The desired result is thus evident. % TODO: this is incorrect. Find a better explanation. 
+%     By a result of Hong and Pan,
+%     \begin{align*}
+%         \frac{ \sigma_{n} }{ \sigma_{1} }
+%         \geq 
+%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
+%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
+%         \sigma_{1}^{-1}
+%         \geq 
+%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
+%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
+%         \sigma_{1}^{-1}
+%         .
+%     \end{align*}
+    By a result of Yu and Gu \cite{yisheng1997note},
+    \begin{align*}
+        \frac{ \sigma_{n} }{ \sigma_{1} }
+        &\geq 
+        \det(\Jacobian\varphi)
+        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
+        \sigma_{1}^{-1}
+%         \geq 
+%         (n-1)^{\frac{n-1}{2}}
+%         \det(\Jacobian\varphi)
+%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
+%         \frac{1}{\sqrt{n} \diam(T)}
+%         \\&
+%         \geq 
+%         \frac{1}{\sqrt{n}}
+%         (n-1)^{\frac{n-1}{2}}
+%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
+        \geq 
+        \sqrt{\frac{ (n-1)^{n-1} }{n} }
+        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
+        .
+    \end{align*}
+    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
+%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
+%     \[
+%         \diam(T) 
+%         \leq 
+%         \sqrt{2} \sigma_1 
+%         \leq 
+%         \sqrt{2} 
+%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
+%         \sigma_n
+%         \leq 
+%         \sqrt{2n^{n}} 
+%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
+%         \sigma_n
+%         .
+%     \]
+%     The desired result is thus evident. 
 \end{proof}
@@
     \begin{align*}
+        \diam(T_1)
+        \leq 
+        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        % \diam(F)
+        % = 
+        \kappa(T_1)
+        \diam(F)
+        ,
+        \qquad 
         \frac{ \vol(T_1) }{ \vol(T_2) }
@@
         \kappa(T_1) \kappa(T_2)
-        ,
-        \qquad 
-        \diam(T_1)
-        \leq 
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \diam(F)
-        % = 
-        \kappa(T_1)
-        \diam(F)
         .
@@
         \leq 
-        \sqrt{2n^{n+1}} 
-        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        =  
-        \sqrt{2n^{n+1}} 
+        \Cdrei{n}
         \frac{ \kappa(T_1) }{ \kappa(T_2) }
@@
     \end{align*}
+    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
 \end{lemma}
 
-% TODO: REMOVE THE FACTORIAL?
-
-\begin{proof}
-    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
-    We estimate 
-    % TODO: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-    % TODO: clarify the first of the following inequalities
-    \begin{align*}
-        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
-        \\
-        h_2 &= n! \frac{\vol(T_2)}{\vol(F)} \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        .
-    \end{align*}
-    The first estimate follows. 
-    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-    \begin{align*}
-        \diam(F)
-        \geq 
-        h
-        =
-        n!
-        \frac{ \vol(T_1) }{ \vol(F') }
-        \geq 
-        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
-        \cdot 
-        \diam(T_1)
-        .
-    \end{align*}
-    That shows the second estimate. 
-    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        &
-        \leq 
-        \sqrt{n} 
-        \cdot 
-        \diam(T_1)
-        %
-        % \sqrt{2n} \left( \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } \right)^{\frac 1 n}
-        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
-        \diam(T_2)^{-1}
-        \\&
-        \leq 
-        \sqrt{n} 
-        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        \diam(F)
-        % \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
-        \diam(F)^{-1}
-        \leq 
-        n\sqrt{2}
-        \kappa(T_1)
-        \kappa(T_2)^{\frac 1 n}
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
-        .
-    \end{align*}
-    All the desired results thus follow. % TODO: improve these results, explain in more detail  
 % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
@@
 % \end{align*}
+% DONE: REMOVE THE FACTORIAL?
+% DONE: I am not 100% sure what that means.
+Is really the heights of F?
+I imagine this is rather the heights of simplices T_1 and T_2, isn't?
+Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
+(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
+% DONE: clarify the first of the following inequalities
+
+%     \begin{align*}
+%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
+%     \end{align*}
+%     Thus we establish the first estimate:
+
+%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
+%     \begin{align*}
+%         \diam(F)
+%         \geq 
+%         h
+%         =
+%         n
+%         \frac{ \vol(T_1) }{ \vol(F') }
+%         \geq 
+%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
+%         \cdot 
+%         \diam(T_1)
+%         .
+%     \end{align*}
+%     That shows the second estimate.
+
+\begin{proof}
+    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
+    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
+    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
+    \begin{align*}
+        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
+    \end{align*}
+    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
+    \begin{align*}
+        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
+    \end{align*}
+    The first estimate follows. 
+    On the other hand, 
+    \begin{align*}
+        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
+        \\
+        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
+        .
+    \end{align*}
+    The second estimate follows. 
+    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\eqref{lemma:affinetransform} and the first estimate imply 
+    \begin{align*}
+        \| \Jacobian \Xi \|
+        &
+        \leq 
+        \Ceins{n}
+        \Czwei{n}
+        \kappa(T_2)
+        \diam(T_1)
+        \diam(T_2)^{-1}
+        \\&
+        \leq 
+        \Ceins{n}
+        \Czwei{n}
+        \kappa(T_2)
+        \kappa(T_1) 
+        \diam(F)
+        \diam(T_2)^{-1}
+        \leq 
+        \Ceins{n}
+        \Czwei{n}
+        \kappa(T_2)
+        \kappa(T_1) 
+        .
+    \end{align*}
+    All the desired results thus follow.
 \end{proof}
@@
     Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
-    Let $U := T_1 \cup T_2$. 
+    Write $U := T_1 \cup T_2$. 
     Then 
@@
 \end{lemma}
-\begin{remark}
-    The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
-\end{remark}
+% \begin{remark}
+%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
+% \end{remark}
 \begin{proof}
@@
         \leq 
-        |\det(\Dif \varphi_1^{-1})|
-        \cdot \| \Dif \varphi_1 \|^{p}
+        |\det(\Jacobian \varphi_1^{-1})|
+        \cdot \| \Jacobian \varphi_1 \|^{p}
         \cdot 
@@
         +
-        |\det(\Dif \varphi_2^{-1})|
-        \cdot \| \Dif \varphi_2 \|^{p}
+        |\det(\Jacobian \varphi_2^{-1})|
+        \cdot \| \Jacobian \varphi_2 \|^{p}
         \cdot 
@@
         \max\left( 
-            |\det(\Dif \varphi_1)|^{-1} \cdot \| \Dif \varphi_1 \|^{p}
+            |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
             ,
-            |\det(\Dif \varphi_2)|^{-1} \cdot \| \Dif \varphi_2 \|^{p}
+            |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
         \right)
@@
         \max\left( 
-            |\det(\Dif \varphi_1)|^{-\frac 1 p} \cdot \| \Dif \varphi_1 \|
+            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \cdot \| \Jacobian \varphi_1 \|
             ,
-            |\det(\Dif \varphi_2)|^{-\frac 1 p} \cdot \| \Dif \varphi_2 \|
+            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \cdot \| \Jacobian \varphi_2 \|
         \right)
@@
         \max\left( 
-            |\det(\Dif \varphi_1)|
+            |\det(\Jacobian \varphi_1)|
             ,
-            |\det(\Dif \varphi_2)|
+            |\det(\Jacobian \varphi_2)|
         \right)^{\frac 1 p}
@@
     \end{align*}
-    % TODO: that abbreviation is to close to the Jacobian / total derivative 
+    % DONE: that abbreviation is to close to the Jacobian / total derivative 
     Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
@@
         \max\left( 
-            |\det(\Dif \varphi_1)|
+            |\det(\Jacobian \varphi_1)|
             ,
-            |\det(\Dif \varphi_2)|
+            |\det(\Jacobian \varphi_2)|
         \right)^{\frac 1 p}
         \max\left( 
-            |\det(\Dif \varphi_1)|^{-\frac 1 p} 
+            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} 
             ,
-            |\det(\Dif \varphi_2)|^{-\frac 1 p} 
+            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} 
         \right)
@@
         \max\left( 
-            |\det(\Dif \varphi_1)|
+            |\det(\Jacobian \varphi_1)|
             ,
-            |\det(\Dif \varphi_2)|
+            |\det(\Jacobian \varphi_2)|
         \right)^{\frac 1 p}
         \min\left( 
-            |\det(\Dif \varphi_1)|
+            |\det(\Jacobian \varphi_1)|
             ,
-            |\det(\Dif \varphi_2)| 
+            |\det(\Jacobian \varphi_2)| 
         \right)^{-\frac 1 p} 
@@
         \max\left( 
-            \frac{ |\det(\Dif \varphi_1)| }{ |\det(\Dif \varphi_2)| }
+            \frac{ |\det(\Jacobian \varphi_1)| }{ |\det(\Jacobian \varphi_2)| }
             ,
-            \frac{ |\det(\Dif \varphi_2)| }{ |\det(\Dif \varphi_1)| }
+            \frac{ |\det(\Jacobian \varphi_2)| }{ |\det(\Jacobian \varphi_1)| }
         \right)^{\frac 1 p}
@@
  \end{align*}
- where the computable constant $C$ is given by ... % TODO
+ where the computable constant $C_{{\rm{PF}},U_F,p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
+ We start with the simplex $T_{0}$. 
  There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
@@
 
+ \todo{MLW, MV: add a figure here to illustrate how the domain is exhausted.}
+
+ We use a recursive argument. 
  Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
  such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
- Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. 
+ This is already satisfied for $m=1$.
+ Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
  By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
@@
  \begin{gather*}
-    \| u'_{F_m} \|_{L^{p}(T_m)}
+    \| w'_{F_m} \|_{L^{p}(T_m)}
     \leq 
@@
     \| c_{m} \|_{L^{p}(T_m)}
-    \leq 
+    = 
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
@@
  \end{align*}
- We summarize the two integrals of $u_{F_m}$. 
+ We sum the two integrals of $u_{F_m}$. 
  % 
@@
  \end{align*}
- We use Definition~\eqref{math:moremeasures} to prove the desired inequality.
+ Taking into account Definition~\eqref{math:moremeasures}, we obtain the desired inequality.
 %  \begin{align*}
@@
 
-We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains,
+We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains. 
 While the underlying idea remains the same, the construction of the potential is slightly different. 
@@
         C_{{\rm PF},T,p} 
-        \| \nabla w \|_{\bfL^{p}(T)} % TODO: bold face or no boldface? No bold face 
+        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
         .
@@
         \vol(F)^\frac{1}{p}
-        \leq 
+        =
         \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
@@
 
+    We use a recursive argument.
     Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $c_{0} = u - w_{m-1}$.
@@
     \end{align*}
-    Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
-    \begin{align*}
-        \nabla w''_{m} = \nabla u - \nabla w'_{m}, 
+    %Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
+    There exists $w''_{m} \in W^{1,p}(T_{m})$ such that 
+    \begin{align*}
+        \nabla w''_{m} = \nabla u_{|T_{m+1}} - \nabla w'_{m}, 
         \quad 
@@
     \end{align*}
-    The trace condition holds because 
+    This is true because 
     \begin{align*}
@@
         &\leq 
-        |\det(\Dif \Xi  )|^{-\frac 1 p} 
-        \| \Dif \Xi   \|
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi   \|
         \cdot 
@@
         C_{???} 
-        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        \| \tilde g \|_{L^{p}(\hat U)}
         .
@@
         \leq 
-        |\det(\Dif \varphi)|^{\frac 1 p} 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
         \| \hat u \|_{L^{p}(\hat T)}
         \leq 
-        |\det(\Dif \varphi)|^{\frac 1 p} 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
         \| \tilde u \|_{L^{p}(\hat U)}
@@
         \\
-        \| \tilde g \|_{\bfL^{p}(\hat U)}
+        \| \tilde g \|_{L^{p}(\hat U)}
         \leq 
         2^{\frac n p}
-        \| \hat g \|_{\bfL^{p}(\hat T)}
+        \| \hat g \|_{L^{p}(\hat T)}
         \leq 
         2^{\frac n p}
-        |\det(\Dif \varphi_1)|^{-\frac 1 p} \| \Dif \varphi \| \cdot 
-        \| \cartan u \|_{\bfL^{p}(T)}
+        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
+        \| \cartan u \|_{L^{p}(T)}
         .
@@
         \left\{\begin{array}{ll}
-            \frac{n-1}{ne^{3}} & \text{ if } k=0
+            \frac{n-1}{n e^{3}} & \text{ if } k=0
             \\

### 2024-07-14 main.tex
partially section 5

@@
 But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfuhrt and veeser
+this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
 which contain finite element patches are not star-shaped with respect to any ball.
@@
 When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. Formally,
+which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
+We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
+Formally,
 \begin{gather*}
-    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
+    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
+    \qquad 
+    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
 \end{gather*}
@@
 We are interested in simplicial complexes that triangulated manifolds. 
-We put particular focus on \emph{shellable} simplicial complexes as a particularly important class of complexes.
+We put particular focus on \emph{shellable} simplicial complexes as an important class of complexes.
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner.
@@
 Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}.
-
-\begin{remark}
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. In particular, this enables the inductive method of proof.
-Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation.
-Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-the gluing interface is a triangulated submanifold of the boundary. 
-This forces the intermediate triangulations to be particularly well-shaped. 
-\end{remark}
 
@@
     \item
-    Let $F \in \Faces(T)$ and let $z_F \in F$ be its midpoint. 
+    Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
     Let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
@@
         \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. % TODO: Define this macro 
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
         \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
@@
     \centering
-    \begin{tikzpicture}
+    \begin{tabular}{c}\begin{tikzpicture}
         \coordinate (O) at (0, 0);
@@
         \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \begin{tikzpicture}
+    \end{tikzpicture}\\ (1) \end{tabular}
+    \begin{tabular}{c}\begin{tikzpicture}
         \coordinate (O) at (0, 0);
@@
         \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \begin{tikzpicture}
+    \end{tikzpicture}\\ (2) \end{tabular}
+    \begin{tabular}{c}\begin{tikzpicture}
         \coordinate (O) at (0, 0);
@@
         \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
-    \begin{tikzpicture}
+    \end{tikzpicture}\\ (3) \end{tabular}
+    \begin{tabular}{c}\begin{tikzpicture}
         \coordinate (O) at (0, 0);
@@
         \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}
+    \end{tikzpicture}\\ (4) \end{tabular}
     \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation. 
     (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
-(2) The new edge patch may already be a subset of the subtriangulation (3) An inadmissible choice because new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like (4) An inadmissible choice because new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
+    (2) The new edge patch may already be a subset of the subtriangulation
+    (3) An inadmissible choice because the new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like
+    (4) An inadmissible choice because the new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=0.5]
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
-        \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
-        \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
-        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-        \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
-        \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
-        \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
-        \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
-        \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
-        \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
-        \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
-    \end{tikzpicture}
-    \begin{tikzpicture}[scale=0.5]
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-        \draw (O) -- (A);
-        \draw (O) -- (B);
-        \draw (O) -- (C);
-        \draw (O) -- (X);
-        \draw (O) -- (Y);
-        \draw (O) -- (Z);
+% \begin{figure}
+%     \centering
+%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
+%         \coordinate (O) at (0, 0);
+%         \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
+%         \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
+%         \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
+%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+%         \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
+%         \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
+%         \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
+%         \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
+%         \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
+%         \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
+%         \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
+%     \end{tikzpicture}\\ (1) \end{tabular}
+%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
+%         \coordinate (O) at (0, 0);
+%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
+%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
+%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
+%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+%         \draw (O) -- (A);
+%         \draw (O) -- (B);
+%         \draw (O) -- (C);
+%         \draw (O) -- (X);
+%         \draw (O) -- (Y);
+%         \draw (O) -- (Z);
+%         %
+%     \end{tikzpicture}\\ (2) \end{tabular}
+%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
+%         \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
+%         % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
 % 
-    \end{tikzpicture}
-    \begin{tikzpicture}[scale=0.5] 
-        \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
-        % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
-
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-        \coordinate (T) at ({0}, {0}, {3});
-
-        \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
-        \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
-
-    \end{tikzpicture}
-
-    \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
-\end{figure}
+%         \coordinate (O) at (0, 0);
+%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
+%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
+%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
+%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+%         \coordinate (T) at ({0}, {0}, {3});
+% 
+%         \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
+% 
+%     \end{tikzpicture}\\ (3) \end{tabular}
+%     \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
+% \end{figure}
 
@@
 \subsection{Shellable simplicial complexes}
+
+\begin{remark}
+It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. In particular, this enables the inductive method of proof.
+Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation.
+Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
+by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
+the gluing interface is a triangulated submanifold of the boundary. 
+This forces the intermediate triangulations to be particularly well-shaped. 
+\end{remark}
 
@@
 \begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possibly enumerations.
+    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
     That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
@@
 \begin{lemma}    
-    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, % TODO: what is non-branching?
-    then
+    Suppose that an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, 
+    that is, each simplex of dimension $n-1$ is contained in at most two simplices. 
+    % TODO: what is non-branching?
+    Then
     $$
@@
 
+    \todo{Double check this proof and make it more explicit.}
     Write $M = |\calT|$. 
@@
     By the induction assumption, they contain a good triangle.
+    \todo{MV:But what if this is the neighbor of $T'$ and adding $T'$ back makes the triangle bad?}
 
@@
     then $\overline{M \setminus T}$ is still a topological $2$-disk.
-    Letting $\calT'$ be the triangulation obtained by removing $T$,
-    we have another triangulation of the $2$-disk that intersects $T$ only at either two or one edges.
+    The triangulation $\calT'$ that is obtained by removing $T$
+    is a triangulation of some $2$-disk that intersects $T$ only at either two or one edges.
     Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
@@
     and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
+    % TODO: cite E&V Math Comp 2020, Lemma B1. 
 \end{proof}

### 2024-07-15 main.tex
remaining annotations

@@
 as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulated manifolds. 
-We put particular focus on \emph{shellable} simplicial complexes as an important class of complexes.
+We are interested in simplicial complexes that triangulate manifolds. 
+Our particular interest are manifold triangulations that are \emph{shellable}.
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
 Patches within triangulations of dimension two and three are examples of such shellable complexes. 
-Our main references for this section are the monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures}.
+The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures} are our main references for this section.
 
@@
 or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
+In the former case, $x$ is called an \emph{interior point}, and in the latter case $x$ is called a \emph{boundary point}. 
 Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional.
@@
     We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$. 
-    Since the boundary is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
+    Since the boundary $\partial \calM$ is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
 
@@
     Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
-    Let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
+    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
     Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
@@
     So each inner face is contained in exactly two $n$-simplices. 
+    \todo{More details}
 
@@
     So each face within $\partial \calM$ is contained in exactly one $n$-simplex. 
+    \todo{More details}
 
@@
     Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
-    If $x \in \partial \calM$ is a boundary simplex, then it is an inner point of some simplex $S \in \calT$.
-    But then this simplex must be a boundary simplex, so the boundary simplices form a triangulation of $\partial \calM$.
+    Every $x \in \calM$ is an inner point of some simplex $S \in \calT$. 
+    If $x \in \partial \calM$ is a boundary point, then $S$ must be a boundary simplex, 
+    so the boundary simplices triangulate all of $\partial \calM$.
     \end{enumerate}
-    All relevant results are proven. 
+    All desired results are thus proven. 
 \end{proof}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO: integrate into narrative 
 Suppose that $\calT$ is an $n$-dimensional simplicial complex that triangulates a manifold. 
@@
 All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-
 We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
@@
 % The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \\
@@
 
-\begin{remark}
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. In particular, this enables the inductive method of proof.
-Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation.
+The notions of \emph{shelling} and \emph{shellable triangulation} have been discussed widely in combinatorial topology and polytopal theory. 
+Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation of a manifold.
+We thus build upon the notion of shelling, as introduced in~\cite[Definition 8.1]{ziegler2012lectures},
+and our definition of shelling is equivalent to the notion of the shellings of simplicial complexes in the aforementioned reference; see also~\cite[Remark~8.3]{ziegler2012lectures}.
+
 Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
@@
 This forces the intermediate triangulations to be particularly well-shaped. 
-\end{remark}
-
 We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-We build upon the notion of shelling, as introduced in~\cite[Definition 8.1]{ziegler2012lectures}.
-Our definition of shelling is equivalent to the notion of the shellings of simplicial complexes in the aforementioned reference; see also~\cite[Remark~8.3]{ziegler2012lectures}.
+It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, 
+as this enables the inductive method of proof.
+\\
 
@@
     that is, each simplex of dimension $n-1$ is contained in at most two simplices. 
-    % TODO: what is non-branching?
+    % DONE: what is non-branching?
     Then
@@
 
-    \todo{Double check this proof and make it more explicit.}
+    %\todo{Double check this proof and make it more explicit.}
     Write $M = |\calT|$. 
-    We call a triangle $T \in \calT$ \emph{good} if it intersects the boundary $\partial M$ in a non-empty union of edges.
+    There is nothing to show if $\calT$ contains only one triangle. 
+    We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
+    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
+    and a triangle is not good in $\calT$ if that intersection is either empty only some of its vertices, or a vertex and the opposite edge.
     % TODO: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
-    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk contains a good triangle. 
-    Clearly, this is the case if the triangulation contains only one triangle. 
-    Now suppose the induction claim is true when the triangulation includes $N$ triangles,
+    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk that contains at least two triangles also contains at least two good triangles.
+
+    Clearly, this is the case if the triangulation of the $2$-disk contains two triangles. 
+    Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
     and assume that $\calT$ includes $N+1$ triangles. 
-    There exists a triangle $T' \in \calT$ with at least one edge in the boundary. 
-    If $T'$ is good, then we are already done. 
-    Otherwise, $T'$ intersects the boundary at one edge and its opposing vertex.
-    Removing $T'$ splits the manifold into two pieces, each of which is a topological $2$-disk.
-    By the induction assumption, they contain a good triangle.
-    \todo{MV:But what if this is the neighbor of $T'$ and adding $T'$ back makes the triangle bad?}
+    There are at least two triangles with an edge on the boundary. 
+    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$,
+    then there exists a triangle $T'$ that intersects $\partial M$ 
+    in one edge and its opposite vertex.
+    Removing $T'$ splits the manifold into two strongly connected components, each of which is a topological $2$-disk.
+    By the induction assumption, each of those components contains at least two triangles 
+    that are good in the respective component. 
+    So each component has at least one triangle that is good in $\calT$.
+
+    % There exists a triangle $T' \in \calT$ with at least one edge in the boundary. 
+    % If $T'$ is good, then we are already done. 
+    % Otherwise, $T'$ intersects the boundary at one edge and its opposing vertex.
+    % \todo{MV:But what if this is the neighbor of $T'$ and adding $T'$ back makes the triangle bad?}
 
@@
 \]
-We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
+We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
 Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
@@
 \end{subequations}
+\todo{MWL: double check the correct sign convention, what is inverse and what is not}
 and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
@@
     \\
-    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
+    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv), 
     % TODO: watch the sign 
     \\
-    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
+    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw),
 \end{align}
 \end{subequations}
-for $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
+where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
 We summarize this as a commuting diagram:
@@
         \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
+        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
     \end{CD}
@@
 \[
-    W^p\Alt^{k}(\Omega) = \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
+    W^p\Alt^{k}(\Omega) 
+    := 
+    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
 \]
@@
     \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    = 
+    := 
     u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
@@
 \\
+
+\todo{cite Guzman and Salgado at the right spot.}\\
 
@@
 \begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. Then 
-    \begin{align*}
-        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)},
-        \qquad 
-        \bfu \in \bfH(\divergence,\Omega)
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
+    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $w \in \bfH(\divergence,\Omega)$ with $\divergence u = \divergence w$ and 
+    \begin{align*}
+        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
         .
@@
 \begin{proof}
+    This is a reduction to Friedrichs' inequality. 
     Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 

### 2024-07-16 main.tex
triangulations

@@
     % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{spanier1995algebraic}. 
+    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
 \end{remark}
@@
 The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures} are our main references for this section. 
+We also refer to Lee's monograph~\cite{lee2011topological} for any further background on manifolds.
 
@@
 
+The following special cases receive particular interest:
+an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball,
+and we sometimes call this a \textit{$n$-disk} triangulation.
+An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere. 
+\\
+
 We know that any manifold $\calM$ has got a topological boundary $\partial\calM$, possibly empty. 
 If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$. 
-
-The following special cases receive particular interest:
-a \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball,
-and we sometimes call this a \textit{$n$-disk} triangulation.
-An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
-
-We gather a few helpful properties of manifold triangulations. 
+We gather a few helpful observations on how these notions relate to triangulations.
 While the reader might deem them obvious, we nevertheless include proofs.
-We begin with the boundary.
 
@@
     \item 
+    We prove an auxiliary result. 
+    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
+    The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
+    Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
+    we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
+    By the Jordan-Brouwer separation theorem~\cite{}, $Y \setminus (X \cup \{y\})$ has got two connected components,
+    and thus $Y \setminus X$ has got two connected components.
+
+    \item
     Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
@@
 
+    Consider the case that $z_F$ lies on the boundary of $\calM$. 
+    If $F$ is contained in at least two distinct $n$-simplices of $\calT$,
+    then we can construct an embedded $n$-dimensional open ball that contains $z_F$.
+    But that contradicts $z_F$ being on the boundary. 
+    So any boundary face can only be contained in one single $n$-simplex.
+
     If $z_F$ is an interior point of $\calM$, 
-    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere $S$ of dimension $n-1$. 
-    At the same time, $X = F \cap \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere $S' \subseteq S$ of dimension $n-2$. % TODO: proofread
+    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
+    At the same time, $X = F \cap \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere of dimension $n-2$. % TODO: proofread
     We see that $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
-    But by construction $\partial \mathring B_F \setminus X$ is homeomorphic to $S \setminus S'$,
-    which has exactly two distinct connected components according to the Jordan-Brouwer separation theorem.
+    But by the auxiliary result above, $K = 2$. 
     We conclude that $F$ is contained in two $n$-simplices of $\calT$.
-    If an inner face $F$ were contained in only one $n$-simplex,
-    then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-    So each inner face is contained in exactly two $n$-simplices. 
-    \todo{More details}
-
-    If $F$ is contained in only one $n$-simplex, then it must be a face in the boundary of $\calM$. 
-    If $F$ were contained in at least two $n$-simplices,
-    then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-    So each face within $\partial \calM$ is contained in exactly one $n$-simplex. 
-    \todo{More details}
+%     But by construction $\partial \mathring B_F \setminus X$ is homeomorphic to $S \setminus S'$,
+%     which has exactly two distinct connected components according to the Jordan-Brouwer separation theorem.
+%     If an inner face $F$ were contained in only one $n$-simplex,
+%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
+%     So each inner face is contained in exactly two $n$-simplices. 
+%     \todo{More details}
+
+%     If $F$ is contained in only one $n$-simplex, then it must be a face in the boundary of $\calM$. 
+%     If $F$ were contained in at least two $n$-simplices,
+%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
+%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex. 
+%     \todo{More details}
+%     {\color{blue}
+%     The doubling $M_{D}$ of the manifold $M$ is obtained by gluing $M$ to a copy of itself along the boundary.
+%     The triangulation $\calT$ can be doubled to get a triangulation of the doubled manifold.
+%     Any boundary face is an interior face of the doubled manifold two $n$-simplices of the doubled triangulation.
+%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex of $\calT$. 
+%     }
 
@@
 
-\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-\begin{proposition}\label{proposition:guerinisavo}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
-    Moreover, 
-    \begin{align*}
-        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
-    \end{align*}
-\end{proposition}
-\begin{proof}
-    The result is true if $\Omega$ has a smooth boundary. 
-    Now suppose that $\Omega$ is a Lipschitz domain. 
-\end{proof}
-
-\subsection{Inequalities for partial boundary conditions on a single simplex}
-
-\begin{lemma}
-    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
-    Then 
-    \begin{align*}
-        \| u \| \leq 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-    such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
-    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
-    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
-
-    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
-    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
-
-    The operator norm bound of the potential operator shows 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        \\&
-        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        .
-    \end{align*}
-    We use the pullback estimates 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        \| \Jacobian\varphi \|_{\infty}^{k}
-        |\det\varphi^{-\frac{1}{p}}|
-        \cdot 
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        .
-    \end{align*}
-    \begin{align*}
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        2^{n-l}
-        \| \hat f \|_{L^{p}(\hat T)} 
-        \leq 
-        2^{n-l}
-        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
-        |\det\varphi^{\frac{1}{p}}|
-        \cdot 
-        \| f \|_{L^{p}(T)} 
-        .
-    \end{align*}
-\end{proof}
-
-\subsection{Constructions over shellable triangulations}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $w \in \bfH(\divergence,\Omega)$ with $\divergence u = \divergence w$ and 
-    \begin{align*}
-        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This is a reduction to Friedrichs' inequality. 
-    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
-    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
-    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
-    which has the same smallest singular value. 
-\end{proof}
-
-\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
-    Let $T$ be an $n$-simplex and with a face $F$. 
-    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
-    \end{align*}
-    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,k,p}
-        \leq 
-        \diam(T)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
-    Then $\cartan \hat u = \hat g$. 
-    % 
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    We define $\tilde g = \cartan \tilde u$
-    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
-    \begin{gather*}
-        \| \tilde u \|_{L^{p}(\hat U)} 
-        \leq 
-        C_{???} 
-        \| \tilde g \|_{L^{p}(\hat U)}
-        .
-    \end{gather*}
-    In addition to that, 
-    \begin{gather*}
-        \| u \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \hat u \|_{L^{p}(\hat T)}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \tilde u \|_{L^{p}(\hat U)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\hat U)}
-        \leq 
-        2^{\frac n p}
-        \| \hat g \|_{L^{p}(\hat T)}
-        \leq 
-        2^{\frac n p}
-        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
-        \| \cartan u \|_{L^{p}(T)}
-        .
-    \end{gather*}
-    The second inequality follows.
-\end{proof}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
-    \end{align*}
-\end{theorem}
-
-\begin{proof}
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \[
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \]
-    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
-
-    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        .
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
-
-    We want to estimate norms. 
-    Lemma~\ref{lemma:todo} gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
-        \\&
-        \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
-    \begin{align*}
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
-    Putting this all together, 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \left( 
-            \| \cartan u \|_{L^{p}(T_{m})} 
-            + 
-            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(U_{m-1})} 
-%         \\&
-%         \leq  
-%         \rho(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-%         + 
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
-%         \| \cartan u \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-
-\subsection{Numerical examples}
-
-% Square 
-% L-shaped 
-% Slit
-
-% Cube 
-% Fichera
-% Crossed bricks
-
-Let $T$ be an $n$-dimensional simplex with some subsimplex $F$ We show that there exists a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is only on one side of the hyperplane.
+Suppose that any $n$-dimensional simplex $T$ with some subsimplex $F$.
+We want to find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is only on one side of the hyperplane.
 
@@
     \begin{align}
-        x 
-        &
-        = 
+        x &= 
         v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
@@
 \end{proof}
+
+\begin{theorem}
+    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
+    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let $M := |\patch_{\calT}(S)| \setminus T$. 
+    There exists a bi-Lipschitz mapping
+    \begin{align*}
+        \varphi : T \rightarrow M
+    \end{align*}
+    satisfying
+    \begin{align*}
+        \Lip( \varphi,      T ) \leq \Cvier{n}{k},
+        \quad 
+        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k},
+    \end{align*}
+    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
+\end{theorem}
+
+\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
+
+\begin{proposition}\label{proposition:guerinisavo}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
+    Moreover, 
+    \begin{align*}
+        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
+    \end{align*}
+\end{proposition}
+\begin{proof}
+    The result is true if $\Omega$ has a smooth boundary. 
+    Now suppose that $\Omega$ is a Lipschitz domain. 
+\end{proof}
+
+\subsection{Inequalities for partial boundary conditions on a single simplex}
+
+\begin{lemma}
+    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    Then 
+    \begin{align*}
+        \| u \| \leq 
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+    such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
+    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
+    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
+    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
+    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
+
+    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
+    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
+
+    The operator norm bound of the potential operator shows 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        \\&
+        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        .
+    \end{align*}
+    We use the pullback estimates 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        \| \Jacobian\varphi \|_{\infty}^{k}
+        |\det\varphi^{-\frac{1}{p}}|
+        \cdot 
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        .
+    \end{align*}
+    \begin{align*}
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        2^{n-l}
+        \| \hat f \|_{L^{p}(\hat T)} 
+        \leq 
+        2^{n-l}
+        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
+        |\det\varphi^{\frac{1}{p}}|
+        \cdot 
+        \| f \|_{L^{p}(T)} 
+        .
+    \end{align*}
+\end{proof}
+
+\subsection{Constructions over shellable triangulations}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
+    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $w \in \bfH(\divergence,\Omega)$ with $\divergence u = \divergence w$ and 
+    \begin{align*}
+        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    This is a reduction to Friedrichs' inequality. 
+    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
+    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
+    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
+    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
+    which has the same smallest singular value. 
+\end{proof}
+
+\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
+    Let $T$ be an $n$-simplex and with a face $F$. 
+    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
+    \begin{align*}
+        \| u \|_{L^{p}(T)}
+        &
+        \leq 
+        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
+    \end{align*}
+    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},T,F,k,p}
+        \leq 
+        \diam(T)
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    Then $\cartan \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    We define $\tilde g = \cartan \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\hat U)} 
+        \leq 
+        C_{???} 
+        \| \tilde g \|_{L^{p}(\hat U)}
+        .
+    \end{gather*}
+    In addition to that, 
+    \begin{gather*}
+        \| u \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \hat u \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \tilde u \|_{L^{p}(\hat U)}
+        ,
+        \\
+        \| \tilde g \|_{L^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{L^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
+        \| \cartan u \|_{L^{p}(T)}
+        .
+    \end{gather*}
+    The second inequality follows.
+\end{proof}
+
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
+    and such that for all $T \in \calT$:
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}
+    \end{align*}
+\end{theorem}
+
+\begin{proof}
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
+    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+
+    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    \[
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \]
+    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
+    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
+    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
+    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
+
+    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
+    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
+    \begin{align*}
+        \trace_F w_{m-1} = \trace_F w'_{m}
+        .
+    \end{align*}
+    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
+    \begin{align*}
+        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
+        \quad 
+        \trace_{\Gamma_{m}} w''_{m} = 0.
+    \end{align*}
+    Indeed, such $w''_{m}$ exists because 
+    \begin{align*}
+        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
+        &= 
+        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
+        \\&= 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
+        = 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
+        = 
+        0
+        .
+    \end{align*}
+    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
+    we find 
+    \begin{gather*}
+        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
+        \\
+        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
+    \end{gather*}
+    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
+
+    We want to estimate norms. 
+    Lemma~\ref{lemma:todo} gives 
+    \begin{align*}
+        \| w''_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
+        \\&
+        \leq 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    We also employ Lemma~\ref{lemma:volumecomparison} to find 
+    \begin{align*}
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi   \|
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        \leq 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        .
+    \end{align*}
+    Putting this all together, 
+    \begin{align*}
+        &
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \left( 
+            \| \cartan u \|_{L^{p}(T_{m})} 
+            + 
+            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        \right) 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(U_{m-1})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+%         + 
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
+%         \| \cartan u \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
+\end{proof}
+
+\subsection{Numerical examples}
+
+% Square 
+% L-shaped 
+% Slit
+
+% Cube 
+% Fichera
+% Crossed bricks
 

### 2024-07-17 main.tex
Update on Overleaf.

@@
     \item 
+    We recall an auxiliary result.
+    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
+    As a consequence of the Jordan-Brouwer separation theorem~\cite[Corollary 5.24]{mayer1989algebraische}~\cite[Corollary 6.4]{massey1981algebraic}, 
+    we know that $Y \setminus X$ has got two connected components.
+
+    \item 
     We prove an auxiliary result. 
@@
     we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    By the Jordan-Brouwer separation theorem~\cite{}, $Y \setminus (X \cup \{y\})$ has got two connected components,
+    As a consequence of the Jordan-Brouwer separation theorem~\cite[Theorem 5.23]{mayer1989algebraische}~\cite[Corollary 5.24]{mayer1989algebraische}~\cite[Corollary 6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
     and thus $Y \setminus X$ has got two connected components.
@@
 Having discussed vector analysis, we review exterior calculus. 
-We give a brief introduction into this topic, and refer to the literature for further background~\cite{...}. 
+We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}. 
 Let $V$ be a real vector space. 
@@
     We want to estimate norms. 
-    Lemma~\ref{lemma:todo} gives 
+    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} gives 
     \begin{align*}

### 2024-07-17 main.tex
clean up

--- 2024-07-16 main.tex
@@
 
+\begin{lemma}    
+    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
+    For $0 \leq m < M$, write 
+    $$
+        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
+        \qquad 
+        I_{m} := X_{m} \cap T_{m+1}.
+    $$ 
+    Then $I$ is the union of $k$ different facets of $T$, 
+    and their intersection is a simplex $S \in \calT$ of dimension $n-k$.
+    Moreover, 
+    $$
+        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
+    $$
+\end{lemma}
+\begin{proof}
+    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
+    that constitute the local patch around some simplex $S$ of dimension $n-k$.
+\end{proof}
+
 \begin{theorem}

### 2024-07-18 main.tex
minor tweak
Update on Overleaf.
rearrange

@@
     u \in W^{1,p}(\Omega)
-    , \tag{P} % DONE: tag poincare inequality 
+    , \tag{P} % DONE: tag Poincar\'e inequality 
 \end{align}
@@
 
-% DONE: INTRODuce a reference simplex 
+% DONE: Introduce a reference simplex 
 % DONE: DEFINE THE JACOBIAN 
@@
     that constitute the local patch around some simplex $S$ of dimension $n-k$.
+    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
+    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
+    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
 \end{proof}
 
-\begin{theorem}
+\begin{theorem}\label{theorem:starreflection}
     Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
@@
     \begin{align*}
-        \Lip( \varphi,      T ) \leq \Cvier{n}{k},
+        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \diam(T),
         \quad 
-        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k},
+        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \diam(T),
     \end{align*}
@@
 \end{theorem}
+\begin{proof}
+\begin{itemize}
+    \item 
+    \todo{Choose hyperplane that puts T on one side}
+    We use Lemma~\ref{lemma:oppositesubsimplex}
+    \item 
+    \todo{Align barycenter of opposite subsimplex with coordinate axis}
+    \item 
+    \todo{opposite simplex cast to disk}
+    \item 
+    \todo{roll out rest of sphere onto disk}
+    \item 
+    \todo{estimate reflection}
+\end{itemize}
+\end{proof}
+
+% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
+% https://eudml.org/doc/258483
+% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
+% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
+\begin{lemma}
+    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
+    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
+    \begin{align*}
+        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R^{2}/r % euclidean 
+    \end{align*}
+    If $K$ is convex, then 
+    \begin{align*}
+        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
+        \\
+        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
+    \end{align*}
+\end{lemma}
+\begin{lemma}
+    .
+\end{lemma}
 
 \section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-\begin{proposition}\label{proposition:guerinisavo}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
-    Moreover, 
-    \begin{align*}
-        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
-    \end{align*}
-\end{proposition}
-\begin{proof}
-    The result is true if $\Omega$ has a smooth boundary. 
-    Now suppose that $\Omega$ is a Lipschitz domain. 
-\end{proof}
-
-\subsection{Inequalities for partial boundary conditions on a single simplex}
-
-\begin{lemma}
-    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
-    Then 
-    \begin{align*}
-        \| u \| \leq 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-    such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
-    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
-    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
-
-    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
-    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
-
-    The operator norm bound of the potential operator shows 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        \\&
-        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        .
-    \end{align*}
-    We use the pullback estimates 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        \| \Jacobian\varphi \|_{\infty}^{k}
-        |\det\varphi^{-\frac{1}{p}}|
-        \cdot 
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        .
-    \end{align*}
-    \begin{align*}
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        2^{n-l}
-        \| \hat f \|_{L^{p}(\hat T)} 
-        \leq 
-        2^{n-l}
-        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
-        |\det\varphi^{\frac{1}{p}}|
-        \cdot 
-        \| f \|_{L^{p}(T)} 
-        .
-    \end{align*}
-\end{proof}
-
-\subsection{Constructions over shellable triangulations}
 
@@
 
-\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
-    Let $T$ be an $n$-simplex and with a face $F$. 
-    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
-    \end{align*}
-    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,k,p}
-        \leq 
-        \diam(T)
-        .
-    \end{align*}
-\end{lemma}
+\begin{proposition}\label{proposition:guerinisavo}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
+    Moreover, 
+    \begin{align*}
+        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
+    \end{align*}
+\end{proposition}
 \begin{proof}
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
-    Then $\cartan \hat u = \hat g$. 
-    % 
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    We define $\tilde g = \cartan \tilde u$
-    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
-    \begin{gather*}
-        \| \tilde u \|_{L^{p}(\hat U)} 
-        \leq 
-        C_{???} 
-        \| \tilde g \|_{L^{p}(\hat U)}
-        .
-    \end{gather*}
-    In addition to that, 
-    \begin{gather*}
-        \| u \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \hat u \|_{L^{p}(\hat T)}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \tilde u \|_{L^{p}(\hat U)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\hat U)}
-        \leq 
-        2^{\frac n p}
-        \| \hat g \|_{L^{p}(\hat T)}
-        \leq 
-        2^{\frac n p}
-        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
-        \| \cartan u \|_{L^{p}(T)}
-        .
-    \end{gather*}
-    The second inequality follows.
+    The result is true if $\Omega$ has a smooth boundary. 
+    Now suppose that $\Omega$ is a Lipschitz domain. 
 \end{proof}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
-    \end{align*}
-\end{theorem}
-
-\begin{proof}
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \[
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \]
-    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
-
-    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        .
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
-
-    We want to estimate norms. 
-    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
-        \\&
-        \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
-    \begin{align*}
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
-    Putting this all together, 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \left( 
-            \| \cartan u \|_{L^{p}(T_{m})} 
-            + 
-            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(U_{m-1})} 
-%         \\&
-%         \leq  
-%         \rho(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-%         + 
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
-%         \| \cartan u \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-
-\subsection{Numerical examples}
-
-% Square 
-% L-shaped 
-% Slit
-
-% Cube 
-% Fichera
-% Crossed bricks
 
@@
 
-% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
-% https://eudml.org/doc/258483
-% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
-% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
 \begin{lemma}
-    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
-    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
-    \begin{align*}
-        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R^{2}/r % euclidean 
-    \end{align*}
-    If $K$ is convex, then 
-    \begin{align*}
-        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
-        \\
-        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
+    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    Then 
+    \begin{align*}
+        \| u \| \leq 
     \end{align*}
 \end{lemma}
-
-\begin{lemma}
-    .
+\begin{proof}
+    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+    such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
+    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
+    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
+    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
+    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
+
+    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
+    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
+
+    The operator norm bound of the potential operator shows 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        \\&
+        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        .
+    \end{align*}
+    We use the pullback estimates 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        \| \Jacobian\varphi \|_{\infty}^{k}
+        |\det\varphi^{-\frac{1}{p}}|
+        \cdot 
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        .
+    \end{align*}
+    \begin{align*}
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        2^{n-l}
+        \| \hat f \|_{L^{p}(\hat T)} 
+        \leq 
+        2^{n-l}
+        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
+        |\det\varphi^{\frac{1}{p}}|
+        \cdot 
+        \| f \|_{L^{p}(T)} 
+        .
+    \end{align*}
+\end{proof}
+
+\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
+    Let $T$ be an $n$-simplex and with a face $F$. 
+    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
+    \begin{align*}
+        \| u \|_{L^{p}(T)}
+        &
+        \leq 
+        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
+    \end{align*}
+    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},T,F,k,p}
+        \leq 
+        \diam(T)
+        .
+    \end{align*}
 \end{lemma}
+\begin{proof}
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    Then $\cartan \hat u = \hat g$. 
+    % 
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    We define $\tilde g = \cartan \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
+    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\hat U)} 
+        \leq 
+        C_{???} 
+        \| \tilde g \|_{L^{p}(\hat U)}
+        .
+    \end{gather*}
+    In addition to that, 
+    \begin{gather*}
+        \| u \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \hat u \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \tilde u \|_{L^{p}(\hat U)}
+        ,
+        \\
+        \| \tilde g \|_{L^{p}(\hat U)}
+        \leq 
+        2^{\frac n p}
+        \| \hat g \|_{L^{p}(\hat T)}
+        \leq 
+        2^{\frac n p}
+        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
+        \| \cartan u \|_{L^{p}(T)}
+        .
+    \end{gather*}
+    The second inequality follows.
+\end{proof}
+
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
+    and such that for all $T \in \calT$:
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}
+    \end{align*}
+\end{theorem}
+
+\begin{proof}
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
+    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+
+    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    \[
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \]
+    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
+    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
+    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
+    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
+
+    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
+    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
+    \begin{align*}
+        \trace_F w_{m-1} = \trace_F w'_{m}
+        .
+    \end{align*}
+    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
+    \begin{align*}
+        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
+        \quad 
+        \trace_{\Gamma_{m}} w''_{m} = 0.
+    \end{align*}
+    Indeed, such $w''_{m}$ exists because 
+    \begin{align*}
+        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
+        &= 
+        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
+        \\&= 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
+        = 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
+        = 
+        0
+        .
+    \end{align*}
+    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
+    we find 
+    \begin{gather*}
+        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
+        \\
+        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
+    \end{gather*}
+    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
+
+    We want to estimate norms. 
+    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} gives 
+    \begin{align*}
+        \| w''_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
+        \\&
+        \leq 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    We also employ Lemma~\ref{lemma:volumecomparison} to find 
+    \begin{align*}
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi   \|
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        \leq 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        .
+    \end{align*}
+    Putting this all together, 
+    \begin{align*}
+        &
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \left( 
+            \| \cartan u \|_{L^{p}(T_{m})} 
+            + 
+            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        \right) 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(T_{m})} 
+        + 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        \| \cartan u \|_{L^{p}(U_{m-1})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
+%         + 
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
+%         \| \cartan u \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
+\end{proof}
+
+\section{Numerical examples}
+
+\subsection{Two-dimensional examples}
+
+% Square 
+% L-shaped 
+% Slit
+
+\subsection{Three-dimensional examples}
+
+% Cube 
+% Fichera
+% Crossed bricks
 

### 2024-07-22 extra.tex
Update on Overleaf.

--- 2024-07-17 main.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{fullpage}
-\input{header}
-
-\usepackage{hyperref}         % For hypertext links
-
-% Title, authors, and affiliations
-% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
-% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
-
-\title{Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations}
-\author{
-    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
-    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{email2@example.com}} \and
-    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
-}
-
-% Theorem environments
-
-\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations.
-This class of triangulations includes local stars in dimension two and three.
-    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
-    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
-    % 
-    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
-    %     The main application that we envision are computable estimates over finite element patches. 
-    %
-    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
-    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
-\end{abstract}
-
-\section{Introduction}\label{section:intro}
-
-% DONE \todo{Reformulate the first paragraph. } % 
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations.
-% which serve a variety of purposes:
-% these constants quantify the fundamental stability properties of partial differential equations, imply lower bounds for the spectra of vector and Hodge Laplacians, and they . 
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-% We study potential operators in the special class of domains with shellable triangulations,
-% which include local stars in 2D and 3D. 
-% We bound the operator norms of our operators in terms of the shape regularity of the triangulation.
-
-% We contribute to the construction of potential operators in vector analysis and exterior calculus over triangulated domains. 
-% We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
-% The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
-% In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
-
-% DONE : MV : remove 'For example' 
-We illustrate the subject of our discussion with the curl operator. 
-% One example application concerns the curl operator. 
-If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$. 
-This boundedness is expressed via the Poincar\'e--Friedrichs inequality 
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
-    \leq 
-    C_{\curl}
-    \| \bff \|_{\bfL^{2}(\Omega)}
-    .
-\end{align*}
-The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.
-
-Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-The majority of estimates in the literature address only gradient potentials. 
-% We accomplish our results for a special class of triangulations, so-called shellable triangulations.
-% We accomplish this task in 
-We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards the more general case. 
-For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
-Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
-\\
-
-Before we outline the main results of this exposition in more details, 
-we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-
-% DONE: MV : Be more didactical: write following as the existence of a potential. 
-Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
-for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:intro:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The different scalar potentials only differ by a constant. 
-Therefore, %when the domain is connected, then 
-this inequality is equivalent to the following statement: 
-\begin{align}\label{math:intro:poincarefriedrichs:grad}
-    \min\limits_{c\in\bbR}
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
-    \quad 
-    \forall
-    u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
-    .\tag{PF} 
-\end{align}
-% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
-% \begin{align}\label{math:intro:poincarefriedrichs:grad}
-%     \min\limits_{c\in\bbR}
-%     \| u - c \|_{L^{p}(\Omega)}
-%     \leq 
-%     C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
-%     \quad 
-%     u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
-%     .\tag{PF} 
-% \end{align}
-Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
-The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
-% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One example for a bounded linear operator is the average-free potential:
-\begin{align*}
-    \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
-\begin{align}\label{math:intro:poincare:grad}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^p(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    , \tag{P} % DONE: tag poincare inequality 
-\end{align}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
-
-Most research on optimal constants has addressed the case of convex domains. 
-% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
-An open set star-shaped with respect to a internal point satisfies Poincar\'e inequalities~\cite[Theorem~3.1]{hurri1988poincare}.
-
-The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-We use the vector field spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
-    .
-\end{align*}
-Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
-\begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
-    \qquad 
-    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
-\end{align*}
-The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
-We are interested in constants for inequalities such as 
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)}
-    ,
-    \qquad 
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
-and whether these constants can be estimated by the operator norms of linear potential operators 
-\begin{align*}
-    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \quad 
-    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-
-Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-% even if the domain is convex, 
-This sharply contrasts to the study of the gradient operator. 
-%
-% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
-We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue}, who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$.
-They provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains.
-This implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
-By duality, that implies lower bounds for the case of full boundary conditions.
-Their study also implies sequences of inequalities, such as the following in 3D convex domains:
-\begin{align}\label{math:intro:guerinisavo}
-    C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
-\end{align}
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
-follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation},
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-\\
-% DONE: cite Guzman and Salgado in a reasonable manner
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
-which contain finite element patches are not star-shaped with respect to any ball.
-
-Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
-However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
-We review some of the main outcomes. 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-% 
-The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted.
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here.
-The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
-Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the interfacing intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed to ensure continuity across that interface. 
-% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
-
-While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
-we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
-We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
-which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
-We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
-
-% General outline 
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-\\
-
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable. 
-\\
-
-% This construction of potentials requires triangulations with special conditions: 
-% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Such triangulations are called \textit{shellable}.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
-% In particular, local stars in 2D and 3D triangulations are shellable. 
-% \\
-
-% auxiliary problems 
-% We construct gradient potentials locally over convex domains or face patches. 
-Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-% DONT: cite VVVV
-While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
-the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
-
-% DONE: cite VVVV
-In the Hilbert space case, $p=2$, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex Lipschitz domains.
-
-But no such results are known for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
-We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
-In comparison to their exposition, our variants of the regularized potential operators are simplified:
-we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
-however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
-We consider the latter outcome to be of independent interest.
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential.
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-% Future work 
-Computable reliable estimates for the Poincar\'e--Friedrichs constant are important: 
-they quantify the fundamental stability properties of partial differential equations in vector analysis,
-such as the Hodge Laplace equation. 
-Upper bounds correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
-% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
-In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
-and they lead to lower bounds for the spectrum of finite element matrices.
-
-Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
-In particular, domains with shellable triangulations are contractible.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-We conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
-These topics remain for future research.
-\\
-
-The remainder of this manuscript is structured as follows.
-We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We review Poincar\'e constants for the gradient over convex domains in~\ref{section:poincare}.
-We develop computable upper bounds for Poincar\'e--Friedrichs constants for the gradient over triangulated domains in Section~\ref{section:gradient}.
-We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
-We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
-We construct an important geometric reflection operator in Section~\ref{section:extension}
-and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-
-\section{Basic notions of triangulations}\label{section:triangulations}
-
-We gather basic notions and definitions concerning simplicial meshes.
-
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
-We call these points the \emph{vertices} of the simplex $T$.
-If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and we call $T$ a \textit{supersimplex} of $S$.
-
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
-\\
-
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if it satisfies the following conditions: 
-(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
-\begin{align*}
-    \underlying{\calT} := \bigcup_{ T \in \calT } T
-    .
-\end{align*}
-We call a set \textit{trianguable} if it is the underlying set of some triangulation.
-
-\begin{remark}
-    Our main interest in this manuscript are finite triangulations of compact sets. 
-    There is another reason why we insist on the triangulation being finite: 
-    if we do not require our simplicial complexes to be finite,
-    then a reasonable definition of simplicial complex would need additional topological conditions. 
-    % 
-    For example, if we modify our definition of simplicial complex to be infinite, 
-    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
-    %
-    A more interesting such example is this:
-    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
-    that underlies an ``infinite $0$-dimensional simplicial complex''.
-    If we place $\calC$ on the x-axis of a 2D coordinate system 
-    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
-    then the resulting set is still compact, even path-connected,  
-    but has an ``infinite $1$-dimensional triangulation''.
-    % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
-\end{remark}
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
-More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
-We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
-The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
-In practice, we not always distinguish between points and singleton simplices. 
-Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-% \begin{remark}
-    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.~\cite{schrijver1998theory}
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra.~\cite{ziegler2012lectures}
-% \end{remark}
-}
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
-We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
-Formally,
-\begin{gather*}
-    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
-    \qquad 
-    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
-\end{gather*}
-We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial observation is the following.
-
-\begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \emptyset$ or there exists $S'' \in \calT$
- such that $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S'')$ with $S, S' \subseteq S''$.
-\end{lemma}
-\begin{proof}
- Let $T \in \calT$ be $n$-dimensional.
- We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
- We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
- Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
- where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
-\end{proof}
-
-We introduce a specific notion of connectivity. 
-Given an $n$-dimensional simplicial complex $\calT$, 
-we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
-Clearly, strongly connected in $\calT$ is an equivalence relation among simplices. 
-A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component.
-
-\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
-\\
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm PF},\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm PF},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, % TODO: cite AAAA somebody, such as Alexandre
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \right)^{p}
-    \leq 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \right)
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-% \begin{align*}
-%     \color{Emerald}
-%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p-1} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     +
-%     2^{p-1} 
-%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     .
-% \end{align*}
-Via an application of the triangle inequality, 
-the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{{\rm P},\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
-Hence $C_{{\rm P},\Omega,2} = C_{{\rm PF},\Omega,2}$.
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^p(\Omega)
-    .
-\end{align*}
-We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}.
-\end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-\\
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
-see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
-\begin{align}\label{math:acostaduran}
-    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{\diam(\Omega)}{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    ,
-    \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
-    \leq 
-    \frac{\diam(\Omega)}{\pi}
-    \| \nabla u \|_{L^{2}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,2}(\Omega)
-    .
-\end{align}
-These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
-\begin{align}\label{math:chuawheeden}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm CW},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where we use an upper bound by Chua and Wheeden:
-\begin{align}
-    C_{{\rm CW},p} 
-    := 
-    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
-    \frac{ 
-        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
-    }{ 
-        \| \nabla v \|_{L^{p}([0,1])} 
-    }
-    \leq 
-    \sqrt[p]{p} 2^{1-\frac 1 p}
-    =
-    2
-    \left( \frac p 2 \right)^{\frac 1 p}
-    .
-\end{align}
-Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
-As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
-
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
-when $1 < p < \infty$, one can show that 
-\begin{align}\label{math:esposito:pf}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where $C_{{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align}
-    C_{{\rm EFNT},p}
-    :=
-    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
-    .
-\end{align}
-Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
-\begin{align}\label{math:esposito:poincare}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    2^{|1-\frac 2 p|}C_{{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
-\begin{align}\label{math:l1estimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{ \diam(\Omega) }{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    .
-\end{align}
-When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
-\begin{align}\label{math:lipschitzestimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{\infty}(\Omega)}
-    \leq 
-    \diam(\Omega)
-    \| \nabla u \|_{L^{\infty}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,\infty}(\Omega)
-    .
-\end{align}
-
-% TODO: Keep ?
-% \begin{example}
-%     We explain why \eqref{math:l1estimate} is optimal. 
-%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
-%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
-%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
-%     and $\Omega$ has diameter $2$. 
-%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
-%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
-%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
-% \end{example}
-
-\begin{remark}
-    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
-    Let us compare the estimate $C_{{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm EFNT},p}$. 
-    In the case $2 \leq p$, 
-    \begin{align*}
-        2^{1-\frac 2 p}
-        C_{{\rm EFNT},p}
-        =
-        \frac{ 2^{1-\frac 2 p} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq 
-        4^{-\frac 1 p}
-        \leq
-        C_{{\rm CW},p} 
-        .
-    \end{align*}
-    In the case $2 \geq p$, 
-    \begin{align*}
-        2^{\frac 2 p - 1}
-        C_{{\rm EFNT},p}
-        =
-        \frac{ 2^{\frac 2 p - 1} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq
-        \frac{ 2^{\frac 2 p-1} }{2}
-        =
-        2^{\frac 2 p - 2}
-        =
-        4^{\frac 1 p - 1}
-        \leq
-        C_{{\rm CW},p} 
-%         % 
-%         .
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
-%         =
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
-%         \leq 
-%         \frac 1 2
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua wheeden upper bound is not optimal!
-    % DONE: Theorem 1.2 in Chua Wheeden 
-% TODO: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{{\rm EFNT},p}$ converges to $1/2$,
-%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-%         \leq 
-%         \frac{1}{2}
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{1}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,1}(\Omega)
-%         .
-%     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{{\rm EFNT},p}$ converges to $1/2$, 
-%     which implies the Poincar\'e inequality 
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,\infty}(\Omega)
-%         %
-%     \end{align*}
-%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % TODO: cite 
-%     % TODO: review this entire result 
-\end{remark}
-
-\todo{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
-
-\begin{remark}
-    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
-    but individual convex domains may allow for better constants.
-    We refer to \cite{matculevich2016explicit} for an overview;
-    for example, triangles allow the reduction of the constant by 20\%.
-\end{remark}
-
-% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
-
-\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
-
-In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. As a preparatory step, 
-Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
-This defines a scalar potential.
-This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
-after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
-The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
-\\
-
-Towards this goal, we introduce quantitative measures for the geometric quality of triangulations. 
-These indicate of the regularity of simplex shapes. 
-Most of such \emph{shape measures} in the literature are based on geometric features, 
-but we also consider indicators based on affine transformations associated with the mesh;
-this is because the properties of these transformations are what shows up in our estimates.
-
-For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.
-
-We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
-\begin{align}\label{math:geometricshapemeasure}
-    \kappa(T)
-    := 
-    \frac{ \diam(T)^{n} }{ n! \vol(T) }
-    .
-\end{align}
-
-\begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
-
-% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
-\begin{align}\label{math:moremeasures}
-    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
-%     \qquad 
-%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
-    \qquad 
-    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
-\end{align}
-Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
-Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
-that preserves $F$. We define 
-\begin{align}\label{math:reflectionmeasure}
-    \xi(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \| \Jacobian \Xi_{S,T} \|
-\end{align}
-to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
-This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
-% we define the quantity 
-% \begin{align*}
-%     \kappa(T)
-%     := 
-%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%     .
-% \end{align*}
-
-% DONE: INTRODuce a reference simplex 
-% DONE: DEFINE THE JACOBIAN 
-\todo{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}
-
-\begin{lemma}\label{lemma:affinetransform}
-    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{align*}
-        \| \Jacobian \varphi \|
-        \leq 
-        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
-        ,
-        \qquad 
-        \| \Jacobian \varphi^{-1} \|
-        \leq 
-        \Czwei{n} \cdot 
-        \kappa(T) 
-        \diam(T)^{-1}
-        .
-    \end{align*}
-    Here, $\Ceins{n} \leq \sqrt{n}$ and $\Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} }$. 
-\end{lemma}
-\begin{proof}
-    We easily verify the first inequality.
-To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
-    The Jacobian determinant is the product of these singular values. 
-%     By a result of Hong and Pan,
-%     \begin{align*}
-%         \frac{ \sigma_{n} }{ \sigma_{1} }
-%         \geq 
-%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
-%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
-%         \sigma_{1}^{-1}
-%         \geq 
-%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
-%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
-%         \sigma_{1}^{-1}
-%         .
-%     \end{align*}
-    By a result of Yu and Gu \cite{yisheng1997note},
-    \begin{align*}
-        \frac{ \sigma_{n} }{ \sigma_{1} }
-        &\geq 
-        \det(\Jacobian\varphi)
-        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
-        \sigma_{1}^{-1}
-%         \geq 
-%         (n-1)^{\frac{n-1}{2}}
-%         \det(\Jacobian\varphi)
-%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
-%         \frac{1}{\sqrt{n} \diam(T)}
-%         \\&
-%         \geq 
-%         \frac{1}{\sqrt{n}}
-%         (n-1)^{\frac{n-1}{2}}
-%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
-        \geq 
-        \sqrt{\frac{ (n-1)^{n-1} }{n} }
-        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
-        .
-    \end{align*}
-    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
-%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
-%     \[
-%         \diam(T) 
-%         \leq 
-%         \sqrt{2} \sigma_1 
-%         \leq 
-%         \sqrt{2} 
-%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
-%         \sigma_n
-%         \leq 
-%         \sqrt{2n^{n}} 
-%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
-%         \sigma_n
-%         .
-%     \]
-%     The desired result is thus evident. 
-\end{proof}
-
-% TODO: REMOVE THE \cdot 
-\begin{lemma}\label{lemma:volumecomparison}
-    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \begin{align*}
-        \diam(T_1)
-        \leq 
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \diam(F)
-        % = 
-        \kappa(T_1)
-        \diam(F)
-        ,
-        \qquad 
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
-        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-        % \cdot 
-        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        % = 
-        \kappa(T_1) \kappa(T_2)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        \leq 
-        \Cdrei{n}
-        \frac{ \kappa(T_1) }{ \kappa(T_2) }
-        .
-    \end{align*}
-    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
-\end{lemma}
-
-% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
-% \begin{align*}
-%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
-%     \leq 
-%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-%     \cdot 
-%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-%     .
-% \end{align*}
-% DONE: REMOVE THE FACTORIAL?
-% DONE: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-% DONE: clarify the first of the following inequalities
-
-%     \begin{align*}
-%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
-%     \end{align*}
-%     Thus we establish the first estimate:
-
-%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-%     \begin{align*}
-%         \diam(F)
-%         \geq 
-%         h
-%         =
-%         n
-%         \frac{ \vol(T_1) }{ \vol(F') }
-%         \geq 
-%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
-%         \cdot 
-%         \diam(T_1)
-%         .
-%     \end{align*}
-%     That shows the second estimate.
-
-\begin{proof}
-    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
-    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
-    \begin{align*}
-        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
-    \end{align*}
-    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
-    \begin{align*}
-        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
-    \end{align*}
-    The first estimate follows. 
-    On the other hand, 
-    \begin{align*}
-        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
-        \\
-        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        .
-    \end{align*}
-    The second estimate follows. 
-    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\eqref{lemma:affinetransform} and the first estimate imply 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        &
-        \leq 
-        \Ceins{n}
-        \Czwei{n}
-        \kappa(T_2)
-        \diam(T_1)
-        \diam(T_2)^{-1}
-        \\&
-        \leq 
-        \Ceins{n}
-        \Czwei{n}
-        \kappa(T_2)
-        \kappa(T_1) 
-        \diam(F)
-        \diam(T_2)^{-1}
-        \leq 
-        \Ceins{n}
-        \Czwei{n}
-        \kappa(T_2)
-        \kappa(T_1) 
-        .
-    \end{align*}
-    All the desired results thus follow.
-\end{proof}
-
-We have already seen a survey of Poincar\'e inequalities over convex domains. 
-Slightly more generally, we are interested in such inequalities over face patches within simplicial triangulations. 
-We state a geometric auxiliary lemma and an estimate of Poincar\'e--Friedrichs constants over face patches 
-that captures the correct asymptotic behavior as $p$ grows to infinity.
-
-\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
-    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
-    Write $U := T_1 \cup T_2$. 
-    Then 
-    \begin{align*}
-        \min\limits_{ c \in \bbR }
-        \| u - c \|_{L^{p}(U)}
-        &
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            \frac{ \vol(T_1) }{ \vol(T_2) }
-            ,
-            \frac{ \vol(T_2) }{ \vol(T_1) }
-        \right)^{\frac 1 p}
-        \max\left( \diam(T_1), \diam(T_2) \right)
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \rho(\calT)^{\frac 1 p}
-        \max\left( \diam(T_1), \diam(T_2) \right)
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
-\end{lemma}
-% \begin{remark}
-%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
-% \end{remark}
-\begin{proof}
-    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
-    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
-    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
-    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
-    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
-    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
-
-    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
-    We observe 
-    \begin{align*}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-        &=
-        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-        +
-        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-        \\&
-        \leq 
-        |\det(\Jacobian \varphi_1^{-1})|
-        \cdot \| \Jacobian \varphi_1 \|^{p}
-        \cdot 
-        \| \nabla u \|_{L^{p}(T_1)}^{p}
-        +
-        |\det(\Jacobian \varphi_2^{-1})|
-        \cdot \| \Jacobian \varphi_2 \|^{p}
-        \cdot 
-        \| \nabla u \|_{L^{p}(T_2)}^{p}
-        \\&
-        \leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
-            ,
-            |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
-        \right)
-        \| \nabla u \|_{L^{p}(U)}^{p}
-        .
-    \end{align*}
-    Hence 
-    \begin{align*}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}
-        &\leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \cdot \| \Jacobian \varphi_1 \|
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \cdot \| \Jacobian \varphi_2 \|
-        \right)
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    Notice that $\hat U$ has diameter $2$. 
-    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
-    \begin{align*}
-        \| \hat w \|_{L^{p}(\hat U)}
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}
-        .
-    \end{align*}
-    Next, setting $w := \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(U)}
-        \leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \| \hat w \|_{L^{p}(\hat U)}
-        .
-    \end{align*}
-    % DONE: that abbreviation is to close to the Jacobian / total derivative 
-    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
-    \begin{align*}
-        \| w \|_{L^{p}(U)}
-        &\leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} 
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} 
-        \right)
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \min\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)| 
-        \right)^{-\frac 1 p} 
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            \frac{ |\det(\Jacobian \varphi_1)| }{ |\det(\Jacobian \varphi_2)| }
-            ,
-            \frac{ |\det(\Jacobian \varphi_2)| }{ |\det(\Jacobian \varphi_1)| }
-        \right)^{\frac 1 p}
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            \frac{ \vol(T_1) }{ \vol(T_2) }
-            ,
-            \frac{ \vol(T_2) }{ \vol(T_1) }
-        \right)^{\frac 1 p}
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    This gives the desired result. 
-\end{proof}
-
-\begin{figure}[t]
-\begin{center}
-\begin{tikzpicture}
-    \coordinate (A) at (0,0);
-    \coordinate (B) at (2,0);
-    \coordinate (C) at (1,1.5);
-    \coordinate (D) at (3,1.5); 
-    \coordinate (E) at (3,3); 
-    \coordinate (F) at (4,0.25); 
-    \coordinate (X) at (1,-1.5);
-    \coordinate (Y) at (3,-1.5); 
-    \coordinate (T) at (5,2);
-
-    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
-    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
-    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
-    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
-    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
-    \coordinate (CentroidDFT) at ($(D)!0.3333!(F)!0.3333!(T)$);
-    \coordinate (CentroidDET) at ($(D)!0.3333!(E)!0.3333!(T)$);
-
-    \draw[fill=gray!10] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!10] (B) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!10] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!10] (B) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (A) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (E) -- cycle;
-
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
-    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET);
-
-%     \node at (A) [below left] {$A$};
-%     \node at (B) [below right] {$B$};
-%     \node at (C) [above] {$C$};
-%     \node at (D) [above right] {$D$};
-%     \node at (T) [above right] {$T$};
-\end{tikzpicture}
-\end{center}
-\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_m = T$.
-    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
-    Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*} % TODO: UNIFY NOTATION FOR THE CONSTANTS 
-        % \color{red}
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \left( 1 + \rho(\calT)^{\frac q p} \right)^{\frac 1 q}
-        \sum_{t=1}^{m}
-        \rho(\calT)^{\frac{m-t}{p}}
-        C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
-        \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
-        \\&\quad \quad \quad 
-        +
-        \rho(\calT)^{\frac{m-1}{p}}
-        % C_{{\rm EFNT},p} \diam(T_0)
-        C_{{\rm{PF}},T_{0},p}
-        \| \nabla u \|_{L^{p}(T_{0})}
-        .
-    \end{align*}
-\end{theorem}
-
-\begin{proof}
- Let $u \in W^{1,p}(\Omega)$. 
- For each $F \in \calT$ of dimension $n-1$, 
- we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that 
- \begin{align*}
-    \| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla u_F \|_{L^{p}(U_F)},
- \end{align*}
- where the computable constant $C_{{\rm{PF}},U_F,p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
- We start with the simplex $T_{0}$. 
- There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
- \[
-    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
- \]
- In particular, $c_{0} := u - w_0$ is a constant function. 
- Now, let $T \in \calT$ be any $n$-simplex. 
- By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
- For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
- We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-%  Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
-We write $\Omega_m := \cup_{j=0}^{m} T_m$.
-Hence $\Omega = \Omega_M$.
-
- \todo{MLW, MV: add a figure here to illustrate how the domain is exhausted.}
-
- We use a recursive argument. 
- Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
- such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
- This is already satisfied for $m=1$.
- Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
- By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
- Since $\nabla u_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}}$,
- there exists a constant $c_{m} := w_{m-1|T_{{m-1}}} - u_{F_{m}|T_{{m-1}}}$.
- We define $w'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $\nabla w'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ 
- and 
- $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
- But that already implies $w'_{F_m} = u_{|F_m} - c_{0}$. 
- We define a measurable function $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$.
- We have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
-
- We assess the norm of this potential. We observe 
- \begin{gather*}
-    \| w'_{F_m} \|_{L^{p}(T_m)}
-    \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
-    +
-    \| c_{m} \|_{L^{p}(T_m)},
-    \qquad 
-    \| c_{m} \|_{L^{p}(T_m)}
-    = 
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| c_{m} \|_{L^{p}(T_{{m-1}})},
-    \\ 
-    \| c_{m} \|_{L^{p}(T_{{m-1}})}
-    \leq 
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
-    .
- \end{gather*}
- In particular,
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
- We sum the two integrals of $u_{F_m}$. 
- % 
- In the special case $p=1$,
- \begin{align*}
-    \| w_{m} \|_{L^{1}(T_m)}
-    \leq 
-    \max\left(
-        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
-    \right)
-    \| u_{F_m} \|_{L^{1}(U_{F_m})}
-    +
-    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
-    .
- \end{align*}
- In the special case $p=\infty$, 
- \begin{align*}
-    \| w_{m} \|_{L^{\infty}(T_m)}
-    \leq 
-    2
-    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
-    +
-    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
-    .
- \end{align*}
- % 1/q = 1 - 1/p = (p-1)/p 
- When $1 < p < \infty$, letting $q := p/(p-1) \in [1,\infty]$ be the complementary exponent, we observe 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \left( 
-        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
-        +
-        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
-    \right)^{\frac 1 p}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    \\&\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
- Recursive application provides the following estimate:
-%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
-%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
-%  then 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &\leq 
-    \sum_{t=1}^{m} 
-    \left( 
-        \prod_{t < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
-    \right)
-    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
-    \| u_{F_t} \|_{L^{p}(U_{F_t})}
-    \\&\quad \quad \quad 
-    +
-    \left( 
-        \prod_{0 < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
-    \right)
-    \| u_{T_0}\|_{L^{p}(T_{0})}
-    .
- \end{align*}
- Taking into account Definition~\eqref{math:moremeasures}, we obtain the desired inequality.
-%  \begin{align*}
-%     \| w_{m} \|_{L^{p}(T_m)}^{p}
-%     &\leq 
-%     (m+1)^{p-1}
-%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
-%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
-%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
-%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
-%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
-%     \\&\quad \quad \quad 
-%     +
-%     (m+1)^{p-1}
-%     \rho(\calT)^{m-1}
-%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
-%     .
-%  \end{align*}
-%  Notice that $p/q = p - 1$.
- % 
- Repeating this argument produces $w \in L^{p}(\Omega)$ 
- such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
- In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
-\end{proof}
-
-We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains. 
-While the underlying idea remains the same, the construction of the potential is slightly different. 
-As an auxiliary result with independent relevance, we compute an upper bound for the Poincar\'e--Friedrichs inequality 
-when homogeneous boundary conditions are imposed on a single face of the boundary. 
-We present this result with two different techniques. 
-While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains. 
-% Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.
-
-\begin{lemma}\label{lemma:mixedbconsimplex}
-    Let $T$ be an $n$-simplex with a face $F$. 
-    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
-    \end{align*}
-    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,p}
-        \leq 
-        C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
-        \quad 
-        C_{{\rm PF},T,F,p}
-        \leq
-        \frac{1}{\sqrt[p]{p}}
-        \diam(T)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
-    \[
-        \| w \|_{L^{p}(T)}
-        \leq 
-        C_{{\rm PF},T,p} 
-        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
-        .
-    \]
-    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
-    We use that 
-    \[
-        \| \gamma \|_{L^{p}(T)}
-        =
-        \gamma \vol(T)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \cdot 
-        \gamma 
-        \vol(F)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \| \gamma \|_{L^{p}(F)}
-        .
-    \]
-    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
-    \begin{align*}
-        \| \gamma \|_{L^{p}(F)}^{p}
-        &
-        \leq 
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p}
-        +
-        p
-        \cdot 
-        \diam(T)
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p-1}
-        \| \nabla w \|_{L^{p}(T)}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
-        \diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
-        %\diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        .
-    \end{align*}
-    Recall that $u = w - \gamma$. The first inequality follows.
-
-    The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Let assume that $1 \leq p < \infty$. 
-    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
-    Without loss of generality, 
-    the segment from to the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
-    and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $\nabla u$ outside of $T$.
-    %With the fundamental theorem of calculus and H\"olders inequality: 
-    \begin{align*}
-        \int_{\Omega} |u(x)|^{p} \diff x dx
-        &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} dx_{1} d\overline{x}
-        \\&
-        \leq
-        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| dy \right|^{p} dx_{1} d\overline{x}
-        \\&
-        \leq
-        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} dx_{1}
-        \\&
-        \leq
-        \int_{0}^{D} x_{1}^{p-1} dx_1 \cdot \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} 
-        \leq
-        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} dx
-        %
-%         \leq
-%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} dx_1 \dots dx_{n-1} dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
-%         \leq 
-%         D^{p} 
-%         \int_{\Omega} |\nabla u|^{p} dx
-%         .
-    \end{align*}
-    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
-
-    Very briefly verify that density argument: 
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$.
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
-    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ is the desired sequence that approximates $u$. 
-\end{proof}
-
-The following potential construction and upper bound for the Poincar\'e--Friedrichs constant 
-serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_m = T$.
-    For any $1 \leq l \leq m$, let $F_{l} = T_{l} \cap T_{l-1}$.
-    Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
-%         &\leq 
-%         \rho(\calT)^{\frac m p}
-%         C_{{\rm PF},T_{0},p} 
-%         \| \nabla u \|_{L^{p}( T_{0} )}
-%         +
-%         \sum_{l=1}^{m} 
-%         \rho(\calT)^{\frac {m-l} p}
-%         C_{{\rm PF},T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}(T_{l})} 
-%         \\&\qquad 
-%         +
-%         \sum_{l=1}^{m} 
-%         \rho(\calT)^{\frac {m-l} p} \xi(\calT)
-%         C_{{\rm PF},T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}(T_{l-1})} 
-%         \\
-        &\leq 
-        \rho(\calT)^{\frac m p}
-        C_{{\rm PF},T_{0},p} 
-        \| \nabla u \|_{L^{p}( T_{0} )}
-        \\&\qquad 
-        +
-        \sum_{l=1}^{m} 
-        \rho(\calT)^{\frac {m-l} p}
-        C_{{\rm PF},T_{l},F_{l},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{l})} 
-            +
-            \rho(\calT)^{\frac {1} p}
-            \xi(\calT)
-            \| \nabla u \|_{L^{p}(T_{l-1})} 
-        \right)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \| w_{m} \|_{L^{p}(T_m)}
-%         &\leq 
-%         \sum_{l=1}^{m} 
-%         \rho(\calT)^{\frac{m-l}{p}}
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}( T_{l} )}
-%         +
-%         \rho(\calT)^{\frac m p}
-%         C_{{\rm PF},T_{0},p} 
-%         \| \nabla u \|_{L^{p}( T_{0} )}
-%         .
-%     \end{align*}
-%     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
-\end{theorem}
-
-\begin{proof}
-    Let $u \in W^{1,p}(\Omega)$. 
-    First, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
-    \[
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \]
-    In particular, $c_{0} := u - w_0$ is a constant function.
-
-    Now, let $T \in \calT$ be any $n$-simplex. 
-    By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
-    For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    We use a recursive argument.
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $c_{0} = u - w_{m-1}$.
-    In particular, $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{m-1}$. 
-    % Let $\hat T$ be the reference simplex.
-    % We fix affine diffeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
-    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
-    %
-    We define $w'_{m} := w_{m-1} \circ \Xi \in W^{1,p}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
-    %
-    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        .
-    \end{align*}
-    %Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
-    There exists $w''_{m} \in W^{1,p}(T_{m})$ such that 
-    \begin{align*}
-        \nabla w''_{m} = \nabla u_{|T_{m+1}} - \nabla w'_{m}, 
-        \quad 
-        \trace_{F_{m}} w''_{m} = 0.
-    \end{align*}
-    This is true because 
-    \begin{align*}
-        \trace_{F_{m}}( \nabla u - \nabla w'_{m} ) 
-        &= 
-        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m}
-        \\&= 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m}
-        = 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \nabla w_{m} = \nabla w'_{m} + \nabla w''_{m} = \nabla w'_{m} + \nabla u - \nabla w'_{m} = \nabla u,
-        % \end{gather*}
-        \\
-        % \begin{gather*}
-        \trace_{F_{m}} w_{m} = \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_{m}$. 
-    In particular, $c_{0} = u - w_{m}$. 
-    Lemma~\ref{lemma:mixedbconsimplex} gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
-        \\&
-        \leq 
-        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
-    \begin{align*}
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
-        \cdot 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
-        \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \cdot 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
-        .
-    \end{align*}
-    Putting this all together, 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{m})} 
-            + 
-            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \rho(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    The existence of $w \in W^{1,p}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-
-\begin{remark}
-    The previous theorems, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} 
-    depend on only a few parameters of the triangulation:
-    the length of any traversal from the root simplex, the ratios of the volumes of adjacent simplices,
-    the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex. 
-    The aforementioned local Poincar\'e--Friedrichs constants can generally be estimated in terms of shape-parameters. 
-    If the face patches of the triangulation are convex, then better estimates are possible. 
-\end{remark}
-
-% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
-% Lemma 5.5
-
-\section{Shellable triangulations of manifolds}\label{section:advancedtriangulations}
-
-We return to the theory of triangulations,
-as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulate manifolds. 
-Our particular interest are manifold triangulations that are \emph{shellable}.
-Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
-Patches within triangulations of dimension two and three are examples of such shellable complexes. 
-The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures} are our main references for this section. 
-We also refer to Lee's monograph~\cite{lee2011topological} for any further background on manifolds.
-
-\subsection{Triangulations of manifolds}
-
-We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
-We recall that this means that for every $x \in \underlying{\calT}$
-there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
-such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| \leq 1 \}$
-or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
-In the former case, $x$ is called an \emph{interior point}, and in the latter case $x$ is called a \emph{boundary point}. 
-Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional.
-
-The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball,
-and we sometimes call this a \textit{$n$-disk} triangulation.
-An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere. 
-\\
-
-We know that any manifold $\calM$ has got a topological boundary $\partial\calM$, possibly empty. 
-If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$. 
-We gather a few helpful observations on how these notions relate to triangulations.
-While the reader might deem them obvious, we nevertheless include proofs.
-
-\begin{lemma}\label{lemma:boundarysimplices}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
-    \begin{itemize}
-        \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
-        \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
-        \item The simplices contained in the boundary constitute a triangulation of the boundary.
-        % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    We prove these statements in several steps.
-    \begin{enumerate}
-    \item 
-    We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
-    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$. 
-    Since the boundary $\partial \calM$ is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
-
-    \item 
-    We prove an auxiliary result. 
-    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
-    Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
-    we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    By the Jordan-Brouwer separation theorem~\cite{}, $Y \setminus (X \cup \{y\})$ has got two connected components,
-    and thus $Y \setminus X$ has got two connected components.
-
-    \item
-    Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
-    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
-    Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
-    The intersection of any two of them is $F$, and their interiors are disjoint.
-
-    Consider the case that $z_F$ lies on the boundary of $\calM$. 
-    If $F$ is contained in at least two distinct $n$-simplices of $\calT$,
-    then we can construct an embedded $n$-dimensional open ball that contains $z_F$.
-    But that contradicts $z_F$ being on the boundary. 
-    So any boundary face can only be contained in one single $n$-simplex.
-
-    If $z_F$ is an interior point of $\calM$, 
-    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
-    At the same time, $X = F \cap \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere of dimension $n-2$. % TODO: proofread
-    We see that $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
-    But by the auxiliary result above, $K = 2$. 
-    We conclude that $F$ is contained in two $n$-simplices of $\calT$.
-%     But by construction $\partial \mathring B_F \setminus X$ is homeomorphic to $S \setminus S'$,
-%     which has exactly two distinct connected components according to the Jordan-Brouwer separation theorem.
-%     If an inner face $F$ were contained in only one $n$-simplex,
-%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-%     So each inner face is contained in exactly two $n$-simplices. 
-%     \todo{More details}
-
-%     If $F$ is contained in only one $n$-simplex, then it must be a face in the boundary of $\calM$. 
-%     If $F$ were contained in at least two $n$-simplices,
-%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex. 
-%     \todo{More details}
-%     {\color{blue}
-%     The doubling $M_{D}$ of the manifold $M$ is obtained by gluing $M$ to a copy of itself along the boundary.
-%     The triangulation $\calT$ can be doubled to get a triangulation of the doubled manifold.
-%     Any boundary face is an interior face of the doubled manifold two $n$-simplices of the doubled triangulation.
-%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex of $\calT$. 
-%     }
-
-    \item
-    Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
-    Every $x \in \calM$ is an inner point of some simplex $S \in \calT$. 
-    If $x \in \partial \calM$ is a boundary point, then $S$ must be a boundary simplex, 
-    so the boundary simplices triangulate all of $\partial \calM$.
-    \end{enumerate}
-    All desired results are thus proven. 
-\end{proof}
-
-Suppose that $\calT$ is an $n$-dimensional simplicial complex that triangulates a manifold. 
-Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
-% The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
-All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
-We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
-% We see that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
-% Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
-% Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
-% The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space. 
-\\
-
-We continue with a few more observations about manifold triangulations.
-
-\begin{lemma}\label{lemma:startopology}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
-    \begin{itemize}
-        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
-        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
-        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    We prove these statements in several steps.
-    \begin{enumerate}
-    \item 
-    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint $z_F$, and dimension $k$.
-    Let $\calS := \patch_{\calT}(S)$ be its star. 
-    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
-    has vertices $v_0, v_1, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$. 
-    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
-    \begin{align*}
-        v_0, \dots, v_{i-1}, z_F, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
-    \end{align*}
-    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
-    that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS' = \patch_{\calS'}(z_F)$. 
-    In particular, $z_F$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$.
-
-    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
-    For $\delta > 0$ small enough, 
-    \begin{align*}
-        B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
-        \quad 
-        S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
-    \end{align*}
-    are subsets of $\patch_{\calT}(S)$.
-    For each $K \in \patch_{\calT}(S)$ that contains $S$ and which has the complementary simplex $F_S$, 
-    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
-    such that 
-    $\phi_{K|S}$ is the identity,
-    such that 
-    $\phi_{K}(S_F) = S_{\delta}(z)$,
-    and such that 
-    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$.
-
-    If $z$ is an inner vertex of $\calS'$, 
-    then the boundary simplices of $\calS'$,
-    which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
-
-    If $z$ is a boundary vertex of $\calS'$,
-    which is the case if and only if $S$ is a boundary simplex, 
-    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
-    which is a topological ball of dimension $n-1$. % TODO: explain why
-
-    \item 
-    We show that each vertex star is strongly connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere is strongly connected. 
-    Now, if $n \geq 1$, then any vertex star in an $(n+1)$-dimensional manifold triangulation is strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
-    The induction argument implies that each vertex star in $\calT$ is strongly connected.
-
-    \item 
-    If the underlying space is connected, then we easily see that the union of the $1$-simplices is path-connected.
-    Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$.
-    We also notice that each vertex star is strongly connected. 
-    We can thus change the first sequence to another $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
-    such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-    \end{enumerate}
-    All relevant results are proven. 
-\end{proof}
-
-\begin{remark}
-    Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
-    Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
-    % Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. ~\cite{todo}
-    We therefore are not in pursuit of any easy combinatorial property that indicates whether a simplicial complex (without any further specific assumptions) triangulates a manifold.
-
-    Conversely, not all topological manifolds, even if compact, can be described as a triangulation. 
-    Such manifolds appear in dimension four and higher:
-    one example is the E8 manifold, which is a compact simply-connected topological $4$-manifold that is homeomorphic to the underlying set of any simplicial complex.
-The construction of such counterexamples typically involves an infinite procedure.
-%     For each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. 
-\end{remark}
-
-\begin{figure}
-    \centering
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (1) \end{tabular}
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (2) \end{tabular}
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (3) \end{tabular}
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (4) \end{tabular}
-    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation. 
-    (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
-    (2) The new edge patch may already be a subset of the subtriangulation
-    (3) An inadmissible choice because the new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like
-    (4) An inadmissible choice because the new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
-\end{figure}
-
-% \begin{figure}
-%     \centering
-%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
-%         \coordinate (O) at (0, 0);
-%         \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
-%         \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
-%         \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
-%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-%         \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
-%         \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
-%         \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
-%         \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
-%         \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
-%         \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
-%         \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
-%     \end{tikzpicture}\\ (1) \end{tabular}
-%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
-%         \coordinate (O) at (0, 0);
-%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-%         \draw (O) -- (A);
-%         \draw (O) -- (B);
-%         \draw (O) -- (C);
-%         \draw (O) -- (X);
-%         \draw (O) -- (Y);
-%         \draw (O) -- (Z);
-%         %
-%     \end{tikzpicture}\\ (2) \end{tabular}
-%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
-%         \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
-%         % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
-% 
-%         \coordinate (O) at (0, 0);
-%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-%         \coordinate (T) at ({0}, {0}, {3});
-% 
-%         \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
-% 
-%     \end{tikzpicture}\\ (3) \end{tabular}
-%     \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
-% \end{figure}
-
-% 3. Shellability 
-\subsection{Shellable simplicial complexes}
-
-The notions of \emph{shelling} and \emph{shellable triangulation} have been discussed widely in combinatorial topology and polytopal theory. 
-Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation of a manifold.
-We thus build upon the notion of shelling, as introduced in~\cite[Definition 8.1]{ziegler2012lectures},
-and our definition of shelling is equivalent to the notion of the shellings of simplicial complexes in the aforementioned reference; see also~\cite[Remark~8.3]{ziegler2012lectures}.
-
-Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-the gluing interface is a triangulated submanifold of the boundary. 
-This forces the intermediate triangulations to be particularly well-shaped. 
-We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, 
-as this enables the inductive method of proof.
-\\
-
-Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
-For any enumeration, we call 
-\begin{align*}
-    I_m 
-    := 
-    \big( 
-        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
-    \big) 
-    \cap 
-    T_{m+1}
-\end{align*}
-be the $m$-th \textit{interface set}. 
-% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface $I_m$ is a manifold of dimension $n-1$.
-
-\begin{remark}
-    We interpret a shelling as the construction of a triangulation 
-    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
-    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
-\end{remark}
-\begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
-    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
-    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
-\end{remark}
-
-The reason of our interest in shellable simplicial complexes is that they can be constructed by successive adhesion of simplices to intermediate complexes, 
-such that the interface is well-behaved: it is a simplicial disk or a simplicial sphere. 
-That leads to the following important consequence.
-
-\begin{lemma}    
-    Suppose that an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, 
-    that is, each simplex of dimension $n-1$ is contained in at most two simplices. 
-    % DONE: what is non-branching?
-    Then
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}
-    $$ 
-    is a manifold with boundary for all $0 \leq m \leq M$.
-    % 
-    In particular, $X_{m}$ is a topological $n$-ball when $m < M$, 
-    and 
-    $X_{M}$ is either a topological $n$-ball or topological $n$-sphere. 
-\end{lemma}
-\begin{proof}  
-    We prove this claim by induction. 
-    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. 
-    Suppose that $X_m := T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a topological $n$-ball and that $T_{m+1}$ is the next $n$-simplex in the shelling.
-    By definition, $I_{m+1} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
-    and it is triangulated by some faces of $T_{m+1}$ and their subsimplices.
-
-    Let $F$ be such a face. 
-    By assumption, $F$ must be contained in exactly one $n$-simplex of $T_{0}, T_{1}, \dots, T_{m}$,
-    and $F$ is in the boundary of $X_{m}$. We conclude that $I_{m}$ triangulates a submanifold of the boundary of $X_{m}$.
-
-    On the one hand, 
-    if $I_{m+1}$ is the entire boundary of $T_{m+1}$, 
-    then it must also be the boundary of the topological $n$-ball $X_{m}$. 
-    Hence $X_{m} \cup T_{m+1}$ must be a topological $n$-sphere and thus a manifold without boundary, which requires $m = M$.
-    On the other hand, 
-    if $I_{m+1}$ is a proper subset of the entire boundary of $T_{m+1}$, 
-    then $X_{m} \cup T_{m+1}$ is still a topological $n$-ball.
-\end{proof}
-
-We collect important examples of shellable triangulations.
-Our main interest are local stars or stars within triangulations.
-
-\begin{example}
-    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
-    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
-\end{example}
-\begin{example}
-    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.~\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
-\end{example}
-
-\begin{lemma}    
-    Any simplicial $2$-disk is shellable.
-    Any simplicial $2$-sphere is shellable. 
-\end{lemma}
-\begin{proof}
-    First, 
-    let $\calS$ be any triangulation of a $2$-sphere. 
-    By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-disk.
-    Any shelling of that disk can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
-    So it remains to show that any triangulation $\calT$ of the two-dimensional disk is shellable. 
-    We will construct the shelling in reverse.
-
-    %\todo{Double check this proof and make it more explicit.}
-    Write $M = |\calT|$. 
-    There is nothing to show if $\calT$ contains only one triangle. 
-    We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
-    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
-    and a triangle is not good in $\calT$ if that intersection is either empty only some of its vertices, or a vertex and the opposite edge.
-    % TODO: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
-    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk that contains at least two triangles also contains at least two good triangles.
-
-    Clearly, this is the case if the triangulation of the $2$-disk contains two triangles. 
-    Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
-    and assume that $\calT$ includes $N+1$ triangles. 
-    There are at least two triangles with an edge on the boundary. 
-    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$,
-    then there exists a triangle $T'$ that intersects $\partial M$ 
-    in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two strongly connected components, each of which is a topological $2$-disk.
-    By the induction assumption, each of those components contains at least two triangles 
-    that are good in the respective component. 
-    So each component has at least one triangle that is good in $\calT$.
-
-    % There exists a triangle $T' \in \calT$ with at least one edge in the boundary. 
-    % If $T'$ is good, then we are already done. 
-    % Otherwise, $T'$ intersects the boundary at one edge and its opposing vertex.
-    % \todo{MV:But what if this is the neighbor of $T'$ and adding $T'$ back makes the triangle bad?}
-
-    Since $\calT$ triangulates a $2$-disk,
-    it contains a good triangle $T$. 
-    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
-    If $T$ intersects with the boundary in exactly one or two edges, 
-    then $\overline{M \setminus T}$ is still a topological $2$-disk.
-    The triangulation $\calT'$ that is obtained by removing $T$
-    is a triangulation of some $2$-disk that intersects $T$ only at either two or one edges.
-    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
-%     Let $\calT$ be a simplicial $2$-disk. 
-%     If $\calT$ contains only one triangle, then there is nothing to show. 
-%     Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
-%     {\color{red}Needs proof}. 
-%   
-%     Now let $\calS$ be any simplicial $2$-sphere. 
-%     By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
-%     Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
-\end{proof}
-
-\begin{lemma}
-    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
-    Then $\patch_{\calT}(V)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    Without loss of generality, $V$ is the origin. 
-    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
-    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
-    which does not affect shellability. 
-    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
-    and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
-    % TODO: cite E&V Math Comp 2020, Lemma B1. 
-\end{proof}
-
-\begin{lemma}
-    Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
-    Then $\patch_{\calT}(S)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    The statement is clear if $S$ is an inner or boundary face of $\calT$. 
-    The statement is also easily verified if $S$ is an inner or boundary edge of $\calT$.
-    When $S$ is an inner vertex, then we apply the preceding lemma.
-
-    It remains to consider the case where $S$ is a boundary vertex. 
-    Then the triangles of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-disk 
-    which is shellable,
-    and any such shelling can be extended to a shelling of $\patch_{\calT}(S)$.
-\end{proof}
-
-\begin{remark}
-    Not all trianguable sets admit a triangulation that is also shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
-
-    For example, there exists a non-shellable triangulation of a tetrahedron. 
-    If we extend this triangulation to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, 
-    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the dimension is larger than the three.
-\end{remark}
-
-\section{Review of vector calculus and exterior calculus}\label{section:calculus}
-
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-
-We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
-Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
-In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
-\[
-    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-\]
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
-\[
-    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \quad 
-    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\]
-We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
-$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
-and
-$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
-for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
-\begin{subequations}\label{eq_definition_piola}
-\begin{align}
-    \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
-    \phi^{\divergence}(\bfw) &= \left( \adj(\Jacobian\phi) \bfw \right)  \circ \phi, \\
-    \phi^{\rm b}(v) &= \left( \det(\Jacobian\phi) v \right)  \circ \phi,
-\end{align}
-\end{subequations}
-\todo{MWL: double check the correct sign convention, what is inverse and what is not}
-and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
-These mappings are invertible. 
-%
-% TODO: bounds on the Jacobian transform 
-%
-We use the commutativity relations 
-\begin{subequations}\label{eq_piola_commute}
-\begin{align}
-    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv), 
-    % TODO: watch the sign 
-    \\
-    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw),
-\end{align}
-\end{subequations}
-where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
-We summarize this as a commuting diagram:
-\begin{align*}
-    \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
-        \\
-        @VV{\phi^{\grad}}V 
-        @VV{\phi^{\curl}}V 
-        @VV{\phi^{\divergence}}V 
-        @VV{\phi^{\rm b}}V 
-        \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
-    \end{CD}
-\end{align*}
-
-\begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
-\end{remark}
-
-%
-% trace properties 
-%
-
-%\section{Review of exterior calculus}
-
-Having discussed vector analysis, we review exterior calculus. 
-We give a brief introduction into this topic, and refer to the literature for further background~\cite{...}. 
-Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
-Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
-if 
-\[ 
-    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
-    = 
-    \text{sign}(\pi) 
-    u( v_1, v_2, \ldots, v_k ) 
-\]
-for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
-By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
-Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
-
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
-their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
-defined by the formula 
-\[
-    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
-    = 
-    \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\]
-for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
-The exterior product is bilinear and associative, and satisfies 
-\begin{align*}
-    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
-    \quad 
-    u_1 \in \Alt^{k}(V),
-    \quad 
-    u_2 \in \Alt^{l}(V).
-\end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined as 
-\begin{align*}
-    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
-    \quad 
-    v_1, v_2, \ldots, v_{k-1} \in V.
-\end{align*}
-We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
-Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
-Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
-This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
-To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
-and introduce the basic $k$-alternators 
-\begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
-\end{align*}
-These define a basis of $\Alt^{k}(\bbR^{n})$.
-Note that 
-$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
-In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).
-
-We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
-which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
-The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
-
-We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
-which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
-Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\[
-    \omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\]
-where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
-\[
-    \cartan\omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \sum_{j=1}^{n} 
-    \frac{\partial \omega_{\sigma}}{\partial x^j} 
-    \, \cartanx^j \wedge 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\]
-The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
-Moreover, it satisfies the Leibniz rule:
-\[ 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \eta \in C^{\infty}\Alt^{l}(\Omega).
-\]
-Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a canonical norm, we can consider the pointwise norms of differential $k$-forms. 
-% First, we notice that the % TODO: introduce a norm 
-We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
-such that its pointwise norm is $p$-integrable. 
-The exterior derivative is defined in the sense of distributions and we introduce 
-\[
-    W^p\Alt^{k}(\Omega) 
-    := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
-\]
-We observe that $u \in L^p\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^p\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
-We let $W^p_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^p\Alt^{k}(\Omega)$ 
-for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^p\Alt^{k}(\bbR^{n})$. 
-The space $W^p_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.
-
-Lastly, we are also interested in differential forms whose trace vanishes along only a part of the boundary. 
-Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^p\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
-\begin{align*}
-    \int_{B_r(x)} \cartan v \wedge \tilde u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
-    .
-\end{align*}
-
-We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
-Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^p\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\[ 
-    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    := 
-    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\]
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.
-
-% TODO: transformationssatz
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms can be translated into classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \[
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \]
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \[ % TODO: what is the convention for the curl and rotation ? look up in the textbooks?
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \]
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
-
-% TODO: spaces with boundary conditions: grad, curl, divergence, exterior derivative; approximation properties
-
-Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\begin{lemma}
-%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
-%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
-%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
-\end{lemma}
-
-% \begin{lemma} % TODO: possibly useful
-%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-% \end{lemma}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}_{0}\Lambda^{k}(\Omega)$.
-\end{lemma}
-\begin{proof}
-    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
-    By the dominated convergence theorem and because $u$ has a weak derivative,
-    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
-    \begin{align*}
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v
-        &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x)
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x)
-        \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x)
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x)
-        = 
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v
-        .
-    \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
-
-    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in \bfW^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
-    Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in \bfW^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
-    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
-    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
-    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
-    The desired result follows. 
-\end{proof}
-
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
-
-We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-We already know the optimal constants for the gradient operator over convex domains,
-and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
-
-For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
-and the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our explicit purpose are explicit bounds for the operator norms, which are of independent interest. 
-\\
-
-\todo{cite Guzman and Salgado at the right spot.}\\
-
-We begin with introducing the Costabel-McIntosh kernel.
-For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{eq:Gl}
-  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
-\end{equation}
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
-we then define the integral operators
-\begin{align}
-  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy
-  \\
-  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
-\end{align}
-We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
-\\
-
-We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
-\begin{align*}
-    G_{\ell}(x,y) 
-    &= 
-    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
-    \\
-    &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
-    .
-\end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives % TODO: define D
-\begin{align*}
-    G_{\ell}(x,y) 
-    &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
-    \\
-    &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
-\end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-We begin with the Poincar\'e operator. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
-We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\ell} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_D(0)} |z|^{k+1-n} dz
-    =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
-    =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
-    =
-    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-    .
-\end{align*}
-We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
-    \\&
-    =
-    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
-    .
-\end{align*}
-Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{n-\ell}$. 
-In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-    &\leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\[
-    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
-\]
-% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
-% 
-We analyze the Bogovski\u{\i} potential operator with similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\ell} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\ell} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-    \\&\leq 
-    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
-    .
-\end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_D(0)} |z|^{k+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-%     .
-% \end{align*}
-% We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
-    \\&
-    =
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{\ell-1}$. 
-In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
-    &\leq 
-    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\[
-    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
-\]
-% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
-Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
-that is, the reconstructed potential has support contained within $\overline\Omega$. 
-\\
-
-Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\ell} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
-leading to 
-\begin{align*}
-    \Bogov_{\ell} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
-    \chi_{\Omega}\left(y+t(x-y)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    .
-\end{align*}
-% We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\ell-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
-% 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\ell,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
-    ,
-    \\
-    \Bogov_{\ell,a} u(x) 
-    &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
-    .
-\end{align*}
-By definition,
-\begin{align*}
-    \Poinc_{\ell} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;,
-    \quad 
-    \Bogov_{\ell} u(x) 
-    =
-    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da\;
-    .
-\end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-That discussion is classical and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators 
-are not yet included in the published literature.
-
-Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\ell,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\ell,a} u(x) 
-    &= 
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
-    ,
-\end{align*}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\ell+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    \;\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \;\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Poinc_{\ell,a} u(x)
-    +
-    \Poinc_{\ell+1,a} \cartan u(x)
-    \\&
-    =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
-    \cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x)
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell} u = u$.
-
-The discussion for the Bogovski\u{\i} operator is almost analogous. 
-Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \Bogov_{\ell,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Bogov_{\ell,a} u(x) 
-    &= 
-    \ell 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
-    ,
-\end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \Bogov_{\ell+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    \;\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \;\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Bogov_{\ell,a} u(x)
-    +
-    \Bogov_{\ell+1,a} \cartan u(x)
-    \\&
-    =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
-    \cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Bogov_{\ell} u(x) + \Bogov_{\ell+1} \cartan u(x)
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell} u = u$.
-\\
-
-We are in the position to establish the main results of this section.
-This includes upper bounds for the Poincar\'--Friedrichs inequalities that we have been looking for. 
-Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.
-
-\begin{theorem}
-    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-        D
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
-        D
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
-    If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
-\end{theorem}
-\begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Poinc_{\ell  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\ell-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\ell} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-    % TODO: definition of weak derivative + definition of boundary condition 
-    % 
-    This completes the proof. 
-\end{proof}
-
-% DONE: Density of C infty mit oder ohne c.
-
-\begin{remark}
-    The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-    while they are increasing for the Bogovski\u{\i} operator.
-    This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over convex domains~\cite{guerini2004eigenvalue}.
-\end{remark}
-
-\begin{remark}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % 
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-\end{remark}
-
-\section{Extension operator on finite element stars}\label{section:extension}
-% Only define the geometric mapping and its important quantities
-% Leave the function spaces etc. for later
-
-Suppose that any $n$-dimensional simplex $T$ with some subsimplex $F$.
-We want to find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is only on one side of the hyperplane.
-
-\begin{lemma}\label{lemma:oppositesubsimplex}
-    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
-    Let $F, F'$ be the two subsimplices of $T$ with respective sets of vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
-    Then $T$ lies on one side of the affine subspace
-    \[
-        A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
-    \]
-    Moreover, $F = T \cap A$.
-\end{lemma}
-\begin{proof}
-    Evidently, $A$ has dimension $n-1$ and $F \cap A \cap T$.
-    Let us now suppose that $x \in A \cap T$.
-    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
-    \begin{align}
-        x &= 
-        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
-        \\&
-        = 
-        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
-        + 
-        \sum_{i=1  }^{k  } \lambda_{i} v_i 
-        + 
-        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
-        + 
-        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
-        .
-    \end{align}
-    We know $x$ can be written as a unique convex combination of the vertices of $T$.
-    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive. 
-    If $x \notin F$, then at least one of these coefficients must be negative. 
-    But then their sum must be negative, which is a contradiction. 
-    The desired statement follows.         
-\end{proof}
-
-\begin{lemma}    
-    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
-    For $0 \leq m < M$, write 
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
-        \qquad 
-        I_{m} := X_{m} \cap T_{m+1}.
-    $$ 
-    Then $I$ is the union of $k$ different facets of $T$, 
-    and their intersection is a simplex $S \in \calT$ of dimension $n-k$.
-    Moreover, 
-    $$
-        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
-    $$
-\end{lemma}
-\begin{proof}
-    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
-    that constitute the local patch around some simplex $S$ of dimension $n-k$.
-\end{proof}
-
-\begin{theorem}
-    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
-    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let $M := |\patch_{\calT}(S)| \setminus T$. 
-    There exists a bi-Lipschitz mapping
-    \begin{align*}
-        \varphi : T \rightarrow M
-    \end{align*}
-    satisfying
-    \begin{align*}
-        \Lip( \varphi,      T ) \leq \Cvier{n}{k},
-        \quad 
-        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k},
-    \end{align*}
-    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
-\end{theorem}
-
-\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
 \begin{proposition}\label{proposition:guerinisavo}
@@
 \end{proof}
-
-\subsection{Inequalities for partial boundary conditions on a single simplex}
-
-\begin{lemma}
-    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
-    Then 
-    \begin{align*}
-        \| u \| \leq 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-    such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
-    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
-    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
-
-    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
-    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
-
-    The operator norm bound of the potential operator shows 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        \\&
-        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        .
-    \end{align*}
-    We use the pullback estimates 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        \| \Jacobian\varphi \|_{\infty}^{k}
-        |\det\varphi^{-\frac{1}{p}}|
-        \cdot 
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        .
-    \end{align*}
-    \begin{align*}
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
-        2^{n-l}
-        \| \hat f \|_{L^{p}(\hat T)} 
-        \leq 
-        2^{n-l}
-        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
-        |\det\varphi^{\frac{1}{p}}|
-        \cdot 
-        \| f \|_{L^{p}(T)} 
-        .
-    \end{align*}
-\end{proof}
-
-\subsection{Constructions over shellable triangulations}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $w \in \bfH(\divergence,\Omega)$ with $\divergence u = \divergence w$ and 
-    \begin{align*}
-        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This is a reduction to Friedrichs' inequality. 
-    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
-    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
-    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
-    which has the same smallest singular value. 
-\end{proof}
-
-\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
-    Let $T$ be an $n$-simplex and with a face $F$. 
-    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
-    \end{align*}
-    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,k,p}
-        \leq 
-        \diam(T)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
-    Then $\cartan \hat u = \hat g$. 
-    % 
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    We define $\tilde g = \cartan \tilde u$
-    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
-    \begin{gather*}
-        \| \tilde u \|_{L^{p}(\hat U)} 
-        \leq 
-        C_{???} 
-        \| \tilde g \|_{L^{p}(\hat U)}
-        .
-    \end{gather*}
-    In addition to that, 
-    \begin{gather*}
-        \| u \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \hat u \|_{L^{p}(\hat T)}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \tilde u \|_{L^{p}(\hat U)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\hat U)}
-        \leq 
-        2^{\frac n p}
-        \| \hat g \|_{L^{p}(\hat T)}
-        \leq 
-        2^{\frac n p}
-        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
-        \| \cartan u \|_{L^{p}(T)}
-        .
-    \end{gather*}
-    The second inequality follows.
-\end{proof}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
-    \end{align*}
-\end{theorem}
-
-\begin{proof}
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \[
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \]
-    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
-
-    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        .
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
-
-    We want to estimate norms. 
-    Lemma~\ref{lemma:todo} gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
-        \\&
-        \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
-    \begin{align*}
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
-    Putting this all together, 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \left( 
-            \| \cartan u \|_{L^{p}(T_{m})} 
-            + 
-            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(U_{m-1})} 
-%         \\&
-%         \leq  
-%         \rho(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-%         + 
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
-%         \| \cartan u \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-
-\subsection{Numerical examples}
-
-% Square 
-% L-shaped 
-% Slit
-
-% Cube 
-% Fichera
-% Crossed bricks
 
@@
 \end{proof}
-
-% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
-% https://eudml.org/doc/258483
-% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
-% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
-\begin{lemma}
-    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
-    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
-    \begin{align*}
-        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R^{2}/r % euclidean 
-    \end{align*}
-    If $K$ is convex, then 
-    \begin{align*}
-        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
-        \\
-        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
-    \end{align*}
-\end{lemma}
-
-\begin{lemma}
-    .
-\end{lemma}
-
-\section*{Acknowledgments}
-
-\bibliographystyle{plain}
-\bibliography{library}
-
-\end{document}

### 2024-07-22 main.tex
Update on Overleaf.

@@
 
+We recall a specialization of this result.
+
+\begin{lemma}\label{theorem:starreflection:facepatch}
+
+\end{lemma}
+
 % https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
@@
 \end{lemma}
-\begin{lemma}
-    .
-\end{lemma}
+\begin{proof}
+    .
+\end{proof}
 
@@
     which has the same smallest singular value. 
-\end{proof}
-
-\begin{proposition}\label{proposition:guerinisavo}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
-    Moreover, 
-    \begin{align*}
-        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
-    \end{align*}
-\end{proposition}
-\begin{proof}
-    The result is true if $\Omega$ has a smooth boundary. 
-    Now suppose that $\Omega$ is a Lipschitz domain. 
-\end{proof}
-
-\begin{proof}
-    The desired results are known for smoothly bounded domains;
-    see Theorem~2.6 of \cite{guerini2004eigenvalue} for % decay in k
-    see \cite[Theorem~1.3]{guerini2004spectre} for
-    \begin{align*}
-        C \diam(\Omega)^{-2} 
-        \leq 
-        \lambda_{k},
-        \qquad 
-        C := 
-        \left\{\begin{array}{ll}
-            \frac{n-1}{n e^{3}} & \text{ if } k=0
-            \\
-            \frac{k(n-k)}{ne^{3}} & \text{ if } 1 \leq k \leq n-1
-            \\
-            \lambda_{1,0}(B) & \text{ if } k = n % Dirichlet eigenvalue over a ball
-        \end{array}\right. 
-        % \frac{\max_{k(n-k),n-1}}{ne^{3}} \diam(\Omega)^{-2}        
-    \end{align*}
-    see \cite{guerini2004eigenvalue} for $n \geq 3$, 
-    \begin{align*}
-        \frac{4}{n^{2} \tbinom{n}{k-1} \diam(\Omega)^{2} } \leq \lambda_{k}
-    \end{align*}
-
-    For each $0 \leq k \leq n$ we let $\mu_{k}$ be the smallest non-zero eigenvalue of the Hodge-Laplace operator acting on $k$-forms.
-For each $0 \leq k \leq n-1$, we let $\sigma_{k}$ be the smallest non-zero singular value of the exterior derivative $\cartan : L^{2}\Lambda^{k}(\Omega) \rightarrow L^{2}\Lambda^{k+1}(\Omega)$.
-We have the relation
-    \begin{align*}
-        \mu_{k} = \min( \sigma_{k}, \sigma_{k-1} )^{2}.
-    \end{align*}
-    We first consider the case where $\Omega$ is strictly convex with smooth boundary. 
-    According to Theorem~2.6 of \cite{guerini2004eigenvalue},
-    \begin{align*}
-        \mu_{0} = \mu_{1} < \dots < \mu_{n}.
-    \end{align*}
-    By definition, we have $\mu_{n} = \sigma_{n-1}^{2}$. 
-    Suppose that we know $\mu_{k} = \sigma_{k-1}^{2}$ for some $2 \leq k \leq n$. Then 
-    \begin{align*}
-        \sigma_{k-1}^{2} = \mu_{k} > \mu_{k-1} = \min( \sigma_{k-1}, \sigma_{k-2} )^{2}
-    \end{align*}
-    implies $\mu_{k-1} = \sigma_{k-2}^{2}$. 
-    Iterating this, we find 
-    \begin{align*}
-        \sigma_{0} < \sigma_{1} < \dots < \sigma_{n-1}.
-    \end{align*}
-    We have shown this when $\Omega$ is strictly convex with smooth boundary.
-
-    We now address the case where $\Omega$ is merely convex. 
-    According to Theorem~A of \cite{blocki1997smooth}, 
-    there exists a continuous convex function $\beta : \overline\Omega \rightarrow \bbR$ that equals zero along $\partial\Omega$, which is negative over $\Omega$, and whose Hessian over $\Omega$ has positive determinant.
-    This already implies that the Hessian of $\beta$ over $\Omega$ is always positive-definite, and so $\beta : \Omega \rightarrow \bbR$ is strictly convex.
-
-    For $\epsilon > 0$ small enough, the sublevel sets 
-    \begin{align*}
-        \Omega_{\epsilon} := \left\{ x \in \Omega \suchthat \beta(x) < -\epsilon \right\}
-    \end{align*}
-    are strictly convex smoothly bounded open sets compactly contained in $\Omega$. 
-    For convenience, we also write $\Omega_{0} := \Omega$.
-
-    We first show that for each $\rho > 0$ there exists $\epsilon > 0$ such that $\Omega \setminus \Omega_{\epsilon} \subseteq \partial\Omega + B_{\rho}(0)$. 
-    Indeed, if that were not the case, then there would exist $\rho > 0$ such that for any $\epsilon > 0$ we can find $x_{\epsilon}$ with $\beta(x_{\epsilon}) > -\epsilon$ but distance at least $\rho$ from $\partial\Omega$.
-We could then pick a subsequence converging to a point $x \in \Omega$ with $\beta(x) = 0$, which is a contradiction.
-
-    %%%%%%%%%%%%%%%%%%%%%%%%%
-    % TODO: from here on 
-    For $\rho > 0$ small enough, the mapping 
-    \begin{align*}
-        A : \partial\Omega \times [0,\rho] \rightarrow \bbR^{n}, \quad (x,s) \mapsto x - \frac{s}{|x|} x
-    \end{align*}
-    is bijective. It satisfies the bounds 
-    \begin{align*}
-        ..
-    \end{align*}
-    and 
-    \begin{align*}
-        ..
-    \end{align*}
-    % TODO:
-    Consequently, there exists $L > 0$ such that for all $\epsilon > 0$ small enough 
-    there exists $B_{\epsilon} : \Omega \rightarrow \Omega_{\epsilon}$ bi-Lipschitz with
-    \begin{align*}
-        \| \Id - B_{\epsilon} \|_{L^{\infty}(\Omega)} < L \epsilon,
-        \quad 
-        \| \Id - \Jacobian B_{\epsilon} \|_{L^{\infty}(\Omega)} < L \epsilon.
-    \end{align*}
-    %%%%%%%%%%%%%%%%%%%%%%%%%
-
-    %%%%%%%%%%%%%%%%%%%%%%%%%
-    For any $\epsilon \geq 0$, we let $X^{k}_{\epsilon} := H\Lambda^{k}(\Omega) \cap \ker\cartan$. 
-    Notice that $B_{\epsilon}^{\ast} X^{k}_{\epsilon} = X^{k}_{0}$. 
-    %
-    Consider any $0 \leq k \leq n-1$. 
-    Let $f \in H\Lambda^{k+1}(\Omega)$ with $\cartan f = 0$.
-    There exists $u_\star \in H\Lambda^{k}(\Omega)$ with $\cartan u = f$ 
-    because $\Omega$ is convex and thus contractible. % TODO: theorem 
-    Notice that $B_{\epsilon}^{-\ast} u_0 \in H\Lambda^{k}(\Omega_{\epsilon})$ 
-    with $\cartan B_{\epsilon}^{-\ast} u_\star = B_{\epsilon}^{-\ast} f$ over $\Omega_{\epsilon}$.
-    % 
-    \begin{align*}
-        ..
-    \end{align*}
-    % TODO
-    We conclude that $P^{k}_{\epsilon} \rightarrow P^{k}_{0}$ in the operator norm. 
-    In particular, the operator norms converge. 
-    %%%%%%%%%%%%%%%%%%%%%%%%%
-
-    For any $0 \leq k \leq n-2$ and $\epsilon > 0$ we have $\| P^{k}_{\epsilon} \| < \| P^{k+1}_{\epsilon} \|$,
-    so that $\| P^{k}_{0} \| \leq \| P^{k+1}_{0} \|$.
-    This had to be shown.
-%     
-%     There exists a bi-Lipschitz mapping $\varphi : \overline{B_1(0)} \rightarrow \Omega$. 
-%     We let $\varphi_{\eps} : \overline{B_1(0)} \rightarrow \bbR^{n}$ be smooth,
-%     uniformly bounded, and pointwise converging to $\varphi$ in the norm of $W^{1,\infty}$. 
-%     For $\epsilon > 0$ small enough, 
-%     the range $\Omega_{\eps}$ of each $\varphi_{\eps}$ is a smoothly bounded domain,
-%     and $\varphi_{\epsilon} : \overline{B_1(0)} \rightarrow \Omega_{\eps}$ is a diffeomorphism.
-%     The diameters of $\Omega_{\eps}$ converge to the diameter of $\Omega$.
-%     The desired claim now follows by the dominated convergence theorem % Given $u \in W^{2}\Lambda^{k}(\Omega)$
-    % TODO: show that the trafo converges to identity.
-    % Write the trafo as perturbation of the identity.
 \end{proof}
@@
 
+We assess the ``efficiency'' of our upper bounds with a few numerical examples in dimension 2D and 3D, with focus on the Hilbert space case $p=2$. 
+Unless the Poincar\'e--Friedrichs constants are known explicitly, we use eigenvalue estimates on a refined mesh as a proxy for the exact value.
+We compare the (approximations of) the exact values with the upper bounds obtained via Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+
 \subsection{Two-dimensional examples}
 
+We consider the following example domains in two dimensions:
+the unit square $\Omega_S$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{SS}$:
+\[
+    \Omega_{S}  = (-1,1)^2,
+    \qquad 
+    \Omega_{L}  = (-1,1)^2 \setminus (0,1)^2,
+    \qquad 
+    \Omega_{SS} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
+\]
 % Square 
@@
 
+We consider the following example domains in two dimensions:
+the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
+\[
+    \Omega_{C}  = (-1,1)^2,
+    \qquad 
+    \Omega_{F}  = (-1,1)^2 \setminus (0,1)^2,
+    \qquad 
+    \Omega_{B} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
+\]
 % Cube 

### 2024-07-23 main.tex
start trafo

@@
 
+\begin{proof}
+    \begin{itemize}
+    \item 
+    Consider any simplex $T$ with one vertex $v_0$ at the origin. 
+    Let $\lambda_{0}, \lambda_{1}, \dots, \lambda_{n}$ be the barycentric coordinates. 
+    The mapping 
+    \begin{align}
+        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+    \end{align}
+    maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
+    On the one hand, by the reverse triangle inequality,
+    \begin{align}
+        \left| F(x) - F(y) \right|
+        &\geq 
+        \left\| 
+            \frac{x}{\|x\|}
+            \sum_{i=1}^{n} \lambda_{i}(x)
+            -
+            \frac{y}{\|y\|}
+            \sum_{i=1}^{n} \lambda_{i}(y)
+        \right\|
+        \\&
+        \geq 
+        \left| 
+            \frac{\|x\|}{\|x\|}
+            \sum_{i=1}^{n} \lambda_{i}(x)
+            -
+            \frac{\|y\|}{\|y\|}
+            \sum_{i=1}^{n} \lambda_{i}(y)
+        \right|
+        \\&
+        = 
+        \left| 
+            \sum_{i=1}^{n} \lambda_{i}(x)
+            -
+            \sum_{i=1}^{n} \lambda_{i}(y)
+        \right|
+        \\&
+        = 
+        \left| 
+            \vec{1}
+            \cdot 
+            A^{-1}( x - y )
+        \right|
+     \end{align}
+     Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$.
+
+    \item 
+    We let $S^{n}_{\star} := S^{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
+    Suppose that $\bar x \in S^n$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
+    We define its stereographic projection as 
+    \begin{align}
+        \pi( \bar x ) 
+        = 
+        \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
+        .
+    \end{align}
+    This is a mapping $\pi : S^{n}_{\star} \rightarrow \bbR^{n}$. 
+    Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
+    \begin{align}
+        \pi^{-1}( y )
+        = 
+        \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
+        +
+        \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
+        .
+    \end{align}
+    \item 
+    Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
+    \begin{align}
+        \mu : \bbR^{n} \rightarrow \bbR^{n},
+        \qquad 
+        y \mapsto \frac{y}{\| y \|}.
+    \end{align}
+    \item 
+    \begin{align}
+        G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
+    \end{align}
+    \item 
+    \begin{align}
+        F^{-1} \pi^{-1} G^{-1} \mu G \pi F
+    \end{align}
+    \end{itemize}
+\end{proof}
+
 \section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}

### 2024-07-25 main.tex
Update on Overleaf.

@@
 
-% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
-% https://eudml.org/doc/258483
-% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
-% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
-\begin{lemma}
-    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
-    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
-    \begin{align*}
-        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R^{2}/r % euclidean 
-    \end{align*}
-    If $K$ is convex, then 
-    \begin{align*}
-        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
-        \\
-        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
-    \end{align*}
-\end{lemma}
 \begin{proof}
-    .
-\end{proof}
-
-\begin{proof}
+    We derive the estimate in several steps. 
     \begin{itemize}
+    \item 
+    We use the following auxiliary lemma. Suppose that $\|\cdot\|_{\alpha}$ and $\|\cdot\|_{\alpha}$ are two norms on a Banach space.
+    Let 
+    $$
+        F_{\alpha,\beta}(x) = \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} }.
+    $$
+    Then 
+    \begin{align*}
+        &
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\alpha}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
+        \right\|_{\alpha}
+        +
+        C_{\beta}^{\alpha} 
+        \left\| 
+            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\alpha}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left| 
+            \| x \|_{\alpha}
+            - 
+            \| y \|_{\alpha}
+        \right|
+        +
+        C_{\beta}^{\alpha} 
+        \frac{ \| y \|_{\alpha} }{ \| y \|_{\beta} } 
+        \left\| x - y \right\|_{\alpha}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        C_{\alpha}^{\beta} 
+        \left\| x - y \right\|_{\alpha}
+        +
+        C_{\beta}^{\alpha} 
+        C_{\alpha}^{\beta} 
+        \left\| x - y \right\|_{\alpha}
+        .
+    \end{align*}
+    \begin{align*}
+        &
+        \| 
+            F(x) - F(y) 
+        \|_{\beta}
+        \\&\leq 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\leq 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            + 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            + 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\leq 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+        \right\|_{\beta}
+            + 
+        \left\| 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+        \right\|_{\beta}
+            + 
+        \left\| 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| 
+            x - y
+        \right\|_{\beta}
+            + 
+        \frac{ \| y \|_{\beta} }{ \| x \|_{\beta} } 
+        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
+        + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \left| 
+            \frac{ 1 }{ \| x \|_{\beta} } 
+            - 
+            \frac{ 1 }{ \| y \|_{\beta} }  
+        \right|
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| 
+            x - y
+        \right\|_{\beta}
+        + 
+        % BEcause w l o g 
+        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
+        + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| 
+            x - y
+        \right\|_{\beta}
+            + 
+        % BEcause w l o g 
+        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
+            + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| x - y \right\|_{\beta}
+            + 
+        % BEcause w l o g 
+        \left\| x - y \right\|_{\alpha}
+            + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \frac{ \left\| x - y \right\|_{\beta} }{ \| y \|_{\beta} \| y \|_{\beta} }
+        \\&\leq 
+        C^{\alpha}_{\beta} 
+        C^{\beta}_{\alpha}
+        \left\| x - y \right\|_{\alpha}
+            + 
+        % BEcause w l o g 
+        \left\| x - y \right\|_{\alpha}
+            + 
+        C^{\alpha}_{\beta} 
+        C^{\beta}_{\alpha}
+        \left\| x - y \right\|_{\alpha}
+        .
+    \end{align*}
     \item 
@@
     \begin{align}
-        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right) = \frac{x}{\|x\|} \left( 1 - \lambda_{0}(x) \right)
     \end{align}
     maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
-    On the one hand, by the reverse triangle inequality,
+    On the one hand, 
+    \begin{align}
+        &
+        F(x) - F(y)
+        \\&
+        =
+        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        -
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        \\&\qquad 
+        +
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        -
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \\&\qquad 
+        +
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        -
+        \frac{y}{\|y\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        .    
+    \end{align}
+    Without loss of generality, $\|y\| \leq \|x\|$. 
+    \begin{align}
+        &
+        \left\| F(x) - F(y) \right\|
+        \\&
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
+        +
+        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
+        \\&\leq
+        \left\| x - y \right\|
+        \sqrt{n} \sigma_{\min}(A^{-1})
+        +
+        \sqrt{n} \sigma_{\min}(A^{-1}) \left\| x - y \right\|
+        +
+        \left\| x - y \right\|
+        \sqrt{n} \sigma_{\min}(A^{-1})
+        \\&\leq
+        3\sqrt{n} \sigma_{\min}(A^{-1})
+        \left\| x - y \right\|
+        .    
+    \end{align}
+    \begin{align}
+        &
+        \left\| F(x) - F(y) \right\|
+        \\&
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
+        +
+        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
+        \\&
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
+        +
+        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \left| \|y\| - \|x\| \right| }{\|x\|}
+        \\&\leq
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
+        +
+        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \| x - y \| }{\|x\|}
+        \\&\leq
+        \leq
+        \left\| x - y \right\|
+        \frac{ \lambda_{0}(x) }{\|x\|}
+        +
+        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
+        +
+        \left( \lambda_{0}(y) \right)
+        \frac{ \| x - y \| }{\|y\|}
+        .    
+    \end{align}
+    On the one hand,
+    we compute the Jacobian  
+    \begin{align}
+        \Jacobian F(x) 
+        = 
+        \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
+        \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        + 
+        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \nabla\lambda_{i}(x) \right)
+        .
+    \end{align}
+    On the other hand, by the reverse triangle inequality,
     \begin{align}
@@
     Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$. 
+    \begin{align}
+        \left| F(x) - F(y) \right|
+        &\geq 
+        \left\| 
+            \frac{x}{\|x\|}
+            \left( 1 - \lambda_{0}(x) \right) 
+            -
+            \frac{y}{\|y\|}
+            \left( 1 - \lambda_{0}(y) \right) 
+        \right\|
+        \\&
+        \geq 
+        \left\| 
+            \frac{x}{\|x\|}
+            \left( 1 - \lambda_{0}(x) \right) 
+            -
+            \frac{y}{\|y\|}
+            \left( 1 - \lambda_{0}(y) \right) 
+        \right\|
+    \end{align}
+    \todo{finish this estimate somehow}
 
@@
     \end{align}
+    \item 
+    We use the following result~\cite[Theorem~3]{alestalo2018radial}:
+    if $f : S \rightarrow S$ is an $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
+    then the radial extension $f : B \rightarrow B$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
     \end{itemize}
+\end{proof}
+
+% Please cite the original version:
+% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
+% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
+% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant
+
+% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
+% https://eudml.org/doc/258483
+% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
+% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
+\begin{lemma}
+    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
+    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
+    \begin{align*}
+        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R^{2}/r % euclidean 
+    \end{align*}
+    If $K$ is convex, then 
+    \begin{align*}
+        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
+        \\
+        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    .
 \end{proof}

### 2024-08-15 draft.tex
transformation

@@
     this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms.
-\end{document}
 
@@
 Kann die Konstante $\sqrt{n}$ noch verbessert werden?
+
+On the other hand, by the reverse triangle inequality,
+    \begin{align}
+        \left| F(x) - F(y) \right|
+        &\geq 
+        \left\| 
+            \frac{x}{\|x\|}
+            \sum_{i=1}^{n} \lambda_{i}(x)
+            -
+            \frac{y}{\|y\|}
+            \sum_{i=1}^{n} \lambda_{i}(y)
+        \right\|
+        \\&
+        \geq 
+        \left| 
+            \frac{\|x\|}{\|x\|}
+            \sum_{i=1}^{n} \lambda_{i}(x)
+            -
+            \frac{\|y\|}{\|y\|}
+            \sum_{i=1}^{n} \lambda_{i}(y)
+        \right|
+        \\&
+        = 
+        \left| 
+            \sum_{i=1}^{n} \lambda_{i}(x)
+            -
+            \sum_{i=1}^{n} \lambda_{i}(y)
+        \right|
+        \\&
+        = 
+        \left| 
+            \vec{1}
+            \cdot 
+            A^{-1}( x - y )
+        \right|
+    \end{align}
+    Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$. 
+    \begin{align}
+        \left| F(x) - F(y) \right|
+        &\geq 
+        \left\| 
+            \frac{x}{\|x\|}
+            \left( 1 - \lambda_{0}(x) \right) 
+            -
+            \frac{y}{\|y\|}
+            \left( 1 - \lambda_{0}(y) \right) 
+        \right\|
+        \\&
+        \geq 
+        \left\| 
+            \frac{x}{\|x\|}
+            \left( 1 - \lambda_{0}(x) \right) 
+            -
+            \frac{y}{\|y\|}
+            \left( 1 - \lambda_{0}(y) \right) 
+        \right\|
+    \end{align}
+    %% \todo{finish this estimate somehow}
+
+    \begin{proof}
+\begin{itemize}
+    \item 
+    % \todo{Choose hyperplane that puts T on one side}
+    We use Lemma~\ref{lemma:oppositesubsimplex}
+    \item 
+    % \todo{Align barycenter of opposite subsimplex with coordinate axis}
+    \item 
+    % \todo{opposite simplex cast to disk}
+    \item 
+    % \todo{roll out rest of sphere onto disk}
+    \item 
+    % \todo{estimate reflection}
+\end{itemize}
+\end{proof}
+
+    We use the following auxiliary result. 
+    Suppose that $\|\cdot\|_{\alpha}$ and $\|\cdot\|_{\alpha}$ are two norms on a Banach space.
+    Let 
+    $$
+        F_{\alpha,\beta}(x) = \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} }.
+    $$
+    Then 
+    \begin{align*}
+        &
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\alpha}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
+        \right\|_{\alpha}
+        +
+        C_{\beta}^{\alpha} 
+        \left\| 
+            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\alpha}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left| 
+            \| x \|_{\alpha}
+            - 
+            \| y \|_{\alpha}
+        \right|
+        +
+        C_{\beta}^{\alpha} 
+        \frac{ \| y \|_{\alpha} }{ \| y \|_{\beta} } 
+        \left\| x - y \right\|_{\alpha}
+        \\&\qquad 
+        \leq 
+        C_{\beta}^{\alpha} 
+        C_{\alpha}^{\beta} 
+        \left\| x - y \right\|_{\alpha}
+        +
+        C_{\beta}^{\alpha} 
+        C_{\alpha}^{\beta} 
+        \left\| x - y \right\|_{\alpha}
+        .
+    \end{align*}
+    \begin{align*}
+        &
+        \| 
+            F(x) - F(y) 
+        \|_{\beta}
+        \\&\leq 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\leq 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            + 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            + 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\leq 
+        \left\| 
+            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
+            - 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+        \right\|_{\beta}
+            + 
+        \left\| 
+            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+        \right\|_{\beta}
+            + 
+        \left\| 
+            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
+            - 
+            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
+        \right\|_{\beta}
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| 
+            x - y
+        \right\|_{\beta}
+            + 
+        \frac{ \| y \|_{\beta} }{ \| x \|_{\beta} } 
+        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
+        + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \left| 
+            \frac{ 1 }{ \| x \|_{\beta} } 
+            - 
+            \frac{ 1 }{ \| y \|_{\beta} }  
+        \right|
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| 
+            x - y
+        \right\|_{\beta}
+        + 
+        % BEcause w l o g 
+        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
+        + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| 
+            x - y
+        \right\|_{\beta}
+            + 
+        % BEcause w l o g 
+        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
+            + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
+        \\&\leq 
+        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
+        \left\| x - y \right\|_{\beta}
+            + 
+        % BEcause w l o g 
+        \left\| x - y \right\|_{\alpha}
+            + 
+        \| y \|_{\alpha} \| y \|_{\beta} 
+        \frac{ \left\| x - y \right\|_{\beta} }{ \| y \|_{\beta} \| y \|_{\beta} }
+        \\&\leq 
+        C^{\alpha}_{\beta} 
+        C^{\beta}_{\alpha}
+        \left\| x - y \right\|_{\alpha}
+            + 
+        % BEcause w l o g 
+        \left\| x - y \right\|_{\alpha}
+            + 
+        C^{\alpha}_{\beta} 
+        C^{\beta}_{\alpha}
+        \left\| x - y \right\|_{\alpha}
+        .
+    \end{align*}
+    % \item 
+    Consider any simplex $T$ with one vertex $v_0$ at the origin. 
+    Let $\lambda_{0}, \lambda_{1}, \dots, \lambda_{n}$ be the barycentric coordinates. 
+    The mapping 
+    \begin{align}
+        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right) = \frac{x}{\|x\|} \left( 1 - \lambda_{0}(x) \right)
+    \end{align}
+    maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
+    On the one hand, 
+    \begin{align}
+        &
+        F(x) - F(y)
+        \\&
+        =
+        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        -
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        \\&\qquad 
+        +
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        -
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \\&\qquad 
+        +
+        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        -
+        \frac{y}{\|y\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        .    
+    \end{align}
+    Without loss of generality, $\|y\| \leq \|x\|$. 
+    \begin{align}
+        &
+        \left\| F(x) - F(y) \right\|
+        \\&
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
+        +
+        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
+        \\&\leq
+        \left\| x - y \right\|
+        \sqrt{n} \sigma_{\min}(A^{-1})
+        +
+        \sqrt{n} \sigma_{\min}(A^{-1}) \left\| x - y \right\|
+        +
+        \left\| x - y \right\|
+        \sqrt{n} \sigma_{\min}(A^{-1})
+        \\&\leq
+        3\sqrt{n} \sigma_{\min}(A^{-1})
+        \left\| x - y \right\|
+        .    
+    \end{align}
+    \begin{align}
+        &
+        \left\| F(x) - F(y) \right\|
+        \\&
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
+        +
+        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
+        \\&
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
+        +
+        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \left| \|y\| - \|x\| \right| }{\|x\|}
+        \\&\leq
+        \leq
+        \left\| x - y \right\|
+        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
+        \\&\qquad 
+        +
+        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
+        +
+        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
+        \frac{ \| x - y \| }{\|x\|}
+        \\&\leq
+        \leq
+        \left\| x - y \right\|
+        \frac{ \lambda_{0}(x) }{\|x\|}
+        +
+        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
+        +
+        \left( \lambda_{0}(y) \right)
+        \frac{ \| x - y \| }{\|y\|}
+        .    
+    \end{align}
+    On the one hand,
+    we compute the Jacobian  
+    \begin{align}
+        \Jacobian F(x) 
+        = 
+        \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
+        \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
+        + 
+        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \nabla\lambda_{i}(x) \right)
+        .
+    \end{align}
+
+\end{document}

### 2024-08-15 main.tex
Update on Overleaf.
transformation

--- 2024-07-22 main.tex
@@
 
+Stars around subsimplices can be turned into vertex stars after a subdivision, 
+and the shape regularity can be controlled.
+
+\begin{lemma}\label{lemma:stardivision}
+    Let $\calT$ be an $n$-dimensional simplicial complex
+    such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
+    Let $z_S$ be the barycenter of $S$ 
+    and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
+    If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
+    then $\vol(T^{\star}) = \vol(T) / n$.
+\end{lemma}
+\begin{proof}
+    This is easy.
+\end{proof}
+
 \begin{lemma}    
@@
     $$ 
-    Then $I$ is the union of $k$ different facets of $T$, 
-    and their intersection is a simplex $S \in \calT$ of dimension $n-k$.
-    Moreover, 
+    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
+    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
     $$
@@
     Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
-    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let $M := |\patch_{\calT}(S)| \setminus T$. 
+    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
+    \begin{align*}
+        M := |\patch_{\calT}(S)| \setminus T.
+    \end{align*}
     There exists a bi-Lipschitz mapping
@@
 \begin{proof}
+    Without loss of generality, the barycenter of $S$ is the origin. 
+    We derive the estimate in several steps. 
     \begin{itemize}
         \item 
-    \todo{Choose hyperplane that puts T on one side}
-    We use Lemma~\ref{lemma:oppositesubsimplex}
+        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
+        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
+        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
+        The subsimplex $S' \subseteq T$ that is complementary to $S$.
+        such that $J$ is the union of exactly those faces of $T$ that contain $S'$.
+
         \item 
-    \todo{Align barycenter of opposite subsimplex with coordinate axis}
+        We construct a new triangulation that contains $T$ and that is a star around $S$.
+        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
+        We define a triangulation $\calS$ by the barycentric refinement of $T$. 
+        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
+
+        We define another simplicial complex $\calS^c$ as follows:
+        whenever $K \in \calS$ is an $n$-simplex, we replace the vertex $z_{S}'$ by new vertex opposite point $-z_{S}'$,
+        giving us a simplex $K'$.
+
+        We let $\calS'$ be the union of $\calS$ and $\calS^c$. 
+        By construction, all these $n$-simplices contain $S$ as a subsimplex,
+        and they are disjoint except for their proper subsimplices. 
+        Hence $\calS'$ is indeed a triangulation. 
+        Moreover, $S$ is an inner subsimplex of that triangulation. 
+        In particular, $\calS'$ is its own star around $S$.
+
+        In what follows, we also use $\calS''$, the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
+        Then $\calS''$ is the local star around the barycenter $z_S$.
+
         \item 
-    \todo{opposite simplex cast to disk}
+        \todo{Reflect onto complement and estimate bi-Lipschitz constant}
+        We introduce a new mapping $\Theta : |\calS| \rightarrow |\calS^c|$.
+
         \item 
-    \todo{roll out rest of sphere onto disk}
+        Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
+        We let $A_T \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
+        That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
+        Then the mapping 
+        \begin{align}
+            F_T(x) 
+            = 
+            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x
+        \end{align}
+        maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
+        \begin{align}
+            F_T^{-1}(x) 
+            = 
+            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x
+        \end{align}
+        We analyze its Lipschitz properties.
+        % 
+        On the one hand, 
+        we compute the Jacobian at any $x \in \mathring T$:
+        \begin{align}
+            \Jacobian F_T(x) 
+            = 
+            \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
+            \left( \vecone \cdot A^{-1} x \right)
+            + 
+            \frac{x}{\|x\|} \left( \vecone \cdot A^{-1} x \right)
+            .
+        \end{align}
+        The Euclidean operator norm is 
+        \begin{align}
+            \| \Jacobian F_T(x) \| 
+            \leq 
+            2 \left| \vecone \cdot A^{-1} x \right|
+            \leq 
+            2 \sqrt{n} \cdot \sigma_{\max}(A^{-1}) 
+            .
+        \end{align}
+        On the one hand, given $x, y \in T$, 
+        where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
+        \begin{align*}
+            &
+            \left\| F_T(x) - F_T(y) \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|A^{-1} x\|_2 - \|A^{-1} y\|_2 \right|
+            \\&\qquad 
+            \leq 
+            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A^{-1}) 
+            \left\| x - y \right\|_{2}
+            .
+        \end{align*}
+        On the other hand, given $x, y \in F_T(T)$, 
+        where $\| A^{-1} y \|_{1} \leq \| A^{-1} x \|_{1}$ without loss of generality, we find 
+        \begin{align*}
+            &
+            \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|x\|_2 - \|y\|_2 \right|
+            \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} }
+            \\&\qquad 
+            \leq 
+            2 \sigma_{\min}(A^{-1})^{-1} 
+            \left\| x - y \right\|_{2}
+            .
+        \end{align*}
+        By convexity of the range of $F_T(T)$, 
+        we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
+        We recall that $\sigma_{\max}(A^{-1}) = \sigma_{\min}(A)^{-1}$ and $\sigma_{\min}(A^{-1})^{-1} = \sigma_{\max}(A)$.
+
         \item 
-    \todo{estimate reflection}
+        Suppose that $S = \{v_0\}$ is a single vertex. 
+        We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
+        Without loss of generality, $S$ is at the origin. 
+        For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
+        We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
+        \todo{Complete}
+
+        \item 
+        \todo{Combine all this to get the final transformation.}
+
+%         \item 
+%         Let $\calU$ be the simplicial complex of dimension $n-1$ that contains precisely those facets of $T$ that do not contain $S$.
+%         We write $Y := F( |\calU| )$. 
+%         \todo{Shape of the outer patch $Y$, star-shaped geometry}
+%         
+%         \item 
+%         We let $\sphere{n}_{\star} := \sphere{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
+%         Suppose that $\bar x \in \sphere{n}$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
+%         We define its stereographic projection as 
+%         \begin{align}
+%             \pi( \bar x ) 
+%             = 
+%             \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
+%             .
+%         \end{align}
+%         This is a mapping $\pi : \sphere{n}_{\star} \rightarrow \bbR^{n}$. 
+%         Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
+%         \begin{align}
+%             \pi^{-1}( y )
+%             = 
+%             \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
+%             +
+%             \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
+%             .
+%         \end{align}
+%         \item 
+%         Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
+%         \begin{align}
+%             \mu : \bbR^{n} \rightarrow \bbR^{n},
+%             \qquad 
+%             y \mapsto \frac{y}{\| y \|}.
+%         \end{align}
+%         \item 
+%         \begin{align}
+%             G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
+%         \end{align}
+%         \item 
+%         We combine these mappings:
+%         \begin{align}
+%             Q : \sphere{n} \rightarrow \sphere{n}, \qquad x \mapsto \pi^{-1} G^{-1} \mu G \pi(x)
+%         \end{align}
+%         We want to analyze its Lipschitz properties. \todo{Stuff}
+%         \item
+%         We have constructed a bi-Lipschitz mapping from the Euclidean unit sphere into itself.
+%         We use the following result~\cite[Theorem~3]{alestalo2018radial}:
+%         if $f : \sphere{n} \rightarrow \sphere{n}$ is any $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
+%         then the radial extension $f : \ball{n} \rightarrow \ball{n}$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
+%         Consequently, \todo{write out}
+%         \item 
+%         In total, we thus have 
+%         \begin{align}
+%             Q' := F^{-1} \pi^{-1} G^{-1} \mu G \pi F
+%             .
+        \end{align}
     \end{itemize}
 \end{proof}
+
+% Please cite the original version:
+% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
+% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
+% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant
 

### 2024-08-16 main.tex
reflection theorem

@@
 \begin{align*}
-    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
     ,
-    \quad 
-    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    \\
+    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
     .
@@
 \begin{proof}
-    Without loss of generality, the barycenter of $S$ is the origin. 
     We derive the estimate in several steps. 
@@
         \item 
-        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
-        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
-        The subsimplex $S' \subseteq T$ that is complementary to $S$.
-        such that $J$ is the union of exactly those faces of $T$ that contain $S'$.
-
-        \item 
-        We construct a new triangulation that contains $T$ and that is a star around $S$.
-        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
-        We define a triangulation $\calS$ by the barycentric refinement of $T$. 
-        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
-
-        We define another simplicial complex $\calS^c$ as follows:
-        whenever $K \in \calS$ is an $n$-simplex, we replace the vertex $z_{S}'$ by new vertex opposite point $-z_{S}'$,
-        giving us a simplex $K'$.
-
-        We let $\calS'$ be the union of $\calS$ and $\calS^c$. 
-        By construction, all these $n$-simplices contain $S$ as a subsimplex,
-        and they are disjoint except for their proper subsimplices. 
-        Hence $\calS'$ is indeed a triangulation. 
-        Moreover, $S$ is an inner subsimplex of that triangulation. 
-        In particular, $\calS'$ is its own star around $S$.
-
-        In what follows, we also use $\calS''$, the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
-        Then $\calS''$ is the local star around the barycenter $z_S$.
-
-        \item 
-        \todo{Reflect onto complement and estimate bi-Lipschitz constant}
-        We introduce a new mapping $\Theta : |\calS| \rightarrow |\calS^c|$.
-
-        \item 
+        We begin with the following preparatory observations. 
         Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
-        We let $A_T \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
+        We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
         That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
@@
             = 
-            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
         \end{align}
@@
             = 
-            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
         \end{align}
@@
             \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
-            \left( \vecone \cdot A^{-1} x \right)
-            + 
-            \frac{x}{\|x\|} \left( \vecone \cdot A^{-1} x \right)
+            \left( \vecone \cdot A_{T}^{-1} x \right)
+            + 
+            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
             .
@@
             \leq 
-            2 \left| \vecone \cdot A^{-1} x \right|
-            \leq 
-            2 \sqrt{n} \cdot \sigma_{\max}(A^{-1}) 
+            2 \left| \vecone \cdot A_{T}^{-1} x \right|
+            \leq 
+            2 \sqrt{n} \cdot \sigma_{\max}(A_{T}^{-1}) 
             .
         \end{align}
+        \todo{Find the best estimate. }
         On the one hand, given $x, y \in T$, 
@@
             \left\| 
-                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
             \right\|_{2}
@@
             \left\| 
-                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
             \right\|_{2}
@@
             \left\| 
-                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
             \right\|_{2}
@@
             \leq 
-            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
             \left\| 
@@
             +
-            \left| \|A^{-1} x\|_2 - \|A^{-1} y\|_2 \right|
+            \left| \|A_{T}^{-1} x\|_2 - \|A_{T}^{-1} y\|_2 \right|
             \\&\qquad 
             \leq 
-            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A^{-1}) 
+            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
             \left\| x - y \right\|_{2}
@@
         On the other hand, given $x, y \in F_T(T)$, 
-        where $\| A^{-1} y \|_{1} \leq \| A^{-1} x \|_{1}$ without loss of generality, we find 
+        where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
         \begin{align*}
@@
             \left\| 
-                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y
+                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
             \right\|_{2}
@@
             \left\| 
-                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y
+                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
             \right\|_{2}
@@
             \left\| 
-                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y
+                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
             \right\|_{2}
@@
             \leq 
-            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
             \left\| 
@@
             \left| \|x\|_2 - \|y\|_2 \right|
-            \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} }
+            \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} }
             \\&\qquad 
             \leq 
-            2 \sigma_{\min}(A^{-1})^{-1} 
+            2 \sigma_{\min}(A_{T}^{-1})^{-1} 
             \left\| x - y \right\|_{2}
@@
         we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
-        We recall that $\sigma_{\max}(A^{-1}) = \sigma_{\min}(A)^{-1}$ and $\sigma_{\min}(A^{-1})^{-1} = \sigma_{\max}(A)$.
+        We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
 
         \item 
-        Suppose that $S = \{v_0\}$ is a single vertex. 
-        We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
-        Without loss of generality, $S$ is at the origin. 
-        For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
-        We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
-        \todo{Complete}
+        Without loss of generality, the barycenter of $S$ is the origin. 
+        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
+        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
+        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
+        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.
 
         \item 
-        \todo{Combine all this to get the final transformation.}
+        We construct a new triangulation that contains $T$ and that is a star around $S$.
+        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
+        We first define a new triangulation $\calS$ by the barycentric refinement of $T$. 
+        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
+
+        We define another simplicial complex $\calS^c$ as follows:
+        whenever $K \in \calS$ is an $n$-simplex, 
+        we replace the vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
+        giving us a simplex $K'$.
+
+        We let $\calS'$ be the union of $\calS$ and $\calS^c$. 
+        By construction, all these $n$-simplices contain $S$ as a subsimplex,
+        and they are disjoint except for their proper subsimplices. 
+        Hence $\calS'$ is indeed a triangulation. 
+        Moreover, $S$ is an inner subsimplex of that triangulation. 
+        In particular, $\calS'$ is its own star around $S$.
+
+        \item 
+        In what follows, we also use $\calR'$, 
+        the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
+        Then $\calR'$ is the local star around the barycenter $z_S$,
+        and all $n$-simplices in $\calR'$ contain $z_{S}$. 
+        We let $\calR$ and $\calR^{c}$ be the corresponding refinements of $\calS$ and $\calS^{c}$, respectively.
+
+        \item 
+        % \todo{Reflect onto complement and estimate bi-Lipschitz constant}
+        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
+        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
+        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
+        be affine reference transformations
+        that agree on the vertices common to $K$ and $K'$.
+        We then define 
+        \begin{align*}
+            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
+        \end{align*}
+        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
+        \begin{align*}
+            \| \Jacobian \Theta_{|K}      \| \leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
+            \qquad 
+            \| \Jacobian \Theta_{|K}^{-1} \| \leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
+        \end{align*}
+
+        \item 
+        % \todo{Combine all this to get the final transformation.}
+        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
+        Using our initial observations, we obtain homeomorphisms 
+        \begin{align*}
+            \Psi_{\calK } : |\calK| \rightarrow \calB,
+            \qquad 
+            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
+        \end{align*}
+        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
+        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
+        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.
+        It follows that 
+        \begin{align*}
+            \Theta_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
+        \end{align*}
+        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
+        We estimate the Jacobians: 
+        \begin{align*}
+            \| \Jacobian \Theta_{S} \| 
+            \leq 
+            \sup_{ K \in \calK  }
+            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
+            \sup_{ K \in \calR' } 
+            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            .
+        \end{align*}
+        Each bisection halves the volume of the triangles. Thus,
+        \begin{align*}
+            \color{red}
+            \| \Jacobian \Theta_{S} \| 
+            &\leq 
+            2 \sup_{ K \in \patch_{\calT}(S) }
+            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
+            4 \sup_{ K \in \patch_{\calT}(S) } 
+            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
+            4 \sup_{ K \in \patch_{\calT}(S) } 
+            \kappa(A_{K})
+            \\&\leq 
+            64
+            \left( \sqrt{n} + 1 \right) 
+            \sup_{ K \in \patch_{\calT}(S) }
+            \sigma_{\max}(A_{K}     ) 
+            \sup_{ K \in \patch_{\calT}(S) } 
+            \sigma_{\max}(A_{K}^{-1}) 
+            \sup_{ K \in \patch_{\calT}(S) } 
+            \kappa(A_{K})
+            .
+        \end{align*}
+        That establishes the final estimate.
+
+%         \item 
+%         Suppose that $S = \{v_0\}$ is a single vertex. 
+%         We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
+%         Without loss of generality, $S$ is at the origin. 
+%         For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
+%         We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
+%         \todo{Complete}
+%
 
@@
 %             .
-        \end{align}
+%         \end{align}
     \end{itemize}
-\end{proof}
-
-% Please cite the original version:
-% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
-% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
-% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant
-
-We recall a specialization of this result.
-
-\begin{lemma}\label{theorem:starreflection:facepatch}
-
-\end{lemma}
-
-% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
-% https://eudml.org/doc/258483
-% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
-% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
-\begin{lemma}
-    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
-    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
-    \begin{align*}
-        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R^{2}/r % euclidean 
-    \end{align*}
-    If $K$ is convex, then 
-    \begin{align*}
-        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
-    \end{align*}
-    satisfies 
-    \begin{align*}
-        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
-        \\
-        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    .
 \end{proof}

### 2024-08-17 main.tex
more updates

@@
     Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
-    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{email2@example.com}} \and
+    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
     Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
@@
 
-Before we outline the main results of this exposition in more details, 
+Before we outline the main results of this exposition in more detail, 
 we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
@@
     \forall
-    u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
+    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
     .\tag{PF} 
@@
 %     \quad 
-%     u \in W^{1,p}(\Omega) % TODO: Use \forall notation 
+%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
 %     .\tag{PF} 
@@
 Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly.~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
 When the domain is not convex but star-shaped with respect to a ball,
@@
 \end{align*}
-Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
+Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
 This only requires that certain sums of distributional partial derivatives are integrable, 
@@
     \| \bfv \|_{L^{p}(\Omega)}
-    \leq 
+    &\leq 
     C_{\curl,\Omega,p}
@@
     ,
-    \qquad 
+    \\%\qquad 
     \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
     \| \bfv \|_{L^{p}(\Omega)}
-    \leq 
+    &\leq 
     C_{\divergence,\Omega,p}
@@
 \end{align*}
-and whether these constants can be estimated by the operator norms of linear potential operators 
+and how these constants can be estimated by the operator norms of linear potential operators 
 \begin{align*}
@@
 We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue}, who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$.
-They provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains.
-This implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
+We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
+% who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
+who provide lower bounds for the spectrum of the Hodge--Laplace operator on smoothly bounded convex domains, 
+thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
 By duality, that implies lower bounds for the case of full boundary conditions.
-Their study also implies sequences of inequalities, such as the following in 3D convex domains:
-\begin{align}\label{math:intro:guerinisavo}
-    C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
-\end{align}
+% They also provide sequences of inequalities, such as the following in 3D smoothly bounded convex domains:
+% \begin{align}\label{math:intro:guerinisavo}
+%     C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
+% \end{align}
+% We emphasize that \cite{guerini2004eigenvalue} only addresses smoothly bounded domains, but the extension to convex domains is a technicality.
+
 When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
@@
 % DONE: cite VVVV
-In the Hilbert space case, $p=2$, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+In the Hilbert space case, $p=2$, and when the domain is smoothly bounded, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
 By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex Lipschitz domains.
-
-But no such results are known for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
+% These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex smoothly bounded domains.
+
+But no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
 We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 
-We conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$.
+We conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over smoothly bounded convex domains, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
 We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
 On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
@@
 and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+We present numerical examples in Section~\ref{section:numericalexamples}.
 
@@
 We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, % TODO: cite AAAA somebody, such as Alexandre
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, \todo{cite Ern...}
 we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
@@
     \leq 
-    C_{{\rm CW},p}
+    C_{{\rm P},{\rm CW},p}
     \diam(\Omega)
@@
 \begin{align}
-    C_{{\rm CW},p} 
+    C_{{\rm P},{\rm CW},p} 
     := 
@@
     \leq 
-    C_{{\rm EFNT},p}
+    C_{{\rm PF},{\rm EFNT},p}
     \diam(\Omega)
@@
 \end{align}
-where $C_{{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
+where $C_{{\rm PF},{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
 \begin{align}
-    C_{{\rm EFNT},p}
+    C_{{\rm PF},{\rm EFNT},p}
     :=
@@
     \leq 
-    2^{|1-\frac 2 p|}C_{{\rm EFNT},p}
+    2^{|1-\frac 2 p|}C_{{\rm PF},{\rm EFNT},p}
     \diam(\Omega)
@@
     Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
-    Let us compare the estimate $C_{{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm EFNT},p}$. 
+    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
+    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm PF},{\rm EFNT},p}$. 
     In the case $2 \leq p$, 
@@
         2^{1-\frac 2 p}
-        C_{{\rm EFNT},p}
+        C_{{\rm PF},{\rm EFNT},p}
         =
@@
         \leq
-        C_{{\rm CW},p} 
+        C_{{\rm P},{\rm CW},p} 
         .
@@
         2^{\frac 2 p - 1}
-        C_{{\rm EFNT},p}
+        C_{{\rm PF},{\rm EFNT},p}
         =
@@
         \frac{ 2^{\frac 2 p-1} }{2}
+        &
         =
         2^{\frac 2 p - 2}
+        \\&
         =
@@
         \leq
-        C_{{\rm CW},p} 
+        C_{{\rm P},{\rm CW},p} 
 %         % 
@@
 % TODO: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{{\rm EFNT},p}$ converges to $1/2$,
+%     In the limit as $p$ goes to $1$, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$,
 %     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
@@
 %     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{{\rm EFNT},p}$ converges to $1/2$, 
+%     In the limit as $p$ goes to infinity, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$, 
 %     which implies the Poincar\'e inequality 
@@
 %     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
-%     \[
+%     \begin{gather*}
 %         \diam(T) 
@@
 %         .
-%     \]
+%     \end{gather*}
 %     The desired result is thus evident. 
@@
 
-% TODO: REMOVE THE \cdot 
+% DONE: REMOVE THE \cdot 
 \begin{lemma}\label{lemma:volumecomparison}
@@
         \leq 
-        2 C_{{\rm EFNT},p}
+        2 C_{{\rm PF},{\rm EFNT},p}
         \max\left( 
@@
         \leq 
-        2 C_{{\rm EFNT},p}
+        2 C_{{\rm PF},{\rm EFNT},p}
         \rho(\calT)^{\frac 1 p}
@@
         \leq 
-        2 C_{{\rm EFNT},p}
+        2 C_{{\rm PF},{\rm EFNT},p}
         \| \nabla \hat u \|_{L^{p}(\hat U)}
@@
         &\leq 
-        2 C_{{\rm EFNT},p}
+        2 C_{{\rm PF},{\rm EFNT},p}
         \max\left( 
@@
     and such that for all $T \in \calT$:
-    \begin{align*} % TODO: UNIFY NOTATION FOR THE CONSTANTS 
+    \todo{Make sure the notation for the PF constants is uniform throughout the paper}
+    \begin{align*} 
         % \color{red}
@@
         C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
+        % 2 C_{{\rm PF},{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
         \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
@@
         \rho(\calT)^{\frac{m-1}{p}}
-        % C_{{\rm EFNT},p} \diam(T_0)
+        % C_{{\rm PF},{\rm EFNT},p} \diam(T_0)
         C_{{\rm{PF}},T_{0},p}
@@
  There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
- \[
+ \begin{gather*}
     \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
- \]
+ \end{gather*}
  In particular, $c_{0} := u - w_0$ is a constant function. 
@@
  We assess the norm of this potential. We observe 
- \begin{gather*}
+ \begin{align*}
     \| w'_{F_m} \|_{L^{p}(T_m)}
@@
     \| c_{m} \|_{L^{p}(T_m)},
-    \qquad 
+    \\
     \| c_{m} \|_{L^{p}(T_m)}
@@
     .
- \end{gather*}
+ \end{align*}
  In particular,
@@
     There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
-    \[
+    \begin{gather*}
         \| w \|_{L^{p}(T)}
@@
         .
-    \]
+    \end{gather*}
     Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
     We use that 
-    \[
+    \begin{gather*}
         \| \gamma \|_{L^{p}(T)}
@@
         .
-    \]
+    \end{gather*}
     Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
@@
     First, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
-    \[
+    \begin{gather*}
         \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \]
+    \end{gather*}
     In particular, $c_{0} := u - w_0$ is a constant function.
@@
         \| \nabla w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
+        &
+        \leq 
         |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
@@
         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
+        \\&
         \leq 
@@
     and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
-    % TODO: cite E&V Math Comp 2020, Lemma B1. 
+    \todo{ cite E\&V Math Comp 2020, Lemma B1.} 
 \end{proof}
@@
 $W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
-\[
+\begin{gather*}
     W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-\]
+\end{gather*}
 The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
 and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
-\[
+\begin{gather*}
     \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \quad 
+    \\ 
     \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\]
+\end{gather*}
 We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
@@
 These mappings are invertible.
+
 %
-% TODO: bounds on the Jacobian transform 
+\todo{bounds on the Jacobian transform }
 %
+
+\todo{double check the sign conventions}
 We use the commutativity relations 
@@
     \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv), 
-    % TODO: watch the sign 
     \\
@@
 if 
-\[ 
+\begin{gather*} 
     u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
@@
     u( v_1, v_2, \ldots, v_k ) 
-\]
+\end{gather*}
 for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
@@
 defined by the formula 
-\[
+\begin{gather*}
     (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
@@
     u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\]
+\end{gather*}
 for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
@@
     \quad 
-    u_1 \in \Alt^{k}(V),
+    \forall u_1 \in \Alt^{k}(V),
     \quad 
-    u_2 \in \Alt^{l}(V).
-\end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined as 
+    \forall u_2 \in \Alt^{l}(V).
+\end{align*}
+We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined via 
 \begin{align*}
@@
     \quad 
-    v_1, v_2, \ldots, v_{k-1} \in V.
+    \forall v_1, v_2, \ldots, v_{k-1} \in V.
 \end{align*}
@@
 \begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, \quad \sigma \in \Sigma(k,n). 
+    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
+    \quad 
+    \forall \sigma \in \Sigma(k,n). 
 \end{align*}
@@
 Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\[
+\begin{gather*}
     \omega = 
@@
     \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\]
+\end{gather*}
 where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
 The exterior derivative \( \cartan\omega \) is defined by
-\[
+\begin{gather*}
     \cartan\omega = 
@@
     \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\]
+\end{gather*}
 The exterior derivative is linear and nilpotent, which means 
@@
 Moreover, it satisfies the Leibniz rule:
-\[ 
+\begin{gather*} 
     \cartan(\omega \wedge \eta) 
@@
     \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \eta \in C^{\infty}\Alt^{l}(\Omega).
-\]
+    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
+    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
+\end{gather*}
 Let us now turn our attention to Sobolev spaces of differential forms. 
 Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a canonical norm, we can consider the pointwise norms of differential $k$-forms. 
-% First, we notice that the % TODO: introduce a norm 
+\todo{introduce a norm here}
 We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
@@
 The exterior derivative is defined in the sense of distributions and we introduce 
-\[
+\begin{gather*}
     W^p\Alt^{k}(\Omega) 
@@
     \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
-\]
+    .
+\end{gather*}
 We observe that $u \in L^p\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^p\Alt^{k+1}(\Omega)$
@@
 The pullback of $u \in W^p\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\[ 
+\begin{gather*} 
     \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
@@
     u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\]
+\end{gather*}
 for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.
 
-% TODO: transformationssatz
+\todo{transformationssatz}
 
@@
     This is expressed formally as the commuting diagram 
-    \[
+    \begin{gather*}
     \begin{CD}
@@
     \end{CD}
-    \]
+    \end{gather*}
     where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
@@
     We summarize the situation in the following commuting diagram: 
-    \[ % TODO: what is the convention for the curl and rotation ? look up in the textbooks?
+    \todo{double check the convention for the curl and rot operators in the literature}
+    \begin{gather*} 
     \begin{CD}
@@
     \end{CD}
-    \]
+    \end{gather*}
     Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
@@
 
-% TODO: spaces with boundary conditions: grad, curl, divergence, exterior derivative; approximation properties
+\todo{spaces with boundary conditions: grad, curl, divergence, exterior derivative; approximation properties}
 
@@
 
+In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $D > 0$.
+
 We begin with introducing the Costabel-McIntosh kernel.
@@
 \begin{align}
-  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy
-  \\
-  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
+  \\
+  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
 \end{align}
@@
 \end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives % TODO: define D
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives 
+% % \todo{define D}
 \begin{align*}
@@
     \int_{B_D(0)} |z|^{k+1-n} dz
+    &
     =
     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
+    \\&
     =
@@
     \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-    &\leq 
+    &
+    \leq 
     \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
@@
     \| u \|_{L^{p}(\Omega)}
+    \\&
     \leq 
@@
 for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\[
+\begin{gather*}
     \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
-\]
+\end{gather*}
 % Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
@@
     \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
-    &\leq 
+    &
+    \leq 
     \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
@@
 for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\[
+\begin{gather*}
     \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
-\]
+\end{gather*}
 % Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
@@
     By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-    % TODO: definition of weak derivative + definition of boundary condition 
+    \todo{definition of weak derivative + definition of boundary condition }
     % 
@@
     while they are increasing for the Bogovski\u{\i} operator.
-    This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over convex domains~\cite{guerini2004eigenvalue}.
+    This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
 \end{remark}
@@
     Then $T$ lies on one side of the affine subspace
-    \[
+    \begin{gather*}
         A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
-    \]
+    \end{gather*}
     Moreover, $F = T \cap A$.
@@
     First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \[
+    \begin{gather*}
         \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \]
+    \end{gather*}
     Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
@@
 
-\section{Numerical examples}
+\section{Numerical examples}\label{section:numericalexamples}
 
@@
 the unit square $\Omega_S$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{SS}$:
-\[
+\begin{gather*}
     \Omega_{S}  = (-1,1)^2,
@@
     \Omega_{SS} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
-\]
+\end{gather*}
 % Square 
@@
 the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
-\[
+\begin{gather*}
     \Omega_{C}  = (-1,1)^2,
@@
     \Omega_{B} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
-\]
+\end{gather*}
 % Cube 

### 2024-08-19 main.tex
minor updates

@@
 \newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+\newcommand{\notice}[1]{\textcolor{red}{REMARK: #1}}
 
@@
 
-% DONE \todo{Reformulate the first paragraph. } % 
+% DONE {Reformulate the first paragraph. } % 
 Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
@@
 
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, \todo{cite Ern...}
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
 we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
@@
 
-\todo{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
+% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
 
@@
 % DONE: DEFINE THE JACOBIAN 
-\todo{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}
+% \notice{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}
 
@@
         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-        \\&
-        \leq 
+        ,
+        \\
+        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
+        &\leq 
         |\det(\Jacobian \varphi_1^{-1})|
@@
         \| \nabla u \|_{L^{p}(T_1)}^{p}
-        +
+        ,
+        \\
+        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
+        &\leq 
         |\det(\Jacobian \varphi_2^{-1})|
@@
         \| \nabla u \|_{L^{p}(T_2)}^{p}
-        \\&
-        \leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
-            ,
-            |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
-        \right)
-        \| \nabla u \|_{L^{p}(U)}^{p}
+%         \\&
+%         \leq 
+%         \max\left( 
+%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
+%             ,
+%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
+%         \right)
+%         \| \nabla u \|_{L^{p}(U)}^{p}
         .
@@
         \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \cdot \| \Jacobian \varphi_1 \|
+            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|
             ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \cdot \| \Jacobian \varphi_2 \|
+            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|
         \right)
@@
         \right)^{\frac 1 p}
+        \\&\qquad 
         \max\left( 
@@
         \right)^{\frac 1 p}
+        \\&\qquad 
         \min\left( 
@@
 \end{center}
-\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+\caption{Strongly connected triangulation of a domain.
+The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+The triangle in dark gray is the triangle being added in the current iteration, and the light gray triangles constitute the subdomain assembled so far.}
 \end{figure}
@@
 
+\begin{figure}[t]
+\begin{center}
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!50] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=white  ] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!50] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!50] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!25] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=gray!50] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\end{center}
+\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.}
+\label{figure:exhausting}
+\end{figure}
+
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
@@
     and such that for all $T \in \calT$:
-    \todo{Make sure the notation for the PF constants is uniform throughout the paper}
+%     DONE {Make sure the notation for the PF constants is uniform throughout the paper}
     \begin{align*} 
@@
 
- \todo{MLW, MV: add a figure here to illustrate how the domain is exhausted.}
+ % DONE \notice{MWL, MV: add a figure here to illustrate how the domain is exhausted.}
 
@@
     \right)^{\frac 1 p}
+    \\&\qquad 
     +
@@
 \begin{lemma}    
-    Suppose that an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$ and is non-branching, 
-    that is, each simplex of dimension $n-1$ is contained in at most two simplices. 
+    Let $\calT$ be an $n$-dimensional simplicial complex 
+    with a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$,
+    such that each simplex of dimension $n-1$ is contained in at most two simplices. 
     % DONE: what is non-branching?
@@
 \begin{example}
-    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.~\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
+    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
 \end{example}
@@
     and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
-    \todo{ cite E\&V Math Comp 2020, Lemma B1.} 
 \end{proof}
 
-\begin{lemma}
+\begin{lemma}[cf. Lemma B1 in \cite{ern2020stable}]
     Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
@@
     \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
-    \phi^{\divergence}(\bfw) &= \left( \adj(\Jacobian\phi) \bfw \right)  \circ \phi, \\
+    \phi^{\divergence}(\bfw) &= \left( \adj(\Jacobian\phi) \bfw \right)  \circ \phi, \\ % TODO: check sign convention 
     \phi^{\rm b}(v) &= \left( \det(\Jacobian\phi) v \right)  \circ \phi,
@@
 \end{subequations}
-\todo{MWL: double check the correct sign convention, what is inverse and what is not}
 and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
 These mappings are invertible. 
-
-%
-\todo{bounds on the Jacobian transform }
-%
-
-\todo{double check the sign conventions}
+Bounds on the Lebesgue norms will follow from a more general result below.
+
 We use the commutativity relations 
@@
 Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a canonical norm, we can consider the pointwise norms of differential $k$-forms. 
-\todo{introduce a norm here}
+Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
 We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
@@
     := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
+    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
     .
@@
 for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.
-
-\todo{transformationssatz}
+We cite an explicit transformation estimate~\cite{licht2019smoothed}.
+
+\begin{theorem} \label{theorem:pullbackestimate}
+ Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
+ Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
+ Then 
+ \begin{align}\label{math:pullbackestimate}
+  \begin{split}
+  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
+  &\leq 
+  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
+  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
+  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+  \\&\leq 
+  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
+  \| \Jacobian \phi^{-1} \|^{\frac{n}{p}}_{L^{\infty}(\Omega')}
+  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+  .
+  \end{split}
+ \end{align}
+\end{theorem}
 
@@
     We summarize the situation in the following commuting diagram: 
-    \todo{double check the convention for the curl and rot operators in the literature}
     \begin{gather*} 
@@
 
-\todo{spaces with boundary conditions: grad, curl, divergence, exterior derivative; approximation properties}
-
+We review a few approximation properties. 
 Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
@@
 
-\todo{cite Guzman and Salgado at the right spot.}\\
-
 In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $D > 0$.
@@
 If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives 
-% % \todo{define D}
 \begin{align*}
@@
 
-\begin{remark}
-    The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-    while they are increasing for the Bogovski\u{\i} operator.
-    This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
-\end{remark}
+% \begin{remark}
+%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
+%     while they are increasing for the Bogovski\u{\i} operator.
+%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
+% \end{remark}
 
@@
     The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
+
+    The operators discussed by Costabel and McIntosh are pseudodifferential operators of negative order, 
+    because their averaging uses a smooth weight, 
+    and hence they discuss a range of operator bounds between different function spaces. 
+    Guzman and Salgado have estimated the operator norm. 
 \end{remark}
 
-\section{Extension operator on finite element stars}\label{section:extension}
-% Only define the geometric mapping and its important quantities
-% Leave the function spaces etc. for later
-
-Suppose that any $n$-dimensional simplex $T$ with some subsimplex $F$.
-We want to find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is only on one side of the hyperplane.
+\section{Reflection on shellable stars}\label{section:extension}
+
+This section is devoted to a crucially important geometric construction. 
+Suppose that we have a shellable simplicial complex. 
+Every time add a simplex according to the shelling sequence, 
+we complete the local star of the some simplex in the triangulation.
+We search for a homeomorphism from the new simplex on its complement in the newly completed star
+such that the interface is preserved. 
+We want this homeomorphism to be bi-Lipschitz and we are particularly interested in the norms of its Jacobian.
+
+We begin with a geometric observation. 
+Suppose that $T$ is any $n$-dimensional simplex with some proper subsimplex $F$.
+We want to find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is on only one side of the hyperplane.
 
@@
 
-Stars around subsimplices can be turned into vertex stars after a subdivision, 
-and the shape regularity can be controlled.
+Next, we observe that stars around subsimplices can represented by vertex stars after a local subdivision of the mesh.
+The shape regularity is controlled in that process.
 
@@
     \begin{align*}
-        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \diam(T),
+        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
         \quad 
-        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \diam(T),
+        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
     \end{align*}
@@
         % 
+        \color{blue}
         On the one hand, 
@@
         \end{align}
-        \todo{Find the best estimate. }
+        \color{black}
         On the one hand, given $x, y \in T$, 
@@
     \end{itemize}
+    The proof is complete. 
 \end{proof}
+
+\begin{remark}
+    While the reflection mapping and its analysis in Theorem~\ref{theorem:starreflection} serve our purpose,
+    it might be possible to improve the estimate with a different analysis or construction.
+\end{remark}
 
@@
     We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+    See Figure~\ref{figure:exhausting} for an illustration.
 
@@
 the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
-\begin{gather*}
-    \Omega_{C}  = (-1,1)^2,
+\begin{align*}
+    \Omega_{C}  = (-1,1)^3,
     \qquad 
-    \Omega_{F}  = (-1,1)^2 \setminus (0,1)^2,
+    \Omega_{F}  = (-1,1)^3 \setminus (0,1)^3,
     \qquad
-    \Omega_{B} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
-\end{gather*}
+    \Omega_{B} &= 
+    \left( (-1,0) \times (-1,0) \times (-1,1) \right)
+    \\&\quad
+    \cup 
+    \left( (-1,0) \times (-1,1) \times (-1,0) \right)
+    \\&\quad
+    \cup 
+    \left( (-1,1) \times (-1,0) \times (-1,0) \right)
+    ,
+\end{align*}
 % Cube 

### 2024-08-20 main.tex
polishing

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 \input{header}
@@
 \begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
+    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
     \leq 
     C_{\curl}
-    \| \bff \|_{\bfL^{2}(\Omega)}
+    \| \bff \|_{L^{2}(\Omega)}
     .
@@
 \begin{align*}
-    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
+    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u(x) \;dx.
 \end{align*}
@@
     = 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \right)^{p}
-    \leq 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \right)
+    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \;dx
     = 
@@
 
-% TODO: Keep ?
+% DONT: Keep ?
 % \begin{example}
@@
     % DONE: Theorem 1.2 in Chua Wheeden 
-% TODO: Keep ?
+% DONT: Keep ?
 %     In the limit as $p$ goes to $1$, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$,
@@
 %     \end{align*}
-%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % TODO: cite 
-%     % TODO: review this entire result 
+%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
+%     % DONT: review this entire result 
 \end{remark}
@@
         \Cdrei{n}
-        \frac{ \kappa(T_1) }{ \kappa(T_2) }
+        \kappa(T_2)^{-1} \kappa(T_1) 
+        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
         .
@@
         \right)^{\frac 1 p}
+        \\&\qquad\qquad 
+        \cdot 
         \max\left( \diam(T_1), \diam(T_2) \right)
@@
     \| w_{m} \|_{L^{p}(T_m)}
+    &
     \leq 
     \| u_{F_m} \|_{L^{p}(T_m)}
+    \\&\qquad 
     +
@@
         C_{{\rm PF},T,F,p}
-        \leq 
+        &\leq 
         C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
-        \quad 
+        \\
+        %\quad 
         C_{{\rm PF},T,F,p}
-        \leq
+        &\leq
         \frac{1}{\sqrt[p]{p}}
@@
     and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $\nabla u$ outside of $T$.
+    We write $\bfg \in \bfL^{\infty}(T)$ for the trivial extension of $\nabla u$ outside of $T$.
     %With the fundamental theorem of calculus and H\"olders inequality: 
-    \begin{align*}
-        \int_{\Omega} |u(x)|^{p} \diff x dx
+    Now:
+    \begin{align*}
+        \int_{\Omega} |u(x)|^{p} \diff x \;dx
         &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} dx_{1} d\overline{x}
+        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
         \\&
         \leq
-        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| dy \right|^{p} dx_{1} d\overline{x}
+        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
         \\&
         \leq
-        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} dx_{1}
+        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
         \\&
         \leq
-        \int_{0}^{D} x_{1}^{p-1} dx_1 \cdot \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} 
-        \leq
-        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} dx
+        \int_{0}^{D} x_{1}^{p-1} \;dx_1 
+        \cdot 
+        \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
+        \leq
+        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} \,dx
         %
 %         \leq
-%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} dx_1 \dots dx_{n-1} dx_{1}
+%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
 %         \\&
 %         \leq
-%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{1}
+%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
 %         \\&
 %         \leq
-%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
 %         \\&
 %         \leq
-%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
+%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
 %         \leq 
 %         D^{p} 
-%         \int_{\Omega} |\nabla u|^{p} dx
-%         .
+%         \int_{\Omega} |\nabla u|^{p} \,dx
+        .
     \end{align*}
@@
         \| \nabla u \|_{L^{p}( T_{0} )}
-        \\&\qquad 
+        \\&\quad 
         +
@@
     \end{align*}
-    Putting this all together, 
+    Putting this all together, we use 
     \begin{align*}
@@
         \right) 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
+    \end{align*}
+    and 
+    \begin{align*}
         \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m})} 
-        + 
+        &
+        \leq  
         \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},F_{m},p} 
+        % C_{{\rm PF},T_{m},F_{m},p} 
         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m})} 
-        + 
+        \leq  
         \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},F_{m},p} 
+        % C_{{\rm PF},T_{m},F_{m},p} 
         \| \nabla u \|_{L^{p}(T_{m-1})} 
@@
     \end{align*}
+%     \begin{align*}
+%         &
+%         \| w_{m} \|_{L^{p}(T_{m})}
+%         \\&
+%         \leq  
+%         \| w'_{m} \|_{L^{p}(T_{m})}
+%         + 
+%         \| w''_{m} \|_{L^{p}(T_{m})}
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         + 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \left( 
+%             \| \nabla u \|_{L^{p}(T_{m})} 
+%             + 
+%             \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+%         \right) 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         + 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla u \|_{L^{p}(T_{m})} 
+%         + 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         + 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla u \|_{L^{p}(T_{m})} 
+%         + 
+%         \rho(\calT)^{\frac 1 p} \xi(\calT)
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         + 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla u \|_{L^{p}(T_{m})} 
+%         + 
+%         \rho(\calT)^{\frac 1 p} \xi(\calT)
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla u \|_{L^{p}(T_{m-1})} 
+%         \\&
+%         \leq  
+%         \rho(\calT)^{\frac 1 p} 
+%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
+%         + 
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{{\rm PF},T_{m},F_{m},p} 
+%         \| \nabla u \|_{L^{p}(T_{m})} 
+%         .
+%     \end{align*}
     The existence of $w \in W^{1,p}(\Omega)$ satisfying the recursive estimate follows. 
@@
     \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
-    \phi^{\divergence}(\bfw) &= \left( \adj(\Jacobian\phi) \bfw \right)  \circ \phi, \\ % TODO: check sign convention 
-    \phi^{\rm b}(v) &= \left( \det(\Jacobian\phi) v \right)  \circ \phi,
+    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
+    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
+    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
 \end{align}
 \end{subequations}
-and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
+and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
 These mappings are invertible. 
@@
 \begin{align}
-    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv), 
-    \\
-    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw),
+    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
+    \\
+    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
+    \\
+    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
 \end{align}
@@
         &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x)
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
         \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x)
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
         \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x)
+        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
         \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x)
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
         = 
@@
 For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{eq:Gl}
-  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
+\begin{equation}\label{math:mainkernel}
+  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
+  .
 \end{equation}
@@
 \begin{align*}
-    \int_{B_D(0)} |z|^{k+1-n} dz
+    \int_{B_D(0)} |z|^{k+1-n} \,dz
     &
     =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
+    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} \,dr
     \\&
     =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
+    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} \,dr
     =
@@
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
     \\&
@@
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
     ,
@@
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     .
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \cartanx^{j} \wedge \cartanx^{\sigma} dt 
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
     ,
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    \;\cartanx^{j} \wedge \cartanx^{\sigma}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \;\cartanx^{\sigma}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
+    \,\cartanx^{\sigma}
     \\&\qquad 
@@
     (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
     .
@@
     \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \cartanx^{\sigma}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad
@@
     (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
     \\&
@@
     \int_{0}^{1} 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
-    \cartanx^{\sigma}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
+    u_{\sigma}(x) \,\cartanx^{\sigma}
     =
@@
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} dt 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
     \\&
@@
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
     ,
@@
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     .
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    \;\cartanx^{j} \wedge \cartanx^{\sigma}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \;\cartanx^{\sigma}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad 
@@
     (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
     .
@@
     \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \cartanx^{j} \cartanx^{\sigma-\sigma(i)} dt 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt (x-a)_{j}
-    \cartanx^{\sigma}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad
@@
     (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) dt 
-    (x-a)_{\sigma(i)} \cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
     \\&
@@
     \int_{1}^\infty 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma-\sigma(i)} dt 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} dt
-    \cartanx^{\sigma}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
     \\&
@@
     \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) dt \cartanx^{\sigma}
+    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
     \\&
@@
         \begin{align*}
-            \| \Jacobian \Theta_{|K}      \| \leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
-            \qquad 
-            \| \Jacobian \Theta_{|K}^{-1} \| \leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
+            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
+            \\
+            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
         \end{align*}
@@
 
-\begin{lemma}
+We are now in the position to estimate Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions.
+The estimates require local Poincar\'e--Friedrichs constants over simplices, 
+with or without boundary conditions.
+
+The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator}
+implies the following estimate for Poincar\'e--Friedrichs constants over convex domains.
+
+\begin{lemma}\label{lemma:PFexteriorsimplex}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
+    Then for each $\bfu \in \bfW^{p}\Lambda^{?}(\Omega)$ there exists $w \in \bfW^{p}\Lambda^{?}(\Omega)$ with $\cartan u = \cartan w$ and 
+    \begin{align*}
+        \| \bfu \|_{L^{p}(\Omega)} 
+        \leq 
+        C_{???} % TODO 
+        \diam(\Omega) 
+        \| \divergence \bfu \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+\end{lemma}
+
+These constants are generally not optimal. 
+For example, when $p=2$ and only the divergence is considered, 
+we have the following improved estimate.
+
+\begin{lemma}\label{lemma:PFfordivergence}
     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
@@
     \begin{align*}
-        \| \bfu \|_{\bfL^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
+        \| \bfu \|_{L^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
         .
@@
 
-\begin{lemma}
+We also need a Poincar\'e--Friedrichs inequality for differential forms over a simplex but subject to homogeneous boundary conditions along a collection of faces.
+
+\begin{lemma}\label{lemma:PFexteriorwithboundaryconditions}
     Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\cartan,\Omega)$ such that 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(\Omega)$ such that 
     $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
@@
 
-    Let $f = \cartan u$ with $u \in \bfW^{p}(\cartan,T)$.
+    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{?}(T)$.
     We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}(\cartan,\Delta^{n})$ and $\cartan \hat u = \hat f$.
+    so that $\hat u \in \cartan \bfW^{p}\Lambda^{?}(\Delta^{n})$ and $\cartan \hat u = \hat f$.
 
@@
 
+The main result of this manuscript is the following theorem.
+
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
@@
         \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
+        \\&
         \leq 
@@
         \right) 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+    \end{align*}
+    and 
+    \begin{align*}
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq  
+        %C_{{\rm PF},T_{m},\Gamma_{m},p} 
         \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
@@
         \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
         \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        %C_{{\rm PF},T_{m},\Gamma_{m},p} 
         \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
@@
         \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(T_{m})} 
-        + 
         \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
+        C%_{{\rm PF},T_{m},\Gamma_{m},p} 
         \| \cartan u \|_{L^{p}(U_{m-1})} 
@@
     \Omega_{L}  = (-1,1)^2 \setminus (0,1)^2,
-    \qquad 
+    \\
     \Omega_{SS} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
@@
 the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
-\begin{align*}
+\begin{gather*}
     \Omega_{C}  = (-1,1)^3,
@@
     \Omega_{F}  = (-1,1)^3 \setminus (0,1)^3,
-    \qquad
+    \\
+    \begin{aligned}
     \Omega_{B} &= 
@@
     ,
-\end{align*}
+    \end{aligned}
+\end{gather*}
 % Cube 
@@
 
+MWL appreciates helpful remarks by Abdellatif Aitelhad.
+
 \bibliographystyle{plain}

### 2024-08-21 main.tex
Update on Overleaf.

@@
-\documentclass[10pt,a4paper]{article}
+\documentclass[10pt,letterpaper]{article}
 \usepackage[utf8]{inputenc}
@@
     \leq 
-    C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
+    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
     \quad 
@@
 %     \leq 
-%     C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
+%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
 %     \quad 
@@
     \leq 
-    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^p(\Omega)},
+    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
     \quad 
@@
 \begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
     ,
     \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
     .
@@
 If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and we call $T$ a \textit{supersimplex} of $S$.
+then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
 
@@
 Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
+Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
 We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
@@
 and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
 since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
@@
     \forall 
-    u \in L^p(\Omega)
+    u \in L^{p}(\Omega)
     .
@@
 \begin{align*}
-    \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^{p}(\Omega)},
 \end{align*}
 and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
+However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
+Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
 satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
@@
     \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
+    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
     \leq 
     \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
+    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    .
+\end{align*}
+A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
 \begin{align*}
@@
 \end{center}
-\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.}
+\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
+The dark gray triangle is the one being currently added, and the light gray triangles constitute the subdomain assembled so far.}
 \label{figure:exhausting}
@@
  We assess the norm of this potential. We observe 
- \begin{align*}
+ \begin{gather*}
     \| w'_{F_m} \|_{L^{p}(T_m)}
@@
     .
- \end{align*}
+ \end{gather*}
  In particular,
@@
         C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
+        ,
     \end{align*}
@@
 In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
+$W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
 \begin{gather*}
-    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    W^{p}(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
 \end{gather*}
@@
 \end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we let $v \lrcorner u \in \Alt^{k-1}(V)$ be defined via 
+We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
 \begin{align*}
@@
 \begin{gather*}
-    W^p\Alt^{k}(\Omega) 
+    W^{p}\Alt^{k}(\Omega) 
     := 
@@
 \end{gather*}
-We observe that $u \in L^p\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^p\Alt^{k+1}(\Omega)$
+We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
 if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
@@
 \end{align*}
-We let $W^p_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^p\Alt^{k}(\Omega)$ 
-for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^p\Alt^{k}(\bbR^{n})$. 
-The space $W^p_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.
+We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
+for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. 
+The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.
 
@@
 Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^p\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
+We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
 such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
@@
 \end{align*}
-
-We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
+If that condition is satisfied, we also write 
+\begin{align*}
+    \trace_{\Gamma} u = 0
+    .
+\end{align*}
+Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
+Lastly, we introduce the closed subspaces 
+\begin{gather*}
+    W^{p}_{0}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
+    .
+\end{gather*}
+We know that $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
+
+We are interested in transformations of Sobolev tensor fields from one domain onto the other. 
 Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^p\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
+The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
 \begin{gather*} 
@@
 \end{gather*}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.
+for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
 We cite an explicit transformation estimate~\cite{licht2019smoothed}.
@@
     &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
     .
@@
     &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
     .
@@
     &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt
     ,
@@
     &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
+    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt
     .
@@
     =
-    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;,
+    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da,
     \quad 
@@
     =
-    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da\;
+    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da
     .
@@
 \begin{align*}
-    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x)
+    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x).
 \end{align*}
@@
     u(x) = \cartan \Bogov_{\ell} u(x) + \Bogov_{\ell+1} \cartan u(x)
+    .
 \end{align*}
@@
     For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
-    \begin{align}
+    \begin{align*}
         x &= 
@@
         .
-    \end{align}
+    \end{align*}
     We know $x$ can be written as a unique convex combination of the vertices of $T$.
@@
             \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
+            .
         \end{align}
@@
     Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
-    Then for each $\bfu \in \bfW^{p}\Lambda^{?}(\Omega)$ there exists $w \in \bfW^{p}\Lambda^{?}(\Omega)$ with $\cartan u = \cartan w$ and 
-    \begin{align*}
-        \| \bfu \|_{L^{p}(\Omega)} 
-        \leq 
-        C_{???} % TODO 
+    Let $0 \leq k < n$. 
+    Then for each $\bfu \in \bfW^{p}\Lambda^{k}(\Omega)$ 
+    there exists $\bfw \in \bfW^{p}\Lambda^{k}(\Omega)$ 
+    with $\cartan \bfu = \cartan \bfw$ and 
+    \begin{align*}
+        \| \bfw \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        n A_{\Poinc}(n,k+1) 
+        \vol_{n}(B_1(0)) 
+        \frac{ \diam(\Omega)^{n} }{|\Omega|} 
         \diam(\Omega)
-        \| \divergence \bfu \|_{L^{p}(\Omega)}
+        \| \cartan \bfu \|_{L^{p}(\Omega)}
         .
@@
 \end{lemma}
+\begin{proof}
+    This follows from the discussion in Section~\ref{section:potentialoperator}.
+\end{proof}
 
@@
     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $w \in \bfH(\divergence,\Omega)$ with $\divergence u = \divergence w$ and 
-    \begin{align*}
-        \| \bfu \|_{L^{2}(\Omega)} \leq \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
+    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
+    \begin{align*}
+        \| \bfw \|_{L^{2}(\Omega)} 
+        \leq 
+        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
         .
@@
 
+\todo{Summarize the next two lemmas into one and complete the estimate}
 \begin{lemma}\label{lemma:PFexteriorwithboundaryconditions}
-    Let $T$ be a simplex and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(\Omega)$ such that 
+    Let $T$ be an $n$-simplex 
+    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    Suppose that $u \in \bfW^{p}\Lambda^{k}(T)$ such that 
     $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
@@
     \begin{align*}
-        \| u \| \leq 
+        \| u \| 
+        \leq 
     \end{align*}
@@
 
-    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{?}(T)$.
+    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{k}(T)$.
     We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}\Lambda^{?}(\Delta^{n})$ and $\cartan \hat u = \hat f$.
+    so that $\hat u \in \cartan \bfW^{p}\Lambda^{k}(\Delta^{n})$ and $\cartan \hat u = \hat f$.
 
@@
         \\&
+        \leq 
         2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
@@
     We use the pullback estimates 
-    \begin{align*}
+    \begin{gather*}
         \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
+        \leq 
         \| \Jacobian\varphi \|_{\infty}^{k}
@@
         \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        .
-    \end{align*}
-    \begin{align*}
+        ,
+        \\
         \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        &\leq 
+        \leq 
         2^{n-l}
@@
         .
-    \end{align*}
+    \end{gather*}
 \end{proof}
@@
         C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
+        ,
     \end{align*}
@@
     There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
     Then $\cartan \hat u = \hat g$. 
@@
 \begin{proof}
+    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
     By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
     We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-    See Figure~\ref{figure:exhausting} for an illustration.
 
@@
     \end{gather*}
-    Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
+    %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
     Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
     with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the interface $\Gamma_{m}$ with $U_{m-1} \subseteq \Omega_{m-1}$.
+    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
+    In accordance to Lemma~\ref{lemma:}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.
 
     We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow U_{m-1}$ is the reflection mapping. 
+    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
+    as in Theorem~\ref{theorem:starreflection}. 
     By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
@@
         \trace_F w_{m-1} = \trace_F w'_{m}
-        .
+        . % TODO: notation, 
     \end{align*}
@@
         \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
         \\&
@@
     \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
+    We also employ Theorem~\ref{theorem:pullbackestimate} to find 
     \begin{align*}
@@
         \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        \\&
-        \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        .
+        .
+    \end{align*}
+    By the properties of the reflection mapping in Theorem~\ref{theorem:starreflection},
+    \begin{align*}
+        ...
     \end{align*}
@@
     \end{align*}
-    and 
+    and \todo{fix estimate}
     \begin{align*}
@@
     \\
-    \Omega_{SS} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ),
+    \Omega_{SS} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ).
 \end{gather*}
@@
     \left( (-1,1) \times (-1,0) \times (-1,0) \right)
-    ,
+    .
     \end{aligned}

### 2024-08-21 draft.tex
reflection theorem
Update on Overleaf.

@@
 \begin{document}
+
+\begin{proof}
+    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
+    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
+    such that the $i$-th coordinate equals zero along $\hat F_i$.
+
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
+    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
+    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
+    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
+    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
+
+    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{k}(T)$.
+    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
+    so that $\hat u \in \cartan \bfW^{p}\Lambda^{k}(\Delta^{n})$ and $\cartan \hat u = \hat f$.
+
+    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
+    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
+
+    The operator norm bound of the potential operator shows 
+    \begin{align*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        &\leq 
+        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        \\&
+        \leq 
+        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
+        .
+    \end{align*}
+    We use the pullback estimates 
+    \begin{gather*}
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        \leq 
+        \| \Jacobian\varphi \|_{\infty}^{k}
+        |\det\varphi^{-\frac{1}{p}}|
+        \cdot 
+        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        ,
+        \\
+        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
+        \leq 
+        2^{n-l}
+        \| \hat f \|_{L^{p}(\hat T)} 
+        \leq 
+        2^{n-l}
+        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
+        |\det\varphi^{\frac{1}{p}}|
+        \cdot 
+        \| f \|_{L^{p}(T)} 
+        .
+    \end{gather*}
+\end{proof}
 
@@
 
+% Please cite the original version:
+% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
+% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
+% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant
+
+We recall a specialization of this result.
+
+\begin{lemma}\label{theorem:starreflection:facepatch}
+
+\end{lemma}
+
+% https://mathoverflow.net/questions/232302/lipschitz-constant-of-cental-projection-of-unit-ball-to-surface-of-convex-body
+% https://eudml.org/doc/258483
+% https://math.stackexchange.com/questions/1476085/uniformly-convex-approximation-of-convex-domain
+% SMOOTH EXHAUSTION FUNCTIONS IN CONVEX DOMAINS
+\begin{lemma}
+    Let $K \subseteq \bbR^{n}$ be a compact set star-shaped with respect to the origin 
+    that contains the ball $B_{r}(0)$ and that is contained in the ball $B_{R}(0)$. Then the function 
+    \begin{align*}
+        f : S \rightarrow \partial K, \quad x \mapsto \arg( \partial K \cap \bbR x )
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R^{2}/r % euclidean 
+    \end{align*}
+    If $K$ is convex, then 
+    \begin{align*}
+        g : S \rightarrow \bbR, \quad x \mapsto \| \bbR x \cap \partial K \|
+    \end{align*}
+    satisfies 
+    \begin{align*}
+        R \sqrt{ R^{2} / r^{2} - 1 } % angular distance 
+        \\
+        \frac R r \sqrt{ R^{2} - r^{2} } % angular distance 
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    .
+\end{proof}
+
 \end{document}

### 2024-08-21 main.tex
Update on Overleaf.

@@
 
+A major structural feature of shellable simplicial complexes 
+is that each time a simplex is added, the local star around a simplex gets completed.
+
+\begin{lemma}\label{lemma:existenceofstar}
+    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
+    For $0 \leq m < M$, write 
+    $$
+        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
+        \qquad 
+        I_{m} := X_{m} \cap T_{m+1}.
+    $$ 
+    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
+    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
+    $$
+        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
+    $$
+\end{lemma}
+\begin{proof}
+    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
+    that constitute the local patch around some simplex $S$ of dimension $n-k$.
+    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
+    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
+    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
+\end{proof}
+
 \begin{remark}
@@
     By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-    \todo{definition of weak derivative + definition of boundary condition }
-    % 
     This completes the proof. 
@@
 
-\begin{lemma}    
-    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
-    For $0 \leq m < M$, write 
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
-        \qquad 
-        I_{m} := X_{m} \cap T_{m+1}.
-    $$ 
-    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
-    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
-    $$
-        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
-    $$
-\end{lemma}
-\begin{proof}
-    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
-    that constitute the local patch around some simplex $S$ of dimension $n-k$.
-    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
-    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
-    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
-\end{proof}
-
 \begin{theorem}\label{theorem:starreflection}
@@
     where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
+
+    \todo{Complete the estimate.}
 \end{theorem}
@@
 
-\todo{Summarize the next two lemmas into one and complete the estimate}
-\begin{lemma}\label{lemma:PFexteriorwithboundaryconditions}
+\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
     Let $T$ be an $n$-simplex 
     and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $u \in \bfW^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
-    Then 
-    \begin{align*}
-        \| u \| 
-        \leq 
+    Suppose that $\bfu \in \bfW^{p}\Lambda^{k}(T)$ such that 
+    $\trace_{T,F_i} \bfu = 0$ for $0 \leq i \leq l$.
+    Then there exists $\bfw \in \bfW^{p}\Lambda^{k}(T)$ such that 
+    $\trace_{T,F_i} \bfw = 0$ for $0 \leq i \leq l$
+    and  
+    \begin{align*}
+        \cartan \bfu = \cartan \bfw,
+        \quad 
+        \| \bfw \| 
+        \leq 
+        C_{{\rm PF},T,F,k,p}
+        \| \cartan \bfu \|
+        ,
+    \end{align*}
+    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},T,F,k,p}
+        \leq 
+        ...
+        \diam(T)
+        .
     \end{align*}
@@
 \begin{proof}
-    We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
-    We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
-    such that the $i$-th coordinate equals zero along $\hat F_i$.
-
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism 
-    that maps the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ onto the boundary patch $\Gamma$. 
-    We let $\Upsilon^{n}$ be constructed by reflecting $\Delta^{n}$ across the coordinate axes $l+1$ through $n$.
-    The boundary $\partial\Upsilon^{n}$ is the reflection of the faces $\hat F_{0}, \hat F_{1}, \dots, \hat F_{l}$ under that process. 
-    Obviously, $\Upsilon^{n}$ is convex with diameter $2$.
-
-    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{k}(T)$.
-    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
-    so that $\hat u \in \cartan \bfW^{p}\Lambda^{k}(\Delta^{n})$ and $\cartan \hat u = \hat f$.
-
-    We construct $\tilde u \in L^{p}(\Upsilon^{n})$ as the reflection $\hat u$ across the coordinate axes $l+1$ through $n$, and we build $\tilde f \in L^{p}(\Upsilon^{n})$ analogously.
-    Then $\tilde u \in \bfW^{p}(\Upsilon^{n})$ with $\cartan \tilde u = \tilde f$.
-
-    The operator norm bound of the potential operator shows 
-    \begin{align*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
+    We can also assume that the face of $\hat T$
+    orthogonal to the $i$-th coordinate axis is mapped 
+    onto the face $F_i$. 
+    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$.
+
+    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    Then $\cartan \hat u = \hat g$. 
+    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes.
+    We define $\tilde g = \cartan \tilde u$
+    and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
+    By construction, $\tilde u \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$.
+
+    The bounds for the potential operators imply 
+    the existence of $\tilde w \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$
+    with $\cartan \tilde w = \cartan \tilde u$ and 
+    \begin{align*}
+        \| \tilde w \|_{L^{p}(\tilde U)}
         &\leq 
-        n A(n,\ell) \frac{ \vol_{n}(B_2(0)) }{|\Upsilon^{n}|} 2 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        \\&
-        \leq 
-        2 n A(n,\ell) \vol_{n}(B_1(0)) \frac{ n! \cdot 2^{n} }{2^{n-l}} 
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})}
-        .
-    \end{align*}
-    We use the pullback estimates 
+        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{|\Omega|} 
+        2
+        \| \tilde g \|_{L^{p}(\tilde U)}
+        \\&\leq 
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{|\Omega|} 
+        \| \tilde g \|_{L^{p}(\tilde U)}
+        .
+    \end{align*}
+    We let $\bfw \in \bfW^{p}\Lambda^{k}(T)$ be defined by $\bfw := \varphi^{-\ast} \tilde w$.
+    By construction, $\cartan \bfw = \cartan \bfu$,
+    and $\bfw$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.
+
+    In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
     \begin{gather*}
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
-        \leq 
-        \| \Jacobian\varphi \|_{\infty}^{k}
-        |\det\varphi^{-\frac{1}{p}}|
-        \cdot 
-        \| \tilde u \|_{L^{p}(\Upsilon^{n})} 
+        \| \bfw \|_{L^{p}(T_{m+1})}
+        \leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \tilde w \|_{L^{p}(\hat T)}
+        \leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \tilde w \|_{L^{p}(\tilde U)}
         ,
         \\
-        \| \tilde f \|_{L^{p}(\Upsilon^{n})} 
-        \leq 
-        2^{n-l}
-        \| \hat f \|_{L^{p}(\hat T)} 
-        \leq 
-        2^{n-l}
-        \| \Jacobian\varphi^{-1} \|_{\infty}^{k+1}
-        |\det\varphi^{\frac{1}{p}}|
-        \cdot 
-        \| f \|_{L^{p}(T)} 
-        .
-    \end{gather*}
-\end{proof}
-
-\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
-    Let $T$ be an $n$-simplex and with a face $F$. 
-    If $u \in W^{p}\Alt^{k}(T)$ such that $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{{\rm PF},T,F,k,p} \| \cartan u \|_{L^{p}(T)}
-        ,
-    \end{align*}
-    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,k,p}
-        \leq 
-        \diam(T)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
-    Then $\cartan \hat u = \hat g$. 
-    % 
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    We define $\tilde g = \cartan \tilde u$
-    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
-    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
-    \begin{gather*}
-        \| \tilde u \|_{L^{p}(\hat U)} 
-        \leq 
-        C_{???} 
-        \| \tilde g \|_{L^{p}(\hat U)}
-        .
-    \end{gather*}
-    In addition to that, 
-    \begin{gather*}
-        \| u \|_{L^{p}(T_{m+1})}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \hat u \|_{L^{p}(\hat T)}
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \tilde u \|_{L^{p}(\hat U)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\hat U)}
+        \| \tilde g \|_{L^{p}(\tilde U)}
         \leq 
@@
     By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We define $w'_{m} := w_{m-1} \circ \Xi_{m} \in W^{p}\Alt^{k}(T_{m})$,
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
     where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
@@
     We want to estimate norms. 
-    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} gives 
+    By construction,
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
+    we can assume 
     \begin{align*}
@@
     \begin{align*}
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k}
+        \cdot 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})}
+        ,
+        \\
         \| \cartan w'_{m} \|_{L^{p}(T_{m})}
@@
         |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
+        \| \Jacobian \Xi \|^{k+1}
         \cdot 
@@
     \end{align*}
+    We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
     By the properties of the reflection mapping in Theorem~\ref{theorem:starreflection},
@@
         ...
-    \end{align*}
-    Putting this all together, 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \left( 
-            \| \cartan u \|_{L^{p}(T_{m})} 
-            + 
-            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-    \end{align*}
-    and \todo{fix estimate}
-    \begin{align*}
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq  
-        %C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        %C_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
-        \\&
-        \leq  
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        C%_{{\rm PF},T_{m},\Gamma_{m},p} 
-        \| \cartan u \|_{L^{p}(U_{m-1})} 
-%         \\&
-%         \leq  
-%         \rho(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
-%         + 
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
-%         \| \cartan u \|_{L^{p}(T_{m})} 
-        .
     \end{align*}

### 2024-08-21 main.tex
Update on Overleaf.

@@
 This indicator quantifies how much reflection across the shared face distorts the geometry.
+
+We also want to compare the diameters of simplices that intersect. We define 
+\begin{align}\label{math:diametercomparison}
+    \theta(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
+    \frac{ \diam(T) }{ \diam(T') }
+\end{align}
+We moreover introduce 
+\begin{align}\label{math:algebraicshapemeasure}
+    \alpha(T)
+    := 
+    \sup_{ \varphi : \Delta^n \rightarrow T } 
+    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\max}( \Jacobian \varphi ) }
+    ,
+    \qquad 
+    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T)
+    ,
+\end{align}
+where the first suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$.
 
@@
     We write $\bfg \in \bfL^{\infty}(T)$ for the trivial extension of $\nabla u$ outside of $T$.
-    %With the fundamental theorem of calculus and H\"olders inequality: 
+    %With the fundamental theorem of calculus and H\"older's inequality: 
     Now:
@@
     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}_{0}\Lambda^{k}(\Omega)$.
+    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
+    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
 \end{lemma}
@@
     \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
+    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
 
     Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in \bfW^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
+    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
     Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in \bfW^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
+    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
     and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
@@
     \end{align*}
-    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
-    If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
+    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
+    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
 \end{theorem}
@@
     \begin{align*}
-        M := |\patch_{\calT}(S)| \setminus T.
+        U := |\patch_{\calT}(S)| \setminus T.
     \end{align*}
@@
     \begin{align*}
-        \varphi : T \rightarrow M
+        \Xi : T \rightarrow U
     \end{align*}
@@
     \begin{align*}
-        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
+        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
         \quad 
-        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
+        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
     \end{align*}
@@
         \begin{align*}
-            \Theta_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
+            \Xi_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
         \end{align*}
@@
         \begin{align*}
-            \| \Jacobian \Theta_{S} \| 
+            \| \Jacobian \Xi_{S} \| 
             \leq 
@@
         \begin{align*}
-            \color{red}
-            \| \Jacobian \Theta_{S} \| 
+            \| \Jacobian \Xi_{S} \| 
             &\leq 
-            2 \sup_{ K \in \patch_{\calT}(S) }
+            2 
+            \sup_{ K \in \patch_{\calT}(S) }
             2 \sigma_{\min}(A_{K}^{-1})^{-1} 
-            4 \sup_{ K \in \patch_{\calT}(S) } 
-            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
-            4 \sup_{ K \in \patch_{\calT}(S) } 
-            \kappa(A_{K})
+            4 
+            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
+            4 
+            \kappa(A_{T})
             \\&\leq 
@@
             \left( \sqrt{n} + 1 \right) 
+            \kappa(A_{T})
+            \sigma_{\max}(A_{T}^{-1}) 
             \sup_{ K \in \patch_{\calT}(S) }
             \sigma_{\max}(A_{K}     ) 
+            .
+        \end{align*}
+        We use 
+        \begin{gather*}
             \sup_{ K \in \patch_{\calT}(S) }
-            \sigma_{\max}(A_{K}^{-1}) 
+            \sigma_{\max}(A_{K}) 
+            \leq 
+            \Ceins{n} 
             \sup_{ K \in \patch_{\calT}(S) }
-            \kappa(A_{K})
-            .
-        \end{align*}
-        That establishes the final estimate.
-
+            \diam(K)
+            \leq 
+            \Ceins{n} 
+            \theta(\calT)
+            \sigma_{\max}(A_{T}) 
+            .
+        \end{gather*}
+        % That establishes the final estimate. 
 %         \item 
@@
     Let $0 \leq k < n$. 
-    Then for each $\bfu \in \bfW^{p}\Lambda^{k}(\Omega)$ 
-    there exists $\bfw \in \bfW^{p}\Lambda^{k}(\Omega)$ 
-    with $\cartan \bfu = \cartan \bfw$ and 
-    \begin{align*}
-        \| \bfw \|_{L^{p}(\Omega)}
+    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
+    with $\cartan u = \cartan w$ and 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
         &
@@
         \diam(\Omega)
-        \| \cartan \bfu \|_{L^{p}(\Omega)}
+        \| \cartan u \|_{L^{p}(\Omega)}
         .
@@
     and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
-    Suppose that $\bfu \in \bfW^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} \bfu = 0$ for $0 \leq i \leq l$.
-    Then there exists $\bfw \in \bfW^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} \bfw = 0$ for $0 \leq i \leq l$
+    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
+    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq l$
     and  
     \begin{align*}
-        \cartan \bfu = \cartan \bfw,
+        \cartan u = \cartan w,
         \quad 
-        \| \bfw \| 
+        \| w \| 
         \leq 
         C_{{\rm PF},T,F,k,p}
-        \| \cartan \bfu \|
+        \| \cartan u \|
         ,
@@
 
-    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
     Then $\cartan \hat u = \hat g$. 
@@
     and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
-    By construction, $\tilde u \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$.
+    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.
 
     The bounds for the potential operators imply 
-    the existence of $\tilde w \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$
+    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
     with $\cartan \tilde w = \cartan \tilde u$ and 
@@
     \end{align*}
-    We let $\bfw \in \bfW^{p}\Lambda^{k}(T)$ be defined by $\bfw := \varphi^{-\ast} \tilde w$.
-    By construction, $\cartan \bfw = \cartan \bfu$,
-    and $\bfw$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.
+    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} \tilde w$.
+    By construction, $\cartan w = \cartan u$,
+    and $w$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.
 
@@
     \begin{gather*}
-        \| \bfw \|_{L^{p}(T_{m+1})}
+        \| w \|_{L^{p}(T_{m+1})}
         \leq 

### 2024-08-22 main.tex
Update on Overleaf.

@@
 and they lead to lower bounds for the spectrum of finite element matrices. 
+The are several avenues for further research going from here.
+
+The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
+There are at least two points where the present techniques can be improved further.
+First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
+Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
+In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
+Better transformations or more careful estimates are likely possible, as are completely different approaches.
+For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
+
+Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over smoothly bounded convex domains, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
+These topics remain for future research.
 
@@
 Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-We conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over smoothly bounded convex domains, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
-These topics remain for future research. 
 \\
@@
 In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^k V\), is given by the binomial coefficient \(\binom{n}{k}\).
+% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
 
@@
     \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
+        \| w \|_{L^{p}(T_m)}
+        \leq 
+        ...
     \end{align*}
@@
     \end{align*}
+    This enables the recursion
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})}
+        \\&\qquad
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+        \| \cartan u      \|_{L^{p}(T_{m})} 
+        \\&\qquad
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k+1} 
+        \| \cartan u_{m-1} \|_{L^{p}(U_{m-1})}
+        .
+    \end{align*}
     The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 

### 2024-08-28 draft.tex
stuff

@@
 \begin{document}
+
+\color{red}
+        On the one hand, given $x, y \in T$, 
+        where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
+        \begin{align*}
+            &
+            \left\| F_T(x) - F_T(y) \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+            \\&\qquad 
+            \leq 
+            2\sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
+            \left\| x - y \right\|_{2}
+            .
+        \end{align*}
+        On the one hand, given $x, y \in T$, 
+        where $\| x \|_{2} \leq \| y \|_{2}$ without loss of generality, we find 
+        \begin{align*}
+            &
+            \left\| F_T(x) - F_T(y) \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+            \frac{\|y\|}{\|x\|}
+            +
+            \|A_{T}^{-1} y\|_1 \|y\|_{2}
+            \left| \frac{1}{\|x\|} - \frac{1}{\|y\|} \right|
+            \\&\qquad 
+            \leq 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+            \frac{\|y\|}{\|x\|}
+            +
+            \|A_{T}^{-1} y\|_1 \|y\|_{2}
+            \left| \frac{ \|y\|_{2} - \|x\|_{2} }{\|x\|_{2} \|y\|_{2}} \right|
+            \\&\qquad 
+            \leq 
+            3 \sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
+            \left\| x - y \right\|_{2}
+            .
+        \end{align*}
+        On the other hand, given $x, y \in F_T(T)$, 
+        where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
+        \begin{align*}
+            &
+            \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left\| 
+                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
+            \right\|_{2}
+            +
+            \left\| 
+                \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
+            \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|x\|_2 - \|y\|_2 \right|
+            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} }
+            +
+            \|y\|_2^{2}
+            \left| 
+            \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} \| A_{T}^{-1} y \|_{1} }
+            \right|
+            \\&\qquad 
+            \leq 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{2} } 
+            \left\| 
+                x - y
+            \right\|_{2}
+            +
+            \left| \|x\|_2 - \|y\|_2 \right|
+            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{2} }
+            +
+            \|y\|_2^{2}
+            \left| 
+            \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{2} \| A_{T}^{-1} y \|_{2} }
+            \right|
+            \\&\qquad 
+            \leq 
+            \left( 2 + \sqrt{n} \frac{\sigma_{\max}(A_{T}^{-1}) }{ \sigma_{\min}(A_{T}^{-1}) } \right) \sigma_{\min}(A_{T}^{-1})^{-1} 
+            \left\| x - y \right\|_{2}
+            \\&\qquad 
+            \leq 
+            \left( 2 + \sqrt{n} \kappa(A_{T}) \right) \sigma_{\max}(A_{T})
+            \left\| x - y \right\|_{2}
+            .
+        \end{align*}
+        By convexity of the range of $F_T(T)$, 
+        we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
+        We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
+        \color{black}
 

### 2024-08-28 main.tex
Update on Overleaf.
stuff

--- 2024-08-21 main.tex
@@
 
-We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
-\begin{align}\label{math:geometricshapemeasure}
+Whenever $T$ is any $n$-dimensional simplex $T$,
+we define the \textit{geometric shape measure} $\kappa(T)$
+and the \textit{algebraic shape measure} $\alpha(T)$ by 
+\begin{align}\label{math:shapemeasure}
     \kappa(T)
@@
     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-    .
-\end{align}
-
-\begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
-
-% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
-\begin{align}\label{math:moremeasures}
-    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
-%     \qquad 
-%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
+    ,
     \qquad 
-    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
-\end{align}
-Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
-Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
-that preserves $F$. We define 
-\begin{align}\label{math:reflectionmeasure}
-    \xi(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \| \Jacobian \Xi_{S,T} \|
-\end{align}
-to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
-This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-We also want to compare the diameters of simplices that intersect. We define 
-\begin{align}\label{math:diametercomparison}
-    \theta(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
-    \frac{ \diam(T) }{ \diam(T') }
-\end{align}
-We moreover introduce 
-\begin{align}\label{math:algebraicshapemeasure}
     \alpha(T)
@@
     \sup_{ \varphi : \Delta^n \rightarrow T } 
-    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\max}( \Jacobian \varphi ) }
-    ,
-    \qquad 
-    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T)
+    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
     ,
 \end{align}
-where the first suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$.
-
-% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
-% we define the quantity 
-% \begin{align*}
-%     \kappa(T)
-%     := 
-%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%     .
-% \end{align*}
-
-% DONE: Introduce a reference simplex 
-% DONE: DEFINE THE JACOBIAN 
-% \notice{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}
+where the last suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
+% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
+Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
+\begin{align}\label{math:shapemeasure:triangulation}
+    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
+    \quad 
+    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T).
+\end{align}
+Here, $\kappa(\calT)$ and $\alpha(\calT)$ are the geometric and algebraic shape measures of the triangulation.
 
@@
     Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{align*}
+    \begin{gather*}
         \| \Jacobian \varphi \|
@@
         \diam(T)^{-1}
-        .
-    \end{align*}
-    Here, $\Ceins{n} \leq \sqrt{n}$ and $\Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} }$. 
+        ,
+        \\
+        \alpha(T)
+        \leq 
+        \Csechs{n}
+        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
+        \kappa(T)
+        .
+    \end{gather*}
+    Here,
+    \begin{align*}
+        \Ceins{n} \leq \sqrt{n},
+        \quad 
+        \Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} },
+        \quad 
+        \Csechs{n} \leq \sqrt{ \frac{n}{ (n-1)^{n-1} } }
+        . 
+    \end{align*}
 \end{lemma}
@@
 
-% DONE: REMOVE THE \cdot 
+\begin{remark}
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    In our convention, the reference simplex has unit shape measure.
+    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
+$\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
+
+% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
+    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
+    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
+    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
+    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
+% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
+\end{remark}
+
+We are interested in the maximal ratio of volumes between neighboring $n$-simplices: 
+\begin{align}\label{math:volumecomparisonmeasure}
+    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
+\end{align}
+We also want to compare the diameters of simplices that intersect. We define 
+\begin{align}\label{math:diametercomparison}
+    \theta(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
+    \frac{ \diam(T) }{ \diam(T') }
+\end{align}
+Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
+that preserves $F$. We define 
+\begin{align}\label{math:reflectionmeasure}
+    \xi(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
+    \| \Jacobian \Xi_{S,T} \|
+\end{align}
+to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
+This indicator quantifies how much reflection across the shared face distorts the geometry.
+
+% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
+% we define the quantity 
+% \begin{align*}
+%     \kappa(T)
+%     := 
+%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%     .
+% \end{align*}
+
 \begin{lemma}\label{lemma:volumecomparison}
@@
 \end{proof}
+
+\begin{remark}
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ but not $\theta(\calT)$. 
+    We can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
+\end{remark}
 
@@
 Suppose that we have a shellable simplicial complex. 
-Every time add a simplex according to the shelling sequence, 
-we complete the local star of the some simplex in the triangulation.
-We search for a homeomorphism from the new simplex on its complement in the newly completed star
-such that the interface is preserved. 
-We want this homeomorphism to be bi-Lipschitz and we are particularly interested in the norms of its Jacobian.
+Every time we add a simplex according to the shelling sequence, 
+we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
+We will need a homeomorphism from the new simplex on its complement in the newly completed star.
+This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
+We are particularly interested in the norms of its Jacobian.
 
@@
 
+The main result of this section constructs the desired homeomorphism. 
+It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
+The construction is completed in several steps,
+and the Lipschitz estimate reflects the shape regularity.
+
 \begin{theorem}\label{theorem:starreflection}
@@
     \begin{align*}
-        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
+        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \theta(\calT) \alpha(T)^{2},
         \quad 
-        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
-    \end{align*}
-    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
+        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \theta(\calT) \alpha(T)^{2},
+    \end{align*}
+    where $...$ and $\Cfive{n}{k} \leq ...$
+    \begin{align*}
+        \Cvier{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
+        ,
+        \qquad 
+        \Cfive{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
+    \end{align*}
 
@@
         % 
-        \color{blue}
+        In what follows, $y \in \bbR^{n}$. 
         On the one hand, 
         we compute the Jacobian at any $x \in \mathring T$:
-        \begin{align}
-            \Jacobian F_T(x) 
-            = 
-            \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
+        \begin{align*}
+            \Jacobian F_T(x) \cdot y
+            &= 
+            \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
+            \left( \vecone \cdot A_{T}^{-1} x \right)
+            + 
+            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
+            \\&= 
+            \left( \Id - \|x\|^{-2} x \otimes x^t \right)
+            \frac{ 1 }{ \|x\| } 
             \left( \vecone \cdot A_{T}^{-1} x \right)
@@
             \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
-            .
-        \end{align}
-        The Euclidean operator norm is 
-        \begin{align}
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            \left( \Id - \hat x \otimes \hat x^t \right) y
+            + 
+            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+            .
+        \end{align*}
+        This is an orthogonal sum of two vectors. Its norm satisfies:
+        \begin{align*}
+            \| \Jacobian F_T(x) \cdot y \|^{2}
+            &= 
+            \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
+            \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
+            + 
+            \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
+            .
+        \end{align*}
+        The Euclidean operator norm satisfies 
+        \begin{align*}
             \| \Jacobian F_T(x) \| 
             \leq 
-            2 \left| \vecone \cdot A_{T}^{-1} x \right|
-            \leq 
-            2 \sqrt{n} \cdot \sigma_{\max}(A_{T}^{-1}) 
-            .
-        \end{align}
-        \color{black}
-        On the one hand, given $x, y \in T$, 
-        where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
-        \begin{align*}
-            &
-            \left\| F_T(x) - F_T(y) \right\|_{2}
-            \\&\qquad 
-            \leq 
+            \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
+            \leq 
+            \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
+            .
+        \end{align*}
+        On the other hand, we can rewrite the Jacobian as:
+        \begin{align*}
+            \Jacobian F_T(x) \cdot y
+            &= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            y
+            - 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            \left( \hat x \otimes \hat x^t \right) y
+            + 
+            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            y
+            - 
+            \hat x 
+            \left( 
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
+                -
+                \vecone^{t} A_{T}^{-1} 
+            \right) y
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            y
+            - 
+            \hat x 
+            \left( 
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+                -
+                A_{T}^{-t} \vecone
+            \right)^{t} y
+            .
+        \end{align*}
+        Its inverse is found via the Woodbury formula: 
+        % Its inverse is easily verified to be:
+        \begin{align*}
+            \Jacobian F_T(x)^{-1}
+            &= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+            \Id
+            - 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
+            \hat x 
+            \left( 
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+                -
+                A_{T}^{-t} \vecone
+            \right)^{t} 
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+            \left( 
+                \Id
+                - 
+                \hat x 
+                \left( 
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                    \hat x
+                    -
+                    \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                    A_{T}^{-t} \vecone
+                \right)^{t}
+            \right)
+            \\&= 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \left( 
+                \Id
+                - 
+                \hat x 
+                \left( 
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                    \hat x
+                    -
+                    \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                    A_{T}^{-t} \vecone
+                \right)^{t}
+            \right)
+            \\&= 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \left( 
+                \Id - \hat x \otimes \hat x^{t}
+                + 
+                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                \hat x \otimes \vecone^{t} A_{T}^{-1}
+            \right)
+            .
+        \end{align*}
+        The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
+        We notice the upper bound 
+        \begin{align*}
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            &= 
+            \| A_{T}^{-1} \hat x \|^{-1}_{1}
+            \\&\leq  
+            \| A_{T}^{-1} \hat x \|^{-1}_{2}
+            \leq 
+            \sigma_{\min}( A_{T}^{-1} )^{-1}
+            = 
+            \sigma_{\max}( A_{T} )
+            .
+        \end{align*}
+        This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
+        %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
+        If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
+        \begin{align*}
+            \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
+            &\leq 
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left\| 
+%                 y
+%             \right\|^{2}
+%             +
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left| 
+%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+%                 \vecone^{t} A_{T}^{-1} y 
+%             \right|^{2}
+%             \\&\leq 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
             \left\| 
-                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
-            \right\|_{2}
-            \\&\qquad 
-            \leq 
-            \left\| 
-                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
-            \right\|_{2}
+                y
+            \right\|^{2}
             +
-            \left\| 
-                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
-            \right\|_{2}
-            \\&\qquad 
-            \leq 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
-            \left\| 
-                x - y
-            \right\|_{2}
-            +
-            \left| \|A_{T}^{-1} x\|_2 - \|A_{T}^{-1} y\|_2 \right|
-            \\&\qquad 
-            \leq 
-            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
-            \left\| x - y \right\|_{2}
-            .
-        \end{align*}
-        On the other hand, given $x, y \in F_T(T)$, 
-        where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
-        \begin{align*}
-            &
-            \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
-            \\&\qquad 
-            \leq 
-            \left\| 
-                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
-            \right\|_{2}
-            \\&\qquad 
-            \leq 
-            \left\| 
-                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
-            \right\|_{2}
-            +
-            \left\| 
-                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
-            \right\|_{2}
-            \\&\qquad 
-            \leq 
-            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
-            \left\| 
-                x - y
-            \right\|_{2}
-            +
-            \left| \|x\|_2 - \|y\|_2 \right|
-            \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} }
-            \\&\qquad 
-            \leq 
-            2 \sigma_{\min}(A_{T}^{-1})^{-1} 
-            \left\| x - y \right\|_{2}
-            .
-        \end{align*}
-        By convexity of the range of $F_T(T)$, 
-        we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
-        We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
+            \frac{ 
+            \left| 
+                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                \vecone^{t} A_{T}^{-1} y 
+            \right|^{2}
+            }{
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
+            }
+            .
+        \end{align*}
+        The operator norm of that inverse is:
+        \begin{align*}
+            \| \Jacobian F_T(x)^{-1} \|
+            \leq 
+            \sigma_{\max}( A_{T} )
+            \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
+            .
+        \end{align*}
+        Since the domain and codomain of $F_{T}$ are convex, 
+        this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse.
 
@@
             \sup_{ K \in \calK  }
-            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
+            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
+            \sigma_{\max}(A_{K}) 
+            %
             \sup_{ K \in \calR' } 
-            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
+            \sqrt{2n} 
+            \sigma_{\max}(A_{K}^{-1}) 
+            %
             \sup_{ K \in \calR  } \kappa(A_{K})
-            .
-        \end{align*}
-        Each bisection halves the volume of the triangles. Thus,
+            \\
+            \| \Jacobian \Xi_{S}^{-1} \| 
+            \leq 
+            \sup_{ K \in \calK  }
+            \sqrt{2n} 
+            \sigma_{\max}(A_{K}^{-1}) 
+            %
+            \sup_{ K \in \calR' } 
+            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
+            \sigma_{\max}(A_{K}) 
+            %
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            .
+        \end{align*}
+        \color{red}
+        Each bisection step reduces the diameter by at most a factor of one half,
+        and it reduces the volume always by a factor of one half. 
+        Via the estimates in Lemma~\ref{lemma:affinetransform}, we thus find 
         \begin{align*}
@@
             &\leq 
-            2 
-            \sup_{ K \in \patch_{\calT}(S) }
-            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
-            4 
-            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
-            4 
-            \kappa(A_{T})
+            2 \left( \sqrt{n} + 1 \right) 
+            \sup_{ K \in \calK  }
+            \Ceins{n} \diam(K) 
+            \sup_{ K \in \calR' } 
+            \Czwei{n} \kappa(K) \diam(K)^{-1}
+            \sup_{ K \in \calR  } \kappa(A_{K})
             \\&\leq 
-            64
-            \left( \sqrt{n} + 1 \right) 
-            \kappa(A_{T})
-            \sigma_{\max}(A_{T}^{-1}) 
-            \sup_{ K \in \patch_{\calT}(S) }
-            \sigma_{\max}(A_{K}     ) 
-            .
-        \end{align*}
-        We use 
-        \begin{gather*}
-            \sup_{ K \in \patch_{\calT}(S) }
-            \sigma_{\max}(A_{K}) 
-            \leq 
+            32 \left( \sqrt{n} + 1 \right) 
+            \theta(\calT)
             \Ceins{n} 
-            \sup_{ K \in \patch_{\calT}(S) }
-            \diam(K)
-            \leq 
+            \Czwei{n} 
+            \kappa(\calT) 
+            \alpha(\calT)
+            \\
+            \| \Jacobian \Xi_{S}^{-1} \| 
+            &\leq 
+            2 \left( \sqrt{n} + 1 \right) 
+            \sup_{ K \in \calK  }
+            \Czwei{n} \kappa(K) \diam(K)^{-1}
+            \sup_{ K \in \calR' } 
+            \Ceins{n} \diam(K)
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            \\
+            &\leq 
+            32 \left( \sqrt{n} + 1 \right) 
+            \theta(\calT)
             \Ceins{n} 
-            \theta(\calT)
-            \sigma_{\max}(A_{T}) 
-            .
-        \end{gather*}
+            \Czwei{n} 
+            \kappa(\calT) 
+            \alpha(\calT)
+            .
+        \end{align*}
+        Together with the definition of $\theta(\calT)$, the desired result follows. 
+%         \color{red}
+%         Each bisection halves the volume of the triangles. Thus,
+%         \begin{align*}
+%             \| \Jacobian \Xi_{S} \| 
+%             &\leq 
+%             2 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             2 \sigma_{\max}(A_{K}) 
+%             4 
+%             \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
+%             4 
+%             \kappa(A_{T})
+%             \\&\leq 
+%             64
+%             \left( \sqrt{n} + 1 \right) 
+%             \kappa(A_{T})
+%             \sigma_{\max}(A_{T}^{-1}) 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}     ) 
+%             \\
+%             \| \Jacobian \Xi_{S}^{-1} \| 
+%             &\leq 
+%             2 \left( \sqrt{n} + 1 \right) 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}) 
+%             \sigma_{\max}(A_{T}^{-1}) 
+%             4 \kappa(A_{T})
+%             \\&\leq 
+%             64
+%             \left( \sqrt{n} + 1 \right) 
+%             \kappa(A_{T})
+%             \sigma_{\max}(A_{T}^{-1}) 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}     ) 
+%             .
+%         \end{align*}
+%         We use 
+%         \begin{gather*}
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}) 
+%             \leq 
+%             \Ceins{n} 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \diam(K)
+%             \leq 
+%             \Ceins{n} 
+%             \theta(\calT)
+%             \sigma_{\max}(A_{T}) 
+%             .
+%         \end{gather*}
+%         \color{black}
         % That establishes the final estimate. 

### 2024-08-28 main.tex

@@
         2^{\frac n p}
-        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
+        |\det( \Jacobian \varphi )|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
         \| \cartan u \|_{L^{p}(T)}

### 2024-08-28 draft.tex
Update on Overleaf.

@@
 \begin{document}
+
+        \item 
+        % \todo{Combine all this to get the final transformation.}
+        The last simplicial complex that we introduce is called $\calK$,
+        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
+
+        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
+        Using our initial observations, we obtain homeomorphisms 
+        \begin{align*}
+            \Psi_{\calK } : |\calK| \rightarrow \calB,
+            \qquad 
+            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
+        \end{align*}
+        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
+        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
+        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.
+        It follows that 
+        \begin{align*}
+            \Xi_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
+        \end{align*}
+        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
+        We estimate the Jacobians: 
+        \begin{align*}
+            \| \Jacobian \Xi_{S} \| 
+            \leq 
+            \sup_{ K \in \calK  }
+            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
+            \sigma_{\max}(A_{K}) 
+            %
+            \sup_{ K \in \calR' } 
+            \sqrt{2n} 
+            \sigma_{\max}(A_{K}^{-1}) 
+            %
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            \\
+            \| \Jacobian \Xi_{S}^{-1} \| 
+            \leq 
+            \sup_{ K \in \calK  }
+            \sqrt{2n} 
+            \sigma_{\max}(A_{K}^{-1}) 
+            %
+            \sup_{ K \in \calR' } 
+            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
+            \sigma_{\max}(A_{K}) 
+            %
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            .
+        \end{align*}
+        \color{red}
+        Each bisection step reduces the diameter by at most a factor of one half,
+        and it reduces the volume always by a factor of one half. 
+        Via the estimates in Lemma~\ref{lemma:affinetransform}, we thus find 
+        \begin{align*}
+            \| \Jacobian \Xi_{S} \| 
+            &\leq 
+            2 \left( \sqrt{n} + 1 \right) 
+            \sup_{ K \in \calK  }
+            \Ceins{n} \diam(K) 
+            \sup_{ K \in \calR' } 
+            \Czwei{n} \kappa(K) \diam(K)^{-1}
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            \\&\leq 
+            32 \left( \sqrt{n} + 1 \right) 
+            \theta(\calT)
+            \Ceins{n} 
+            \Czwei{n} 
+            \kappa(\calT) 
+            \alpha(\calT)
+            \\
+            \| \Jacobian \Xi_{S}^{-1} \| 
+            &\leq 
+            2 \left( \sqrt{n} + 1 \right) 
+            \sup_{ K \in \calK  }
+            \Czwei{n} \kappa(K) \diam(K)^{-1}
+            \sup_{ K \in \calR' } 
+            \Ceins{n} \diam(K)
+            \sup_{ K \in \calR  } \kappa(A_{K})
+            \\
+            &\leq 
+            32 \left( \sqrt{n} + 1 \right) 
+            \theta(\calT)
+            \Ceins{n} 
+            \Czwei{n} 
+            \kappa(\calT) 
+            \alpha(\calT)
+            .
+        \end{align*}
+        Together with the definition of $\theta(\calT)$, the desired result follows. 
+%         \color{red}
+%         Each bisection halves the volume of the triangles. Thus,
+%         \begin{align*}
+%             \| \Jacobian \Xi_{S} \| 
+%             &\leq 
+%             2 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             2 \sigma_{\max}(A_{K}) 
+%             4 
+%             \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
+%             4 
+%             \kappa(A_{T})
+%             \\&\leq 
+%             64
+%             \left( \sqrt{n} + 1 \right) 
+%             \kappa(A_{T})
+%             \sigma_{\max}(A_{T}^{-1}) 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}     ) 
+%             \\
+%             \| \Jacobian \Xi_{S}^{-1} \| 
+%             &\leq 
+%             2 \left( \sqrt{n} + 1 \right) 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}) 
+%             \sigma_{\max}(A_{T}^{-1}) 
+%             4 \kappa(A_{T})
+%             \\&\leq 
+%             64
+%             \left( \sqrt{n} + 1 \right) 
+%             \kappa(A_{T})
+%             \sigma_{\max}(A_{T}^{-1}) 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}     ) 
+%             .
+%         \end{align*}
+%         We use 
+%         \begin{gather*}
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \sigma_{\max}(A_{K}) 
+%             \leq 
+%             \Ceins{n} 
+%             \sup_{ K \in \patch_{\calT}(S) }
+%             \diam(K)
+%             \leq 
+%             \Ceins{n} 
+%             \theta(\calT)
+%             \sigma_{\max}(A_{T}) 
+%             .
+%         \end{gather*}
+%         \color{black}
+        % That establishes the final estimate. 
+%         \item 
+%         Suppose that $S = \{v_0\}$ is a single vertex. 
+%         We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
+%         Without loss of generality, $S$ is at the origin. 
+%         For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
+%         We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
+%         \todo{Complete}
+%
+
+%         \item 
+%         Let $\calU$ be the simplicial complex of dimension $n-1$ that contains precisely those facets of $T$ that do not contain $S$.
+%         We write $Y := F( |\calU| )$. 
+%         \todo{Shape of the outer patch $Y$, star-shaped geometry}
+%         
+%         \item 
+%         We let $\sphere{n}_{\star} := \sphere{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
+%         Suppose that $\bar x \in \sphere{n}$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
+%         We define its stereographic projection as 
+%         \begin{align*}
+%             \pi( \bar x ) 
+%             = 
+%             \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
+%             .
+%         \end{align*}
+%         This is a mapping $\pi : \sphere{n}_{\star} \rightarrow \bbR^{n}$. 
+%         Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
+%         \begin{align*}
+%             \pi^{-1}( y )
+%             = 
+%             \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
+%             +
+%             \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
+%             .
+%         \end{align*}
+%         \item 
+%         Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
+%         \begin{align*}
+%             \mu : \bbR^{n} \rightarrow \bbR^{n},
+%             \qquad 
+%             y \mapsto \frac{y}{\| y \|}.
+%         \end{align*}
+%         \item 
+%         \begin{align*}
+%             G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
+%         \end{align*}
+%         \item 
+%         We combine these mappings:
+%         \begin{align*}
+%             Q : \sphere{n} \rightarrow \sphere{n}, \qquad x \mapsto \pi^{-1} G^{-1} \mu G \pi(x)
+%         \end{align*}
+%         We want to analyze its Lipschitz properties. \todo{Stuff}
+%         \item
+%         We have constructed a bi-Lipschitz mapping from the Euclidean unit sphere into itself.
+%         We use the following result~\cite[Theorem~3]{alestalo2018radial}:
+%         if $f : \sphere{n} \rightarrow \sphere{n}$ is any $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
+%         then the radial extension $f : \ball{n} \rightarrow \ball{n}$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
+%         Consequently, \todo{write out}
+%         \item 
+%         In total, we thus have 
+%         \begin{align*}
+%             Q' := F^{-1} \pi^{-1} G^{-1} \mu G \pi F
+%             .
+%         \end{align*}
+
+        \item 
+        We begin with the following preparatory observations. 
+        Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
+        We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
+        That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
+        Then the mapping 
+        \begin{align}
+            F_T(x) 
+            = 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
+        \end{align}
+        maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
+        \begin{align}
+            F_T^{-1}(x) 
+            = 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
+            .
+        \end{align}
+        We analyze its Lipschitz properties.
+        % 
+        In what follows, $y \in \bbR^{n}$. 
+        On the one hand, 
+        we compute the Jacobian at any $x \in \mathring T$:
+        \begin{align*}
+            \Jacobian F_T(x) \cdot y
+            &= 
+            \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
+            \left( \vecone \cdot A_{T}^{-1} x \right)
+            + 
+            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
+            \\&= 
+            \left( \Id - \|x\|^{-2} x \otimes x^t \right)
+            \frac{ 1 }{ \|x\| } 
+            \left( \vecone \cdot A_{T}^{-1} x \right)
+            + 
+            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            \left( \Id - \hat x \otimes \hat x^t \right) y
+            + 
+            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+            .
+        \end{align*}
+        This is an orthogonal sum of two vectors. Its norm satisfies:
+        \begin{align*}
+            \| \Jacobian F_T(x) \cdot y \|^{2}
+            &= 
+            \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
+            \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
+            + 
+            \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
+            .
+        \end{align*}
+        The Euclidean operator norm satisfies 
+        \begin{align*}
+            \| \Jacobian F_T(x) \| 
+            \leq 
+            \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
+            \leq 
+            \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
+            .
+        \end{align*}
+        On the other hand, we can rewrite the Jacobian as:
+        \begin{align*}
+            \Jacobian F_T(x) \cdot y
+            &= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            y
+            - 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            \left( \hat x \otimes \hat x^t \right) y
+            + 
+            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            y
+            - 
+            \hat x 
+            \left( 
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
+                -
+                \vecone^{t} A_{T}^{-1} 
+            \right) y
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+            y
+            - 
+            \hat x 
+            \left( 
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+                -
+                A_{T}^{-t} \vecone
+            \right)^{t} y
+            .
+        \end{align*}
+        Its inverse is found via the Woodbury formula: 
+        % Its inverse is easily verified to be:
+        \begin{align*}
+            \Jacobian F_T(x)^{-1}
+            &= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+            \Id
+            - 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
+            \hat x 
+            \left( 
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+                -
+                A_{T}^{-t} \vecone
+            \right)^{t} 
+            \\&= 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+            \left( 
+                \Id
+                - 
+                \hat x 
+                \left( 
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                    \hat x
+                    -
+                    \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                    A_{T}^{-t} \vecone
+                \right)^{t}
+            \right)
+            \\&= 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \left( 
+                \Id
+                - 
+                \hat x 
+                \left( 
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                    \hat x
+                    -
+                    \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                    A_{T}^{-t} \vecone
+                \right)^{t}
+            \right)
+            \\&= 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \left( 
+                \Id - \hat x \otimes \hat x^{t}
+                + 
+                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                \hat x \otimes \vecone^{t} A_{T}^{-1}
+            \right)
+            .
+        \end{align*}
+        The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
+        We notice the upper bound 
+        \begin{align*}
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            &= 
+            \| A_{T}^{-1} \hat x \|^{-1}_{1}
+            \\&\leq  
+            \| A_{T}^{-1} \hat x \|^{-1}_{2}
+            \leq 
+            \sigma_{\min}( A_{T}^{-1} )^{-1}
+            = 
+            \sigma_{\max}( A_{T} )
+            .
+        \end{align*}
+        This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
+        %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
+        If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
+        \begin{align*}
+            \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
+            &\leq 
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left\| 
+%                 y
+%             \right\|^{2}
+%             +
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left| 
+%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+%                 \vecone^{t} A_{T}^{-1} y 
+%             \right|^{2}
+%             \\&\leq 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+            \left\| 
+                y
+            \right\|^{2}
+            +
+            \frac{ 
+            \left| 
+                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                \vecone^{t} A_{T}^{-1} y 
+            \right|^{2}
+            }{
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
+            }
+            .
+        \end{align*}
+        The operator norm of that inverse is:
+        \begin{align*}
+            \| \Jacobian F_T(x)^{-1} \|
+            \leq 
+            \sigma_{\max}( A_{T} )
+            \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
+            .
+        \end{align*}
+        Since the domain and codomain of $F_{T}$ are convex, 
+        this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse.
 

### 2024-08-28 main.tex
Update on Overleaf.

@@
 Since $\Omega$ is connected, this is equivalent to  
-\begin{align}
+\begin{align*}
     \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
@@
     .
-\end{align}
+\end{align*}
 We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
@@
 % for all $u \in W^{1,p}(\Omega)$
-\begin{align}
+\begin{align*}
     \| u - u_{\Omega} \|_{L^{p}(\Omega)}
@@
     ,
-\end{align}
+\end{align*}
 where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
@@
 where we use an upper bound by Chua and Wheeden:
-\begin{align}
+\begin{align*}
     C_{{\rm P},{\rm CW},p} 
@@
     .
-\end{align}
+\end{align*}
 Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
@@
 where $C_{{\rm PF},{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align}
+\begin{align*}
     C_{{\rm PF},{\rm EFNT},p}
@@
     .
-\end{align}
+\end{align*}
 Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
@@
 \begin{subequations}\label{eq_definition_piola}
-\begin{align}
+\begin{align*}
     \phi^{\grad}(v) &= v \circ \phi, \\
@@
     \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
-\end{align}
+\end{align*}
 \end{subequations}
@@
 we then define the integral operators
-\begin{align}
+\begin{align*}
   \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
@@
   \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align}
+\end{align*}
 We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
@@
         \item 
-        We begin with the following preparatory observations. 
-        Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
-        We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
-        That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
-        Then the mapping 
-        \begin{align}
-            F_T(x) 
-            = 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
-        \end{align}
-        maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
-        \begin{align}
-            F_T^{-1}(x) 
-            = 
-            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
-            .
-        \end{align}
-        We analyze its Lipschitz properties.
-        % 
-        In what follows, $y \in \bbR^{n}$. 
-        On the one hand, 
-        we compute the Jacobian at any $x \in \mathring T$:
-        \begin{align*}
-            \Jacobian F_T(x) \cdot y
-            &= 
-            \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
-            \left( \vecone \cdot A_{T}^{-1} x \right)
-            + 
-            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
-            \\&= 
-            \left( \Id - \|x\|^{-2} x \otimes x^t \right)
-            \frac{ 1 }{ \|x\| } 
-            \left( \vecone \cdot A_{T}^{-1} x \right)
-            + 
-            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
-            \\&= 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-            \left( \Id - \hat x \otimes \hat x^t \right) y
-            + 
-            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
-            .
-        \end{align*}
-        This is an orthogonal sum of two vectors. Its norm satisfies:
-        \begin{align*}
-            \| \Jacobian F_T(x) \cdot y \|^{2}
-            &= 
-            \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
-            \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
-            + 
-            \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
-            .
-        \end{align*}
-        The Euclidean operator norm satisfies 
-        \begin{align*}
-            \| \Jacobian F_T(x) \| 
-            \leq 
-            \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
-            \leq 
-            \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
-            .
-        \end{align*}
-        On the other hand, we can rewrite the Jacobian as:
-        \begin{align*}
-            \Jacobian F_T(x) \cdot y
-            &= 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-            y
-            - 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-            \left( \hat x \otimes \hat x^t \right) y
-            + 
-            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
-            \\&= 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-            y
-            - 
-            \hat x 
-            \left( 
-                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
-                -
-                \vecone^{t} A_{T}^{-1} 
-            \right) y
-            \\&= 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-            y
-            - 
-            \hat x 
-            \left( 
-                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
-                -
-                A_{T}^{-t} \vecone
-            \right)^{t} y
-            .
-        \end{align*}
-        Its inverse is found via the Woodbury formula: 
-        % Its inverse is easily verified to be:
-        \begin{align*}
-            \Jacobian F_T(x)^{-1}
-            &= 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-            \Id
-            - 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
-            \hat x 
-            \left( 
-                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
-                -
-                A_{T}^{-t} \vecone
-            \right)^{t} 
-            \\&= 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-            \left( 
-                \Id
-                - 
-                \hat x 
-                \left( 
-                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
-                    \hat x
-                    -
-                    \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-                    A_{T}^{-t} \vecone
-                \right)^{t}
-            \right)
-            \\&= 
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-            \left( 
-                \Id
-                - 
-                \hat x 
-                \left( 
-                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
-                    \hat x
-                    -
-                    \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-                    A_{T}^{-t} \vecone
-                \right)^{t}
-            \right)
-            \\&= 
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-            \left( 
-                \Id - \hat x \otimes \hat x^{t}
-                + 
-                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-                \hat x \otimes \vecone^{t} A_{T}^{-1}
-            \right)
-            .
-        \end{align*}
-        The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
-        We notice the upper bound 
-        \begin{align*}
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-            &= 
-            \| A_{T}^{-1} \hat x \|^{-1}_{1}
-            \\&\leq  
-            \| A_{T}^{-1} \hat x \|^{-1}_{2}
-            \leq 
-            \sigma_{\min}( A_{T}^{-1} )^{-1}
-            = 
-            \sigma_{\max}( A_{T} )
-            .
-        \end{align*}
-        This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
-        %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
-        If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
-        \begin{align*}
-            \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
-            &\leq 
-%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
-%             \left\| 
-%                 y
-%             \right\|^{2}
-%             +
-%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
-%             \left| 
-%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-%                 \vecone^{t} A_{T}^{-1} y 
-%             \right|^{2}
-%             \\&\leq 
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
-            \left\| 
-                y
-            \right\|^{2}
-            +
-            \frac{ 
-            \left| 
-                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-                \vecone^{t} A_{T}^{-1} y 
-            \right|^{2}
-            }{
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
-            }
-            .
-        \end{align*}
-        The operator norm of that inverse is:
-        \begin{align*}
-            \| \Jacobian F_T(x)^{-1} \|
-            \leq 
-            \sigma_{\max}( A_{T} )
-            \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
-            .
-        \end{align*}
-        Since the domain and codomain of $F_{T}$ are convex, 
-        this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse.
-
-        \item 
         Without loss of generality, the barycenter of $S$ is the origin. 
-        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
-        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
+        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
+        %We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
+        %So $J$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
         We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
@@
         \item 
-        We construct a new triangulation that contains $T$ and that is a star around $S$.
-        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
-        We first define a new triangulation $\calS$ by the barycentric refinement of $T$. 
+        We let $z'_{S}$ be the midpoint of $S'$. 
+        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary $S'$. 
         All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
@@
         We let $\calR$ and $\calR^{c}$ be the corresponding refinements of $\calS$ and $\calS^{c}$, respectively.
+
+        The last simplicial complex that we introduce is called $\calK$,
+        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
 
@@
         \item 
-        % \todo{Combine all this to get the final transformation.}
-        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
-        Using our initial observations, we obtain homeomorphisms 
-        \begin{align*}
-            \Psi_{\calK } : |\calK| \rightarrow \calB,
-            \qquad 
-            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
-        \end{align*}
-        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
-        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
-        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.
+        We introduce a bi-Lipschitz mapping 
+        \begin{align*}
+            \Psi : |\calR'| \rightarrow |\calK|
+        \end{align*}
+        in the following manner. Let $T \in \calR'$ be an $n$-dimensional simplex and let $x \in T$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
+        We define 
+        \begin{align*}
+            \Psi(x) 
+            = 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
+            .
+        \end{align*}
+        One easily verifies that this defines a continuous mapping $\Psi$. 
+        By the same line of thought, we see that it is invertible with inverse 
+        \begin{align*}
+            \Psi^{-1}(x) 
+            = 
+            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} } x
+            .
+        \end{align*}
+        We analyze its Jacobian. 
+        First, by assumption,
+        \begin{align*}
+            \Psi(x) 
+            = 
+            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
+            .
+        \end{align*}
+        In what follows, $y \in \bbR^n$. We observe 
+        \begin{align*}
+            \Jacobian \Psi(x) \cdot y 
+            &= 
+            \frac{ 
+                ( A_{T}^{-t} \vecone \cdot y ) 
+                ( A_{K}^{-t} \vecone \cdot x )
+                -
+                ( A_{T}^{-t} \vecone \cdot x )
+                ( A_{K}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot x )^2
+            } 
+            x
+            + 
+            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
+            \\&= 
+            \frac{ 
+                ( A_{T}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot  x )
+            } 
+            x
+            -
+            \frac{ 
+                ( A_{T}^{-t} \vecone \cdot x )
+                ( A_{K}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot  x )^2
+            } 
+            x
+            + 
+            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
+            \\&= 
+            \frac{ 
+                ( A_{T}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot  x )
+            } 
+            x
+            +
+            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
+            \left( 
+                y
+                -
+                \frac{ 
+                    ( A_{K}^{-t} \vecone \cdot y ) 
+                }{ 
+                    ( A_{K}^{-t} \vecone \cdot  x ) 
+                } 
+                x
+            \right)
+            .
+        \end{align*}
+        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes.
+We conclude that
+        \[
+             A_{K}^{-t} \vecone \cdot x 
+             = 
+             \vecone \cdot A_{K}^{-1} x 
+             \geq 
+             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
+        \]
+        Together with the Xu-Zikatanov inequality, we obtain the upper bound 
+        \begin{align*}
+            \| \Jacobian \Psi(x) \|
+            &\leq 
+            \sqrt{n}
+            \frac{ \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
+            \left( 
+            1
+            + 
+            n
+            \frac{ \sigma_{\max}( A_{T}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
+            \right) 
+            .
+        \end{align*}
+        By completely analogous arguments, we find 
+        \begin{align*}
+            \| \Jacobian \Psi(x) \|
+            &\leq 
+            \sqrt{n}
+            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{T}^{-1} ) }
+            \left( 
+            1
+            + 
+            n
+            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{T}^{-2} ) }
+            \right) 
+            .
+        \end{align*}
         It follows that 
         \begin{align*}
-            \Xi_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
+            \Xi := \Psi \circ \Theta
         \end{align*}
         is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
-        We estimate the Jacobians: 
-        \begin{align*}
-            \| \Jacobian \Xi_{S} \| 
-            \leq 
-            \sup_{ K \in \calK  }
-            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
-            \sigma_{\max}(A_{K}) 
-            %
-            \sup_{ K \in \calR' } 
-            \sqrt{2n} 
-            \sigma_{\max}(A_{K}^{-1}) 
-            %
-            \sup_{ K \in \calR  } \kappa(A_{K})
-            \\
-            \| \Jacobian \Xi_{S}^{-1} \| 
-            \leq 
-            \sup_{ K \in \calK  }
-            \sqrt{2n} 
-            \sigma_{\max}(A_{K}^{-1}) 
-            %
-            \sup_{ K \in \calR' } 
-            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
-            \sigma_{\max}(A_{K}) 
-            %
-            \sup_{ K \in \calR  } \kappa(A_{K})
-            .
-        \end{align*}
-        \color{red}
+        It preserves the interface from $T$ onto $U$. 
+        It is continuous and bi-Lipschitz due to Rademacher's theorem.
+
+        \item 
+        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
         Each bisection step reduces the diameter by at most a factor of one half,
         and it reduces the volume always by a factor of one half. 
-        Via the estimates in Lemma~\ref{lemma:affinetransform}, we thus find 
+        We use the estimates in Lemma~\ref{lemma:affinetransform}.
+        This shows
+
+        \color{red}
         \begin{align*}
@@
         Together with the definition of $\theta(\calT)$, the desired result follows.
-%         \color{red}
-%         Each bisection halves the volume of the triangles. Thus,
-%         \begin{align*}
-%             \| \Jacobian \Xi_{S} \| 
-%             &\leq 
-%             2 
-%             \sup_{ K \in \patch_{\calT}(S) }
-%             2 \sigma_{\max}(A_{K}) 
-%             4 
-%             \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
-%             4 
-%             \kappa(A_{T})
-%             \\&\leq 
-%             64
-%             \left( \sqrt{n} + 1 \right) 
-%             \kappa(A_{T})
-%             \sigma_{\max}(A_{T}^{-1}) 
-%             \sup_{ K \in \patch_{\calT}(S) }
-%             \sigma_{\max}(A_{K}     ) 
-%             \\
-%             \| \Jacobian \Xi_{S}^{-1} \| 
-%             &\leq 
-%             2 \left( \sqrt{n} + 1 \right) 
-%             \sup_{ K \in \patch_{\calT}(S) }
-%             \sigma_{\max}(A_{K}) 
-%             \sigma_{\max}(A_{T}^{-1}) 
-%             4 \kappa(A_{T})
-%             \\&\leq 
-%             64
-%             \left( \sqrt{n} + 1 \right) 
-%             \kappa(A_{T})
-%             \sigma_{\max}(A_{T}^{-1}) 
-%             \sup_{ K \in \patch_{\calT}(S) }
-%             \sigma_{\max}(A_{K}     ) 
-%             .
-%         \end{align*}
-%         We use 
-%         \begin{gather*}
-%             \sup_{ K \in \patch_{\calT}(S) }
-%             \sigma_{\max}(A_{K}) 
-%             \leq 
-%             \Ceins{n} 
-%             \sup_{ K \in \patch_{\calT}(S) }
-%             \diam(K)
-%             \leq 
-%             \Ceins{n} 
-%             \theta(\calT)
-%             \sigma_{\max}(A_{T}) 
-%             .
-%         \end{gather*}
-%         \color{black}
-        % That establishes the final estimate. 
-%         \item 
-%         Suppose that $S = \{v_0\}$ is a single vertex. 
-%         We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
-%         Without loss of generality, $S$ is at the origin. 
-%         For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
-%         We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
-%         \todo{Complete}
-%
-
-%         \item 
-%         Let $\calU$ be the simplicial complex of dimension $n-1$ that contains precisely those facets of $T$ that do not contain $S$.
-%         We write $Y := F( |\calU| )$. 
-%         \todo{Shape of the outer patch $Y$, star-shaped geometry}
-%         
-%         \item 
-%         We let $\sphere{n}_{\star} := \sphere{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
-%         Suppose that $\bar x \in \sphere{n}$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
-%         We define its stereographic projection as 
-%         \begin{align}
-%             \pi( \bar x ) 
-%             = 
-%             \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
-%             .
-%         \end{align}
-%         This is a mapping $\pi : \sphere{n}_{\star} \rightarrow \bbR^{n}$. 
-%         Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
-%         \begin{align}
-%             \pi^{-1}( y )
-%             = 
-%             \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
-%             +
-%             \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
-%             .
-%         \end{align}
-%         \item 
-%         Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
-%         \begin{align}
-%             \mu : \bbR^{n} \rightarrow \bbR^{n},
-%             \qquad 
-%             y \mapsto \frac{y}{\| y \|}.
-%         \end{align}
-%         \item 
-%         \begin{align}
-%             G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
-%         \end{align}
-%         \item 
-%         We combine these mappings:
-%         \begin{align}
-%             Q : \sphere{n} \rightarrow \sphere{n}, \qquad x \mapsto \pi^{-1} G^{-1} \mu G \pi(x)
-%         \end{align}
-%         We want to analyze its Lipschitz properties. \todo{Stuff}
-%         \item
-%         We have constructed a bi-Lipschitz mapping from the Euclidean unit sphere into itself.
-%         We use the following result~\cite[Theorem~3]{alestalo2018radial}:
-%         if $f : \sphere{n} \rightarrow \sphere{n}$ is any $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
-%         then the radial extension $f : \ball{n} \rightarrow \ball{n}$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
-%         Consequently, \todo{write out}
-%         \item 
-%         In total, we thus have 
-%         \begin{align}
-%             Q' := F^{-1} \pi^{-1} G^{-1} \mu G \pi F
-%             .
-%         \end{align}
+
     \end{itemize}

### 2024-08-29 main.tex
Update on Overleaf.

@@
 \usepackage{hyperref}         % For hypertext links
+
+\usepackage{enumitem}
+\setitemize[1]{left=0.0cm}
 
@@
     \begin{align*}
-        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \theta(\calT) \alpha(T)^{2},
+        \Lip( \Xi,      T ) \leq \Cvier{n}{k}(\calT),
         \quad 
-        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \theta(\calT) \alpha(T)^{2},
-    \end{align*}
-    where $...$ and $\Cfive{n}{k} \leq ...$
-    \begin{align*}
-        \Cvier{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
-        ,
-        \qquad 
-        \Cfive{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
-    \end{align*}
-
-    \todo{Complete the estimate.}
+        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k}(\calT),
+    \end{align*}
+    where $\Cvier{n}{k}(\calT)$ and $\Cfive{n}{k}(\calT)$ are constants as stated in the proof. 
 \end{theorem}
@@
         \end{align*}
-        in the following manner. Let $T \in \calR'$ be an $n$-dimensional simplex and let $x \in T$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
+        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
         We define 
@@
             = 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
+            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
             .
@@
             = 
-            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} } x
+            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x
             .
@@
             = 
-            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
             .
@@
             \frac{ 
-                ( A_{T}^{-t} \vecone \cdot y ) 
+                ( A_{{G}}^{-t} \vecone \cdot y ) 
                 ( A_{K}^{-t} \vecone \cdot x )
                 -
-                ( A_{T}^{-t} \vecone \cdot x )
+                ( A_{{G}}^{-t} \vecone \cdot x )
                 ( A_{K}^{-t} \vecone \cdot y ) 
@@
             + 
-            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
             \\&= 
             \frac{ 
-                ( A_{T}^{-t} \vecone \cdot y ) 
+                ( A_{{G}}^{-t} \vecone \cdot y ) 
             }{ 
@@
             \frac{ 
-                ( A_{T}^{-t} \vecone \cdot x )
+                ( A_{{G}}^{-t} \vecone \cdot x )
                 ( A_{K}^{-t} \vecone \cdot y ) 
@@
             + 
-            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
             \\&= 
             \frac{ 
-                ( A_{T}^{-t} \vecone \cdot y ) 
+                ( A_{{G}}^{-t} \vecone \cdot y ) 
             }{ 
@@
             +
-            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
             \left( 
@@
         \end{align*}
+        We see that the last summand is an oblique projection of $y$. 
         The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes.
@@
             \sqrt{n}
-            \frac{ \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
+            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
             \left( 
@@
             n
-            \frac{ \sigma_{\max}( A_{T}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
+            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
             \right) 
@@
         \begin{align*}
-            \| \Jacobian \Psi(x) \|
+            \| \Jacobian \Psi^{-1}(x) \|
             &\leq 
             \sqrt{n}
-            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{T}^{-1} ) }
+            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-1} ) }
             \left( 
@@
             n
-            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{T}^{-2} ) }
+            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-2} ) }
             \right) 
@@
         \end{align*}
-        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
-        It preserves the interface from $T$ onto $U$. 
+        is a mapping from ${G}$ onto $U = \overline{\patch_{\calT}(S) \setminus {G}}$.
+        It preserves the interface from ${G}$ onto $U$. 
         It is continuous and bi-Lipschitz due to Rademacher's theorem.
@@
         We use the estimates in Lemma~\ref{lemma:affinetransform}.
-        This shows
-
-        \color{red}
-        \begin{align*}
-            \| \Jacobian \Xi_{S} \| 
+        When $K \in \calK \cup \calS'r$, then 
+        \begin{align*}
+             \sigma_{\max}( A_{K}^{-1} )
              &\leq 
-            2 \left( \sqrt{n} + 1 \right) 
-            \sup_{ K \in \calK  }
-            \Ceins{n} \diam(K) 
-            \sup_{ K \in \calR' } 
-            \Czwei{n} \kappa(K) \diam(K)^{-1}
-            \sup_{ K \in \calR  } \kappa(A_{K})
-            \\&\leq 
-            32 \left( \sqrt{n} + 1 \right) 
-            \theta(\calT)
+             \Czwei{n} \kappa(K) \diam(K)
+             \leq 
+             2 \Czwei{n} \kappa(\calT) \diam(K)^{-1}
+             \\
+             \sigma_{\min}( A_{K}^{-1} )^{-1}
+             &= 
+             \sigma_{\max}( A_{K} ) 
+             \leq 
+             \Ceins{n} \diam(K),
+             \\ 
+             \kappa( A_{K} )
+             &\leq 
+             \Csechs{n} \kappa(K) \leq 2 \Csechs{n} \kappa(\calT)
+             .
+        \end{align*}
+        When ${G} \in \calR'$ is not our original simplex, then 
+        \begin{align*}
+             \sigma_{\max}( A_{{G}}^{-1} )
+             &\leq 
+             \Czwei{n} \kappa({G}) \diam({G})
+             \leq 
+             4 \Czwei{n} \kappa(\calT) \diam(G)^{-1},
+             \\
+             \sigma_{\min}( A_{{G}}^{-1} )^{-1}
+             &= 
+             \sigma_{\max}( A_{{G}} ) 
+             \leq 
+             \Ceins{n} \diam({G}),
+             \\ 
+             \kappa( A_{{G}} )
+             &\leq 
+             \Csechs{n} \kappa({G}) \leq 4 \Csechs{n} \kappa(\calT)
+             .
+        \end{align*}
+        All the diameters above are comparable up to a factor of $\theta(\calT)$.
+        In summary,
+        \begin{gather*}
+            \| \Jacobian \Theta_{|K}      \| \leq 2 \Csechs{n} \kappa(\calT)
+            ,
+            \qquad 
+            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Csechs{n} \kappa(\calT)
+            ,
+            \\
+            \| \Jacobian \Xi(x) \|
+            \leq 
+            \sqrt{n}
+            4 
+            \kappa(\calT) 
             \Ceins{n} 
             \Czwei{n} 
+            \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
+            \left( 
+                1
+                + 
+                n
+                2 \Csechs{n} \kappa(\calT)
+                4 
                 \kappa(\calT) 
-            \alpha(\calT)
-            \\
-            \| \Jacobian \Xi_{S}^{-1} \| 
-            &\leq 
-            2 \left( \sqrt{n} + 1 \right) 
-            \sup_{ K \in \calK  }
-            \Czwei{n} \kappa(K) \diam(K)^{-1}
-            \sup_{ K \in \calR' } 
-            \Ceins{n} \diam(K)
-            \sup_{ K \in \calR  } \kappa(A_{K})
-            \\
-            &\leq 
-            32 \left( \sqrt{n} + 1 \right) 
-            \theta(\calT)
                 \Ceins{n} 
                 \Czwei{n} 
+                \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
+            \right) 
+            2 \Csechs{n} \kappa(\calT)
+            ,
+            \\
+            \| \Jacobian \Xi^{-1}(x) \|
+            \leq 
+            \sqrt{n}
+            2 
             \kappa(\calT) 
-            \alpha(\calT)
-            .
-        \end{align*}
-        Together with the definition of $\theta(\calT)$, the desired result follows.
-
+            \Ceins{n} 
+            \Czwei{n} 
+            \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
+            \left( 
+                1
+                + 
+                n
+                2 \Csechs{n} \kappa(\calT)
+                2 
+                \kappa(\calT) 
+                \Ceins{n} 
+                \Czwei{n} 
+                \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
+            \right) 
+            2 \Csechs{n} \kappa(\calT)
+            .
+        \end{gather*}
     \end{itemize}
@@
     While the reflection mapping and its analysis in Theorem~\ref{theorem:starreflection} serve our purpose,
-    it might be possible to improve the estimate with a different analysis or construction.
+    it might be possible to improve the estimate with an improved analysis or construction.
 \end{remark}

### 2024-08-29 main.tex
clean up

@@
 
+    \todo{Decide which paragraph remains...}
+
     \item
@@
     Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
-    The intersection of any two of them is $F$, and their interiors are disjoint.
-
-    Consider the case that $z_F$ lies on the boundary of $\calM$. 
-    If $F$ is contained in at least two distinct $n$-simplices of $\calT$,
-    then we can construct an embedded $n$-dimensional open ball that contains $z_F$.
-    But that contradicts $z_F$ being on the boundary. 
-    So any boundary face can only be contained in one single $n$-simplex.
+    The intersection of any two of them is $F$, but their interiors are disjoint because otherwise they would coincide.
 
@@
     then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
-    At the same time, $X = F \cap \partial \mathring B_F$ is empty if $n=1$ or homeomorphic to a sphere of dimension $n-2$. % TODO: proofread
-    We see that $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
+    Consider $X = F \cap \partial \mathring B_F$.
+    If $n=1$, then $X$ is empty and $\partial \mathring B_F$ has $K$ distinct connected components. .
+    If $n > 1$, then $X$ is homeomorphic to a sphere of dimension $n-2$
+    and again $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
     But by the auxiliary result above, $K = 2$. 
     We conclude that $F$ is contained in two $n$-simplices of $\calT$.
-%     But by construction $\partial \mathring B_F \setminus X$ is homeomorphic to $S \setminus S'$,
-%     which has exactly two distinct connected components according to the Jordan-Brouwer separation theorem.
-%     If an inner face $F$ were contained in only one $n$-simplex,
-%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-%     So each inner face is contained in exactly two $n$-simplices. 
-%     \todo{More details}
-
-%     If $F$ is contained in only one $n$-simplex, then it must be a face in the boundary of $\calM$. 
-%     If $F$ were contained in at least two $n$-simplices,
-%     then we could construct a homeomorphism from the $n$-ball onto itself that maps an interior point on the its boundary, which cannot be.
-%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex. 
-%     \todo{More details}
-%     {\color{blue}
-%     The doubling $M_{D}$ of the manifold $M$ is obtained by gluing $M$ to a copy of itself along the boundary.
-%     The triangulation $\calT$ can be doubled to get a triangulation of the doubled manifold.
-%     Any boundary face is an interior face of the doubled manifold two $n$-simplices of the doubled triangulation.
-%     So each face within $\partial \calM$ is contained in exactly one $n$-simplex of $\calT$. 
-%     }
+
+    Consider the case that $z_F$ lies on the boundary of $\calM$
+    and suppose that $F$ is contained in $K$ distinct $n$-simplices of $\calT$.
+    By adding at least one dimension, we can double the manifold $\calM$ along the boundary and obtain the doubled manifold $\calM'$.
+Similarly, we can construct a doubling of the triangulation $\calT'$ such that $F$ is contained in exactly $2K$ distinct $n$-simplices of $\calT'$.
+We know that $\calM'$ is a manifold without boundary, and hence $F$ is an interior simplex of $\calT'$.
+    This implies $K=1$.
+    So any boundary face can only be contained in one single $n$-simplex.
 
@@
 
+    \item 
     So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
@@
     \end{align*}
-    are subsets of $\patch_{\calT}(S)$.
-    For each $K \in \patch_{\calT}(S)$ that contains $S$ and which has the complementary simplex $F_S$, 
+    are compactly contained subsets of $|\patch_{\calT}(S)|$.
+    For each simplex $K \in \patch_{\calT}(S)$ that contains the vertex $z$ and which has the opposite face $F_K$, 
     we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
     such that 
-    $\phi_{K|S}$ is the identity,
+    $\phi_{K}(z) = z$, 
     such that 
-    $\phi_{K}(S_F) = S_{\delta}(z)$,
+    $\phi_{K}( K \cap S_{\delta}(z) ) = F_{K}$,
+    such that 
+    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$,
     and such that 
-    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$.
+    $\phi_{K}$ maps $[0,1]\cdot v$ linearly into $\bbR \cdot v$. 
+    This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$.
 
@@
     which is the case if and only if $S$ is a boundary simplex, 
-    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z)$, 
-    which is a topological ball of dimension $n-1$. % TODO: explain why
+    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ along $\phi$.
+    The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
+    and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. Notice that 
+    \begin{align*}
+        \partial\left( { B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)| \right)
+        =
+        S_{\delta}(z) \cap |\patch_{\calT}(S)|
+        \cup 
+        \overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|
+        .
+    \end{align*}
+    Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ from $\overline{B_{\delta}(z)} \cap |\calT|$
+    onto the closed unit ball.
+Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere.
+Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
+    But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$.
 
@@
     We show that each vertex star is strongly connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere is strongly connected. 
-    Now, if $n \geq 1$, then any vertex star in an $(n+1)$-dimensional manifold triangulation is strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
+    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are strongly connected. 
+    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
     The induction argument implies that each vertex star in $\calT$ is strongly connected.
@@
     Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$.
-    We also notice that each vertex star is strongly connected. 
-    We can thus change the first sequence to another $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
-    such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
+    As each vertex star is strongly connected, 
+    we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
+    is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+    This just means that $\calT$ is strongly connected. 
     \end{enumerate}
@@
 
-    %\todo{Double check this proof and make it more explicit.}
     Write $M = |\calT|$. 
@@
     Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
-    and a triangle is not good in $\calT$ if that intersection is either empty only some of its vertices, or a vertex and the opposite edge.
-    % TODO: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
+    and a triangle is not good in $\calT$ if that intersection is either empty, only some of its vertices, or a vertex and the opposite edge.
+    % DONE: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
     We show by an induction argument over the number of triangles that every triangulation of a $2$-disk that contains at least two triangles also contains at least two good triangles.
@@
     So each component has at least one triangle that is good in $\calT$. 
-
-    % There exists a triangle $T' \in \calT$ with at least one edge in the boundary. 
-    % If $T'$ is good, then we are already done. 
-    % Otherwise, $T'$ intersects the boundary at one edge and its opposing vertex.
-    % \todo{MV:But what if this is the neighbor of $T'$ and adding $T'$ back makes the triangle bad?}
-
-    Since $\calT$ triangulates a $2$-disk,
+    Hence $\calT$ contains two good triangles, which completes the induction step.
+
+    We conclude that whenever $\calT$ triangulates a $2$-disk,
     it contains a good triangle $T$. 
@@
     Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
-%     Let $\calT$ be a simplicial $2$-disk. 
-%     If $\calT$ contains only one triangle, then there is nothing to show. 
-%     Otherwise, there exists at least one triangle $T$ that touches the boundary of the disk at either one or two edges 
-%     {\color{red}Needs proof}. 
-%   
-%     Now let $\calS$ be any simplicial $2$-sphere. 
-%     By removing any triangle $S \in \calS$, we obtain a simplicial $2$-disk, which is shellable. 
-%     Any of its shellings can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    The proof is complete. 
 \end{proof}
@@
     Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
-    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
+    then the intersection of those facets is an interior simplex $S \in \calT$ of dimension $n-k$ that satisfies 
     $$
@@
     that constitute the local patch around some simplex $S$ of dimension $n-k$.
-    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
-    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
-    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
+    By assumption, $S$ must be a boundary simplex of $X_{m}$ and it is an interior simplex of $X_{m+1}$. 
+    But then $S$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
+    which means that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$. 
+    This had to be shown.
 \end{proof}
@@
         \item 
-        % \todo{Reflect onto complement and estimate bi-Lipschitz constant}
         We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
@@
         \trace_F w_{m-1} = \trace_F w'_{m}
-        . % TODO: notation, 
+        . 
     \end{align*}

### 2024-08-29 main.tex
Update on Overleaf.

@@
     We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
-    We will use the following fact: if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$. 
+    We will use the following fact:\footnote{To see this, one easily constructs a continuous deformation of $\calM$ into itself to move any chosen point on $S$ to any other chosen point on $S$.} if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$.
     Since the boundary $\partial \calM$ is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
@@
     Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    As a consequence of the Jordan-Brouwer separation theorem~\cite[Corollary 5.24]{mayer1989algebraische}~\cite[Corollary 6.4]{massey1981algebraic}, 
+    As a consequence of the Jordan-Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
     we know that $Y \setminus X$ has got two connected components.
 
-    \item 
-    We prove an auxiliary result. 
-    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
-    Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
-    we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    As a consequence of the Jordan-Brouwer separation theorem~\cite[Theorem 5.23]{mayer1989algebraische}~\cite[Corollary 5.24]{mayer1989algebraische}~\cite[Corollary 6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
-    and thus $Y \setminus X$ has got two connected components.
-
-    \todo{Decide which paragraph remains...}
+    % \item 
+    % We prove an auxiliary result. 
+    % Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
+    % The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
+    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
+    % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
+    % As a consequence of the Jordan-Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
+    % and thus $Y \setminus X$ has got two connected components.
 
@@
 
-    Consider the case that $z_F$ lies on the boundary of $\calM$
-    and suppose that $F$ is contained in $K$ distinct $n$-simplices of $\calT$.
-    By adding at least one dimension, we can double the manifold $\calM$ along the boundary and obtain the doubled manifold $\calM'$.
+    Consider the case that $z_F$ lies on the boundary of $\calM$ and suppose that $F$ is contained in $K$ distinct $n$-simplices of $\calT$.
+    By adding at least one dimension, we can double\footnote{The reader is referred to Lee's textbook~\cite{lee2012smooth} for more background and the technicalities.} the manifold $\calM$ along the boundary and obtain the doubled manifold $\calM'$.
     Similarly, we can construct a doubling of the triangulation $\calT'$ such that $F$ is contained in exactly $2K$ distinct $n$-simplices of $\calT'$. 
@@
     This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$. 
+    Moreover, one easily verifies that $\phi$ is bi-Lipschitz.
+    For $\delta > 0$ small enough, $B_{\delta}(z)$ is homeomorphic to the unit ball and that homeomorphism maps $S_{\delta}(z)$ onto the unit sphere.
 
@@
 
-    If $z$ is a boundary vertex of $\calS'$,
-    which is the case if and only if $S$ is a boundary simplex, 
-    then the underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ along $\phi$.
-    The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
-    and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. Notice that 
-    \begin{align*}
-        \partial\left( { B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)| \right)
-        =
-        S_{\delta}(z) \cap |\patch_{\calT}(S)|
-        \cup 
-        \overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|
-        .
-    \end{align*}
-    Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ from $\overline{B_{\delta}(z)} \cap |\calT|$
-    onto the closed unit ball.
-Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere.
+    Now suppose that $z$ is a boundary vertex of $\calS'$,
+    which is the case if and only if $S$ is a boundary simplex. 
+    Write 
+    \[
+        B_{H} = \left\{ x \in B_1(0) \suchthat* x_1 \leq 0 \right\},
+        \quad 
+        S_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 \leq 0 \right\}.
+        \quad 
+        D_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
+    \]
+    Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $D_H$,
+    and which maps $z$ to the origin. 
+    %
+    It follows that $\phi'$ maps the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$ onto $S_H$.
+    %
+    Assuming that $\delta$ is small enough once more, 
+    we now verify that $\phi^{-1}$ maps $|\carapace(S)|$ onto $S_{\delta}(z) \cap |\patch_{\calT}(S)|$.
+    The latter equals the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$.
+    It follows that $\carapace(S)$ triangulates a topological ball of dimension $n-1$.
+
+    % We let $\calM'$ be the doubling of the manifold and let $\calT'$ be the doubling of the present triangulation;
+    % we refer to Lee's textbook~\cite{lee2011topological} for details. 
+    % The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
+    % and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. 
+    % The underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ along $\phi$.
+    % The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
+    % and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. 
+    % Notice that 
+    % \begin{align*}
+    %     \partial\left( { B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)| \right)
+    %     =
+    %     S_{\delta}(z) \cap |\patch_{\calT}(S)|
+    %     \cup 
+    %     \overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|
+    %     .
+    % \end{align*}
+    % Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere.
 Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
-    But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$.
+    % But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$.
 

### 2024-09-01 main.tex
overhaul

@@
 We recall that this means that for every $x \in \underlying{\calT}$
-there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
-such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| \leq 1 \}$
-or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
+% there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
+there exists an open neighborhood $U(x) \subseteq \underlying{\calT}$ and an embedding $\phi : U(x) \rightarrow \bbR^{n}$
+such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the open unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| < 1 \}$
+or onto the half-ball $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
 In the former case, $x$ is called an \emph{interior point}, and in the latter case $x$ is called a \emph{boundary point}. 
@@
     If $z_F$ is an interior point of $\calM$, 
-    then we can assume that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
+    then we can assume by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
     Consider $X = F \cap \partial \mathring B_F$.
-    If $n=1$, then $X$ is empty and $\partial \mathring B_F$ has $K$ distinct connected components. .
+    If $n=1$, then $X$ is empty and $\partial \mathring B_F$ has $K$ distinct connected components. 
     If $n > 1$, then $X$ is homeomorphic to a sphere of dimension $n-2$
@@
 
-We continue with a few more observations about manifold triangulations.
+We continue with a few more observations about manifold triangulations
+at the intersection of topology and combinatorics. 
+These include the topology of local stars, which is a surprisingly non-trivial topic. 
+We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{locally vertex combinatorial}
+if the local star of every simpelx $S \in \calT$ is a triangulated $n$-dimensional ball that contains $S$.
+We gather some results that are hard to find in the literature.
 
@@
     Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
+    Suppose that $1 \leq n \leq 3$. Then the following holds:
     \begin{itemize}
-        \item If $S$ is an inner simplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
+        \item
+        If $S \in \calT$ is an inner simplex, 
+        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
         and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
-        \item If $S$ is a boundary subsimplex, then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
+        \item
+        If $S \in \calT$ is a boundary subsimplex, 
+        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
         and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
-        \item If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
     \end{itemize}
@@
 \begin{proof}
+    The lemma is obvious if $n = 1$, so we assume $n \geq 2$ in what follows. 
     We prove these statements in several steps. 
+    The reader is assumed to have some background in topology. 
     \begin{enumerate}
@@
     In particular, $z_F$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
+    So it remains to study the topology of vertex stars.
 
     \item 
-    So it remains to study the topology of vertex stars. Suppose that $S = \{z\}$ is a singleton simplex. 
-    For $\delta > 0$ small enough, 
-    \begin{align*}
-        B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
-        \quad 
-        S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
-    \end{align*}
-    are compactly contained subsets of $|\patch_{\calT}(S)|$.
-    For each simplex $K \in \patch_{\calT}(S)$ that contains the vertex $z$ and which has the opposite face $F_K$, 
-    we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
-    such that 
-    $\phi_{K}(z) = z$, 
-    such that 
-    $\phi_{K}( K \cap S_{\delta}(z) ) = F_{K}$,
-    such that 
-    for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$,
-    and such that 
-    $\phi_{K}$ maps $[0,1]\cdot v$ linearly into $\bbR \cdot v$. 
-    This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$. 
-    Moreover, one easily verifies that $\phi$ is bi-Lipschitz.
-    For $\delta > 0$ small enough, $B_{\delta}(z)$ is homeomorphic to the unit ball and that homeomorphism maps $S_{\delta}(z)$ onto the unit sphere.
-
-    If $z$ is an inner vertex of $\calS'$, 
-    then the boundary simplices of $\calS'$,
-    which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
-
-    Now suppose that $z$ is a boundary vertex of $\calS'$,
-    which is the case if and only if $S$ is a boundary simplex. 
-    Write 
-    \[
-        B_{H} = \left\{ x \in B_1(0) \suchthat* x_1 \leq 0 \right\},
-        \quad 
-        S_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 \leq 0 \right\}.
-        \quad 
-        D_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
-    \]
-    Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $D_H$,
-    and which maps $z$ to the origin. 
+    Suppose that $2 \leq n \leq 3$ and that $\calM$ is a manifold without boundary. 
+    Under these assumptions, 
+    as explained in the proof of Theorem~1 in \cite{Siebenmann1979},
+    the set $\carapace(V)$ is a triangulation of a sphere of dimension $n-1$ for any inner vertex $V$. 
+    There exists a homeomorphism from the closed cone of $\underlying{\carapace(V)}$ onto the local star $\underlying{\patch_{\calT}(V)}$.
+    But then that closed cone and hence $\underlying{\patch_{\calT}(V)}$ are homeomorphic to an $n$-dimensional ball.
+
+    \item 
+    If $2 \leq n \leq 3$ and $\calM$ has a non-empty boundary, then we use an approach as in the proof of Lemma~\ref{lemma:boundarysimplices}: 
+    we let $\calM'$ denote the doubling of the manifold and $\calT'$ be the doubling of the triangulation $\calT$. 
+    Let $V \in \calT$ be a vertex. 
+    If $V$ is an inner vertex of $\calT$, then $\carapace(V) \subseteq \calT \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT \subseteq \calT'$ triangulates a ball of dimension $n$, as discussed above.
+    If $V$ is a boundary vertex of $\calT$, then it is an inner vertex of $\calT'$,
+    and so $\carapace_{\calT}(V) \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT'$ triangulates a ball of dimension $n$.
+    We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$.
+`
+    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere. 
+    It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
+    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the local star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.
+
+    \item 
+%     Suppose that $S = \{z\}$ is a singleton simplex. 
+%     For $\delta > 0$ small enough, 
+%     \begin{align*}
+%         B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
+%         \quad 
+%         S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
+%     \end{align*}
+%     are compactly contained subsets of $|\patch_{\calT}(S)|$.
+%     For each simplex $K \in \patch_{\calT}(S)$ that contains the vertex $z$ and which has the opposite face $F_K$, 
+%     we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
+%     such that 
+%     $\phi_{K}(z) = z$, 
+%     such that 
+%     $\phi_{K}( K \cap S_{\delta}(z) ) = F_{K}$,
+%     such that 
+%     for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$,
+%     and such that 
+%     $\phi_{K}$ maps $[0,1]\cdot v$ linearly into $\bbR \cdot v$. 
+%     This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$. 
+%     Moreover, one easily verifies that $\phi$ is bi-Lipschitz.
+%     %     For $\delta > 0$ small enough, $B_{\delta}(z)$ is homeomorphic to the unit ball and that homeomorphism maps $S_{\delta}(z)$ onto the unit sphere. 
+%     \item 
+%     One sees that $\phi$ defines a mapping from the closed 
+%     homeomorphism between cone of link and ball 
 %     
-    It follows that $\phi'$ maps the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$ onto $S_H$.
+%     If $z$ is an inner vertex of $\calS'$, 
+%     then the boundary simplices of $\calS'$,
+%     which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
 %     
-    Assuming that $\delta$ is small enough once more, 
-    we now verify that $\phi^{-1}$ maps $|\carapace(S)|$ onto $S_{\delta}(z) \cap |\patch_{\calT}(S)|$.
-    The latter equals the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$.
-    It follows that $\carapace(S)$ triangulates a topological ball of dimension $n-1$.
-
+%     Now suppose that $z$ is a boundary vertex of $\calS'$,
+%     which is the case if and only if $S$ is a boundary simplex. 
+%     Write 
+%     \[
+%         B_{H} = \left\{ x \in B_1(0) \suchthat* x_1 \leq 0 \right\},
+%         \quad 
+%         S_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 \leq 0 \right\}.
+%         \quad 
+%         D_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
+%     \]
+%     Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $D_H$,
+%     and which maps $z$ to the origin. 
+%         %
+%     It follows that $\phi'$ maps the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$ onto $S_H$.
+%         %
+%     Assuming that $\delta$ is small enough once more, 
+%     we now verify that $\phi^{-1}$ maps $|\carapace(S)|$ onto $S_{\delta}(z) \cap |\patch_{\calT}(S)|$.
+%     The latter equals the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$.
+%     It follows that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
     % We let $\calM'$ be the doubling of the manifold and let $\calT'$ be the doubling of the present triangulation;
@@
     % But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
-
-    \item 
-    We show that each vertex star is strongly connected via a short induction argument.
+    \end{enumerate}
+    All relevant results are proven. 
+\end{proof}
+
+\begin{lemma}\label{lemma:connectivity}
+    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
+    If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
+\end{lemma}
+\begin{proof}
+    We first show that each vertex star is strongly connected via a short induction argument.
     Clearly, any simplicial $1$-ball and simplicial $1$-sphere are strongly connected. 
@@
 
-    \item 
-    If the underlying space is connected, then we easily see that the union of the $1$-simplices is path-connected.
+    If the underlying space $\underlying{\calT}$ is connected, 
+    then we easily see that the union of the $1$-simplices is path-connected.
     Given $n$-simplices $S,S' \in \calT$, 
@@
     This just means that $\calT$ is strongly connected. 
-    \end{enumerate}
-    All relevant results are proven. 
 \end{proof}
@@
 \begin{remark}
+    Triangulations with the property that all vertex stars are homeomorphic to a ball are also called \emph{combinatorial} \cite[Section~1]{Bagchi2005}.
+    All manifolds of dimension up to three admit smooth structures and smooth manifolds admit combinatorial triangulations. 
+    There are triangulations of manifolds in dimension higher than $3$ where not every vertex star is homeomorphic to a ball.
+
     Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
@@
 \begin{theorem}\label{theorem:starreflection}
-    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
-    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
+    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
+    Let $S \in \calT$ be a simplex of dimension $k < n$,
+    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
+    and let 
     \begin{align*}

### 2024-09-03 main.tex
Update on Overleaf.
some draft section

@@
 
-    \item 
 %     Suppose that $S = \{z\}$ is a singleton simplex. 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:stars_are_shellable}
     Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
@@
         It preserves the interface from ${G}$ onto $U$.
-        It is continuous and bi-Lipschitz due to Rademacher's theorem.
+
+        \item 
+        \color{red}
+        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
+        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+        After application of a piecewise linear Lipschitz mapping, 
+        we can assume that $|\calK|$ is convex without loss of generality. 
+        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.
+
+        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
+        \color{black}
 

### 2024-09-03 main.tex
last sections

--- 2024-09-01 main.tex
@@
     satisfying
-    \begin{align*}
-        \Lip( \Xi,      T ) \leq \Cvier{n}{k}(\calT),
+    \begin{gather*}
+        \| \Jacobian\Xi \|          \leq \Cvier{n}(\calT),
         \quad 
-        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k}(\calT),
-    \end{align*}
-    where $\Cvier{n}{k}(\calT)$ and $\Cfive{n}{k}(\calT)$ are constants as stated in the proof. 
+        \| \Jacobian\Xi^{-1} \|     \leq \Cfive{n}(\calT),
+        \\
+        \| \det\Jacobian\Xi \|      \leq \Cdetvier{n}(\calT),
+        \quad 
+        \| \det\Jacobian\Xi^{-1} \| \leq \Cdetfive{n}(\calT),
+    \end{gather*}
+    where the constants on the right-hand sides are as stated in the proof. 
 \end{theorem}
@@
         \end{align*}
+        \color{red}
+        By construction, 
+        \begin{align*}
+            \det( \Jacobian \Theta_{|K} )
+            = 
+            \det( \Jacobian^{-1} \Theta_{|K} )
+            =
+            1
+            .
+        \end{align*}
+        \color{black}
 
@@
         \leq 
-        C_{{\rm PF},T,F,k,p}
+        C_{{\rm PF},\Gamma,l,k,p}(T)
+        \diam(T)^{k} 
         \| \cartan u \|
-        ,
-    \end{align*}
-    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,k,p}
-        \leq 
-        ...
-        \diam(T)
+        .
+    \end{align*}
+    Here, $C_{{\rm PF},\Gamma,l,k,p}(T) > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},\Gamma,l,k,p}(T)
+        \leq 
+        2^{\frac n p}
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
+        \Ceins{n}(T)^{k}
+        % \| \Jacobian \varphi \|^{k}
         .
@@
     In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
+    We see that $\vol(\tilde U) = (l+1)/n!$
 
@@
         &\leq 
-        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{|\Omega|} 
+        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{ \vol(\tilde U) } 
         2
@@
         \\&\leq 
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{|\Omega|} 
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
         \| \tilde g \|_{L^{p}(\tilde U)}
@@
         2^{\frac n p}
-        |\det( \Jacobian \varphi )|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
+        |\det( \Jacobian \varphi )|^{-\frac 1 p} 
+        \| \Jacobian \varphi \|^{k}
+        \cdot 
         \| \cartan u \|_{L^{p}(T)}
@@
 \end{proof}
+
+In what follows, use the abbreviation
+\begin{align*}
+    C_{{\rm PF},\Gamma,k,p}(\calT) 
+    :=
+    \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
+    C_{{\rm PF},\Gamma,l,k,p}(T)   
+\end{align*}
+whenever $\calT$ is an $n$-dimensional triangulation.
 
@@
     there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        \leq 
-        ...
+    and such that for each $T_{m} \in \calT$ in the shelling
+    we have the following recursive estimate: 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+%         &
+%         \leq  
+%         C_{{\rm PF},\Gamma,k,p}(\calT) 
+%         \Cdetfive{n}(\calT)^{\frac 1 p} 
+%         \Cvier{n}(\calT)^{k+1} 
+%         \diam(T)^{k} 
+%         \| \cartan u \|_{L^{p}(U_{m-1})}
+%         \\&\qquad
+%         + 
+%         C_{{\rm PF},\Gamma,k,p}(\calT) 
+%         \diam(T)^{k} 
+%         \| \cartan u      \|_{L^{p}(T_{m})} 
+%         \\&\qquad
+%         + 
+%         \Cdetfive{n}(\calT)^{-\frac 1 p} 
+%         \Cvier{n}(\calT)^{k} 
+%         \| w \|_{L^{p}(U_{m-1})}
+%         \\
+        &
+        \leq  
+        C_{{\rm PF},\Gamma,k,p}(\calT) 
+        \diam(T)^{k} 
+        \left( 
+            \| \cartan u      \|_{L^{p}(T_{m})} 
+            +
+            \Cvier{n}(\calT)^{k+1} 
+            \Cdetfive{n}(\calT)^{\frac 1 p} 
+            \| \cartan u \|_{L^{p}(U_{m-1})}
+        \right)
+        \\&\qquad
+        + 
+        \Cvier{n}(\calT)^{k} 
+        \Cdetfive{n}(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(U_{m-1})}
+        .
     \end{align*}
@@
     By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
 
@@
         &\leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi \|^{k}
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi_{m} \|^{k}
         \cdot 
@@
         &\leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi \|^{k+1}
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi_{m} \|^{k+1}
         \cdot 
@@
     We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
-    By the properties of the reflection mapping in Theorem~\ref{theorem:starreflection},
-    \begin{align*}
-        ...
-    \end{align*}
-    This enables the recursion
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi \|^{k} 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})}
-        \\&\qquad
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
-        \| \cartan u      \|_{L^{p}(T_{m})} 
-        \\&\qquad
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi \|^{k+1} 
-        \| \cartan u_{m-1} \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
+    We use the properties of the reflection mapping in Theorem~\ref{theorem:starreflection}. 
+%     \begin{align*}
+%         ...
+%     \end{align*}
+%     This enables the recursion
+%     \begin{align*}
+%         \| w_{m} \|_{L^{p}(T_{m})}
+%         &
+%         \leq  
+%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+%         \| \Jacobian \Xi_{m} \|^{k} 
+%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
+%         \\&\qquad
+%         + 
+%         C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+%         \| \cartan u      \|_{L^{p}(T_{m})} 
+%         \\&\qquad
+%         + 
+%         C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+%         \| \Jacobian \Xi_{m} \|^{k+1} 
+%         \| \cartan u \|_{L^{p}(U_{m-1})}
+%         .
+%     \end{align*}
     The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 

### 2024-09-08 main.tex
major update

@@
 %         \leq 
-%         \frac 1 2
+%         \frac{1}{2}
         .
@@
         We let $z'_{S}$ be the midpoint of $S'$. 
-        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary $S'$. 
+        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary simplex $S'$. 
         All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
@@
         \end{align*}
-        \color{red}
+        \color{blue}
         By construction, 
         \begin{align*}
-            \det( \Jacobian \Theta_{|K} )
-            = 
-            \det( \Jacobian^{-1} \Theta_{|K} )
+            |\det( \Jacobian      \Theta_{|K} )|
+            = 
+            |\det( \Jacobian^{-1} \Theta_{|K} )|
             =
@@
         \end{align*}
+        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
+        Clearly,
+        \begin{align*}
+            \Theta_{|K}(x) 
+            = 
+            x
+            - 
+            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+            .
+        \end{align*}
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $\hat h_z$,
+        and when $x = z_{S'}$, then 
+        \begin{align*}
+            -z_{S'} 
+            =
+            z_{S'}
+            - 
+            2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+            .
+        \end{align*}
+        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
+        \begin{align*}
+            \Theta_{|K}( h_z ) 
+            &= 
+            h_z
+            - 
+            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
+            \\&= 
+            h_z
+            - 
+            2 z_{S'}
+            \\&= 
+            - h_{z}
+            - 
+            2 b_{z}
+            .
+        \end{align*}
+        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
+        We study the singular values of the matrix 
+        \begin{align*}
+            \begin{pmatrix}
+            -1                 & 0
+            \\ 
+            -2 \|b_z\|/\|h_z\| & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            -1             & 0
+            \\ 
+            -2 \tan(\beta) & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            0             & \tan(\beta)
+             \\ 
+            -\tan(\beta) & 0
+            \end{pmatrix}
+            +
+            \begin{pmatrix}
+            -1           & -\tan(\beta)
+             \\ 
+            \tan(\beta) & 1
+            \end{pmatrix}
+            .
+        \end{align*}
+        It follows that $\det(\Theta_{|K}) = 1$. 
+        Its singular values satisfy 
+        \begin{align*}
+            ( \sigma_{\max} + \sigma_{\min} )/2
+            =
+            \tan(\beta)
+            ,
+            \qquad 
+            ( \sigma_{\max} - \sigma_{\min} )/2
+            =
+            \sqrt{ 1 + \tan^{2}(\beta) }
+            ,
+        \end{align*}
+        which means that 
+        \begin{align*}
+            \sigma_{\max} = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
+            ,
+            \qquad 
+            \sigma_{\min} = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
+            .
+        \end{align*}
+        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        By the definition of the cosine, $\cos(\beta) \leq \| h_{z} \| / \| z_{S'} \|$. 
+        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
+        which is also a face of $T$. Then $(n-k-1) h_{z}$ is the height vector of $F_{z}$ in $T$. 
+        Thus 
+        \begin{align*}
+            \frac{ \| h_{z} \| }{ \| z_{S'} \| }
+            \geq 
+            \frac{ (n-k-1)^{-1} \| (n-k-1) h_{z} \| }{ \| z_{S'} \| }
+            \geq 
+            \frac{ (n-k-1)^{-1} n \vol(T) }{ \| z_{S'} \| \vol(F_{z}) }
+            \geq 
+            \frac{n}{ n-k-1 }
+            \cdot 
+            \frac{ \vol(T) }{ \diam(T)^{n} }
+            .
+%             \\
+%             \leq 
+%             \frac{ n \vol(K) }{ \| z_{S'} \| \vol(F_{z}) }
+%             \leq 
+%             \frac{ \vol(T) }{ \| z_{S'} \| \vol(F_{z}) }
+%             \leq 
+%             \frac{ \vol(T) }{ \diam(T)^{n} }
+%             .
+        \end{align*}
+
+What are the singular values of a $2x2$ (lower) unit triangular matrix? Suppose we have the matrix
+Suppose we have the matrix 
+\begin{align*}
+    \begin{pmatrix}
+    1 & 0
+    \\ 
+    b & 1
+    \end{pmatrix}
+\end{align*}
+Following up a generic formula found here, 
+https://math.stackexchange.com/a/861774/3557
+I decompose 
+\begin{align*}
+    \begin{pmatrix}
+    1 & 0
+    \\ 
+    b & 1
+    \end{pmatrix}
+    =
+    \frac 1 2 
+    \begin{pmatrix}
+    2 & -b
+    \\ 
+    b & 2
+    \end{pmatrix}
+    +
+    \frac 1 2 
+    \begin{pmatrix}
+    0 & b
+    \\ 
+    b & 0
+    \end{pmatrix}
+\end{align*}
+The singular values $w_1$ and $w_2$ are implicitly given by 
+\begin{align*}
+    \frac{ w_1 + w_2 }{2} = \frac 1 2 \sqrt{ 4 + b^2 }
+    \\
+    \frac{ w_1 - w_2 }{2} = \frac 1 2 |b|
+\end{align*}
+If we assume that the first value is at least the second value, 
+then adding and subtracting these equations leads to 
+\begin{align*}
+    w_1 = \frac 1 2 \sqrt{ 4 + b^2 } + \frac 1 2 |b|
+    \\
+    w_2 = \frac 1 2 \sqrt{ 4 + b^2 } - \frac 1 2 |b|
+\end{align*}
+I would like to know whether that reasoning is correct
+
+foo
+\begin{align*}
+    \lambda^2 = \frac{1}{2} \left( a + c \pm \sqrt{ a^2 - 2 a c + c^2 + 4b^2 } \right)
+\end{align*}
+\begin{align*}
+    \lambda 
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ (1+t^2) + 1 \pm \sqrt{ (1+t^2)^2 - 2 (1+t^2)   +   1 + 4t^2 } } 
+    \\
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{ 1 + 2t^2 + t^4 - 2 - 2 t^2 + 1 + 4t^2 } } 
+    \\
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{          + t^4                 + 4t^2 } } 
+    \\
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
+    .
+\end{align*}
+\begin{align*}
+    \lambda = \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
+\end{align*}
+\begin{align*}
+    \left( t^2 + 2 + t \sqrt{ t^2 + 4 } \right)
+    \left( t^2 + 2 - t \sqrt{ t^2 + 4 } \right)
+    =
+    t^{4} + 4 t^{2} + 4
+    -
+    t^{2} ( t^{2} + 4 )
+    =
+    4
+\end{align*}
+\begin{align*}
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
+    &=
+    \sqrt{1+a^2/4} \pm a/2
+    \\
+    \frac 1 2 \left( t^2 + 2 \pm t \sqrt{ t^2 + 4 } \right)
+    &=
+    1+a^2/4
+    \pm
+    a \sqrt{1+a^2/4}
+    + 
+    a^2/4
+    \\&=
+    1
+    +
+    2a^2/4
+    \pm
+    a \sqrt{1+a^2/4}
+    \\
+    1 + \frac{t^2}{2} \pm t \sqrt{ \frac{t^2}{4} + 1 } 
+    &=
+    1
+    +
+    a^2/2
+    \pm
+    a \sqrt{1+a^2/4}
+    .
+\end{align*}
+
+        \item 
+        We prove another auxiliary result.
+        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
+        Define 
+        \begin{align*}
+            F(x) 
+            = 
+            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
+            x
+            .
+        \end{align*}
+        This is defined away from the hyperplane orthogonal to $h_2$.
+        This is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
+        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed, 
+        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
+
+        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
+        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $h_2$, respectively, and the vector $x$.
+        In what follows, $y \in \bbR^{n}$.
+        \begin{align*}
+            \Jacobian F(x) \cdot y
+            &=
+            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
+            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
+            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
+            +
+            x
+            \otimes 
+            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
+            \frac{ h_1^{t} y }{ \| h_1 \|^{2} }
+            \\&=
+            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
+            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
+            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
+            +
+            \hat x
+            \otimes 
+            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
+            \\&=
+            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
+            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
+            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
+            +
+            \hat x
+            \otimes 
+            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
+            \\&=
+            \frac{ \| h_2 \| }{ \| h_1 \| }
+            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
+            \left( 
+                y 
+                - 
+                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
+                + 
+                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
+            \right)
+            .
+        \end{align*}
+        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
+        Notice that $a \perp \hat x$ by definition.
+The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
+Over that two-dimensional subspace, it can be represented by a triangular matrix.
+        Its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are~\cite{blinn1996consider} 
+        \begin{align*}
+            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
+            \qquad 
+            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
+        \end{align*}
+        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
+        We notice the obvious upper bound 
+        \begin{align*}
+            \|a\| 
+            \leq 
+            2 \max_{1 \leq i \leq 2} 
+            \left( 
+                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
+            \right)
+            .
+        \end{align*}
+
+        \item 
+        We introduce a bi-Lipschitz mapping 
+        \begin{align*}
+            \Psi : |\calR'| \rightarrow |\calK|
+        \end{align*}
+        in the following manner.
+Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
+There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
+We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively.
+They define respective hyperplanes $H_{G}$ and $H_{K}$,
+        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
+        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
+        We define 
+        \begin{align*}
+            \Psi(x) 
+            = 
+            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
+            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
+            x
+            .
+        \end{align*}
+        One easily verifies that this defines a continuous mapping $\Psi$. 
+        By the same line of thought, we see that it is invertible with inverse satisfying 
+        \begin{align*}
+            \Psi^{-1}(z) 
+            = 
+            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
+            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
+            z,
+            \qquad 
+            z = \Psi(x)
+            .
+        \end{align*}
+        Our previous observations enable estimates for the Jacobians. 
+        We have the operator norm and determinant formulas 
+        \begin{gather*}
+            \| \Jacobian\Psi(x) \|
+            = 
+            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            \left( 
+                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
+            \right)
+            \\
+            \| \Jacobian\Psi(z)^{-1} \|
+            = 
+            \frac{ \| h_{{G}} \| }{ \| h_K \| }
+            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
+            \left( 
+                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
+            \right)^{-1},
+            \\
+            \det\Jacobian\Psi(x)
+            =
+            \left( 
+            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            \right)^{n},
+            \qquad
+            \det\Jacobian\Psi^{-1}(x)
+            =
+            \left( 
+            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
+            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
+            \right)^{n}
+        \end{gather*}
+        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
+        and where $a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K$.
+
+        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
+        By the definition of the cosine, 
+        \begin{align*}
+            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            \leq 
+            \frac{ \| x_K \| }{ \| h_{{G}} \| }
+            \leq 
+            \frac{ \diam(K) }{ \| h_{{G}} \| }
+            ,
+            \qquad 
+            \frac{ \| h_{{G}} \| }{ \| h_K \| }
+            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
+            \leq 
+            \frac{ \| x_{G} \| }{ \| h_{K} \| }
+            \leq 
+            \frac{ \diam(G) }{ \| h_{K} \| }
+            .
+        \end{align*}
+%         \begin{align*}
+%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
+%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+%             \leq 
+%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
+%             .
+%         \end{align*}
+
+        The diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
+        The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
+        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of the origin in some simplex in $\calS'$
+        by scaling with $(k+1)^{-1}$.
+Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $\kappa(A)^{-2}$.
+The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
+        In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
+        It follows that $\|x_{G}\| \leq \diam(T)$.
+
+        We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
+        Recall that 
+        \begin{align*}
+            \frac{ \|h_{F}\|}{\diam(T)}
+            = 
+            \frac{ n \vol(T) }{ \vol(F) \diam(T) }
+            \geq 
+            \frac{ n \vol(T) }{ \diam(T)^{n} }
+            \geq 
+            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            .
+        \end{align*}
+        We conclude that 
+        \begin{gather*}
+            \frac{ \diam(K) }{ \| h_{{G}} \| }
+            \leq 
+            (k+1)\kappa(A)^{2}
+            \frac{ \diam(K) }{ \| h_{T} \| }
+            \leq 
+            (k+1)\kappa(A)^{2}
+            \theta(\calT)
+            \frac{ \diam(T) }{ \| h_{T} \| }
+            \leq 
+            (k+1)\kappa(A)^{2}
+            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            ,
+            \\
+            \frac{ \| x_{G} \| }{ \| h_{K} \| }
+            \leq 
+            (k+1)
+            \frac{ \diam(T) }{ \| h_{K} \| }
+            \leq 
+            (k+1)
+            \theta(\calT)
+            \frac{ \diam(K) }{ \| h_{K} \| }
+            \leq 
+            (k+1)
+            \theta(\calT)
+            \sup_{ K \in \patch_{\calT}(S) }
+            (n-1)! \cdot \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            .
+        \end{gather*}
+        \begin{gather*}
+            \frac{ \diam(K) }{ \| h_{{K}} \| }
+            \leq 
+            (k+1)
+            \sup_{ K \in \patch_{\calT}(S) }
+            (n-1)! \cdot \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            ,
+            \\
+            \frac{ \| x_{G} \| }{ \| h_{G} \| }
+            \leq 
+            (k+1)\kappa(A)^{2}
+            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            .
+        \end{gather*}
+
+        %         To simplify that expression, we make another observation regarding the height vectors. 
+        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
+        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
+        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
+        %         From this obversation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
+        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
+        %         with the factor $(k+1)^{-1}$.
+
+        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$.
+That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
+        We calculate 
+        \begin{align*}
+            \|a\|
+            = 
+            \left\|
+            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
+            - 
+            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
+            \right\|
+            &
+            \leq 
+            \frac{\|x_{G}\|}{\|h_{G}\|} 
+            + 
+            \frac{\|x_{K}\|}{\|h_{K}\|} 
+            \\&
+            \leq 
+            (k+1) 
+            (n-1)! \cdot 
+            \left( 1 + \kappa(A)^{2} \right)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            .
+        \end{align*}
+        \todo{bound $\kappa(A)$ right away...}
+
+        \item 
+        We define a mapping $ \Xi : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
+        \begin{align*}
+            \Xi := \Psi \circ \Theta.
+        \end{align*}
+        It preserves the interface from $T$ onto $U$. We briefly recapitulate why it is bi-Lipschitz.
+
+        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
+        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+        After application of a piecewise linear Lipschitz mapping, 
+        we can assume that $|\calK|$ is convex without loss of generality. 
+        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
+        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz.
+
+        We recall the upper bound $\sqrt{1+\theta^2} \leq 1 + \theta$ for any $\theta \geq 0$.
+
+        \begin{align*}
+            |\det(\Xi)|
+            \leq 
+            (k+1)^{n}
+            (n-1)!^{n}
+            \theta(\calT)^{n}
+            \kappa(A)^{2n}
+            \mu(\calT)
+            ,
+            \qquad 
+            |\det(\Xi^{-1})|
+            \leq 
+            (k+1)^{n}
+            (n-1)!^{n}
+            \theta(\calT)^{n}
+            \mu(\calT)
+            .
+        \end{align*}
+
         \color{black}
+
+        \item 
+        We introduce a bi-Lipschitz mapping 
+        \begin{align*}
+            \Psi : |\calR'| \rightarrow |\calK|
+        \end{align*}
+        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There
 
@@
 
-In what follows, use the abbreviation
+Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
 \begin{align*}
@@
 \end{align*}
-whenever $\calT$ is an $n$-dimensional triangulation.
+
+Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
+For each $1 \leq m \leq M$, there exists a simplex $S_{m} \in \calT$ 
+such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
+We then let $U_{m}$ be the closure $\patch_{\calT}(S_{m}) \setminus T_{m}$,
+and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
 

### 2024-09-09 main.tex
completing edges

@@
     \begin{gather*}
-        \| \Jacobian\Xi \|          \leq \Cvier{n}(\calT),
+        \| \Jacobian\Xi \|          \leq \Cvier{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi^{-1} \|     \leq \Cfive{n}(\calT),
-        \\
-        \| \det\Jacobian\Xi \|      \leq \Cdetvier{n}(\calT),
+        \| \Jacobian\Xi^{-1} \|     \leq \Cfive{n}{k}(\calT),
+        \\
+        \| \det\Jacobian\Xi \|      \leq \Cdetvier{n}{k}(\calT),
         \quad 
-        \| \det\Jacobian\Xi^{-1} \| \leq \Cdetfive{n}(\calT),
+        \| \det\Jacobian\Xi^{-1} \| \leq \Cdetfive{n}{k}(\calT),
     \end{gather*}
@@
         \end{align*}
-        \color{blue}
-        By construction, 
+        By construction, the mapping preserves volumes:
         \begin{align*}
@@
         \end{align*}
+        We want to characterize the singular values of this transform. 
         We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
-        Clearly,
+        We can write
         \begin{align*}
@@
         Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $\hat h_z$,
-        and when $x = z_{S'}$, then 
-        \begin{align*}
-            -z_{S'} 
-            =
-            z_{S'}
-            - 
-            2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
-            .
-        \end{align*}
+        and that it equals $-z_{S'}$ when $x = z_{S'}$.
+%         and when $x = z_{S'}$, then 
+%         \begin{align*}
+%             -z_{S'} 
+%             =
+%             z_{S'}
+%             - 
+%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+%             .
+%         \end{align*}
         If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
@@
             2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
-            \\&= 
+            %\\&
+            = 
             h_z
@@
             2 z_{S'}
-            \\&= 
+            %\\&
+            = 
             - h_{z}
@@
         \begin{align*}
+            B 
+            := 
             \begin{pmatrix}
@@
             \end{pmatrix}
-            =
-            \begin{pmatrix}
-            0             & \tan(\beta)
-             \\ 
-            -\tan(\beta) & 0
-            \end{pmatrix}
-            +
-            \begin{pmatrix}
-            -1           & -\tan(\beta)
-             \\ 
-            \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        It follows that $\det(\Theta_{|K}) = 1$. 
-        Its singular values satisfy 
-        \begin{align*}
-            ( \sigma_{\max} + \sigma_{\min} )/2
-            =
-            \tan(\beta)
-            ,
-            \qquad 
-            ( \sigma_{\max} - \sigma_{\min} )/2
-            =
-            \sqrt{ 1 + \tan^{2}(\beta) }
-            ,
-        \end{align*}
-        which means that 
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
-            ,
-            \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
-            .
-        \end{align*}
-        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        By the definition of the cosine, $\cos(\beta) \leq \| h_{z} \| / \| z_{S'} \|$. 
+            .
+        \end{align*}
+        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
+        Its square roots are the desired singular values of $B$:
+        \begin{align*}
+            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
+            ,
+            \\
+            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
+            .
+        \end{align*}
+        \begin{align*}
+            \lambda
+        \end{align*}
+        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$. 
+        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
+
+%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \| / \| h_{z} \|$, and we know $\|b_z\| \leq \|z_{S'}\|$. 
         Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
-        which is also a face of $T$. Then $(n-k-1) h_{z}$ is the height vector of $F_{z}$ in $T$. 
+        which is also a face of $T$. Then $(n-k) h_{z}$ is the height vector of $F_{z}$ in $T$. 
         Thus 
         \begin{align*}
-            \frac{ \| h_{z} \| }{ \| z_{S'} \| }
-            \geq 
-            \frac{ (n-k-1)^{-1} \| (n-k-1) h_{z} \| }{ \| z_{S'} \| }
-            \geq 
-            \frac{ (n-k-1)^{-1} n \vol(T) }{ \| z_{S'} \| \vol(F_{z}) }
-            \geq 
-            \frac{n}{ n-k-1 }
+            \frac{ \| b_{z} \| }{ \| h_{z} \| }
+            = 
+            \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
+            = 
+            \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
+            \leq 
+            \frac{ n-k-1 }{n!}
             \cdot 
-            \frac{ \vol(T) }{ \diam(T)^{n} }
-            .
-%             \\
-%             \leq 
-%             \frac{ n \vol(K) }{ \| z_{S'} \| \vol(F_{z}) }
-%             \leq 
-%             \frac{ \vol(T) }{ \| z_{S'} \| \vol(F_{z}) }
-%             \leq 
-%             \frac{ \vol(T) }{ \diam(T)^{n} }
-%             .
-        \end{align*}
-
-What are the singular values of a $2x2$ (lower) unit triangular matrix? Suppose we have the matrix
-Suppose we have the matrix 
-\begin{align*}
-    \begin{pmatrix}
-    1 & 0
-    \\ 
-    b & 1
-    \end{pmatrix}
-\end{align*}
-Following up a generic formula found here, 
-https://math.stackexchange.com/a/861774/3557
-I decompose 
-\begin{align*}
-    \begin{pmatrix}
-    1 & 0
-    \\ 
-    b & 1
-    \end{pmatrix}
-    =
-    \frac 1 2 
-    \begin{pmatrix}
-    2 & -b
-    \\ 
-    b & 2
-    \end{pmatrix}
-    +
-    \frac 1 2 
-    \begin{pmatrix}
-    0 & b
-    \\ 
-    b & 0
-    \end{pmatrix}
-\end{align*}
-The singular values $w_1$ and $w_2$ are implicitly given by 
-\begin{align*}
-    \frac{ w_1 + w_2 }{2} = \frac 1 2 \sqrt{ 4 + b^2 }
-    \\
-    \frac{ w_1 - w_2 }{2} = \frac 1 2 |b|
-\end{align*}
-If we assume that the first value is at least the second value, 
-then adding and subtracting these equations leads to 
-\begin{align*}
-    w_1 = \frac 1 2 \sqrt{ 4 + b^2 } + \frac 1 2 |b|
-    \\
-    w_2 = \frac 1 2 \sqrt{ 4 + b^2 } - \frac 1 2 |b|
-\end{align*}
-I would like to know whether that reasoning is correct
-
-foo
-\begin{align*}
-    \lambda^2 = \frac{1}{2} \left( a + c \pm \sqrt{ a^2 - 2 a c + c^2 + 4b^2 } \right)
-\end{align*}
-\begin{align*}
-    \lambda 
-    &= 
-    \frac{1}{\sqrt 2} \sqrt{ (1+t^2) + 1 \pm \sqrt{ (1+t^2)^2 - 2 (1+t^2)   +   1 + 4t^2 } } 
-    \\
-    &= 
-    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{ 1 + 2t^2 + t^4 - 2 - 2 t^2 + 1 + 4t^2 } } 
-    \\
-    &= 
-    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{          + t^4                 + 4t^2 } } 
-    \\
-    &= 
-    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
-    .
-\end{align*}
-\begin{align*}
-    \lambda = \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
-\end{align*}
-\begin{align*}
-    \left( t^2 + 2 + t \sqrt{ t^2 + 4 } \right)
-    \left( t^2 + 2 - t \sqrt{ t^2 + 4 } \right)
-    =
-    t^{4} + 4 t^{2} + 4
-    -
-    t^{2} ( t^{2} + 4 )
-    =
-    4
-\end{align*}
-\begin{align*}
-    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
-    &=
-    \sqrt{1+a^2/4} \pm a/2
-    \\
-    \frac 1 2 \left( t^2 + 2 \pm t \sqrt{ t^2 + 4 } \right)
-    &=
-    1+a^2/4
-    \pm
-    a \sqrt{1+a^2/4}
-    + 
-    a^2/4
-    \\&=
-    1
-    +
-    2a^2/4
-    \pm
-    a \sqrt{1+a^2/4}
-    \\
-    1 + \frac{t^2}{2} \pm t \sqrt{ \frac{t^2}{4} + 1 } 
-    &=
-    1
-    +
-    a^2/2
-    \pm
-    a \sqrt{1+a^2/4}
+            \frac{ \diam(T)^{n} }{ \vol(T) }
+            :=
+            \beta_T
+            .
+        \end{align*}
+        This establishes bounds on the singular values of the transformation in terms of the mesh geometry. 
+        We write 
+        \begin{align*}
+            \beta_T 
+            := 
+%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
+%             \geq 
+            \sqrt{ 
+                1 + (n-k)^{2} \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+            } 
+            + 
+            (n-k) \frac{ \diam(T)^{n} }{ n! \vol(T) }            
             .
@@
 Over that two-dimensional subspace, it can be represented by a triangular matrix.
-        Its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are~\cite{blinn1996consider} 
+        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
+        %~\cite{blinn1996consider} 
         \begin{align*}
@@
         by scaling with $(k+1)^{-1}$.
-Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $\kappa(A)^{-2}$.
+Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $\beta_T$.
 The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
@@
         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
-        Recall that 
-        \begin{align*}
-            \frac{ \|h_{F}\|}{\diam(T)}
-            = 
-            \frac{ n \vol(T) }{ \vol(F) \diam(T) }
-            \geq 
-            \frac{ n \vol(T) }{ \diam(T)^{n} }
-            \geq 
-            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
+        \begin{align*}
+            \frac{\diam(T)}{ \|h_{F}\|}
+            \leq  
+            \frac{ \vol(F) \diam(T) }{ n \vol(T) }
+            \leq 
+            \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
             \leq 
-            (k+1)\kappa(A)^{2}
+            (k+1)\beta_T
             \frac{ \diam(K) }{ \| h_{T} \| }
             \leq 
-            (k+1)\kappa(A)^{2}
+            (k+1)\beta_T
             \theta(\calT)
@@
             \leq 
-            (k+1)\kappa(A)^{2}
-            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (k+1)\beta_T
+            \theta(\calT)
+            \frac{ \diam(T)^{n} }{ n! \vol(T) }
             ,
@@
             (k+1)
+            \sup_{ K \in \patch_{\calT}(S) }
             \frac{ \diam(T) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \theta(\calT)
-            \frac{ \diam(K) }{ \| h_{K} \| }
             \leq 
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            (n-1)! \cdot \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \frac{ \diam(K) }{ \| h_{K} \| }
+            \leq 
+            (k+1)
+            \theta(\calT)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            (n-1)! \cdot \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            ,
-            \\
+            \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            ,
+            \qquad 
             \frac{ \| x_{G} \| }{ \| h_{G} \| }
             \leq 
-            (k+1)\kappa(A)^{2}
-            (n-1)! \cdot \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (k+1)\beta_T
+            \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
             (k+1) 
-            (n-1)! \cdot 
-            \left( 1 + \kappa(A)^{2} \right)
+            \left( 1 + \beta_T \right)
             \sup_{ K \in \patch_{\calT}(S) }
@@
         \end{align*}
-        \todo{bound $\kappa(A)$ right away...}
 
@@
         We recall the upper bound $\sqrt{1+\theta^2} \leq 1 + \theta$ for any $\theta \geq 0$. 
-
+        This leads to  
+        \begin{align*}
+            \| \Jacobian \Xi \|
+            &\leq 
+            \Cvier{n}{k}(\calT)
+            :=
+            (k+1) 
+            \mu(\calT)
+            \beta_T
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + \beta_T \right)
+                \mu(\calT)
+            \Big)            
+            \\
+            \| \Jacobian \Xi^{-1} \|
+            &\leq  
+            \Cfive{n}{k}(\calT)
+            :=
+            (k+1) 
+            \mu(\calT)
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + \beta_T \right)
+                \mu(\calT)
+            \Big)            
+        \end{align*}
+        We get the determinant estimate 
         \begin{align*}
@@
             \leq 
+            \Cdetvier{n}{k}(\calT)
+            :=
             (k+1)^{n}
-            (n-1)!^{n}
             \theta(\calT)^{n}
-            \kappa(A)^{2n}
-            \mu(\calT)
+            \beta_T^{n}
+            \mu(\calT)^{n}
             ,
@@
             \leq 
+            \Cdetfive{n}{k}(\calT)
+            :=
             (k+1)^{n}
-            (n-1)!^{n}
             \theta(\calT)^{n}
-            \mu(\calT)
-            .
-        \end{align*}
-
-        \color{black}
+            \mu(\calT)^{n}
+            .
+        \end{align*}
+        This completes the desired estimates.
 
@@
 %         C_{{\rm PF},\Gamma,k,p}(\calT) 
-%         \Cdetfive{n}(\calT)^{\frac 1 p} 
-%         \Cvier{n}(\calT)^{k+1} 
+%         \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
+%         \Cvier{n}{k}(\calT)^{k+1} 
 %         \diam(T)^{k} 
@@
 %         + 
-%         \Cdetfive{n}(\calT)^{-\frac 1 p} 
-%         \Cvier{n}(\calT)^{k} 
+%         \Cdetfive{n}{k}(\calT)^{-\frac 1 p} 
+%         \Cvier{n}{k}(\calT)^{k} 
 %         \| w \|_{L^{p}(U_{m-1})}
@@
             +
-            \Cvier{n}(\calT)^{k+1} 
-            \Cdetfive{n}(\calT)^{\frac 1 p} 
+            \Cvier{n}{k}(\calT)^{k+1} 
+            \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
             \| \cartan u \|_{L^{p}(U_{m-1})}
@@
         + 
-        \Cvier{n}(\calT)^{k} 
-        \Cdetfive{n}(\calT)^{\frac 1 p} 
+        \Cvier{n}{k}(\calT)^{k} 
+        \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
         \| w \|_{L^{p}(U_{m-1})}

### 2024-09-09 main.tex
additional construction

@@
         \item 
+        Consider any $n$-simplex $R \in \calR$ and let $R^c \in \calR^{c}$ be its image under $\Theta$.
+        We construct a bi-Lipschitz mapping 
+        \begin{align*}
+            \Gamma_{R} : R \cup R^{c} \rightarrow R^{c}
+        \end{align*}
+        and analyze its properties. The construction will be such that the union of $\Gamma_{R}$ for all $n$-simplices $R \in \calR$
+        will define a bi-Lipschitz mapping 
+        \begin{align*}
+            \Gamma : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}
+        \end{align*}
+        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
+
+        We write $h_{z}$ for the height of $z_{S'}$ within $K$.
+        Given $x \in K \cup K^{c}$, we can write uniquely
+        \begin{align*}
+            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c}.
+        \end{align*}
+        Notice that 
+        \begin{align*}
+            t = \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+        \end{align*}
+        We define 
+        \begin{align*}
+            \Gamma_{K}(x) = x - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
+        \end{align*}
+        We readily verify that this transformation satisfies the desired properties. 
+        It remains to analyze its Jacobian.
+
+        We have an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$.
+        With that,
+        \begin{align*}
+            \Jacobian \Gamma_{K}(x)
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            z_{S'} \otimes h_{z}^{t}
+            =
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
+            z_{S'} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            h_{z} \otimes h_{z}^{t}
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            b_{z} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 } 
+            \hat h_{z} \otimes \hat h_{z}^{t}
+            - 
+            \frac{ \|b_z\| }{ 2 \| h_{z} \| } 
+            \hat b_{z} \otimes \hat h_{z}^{t}
+            .
+        \end{align*}
+        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
+        Hence $\tan(\beta) = \| b_z \| / \| h_z \|$. It remains to study the singular values of the matrix 
+        \begin{align*}
+            C 
+            = 
+            \frac 1 2 
+            \begin{pmatrix}
+                1 & 0 
+                \tan(\beta) & 2 
+            \end{pmatrix}
+        \end{align*}
+        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
+        \begin{align*}
+            \sigma_{\max} = \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
+            ,
+            \\
+            \sigma_{\min} = \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
+            .
+        \end{align*}
+        These are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Gamma$,
+        the remaining eigenvalues being equal to $1$. Upon close inspection, we see that 
+        \begin{align*}
+            \sigma_{\max} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            ,
+            \\
+            \sigma_{\min} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            .
+        \end{align*}
+        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
+        Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
+        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        Similar as above, we use the upper bound 
+        \begin{align*}
+            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \mu(T).
+        \end{align*}
+        We conclude that 
+        \begin{gather*}
+            \| \Jacobian\Gamma \| 
+            \leq 
+            \frac 1 4 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
+            ,
+            \\
+            \| \Jacobian\Gamma^{-1} \| 
+            \leq 
+            \frac 1 2 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
+            \\
+            \det \Jacobian\Gamma = \frac 1 2 
+            .
+        \end{gather*}
+
+        \item 
         We introduce a bi-Lipschitz mapping 

### 2024-09-10 main.tex
general updates and corrections

--- 2024-09-09 main.tex
@@
         \leq 
-        \Csechs{n}
+        \Cdrei{n}
         % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
@@
         \quad 
-        \Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} },
+        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
         \quad 
-        \Csechs{n} \leq \sqrt{ \frac{n}{ (n-1)^{n-1} } }
+        \Cdrei{n} \leq \sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
         . 
@@
     The Jacobian determinant is the product of these singular values. 
-%     By a result of Hong and Pan,
+    By a result of Hong and Pan \cite{hong1992lower},
+    \begin{align*}
+        \sigma_{n}
+        &\geq 
+        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
+        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
+        = 
+        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
+        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
+        .
+    \end{align*}
+%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
+    The second inequality follows. 
+    To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
+
+%     By a result of Yu and Gu \cite{yisheng1997note},
 %     \begin{align*}
 %         \frac{ \sigma_{n} }{ \sigma_{1} }
-%         \geq 
-%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
-%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
+%         &\geq 
+%         \det(\Jacobian\varphi)
+%         \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
 %         \sigma_{1}^{-1}
 %         \geq 
-%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
-%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
-%         \sigma_{1}^{-1}
-%         .
-%     \end{align*}
-    By a result of Yu and Gu \cite{yisheng1997note},
-    \begin{align*}
-        \frac{ \sigma_{n} }{ \sigma_{1} }
-        &\geq 
-        \det(\Jacobian\varphi)
-        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
-        \sigma_{1}^{-1}
-%         \geq 
-%         (n-1)^{\frac{n-1}{2}}
+%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
 %         \det(\Jacobian\varphi)
@@
 %         \geq 
+%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
 %         \frac{1}{\sqrt{n}}
-%         (n-1)^{\frac{n-1}{2}}
-%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
-        \geq 
-        \sqrt{\frac{ (n-1)^{n-1} }{n} }
-        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
-        .
-    \end{align*}
-    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
+%         \frac{ n! \vol(T) }{ \diam(T)^{n} }
+%         .
+%     \end{align*}
+%     Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. % THIS IS OPTIMAL
 %     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
@@
 
+\todo{Tighter estimate via geometry}
 \begin{lemma}\label{lemma:volumecomparison}
@@
         \leq 
-        \Cdrei{n}
+        \Cvier{n}
         \kappa(T_2)^{-1} \kappa(T_1) 
@@
     \end{align*}
-    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
+    Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
 \end{lemma}
@@
     \begin{align*}
-        U := |\patch_{\calT}(S)| \setminus T.
-    \end{align*}
+        U := \overline{ |\patch_{\calT}(S)| \setminus T },
+        \qquad 
+        {\Gamma_I} := U \cap T,
+        \qquad 
+        {\Gamma_J} := \overline{ \partial T \setminus \partial U }.
+    \end{align*}
+    \begin{enumerate}
+    \item 
     There exists a bi-Lipschitz mapping
     \begin{align*}
-        \Xi : T \rightarrow U
-    \end{align*}
-    satisfying
+        \Xi_{1} : T \rightarrow U
+    \end{align*}
+    which is the identity along ${\Gamma_I} = T \cap U$ and which satisfies the upper bounds 
     \begin{gather*}
-        \| \Jacobian\Xi \|          \leq \Cvier{n}{k}(\calT),
+        \| \Jacobian\Xi_{1} \|          \leq \Cfive{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi^{-1} \|     \leq \Cfive{n}{k}(\calT),
-        \\
-        \| \det\Jacobian\Xi \|      \leq \Cdetvier{n}{k}(\calT),
+        \| \Jacobian\Xi_{1}^{-1} \|     \leq \Csechs{n}{k}(\calT),
+        \\
+        \| \det\Jacobian\Xi_{1} \|      \leq \Cdetfive{n}{k}(\calT),
         \quad 
-        \| \det\Jacobian\Xi^{-1} \| \leq \Cdetfive{n}{k}(\calT),
+        \| \det\Jacobian\Xi_{1}^{-1} \| \leq \Cdetsechs{n}{k}(\calT),
     \end{gather*}
     where the constants on the right-hand sides are as stated in the proof. 
+    \item 
+    There exists a bi-Lipschitz mapping
+    \begin{align*}
+        \Xi_{2} : T \rightarrow U
+    \end{align*}
+    which is the identity along $\partial U \setminus \partial T$ and which satisfies the upper bounds 
+    \begin{gather*}
+        \| \Jacobian\Xi_{2} \|          \leq \Csieb{n}{k}(\calT),
+        \quad 
+        \| \Jacobian\Xi_{2}^{-1} \|     \leq \Cacht{n}{k}(\calT),
+        \\
+        \| \det\Jacobian\Xi_{2} \|      \leq \Cdetsieb{n}{k}(\calT),
+        \quad 
+        \| \det\Jacobian\Xi_{2}^{-1} \| \leq \Cdetacht{n}{k}(\calT),
+    \end{gather*}
+    where the constants on the right-hand sides are as stated in the proof. 
+    \end{enumerate}
 \end{theorem}
@@
     We derive the estimate in several steps. 
+    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
     \begin{itemize}
         \item 
-        Without loss of generality, the barycenter of $S$ is the origin. 
+        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
         % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        %We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
-        %So $J$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
+        %We let ${\Gamma_J} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
+        %So ${\Gamma_J}$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
         We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
-        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.
+        Note that ${\Gamma_J}$ is the union of exactly those faces of $T$ that contain $S'$,
+        whereas ${\Gamma_I} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.
 
@@
         \item 
-        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
+        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ as follows.
         Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
@@
         \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $\hat h_z$,
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_z$,
         and that it equals $-z_{S'}$ when $x = z_{S'}$.
@@
             2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
+            = 
+            h_z
+            - 
+            2 z_{S'} \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle}
             %\\&
@@
         \begin{align*}
-            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
-            ,
-            \\
-            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
-            .
-        \end{align*}
-        \begin{align*}
-            \lambda
-        \end{align*}
-        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$. 
+            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
+            ,
+            \\
+            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
+            .
+        \end{align*}
         They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
+        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
+        whereas all its other singular values equal $1$.
 
@@
             \leq 
-            \frac{ n-k-1 }{n!}
+            \frac{ n-k }{n!}
             \cdot 
             \frac{ \diam(T)^{n} }{ \vol(T) }
-            :=
-            \beta_T
-            .
-        \end{align*}
-        This establishes bounds on the singular values of the transformation in terms of the mesh geometry. 
+            .
+        \end{align*}
+        This establishes bounds on the singular values of the transformation. 
         We write 
@@
         \end{align*}
+
+        \item 
+        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
+        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Phi$.
+        We construct a bi-Lipschitz mapping 
+        \begin{align*}
+            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}
+        \end{align*}
+        and analyze its properties. The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
+        will define the required mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
+        which will be bi-Lipschitz and the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
+
+        We write $h_{z}$ for the height of $z_{S'}$ within $K$.
+        Given $x \in K \cup K^{c}$, we have a unique representation
+        \begin{align*}
+            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c}.
+        \end{align*}
+        Notice that 
+        \begin{align*}
+            t = \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+            .
+        \end{align*}
+        Based on that observation, we define 
+        \begin{align*}
+            \Phi_{K}(x) := x - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
+            .
+        \end{align*}
+        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
+        that satifies the desired mapping properties. 
+        It remains to analyze its Jacobian to get explicit estimates.
+
+        We have an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$.
+        With that,
+        \begin{align*}
+            \Jacobian \Phi_{K}(x)
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
+            z_{S'} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            h_{z} \otimes h_{z}^{t}
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            b_{z} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
+            h_{z} \otimes h_{z}^{t}
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            b_{z} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 } 
+            \hat h_{z} \otimes \hat h_{z}^{t}
+            - 
+            \frac{ \|b_z\| }{ 2 \| h_{z} \| } 
+            \hat b_{z} \otimes \hat h_{z}^{t}
+            .
+        \end{align*}
+        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
+        Hence $\tan(\beta) = \| b_z \| / \| h_z \|$. It remains to study the singular values of the matrix 
+        \begin{align*}
+            C 
+            = 
+            \frac 1 2 
+            \begin{pmatrix}
+                -1 & 0 
+                \\
+                -\tan(\beta) & 2 
+            \end{pmatrix}
+        \end{align*}
+        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
+        \begin{align*}
+            \sigma_{\max} 
+            = 
+            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
+            =
+            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            ,
+            \\
+            \sigma_{\min} 
+            = 
+            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
+            =
+            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            .
+        \end{align*}
+        These are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. 
+%         Upon close inspection, we see that 
+%         \begin{align*}
+%             \sigma_{\max} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+%             ,
+%             \\
+%             \sigma_{\min} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+%             .
+%         \end{align*}
+        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
+        Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
+        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        Similar as above, we use the upper bound 
+        \begin{align*}
+            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \mu(T).
+        \end{align*}
+        We conclude that 
+        \begin{gather*}
+            \| \Jacobian\Phi_{K} \| 
+            \leq 
+            \frac 1 4 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
+            ,
+            \\
+            \| \Jacobian\Phi_{K}^{-1} \| 
+            \leq 
+            \frac 1 2 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
+            ,
+            \\
+            \det \Jacobian\Phi = \frac 1 2 
+            .
+        \end{gather*}
+        This finishes the discussion of the transformation $\Phi$.
 
@@
 
-        \item 
-        We define a mapping $ \Xi : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
-        \begin{align*}
-            \Xi := \Psi \circ \Theta.
-        \end{align*}
-        It preserves the interface from $T$ onto $U$. We briefly recapitulate why it is bi-Lipschitz.
+        \todo{TODO: Integrate the following paragraph and make it two-sided.}
+        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz over some essentially disjoint closed partitions over their respective domains.
+        It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
+        Rademacher's theorem then shows that both have essentially bounded weak Jacobians almost everywhere.
 
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.
-        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz.
-
-        We recall the upper bound $\sqrt{1+\theta^2} \leq 1 + \theta$ for any $\theta \geq 0$. 
-        This leads to  
-        \begin{align*}
-            \| \Jacobian \Xi \|
+
+        \item 
+        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
+        \begin{align*}
+            \Xi_{1} := \Psi \circ \Theta.
+        \end{align*}
+        It preserves the interface from $T$ onto $U$. 
+        % We briefly recapitulate why it is bi-Lipschitz.
+%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
+%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+%         After application of a piecewise linear Lipschitz mapping, 
+%         we can assume that $|\calK|$ is convex without loss of generality. 
+%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
+%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
+        The combination of the previous estimates for $\Psi$ and $\Theta$,
+        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
+        provide 
+        \begin{align*}
+            \| \Jacobian \Xi_{1} \|
             &\leq 
-            \Cvier{n}{k}(\calT)
+            \Cfive{n}{k}(\calT)
             :=
+            (k+1) 
+            \theta(\calT)
+            \mu(\calT)
+            \beta_T^{2}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + \beta_T \right)
+                \mu(\calT)
+            \Big)            
+            ,
+            \\
+            \| \Jacobian \Xi_{1}^{-1} \|
+            &\leq  
+            \Csechs{n}{k}(\calT)
+            :=
+            (k+1) 
+            \theta(\calT)
+            \mu(\calT)
+            \beta_T
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + \beta_T \right)
+                \mu(\calT)
+            \Big)            
+            .
+        \end{align*}
+        We get the determinant estimates
+        \begin{align*}
+            |\det(\Xi_{1})|
+            \leq 
+            \Cdetfive{n}{k}(\calT)
+            :=
+            (k+1)^{n}
+            \theta(\calT)^{n}
+            \beta_T^{n}
+            \mu(\calT)^{n}
+            ,
+            \qquad 
+            |\det(\Xi_{1}^{-1})|
+            \leq 
+            \Cdetsechs{n}{k}(\calT)
+            :=
+            (k+1)^{n}
+            \theta(\calT)^{n}
+            \mu(\calT)^{n}
+            .
+        \end{align*}
+        This completes the desired estimates for $\Xi_{1}$.
+
+        \item 
+        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U $ by setting 
+        \begin{align*}
+            \Xi_{2} := \Psi \circ \Phi.
+        \end{align*}
+        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
+        The combination of the previous estimates for $\Psi$ and $\Phi$ now lead to 
+        \begin{align*}
+            \| \Jacobian \Xi_{2} \|
+            &\leq 
+            \Csieb{n}{k}(\calT)
+            :=
+            \frac 1 4
+            % \left( \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \sqrt{ 1 + (k+1)^2 \mu(T)^2 } \right)
+            \left( 4 + (k+1) \mu(T) \right)
+            \cdot 
             (k+1) 
@@
             \\
-            \| \Jacobian \Xi^{-1} \|
+            \| \Jacobian \Xi_{2}^{-1} \|
             &\leq  
-            \Cfive{n}{k}(\calT)
+            \Cacht{n}{k}(\calT)
             :=
+            \frac 1 2
+            %\left( \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \sqrt{ 1 + (k+1)^2 \mu(T)^2 } \right)
+            \left( 4 + (k+1) \mu(T) \right)
+            \cdot 
             (k+1) 
@@
         \begin{align*}
-            |\det(\Xi)|
-            \leq 
-            \Cdetvier{n}{k}(\calT)
+            |\det(\Xi_{2})|
+            \leq 
+            \Cdetsieb{n}{k}(\calT)
             :=
+            \frac 1 2 
             (k+1)^{n}
@@
             \qquad 
-            |\det(\Xi^{-1})|
-            \leq 
-            \Cdetfive{n}{k}(\calT)
+            |\det(\Xi_{2}^{-1})|
+            \leq 
+            \Cdetacht{n}{k}(\calT)
             :=
+            2
             (k+1)^{n}
@@
         \end{align*}
-        This completes the desired estimates.
+        This completes the desired estimates for $\Xi_{2}$.
 
@@
              &\leq 
-             \Csechs{n} \kappa(K) \leq 2 \Csechs{n} \kappa(\calT)
+             \Cdrei{n} \kappa(K) \leq 2 \Cdrei{n} \kappa(\calT)
              .
@@
              &\leq 
-             \Csechs{n} \kappa({G}) \leq 4 \Csechs{n} \kappa(\calT)
+             \Cdrei{n} \kappa({G}) \leq 4 \Cdrei{n} \kappa(\calT)
              .
@@
         \begin{gather*}
-            \| \Jacobian \Theta_{|K}      \| \leq 2 \Csechs{n} \kappa(\calT)
+            \| \Jacobian \Theta_{|K}      \| \leq 2 \Cdrei{n} \kappa(\calT)
             ,
             \qquad 
-            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Csechs{n} \kappa(\calT)
+            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Cdrei{n} \kappa(\calT)
             ,
@@
                 n
-                2 \Csechs{n} \kappa(\calT)
+                2 \Cdrei{n} \kappa(\calT)
                 4 
@@
             \right) 
-            2 \Csechs{n} \kappa(\calT)
+            2 \Cdrei{n} \kappa(\calT)
             ,
@@
                 n
-                2 \Csechs{n} \kappa(\calT)
+                2 \Cdrei{n} \kappa(\calT)
                 2 
@@
             \right) 
-            2 \Csechs{n} \kappa(\calT)
+            2 \Cdrei{n} \kappa(\calT)
             .
@@
 %         C_{{\rm PF},\Gamma,k,p}(\calT) 
-%         \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
-%         \Cvier{n}{k}(\calT)^{k+1} 
+%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+%         \Cfive{n}{k}(\calT)^{k+1} 
 %         \diam(T)^{k} 
@@
 %         + 
-%         \Cdetfive{n}{k}(\calT)^{-\frac 1 p} 
-%         \Cvier{n}{k}(\calT)^{k} 
+%         \Cdetsechs{n}{k}(\calT)^{-\frac 1 p} 
+%         \Cfive{n}{k}(\calT)^{k} 
 %         \| w \|_{L^{p}(U_{m-1})}
@@
             +
-            \Cvier{n}{k}(\calT)^{k+1} 
-            \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
+            \Cfive{n}{k}(\calT)^{k+1} 
+            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
             \| \cartan u \|_{L^{p}(U_{m-1})}
@@
         + 
-        \Cvier{n}{k}(\calT)^{k} 
-        \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
+        \Cfive{n}{k}(\calT)^{k} 
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
         \| w \|_{L^{p}(U_{m-1})}

### 2024-09-11 main.tex
theo's annotations

--- 2024-09-09 main.tex
@@
 we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
-This boundedness is expressed via the Poincar\'e--Friedrichs inequality 
+Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
 \begin{align*}
@@
 \end{align*}
-The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.
+The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. 
+Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.
 
@@
 % \end{align}
-Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
-The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
+Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
+The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
 % Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One example for a bounded linear operator is the average-free potential:
+One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
 \begin{align*}
@@
 then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
-An open set star-shaped with respect to a internal point satisfies Poincar\'e inequalities~\cite[Theorem~3.1]{hurri1988poincare}.
+Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence
 
@@
 % who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
-who provide lower bounds for the spectrum of the Hodge--Laplace operator on smoothly bounded convex domains, 
+who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
 thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
@@
 One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators. 
+which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
 However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
@@
 % DONE: cite VVVV
-In the Hilbert space case, $p=2$, and when the domain is smoothly bounded, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
 By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
@@
 
-But no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
+However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy.
+% DONE: Theo : But -> However
 We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 We consider the latter outcome to be of independent interest. 
+\todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
+we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
+% the curl of a vector field over a tetrahedron with vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential. % DONE : Theo : unclear sentence 
 We achieve this by constructing an auxiliary problem subject to full boundary conditions.
@@
 % Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
+\todo{Where to place this paragraph?}
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
@@
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-% Future work 
-Computable reliable estimates for the Poincar\'e--Friedrichs constant are important: 
-they quantify the fundamental stability properties of partial differential equations in vector analysis,
-such as the Hodge Laplace equation. 
-Upper bounds correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
+% DONE: Theo : paragraph feels misplaced 
+\\
+
+% Future work % DONE: Theo : parts already mentioned ??? 
+% Computable reliable estimates are important: 
+% they quantify the fundamental stability properties of partial differential equations in vector analysis,
+% such as the Hodge Laplace equation. 
+Any upper bounds for the Poincar\'e--Friedrichs constant corresponds to a lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
 % Furthermore, their constants enter the stability and convergence theory of finite element methods. 
-In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
+In numerical methods, upper bounds for the Poincar\'e--Friedrichs for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
 and they lead to lower bounds for the spectrum of finite element matrices. 
-The are several avenues for further research going from here.
+There are several avenues for further research going from here.
 
@@
 
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over smoothly bounded convex domains, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
+Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
 We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
@@
 When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
+which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
 We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
@@
 we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+% TODO: Theo suggests reverse order of that sequence
 We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
@@
     .
-\end{align*}
-Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
+\end{align*} % DONE: Theo : following sentence : which upper bound ?
+Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
 As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
@@
     % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}
+    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
     Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
@@
 %         \leq 
-%         \frac{1}{2}
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+%         \frac 1 2
+        .
+    \end{align*}
+    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
     % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
@@
 
-In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. As a preparatory step, 
-Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
+In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
+As a preparatory step, given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
 This defines a scalar potential.
@@
 For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.
+
+% TODO: Theo : Should shape measures and their discussion be put into the previous section ?
 
@@
 \begin{example}
-    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
+    The standard triangulation of the $3$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable, as are its higher-dimensional generalizations.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
 \end{example}
@@
 we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our explicit purpose are explicit bounds for the operator norms, which are of independent interest. 
+However, our purpose are explicit bounds for the operator norms, which are of independent interest. 
 \\
@@
 We are in the position to establish the main results of this section.
-This includes upper bounds for the Poincar\'--Friedrichs inequalities that we have been looking for. 
+This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
 Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
@@
     The operators discussed by Costabel and McIntosh are pseudodifferential operators of negative order, 
-    because their averaging uses a smooth weight, 
-    and hence they discuss a range of operator bounds between different function spaces. 
-    Guzman and Salgado have estimated the operator norm. 
+    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudodifferential operators 
+    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
+    % Guzman and Salgado have estimated the operator norm. \todo{Describe Guzman and Salgado's contribution in more detail.} 
 \end{remark}
@@
     satisfying
-    \begin{gather*}
-        \| \Jacobian\Xi \|          \leq \Cvier{n}{k}(\calT),
+    \begin{align*}
+        \Lip( \Xi,      T ) \leq \Cvier{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi^{-1} \|     \leq \Cfive{n}{k}(\calT),
-        \\
-        \| \det\Jacobian\Xi \|      \leq \Cdetvier{n}{k}(\calT),
-        \quad 
-        \| \det\Jacobian\Xi^{-1} \| \leq \Cdetfive{n}{k}(\calT),
-    \end{gather*}
-    where the constants on the right-hand sides are as stated in the proof. 
+        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k}(\calT),
+    \end{align*}
+    where $\Cvier{n}{k}(\calT)$ and $\Cfive{n}{k}(\calT)$ are constants as stated in the proof. 
 \end{theorem}
@@
         We let $z'_{S}$ be the midpoint of $S'$. 
-        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary simplex $S'$. 
+        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary $S'$. 
         All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
@@
         \end{align*}
-        By construction, the mapping preserves volumes:
-        \begin{align*}
-            |\det( \Jacobian      \Theta_{|K} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|K} )|
-            =
-            1
-            .
-        \end{align*}
-        We want to characterize the singular values of this transform. 
-        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
-        We can write
-        \begin{align*}
-            \Theta_{|K}(x) 
-            = 
-            x
-            - 
-            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
-            .
-        \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $\hat h_z$,
-        and that it equals $-z_{S'}$ when $x = z_{S'}$.
-%         and when $x = z_{S'}$, then 
-%         \begin{align*}
-%             -z_{S'} 
-%             =
-%             z_{S'}
-%             - 
-%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
-%             .
-%         \end{align*}
-        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
-        \begin{align*}
-            \Theta_{|K}( h_z ) 
-            &= 
-            h_z
-            - 
-            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
-            %\\&
-            = 
-            h_z
-            - 
-            2 z_{S'}
-            %\\&
-            = 
-            - h_{z}
-            - 
-            2 b_{z}
-            .
-        \end{align*}
-        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
-        We study the singular values of the matrix 
-        \begin{align*}
-            B 
-            := 
-            \begin{pmatrix}
-            -1                 & 0
-            \\ 
-            -2 \|b_z\|/\|h_z\| & 1
-            \end{pmatrix}
-            =
-            \begin{pmatrix}
-            -1             & 0
-            \\ 
-            -2 \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
-        Its square roots are the desired singular values of $B$:
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
-            ,
-            \\
-            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
-            .
-        \end{align*}
-        \begin{align*}
-            \lambda
-        \end{align*}
-        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$. 
-        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
-
-%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \| / \| h_{z} \|$, and we know $\|b_z\| \leq \|z_{S'}\|$. 
-        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
-        which is also a face of $T$. Then $(n-k) h_{z}$ is the height vector of $F_{z}$ in $T$. 
-        Thus 
-        \begin{align*}
-            \frac{ \| b_{z} \| }{ \| h_{z} \| }
-            = 
-            \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            = 
-            \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
-            \leq 
-            \frac{ n-k-1 }{n!}
-            \cdot 
-            \frac{ \diam(T)^{n} }{ \vol(T) }
-            :=
-            \beta_T
-            .
-        \end{align*}
-        This establishes bounds on the singular values of the transformation in terms of the mesh geometry. 
-        We write 
-        \begin{align*}
-            \beta_T 
-            := 
-%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
-%             \geq 
-            \sqrt{ 
-                1 + (n-k)^{2} \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
-            } 
-            + 
-            (n-k) \frac{ \diam(T)^{n} }{ n! \vol(T) }            
-            .
-        \end{align*}
-
-        \item 
-        We prove another auxiliary result.
-        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
-        Define 
-        \begin{align*}
-            F(x) 
-            = 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
-            x
-            .
-        \end{align*}
-        This is defined away from the hyperplane orthogonal to $h_2$.
-        This is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
-        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed, 
-        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
-
-        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
-        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $h_2$, respectively, and the vector $x$.
-        In what follows, $y \in \bbR^{n}$.
-        \begin{align*}
-            \Jacobian F(x) \cdot y
-            &=
-            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
-            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            +
-            x
-            \otimes 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ h_1^{t} y }{ \| h_1 \|^{2} }
-            \\&=
-            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
-            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
-            +
-            \hat x
-            \otimes 
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
-            \\&=
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
-            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
-            +
-            \hat x
-            \otimes 
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
-            \\&=
-            \frac{ \| h_2 \| }{ \| h_1 \| }
-            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
-            \left( 
-                y 
-                - 
-                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
-                + 
-                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
-            \right)
-            .
-        \end{align*}
-        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
-        Notice that $a \perp \hat x$ by definition.
-The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
-Over that two-dimensional subspace, it can be represented by a triangular matrix.
-        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
-        %~\cite{blinn1996consider} 
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
-            \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
-        \end{align*}
-        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
-        We notice the obvious upper bound 
-        \begin{align*}
-            \|a\| 
-            \leq 
-            2 \max_{1 \leq i \leq 2} 
-            \left( 
-                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
-            \right)
-            .
-        \end{align*}
-
-        \item 
-        We introduce a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|
-        \end{align*}
-        in the following manner.
-Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
-There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively.
-They define respective hyperplanes $H_{G}$ and $H_{K}$,
-        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
-        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
-        We define 
-        \begin{align*}
-            \Psi(x) 
-            = 
-            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
-            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
-            x
-            .
-        \end{align*}
-        One easily verifies that this defines a continuous mapping $\Psi$. 
-        By the same line of thought, we see that it is invertible with inverse satisfying 
-        \begin{align*}
-            \Psi^{-1}(z) 
-            = 
-            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
-            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
-            z,
-            \qquad 
-            z = \Psi(x)
-            .
-        \end{align*}
-        Our previous observations enable estimates for the Jacobians. 
-        We have the operator norm and determinant formulas 
-        \begin{gather*}
-            \| \Jacobian\Psi(x) \|
-            = 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
-            \right)
-            \\
-            \| \Jacobian\Psi(z)^{-1} \|
-            = 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
-            \right)^{-1},
-            \\
-            \det\Jacobian\Psi(x)
-            =
-            \left( 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \right)^{n},
-            \qquad
-            \det\Jacobian\Psi^{-1}(x)
-            =
-            \left( 
-            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
-            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
-            \right)^{n}
-        \end{gather*}
-        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
-        and where $a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K$.
-
-        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
-        By the definition of the cosine, 
-        \begin{align*}
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \leq 
-            \frac{ \| x_K \| }{ \| h_{{G}} \| }
-            \leq 
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
-            ,
-            \qquad 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            \leq 
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
-            \frac{ \diam(G) }{ \| h_{K} \| }
-            .
-        \end{align*}
-%         \begin{align*}
-%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
-%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-%             \leq 
-%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
-%             .
-%         \end{align*}
-
-        The diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
-        The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
-        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of the origin in some simplex in $\calS'$
-        by scaling with $(k+1)^{-1}$.
-Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $\beta_T$.
-The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows that $\|x_{G}\| \leq \diam(T)$.
-
-        We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
-        \begin{align*}
-            \frac{\diam(T)}{ \|h_{F}\|}
-            \leq  
-            \frac{ \vol(F) \diam(T) }{ n \vol(T) }
-            \leq 
-            \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            .
-        \end{align*}
-        We conclude that 
-        \begin{gather*}
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
-            \leq 
-            (k+1)\beta_T
-            \frac{ \diam(K) }{ \| h_{T} \| }
-            \leq 
-            (k+1)\beta_T
-            \theta(\calT)
-            \frac{ \diam(T) }{ \| h_{T} \| }
-            \leq 
-            (k+1)\beta_T
-            \theta(\calT)
-            \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            ,
-            \\
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(T) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \theta(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \theta(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{gather*}
-        \begin{gather*}
-            \frac{ \diam(K) }{ \| h_{{K}} \| }
-            \leq 
-            (k+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            ,
-            \qquad 
-            \frac{ \| x_{G} \| }{ \| h_{G} \| }
-            \leq 
-            (k+1)\beta_T
-            \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            .
-        \end{gather*}
-
-        %         To simplify that expression, we make another observation regarding the height vectors. 
-        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
-        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
-        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this obversation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
-        %         with the factor $(k+1)^{-1}$.
-
-        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$.
-That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
-        We calculate 
-        \begin{align*}
-            \|a\|
-            = 
-            \left\|
-            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
-            - 
-            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
-            \right\|
-            &
-            \leq 
-            \frac{\|x_{G}\|}{\|h_{G}\|} 
-            + 
-            \frac{\|x_{K}\|}{\|h_{K}\|} 
-            \\&
-            \leq 
-            (k+1) 
-            \left( 1 + \beta_T \right)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-
-        \item 
-        We define a mapping $ \Xi : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
-        \begin{align*}
-            \Xi := \Psi \circ \Theta.
-        \end{align*}
-        It preserves the interface from $T$ onto $U$. We briefly recapitulate why it is bi-Lipschitz.
-
-        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-        After application of a piecewise linear Lipschitz mapping, 
-        we can assume that $|\calK|$ is convex without loss of generality. 
-        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz.
-
-        We recall the upper bound $\sqrt{1+\theta^2} \leq 1 + \theta$ for any $\theta \geq 0$. 
-        This leads to  
-        \begin{align*}
-            \| \Jacobian \Xi \|
-            &\leq 
-            \Cvier{n}{k}(\calT)
-            :=
-            (k+1) 
-            \mu(\calT)
-            \beta_T
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + \beta_T \right)
-                \mu(\calT)
-            \Big)            
-            \\
-            \| \Jacobian \Xi^{-1} \|
-            &\leq  
-            \Cfive{n}{k}(\calT)
-            :=
-            (k+1) 
-            \mu(\calT)
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + \beta_T \right)
-                \mu(\calT)
-            \Big)            
-        \end{align*}
-        We get the determinant estimate 
-        \begin{align*}
-            |\det(\Xi)|
-            \leq 
-            \Cdetvier{n}{k}(\calT)
-            :=
-            (k+1)^{n}
-            \theta(\calT)^{n}
-            \beta_T^{n}
-            \mu(\calT)^{n}
-            ,
-            \qquad 
-            |\det(\Xi^{-1})|
-            \leq 
-            \Cdetfive{n}{k}(\calT)
-            :=
-            (k+1)^{n}
-            \theta(\calT)^{n}
-            \mu(\calT)^{n}
-            .
-        \end{align*}
-        This completes the desired estimates.
-
-        \item 
-        We introduce a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|
-        \end{align*}
-        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There
 
@@
 
-        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
+        A similar argument applies to the triangulation $\calR'$. 
+        We conclude that $\Xi$ is bi-Lipchitz. 
         \color{black}
+
+        \item 
+        \color{red}
+        We collect several geometric facts.
 
@@
         \leq 
-        C_{{\rm PF},\Gamma,l,k,p}(T)
-        \diam(T)^{k} 
+        C_{{\rm PF},T,F,k,p}
         \| \cartan u \|
-        .
-    \end{align*}
-    Here, $C_{{\rm PF},\Gamma,l,k,p}(T) > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},\Gamma,l,k,p}(T)
-        \leq 
-        2^{\frac n p}
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \Ceins{n}(T)^{k}
-        % \| \Jacobian \varphi \|^{k}
+        ,
+    \end{align*}
+    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{{\rm PF},T,F,k,p}
+        \leq 
+        ...
+        \diam(T)
         .
@@
     In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$.
-    We see that $\vol(\tilde U) = (l+1)/n!$
 
@@
         &\leq 
-        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{ \vol(\tilde U) } 
+        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{|\Omega|} 
         2
@@
         \\&\leq 
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{|\Omega|} 
         \| \tilde g \|_{L^{p}(\tilde U)}
@@
         2^{\frac n p}
-        |\det( \Jacobian \varphi )|^{-\frac 1 p} 
-        \| \Jacobian \varphi \|^{k}
-        \cdot 
+        |\det( \Jacobian \varphi )|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
         \| \cartan u \|_{L^{p}(T)}
@@
 \end{proof}
-
-Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
-\begin{align*}
-    C_{{\rm PF},\Gamma,k,p}(\calT) 
-    :=
-    \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
-    C_{{\rm PF},\Gamma,l,k,p}(T)   
-\end{align*}
-
-Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
-For each $1 \leq m \leq M$, there exists a simplex $S_{m} \in \calT$ 
-such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
-We then let $U_{m}$ be the closure $\patch_{\calT}(S_{m}) \setminus T_{m}$,
-and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
 
@@
     there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for each $T_{m} \in \calT$ in the shelling
-    we have the following recursive estimate: 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-%         &
-%         \leq  
-%         C_{{\rm PF},\Gamma,k,p}(\calT) 
-%         \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
-%         \Cvier{n}{k}(\calT)^{k+1} 
-%         \diam(T)^{k} 
-%         \| \cartan u \|_{L^{p}(U_{m-1})}
-%         \\&\qquad
-%         + 
-%         C_{{\rm PF},\Gamma,k,p}(\calT) 
-%         \diam(T)^{k} 
-%         \| \cartan u      \|_{L^{p}(T_{m})} 
-%         \\&\qquad
-%         + 
-%         \Cdetfive{n}{k}(\calT)^{-\frac 1 p} 
-%         \Cvier{n}{k}(\calT)^{k} 
-%         \| w \|_{L^{p}(U_{m-1})}
-%         \\
-        &
-        \leq  
-        C_{{\rm PF},\Gamma,k,p}(\calT) 
-        \diam(T)^{k} 
-        \left( 
-            \| \cartan u      \|_{L^{p}(T_{m})} 
-            +
-            \Cvier{n}{k}(\calT)^{k+1} 
-            \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
-            \| \cartan u \|_{L^{p}(U_{m-1})}
-        \right)
-        \\&\qquad
-        + 
-        \Cvier{n}{k}(\calT)^{k} 
-        \Cdetfive{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(U_{m-1})}
-        .
+    and such that for all $T \in \calT$:
+    \begin{align*}
+        \| w \|_{L^{p}(T_m)}
+        \leq 
+        ...
     \end{align*}
@@
     By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m} \subseteq \Omega_{m}$ be the complement of $T_{m}$ in that newly completed star.
 
@@
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi_{m} \|^{k}
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k}
         \cdot 
@@
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi_{m} \|^{k+1}
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k+1}
         \cdot 
@@
     We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
-    We use the properties of the reflection mapping in Theorem~\ref{theorem:starreflection}. 
-%     \begin{align*}
-%         ...
-%     \end{align*}
-%     This enables the recursion
-%     \begin{align*}
-%         \| w_{m} \|_{L^{p}(T_{m})}
-%         &
-%         \leq  
-%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-%         \| \Jacobian \Xi_{m} \|^{k} 
-%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
-%         \\&\qquad
-%         + 
-%         C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
-%         \| \cartan u      \|_{L^{p}(T_{m})} 
-%         \\&\qquad
-%         + 
-%         C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
-%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-%         \| \Jacobian \Xi_{m} \|^{k+1} 
-%         \| \cartan u \|_{L^{p}(U_{m-1})}
-%         .
-%     \end{align*}
+    By the properties of the reflection mapping in Theorem~\ref{theorem:starreflection},
+    \begin{align*}
+        ...
+    \end{align*}
+    This enables the recursion
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k} 
+        \| w_{m-1} \|_{L^{p}(U_{m-1})}
+        \\&\qquad
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+        \| \cartan u      \|_{L^{p}(T_{m})} 
+        \\&\qquad
+        + 
+        C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi \|^{k+1} 
+        \| \cartan u_{m-1} \|_{L^{p}(U_{m-1})}
+        .
+    \end{align*}
     The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 

### 2024-09-11 main.tex
more text

--- 2024-09-10 main.tex
@@
 
-\section{Reflection on shellable stars}\label{section:extension}
-
-This section is devoted to a crucially important geometric construction. 
+\section{Reflections and Deformations on shellable stars}\label{section:extension}
+
+This section is devoted to crucially important geometric constructions. 
 Suppose that we have a shellable simplicial complex. 
@@
 We are particularly interested in the norms of its Jacobian.
+
+This reflection will be used subsequently to generalize the discussion in Section~\ref{section:gradient}
+to the setting of differential forms. 
+In addition to that, this endeavor will also produce another geometric tool 
+which enables an additional possibility to estimate Poincar\'e--Friedrichs constants:
+we construct a deformation which maps the entire star into the complement of the newly completed star. 
+Again, we give explicit estimates of the Jacobian.
 
@@
 \begin{remark}
-    While the reflection mapping and its analysis in Theorem~\ref{theorem:starreflection} serve our purpose,
+    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
+    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
+    While the reflection and deformation mappings in Theorem~\ref{theorem:starreflection} serve our purpose,
     it might be possible to improve the estimate with an improved analysis or construction.

### 2024-09-11 main.tex

@@
     \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
     % DONE: what exactly is the limit as p -> 1 ? It converges to 1.

### 2024-09-13 main.tex
improvements

@@
 \usepackage[utf8]{inputenc}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 \input{header}
@@
 \usepackage{hyperref}         % For hypertext links
+\usepackage{tikz-3dplot}      % 3d plots
 
@@
 \end{align*}
-The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. 
-Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.
+The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
+\color{blue}
+Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
+% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
+In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
+\color{black}
+\\
 
@@
 as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation},
+We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
 but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
@@
 We consider the latter outcome to be of independent interest. 
-\todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
+% DONE \todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 % such as the Hodge Laplace equation. 
-Any upper bounds for the Poincar\'e--Friedrichs constant corresponds to a lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
-% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
-In numerical methods, upper bounds for the Poincar\'e--Friedrichs for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
-and they lead to lower bounds for the spectrum of finite element matrices. 
 There are several avenues for further research going from here. 
-
 The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
@@
 
-This section is devoted to crucially important geometric constructions. 
+This section is devoted to geometric operations that are crucially important for our main result. 
 Suppose that we have a shellable simplicial complex. 
@@
 we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
-We will need a homeomorphism from the new simplex on its complement in the newly completed star.
+We will need a homeomorphism going from the new simplex onto its complement within the newly completed star.
 This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
 We are particularly interested in the norms of its Jacobian.
-
-This reflection will be used subsequently to generalize the discussion in Section~\ref{section:gradient}
-to the setting of differential forms. 
-In addition to that, this endeavor will also produce another geometric tool 
-which enables an additional possibility to estimate Poincar\'e--Friedrichs constants:
-we construct a deformation which maps the entire star into the complement of the newly completed star. 
+We inerpret this as a nonlinear reflection. It will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms.
+
+In addition to that, this endeavor will produce another geometric tool 
+that enables an additional estimate Poincar\'e--Friedrichs constants:
+we construct a bi-Lipschitz deformation which maps the entire star 
+into the complement of the newly completed star. 
 Again, we give explicit estimates of the Jacobian.
-
-We begin with a geometric observation. 
+\\
+
+We begin with the following observation. 
 Suppose that $T$ is any $n$-dimensional simplex with some proper subsimplex $F$.
-We want to find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is on only one side of the hyperplane.
+We find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is on only one side of the hyperplane.
 
@@
     Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
-    Let $F, F'$ be the two subsimplices of $T$ with respective sets of vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
+    Let $F, F'$ be the two subsimplices of $T$ with respective vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
     Then $T$ lies on one side of the affine subspace
     \begin{gather*}
-        A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
+        A 
+        := 
+        v_0 
+        + 
+        \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} 
+        +  
+        \operatorname{lin}\{ v_{k+1} - v_n, \dots, v_{n-1} - v_n \}.
     \end{gather*}
@@
 \begin{proof}
-    Evidently, $A$ has dimension $n-1$ and $F \cap A \cap T$.
+    Evidently, the linear spans 
+    \begin{gather*}
+        A_{0} := \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \},
+        \qquad 
+        A_{1} := \operatorname{lin}\{ v_{k+1} - v_n, \dots, v_{n-1} - v_n \}
+    \end{gather*}
+    intersect only at the origin, since otherwise the vertices of $T$ are not affinely independent. 
+    So $A$ has dimension $n-1$. 
+    Obviously, $F \subset A \cap T$. 
     Let us now suppose that $x \in A \cap T$.
@@
     \end{align*}
-    We know $x$ can be written as a unique convex combination of the vertices of $T$.
+    We know that this is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
     Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive.
-    If $x \notin F$, then at least one of these coefficients must be negative. 
-    But then their sum must be negative, which is a contradiction. 
+    But if $x \notin F$, then at least one of them must be negative,
+    and thus their sum must be negative, which is a contradiction. 
+    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are zero,
+    which implies $x \in F$.
     The desired statement follows.         
@@
 
+% \begin{figure}
+% \tdplotsetmaincoords{60}{120}
+% \centering
+% \begin{tikzpicture}[tdplot_main_coords]
+% \coordinate (A) at (0, 0, 0);
+% \coordinate (B) at (2, 0, 0);
+% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
+% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
+% \coordinate (A) at (0, 0, 0);
+% \coordinate (B) at (2, 0, 0);
+% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
+% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
+% \draw[thick] (A) -- (B) 
+% \draw[] (B) -- (C) 
+% \draw[] (C) -- (A) 
+% \draw[] (A) -- (D);
+% \draw[thick] (B) -- (D);
+% \draw[] (C) -- (D);
+% \node at (A) [below left] {$A(0,0,0)$};
+% \node at (B) [below right] {$B(2,0,0)$};
+% \node at (C) [above right] {$C(1,\sqrt{3},0)$};
+% \node at (D) [above] {$D(1, \frac{1}{\sqrt{3}}, \sqrt{\frac{8}{3}})$};
+% \end{tikzpicture} 
+% \caption{test}
+% \end{figure}
+
 Next, we observe that stars around subsimplices can represented by vertex stars after a local subdivision of the mesh.
@@
 
+% \begin{lemma}\label{lemma:stardivision}
+%     Let $\calT$ be an $n$-dimensional simplicial complex
+%     such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
+%     Let $z_S$ be the barycenter of $S$ 
+%     and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
+%     If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
+%     then $\vol(T^{\star}) = \vol(T) / n$.
+% \end{lemma}
 \begin{lemma}\label{lemma:stardivision}
-    Let $\calT$ be an $n$-dimensional simplicial complex
-    such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
-    Let $z_S$ be the barycenter of $S$ 
-    and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
-    If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
-    then $\vol(T^{\star}) = \vol(T) / n$.
+    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$,
+    let $z_S$ be the barycenter of $S$, 
+    and let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ at $z_{S}$.
+    Then $\vol(T') = \vol(T) / n$. 
 \end{lemma}
@@
 
-The main result of this section constructs the desired homeomorphism. 
+We know construct the main result of this section, namely the desired bi-Lipschitz homeomorphism. 
 It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
@@
         \qquad 
-        {\Gamma_I} := U \cap T,
+        {\Gamma_1} := U \cap T,
         \qquad 
-        {\Gamma_J} := \overline{ \partial T \setminus \partial U }.
+        {\Gamma_2} := \overline{ \partial T \setminus \partial U }.
     \end{align*}
@@
     \end{align*}
-    which is the identity along ${\Gamma_I} = T \cap U$ and which satisfies the upper bounds 
+    which is the identity along ${\Gamma_1} = T \cap U$ and which satisfies the upper bounds 
     \begin{gather*}
@@
         % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        %We let ${\Gamma_J} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
-        %So ${\Gamma_J}$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
+        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
+        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
         We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
-        Note that ${\Gamma_J}$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_I} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.
+        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
+        whereas ${\Gamma_1} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.
 
@@
             - 
-            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+            2 \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+            \hat z_{S'}
             .
@@
             - 
-            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
+            2 \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle} z_{S'}
             = 
@@
             - 
-            2 z_{S'} \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle}
+            2 \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle} z_{S'}
             %\\&
@@
             +
+            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
             x
-            \otimes 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ h_1^{t} y }{ \| h_1 \|^{2} }
             \\&=
@@
             +
+            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
             \hat x
-            \otimes 
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \hat h_1^{t} y }{ \| h_1 \| }
             \\&=
@@
         where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
-        and where $a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K$.
-
+        and where 
+        \begin{align*}
+            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
+            .
+        \end{align*}
         We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
@@
 
-        \todo{TODO: Integrate the following paragraph and make it two-sided.}
-        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz over some essentially disjoint closed partitions over their respective domains.
+        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
         It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
-        Rademacher's theorem then shows that both have essentially bounded weak Jacobians almost everywhere.
+        Rademacher's theorem then shows that both have essentially bounded weak Jacobians.
 
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
+        \todo{not enough}
 
@@
             |\det(\Xi_{1})|
-            \leq 
+            &\leq 
             \Cdetfive{n}{k}(\calT)
@@
             ,
-            \qquad 
+            \\
             |\det(\Xi_{1}^{-1})|
-            \leq 
+            &\leq 
             \Cdetsechs{n}{k}(\calT)
@@
             |\det(\Xi_{2})|
-            \leq 
+            &\leq 
             \Cdetsieb{n}{k}(\calT)
@@
             ,
-            \qquad 
+            \\
             |\det(\Xi_{2}^{-1})|
-            \leq 
+            &\leq 
             \Cdetacht{n}{k}(\calT)
@@
     While the reflection and deformation mappings in Theorem~\ref{theorem:starreflection} serve our purpose,
-    it might be possible to improve the estimate with an improved analysis or construction.
+    it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
 \end{remark}
@@
 We consider the following example domains in two dimensions:
-the unit square $\Omega_S$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{SS}$:
+the unit square $\Omega_Q$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{S}$:
 \begin{gather*}
-    \Omega_{S}  = (-1,1)^2,
+    \Omega_{Q}  = (-1,1)^2,
     \qquad 
@@
     \\
-    \Omega_{SS} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ).
+    \Omega_{S} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ).
 \end{gather*}

### 2024-09-14 main.tex
additional theorem

@@
     The second estimate follows. 
-    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\eqref{lemma:affinetransform} and the first estimate imply 
+    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:affinetransform} and the first estimate imply 
     \begin{align*}
@@
     All the desired results thus follow.
+
+    Without loss of generality, $F$ lies in the plane of the second to last coordinates,
+    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
+    After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
+    If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
+    are all one with the possibe exception of the singular values of the matrix 
+    \begin{align*}
+        A = 
+        \begin{pmatrix}
+            a_1/h & 0
+            \\
+            a_2/h & 1
+        \end{pmatrix}
+    \end{align*}
+    Its singular values are 
+    \begin{align*}
+        \sigma_{\max}
+        &= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            }
+        +
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        ,
+        \\
+        \sigma_{\min}
+        &=
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        -
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        .
+    \end{align*}
+
 \end{proof}
@@
     \end{align*}
+    \todo{Settle the notation}
 \end{theorem}
@@
     By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+    We write $\Omega_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.
 
@@
 
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
+    such that 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        \leq 
+        C_{\PF,T,k,p}(T_{0})
+        \prod_{i=0}^{m} 
+        C_{???}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+\end{theorem}
+\begin{proof}
+    We prove this via induction. 
+    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
+    Let us assume that the statement is true for some integer $m-1 \geq 0$.
+
+    We write $\Omega_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
+    which is a triangulated $n$-dimensional submanifold with boundary.
+    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
+    which is a collection of faces of $T_{m}$. 
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
+    and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Theorem~\ref{theorem:starreflection},
+    which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
+    By assumption, 
+    there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
+    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
+    \begin{align*}
+        \| w_{m-1} \|_{L^{p}(T_{m})}
+        \leq 
+        C_{\PF,T,k,p}(T_{0})
+        \prod_{i=0}^{m} 
+        C_{???}
+        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    Because pullback and exterior derivative commute, 
+    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
+    Moreover, the desired estimate follow from Theorem~\ref{theorem:starreflection}.
+    The proof is complete. 
+\end{proof}
+
 \section{Numerical examples}\label{section:numericalexamples}

### 2024-09-16 main.tex
hpfem
minor corrections

@@
 We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
+if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
 for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
@@
     \leq 
-    C_{{\rm PF},\Omega,p} 
+    C_{\PF,\Omega,p} 
     \| \bff \|_{L^{p}(\Omega)}
@@
     \leq 
-    C_{{\rm PF},\Omega,p} 
+    C_{\PF,\Omega,p} 
     \| \nabla u \|_{L^{p}(\Omega)},
@@
 \end{align*}
-We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
 \\
@@
 \begin{align*}
-    C_{{\rm P},\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}.
+    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
 \end{align*}
 In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
-Hence $C_{{\rm P},\Omega,2} = C_{{\rm PF},\Omega,2}$.
+Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
 This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
@@
 \begin{align}\label{math:p_vs_pf}
-    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}.
+    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
 \end{align}
@@
 \begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
+\end{align*}
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
 However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
@@
     \leq 
-    C_{{\rm PF},{\rm EFNT},p}
+    C_{\PF,{\rm EFNT},p}
     \diam(\Omega)
@@
 \end{align}
-where $C_{{\rm PF},{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align*}
-    C_{{\rm PF},{\rm EFNT},p}
+where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
+\begin{align*}
+    C_{\PF,{\rm EFNT},p}
     :=
@@
     \leq 
-    2^{|1-\frac 2 p|}C_{{\rm PF},{\rm EFNT},p}
+    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
     \diam(\Omega)
@@
     Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm PF},{\rm EFNT},p}$. 
+    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
     In the case $2 \leq p$, 
@@
         2^{1-\frac 2 p}
-        C_{{\rm PF},{\rm EFNT},p}
+        C_{\PF,{\rm EFNT},p}
         =
@@
         2^{\frac 2 p - 1}
-        C_{{\rm PF},{\rm EFNT},p}
+        C_{\PF,{\rm EFNT},p}
         =
@@
 % DONT: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$,
+%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
 %     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
@@
 %     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$, 
+%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
 %     which implies the Poincar\'e inequality 
@@
         \leq 
-        2 C_{{\rm PF},{\rm EFNT},p}
+        2 C_{\PF,{\rm EFNT},p}
         \max\left( 
@@
         \leq 
-        2 C_{{\rm PF},{\rm EFNT},p}
+        2 C_{\PF,{\rm EFNT},p}
         \rho(\calT)^{\frac 1 p}
@@
         \leq 
-        2 C_{{\rm PF},{\rm EFNT},p}
+        2 C_{\PF,{\rm EFNT},p}
         \| \nabla \hat u \|_{L^{p}(\hat U)}
@@
         &\leq 
-        2 C_{{\rm PF},{\rm EFNT},p}
+        2 C_{\PF,{\rm EFNT},p}
         \max\left( 
@@
         C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{{\rm PF},{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
+        % 2 C_{\PF,{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
         \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
@@
         \rho(\calT)^{\frac{m-1}{p}}
-        % C_{{\rm PF},{\rm EFNT},p} \diam(T_0)
+        % C_{\PF,{\rm EFNT},p} \diam(T_0)
         C_{{\rm{PF}},T_{0},p}
@@
         \leq 
-        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
-        ,
-    \end{align*}
-    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},T,F,p}
+        C_{\PF,T,F,p} \| \nabla u \|_{L^{p}(T)}
+        ,
+    \end{align*}
+    where $C_{\PF,T,F,p} > 0$ is a constant such that 
+    \begin{align*}
+        C_{\PF,T,F,p}
         &\leq 
-        C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
+        C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
         \\
         %\quad 
-        C_{{\rm PF},T,F,p}
+        C_{\PF,T,F,p}
         &\leq
@@
         \leq 
-        C_{{\rm PF},T,p} 
+        C_{\PF,T,p} 
         \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
@@
         \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
+        \left( C_{\PF,T,p}^{p} + p \cdot C_{\PF,T,p}^{p-1} \right) 
         \diam(T)^{p}
@@
         \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
+        \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right) 
         %\diam(T)^{p}
@@
 %         \rho(\calT)^{\frac m p}
-%         C_{{\rm PF},T_{0},p} 
+%         C_{\PF,T_{0},p} 
 %         \| \nabla u \|_{L^{p}( T_{0} )}
@@
 %         \rho(\calT)^{\frac {m-l} p}
-%         C_{{\rm PF},T_{l},F_{l},p} 
+%         C_{\PF,T_{l},F_{l},p} 
 %         \| \nabla u \|_{L^{p}(T_{l})} 
@@
 %         \rho(\calT)^{\frac {m-l} p} \xi(\calT)
-%         C_{{\rm PF},T_{l},F_{l},p} 
+%         C_{\PF,T_{l},F_{l},p} 
 %         \| \nabla u \|_{L^{p}(T_{l-1})} 
@@
         \rho(\calT)^{\frac m p}
-        C_{{\rm PF},T_{0},p} 
+        C_{\PF,T_{0},p} 
         \| \nabla u \|_{L^{p}( T_{0} )}
@@
         \rho(\calT)^{\frac {m-l} p}
-        C_{{\rm PF},T_{l},F_{l},p} 
+        C_{\PF,T_{l},F_{l},p} 
         \left( 
@@
 %         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{l},F_{l},p} 
+%         C_{\PF,T_{l},F_{l},p} 
 %         \| \nabla u \|_{L^{p}( T_{l} )}
@@
         \leq 
-        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
+        C_{\PF,T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
         \\&
         \leq 
-        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        C_{\PF,T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{\PF,T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
         .
@@
         + 
-        C_{{\rm PF},T_{m},F_{m},p} 
+        C_{\PF,T_{m},F_{m},p} 
         \left( 
@@
         \rho(\calT)^{\frac 1 p} \xi(\calT)
-        % C_{{\rm PF},T_{m},F_{m},p} 
+        % C_{\PF,T_{m},F_{m},p} 
         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
@@
         \rho(\calT)^{\frac 1 p} \xi(\calT)
-        % C_{{\rm PF},T_{m},F_{m},p} 
+        % C_{\PF,T_{m},F_{m},p} 
         \| \nabla u \|_{L^{p}(T_{m-1})} 
@@
 %         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \| \nabla u \|_{L^{p}(T_{m})} 
@@
 %         + 
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \left( 
@@
 %         + 
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \| \nabla u \|_{L^{p}(T_{m})} 
 %         + 
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
@@
 %         + 
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \| \nabla u \|_{L^{p}(T_{m})} 
@@
 %         \rho(\calT)^{\frac 1 p} \xi(\calT)
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
@@
 %         \rho(\calT)^{\frac 1 p} \xi(\calT)
-%         C_{{\rm PF},T_{m},F_{m},p} 
+%         C_{\PF,T_{m},F_{m},p} 
 %         \| \nabla u \|_{L^{p}(T_{m-1})} 
@@
         \leq 
-        C_{{\rm PF},\Gamma,l,k,p}(T)
+        C_{\PF,\Gamma,l,k,p}(T)
         \diam(T)^{k} 
@@
     \end{align*}
-    Here, $C_{{\rm PF},\Gamma,l,k,p}(T) > 0$ is a constant such that 
-    \begin{align*}
-        C_{{\rm PF},\Gamma,l,k,p}(T)
+    Here, $C_{\PF,\Gamma,l,k,p}(T) > 0$ is a constant such that 
+    \begin{align*}
+        C_{\PF,\Gamma,l,k,p}(T)
         \leq 
@@
         2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \Ceins{n}(T)^{k}
+        \alpha(T)^{k-1}
+        \Ceins{n}(T)
         % \| \Jacobian \varphi \|^{k}
@@
     In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
-    \begin{gather*}
+    \begin{align*}
         \| w \|_{L^{p}(T_{m+1})}
-        \leq 
+        &\leq 
         |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \Jacobian \varphi^{-1} \|^{k-1}
         \| \tilde w \|_{L^{p}(\hat T)}
+        \\&
         \leq 
         |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \| \Jacobian \varphi^{-1} \|^{k-1}
         \| \tilde w \|_{L^{p}(\tilde U)}
@@
         \| \tilde g \|_{L^{p}(\tilde U)}
-        \leq 
+        &\leq 
         2^{\frac n p}
@@
         2^{\frac n p}
-        |\det( \Jacobian \varphi )|^{-\frac 1 p} 
+        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
         \| \Jacobian \varphi \|^{k}
@@
 \begin{align*}
-    C_{{\rm PF},\Gamma,k,p}(\calT) 
+    C_{\PF,\Gamma,k,p}(\calT) 
     :=
     \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
-    C_{{\rm PF},\Gamma,l,k,p}(T)   
+    C_{\PF,\Gamma,l,k,p}(T)   
 \end{align*}
@@
 %         \leq  
-%         C_{{\rm PF},\Gamma,k,p}(\calT) 
+%         C_{\PF,\Gamma,k,p}(\calT) 
 %         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
@@
 %         + 
-%         C_{{\rm PF},\Gamma,k,p}(\calT) 
+%         C_{\PF,\Gamma,k,p}(\calT) 
 %         \diam(T)^{k} 
@@
         \leq  
-        C_{{\rm PF},\Gamma,k,p}(\calT) 
+        C_{\PF,\Gamma,k,p}(\calT) 
         \diam(T)^{k} 
@@
         \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
+        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
         \\&
         \leq 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
         .
@@
 %         + 
-%         C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+%         C_{\PF,T_{m},\Gamma_{m},k,p} 
 %         \| \cartan u      \|_{L^{p}(T_{m})} 
@@
 %         + 
-%         C_{{\rm PF},T_{m},\Gamma_{m},k,p} 
+%         C_{\PF,T_{m},\Gamma_{m},k,p} 
 %         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
@@
 
+\subsection{Estimates for partial boundary conditions}
+
+We first assess the constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
+which relies on estimates for the Bogovski\u{i} operator over an auxiliary reference domain.
+Our experiments over triangles and tetrahedra indicate we overestimate by several magnitudes.
+%
+We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
+Numerical examples indicate that this holds for $p=2$.
+
 \subsection{Two-dimensional examples}
@@
     \\
-    \Omega_{S} = (-1,1)^2 \setminus ( (0,1) \times \{0\} ).
+    \Omega_{S} = (-1,1)^2 \setminus ( [0,1) \times \{0\} ).
 \end{gather*}
@@
     \qquad 
-    \Omega_{F}  = (-1,1)^3 \setminus (0,1)^3,
+    \Omega_{F}  = (-1,1)^3 \setminus [0,1)^3,
     \\
@@
     \left( (-1,0) \times (-1,0) \times (-1,1) \right)
-    \\&\quad
+    \\&\qquad
     \cup 
     \left( (-1,0) \times (-1,1) \times (-1,0) \right)
-    \\&\quad
+    \\&\qquad
     \cup 

### 2024-09-16 main.tex
correction

@@
 
+\usepackage{comment}          % 
 \usepackage{hyperref}         % For hypertext links
@@
 and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component. 
-
-\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
-\\
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align*}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align*}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \;dx
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-% \begin{align*}
-%     \color{Emerald}
-%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p-1} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     +
-%     2^{p-1} 
-%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     .
-% \end{align*}
-Via an application of the triangle inequality, 
-the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
-Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
-\end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-\\
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
-see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
-\begin{align}\label{math:acostaduran}
-    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{\diam(\Omega)}{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    ,
-    \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
-    \leq 
-    \frac{\diam(\Omega)}{\pi}
-    \| \nabla u \|_{L^{2}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,2}(\Omega)
-    .
-\end{align}
-These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
-\begin{align}\label{math:chuawheeden}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},{\rm CW},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where we use an upper bound by Chua and Wheeden:
-\begin{align*}
-    C_{{\rm P},{\rm CW},p} 
-    := 
-    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
-    \frac{ 
-        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
-    }{ 
-        \| \nabla v \|_{L^{p}([0,1])} 
-    }
-    \leq 
-    \sqrt[p]{p} 2^{1-\frac 1 p}
-    =
-    2
-    \left( \frac p 2 \right)^{\frac 1 p}
-    .
-\end{align*} % DONE: Theo : following sentence : which upper bound ?
-Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
-As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
-
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
-when $1 < p < \infty$, one can show that 
-\begin{align}\label{math:esposito:pf}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align*}
-    C_{\PF,{\rm EFNT},p}
-    :=
-    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
-    .
-\end{align*}
-Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
-\begin{align}\label{math:esposito:poincare}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
-\begin{align}\label{math:l1estimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{ \diam(\Omega) }{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    .
-\end{align}
-When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
-\begin{align}\label{math:lipschitzestimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{\infty}(\Omega)}
-    \leq 
-    \diam(\Omega)
-    \| \nabla u \|_{L^{\infty}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,\infty}(\Omega)
-    .
-\end{align}
-
-% DONT: Keep ?
-% \begin{example}
-%     We explain why \eqref{math:l1estimate} is optimal. 
-%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
-%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
-%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
-%     and $\Omega$ has diameter $2$. 
-%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
-%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
-%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
-% \end{example}
-
-\begin{remark}
-    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
-    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
-    In the case $2 \leq p$, 
-    \begin{align*}
-        2^{1-\frac 2 p}
-        C_{\PF,{\rm EFNT},p}
-        =
-        \frac{ 2^{1-\frac 2 p} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq 
-        4^{-\frac 1 p}
-        \leq
-        C_{{\rm P},{\rm CW},p} 
-        .
-    \end{align*}
-    In the case $2 \geq p$, 
-    \begin{align*}
-        2^{\frac 2 p - 1}
-        C_{\PF,{\rm EFNT},p}
-        =
-        \frac{ 2^{\frac 2 p - 1} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq
-        \frac{ 2^{\frac 2 p-1} }{2}
-        &
-        =
-        2^{\frac 2 p - 2}
-        \\&
-        =
-        4^{\frac 1 p - 1}
-        \leq
-        C_{{\rm P},{\rm CW},p} 
-%         % 
-%         .
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
-%         =
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
-%         \leq 
-%         \frac{1}{2}
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua wheeden upper bound is not optimal!
-    % DONE: Theorem 1.2 in Chua Wheeden 
-% DONT: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
-%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-%         \leq 
-%         \frac{1}{2}
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{1}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,1}(\Omega)
-%         .
-%     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
-%     which implies the Poincar\'e inequality 
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,\infty}(\Omega)
-%         %
-%     \end{align*}
-%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
-%     % DONT: review this entire result 
-\end{remark}
-
-% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
-
-\begin{remark}
-    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
-    but individual convex domains may allow for better constants.
-    We refer to \cite{matculevich2016explicit} for an overview;
-    for example, triangles allow the reduction of the constant by 20\%.
-\end{remark}
-
-% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
-
-\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
-
-In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
-As a preparatory step, given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
-This defines a scalar potential.
-This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
-after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
-The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
-\\
-
-Towards this goal, we introduce quantitative measures for the geometric quality of triangulations. 
+\\
+
+We shift gears and move from a combinatorial study of triangulations to an analytical study:
+we introduce quantitative measures for the geometric quality of triangulations. 
 These indicate of the regularity of simplex shapes. 
 Most of such \emph{shape measures} in the literature are based on geometric features, 
-but we also consider indicators based on affine transformations associated with the mesh;
-this is because the properties of these transformations are what shows up in our estimates.
-
-For the purpose of the usual scaling arguments, we introduce the reference simplex $\Delta^n \subseteq \bbR^n$ as the convex closure of the origin and the $n$ canonical unit vectors.
-
-% TODO: Theo : Should shape measures and their discussion be put into the previous section ?
+but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates.
+
+For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
 
@@
 
-\todo{Tighter estimate via geometry}
 \begin{lemma}\label{lemma:volumecomparison}
@@
 
-    Without loss of generality, $F$ lies in the plane of the second to last coordinates,
-    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-    After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
-    If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
-    are all one with the possibe exception of the singular values of the matrix 
-    \begin{align*}
-        A = 
-        \begin{pmatrix}
-            a_1/h & 0
-            \\
-            a_2/h & 1
-        \end{pmatrix}
-    \end{align*}
-    Its singular values are 
-    \begin{align*}
-        \sigma_{\max}
-        &= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            }
-        +
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        ,
-        \\
-        \sigma_{\min}
-        &=
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        -
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        .
-    \end{align*}
-
+%     \todo{Tighter estimate via geometry}
+%     Without loss of generality, $F$ lies in the plane of the second to last coordinates,
+%     so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
+%     After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
+%     If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
+%     are all one with the possibe exception of the singular values of the matrix 
+%     \begin{align*}
+%         A = 
+%         \begin{pmatrix}
+%             a_1/h & 0
+%             \\
+%             a_2/h & 1
+%         \end{pmatrix}
+%     \end{align*}
+%     Its singular values are 
+%     \begin{align*}
+%         \sigma_{\max}
+%         &= 
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+%         \\&= 
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+%             } }
+%         \\&= 
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+%             }
+%         +
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+%             }
+%         \\&= 
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+%             }
+%         +
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+%             }
+%         \\&= 
+%         \frac{1}{2}
+%         \sqrt{ 
+%             \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+%             }
+%         +
+%         \frac{1}{2}
+%         \sqrt{ 
+%             \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+%             }
+%         ,
+%         \\
+%         \sigma_{\min}
+%         &=
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+%         \\&= 
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+%             }
+%         -
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+%             }
+%         .
+%     \end{align*}
 \end{proof}
@@
     Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ but not $\theta(\calT)$. 
-    We can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
+    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
+    If we have an upper estimate for the number of simplices sharing a given vertex, 
+    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
 \end{remark}
+%%%%%%%% END HERE
+
+\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+
+We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
+We take the opportunity to discuss convex domains as a preparatory special case.
+This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
+\\
+
+Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
+Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
+We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
+
+We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
+if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
+for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:inequalitypf:gradient}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+Since $\Omega$ is connected, this is equivalent to  
+\begin{align*}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+\\
+
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
+we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
+if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
+% for all $u \in W^{1,p}(\Omega)$
+\begin{align*}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm P},\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
+\begin{align*}
+    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u(x) \;dx.
+\end{align*}
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
+Towards a converse inequality, 
+let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align*}
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \;dx
+    = 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align*}
+Here, we have used H\"older's or Jensen's inequality. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
+The triangle inequality now shows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)} 
+    \leq
+    2
+    \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+% \begin{align*}
+%     \color{Emerald}
+%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p-1} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     +
+%     2^{p-1} 
+%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     .
+% \end{align*}
+Via an application of the triangle inequality, 
+the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
+\end{align*}
+In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
+Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
+This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}
+    \leq 
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| u \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
+We thus conclude 
+\begin{align}\label{math:p_vs_pf}
+    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
+\end{align}
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
+\\
+
+There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
+We define the potential 
+\begin{align*}
+    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*}
+If there is a Poincar\'e--Friedrichs constant, then by definition
+\begin{align*}
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
+\end{align*}
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
+Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
+\begin{align*}
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    .
+\end{align*}
+A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
+\begin{align*}
+    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
+\\
+
+In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
+This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+
+\begin{remark}
+    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
+    We want to generalize the discussion to the curl and divergence operators. 
+    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
+    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
+    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
+    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
+    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
+    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
+\end{remark}
+
+% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+
+\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
+
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
+see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
+\begin{align}\label{math:acostaduran}
+    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
+    \leq 
+    \frac{\diam(\Omega)}{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,1}(\Omega)
+    ,
+    \\
+    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
+    \leq 
+    \frac{\diam(\Omega)}{\pi}
+    \| \nabla u \|_{L^{2}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,2}(\Omega)
+    .
+\end{align}
+These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
+Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
+\begin{align}\label{math:chuawheeden}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm P},{\rm CW},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where we use an upper bound by Chua and Wheeden:
+\begin{align*}
+    C_{{\rm P},{\rm CW},p} 
+    := 
+    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
+    \frac{ 
+        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
+    }{ 
+        \| \nabla v \|_{L^{p}([0,1])} 
+    }
+    \leq 
+    \sqrt[p]{p} 2^{1-\frac 1 p}
+    =
+    2
+    \left( \frac p 2 \right)^{\frac 1 p}
+    .
+\end{align*} % DONE: Theo : following sentence : which upper bound ?
+Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
+As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
+
+We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
+when $1 < p < \infty$, one can show that 
+\begin{align}\label{math:esposito:pf}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,{\rm EFNT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
+\begin{align*}
+    C_{\PF,{\rm EFNT},p}
+    :=
+    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
+    .
+\end{align*}
+Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+\begin{align}\label{math:esposito:poincare}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}
+When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
+\begin{align}\label{math:l1estimate}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{1}(\Omega)}
+    \leq 
+    \frac{ \diam(\Omega) }{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,1}(\Omega)
+    .
+\end{align}
+When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
+\begin{align}\label{math:lipschitzestimate}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{\infty}(\Omega)}
+    \leq 
+    \diam(\Omega)
+    \| \nabla u \|_{L^{\infty}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,\infty}(\Omega)
+    .
+\end{align}
+
+% DONT: Keep ?
+% \begin{example}
+%     We explain why \eqref{math:l1estimate} is optimal. 
+%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
+%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
+%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
+%     and $\Omega$ has diameter $2$. 
+%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
+%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
+%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
+% \end{example}
+
+\begin{remark}
+    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
+    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
+    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
+    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
+    In the case $2 \leq p$, 
+    \begin{align*}
+        2^{1-\frac 2 p}
+        C_{\PF,{\rm EFNT},p}
+        =
+        \frac{ 2^{1-\frac 2 p} }{2}
+        \frac{ \sin(\pi/p) }{ \pi/p }
+        \frac{ 1 }{ \sqrt[p]{p-1} }
+        \leq 
+        4^{-\frac 1 p}
+        \leq
+        C_{{\rm P},{\rm CW},p} 
+        .
+    \end{align*}
+    In the case $2 \geq p$, 
+    \begin{align*}
+        2^{\frac 2 p - 1}
+        C_{\PF,{\rm EFNT},p}
+        =
+        \frac{ 2^{\frac 2 p - 1} }{2}
+        \frac{ \sin(\pi/p) }{ \pi/p }
+        \frac{ 1 }{ \sqrt[p]{p-1} }
+        \leq
+        \frac{ 2^{\frac 2 p-1} }{2}
+        &
+        =
+        2^{\frac 2 p - 2}
+        \\&
+        =
+        4^{\frac 1 p - 1}
+        \leq
+        C_{{\rm P},{\rm CW},p} 
+%         % 
+%         .
+%         4^{\frac 1 p}
+%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
+%         =
+%         4^{\frac 1 p}
+%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
+%         \leq 
+%         \frac{1}{2}
+        .
+    \end{align*}
+    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
+    % DONT: insert the original inequality by chua and Wheeden
+    % DONE: chua wheeden upper bound is not optimal!
+    % DONE: Theorem 1.2 in Chua Wheeden 
+% DONT: Keep ?
+%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
+%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
+%     \begin{align*}
+%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
+%         \leq 
+%         \frac{1}{2}
+%         \diam(\Omega)
+%         \| \nabla u \|_{L^{1}(\Omega)}
+%         ,
+%         \quad
+%         \forall 
+%         u \in W^{1,1}(\Omega)
+%         .
+%     \end{align*}
+%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
+%     which implies the Poincar\'e inequality 
+%     \begin{align*}
+%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
+%         \leq 
+%         \diam(\Omega)
+%         \| \nabla u \|_{L^{\infty}(\Omega)}
+%         ,
+%         \quad
+%         \forall 
+%         u \in W^{1,\infty}(\Omega)
+%         %
+%     \end{align*}
+%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
+%     % DONT: review this entire result 
+\end{remark}
+
+% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
+
+\begin{remark}
+    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    but individual convex domains may allow for better constants.
+    We refer to \cite{matculevich2016explicit} for an overview;
+    for example, triangles allow the reduction of the constant by 20\%.
+\end{remark}
+
+% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
+
+\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
+
+In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
+As a preparatory step, given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
+This defines a scalar potential.
+This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
+after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
+The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
+\\
 
@@
  \end{align*}
- Taking into account Definition~\eqref{math:moremeasures}, we obtain the desired inequality.
+ Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality.
 %  \begin{align*}
@@
 \begin{lemma}\label{lemma:stars_are_shellable}
-    Let $\calT$ be a $n$-dimensional manifold triangulation and $V \in \Vertices(\calT)$ be an inner vertex.
+    Let $\calT$ be a $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
     Then $\patch_{\calT}(V)$ is shellable. 
@@
 \begin{proof}
-    Without loss of generality, $V$ is the origin. 
-    Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
-    We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
-    which does not affect shellability. 
-    The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
-    and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
+    This is Lemma~8.7 in \cite{ziegler2012lectures}.
+%     Without loss of generality, $V$ is the origin. 
+%     Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
+%     We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
+%     which does not affect shellability. 
+%     The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
+%     and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
 \end{proof}
@@
 
-        \item 
-        We introduce a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|
-        \end{align*}
-        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There
-
+\begin{comment}
         \item 
@@
         \end{gather*}
+\end{comment}
     \end{itemize}
@@
         .
-    \end{gather*}
+    \end{align*}
     The second inequality follows.

### 2024-09-16 main.tex
major update

@@
 % Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
-\todo{Where to place this paragraph?}
+\todo{What is the best place for this paragraph?}
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
@@
 but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
+All these quantities have in common that they can be computed from purely local information. 
+While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
+
+\todo{MWL: The different geometric quantities in this section should really be just what is needed later.
+Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
+Any inequalities here should be as tight as possible.
+}
+
+We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
+Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$.
 
@@
 
+Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
+where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
+We recall that the $\ell^{2}$ operator norm of $\|A\|_{2}$ agrees with $\sigma_{\max}(A)$,
+and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
+% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
+
 Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{geometric shape measure} $\kappa(T)$
-and the \textit{algebraic shape measure} $\alpha(T)$ by 
+we define the \textit{geometric shape measure} $\kappa(T)$,
+the \textit{algebraic shape measure} $\kappa_{2}(T)$,
+and the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$ 
+by 
 \begin{align}\label{math:shapemeasure}
@@
     \qquad 
-    \alpha(T)
+    \kappa_{\maxcol}(T)
+    := 
+    \frac{ \diam(T) }{ \height(T) }
+    ,
+    \qquad 
+    \kappa_{2}(T)
     := 
@@
     \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
+%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
     ,
 \end{align}
-where the last suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
+where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
 % DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
+
+When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
 \begin{align}\label{math:shapemeasure:triangulation}
-    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
+    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
+    ,
     \quad 
-    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T).
+    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
+    ,
+    \quad 
+    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
+    .
 \end{align}
-Here, $\kappa(\calT)$ and $\alpha(\calT)$ are the geometric and algebraic shape measures of the triangulation.
-
-\begin{lemma}\label{lemma:affinetransform}
+We call these the geometric, algebraic, and aspect shape measure, respectively, of the triangulation.
+
+We gather a few relationships between geometric and algebraic entities and compare the different shape measures.
+
+\begin{lemma}\label{lemma:measurerelationships}
     Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
@@
         \\
-        \alpha(T)
+        \kappa_{2}(T)
         \leq 
@@
         % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
+        \kappa(T)
+        ,
+        \qquad 
+        %         \kappa(T)^{\frac 1 n}
+        %         \leq 
+        \kappa_{\maxcol}(T)
+        \leq 
         \kappa(T)
@@
         \quad 
-        \Cdrei{n} \leq \sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
+        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
         . 
@@
 \begin{proof}
+%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
+%     except for the vertex $\varphi(0)$. It immediately follows that 
+%     \begin{align*}
+%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
+%         .
+%     \end{align*}
+%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
+%     
     We easily verify the first inequality.
@@
 %     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
-    The second inequality follows. 
-    To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
-
-%     By a result of Yu and Gu \cite{yisheng1997note},
+    The second inequality follows by taking the reciprocal. 
+    The definition of the condition number now gives the third inequalities. 
+    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
+    Finally, 
+    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
+    \begin{align*}
+        \frac{ \diam(T) }{ \height(T) }
+        \leq 
+        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
+        \leq 
+        \frac{ \diam(T)^{n} }{ n! \vol(T) }
+        .
+    \end{align*}
+%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
 %     \begin{align*}
-%         \frac{ \sigma_{n} }{ \sigma_{1} }
-%         &\geq 
-%         \det(\Jacobian\varphi)
-%         \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
-%         \sigma_{1}^{-1}
-%         \geq 
-%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
-%         \det(\Jacobian\varphi)
-%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
-%         \frac{1}{\sqrt{n} \diam(T)}
-%         \\&
-%         \geq 
-%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
-%         \frac{1}{\sqrt{n}}
-%         \frac{ n! \vol(T) }{ \diam(T)^{n} }
+%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%         \leq 
+%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
 %         .
 %     \end{align*}
-%     Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. % THIS IS OPTIMAL
-%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
-%     \begin{gather*}
-%         \diam(T) 
-%         \leq 
-%         \sqrt{2} \sigma_1 
-%         \leq 
-%         \sqrt{2} 
-%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
-%         \sigma_n
-%         \leq 
-%         \sqrt{2n^{n}} 
-%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
-%         \sigma_n
-%         .
-%     \end{gather*}
-%     The desired result is thus evident. 
+    That shows the fourth and last of the inequalities. 
 \end{proof}
@@
     The second estimate follows. 
-    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:affinetransform} and the first estimate imply 
+    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
     \begin{align*}
@@
 \begin{align*}
-    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u(x) \;dx.
+    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
 \end{align*}
@@
     = 
-    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} |\Omega|^{-1} \int_{\Omega} |u(x)|^{p} \;dx
+    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
     = 
@@
  \end{align*}
- Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality.
+ % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
+ We obtain the desired estimate. 
 %  \begin{align*}
@@
 \begin{equation}\label{math:mainkernel}
-  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
+  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
   .
@@
     &= 
-    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} |\Omega|^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
     \\
     &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
     .
@@
     &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
     \\
     &= 
-    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
 \end{align*}
@@
 %     \\&\leq 
-%     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
     \\&\leq 
-    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
     .
@@
     \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
     D
@@
     \leq 
-    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
     D
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
+% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
 % 
@@
     \\&\leq 
-    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
     \\&\leq 
-    \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
+    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
     .
@@
     \leq 
-    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
+    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
     D
@@
     \leq 
-    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
     D
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
+% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
 Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
@@
         &\leq 
-        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
         D
@@
         &\leq 
-        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
+        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
         D
@@
             \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            = 
-            \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
-            \leq 
-            \frac{ n-k }{n!}
-            \cdot 
-            \frac{ \diam(T)^{n} }{ \vol(T) }
+            \leq 
+            (n-k) \kappa_{\maxcol}(T)
+%             = 
+%             \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
+%             \leq 
+%             \frac{ n-k }{n!}
+%             \cdot 
+%             \frac{ \diam(T)^{n} }{ \vol(T) }
             .
@@
         \begin{align*}
-            \beta_T 
+            B_{T} 
             := 
@@
             \sqrt{ 
-                1 + (n-k)^{2} \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+                1 + (n-k)^{2} \kappa_{\maxcol}(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
             } 
             + 
-            (n-k) \frac{ \diam(T)^{n} }{ n! \vol(T) }            
+            (n-k) \kappa_{\maxcol}(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
             .
@@
         \begin{align*}
-            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \mu(T).
+            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \kappa_{\maxcol}(T).
         \end{align*}
@@
             \leq 
-            \frac 1 4 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
+            \frac 1 4 \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 }
             ,
@@
             \leq 
-            \frac 1 2 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
+            \frac 1 2 \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 }
             ,
@@
         by scaling with $(k+1)^{-1}$.
-Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $\beta_T$.
+Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
 The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
@@
             \leq  
-            \frac{ \vol(F) \diam(T) }{ n \vol(T) }
-            \leq 
-            \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \kappa_{\maxcol}(T)
+            % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
             \leq 
-            (k+1)\beta_T
+            (k+1)B_{T}
             \frac{ \diam(K) }{ \| h_{T} \| }
             \leq 
-            (k+1)\beta_T
+            (k+1)B_{T}
             \theta(\calT)
@@
             \leq 
-            (k+1)\beta_T
+            (k+1)B_{T}
             \theta(\calT)
-            \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \kappa_{\maxcol}(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             ,
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             ,
@@
             \leq 
-            (k+1)\beta_T
-            \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (k+1)B_{T}
+            \kappa_{\maxcol}({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
             (k+1) 
-            \left( 1 + \beta_T \right)
+            \left( 1 + B_{T} \right)
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
             \theta(\calT)
-            \mu(\calT)
-            \beta_T^{2}
+            \kappa_{\maxcol}(\calT)
+            B_{T}^{2}
             \Big( 
@@
                 (k+1) 
-                \left( 1 + \beta_T \right)
-                \mu(\calT)
+                \left( 1 + B_{T} \right)
+                \kappa_{\maxcol}(\calT)
             \Big)            
@@
             \theta(\calT)
-            \mu(\calT)
-            \beta_T
+            \kappa_{\maxcol}(\calT)
+            B_{T}
             \Big( 
@@
             \theta(\calT)^{n}
-            \beta_T^{n}
-            \mu(\calT)^{n}
+            B_{T}^{n}
+            \kappa_{\maxcol}(\calT)^{n}
             ,
@@
             \theta(\calT)^{n}
-            \mu(\calT)^{n}
+            \kappa_{\maxcol}(\calT)^{n}
             .
@@
             \frac 1 4
-            % \left( \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \sqrt{ 1 + (k+1)^2 \mu(T)^2 } \right)
-            \left( 4 + (k+1) \mu(T) \right)
+            % \left( \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 } \right)
+            \left( 4 + (k+1) \kappa_{\maxcol}(T) \right)
             \cdot 
             (k+1) 
-            \mu(\calT)
-            \beta_T
+            \kappa_{\maxcol}(\calT)
+            B_{T}
             \Big( 
@@
             \frac 1 2
-            %\left( \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \sqrt{ 1 + (k+1)^2 \mu(T)^2 } \right)
-            \left( 4 + (k+1) \mu(T) \right)
+            %\left( \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 } \right)
+            \left( 4 + (k+1) \kappa_{\maxcol}(T) \right)
             \cdot 
             (k+1) 
-            \mu(\calT)
+            \kappa_{\maxcol}(\calT)
             \Big( 
@@
         and it reduces the volume always by a factor of one half. 
-        We use the estimates in Lemma~\ref{lemma:affinetransform}.
+        We use the estimates in Lemma~\ref{lemma:measurerelationships}.
         When $K \in \calK \cup \calS'r$, then 
@@
         \vol_{n}(B_1(0)) 
-        \frac{ \diam(\Omega)^{n} }{|\Omega|} 
+        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
         \diam(\Omega)
@@
         2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \alpha(T)^{k-1}
+        \kappa_{2}(T)^{k-1}
         \Ceins{n}(T)
@@
     \end{align*}
-    \todo{Settle the notation}
+    \todo{The notation $U_m$ should be settled in the definition of shellings.}
 \end{theorem}

### 2024-09-16 main.tex
Update on Overleaf.

@@
 we define the \textit{geometric shape measure} $\kappa(T)$,
-the \textit{algebraic shape measure} $\kappa_{2}(T)$,
-and the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$ 
+the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$,
+and 
+the \textit{algebraic shape measure} $\kappa_{2}(T)$
 by 
@@
 \end{align}
-We call these the geometric, algebraic, and aspect shape measure, respectively, of the triangulation.
+We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
 

### 2024-09-16 main.tex
minor change

--- 2024-09-16 main.tex
@@
 The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
-\color{blue}
+%\color{blue}
 Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
@@
 In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
-\color{black}
+% \color{black}
 \\

### 2024-09-17 main.tex
updates in Section 4

@@
 Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{geometric shape measure} $\kappa(T)$,
-the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$,
+we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
+the \textit{aspect shape measure} $\aspectratio(T)$,
 and 
-the \textit{algebraic shape measure} $\kappa_{2}(T)$
+the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
 by 
 \begin{align}\label{math:shapemeasure}
-    \kappa(T)
+    \geometricshapemeasure(T)
     := 
@@
     \qquad 
-    \kappa_{\maxcol}(T)
+    \aspectratio(T)
     := 
@@
     \qquad 
-    \kappa_{2}(T)
+    \algebraicshapemeasure(T)
     := 
@@
 where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
+% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
 
@@
 \begin{align}\label{math:shapemeasure:triangulation}
-    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
+    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
     ,
     \quad 
-    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
+    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
     ,
     \quad 
-    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
+    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
     .
@@
         \Czwei{n} \cdot 
-        \kappa(T) 
+        \geometricshapemeasure(T) 
         \diam(T)^{-1}
@@
         \\
-        \kappa_{2}(T)
+        \algebraicshapemeasure(T)
         \leq 
@@
         % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
-        \kappa(T)
+        \geometricshapemeasure(T)
         ,
         \qquad 
-        %         \kappa(T)^{\frac 1 n}
+        %         \geometricshapemeasure(T)^{\frac 1 n}
         %         \leq 
-        \kappa_{\maxcol}(T)
-        \leq 
-        \kappa(T)
+        \aspectratio(T)
+        \leq 
+        \geometricshapemeasure(T)
         .
@@
 \begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
     In our convention, the reference simplex has unit shape measure.
-    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
+    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
+$\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
 
@@
     % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
+    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
     The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
@@
 
-We are interested in the maximal ratio of volumes between neighboring $n$-simplices: 
-\begin{align}\label{math:volumecomparisonmeasure}
-    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
-\end{align}
-We also want to compare the diameters of simplices that intersect. We define 
-\begin{align}\label{math:diametercomparison}
-    \theta(\calT) 
+We are interested in the maximal ratio of volumes between neighboring $n$-simplices, written $\volumeratio(\calT)$,
+and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
+\begin{align}
+    \volumeratio(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
+    \frac{ \vol(T) }{ \vol(T') }
+    ,
+    \qquad 
+    \diameterratio(\calT) 
     := 
@@
     \frac{ \diam(T) }{ \diam(T') }
+    .
 \end{align}
-Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
+Whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
 that preserves $F$. We define 
 \begin{align}\label{math:reflectionmeasure}
-    \xi(\calT) 
+    \reflectionestimate(\calT) 
     := 
     \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \| \Jacobian \Xi_{S,T} \|
+    \| \Jacobian \Xi_{T,T'} \|
 \end{align}
@@
 % \begin{align*}
-%     \kappa(T)
+%     \geometricshapemeasure(T)
 %     := 
@@
         % = 
-        \kappa(T_1)
+        \geometricshapemeasure(T_1)
         \diam(F)
@@
         % = 
-        \kappa(T_1) \kappa(T_2)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
+        \aspectratio(T_1) \aspectratio(T_2)
+        .
+    \end{align*}
+    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
     \begin{align*}
@@
         \leq 
-        \Cvier{n}
-        \kappa(T_2)^{-1} \kappa(T_1) 
-        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
-        .
-    \end{align*}
-    Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
+        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
+        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
+        .
+    \end{align*}
+%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
 \end{lemma}
@@
 \begin{proof}
-    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
-    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
-    \begin{align*}
-        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
-    \end{align*}
-    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
-    \begin{align*}
-        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
+    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
+%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
+%     \begin{align*}
+%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
+%     \end{align*}
+%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
+    Now, 
+    \begin{align*}
+%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
+        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
     \end{align*}
     The first estimate follows. 
+    As for the second estimate,
+    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
+    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
+    \begin{align*}
+        \frac{ \vol(T_1) }{ \vol(T_2) }
+        = 
+        \frac{ h_1 }{ h_2 }
+        \leq
+        \frac{ \diam(T_1) }{ h_2 }
+        \leq
+        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
+        \leq
+        \aspectratio(T_{1}) \aspectratio(T_{2})
+        .
+    \end{align*}
+\begin{comment}
     On the other hand, 
     \begin{align*}
-        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
-        \\
-        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
+        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
+%         \\
+%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
+        h_1 \leq \aspectratio(T_{1}) \diam(F),
+        \qquad 
+        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
         .
@@
     The second estimate follows. 
-    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
+    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
+    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
+    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
     \begin{align*}
         \| \Jacobian \Xi \|
-        &
-        \leq 
-        \Ceins{n}
-        \Czwei{n}
-        \kappa(T_2)
-        \diam(T_1)
-        \diam(T_2)^{-1}
-        \\&
-        \leq 
-        \Ceins{n}
-        \Czwei{n}
-        \kappa(T_2)
-        \kappa(T_1) 
-        \diam(F)
-        \diam(T_2)^{-1}
-        \leq 
-        \Ceins{n}
-        \Czwei{n}
-        \kappa(T_2)
-        \kappa(T_1) 
-        .
-    \end{align*}
-    All the desired results thus follow.
-
-%     \todo{Tighter estimate via geometry}
-%     Without loss of generality, $F$ lies in the plane of the second to last coordinates,
-%     so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-%     After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
-%     If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
-%     are all one with the possibe exception of the singular values of the matrix 
+        \leq 
+        \| \Jacobian\phi_{2} \| \cdot \| \Jacobian\phi_{1}^{-1} \|
+        \leq 
+        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
+        \leq 
+        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
+        \leq 
+        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
+        .
+    \end{align*}
 %     \begin{align*}
-%         A = 
-%         \begin{pmatrix}
-%             a_1/h & 0
-%             \\
-%             a_2/h & 1
-%         \end{pmatrix}
-%     \end{align*}
-%     Its singular values are 
-%     \begin{align*}
-%         \sigma_{\max}
-%         &= 
-%         \frac{1}{\sqrt 2}
-%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-%         \\&= 
-%         \frac{1}{\sqrt 2}
-%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-%             } }
-%         \\&= 
-%         \frac{1}{\sqrt 2}
-%         \sqrt{ 
-%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-%             }
-%         +
-%         \frac{1}{\sqrt 2}
-%         \sqrt{ 
-%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-%             }
-%         \\&= 
-%         \frac{1}{2}
-%         \sqrt{ 
-%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-%             }
-%         +
-%         \frac{1}{2}
-%         \sqrt{ 
-%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-%             }
-%         \\&= 
-%         \frac{1}{2}
-%         \sqrt{ 
-%             \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-%             }
-%         +
-%         \frac{1}{2}
-%         \sqrt{ 
-%             \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-%             }
-%         ,
-%         \\
-%         \sigma_{\min}
-%         &=
-%         \frac{1}{\sqrt 2}
-%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-%         \\&= 
-%         \frac{1}{2}
-%         \sqrt{ 
-%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-%             }
-%         -
-%         \frac{1}{2}
-%         \sqrt{ 
-%             1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-%             }
+%         \| \Jacobian \Xi \|
+%         &
+%         \leq 
+%         \Ceins{n}
+%         \Czwei{n}
+%         \geometricshapemeasure(T_2)
+%         \diam(T_1)
+%         \diam(T_2)^{-1}
+%         \\&
+%         \leq 
+%         \Ceins{n}
+%         \Czwei{n}
+%         \geometricshapemeasure(T_2)
+%         \geometricshapemeasure(T_1) 
+%         \diam(F)
+%         \diam(T_2)^{-1}
+%         \leq 
+%         \Ceins{n}
+%         \Czwei{n}
+%         \geometricshapemeasure(T_2)
+%         \geometricshapemeasure(T_1) 
 %         .
 %     \end{align*}
+    All the desired results thus follow.
+\end{comment}
+    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
+    Writing $h_0$ for the unit normal in direction $z_1$, we have 
+    \begin{align*}
+        \Xi(x) 
+        = 
+        x 
+        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
+        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
+        ,
+        \qquad 
+        x \in \bbR^{n}
+        .
+    \end{align*}
+    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
+    By the Xu-Zikanatov estimate,
+    \begin{align*}
+        \| \Jacobian \Xi \|
+        \leq 
+        \frac{ \diam(T_1) }{ \height(T_1) }
+        +
+        \frac{ \diam(T_2) }{ \height(T_1) }
+        \leq 
+        \left( 1 + \aspectratio(T_2) \right)
+        \aspectratio(T_1)
+        .
+    \end{align*}
+    The desired estimates are shown.
+\begin{comment}
+    \todo{Tighter estimate via geometry}
+    Matrix inverse lemma:
+    \begin{align*}
+        A ( A + (z_2-z_1) e_1^t )^{-1}
+        =
+        \Id
+        - 
+        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
+        (z_2-z_1) e_1^t \cdot A^{-1}
+        =
+        \Id
+        - 
+        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
+        (z_2-z_1) e_1^t \cdot A^{-1}
+        .
+    \end{align*}
+    Putting in a multiple of $\alpha z_1$, we find 
+    \begin{align*}
+        \alpha z_1
+        -
+        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
+        (z_2-z_1) 
+        .
+    \end{align*}
+
+    Without loss of generality, $F$ lies in the hyerplane plane of the second to last coordinates,
+    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
+    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
+    We can write 
+    \begin{align*}
+        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
+    \end{align*}
+    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
+    \begin{align*}
+        A = 
+        \begin{pmatrix}
+            b_1/a_1 & 0 & 0
+            \\
+            (b_2-a_2)/a_1 & 1 & 0
+            \\
+            b_3/a_1 & 0 & 1
+        \end{pmatrix}
+        =:
+        \begin{pmatrix}
+            c_1 & 0 & 0
+            \\
+            c_2 & 1 & 0
+            \\
+            c_3 & 0 & 1
+        \end{pmatrix}
+    \end{align*}
+    Its singular values are $1$ and 
+    \begin{align*}
+        \sigma_{\max}
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            +
+            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
+        }
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            +
+            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        }
+        =
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+        +
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        =
+        \frac{1}{2}
+        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
+        +
+        \frac{1}{2}
+        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
+        \leq 
+        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
+        .
+    \end{align*}
+    \begin{align*}
+        \sigma_{\max}
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            -
+            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
+        }
+        =
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+        -
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        .
+    \end{align*}
+
+    \begin{align*}
+        \sigma_{\max}
+        &= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            }
+        +
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        ,
+        \\
+        \sigma_{\min}
+        &=
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        -
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        .
+    \end{align*}
+    It follows that 
+    \begin{align*}
+        \det \Jacobian\Xi
+        &=
+        \frac{1}{4}
+        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+        +
+        \frac{1}{4}
+        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+        \\
+        \frac{1}{2} + \frac{1}{2} 
+        .
+    \end{align*}
+    Matrix determinant lemma:
+    \begin{align*}
+        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
+        =
+        \left( e_{n} A^{-1} z_2 \right) \det(A)
+        =
+        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
+        .
+    \end{align*}
+\end{comment}
 \end{proof}
@@
 \begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ but not $\theta(\calT)$. 
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
     As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
@@
 \begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
-    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
+    Let $\calT$ be a triangulation.
+    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
     Write $U := T_1 \cup T_2$. 
@@
         &
+%         \leq 
+%         2 C_{\PF,{\rm EFNT},p}
+%         \max\left( 
+%             \frac{ \vol(T_1) }{ \vol(T_2) }
+%             ,
+%             \frac{ \vol(T_2) }{ \vol(T_1) }
+%         \right)^{\frac 1 p}
+%         \\&\qquad\qquad 
+%         \cdot 
+%         \max\left( \diam(T_1), \diam(T_2) \right)
+%         \| \nabla u \|_{L^{p}(U)}
+%         \\&
         \leq 
         2 C_{\PF,{\rm EFNT},p}
-        \max\left( 
-            \frac{ \vol(T_1) }{ \vol(T_2) }
-            ,
-            \frac{ \vol(T_2) }{ \vol(T_1) }
-        \right)^{\frac 1 p}
-        \\&\qquad\qquad 
-        \cdot 
+        \volumeratio(\calT)^{\frac 1 p}
         \max\left( \diam(T_1), \diam(T_2) \right)
         \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \rho(\calT)^{\frac 1 p}
-        \max\left( \diam(T_1), \diam(T_2) \right)
-        \| \nabla u \|_{L^{p}(U)}
-        .
     \end{align*}
@@
 \begin{proof}
-    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
-    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
-    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
-    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
-    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
-    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
+    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
+    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
+    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
+    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
+    be affine transformations that map the $e_{i}$ to $v_{i}$ for $i = 0, \dots, n-1$ 
+    and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
+    Write $\hat U := \Delta_1 \cup \Delta_2$.
+    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
 
@@
     We observe 
-    \begin{align*}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-        &=
-        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-        +
-        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-        ,
-        \\
-        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-        &\leq 
-        |\det(\Jacobian \varphi_1^{-1})|
-        \cdot \| \Jacobian \varphi_1 \|^{p}
-        \cdot 
-        \| \nabla u \|_{L^{p}(T_1)}^{p}
-        ,
-        \\
-        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-        &\leq 
-        |\det(\Jacobian \varphi_2^{-1})|
-        \cdot \| \Jacobian \varphi_2 \|^{p}
-        \cdot 
-        \| \nabla u \|_{L^{p}(T_2)}^{p}
-%         \\&
-%         \leq 
+%     \begin{align*}
+%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
+%         &=
+%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
+%         +
+%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
+%         ,
+%         \\
+%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
+%         &\leq 
+%         |\det(\Jacobian \varphi_1^{-1})|
+%         \cdot \| \Jacobian \varphi_1 \|^{p}
+%         \cdot 
+%         \| \nabla u \|_{L^{p}(T_1)}^{p}
+%         ,
+%         \\
+%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
+%         &\leq 
+%         |\det(\Jacobian \varphi_2^{-1})|
+%         \cdot \| \Jacobian \varphi_2 \|^{p}
+%         \cdot 
+%         \| \nabla u \|_{L^{p}(T_2)}^{p}
+%         \\
+%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
+%         &\leq 
 %         \max\left( 
@@
 %         \| \nabla u \|_{L^{p}(U)}^{p}
-        .
-    \end{align*}
-    Hence 
+%         .
+%     \end{align*}
+%     Hence 
     \begin{align*}
@@
     \end{align*}
-    Notice that $\hat U$ has diameter $2$. 
+    Notice that $\hat U$ is convex and has diameter $2$. 
     There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
@@
     \end{align*}
+    The desired result now follows from noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\| \Jacobian \varphi_i \| \leq \Ceins{n} \diam(T_i)$
+    for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}.
+\begin{comment}
     % DONE: that abbreviation is to close to the Jacobian / total derivative 
@@
     This gives the desired result. 
+\end{comment}
 \end{proof}
@@
         &\leq 
-        \left( 1 + \rho(\calT)^{\frac q p} \right)^{\frac 1 q}
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
         \sum_{t=1}^{m}
-        \rho(\calT)^{\frac{m-t}{p}}
+        \volumeratio(\calT)^{\frac{m-t}{p}}
         C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{\PF,{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
+        % 2 C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
         \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
@@
         +
-        \rho(\calT)^{\frac{m-1}{p}}
+        \volumeratio(\calT)^{\frac{m-1}{p}}
         % C_{\PF,{\rm EFNT},p} \diam(T_0)
@@
 %     (m+1)^{p-1}
-%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
-%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
-%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
-%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
+%     % \sum_{t=1}^{m} \volumeratio(\calT)^{m-t} 
+%     % \sum_{t=0}^{m-1} \volumeratio(\calT)^{t} 
+%     \frac{\volumeratio(\calT)^{m}-1}{\volumeratio(\calT)-1}
+%     \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{p/q}
 %     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
@@
 %     (m+1)^{p-1}
-%     \rho(\calT)^{m-1}
+%     \volumeratio(\calT)^{m-1}
 %     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
@@
 %         &\leq 
-%         \rho(\calT)^{\frac m p}
+%         \volumeratio(\calT)^{\frac m p}
 %         C_{\PF,T_{0},p} 
@@
 %         \sum_{l=1}^{m} 
-%         \rho(\calT)^{\frac {m-l} p}
+%         \volumeratio(\calT)^{\frac {m-l} p}
 %         C_{\PF,T_{l},F_{l},p} 
@@
 %         \sum_{l=1}^{m} 
-%         \rho(\calT)^{\frac {m-l} p} \xi(\calT)
+%         \volumeratio(\calT)^{\frac {m-l} p} \reflectionestimate(\calT)
 %         C_{\PF,T_{l},F_{l},p} 
@@
         &\leq 
-        \rho(\calT)^{\frac m p}
+        \volumeratio(\calT)^{\frac m p}
         C_{\PF,T_{0},p} 
@@
         \sum_{l=1}^{m} 
-        \rho(\calT)^{\frac {m-l} p}
+        \volumeratio(\calT)^{\frac {m-l} p}
         C_{\PF,T_{l},F_{l},p} 
@@
             +
-            \rho(\calT)^{\frac {1} p}
-            \xi(\calT)
+            \volumeratio(\calT)^{\frac {1} p}
+            \reflectionestimate(\calT)
             \| \nabla u \|_{L^{p}(T_{l-1})} 
@@
 %         \sum_{l=1}^{m} 
-%         \rho(\calT)^{\frac{m-l}{p}}
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         \volumeratio(\calT)^{\frac{m-l}{p}}
+%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
 %         C_{\PF,T_{l},F_{l},p} 
@@
 %         +
-%         \rho(\calT)^{\frac m p}
+%         \volumeratio(\calT)^{\frac m p}
 %         C_{\PF,T_{0},p} 
@@
         \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
         \cdot 
@@
         \leq  
-        \rho(\calT)^{\frac 1 p} 
+        \volumeratio(\calT)^{\frac 1 p} 
         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
@@
         \leq  
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
         % C_{\PF,T_{m},F_{m},p} 
@@
 %         \leq  
-%         \rho(\calT)^{\frac 1 p} 
+%         \volumeratio(\calT)^{\frac 1 p} 
 %         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
 %         + 
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
 %         C_{\PF,T_{m},F_{m},p} 
@@
 %         \leq  
-%         \rho(\calT)^{\frac 1 p} 
+%         \volumeratio(\calT)^{\frac 1 p} 
 %         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
@@
 %         + 
-%         \rho(\calT)^{\frac 1 p} \xi(\calT)
+%         \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
 %         C_{\PF,T_{m},F_{m},p} 
@@
 % 
-We analyze the Bogovski\u{\i} potential operator with similar means. 
+We analyze the Bogovski\u{\i} potential operator by similar means. 
 Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
@@
     \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
 \end{align*}
+\todo{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
 In summary, after taking the average over $a \in \Omega$:
@@
     \begin{align*}
-        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
+        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}\Alt^{\ell-1}(\Omega)
         ,
@@
         \begin{align*}
-            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
-            \\
-            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
+            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
+            \\
+            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
         \end{align*}
@@
             \leq 
-            (n-k) \kappa_{\maxcol}(T)
+            (n-k) \aspectratio(T)
 %             = 
@@
             \sqrt{ 
-                1 + (n-k)^{2} \kappa_{\maxcol}(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
             } 
             + 
-            (n-k) \kappa_{\maxcol}(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
+            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
             .
@@
         \begin{align*}
-            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \kappa_{\maxcol}(T).
+            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \aspectratio(T).
         \end{align*}
@@
             \leq 
-            \frac 1 4 \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 }
+            \frac 1 4 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
             ,
@@
             \leq 
-            \frac 1 2 \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 }
+            \frac 1 2 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
             ,
@@
             \leq  
-            \kappa_{\maxcol}(T)
+            \aspectratio(T)
             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
@@
             (k+1)B_{T}
-            \theta(\calT)
+            \diameterratio(\calT)
             \frac{ \diam(T) }{ \| h_{T} \| }
@@
             (k+1)B_{T}
-            \theta(\calT)
-            \kappa_{\maxcol}(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \diameterratio(\calT)
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             ,
@@
             (k+1)
-            \theta(\calT)
+            \diameterratio(\calT)
             \sup_{ K \in \patch_{\calT}(S) }
@@
             (k+1)
-            \theta(\calT)
+            \diameterratio(\calT)
             \sup_{ K \in \patch_{\calT}(S) }
-            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             ,
@@
             (k+1)B_{T}
-            \kappa_{\maxcol}({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
             (k+1) 
-            \theta(\calT)
-            \kappa_{\maxcol}(\calT)
+            \diameterratio(\calT)
+            \aspectratio(\calT)
             B_{T}^{2}
@@
                 \left( 1 + B_{T} \right)
-                \kappa_{\maxcol}(\calT)
+                \aspectratio(\calT)
             \Big)            
@@
             (k+1) 
-            \theta(\calT)
-            \kappa_{\maxcol}(\calT)
+            \diameterratio(\calT)
+            \aspectratio(\calT)
             B_{T}
@@
             (k+1)^{n}
-            \theta(\calT)^{n}
+            \diameterratio(\calT)^{n}
             B_{T}^{n}
-            \kappa_{\maxcol}(\calT)^{n}
+            \aspectratio(\calT)^{n}
             ,
@@
             (k+1)^{n}
-            \theta(\calT)^{n}
-            \kappa_{\maxcol}(\calT)^{n}
+            \diameterratio(\calT)^{n}
+            \aspectratio(\calT)^{n}
             .
@@
             \frac 1 4
-            % \left( \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 } \right)
-            \left( 4 + (k+1) \kappa_{\maxcol}(T) \right)
+            % \left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
+            \left( 4 + (k+1) \aspectratio(T) \right)
             \cdot 
             (k+1) 
-            \kappa_{\maxcol}(\calT)
+            \aspectratio(\calT)
             B_{T}
@@
             \frac 1 2
-            %\left( \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 } \right)
-            \left( 4 + (k+1) \kappa_{\maxcol}(T) \right)
+            %\left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
+            \left( 4 + (k+1) \aspectratio(T) \right)
             \cdot 
             (k+1) 
-            \kappa_{\maxcol}(\calT)
+            \aspectratio(\calT)
             \Big( 
@@
              &\leq 
-             \Czwei{n} \kappa(K) \diam(K)
-             \leq 
-             2 \Czwei{n} \kappa(\calT) \diam(K)^{-1}
+             \Czwei{n} \geometricshapemeasure(K) \diam(K)
+             \leq 
+             2 \Czwei{n} \geometricshapemeasure(\calT) \diam(K)^{-1}
              \\
@@
              \\ 
-             \kappa( A_{K} )
+             \geometricshapemeasure( A_{K} )
              &\leq 
-             \Cdrei{n} \kappa(K) \leq 2 \Cdrei{n} \kappa(\calT)
+             \Cdrei{n} \geometricshapemeasure(K) \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
              .
@@
              &\leq 
-             \Czwei{n} \kappa({G}) \diam({G})
-             \leq 
-             4 \Czwei{n} \kappa(\calT) \diam(G)^{-1},
+             \Czwei{n} \geometricshapemeasure({G}) \diam({G})
+             \leq 
+             4 \Czwei{n} \geometricshapemeasure(\calT) \diam(G)^{-1},
              \\
@@
              \\ 
-             \kappa( A_{{G}} )
+             \geometricshapemeasure( A_{{G}} )
              &\leq 
-             \Cdrei{n} \kappa({G}) \leq 4 \Cdrei{n} \kappa(\calT)
-             .
-        \end{align*}
-        All the diameters above are comparable up to a factor of $\theta(\calT)$.
+             \Cdrei{n} \geometricshapemeasure({G}) \leq 4 \Cdrei{n} \geometricshapemeasure(\calT)
+             .
+        \end{align*}
+        All the diameters above are comparable up to a factor of $\diameterratio(\calT)$.
         In summary,
         \begin{gather*}
-            \| \Jacobian \Theta_{|K}      \| \leq 2 \Cdrei{n} \kappa(\calT)
+            \| \Jacobian \Theta_{|K}      \| \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
             ,
             \qquad 
-            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Cdrei{n} \kappa(\calT)
+            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
             ,
@@
             4 
-            \kappa(\calT) 
+            \geometricshapemeasure(\calT) 
             \Ceins{n} 
             \Czwei{n} 
-            \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
+            \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
             \left( 
@@
                 n
-                2 \Cdrei{n} \kappa(\calT)
+                2 \Cdrei{n} \geometricshapemeasure(\calT)
                 4 
-                \kappa(\calT) 
+                \geometricshapemeasure(\calT) 
                 \Ceins{n} 
                 \Czwei{n} 
-                \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
+                \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
             \right) 
-            2 \Cdrei{n} \kappa(\calT)
+            2 \Cdrei{n} \geometricshapemeasure(\calT)
             ,
@@
             2 
-            \kappa(\calT) 
+            \geometricshapemeasure(\calT) 
             \Ceins{n} 
             \Czwei{n} 
-            \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
+            \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
             \left( 
@@
                 n
-                2 \Cdrei{n} \kappa(\calT)
+                2 \Cdrei{n} \geometricshapemeasure(\calT)
                 2 
-                \kappa(\calT) 
+                \geometricshapemeasure(\calT) 
                 \Ceins{n} 
                 \Czwei{n} 
-                \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
+                \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
             \right) 
-            2 \Cdrei{n} \kappa(\calT)
+            2 \Cdrei{n} \geometricshapemeasure(\calT)
             .
@@
         2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \kappa_{2}(T)^{k-1}
+        \algebraicshapemeasure(T)^{k-1}
         \Ceins{n}(T)
@@
 
-MWL appreciates helpful remarks by Abdellatif Aitelhad.
+MWL appreciates helpful remarks by Abdellatif Aitelhad and by Martin Costabel.
 

### 2024-09-18 main.tex
Update on Overleaf.
clean up

@@
-\documentclass[10pt,letterpaper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 \input{header}
@@
 
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if it satisfies the following conditions: 
+A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} 
+if it satisfies the following conditions: 
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
@@
 We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
 \begin{align*}
@@
 \end{align*}
-We call a set \textit{trianguable} if it is the underlying set of some triangulation.
-
+We call any set \textit{trianguable} if it is the underlying set of some triangulation. 
+\\
+
+\begin{comment}
 \begin{remark}
@@
 \end{remark}
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
-More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
-We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
-The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
+\end{comment}
+
+Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$,
+and $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
+We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
+
+Whenever $\calT$ is a simplicial complex, 
+the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
+% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
 In practice, we not always distinguish between points and singleton simplices.
-Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
+% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
+Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
 % \begin{remark}
@@
 }
+% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
+% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\todo{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
 
@@
 \begin{gather*}
-    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
+    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
+    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
     \qquad 
@@
 \end{gather*}
-We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial observation is the following.
+We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+A crucial structural observation is the following.~\footnote{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}
 
@@
  Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \emptyset$ or there exists $S'' \in \calT$
- such that $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S'')$ with $S, S' \subseteq S''$.
+ Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
+ such that 
+ \begin{align*}
+    \patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S''),
+    \qquad 
+    \Vertices(S) \cup \Vertices(S') = \Vertices(S'').
+ \end{align*}
 \end{lemma}
@@
 These indicate of the regularity of simplex shapes. 
+All these quantities have in common that they can be computed from purely local information. 
 Most of such \emph{shape measures} in the literature are based on geometric features, 
 but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
-All these quantities have in common that they can be computed from purely local information. 
 While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
@@
 We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$.
+Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
+where the height of a vertex is defined as the distance to the affine span of its opposing face.
 
@@
     but individual convex domains may allow for better constants.
-    We refer to \cite{matculevich2016explicit} for an overview;
-    for example, triangles allow the reduction of the constant by 20\%.
+    We refer to \cite{matculevich2016explicit} for an overview of some improved inequalities, such as for triangles.
+    % for example, triangles allow the reduction of the constant by 20\%.
 \end{remark}
 
+Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
+a \emph{spanning tree} is an enumeration of the all $n$-dimensional simplices $T_{0}, \dots, T_{M}$
+where for each $1 \leq m \leq M$ we have fixed $0 \leq j(m) \leq m-1$ such that 
+$T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
+We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
+
 % DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
@@
 In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
-As a preparatory step, given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
-This defines a scalar potential.
-This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
-after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
+We achieve by explicitly constructing scalar potentials of gradients.
+We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
+We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells.
+we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
 The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
@@
 
-We have already seen a survey of Poincar\'e inequalities over convex domains. 
-Slightly more generally, we are interested in such inequalities over face patches within simplicial triangulations. 
-We state a geometric auxiliary lemma and an estimate of Poincar\'e--Friedrichs constants over face patches 
-that captures the correct asymptotic behavior as $p$ grows to infinity.
+We construct scalar potentials over larger and larger intermediate subdomains. 
+Two different variations of that idea are analyzed;
+while the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
+On the one hand, we can cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
+Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece.
+This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result.
+
+On the other hand, we assess an alternative route towards constructing scalar gradient potentials over triangulated domains. 
+While the underlying idea remains the same, the construction of the potential is slightly different. 
+we can extend the potential on each intermediate domain to another simplex by solving a local auxiliary problem on that simplex subject to partial boundary conditions.
+This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
+As an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex} computes an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed on a single face of the boundary.
+
+We emphasize that the second approach to constructing potentials and bounding Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+Our estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
 
@@
     \end{align*}
-    The desired result now follows from noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\| \Jacobian \varphi_i \| \leq \Ceins{n} \diam(T_i)$
-    for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}.
+    Noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\| \Jacobian \varphi_i \| \leq \Ceins{n} \diam(T_i)$
+    for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}, we conclude the desired result.
 \begin{comment}
@@
  For each $F \in \calT$ of dimension $n-1$, 
- we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that 
- \begin{align*}
-    \| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla u_F \|_{L^{p}(U_F)},
+ we let $w_F \in W^{1,p}(U_F)$ such that $\nabla w_F = \nabla u$ over $U_F$ and such that 
+ \begin{align*}
+    \| w_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla w_F \|_{L^{p}(U_F)},
  \end{align*}
@@
  In particular, $c_{0} := u - w_0$ is a constant function.
+
  Now, let $T \in \calT$ be any $n$-simplex. 
  By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
- For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
- We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
+ We let $\Omega_m := \cup_{j=0}^{m} T_m$ for any $0 \leq m \leq M$,
+ which is a triangulated $n$-dimensional submanifold with boundary.
+ For any $1 \leq m \leq M$ we write $F_m := T_m \cap T_{m-1}$,
+ which is a face of dimension $n-1$.
 
@@
 
- We use a recursive argument. 
- Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
+ We construct the potential recursively. 
+ We have seen that $c_{0} = w_{0} - u_{|\Omega_{0}}$ is a constant. 
+ Assume that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
  such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
- This is already satisfied for $m=1$.
+ % Note that this assumption is already satisfied when $m=1$.
  Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
  By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
- Since $\nabla u_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}}$,
- there exists a constant $c_{m} := w_{m-1|T_{{m-1}}} - u_{F_{m}|T_{{m-1}}}$.
- We define $w'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $\nabla w'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ 
+ Since $$\nabla w_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}},$$
+ there exists a constant $$c_{m} := w_{m-1|T_{{m-1}}} - w_{F_{m}|T_{{m-1}}}.$$
+ We define $w'_{F_m} := w_{F_m} + c_{m} \in W^{1,p}(U_F)$.
+ By construction, $$\nabla w'_{F_m} = \nabla w_{F_m} = \nabla u_{|U_{F_m}}$$ 
  and 
  $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
- But that already implies $w'_{F_m} = u_{|F_m} - c_{0}$. 
- We define a measurable function $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$.
- We have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
+ But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
+ Letting $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
+ we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
 
@@
     \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
+    \| w_{F_m} \|_{L^{p}(T_m)}
     +
@@
     \leq 
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
+    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
     .
@@
     \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
+    \| w_{F_m} \|_{L^{p}(T_m)}
     \\&\qquad 
@@
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
+    \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
     +
@@
  \end{align*}
- We sum the two integrals of $u_{F_m}$. 
+ We sum the two integrals of $w_{F_m}$. 
  % 
@@
     \right)
-    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    \| w_{F_m} \|_{L^{1}(U_{F_m})}
     +
@@
     2
-    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+    \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
     +
@@
  % 1/q = 1 - 1/p = (p-1)/p 
- When $1 < p < \infty$, letting $q := p/(p-1) \in [1,\infty]$ be the complementary exponent, we observe 
+ When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
  \begin{align*}
@@
     \left( 
-        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
-        +
-        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
+        \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
+        +
+        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
     \right)^{\frac 1 p}
@@
     \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
+    \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
     +
@@
     \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
-    \| u_{F_t} \|_{L^{p}(U_{F_t})}
+    \| w_{F_t} \|_{L^{p}(U_{F_t})}
     \\&\quad \quad \quad 
@@
     \right)
-    \| u_{T_0}\|_{L^{p}(T_{0})}
+    \| w_{T_0}\|_{L^{p}(T_{0})}
     .
@@
 %     \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{p/q}
-%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
+%     \| w_{F_t} \|_{L^{p}(U_{F_t})}^{p}
 %     \\&\quad \quad \quad 
@@
 %     \volumeratio(\calT)^{m-1}
-%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
+%     \| w_{T_0}\|_{L^{p}(T_{0})}^{p}
 %     .
@@
 
-We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains. 
-While the underlying idea remains the same, the construction of the potential is slightly different. 
-As an auxiliary result with independent relevance, we compute an upper bound for the Poincar\'e--Friedrichs inequality 
-when homogeneous boundary conditions are imposed on a single face of the boundary. 
-We present this result with two different techniques. 
-While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains. 
-% Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.
-
 \begin{lemma}\label{lemma:mixedbconsimplex}
@@
     where $C_{\PF,T,F,p} > 0$ is a constant such that 
-    \begin{align*}
-        C_{\PF,T,F,p}
-        &\leq 
-        C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
-        \\
-        %\quad 
-        C_{\PF,T,F,p}
-        &\leq
-        \frac{1}{\sqrt[p]{p}}
-        \diam(T)
-        .
-    \end{align*}
+    $C_{\PF,T,F,p} \leq \frac{1}{\sqrt[p]{p}} \diam(T)$.
+%     \begin{align*}
+%         C_{\PF,T,F,p}
+%         &\leq 
+%         C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
+%         \\
+%         C_{\PF,T,F,p}
+%         &\leq
+%         \frac{1}{\sqrt[p]{p}}
+%         \diam(T)
+%         .
+%     \end{align*}
 \end{lemma}
 \begin{proof}
+\begin{comment}
     There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
@@
     Recall that $u = w - \gamma$. The first inequality follows. 
-
-    The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Let assume that $1 \leq p < \infty$. 
-    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
+\end{comment}
+    % The second inequality follows from Rademacher's theorem when $p = \infty$.
+    Since the inequality follows from Rademacher's theorem when $p = \infty$,
+    we assume $1 \leq p < \infty$. 
+    Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
     Without loss of generality, 
@@
     and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg \in \bfL^{\infty}(T)$ for the trivial extension of $\nabla u$ outside of $T$.
+    We write $\bfg \in \bfL^{\infty}(\bbR^{n})$ for the trivial extension of $\nabla u$ outside of $T$.
     %With the fundamental theorem of calculus and H\"older's inequality: 
-    Now:
-    \begin{align*}
-        \int_{\Omega} |u(x)|^{p} \diff x \;dx
+    We verify
+    \begin{align*}
+        \int_{T} |u(x)|^{p} \diff x \;dx
         &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
+        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
         \\&
         \leq
-        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
+        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
         \\&
         \leq
-        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
+        \int_{0}^{\diam(T)} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
         \\&
         \leq
-        \int_{0}^{D} x_{1}^{p-1} \;dx_1 
+        \int_{0}^{\diam(T)} x_{1}^{p-1} \;dx_1 
         \cdot 
-        \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
-        \leq
-        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} \,dx
+        \int_{T} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
+        \leq
+        \frac{\diam(T)^{p}}{p} \int_{T} \left| \nabla u( x ) \right|^{p} \,dx
         %
@@
     \end{align*}
-    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
+    That $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
+    for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
 
     Very briefly verify that density argument: 
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    There exists $\varphi : \Delta^{n} \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
     We let $\hat u := u \circ \varphi$.
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\Delta^{n}$.
     We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
     Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
-    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ is the desired sequence that approximates $u$. 
+    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$. 
 \end{proof}
 
-The following potential construction and upper bound for the Poincar\'e--Friedrichs constant 
-serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+% \begin{remark}
+%     While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains.  
+% \end{remark}
 

### 2024-09-18 main.tex
some updates

@@
 We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial structural observation is the following.~\footnote{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}
+A crucial structural observation is the following.~\footnote{\todo{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}}
 
@@
 \end{remark}
-
-Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
-a \emph{spanning tree} is an enumeration of the all $n$-dimensional simplices $T_{0}, \dots, T_{M}$
-where for each $1 \leq m \leq M$ we have fixed $0 \leq j(m) \leq m-1$ such that 
-$T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
-We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
 
@@
     \end{align*}
+    \todo{Rewrite this result.}
+    When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}
+        &\leq 
+        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
+        \left( 
+            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
+            +
+            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
+        \right)^{\frac 1 p}
+        \\&\qquad 
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
+        \\&\leq 
+        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
+        \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
+        .
+    \end{align*}
 \end{theorem}
@@
  But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
- Letting $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
+ Defining $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
  we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
@@
  \begin{gather*}
+    \| w_{m} \|_{L^{p}(T_m)}
+    =
     \| w'_{F_m} \|_{L^{p}(T_m)}
@@
 
+We discuss the Sobolev spaces of vector calculus and exterior calculus 
+with particular emphasis on their transformation behavior. 
 We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
@@
 
-We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
 Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
@@
 In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-$W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
+% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
+The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
 \begin{gather*}
-    W^{p}(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
     .
@@
 The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
+and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
 \begin{gather*}
@@
 Bounds on the Lebesgue norms will follow from a more general result below. 
-
+% 
 We use the commutativity relations 
@@
     This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
+    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
+    In some literature conventions, the Piola transform is in the direction of the original mapping. 
 \end{remark}
@@
 Having discussed vector analysis, we review exterior calculus. 
-We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}. 
+We begin with exterior algebra. 
+%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}. 
 Let $V$ be a real vector space. 
@@
         \end{align*}
-        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
-        \begin{align*}
-            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
-            \\
-            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
-        \end{align*}
+        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
+        % \begin{align*}
+        %     \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
+        %     \\
+        %     \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
+        % \end{align*}
         By construction, the mapping preserves volumes:

### 2024-09-19 main.tex
add paragraph on spanning trees

--- 2024-09-18 main.tex
@@
 
-Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
-a \emph{spanning tree} is an enumeration of the all $n$-dimensional simplices $T_{0}, \dots, T_{M}$
-where for each $1 \leq m \leq M$ we have fixed $0 \leq j(m) \leq m-1$ such that 
-$T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
-We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
-
 % DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
@@
 This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result.
+
+For the agenda of this section, the following combinatorial notion of triangulations will be helpful. 
+Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
+a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
+where for each index $1 \leq m \leq M$ we have fixed index $0 \leq j(m) \leq m-1$ 
+such that $T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
+We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
 

### 2024-09-19 main.tex
minor changes

--- 2024-09-18 main.tex
@@
 
-This section is devoted to geometric operations that are crucially important for our main result. 
-Suppose that we have a shellable simplicial complex. 
-Every time we add a simplex according to the shelling sequence, 
-we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
-We will need a homeomorphism going from the new simplex onto its complement within the newly completed star.
-This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
-We are particularly interested in the norms of its Jacobian.
-We inerpret this as a nonlinear reflection. It will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms.
-
-In addition to that, this endeavor will produce another geometric tool 
-that enables an additional estimate Poincar\'e--Friedrichs constants:
-we construct a bi-Lipschitz deformation which maps the entire star 
-into the complement of the newly completed star. 
-Again, we give explicit estimates of the Jacobian.
-\\
+This section is devoted to geometric operations that are crucial for our main result. 
+Consider the situation where we have an $n$-dimensional local star around some simplex $S$ and some $n$-dimensional simplex $T$ within that local star.
+We will need a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$.
+This homeomorphism is required to preserve the interface and we interpret it as a nonlinear reflection. 
+We ensure that the homeomorphism is bi-Lipschitz and we are particularly interested in the norms of its Jacobian.
+This nonlinear reflection will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms. 
+Additionally, this endeavor produces another geometric tool:
+we construct a bi-Lipschitz deformation which contracts the entire star into the complement of the newly completed star.
 
@@
     Obviously, $F \subset A \cap T$. 
-    Let us now suppose that $x \in A \cap T$.
-    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
+    Suppose now that $x \in A \cap T$.
+    There exist $\lambda_1,\dots,\lambda_{n-1} \in \bbR$ such that 
     \begin{align*}
@@
     \end{align*}
-    We know that this is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
+    This is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
     Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive.
@@
     and thus their sum must be negative, which is a contradiction. 
-    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are zero,
-    which implies $x \in F$.
-    The desired statement follows.         
+    Hence $\lambda_{k+1} = \dots = \lambda_{n-1} = 0$, implying $x \in F$.
 \end{proof}
@@
 
-Next, we observe that stars around subsimplices can represented by vertex stars after a local subdivision of the mesh.
+Next, we observe local stars can be subdivided to vertex stars.
 The shape regularity is controlled in that process.
@@
 
-We know construct the main result of this section, namely the desired bi-Lipschitz homeomorphism. 
-It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
-The construction is completed in several steps,
-and the Lipschitz estimate reflects the shape regularity.
+We now provide the bi-Lipschitz nonlinear reflection across the interface between the selected simplex and the remainder of the local star
+as well as the bi-Lipschitz contraction from the local star onto the complement of the selected simplex.
 
@@
 
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
     Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.

### 2024-09-27 revision/main.tex
include MV revision in a subfolder

--- 2024-09-19 main.tex
@@
-\documentclass[10pt,a4paper]{article}
+\documentclass[10pt,letterpaper]{article}
 \usepackage[utf8]{inputenc}
-% \usepackage{fullpage}
+\usepackage{fullpage}
 \input{header}
@@
 
-% Title, authors, and affiliations
-% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
-% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
-
-\title{Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations}
+\usepackage{bm} % preferred version of bold symbols
+\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
+\usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
+\usepackage[textsize=tiny,color=blue!50!white]{todonotes}
+\setlength{\marginparwidth}{2cm}
+
+\newcommand\cye[1]{%
+  \protect\leavevmode
+  \begingroup
+    \color{red!35!yellow}%
+    #1%
+  \endgroup
+}
+
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations}
 \author{
@@
     Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
+    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \&
+CERMICS, Ecole des Ponts, 77455 Marne-la-Vallée, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
 }
@@
 
-\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
 \newcommand{\notice}[1]{\textcolor{red}{REMARK: #1}}
 
+\newcommand{\disk}{\cye{ball}}
+
 \begin{document}
@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations.
-This class of triangulations includes local stars in dimension two and three.
-    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
-    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
+    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations.
+This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
+    \cye{We derive} computable bounds \cye{on} the operator norms of our potentials that only depend on the geometry.
+We thus obtain computable upper bounds for \cye{constants in} Poincar\'e--Friedrichs inequalities \cye{as well as} computable lower bounds for the eigenvalues of several vector Laplacians.
+    As a result with independent standing, we \cye{also} establish Poincar\'e--Friedrichs inequalities \cye{with computable constants} for the $L^{p}$ de~Rham complex over convex bounded domains. 
+    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
+    \cye{Computational examples illustrate the theoretical findings.}
+\end{abstract}
+
+\tableofcontents
+
+\todo[inline]{MV: Added table of contents: for us, to see the structure of and the main terminology used in the paper}
+
+\section{Introduction}\label{section:intro}
+
+\todo[inline]{MV: Added subsections and reorganized.}
+
+Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
+The operator norms of the\cye{se} potentials are upper bounds for the Poincar\'e--Friedrichs constants, which quantify the fundamental stability features of a variety of partial differential equations.
+In numerical methods, estimates for the Poincar\'e--Friedrichs constant\cye{s} enter the stability and convergence theory and spectral bounds for \cye{stiffness} matrices.
+\cye{Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians}.
+However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or \cye{more generally} the exterior derivative are \cye{largely unavailable}.
+
+\cye{Our main purpose here is to fill this gap.
+In the gradient case, we can go over with so-called face-connected triangulations.
+However, to proceed} in the \cye{general exterior derivative case, we are brought to} so-called shellable triangulations.
+Even though only contractible domains can ever admit a shellable triangulation, 
+having computable upper bounds for such domains is an important stepping stone towards more general cases.
+\cye{Still, we cover most practical nonconvex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
+\cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}
+
+\cye{Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be an connected open set.} \todo[inline]{MV: Here not necessarily bounded?
+But then we sometimes need $\Omega \subseteq \bbR^{n}$ of finite measure \ldots I would be fine with $\Omega$ bounded all the time.} Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
+Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector\cye{-valued} fields.
+
+\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{section:intro_grad}
+
+Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
+\begin{align} \label{equation:W1p}
+    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
+\end{align}
+For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\cye{\grad}}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\cye{\grad}}( \bff ) = \bff$.
+Then,
 %
-    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
-    %     The main application that we envision are computable estimates over finite element patches. 
+\begin{align*}
+    \Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
+\end{align*}
+is the {\em potential operator}. A particular example of our interest is
 %
-    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
-    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
-\end{abstract}
-
-\section{Introduction}\label{section:intro}
-
-% DONE {Reformulate the first paragraph. } % 
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations.
-% which serve a variety of purposes:
-% these constants quantify the fundamental stability properties of partial differential equations, imply lower bounds for the spectra of vector and Hodge Laplacians, and they . 
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-% We study potential operators in the special class of domains with shellable triangulations,
-% which include local stars in 2D and 3D. 
-% We bound the operator norms of our operators in terms of the shape regularity of the triangulation.
-
-% We contribute to the construction of potential operators in vector analysis and exterior calculus over triangulated domains. 
-% We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
-% The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
-% In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
-
-% DONE : MV : remove 'For example' 
-We illustrate the subject of our discussion with the curl operator. 
-% One example application concerns the curl operator. 
-If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
-Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
-    \leq 
-    C_{\curl}
-    \| \bff \|_{L^{2}(\Omega)}
-    .
-\end{align*}
-The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
-%\color{blue}
-Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
-% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
-% \color{black}
-\\
-
-Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-The majority of estimates in the literature address only gradient potentials. 
-% We accomplish our results for a special class of triangulations, so-called shellable triangulations.
-% We accomplish this task in 
-We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards the more general case. 
-For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
-Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
-\\
-
-Before we outline the main results of this exposition in more detail, 
-we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-
-% DONE: MV : Be more didactical: write following as the existence of a potential. 
-Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
-for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:intro:inequalitypf:gradient} 
+\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
+    \Phi_{\cye{\grad}}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+\end{align}
+%
+Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\cye{\grad}}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
+
+\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\cye{\grad}}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
+\begin{align}\label{math:pot_grad_norm}
+    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} }.
+\end{align}\end{subequations}}
+This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
+\begin{subequations}\label{math:PF_gradient}\begin{align} \label{math:PF_gradient_1}
     \| u \|_{L^{p}(\Omega)}
@@
     C_{\grad,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
+    \| \bff \|_{\cye{\bfL}^{p}(\Omega)}.
 \end{align}
-We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The different scalar potentials only differ by a constant. 
-Therefore, %when the domain is connected, then 
-this inequality is equivalent to the following statement: 
-\begin{align}\label{math:intro:poincarefriedrichs:grad}
-    \min\limits_{c\in\bbR}
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
+Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
+\begin{align} \label{math:PF_gradient_2}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p}
+    \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)},
     \quad 
     \forall 
-    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
-    .\tag{PF} 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}\end{subequations}
+We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
+\begin{align} \label{math:pot_PF_grad}
+    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
+    \| u \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\grad,\Omega,p}
+    \| \bff \|_{\cye{\bfL}^{p}(\Omega)}.
 \end{align}
-% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
-% \begin{align}\label{math:intro:poincarefriedrichs:grad}
-%     \min\limits_{c\in\bbR}
-%     \| u - c \|_{L^{p}(\Omega)}
-%     \leq 
-%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-%     \quad 
-%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
-%     .\tag{PF} 
-% \end{align}
-Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
-The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
-\begin{align*}
-    \Phi_{\grad}( \bff ) 
+for all $\bff \in \nabla W^{1,p}(\Omega)$.}
+
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
+Most research on optimal constants has addressed the case of convex domains.
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+When the domain is not convex but star-shaped with respect to a ball,
+then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} \todo{MV: OK???} inequality~\cite{brenner2008mathematical,ern2021finite}. 
+Poincar\'e\cye{--Friedrichs} \todo{MV: OK???} inequalities \cye{actually} hold over \cye{merely}\todo{MV: OK???} star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}.
+\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
+
+\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
+
+Consider the vector-valued spaces
+\begin{subequations}\label{equation:W_curl_div_p} \begin{align}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
+    .
+\end{align}\end{subequations}
+The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
+This only requires that certain sums of distributional partial derivatives are integrable, 
+and hence these spaces are not classical Sobolev spaces of vector\cye{-valued} fields.
+
+\cye{Let a vector-valued field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
+We are interested in constants for inequalities such as 
+\begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
+    \min\limits_{ \substack{ \cye{\bfu} \in \bfW^{p}(\curl,\Omega) \\ \curl \cye{\bfu} = \bff } } 
+    \| \cye{\bfu} \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\curl,\Omega,p}
+    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
+    ,
+    \\
+    \min\limits_{ \substack{ \cye{\bfu} \in \bfW^{p}(\divergence,\Omega) \\ \divergence \cye{\bfu} = f } } 
+    \| \cye{\bfu} \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\divergence,\Omega,p}
+    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
+    ,
+\end{align}\end{subequations}
+and how these constants can be estimated by the operator norms of {\em linear} potential operators 
+\begin{align*}
+    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \\
+    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
+\end{align*}
+The fundamental difference \cye{with respect to Section~\ref{section:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
+In Section~\ref{section:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
+It is thus trivially complemented for all $p$, with a canonical choice of projection.
+By contrast, in the Banach space case \cye{$p \neq 2$}, it is not immediately evident that the kernels of the curl and divergence operators are complemented\cye{,} and a canonical projection only exists here in the Hilbert setting $p=2$.
+\cye{Actually,} the existence of a bounded linear potential operator is \cye{here} a non-trivial fact even in the Hilbert space case \cye{$p = 2$}.
+
+\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
+Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
+\begin{align}
+    \label{math:Weber}
+    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
+\end{align}
+for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
+Yet another writing is 
+\label{math:PF_orth} \begin{align}
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
+\end{align}
+for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
+We refer to Friedrichs~\cite[equation~(5)]{Fried_diff_forms_55}, Gaffney~\cite[equation~(2)]{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
+However, that easy observation seems restricted to $p=2$.
+
+Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
+\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broder setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
+
+\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
+
+Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
+This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
+\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $w \in W^{p}\Alt^{k}(\Omega)$, there exists $u \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
+\begin{align} \label{math:PF_DF} 
+    \| u \|_{L^{p}(\Omega} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
+\end{align} 
+}\todo[inline]{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparsion with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
+
+In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
+\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
+
+Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
+\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
+Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+
+\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
+
+\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
+\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
+Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
+\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever postprocessing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
+\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
+
+\subsection{\cye{Objectives and methodology}}
+
+The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
+\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
+
+\subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
+
+Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
+For scalar-valued functions in the context of Section~\ref{section:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
+%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
+Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
+
+In the gradient case of Section~\ref{section:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
+
+For vector-valued fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
+We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
+The basic inductive strategy remains the same.
+We start by constructing, say, a curl potential, over a single simplex.
+Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
+However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
+Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
+With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
+
+\subsubsection{\cye{Analytical constants over convex domains}}
+
+\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (nonconvex and non-star-shaped) triangulated domains.
+Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
+In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
+The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
+
+\subsubsection{\cye{Domains star-shaped with respect to a ball}}
+
+\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
+This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
+Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
+This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this \cye{in particular} occurs when the domain has sharp reentrant corners.
+Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
+which contain local finite element patches \cye{that} are not star-shaped with respect to any ball.
+
+\subsubsection{\cye{Potentials subject to partial boundary conditions}}
+
+\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
+\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalit\cye{ies} subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
+We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
+
+\subsection{\cye{Main results}}
+
+\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be nonconvex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
+Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.} \todo{MV: remark from after Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} moved here.}
+The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
+\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
+
+\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+They treat triangulated domains that can be nonconvex and non-star-shaped but where the triangulation is shellable.
+As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
+The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei}.}
+
+\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
+\cye{This is summarized in Theorem~\ref{theorem:PF_EC}.} \todo{MV: The discussion from before Theorem~\ref{theorem:PF_EC} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
+
+\subsection{\cye{Organization of this manuscript}}
+
+The remainder of this manuscript is structured as follows.
+We review Poincar\'e\cye{--Friedrichs} constants for the gradient over convex domains in \cye{Section}~\ref{section:poincare}.
+\cye{We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.}
+We review basic notions of triangulations in Section~\ref{section:triangulations}.
+We develop computable upper bounds for \cye{the} Poincar\'e--Friedrichs constants for the gradient over \cye{face-connected} triangulated domains in Section~\ref{section:gradient}.
+We \cye{pass to} the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
+\cye{Our} regularized potential operators over convex sets are \cye{then introduced} in Section~\ref{section:potentialoperator}\cye{, giving rise to to computable Poincar\'e\cye{--Friedrichs} constants as their operator norms}.
+We \cye{subsequently pass to a} review of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
+We construct an important geometric reflection operator in Section~\ref{section:extension}
+and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+We present numerical examples in Section~\ref{section:numericalexamples} \cye{and conclude by some outlook in Section~\ref{section:outlook}}.
+
+\section{\cye{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and \cye{analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
+
+\todo[inline]{MV: Discussion reorganized.}
+
+\cye{In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.} \cye{We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.} We \cye{in particular} take the opportunity to discuss convex domains as a special case.
+This survey serves as a building block in constructing computable constants over triangulated domains \cye{in a combinatorial way below} but we believe it \cye{is also} of independent interest.
+
+\subsection{Nonlinear and linear potentials}
+
+In the Banach setting $p \neq 2$, finding a norm-minimizing potential \cye{such as $\Phi_{\cye{\grad}}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$} is a nonlinear operation.
+Its existence \cye{may actually} not be guaranteed unless $1 < p < \infty$.
+\cye{However}, any \textit{linear} potential operator $\overline\Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi_{\cye{\grad}}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ \cye{has the} operator norm that \cye{gives} the \cye{upper} bound 
+\begin{align}\label{math:PF_P}
+    \cye{C_{\grad,\Omega,p} = } \max\limits_{ u \in \cye{\cancel{\nabla}} W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in \cye{\cancel{\nabla}} W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
+    .
+\end{align}
+\cye{This explains our interest in the construction of} {\em linear potential operators}.
+
+\subsection{Poincar\'e--Friedrichs and Poincar\'e inequalities}
+
+\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\cye{\grad}}( \bff ) = \bff$ determines $\overline \Phi_{\cye{\grad}}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
+\begin{align*}
+    \overline\Phi_{\cye{\grad}}( \nabla u ) \cye{:}= u - u_{\Omega},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_\Omega$ denotes the average of $u$ \cye{over $\Omega$}, that is,
+\begin{align*}
+    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
+\end{align*}
+\cye{This potential operator can also implicitly be defined by}
+\begin{align*}
+    \overline \Phi_{\grad}( \bff ) 
     := 
-    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
+    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\cye{\bfL}^{p}(\Omega)},
     \quad 
@@
 \end{align*} 
-Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
-\begin{align}\label{math:intro:poincare:grad}
+Its operator norm is the \cye{best} constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
+\begin{align}\label{math:P_gradient}
     \| u - u_{\Omega} \|_{L^{p}(\Omega)}
     \leq 
-    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
+    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)},
     \quad 
@@
     u \in W^{1,p}(\Omega)
-    , \tag{P} % DONE: tag Poincar\'e inequality 
+    . 
 \end{align}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
-
-Most research on optimal constants has addressed the case of convex domains. 
-% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence
-
-The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-We use the vector field spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align*}
-Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
-\begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
-    \qquad 
-    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
-\end{align*}
-The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
-We are interested in constants for inequalities such as 
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)}
-    ,
-    \\%\qquad 
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
-and how these constants can be estimated by the operator norms of linear potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-
-Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-% even if the domain is convex, 
-This sharply contrasts to the study of the gradient operator. 
+\cye{Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient},} 
 %
-% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
-We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
-% who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
-who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
-thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
-By duality, that implies lower bounds for the case of full boundary conditions.
-% They also provide sequences of inequalities, such as the following in 3D smoothly bounded convex domains:
-% \begin{align}\label{math:intro:guerinisavo}
-%     C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
-% \end{align}
-% We emphasize that \cite{guerini2004eigenvalue} only addresses smoothly bounded domains, but the extension to convex domains is a technicality.
-
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
-follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-\\
-% DONE: cite Guzman and Salgado in a reasonable manner
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
-which contain finite element patches are not star-shaped with respect to any ball.
-
-Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
-However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
-We review some of the main outcomes. 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-% 
-The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted.
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here.
-The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
-Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the interfacing intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed to ensure continuity across that interface. 
-% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
-
-While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
-we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
-We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
-which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
-We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
-
-% General outline 
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-\\
-
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable. 
-\\
-
-% This construction of potentials requires triangulations with special conditions: 
-% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Such triangulations are called \textit{shellable}.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
-% In particular, local stars in 2D and 3D triangulations are shellable. 
-% \\
-
-% auxiliary problems 
-% We construct gradient potentials locally over convex domains or face patches. 
-Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-% DONT: cite VVVV
-While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
-the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
-
-% DONE: cite VVVV
-In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-% These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex smoothly bounded domains.
-
-However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy.
-% DONE: Theo : But -> However
-We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
-In comparison to their exposition, our variants of the regularized potential operators are simplified:
-we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
-however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
-We consider the latter outcome to be of independent interest. 
-% DONE \todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-% the curl of a vector field over a tetrahedron with vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential. % DONE : Theo : unclear sentence 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
-\todo{What is the best place for this paragraph?}
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-% DONE: Theo : paragraph feels misplaced 
-\\
-
-% Future work % DONE: Theo : parts already mentioned ??? 
-% Computable reliable estimates are important: 
-% they quantify the fundamental stability properties of partial differential equations in vector analysis,
-% such as the Hodge Laplace equation. 
-There are several avenues for further research going from here. 
-The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
-There are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
-In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
-Better transformations or more careful estimates are likely possible, as are completely different approaches.
-For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
-
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
-These topics remain for future research.
-
-Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
-In particular, domains with shellable triangulations are contractible.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-\\
-
-The remainder of this manuscript is structured as follows.
-We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We review Poincar\'e constants for the gradient over convex domains in~\ref{section:poincare}.
-We develop computable upper bounds for Poincar\'e--Friedrichs constants for the gradient over triangulated domains in Section~\ref{section:gradient}.
-We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
-We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
-We construct an important geometric reflection operator in Section~\ref{section:extension}
-and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-We present numerical examples in Section~\ref{section:numericalexamples}.
-
-\section{Basic notions of triangulations}\label{section:triangulations}
-
-We gather basic notions and definitions concerning simplicial meshes.
-
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
-We call these points the \emph{vertices} of the simplex $T$.
-If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
-
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
-\\
-
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} 
-if it satisfies the following conditions: 
-(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
-\begin{align*}
-    \underlying{\calT} := \bigcup_{ T \in \calT } T
-    .
-\end{align*}
-We call any set \textit{trianguable} if it is the underlying set of some triangulation. 
-\\
-
-\begin{comment}
-\begin{remark}
-    Our main interest in this manuscript are finite triangulations of compact sets. 
-    There is another reason why we insist on the triangulation being finite: 
-    if we do not require our simplicial complexes to be finite,
-    then a reasonable definition of simplicial complex would need additional topological conditions. 
-    % 
-    For example, if we modify our definition of simplicial complex to be infinite, 
-    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
-    %
-    A more interesting such example is this:
-    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
-    that underlies an ``infinite $0$-dimensional simplicial complex''.
-    If we place $\calC$ on the x-axis of a 2D coordinate system 
-    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
-    then the resulting set is still compact, even path-connected,  
-    but has an ``infinite $1$-dimensional triangulation''.
-    % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
-\end{remark}
-\end{comment}
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$,
-and $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
-
-Whenever $\calT$ is a simplicial complex, 
-the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
-In practice, we not always distinguish between points and singleton simplices.
-% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
-% \begin{remark}
-    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.~\cite{schrijver1998theory}
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra.~\cite{ziegler2012lectures}
-% \end{remark}
-}
-% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\todo{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
-We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
-Formally,
-\begin{gather*}
-    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
-    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
-    \qquad 
-    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
-\end{gather*}
-We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial structural observation is the following.~\footnote{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}
-
-\begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
- such that 
- \begin{align*}
-    \patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S''),
-    \qquad 
-    \Vertices(S) \cup \Vertices(S') = \Vertices(S'').
- \end{align*}
-\end{lemma}
-\begin{proof}
- Let $T \in \calT$ be $n$-dimensional.
- We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
- We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
- Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
- where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
-\end{proof}
-
-We introduce a specific notion of connectivity. 
-Given an $n$-dimensional simplicial complex $\calT$, 
-we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-% TODO: Theo suggests reverse order of that sequence
-We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
-Clearly, strongly connected in $\calT$ is an equivalence relation among simplices. 
-A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component. 
-\\
-
-We shift gears and move from a combinatorial study of triangulations to an analytical study:
-we introduce quantitative measures for the geometric quality of triangulations. 
-These indicate of the regularity of simplex shapes. 
-All these quantities have in common that they can be computed from purely local information. 
-Most of such \emph{shape measures} in the literature are based on geometric features, 
-but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
-While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
-
-\todo{MWL: The different geometric quantities in this section should really be just what is needed later.
-Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
-Any inequalities here should be as tight as possible.
-}
-
-We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
-where the height of a vertex is defined as the distance to the affine span of its opposing face.
-
-For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
-
-Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
-where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
-We recall that the $\ell^{2}$ operator norm of $\|A\|_{2}$ agrees with $\sigma_{\max}(A)$,
-and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
-% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
-
-Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
-the \textit{aspect shape measure} $\aspectratio(T)$,
-and 
-the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
-by 
-\begin{align}\label{math:shapemeasure}
-    \geometricshapemeasure(T)
-    := 
-    \frac{ \diam(T)^{n} }{ n! \vol(T) }
-    ,
-    \qquad 
-    \aspectratio(T)
-    := 
-    \frac{ \diam(T) }{ \height(T) }
-    ,
-    \qquad 
-    \algebraicshapemeasure(T)
-    := 
-    \sup_{ \varphi : \Delta^n \rightarrow T } 
-    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
-%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
-    ,
-\end{align}
-where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-
-When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
-\begin{align}\label{math:shapemeasure:triangulation}
-    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
-    ,
-    \quad 
-    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
-    ,
-    \quad 
-    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
-    .
-\end{align}
-We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
-
-We gather a few relationships between geometric and algebraic entities and compare the different shape measures.
-
-\begin{lemma}\label{lemma:measurerelationships}
-    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{gather*}
-        \| \Jacobian \varphi \|
-        \leq 
-        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
-        ,
-        \qquad 
-        \| \Jacobian \varphi^{-1} \|
-        \leq 
-        \Czwei{n} \cdot 
-        \geometricshapemeasure(T) 
-        \diam(T)^{-1}
-        ,
-        \\
-        \algebraicshapemeasure(T)
-        \leq 
-        \Cdrei{n}
-        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
-        \geometricshapemeasure(T)
-        ,
-        \qquad 
-        %         \geometricshapemeasure(T)^{\frac 1 n}
-        %         \leq 
-        \aspectratio(T)
-        \leq 
-        \geometricshapemeasure(T)
-        .
-    \end{gather*}
-    Here,
-    \begin{align*}
-        \Ceins{n} \leq \sqrt{n},
-        \quad 
-        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
-        \quad 
-        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
-        . 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
-%     except for the vertex $\varphi(0)$. It immediately follows that 
-%     \begin{align*}
-%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
-%         .
-%     \end{align*}
-%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
-%     
-    We easily verify the first inequality.
-To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
-    The Jacobian determinant is the product of these singular values. 
-    By a result of Hong and Pan \cite{hong1992lower},
-    \begin{align*}
-        \sigma_{n}
-        &\geq 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
-        = 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
-        .
-    \end{align*}
-%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
-    The second inequality follows by taking the reciprocal. 
-    The definition of the condition number now gives the third inequalities. 
-    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
-    Finally, 
-    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
-    \begin{align*}
-        \frac{ \diam(T) }{ \height(T) }
-        \leq 
-        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
-        \leq 
-        \frac{ \diam(T)^{n} }{ n! \vol(T) }
-        .
-    \end{align*}
-%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
-%     \begin{align*}
-%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%         \leq 
-%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
-%         .
-%     \end{align*}
-    That shows the fourth and last of the inequalities. 
-\end{proof}
-
-\begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
-
-% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-We are interested in the maximal ratio of volumes between neighboring $n$-simplices, written $\volumeratio(\calT)$,
-and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
-\begin{align}
-    \volumeratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
-    \frac{ \vol(T) }{ \vol(T') }
-    ,
-    \qquad 
-    \diameterratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
-    \frac{ \diam(T) }{ \diam(T') }
-    .
-\end{align}
-Whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
-that preserves $F$. We define 
-\begin{align}\label{math:reflectionmeasure}
-    \reflectionestimate(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \| \Jacobian \Xi_{T,T'} \|
-\end{align}
-to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
-This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
-% we define the quantity 
-% \begin{align*}
-%     \geometricshapemeasure(T)
-%     := 
-%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%     .
-% \end{align*}
-
-\begin{lemma}\label{lemma:volumecomparison}
-    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \begin{align*}
-        \diam(T_1)
-        \leq 
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \diam(F)
-        % = 
-        \geometricshapemeasure(T_1)
-        \diam(F)
-        ,
-        \qquad 
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
-        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-        % \cdot 
-        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        % = 
-        \aspectratio(T_1) \aspectratio(T_2)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        \leq 
-        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-        .
-    \end{align*}
-%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
-\end{lemma}
-
-% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
-% \begin{align*}
-%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
-%     \leq 
-%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-%     \cdot 
-%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-%     .
-% \end{align*}
-% DONE: REMOVE THE FACTORIAL?
-% DONE: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-% DONE: clarify the first of the following inequalities
-
-%     \begin{align*}
-%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
-%     \end{align*}
-%     Thus we establish the first estimate:
-
-%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-%     \begin{align*}
-%         \diam(F)
-%         \geq 
-%         h
-%         =
-%         n
-%         \frac{ \vol(T_1) }{ \vol(F') }
-%         \geq 
-%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
-%         \cdot 
-%         \diam(T_1)
-%         .
-%     \end{align*}
-%     That shows the second estimate.
-
-\begin{proof}
-    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
-%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
-%     \begin{align*}
-%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
-%     \end{align*}
-%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
-    Now, 
-    \begin{align*}
-%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
-        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
-    \end{align*}
-    The first estimate follows. 
-    As for the second estimate,
-    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
-    \begin{align*}
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        = 
-        \frac{ h_1 }{ h_2 }
-        \leq
-        \frac{ \diam(T_1) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \aspectratio(T_{2})
-        .
-    \end{align*}
-\begin{comment}
-    On the other hand, 
-    \begin{align*}
-        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
-%         \\
-%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        h_1 \leq \aspectratio(T_{1}) \diam(F),
-        \qquad 
-        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
-        .
-    \end{align*}
-    The second estimate follows. 
-    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
-    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
-    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        \leq 
-        \| \Jacobian\phi_{2} \| \cdot \| \Jacobian\phi_{1}^{-1} \|
-        \leq 
-        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \| \Jacobian \Xi \|
-%         &
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \diam(T_1)
-%         \diam(T_2)^{-1}
-%         \\&
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         \diam(F)
-%         \diam(T_2)^{-1}
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         .
-%     \end{align*}
-    All the desired results thus follow.
-\end{comment}
-    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    Writing $h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
-    \begin{align*}
-        \| \Jacobian \Xi \|
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \left( 1 + \aspectratio(T_2) \right)
-        \aspectratio(T_1)
-        .
-    \end{align*}
-    The desired estimates are shown.
-\begin{comment}
-    \todo{Tighter estimate via geometry}
-    Matrix inverse lemma:
-    \begin{align*}
-        A ( A + (z_2-z_1) e_1^t )^{-1}
-        =
-        \Id
-        - 
-        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        =
-        \Id
-        - 
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        .
-    \end{align*}
-    Putting in a multiple of $\alpha z_1$, we find 
-    \begin{align*}
-        \alpha z_1
-        -
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) 
-        .
-    \end{align*}
-
-    Without loss of generality, $F$ lies in the hyerplane plane of the second to last coordinates,
-    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
-    We can write 
-    \begin{align*}
-        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
-    \end{align*}
-    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
-    \begin{align*}
-        A = 
-        \begin{pmatrix}
-            b_1/a_1 & 0 & 0
-            \\
-            (b_2-a_2)/a_1 & 1 & 0
-            \\
-            b_3/a_1 & 0 & 1
-        \end{pmatrix}
-        =:
-        \begin{pmatrix}
-            c_1 & 0 & 0
-            \\
-            c_2 & 1 & 0
-            \\
-            c_3 & 0 & 1
-        \end{pmatrix}
-    \end{align*}
-    Its singular values are $1$ and 
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        +
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        =
-        \frac{1}{2}
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        +
-        \frac{1}{2}
-        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
-        \leq 
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        .
-    \end{align*}
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            -
-            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        -
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        .
-    \end{align*}
-
-    \begin{align*}
-        \sigma_{\max}
-        &= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            }
-        +
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        ,
-        \\
-        \sigma_{\min}
-        &=
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        -
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        .
-    \end{align*}
-    It follows that 
-    \begin{align*}
-        \det \Jacobian\Xi
-        &=
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-        +
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-        \\
-        \frac{1}{2} + \frac{1}{2} 
-        .
-    \end{align*}
-    Matrix determinant lemma:
-    \begin{align*}
-        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
-        =
-        \left( e_{n} A^{-1} z_2 \right) \det(A)
-        =
-        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
-        .
-    \end{align*}
-\end{comment}
-\end{proof}
-
-\begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
-    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
-    If we have an upper estimate for the number of simplices sharing a given vertex, 
-    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
-\end{remark}
-%%%%%%%% END HERE
-
-\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
-\\
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align*}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align*}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
+\begin{align*}
+    \cye{C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.}
+\end{align*}
+
 Towards a converse inequality, 
 let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
+\begin{align} \label{math:aver_norm}
     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
@@
     .
-\end{align*}
+\end{align}
 Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| \cye{u}_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
 We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
@@
 \end{align*}
-% \begin{align*}
-%     \color{Emerald}
-%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p-1} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     +
-%     2^{p-1} 
-%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     .
-% \end{align*}
-Via an application of the triangle inequality, 
-the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
-Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+\cye{Thus}, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    \cye{C_{\grad,\Omega,p}} \leq 2 \cye{\overline C_{\grad,\Omega,p}}.
+\end{align*}
+In the special case $p=2$, since the average \cye{becomes the} orthogonal projection, and this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
+Hence,
+\begin{align*}
+    \cye{\overline C_{\grad,\Omega,2}} = \cye{C_{\grad,\Omega,2}}. 
+\end{align*}
+
+\cye{From~\eqref{math:aver_norm},} Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ \cye{as}
 \begin{align*}
@@
     u \in L^{p}(\Omega)
-    .
-\end{align*}
-We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+    ,
+\end{align*}
+\cye{where we have also used} $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
 The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
@@
 \begin{align}\label{math:p_vs_pf}
-    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
+    \cye{C_{\grad,\Omega,p}} \leq 2^{|2/p-1|} \cye{\overline C_{\grad,\Omega,p}}.
 \end{align}
 In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-\\
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
-see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
+
+\subsection{\cye{Analytical constants in} Poincar\'e--Friedrichs inequalities over convex domains} \label{section: PX_convex}
+
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} \cye{or \cite[Lemma~3.24]{ern2021finite}} 
 \begin{align}\label{math:acostaduran}
@@
     u \in W^{1,2}(\Omega)
-    .
+    ,
 \end{align}
+\cye{where $\diam(\Omega)$ is the diameter of the domain $\Omega$.}
 These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
@@
     .
-\end{align*} % DONE: Theo : following sentence : which upper bound ?
+\end{align*} 
 Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
@@
 
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
+We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}, \cite[Theorem~1.1]{esposito2013poincare}): 
 when $1 < p < \infty$, one can show that 
@@
 \end{align*}
-Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+Note that the last inequalities \cye{from~\eqref{math:p_vs_pf}} imply, again when $1 < p < \infty$, the Poincar\'e inequalities
 \begin{align}\label{math:esposito:poincare}
@@
     % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
+    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant via~\eqref{math:p_vs_pf}. 
     Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
@@
 \begin{remark}
-    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    \cye{The above} Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
     but individual convex domains may allow for better constants.
-    We refer to \cite{matculevich2016explicit} for an overview of some improved inequalities, such as for triangles.
-    % for example, triangles allow the reduction of the constant by 20\%.
+    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for \cye{discussions};
+    for example, triangles allow the reduction of the constant by 20\%.
 \end{remark}
 
-% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
-
-\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
-
-In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
-We achieve by explicitly constructing scalar potentials of gradients.
-We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
-We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells.
-we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
-\\
-
-We construct scalar potentials over larger and larger intermediate subdomains. 
-Two different variations of that idea are analyzed;
-while the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
-On the one hand, we can cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
-Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece.
-This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result.
-
-For the agenda of this section, the following combinatorial notion of triangulations will be helpful. 
-Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
-a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
-where for each index $1 \leq m \leq M$ we have fixed index $0 \leq j(m) \leq m-1$ 
-such that $T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
-We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
-
-On the other hand, we assess an alternative route towards constructing scalar gradient potentials over triangulated domains. 
-While the underlying idea remains the same, the construction of the potential is slightly different. 
-we can extend the potential on each intermediate domain to another simplex by solving a local auxiliary problem on that simplex subject to partial boundary conditions.
-This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
-As an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex} computes an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed on a single face of the boundary.
-
-We emphasize that the second approach to constructing potentials and bounding Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-Our estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
+\section{Basic notions of triangulations}\label{section:triangulations}
+
+We gather \cye{here} basic notions and definitions concerning simplicial meshes.
+
+\subsection{\cye{A triangulation or a simplicial complex}}
+
+A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
+We call these points the \emph{vertices} of the simplex $T$.
+If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
+then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
+
+The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
+and its remaining points constitute the \textit{boundary} of the simplex.
+
+A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if it satisfies the following conditions: 
+(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
+% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\todo{MV: Don't we only use $n$-dimensional simplicial complexes?
+That would be a simplification of our presentation.}\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is defined as the union 
+\begin{align*}
+    \underlying{\calT} := \bigcup_{ T \in \calT } T
+    .
+\end{align*}
+We call a set \textit{triangu\cye{l}able} if it is the underlying set of some triangulation.
+
+\begin{remark}
+    Our main interest in this manuscript are finite triangulations of compact sets. 
+    There is another reason why we insist on the triangulation being finite: 
+    if we do not require our simplicial complexes to be finite,
+    then a reasonable definition of simplicial complex would need additional topological conditions. 
+    % 
+    For example, if we modify our definition of simplicial complex to be infinite, 
+    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
+    %
+    A more interesting such example is this:
+    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
+    that underlies an ``infinite $0$-dimensional simplicial complex''.
+    If we place $\calC$ on the x-axis of a 2D coordinate system 
+    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
+    then the resulting set is still compact, even path-connected,  
+    but has an ``infinite $1$-dimensional triangulation''.
+    % 
+    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
+\end{remark}
+
+Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
+More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
+Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
+We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
+The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
+Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
+In practice, we not always distinguish between points and singleton simplices. 
+Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
+    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
+    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
+}
+
+\todo[inline]{MV: Do we really need all these notions?}
+
+When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{star} of $T$, 
+which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
+We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
+Formally,
+\begin{gather*}
+    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
+    \qquad 
+    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
+\end{gather*}
+We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+A crucial observation is the following.
+
+\begin{lemma}
+ Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
+ Then either $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \emptyset$ or there exists $S'' \in \calT$
+ such that $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S'')$ with $S, S' \subseteq S''$.
+\end{lemma}
+\begin{proof}
+ Let $T \in \calT$ be $n$-dimensional.
+ We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
+ We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
+ Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
+ where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
+\end{proof}
+
+We introduce a specific notion of connectivity. 
+Given an $n$-dimensional simplicial complex $\calT$, 
+we call $n$-simplices $S,S' \in \calT$ \emph{\cye{face} connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+% TODO: Theo suggests reverse order of that sequence
+We call such a sequence a \emph{\cye{face} path} from $S$ to $S'$ in $\calT$. 
+Clearly, \cye{face} connected in $\calT$ is an equivalence relation among simplices. 
+A \emph{\cye{face-}connected component} of $\calT$ is an equivalence class under this equivalence relation, 
+and we call $\calT$ \emph{\cye{face} connected} if it has only one \cye{face-}connected component.
+
+\subsection{\cye{Quantitative measures for the geometric quality of triangulations}} \label{section:qual_triang}
+
+We \cye{now} shift gears and move from a combinatorial study of triangulations to an analytical study:
+we introduce quantitative measures for the geometric quality of triangulations. 
+These indicate of the regularity of simplex shapes. 
+Most of such \emph{shape measures} in the literature are based on geometric features, 
+but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
+All these quantities have in common that they can be computed from purely local information. 
+While there are many equivalent shape measures, we use the ones that most immediate\cye{ly} appear in our proofs.
+
+\todo[inline]{MWL: The different geometric quantities in this section should really be just what is needed later.
+Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
+Any inequalities here should be as tight as possible.
+}
+
+We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
+Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$.
+
+For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
+
+Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
+where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
+We recall that the $\ell^{2}$ operator norm of \cye{$A$,} $\|A\|_{2}$\cye{,} agrees with $\sigma_{\max}(A)$,
+and\cye{,} if $A$ is invertible, then $\|A^{-1}\|_{\cye{2}} = \sigma_{\min}(A)^{-1}$.
+
+Whenever $T$ is any $n$-dimensional simplex $T$,
+we define the \textit{geometric shape measure} $\kappa(T)$,
+the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$,
+and 
+the \textit{algebraic shape measure} $\kappa_{2}(T)$
+by 
+\begin{align}\label{math:shapemeasure}
+    \kappa(T)
+    := 
+    \frac{ \diam(T)^{n} }{ n! \vol(T) }
+    ,
+    \qquad 
+    \kappa_{\maxcol}(T)
+    := 
+    \frac{ \diam(T) }{ \height(T) }
+    ,
+    \qquad 
+    \kappa_{2}(T)
+    := 
+    \sup_{ \varphi : \Delta^n \rightarrow T } 
+    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
+    ,
+\end{align}
+where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
+% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
+
+When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
+\begin{align}\label{math:shapemeasure:triangulation}
+    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
+    ,
+    \quad 
+    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
+    ,
+    \quad 
+    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
+    .
+\end{align}
+We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
+
+\cye{We will use below} the maximal ratio of volumes between \cye{face-}neighboring $n$-simplices: 
+\begin{align}\label{math:volumecomparisonmeasure}
+    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
+\end{align}
+We \cye{will also} compare the diameters of simplices that intersect \cye{at least in one point}. \cye{For this purpose,} we define 
+\begin{align}\label{math:diametercomparison}
+    \theta(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
+    \frac{ \diam(T) }{ \diam(T') }
+\end{align}
+\cye{Finally,} whenever $S,T$ are two $n$-simplices that share a common face $F$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
+that preserves $F$. We \cye{then} define 
+\begin{align}\label{math:reflectionmeasure}
+    \xi(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
+    \| \Jacobian \Xi_{S,T} \|_{\cye{2}}
+\end{align}
+to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
+This indicator quantifies how much reflection across the shared face distorts the geometry.
+
+\subsection{\cye{Relationships between geometric and algebraic entities in a single simplex}}
+
+We \cye{now} gather a few relationships between geometric and algebraic entities and compare the different shape measures \cye{in a single simplex}.
+
+\begin{lemma}\label{lemma:measurerelationships}
+    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
+    \begin{gather*}
+        \| \Jacobian \varphi \|_{\cye{2}}
+        \leq 
+        \Ceins{n} \diam(T) % DONE: can this improved?
+        ,
+        \qquad 
+        \| \Jacobian \varphi^{-1} \|_{\cye{2}}
+        \leq 
+        \Czwei{n} 
+        \kappa(T) 
+        \diam(T)^{-1}
+        ,
+        \\
+        \kappa_{2}(T)
+        \leq 
+        \Cdrei{n}
+        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
+        \kappa(T)
+        ,
+        \qquad 
+        %         \kappa(T)^{\frac 1 n}
+        %         \leq 
+        \kappa_{\maxcol}(T)
+        \leq 
+        \kappa(T)
+        .
+    \end{gather*}
+    Here,
+    \begin{align*}
+        \Ceins{n} \leq \sqrt{n},
+        \quad 
+        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{\cye{2}}{\cye{n-1}}}, 
+        \quad 
+        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
+        . 
+    \end{align*}\todo{MV: Exponent flipped???}
+\end{lemma}
+\begin{proof}
+%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
+%     except for the vertex $\varphi(0)$. It immediately follows that 
+%     \begin{align*}
+%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \height(T)^{-1}
+%         .
+%     \end{align*}
+%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
+%     
+    We easily verify the first inequality.\todo{MV: Could we show how?
+Isn't $\Ceins{n}$ just 1?} To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
+    The Jacobian determinant is the product of these singular values. 
+    By a result of Hong and Pan \cite{hong1992lower},
+    \begin{align}\label{equation:Hong_Pan}
+        \sigma_{n}
+        &\geq 
+        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
+        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
+        = 
+        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
+        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
+        .
+    \end{align}
+%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
+    The second inequality follows by taking the reciprocal. 
+    The definition of the condition number now gives the third inequalit\cye{y}. 
+    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
+    Finally, 
+    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
+    \begin{align*}
+        \frac{ \diam(T) }{ \height(T) }
+        \cye{=} 
+        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
+        \leq 
+        \frac{ \diam(T)^{n} }{ n! \vol(T) }
+        .
+    \end{align*}\todo{MV: ???}
+%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
+%     \begin{align*}
+%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%         \leq 
+%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
+%         .
+%     \end{align*}
+    That shows the fourth and last of the inequalities. 
+\end{proof}
+
+\begin{remark}
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    In our convention, the reference simplex has unit shape measure.
+    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
+$\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
+
+% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
+    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}\cye{, which also called} \emph{thickness}~\cite{munkres2016elementary}\todo{MV: Correct?}.
+    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
+    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex\cye{.} 
+% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
+\end{remark}
+
+\subsection{\cye{Relationships between geometric and algebraic entities in two neighboring simplices}}
+
+\cye{We now continue in two simplices sharing a face.}
+
+% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
+% we define the quantity 
+% \begin{align*}
+%     \kappa(T)
+%     := 
+%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%     .
+% \end{align*}
+
+\begin{lemma}\label{lemma:volumecomparison}
+    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
+    \begin{align*}
+        \diam(T_1)
+        \leq 
+        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        % \diam(F)
+        % = 
+        \kappa(T_1)
+        \diam(F)
+        ,
+        \qquad 
+        \frac{ \vol(T_1) }{ \vol(T_2) }
+        \leq 
+        % \frac{\diam(T_1)^{n}}{n! \vol(T_1)} 
+        % 
+        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
+        % = 
+        \kappa(T_1) \kappa(T_2)
+        .
+    \end{align*}
+    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
+    \begin{align*}
+        \| \Jacobian \Xi \|_{\cye{2}}
+        \leq 
+        \Cvier{n}
+        \cye{\kappa(T_2)} \kappa(T_1)\cye{.}
+    \end{align*}
+    Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
+\end{lemma}
+
+% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
+% \begin{align*}
+%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
+%     \leq 
+%     \frac{\diam(T_1)^{n}}{n! \vol(T_1)} 
+%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
+%     .
+% \end{align*}
+% DONE: REMOVE THE FACTORIAL?
+% DONE: I am not 100% sure what that means.
+Is really the heights of F?
+I imagine this is rather the heights of simplices T_1 and T_2, isn't?
+Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
+(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
+% DONE: clarify the first of the following inequalities
+
+%     \begin{align*}
+%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
+%     \end{align*}
+%     Thus we establish the first estimate:
+
+%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
+%     \begin{align*}
+%         \diam(F)
+%         \geq 
+%         h
+%         =
+%         n
+%         \frac{ \vol(T_1) }{ \vol(F') }
+%         \geq 
+%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
+%         \diam(T_1)
+%         .
+%     \end{align*}
+%     That shows the second estimate.
+
+\begin{proof}
+    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
+    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
+    The diameter of $F$ is at least as large as the height $h_S$ of some other face\cye{\sout{t}} $S$ of $T$. Recursive application of the volume formula shows 
+    \begin{align*}
+        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n\cye{.}
+    \end{align*}
+    Now, \cye{as} $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$\cye{,} 
+    \begin{align*}
+        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
+    \end{align*}
+    The first estimate follows.
+
+    On the other hand, 
+    \begin{align*}
+        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n\cye{!} \vol(T_1)} \diam(F),
+        \\
+        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cye{(n-1)!} \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cye{!} \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
+        .
+    \end{align*}
+    The second estimate follows.
+
+    Lastly, \cye{for} $\Xi : T_1 \rightarrow T_2$ \cye{defined} above, Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
+    \begin{align*}
+        \| \Jacobian \Xi \|_{\cye{2}}
+        &
+        \leq 
+        \Ceins{n}
+        \Czwei{n}
+        \kappa(T_2)
+        \diam(T_1)
+        \diam(T_2)^{-1}
+        \\&
+        \leq 
+        \Ceins{n}
+        \Czwei{n}
+        \kappa(T_2)
+        \kappa(T_1) 
+        \diam(F)
+        \diam(T_2)^{-1}
+        \leq 
+        \Ceins{n}
+        \Czwei{n}
+        \kappa(T_2)
+        \kappa(T_1) 
+        .
+    \end{align*}\todo{MV: How does the fist estimate follow?}
+    All the desired results thus follow.
+
+%     \todo{Tighter estimate via geometry}
+%     Without loss of generality, $F$ lies in the plane of the second to last coordinates,
+%     so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
+%     After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
+%     If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
+%     are all one with the possible exception of the singular values of the matrix 
+%     \begin{align*}
+%         A = 
+%         \begin{pmatrix}
+%             a_1/h & 0
+%             \\
+%             a_2/h & 1
+%         \end{pmatrix}
+%     \end{align*}
+%     Its singular values are 
+%     \begin{align*}
+%         \sigma_{\max}
+%         &= 
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+%         \\&= 
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+%             } }
+%         \\&= 
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+%             }
+%         +
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 
+%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+%             }
+%         \\&= 
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+%             }
+%         +
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+%             }
+%         \\&= 
+%         \frac{1}{2}
+%         \sqrt{ 
+%             \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+%             }
+%         +
+%         \frac{1}{2}
+%         \sqrt{ 
+%             \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+%             }
+%         ,
+%         \\
+%         \sigma_{\min}
+%         &=
+%         \frac{1}{\sqrt 2}
+%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+%         \\&= 
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+%             }
+%         -
+%         \frac{1}{2}
+%         \sqrt{ 
+%             1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+%             }
+%         .
+%     \end{align*}
+\end{proof}
+
+\begin{remark}
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ \cye{of~\eqref{math:volumecomparisonmeasure}} but not $\theta(\calT)$ \cye{of~\eqref{math:diametercomparison}}. 
+    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one \cye{face}\todo{MV: OK?} in terms of the shape measure. 
+    If we have an upper estimate for the number of simplices sharing a given vertex, 
+    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
+\end{remark}
+%%%%%%%% END HERE
+
+\section{\cye{Combinatorial} Poincar\'e--Friedrichs \cye{constants over} triangulated domains\cye{: the gradient case}}\label{section:gradient}
+
+In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
+\cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
+Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure.
+We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}.
+We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
+This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+
+%Section~\ref{section:qual_triang}
+
+\subsection{\cye{Poincar\'e--Friedrichs constants over face patches}}
+
+\cye{We start by extending the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations} in a way which captures the correct asymptotic behavior as $p$ grows to infinity.
+\cye{Let us stress that face patches are not necessarily convex and remark that our result is in particular sharp when $T_1$ and $T_2$ have similar volumes and diameters}.
 
 \begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
-    Let $\calT$ be a triangulation.
-    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
+    Suppose that $\cye{T_1}, \cye{T_2}$ are two $n$-simplices \cye{from an $n$-dimensional triangulation $\calT$} whose intersection is a common face $F := T_1 \cap T_2$. 
     Write $U := T_1 \cup T_2$. 
@@
         &
-%         \leq 
-%         2 C_{\PF,{\rm EFNT},p}
-%         \max\left( 
-%             \frac{ \vol(T_1) }{ \vol(T_2) }
-%             ,
-%             \frac{ \vol(T_2) }{ \vol(T_1) }
-%         \right)^{\frac 1 p}
-%         \\&\qquad\qquad 
-%         \cdot 
-%         \max\left( \diam(T_1), \diam(T_2) \right)
-%         \| \nabla u \|_{L^{p}(U)}
-%         \\&
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \volumeratio(\calT)^{\frac 1 p}
+        \leq 
+        2 \cye{\Ceins{n}} C_{\PF,{\rm EFNT},p}
+        \max\left( 
+            \frac{ \vol(T_1) }{ \vol(T_2) }
+            ,
+            \frac{ \vol(T_2) }{ \vol(T_1) }
+        \right)^{\frac 1 p}
+        \\&\qquad\qquad 
+        \cdot 
         \max\left( \diam(T_1), \diam(T_2) \right)
+        \| \nabla u \|_{L^{p}(U)}
+        \\&
+        \leq \underbrace{
+        2 \cye{\Ceins{n}} C_{\PF,{\rm EFNT},p}
+        \rho(\calT)^{\frac 1 p}
+        \max\left( \diam(T_1), \diam(T_2) \right)}_{\cye{C_{{\rm{PF}},T_1 \cup T_2,p}}}
         \| \nabla u \|_{L^{p}(U)}
@@
 \begin{proof}
-    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
-    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
-    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
-    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
-    be affine transformations that map the $e_{i}$ to $v_{i}$ for $i = 0, \dots, n-1$ 
-    and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
-    Write $\hat U := \Delta_1 \cup \Delta_2$.
-    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
+    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
+    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
+    Let $\hat U := \hat T_1 \cup \hat T_2$, which is \cye{(crucially)} convex. 
+    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
+    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
+    Note that these affine transformations define a bi-Lipschitz \cye{piecewise affine} mapping $\varphi : \hat U \rightarrow U$.
 
@@
     We observe 
-%     \begin{align*}
-%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-%         &=
-%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-%         +
-%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-%         ,
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-%         &\leq 
-%         |\det(\Jacobian \varphi_1^{-1})|
-%         \cdot \| \Jacobian \varphi_1 \|^{p}
-%         \cdot 
-%         \| \nabla u \|_{L^{p}(T_1)}^{p}
-%         ,
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-%         &\leq 
-%         |\det(\Jacobian \varphi_2^{-1})|
-%         \cdot \| \Jacobian \varphi_2 \|^{p}
-%         \cdot 
-%         \| \nabla u \|_{L^{p}(T_2)}^{p}
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-%         &\leq 
-%         \max\left( 
-%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
-%             ,
-%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
-%         \right)
-%         \| \nabla u \|_{L^{p}(U)}^{p}
-%         .
-%     \end{align*}
-%     Hence 
+    \begin{subequations}\label{equation:map_bounds}\begin{align}
+        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
+        &=
+        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
+        +
+        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
+        ,
+        \\
+        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
+        &\leq 
+        |\det(\Jacobian \varphi_1^{-1})|
+        \| \Jacobian \varphi_1 \|_{\cye{2}}^{p}
+        \| \nabla u \|_{L^{p}(T_1)}^{p}
+        ,
+        \\
+        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
+        &\leq 
+        |\det(\Jacobian \varphi_2^{-1})|
+        \| \Jacobian \varphi_2 \|_{\cye{2}}^{p}
+        \| \nabla u \|_{L^{p}(T_2)}^{p}
+        .
+    \end{align}\end{subequations}
+    Hence 
     \begin{align*}
@@
         \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|
+            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|_{\cye{2}}
+            ,
+            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|_{\cye{2}}
         \right)
@@
     \end{align*}
-    Notice that $\hat U$ is convex and has diameter $2$. 
-    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
+    Notice that $\hat U$ has diameter $2$. \cye{Thus, from~\eqref{math:esposito:pf},} there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
     \begin{align*}
@@
     \end{align*}
-    Noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\| \Jacobian \varphi_i \| \leq \Ceins{n} \diam(T_i)$
-    for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}, we conclude the desired result.
-\begin{comment}
     % DONE: that abbreviation is to close to the Jacobian / total derivative 
-    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
+    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. \cye{Also using $\| \Jacobian \varphi_i \|_{\cye{2}} \leq \Ceins{n} \diam(T_i)$ from Lemma~\ref{lemma:measurerelationships},}
     \begin{align*}
@@
         &\leq 
-        2 C_{\PF,{\rm EFNT},p}
+        2 \cye{\Ceins{n}} C_{\PF,{\rm EFNT},p}
         \max\left( 
@@
         \\&
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
+        \cye{=} 
+        2 \cye{\Ceins{n}} C_{\PF,{\rm EFNT},p}
         \max\left( 
@@
     \end{align*}
-    This gives the desired result. 
-\end{comment}
+    \cye{In the last equality, we have also used $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$ that we have already employed in~\eqref{equation:Hong_Pan}.} This gives the desired result. 
 \end{proof}
@@
 \end{center}
-\caption{Strongly connected triangulation of a domain.
-The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-The triangle in dark gray is the triangle being added in the current iteration, and the light gray triangles constitute the subdomain assembled so far.}
+\caption{\cye{Face-}connected triangulation of a domain.
+The arrows depict a tree in the \cye{face} connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+\cye{\sout{The triangle in dark gray is the triangle being added in the current iteration, and the light gray triangles constitute the subdomain assembled so far.}}}
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{center}
-\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
+\caption{Exhausting a domain step by step as in Theorem\cye{s}~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
 The dark gray triangle is the one being currently added, and the light gray triangles constitute the subdomain assembled so far.}
@@
 
+\subsection{\cye{Poincar\'e--Friedrichs constants over a face-connected triangulation}}
+
+\cye{The following is our first computable estimate of Poincar\'e--Friedrichs constants over triangulated domains obtained in a stepwise, combinatorial way:}
+
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_m = T$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an \cye{$n$-dimensional} \cye{face-}connected finite triangulation $\calT$.
+    Let $T_0 \in \calT$ be an $n$-simplex \cye{and} for all $n$-simplices $T \in \calT$, 
+    fix a \cye{face} path $T_0, T_1, \dots, T_{\cye{M}} = T$.
     Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
     Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
-    and such that for all $T \in \calT$:
-%     DONE {Make sure the notation for the PF constants is uniform throughout the paper}
+    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
+    and such that for all $T \in \calT$\cye{, we have the following recursive estimate}:
     \begin{align*} 
         % \color{red}
-        \| w \|_{L^{p}(T_m)}
+        \| w \|_{L^{p}(T_{\cye{M}})}
         &\leq 
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        \sum_{t=1}^{m}
-        \volumeratio(\calT)^{\frac{m-t}{p}}
-        C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
-        \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
+        \left( 1 + \rho(\calT)^{\frac q p} \right)^{\frac 1 q}
+        \sum_{\cye{l}=1}^{{\cye{M}}}
+        \rho(\calT)^{\frac{{\cye{M}}-\cye{l}}{p}}
+        C_{{\rm{PF}},T_{\cye{l}} \cup T_{\cye{l}-1},p}
+        % 2 C_{\PF,{\rm EFNT},p} \rho(\calT)^{\frac 1 p} \max\left( \diam(T_{\cye{l}}), \diam(T_{\cye{l}-1}) \right)
+        \| \nabla u \|_{L^{p}(T_{\cye{l}} \cup T_{\cye{l}-1})}
         \\&\quad \quad \quad 
         +
-        \volumeratio(\calT)^{\frac{m-1}{p}}
+        \rho(\calT)^{\frac{{\cye{M}}-1}{p}}
         % C_{\PF,{\rm EFNT},p} \diam(T_0)
@@
     \end{align*}
-\end{theorem}
+\end{theorem}\todo{MV: I think we should also write down the bound for $\| w \|_{L^{p}(\Omega)}.$}
 
 \begin{proof}
+\todo[inline]{MV: Reworked and simplified the beginning of the proof.}
  Let $u \in W^{1,p}(\Omega)$. 
- For each $F \in \calT$ of dimension $n-1$, 
- we let $w_F \in W^{1,p}(U_F)$ such that $\nabla w_F = \nabla u$ over $U_F$ and such that 
- \begin{align*}
-    \| w_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla w_F \|_{L^{p}(U_F)},
- \end{align*}
- where the computable constant $C_{{\rm{PF}},U_F,p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
- We start with the simplex $T_{0}$. 
- There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+ \cye{On the first} simplex $T_{0}$, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
  \begin{gather*}
@@
  \end{gather*}
- In particular, $c_{0} := u - w_0$ is a constant function.
-
- Now, let $T \in \calT$ be any $n$-simplex. 
- By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
- We let $\Omega_m := \cup_{j=0}^{m} T_m$ for any $0 \leq m \leq M$,
- which is a triangulated $n$-dimensional submanifold with boundary.
- For any $1 \leq m \leq M$ we write $F_m := T_m \cap T_{m-1}$,
- which is a face of dimension $n-1$.
-
-%  Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
-We write $\Omega_m := \cup_{j=0}^{m} T_m$.
-Hence $\Omega = \Omega_M$.
-
- % DONE \notice{MWL, MV: add a figure here to illustrate how the domain is exhausted.}
-
- We construct the potential recursively. 
- We have seen that $c_{0} = w_{0} - u_{|\Omega_{0}}$ is a constant. 
- Assume that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
- such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
- % Note that this assumption is already satisfied when $m=1$.
- Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
- By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
- Since $$\nabla w_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}},$$
- there exists a constant $$c_{m} := w_{m-1|T_{{m-1}}} - w_{F_{m}|T_{{m-1}}}.$$
- We define $w'_{F_m} := w_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $$\nabla w'_{F_m} = \nabla w_{F_m} = \nabla u_{|U_{F_m}}$$ 
- and 
- $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
- But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
- Letting $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
- we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
-
- We assess the norm of this potential. We observe 
+ In particular, $c_{0} := \cye{w_0} - \cye{u}$ is a constant function. 
+ \cye{We then define 
+  \begin{align*}
+    w := u + c_0
+  \end{align*} 
+  (note that $w|_{T_{0}} = w_0$). Clearly,} 
+ $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$. \cye{We verify that $w$ fulfills the desired estimate.}
+
+ Let $T \in \calT$ be any $n$-simplex. 
+ By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}. 
+ For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}. \cye{Recall the notation $U_{F_m} := T_m \cup T_{m-1}$.}
+ We let $u_{F_m} \in W^{1,p}(U_{F_m})$ \cye{be} such that $\nabla u_{F_m} = \nabla u$ over $U_{F_m}$ and 
+ \begin{align*}
+    \| u_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\rm{PF}},U_{F_m},p} \| \nabla u_{F_m} \|_{L^{p}(U_{F_m})},
+ \end{align*}
+ where the computable constant $C_{{\rm{PF}},U_{F_m},p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
+\cye{Since $\nabla (w|_{U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u|_{U_{F_m}})$, we can define the constant
+ \begin{align*}
+    c_{m} := w|_{U_{F_m}} - u_{F_{m}}.
+ \end{align*}
+ }
+ \cye{\sout{We finally write $\Omega_m := \cup_{j=0}^{m} T_m$, which is triangulated $n$-dimensional submanifold with boundary}}.\todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
+As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
+
+\begin{figure}[h]
+\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
+\end{figure}
+
+ We \cye{now} assess the norm of the potential \cye{$w$}. \cye{For any $1 \leq m \leq M$,} we observe 
  \begin{gather*}
-    \| w'_{F_m} \|_{L^{p}(T_m)}
-    \leq 
-    \| w_{F_m} \|_{L^{p}(T_m)}
+    \| \cye{w} \|_{L^{p}(T_m)}
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
     +
@@
     \leq 
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
     .
  \end{gather*}
- In particular,
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
+ \cye{Consequently},
+ \begin{align*}
+    \| \cye{w} \|_{L^{p}(T_m)}
     &
     \leq 
-    \| w_{F_m} \|_{L^{p}(T_m)}
+    \| u_{F_m} \|_{L^{p}(T_m)}
     \\&\qquad 
@@
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
+    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
     +
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
- We sum the two integrals of $w_{F_m}$. 
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
+    .
+ \end{align*}
+ We sum the two integrals of $u_{F_m}$. 
  % 
@@
  \begin{align*}
-    \| w_{m} \|_{L^{1}(T_m)}
+    \| \cye{w} \|_{L^{1}(T_m)}
     \leq 
@@
     \right)
-    \| w_{F_m} \|_{L^{1}(U_{F_m})}
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
     +
     \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
+    \| \cye{w}\|_{L^{1}(T_{{m-1}})}
     .
@@
  \begin{align*}
-    \| w_{m} \|_{L^{\infty}(T_m)}
+    \| \cye{w} \|_{L^{\infty}(T_m)}
     \leq 
     2
-    \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
-    +
-    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
+    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+    +
+    \| \cye{w}\|_{L^{\infty}(T_{{m-1}})}
     .
@@
  % 1/q = 1 - 1/p = (p-1)/p 
- When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
+ When $1 < p < \infty$, \cye{recalling the complementary exponent} $q = p/(p-1) \in [1,\infty]$, we observe \cye{using the H\"older inequality}
+ \begin{align*}
+    \| \cye{w} \|_{L^{p}(T_m)}
     &\leq 
@@
     \left( 
-        \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
-        +
-        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
     \right)^{\frac 1 p}
@@
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    \\&\leq 
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
+    \\&\cye{=} 
     \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
+    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
     +
     \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
     .
@@
  \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
+    \| \cye{w} \|_{L^{p}(T_m)}
     &\leq 
@@
     \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
-    \| w_{F_t} \|_{L^{p}(U_{F_t})}
+    \| u_{F_t} \|_{L^{p}(U_{F_t})}
     \\&\quad \quad \quad 
@@
     \right)
-    \| w_{T_0}\|_{L^{p}(T_{0})}
+    \| u_{T_0}\|_{L^{p}(T_{0})}
     .
@@
 %  \begin{align*}
-%     \| w_{m} \|_{L^{p}(T_m)}^{p}
+%     \| \cye{w} \|_{L^{p}(T_m)}^{p}
 %     &\leq 
 %     (m+1)^{p-1}
-%     % \sum_{t=1}^{m} \volumeratio(\calT)^{m-t} 
-%     % \sum_{t=0}^{m-1} \volumeratio(\calT)^{t} 
-%     \frac{\volumeratio(\calT)^{m}-1}{\volumeratio(\calT)-1}
-%     \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{p/q}
-%     \| w_{F_t} \|_{L^{p}(U_{F_t})}^{p}
+%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
+%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
+%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
+%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
+%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
 %     \\&\quad \quad \quad 
@@
 %     (m+1)^{p-1}
-%     \volumeratio(\calT)^{m-1}
-%     \| w_{T_0}\|_{L^{p}(T_{0})}^{p}
+%     \rho(\calT)^{m-1}
+%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
 %     .
@@
  % 
- Repeating this argument produces $w \in L^{p}(\Omega)$ 
- such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
- In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
 \end{proof}
+
+\cye{\begin{remark}
+The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} overestimates the best one increasingly with increasing number of $n$-simplices in the triangulation $\calT$.
+For this reason, we target its use to local patches (stars), in particular nonconvex boundary stars such as that of Figure~\ref{figure:exhausting}.
+Clearly, the same building principle applies when we can obtain a nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a  face-connected path.
+The proof proceeds verbatim, where we merely replace the simplices $T_{m}$ by the convex local patches $U_m$.
+This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a large decrease of the overestimation of the best Poincar\'e--Friedrichs constant.
+\end{remark}}
+
+\subsection{\cye{Poincar\'e--Friedrichs constants over an $n$-simplex with homogeneous Dirichlet condition on a face}}
+
+We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains. 
+While the underlying idea remains the same, the construction of the potential is slightly different. 
+As an auxiliary result with independent relevance, we compute an upper bound for the Poincar\'e--Friedrichs inequality 
+when homogeneous boundary conditions are imposed on a single face of the boundary. 
+We present this result with two different techniques. 
+While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains. 
+% Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.
 
@@
     where $C_{\PF,T,F,p} > 0$ is a constant such that 
-    $C_{\PF,T,F,p} \leq \frac{1}{\sqrt[p]{p}} \diam(T)$.
-%     \begin{align*}
-%         C_{\PF,T,F,p}
-%         &\leq 
-%         C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
-%         \\
-%         C_{\PF,T,F,p}
-%         &\leq
-%         \frac{1}{\sqrt[p]{p}}
-%         \diam(T)
-%         .
-%     \end{align*}
+    \begin{align*}
+        C_{\PF,T,F,p}
+        &\leq 
+        C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
+        \\
+        \cye{C_{\PF,T,F,\infty}}
+        &\cye{\leq 
+        2 C_{\PF,T,\infty},  }
+        \\
+        %\quad 
+        C_{\PF,T,F,p}
+        &\leq
+        \frac{1}{\sqrt[p]{p}}
+        \diam(T)
+        .
+    \end{align*}\todo{MV: What is $\sqrt[\infty]{\infty}$?}
 \end{lemma}
 \begin{proof}
-\begin{comment}
     There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
@@
         \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \cdot 
         \gamma 
@@
         p
-        \cdot 
         \diam(T)
@@
         \\&
-        \leq 
+        \cye{\cancel{\leq 
         \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot C_{\PF,T,p}^{p-1} \right) 
+        \left( C_{\PF,T,p}^{p} + p C_{\PF,T,p}^{p-1} \right) 
         \diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
+        \| \nabla w \|_{L^{p}(T)}^{p}}}
         \\&
         \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right) 
+        \frac{ \vol(F) }{ \vol(T) } 
+        \left( C_{\PF,T,p}^{p} + p \diam(T) C_{\PF,T,p}^{p-1} \right) 
         %\diam(T)^{p}
@@
     \end{align*}
-    Recall that $u = w - \gamma$. The first inequality follows. 
-\end{comment}
-    % The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Since the inequality follows from Rademacher's theorem when $p = \infty$,
-    we assume $1 \leq p < \infty$. 
-    Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
+    Recall that $u = w - \gamma$. The first inequality follows \cye{when $1 \leq p < \infty$}. \cye{When $p = \infty$, 
+    \begin{align*}
+            \| \gamma \|_{L^{\infty}(T)}
+        =
+        \| \gamma \|_{L^{\infty}(F)}
+        =
+        \| \trace_{F} w \|_{L^{\infty}(F)}
+        \leq
+        \| w \|_{L^{\infty}(T)}
+    \end{align*}
+and we conclude similarly by the triangle inequality.    
+    }
+
+    The second inequality follows from Rademacher's theorem when $p = \infty$.
+    Let assume that $1 \leq p < \infty$. 
+    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
     Without loss of generality, 
@@
     and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg \in \bfL^{\infty}(\bbR^{n})$ for the trivial extension of $\nabla u$ outside of $T$.
-    %With the fundamental theorem of calculus and H\"older's inequality: 
-    We verify
-    \begin{align*}
-        \int_{T} |u(x)|^{p} \diff x \;dx
+    We write \cye{respectively $u$ and} $\bfg \cye{\cancel{\in \bfL^{\infty}(T)}}$ for the trivial extension of \cye{$u$ and} $\nabla u$ outside of $T$.
+    \cye{Using the fundamental theorem of calculus and H\"older's inequality,} 
+    \begin{align*}
+        \int_{\Omega} |u(x)|^{p} \diff x \;dx
         &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
+        \int_{\bbR^{n-1}} \int_{0}^{\cye{\diam(T)}} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
         \\&
         \leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
+        \int_{\bbR^{n-1}} \int_{0}^{\cye{\diam(T)}} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
         \\&
         \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
+        \int_{0}^{\cye{\diam(T)}} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
         \\&
         \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \;dx_1 
-        \cdot 
-        \int_{T} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
-        \leq
-        \frac{\diam(T)^{p}}{p} \int_{T} \left| \nabla u( x ) \right|^{p} \,dx
+        \int_{0}^{\cye{\diam(T)}} x_{1}^{p-1} \;dx_1 
+        \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
+        \leq
+        \frac{\cye{\diam(T)}^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} \,dx
         %
@@
 %         \leq
-%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
+%         \int_{\Omega} \int_{0}^{\cye{\diam(T)}} \cye{\diam(T)}^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
 %         \leq 
-%         D^{p} 
+%         \cye{\diam(T)}^{p} 
 %         \int_{\Omega} |\nabla u|^{p} \,dx
@@
     \end{align*}
-    That $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
-    for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
-
+
+    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T)\cye{/\sqrt[p]{p}} \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.
     Very briefly verify that density argument: 
-    There exists $\varphi : \Delta^{n} \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    There exists \cye{affine} $\varphi : \hat T \rightarrow \cye{T}$ mapping the convex closure of the $n$ unit vectors \cye{(the reference element $\hat T$)} onto the face $F$.
     We let $\hat u := u \circ \varphi$.
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\Delta^{n}$.
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
     We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
     Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
-    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$. 
+    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ is the desired sequence that approximates $u$. 
 \end{proof}
 
-% \begin{remark}
-%     While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains.  
-% \end{remark}
+\subsection{\cye{Poincar\'e--Friedrichs constants over a face-connected triangulation}}
+
+The following potential construction and upper bound for the Poincar\'e--Friedrichs constant 
+serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+\cye{It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.}
+
+\todo[inline]{MV: Why a second theorem?
+We should explain the difference of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+Which is better and when?}
 
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_m = T$.
-    For any $1 \leq l \leq m$, let $F_{l} = T_{l} \cap T_{l-1}$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an \cye{$n$-dimensional} \cye{face-}connected finite triangulation $\calT$.
+    Let $T_0 \in \calT$ be an $n$-simplex \cye{and} for all $n$-simplices $T \in \calT$, 
+    fix a \cye{face} path $T_0, T_1, \dots, T_{\cye{M}} = T$. For any $1 \leq l \leq \cye{M}$, let $F_l = T_l \cap T_{l-1}$.
     Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
+    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
+    and such that for all $T \in \calT$\cye{, we have the following recursive estimate}:
+    \begin{align*}
+        \| \cye{w} \|_{L^{p}(T_{\cye{M}})}
 %         &\leq 
-%         \volumeratio(\calT)^{\frac m p}
+%         \rho(\calT)^{\frac \cye{M} p}
 %         C_{\PF,T_{0},p} 
@@
 %         +
-%         \sum_{l=1}^{m} 
-%         \volumeratio(\calT)^{\frac {m-l} p}
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac {\cye{M}-l} p}
 %         C_{\PF,T_{l},F_{l},p} 
@@
 %         +
-%         \sum_{l=1}^{m} 
-%         \volumeratio(\calT)^{\frac {m-l} p} \reflectionestimate(\calT)
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac {\cye{M}-l} p} \xi(\calT)
 %         C_{\PF,T_{l},F_{l},p} 
@@
         &\leq 
-        \volumeratio(\calT)^{\frac m p}
-        C_{\PF,T_{0},p} 
-        \| \nabla u \|_{L^{p}( T_{0} )}
-        \\&\quad 
-        +
-        \sum_{l=1}^{m} 
-        \volumeratio(\calT)^{\frac {m-l} p}
+        \sum_{l=1}^{\cye{M}} 
+        \rho(\calT)^{\frac {\cye{M}-l} p}
         C_{\PF,T_{l},F_{l},p} 
@@
             +
-            \volumeratio(\calT)^{\frac {1} p}
-            \reflectionestimate(\calT)
+            \rho(\calT)^{\frac {1} p}
+            \xi(\calT)
             \| \nabla u \|_{L^{p}(T_{l-1})} 
         \right)
+        \\&\quad 
+        + \rho(\calT)^{\frac{\cye{M}}{p}}
+        C_{\PF,T_{0},p} 
+        \| \nabla u \|_{L^{p}( T_{0} )}
         .
@@
 %     \begin{align*}
-%         \| w_{m} \|_{L^{p}(T_m)}
+%         \| w_{\cye{M}} \|_{L^{p}(T_{\cye{M}})}
 %         &\leq 
-%         \sum_{l=1}^{m} 
-%         \volumeratio(\calT)^{\frac{m-l}{p}}
-%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac{\cye{M}-l}{p}}
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
 %         C_{\PF,T_{l},F_{l},p} 
@@
 %         +
-%         \volumeratio(\calT)^{\frac m p}
+%         \rho(\calT)^{\frac \cye{M} p}
 %         C_{\PF,T_{0},p} 
@@
 %     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
-\end{theorem}
+\end{theorem}\todo{MV: Synchronized the announcement and notation with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+\todo{MV: I think we should also write down the bound for $\| w \|_{L^{p}(\Omega)}.$}
 
 \begin{proof}
-    Let $u \in W^{1,p}(\Omega)$. 
-    First, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+\todo[inline]{MV: Reworked and simplified the proof.}
+
+\cye{We start as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}  Let $u \in W^{1,p}(\Omega)$. 
+ \cye{On the first} simplex $T_{0}$, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
  \begin{gather*}
@@
  \end{gather*}
-    In particular, $c_{0} := u - w_0$ is a constant function.
-
-    Now, let $T \in \calT$ be any $n$-simplex. 
-    By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
-    For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    We use a recursive argument.
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $c_{0} = u - w_{m-1}$.
-    In particular, $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{m-1}$. 
-    % Let $\hat T$ be the reference simplex.
-    % We fix affine diffeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
-    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
-    %
-    We define $w'_{m} := w_{m-1} \circ \Xi \in W^{1,p}(T_{m})$,
+ In particular, $c_{0} := \cye{w_0} - \cye{u}$ is a constant function. 
+ \cye{We then define 
+   \begin{align*}
+    w := u + c_0
+  \end{align*} 
+ (note that $w|_{T_{0}} = w_0$). Clearly,} 
+ $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$. \cye{We verify that $w$ fulfills the desired estimate.}
+
+ Let $T \in \calT$ be any $n$-simplex. 
+ By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}. 
+ For any $1 \leq m \leq M$, \cye{recall that} $F_m := T_m \cap T_{m-1}$ \cye{is}  a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}.
+
+    \cye{\sout{We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.}}
+   \todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
+As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
+
+\begin{figure}[h]
+\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
+\end{figure}
+
+    \cye{\sout{We use a recursive argument.}} Suppose that $\cye{1} < m \leq M$.
+    We define $w'_{m} := w\cye{|_{T_{m-1}}} \circ \Xi \in W^{1,p}(T_{m})$,
     where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
@@
     \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        .
-    \end{align*}
-    %Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
-    There exists $w''_{m} \in W^{1,p}(T_{m})$ such that 
-    \begin{align*}
-        \nabla w''_{m} = \nabla u_{|T_{m+1}} - \nabla w'_{m}, 
-        \quad 
-        \trace_{F_{m}} w''_{m} = 0.
-    \end{align*}
-    This is true because 
-    \begin{align*}
-        \trace_{F_{m}}( \nabla u - \nabla w'_{m} ) 
-        &= 
-        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m}
-        \\&= 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m}
-        = 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \nabla w_{m} = \nabla w'_{m} + \nabla w''_{m} = \nabla w'_{m} + \nabla u - \nabla w'_{m} = \nabla u,
-        % \end{gather*}
-        \\
-        % \begin{gather*}
-        \trace_{F_{m}} w_{m} = \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_{m}$. 
-    In particular, $c_{0} = u - w_{m}$. 
-    Lemma~\ref{lemma:mixedbconsimplex} gives 
+        \trace_{F_{\cye{m}}} w'_{m} = \trace_{F_{\cye{m}}} w\cye{|_{T_{m-1}}}
+        .
+    \end{align*}
+    We now define $w''_{m} \in W^{1,p}(T_{m})$ as
+\cye{    \begin{align}\label{equation:w''}
+        w''_{m} := u|_{T_{\cye{m}}} - w'_{m} + c_0 = w|_{T_{\cye{m}}} - w'_{m} = u|_{T_{\cye{m}}} - u\cye{|_{T_{m-1}}} \circ \Xi.
+    \end{align}
+    We crucially note that $w''_{m}$ is trace free on $F_{m}$ since
+    \begin{align*}
+        \trace_{F_{m}} w''_{m} = \trace_{F_{m}} (u|_{T_{\cye{m}}} - w'_{m} + c_0) = \trace_{F_{m}} (u|_{T_{m-1}} - w\cye{|_{T_{m-1}}} + c_0) = 0.
+    \end{align*}}
+    Lemma~\ref{lemma:mixedbconsimplex} gives\cye{, from the first expression in~\eqref{equation:w''}}
     \begin{align*}
@@
         \leq 
-        C_{\PF,T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
-        \\&
-        \leq 
-        C_{\PF,T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{\PF,T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
-    \begin{align*}
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
-        &
-        \leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
-        \cdot 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
-        \\&
-        \leq 
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        \cdot 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
-        .
-    \end{align*}
-    Putting this all together, we use 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
         C_{\PF,T_{m},F_{m},p} 
@@
         \right) 
-    \end{align*}
-    and 
+        .
+    \end{align*}
+    We also employ\cye{~\eqref{math:reflectionmeasure} \sout{Lemma~\ref{lemma:volumecomparison}}} to find 
     \begin{align*}
@@
         \leq 
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        % C_{\PF,T_{m},F_{m},p} 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        % C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi   \|_{\cye{2}}
+        \| \nabla \cye{w} \|_{L^{p}(T_{m-1})}
+        \\&
+        \leq 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla \cye{w} \|_{L^{p}(T_{m-1})}
+        \\&
+        \cye{=
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla u \|_{L^{p}(T_{m-1})} }
+        .
+    \end{align*}
+    \todo{MV: How $|\det(\Jacobian\Xi)|^{-\frac 1 p} \leq \rho(\calT)^{\frac 1 p}$ follows?}
+    \cye{From the second expression in~\eqref{equation:w''}, we then finally have} 
+    \begin{align*}
+        &
+        \| \cye{w} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| \cye{w} \|_{L^{p}(T_{m-1})} 
+        + 
+        C_{\PF,T_{m},F_{m},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{m})} 
+            + 
+            \cye{\rho(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla u \|_{L^{p}(T_{m-1})}}
+        \right). 
+    \end{align*}
+\cye{Therefrom, the desired estimate follows.}
+\end{proof}
+
+% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
+% Lemma 5.5
+
+\section{Review of vector calculus and exterior calculus}\label{section:calculus}
+
+We review \cye{in this section} the Sobolev spaces of vector \cye{and exterior} calculus and their transformation behavior.
+We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
+Let $\Omega \subseteq \bbR^{3}$ be a bounded open\todo{MV: Connected??
+Weakly Lipschitz??} set.
+\todo{MV: Slightly reorganized.}
+
+\subsection{\cye{Vector calculus}}
+
+\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
+\begin{gather*}
+    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
+\end{gather*}
+We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
+Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+The gradient-, curl-, \cye{and} divergence-conforming Piola transformations are \cye{respectively} the mappings 
+$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
+$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, \cye{and} 
+$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
+\cye{We will also use}
+$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
+We define them 
+for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
+\begin{subequations}\label{eq_definition_piola}
+\begin{align*}
+    \phi^{\grad}(v) &= v \circ \phi, \\
+    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
+    \phi^{\divergence}(\bfw) &= \cye{\adj}(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
+    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
+\end{align*}
+\end{subequations}\todo{MV: $\adj$ undefined}
+and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
+These mappings are invertible. 
+Bounds on the Lebesgue norms will follow from a more general result below.
+
+We use the commutativity relations 
+\begin{subequations}\label{eq_piola_commute}
+\begin{align}
+    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
+    \\
+    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
+    \\
+    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
+\end{align}
+\end{subequations}
+where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
+We summarize this as a commuting diagram:
+\begin{align*}
+    \begin{CD}
+        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
+        \\
+        @VV{\phi^{\grad}}V 
+        @VV{\phi^{\curl}}V 
+        @VV{\phi^{\divergence}}V 
+        @VV{\phi^{\rm b}}V 
+        \\
+        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
+    \end{CD}
+\end{align*}
+
+\begin{remark}
+    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
+    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
+    This definition is in accordance with the notion of pullback, which we will review shortly. 
+    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
+    The literature also knows the Piola transform in the direction of the original mapping. 
+\end{remark}
+
+\subsection{\cye{Exterior calculus}}
+
+\cye{We now move to} exterior calculus. 
+We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}. 
+Let $V$ be a real vector space. 
+Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
+Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
+if 
+\begin{gather*} 
+    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
+    = 
+    \text{sign}(\pi) 
+    u( v_1, v_2, \ldots, v_k ) 
+\end{gather*}
+for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
+By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
+Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
+
+The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
+Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
+their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
+defined by the formula 
+\begin{gather*}
+    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
+    = 
+    \frac{1}{k! l!} 
+    % \sum_{ \pi \in S_{k+l}} 
+    \sum_{ \pi } 
+    \signum(\pi) 
+    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
+    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
+\end{gather*}
+for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
+Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
+% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
+The exterior product is bilinear and associative, and satisfies 
+\begin{align*}
+    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
+    \quad 
+    \forall u_1 \in \Alt^{k}(V),
+    \quad 
+    \forall u_2 \in \Alt^{l}(V).
+\end{align*}
+We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
+\begin{align*}
+    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
+    \quad 
+    \forall v_1, v_2, \ldots, v_{k-1} \in V.
+\end{align*}
+
+We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
+Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
+Moreover, this particular setting comes with a canonical basis. 
+We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
+This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
+To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
+we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
+and introduce the basic $k$-alternators 
+\begin{align*}
+    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
+    \quad 
+    \forall \sigma \in \Sigma(k,n). 
+\end{align*}
+These define a basis of $\Alt^{k}(\bbR^{n})$.
+Note that 
+$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
+In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
+% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
+
+We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
+which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
+The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
+
+\subsection{\cye{Smooth differential forms}}
+
+We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
+which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
+The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
+to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
+Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
+\begin{gather*}
+    \omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \omega_{\sigma} \, 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
+\end{gather*}
+where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
+The exterior derivative \( \cartan\omega \) is defined by
+\begin{gather*}
+    \cartan\omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \sum_{j=1}^{n} 
+    \frac{\partial \omega_{\sigma}}{\partial x^j} 
+    \, \cartanx^j \wedge 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
+\end{gather*}
+The exterior derivative is linear and nilpotent, which means 
+\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
+Moreover, it satisfies the Leibniz rule:
+\begin{gather*} 
+    \cartan(\omega \wedge \eta) 
+    = 
+    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
+    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
+    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
+\end{gather*}
+
+\subsection{\cye{Sobolev spaces of differential forms}}
+
+Let us now turn our attention to Sobolev spaces of differential forms. 
+Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
+We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
+such that its pointwise norm is $p$-integrable. 
+The exterior derivative is defined in the sense of distributions and we introduce 
+\begin{gather*}
+    W^{p}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
+    .
+\end{gather*}
+We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
+if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
+\begin{align*}
+    \int_{\Omega} \cartan v \wedge u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{\Omega} v \wedge f 
+    .
+\end{align*}
+\cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
+for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
+
+Lastly, we are also interested in differential forms whose trace vanishes along only a part of the boundary. 
+Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
+We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
+such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+\begin{align*}
+    \int_{B_r(x)} \cartan v \wedge \tilde u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
+    .
+\end{align*}
+If that condition is satisfied, we also write 
+\begin{align*}
+    \trace_{\Gamma} u = 0
+    .
+\end{align*}
+Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
+Lastly, we introduce the closed subspaces 
+\begin{gather*}
+    W^{p}_{0}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
+    .
+\end{gather*}
+\cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
+We know that $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
+
+\subsection{\cye{Transformations by bi-Lipschitz mappings}}
+
+We are interested in transformations of Sobolev tensor fields from one domain onto \cye{an}other. 
+Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
+\begin{align} \label{equation:pullback}
+    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
+    := 
+    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
+\end{align}
+for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
+We cite an explicit transformation estimate~\cite{licht2019smoothed}.
+
+\todo{MV: Changed to ``Proposition''. Only the main results are termed ``Theorem''.}
+
+\begin{proposition} \label{proposition:pullbackestimate}
+ Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
+ Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
+ Then 
+ \begin{align}\label{math:pullbackestimate}
+  \begin{split}
+  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
+  &\leq 
+  \| \Jacobian \phi \|^{k}_{L^{\cye{\infty}}(\Omega)}
+  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\cye{\infty}}(\Omega')}
+  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+  \\ \cye{\| d \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}} &\leq 
+  \| \Jacobian \phi \|^{k}_{L^{\cye{\infty}}(\Omega)}
+  \| \Jacobian \phi^{-1} \|^{\frac{n}{p}}_{L^{\cye{\infty}}(\Omega')}
+  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+  .
+  \end{split}
+ \end{align}
+\end{proposition}\todo{MV: ??? What is the correct norm? $L^\infty(\Omega)$ or $L^2(\Omega)$ as in~\eqref{equation:map_bounds}??}
+
+\begin{remark}
+    In three dimensions, 
+    the calculus of differential forms can be translated into classical vector calculus. 
+    This is expressed formally as the commuting diagram 
+    \begin{gather*}
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        @VV{\varpi^{3}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\, ,}
+    \end{gather*}
+    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
+    \begin{align*}
+     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
+     &= 
+     \left( u_1, u_2, u_3 \right), 
+     \\
+     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
+     &= 
+     \left( u_{23}, - u_{13}, u_{12} \right).   
+    \end{align*}
+    In two dimensions, 
+    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
+    To the authors' best knowledge, neither convention is dominant in the literature.
+    We summarize the situation in the following commuting diagram: 
+    \begin{gather*} 
+    \begin{CD}
+        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
+        \\
+        @AA{\varkappa^{0}}A 
+        @AA{\varkappa^{1}}A 
+        @AA{\varkappa^{2}}A 
+        \\
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\,.}
+    \end{gather*}
+    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
+We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
+    The other vertical arrows are the identity. 
+    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
+\end{remark}
+
+\subsection{\cye{Some approximation properties}}
+
+We \cye{finally} review a few approximation properties. 
+Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
+Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
+
+\begin{lemma}
+%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
+%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
+%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    If $u \in L^{p}(\Omega)$, then \cye{the convolution} $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
+\end{lemma}
+
+% \begin{lemma} % TODO: possibly useful
+%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
+% \end{lemma}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
+    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
+\end{lemma}
+\begin{proof}
+    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
+    By the dominated convergence theorem and because $u$ has a weak derivative,
+    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
+    \begin{align*}
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
+        &= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
+        \\&= 
+        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
+        = 
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
+        .
+    \end{align*}
+    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
+
+    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
+    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
+    Define $\varphi_t(x) = tx$ for $t > 1$. 
+    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
+    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
+    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
+    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
+    The desired result follows. 
+\end{proof}
+
+\section{Regularized potential operators \cye{with analytical bounds on operator norms for exterior derivatives} over convex sets}\label{section:potentialoperator}
+
+We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
+either the $L^{p}$ de~Rham complex without boundary conditions, \cye{or} the $L^{p}$ de~Rham with full boundary conditions. 
+The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who analyze them as pseudo\cye{-}differential operators over domains star-shaped with respect to a ball. 
+In comparison to their work, our discussion is more modest:
+we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+However, our purpose are explicit bounds for the operator norms, \cye{giving the Poincar\'e--Friedrichs constants}.
+Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open\todo{MV: Weakly Lipschitz??} set with diameter $\cye{\diam(\Omega)} > 0$\todo{MV: Unifying the notation.}.
+
+\subsection{\cye{Regularized Poincar\'e and Bogovski\u{\i} operators}}
+
+We begin with introducing the Costabel\cye{--}McIntosh kernel.
+For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
+\begin{equation}\label{math:mainkernel}
+  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
+  .
+\end{equation}
+Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
+we then define the integral operators
+\begin{align*}
+  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
+  \\
+  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
+\end{align*}
+We call $\Poinc_{\ell}$ the {\em Poincar\'e operator} and $\Bogov_{\ell}$ the {\em Bogovski\u{\i} operator}.
+
+We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
+In order to analyze the properties of the potential operators,
+we first rewrite the Costabel\cye{--}McIntosh kernel $G_{\ell}$.
+Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
+\begin{align*}
+    G_{\ell}(x,y) 
+    &= 
+    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \\
+    &= 
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    .
+\end{align*}
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \cye{\diam(\Omega)}$, which gives 
+\begin{align*}
+    G_{\ell}(x,y) 
+    &= 
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{\cye{\diam(\Omega)}} r^{n-k-1} \,dr 
+    \\
+    &= 
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k}.
+\end{align*}
+We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
+
+We begin with the Poincar\'e operator. \cye{Let $B_{\cye{\diam(\Omega)}}(0)$ be the $n$-dimensional ball centered at the origin.}
+Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
+We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| \Poinc_{\ell} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+%     \\&\leq 
+%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_{\cye{\diam(\Omega)}}(0)}(x-y) |u(y)| \,dy
+    .
+\end{align*}
+We recall the radial integrals\cye{, where $S_1$ stands for\todo{MV: ???}}
+\begin{align*}
+    \int_{B_{\cye{\diam(\Omega)}}(0)} |z|^{k+1-n} \,dz
+    &
+    =
+    \vol_{n-1}(S_1) \int_{0}^{\cye{\diam(\Omega)}} r^{k+1-n} r^{n-1} \,dr
+    \\&
+    =
+    \vol_{n-1}(S_1) \int_{0}^{\cye{\diam(\Omega)}} r^{k} \,dr
+    =
+    \vol_{n-1}(S_1) \frac{\cye{\diam(\Omega)}^{k+1}}{k+1}
+    .
+\end{align*}
+We compute 
+\begin{align}
+    &
+    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \chi_{B_{\cye{\diam(\Omega)}}(0)}(z) |z|^{k+1-n} \,dz
+    \nonumber \\&
+    =
+    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \int_{B_{\cye{\diam(\Omega)}}(0)} |z|^{k+1-n} \,dz
+    \nonumber \\&
+    =
+    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \frac{\cye{\diam(\Omega)}^{k+1}}{k+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) \cye{\diam(\Omega)}^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}} \label{equation:A_Poinc}
+    .
+\end{align}
+Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
+and which is bounded by $2^{n-\ell}$. 
+In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
+    &
+    \leq 
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ \cye{\diam(\Omega)}^{n} }{\vol(\Omega)} 
+    \cye{\diam(\Omega)}
+    \| u \|_{L^{p}(\Omega)}
+    \\&
+    \leq 
+    n A_{\Poinc}(n,\ell) \frac{ \cye{\vol}(B_{\cye{\diam(\Omega)}}(0)) }{\vol(\Omega)} 
+    \cye{\diam(\Omega)}
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
+Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\begin{gather*}
+    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
+\end{gather*}
+% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \cye{\vol}(B_{\cye{\diam(\Omega)}}(0)) \cye{\diam(\Omega)}$. 
+%
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
+
+We analyze the Bogovski\u{\i} potential operator with similar means. 
+Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
+First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
+Consider now the case $x \in \overline\Omega$. 
+We estimate $\Bogov_{\ell} u(x)$ pointwise by 
+\begin{align*}
+    \left| \Bogov_{\ell} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+    \\&\leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \chi_{B_{\cye{\diam(\Omega)}}(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
+    .
+\end{align*}
+Using once more the radial integrals discussed above, we compute 
+% We recall the radial integrals 
 % \begin{align*}
-%         &
-%         \| w_{m} \|_{L^{p}(T_{m})}
-%         \\&
-%         \leq  
-%         \| w'_{m} \|_{L^{p}(T_{m})}
-%         + 
-%         \| w''_{m} \|_{L^{p}(T_{m})}
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \left( 
-%             \| \nabla u \|_{L^{p}(T_{m})} 
-%             + 
-%             \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-%         \right) 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         + 
-%         \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         + 
-%         \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
+%     \int_{B_{\cye{\diam(\Omega)}}(0)} |z|^{k+1-n} dz
+%     =
+%     \vol_{n-1}(S_1) \int_{0}^{\cye{\diam(\Omega)}} r^{k+1-n} r^{n-1} dr
+%     =
+%     \vol_{n-1}(S_1) \int_{0}^{\cye{\diam(\Omega)}} r^{k} dr
+%     =
+%     \vol_{n-1}(S_1) \frac{\cye{\diam(\Omega)}^{k+1}}{k+1}
 %     .
 % \end{align*}
-    The existence of $w \in W^{1,p}(\Omega)$ satisfying the recursive estimate follows. 
+% We compute 
+\begin{align}
+    &
+    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \chi_{B_{\cye{\diam(\Omega)}}(0)}(z) |z|^{k+1-n} \,dz
+    \nonumber \\&
+    =
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \int_{B_{\cye{\diam(\Omega)}}(0)} |z|^{k+1-n} \,dz
+    \nonumber \\&
+    =
+    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \cye{\diam(\Omega)}^{n-k} }{n-k} \frac{\cye{\diam(\Omega)}^{k+1}}{k+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) \cye{\diam(\Omega)}^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}} \label{equation:A_Bogov}
+    .
+\end{align}
+Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
+and which is bounded by $2^{\ell-1}$. 
+In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
+    &
+    \leq 
+    \vol_{n-1}(S_1) A(n,\ell) \frac{ \cye{\diam(\Omega)}^{n} }{\vol(\Omega)} 
+    \cye{\diam(\Omega)}
+    \| u \|_{L^{p}(\Omega)}
+    \\&
+    \leq 
+    n A_{\Bogov}(n,\ell) \frac{ \cye{\vol}(B_{\cye{\diam(\Omega)}}(0)) }{\vol(\Omega)} 
+    \cye{\diam(\Omega)}
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u$ is essentially bounded.
+Since that space is dense in the Lebesgue spaces, a density argument yields: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\begin{gather*}
+    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
+\end{gather*}
+% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \cye{\vol}(B_{\cye{\diam(\Omega)}}(0)) \cye{\diam(\Omega)}$. 
+Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
+that is, the reconstructed potential has support contained within $\overline\Omega$.
+
+\subsection{\cye{Additional properties}}
+
+Additional properties of these operators become apparent after a change of variables. 
+We write down the full definition of these operators and perform two substitutions.
+For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
+leading to 
+\begin{align*}
+    \Poinc_{\ell} u(x) 
+    &= 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
+    \chi_{\Omega}\left(x+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
+    .
+\end{align*}
+For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+leading to 
+\begin{align*}
+    \Bogov_{\ell} u(x) 
+    &= 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \chi_{\Omega}\left(y+t(x-y)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
+    .
+\end{align*}
+% We first discuss the support properties of this operator. 
+% Suppose that $u \in C^{\infty}\Alt^{\ell-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
+% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
+% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
+% 
+Given $a \in \Omega$, we introduce the potential operators 
+\begin{align*}
+    \Poinc_{\ell,a} u(x) 
+    &:= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt
+    ,
+    \\
+    \Bogov_{\ell,a} u(x) 
+    &:= 
+    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt
+    .
+\end{align*}
+By definition,
+\begin{align*}
+    \Poinc_{\ell} u(x) 
+    =
+    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da,
+    \quad 
+    \Bogov_{\ell} u(x) 
+    =
+    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da
+    .
+\end{align*}
+We study the interaction of these potential operator with the exterior derivative in more detail.
+% 
+That discussion is classical and establishes the exactness of several de~Rham complexes. 
+We recapitulate these arguments since our variants of the regularized potential operators 
+are not yet included in the published literature.
+
+Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$.
+We rewrite the Poincar\'e potential,
+\begin{align*}
+    \Poinc_{\ell,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Poinc_{\ell,a} u(x) 
+    &= 
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    ,
+\end{align*}
+and apply the Poincar\'e potential operator to this result, which gives 
+\begin{align*}
+    \Poinc_{\ell+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
+    \,\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Poinc_{\ell,a} u(x)
+    +
+    \Poinc_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{0}^{1} 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    u_{\sigma}(x) \,\cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x).
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell} u = u$.
+
+The discussion for the Bogovski\u{\i} operator is almost analogous. 
+Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
+We rewrite the Bogovski\u{\i} potential,
+\begin{align*}
+    \Bogov_{\ell,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Bogov_{\ell,a} u(x) 
+    &= 
+    \ell 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    ,
+\end{align*}
+and apply the Bogovski\u{\i} potential operator to this result, which gives 
+\begin{align*}
+    \Bogov_{\ell+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Bogov_{\ell,a} u(x)
+    +
+    \Bogov_{\ell+1,a} \cartan u(x)
+    \\&
+    =
+    \ell
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \int_{1}^\infty 
+    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(k,n)} 
+    u_{\sigma}(x) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Bogov_{\ell} u(x) + \Bogov_{\ell+1} \cartan u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell} u = u$.
+
+\subsection{\cye{Operator norms as bounds for the Poincar\'e--Friedrichs constants}}
+
+We now state the main results of this section.
+\cye{Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\ell$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\ell)$ and $A_{\Bogov}(n,\ell)$}.
+
+\begin{theorem}\label{theorem:PF_EC}
+    Let $\Omega \subseteq \bbR^{n}$ be and convex \cye{bounded open} \cye{set}\todo{MV: Weakly Lipschitz??} and let $1 \leq p < \infty$. 
+    We have bounded operators 
+    \begin{align*}
+        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \cye{W^{p}}\Alt^{\ell-1}(\Omega)
+        ,
+        \qquad 
+        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \cye{W^{p}_{0}}\Alt^{\ell-1}(\Omega)
+        .
+    \end{align*}
+    They satisfy the operator norm bounds 
+    \begin{align*}
+        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Poinc}(n,\ell) \frac{ \cye{\vol}(B_{\cye{\diam(\Omega)}}(0)) }{\vol(\Omega)} 
+        \cye{\diam(\Omega)}
+        \| u \|_{L^{p}(\Omega)}
+        ,
+        \\
+        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Bogov}(n,\ell) \frac{ \cye{\vol}(B_{\cye{\diam(\Omega)}}(0)) }{\vol(\Omega)} 
+        \cye{\diam(\Omega)}
+        \| u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell \cye{-1}}(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
+    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
+\end{theorem}
+
+\todo[inline]{MV: Do $\Poinc_{\ell}$ and $\Bogov_{\ell}$ still map piecewise polynomials to piecewise polynomials?
+Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}
+
+\begin{proof}
+    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.
+
+    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Poinc_{\ell  } u$. 
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\ell-1}(\Omega)$, we verify 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
+        +
+        (-1)^{k(n-k)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{k(n-k)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
+
+    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Bogov_{\ell} u$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
+    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
+    it holds that 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
+        +
+        (-1)^{k(n-k)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{k(n-k)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
+    This completes the proof. 
 \end{proof}
 
-\begin{remark}
-    The previous theorems, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} 
-    depend on only a few parameters of the triangulation:
-    the length of any traversal from the root simplex, the ratios of the volumes of adjacent simplices,
-    the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex. 
-    The aforementioned local Poincar\'e--Friedrichs constants can generally be estimated in terms of shape-parameters. 
-    If the face patches of the triangulation are convex, then better estimates are possible. 
+% DONE: Density of C infty mit oder ohne c.
+
+% \begin{remark}
+%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
+%     while they are increasing for the Bogovski\u{\i} operator.
+%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
+% \end{remark}
+
+\begin{remark} \label{remark:reg_Poinc_Bog}
+    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    These potentials enable the analysis of de~Rham complexes without boundary conditions.
+    % 
+    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+    Their generalization to differential forms was \cye{again} first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
+
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they \cye{can} study domains star-shaped with respect to a ball. 
+    The\cye{ir} operators are pseudodifferential operators of negative order, 
+    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudodifferential operators 
+    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
+    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
+\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
+
 \end{remark}
-
-% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
-% Lemma 5.5
 
@@
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
-Patches within triangulations of dimension two and three are examples of such shellable complexes. 
-The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler2012lectures} are our main references for this section. 
+\cye{Local} patches \cye{(stars)} within triangulations of dimension two and three are examples of such shellable complexes. 
+The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures} are our main references for this section. 
 We also refer to Lee's monograph~\cite{lee2011topological} for any further background on manifolds.
+
+\begin{figure}[h]
+\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
+\label{figure:not_manifold_triang}
+\caption{A manifold triangulation (left) and not a manifold triangulation (right)}
+\end{figure}
 
@@
 Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional. 
+\cye{An example of a manifold triangulation and an example which is not a manifold triangulation are given in Figure~\ref{figure:not_manifold_triang}.}
 
 The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball,
-and we sometimes call this a \textit{$n$-disk} triangulation.
+an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball\cye{\sout{,
+and we sometimes call this a \textit{$n$-disk} triangulation}}.
 An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
-\\
 
@@
 \begin{lemma}\label{lemma:boundarysimplices}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
+    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying \cye{set} is a manifold $\calM$. 
     \begin{itemize}
@@
     \item 
-    We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
+    \cye{Let} $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
     We will use the following fact:\footnote{To see this, one easily constructs a continuous deformation of $\calM$ into itself to move any chosen point on $S$ to any other chosen point on $S$.} if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$.
@@
     Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    As a consequence of the Jordan-Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
+    As a consequence of the Jordan\cye{--}Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
     we know that $Y \setminus X$ has got two connected components.
@@
     % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    % As a consequence of the Jordan-Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
+    % As a consequence of the Jordan\cye{--}Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
     % and thus $Y \setminus X$ has got two connected components.
@@
     If $z_F$ is an interior point of $\calM$, 
-    then we can assume by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
+    then we \cye{it follows} by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
     Consider $X = F \cap \partial \mathring B_F$.
@@
 % The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space.
-\\
 
@@
 at the intersection of topology and combinatorics. 
-These include the topology of local stars, which is a surprisingly non-trivial topic. 
+These include the topology of local \cye{patches} (stars), which is a surprisingly non-trivial topic. 
 We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{locally vertex combinatorial}
-if the local star of every simpelx $S \in \calT$ is a triangulated $n$-dimensional ball that contains $S$.
+if the star of every simpl\cye{e}x $S \in \calT$ is a triangulated $n$-dimensional ball that contains $S$.
 We gather some results that are hard to find in the literature.
@@
     \item 
-    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint $z_F$, and dimension $k$.
+    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint\todo{MV: barycenter???} $z_{\cye{S}}$\todo{MV: OK?}, and dimension $k$.
     Let $\calS := \patch_{\calT}(S)$ be its star. 
@@
     \begin{align*}
-        v_0, \dots, v_{i-1}, z_F, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
+        v_0, \dots, v_{i-1}, z_{\cye{S}}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
     \end{align*}
@@
     that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS' = \patch_{\calS'}(z_F)$. 
-    In particular, $z_F$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
+    Moreover, $\calS' = \patch_{\calS'}(z_{\cye{S}})$. 
+    In particular, $z_{\cye{S}}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
     So it remains to study the topology of vertex stars.
@@
     the set $\carapace(V)$ is a triangulation of a sphere of dimension $n-1$ for any inner vertex $V$. 
-    There exists a homeomorphism from the closed cone of $\underlying{\carapace(V)}$ onto the local star $\underlying{\patch_{\calT}(V)}$.
+    There exists a homeomorphism from the closed cone of $\underlying{\carapace(V)}$ onto the star $\underlying{\patch_{\calT}(V)}$.
     But then that closed cone and hence $\underlying{\patch_{\calT}(V)}$ are homeomorphic to an $n$-dimensional ball.
@@
     We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$.
-`
     The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere. 
     It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
-    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the local star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.
+    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.
 
@@
 %         \quad 
-%         D_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
+%         \cye{\diam(\Omega)}_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
 %     \]
-%     Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $D_H$,
+%     Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $\cye{\diam(\Omega)}_H$,
 %     and which maps $z$ to the origin. 
@@
     % Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere.
-Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
+Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a \disk\ of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
     % But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
@@
     Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
+    If the underlying space of $\calT$ is connected, then $\calT$ is \cye{face} connected.
 \end{lemma}
 \begin{proof}
-    We first show that each vertex star is strongly connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are strongly connected. 
-    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
-    The induction argument implies that each vertex star in $\calT$ is strongly connected.
+    We first show that each vertex star is \cye{face} connected via a short induction argument.
+    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are \cye{face} connected. 
+    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already \cye{face} connected if all simplicial $n$-balls and $n$-spheres are \cye{face} connected.
+    The induction argument implies that each vertex star in $\calT$ is \cye{face} connected.
 
@@
     we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
-    As each vertex star is strongly connected, 
+    As each vertex star is \cye{face} connected, 
     we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
     is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-    This just means that $\calT$ is strongly connected. 
+    This just means that $\calT$ is \cye{face} connected. 
 \end{proof}
@@
     Such manifolds appear in dimension four and higher:
-    one example is the E8 manifold, which is a compact simply-connected topological $4$-manifold that is homeomorphic to the underlying set of any simplicial complex.
+    one example is the E8 manifold\todo{MV: reference?}, which is a compact simply-connected topological $4$-manifold that is homeomorphic to the underlying set of any simplicial complex.
 The construction of such counterexamples typically involves an infinite procedure.
@@
 % 3. Shellability 
-\subsection{Shellable simplicial complexes}
-
-The notions of \emph{shelling} and \emph{shellable triangulation} have been discussed widely in combinatorial topology and polytopal theory. 
+\subsection{Shellable simplicial complexes}\label{section:shellability}
+
+The notions of shelling and shellable triangulation have been discussed widely in combinatorial topology and polytopal theory. 
 Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation of a manifold.
-We thus build upon the notion of shelling, as introduced in~\cite[Definition 8.1]{ziegler2012lectures},
-and our definition of shelling is equivalent to the notion of the shellings of simplicial complexes in the aforementioned reference; see also~\cite[Remark~8.3]{ziegler2012lectures}.
-
-Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-the gluing interface is a triangulated submanifold of the boundary. 
 This forces the intermediate triangulations to be particularly well-shaped. 
-We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, 
-as this enables the inductive method of proof.
-\\
+We build upon the notion of shelling as introduced in~\cite[Definition 8.1]{ziegler1995lectures},
+where our definition of shelling is equivalent to the notion of the shellings of simplicial complexes, see also~\cite[Remark~8.3]{ziegler1995lectures}.
+
+\todo[inline]{MV: Shortened, narrowed, removed repetitions.}
 
@@
 % Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface $I_m$ is a manifold of dimension $n-1$.
+We call the enumeration a \emph{shelling} if each interface \cye{set} $I_m$ is a \cye{triangulated} manifold of dimension $n-1$.
 
@@
 
-The reason of our interest in shellable simplicial complexes is that they can be constructed by successive adhesion of simplices to intermediate complexes, 
-such that the interface is well-behaved: it is a simplicial disk or a simplicial sphere. 
-That leads to the following important consequence.
-
-\begin{lemma}    
+The reason of our interest in shellable simplicial complexes is that they can be constructed by \cye{a} successive adhesion of simplices to intermediate complexes \cye{where these intermediate complexes are} simplicial \disk s \cye{\sout{or a simplicial spheres}}, as shows the following important consequence.\todo{MV: OK?
+``Intermediate'' excludes the last one.}
+
+\begin{lemma}\label{lemma:shell_triang_man}
     Let $\calT$ be an $n$-dimensional simplicial complex 
@@
     $$ 
-    is a manifold with boundary for all $0 \leq m \leq M$.
+    is a \cye{triangulated} manifold with boundary for all $0 \leq m \leq M$.
     % 
@@
     Suppose that $X_m := T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a topological $n$-ball and that $T_{m+1}$ is the next $n$-simplex in the shelling.
-    By definition, $I_{m+1} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
+    By definition, $I_{\cye{m}} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
     and it is triangulated by some faces of $T_{m+1}$ and their subsimplices.
@@
     On the one hand, 
-    if $I_{m+1}$ is the entire boundary of $T_{m+1}$, 
+    if $I_{\cye{m}}$ is the entire boundary of $T_{m+1}$, 
     then it must also be the boundary of the topological $n$-ball $X_{m}$. 
@@
     On the other hand, 
-    if $I_{m+1}$ is a proper subset of the entire boundary of $T_{m+1}$, 
+    if $I_{\cye{m}}$ is a proper subset of the entire boundary of $T_{m+1}$, 
     then $X_{m} \cup T_{m+1}$ is still a topological $n$-ball.
@@
 
-We collect important examples of shellable triangulations.
-Our main interest are local stars or stars within triangulations.
-
-\begin{example}
-    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
-    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
+We \cye{now} collect important examples of shellable triangulations.
+\cye{Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, nonshellable situations can arise}.
+Our main interest are local \cye{patches} (stars) within triangulations\cye{: these are shellable up to three space dimensions, but not necessarily beyond}.
+
+\begin{example}\label{example:shell_simpl}
+    Any simplex $T$ \cye{(}trivially\cye{)} has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
+    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling\cye{, cf.~\cite[Example 8.2.(iii)]{ziegler1995lectures}}.
 \end{example}
@@
 
-\begin{lemma}    
-    Any simplicial $2$-disk is shellable.
+\cye{\begin{example}
+    There exists a non-shellable triangulation of a tetrahedron and of a cube in $n=3$, see~\cite[Example 8.9]{ziegler1995lectures}.
+\end{example}}\todo{MV: 3D counterexamples directly here and straight to the point.}
+
+\begin{lemma}\label{lemma:shell_2D}
+    Any simplicial $2$-\disk\ is shellable.
     Any simplicial $2$-sphere is shellable. 
@@
     let $\calS$ be any triangulation of a $2$-sphere. 
-    By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-disk.
-    Any shelling of that disk can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
-    So it remains to show that any triangulation $\calT$ of the two-dimensional disk is shellable. 
+    By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-\disk.
+    Any shelling of that \disk\ can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    So it remains to show that any triangulation $\calT$ of the two-dimensional \disk\ is shellable. 
     We will construct the shelling in reverse.
@@
     % DONE: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
-    We show by an induction argument over the number of triangles that every triangulation of a $2$-disk that contains at least two triangles also contains at least two good triangles.
-
-    Clearly, this is the case if the triangulation of the $2$-disk contains two triangles. 
+    We show by an induction argument over the number of triangles that every triangulation of a $2$-\disk\ that contains at least two triangles also contains at least two good triangles.
+
+    Clearly, this is the case if the triangulation of the $2$-\disk\ contains two triangles. 
     Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
@@
     There are at least two triangles with an edge on the boundary. 
-    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$,
-    then there exists a triangle $T'$ that intersects $\partial M$ 
+    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$.
+    Then there exists a triangle $T'$ that intersects $\partial M$ 
     in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two strongly connected components, each of which is a topological $2$-disk.
+    Removing $T'$ splits the manifold into two \cye{face-}connected components, each of which is a topological $2$-\disk.
     By the induction assumption, each of those components contains at least two triangles 
@@
 
-    We conclude that whenever $\calT$ triangulates a $2$-disk,
+    We conclude that whenever $\calT$ triangulates a $2$-\disk,
     it contains a good triangle $T$. 
@@
     If $T$ intersects with the boundary in exactly one or two edges, 
-    then $\overline{M \setminus T}$ is still a topological $2$-disk.
+    then $\overline{M \setminus T}$ is still a topological $2$-\disk.
     The triangulation $\calT'$ that is obtained by removing $T$
-    is a triangulation of some $2$-disk that intersects $T$ only at either two or one edges.
-    Any shelling of $\calT'$ can be extended to a shelling of $\calT$.
-    The proof is complete. 
+    is a triangulation of some $2$-\disk\ that intersects $T$ only at either two or one edges.
+    Any shelling of $\calT'$ can \cye{in this way} be extended to a shelling of $\calT$\cye{, and} the proof is complete. 
 \end{proof}
@@
 \begin{proof}
-    This is Lemma~8.7 in \cite{ziegler2012lectures}.
+    This is Lemma~8.7 in \cite{ziegler1995lectures}.
 %     Without loss of generality, $V$ is the origin. 
@@
 %     The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
-%     and is thus shellable~\cite[Theorem~8.12]{ziegler2012lectures}. 
+%     and is thus shellable~\cite[Theorem~8.12]{ziegler1995lectures}. 
 \end{proof}
 
-\begin{lemma}[cf. Lemma B1 in \cite{ern2020stable}]
+\begin{lemma}
     Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
@@
 \begin{proof}
-    The statement is clear if $S$ is an inner or boundary face of $\calT$. 
-    The statement is also easily verified if $S$ is an inner or boundary edge of $\calT$.
-    When $S$ is an inner vertex, then we apply the preceding lemma.
-
-    It remains to consider the case where $S$ is a boundary vertex. 
-    Then the triangles of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-disk 
-    which is shellable,
-    and any such shelling can be extended to a shelling of $\patch_{\calT}(S)$.
+    \cye{For $S$ a tetrahedron, this is Example~\ref{example:shell_simpl}.}
+    The statement is \cye{also} clear if $S$ is an inner or boundary face of $\calT$\cye{, where we only need to enumerate respectively one or two tetrahedra}. 
+    The statement is \cye{still} easily verified if $S$ is an inner or boundary edge of $\calT$\cye{: one chooses a starting tetrahedron (with a boundary face) and rotates around the edge in a fixed direction to create a suitable enumeration}.
+
+    \cye{When $S$ is an inner vertex, then the \cye{faces} (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-sphere.
+Similarly, when $S$ is a boundary vertex, then the \cye{faces} (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
+Both these $2$-dimensional complexes are shellable \cye{by Lemma~\ref{lemma:shell_2D}}, and any such shelling \cye{immediately yields} a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondance between the tetrahedra in $\calT$ and the triangles.}\footnote{\cye{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}}\todo{MV: but not Lemma~\ref{lemma:stars_are_shellable}, because this first needs the triangulation $\calT$ itself to be shellable, right?}
 \end{proof}
 
+\begin{remark}
+    Not all triangu\cye{l}able sets admit a triangulation that is shellable. 
+    Moreover, even if a set admits a shellable triangulation, not all of its triangulations \cye{are} be shellable.
+\cye{For example, if we extend the non-shellable triangulation of a tetrahedron from~\cite[Example 8.9]{ziegler1995lectures}} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$,
+    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
+    This demonstrates that patches around boundary simplices are not necessarily shellable when the \cye{space} dimension \cye{$n$} is larger than three.
+\end{remark}\todo{MV: Moved up a bit.}
+
 A major structural feature of shellable simplicial complexes 
-is that each time a simplex is added, the local star around a simplex gets completed.
+is that each time a\cye{n $n$-}simplex is added, star\cye{s} around \cye{lower-dimensional} simpl\cye{ices} gets completed.
 
@@
     $$ 
-    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
-    then the intersection of those facets is an interior simplex $S \in \calT$ of dimension $n-k$ that satisfies 
+    \cye{\sout{Whenever} Then} $I_{m}$ is \cye{a} union of $k$ different face\cye{\sout{t}}s of $T$,\todo{MV: this is a property, not an assumption, right?} \cye{$1 \leq k \leq n$,} \cye{and} the intersection of those face\cye{\sout{t}}s is an interior simplex $S_{\cye{m}} \in \calT$ of dimension $n-k$ that satisfies
     $$
-        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
+        \patch_{X_{m+1}}(S_{\cye{m}}) = \patch_{\calT}(S_{\cye{m}}).
     $$
@@
 \begin{proof}
-    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
-    that constitute the local patch around some simplex $S$ of dimension $n-k$.
-    By assumption, $S$ must be a boundary simplex of $X_{m}$ and it is an interior simplex of $X_{m+1}$. 
-    But then $S$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
-    which means that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$. 
-    This had to be shown.
+    We know $I_{m}$ is a \cye{triangulated} submanifold of the boundary of $T$, and so it must be a collection of $k$ face\cye{\sout{t}}s \cye{of $T$, $1 \leq k \leq n$ ($k = n + 1$ can happen for the last enumerated simplex $m = M$ when $\calT$ is an $n$-sphere).
+$I_{m}$ also} constitutes \cye{a} local patch \cye{(star) of $(n-1)$-dimensional simplices around} some simplex $S_{\cye{m}}$ of dimension $n-k$ \cye{in $I_{m}$}.
+    By \cye{definition}, $S_{\cye{m}}$ \cye{is} be a boundary simplex of $X_{m}$\cye{,} and it is an interior simplex of $X_{m+1}$. 
+    But then $S_{\cye{m}}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
+    which means that $\patch_{X_{m+1}}(S_{\cye{m}}) = \patch_{\calT}(S_{\cye{m}})$. 
 \end{proof}
 
-\begin{remark}
-    Not all trianguable sets admit a triangulation that is also shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
-
-    For example, there exists a non-shellable triangulation of a tetrahedron. 
-    If we extend this triangulation to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, 
-    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the dimension is larger than the three.
-\end{remark}
-
-\section{Review of vector calculus and exterior calculus}\label{section:calculus}
-
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-
-We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
-Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
-In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-$W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
-\begin{gather*}
-    W^{p}(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
-\begin{gather*}
-    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \\ 
-    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}
-We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
-$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
-and
-$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
-for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
-\begin{subequations}\label{eq_definition_piola}
-\begin{align*}
-    \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
-    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
-    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
-\end{align*}
-\end{subequations}
-and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
-These mappings are invertible. 
-Bounds on the Lebesgue norms will follow from a more general result below.
-
-We use the commutativity relations 
-\begin{subequations}\label{eq_piola_commute}
-\begin{align}
-    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
-    \\
-    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
-\end{align}
-\end{subequations}
-where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
-We summarize this as a commuting diagram:
-\begin{align*}
-    \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
-        \\
-        @VV{\phi^{\grad}}V 
-        @VV{\phi^{\curl}}V 
-        @VV{\phi^{\divergence}}V 
-        @VV{\phi^{\rm b}}V 
-        \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
-    \end{CD}
-\end{align*}
-
-\begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
-\end{remark}
-
-%
-% trace properties 
-%
-
-%\section{Review of exterior calculus}
-
-Having discussed vector analysis, we review exterior calculus. 
-We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}. 
-Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
-Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
-if 
-\begin{gather*} 
-    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
-    = 
-    \text{sign}(\pi) 
-    u( v_1, v_2, \ldots, v_k ) 
-\end{gather*}
-for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
-By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
-Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
-
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
-their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
-defined by the formula 
-\begin{gather*}
-    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
-    = 
-    \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\end{gather*}
-for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
-The exterior product is bilinear and associative, and satisfies 
-\begin{align*}
-    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
-    \quad 
-    \forall u_1 \in \Alt^{k}(V),
-    \quad 
-    \forall u_2 \in \Alt^{l}(V).
-\end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
-\begin{align*}
-    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
-    \quad 
-    \forall v_1, v_2, \ldots, v_{k-1} \in V.
-\end{align*}
-We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
-Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
-Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
-This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
-To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
-and introduce the basic $k$-alternators 
-\begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
-    \quad 
-    \forall \sigma \in \Sigma(k,n). 
-\end{align*}
-These define a basis of $\Alt^{k}(\bbR^{n})$.
-Note that 
-$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
-In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
-
-We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
-which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
-The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
-
-We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
-which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
-Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather*}
-    \omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather*}
-where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
-\begin{gather*}
-    \cartan\omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \sum_{j=1}^{n} 
-    \frac{\partial \omega_{\sigma}}{\partial x^j} 
-    \, \cartanx^j \wedge 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\end{gather*}
-The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
-Moreover, it satisfies the Leibniz rule:
-\begin{gather*} 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
-\end{gather*}
-Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
-We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
-such that its pointwise norm is $p$-integrable. 
-The exterior derivative is defined in the sense of distributions and we introduce 
-\begin{gather*}
-    W^{p}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
-    .
-\end{gather*}
-We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
-We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. 
-The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.
-
-Lastly, we are also interested in differential forms whose trace vanishes along only a part of the boundary. 
-Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
-\begin{align*}
-    \int_{B_r(x)} \cartan v \wedge \tilde u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
-    .
-\end{align*}
-If that condition is satisfied, we also write 
-\begin{align*}
-    \trace_{\Gamma} u = 0
-    .
-\end{align*}
-Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
-Lastly, we introduce the closed subspaces 
-\begin{gather*}
-    W^{p}_{0}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
-    .
-\end{gather*}
-We know that $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
-
-We are interested in transformations of Sobolev tensor fields from one domain onto the other. 
-Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\begin{gather*} 
-    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    := 
-    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\end{gather*}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
-We cite an explicit transformation estimate~\cite{licht2019smoothed}.
-
-\begin{theorem} \label{theorem:pullbackestimate}
- Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
- Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
- Then 
- \begin{align}\label{math:pullbackestimate}
-  \begin{split}
-  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-  &\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-  \\&\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-  \| \Jacobian \phi^{-1} \|^{\frac{n}{p}}_{L^{\infty}(\Omega')}
-  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-  .
-  \end{split}
- \end{align}
-\end{theorem}
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms can be translated into classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \begin{gather*}
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \end{gather*}
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \begin{gather*} 
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \end{gather*}
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
-
-We review a few approximation properties. 
-Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\begin{lemma}
-%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
-%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
-%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
-\end{lemma}
-
-% \begin{lemma} % TODO: possibly useful
-%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-% \end{lemma}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
-\end{lemma}
-\begin{proof}
-    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
-    By the dominated convergence theorem and because $u$ has a weak derivative,
-    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
-    \begin{align*}
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
-        &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
-        = 
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
-        .
-    \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
-
-    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
-    Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
-    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
-    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
-    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
-    The desired result follows. 
-\end{proof}
-
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
-
-We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-We already know the optimal constants for the gradient operator over convex domains,
-and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
-
-For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
-and the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our purpose are explicit bounds for the operator norms, which are of independent interest. 
-\\
-
-In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $D > 0$.
-
-We begin with introducing the Costabel-McIntosh kernel.
-For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{math:mainkernel}
-  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
-  .
-\end{equation}
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
-we then define the integral operators
-\begin{align*}
-  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
-  \\
-  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align*}
-We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
-\\
-
-We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
-\begin{align*}
-    G_{\ell}(x,y) 
-    &= 
-    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
-    .
-\end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives 
-\begin{align*}
-    G_{\ell}(x,y) 
-    &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
-\end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-We begin with the Poincar\'e operator. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
-We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\ell} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_D(0)} |z|^{k+1-n} \,dz
-    &
-    =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} \,dr
-    \\&
-    =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-    .
-\end{align*}
-We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
-    \\&
-    =
-    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
-    .
-\end{align*}
-Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{n-\ell}$. 
-In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
-% 
-We analyze the Bogovski\u{\i} potential operator by similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\ell} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\ell} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
-    .
-\end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_D(0)} |z|^{k+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-%     .
-% \end{align*}
-% We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
-    \\&
-    =
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{\ell-1}$. 
-In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-    D
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
-Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
-that is, the reconstructed potential has support contained within $\overline\Omega$. 
-\\
-
-Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\ell} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
-leading to 
-\begin{align*}
-    \Bogov_{\ell} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
-    \chi_{\Omega}\left(y+t(x-y)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-% We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\ell-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
-% 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\ell,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt
-    ,
-    \\
-    \Bogov_{\ell,a} u(x) 
-    &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt
-    .
-\end{align*}
-By definition,
-\begin{align*}
-    \Poinc_{\ell} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da,
-    \quad 
-    \Bogov_{\ell} u(x) 
-    =
-    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da
-    .
-\end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-That discussion is classical and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators 
-are not yet included in the published literature.
-
-Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\ell,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\ell,a} u(x) 
-    &= 
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    ,
-\end{align*}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\ell+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
-    \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Poinc_{\ell,a} u(x)
-    +
-    \Poinc_{\ell+1,a} \cartan u(x)
-    \\&
-    =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{0}^{1} 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}(x) \,\cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-\todo{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x).
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell} u = u$.
-
-The discussion for the Bogovski\u{\i} operator is almost analogous. 
-Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \Bogov_{\ell,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Bogov_{\ell,a} u(x) 
-    &= 
-    \ell 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    ,
-\end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \Bogov_{\ell+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Bogov_{\ell,a} u(x)
-    +
-    \Bogov_{\ell+1,a} \cartan u(x)
-    \\&
-    =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
-    \int_{1}^\infty 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Bogov_{\ell} u(x) + \Bogov_{\ell+1} \cartan u(x)
-    .
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell} u = u$.
-\\
-
-We are in the position to establish the main results of this section.
-This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
-Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.
-
-\begin{theorem}
-    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}\Alt^{\ell-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-        D
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-        D
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
-    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
-\end{theorem}
-\begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Poinc_{\ell  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\ell-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\ell} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-    This completes the proof. 
-\end{proof}
-
-% DONE: Density of C infty mit oder ohne c.
-
-% \begin{remark}
-%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-%     while they are increasing for the Bogovski\u{\i} operator.
-%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
-% \end{remark}
-
-\begin{remark}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % 
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-
-    The operators discussed by Costabel and McIntosh are pseudodifferential operators of negative order, 
-    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudodifferential operators 
-    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \todo{Describe Guzman and Salgado's contribution in more detail.} 
-\end{remark}
-
-\section{Reflections and Deformations on shellable stars}\label{section:extension}
-
-This section is devoted to geometric operations that are crucially important for our main result. 
+\section{Reflections and deformations on shellable stars}\label{section:extension}
+
+This section is devoted to geometric operations that are crucially important for our main result \cye{in Section~\ref{section:poincarefriedrichs} below}. 
 Suppose that we have a shellable simplicial complex. 
 Every time we add a simplex according to the shelling sequence, 
-we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
-We will need a homeomorphism going from the new simplex onto its complement within the newly completed star.
+we complete the local \cye{patch} (star) of some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
+We will need a homeomorphism going from the new simplex onto its complement within the newly completed star\cye{, such as the two- and three-color maps in \cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}}.
 This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
 We are particularly interested in the norms of its Jacobian.
-We inerpret this as a nonlinear reflection. It will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms.
+We in\cye{t}erpret this as a nonlinear reflection. It will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms.
 
 In addition to that, this endeavor will produce another geometric tool 
-that enables an additional estimate Poincar\'e--Friedrichs constants:
+that enables an additional estimate \cye{of} Poincar\'e--Friedrichs constants:
 we construct a bi-Lipschitz deformation which maps the entire star 
@@
 Again, we give explicit estimates of the Jacobian.
-\\
 
@@
 
-Next, we observe that stars around subsimplices can represented by vertex stars after a local subdivision of the mesh.
+Next, we observe that stars around subsimplices can \cye{by} represented by vertex stars after a local subdivision of the mesh.
 The shape regularity is controlled in that process.
@@
 \begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$,
+    Let $T$ be an $n$-dimensional simplex with a $\cye{(n-1)}$-dimensional subsimplex $S$,
     let $z_S$ be the barycenter of $S$, 
@@
 \begin{proof}
-    This is easy.
+    \cye{The proof is obvious}.
 \end{proof}
 
-We know construct the main result of this section, namely the desired bi-Lipschitz homeomorphism. 
+\todo[inline]{MV: Some illustrations would be great.}
+
+We now construct the main result of this section, namely the desired bi-Lipschitz homeomorphism. 
 It can be imagined as the reflection across the interface between the selected simplex and the remainder of the star. 
@@
 
-\begin{theorem}\label{theorem:starreflection}
+\todo{MV: Changed to ``Proposition''. Only the main results are termed ``Theorem''.}
+
+\begin{proposition}\label{proposition:starreflection}
     Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
@@
     \begin{gather*}
-        \| \Jacobian\Xi_{1} \|          \leq \Cfive{n}{k}(\calT),
+        \| \Jacobian\Xi_{1} \|_{\cye{2}}          \leq \Cfive{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi_{1}^{-1} \|     \leq \Csechs{n}{k}(\calT),
-        \\
-        \| \det\Jacobian\Xi_{1} \|      \leq \Cdetfive{n}{k}(\calT),
+        \| \Jacobian\Xi_{1}^{-1} \|_{\cye{2}}     \leq \Csechs{n}{k}(\calT),
+        \\
+        \| \det\Jacobian\Xi_{1} \|_{\cye{2}}      \leq \Cdetfive{n}{k}(\calT),
         \quad 
-        \| \det\Jacobian\Xi_{1}^{-1} \| \leq \Cdetsechs{n}{k}(\calT),
+        \| \det\Jacobian\Xi_{1}^{-1} \|_{\cye{2}} \leq \Cdetsechs{n}{k}(\calT),
     \end{gather*}
@@
     \begin{align*}
-        \Xi_{2} : T \rightarrow U
+        \Xi_{2} : \cye{\underlying{\patch_{\calT}(S)}} \rightarrow U
     \end{align*}
@@
     \begin{gather*}
-        \| \Jacobian\Xi_{2} \|          \leq \Csieb{n}{k}(\calT),
+        \| \Jacobian\Xi_{2} \|_{\cye{2}}          \leq \Csieb{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi_{2}^{-1} \|     \leq \Cacht{n}{k}(\calT),
-        \\
-        \| \det\Jacobian\Xi_{2} \|      \leq \Cdetsieb{n}{k}(\calT),
+        \| \Jacobian\Xi_{2}^{-1} \|_{\cye{2}}     \leq \Cacht{n}{k}(\calT),
+        \\
+        \| \det\Jacobian\Xi_{2} \|_{\cye{2}}      \leq \Cdetsieb{n}{k}(\calT),
         \quad 
-        \| \det\Jacobian\Xi_{2}^{-1} \| \leq \Cdetacht{n}{k}(\calT),
+        \| \det\Jacobian\Xi_{2}^{-1} \|_{\cye{2}} \leq \Cdetacht{n}{k}(\calT),
     \end{gather*}
@@
     \end{enumerate}
-\end{theorem}
+\end{proposition}
 \begin{proof}
@@
         the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
-        Then $\calR'$ is the local star around the barycenter $z_S$,
+        Then $\calR'$ is the star around the barycenter $z_S$,
         and all $n$-simplices in $\calR'$ contain $z_{S}$. 
@@
         \begin{align*}
-            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
-            \\
-            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
+            \| \Jacobian \Theta_{|K}      \|_{\cye{2}} &\leq \| A_{K'} \|_{\cye{2}} \| A_{K}^{-1} \|_{\cye{2}} \leq \kappa(A_{K}),
+            \\
+            \| \Jacobian \Theta_{|K}^{-1} \|_{\cye{2}} &\leq \| A_{K'}^{-1} \|_{\cye{2}} \| A_{K} \|_{\cye{2}} \leq \kappa(A_{K}).
         \end{align*}
@@
         \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_z$,
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orth\cye{o}gonal to $h_z$,
         and that it equals $-z_{S'}$ when $x = z_{S'}$.
@@
         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
+        Then $\| h_z \|_{\cye{2}} = \cos(\beta) \|z_{S'}\|_{\cye{2}}$ and $\| b_z \|_{\cye{2}} = \sin(\beta) \|z_{S'}\|_{\cye{2}}$. 
         We study the singular values of the matrix 
@@
             \\ 
-            -2 \|b_z\|/\|h_z\| & 1
+            -2 \|b_z\|_{\cye{2}}/\|h_z\|_{\cye{2}} & 1
             \end{pmatrix}
@@
         \end{align*}
-        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
+        They are monoton\cye{ous}ly increasing and decreasing, respectively, in $\tan(\beta)$. 
         These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
@@
 %         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \| / \| h_{z} \|$, and we know $\|b_z\| \leq \|z_{S'}\|$. 
+        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \|_{\cye{2}} / \| h_{z} \|_{\cye{2}}$, and we know $\|b_z\|_{\cye{2}} \leq \|z_{S'}\|_{\cye{2}}$. 
         Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
@@
         \begin{align*}
-            \frac{ \| b_{z} \| }{ \| h_{z} \| }
-            = 
-            \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            \leq 
-            (n-k) \aspectratio(T)
+            \frac{ \| b_{z} \|_{\cye{2}} }{ \| h_{z} \|_{\cye{2}} }
+            = 
+            \frac{ \| b_{z} \|_{\cye{2}} }{ (n-k)^{-1} \| (n-k) h_{z} \|_{\cye{2}} }
+            \leq 
+            (n-k) \kappa_{\maxcol}(T)
 %             = 
-%             \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
+%             \frac{ \| b_{z} \|_{\cye{2}} \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
 %             \leq 
@@
             \sqrt{ 
-                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+                1 + (n-k)^{2} \kappa_{\maxcol}(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
             } 
             + 
-            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
+            (n-k) \kappa_{\maxcol}(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
             .
@@
         We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
-        that satifies the desired mapping properties. 
+        that sati\cye{s}fies the desired mapping properties. 
         It remains to analyze its Jacobian to get explicit estimates.
@@
             - 
-            \frac{ \|b_z\| }{ 2 \| h_{z} \| } 
+            \frac{ \|b_z\|_{\cye{2}} }{ 2 \| h_{z} \|_{\cye{2}} } 
             \hat b_{z} \otimes \hat h_{z}^{t}
@@
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence $\tan(\beta) = \| b_z \| / \| h_z \|$. It remains to study the singular values of the matrix 
+        Hence $\tan(\beta) = \| b_z \|_{\cye{2}} / \| h_z \|_{\cye{2}}$. It remains to study the singular values of the matrix 
         \begin{align*}
@@
                 -\tan(\beta) & 2 
-            \end{pmatrix}
+            \end{pmatrix}\cye{.}
         \end{align*}
@@
 %         \end{align*}
-        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
+        These are monoton\cye{ous}ly increasing and decreasing, respectively, in $\tan(\beta)$. 
         Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
@@
         \begin{align*}
-            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \aspectratio(T).
+            \tan(\beta) = \frac{\|b_z\|_{\cye{2}}}{\|h_z\|_{\cye{2}}} \leq (k+1) \kappa_{\maxcol}(T).
         \end{align*}
@@
         \begin{gather*}
-            \| \Jacobian\Phi_{K} \| 
-            \leq 
-            \frac 1 4 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
-            ,
-            \\
-            \| \Jacobian\Phi_{K}^{-1} \| 
-            \leq 
-            \frac 1 2 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
+            \| \Jacobian\Phi_{K} \|_{\cye{2}} 
+            \leq 
+            \frac 1 4 \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 }
+            ,
+            \\
+            \| \Jacobian\Phi_{K}^{-1} \|_{\cye{2}} 
+            \leq 
+            \frac 1 2 \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 }
             ,
@@
             = 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
+            \frac{ \| h_2 \|_{\cye{2}}^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, x \rangle }{ \| h_1 \|_{\cye{2}}^{2} }
             x
@@
         onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed, 
-        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
+        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|_{\cye{2}}^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|_{\cye{2}}^{2}$.
 
@@
         \begin{align*}
-            \Jacobian F(x) \cdot y
+            \Jacobian F(x) y
             &=
-            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
+            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\|_{\cye{2}} \|x\|_{\cye{2}} \cos(\alpha_2) }
             \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
@@
             +
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
+            \frac{ \| h_2 \|_{\cye{2}}^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \| h_1 \|_{\cye{2}}^{2} }
             x
@@
             +
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
+            \frac{ \| h_2 \|_{\cye{2}} }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \|_{\cye{2}} }
             \hat x
             \\&=
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
+            \frac{ \| h_2 \|_{\cye{2}} }{ \cos(\alpha_2) }
             \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
-            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
-            +
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
+            \frac{ \cos(\alpha_1) }{ \| h_1 \|_{\cye{2}} }
+            +
+            \frac{ \| h_2 \|_{\cye{2}} }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \|_{\cye{2}} }
             \hat x
             \\&=
-            \frac{ \| h_2 \| }{ \| h_1 \| }
+            \frac{ \| h_2 \|_{\cye{2}} }{ \| h_1 \|_{\cye{2}} }
             \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
@@
         \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
+            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|_{\cye{2}}^{2} }{ 4 } } + \frac{ \|a\|_{\cye{2}} }{2},
             \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
-        \end{align*}
-        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
+            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|_{\cye{2}}^{2} }{ 4 } } - \frac{ \|a\|_{\cye{2}} }{2}.     
+        \end{align*}
+        Notice that these are strictly monoton\cye{ous}ly increasing or decreasing, respectively, in $\|a\|_{\cye{2}}$.
         We notice the obvious upper bound 
         \begin{align*}
-            \|a\| 
+            \|a\|_{\cye{2}} 
             \leq 
@@
             = 
-            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
-            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
+            \frac{ \| h_K \|_{\cye{2}}^{2} }{ \langle h_K, x \rangle }
+            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|_{\cye{2}}^{2} }
             x
@@
             = 
-            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
-            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
+            \frac{ \| h_{{G}} \|_{\cye{2}}^{2} }{ \langle h_{{G}}, z \rangle }
+            \frac{ \langle h_K, z \rangle }{ \| h_K \|_{\cye{2}}^{2} }
             z,
@@
         \begin{gather*}
-            \| \Jacobian\Psi(x) \|
-            = 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \| \Jacobian\Psi(x) \|_{\cye{2}}
+            = 
+            \frac{ \| h_K \|_{\cye{2}} }{ \| h_{{G}} \|_{\cye{2}} }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
             \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
-            \right)
-            \\
-            \| \Jacobian\Psi(z)^{-1} \|
-            = 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
+                \sqrt{ 1 + \frac{ \|a\|_{\cye{2}}^{2} }{ 4 } } + \frac{ \|a\|_{\cye{2}} }{2}
+            \right)\cye{,}
+            \\
+            \| \Jacobian\Psi(z)^{-1} \|_{\cye{2}}
+            = 
+            \frac{ \| h_{{G}} \|_{\cye{2}} }{ \| h_K \|_{\cye{2}} }
             \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
             \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
+                \sqrt{ 1 + \frac{ \|a\|_{\cye{2}}^{2} }{ 4 } } - \frac{ \|a\|_{\cye{2}} }{2}
             \right)^{-1},
@@
             \left( 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \| h_K \|_{\cye{2}} }{ \| h_{{G}} \|_{\cye{2}} }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
@@
             \left( 
-            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
+            \frac{ \| h_{{G}} \|_{\cye{2}} }{ \| h_{K} \|_{\cye{2}} }
             \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
-            \right)^{n}
+            \right)^{n}\cye{,}
         \end{gather*}
@@
         \begin{align*}
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \| h_K \|_{\cye{2}} }{ \| h_{{G}} \|_{\cye{2}} }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
             \leq 
-            \frac{ \| x_K \| }{ \| h_{{G}} \| }
-            \leq 
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
+            \frac{ \| x_K \|_{\cye{2}} }{ \| h_{{G}} \|_{\cye{2}} }
+            \leq 
+            \frac{ \diam(K) }{ \| h_{{G}} \|_{\cye{2}} }
             ,
             \qquad 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
+            \frac{ \| h_{{G}} \|_{\cye{2}} }{ \| h_K \|_{\cye{2}} }
             \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
             \leq 
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
-            \frac{ \diam(G) }{ \| h_{K} \| }
+            \frac{ \| x_{G} \|_{\cye{2}} }{ \| h_{K} \|_{\cye{2}} }
+            \leq 
+            \frac{ \diam(G) }{ \| h_{K} \|_{\cye{2}} }
             .
@@
 %         \begin{align*}
-%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
+%             \frac{ \| h_K \|_{\cye{2}} }{ \| h_{{G}} \|_{\cye{2}} }
 %             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
 %             \leq 
-%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
+%             \frac{ \| x_K \|_{\cye{2}} }{ \| x_{{G}} \|_{\cye{2}} }
 %             .
@@
 The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        In o\cye{r}der to estimate $\|x_{G}\|_{\cye{2}}$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows that $\|x_{G}\| \leq \diam(T)$.
+        It follows that $\|x_{G}\|_{\cye{2}} \leq \diam(T)$.
 
@@
         \begin{align*}
-            \frac{\diam(T)}{ \|h_{F}\|}
-            \leq  
-            \aspectratio(T)
+            \frac{\diam(T)}{ \|h_{F}\|_{\cye{2}}}
+            \leq  
+            \kappa_{\maxcol}(T)
             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
@@
         \begin{gather*}
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
+            \frac{ \diam(K) }{ \| h_{{G}} \|_{\cye{2}} }
             \leq 
             (k+1)B_{T}
-            \frac{ \diam(K) }{ \| h_{T} \| }
+            \frac{ \diam(K) }{ \| h_{T} \|_{\cye{2}} }
             \leq 
             (k+1)B_{T}
-            \diameterratio(\calT)
-            \frac{ \diam(T) }{ \| h_{T} \| }
+            \theta(\calT)
+            \frac{ \diam(T) }{ \| h_{T} \|_{\cye{2}} }
             \leq 
             (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            ,
-            \\
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
+            \theta(\calT)
+            \kappa_{\maxcol}(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            ,
+            \\
+            \frac{ \| x_{G} \|_{\cye{2}} }{ \| h_{K} \|_{\cye{2}} }
             \leq 
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(T) }{ \| h_{K} \| }
+            \frac{ \diam(T) }{ \| h_{K} \|_{\cye{2}} }
             \leq 
             (k+1)
-            \diameterratio(\calT)
+            \theta(\calT)
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K) }{ \| h_{K} \| }
+            \frac{ \diam(K) }{ \| h_{K} \|_{\cye{2}} }
             \leq 
             (k+1)
-            \diameterratio(\calT)
+            \theta(\calT)
             \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
         \begin{gather*}
-            \frac{ \diam(K) }{ \| h_{{K}} \| }
+            \frac{ \diam(K) }{ \| h_{{K}} \|_{\cye{2}} }
             \leq 
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             ,
             \qquad 
-            \frac{ \| x_{G} \| }{ \| h_{G} \| }
+            \frac{ \| x_{G} \|_{\cye{2}} }{ \| h_{G} \|_{\cye{2}} }
             \leq 
             (k+1)B_{T}
-            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \kappa_{\maxcol}({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
         %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this obversation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
+        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
         %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
@@
         \begin{align*}
-            \|a\|
+            \|a\|_{\cye{2}}
             = 
             \left\|
-            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
+            \frac{\|x_{G}\|_{\cye{2}}}{\|h_{G}\|_{\cye{2}}} \hat h_{{G}} 
             - 
-            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
-            \right\|
+            \frac{\|x_{K}\|_{\cye{2}}}{\|h_{K}\|_{\cye{2}}} \hat h_K
+            \right\|_{\cye{2}}
             &
             \leq 
-            \frac{\|x_{G}\|}{\|h_{G}\|} 
-            + 
-            \frac{\|x_{K}\|}{\|h_{K}\|} 
+            \frac{\|x_{G}\|_{\cye{2}}}{\|h_{G}\|_{\cye{2}}} 
+            + 
+            \frac{\|x_{K}\|_{\cye{2}}}{\|h_{K}\|_{\cye{2}}} 
             \\&
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            \kappa_{\maxcol}(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
             .
@@
         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}\todo{MV: ???}. 
         After application of a piecewise linear Lipschitz mapping, 
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \todo{not enough}
+        \todo{MWL: not enough}
 
@@
         \begin{align*}
-            \| \Jacobian \Xi_{1} \|
+            \| \Jacobian \Xi_{1} \|_{\cye{2}}
             &\leq 
@@
             (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
+            \theta(\calT)
+            \kappa_{\maxcol}(\calT)
             B_{T}^{2}
@@
                 \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
+                \kappa_{\maxcol}(\calT)
             \Big)            
@@
             \\
-            \| \Jacobian \Xi_{1}^{-1} \|
+            \| \Jacobian \Xi_{1}^{-1} \|_{\cye{2}}
             &\leq  
@@
             (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
+            \theta(\calT)
+            \kappa_{\maxcol}(\calT)
             B_{T}
@@
             (k+1)^{n}
-            \diameterratio(\calT)^{n}
+            \theta(\calT)^{n}
             B_{T}^{n}
-            \aspectratio(\calT)^{n}
+            \kappa_{\maxcol}(\calT)^{n}
             ,
@@
             (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
+            \theta(\calT)^{n}
+            \kappa_{\maxcol}(\calT)^{n}
             .
@@
         \begin{align*}
-            \| \Jacobian \Xi_{2} \|
+            \| \Jacobian \Xi_{2} \|_{\cye{2}}
             &\leq 
@@
             \frac 1 4
-            % \left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
-            \left( 4 + (k+1) \aspectratio(T) \right)
-            \cdot 
+            % \left( \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 } \right)
+            \left( 4 + (k+1) \kappa_{\maxcol}(T) \right)
             (k+1) 
-            \aspectratio(\calT)
+            \kappa_{\maxcol}(\calT)
             B_{T}
@@
                 \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            \\
-            \| \Jacobian \Xi_{2}^{-1} \|
+                \kappa_{\maxcol}(\calT)
+            \Big)\cye{,}            
+            \\
+            \| \Jacobian \Xi_{2}^{-1} \|_{\cye{2}}
             &\leq  
@@
             \frac 1 2
-            %\left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
-            \left( 4 + (k+1) \aspectratio(T) \right)
-            \cdot 
+            %\left( \sqrt{ 9 + (k+1)^2 \kappa_{\maxcol}(T)^2 } + \sqrt{ 1 + (k+1)^2 \kappa_{\maxcol}(T)^2 } \right)
+            \left( 4 + (k+1) \kappa_{\maxcol}(T) \right)
             (k+1) 
-            \aspectratio(\calT)
+            \kappa_{\maxcol}(\calT)
             \Big( 
@@
                 \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
+                \kappa_{\maxcol}(\calT)
+            \Big)\cye{.}            
         \end{align*}
@@
             = 
-            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
+            \frac{ \| A_{{G}}^{-1} x \|_{\cye{2}}_{1} }{ \| A_{K}^{-1} x \|_{\cye{2}}_{1} } x
             .
@@
             = 
-            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x
+            \frac{ \| A_{K}^{-1} x \|_{\cye{2}}_{1} }{ \| A_{{G}}^{-1} x \|_{\cye{2}}_{1} } x
             .
@@
         We see that the last summand is an oblique projection of $y$. 
-        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes.
+        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|_{\cye{2}}$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes.
 We conclude that
@@
              \geq 
-             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
+             \sigma_{\min}( A_{K}^{-1} ) \| x \|_{\cye{2}}.
         \]
@@
         \begin{align*}
-            \| \Jacobian \Psi(x) \|
+            \| \Jacobian \Psi(x) \|_{\cye{2}}
             &\leq 
@@
         \begin{align*}
-            \| \Jacobian \Psi^{-1}(x) \|
+            \| \Jacobian \Psi^{-1}(x) \|_{\cye{2}}
             &\leq 
@@
              &\leq 
-             \Czwei{n} \geometricshapemeasure(K) \diam(K)
-             \leq 
-             2 \Czwei{n} \geometricshapemeasure(\calT) \diam(K)^{-1}
+             \Czwei{n} \kappa(K) \diam(K)
+             \leq 
+             2 \Czwei{n} \kappa(\calT) \diam(K)^{-1}
              \\
@@
              \\ 
-             \geometricshapemeasure( A_{K} )
+             \kappa( A_{K} )
              &\leq 
-             \Cdrei{n} \geometricshapemeasure(K) \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+             \Cdrei{n} \kappa(K) \leq 2 \Cdrei{n} \kappa(\calT)
              .
@@
              &\leq 
-             \Czwei{n} \geometricshapemeasure({G}) \diam({G})
-             \leq 
-             4 \Czwei{n} \geometricshapemeasure(\calT) \diam(G)^{-1},
+             \Czwei{n} \kappa({G}) \diam({G})
+             \leq 
+             4 \Czwei{n} \kappa(\calT) \diam(G)^{-1},
              \\
@@
              \\ 
-             \geometricshapemeasure( A_{{G}} )
+             \kappa( A_{{G}} )
              &\leq 
-             \Cdrei{n} \geometricshapemeasure({G}) \leq 4 \Cdrei{n} \geometricshapemeasure(\calT)
-             .
-        \end{align*}
-        All the diameters above are comparable up to a factor of $\diameterratio(\calT)$.
+             \Cdrei{n} \kappa({G}) \leq 4 \Cdrei{n} \kappa(\calT)
+             .
+        \end{align*}
+        All the diameters above are comparable up to a factor of $\theta(\calT)$.
         In summary,
         \begin{gather*}
-            \| \Jacobian \Theta_{|K}      \| \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+            \| \Jacobian \Theta_{|K}      \|_{\cye{2}} \leq 2 \Cdrei{n} \kappa(\calT)
             ,
             \qquad 
-            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
-            ,
-            \\
-            \| \Jacobian \Xi(x) \|
+            \| \Jacobian \Theta_{|K}^{-1} \|_{\cye{2}} \leq 2 \Cdrei{n} \kappa(\calT)
+            ,
+            \\
+            \| \Jacobian \Xi(x) \|_{\cye{2}}
             \leq 
@@
             4 
-            \geometricshapemeasure(\calT) 
+            \kappa(\calT) 
             \Ceins{n} 
             \Czwei{n} 
-            \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
+            \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
             \left( 
@@
                 n
-                2 \Cdrei{n} \geometricshapemeasure(\calT)
+                2 \Cdrei{n} \kappa(\calT)
                 4 
-                \geometricshapemeasure(\calT) 
+                \kappa(\calT) 
                 \Ceins{n} 
                 \Czwei{n} 
-                \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
+                \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
             \right) 
-            2 \Cdrei{n} \geometricshapemeasure(\calT)
-            ,
-            \\
-            \| \Jacobian \Xi^{-1}(x) \|
+            2 \Cdrei{n} \kappa(\calT)
+            ,
+            \\
+            \| \Jacobian \Xi^{-1}(x) \|_{\cye{2}}
             \leq 
@@
             2 
-            \geometricshapemeasure(\calT) 
+            \kappa(\calT) 
             \Ceins{n} 
             \Czwei{n} 
-            \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
+            \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
             \left( 
@@
                 n
-                2 \Cdrei{n} \geometricshapemeasure(\calT)
+                2 \Cdrei{n} \kappa(\calT)
                 2 
-                \geometricshapemeasure(\calT) 
+                \kappa(\calT) 
                 \Ceins{n} 
                 \Czwei{n} 
-                \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
+                \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
             \right) 
-            2 \Cdrei{n} \geometricshapemeasure(\calT)
+            2 \Cdrei{n} \kappa(\calT)
             .
@@
     where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
-    While the reflection and deformation mappings in Theorem~\ref{theorem:starreflection} serve our purpose,
+    While the reflection and deformation mappings in \cye{Proposition}~\ref{proposition:starreflection} serve our purpose,
     it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
@@
 
-\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-We are now in the position to estimate Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions.
+\section{\cye{Combinatorial} Poincar\'e--Friedrichs \cye{constants over} triangulated domains\cye{: the exterior derivative case}}\label{section:poincarefriedrichs}
+
+We are now in the position to estimate Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this \cye{in particular} includes the curl and divergence operators in three \cye{space} dimensions.
 The estimates require local Poincar\'e--Friedrichs constants over simplices, 
@@
 
+\subsection{\cye{Poincar\'e--Friedrichs constants over an $n$-simplex}}
+
 The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator}
@@
 \begin{lemma}\label{lemma:PFexteriorsimplex}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. \todo{MV: We need weakly Lipschitz, right?}
     Let $0 \leq k < n$. 
@@
     there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
-    with $\cartan u = \cartan w$ and 
+    with $\cartan w = \cartan u$ and 
     \begin{align*}
@@
         \leq 
+        \underbrace{
         n A_{\Poinc}(n,k+1) 
@@
         \diam(\Omega)
+        }_{\cye{=:C_{{\rm{PF}},k,\Omega,p}}}
         \| \cartan u \|_{L^{p}(\Omega)}
@@
 \begin{proof}
-    This follows from the discussion in Section~\ref{section:potentialoperator}.
+    This follows from~\cye{Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) =         \vol_{n}(B_1(0)) \diam(\Omega)^{n}$}.
 \end{proof}
@@
 These constants are generally not optimal. 
-For example, when $p=2$ and only the divergence is considered, 
+For example, when $p=2$ and \cye{when} only the divergence is considered, 
 we have the following improved estimate.
@@
     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
+    Then for each $\bfu \in \bfH(\divergence,\Omega)$ \todo{MV: We need weakly Lipschitz, right?} there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
     \begin{align*}
@@
 \begin{proof}
-    This is a reduction to Friedrichs' inequality. 
+    This is a reduction to \cye{the} Friedrichs inequality. 
     Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
     Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
+    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to \cye{the} Friedrichs inequality. 
     The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
@@
 \end{proof}
+
+\subsection{\cye{Poincar\'e--Friedrichs constants over an $n$-simplex with homogeneous Dirichlet condition on some faces}}
 
@@
     Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    $\trace_{F_i} u = 0$ for $0 \leq i \leq l$.
     Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq l$
+    $\trace_{F_i} w = 0$ for $0 \leq i \leq l$
     and  
     \begin{align*}
-        \cartan u = \cartan w,
+        \cartan w = \cartan u,
         \quad 
-        \| w \| 
+        \| w \|_{\cye{L^{p}(\Omega)}}
         \leq 
         C_{\PF,\Gamma,l,k,p}(T)
-        \diam(T)^{k} 
-        \| \cartan u \|
-        .
-    \end{align*}
+        \diam(T)^{\cye{k}} 
+        \| \cartan u \|_{\cye{L^{p}(\Omega)}}
+        .
+    \end{align*}\todo[inline]{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
+Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
+Moreover, so far, all the constants $C_{{\rm{PF}},T,p}$, $C_{{\rm{PF}},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\rm{PF}},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
+Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
+We should unify.}
     Here, $C_{\PF,\Gamma,l,k,p}(T) > 0$ is a constant such that 
@@
         2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \algebraicshapemeasure(T)^{k-1}
-        \Ceins{n}(T)
+        \kappa_{2}(T)^{k-1}
+        \Ceins{n}\cye{\cancel{(T)}}
         % \| \Jacobian \varphi \|^{k}
         .
-    \end{align*}
+    \end{align*}\todo{MV: ???}
 \end{lemma}
 \begin{proof}
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
+    There exists $\varphi : \hat T \rightarrow \cye{T}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
     We can also assume that the face of $\hat T$
@@
 
-    In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m+1})}
+    In addition to that, by \cye{Proposition}~\ref{proposition:pullbackestimate}:
+    \begin{align*}
+        \| w \|_{L^{p}(\cye{T})}
         &\leq 
@@
         \| \Jacobian \varphi \|^{k}
-        \cdot 
         \| \cartan u \|_{L^{p}(T)}
         .
-    \end{align*}
-    The second inequality follows.
+    \end{align*}\todo{MV: the norms of the Jacobians have to be fixed.}
+    The second inequality follows.\todo{MV: Please a few more details.}
 \end{proof}
@@
     \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
-    C_{\PF,\Gamma,l,k,p}(T)   
-\end{align*}
+    C_{\PF,\Gamma,l,k,p}(T) \cye{.}
+\end{align*}
+
+\subsection{\cye{Poincar\'e--Friedrichs constants over a shellable triangulation}}
 
 Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
-For each $1 \leq m \leq M$, there exists a simplex $S_{m} \in \calT$ 
-such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
-We then let $U_{m}$ be the closure $\patch_{\calT}(S_{m}) \setminus T_{m}$,
-and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
-
-The main result of this manuscript is the following theorem.
+For each $1 \leq m \leq M$, there exists a simplex $S_{m\cye{-1}} \in \calT$ 
+such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $\cye{\cancel{T_{m} \in}} \patch_{\calT}(S_{m\cye{-1}})$.
+\cye{This is precisely $S_m \in \calT$ from Lemma~\ref{lemma:existenceofstar} (there the last simplex is called $T_{m+1}$)}.
+\todo[inline]{MV: It might be good to synchronize the indices between the shellability definitions in Section~\ref{section:shellability} and Theorems~\ref{theorem:poincarefriedrichsestimate:grad}, \ref{theorem:poincarefriedrichsestimate:gradzwei}, \ref{theorem:poincarefriedrichsestimate:exterior}, \ref{theorem:poincarefriedrichsestimate:exterior:contraction}.}
+We then let $U_{m \cye{-1}}$ be the closure \cye{of} $\patch_{\calT}(S_{m\cye{-1}}) \setminus T_{m}$,
+and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m\cye{-1}})$. 
+The main result of this manuscript \cye{for nonconvex and non-star-shaped triangulated domains} is the following theorem.
 
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with \cye{an $n$-dimensional} shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_{\cye{M}}$ be a shelling.
     Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for each $T_{m} \in \calT$ in the shelling
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
+    and such that for each $T_{m} \in \calT$ in the shelling\cye{, $1 \leq m \leq M$,} 
     we have the following recursive estimate: 
@@
         \leq  
-        C_{\PF,\Gamma,k,p}(\calT) 
+        C_{\PF,\cye{T_m, I_{m-1}},k,p}(\calT) 
         \diam(T)^{k} 
@@
     \end{align*}
-    \todo{The notation $U_m$ should be settled in the definition of shellings.}
-\end{theorem}
+    \todo{MWL: The notation $U_m$ should be settled in the definition of shellings.}
+\end{theorem}\todo{MV: I think we should also write down the bound for $\| w \|_{L^{p}(\Omega)}.$}
 
@@
     This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_{\cye{M}}$. 
+    We write $\Omega_m := \cup_{j=0}^{m} T_j$, \cye{$0 \leq m \leq M$,} which is \cye{by Lemma~\ref{lemma:shell_triang_man}} a triangulated $n$-dimensional submanifold with boundary.
+\todo[inline]{MV: It might also be good to synchronize the notations $X_{m}$ and $\Omega_m$.
+I would go for $X_{m}$, since this is a union of $n$-simplices (closed), whereas $\Omega_m$ has a connotation of a domain (open).}
+    For $0 < m \leq M$, by \cye{the definition of shellability in Section~\ref{section:shellability}}, $T_{m}$ and $\cye{\Omega_{m-1}}$ share the interface $\cye{I}_{m\cye{-1}}$, which is a collection of faces of $T_{m}$.
+    \cye{It follows from} Lemma~\ref{lemma:existenceofstar} \cye{that} adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m\cye{-1}} \in \calT$, \cye{where} $U_{m-1} \subseteq \Omega_{m-1}$ is the complement of $T_{m}$ in that newly completed star.\todo{MV: Short, as already explained above in details.}
+
+    \cye{We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound.} Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, \cye{on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex},} there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
     \begin{gather*}
@@
     \end{gather*}
-    %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
+    \cye{We define $w|_{T_0} := w_0$.}
+    Suppose now that $0 < m \leq M$ such that $w\cye{|_{\Omega_{m-1}}} \in W^{p}\Alt^{k}(\Omega_{m-1})$ with $\cartan w = \cartan u$ over $\Omega_{m-1}$.
+\cye{This is true for $m=1$.
+We now define, as in~\cite[equations~(5.12) and~(5.14)]{ern2020stable} or~\cite[equations~(6.7) and~(6.9)]{Chaum_Voh_p_rob_3D_H_curl_24},
+    \begin{align} \label{equation:w''_ext_der}
+    w|_{T_m} := u|_{T_m} + \Xi_{m}^{\ast}((w - u)|_{U_{m-1}}),
+    \end{align}
+\todo[inline]{MV: Direct and simple definition. Only one object. Namely avoids the checking of the compatibility of the boundary condition, which is a bit tedious and requires a rigorous apparatus.}
     where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
-    as in Theorem~\ref{theorem:starreflection}. 
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        . 
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
+    as \cye{$\Xi_{1}$} in \cye{Proposition}~\ref{proposition:starreflection} \cye{and the pullback is defined in~\eqref{equation:pullback}}. Clearly, $w|_{T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
+    \begin{align*}
+        \trace_{\cye{I}_{m\cye{-1}}} w|_{T_m} = \trace_{\cye{I}_{m\cye{-1}}} w|_{\Omega_{m-1}},
+    \end{align*}
+    since $u$ is trace continuous over $I_{m-1}$ and $\Xi_{m}$ is the identity along $I_{m-1}$, and
+    \begin{align*}
+        \cartan w = \cartan u \text{ over } T_m,
+    \end{align*}
+    since $\cartan w = \cartan u$ over $\Omega_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
+    \begin{align*}
+    w|_{\Omega_{m}} \in W^{p}\Alt^{k}(\Omega_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } \Omega_{m}. 
+    \end{align*}
+    }
 
@@
     \begin{align*}
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-    we can assume 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
+        \| \cye{w} \|_{L^{p}(T_{m})}
+        \leq  
+        \| \cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})} \|_{L^{p}(T_{m})}
+        + 
+        \| \cye{u - \Xi_{m}^{\ast}(u|_{U_{m-1}})} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, \cye{since $\trace_{I_{m-1}} (u|_{T_m} - \Xi_{m}^{\ast}(u|_{U_{m-1}})) = 0$, we have}
+    \begin{align*}
+        \| \cye{u - \Xi_{m}^{\ast}(u|_{U_{m-1}})} \|_{L^{p}(T_{m})} 
         &
         \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Theorem~\ref{theorem:pullbackestimate} to find 
-    \begin{align*}
-        \| w'_{m} \|_{L^{p}(T_{m})}
+        C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
+        + \| \cartan (\Xi_{m}^{\ast}(u|_{U_{m-1}})) \|_{L^{p}(T_{m})} )
+        .
+    \end{align*}\todo{MV: $\diam(T)^{\cye{k}}$???}
+    We also use \cye{Proposition}~\ref{proposition:pullbackestimate} to find 
+    \begin{align*}
+        \| \cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})} \|_{L^{p}(T_{m})}
         &\leq 
@@
         \| \Jacobian \Xi_{m} \|^{k}
-        \cdot 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})}
-        ,
-        \\
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        \| \cye{w} \|_{L^{p}(U_{m-1})}
+        ,
+        \\
+        \| \cartan (\cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})}) \|_{L^{p}(T_{m})}
         &\leq 
@@
         \| \Jacobian \Xi_{m} \|^{k+1}
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
-    We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
-    We use the properties of the reflection mapping in Theorem~\ref{theorem:starreflection}. 
+        \| \cartan \cye{u} \|_{L^{p}(U_{m-1})}
+        ,
+    \end{align*}\todo{MV: Which norms of the Jacobians and their determinants?}
+    \cye{where we have employed} that $\cartan w = \cartan u$ \cye{over $\Omega_{m-1}$}. 
+    Using the properties of the reflection mapping in \cye{Proposition}~\ref{proposition:starreflection}, the desired recursive estimate follows. 
 %     \begin{align*}
@@
 %         + 
-%         C_{\PF,T_{m},\Gamma_{m},k,p} 
+%         C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} 
 %         \| \cartan u      \|_{L^{p}(T_{m})} 
@@
 %         + 
-%         C_{\PF,T_{m},\Gamma_{m},k,p} 
+%         C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} 
 %         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
@@
 %     \end{align*}
-    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
 \end{proof}
 
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
+\todo[inline]{MV: Why a second theorem?
+Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
+Which is better and when?}
+
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an \cye{$n$-dimensional} shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_{\cye{M}}$ be a shelling.
     Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    such that 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
+    and such that \cye{for each $T_{m} \in \calT$ in the shelling, $1 \leq m \leq M$,
+    we have the following recursive estimate:} 
     \begin{align*}
@@
     which is a triangulated $n$-dimensional submanifold with boundary.
-    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
+    By assumption, $T_{m}$ and $\cye{\Omega_{m-1}}$ share the interface $\cye{I}_{m\cye{-1}} \subset \partial T_{m}$, 
     which is a collection of faces of $T_{m}$. 
@@
 
-    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Theorem~\ref{theorem:starreflection},
+    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in \cye{Proposition}~\ref{proposition:starreflection},
     which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
@@
     we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
-    Moreover, the desired estimate follow from Theorem~\ref{theorem:starreflection}.
-    The proof is complete. 
+    Moreover, the desired estimate follow from \cye{Proposition}~\ref{proposition:starreflection}.
+    The proof is complete. \todo{MV: I do not get this.}
 \end{proof}
@@
 
+\section{\cye{Outlook}} \todo{MV: Added this section at the end and moved here the corresponding contents from the introduction} \label{section:outlook}
+
+There are several avenues for further research going \cye{further from the results established in this manuscript}.
+
+\cye{Our} upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), where there are at least two points where the present techniques can be improved further.
+First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex \cye{\sout{domains}simplices} \todo{MV: ???} \cye{already} leave room for improvement.
+Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a star.
+In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
+Better transformations or more careful estimates are likely possible, as are completely different approaches.
+For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
+
+Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators \cye{in the sprit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now}.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
+
+\cye{Concerning the domains considered,} estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to \cye{\sout{spaces} domains} \todo{MV: ???} with simplicial homology groups of \disk s and spheres.
+In particular, domains with shellable triangulations are contractible.
+\cye{We believe that in the forthcoming works, t}hese estimates will \cye{become} subcomponent\cye{s} in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+
 \section*{Acknowledgments}
 
-MWL appreciates helpful remarks by Abdellatif Aitelhad and by Martin Costabel.
-
-\bibliographystyle{plain}
+MWL appreciates helpful remarks by Abdellatif Aitelhad.
+
+%\bibliographystyle{plain}
+\bibliographystyle{acm_mod}
 \bibliography{library}

### 2024-09-27 main.tex
first batch of changes

--- 2024-09-19 main.tex
@@
 
+% Added by MV 
+\usepackage{bm} % preferred version of bold symbols
+\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
+\usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
+\usepackage[textsize=tiny,color=blue!50!white]{todonotes}
+\setlength{\marginparwidth}{2cm}
+
+\newcommand\cye[1]{%
+\protect\leavevmode
+\begingroup
+    \color{red!35!yellow}%
+    #1%
+\endgroup
+}
+
 \usepackage{enumitem}
@@
 
-\title{Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations}
 \author{
@@
     Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
+    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
 }
@@
 
-\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+\newcommand{\martin}[1]{\textcolor{red}{TODO: #1}}
 \newcommand{\notice}[1]{\textcolor{red}{REMARK: #1}}
+\newcommand{\disk}{\cye{ball}}
 
@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations.
-This class of triangulations includes local stars in dimension two and three.
+    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
+    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
     The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
@@
     As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
-    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
+    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
+    \martin{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
+    \cye{Computational examples illustrate the theoretical findings.}
+    \\
+
+    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
+    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
+    \cye{We derive} computable bounds \cye{on} the operator norms of our potentials that only depend on the geometry.
+We thus obtain computable upper bounds for \cye{constants in} Poincar\'e--Friedrichs inequalities \cye{as well as} computable lower bounds for the eigenvalues of several vector Laplacians.
+    As a result with independent standing, we \cye{also} establish Poincar\'e--Friedrichs inequalities \cye{with computable constants} for the $L^{p}$ de~Rham complex over convex bounded domains.
+    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
+    \cye{Computational examples illustrate the theoretical findings.}
 \end{abstract}
+
+\tableofcontents
+\todo[inline]{MV: Added table of contents: for us, to see the structure of and the main terminology used in the paper}
 
@@
 We consider the latter outcome to be of independent interest. 
-% DONE \todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
+% DONE \martin{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 % Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
-\todo{What is the best place for this paragraph?}
+\martin{What is the best place for this paragraph?}
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
@@
 % Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\todo{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
+% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\martin{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
 
@@
 
-\todo{MWL: The different geometric quantities in this section should really be just what is needed later.
+\martin{MWL: The different geometric quantities in this section should really be just what is needed later.
 Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
@@
 \begin{comment}
-    \todo{Tighter estimate via geometry}
+    \martin{Tighter estimate via geometry}
     Matrix inverse lemma:
@@
 \end{align*}
-\todo{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+\martin{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
 In summary, after taking the average over $a \in \Omega$:
@@
     have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \todo{Describe Guzman and Salgado's contribution in more detail.} 
+    % Guzman and Salgado have estimated the operator norm. \martin{Describe Guzman and Salgado's contribution in more detail.} 
 \end{remark}
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \todo{not enough}
+        \martin{not enough}
 
@@
     \end{align*}
-    \todo{The notation $U_m$ should be settled in the definition of shellings.}
+    \martin{The notation $U_m$ should be settled in the definition of shellings.}
 \end{theorem}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{acm_mod}
 \bibliography{library}

### 2024-09-27 main.tex
process changes to vector calculus section

@@
 \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
-\usepackage[textsize=tiny,color=blue!50!white]{todonotes}
+% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
+\newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
 \setlength{\marginparwidth}{2cm}
@@
 
-\newcommand{\martin}[1]{\textcolor{red}{TODO: #1}}
+\newcommand{\mwl}[1]{\textcolor{red}{MWL: #1}}
 \newcommand{\notice}[1]{\textcolor{red}{REMARK: #1}}
@@
     This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
-    \martin{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
+    \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
     \cye{Computational examples illustrate the theoretical findings.}
@@
 We consider the latter outcome to be of independent interest. 
-% DONE \martin{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
+% DONE \mwl{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 % Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
-\martin{What is the best place for this paragraph?}
+\mwl{What is the best place for this paragraph?}
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
@@
 % Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\martin{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
+% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
 
@@
 
-\martin{MWL: The different geometric quantities in this section should really be just what is needed later.
+\mwl{MWL: The different geometric quantities in this section should really be just what is needed later.
 Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
@@
 \begin{comment}
-    \martin{Tighter estimate via geometry}
+    \mwl{Tighter estimate via geometry}
     Matrix inverse lemma:
@@
 
-We discuss the Sobolev spaces of vector calculus and exterior calculus 
-with particular emphasis on their transformation behavior. 
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-
-Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
+% We discuss the Sobolev spaces of vector calculus and exterior calculus 
+% with particular emphasis on their transformation behavior. 
+% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
+% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
+% TODO: Fuse these two paragraphs
+
+We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
+We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
+
+Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
+
+\subsection{Vector calculus}
+
+\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
+\begin{gather*}
+    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
+\end{gather*}
+\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
 First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
@@
     \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}
+\end{gather*}}
+
 We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
 Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
+\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
 $\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
-and
+$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
+$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
+We also introduce 
 $\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
@@
 \end{subequations}
-and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
-These mappings are invertible. 
+Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
+These transformations are invertible. 
 Bounds on the Lebesgue norms will follow from a more general result below. 
-% 
 We use the commutativity relations 
@@
     One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
-    In some literature conventions, the Piola transform is in the direction of the original mapping. 
+    The literature also knows the Piola transform in the direction of the original mapping. 
 \end{remark}
 
-%
-% trace properties 
-%
-
-%\section{Review of exterior calculus}
-
-Having discussed vector analysis, we review exterior calculus. 
-We begin with exterior algebra. 
+\subsection{Exterior calculus}
+
+%\cye{We now move to} exterior calculus. 
 %We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
+
+\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
 Let $V$ be a real vector space. 
@@
 \end{align*}
+
 We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
@@
 The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
+
+\subsection{Smooth differential forms}
 
@@
 \end{gather*}
+
+\subsection{Sobolev spaces of differential forms}
+
 Let us now turn our attention to Sobolev spaces of differential forms. 
@@
 \end{align*}
-We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. 
-The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.
-
-Lastly, we are also interested in differential forms whose trace vanishes along only a part of the boundary. 
+% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
+% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
+% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
+Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
 Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
@@
 \end{gather*}
-We know that $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
-
-We are interested in transformations of Sobolev tensor fields from one domain onto the other. 
+% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
+\mwl{This is a closed subspace.
+We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
+Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}
+
+\subsection{Transformations by bi-Lipschitz mappings}
+
+We are interested in transformations of Sobolev tensor fields from one domain onto \cye{an}other. 
 Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
 The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\begin{gather*} 
+\begin{align} \label{equation:pullback}
     \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
@@
     u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\end{gather*}
+\end{align}
 for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
@@
 
-\begin{theorem} \label{theorem:pullbackestimate}
+\begin{proposition} \label{proposition:pullbackestimate}
  Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
@@
   &\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-  \\&\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-  \| \Jacobian \phi^{-1} \|^{\frac{n}{p}}_{L^{\infty}(\Omega')}
+  \| \Jacobian \phi \|^{k}_{L^{\cye{\infty}}(\Omega)}
+  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\cye{\infty}}(\Omega')}
   \| u \|_{L^{p}\Lambda^{k}(\Omega')}
@@
  \end{align}
-\end{theorem}
+\end{proposition}
+\notice{MWL:I have simplified the statement to what is needed later.}
 
@@
     \end{CD}
+    \cye{\, ,}
     \end{gather*}
@@
     \end{CD}
+    \cye{\,.}
     \end{gather*}
@@
 
-We review a few approximation properties. 
+\subsection{Some approximation properties}
+
+We finally review a few approximation properties. 
 Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
@@
     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
+    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
 \end{lemma}
@@
 \end{align*}
-\martin{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+\mwl{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
 In summary, after taking the average over $a \in \Omega$:
@@
     have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \martin{Describe Guzman and Salgado's contribution in more detail.} 
+    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.} 
 \end{remark}
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \martin{not enough}
+        \mwl{not enough}
 
@@
 
-    In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
+    In addition to that, by Theorem~\ref{proposition:pullbackestimate}:
     \begin{align*}
@@
     \end{align*}
-    \martin{The notation $U_m$ should be settled in the definition of shellings.}
+    \mwl{The notation $U_m$ should be settled in the definition of shellings.}
 \end{theorem}
@@
     \end{align*}
-    We also employ Theorem~\ref{theorem:pullbackestimate} to find 
+    We also employ Theorem~\ref{proposition:pullbackestimate} to find 
     \begin{align*}

### 2024-09-27 main.tex
some additional local change in scalar estimate for poincare

--- 2024-09-27 main.tex
@@
-\documentclass[10pt,letterpaper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
@@
 
-% Added by MV 
-\usepackage{bm} % preferred version of bold symbols
-\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
-\usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
-\usepackage[textsize=tiny,color=blue!50!white]{todonotes}
-\setlength{\marginparwidth}{2cm}
-
-\newcommand\cye[1]{%
-\protect\leavevmode
-\begingroup
-    \color{red!35!yellow}%
-    #1%
-\endgroup
-}
-
 \usepackage{enumitem}
@@
 
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations}
 \author{
@@
     Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
+    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
 }
@@
 
-\newcommand{\martin}[1]{\textcolor{red}{TODO: #1}}
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
 \newcommand{\notice}[1]{\textcolor{red}{REMARK: #1}}
-\newcommand{\disk}{\cye{ball}}
 
@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
+    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations.
+This class of triangulations includes local stars in dimension two and three.
     The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
@@
     As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
-    \martin{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
-    \cye{Computational examples illustrate the theoretical findings.}
-    \\
-
-    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
-    \cye{We derive} computable bounds \cye{on} the operator norms of our potentials that only depend on the geometry.
-We thus obtain computable upper bounds for \cye{constants in} Poincar\'e--Friedrichs inequalities \cye{as well as} computable lower bounds for the eigenvalues of several vector Laplacians.
-    As a result with independent standing, we \cye{also} establish Poincar\'e--Friedrichs inequalities \cye{with computable constants} for the $L^{p}$ de~Rham complex over convex bounded domains.
-    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
-    \cye{Computational examples illustrate the theoretical findings.}
+    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
+    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
 \end{abstract}
-
-\tableofcontents
-\todo[inline]{MV: Added table of contents: for us, to see the structure of and the main terminology used in the paper}
 
@@
 We consider the latter outcome to be of independent interest. 
-% DONE \martin{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
+% DONE \todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 % Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
-\martin{What is the best place for this paragraph?}
+\todo{What is the best place for this paragraph?}
 Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
@@
 % Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\martin{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
+% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\todo{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
 
@@
 
-\martin{MWL: The different geometric quantities in this section should really be just what is needed later.
+\todo{MWL: The different geometric quantities in this section should really be just what is needed later.
 Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
@@
 \begin{comment}
-    \martin{Tighter estimate via geometry}
+    \todo{Tighter estimate via geometry}
     Matrix inverse lemma:
@@
         \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \left( 
-            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
-            +
-            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
-        \right)^{\frac 1 p}
-        \\&\qquad 
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-        \\&\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
         \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
@@
  \end{align*}
- Recursive application provides the following estimate:
-%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
-%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
-%  then 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &\leq 
-    \sum_{t=1}^{m} 
-    \left( 
-        \prod_{t < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
-    \right)
-    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
-    \| w_{F_t} \|_{L^{p}(U_{F_t})}
-    \\&\quad \quad \quad 
-    +
-    \left( 
-        \prod_{0 < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
-    \right)
-    \| w_{T_0}\|_{L^{p}(T_{0})}
-    .
- \end{align*}
+%  Recursive application provides the following estimate:
+%  \begin{align*}
+%     \| w_{m} \|_{L^{p}(T_m)}
+%     &\leq 
+%     \sum_{t=1}^{m} 
+%     \left( 
+%         \prod_{t < l \leq m} 
+%         \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+%     \right)
+%     \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
+%     \| w_{F_t} \|_{L^{p}(U_{F_t})}
+%     \\&\quad \quad \quad 
+%     +
+%     \left( 
+%         \prod_{0 < l \leq m} 
+%         \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+%     \right)
+%     \| w_{T_0}\|_{L^{p}(T_{0})}
+%     .
+%  \end{align*}
+%  We obtain the desired estimate. 
  % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
- We obtain the desired estimate. 
 %  \begin{align*}
@@
 \end{align*}
-\martin{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+\todo{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
 In summary, after taking the average over $a \in \Omega$:
@@
     have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \martin{Describe Guzman and Salgado's contribution in more detail.} 
+    % Guzman and Salgado have estimated the operator norm. \todo{Describe Guzman and Salgado's contribution in more detail.} 
 \end{remark}
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \martin{not enough}
+        \todo{not enough}
 
@@
     \end{align*}
-    \martin{The notation $U_m$ should be settled in the definition of shellings.}
+    \todo{The notation $U_m$ should be settled in the definition of shellings.}
 \end{theorem}
@@
 
-MWL appreciates helpful remarks by Abdellatif Aitelhad and by Martin Costabel.
-
-\bibliographystyle{acm_mod}
+MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
+
+\bibliographystyle{plain}
 \bibliography{library}

### 2024-09-27 main.tex
changes: Sobolev vector fields, potentials, nonlinear reflection

--- 2024-09-27 main.tex
@@
 \usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
-\usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
+% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
 % \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
@@
 
+{\color{red}
 We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
@@
 However, our purpose are explicit bounds for the operator norms, which are of independent interest.
-\\
-
-In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $D > 0$.
+
+In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
+}
+
+We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
+either the $L^{p}$ de~Rham complex without boundary conditions, \cye{or} the $L^{p}$ de~Rham with full boundary conditions. 
+The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who analyze them as pseudo\cye{-}differential operators over domains star-shaped with respect to a ball. 
+In comparison to their work, our discussion is more modest:
+we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+However, our purpose are explicit bounds for the operator norms, \cye{giving the Poincar\'e--Friedrichs constants}.
+Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open\todo{MV: Weakly Lipschitz??} set with diameter $\cye{\diam(\Omega)} > 0$\todo{MV: Unifying the notation.}.
+
+\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
 
@@
 We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator.
-\\
 
@@
 \end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives 
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
 \begin{align*}
@@
     &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{\diam(\Omega)} r^{n-k-1} \,dr 
     \\
     &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
+    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ \diam(\Omega)^{n-k} }{n-k}.
 \end{align*}
@@
 
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
+
 We begin with the Poincar\'e operator. 
+Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
 Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
@@
 %     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
     \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
     .
@@
 \begin{align*}
-    \int_{B_D(0)} |z|^{k+1-n} \,dz
+    \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
     &
     =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} \,dr
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} \,dr
     \\&
     =
-    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
-    .
-\end{align*}
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} \,dr
+    =
+    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
+    ,
+\end{align*}
+where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
 We compute 
-\begin{align*}
+\begin{align}
     &
-    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
+    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
     \\&
     =
-    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
+    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
     \\&
     =
-    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
+    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
     %\\&
     =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
-    .
-\end{align*}
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
+    \label{equation:A_Poinc}
+    .
+\end{align}
 Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
@@
     \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
-    D
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \diam(\Omega)
     \| u \|_{L^{p}(\Omega)}
@@
     \leq 
-    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-    D
+    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    \diam(\Omega)
     \| u \|_{L^{p}(\Omega)}
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
+% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 %
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
+
 We analyze the Bogovski\u{\i} potential operator by similar means. 
@@
     \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
     \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
+    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
     .
@@
 % \begin{align*}
-%     \int_{B_D(0)} |z|^{k+1-n} dz
+%     \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} dz
 %     =
-%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} dr
 %     =
-%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} dr
 %     =
-%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
+%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
 %     .
@@
     &
-    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
+    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
     \\&
     =
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
+    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
     \\&
     =
-    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
+    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
     %\\&
     =
-    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
+    \label{equation:A_Bogov}
     .
@@
     \leq 
-    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
-    D
+    \vol_{n-1}(S_1) A(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \diam(\Omega)
     \| u \|_{L^{p}(\Omega)}
@@
     \leq 
-    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-    D
+    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    \diam(\Omega)
     \| u \|_{L^{p}(\Omega)}
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
+% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
@@
 \\
+
+\subsection{Additional properties}
 
@@
 
-We are in the position to establish the main results of this section.
+\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
+
+\mwl{We are in the position to establish the main results of this section.
+Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.
 This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
 Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.
-
-\begin{theorem}
-    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
+though the dimension and the form degree enters the estimate.}
+
+We now state the main results of this section.
+\cye{Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\ell$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\ell)$ and $A_{\Bogov}(n,\ell)$}.
+
+\begin{theorem}\label{theorem:PF_EC}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
     We have bounded operators 
@@
         &\leq 
-        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-        D
+        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
         \| u \|_{L^{p}(\Omega)}
@@
         &\leq 
-        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
-        D
+        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
         \| u \|_{L^{p}(\Omega)}
@@
 \end{theorem}
+
+\todo[inline]{MV: Do $\Poinc_{\ell}$ and $\Bogov_{\ell}$ still map piecewise polynomials to piecewise polynomials?
+Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
+
 \begin{proof}
@@
     The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
     These potentials enable the analysis of de~Rham complexes without boundary conditions.
@@
     The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
     In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
@@
     Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they study domains star-shaped with respect to a ball. 
+    which is why they can study domains star-shaped with respect to a ball. 
     Instead, we average over the entire domain, which requires a convex geometry. 
@@
     % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
+
+    {\color{blue}
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they \cye{can} study domains star-shaped with respect to a ball. 
+    The\cye{ir} operators are pseudodifferential operators of negative order, 
+    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudodifferential operators 
+    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
+    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
+\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
+    }
 \end{remark}
@@
 
-This section is devoted to geometric operations that are crucial for our main result. 
-Consider the situation where we have an $n$-dimensional local star around some simplex $S$ and some $n$-dimensional simplex $T$ within that local star.
-We will need a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$.
+This section is devoted to geometric operations that are crucial for our main result in Section~\ref{section:poincarefriedrichs} below. 
+Consider the situation where we have an $n$-dimensional local patch (star) around some simplex $S$ and some $n$-dimensional simplex $T$ within that local star. 
+We will need a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$,
+similar to the two- and three-color maps in \cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}
 This homeomorphism is required to preserve the interface and we interpret it as a nonlinear reflection. 
@@
 we construct a bi-Lipschitz deformation which contracts the entire star into the complement of the newly completed star. 
+This deformation will enable additional estimates of Poincar\'e--Friedrichs constants.
 
@@
 
+\mwl{TODO: Illustration}
+
 We now provide the bi-Lipschitz nonlinear reflection across the interface between the selected simplex and the remainder of the local star
@@
 
-\begin{theorem}\label{theorem:starreflection}
+\begin{proposition}\label{proposition:starreflection}
     Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
@@
     \begin{align*}
-        \Xi_{2} : T \rightarrow U
+        \Xi_{2} : \underlying{\star_{\calT}(S)} \rightarrow U
     \end{align*}
@@
     \end{enumerate}
-\end{theorem}
+\end{proposition}
+\mwl{TODO: throughout this manuscript, all vector and operator norms should indicate the exponent.}
 \begin{proof}
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \mwl{not enough}
+        \mwl{TODO: not enough. Make this more explicit.}
 
@@
     where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
-    While the reflection and deformation mappings in Theorem~\ref{theorem:starreflection} serve our purpose,
+    While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
     it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
@@
 
-    In addition to that, by Theorem~\ref{proposition:pullbackestimate}:
+    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
     \begin{align*}
@@
     where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
-    as in Theorem~\ref{theorem:starreflection}. 
+    as in Proposition~\ref{proposition:starreflection}. 
     By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
@@
     \end{align*}
-    We also employ Theorem~\ref{proposition:pullbackestimate} to find 
+    We also employ Proposition~\ref{proposition:pullbackestimate} to find 
     \begin{align*}
@@
     We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
-    We use the properties of the reflection mapping in Theorem~\ref{theorem:starreflection}. 
+    We use the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}. 
 %     \begin{align*}
@@
 
-    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Theorem~\ref{theorem:starreflection},
+    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
     which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
@@
     we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
-    Moreover, the desired estimate follow from Theorem~\ref{theorem:starreflection}.
+    Moreover, the desired estimate follow from Proposition~\ref{proposition:starreflection}.
     The proof is complete. 
@@
 
-MWL appreciates helpful remarks by Abdellatif Aitelhad and by Martin Costabel.
+MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
 

### 2024-09-27 main.tex
process shellability

@@
 \begin{lemma}\label{lemma:boundarysimplices}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$. 
+    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying set is a manifold $\calM$. 
     \begin{itemize}
@@
     \item 
-    We $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
+    Let $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
     We will use the following fact:\footnote{To see this, one easily constructs a continuous deformation of $\calM$ into itself to move any chosen point on $S$ to any other chosen point on $S$.} if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$.
@@
     Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    As a consequence of the Jordan-Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
+    As a consequence of the Jordan--Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
     we know that $Y \setminus X$ has got two connected components.
@@
     % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    % As a consequence of the Jordan-Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
+    % As a consequence of the Jordan--Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
     % and thus $Y \setminus X$ has got two connected components.
@@
     If $z_F$ is an interior point of $\calM$, 
-    then we can assume by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
+    then it follows by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
     Consider $X = F \cap \partial \mathring B_F$.
@@
 at the intersection of topology and combinatorics. 
-These include the topology of local stars, which is a surprisingly non-trivial topic. 
+These include the topology of local patches (stars), which is a surprisingly non-trivial topic. 
 We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{locally vertex combinatorial}
-if the local star of every simpelx $S \in \calT$ is a triangulated $n$-dimensional ball that contains $S$.
+if the star of every simplex $S \in \calT$ is a triangulated $n$-dimensional ball that contains $S$.
 We gather some results that are hard to find in the literature.
@@
     \item 
-    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with midpoint $z_F$, and dimension $k$.
+    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{\cye{S}}$\todo{MV: OK?}, and dimension $k$.
     Let $\calS := \patch_{\calT}(S)$ be its star. 
@@
     Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    If the underlying space of $\calT$ is connected, then $\calT$ is strongly connected.
+    If the underlying space of $\calT$ is connected, then $\calT$ is \cye{face} connected. \mwl{TODO Add a hyphen to each such instance.}
 \end{lemma}
 \begin{proof}
-    We first show that each vertex star is strongly connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are strongly connected. 
-    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already strongly connected if all simplicial $n$-balls and $n$-spheres are strongly connected.
-    The induction argument implies that each vertex star in $\calT$ is strongly connected.
+    We first show that each vertex star is \cye{face} connected via a short induction argument.
+    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are \cye{face} connected. 
+    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already \cye{face} connected if all simplicial $n$-balls and $n$-spheres are \cye{face} connected.
+    The induction argument implies that each vertex star in $\calT$ is \cye{face} connected.
 
@@
     Such manifolds appear in dimension four and higher:
-    one example is the E8 manifold, which is a compact simply-connected topological $4$-manifold that is homeomorphic to the underlying set of any simplicial complex.
+    one example is the E8 manifold\todo{MV: reference?}, which is a compact simply-connected topological $4$-manifold that is not homeomorphic to the underlying set of any simplicial complex.
 The construction of such counterexamples typically involves an infinite procedure.
@@
 % 3. Shellability 
-\subsection{Shellable simplicial complexes}
-
-The notions of \emph{shelling} and \emph{shellable triangulation} have been discussed widely in combinatorial topology and polytopal theory. 
+\subsection{Shellable simplicial complexes}\label{subsection:shellability}
+
+The notions of shelling and shellable triangulation have been discussed widely in combinatorial topology and polytopal theory. 
 Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation of a manifold.
-We thus build upon the notion of shelling, as introduced in~\cite[Definition 8.1]{ziegler2012lectures},
-and our definition of shelling is equivalent to the notion of the shellings of simplicial complexes in the aforementioned reference; see also~\cite[Remark~8.3]{ziegler2012lectures}.
-
-Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
+This forces the intermediate triangulations to be particularly well-shaped. 
+We build upon the notion of shelling as introduced in~\cite[Definition 8.1]{ziegler1995lectures},
+where our definition of shelling is equivalent to the notion of the shellings of simplicial complexes, see also~\cite[Remark~8.3]{ziegler1995lectures}.
+
+\todo[inline]{MV: Shortened, narrowed, removed repetitions.}
+
+\mwl{Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
 by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
@@
 It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, 
-as this enables the inductive method of proof.
-\\
+as this enables the inductive method of proof.}
 
@@
 \begin{proof}
-    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
-    that constitute the local patch around some simplex $S$ of dimension $n-k$.
-    By assumption, $S$ must be a boundary simplex of $X_{m}$ and it is an interior simplex of $X_{m+1}$. 
-    But then $S$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
-    which means that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$. 
-    This had to be shown.
+    We know $I_{m}$ is a \cye{triangulated} submanifold of the boundary of $T$, and so it must be a collection of $k$ face\cye{\sout{t}}s \cye{of $T$, $1 \leq k \leq n$ ($k = n + 1$ can happen for the last enumerated simplex $m = M$ when $\calT$ is an $n$-sphere).
+$I_{m}$ also} constitutes \cye{a} local patch \cye{(star) of $(n-1)$-dimensional simplices around} some simplex $S_{\cye{m}}$ of dimension $n-k$ \cye{in $I_{m}$}.
+    By \cye{definition}, $S_{\cye{m}}$ \cye{is} be a boundary simplex of $X_{m}$\cye{,} and it is an interior simplex of $X_{m+1}$. 
+    But then $S_{\cye{m}}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
+    which means that $\patch_{X_{m+1}}(S_{\cye{m}}) = \patch_{\calT}(S_{\cye{m}})$. 
 \end{proof}

### 2024-09-27 main.tex
outlook and basic combinatorics

@@
 
-We gather basic notions and definitions concerning simplicial meshes.
+We gather here basic notions and definitions concerning simplicial meshes.
+
+\subsection{\cye{A triangulation or a simplicial complex}}
 
@@
 and its remaining points constitute the \textit{boundary} of the simplex.
-\\
-
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} 
-if it satisfies the following conditions: 
+
+A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
 % (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler2012lectures}).}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\todo{MV: Don't we only use $n$-dimensional simplicial complexes?
+That would be a simplification of our presentation.}\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is \sout{defined as} the union 
 \begin{align*}
@@
 \end{align*}
-We call any set \textit{trianguable} if it is the underlying set of some triangulation. 
+We call any set triangulable if it is the underlying set of some triangulation. 
 \\
@@
     Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics.~\cite{schrijver1998theory}
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra.~\cite{ziegler2012lectures}
+    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler2012lectures}.
 % \end{remark}
@@
 Given an $n$-dimensional simplicial complex $\calT$, 
-we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+we call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
 % TODO: Theo suggests reverse order of that sequence
 We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
-Clearly, strongly connected in $\calT$ is an equivalence relation among simplices. 
-A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component. 
+Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
+A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
+and we call $\calT$ \emph{face-connected} if it has only one face-connected component. 
 \\
@@
 For the agenda of this section, the following combinatorial notion of triangulations will be helpful. 
-Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
+Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
 a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
@@
 
-%  Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
+%  Since $\calT$ is face-connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
 We write $\Omega_m := \cup_{j=0}^{m} T_m$.
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly connected finite triangulation $\calT$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a face-connected finite triangulation $\calT$.
     Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
@@
 \begin{remark}
-    Not all triangu\cye{l}able sets admit a triangulation that is shellable. 
+    Not all triangulable sets admit a triangulation that is shellable. 
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations \cye{are} be shellable.
@@
 \begin{remark}
-    Not all trianguable sets admit a triangulation that is also shellable. 
+    Not all triangulable sets admit a triangulation that is also shellable. 
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
@@
 
+\section{\cye{Outlook}} \todo{MV: Added this section at the end and moved here the corresponding contents from the introduction} \label{section:outlook}
+
+There are several avenues for further research going \cye{further from the results established in this manuscript}.
+
+\cye{Our} upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), where there are at least two points where the present techniques can be improved further.
+First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex \cye{\sout{domains}simplices} \todo{MV: ???} \cye{already} leave room for improvement.
+Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a star.
+In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
+Better transformations or more careful estimates are likely possible, as are completely different approaches.
+For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
+
+Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators \cye{in the sprit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now}.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
+
+\cye{Concerning the domains considered,} estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to \cye{\sout{spaces} domains} \todo{MV: ???} with simplicial homology groups of \disk s and spheres.
+In particular, domains with shellable triangulations are contractible.
+\cye{We believe that in the forthcoming works, t}hese estimates will \cye{become} subcomponent\cye{s} in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+
+\mwl{
+% Future work % DONE: Theo : parts already mentioned ??? 
+% Computable reliable estimates are important: 
+% they quantify the fundamental stability properties of partial differential equations in vector analysis,
+% such as the Hodge Laplace equation. 
+There are several avenues for further research going from here. 
+The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
+There are at least two points where the present techniques can be improved further.
+First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
+Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
+In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
+Better transformations or more careful estimates are likely possible, as are completely different approaches.
+For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
+
+Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
+These topics remain for future research.
+
+Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
+In particular, domains with shellable triangulations are contractible.
+However, these estimates are important partial results.
+Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+}
+
 \section*{Acknowledgments}

### 2024-09-27 main.tex
typos

@@
 
-\newcommand{\mwl}[1]{\textcolor{red}{MWL: #1}}
-\newcommand{\notice}[1]{\textcolor{red}{REMARK: #1}}
+\newcommand{\mwl}[1]{\color{red}{MWL: #1}}
+\newcommand{\notice}[1]{\color{red}{REMARK: #1}}
 \newcommand{\disk}{\cye{ball}}
@@
     Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    If the underlying space of $\calT$ is connected, then $\calT$ is \cye{face} connected. \mwl{TODO Add a hyphen to each such instance.}
+    If the underlying space of $\calT$ is connected, then $\calT$ is face-connected.
 \end{lemma}
 \begin{proof}
-    We first show that each vertex star is \cye{face} connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are \cye{face} connected. 
-    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already \cye{face} connected if all simplicial $n$-balls and $n$-spheres are \cye{face} connected.
-    The induction argument implies that each vertex star in $\calT$ is \cye{face} connected.
+    We first show that each vertex star is face-connected via a short induction argument.
+    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are face-connected. 
+    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already face-connected if all simplicial $n$-balls and $n$-spheres are face-connected.
+    The induction argument implies that each vertex star in $\calT$ is face-connected.
 
@@
     we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
-    As each vertex star is \cye{face} connected, 
+    As each vertex star is face-connected, 
     we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
     is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-    This just means that $\calT$ is \cye{face} connected. 
+    This just means that $\calT$ is face-connected. 
 \end{proof}

### 2024-09-27 main.tex
triangulation shape measure; scalar potential over triangulations; some macros

@@
 \usepackage{tikz-3dplot}      % 3d plots 
+\usepackage{enumitem}
+\setitemize[1]{left=0.0cm}
 
@@
 
-\usepackage{enumitem}
-\setitemize[1]{left=0.0cm}
+\newcommand{\mwl}[1]{{\color{red} MWL: #1}}
+\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
+\newcommand{\disk}{\cye{ball}}
 
@@
 }
-
-% Theorem environments
-
-\newcommand{\mwl}[1]{\color{red}{MWL: #1}}
-\newcommand{\notice}[1]{\color{red}{REMARK: #1}}
-\newcommand{\disk}{\cye{ball}}
 
@@
 Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
 In particular, local stars in 2D and 3D triangulations are shellable. 
@@
 Such triangulations are called \textit{shellable}.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
 % In particular, local stars in 2D and 3D triangulations are shellable. 
@@
     and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler2012lectures}.
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
 % \end{remark}
@@
 where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
-We recall that the $\ell^{2}$ operator norm of $\|A\|_{2}$ agrees with $\sigma_{\max}(A)$,
+We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
 and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
@@
     \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
-%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
+%     \sup_{ \varphi : \Delta^n \rightarrow T } \matnorm{\Jacobian \varphi}_{\maxcol} \matnorm{ \Jacobian \varphi^{-1} }_{\maxcol}
     ,
@@
 
-We gather a few relationships between geometric and algebraic entities and compare the different shape measures.
+We now gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
 
@@
     \begin{gather*}
-        \| \Jacobian \varphi \|
+        \matnorm{\Jacobian \varphi}
         \leq 
@@
         \qquad 
-        \| \Jacobian \varphi^{-1} \|
+        \matnorm{ \Jacobian \varphi^{-1} }
         \leq 
@@
         \quad 
-        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
+        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
         \quad 
@@
 %     \begin{align*}
-%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
+%         \matnorm{ \Jacobian \varphi^{-1} }_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
 %         .
@@
     The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
+    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
     Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
@@
 
-We are interested in the maximal ratio of volumes between neighboring $n$-simplices, written $\volumeratio(\calT)$,
+We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
 and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
@@
 \end{align}
-Whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
-that preserves $F$. We define 
+Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
+that preserves $F$. We then define 
 \begin{align}\label{math:reflectionmeasure}
@@
     \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \| \Jacobian \Xi_{T,T'} \|
+    \matnorm{ \Jacobian \Xi_{T,T'} }
 \end{align}
@@
     \begin{align*}
-        \| \Jacobian \Xi \|
+        \matnorm{ \Jacobian \Xi }
         \leq 
@@
     \begin{align*}
-        \| \Jacobian \Xi \|
-        \leq 
-        \| \Jacobian\phi_{2} \| \cdot \| \Jacobian\phi_{1}^{-1} \|
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }
         \leq 
@@
 %     \begin{align*}
-%         \| \Jacobian \Xi \|
+%         \matnorm{ \Jacobian \Xi }
 %         &
@@
 \begin{remark}
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ \cye{of~\eqref{math:volumecomparisonmeasure}} but not $\theta(\calT)$ \cye{of~\eqref{math:diametercomparison}}. 
     Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
-    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
+    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
     If we have an upper estimate for the number of simplices sharing a given vertex, 
@@
 %%%%%%%% END HERE
+
+\mwl{Throughout the manuscript, use a macro for opnorm and equip the matrices with the operator norm index.}
 
@@
 
+{\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
+\cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
+Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure.
+We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}.
+We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
+This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+}
+
 We construct scalar potentials over larger and larger intermediate subdomains. 
@@
 
+{\color{blue}\cye{We start by extending the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations} in a way which captures the correct asymptotic behavior as $p$ grows to infinity.
+\cye{Let us stress that face patches are not necessarily convex and remark that our result is in particular sharp when $T_1$ and $T_2$ have similar volumes and diameters}.}
+
 \begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
@@
 %         \leq 
-%         2 C_{\PF,{\rm EFNT},p}
+%         2 \Ceins{n} C_{\PF,{\rm EFNT},p}
 %         \max\left( 
@@
         \leq 
-        2 C_{\PF,{\rm EFNT},p}
+        2 \Ceins{n} C_{\PF,{\rm EFNT},p}
         \volumeratio(\calT)^{\frac 1 p}
@@
     \end{align*}
-    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
+    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$. \mwl{Introduce constant $C_{{\rm{PF}},T_1 \cup T_2,p}$}
 \end{lemma}
@@
     and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
-    Write $\hat U := \Delta_1 \cup \Delta_2$.
+    Write $\hat U := \Delta_1 \cup \Delta_2$, which is (crucially) convex. .
     We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
@@
 %         |\det(\Jacobian \varphi_1^{-1})|
-%         \cdot \| \Jacobian \varphi_1 \|^{p}
+%         \cdot \matnorm{ \Jacobian \varphi_1 }^{p}
 %         \cdot 
@@
 %         |\det(\Jacobian \varphi_2^{-1})|
-%         \cdot \| \Jacobian \varphi_2 \|^{p}
+%         \cdot \matnorm{ \Jacobian \varphi_2 }^{p}
 %         \cdot 
@@
 %         \max\left( 
-%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
+%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \matnorm{ \Jacobian \varphi_1 }^{p}
 %             ,
-%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
+%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \matnorm{ \Jacobian \varphi_2 }^{p}
 %         \right)
@@
         \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|
+            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_1 }
             ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|
+            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_2 }
         \right)
@@
     Notice that $\hat U$ is convex and has diameter $2$. 
-    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
+    Thus, due to~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
     \begin{align*}
@@
     \end{align*}
-    Noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\| \Jacobian \varphi_i \| \leq \Ceins{n} \diam(T_i)$
-    for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}, we conclude the desired result.
+    \cye{In the last equality, we have also used $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$ that we have already employed in~\eqref{equation:Hong_Pan}.}
+    Noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$ for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}, we conclude the desired result.
 \begin{comment}
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_m = T$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a face-connected $n$-dimensional finite triangulation $\calT$.
+    We fix an $n$-simplex $T_0 \in \calT$ and for all $n$-simplices $T \in \calT$ 
+    we fix a strong path $T_0, T_1, \dots, T_{M} = T$.
     Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
@@
     \end{align*}
-    \todo{Rewrite this result.}
+    \todo{Rewrite this result. First a local recursive one, then a global bound}
+    \todo{Ensure big $M$ at all indices here.}
     When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
@@
 \end{theorem}
-
+\begin{proof}
+\todo[inline]{MV: Reworked and simplified the beginning of the proof.}
+ Let $u \in W^{1,p}(\Omega)$. 
+ \cye{On the first} simplex $T_{0}$, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+ \begin{gather*}
+    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+ \end{gather*}
+ In particular, $c_{0} := \cye{w_0} - \cye{u}$ is a constant function. 
+ \cye{We then define 
+  \begin{align*}
+    w := u + c_0
+  \end{align*} 
+  (note that $w|_{T_{0}} = w_0$). Clearly,} 
+ $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$. \cye{We verify that $w$ fulfills the desired estimate.}
+
+ Let $T \in \calT$ be any $n$-simplex. 
+ By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}. 
+ For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}. \cye{Recall the notation $U_{F_m} := T_m \cup T_{m-1}$.}
+ We let $u_{F_m} \in W^{1,p}(U_{F_m})$ \cye{be} such that $\nabla u_{F_m} = \nabla u$ over $U_{F_m}$ and 
+ \begin{align*}
+    \| u_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\rm{PF}},U_{F_m},p} \| \nabla u_{F_m} \|_{L^{p}(U_{F_m})},
+ \end{align*}
+ where the computable constant $C_{{\rm{PF}},U_{F_m},p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
+\cye{Since $\nabla (w|_{U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u|_{U_{F_m}})$, we can define the constant
+ \begin{align*}
+    c_{m} := w|_{U_{F_m}} - u_{F_{m}}.
+ \end{align*}
+ }
+ \cye{\sout{We finally write $\Omega_m := \cup_{j=0}^{m} T_m$, which is triangulated $n$-dimensional submanifold with boundary}}.\todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
+As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
+
+\begin{figure}[h]
+\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
+\end{figure}
+
+ We \cye{now} assess the norm of the potential \cye{$w$}. \cye{For any $1 \leq m \leq M$,} we observe 
+ \begin{gather*}
+    \| \cye{w} \|_{L^{p}(T_m)}
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
+    +
+    \| c_{m} \|_{L^{p}(T_m)},
+    \\
+    \| c_{m} \|_{L^{p}(T_m)}
+    = 
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| c_{m} \|_{L^{p}(T_{{m-1}})},
+    \\ 
+    \| c_{m} \|_{L^{p}(T_{{m-1}})}
+    \leq 
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
+    .
+ \end{gather*}
+ \cye{Consequently},
+ \begin{align*}
+    \| \cye{w} \|_{L^{p}(T_m)}
+    &
+    \leq 
+    \| u_{F_m} \|_{L^{p}(T_m)}
+    \\&\qquad 
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
+    .
+ \end{align*}
+ We sum the two integrals of $u_{F_m}$. 
+ % 
+ In the special case $p=1$,
+ \begin{align*}
+    \| \cye{w} \|_{L^{1}(T_m)}
+    \leq 
+    \max\left(
+        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
+    \right)
+    \| u_{F_m} \|_{L^{1}(U_{F_m})}
+    +
+    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
+    \| \cye{w}\|_{L^{1}(T_{{m-1}})}
+    .
+ \end{align*}
+ In the special case $p=\infty$, 
+ \begin{align*}
+    \| \cye{w} \|_{L^{\infty}(T_m)}
+    \leq 
+    2
+    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
+    +
+    \| \cye{w}\|_{L^{\infty}(T_{{m-1}})}
+    .
+ \end{align*}
+ % 1/q = 1 - 1/p = (p-1)/p 
+ When $1 < p < \infty$, \cye{recalling the complementary exponent} $q = p/(p-1) \in [1,\infty]$, we observe \cye{using the H\"older inequality}
+ \begin{align*}
+    \| \cye{w} \|_{L^{p}(T_m)}
+    &\leq 
+    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
+    \left( 
+        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
+        +
+        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
+    \right)^{\frac 1 p}
+    \\&\qquad 
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
+    \\&\cye{=} 
+    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
+    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
+    +
+    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
+    .
+ \end{align*}
+ Recursive application provides the following estimate:
+%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
+%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
+%  then 
+ \begin{align*}
+    \| \cye{w} \|_{L^{p}(T_m)}
+    &\leq 
+    \sum_{t=1}^{m} 
+    \left( 
+        \prod_{t < l \leq m} 
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+    \right)
+    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
+    \| u_{F_t} \|_{L^{p}(U_{F_t})}
+    \\&\quad \quad \quad 
+    +
+    \left( 
+        \prod_{0 < l \leq m} 
+        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+    \right)
+    \| u_{T_0}\|_{L^{p}(T_{0})}
+    .
+ \end{align*}
+ % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
+ We obtain the desired estimate. 
+%  \begin{align*}
+%     \| \cye{w} \|_{L^{p}(T_m)}^{p}
+%     &\leq 
+%     (m+1)^{p-1}
+%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
+%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
+%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
+%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
+%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
+%     \\&\quad \quad \quad 
+%     +
+%     (m+1)^{p-1}
+%     \rho(\calT)^{m-1}
+%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
+%     .
+%  \end{align*}
+%  Notice that $p/q = p - 1$.
+ % 
+\end{proof}
 \begin{proof}
@@
 
+\cye{\begin{remark}
+The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} overestimates the best one increasingly with increasing number of $n$-simplices in the triangulation $\calT$.
+For this reason, we target its use to local patches (stars), in particular nonconvex boundary stars such as that of Figure~\ref{figure:exhausting}.
+Clearly, the same building principle applies when we can obtain a nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a  face-connected path.
+The proof proceeds verbatim, where we merely replace the simplices $T_{m}$ by the convex local patches $U_m$.
+This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a large decrease of the overestimation of the best Poincar\'e--Friedrichs constant.
+\end{remark}}
+
 \begin{lemma}\label{lemma:mixedbconsimplex}
-    Let $T$ be an $n$-simplex with a face $F$. 
+    Let $T$ be an $n$-simplex with a face $F$ and $p \in [1,\infty]$. 
     If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
@@
     \end{align*}
-    where $C_{\PF,T,F,p} > 0$ is a constant such that 
-    $C_{\PF,T,F,p} \leq \frac{1}{\sqrt[p]{p}} \diam(T)$.
+    where $C_{\PF,T,F,p} = \frac{1}{\sqrt[p]{p}} \diam(T)$ for $p < \infty$ and $C_{\PF,T,F,\infty} = 1$. 
 %     \begin{align*}
@@
     % The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Since the inequality follows from Rademacher's theorem when $p = \infty$,
+    Since the inequality follows from Rademacher's theorem in the limit case $p = \infty$,
     we assume $1 \leq p < \infty$. 
     Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
+    We trivially extend $u$ to a function over the entire $\bbR^{n}$.
     Without loss of generality, 
@@
     %With the fundamental theorem of calculus and H\"older's inequality: 
-    We verify
+    Using the fundamental theorem of calculus and H\"older's inequality, 
     \begin{align*}
@@
     for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$. 
-
     Very briefly verify that density argument: 
-    There exists $\varphi : \Delta^{n} \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
+    There exists affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
     We let $\hat u := u \circ \varphi$.
@@
 % \end{remark}
+
+The following potential construction and upper bound for the Poincar\'e--Friedrichs constant 
+serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+\cye{It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.}
+
+\todo[inline]{MV: Why a second theorem?
+We should explain the difference of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+Which is better and when?}
 
@@
 \end{theorem}
-
+\begin{theorem}%\label{theorem:poincarefriedrichsestimate:gradzwei}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an \cye{$n$-dimensional} \cye{face-}connected finite triangulation $\calT$.
+    Let $T_0 \in \calT$ be an $n$-simplex \cye{and} for all $n$-simplices $T \in \calT$, 
+    fix a \cye{face} path $T_0, T_1, \dots, T_{\cye{M}} = T$. For any $1 \leq l \leq \cye{M}$, let $F_l = T_l \cap T_{l-1}$.
+    Then for any $u \in W^{1,p}(\Omega)$ 
+    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
+    and such that for all $T \in \calT$\cye{, we have the following recursive estimate}:
+    \begin{align*}
+        \| \cye{w} \|_{L^{p}(T_{\cye{M}})}
+%         &\leq 
+%         \rho(\calT)^{\frac \cye{M} p}
+%         C_{\PF,T_{0},p} 
+%         \| \nabla u \|_{L^{p}( T_{0} )}
+%         +
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac {\cye{M}-l} p}
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l})} 
+%         \\&\qquad 
+%         +
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac {\cye{M}-l} p} \xi(\calT)
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l-1})} 
+%         \\
+        &\leq 
+        \sum_{l=1}^{\cye{M}} 
+        \rho(\calT)^{\frac {\cye{M}-l} p}
+        C_{\PF,T_{l},F_{l},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{l})} 
+            +
+            \rho(\calT)^{\frac {1} p}
+            \xi(\calT)
+            \| \nabla u \|_{L^{p}(T_{l-1})} 
+        \right)
+        \\&\quad 
+        + \rho(\calT)^{\frac{\cye{M}}{p}}
+        C_{\PF,T_{0},p} 
+        \| \nabla u \|_{L^{p}( T_{0} )}
+        .
+    \end{align*}
+%     \begin{align*}
+%         \| w_{\cye{M}} \|_{L^{p}(T_{\cye{M}})}
+%         &\leq 
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac{\cye{M}-l}{p}}
+%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}( T_{l} )}
+%         +
+%         \rho(\calT)^{\frac \cye{M} p}
+%         C_{\PF,T_{0},p} 
+%         \| \nabla u \|_{L^{p}( T_{0} )}
+%         .
+%     \end{align*}
+%     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
+\end{theorem}\todo{MV: Synchronized the announcement and notation with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+
+\begin{proof}
+\todo[inline]{MV: Reworked and simplified the proof.}
+
+\cye{We start as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}  Let $u \in W^{1,p}(\Omega)$. 
+ \cye{On the first} simplex $T_{0}$, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+ \begin{gather*}
+    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+ \end{gather*}
+ In particular, $c_{0} := \cye{w_0} - \cye{u}$ is a constant function. 
+ \cye{We then define 
+   \begin{align*}
+    w := u + c_0
+  \end{align*} 
+ (note that $w|_{T_{0}} = w_0$). Clearly,} 
+ $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$. \cye{We verify that $w$ fulfills the desired estimate.}
+
+ Let $T \in \calT$ be any $n$-simplex. 
+ By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}. 
+ For any $1 \leq m \leq M$, \cye{recall that} $F_m := T_m \cap T_{m-1}$ \cye{is}  a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}.
+
+    \cye{\sout{We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.}}
+   \todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
+As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
+
+\begin{figure}[h]
+\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
+\end{figure}
+
+    \cye{\sout{We use a recursive argument.}} Suppose that $\cye{1} < m \leq M$.
+    We define $w'_{m} := w\cye{|_{T_{m-1}}} \circ \Xi \in W^{1,p}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
+    %
+    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
+    \begin{align*}
+        \trace_{F_{\cye{m}}} w'_{m} = \trace_{F_{\cye{m}}} w\cye{|_{T_{m-1}}}
+        .
+    \end{align*}
+    We now define $w''_{m} \in W^{1,p}(T_{m})$ as
+\cye{    \begin{align}\label{equation:w''}
+        w''_{m} := u|_{T_{\cye{m}}} - w'_{m} + c_0 = w|_{T_{\cye{m}}} - w'_{m} = u|_{T_{\cye{m}}} - u\cye{|_{T_{m-1}}} \circ \Xi.
+    \end{align}
+    We crucially note that $w''_{m}$ is trace free on $F_{m}$ since
+    \begin{align*}
+        \trace_{F_{m}} w''_{m} = \trace_{F_{m}} (u|_{T_{\cye{m}}} - w'_{m} + c_0) = \trace_{F_{m}} (u|_{T_{m-1}} - w\cye{|_{T_{m-1}}} + c_0) = 0.
+    \end{align*}}
+    Lemma~\ref{lemma:mixedbconsimplex} gives\cye{, from the first expression in~\eqref{equation:w''}}
+    \begin{align*}
+        \| w''_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{\PF,T_{m},F_{m},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{m})} 
+            + 
+            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        \right) 
+        .
+    \end{align*}
+    We also employ\cye{~\eqref{math:reflectionmeasure} \sout{Lemma~\ref{lemma:volumecomparison}}} to find 
+    \begin{align*}
+        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
+        &
+        \leq 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \matnorm{ \Jacobian \Xi }
+        \| \nabla \cye{w} \|_{L^{p}(T_{m-1})}
+        \\&
+        \leq 
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla \cye{w} \|_{L^{p}(T_{m-1})}
+        \\&
+        \cye{=
+        \rho(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla u \|_{L^{p}(T_{m-1})} }
+        .
+    \end{align*}
+    \todo{MV: How $|\det(\Jacobian\Xi)|^{-\frac 1 p} \leq \rho(\calT)^{\frac 1 p}$ follows?}
+    \cye{From the second expression in~\eqref{equation:w''}, we then finally have} 
+    \begin{align*}
+        &
+        \| \cye{w} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \rho(\calT)^{\frac 1 p} 
+        \| \cye{w} \|_{L^{p}(T_{m-1})} 
+        + 
+        C_{\PF,T_{m},F_{m},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{m})} 
+            + 
+            \cye{\rho(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla u \|_{L^{p}(T_{m-1})}}
+        \right). 
+    \end{align*}
+\cye{Therefrom, the desired estimate follows.}
+\end{proof}
 \begin{proof}
@@
         |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi   \|
+        \matnorm{ \Jacobian \Xi   }
         \cdot 
@@
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler2012lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
+    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
 
@@
 
-\begin{remark}
+\begin{remark} \label{remark:reg_Poinc_Bog}
     The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
@@
     \begin{gather*}
-        \| \Jacobian\Xi_{1} \|          \leq \Cfive{n}{k}(\calT),
+        \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi_{1}^{-1} \|     \leq \Csechs{n}{k}(\calT),
-        \\
-        \| \det\Jacobian\Xi_{1} \|      \leq \Cdetfive{n}{k}(\calT),
+        \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
+        \\
+        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
         \quad 
-        \| \det\Jacobian\Xi_{1}^{-1} \| \leq \Cdetsechs{n}{k}(\calT),
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT),
     \end{gather*}
@@
     \begin{gather*}
-        \| \Jacobian\Xi_{2} \|          \leq \Csieb{n}{k}(\calT),
+        \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
         \quad 
-        \| \Jacobian\Xi_{2}^{-1} \|     \leq \Cacht{n}{k}(\calT),
-        \\
-        \| \det\Jacobian\Xi_{2} \|      \leq \Cdetsieb{n}{k}(\calT),
+        \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
+        \\
+        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
         \quad 
-        \| \det\Jacobian\Xi_{2}^{-1} \| \leq \Cdetacht{n}{k}(\calT),
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT),
     \end{gather*}
@@
         % \begin{align*}
-        %     \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
+        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
         %     \\
-        %     \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
+        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
         % \end{align*}
@@
         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
+        Then $\vecnorm{ h_z } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_z } = \sin(\beta) \vecnorm{ z_{S'} }$. 
         We study the singular values of the matrix 
@@
             \\ 
-            -2 \|b_z\|/\|h_z\| & 1
+            -2 \vecnorm{ b_z }/\vecnorm{ h_z } & 1
             \end{pmatrix}
@@
 %         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \| / \| h_{z} \|$, and we know $\|b_z\| \leq \|z_{S'}\|$. 
+        By the definition of the tangent, $\tan(\beta) \leq \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$, and we know $\vecnorm{ b_z } \leq \vecnorm{ z_{S'} }$. 
         Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
@@
         \begin{align*}
-            \frac{ \| b_{z} \| }{ \| h_{z} \| }
-            = 
-            \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
+            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
+            = 
+            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
             \leq 
@@
 %             = 
-%             \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
+%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
 %             \leq 
@@
             - 
-            \frac{ \|b_z\| }{ 2 \| h_{z} \| } 
+            \frac{ \vecnorm{ b_z } }{ 2 \vecnorm{ h_{z} } } 
             \hat b_{z} \otimes \hat h_{z}^{t}
@@
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence $\tan(\beta) = \| b_z \| / \| h_z \|$. It remains to study the singular values of the matrix 
+        Hence $\tan(\beta) = \vecnorm{ b_z } / \vecnorm{ h_z }$. It remains to study the singular values of the matrix 
         \begin{align*}
@@
         \begin{align*}
-            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \aspectratio(T).
+            \tan(\beta) = \frac{\vecnorm{ b_z }}{\vecnorm{ h_z }} \leq (k+1) \aspectratio(T).
         \end{align*}
@@
         \begin{gather*}
-            \| \Jacobian\Phi_{K} \| 
+            \matnorm{ \Jacobian\Phi_{K} } 
             \leq 
@@
             \\
-            \| \Jacobian\Phi_{K}^{-1} \| 
+            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
             \leq 
@@
         \begin{gather*}
-            \| \Jacobian\Psi(x) \|
+            \matnorm{ \Jacobian\Psi(x) }
             = 
@@
             \\
-            \| \Jacobian\Psi(z)^{-1} \|
+            \matnorm{ \Jacobian\Psi(z)^{-1} }
             = 
@@
         \begin{align*}
-            \| \Jacobian \Xi_{1} \|
+            \matnorm{ \Jacobian \Xi_{1} }
             &\leq 
@@
             \\
-            \| \Jacobian \Xi_{1}^{-1} \|
+            \matnorm{ \Jacobian \Xi_{1}^{-1} }
             &\leq  
@@
         \begin{align*}
-            \| \Jacobian \Xi_{2} \|
+            \matnorm{ \Jacobian \Xi_{2} }
             &\leq 
@@
             \\
-            \| \Jacobian \Xi_{2}^{-1} \|
+            \matnorm{ Jacobian \Xi_{2}^{-1} }
             &\leq  
@@
         \begin{align*}
-            \| \Jacobian \Psi(x) \|
+            \matnorm{ \Jacobian \Psi(x) }
             &\leq 
@@
         \begin{align*}
-            \| \Jacobian \Psi^{-1}(x) \|
+            \matnorm{ \Jacobian \Psi^{-1}(x) }
             &\leq 
@@
         \begin{gather*}
-            \| \Jacobian \Theta_{|K}      \| \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+            \matnorm{ \Jacobian \Theta_{|K}      } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
             ,
             \qquad 
-            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+            \matnorm{ \Jacobian \Theta_{|K}^{-1} } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
             ,
             \\
-            \| \Jacobian \Xi(x) \|
+            \matnorm{ \Jacobian \Xi(x) }
             \leq 
@@
             \\
-            \| \Jacobian \Xi^{-1}(x) \|
+            \matnorm{ \Jacobian \Xi^{-1}(x) }
             \leq 
@@
         \Ceins{n}(T)
-        % \| \Jacobian \varphi \|^{k}
+        % \matnorm{\Jacobian \varphi}^{k}
         .
@@
         |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \Jacobian \varphi^{-1} \|^{k-1}
+        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
         \| \tilde w \|_{L^{p}(\hat T)}
@@
         |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \| \Jacobian \varphi^{-1} \|^{k-1}
+        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
         \| \tilde w \|_{L^{p}(\tilde U)}
@@
         |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
-        \| \Jacobian \varphi \|^{k}
+        \matnorm{\Jacobian \varphi}^{k}
         \cdot 
@@
         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi_{m} \|^{k}
+        \matnorm{ \Jacobian \Xi_{m} }^{k}
         \cdot 
@@
         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-        \| \Jacobian \Xi_{m} \|^{k+1}
+        \matnorm{ \Jacobian \Xi_{m} }^{k+1}
         \cdot 
@@
 %         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-%         \| \Jacobian \Xi_{m} \|^{k} 
+%         \matnorm{ \Jacobian \Xi_{m} }^{k} 
 %         \| w_{m-1} \|_{L^{p}(U_{m-1})}
@@
 %         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-%         \| \Jacobian \Xi_{m} \|^{k+1} 
+%         \matnorm{ \Jacobian \Xi_{m} }^{k+1} 
 %         \| \cartan u \|_{L^{p}(U_{m-1})}

### 2024-09-29 draft.tex
completing edges
section on gradient potentials over triangulated domains

@@
 \begin{document}
+
+ \mwl{First estimate, alternative description}
+    We use a recursive argument.
+    Suppose that $0 < m \leq M$ such that there exists $w_{\iota(m)} \in W^{1,p}(\Omega_{\iota(m)})$ with $c_{0} = u - w_{\iota(m)}$.
+    In particular, $\nabla w_{\iota(m)} = \nabla u$ over $\Omega_{\iota(m)}$. 
+    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{\iota(m)}$. 
+    % Let $\hat T$ be the reference simplex.
+    % We fix affine diffeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
+    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
+    %
+    We define $w'_{m} := w_{\iota(m)} \circ \Xi \in W^{1,p}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow T_{\iota(m)}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
+    %
+    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
+    \begin{align*}
+        \trace_F w_{\iota(m)} = \trace_F w'_{m}
+        .
+    \end{align*}
+    %Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
+    There exists $w''_{m} \in W^{1,p}(T_{m})$ such that 
+    \begin{align*}
+        \nabla w''_{m} = \nabla u_{|T_{m+1}} - \nabla w'_{m}, 
+        \quad 
+        \trace_{F_{m}} w''_{m} = 0.
+    \end{align*}
+    This is true because 
+    \begin{align*}
+        \trace_{F_{m}}( \nabla u - \nabla w'_{m} ) 
+        &= 
+        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m}
+        \\&= 
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m}
+        = 
+        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{\iota(m)}
+        = 
+        0
+        .
+    \end{align*}
+    Setting $w_{m} := w_{\iota(m)}$ over $\Omega_{\iota(m)}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
+    we find 
+    \begin{gather*}
+        \nabla w_{m} = \nabla w'_{m} + \nabla w''_{m} = \nabla w'_{m} + \nabla u - \nabla w'_{m} = \nabla u,
+        % \end{gather*}
+        \\
+        % \begin{gather*}
+        \trace_{F_{m}} w_{m} = \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{\iota(m)}.
+    \end{gather*}
+    That means that $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_{m}$. 
+    In particular, $c_{0} = u - w_{m}$. 
+    Lemma~\ref{lemma:mixedbconsimplex} gives 
+    \begin{align*}
+        \| w''_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{\PF,T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
+        \\&
+        \leq 
+        C_{\PF,T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{\PF,T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    We also employ Lemma~\ref{lemma:volumecomparison} to find 
+    \begin{align*}
+        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
+        &
+        \leq 
+        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
+        \matnorm{ \Jacobian \Xi   }
+        \cdot 
+        \| \nabla w_{\iota(m)} \|_{L^{p}(T_{\iota(m)})}
+        \\&
+        \leq 
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
+        \cdot 
+        \| \nabla w_{\iota(m)} \|_{L^{p}(T_{\iota(m)})}
+        .
+    \end{align*}
+    Putting this all together, we use 
+    \begin{align*}
+        &
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq  
+        \volumeratio(\calT)^{\frac 1 p} 
+        \| w_{\iota(m)} \|_{L^{p}(T_{\iota(m)})} 
+        + 
+        C_{\PF,T_{m},F_{m},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{m})} 
+            + 
+            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        \right) 
+    \end{align*}
+    and 
+    \begin{align*}
+        \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq  
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
+        % C_{\PF,T_{m},F_{m},p} 
+        \| \nabla w_{\iota(m)} \|_{L^{p}(T_{\iota(m)})} 
+        \leq  
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
+        % C_{\PF,T_{m},F_{m},p} 
+        \| \nabla u \|_{L^{p}(T_{\iota(m)})} 
+        .
+    \end{align*}
+    The existence of $w \in W^{1,p}(\Omega)$ satisfying the recursive estimate follows.
+
+        \begin{align*}
+        \| w_{m} \|_{L^{p}(T_m)}
+%         &\leq 
+%         \volumeratio(\calT)^{\frac m p}
+%         C_{\PF,T_{0},p} 
+%         \| \nabla u \|_{L^{p}( T_{0} )}
+%         +
+%         \sum_{l=1}^{m} 
+%         \volumeratio(\calT)^{\frac {m-l} p}
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l})} 
+%         \\&\qquad 
+%         +
+%         \sum_{l=1}^{m} 
+%         \volumeratio(\calT)^{\frac {m-l} p} \reflectionestimate(\calT)
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l-1})} 
+%         \\
+        &\leq 
+        \volumeratio(\calT)^{\frac m p}
+        C_{\PF,T_{0},p} 
+        \| \nabla u \|_{L^{p}( T_{0} )}
+        \\&\quad 
+        +
+        \sum_{l=1}^{m} 
+        \volumeratio(\calT)^{\frac {m-l} p}
+        C_{\PF,T_{l},F_{l},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{l})} 
+            +
+            \volumeratio(\calT)^{\frac {1} p}
+            \reflectionestimate(\calT)
+            \| \nabla u \|_{L^{p}(T_{l-1})} 
+        \right)
+        .
+    \end{align*}
+    \begin{align*}
+        \| \cye{w} \|_{L^{p}(T_{\cye{M}})}
+%         &\leq 
+%         \rho(\calT)^{\frac \cye{M} p}
+%         C_{\PF,T_{0},p} 
+%         \| \nabla u \|_{L^{p}( T_{0} )}
+%         +
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac {\cye{M}-l} p}
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l})} 
+%         \\&\qquad 
+%         +
+%         \sum_{l=1}^{\cye{M}} 
+%         \rho(\calT)^{\frac {\cye{M}-l} p} \xi(\calT)
+%         C_{\PF,T_{l},F_{l},p} 
+%         \| \nabla u \|_{L^{p}(T_{l-1})} 
+%         \\
+        &\leq 
+        \sum_{l=1}^{\cye{M}} 
+        \rho(\calT)^{\frac {\cye{M}-l} p}
+        C_{\PF,T_{l},F_{l},p} 
+        \left( 
+            \| \nabla u \|_{L^{p}(T_{l})} 
+            +
+            \rho(\calT)^{\frac {1} p}
+            \xi(\calT)
+            \| \nabla u \|_{L^{p}(T_{l-1})} 
+        \right)
+        \\&\quad 
+        + \rho(\calT)^{\frac{\cye{M}}{p}}
+        C_{\PF,T_{0},p} 
+        \| \nabla u \|_{L^{p}( T_{0} )}
+        .
+    \end{align*}
+
+    Let $T \in \calT$ be any $n$-simplex. 
+    Now, let $T \in \calT$ be any $n$-simplex. 
+    By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}.
+
+    For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}. 
+    \cye{Recall the notation $U_{F_m} := T_m \cup T_{m-1}$.}
+    For any $1 \leq m \leq M$, \cye{recall that} $F_m := T_m \cap T_{m-1}$ \cye{is}  a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}.
+
+    By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices.
+
+    \todo[inline]{MV: Why a second theorem?
+We should explain the difference of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+Which is better and when?}
+
+    \begin{figure}[t]
+\begin{center}
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!50] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=white  ] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!50] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!50] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\quad
+\begin{tikzpicture}
+    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
+    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
+    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!25] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=gray!50] (B) -- (C) -- (F) -- cycle; 
+\end{tikzpicture}
+\end{center}
+\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
+The dark gray triangle is the one being currently added, and the light gray triangles constitute the subdomain assembled so far.}
+\label{figure:exhausting}
+\end{figure}
+
+\begin{remark}
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} depends on only a few parameters of the triangulation:
+    the length of any traversal from the root simplex, the ratios of the volumes of adjacent simplices,
+    the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex. 
+    The aforementioned local Poincar\'e--Friedrichs constants can generally be estimated in terms of shape-parameters. 
+    If the face patches of the triangulation are convex, then better estimates are possible. 
+\end{remark}
+
+We write $\Omega_{m} \subseteq \bbR^{n}$ for the domain with $\overline\Omega_m := \cup_{j=0}^{m} T_m$, 
+    which is a triangulated $n$-dimensional submanifold with boundary.
+    \cye{\sout{We finally write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.}}
+    \todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
+As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
+
+    \mwl{Where to place that construction?}
+ We construct the potential recursively. 
+ We have seen that $c_{0} = w_{0} - u_{|\Omega_{0}}$ is a constant. 
+ Assume that $1 \leq m \leq M$ such that there exists $w_{\iota(m)} \in W^{1,p}(\Omega_{\iota(m)})$ 
+ such that $c_{0} = w_{\iota(m)} - u_{|\Omega_{\iota(m)}}$ is the constant above. 
+ % Note that this assumption is already satisfied when $m=1$.
+ Hence $\nabla w_{\iota(m)} = \nabla u$ over $\Omega_{\iota(m)}$. 
+ By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{\iota(m)}}$. 
+ Since $$\nabla w_{F_{m}|T_{{\iota(m)}}} = \nabla w_{\iota(m)|T_{{\iota(m)}}},$$
+ there exists a constant $$c_{m} := w_{\iota(m)|T_{{\iota(m)}}} - w_{F_{m}|T_{{\iota(m)}}}.$$
+ We define $w'_{F_m} := w_{F_m} + c_{m} \in W^{1,p}(U_F)$.
+ By construction, $$\nabla w'_{F_m} = \nabla w_{F_m} = \nabla u_{|U_{F_m}}$$ 
+ and 
+ $w'_{F_{m}|T_{{\iota(m)}}} = w_{\iota(m)|T_{{\iota(m)}}}$. 
+ But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
+ Defining $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{\iota(m)}$ with $w'_{F_m|T_m}$,
+ we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
+
+ \mwl{Closure}
+ We obtain the desired estimate. 
+ Repeating this argument produces $w \in L^{p}(\Omega)$ 
+ such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
+ In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
+
+        \color{blue}
+        We study the singular values of the matrix 
+        \begin{align*}
+            \begin{pmatrix}
+            -1                 & 0
+            \\ 
+            -2 \|b_z\|/\|h_z\| & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            -1             & 0
+            \\ 
+            -2 \tan(\beta) & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            0             & \tan(\beta)
+             \\ 
+            -\tan(\beta) & 0
+            \end{pmatrix}
+            +
+            \begin{pmatrix}
+            -1           & -\tan(\beta)
+             \\ 
+            \tan(\beta) & 1
+            \end{pmatrix}
+            .
+        \end{align*}
+        It follows that $\det(\Theta_{|K}) = 1$. 
+        Its singular values satisfy 
+        \begin{align*}
+            ( \sigma_{\max} + \sigma_{\min} )/2
+            =
+            \tan(\beta)
+            ,
+            \qquad 
+            ( \sigma_{\max} - \sigma_{\min} )/2
+            =
+            \sqrt{ 1 + \tan^{2}(\beta) }
+            .
+        \end{align*}
+        We arrive at 
+        \begin{align*}
+            \sigma_{\max} = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
+            ,
+            \qquad 
+            \sigma_{\min} = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
+            .
+        \end{align*}
+\begin{align*}
+    \lambda^2 = \frac{1}{2} \left( a + c \pm \sqrt{ a^2 - 2 a c + c^2 + 4b^2 } \right)
+\end{align*}
+\begin{align*}
+    \lambda 
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ (1+t^2) + 1 \pm \sqrt{ (1+t^2)^2 - 2 (1+t^2)   +   1 + 4t^2 } } 
+    \\
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{ 1 + 2t^2 + t^4 - 2 - 2 t^2 + 1 + 4t^2 } } 
+    \\
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm \sqrt{          + t^4                 + 4t^2 } } 
+    \\
+    &= 
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
+    .
+\end{align*}
+\begin{align*}
+    \lambda = \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
+\end{align*}
+\begin{align*}
+    \left( t^2 + 2 + t \sqrt{ t^2 + 4 } \right)
+    \left( t^2 + 2 - t \sqrt{ t^2 + 4 } \right)
+    =
+    t^{4} + 4 t^{2} + 4
+    -
+    t^{2} ( t^{2} + 4 )
+    =
+    4
+\end{align*}
+\begin{align*}
+    \frac{1}{\sqrt 2} \sqrt{ t^2 + 2 \pm t \sqrt{ t^2 + 4 } } 
+    &=
+    \sqrt{1+a^2/4} \pm a/2
+    \\
+    \frac 1 2 \left( t^2 + 2 \pm t \sqrt{ t^2 + 4 } \right)
+    &=
+    1+a^2/4
+    \pm
+    a \sqrt{1+a^2/4}
+    + 
+    a^2/4
+    \\&=
+    1
+    +
+    2a^2/4
+    \pm
+    a \sqrt{1+a^2/4}
+    \\
+    1 + \frac{t^2}{2} \pm t \sqrt{ \frac{t^2}{4} + 1 } 
+    &=
+    1
+    +
+    a^2/2
+    \pm
+    a \sqrt{1+a^2/4}
+    .
+\end{align*}
+\color{black}
 

### 2024-09-29 main.tex
section on gradient potentials over triangulated domains

@@
 \usepackage{fullpage}
+%\usepackage[margin=0.1cm]{geometry}
 \input{header}
@@
 
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations}
 \author{
@@
 \tableofcontents
-\todo[inline]{MV: Added table of contents: for us, to see the structure of and the main terminology used in the paper}
 
@@
 
-We introduce a specific notion of connectivity. 
-Given an $n$-dimensional simplicial complex $\calT$, 
-we call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
+We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
+We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
 % TODO: Theo suggests reverse order of that sequence
-We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
+We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. \mwl{Change the terminology strong path to something else.}
 Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
@@
 and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
-\\
+
+\mwl{We should use clarify face vs facet}
+
+\subsection{...}
 
@@
 and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
-\begin{align}
+\begin{align}\label{math:volumeratio}
     \volumeratio(\calT) 
@@
     ,
-    \qquad 
+\end{align}
+\begin{align}\label{math:diameterratio}
     \diameterratio(\calT) 
@@
 \begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ \cye{of~\eqref{math:volumecomparisonmeasure}} but not $\theta(\calT)$ \cye{of~\eqref{math:diametercomparison}}. 
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diametercomparison}}.
     Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
@@
 
-In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
-We achieve by explicitly constructing scalar potentials of gradients.
-We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
+\mwl{In this section, we develop a stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
+The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
+We perform a discrete analogue of this procedure over triangulated domains: 
+having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.
+%We construct a scalar potential for a given gradient vector field on larger and larger triangulated subdomains.
+We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face, thus constructing a scalar potential over larger and larger subdomains.
+This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.}
+
+% We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
 We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells.
-we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
-\\
-
-{\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
+We construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
+% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+% 
+% {\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
 \cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure.
+% Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure.
 We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}.
-We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
-This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-}
-
-We construct scalar potentials over larger and larger intermediate subdomains. 
-Two different variations of that idea are analyzed;
-while the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
-On the one hand, we can cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
-Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece.
-This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result.
-
-For the agenda of this section, the following combinatorial notion of triangulations will be helpful. 
-Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
-a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
-where for each index $1 \leq m \leq M$ we have fixed index $0 \leq j(m) \leq m-1$ 
-such that $T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
-We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
-
-On the other hand, we assess an alternative route towards constructing scalar gradient potentials over triangulated domains. 
-While the underlying idea remains the same, the construction of the potential is slightly different. 
-we can extend the potential on each intermediate domain to another simplex by solving a local auxiliary problem on that simplex subject to partial boundary conditions.
-This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
-As an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex} computes an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed on a single face of the boundary.
-
-We emphasize that the second approach to constructing potentials and bounding Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-Our estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
-
-{\color{blue}\cye{We start by extending the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations} in a way which captures the correct asymptotic behavior as $p$ grows to infinity.
-\cye{Let us stress that face patches are not necessarily convex and remark that our result is in particular sharp when $T_1$ and $T_2$ have similar volumes and diameters}.}
+% We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
+% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+% }
+
+% While the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
+% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result. 
+% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
+
+We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
+% This is inspired by the classical proof of what is often called Friedrichs' inequality.
+
+\begin{lemma}\label{lemma:mixedbconsimplex}
+    Let $T$ be an $n$-simplex with a face $F$ and $p \in [1,\infty]$. 
+    If $u \in W^{1,p}(T)$ with $\trace_{F} u = 0$, then 
+    \begin{align*}
+        \| u \|_{L^{p}(T)}
+        &
+        \leq 
+        C_{\PF,T,F,p} \| \nabla u \|_{L^{p}(T)}
+        ,
+    \end{align*}
+    where $C_{\PF,T,F,p} = p^{-\frac 1 p} \diam(T)$ for $p < \infty$ and $C_{\PF,T,F,\infty} = \diam(T)$. 
+%     \begin{align*}
+%         C_{\PF,T,F,p}
+%         &\leq 
+%         C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
+%         \\
+%         C_{\PF,T,F,p}
+%         &\leq
+%         \frac{1}{\sqrt[p]{p}}
+%         \diam(T)
+%         .
+%     \end{align*}
+\end{lemma}
+\begin{proof}
+\begin{comment}
+    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
+    \begin{gather*}
+        \| w \|_{L^{p}(T)}
+        \leq 
+        C_{\PF,T,p} 
+        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
+        .
+    \end{gather*}
+    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
+    We use that 
+    \begin{gather*}
+        \| \gamma \|_{L^{p}(T)}
+        =
+        \gamma \vol(T)^\frac{1}{p}
+        =
+        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
+        \cdot 
+        \gamma 
+        \vol(F)^\frac{1}{p}
+        =
+        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
+        \| \gamma \|_{L^{p}(F)}
+        .
+    \end{gather*}
+    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
+    \begin{align*}
+        \| \gamma \|_{L^{p}(F)}^{p}
+        &
+        \leq 
+        \frac{ \vol(F) }{ \vol(T) }
+        \| w \|_{L^{p}(T)}^{p}
+        +
+        p
+        \cdot 
+        \diam(T)
+        \frac{ \vol(F) }{ \vol(T) }
+        \| w \|_{L^{p}(T)}^{p-1}
+        \| \nabla w \|_{L^{p}(T)}
+        \\&
+        \leq 
+        \left( \frac{ \vol(F) }{ \vol(T) } \right)
+        \left( C_{\PF,T,p}^{p} + p \cdot C_{\PF,T,p}^{p-1} \right) 
+        \diam(T)^{p}
+        \| \nabla w \|_{L^{p}(T)}^{p}
+        \\&
+        \leq 
+        \left( \frac{ \vol(F) }{ \vol(T) } \right)
+        \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right) 
+        %\diam(T)^{p}
+        \| \nabla w \|_{L^{p}(T)}^{p}
+        .
+    \end{align*}
+    Recall that $u = w - \gamma$. The first inequality follows. 
+\end{comment}
+    % The second inequality follows from Rademacher's theorem when $p = \infty$.
+    Since the inequality follows from Rademacher's theorem in the limit case $p = \infty$,
+    we assume $1 \leq p < \infty$. 
+    Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
+    We extend $u$ by zero to a function over the entire $\bbR^{n}$.
+    Without loss of generality, 
+    the segment from the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
+    and the minimal first coordinate among all the points of $F$ equals $0$. 
+    We write $\bfg$ for the trivial extension of $\nabla u$ over the entire $\bbR^{n}$.
+    %With the fundamental theorem of calculus and H\"older's inequality: 
+    Using the fundamental theorem of calculus and H\"older's inequality, 
+    \begin{align*}
+        \int_{T} |u(x)|^{p} \diff x \;dx
+        &\leq
+        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
+        \\&
+        \leq
+        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
+        \\&
+        \leq
+        \int_{0}^{\diam(T)} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
+        \\&
+        \leq
+        \int_{0}^{\diam(T)} x_{1}^{p-1} \;dx_1 
+        \cdot 
+        \int_{T} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
+        \leq
+        \frac{\diam(T)^{p}}{p} \int_{T} \left| \nabla u( x ) \right|^{p} \,dx
+        %
+%         \leq
+%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
+%         \\&
+%         \leq
+%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
+%         \\&
+%         \leq
+%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
+%         \\&
+%         \leq
+%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
+%         \leq 
+%         D^{p} 
+%         \int_{\Omega} |\nabla u|^{p} \,dx
+        .
+    \end{align*}
+    That $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
+    for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$. 
+    Very briefly verify that density argument: 
+    There exists affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ from the reference simplex onto $T$ that maps the convex closure of the $n$ unit vectors onto the face $F$.
+    We let $\hat u := u \circ \varphi$.
+    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\Delta^{n}$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
+    Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
+    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$ within the Banach space $W^{1,p}(T)$
+    and has the desired support property. 
+\end{proof}
+
+% \begin{remark}
+%     While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains.  
+% \end{remark}
+
+The next auxiliary result extends the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations.
+We point out that face patches are not necessarily convex.
+The following result is reasonably sharp when the two simplices have similar volumes and diameters.
 
@@
     Write $U := T_1 \cup T_2$. 
-    Then 
+    If $p \in [1,\infty]$ and $u \in W^{1,p}(\Omega)$,
+    then 
     \begin{align*}
@@
         \leq 
-        2 \Ceins{n} C_{\PF,{\rm EFNT},p}
-        \volumeratio(\calT)^{\frac 1 p}
-        \max\left( \diam(T_1), \diam(T_2) \right)
+        C_{{\rm{PF}},T_1 \cup T_2,p}
         \| \nabla u \|_{L^{p}(U)}
-    \end{align*}
-    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$. \mwl{Introduce constant $C_{{\rm{PF}},T_1 \cup T_2,p}$}
+        .
+    \end{align*}
+    Here, $C_{{\rm{PF}},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
 \end{lemma}
@@
     We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
-    be affine transformations that map the $e_{i}$ to $v_{i}$ for $i = 0, \dots, n-1$ 
-    and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
-    Write $\hat U := \Delta_1 \cup \Delta_2$, which is (crucially) convex. .
+    be affine transformations that the origin to $v_0$, that map each unit vector $e_{i}$ to $v_{i}$ for $i = 1, \dots, n-1$,
+    and that satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
+    Write $\hat U := \Delta_1 \cup \Delta_2$.
     We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
@@
     \end{align*}
-    Notice that $\hat U$ is convex and has diameter $2$. 
-    Thus, due to~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
+    Notice that $\hat U$ has diameter $2$ and is (crucially) convex. 
+    Thus, due to Poincar\'e--Friedrichs inequality~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
     \begin{align*}
@@
     \end{align*}
-    \cye{In the last equality, we have also used $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$ that we have already employed in~\eqref{equation:Hong_Pan}.}
-    Noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$ for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}, we conclude the desired result.
+    For both $i = 1,2$, we now recall the well-known equation $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$, 
+    % which we have already employed in~\eqref{equation:Hong_Pan}, 
+    and the estimate $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$, which is given in Lemma~\ref{lemma:measurerelationships}. We conclude the desired result.
 \begin{comment}
@@
 \end{proof}
-
-\begin{figure}[t]
-\begin{center}
-\begin{tikzpicture}
-    \coordinate (A) at (0,0);
-    \coordinate (B) at (2,0);
-    \coordinate (C) at (1,1.5);
-    \coordinate (D) at (3,1.5); 
-    \coordinate (E) at (3,3); 
-    \coordinate (F) at (4,0.25); 
-    \coordinate (X) at (1,-1.5);
-    \coordinate (Y) at (3,-1.5); 
-    \coordinate (T) at (5,2);
-
-    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
-    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
-    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
-    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
-    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
-    \coordinate (CentroidDFT) at ($(D)!0.3333!(F)!0.3333!(T)$);
-    \coordinate (CentroidDET) at ($(D)!0.3333!(E)!0.3333!(T)$);
-
-    \draw[fill=gray!10] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!10] (B) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!10] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!10] (B) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (A) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (E) -- cycle;
-
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
-    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET);
-
-%     \node at (A) [below left] {$A$};
-%     \node at (B) [below right] {$B$};
-%     \node at (C) [above] {$C$};
-%     \node at (D) [above right] {$D$};
-%     \node at (T) [above right] {$T$};
-\end{tikzpicture}
-\end{center}
-\caption{Strongly connected triangulation of a domain.
-The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-The triangle in dark gray is the triangle being added in the current iteration, and the light gray triangles constitute the subdomain assembled so far.}
-\end{figure}
 
@@
 
+The main result of this section constructs a potential and gives an upper bound for the Poincar\'e--Friedrichs constant.  
+It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.
+The procedure serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+
+Two different variations of underlying idea are analyzed. 
+On the one hand, we extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that simplex.
+This auxiliary problem will be subject to partial boundary conditions.
+% We present an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex}, where we compute an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
+% We emphasize that this construction of potentials and bounding of Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+On the other hand, we can instead cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
+Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece by adjusting the local constants of integration.
+Both estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
+
+For the remainder of this section, the following combinatorial notion of triangulations is used. 
+Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
+a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
+where for each index $1 \leq m \leq M$ we have a fixed index $0 \leq \iota(m) \leq m-1$ 
+such that $T_{m}$ and $T_{\iota(m)}$ are face-neighboring.
+We call $T_{\iota(m)}$ the \emph{precursor} of $T_{m}$ within the spanning tree. 
+The reader is referred to Figure~\ref{figure:spanningtree} for an illustration.
+
 \begin{figure}[t]
 \begin{center}
-\begin{tikzpicture}
-    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
-    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
-    \draw[fill=gray!50] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=white  ] (A) -- (C) -- (D) -- cycle; 
-    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
-\end{tikzpicture}
-\quad
-\begin{tikzpicture}
-    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
-    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
-    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!50] (A) -- (C) -- (D) -- cycle; 
-    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
-\end{tikzpicture}
-\quad
-\begin{tikzpicture}
-    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
-    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
-    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!50] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
-\end{tikzpicture}
-\quad
-\begin{tikzpicture}
-    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
-    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
-    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!25] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!50] (B) -- (C) -- (F) -- cycle; 
+\begin{tikzpicture}[rotate=-60]
+    \coordinate (A) at (0,0);
+    \coordinate (B) at (2,0);
+    \coordinate (C) at (1,1.5);
+    \coordinate (D) at (3,1.5); 
+    \coordinate (E) at (3,3); 
+    \coordinate (F) at (4,0.25); 
+    \coordinate (X) at (1,-1.5);
+    \coordinate (Y) at (3,-1.5); 
+    \coordinate (T) at (5,2);
+
+    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
+    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
+    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
+    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
+    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
+    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
+    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
+    \coordinate (CentroidDFT) at ($(D)!0.3333!(F)!0.3333!(T)$);
+    \coordinate (CentroidDET) at ($(D)!0.3333!(E)!0.3333!(T)$);
+
+    \draw[fill=gray!10] (A) -- (B) -- (C) -- cycle; 
+    \draw[fill=gray!10] (B) -- (C) -- (D) -- cycle; 
+    \draw[fill=gray!10] (C) -- (D) -- (E) -- cycle; 
+    \draw[fill=gray!10] (B) -- (D) -- (F) -- cycle; 
+    \draw[fill=gray!10] (A) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!10] (Y) -- (B) -- (X) -- cycle; 
+    \draw[fill=gray!10] (Y) -- (B) -- (F) -- cycle; 
+    \draw[fill=gray!10] (T) -- (D) -- (F) -- cycle; 
+    \draw[fill=gray!10] (T) -- (D) -- (E) -- cycle;
+
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
+    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
+    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET);
+
+%     \node at (A) [below left] {$A$};
+%     \node at (B) [below right] {$B$};
+%     \node at (C) [above] {$C$};
+%     \node at (D) [above right] {$D$};
+%     \node at (T) [above right] {$T$};
 \end{tikzpicture}
 \end{center}
-\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
-The dark gray triangle is the one being currently added, and the light gray triangles constitute the subdomain assembled so far.}
-\label{figure:exhausting}
+\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
+\label{figure:spanningtree}
 \end{figure}
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a face-connected $n$-dimensional finite triangulation $\calT$.
-    We fix an $n$-simplex $T_0 \in \calT$ and for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_{M} = T$.
-    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
+    Let $\calT$ be a face-connected $n$-dimensional finite triangulation 
+    with a spanning tree $T_0, T_1, \dots, T_{M}$. \mwl{should be a sequence with precursor function}
+    For any $1 \leq m \leq \cye{M}$, let $F_m = T_m \cap T_{\iota(m)}$.
+    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
+    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
     Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
-    and such that for all $T \in \calT$:
-%     DONE {Make sure the notation for the PF constants is uniform throughout the paper}
-    \begin{align*} 
-        % \color{red}
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        \sum_{t=1}^{m}
-        \volumeratio(\calT)^{\frac{m-t}{p}}
-        C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
-        % 2 C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
-        \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
-        \\&\quad \quad \quad 
-        +
-        \volumeratio(\calT)^{\frac{m-1}{p}}
-        % C_{\PF,{\rm EFNT},p} \diam(T_0)
-        C_{{\rm{PF}},T_{0},p}
-        \| \nabla u \|_{L^{p}(T_{0})}
-        .
-    \end{align*}
-    \todo{Rewrite this result. First a local recursive one, then a global bound}
-    \todo{Ensure big $M$ at all indices here.}
-    When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
-        &\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-        .
-    \end{align*}
-\end{theorem}
-\begin{proof}
-\todo[inline]{MV: Reworked and simplified the beginning of the proof.}
- Let $u \in W^{1,p}(\Omega)$. 
- \cye{On the first} simplex $T_{0}$, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
+    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
+    and such that for all $1 \leq m \leq M$
+    we have the following recursive estimates:
     \begin{gather*}
@@
     \end{gather*}
- In particular, $c_{0} := \cye{w_0} - \cye{u}$ is a constant function. 
- \cye{We then define 
-  \begin{align*}
-    w := u + c_0
-  \end{align*} 
-  (note that $w|_{T_{0}} = w_0$). Clearly,} 
- $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$. \cye{We verify that $w$ fulfills the desired estimate.}
-
- Let $T \in \calT$ be any $n$-simplex. 
- By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}. 
- For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}. \cye{Recall the notation $U_{F_m} := T_m \cup T_{m-1}$.}
- We let $u_{F_m} \in W^{1,p}(U_{F_m})$ \cye{be} such that $\nabla u_{F_m} = \nabla u$ over $U_{F_m}$ and 
- \begin{align*}
-    \| u_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\rm{PF}},U_{F_m},p} \| \nabla u_{F_m} \|_{L^{p}(U_{F_m})},
- \end{align*}
- where the computable constant $C_{{\rm{PF}},U_{F_m},p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
-\cye{Since $\nabla (w|_{U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u|_{U_{F_m}})$, we can define the constant
- \begin{align*}
-    c_{m} := w|_{U_{F_m}} - u_{F_{m}}.
- \end{align*}
- }
- \cye{\sout{We finally write $\Omega_m := \cup_{j=0}^{m} T_m$, which is triangulated $n$-dimensional submanifold with boundary}}.\todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
-As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
-
-\begin{figure}[h]
-\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
-\end{figure}
-
- We \cye{now} assess the norm of the potential \cye{$w$}. \cye{For any $1 \leq m \leq M$,} we observe 
- \begin{gather*}
-    \| \cye{w} \|_{L^{p}(T_m)}
-    \leq 
-    \| u_{F_m} \|_{L^{p}(T_m)}
-    +
-    \| c_{m} \|_{L^{p}(T_m)},
-    \\
-    \| c_{m} \|_{L^{p}(T_m)}
-    = 
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| c_{m} \|_{L^{p}(T_{{m-1}})},
-    \\ 
-    \| c_{m} \|_{L^{p}(T_{{m-1}})}
-    \leq 
-    \| \cye{w}\|_{L^{p}(T_{{m-1}})} + \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
-    .
- \end{gather*}
- \cye{Consequently},
- \begin{align*}
-    \| \cye{w} \|_{L^{p}(T_m)}
+    and for $1 \leq m \leq M$ we have 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
         &
         \leq  
-    \| u_{F_m} \|_{L^{p}(T_m)}
-    \\&\qquad 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
- We sum the two integrals of $u_{F_m}$. 
- % 
- In the special case $p=1$,
- \begin{align*}
-    \| \cye{w} \|_{L^{1}(T_m)}
-    \leq 
-    \max\left(
-        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
-    \right)
-    \| u_{F_m} \|_{L^{1}(U_{F_m})}
-    +
-    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-    \| \cye{w}\|_{L^{1}(T_{{m-1}})}
-    .
- \end{align*}
- In the special case $p=\infty$, 
- \begin{align*}
-    \| \cye{w} \|_{L^{\infty}(T_m)}
-    \leq 
-    2
-    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
-    +
-    \| \cye{w}\|_{L^{\infty}(T_{{m-1}})}
-    .
- \end{align*}
- % 1/q = 1 - 1/p = (p-1)/p 
- When $1 < p < \infty$, \cye{recalling the complementary exponent} $q = p/(p-1) \in [1,\infty]$, we observe \cye{using the H\"older inequality}
- \begin{align*}
-    \| \cye{w} \|_{L^{p}(T_m)}
+        \volumeratio(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(T_{\iota(m)})} 
+        + 
+%         C_{\PF,T_{m},F_{m},p} 
+%         \left( 
+%             \| \nabla u \|_{L^{p}(T_{m})} 
+%             + 
+%             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+%             \| \nabla u \|_{L^{p}(T_{\iota(m)})}
+%         \right)
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
+        C_{\PF,T_{m},F_{m},p} 
+        \| \nabla u \|_{L^{p}(U_{F_m})} 
+        ,
+        \\
+        \| w \|_{L^{p}(T_m)}
         &\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \left( 
-        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
-        +
-        \| u_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
-    \right)^{\frac 1 p}
-    \\&\qquad 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
-    \\&\cye{=} 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| \cye{w}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
- Recursive application provides the following estimate:
-%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
-%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
-%  then 
- \begin{align*}
-    \| \cye{w} \|_{L^{p}(T_m)}
-    &\leq 
-    \sum_{t=1}^{m} 
-    \left( 
-        \prod_{t < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
-    \right)
-    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
-    \| u_{F_t} \|_{L^{p}(U_{F_t})}
-    \\&\quad \quad \quad 
-    +
-    \left( 
-        \prod_{0 < l \leq m} 
-        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
-    \right)
-    \| u_{T_0}\|_{L^{p}(T_{0})}
-    .
- \end{align*}
- % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
- We obtain the desired estimate. 
-%  \begin{align*}
-%     \| \cye{w} \|_{L^{p}(T_m)}^{p}
-%     &\leq 
-%     (m+1)^{p-1}
-%     % \sum_{t=1}^{m} \rho(\calT)^{m-t} 
-%     % \sum_{t=0}^{m-1} \rho(\calT)^{t} 
-%     \frac{\rho(\calT)^{m}-1}{\rho(\calT)-1}
-%     \left( 1 + \rho(\calT)^{\frac q p} \right)^{p/q}
-%     \| u_{F_t} \|_{L^{p}(U_{F_t})}^{p}
-%     \\&\quad \quad \quad 
-%     +
-%     (m+1)^{p-1}
-%     \rho(\calT)^{m-1}
-%     \| u_{T_0}\|_{L^{p}(T_{0})}^{p}
-%     .
-%  \end{align*}
-%  Notice that $p/q = p - 1$.
- % 
-\end{proof}
+        \volumeratio(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        +
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
+        C_{{\rm{PF}},U_{F_m},p} 
+        \| \nabla u \|_{L^{p}(U_{F_m})} 
+        . 
+    \end{align*}
+\end{theorem}
+
 \begin{proof}
     Let $u \in W^{1,p}(\Omega)$. 
- For each $F \in \calT$ of dimension $n-1$, 
- we let $w_F \in W^{1,p}(U_F)$ such that $\nabla w_F = \nabla u$ over $U_F$ and such that 
- \begin{align*}
-    \| w_F \|_{L^{p}(U_F)} \leq C_{{\rm{PF}},U_F,p} \| \nabla w_F \|_{L^{p}(U_F)},
- \end{align*}
- where the computable constant $C_{{\rm{PF}},U_F,p}$ is determined via Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}.
- We start with the simplex $T_{0}$. 
+    We start with the Poincar\'e--Friedrichs inequality on the first simplex $T_{0}$. 
     There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
@@
     \end{gather*}
- In particular, $c_{0} := u - w_0$ is a constant function.
-
- Now, let $T \in \calT$ be any $n$-simplex. 
- By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
- We let $\Omega_m := \cup_{j=0}^{m} T_m$ for any $0 \leq m \leq M$,
- which is a triangulated $n$-dimensional submanifold with boundary.
- For any $1 \leq m \leq M$ we write $F_m := T_m \cap T_{m-1}$,
- which is a face of dimension $n-1$.
-
-%  Since $\calT$ is face-connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$.
-We write $\Omega_m := \cup_{j=0}^{m} T_m$.
-Hence $\Omega = \Omega_M$.
-
- % DONE \notice{MWL, MV: add a figure here to illustrate how the domain is exhausted.}
-
- We construct the potential recursively. 
- We have seen that $c_{0} = w_{0} - u_{|\Omega_{0}}$ is a constant. 
- Assume that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
- such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
- % Note that this assumption is already satisfied when $m=1$.
- Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
- By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
- Since $$\nabla w_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}},$$
- there exists a constant $$c_{m} := w_{m-1|T_{{m-1}}} - w_{F_{m}|T_{{m-1}}}.$$
- We define $w'_{F_m} := w_{F_m} + c_{m} \in W^{1,p}(U_F)$.
- By construction, $$\nabla w'_{F_m} = \nabla w_{F_m} = \nabla u_{|U_{F_m}}$$ 
- and 
- $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
- But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
- Defining $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
- we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.
-
- We assess the norm of this potential. We observe 
- \begin{gather*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    =
-    \| w'_{F_m} \|_{L^{p}(T_m)}
-    \leq 
-    \| w_{F_m} \|_{L^{p}(T_m)}
-    +
-    \| c_{m} \|_{L^{p}(T_m)},
-    \\
-    \| c_{m} \|_{L^{p}(T_m)}
-    = 
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| c_{m} \|_{L^{p}(T_{{m-1}})},
-    \\ 
-    \| c_{m} \|_{L^{p}(T_{{m-1}})}
-    \leq 
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
-    .
- \end{gather*}
- In particular,
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &
-    \leq 
-    \| w_{F_m} \|_{L^{p}(T_m)}
-    \\&\qquad 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
- We sum the two integrals of $w_{F_m}$. 
- % 
- In the special case $p=1$,
- \begin{align*}
-    \| w_{m} \|_{L^{1}(T_m)}
-    \leq 
-    \max\left(
-        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
+    In particular, $c_{0} := w_0 - u$ is a constant function. 
+    We then define 
+    \begin{align*}
+        w := u + c_0
+        .
+    \end{align*} 
+    Clearly, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
+    By construction $w_{|T_{0}} = w_0$. 
+    We verify that $w$ satisfies the two desired recursive estimates.
+
+    We continue by discussing the first recursive estimate. 
+    Suppose that $1 \leq m \leq M$.
+    Recall that we write $F_m := T_m \cap T_{\iota(m)}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$. 
+    We define $w'_{m} := w_{|T_{\iota(m)}} \circ \Xi \in W^{1,p}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow T_{\iota(m)}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
+    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
+    \begin{align*}
+        \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{|T_{\iota(m)}}
+        .
+    \end{align*}
+    We now define $w''_{m} \in W^{1,p}(T_{m})$ via 
+    \begin{align}\label{equation:w''}
+        w''_{m} 
+        := 
+%         u_{|T_{m}} - w'_{m} + c_0 
+%         = 
+        w_{|T_{m}} - w'_{m} = u_{|T_{m}} - u_{|T_{\iota(m)}} \circ \Xi.
+    \end{align}
+    We crucially note that $w''_{m}$ is trace-free along $F_{m}$ since
+    \begin{align*}
+        \trace_{F_{m}} w''_{m} 
+        = 
+        \trace_{F_{m}} \left( 
+            w_{|T_{m}} - w'_{m} 
         \right) 
-    \| w_{F_m} \|_{L^{1}(U_{F_m})}
-    +
-    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
-    .
- \end{align*}
- In the special case $p=\infty$, 
- \begin{align*}
-    \| w_{m} \|_{L^{\infty}(T_m)}
-    \leq 
-    2
-    \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
-    +
-    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
-    .
- \end{align*}
- % 1/q = 1 - 1/p = (p-1)/p 
- When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
- \begin{align*}
-    \| w_{m} \|_{L^{p}(T_m)}
-    &\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \left( 
-        \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
-        +
-        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
-    \right)^{\frac 1 p}
-    \\&\qquad 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    \\&\leq 
-    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-    \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
-    +
-    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
-    .
- \end{align*}
-%  Recursive application provides the following estimate:
-%  \begin{align*}
-%     \| w_{m} \|_{L^{p}(T_m)}
-%     &\leq 
-%     \sum_{t=1}^{m} 
-%     \left( 
-%         \prod_{t < l \leq m} 
-%         \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+        =
+        \trace_{F_{m}} w_{|T_{m}}
+        -
+        \trace_{F_{m}} w_{|T_{\iota(m)}}
+        =
+        \trace_{F_{m}} u_{|T_{m}}
+        -
+        \trace_{F_{m}} u_{|T_{\iota(m)}}
+%         = 
+%         \trace_{F_{m}} \left( 
+%             u_{|T_{m}} - w'_{m} + c_0 
 %         \right) 
-%     \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
-%     \| w_{F_t} \|_{L^{p}(U_{F_t})}
-%     \\&\quad \quad \quad 
-%     +
-%     \left( 
-%         \prod_{0 < l \leq m} 
-%         \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
+%         = 
+%         \trace_{F_{m}} \left( 
+%             u_{|T_{\iota(m)}} - w_{|T_{\iota(m)}} + c_0 
 %         \right) 
-%     \| w_{T_0}\|_{L^{p}(T_{0})}
-%     .
-%  \end{align*}
-%  We obtain the desired estimate. 
- % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
-%  \begin{align*}
-%     \| w_{m} \|_{L^{p}(T_m)}^{p}
-%     &\leq 
-%     (m+1)^{p-1}
-%     % \sum_{t=1}^{m} \volumeratio(\calT)^{m-t} 
-%     % \sum_{t=0}^{m-1} \volumeratio(\calT)^{t} 
-%     \frac{\volumeratio(\calT)^{m}-1}{\volumeratio(\calT)-1}
-%     \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{p/q}
-%     \| w_{F_t} \|_{L^{p}(U_{F_t})}^{p}
-%     \\&\quad \quad \quad 
-%     +
-%     (m+1)^{p-1}
-%     \volumeratio(\calT)^{m-1}
-%     \| w_{T_0}\|_{L^{p}(T_{0})}^{p}
-%     .
-%  \end{align*}
-%  Notice that $p/q = p - 1$.
- % 
- Repeating this argument produces $w \in L^{p}(\Omega)$ 
- such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
- In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
-\end{proof}
-
-\cye{\begin{remark}
-The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} overestimates the best one increasingly with increasing number of $n$-simplices in the triangulation $\calT$.
-For this reason, we target its use to local patches (stars), in particular nonconvex boundary stars such as that of Figure~\ref{figure:exhausting}.
-Clearly, the same building principle applies when we can obtain a nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a  face-connected path.
-The proof proceeds verbatim, where we merely replace the simplices $T_{m}$ by the convex local patches $U_m$.
-This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a large decrease of the overestimation of the best Poincar\'e--Friedrichs constant.
-\end{remark}}
-
-\begin{lemma}\label{lemma:mixedbconsimplex}
-    Let $T$ be an $n$-simplex with a face $F$ and $p \in [1,\infty]$. 
-    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{\PF,T,F,p} \| \nabla u \|_{L^{p}(T)}
-        ,
-    \end{align*}
-    where $C_{\PF,T,F,p} = \frac{1}{\sqrt[p]{p}} \diam(T)$ for $p < \infty$ and $C_{\PF,T,F,\infty} = 1$. 
-%     \begin{align*}
-%         C_{\PF,T,F,p}
-%         &\leq 
-%         C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
-%         \\
-%         C_{\PF,T,F,p}
-%         &\leq
-%         \frac{1}{\sqrt[p]{p}}
-%         \diam(T)
-%         .
-%     \end{align*}
-\end{lemma}
-\begin{proof}
-\begin{comment}
-    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
-    \begin{gather*}
-        \| w \|_{L^{p}(T)}
-        \leq 
-        C_{\PF,T,p} 
-        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
-        .
-    \end{gather*}
-    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
-    We use that 
-    \begin{gather*}
-        \| \gamma \|_{L^{p}(T)}
-        =
-        \gamma \vol(T)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \cdot 
-        \gamma 
-        \vol(F)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \| \gamma \|_{L^{p}(F)}
-        .
-    \end{gather*}
-    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
-    \begin{align*}
-        \| \gamma \|_{L^{p}(F)}^{p}
-        &
-        \leq 
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p}
-        +
-        p
-        \cdot 
-        \diam(T)
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p-1}
-        \| \nabla w \|_{L^{p}(T)}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot C_{\PF,T,p}^{p-1} \right) 
-        \diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right) 
-        %\diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        .
-    \end{align*}
-    Recall that $u = w - \gamma$. The first inequality follows. 
-\end{comment}
-    % The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Since the inequality follows from Rademacher's theorem in the limit case $p = \infty$,
-    we assume $1 \leq p < \infty$. 
-    Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
-    We trivially extend $u$ to a function over the entire $\bbR^{n}$.
-    Without loss of generality, 
-    the segment from to the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
-    and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg \in \bfL^{\infty}(\bbR^{n})$ for the trivial extension of $\nabla u$ outside of $T$.
-    %With the fundamental theorem of calculus and H\"older's inequality: 
-    Using the fundamental theorem of calculus and H\"older's inequality, 
-    \begin{align*}
-        \int_{T} |u(x)|^{p} \diff x \;dx
-        &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
-        \\&
-        \leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
-        \\&
-        \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
-        \\&
-        \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \;dx_1 
-        \cdot 
-        \int_{T} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
-        \leq
-        \frac{\diam(T)^{p}}{p} \int_{T} \left| \nabla u( x ) \right|^{p} \,dx
-        %
-%         \leq
-%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
-%         \leq 
-%         D^{p} 
-%         \int_{\Omega} |\nabla u|^{p} \,dx
-        .
-    \end{align*}
-    That $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
-    for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$. 
-    Very briefly verify that density argument: 
-    There exists affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$.
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\Delta^{n}$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
-    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$. 
-\end{proof}
-
-% \begin{remark}
-%     While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains.  
-% \end{remark}
-
-The following potential construction and upper bound for the Poincar\'e--Friedrichs constant 
-serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-\cye{It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.}
-
-\todo[inline]{MV: Why a second theorem?
-We should explain the difference of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-Which is better and when?}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a face-connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
-    we fix a strong path $T_0, T_1, \dots, T_m = T$.
-    For any $1 \leq l \leq m$, let $F_{l} = T_{l} \cap T_{l-1}$.
-    Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
-    and such that for all $T \in \calT$:
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_m)}
-%         &\leq 
-%         \volumeratio(\calT)^{\frac m p}
-%         C_{\PF,T_{0},p} 
-%         \| \nabla u \|_{L^{p}( T_{0} )}
-%         +
-%         \sum_{l=1}^{m} 
-%         \volumeratio(\calT)^{\frac {m-l} p}
-%         C_{\PF,T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}(T_{l})} 
-%         \\&\qquad 
-%         +
-%         \sum_{l=1}^{m} 
-%         \volumeratio(\calT)^{\frac {m-l} p} \reflectionestimate(\calT)
-%         C_{\PF,T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}(T_{l-1})} 
-%         \\
-        &\leq 
-        \volumeratio(\calT)^{\frac m p}
-        C_{\PF,T_{0},p} 
-        \| \nabla u \|_{L^{p}( T_{0} )}
-        \\&\quad 
-        +
-        \sum_{l=1}^{m} 
-        \volumeratio(\calT)^{\frac {m-l} p}
-        C_{\PF,T_{l},F_{l},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{l})} 
-            +
-            \volumeratio(\calT)^{\frac {1} p}
-            \reflectionestimate(\calT)
-            \| \nabla u \|_{L^{p}(T_{l-1})} 
-        \right)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \| w_{m} \|_{L^{p}(T_m)}
-%         &\leq 
-%         \sum_{l=1}^{m} 
-%         \volumeratio(\calT)^{\frac{m-l}{p}}
-%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
-%         C_{\PF,T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}( T_{l} )}
-%         +
-%         \volumeratio(\calT)^{\frac m p}
-%         C_{\PF,T_{0},p} 
-%         \| \nabla u \|_{L^{p}( T_{0} )}
-%         .
-%     \end{align*}
-%     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
-\end{theorem}
-\begin{theorem}%\label{theorem:poincarefriedrichsestimate:gradzwei}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with an \cye{$n$-dimensional} \cye{face-}connected finite triangulation $\calT$.
-    Let $T_0 \in \calT$ be an $n$-simplex \cye{and} for all $n$-simplices $T \in \calT$, 
-    fix a \cye{face} path $T_0, T_1, \dots, T_{\cye{M}} = T$. For any $1 \leq l \leq \cye{M}$, let $F_l = T_l \cap T_{l-1}$.
-    Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
-    and such that for all $T \in \calT$\cye{, we have the following recursive estimate}:
-    \begin{align*}
-        \| \cye{w} \|_{L^{p}(T_{\cye{M}})}
-%         &\leq 
-%         \rho(\calT)^{\frac \cye{M} p}
-%         C_{\PF,T_{0},p} 
-%         \| \nabla u \|_{L^{p}( T_{0} )}
-%         +
-%         \sum_{l=1}^{\cye{M}} 
-%         \rho(\calT)^{\frac {\cye{M}-l} p}
-%         C_{\PF,T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}(T_{l})} 
-%         \\&\qquad 
-%         +
-%         \sum_{l=1}^{\cye{M}} 
-%         \rho(\calT)^{\frac {\cye{M}-l} p} \xi(\calT)
-%         C_{\PF,T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}(T_{l-1})} 
-%         \\
-        &\leq 
-        \sum_{l=1}^{\cye{M}} 
-        \rho(\calT)^{\frac {\cye{M}-l} p}
-        C_{\PF,T_{l},F_{l},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{l})} 
-            +
-            \rho(\calT)^{\frac {1} p}
-            \xi(\calT)
-            \| \nabla u \|_{L^{p}(T_{l-1})} 
-        \right)
-        \\&\quad 
-        + \rho(\calT)^{\frac{\cye{M}}{p}}
-        C_{\PF,T_{0},p} 
-        \| \nabla u \|_{L^{p}( T_{0} )}
-        .
-    \end{align*}
-%     \begin{align*}
-%         \| w_{\cye{M}} \|_{L^{p}(T_{\cye{M}})}
-%         &\leq 
-%         \sum_{l=1}^{\cye{M}} 
-%         \rho(\calT)^{\frac{\cye{M}-l}{p}}
-%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
-%         C_{\PF,T_{l},F_{l},p} 
-%         \| \nabla u \|_{L^{p}( T_{l} )}
-%         +
-%         \rho(\calT)^{\frac \cye{M} p}
-%         C_{\PF,T_{0},p} 
-%         \| \nabla u \|_{L^{p}( T_{0} )}
-%         .
-%     \end{align*}
-%     \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
-\end{theorem}\todo{MV: Synchronized the announcement and notation with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-
-\begin{proof}
-\todo[inline]{MV: Reworked and simplified the proof.}
-
-\cye{We start as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}  Let $u \in W^{1,p}(\Omega)$. 
- \cye{On the first} simplex $T_{0}$, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
- \begin{gather*}
-    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
- \end{gather*}
- In particular, $c_{0} := \cye{w_0} - \cye{u}$ is a constant function. 
- \cye{We then define 
-   \begin{align*}
-    w := u + c_0
-  \end{align*} 
- (note that $w|_{T_{0}} = w_0$). Clearly,} 
- $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$. \cye{We verify that $w$ fulfills the desired estimate.}
-
- Let $T \in \calT$ be any $n$-simplex. 
- By assumption, there exists a \cye{face} path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices \cye{from $\calT$}. 
- For any $1 \leq m \leq M$, \cye{recall that} $F_m := T_m \cap T_{m-1}$ \cye{is}  a face of dimension $n-1$ \cye{shared by the $n$-simplices $T_m$ and $T_{m-1}$}.
-
-    \cye{\sout{We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.}}
-   \todo[inline]{MV: False, $\Omega_m$ is not necessarily a triangulated $n$-dimensional submanifold with boundary, see the 7-triangles example standing for $\Omega_m$ (then the 8th one gives $\Omega_{m+1} = \Omega$).
-As discussed online, we fortunately do not need here a submanifold with boundary (but we will need it and have it for shellable triangulations.) Actually, here we do not need $\Omega_m$ at all.}
-
-\begin{figure}[h]
-\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
-\end{figure}
-
-    \cye{\sout{We use a recursive argument.}} Suppose that $\cye{1} < m \leq M$.
-    We define $w'_{m} := w\cye{|_{T_{m-1}}} \circ \Xi \in W^{1,p}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
-    %
-    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
-    \begin{align*}
-        \trace_{F_{\cye{m}}} w'_{m} = \trace_{F_{\cye{m}}} w\cye{|_{T_{m-1}}}
-        .
-    \end{align*}
-    We now define $w''_{m} \in W^{1,p}(T_{m})$ as
-\cye{    \begin{align}\label{equation:w''}
-        w''_{m} := u|_{T_{\cye{m}}} - w'_{m} + c_0 = w|_{T_{\cye{m}}} - w'_{m} = u|_{T_{\cye{m}}} - u\cye{|_{T_{m-1}}} \circ \Xi.
-    \end{align}
-    We crucially note that $w''_{m}$ is trace free on $F_{m}$ since
-    \begin{align*}
-        \trace_{F_{m}} w''_{m} = \trace_{F_{m}} (u|_{T_{\cye{m}}} - w'_{m} + c_0) = \trace_{F_{m}} (u|_{T_{m-1}} - w\cye{|_{T_{m-1}}} + c_0) = 0.
-    \end{align*}}
-    Lemma~\ref{lemma:mixedbconsimplex} gives\cye{, from the first expression in~\eqref{equation:w''}}
+        = 0.
+    \end{align*}
+    We apply Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''}, which gives 
     \begin{align*}
@@
         &
+        \leq 
+        C_{\PF,T_{m},F_{m},p} 
+        \left( 
+            \| \nabla w \|_{L^{p}(T_{m})} 
+            + 
+            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
+        \right) 
         \leq 
@@
     \end{align*}
-    We also employ\cye{~\eqref{math:reflectionmeasure} \sout{Lemma~\ref{lemma:volumecomparison}}} to find 
+    Using Lemma~\ref{lemma:volumecomparison} as well as Definitions~\eqref{math:volumeratio} and~\eqref{math:reflectionmeasure}, we find 
     \begin{align*}
@@
         \matnorm{ \Jacobian \Xi }
-        \| \nabla \cye{w} \|_{L^{p}(T_{m-1})}
+        \| \nabla w \|_{L^{p}(T_{\iota(m)})}
         \\&
         \leq 
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla \cye{w} \|_{L^{p}(T_{m-1})}
+        \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla w \|_{L^{p}(T_{\iota(m)})}
         \\&
-        \cye{=
-        \rho(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla u \|_{L^{p}(T_{m-1})} }
-        .
-    \end{align*}
-    \todo{MV: How $|\det(\Jacobian\Xi)|^{-\frac 1 p} \leq \rho(\calT)^{\frac 1 p}$ follows?}
-    \cye{From the second expression in~\eqref{equation:w''}, we then finally have} 
-    \begin{align*}
+        =
+        \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla u \|_{L^{p}(T_{\iota(m)})}
+        .
+    \end{align*}
+    % The second expression in~\eqref{equation:w''} shows $w_{|T_{m}} = w''_{m} + w'_{m}$. We finally find 
+    Since $w_{|T_{m}} = w''_{m} + w'_{m}$, we finally find 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
         &
-        \| \cye{w} \|_{L^{p}(T_{m})}
-        \\&
         \leq  
@@
         \leq  
-        \rho(\calT)^{\frac 1 p} 
-        \| \cye{w} \|_{L^{p}(T_{m-1})} 
+        \volumeratio(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(T_{\iota(m)})} 
         + 
@@
             + 
-            \cye{\rho(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla u \|_{L^{p}(T_{m-1})}}
+            \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+        \| \nabla u \|_{L^{p}(T_{\iota(m)})}
         \right). 
     \end{align*}
-\cye{Therefrom, the desired estimate follows.}
+    We now use H\"older's inequality. 
+    Therefrom, the first recursive estimate follows.
+
+    Now we discuss the second recursive estimate. 
+    Suppose again that $1 \leq m \leq M$. 
+    Recall that we write $U_{F_m} := T_m \cup T_{\iota(m)}$. 
+    We use the Poincar\'e--Friedrichs inequality over $U_{F_{m}}$,
+    as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
+    to find $w_{F_m} \in W^{1,p}(U_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $U_{F_m}$ and 
+    \begin{align}\label{math:wFm_inequality}
+        \| w_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\rm{PF}},U_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(U_{F_m})}.
+    \end{align}
+%     \cye{Since $\nabla (w|_{U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u|_{U_{F_m}})$, 
+    We can define the constant
+    \begin{align*}
+    c_{m} := w|_{U_{F_m}} - w_{F_{m}}.
+    \end{align*}
+    We now observe that 
+    \begin{gather*}
+        \| w \|_{L^{p}(T_m)}
+        \leq 
+        \| w_{F_m} \|_{L^{p}(T_m)}
+        +
+        \| c_{m} \|_{L^{p}(T_m)},
+        \\
+        \| c_{m} \|_{L^{p}(T_m)}
+        = 
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
+        \| c_{m} \|_{L^{p}(T_{{\iota(m)}})},
+        \\ 
+        \| c_{m} \|_{L^{p}(T_{{\iota(m)}})}
+        \leq 
+        \| w \|_{L^{p}(T_{{\iota(m)}})} + \| w_{F_{m}} \|_{L^{p}(T_{{\iota(m)}})} 
+        .
+    \end{gather*}
+    In combination, 
+    \begin{align*}
+        \| w \|_{L^{p}(T_m)}
+        &
+        \leq 
+        \| w_{F_m} \|_{L^{p}(T_m)}
+        \\&\qquad 
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
+        \| w_{F_{m}} \|_{L^{p}(T_{{\iota(m)}})}
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
+        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        .
+    \end{align*}
+    We sum the two integrals of $w_{F_m}$. 
+    % 
+    % 1/q = 1 - 1/p = (p-1)/p 
+    When $1 < p < \infty$, recalling the complementary exponent $q = p/(p-1) \in (1,\infty)$, 
+    we use H\"older's inequality to verify 
+    \begin{align*}
+        \| w \|_{L^{p}(T_m)}
+        &\leq 
+        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{\iota(m)}})^{\frac q p} } \right)^{\frac 1 q}
+        \left( 
+            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
+            +
+            \| w_{F_{m}} \|_{L^{p}(T_{{\iota(m)}})}^{p}
+        \right)^{\frac 1 p}
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
+        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        \\&\leq 
+        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{\iota(m)}})^{\frac q p} } \right)^{\frac 1 q}
+        \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
+        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        .
+    \end{align*}
+    In the special case $p=1$,
+    \begin{align*}
+        \| w\|_{L^{1}(T_m)}
+        \leq 
+        \max\left(
+            1, \frac{ \vol(T_m) }{ \vol(T_{{\iota(m)}}) } 
+        \right)
+        \| w_{F_m} \|_{L^{1}(U_{F_m})}
+        +
+        \frac{ \vol(T_m) }{ \vol(T_{{\iota(m)}}) }
+        \| w \|_{L^{1}(T_{{\iota(m)}})}
+        .
+    \end{align*}
+    In the limit case $p=\infty$, 
+    \begin{align*}
+        \| w \|_{L^{\infty}(T_m)}
+        \leq 
+        2
+        \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
+        +
+        \| w \|_{L^{\infty}(T_{{\iota(m)}})}
+        .
+    \end{align*}
+    The local inequality~\eqref{math:wFm_inequality} now provides the second recursive estimate. 
+    The proof is complete.
 \end{proof}
+
+\begin{corollary}
+    Under the assumptions of Theorem~\ref{theorem:poincarefriedrichsestimate:grad},
+    whenever $T_0, T_1, \dots, T_m$ is a face-path of $n$-simplices in $\calT$,
+    we have 
+    \begin{align*}
+        \| w \|_{L^{p}(T_m)}
+        &\leq 
+        \sum_{\ell=1}^{m} 
+        \volumeratio^{\frac{m-\ell}{p}}
+        \min\left( 
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
+        C_{{\rm{PF}},U_{F_\ell},p} 
+        ,
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
+        C_{\PF,T_{\ell},F_{\ell},p} 
+        \right)
+        \| \nabla u \|_{L^{p}(U_{F_\ell})}
+        \\&
+        \qquad 
+        \qquad 
+        +
+        \volumeratio^{\frac m p}
+        C_{{\rm{PF}},T_{0},p}
+        \| \nabla u \|_{L^{p}(T_{0})}
+        .
+    \end{align*}
+\end{corollary}
 \begin{proof}
-    Let $u \in W^{1,p}(\Omega)$. 
-    First, there exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    In particular, $c_{0} := u - w_0$ is a constant function.
-
-    Now, let $T \in \calT$ be any $n$-simplex. 
-    By assumption, there exists a strong path $T_0, T_1, \dots, T_M = T$, composed of $n$-simplices. 
-    For any $1 \leq m \leq M$ we let $F_m := T_m \cap T_{m-1}$ be a face of dimension $n-1$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    We use a recursive argument.
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $c_{0} = u - w_{m-1}$.
-    In particular, $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{m-1}$. 
-    % Let $\hat T$ be the reference simplex.
-    % We fix affine diffeomorphisms $\varphi : \hat T \rightarrow T_{j(m)}$ and $\vartheta : \hat T \rightarrow T_{m+1}$,
-    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
-    %
-    We define $w'_{m} := w_{m-1} \circ \Xi \in W^{1,p}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
-    %
-    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        .
-    \end{align*}
-    %Write $w''_{m} = u - w'_{m} \in W^{1,p}(T_{m})$. Then 
-    There exists $w''_{m} \in W^{1,p}(T_{m})$ such that 
-    \begin{align*}
-        \nabla w''_{m} = \nabla u_{|T_{m+1}} - \nabla w'_{m}, 
-        \quad 
-        \trace_{F_{m}} w''_{m} = 0.
-    \end{align*}
-    This is true because 
-    \begin{align*}
-        \trace_{F_{m}}( \nabla u - \nabla w'_{m} ) 
-        &= 
-        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m}
-        \\&= 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m}
-        = 
-        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \nabla w_{m} = \nabla w'_{m} + \nabla w''_{m} = \nabla w'_{m} + \nabla u - \nabla w'_{m} = \nabla u,
-        % \end{gather*}
-        \\
-        % \begin{gather*}
-        \trace_{F_{m}} w_{m} = \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_{m}$. 
-    In particular, $c_{0} = u - w_{m}$. 
-    Lemma~\ref{lemma:mixedbconsimplex} gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
-        \\&
-        \leq 
-        C_{\PF,T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{\PF,T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Lemma~\ref{lemma:volumecomparison} to find 
-    \begin{align*}
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
-        &
-        \leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \matnorm{ \Jacobian \Xi   }
-        \cdot 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
-        \\&
-        \leq 
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        \cdot 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})}
-        .
-    \end{align*}
-    Putting this all together, we use 
-    \begin{align*}
-        &
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{m})} 
-            + 
-            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-    \end{align*}
-    and 
-    \begin{align*}
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        % C_{\PF,T_{m},F_{m},p} 
-        \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        % C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-%     \begin{align*}
-%         &
-%         \| w_{m} \|_{L^{p}(T_{m})}
-%         \\&
-%         \leq  
-%         \| w'_{m} \|_{L^{p}(T_{m})}
-%         + 
-%         \| w''_{m} \|_{L^{p}(T_{m})}
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \left( 
-%             \| \nabla u \|_{L^{p}(T_{m})} 
-%             + 
-%             \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-%         \right) 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         + 
-%         \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         + 
-%         \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m-1})} 
-%         \\&
-%         \leq  
-%         \volumeratio(\calT)^{\frac 1 p} 
-%         \| w_{m-1} \|_{L^{p}(T_{m-1})} 
-%         + 
-%         \left( 1 + \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) \right) 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \| \nabla u \|_{L^{p}(T_{m})} 
-%         .
-%     \end{align*}
-    The existence of $w \in W^{1,p}(\Omega)$ satisfying the recursive estimate follows. 
+    This follows by repeated application of the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
 \end{proof}
@@
 \begin{remark}
-    The previous theorems, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei} 
-    depend on only a few parameters of the triangulation:
-    the length of any traversal from the root simplex, the ratios of the volumes of adjacent simplices,
-    the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex. 
-    The aforementioned local Poincar\'e--Friedrichs constants can generally be estimated in terms of shape-parameters. 
-    If the face patches of the triangulation are convex, then better estimates are possible. 
+    The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases.
+We hence target its use to local patches (stars), in particular nonconvex boundary stars.
+The latter occur inevitably at reentrant corners.
+Clearly, the same building principle applies whenever we have any nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a face-connected path.
+The proof proceeds verbatim, where we merely replace the simplices $T_{m}$ by the convex local patches $U_m$.
+This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant.
 \end{remark}
@@
 \begin{figure}[h]
-\centerline{\includegraphics[width=0.2\textwidth]{homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{homotopic_ball.jpg}}
+\centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
 \label{figure:not_manifold_triang}
@@
     in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two \cye{face-}connected components, each of which is a topological $2$-\disk.
+    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk.
     By the induction assumption, each of those components contains at least two triangles 
@@
         We want to characterize the singular values of this transform. 
-        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
+        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
         We can write
@@
             - 
-            2 \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+            2 \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
             \hat z_{S'}
@@
         \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_z$,
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_{z}$,
         and that it equals $-z_{S'}$ when $x = z_{S'}$.
@@
 %             - 
-%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
+%             2 \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
 %             .
 %         \end{align*}
-        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
-        \begin{align*}
-            \Theta_{|K}( h_z ) 
+        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$, then 
+        \begin{align*}
+            \Theta_{|K}( h_{z} ) 
             &= 
-            h_z
+            h_{z}
             - 
-            2 \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle} z_{S'}
-            = 
-            h_z
+            2 \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            = 
+            h_{z}
             - 
-            2 \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle} z_{S'}
+            2 \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
             %\\&
             = 
-            h_z
+            h_{z}
             - 
@@
         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\vecnorm{ h_z } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_z } = \sin(\beta) \vecnorm{ z_{S'} }$. 
+        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
         We study the singular values of the matrix 
@@
             \\ 
-            -2 \vecnorm{ b_z }/\vecnorm{ h_z } & 1
+            -2 \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
             \end{pmatrix}
@@
 %         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        By the definition of the tangent, $\tan(\beta) \leq \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$, and we know $\vecnorm{ b_z } \leq \vecnorm{ z_{S'} }$. 
+        By the definition of the tangent, $\tan(\beta) \leq \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$, and we know $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$. 
         Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
@@
             - 
-            \frac{ \vecnorm{ b_z } }{ 2 \vecnorm{ h_{z} } } 
+            \frac{ \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
             \hat b_{z} \otimes \hat h_{z}^{t}
@@
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence $\tan(\beta) = \vecnorm{ b_z } / \vecnorm{ h_z }$. It remains to study the singular values of the matrix 
+        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
         \begin{align*}
@@
         \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_z }}{\vecnorm{ h_z }} \leq (k+1) \aspectratio(T).
+            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
         \end{align*}
@@
 \begin{proof}
-    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
+    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
     By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 

### 2024-09-29 main.tex
shellable triangulations

@@
 \usepackage{fullpage}
-%\usepackage[margin=0.1cm]{geometry}
+\usepackage[margin=0.1cm]{geometry}
 \input{header}
@@
 
-\newcommand{\mwl}[1]{{\color{red} MWL: #1}}
+\newcommand{\mwl}[1]{{\color{red}#1}}
 \newcommand{\notice}[1]{{\color{red}REMARK: #1}}
@@
 \begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diametercomparison}}.
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diameterratio}}. 
     Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
@@
 
-\mwl{In this section, we develop a stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
+In this section, we develop a stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
 The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
@@
 We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face, thus constructing a scalar potential over larger and larger subdomains.
-This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.}
+This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
 
@@
 The next auxiliary result extends the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations.
-We point out that face patches are not necessarily convex.
+We emphasize that face patches are not necessarily convex.
 The following result is reasonably sharp when the two simplices have similar volumes and diameters.
@@
 
+\begin{comment}
 For the remainder of this section, the following combinatorial notion of triangulations is used. 
@@
 The reader is referred to Figure~\ref{figure:spanningtree} for an illustration. 
+\end{comment}
 
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\calT$ be a face-connected $n$-dimensional finite triangulation 
-    with a spanning tree $T_0, T_1, \dots, T_{M}$. \mwl{should be a sequence with precursor function}
-    For any $1 \leq m \leq \cye{M}$, let $F_m = T_m \cap T_{\iota(m)}$.
+    Let $\calT$ be a face-connected $n$-dimensional finite triangulation. 
     Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
@@
     there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
-    and such that for all $1 \leq m \leq M$
-    we have the following recursive estimates:
+    and satisfying the following estimates:
+    there exists an $n$-simplex $T_0 \in \calT$ with 
     \begin{gather*}
@@
     \end{gather*}
-    and for $1 \leq m \leq M$ we have 
+    and whenever $T_0, T_1, \dots, T_M$ is a face path,
+    then for all $1 \leq m \leq$ we the following recursive estimates:
     \begin{align*}
@@
     \end{align*}
+    Here, for any $1 \leq m \leq M$, let $F_m = T_m \cap T_{m-1}$.
 \end{theorem}
@@
     We verify that $w$ satisfies the two desired recursive estimates.
-
-    We continue by discussing the first recursive estimate. 
-    Suppose that $1 \leq m \leq M$.
-    Recall that we write $F_m := T_m \cap T_{\iota(m)}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$. 
-    We define $w'_{m} := w_{|T_{\iota(m)}} \circ \Xi \in W^{1,p}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow T_{\iota(m)}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
+    Suppose that $T_0, T_1, \dots, T_M$ is a face path in $\calT$
+    and that $1 \leq m \leq M$.
+    Recall that we write $F_m := T_m \cap T_{m-1}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$.
+
+    We proceed with showing the first recursive estimate. 
+    We define $w'_{m} := w_{|T_{m-1}} \circ \Xi \in W^{1,p}(T_{m})$,
+    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
     By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
     \begin{align*}
-        \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{|T_{\iota(m)}}
+        \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{|T_{m-1}}
         .
@@
 %         = 
-        w_{|T_{m}} - w'_{m} = u_{|T_{m}} - u_{|T_{\iota(m)}} \circ \Xi.
+        w_{|T_{m}} - w'_{m} = u_{|T_{m}} - u_{|T_{m-1}} \circ \Xi.
     \end{align}
@@
         -
-        \trace_{F_{m}} w_{|T_{\iota(m)}}
+        \trace_{F_{m}} w_{|T_{m-1}}
         =
@@
         -
-        \trace_{F_{m}} u_{|T_{\iota(m)}}
+        \trace_{F_{m}} u_{|T_{m-1}}
 %         = 
@@
 %         \trace_{F_{m}} \left( 
-%             u_{|T_{\iota(m)}} - w_{|T_{\iota(m)}} + c_0 
+%             u_{|T_{m-1}} - w_{|T_{m-1}} + c_0 
 %         \right) 
@@
         \matnorm{ \Jacobian \Xi }
-        \| \nabla w \|_{L^{p}(T_{\iota(m)})}
+        \| \nabla w \|_{L^{p}(T_{m-1})}
         \\&
@@
         \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla w \|_{L^{p}(T_{\iota(m)})}
+        \| \nabla w \|_{L^{p}(T_{m-1})}
         \\&
@@
         \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla u \|_{L^{p}(T_{\iota(m)})}
+        \| \nabla u \|_{L^{p}(T_{m-1})}
         .
@@
         \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{\iota(m)})} 
+        \| w \|_{L^{p}(T_{m-1})} 
         + 
@@
             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla u \|_{L^{p}(T_{\iota(m)})}
+        \| \nabla u \|_{L^{p}(T_{m-1})}
         \right). 
@@
     Suppose again that $1 \leq m \leq M$. 
-    Recall that we write $U_{F_m} := T_m \cup T_{\iota(m)}$. 
+    Recall that we write $U_{F_m} := T_m \cup T_{m-1}$. 
     We use the Poincar\'e--Friedrichs inequality over $U_{F_{m}}$,
@@
         = 
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
-        \| c_{m} \|_{L^{p}(T_{{\iota(m)}})},
-        \\ 
-        \| c_{m} \|_{L^{p}(T_{{\iota(m)}})}
-        \leq 
-        \| w \|_{L^{p}(T_{{\iota(m)}})} + \| w_{F_{m}} \|_{L^{p}(T_{{\iota(m)}})} 
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| c_{m} \|_{L^{p}(T_{{m-1}})},
+        \\ 
+        \| c_{m} \|_{L^{p}(T_{{m-1}})}
+        \leq 
+        \| w \|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
         .
@@
         +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
-        \| w_{F_{m}} \|_{L^{p}(T_{{\iota(m)}})}
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
+        +
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| w \|_{L^{p}(T_{{m-1}})}
         .
@@
         &\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{\iota(m)}})^{\frac q p} } \right)^{\frac 1 q}
+        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
         \left( 
@@
             +
-            \| w_{F_{m}} \|_{L^{p}(T_{{\iota(m)}})}^{p}
+            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
         \right)^{\frac 1 p}
         +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| w \|_{L^{p}(T_{{m-1}})}
         \\&\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{\iota(m)}})^{\frac q p} } \right)^{\frac 1 q}
+        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
         \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
         +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{\iota(m)}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
+        \| w \|_{L^{p}(T_{{m-1}})}
         .
@@
         \max\left(
-            1, \frac{ \vol(T_m) }{ \vol(T_{{\iota(m)}}) } 
+            1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
         \right)
@@
         +
-        \frac{ \vol(T_m) }{ \vol(T_{{\iota(m)}}) }
-        \| w \|_{L^{1}(T_{{\iota(m)}})}
+        \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
+        \| w \|_{L^{1}(T_{{m-1}})}
         .
@@
         +
-        \| w \|_{L^{\infty}(T_{{\iota(m)}})}
+        \| w \|_{L^{\infty}(T_{{m-1}})}
         .
@@
 The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a face-connected path.
-The proof proceeds verbatim, where we merely replace the simplices $T_{m}$ by the convex local patches $U_m$.
+Clearly, the same building principle applies whenever we have any nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ U_m \}$ with a face-connected path.
+The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ U_m \}$.
 This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant.
@@
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
-\cye{Local} patches \cye{(stars)} within triangulations of dimension two and three are examples of such shellable complexes. 
+Local patches (stars) within triangulations of dimension two and three are examples of such shellable complexes. 
 The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures} are our main references for this section. 
@@
 \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
+\caption{A manifold triangulation (left) and not a manifold triangulation (right)}
 \label{figure:not_manifold_triang}
-\caption{A manifold triangulation (left) and not a manifold triangulation (right)}
 \end{figure}
@@
 Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional. 
-\cye{An example of a manifold triangulation and an example which is not a manifold triangulation are given in Figure~\ref{figure:not_manifold_triang}.}
+An example of a manifold triangulation and an example which is not a manifold triangulation are given in Figure~\ref{figure:not_manifold_triang}.
 
 The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball\cye{\sout{,
-and we sometimes call this a \textit{$n$-disk} triangulation}}.
+an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball\mwl{, and we sometimes call this a \textit{$n$-disk} triangulation}.
 An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
@@
     Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
-    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ so small that it only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
+    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ 
+    homeomorphic to an $n$-dimensional ball 
+    so small that its closure $\overline{B_F}$ only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
     Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
@@
 
-We continue with a few more observations about manifold triangulations
-at the intersection of topology and combinatorics. 
-These include the topology of local patches (stars), which is a surprisingly non-trivial topic. 
-We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{locally vertex combinatorial}
-if the star of every simplex $S \in \calT$ is a triangulated $n$-dimensional ball that contains $S$.
-We gather some results that are hard to find in the literature.
+We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. This topics is surprisingly non-trivial and 
+we gather some results that are hard to find in the literature.
+
+We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{combinatorial}
+if for every vertex $V \in \calT$ the local star $\patch_{\calT}(V)$ is a simplicial ball of dimension $n$.
 
@@
     \item 
-    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{\cye{S}}$\todo{MV: OK?}, and dimension $k$.
+    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{S}$, and dimension $k$.
     Let $\calS := \patch_{\calT}(S)$ be its star. 
@@
     For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
-    \begin{align*}
-        v_0, \dots, v_{i-1}, z_{\cye{S}}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}.
-    \end{align*}
+    $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
+%     \begin{align*}
+%         $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
+%     \end{align*}
     The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
     that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS' = \patch_{\calS'}(z_{\cye{S}})$. 
-    In particular, $z_{\cye{S}}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
+    Moreover, $\calS' = \patch_{\calS'}(z_{S})$. 
+    In particular, $z_{S}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
     So it remains to study the topology of vertex stars.
@@
     Conversely, not all topological manifolds, even if compact, can be described as a triangulation. 
-    Such manifolds appear in dimension four and higher:
-    one example is the E8 manifold\todo{MV: reference?}, which is a compact simply-connected topological $4$-manifold that is not homeomorphic to the underlying set of any simplicial complex.
-The construction of such counterexamples typically involves an infinite procedure.
+    Such manifolds, some even compact and simply-connected, appear in dimension four and higher~\cite{akbulut2014casson}.
 %     For each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. 
 \end{remark}
-
-\begin{figure}
-    \centering
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (1) \end{tabular}
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (2) \end{tabular}
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (3) \end{tabular}
-    \begin{tabular}{c}\begin{tikzpicture}
-        \coordinate (O) at (0, 0);
-        \coordinate (A) at ({cos(0)}, {sin(0)});
-        \coordinate (B) at ({cos(60)}, {sin(60)});
-        \coordinate (C) at ({cos(120)}, {sin(120)});
-        \coordinate (D) at ({cos(180)}, {sin(180)});
-        \coordinate (E) at ({cos(240)}, {sin(240)});
-        \coordinate (F) at ({cos(300)}, {sin(300)});
-        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
-        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
-        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
-    \end{tikzpicture}\\ (4) \end{tabular}
-    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation. 
-    (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
-    (2) The new edge patch may already be a subset of the subtriangulation
-    (3) An inadmissible choice because the new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like
-    (4) An inadmissible choice because the new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
-\end{figure}
-
-% \begin{figure}
-%     \centering
-%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
-%         \coordinate (O) at (0, 0);
-%         \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
-%         \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
-%         \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
-%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-%         \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
-%         \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
-%         \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
-%         \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
-%         \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
-%         \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
-%         \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
-%     \end{tikzpicture}\\ (1) \end{tabular}
-%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
-%         \coordinate (O) at (0, 0);
-%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-%         \draw (O) -- (A);
-%         \draw (O) -- (B);
-%         \draw (O) -- (C);
-%         \draw (O) -- (X);
-%         \draw (O) -- (Y);
-%         \draw (O) -- (Z);
-%         %
-%     \end{tikzpicture}\\ (2) \end{tabular}
-%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
-%         \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
-%         % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
-% 
-%         \coordinate (O) at (0, 0);
-%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
-%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
-%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
-%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
-%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
-%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
-%         \coordinate (T) at ({0}, {0}, {3});
-% 
-%         \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
-%         \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
-% 
-%     \end{tikzpicture}\\ (3) \end{tabular}
-%     \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
-% \end{figure}
 
@@
 
-\todo[inline]{MV: Shortened, narrowed, removed repetitions.}
-
-\mwl{Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-the gluing interface is a triangulated submanifold of the boundary. 
-This forces the intermediate triangulations to be particularly well-shaped. 
-We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, 
-as this enables the inductive method of proof.}
+% \mwl{Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
+% by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
+% the gluing interface is a triangulated submanifold of the boundary. 
+% This forces the intermediate triangulations to be particularly well-shaped. 
+% We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
+%It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, as this enables the inductive method of proof.
+% }
 
@@
 \end{align*}
-be the $m$-th \textit{interface set}. 
+the $m$-th \textit{interface set}. 
 % Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface \cye{set} $I_m$ is a \cye{triangulated} manifold of dimension $n-1$.
+We call the enumeration a \emph{shelling} if each interface set $I_m$ is a triangulated manifold of dimension $n-1$.
 
@@
 
-The reason of our interest in shellable simplicial complexes is that they can be constructed by \cye{a} successive adhesion of simplices to intermediate complexes \cye{where these intermediate complexes are} simplicial \disk s \cye{\sout{or a simplicial spheres}}, as shows the following important consequence.\todo{MV: OK?
-``Intermediate'' excludes the last one.}
+The reason of our interest in shellable simplicial complexes is that they can be constructed via successive adhesion of simplices.
+The resulting succession of simplicial complexes consists of simplicial balls or spheres.
 
@@
     $$ 
-    is a \cye{triangulated} manifold with boundary for all $0 \leq m \leq M$.
+    is a triangulated manifold with boundary for all $0 \leq m \leq M$.
     % 
@@
     Suppose that $X_m := T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a topological $n$-ball and that $T_{m+1}$ is the next $n$-simplex in the shelling.
-    By definition, $I_{\cye{m}} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
+    By definition, $I_{m} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
     and it is triangulated by some faces of $T_{m+1}$ and their subsimplices.
@@
     On the one hand, 
-    if $I_{\cye{m}}$ is the entire boundary of $T_{m+1}$, 
+    if $I_{m}$ is the entire boundary of $T_{m+1}$, 
     then it must also be the boundary of the topological $n$-ball $X_{m}$. 
@@
     On the other hand, 
-    if $I_{\cye{m}}$ is a proper subset of the entire boundary of $T_{m+1}$, 
+    if $I_{m}$ is a proper subset of the entire boundary of $T_{m+1}$, 
     then $X_{m} \cup T_{m+1}$ is still a topological $n$-ball.
@@
 
-We \cye{now} collect important examples of shellable triangulations.
-\cye{Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, nonshellable situations can arise}.
-Our main interest are local \cye{patches} (stars) within triangulations\cye{: these are shellable up to three space dimensions, but not necessarily beyond}.
+We now collect important examples of shellable triangulations.
+Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, nonshellable situations can arise.
+Our main interest are local patches (stars) within triangulations: these are shellable up to three space dimensions, but not necessarily beyond.
 
 \begin{example}\label{example:shell_simpl}
-    Any simplex $T$ \cye{(}trivially\cye{)} has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
-    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling\cye{, cf.~\cite[Example 8.2.(iii)]{ziegler1995lectures}}.
+    Any simplex $T$ (trivially) has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
+    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling\mwl{; see Example 8.2.(iii) in~\cite{ziegler1995lectures}}.
 \end{example}
@@
 \end{example}
-
-\cye{\begin{example}
+\begin{example}
     There exists a non-shellable triangulation of a tetrahedron and of a cube in $n=3$, see~\cite[Example 8.9]{ziegler1995lectures}.
-\end{example}}\todo{MV: 3D counterexamples directly here and straight to the point.}
+\end{example}
 
@@
     is a triangulation of some $2$-\disk\ that intersects $T$ only at either two or one edges.
-    Any shelling of $\calT'$ can \cye{in this way} be extended to a shelling of $\calT$\cye{, and} the proof is complete. 
+    Any shelling of $\calT'$ can in this way be extended to a shelling of $\calT$, and the proof is complete. 
+\end{proof}
+
+\begin{lemma}
+    Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
+    Then $\patch_{\calT}(S)$ is shellable. 
+\end{lemma}
+\begin{proof}
+    The statement is trivially true if $S$ is a tetrahedron. 
+    The statement is clear if $S$ is an inner or boundary face of $\calT$,
+    where we only need to enumerate either one or two tetrahedra. 
+    The statement is still easily verified if $S$ is an inner or boundary edge of $\calT$:
+    one chooses a starting tetrahedron (with a boundary face if $S$ is a boundary edge) and rotates around the edge in a fixed direction to create a suitable enumeration. 
+    When $S$ is an inner vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-sphere.
+    Similarly, when $S$ is a boundary vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
+    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondance between the tetrahedra in $\calT$ and the triangles.
+    \footnote{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}
 \end{proof}
@@
 
-\begin{lemma}
-    Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
-    Then $\patch_{\calT}(S)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    \cye{For $S$ a tetrahedron, this is Example~\ref{example:shell_simpl}.}
-    The statement is \cye{also} clear if $S$ is an inner or boundary face of $\calT$\cye{, where we only need to enumerate respectively one or two tetrahedra}. 
-    The statement is \cye{still} easily verified if $S$ is an inner or boundary edge of $\calT$\cye{: one chooses a starting tetrahedron (with a boundary face) and rotates around the edge in a fixed direction to create a suitable enumeration}.
-
-    \cye{When $S$ is an inner vertex, then the \cye{faces} (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-sphere.
-Similarly, when $S$ is a boundary vertex, then the \cye{faces} (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
-Both these $2$-dimensional complexes are shellable \cye{by Lemma~\ref{lemma:shell_2D}}, and any such shelling \cye{immediately yields} a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondance between the tetrahedra in $\calT$ and the triangles.}\footnote{\cye{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}}\todo{MV: but not Lemma~\ref{lemma:stars_are_shellable}, because this first needs the triangulation $\calT$ itself to be shellable, right?}
-\end{proof}
-
 \begin{remark}
     Not all triangulable sets admit a triangulation that is shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations \cye{are} be shellable.
-\cye{For example, if we extend the non-shellable triangulation of a tetrahedron from~\cite[Example 8.9]{ziegler1995lectures}} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$,
-    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the \cye{space} dimension \cye{$n$} is larger than three.
-\end{remark}\todo{MV: Moved up a bit.}
-
-A major structural feature of shellable simplicial complexes 
-is that each time a\cye{n $n$-}simplex is added, star\cye{s} around \cye{lower-dimensional} simpl\cye{ices} gets completed.
+    Moreover, even if a set admits a shellable triangulation, not all of its triangulations are be shellable.
+For example, if we extend the non-shellable triangulation of the tetrahedron from~\cite[Example 8.9]{ziegler1995lectures} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
+    This demonstrates that patches around boundary simplices are not necessarily shellable when the space dimension $n$ is larger than three.
+\end{remark}
+\begin{remark}
+    Not all triangulable sets admit a triangulation that is also shellable. 
+    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
+    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
+\end{remark}
+
+A major structural feature of shellable simplicial complexes is that each time an $n$-simplex is added, stars around lower-dimensional simplices gets completed.
 
@@
     $$ 
-    \cye{\sout{Whenever} Then} $I_{m}$ is \cye{a} union of $k$ different face\cye{\sout{t}}s of $T$,\todo{MV: this is a property, not an assumption, right?} \cye{$1 \leq k \leq n$,} \cye{and} the intersection of those face\cye{\sout{t}}s is an interior simplex $S_{\cye{m}} \in \calT$ of dimension $n-k$ that satisfies
+    Then $I_{m}$ is a union of $k$ different faces of $T$, $1 \leq k \leq n$, and the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-k$ that satisfies 
     $$
-        \patch_{X_{m+1}}(S_{\cye{m}}) = \patch_{\calT}(S_{\cye{m}}).
+        \patch_{X_{m+1}}(S_{m}) = \patch_{\calT}(S_{m}).
     $$
@@
 \begin{proof}
-    We know $I_{m}$ is a \cye{triangulated} submanifold of the boundary of $T$, and so it must be a collection of $k$ face\cye{\sout{t}}s \cye{of $T$, $1 \leq k \leq n$ ($k = n + 1$ can happen for the last enumerated simplex $m = M$ when $\calT$ is an $n$-sphere).
-$I_{m}$ also} constitutes \cye{a} local patch \cye{(star) of $(n-1)$-dimensional simplices around} some simplex $S_{\cye{m}}$ of dimension $n-k$ \cye{in $I_{m}$}.
-    By \cye{definition}, $S_{\cye{m}}$ \cye{is} be a boundary simplex of $X_{m}$\cye{,} and it is an interior simplex of $X_{m+1}$. 
-    But then $S_{\cye{m}}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
-    which means that $\patch_{X_{m+1}}(S_{\cye{m}}) = \patch_{\calT}(S_{\cye{m}})$. 
+    We know $I_{m}$ is a triangulated submanifold of the boundary of $T$, and so it must be a collection of $k$ faces of $T$, $1 \leq k \leq n$ ($k = n + 1$ can happen for the last enumerated simplex $m = M$ when $\calT$ is an $n$-sphere).
+$I_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-k$ in $I_{m}$.
+    By definition, $S_{m}$ is a boundary simplex of $X_{m}$, and it is an interior simplex of $X_{m+1}$. 
+    But then $S_{m}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
+    which means that $\patch_{X_{m+1}}(S_{m}) = \patch_{\calT}(S_{m})$. 
 \end{proof}
-
-\begin{remark}
-    Not all triangulable sets admit a triangulation that is also shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions.
-
-    For example, there exists a non-shellable triangulation of a tetrahedron. 
-    If we extend this triangulation to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, 
-    then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the dimension is larger than the three.
-\end{remark}
 

### 2024-09-29 draft.tex
stuff

@@
  In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
+
+\begin{figure}
+    \centering
+    \begin{tabular}{c}\begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
+        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}\\ (1) \end{tabular}
+    \begin{tabular}{c}\begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
+        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}\\ (2) \end{tabular}
+    \begin{tabular}{c}\begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
+        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}\\ (3) \end{tabular}
+    \begin{tabular}{c}\begin{tikzpicture}
+        \coordinate (O) at (0, 0);
+        \coordinate (A) at ({cos(0)}, {sin(0)});
+        \coordinate (B) at ({cos(60)}, {sin(60)});
+        \coordinate (C) at ({cos(120)}, {sin(120)});
+        \coordinate (D) at ({cos(180)}, {sin(180)});
+        \coordinate (E) at ({cos(240)}, {sin(240)});
+        \coordinate (F) at ({cos(300)}, {sin(300)});
+        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
+        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
+        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
+    \end{tikzpicture}\\ (4) \end{tabular}
+    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation. 
+    (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line.
+    (2) The new edge patch may already be a subset of the subtriangulation
+    (3) An inadmissible choice because the new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like
+    (4) An inadmissible choice because the new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
+\end{figure}
+
+% \begin{figure}
+%     \centering
+%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
+%         \coordinate (O) at (0, 0);
+%         \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
+%         \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
+%         \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
+%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+%         \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
+%         \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
+%         \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
+%         \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
+%         \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
+%         \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
+%         \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
+%     \end{tikzpicture}\\ (1) \end{tabular}
+%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
+%         \coordinate (O) at (0, 0);
+%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
+%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
+%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
+%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+%         \draw (O) -- (A);
+%         \draw (O) -- (B);
+%         \draw (O) -- (C);
+%         \draw (O) -- (X);
+%         \draw (O) -- (Y);
+%         \draw (O) -- (Z);
+%         %
+%     \end{tikzpicture}\\ (2) \end{tabular}
+%     \begin{tabular}{c}\begin{tikzpicture}[scale=0.5]
+%         \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
+%         % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}
+% 
+%         \coordinate (O) at (0, 0);
+%         \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
+%         \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
+%         \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
+%         \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
+%         \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
+%         \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
+%         \coordinate (T) at ({0}, {0}, {3});
+% 
+%         \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
+%         \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;
+% 
+%     \end{tikzpicture}\\ (3) \end{tabular}
+%     \caption{Example of a connected $2$-dimensional manifold triangulation, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
+% \end{figure}
 

### 2024-09-29 main.tex
stuff

@@
 
-\subsection{\cye{A triangulation or a simplicial complex}}
+\subsection{A triangulation or a simplicial complex}
 
@@
 % (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\todo{MV: Don't we only use $n$-dimensional simplicial complexes?
-That would be a simplification of our presentation.}\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
 We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is \sout{defined as} the union 
@@
 We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
-We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-% TODO: Theo suggests reverse order of that sequence
-We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. \mwl{Change the terminology strong path to something else.}
+We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
 Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
@@
 and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
-
-\mwl{We should use clarify face vs facet}
 
@@
 %%%%%%%% END HERE
-
-\mwl{Throughout the manuscript, use a macro for opnorm and equip the matrices with the operator norm index.}
 
@@
 
-We are interested in transformations of Sobolev tensor fields from one domain onto \cye{an}other. 
+We are interested in transformations of Sobolev tensor fields from one domain onto another. 
 Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
@@
   &\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\cye{\infty}}(\Omega)}
-  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\cye{\infty}}(\Omega')}
+  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
+  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
   \| u \|_{L^{p}\Lambda^{k}(\Omega')}
@@
 
-{\color{red}
 We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
@@
 
+\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
 For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
-and the $L^{p}$ de~Rham with full boundary conditions. 
+We solve this for two special cases: 
+either the $L^{p}$ de~Rham complex without boundary conditions, 
+or the $L^{p}$ de~Rham with full boundary conditions. 
+either the $L^{p}$ de~Rham complex without boundary conditions, 
+or the $L^{p}$ de~Rham with full boundary conditions. 
 The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
 We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
+who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
 % 
-In comparison to their work, our discussion is more modest:
+In comparison to their extensive work, our discussion is more modest:
 we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our purpose are explicit bounds for the operator norms, which are of independent interest.
-
-In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
-}
-
-We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
-either the $L^{p}$ de~Rham complex without boundary conditions, \cye{or} the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudo\cye{-}differential operators over domains star-shaped with respect to a ball. 
-In comparison to their work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our purpose are explicit bounds for the operator norms, \cye{giving the Poincar\'e--Friedrichs constants}.
-Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open\todo{MV: Weakly Lipschitz??} set with diameter $\cye{\diam(\Omega)} > 0$\todo{MV: Unifying the notation.}.
+However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
+
+%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
+Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
+\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
 
@@
 We begin with introducing the Costabel-McIntosh kernel.
-For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
+For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
 \begin{equation}\label{math:mainkernel}
-  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
-  .
+  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
+  ,
 \end{equation}
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
+where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
+Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
 we then define the integral operators
 \begin{align*}
-  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
-  \\
-  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align*}
-We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator.
-
-We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
+  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
+  \\
+  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
+\end{align*}
+We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.
+
+We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
 In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
+we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
 Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
 \begin{align*}
-    G_{\ell}(x,y) 
+    \calG_{\mia}(x,y) 
     &= 
-    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
     \\
     &= 
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
     \\
     &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
     .
@@
 \begin{align*}
-    G_{\ell}(x,y) 
+    \calG_{\mia}(x,y) 
     &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{\diam(\Omega)} r^{n-k-1} \,dr 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
     \\
     &= 
-    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ \diam(\Omega)^{n-k} }{n-k}.
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
 \end{align*}
@@
 Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
-We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\ell} u(x) \right|
+Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
+We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| \Poinc_{\mia} u(x) \right|
     &=
     \left| 
-        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
+        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
     \right| 
 %     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
     \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
     .
@@
 \begin{align*}
-    \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
+    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
     &
     =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} \,dr
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
     \\&
     =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
+    =
+    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
     ,
@@
     &
-    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
+    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
     \\&
     =
-    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
+    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
     \\&
     =
-    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
+    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
     %\\&
     =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
     \label{equation:A_Poinc}
@@
 \end{align}
-Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{n-\ell}$. 
-In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
+Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
+and which is bounded by $2^{n-\mia}$. 
+In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
 So the convolution of $u$ is taken against an integrable function. 
@@
 \begin{align*}
-    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
+    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
     &
     \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
     \diam(\Omega)
@@
     \leq 
-    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
     \diam(\Omega)
@@
 \end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
+We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
 Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
@@
 \begin{gather*}
-    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
+    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 %
@@
 We analyze the Bogovski\u{\i} potential operator by similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
+Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
+First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
 Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\ell} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\ell} u(x) \right|
+We estimate $\Bogov_{\mia} u(x)$ pointwise by 
+\begin{align*}
+    \left| \Bogov_{\mia} u(x) \right|
     &=
     \left| 
-        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
+        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
     \right| 
     \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
     \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
+    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
     .
@@
 % \begin{align*}
-%     \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} dz
+%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
 %     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} dr
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
 %     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} dr
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
 %     =
-%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
+%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
 %     .
@@
     &
-    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
+    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
     \\&
     =
-    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
+    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
     \\&
     =
-    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
+    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
     %\\&
     =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
     \label{equation:A_Bogov}
@@
 \end{align*}
-Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
-and which is bounded by $2^{\ell-1}$. 
-In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
+Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
+and which is bounded by $2^{\mia-1}$. 
+In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
 So the convolution of $u$ is taken against an integrable function. 
@@
 \begin{align*}
-    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
+    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
     &
     \leq 
-    \vol_{n-1}(S_1) A(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
     \diam(\Omega)
@@
     \leq 
-    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
     \diam(\Omega)
@@
 \begin{gather*}
-    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
+    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
+% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
 that is, the reconstructed potential has support contained within $\overline\Omega$. 
@@
 \begin{align*}
-    \Poinc_{\ell} u(x) 
+    \Poinc_{\mia} u(x) 
     &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
     \chi_{\Omega}\left(x+t(y-x)\right) 
@@
     &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
+    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
     .
@@
 \begin{align*}
-    \Bogov_{\ell} u(x) 
+    \Bogov_{\mia} u(x) 
     &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
     \chi_{\Omega}\left(y+t(x-y)\right) 
@@
     &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da
+    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
     .
@@
 % We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\ell-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
+% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
+% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
+% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
 % 
@@
 \begin{align*}
-    \Poinc_{\ell,a} u(x) 
+    \Poinc_{\mia,a} u(x) 
     &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt
-    ,
-    \\
-    \Bogov_{\ell,a} u(x) 
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
+    ,
+    \\
+    \Bogov_{\mia,a} u(x) 
     &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt
+    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
     .
@@
 \begin{align*}
-    \Poinc_{\ell} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da,
+    \Poinc_{\mia} u(x) 
+    =
+    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
     \quad 
-    \Bogov_{\ell} u(x) 
-    =
-    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da
+    \Bogov_{\mia} u(x) 
+    =
+    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
     .
@@
 
-Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$.
+Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
 We rewrite the Poincar\'e potential,
 \begin{align*}
-    \Poinc_{\ell,a} u(x) 
+    \Poinc_{\mia,a} u(x) 
     &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
     \\&
@@
     (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
+    \sum_{\sigma \in \Sigma(\mia,n)}
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
     \\&
     = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
     ,
@@
 \begin{align*}
-    \cartan \Poinc_{\ell,a} u(x) 
+    \cartan \Poinc_{\mia,a} u(x) 
     &= 
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     .
@@
     =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
     \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
@@
 \begin{align*}
-    \Poinc_{\ell+1,a} \cartan u(x)
+    \Poinc_{\mia+1,a} \cartan u(x)
     &=
     (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     \,\cartanx^{j} \wedge \cartanx^{\sigma}
@@
     = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
     \,\cartanx^{\sigma}
@@
     - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     \,(x-a)_{\sigma(i)} 
@@
     &
-    \cartan \Poinc_{\ell,a} u(x)
-    +
-    \Poinc_{\ell+1,a} \cartan u(x)
+    \cartan \Poinc_{\mia,a} u(x)
+    +
+    \Poinc_{\mia+1,a} \cartan u(x)
     \\&
     =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{0}^{1} 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     \int_{0}^{1} 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad
     - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
@@
     =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{0}^{1} 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
     \\&
     =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
     \\&
     =
-    \sum_{\sigma \in \Sigma(k,n)} 
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     u_{\sigma}(x) \,\cartanx^{\sigma}
@@
 \end{align*}
-\mwl{What if $\ell = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+\mwl{What if $\mia = 0$ and $u$ is constant? The reconstruction is not complete for constants}
 In summary, after taking the average over $a \in \Omega$:
 \begin{align*}
-    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x).
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\ell} u = u$.
+    u(x) = \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x).
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
 
 The discussion for the Bogovski\u{\i} operator is almost analogous. 
-Suppose that $u \in C^{\infty}\Alt^{\ell}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
+Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
 We rewrite the Bogovski\u{\i} potential,
 \begin{align*}
-    \Bogov_{\ell,a} u(x) 
+    \Bogov_{\mia,a} u(x) 
     &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
     \\&
@@
     (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)}
+    \sum_{\sigma \in \Sigma(\mia,n)}
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
     \\&
     = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
     ,
@@
 \begin{align*}
-    \cartan \Bogov_{\ell,a} u(x) 
+    \cartan \Bogov_{\mia,a} u(x) 
     &= 
-    \ell 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \mia 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     .
@@
 \begin{align*}
-    \Bogov_{\ell+1,a} \cartan u(x)
+    \Bogov_{\mia+1,a} \cartan u(x)
     &=
     (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     \,\cartanx^{j} \wedge \cartanx^{\sigma}
@@
     = 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad 
     - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
@@
     &
-    \cartan \Bogov_{\ell,a} u(x)
-    +
-    \Bogov_{\ell+1,a} \cartan u(x)
+    \cartan \Bogov_{\mia,a} u(x)
+    +
+    \Bogov_{\mia+1,a} \cartan u(x)
     \\&
     =
-    \ell
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{1}^\infty 
-    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     + 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     \int_{1}^\infty 
-    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad
     - 
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
@@
     =
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
     \int_{1}^\infty 
-    \ell t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
     +
-    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
     \\&
     =
-    \sum_{\sigma \in \Sigma(k,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\ell} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
     \\&
     =
-    \sum_{\sigma \in \Sigma(k,n)} 
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     u_{\sigma}(x) \cartanx^{\sigma}
@@
 \begin{align*}
-    u(x) = \cartan \Bogov_{\ell} u(x) + \Bogov_{\ell+1} \cartan u(x)
-    .
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\ell} u = u$.
+    u(x) = \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
 \\
@@
 \mwl{We are in the position to establish the main results of this section.
-Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.
+Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
 This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
@@
 We now state the main results of this section.
-\cye{Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\ell$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\ell)$ and $A_{\Bogov}(n,\ell)$}.
+\cye{Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\mia$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$}.
 
@@
     \begin{align*}
-        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}\Alt^{\ell-1}(\Omega)
+        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
         ,
         \qquad 
-        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
+        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
         .
@@
     \begin{align*}
-        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
+        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
         &\leq 
-        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
         \diam(\Omega)
@@
         \\
-        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
+        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
         &\leq 
-        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
         \diam(\Omega)
@@
     \end{align*}
-    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
-    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
+    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
+    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
 \end{theorem}
 
-\todo[inline]{MV: Do $\Poinc_{\ell}$ and $\Bogov_{\ell}$ still map piecewise polynomials to piecewise polynomials?
+\todo[inline]{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
 Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
@@
 \begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Poinc_{\ell  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\ell-1}(\Omega)$, we verify 
+    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\mia}(\Omega)$.
+
+    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Poinc_{\mia  } u$. 
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
     \begin{align*}
@@
         &=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
         \\&=
-        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
         .
@@
         &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\ell} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\ell}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\ell-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\ell-1}(\bbR^{n})$, 
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+
+    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Bogov_{\mia} u$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
+    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
     it holds that 
@@
         &=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\ell  } u_{i}
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
         \\&=
-        \int_{\Omega} v \wedge \Bogov_{\ell+1} \cartan u_{i}
-        +
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
         .
@@
         &=
-        (-1)^{k(n-k)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\ell  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
     This completes the proof. 
@@
 
-    The operators discussed by Costabel and McIntosh are pseudodifferential operators of negative order, 
+    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
     because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudodifferential operators 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
     have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
@@
     which is why they \cye{can} study domains star-shaped with respect to a ball. 
-    The\cye{ir} operators are pseudodifferential operators of negative order, 
+    The\cye{ir} operators are pseudo-differential operators of negative order, 
     because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudodifferential operators 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
     have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
@@
 
-\section{\cye{Outlook}} \todo{MV: Added this section at the end and moved here the corresponding contents from the introduction} \label{section:outlook}
-
-There are several avenues for further research going \cye{further from the results established in this manuscript}.
-
-\cye{Our} upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), where there are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex \cye{\sout{domains}simplices} \todo{MV: ???} \cye{already} leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a star.
+\section{Outlook}\label{section:outlook}
+
+The most important outcome of this research have been computable upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches. 
+There are several avenues for further research going further from the results established in this manuscript.
+Our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), where there are at least two points where the present techniques can be improved further.
+First, we utilize local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) \mwl{already} leave room for improvement.
+Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
 In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
@@
 Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators \cye{in the sprit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now}.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the sprit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
 % We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
@@
 
-\cye{Concerning the domains considered,} estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to \cye{\sout{spaces} domains} \todo{MV: ???} with simplicial homology groups of \disk s and spheres.
+Concerning the geometric setting, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to topological balls and spheres.
 In particular, domains with shellable triangulations are contractible.
-\cye{We believe that in the forthcoming works, t}hese estimates will \cye{become} subcomponent\cye{s} in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-\mwl{
+We expect that in the forthcoming works, these estimates will become subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+
 % Future work % DONE: Theo : parts already mentioned ??? 
@@
 % such as the Hodge Laplace equation.
-There are several avenues for further research going from here. 
-The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
-There are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
-In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
-Better transformations or more careful estimates are likely possible, as are completely different approaches.
-For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
-
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
-These topics remain for future research.
-
-Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
-In particular, domains with shellable triangulations are contractible.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-}
 

### 2024-09-30 main.tex
additional work ...

@@
 We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
-% This is inspired by the classical proof of what is often called Friedrichs' inequality.
+% This is inspired by the classical proof of what is often called the Friedrichs inequality.
 
@@
         \leq 
+        C_{{\rm{PF}},k,\Omega,p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    where 
+    \begin{align*}
+        C_{{\rm{PF}},k,\Omega,p} 
+        = 
         n A_{\Poinc}(n,k+1) 
@@
         \diam(\Omega)
-        \| \cartan u \|_{L^{p}(\Omega)}
         .
@@
     This follows from the discussion in Section~\ref{section:potentialoperator}.
+    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
 \end{proof}
@@
 These constants are generally not optimal. 
-For example, when $p=2$ and only the divergence is considered, 
+For example, when $p=2$ and when only the divergence is considered, 
 we have the following improved estimate.
@@
 \begin{proof}
-    This is a reduction to Friedrichs' inequality. 
+    This is a reduction to the Friedrichs inequality. 
     Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
     Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
+    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
     The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
@@
     Let $T$ be an $n$-simplex 
-    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
+    and let $F_{0},\dots,F_{\ell}$ be $\ell+1$ different faces of $T$. 
     Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
+    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq \ell$.
     Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq l$
+    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq \ell$
     and  
     \begin{align*}
-        \cartan u = \cartan w,
+        \cartan w = \cartan u,
         \quad 
-        \| w \| 
-        \leq 
-        C_{\PF,\Gamma,l,k,p}(T)
+        \| w \|_{L^{p}(\Omega)} 
+        \leq 
+        C_{\PF,\Gamma,\ell,k,p}(T)
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    Here, $C_{\PF,\Gamma,\ell,k,p}(T) > 0$ is a constant such that 
+    \begin{align*}
+        C_{\PF,\Gamma,\ell,k,p}(T)
+        \leq 
+        2^{\frac n p}
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (\ell+1)/n! } 
+        \algebraicshapemeasure(T)^{k-1}
+        \Ceins{n}(T)^{k}
         \diam(T)^{k} 
-        \| \cartan u \|
-        .
-    \end{align*}
-    Here, $C_{\PF,\Gamma,l,k,p}(T) > 0$ is a constant such that 
-    \begin{align*}
-        C_{\PF,\Gamma,l,k,p}(T)
-        \leq 
-        2^{\frac n p}
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \algebraicshapemeasure(T)^{k-1}
-        \Ceins{n}(T)
         % \matnorm{\Jacobian \varphi}^{k}
@@
 \end{lemma}
+\todo{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
+Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
+Moreover, so far, all the constants $C_{{\rm{PF}},T,p}$, $C_{{\rm{PF}},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\rm{PF}},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
+Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
+We should unify.}
 \begin{proof}
-    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
+    There exists $\varphi : \hat T \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
     We can also assume that the face of $\hat T$
@@
     \begin{align*}
-        \| w \|_{L^{p}(T_{m+1})}
+        \| w \|_{L^{p}(T)}
         &\leq 
@@
     \end{align*}
+    \todo{MV: the norms of the Jacobians have to be fixed.}
     The second inequality follows.
+    \todo{MV: Please a few more details.}
 \end{proof}
@@
 
-The main result of this manuscript is the following theorem.
+Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
+For each $1 \leq m \leq M$, there exists a simplex $S_{m\cye{-1}} \in \calT$ 
+such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $\cye{\cancel{T_{m} \in}} \patch_{\calT}(S_{m\cye{-1}})$.
+\cye{This is precisely $S_m \in \calT$ from Lemma~\ref{lemma:existenceofstar} (there the last simplex is called $T_{m+1}$)}.
+
+\todo[inline]{MV: It might be good to synchronize the indices between the shellability definitions in Section~\ref{section:shellability} and Theorems~\ref{theorem:poincarefriedrichsestimate:grad}, \ref{theorem:poincarefriedrichsestimate:gradzwei}, \ref{theorem:poincarefriedrichsestimate:exterior}, \ref{theorem:poincarefriedrichsestimate:exterior:contraction}.}
+
+We then let $U_{m \cye{-1}}$ be the closure \cye{of} $\patch_{\calT}(S_{m\cye{-1}}) \setminus T_{m}$,
+and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m\cye{-1}})$.
+
+The main result of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorem.
 
@@
 \end{theorem}
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with \cye{an $n$-dimensional} shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_{\cye{M}}$ be a shelling.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
+    and such that for each $T_{m} \in \calT$ in the shelling\cye{, $1 \leq m \leq M$,} 
+    we have the following recursive estimate: 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        C_{\PF,\cye{T_m, I_{m-1}},k,p}(\calT) 
+        \diam(T)^{k} 
+        \left( 
+            \| \cartan u      \|_{L^{p}(T_{m})} 
+            +
+            \Cfive{n}{k}(\calT)^{k+1} 
+            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+            \| \cartan u \|_{L^{p}(U_{m-1})}
+        \right)
+        \\&\qquad
+        + 
+        \Cfive{n}{k}(\calT)^{k} 
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(U_{m-1})}
+        .
+    \end{align*}
+    \todo{MWL: The notation $U_m$ should be settled in the definition of shellings.}
+\end{theorem}\todo{MV: I think we should also write down the bound for $\| w \|_{L^{p}(\Omega)}.$}
 
@@
 \end{proof}
+\begin{proof}
+    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_{\cye{M}}$. 
+    We write $\Omega_m := \cup_{j=0}^{m} T_j$, \cye{$0 \leq m \leq M$,} which is \cye{by Lemma~\ref{lemma:shell_triang_man}} a triangulated $n$-dimensional submanifold with boundary.
+\todo[inline]{MV: It might also be good to synchronize the notations $X_{m}$ and $\Omega_m$.
+I would go for $X_{m}$, since this is a union of $n$-simplices (closed), whereas $\Omega_m$ has a connotation of a domain (open).}
+    For $0 < m \leq M$, by \cye{the definition of shellability in Section~\ref{section:shellability}}, $T_{m}$ and $\cye{\Omega_{m-1}}$ share the interface $\cye{I}_{m\cye{-1}}$, which is a collection of faces of $T_{m}$.
+    \cye{It follows from} Lemma~\ref{lemma:existenceofstar} \cye{that} adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m\cye{-1}} \in \calT$, \cye{where} $U_{m-1} \subseteq \Omega_{m-1}$ is the complement of $T_{m}$ in that newly completed star.\todo{MV: Short, as already explained above in details.}
+
+    \cye{We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound.} Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, \cye{on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex},} there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    \begin{gather*}
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \end{gather*}
+    \cye{We define $w|_{T_0} := w_0$.}
+    Suppose now that $0 < m \leq M$ such that $w\cye{|_{\Omega_{m-1}}} \in W^{p}\Alt^{k}(\Omega_{m-1})$ with $\cartan w = \cartan u$ over $\Omega_{m-1}$.
+\cye{This is true for $m=1$.
+We now define, as in~\cite[equations~(5.12) and~(5.14)]{ern2020stable} or~\cite[equations~(6.7) and~(6.9)]{Chaum_Voh_p_rob_3D_H_curl_24},
+    \begin{align} \label{equation:w''_ext_der}
+    w|_{T_m} := u|_{T_m} + \Xi_{m}^{\ast}((w - u)|_{U_{m-1}}),
+    \end{align}
+\todo[inline]{MV: Direct and simple definition. Only one object. Namely avoids the checking of the compatibility of the boundary condition, which is a bit tedious and requires a rigorous apparatus.}
+    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
+    as \cye{$\Xi_{1}$} in \cye{Proposition}~\ref{proposition:starreflection} \cye{and the pullback is defined in~\eqref{equation:pullback}}. Clearly, $w|_{T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
+    \begin{align*}
+        \trace_{\cye{I}_{m\cye{-1}}} w|_{T_m} = \trace_{\cye{I}_{m\cye{-1}}} w|_{\Omega_{m-1}},
+    \end{align*}
+    since $u$ is trace continuous over $I_{m-1}$ and $\Xi_{m}$ is the identity along $I_{m-1}$, and
+    \begin{align*}
+        \cartan w = \cartan u \text{ over } T_m,
+    \end{align*}
+    since $\cartan w = \cartan u$ over $\Omega_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
+    \begin{align*}
+    w|_{\Omega_{m}} \in W^{p}\Alt^{k}(\Omega_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } \Omega_{m}. 
+    \end{align*}
+    }
+
+    We want to estimate norms. 
+    By construction,
+    \begin{align*}
+        \| \cye{w} \|_{L^{p}(T_{m})}
+        \leq  
+        \| \cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})} \|_{L^{p}(T_{m})}
+        + 
+        \| \cye{u - \Xi_{m}^{\ast}(u|_{U_{m-1}})} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, \cye{since $\trace_{I_{m-1}} (u|_{T_m} - \Xi_{m}^{\ast}(u|_{U_{m-1}})) = 0$, we have}
+    \begin{align*}
+        \| \cye{u - \Xi_{m}^{\ast}(u|_{U_{m-1}})} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
+        + \| \cartan (\Xi_{m}^{\ast}(u|_{U_{m-1}})) \|_{L^{p}(T_{m})} )
+        .
+    \end{align*}\todo{MV: $\diam(T)^{\cye{k}}$???}
+    We also use \cye{Proposition}~\ref{proposition:pullbackestimate} to find 
+    \begin{align*}
+        \| \cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})} \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi_{m} \|^{k}
+        \| \cye{w} \|_{L^{p}(U_{m-1})}
+        ,
+        \\
+        \| \cartan (\cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})}) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+        \| \Jacobian \Xi_{m} \|^{k+1}
+        \| \cartan \cye{u} \|_{L^{p}(U_{m-1})}
+        ,
+    \end{align*}\todo{MV: Which norms of the Jacobians and their determinants?}
+    \cye{where we have employed} that $\cartan w = \cartan u$ \cye{over $\Omega_{m-1}$}. 
+    Using the properties of the reflection mapping in \cye{Proposition}~\ref{proposition:starreflection}, the desired recursive estimate follows. 
+%     \begin{align*}
+%         ...
+%     \end{align*}
+%     This enables the recursion
+%     \begin{align*}
+%         \| w_{m} \|_{L^{p}(T_{m})}
+%         &
+%         \leq  
+%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+%         \| \Jacobian \Xi_{m} \|^{k} 
+%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
+%         \\&\qquad
+%         + 
+%         C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} 
+%         \| \cartan u      \|_{L^{p}(T_{m})} 
+%         \\&\qquad
+%         + 
+%         C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} 
+%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
+%         \| \Jacobian \Xi_{m} \|^{k+1} 
+%         \| \cartan u \|_{L^{p}(U_{m-1})}
+%         .
+%     \end{align*}
+\end{proof}
 
@@
     The proof is complete. 
+\end{proof}
+\todo[inline]{MV: Why a second theorem?
+Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
+Which is better and when?}
+
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an \cye{$n$-dimensional} shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_{\cye{M}}$ be a shelling.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
+    and such that \cye{for each $T_{m} \in \calT$ in the shelling, $1 \leq m \leq M$,
+    we have the following recursive estimate:} 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        \leq 
+        C_{\PF,T,k,p}(T_{0})
+        \prod_{i=0}^{m} 
+        C_{???}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+\end{theorem}
+\begin{proof}
+    We prove this via induction. 
+    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
+    Let us assume that the statement is true for some integer $m-1 \geq 0$.
+
+    We write $\Omega_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
+    which is a triangulated $n$-dimensional submanifold with boundary.
+    By assumption, $T_{m}$ and $\cye{\Omega_{m-1}}$ share the interface $\cye{I}_{m\cye{-1}} \subset \partial T_{m}$, 
+    which is a collection of faces of $T_{m}$. 
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
+    and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in \cye{Proposition}~\ref{proposition:starreflection},
+    which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
+    By assumption, 
+    there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
+    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
+    \begin{align*}
+        \| w_{m-1} \|_{L^{p}(T_{m})}
+        \leq 
+        C_{\PF,T,k,p}(T_{0})
+        \prod_{i=0}^{m} 
+        C_{???}
+        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    Because pullback and exterior derivative commute, 
+    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
+    Moreover, the desired estimate follow from \cye{Proposition}~\ref{proposition:starreflection}.
+    The proof is complete. \todo{MV: I do not get this.}
 \end{proof}

### 2024-10-01 main.tex
more updates...

--- 2024-09-29 main.tex
@@
     \end{align}
-%     \cye{Since $\nabla (w|_{U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u|_{U_{F_m}})$, 
+%     \cye{Since $\nabla (w_{|U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|U_{F_m}})$, 
     We can define the constant
     \begin{align*}
-    c_{m} := w|_{U_{F_m}} - w_{F_{m}}.
+    c_{m} := w_{|U_{F_m}} - w_{F_{m}}.
     \end{align*}
@@
 \begin{align*}
-    I_m 
+    \Gamma_m 
     := 
@@
 % Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface set $I_m$ is a triangulated manifold of dimension $n-1$.
+We call the enumeration a \emph{shelling} if each interface set $\Gamma_m$ is a triangulated manifold of dimension $n-1$.
 
@@
     We prove this claim by induction. 
-    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. 
-    Suppose that $X_m := T_{0} \cup T_{1} \cup \dots \cup T_{m}$ is a topological $n$-ball and that $T_{m+1}$ is the next $n$-simplex in the shelling.
-    By definition, $I_{m} := X_{m} \cap T_{m+1}$ is a submanifold of $\partial T_{m+1}$,
-    and it is triangulated by some faces of $T_{m+1}$ and their subsimplices.
+    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. Let $1 \leq m \leq M$ and suppose that 
+    \begin{align*}
+        X_{m-1} := T_{0} \cup T_{1} \cup \dots \cup T_{m-1}
+    \end{align*}
+    is a topological $n$-ball. Let $T_{m}$ is the next $n$-simplex in the shelling.
+    By definition, $\Gamma_{m} := X_{m-1} \cap T_{m}$ is a submanifold of $\partial T_{m}$,
+    and it is triangulated by some faces of $T_{m}$ and their subsimplices.
 
     Let $F$ be such a face. 
-    By assumption, $F$ must be contained in exactly one $n$-simplex of $T_{0}, T_{1}, \dots, T_{m}$,
-    and $F$ is in the boundary of $X_{m}$. We conclude that $I_{m}$ triangulates a submanifold of the boundary of $X_{m}$.
+    By assumption, $F$ must be contained in exactly one $n$-simplex of $T_{0}, T_{1}, \dots, T_{m-1}$,
+    and $F$ is in the boundary of $X_{m-1}$. 
+    We conclude that $\Gamma_{m}$ triangulates a submanifold of the boundary of $X_{m-1}$.
 
     On the one hand, 
-    if $I_{m}$ is the entire boundary of $T_{m+1}$, 
-    then it must also be the boundary of the topological $n$-ball $X_{m}$. 
-    Hence $X_{m} \cup T_{m+1}$ must be a topological $n$-sphere and thus a manifold without boundary, which requires $m = M$.
+    if $\Gamma_{m}$ is the entire boundary of $T_{m}$, 
+    then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
+    Hence $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
+    which requires $m = M$.
     On the other hand, 
-    if $I_{m}$ is a proper subset of the entire boundary of $T_{m+1}$, 
-    then $X_{m} \cup T_{m+1}$ is still a topological $n$-ball.
+    if $\Gamma_{m}$ is a proper subset of the entire boundary of $T_{m}$, 
+    then $X_{m-1} \cup T_{m}$ is still a topological $n$-ball.
 \end{proof}
@@
     Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
-    For $0 \leq m < M$, write 
+    For $0 \leq m \leq M$, write 
     $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
-        \qquad 
-        I_{m} := X_{m} \cap T_{m+1}.
+        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}.
     $$ 
-    Then $I_{m}$ is a union of $k$ different faces of $T$, $1 \leq k \leq n$, and the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-k$ that satisfies 
+    For $1 \leq m \leq M$, write 
     $$
-        \patch_{X_{m+1}}(S_{m}) = \patch_{\calT}(S_{m}).
+        \Gamma_{m} := X_{m-1} \cap T_{m}.
+    $$ 
+    Then $\Gamma_{m}$ is a union of $\ell$ different faces of $T_{m}$, $1 \leq k \leq n+1$.
+    If $m < M$, then the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-k$ that satisfies 
+    $$
+        \patch_{X_{m}}(S_{m}) = \patch_{\calT}(S_{m}).
     $$
@@
 \begin{proof}
-    We know $I_{m}$ is a triangulated submanifold of the boundary of $T$, and so it must be a collection of $k$ faces of $T$, $1 \leq k \leq n$ ($k = n + 1$ can happen for the last enumerated simplex $m = M$ when $\calT$ is an $n$-sphere).
-$I_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-k$ in $I_{m}$.
-    By definition, $S_{m}$ is a boundary simplex of $X_{m}$, and it is an interior simplex of $X_{m+1}$. 
+    We know $\Gamma_{m}$ is a triangulated submanifold of the boundary of $T_{m}$, 
+    and so it must be a collection of $k$ faces of $T$, $1 \leq k \leq n+1$.
+    Note that $k = n + 1$ can only happen for the last enumerated simplex, $m = M$, if $\calT$ triangulates an $n$-sphere. 
+    $\Gamma_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-k$ in $\Gamma_{m}$.
+    By definition, $S_{m}$ is a boundary simplex of $X_{m}$, 
+    and it is an interior simplex of $X_{m+1}$. 
     But then $S_{m}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
@@
     :=
-    \max\limits_{ \substack{ T \in \calT \; \dim(T)=n \\ 0 \leq l \leq n } }
+    \max\limits_{ \substack{ T \in \calT \\ \dim(T)=n \\ 0 \leq l \leq n } }
     C_{\PF,\Gamma,l,k,p}(T)
-\end{align*}
-
+    .
+\end{align*}
+We settle the following notation for our main result. 
 Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
-For each $1 \leq m \leq M$, there exists a simplex $S_{m} \in \calT$ 
+For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
+\begin{align*}
+    \Gamma_{m} := T_{m} \cap \left( T_{0} \cup \dots \cup T_{m-1} \right)
+\end{align*}
+According to Lemma~\ref{lemma:existenceofstar}, 
+there exists a simplex $S_{m} \in \calT$ 
 such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
-We then let $U_{m}$ be the closure $\patch_{\calT}(S_{m}) \setminus T_{m}$,
-and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
-
-The main result of this manuscript is the following theorem.
+In particular, $\patch_{\calT}(S_{m})$ is already included in the union of the simplices up to $T_m$. 
+We write 
+\begin{align*}
+    U_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
+\end{align*}
+for the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
+
+The main result of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorem.
 
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling.
     Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
-    and such that for each $T_{m} \in \calT$ in the shelling
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
+    and such that for each $T_{m} \in \calT$, $1 \leq m \leq M$, in the shelling
     we have the following recursive estimate: 
@@
         \| w \|_{L^{p}(T_{m})}
-%         &
-%         \leq  
-%         C_{\PF,\Gamma,k,p}(\calT) 
-%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-%         \Cfive{n}{k}(\calT)^{k+1} 
-%         \diam(T)^{k} 
-%         \| \cartan u \|_{L^{p}(U_{m-1})}
-%         \\&\qquad
-%         + 
-%         C_{\PF,\Gamma,k,p}(\calT) 
-%         \diam(T)^{k} 
-%         \| \cartan u      \|_{L^{p}(T_{m})} 
-%         \\&\qquad
-%         + 
-%         \Cdetsechs{n}{k}(\calT)^{-\frac 1 p} 
-%         \Cfive{n}{k}(\calT)^{k} 
-%         \| w \|_{L^{p}(U_{m-1})}
-%         \\
         &
         \leq  
-        C_{\PF,\Gamma,k,p}(\calT) 
+        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
         \diam(T)^{k} 
@@
 \end{theorem}
-
 \begin{proof}
@@
     By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $\Omega_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.
+    We write $X_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.
 
@@
     %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $\Omega_{m-1}$. 
-    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
+    with $\cartan w_{m-1} = \cartan u$ over $X_{m-1}$. 
+    By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
 
@@
     \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $\Omega_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
+    Setting $w_{m} := w_{m-1}$ over $X_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
     we find 
@@
     \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(\Omega_{m})$ with $\cartan w_{m} = \cartan u$ over $\Omega_{m}$.
+    That means that $w_{m} \in W^{p}\Alt^{k}(X_{m})$ with $\cartan w_{m} = \cartan u$ over $X_{m}$.
 
@@
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-        \matnorm{ \Jacobian \Xi_{m} }^{k}
+        \|\det(\Jacobian \Xi_{m}  )\|_{L^{\infty}(T_{m})}^{-\frac 1 p} 
+        \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k}
         \cdot 
@@
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-        \matnorm{ \Jacobian \Xi_{m} }^{k+1}
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(U_{m})} 
+        \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k+1}
         \cdot 
@@
     \end{align*}
-    We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
+    \begin{align*}
+        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
+        \| w \|_{L^{p}(U_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|U_{m-1}})) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
+        \| \cartan u \|_{L^{p}(U_{m-1})}
+        ,
+    \end{align*}
+    We have assumed that $\cartan w_{m-1} = \cartan u_{|X_{m-1}}$. 
     We use the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}. 
-%     \begin{align*}
-%         ...
-%     \end{align*}
-%     This enables the recursion
-%     \begin{align*}
-%         \| w_{m} \|_{L^{p}(T_{m})}
-%         &
-%         \leq  
-%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-%         \matnorm{ \Jacobian \Xi_{m} }^{k} 
-%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
-%         \\&\qquad
-%         + 
-%         C_{\PF,T_{m},\Gamma_{m},k,p} 
-%         \| \cartan u      \|_{L^{p}(T_{m})} 
-%         \\&\qquad
-%         + 
-%         C_{\PF,T_{m},\Gamma_{m},k,p} 
-%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
-%         \matnorm{ \Jacobian \Xi_{m} }^{k+1} 
-%         \| \cartan u \|_{L^{p}(U_{m-1})}
-%         .
-%     \end{align*}
     The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
 \end{proof}
+\begin{proof}
+    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
+    We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
+    For $0 < m \leq M$, by the definition of shellability in Section~\ref{section:shellability}, 
+    $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
+    It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
+    where $U_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
+
+    We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound. 
+    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex}, 
+    there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    \begin{gather*}
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \end{gather*}
+    We define $w_{|T_0} := w_0$. 
+    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
+    This is true for $m = 1$. 
+    We now define, as in Equations~(5.12) and~(5.14) of~\cite{ern2020stable} or Equations~(6.7) and~(6.9)~\cite{Chaum_Voh_p_rob_3D_H_curl_24},
+    \begin{align} \label{equation:w''_ext_der}
+        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{U_{m-1}}),
+    \end{align}
+    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
+    as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
+    Clearly, $w_{|T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
+    \begin{align*}
+        \trace_{\Gamma_{m}} w_{|T_m} = \trace_{\Gamma_{m}} w_{|X_{m-1}},
+    \end{align*}
+    since $u$ is trace continuous over $\Gamma_{m-1}$ and $\Xi_{m}$ is the identity along $\Gamma_{m-1}$, and
+    \begin{align*}
+        \cartan w = \cartan u \text{ over } T_m,
+    \end{align*}
+    since $\cartan w = \cartan u$ over $X_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
+    \begin{align*}
+        w_{|X_{m}} \in W^{p}\Alt^{k}(X_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } X_{m}. 
+    \end{align*}
+
+    We want to estimate norms. 
+    By construction,
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        \leq  
+        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        + 
+        \| u - \Xi_{m}^{\ast}(u_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|U_{m-1}})) = 0$, we have
+    \begin{align*}
+        \| u - \Xi_{m}^{\ast}(u_{|U_{m-1}}) \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
+        + \| \cartan (\Xi_{m}^{\ast}(u_{|U_{m-1}})) \|_{L^{p}(T_{m})} )
+        .
+    \end{align*}
+    We also use Proposition~\ref{proposition:pullbackestimate} to find 
+    \begin{align*}
+        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        &\leq 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
+        \| w \|_{L^{p}(U_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|U_{m-1}})) \|_{L^{p}(T_{m})}
+        &\leq 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
+        \| \cartan u \|_{L^{p}(U_{m-1})}
+        ,
+    \end{align*}
+    \mwl{MV: Which norms of the Jacobians and their determinants?}
+    where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
+    Using the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}, the desired recursive estimate follows. 
+\end{proof}
 
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_m$ be a shelling.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling.
     Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
     such that 
@@
 
-    We write $\Omega_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
+    We write $X_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
     which is a triangulated $n$-dimensional submanifold with boundary.
-    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
+    By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
     which is a collection of faces of $T_{m}$. 
     In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
-    and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+    and we let $U_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
 
@@
     By assumption, 
-    there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
+    there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
     such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
@@
 \end{proof}
+\todo[inline]{MV: Why a second theorem?
+Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
+Which is better and when?
+Add more details to the estimates}
 

### 2024-10-01 main.tex
add new intro and PF gradient section, clean up, various improvements

@@
 \begingroup
-    \color{red!35!yellow}%
+    \color{blue}%
     #1%
@@
 }
+% \color{red!35!yellow}
 
@@
     Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
+    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{martin.vohralik@inria.fr}
 }
@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
+    We construct potentials for the gradient, the curl, and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
+    This class of triangulations in particular includes local patches (stars) in dimension two and three.
     The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
-    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
+    % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
+    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
     % 
@@
     %
-    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
+    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over convex bounded domains. 
+    This is achieved through a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators where we can bound their operator norms.
     \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
-    \cye{Computational examples illustrate the theoretical findings.}
-    \\
-
-    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
-    \cye{We derive} computable bounds \cye{on} the operator norms of our potentials that only depend on the geometry.
-We thus obtain computable upper bounds for \cye{constants in} Poincar\'e--Friedrichs inequalities \cye{as well as} computable lower bounds for the eigenvalues of several vector Laplacians.
-    As a result with independent standing, we \cye{also} establish Poincar\'e--Friedrichs inequalities \cye{with computable constants} for the $L^{p}$ de~Rham complex over convex bounded domains.
-    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
-    \cye{Computational examples illustrate the theoretical findings.}
+    Computational examples illustrate the theoretical findings.
 \end{abstract}
@@
 
-% DONE {Reformulate the first paragraph. } % 
+Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
+The operator norms of the\cye{se} potentials are upper bounds for the Poincar\'e--Friedrichs constants, which quantify the fundamental stability features of a variety of partial differential equations.
+In numerical methods, estimates for the Poincar\'e--Friedrichs constant\cye{s} enter the stability and convergence theory and spectral bounds for \cye{stiffness} matrices.
+\cye{Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians}.
+However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or \cye{more generally} the exterior derivative are \cye{largely unavailable}.
+
+\cye{Our main purpose here is to fill this gap.
+In the gradient case, we can go over with so-called face-connected triangulations.
+However, to proceed} in the \cye{general exterior derivative case, we are brought to} so-called shellable triangulations.
+Even though only contractible domains can ever admit a shellable triangulation, 
+having computable upper bounds for such domains is an important stepping stone towards more general cases.
+\cye{Still, we cover most practical nonconvex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
+\cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}
+
+Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be a bounded connected open set.
+Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
+Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector\cye{-valued} fields.
+
+%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{section:intro_grad}
+
+Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
+\begin{align} \label{equation:W1p}
+    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
+\end{align}
+For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\cye{\grad}}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\cye{\grad}}( \bff ) = \bff$.
+Then,
+%
+\begin{align*}
+    \Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
+\end{align*}
+is the {\em potential operator}. A particular example of our interest is
+%
+\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
+    \Phi_{\cye{\grad}}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+\end{align}
+%
+Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\cye{\grad}}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
+
+\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\cye{\grad}}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
+\begin{align}\label{math:pot_grad_norm}
+    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} }.
+\end{align}\end{subequations}}
+This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
+\begin{subequations}\label{math:PF_gradient}\begin{align} \label{math:PF_gradient_1}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p} 
+    \| \bff \|_{\cye{\bfL}^{p}(\Omega)}.
+\end{align}
+Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
+\begin{align} \label{math:PF_gradient_2}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p}
+    \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}\end{subequations}
+We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
+\begin{align} \label{math:pot_PF_grad}
+    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
+    \| u \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\grad,\Omega,p}
+    \| \bff \|_{\cye{\bfL}^{p}(\Omega)}.
+\end{align}
+for all $\bff \in \nabla W^{1,p}(\Omega)$.}
+
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
+Most research on optimal constants has addressed the case of convex domains.
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+When the domain is not convex but star-shaped with respect to a ball,
+then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
+Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
+\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
+
+%\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
+
+Consider the vector-valued spaces
+\begin{subequations}\label{equation:W_curl_div_p} \begin{align}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
+    .
+\end{align}\end{subequations}
+The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
+This only requires that certain sums of distributional partial derivatives are integrable, 
+and hence these spaces are not classical Sobolev spaces of vector\cye{-valued} fields.
+
+\cye{Let a vector-valued field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
+We are interested in constants for inequalities such as 
+\begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
+    \min\limits_{ \substack{ \cye{\bfu} \in \bfW^{p}(\curl,\Omega) \\ \curl \cye{\bfu} = \bff } } 
+    \| \cye{\bfu} \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\curl,\Omega,p}
+    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
+    ,
+    \\
+    \min\limits_{ \substack{ \cye{\bfu} \in \bfW^{p}(\divergence,\Omega) \\ \divergence \cye{\bfu} = f } } 
+    \| \cye{\bfu} \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\divergence,\Omega,p}
+    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
+    ,
+\end{align}\end{subequations}
+and how these constants can be estimated by the operator norms of {\em linear} potential operators 
+\begin{align*}
+    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \\
+    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
+\end{align*}
+The fundamental difference \cye{with respect to Section~\ref{section:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
+In Section~\ref{section:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
+It is thus trivially complemented for all $p$, with a canonical choice of projection.
+By contrast, in the Banach space case \cye{$p \neq 2$}, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
+\cye{Actually,} the existence of a bounded linear potential operator is \cye{here} a non-trivial fact even in the Hilbert space case \cye{$p = 2$}.
+
+\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
+Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
+\begin{align}
+    \label{math:Weber}
+    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
+\end{align}
+for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
+Yet another writing is 
+\label{math:PF_orth} \begin{align}
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
+\end{align}
+for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
+We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
+However, that easy observation seems restricted to $p=2$.
+
+Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
+\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broder setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
+
+%\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
+
+Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
+This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
+\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $w \in W^{p}\Alt^{k}(\Omega)$, there exists $u \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
+\begin{align} \label{math:PF_DF} 
+    \| u \|_{L^{p}(\Omega} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
+\end{align} 
+}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparsion with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
+
+In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
+\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
+
+Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
+\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
+Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+
+%\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
+
+\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
+\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
+Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
+\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever postprocessing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
+\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
+
+%\subsection{\cye{Objectives and methodology}}
+
+The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
+\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
+
+% \subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
+
+Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
+For scalar-valued functions in the context of Section~\ref{section:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
+%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
+Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
+
+In the gradient case of Section~\ref{section:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+%\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
+
+For vector-valued fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
+We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
+The basic inductive strategy remains the same.
+We start by constructing, say, a curl potential, over a single simplex.
+Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
+However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
+Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
+With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
+
+%\subsubsection{\cye{Analytical constants over convex domains}}
+
+\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (nonconvex and non-star-shaped) triangulated domains.
+Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
+In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
+The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
+
+%\subsubsection{\cye{Domains star-shaped with respect to a ball}}
+
+\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
+This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
+Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
+This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this \cye{in particular} occurs when the domain has sharp reentrant corners.
+Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
+which contain local finite element patches \cye{that} are not star-shaped with respect to any ball.
+
+%\subsubsection{\cye{Potentials subject to partial boundary conditions}}
+
+\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
+\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalit\cye{ies} subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
+We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
+
+%\subsection{\cye{Main results}}
+
+\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be nonconvex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
+Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.}
+\mwl{MV: remark from after Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} moved here.} 
+The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
+\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
+
+\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+They treat triangulated domains that can be nonconvex and non-star-shaped but where the triangulation is shellable.
+As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
+The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei}.}
+
+\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
+\cye{This is summarized in Theorem~\ref{theorem:PF_EC}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:PF_EC} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
+
+\section{Introduction}\label{section:intro}
+
 Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
@@
 which quantify the fundamental stability features of a variety of partial differential equations.
-% which serve a variety of purposes:
-% these constants quantify the fundamental stability properties of partial differential equations, imply lower bounds for the spectra of vector and Hodge Laplacians, and they . 
 However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-% We study potential operators in the special class of domains with shellable triangulations,
-% which include local stars in 2D and 3D. 
-% We bound the operator norms of our operators in terms of the shape regularity of the triangulation.
-
-% We contribute to the construction of potential operators in vector analysis and exterior calculus over triangulated domains. 
-% We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
-% The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
-% In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
-
-% DONE : MV : remove 'For example' 
+
 We illustrate the subject of our discussion with the curl operator. 
-% One example application concerns the curl operator. 
 If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
@@
 The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
-%\color{blue}
 Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
-% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
 In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
-% \color{black}
 \\
@@
 The majority of estimates in the literature address only gradient potentials. 
-% We accomplish our results for a special class of triangulations, so-called shellable triangulations.
-% We accomplish this task in 
 We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
@@
 
-% DONE: MV : Be more didactical: write following as the existence of a potential. 
 Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
@@
 The different scalar potentials only differ by a constant. 
-Therefore, %when the domain is connected, then 
+Therefore, 
 this inequality is equivalent to the following statement: 
@@
 \end{align}
-% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
-% \begin{align}\label{math:intro:poincarefriedrichs:grad}
-%     \min\limits_{c\in\bbR}
-%     \| u - c \|_{L^{p}(\Omega)}
-%     \leq 
-%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-%     \quad 
-%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
-%     .\tag{PF} 
-% \end{align}
 Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
@@
     u \in W^{1,p}(\Omega)
-    , \tag{P} % DONE: tag Poincar\'e inequality 
+    , \tag{P} 
 \end{align}
@@
 Most research on optimal constants has addressed the case of convex domains. 
-% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
 Notably, if the constants are required to depend on the convex domain only via its diameter, 
@@
 Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-% even if the domain is convex, 
 This sharply contrasts to the study of the gradient operator. 
-%
-% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
 We can access some estimates from the literature in the formalism of exterior calculus. 
 We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
-% who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
 who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
@@
 By duality, that implies lower bounds for the case of full boundary conditions.
-% They also provide sequences of inequalities, such as the following in 3D smoothly bounded convex domains:
-% \begin{align}\label{math:intro:guerinisavo}
-%     C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
-% \end{align}
-% We emphasize that \cite{guerini2004eigenvalue} only addresses smoothly bounded domains, but the extension to convex domains is a technicality.
 
@@
 \\
-% DONE: cite Guzman and Salgado in a reasonable manner
 
@@
 and that difference can easily be removed to ensure continuity across that interface.
-% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
 
@@
 
-% This construction of potentials requires triangulations with special conditions: 
-% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Such triangulations are called \textit{shellable}.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
-% In particular, local stars in 2D and 3D triangulations are shellable. 
-% \\
-
-% auxiliary problems 
-% We construct gradient potentials locally over convex domains or face patches. 
 Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
 Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-% DONT: cite VVVV
 While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
@@
 
-% DONE: cite VVVV
 In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
 By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-% These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex smoothly bounded domains.
 
 However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
-% DONE: Theo : But -> However
 We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 We consider the latter outcome to be of independent interest.
-% DONE \mwl{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-% the curl of a vector field over a tetrahedron with vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential. % DONE : Theo : unclear sentence 
 We achieve this by constructing an auxiliary problem subject to full boundary conditions.
@@
 
-% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
 \mwl{What is the best place for this paragraph?}
@@
 The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-% DONE: Theo : paragraph feels misplaced 
-\\
-
-% Future work % DONE: Theo : parts already mentioned ??? 
-% Computable reliable estimates are important: 
-% they quantify the fundamental stability properties of partial differential equations in vector analysis,
-% such as the Hodge Laplace equation. 
+\\
+
 There are several avenues for further research going from here. 
@@
 We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
 On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
@@
 
+\subsection{Organization of this manuscript}
+
 The remainder of this manuscript is structured as follows.
+We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
+We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.
 We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We review Poincar\'e constants for the gradient over convex domains in~\ref{section:poincare}.
-We develop computable upper bounds for Poincar\'e--Friedrichs constants for the gradient over triangulated domains in Section~\ref{section:gradient}.
-We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
-We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
-Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
-We construct an important geometric reflection operator in Section~\ref{section:extension}
-and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-We present numerical examples in Section~\ref{section:numericalexamples}.
+We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
+We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
+Our regularized potential operators over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
+giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
+We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
+and we construct an important geometric reflection operator in Section~\ref{section:extension}. 
+We finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}.
 
@@
 
-\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
-\\
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
+\section{{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and {analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
+
+\todo[inline]{MV: Discussion reorganized.}
+
+\cye{In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.} \cye{We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.} We \cye{in particular} take the opportunity to discuss convex domains as a special case.
+This survey serves as a building block in constructing computable constants over triangulated domains \cye{in a combinatorial way below} but we believe it \cye{is also} of independent interest.
+
+\subsection{Nonlinear and linear potentials}
+
+In the Banach setting $p \neq 2$, finding a norm-minimizing potential \cye{such as $\Phi_{\cye{\grad}}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$} is a nonlinear operation.
+Its existence \cye{may actually} not be guaranteed unless $1 < p < \infty$.
+\cye{However}, any \textit{linear} potential operator $\overline\Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi_{\cye{\grad}}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ \cye{has the} operator norm that \cye{gives} the \cye{upper} bound 
+\begin{align}\label{math:PF_P}
+    \mwl{C_{\grad,\Omega,p} = } 
+    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
     .
 \end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align*}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
+\cye{This explains our interest in the construction of} {\em linear potential operators}.
+
+\subsection{Poincar\'e--Friedrichs and Poincar\'e inequalities}
+
+\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\cye{\grad}}( \bff ) = \bff$ determines $\overline \Phi_{\cye{\grad}}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
+\begin{align*}
+    \overline\Phi_{\cye{\grad}}( \nabla u ) \cye{:}= u - u_{\Omega},
     \quad 
@@
     u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align*}
+    ,
+\end{align*}
+where $u_\Omega$ denotes the average of $u$ \cye{over $\Omega$}, that is,
+\begin{align*}
+    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
+\end{align*}
+\cye{This potential operator can also implicitly be defined by}
+\begin{align*}
+    \overline \Phi_{\grad}( \bff ) 
+    := 
+    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\cye{\bfL}^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*} 
+Its operator norm is the \cye{best} constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
+\begin{align}\label{math:P_gradient}
     \| u - u_{\Omega} \|_{L^{p}(\Omega)}
     \leq 
-    C_{{\rm P},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
+    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)},
     \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    . 
+\end{align}
+\cye{Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient},} 
+%
+\begin{align*}
+    \cye{C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.}
+\end{align*}
+
 Towards a converse inequality, 
 let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
+\begin{align} \label{math:aver_norm}
     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
@@
 \begin{align}\label{math:p_vs_pf}
-    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
+    \cye{C_{\grad,\Omega,p}} \leq 2^{|2/p-1|} \cye{\overline C_{\grad,\Omega,p}}.
 \end{align}
 In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-\\
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
-see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
+
+\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over convex domains} \label{section: PX_convex}
+
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} \cye{or \cite[Lemma~3.24]{ern2021finite}} 
 \begin{align}\label{math:acostaduran}
@@
 \begin{remark}
+    \cye{The above} Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    but individual convex domains may allow for better constants.
+    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for \cye{discussions};
+    for example, triangles allow the reduction of the constant by 20\%.
+\end{remark}
+
+\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+
+We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
+We take the opportunity to discuss convex domains as a preparatory special case.
+This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
+\\
+
+Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
+Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
+We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
+
+We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
+if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
+for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:inequalitypf:gradient}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+Since $\Omega$ is connected, this is equivalent to  
+\begin{align*}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+\\
+
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
+we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
+if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
+% for all $u \in W^{1,p}(\Omega)$
+\begin{align*}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm P},\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
+\begin{align*}
+    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
+\end{align*}
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
+Towards a converse inequality, 
+let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align*}
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
+    = 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align*}
+Here, we have used H\"older's or Jensen's inequality. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
+The triangle inequality now shows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)} 
+    \leq
+    2
+    \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+% \begin{align*}
+%     \color{Emerald}
+%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p-1} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     +
+%     2^{p-1} 
+%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     .
+% \end{align*}
+Via an application of the triangle inequality, 
+the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
+\end{align*}
+In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
+Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
+This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}
+    \leq 
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| u \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
+We thus conclude 
+\begin{align}\label{math:p_vs_pf}
+    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
+\end{align}
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
+\\
+
+There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
+We define the potential 
+\begin{align*}
+    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*}
+If there is a Poincar\'e--Friedrichs constant, then by definition
+\begin{align*}
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
+\end{align*}
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
+Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
+\begin{align*}
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    .
+\end{align*}
+A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
+\begin{align*}
+    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
+\\
+
+In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
+This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+
+\begin{remark}
+    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
+    We want to generalize the discussion to the curl and divergence operators. 
+    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
+    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
+    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
+    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
+    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
+    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
+\end{remark}
+
+% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+
+\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
+
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
+see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
+\begin{align}\label{math:acostaduran}
+    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
+    \leq 
+    \frac{\diam(\Omega)}{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,1}(\Omega)
+    ,
+    \\
+    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
+    \leq 
+    \frac{\diam(\Omega)}{\pi}
+    \| \nabla u \|_{L^{2}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,2}(\Omega)
+    .
+\end{align}
+These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
+Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
+\begin{align}\label{math:chuawheeden}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm P},{\rm CW},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where we use an upper bound by Chua and Wheeden:
+\begin{align*}
+    C_{{\rm P},{\rm CW},p} 
+    := 
+    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
+    \frac{ 
+        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
+    }{ 
+        \| \nabla v \|_{L^{p}([0,1])} 
+    }
+    \leq 
+    \sqrt[p]{p} 2^{1-\frac 1 p}
+    =
+    2
+    \left( \frac p 2 \right)^{\frac 1 p}
+    .
+\end{align*} % DONE: Theo : following sentence : which upper bound ?
+Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
+As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
+
+We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
+when $1 < p < \infty$, one can show that 
+\begin{align}\label{math:esposito:pf}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,{\rm EFNT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align}
+where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
+\begin{align*}
+    C_{\PF,{\rm EFNT},p}
+    :=
+    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
+    .
+\end{align*}
+Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+\begin{align}\label{math:esposito:poincare}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
+    \diam(\Omega)
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}
+When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
+\begin{align}\label{math:l1estimate}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{1}(\Omega)}
+    \leq 
+    \frac{ \diam(\Omega) }{2}
+    \| \nabla u \|_{L^{1}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,1}(\Omega)
+    .
+\end{align}
+When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
+\begin{align}\label{math:lipschitzestimate}
+    \min\limits_{ c \in \bbR }
+    \| u - c \|_{L^{\infty}(\Omega)}
+    \leq 
+    \diam(\Omega)
+    \| \nabla u \|_{L^{\infty}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in W^{1,\infty}(\Omega)
+    .
+\end{align}
+
+% DONT: Keep ?
+% \begin{example}
+%     We explain why \eqref{math:l1estimate} is optimal. 
+%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
+%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
+%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
+%     and $\Omega$ has diameter $2$. 
+%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
+%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
+%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
+% \end{example}
+
+\begin{remark}
+    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
+    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
+    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
+    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
+    In the case $2 \leq p$, 
+    \begin{align*}
+        2^{1-\frac 2 p}
+        C_{\PF,{\rm EFNT},p}
+        =
+        \frac{ 2^{1-\frac 2 p} }{2}
+        \frac{ \sin(\pi/p) }{ \pi/p }
+        \frac{ 1 }{ \sqrt[p]{p-1} }
+        \leq 
+        4^{-\frac 1 p}
+        \leq
+        C_{{\rm P},{\rm CW},p} 
+        .
+    \end{align*}
+    In the case $2 \geq p$, 
+    \begin{align*}
+        2^{\frac 2 p - 1}
+        C_{\PF,{\rm EFNT},p}
+        =
+        \frac{ 2^{\frac 2 p - 1} }{2}
+        \frac{ \sin(\pi/p) }{ \pi/p }
+        \frac{ 1 }{ \sqrt[p]{p-1} }
+        \leq
+        \frac{ 2^{\frac 2 p-1} }{2}
+        &
+        =
+        2^{\frac 2 p - 2}
+        \\&
+        =
+        4^{\frac 1 p - 1}
+        \leq
+        C_{{\rm P},{\rm CW},p} 
+%         % 
+%         .
+%         4^{\frac 1 p}
+%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
+%         =
+%         4^{\frac 1 p}
+%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
+%         \leq 
+%         \frac{1}{2}
+        .
+    \end{align*}
+    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
+    % DONT: insert the original inequality by chua and Wheeden
+    % DONE: chua wheeden upper bound is not optimal!
+    % DONE: Theorem 1.2 in Chua Wheeden 
+% DONT: Keep ?
+%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
+%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
+%     \begin{align*}
+%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
+%         \leq 
+%         \frac{1}{2}
+%         \diam(\Omega)
+%         \| \nabla u \|_{L^{1}(\Omega)}
+%         ,
+%         \quad
+%         \forall 
+%         u \in W^{1,1}(\Omega)
+%         .
+%     \end{align*}
+%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
+%     which implies the Poincar\'e inequality 
+%     \begin{align*}
+%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
+%         \leq 
+%         \diam(\Omega)
+%         \| \nabla u \|_{L^{\infty}(\Omega)}
+%         ,
+%         \quad
+%         \forall 
+%         u \in W^{1,\infty}(\Omega)
+%         %
+%     \end{align*}
+%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
+%     % DONT: review this entire result 
+\end{remark}
+
+% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
+
+\begin{remark}
     Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
@@
 % 
-% {\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
+% {\color{blue}In this section, we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
 \cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
@@
 
-\todo[inline]{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
+\todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
 Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
@@
     We define $w_{|T_0} := w_0$. 
-    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
+    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
     This is true for $m = 1$. 
@@
     \end{align*}
-    \mwl{MV: Which norms of the Jacobians and their determinants?}
     where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
@@
 \end{proof}
-\todo[inline]{MV: Why a second theorem?
+\todo{MV: Why a second theorem?
 Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?

### 2024-10-01 main.tex
spell checker

@@
 having computable upper bounds for such domains is an important stepping stone towards more general cases.
-\cye{Still, we cover most practical nonconvex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
+\cye{Still, we cover most practical non-convex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
 \cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}
@@
 Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
-\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broder setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
+\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
 
@@
 \end{align} 
-}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparsion with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
+}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparison with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
 
@@
 Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
-\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever postprocessing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
+\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
 \cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
@@
 
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (nonconvex and non-star-shaped) triangulated domains.
+\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
 Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
@@
 
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be nonconvex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
+\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
 Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.}
@@
 \cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be nonconvex and non-star-shaped but where the triangulation is shellable.
+They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
 As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
@@
 
-    Without loss of generality, $F$ lies in the hyerplane plane of the second to last coordinates,
+    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
     so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
@@
     % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua wheeden upper bound is not optimal!
+    % DONE: chua Wheeden upper bound is not optimal!
     % DONE: Theorem 1.2 in Chua Wheeden 
@@
 
-% While the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
+% While the underlying idea remains the same, they differ in the way the intermediate potentials are extended.
 % This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result. 
@@
     The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases.
-We hence target its use to local patches (stars), in particular nonconvex boundary stars.
+We hence target its use to local patches (stars), in particular non-convex boundary stars.
 The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ U_m \}$ with a face-connected path.
+Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ U_m \}$ with a face-connected path.
 The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ U_m \}$.
@@
     % The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
-    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
+    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the north pole without loss of generality, and a stereographic projection, 
     % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
@@
 We now collect important examples of shellable triangulations.
-Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, nonshellable situations can arise.
+Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, non-shellable situations can arise.
 Our main interest are local patches (stars) within triangulations: these are shellable up to three space dimensions, but not necessarily beyond.
@@
     Similarly, when $S$ is a boundary vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
-    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondance between the tetrahedra in $\calT$ and the triangles.
+    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondence between the tetrahedra in $\calT$ and the triangles.
     \footnote{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}
@@
         \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_{z}$,
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
         and that it equals $-z_{S'}$ when $x = z_{S'}$.
@@
         We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
-        that satifies the desired mapping properties. 
+        that satisfies the desired mapping properties. 
         It remains to analyze its Jacobian to get explicit estimates.
@@
 %         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
+%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
         The combination of the previous estimates for $\Psi$ and $\Theta$,
@@
         A similar argument applies to the triangulation $\calR'$. 
-        We conclude that $\Xi$ is bi-Lipchitz. 
+        We conclude that $\Xi$ is bi-Lipschitz. 
         \color{black}
@@
 Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the sprit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
 % We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.

### 2024-10-01 main.tex
reorder sections
trying to unify approaches

@@
 Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
-Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector\cye{-valued} fields.
+Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
 
@@
 \end{align}
-For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\cye{\grad}}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\cye{\grad}}( \bff ) = \bff$.
+For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
 Then,
@@
 \begin{align*}
-    \Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
+    \Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
 \end{align*}
@@
 \begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
-    \Phi_{\cye{\grad}}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
 \end{align}
 %
-Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\cye{\grad}}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
-
-\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\cye{\grad}}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
+Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
+
+\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
 \begin{align}\label{math:pot_grad_norm}
     C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} }.
+    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
 \end{align}\end{subequations}}
@@
     C_{\grad,\Omega,p} 
-    \| \bff \|_{\cye{\bfL}^{p}(\Omega)}.
+    \| \bff \|_{\fooL^{p}(\Omega)}.
 \end{align}
@@
     C_{\grad,\Omega,p}
-    \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)},
+    \| \nabla u \|_{\fooL^{p}(\Omega)},
     \quad 
@@
     C_{\grad,\Omega,p}
-    \| \bff \|_{\cye{\bfL}^{p}(\Omega)}.
+    \| \bff \|_{\fooL^{p}(\Omega)}.
 \end{align}
@@
 This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector\cye{-valued} fields.
-
-\cye{Let a vector-valued field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
+and hence these spaces are not classical Sobolev spaces of vector  fields.
+
+\cye{Let a vector field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
 We are interested in constants for inequalities such as 
 \begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
-    \min\limits_{ \substack{ \cye{\bfu} \in \bfW^{p}(\curl,\Omega) \\ \curl \cye{\bfu} = \bff } } 
-    \| \cye{\bfu} \|_{L^{p}(\Omega)}
+    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
+    \| \bfu \|_{L^{p}(\Omega)}
     &\leq 
@@
     \\
-    \min\limits_{ \substack{ \cye{\bfu} \in \bfW^{p}(\divergence,\Omega) \\ \divergence \cye{\bfu} = f } } 
-    \| \cye{\bfu} \|_{L^{p}(\Omega)}
+    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfu = f } } 
+    \| \bfu \|_{L^{p}(\Omega)}
     &\leq 
@@
 It is thus trivially complemented for all $p$, with a canonical choice of projection.
-By contrast, in the Banach space case \cye{$p \neq 2$}, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
-\cye{Actually,} the existence of a bounded linear potential operator is \cye{here} a non-trivial fact even in the Hilbert space case \cye{$p = 2$}.
+By contrast, in the Banach space case $p \neq 2$, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
+\cye{Actually,} the existence of a bounded linear potential operator here is a non-trivial fact even in the Hilbert space case $p = 2$.
 
@@
 
-For vector-valued fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
+For vector fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
 We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
@@
 
-\todo[inline]{MV: Discussion reorganized.}
-
-\cye{In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.} \cye{We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.} We \cye{in particular} take the opportunity to discuss convex domains as a special case.
-This survey serves as a building block in constructing computable constants over triangulated domains \cye{in a combinatorial way below} but we believe it \cye{is also} of independent interest.
+In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
+We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
+In particular, we take the opportunity to discuss convex domains as a special case.
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
 
@@
 
-In the Banach setting $p \neq 2$, finding a norm-minimizing potential \cye{such as $\Phi_{\cye{\grad}}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$} is a nonlinear operation.
-Its existence \cye{may actually} not be guaranteed unless $1 < p < \infty$.
-\cye{However}, any \textit{linear} potential operator $\overline\Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi_{\cye{\grad}}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ \cye{has the} operator norm that \cye{gives} the \cye{upper} bound 
+In the Banach setting $p \neq 2$, finding a norm-minimizing potential such as $\Phi_{\grad}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$ is a nonlinear operation.
+Its existence may actually not be guaranteed unless $1 < p < \infty$.
+However, any \textit{linear} potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi_{\grad}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ has the operator norm that \cye{gives} the upper bound 
 \begin{align}\label{math:PF_P}
@@
     \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} }
+    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }
     \leq 
     \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi_{\cye{\grad}}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
+    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
     .
 \end{align}
-\cye{This explains our interest in the construction of} {\em linear potential operators}.
+This explains our interest in the construction of {\em linear potential operators}.
 
@@
 
-\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\cye{\grad}}( \bff ) = \bff$ determines $\overline \Phi_{\cye{\grad}}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\cye{\grad}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
-\begin{align*}
-    \overline\Phi_{\cye{\grad}}( \nabla u ) \cye{:}= u - u_{\Omega},
+\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\grad}( \bff ) = \bff$ determines $\overline \Phi_{\grad}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
+\begin{align*}
+    \overline\Phi_{\grad}( \nabla u ) \cye{:}= u - u_{\Omega},
     \quad 
@@
 \end{align*}
-where $u_\Omega$ denotes the average of $u$ \cye{over $\Omega$}, that is,
+where $u_\Omega$ denotes the average of $u$ over the domain $\Omega$, that is,
 \begin{align*}
@@
 \end{align*}
-\cye{This potential operator can also implicitly be defined by}
+This potential operator can also implicitly be defined by
 \begin{align*}
@@
     := 
-    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\cye{\bfL}^{p}(\Omega)},
+    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\fooL^{p}(\Omega)},
     \quad 
@@
 \end{align*} 
-Its operator norm is the \cye{best} constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
+Its operator norm is the best constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
 \begin{align}\label{math:P_gradient}
@@
     \leq 
-    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\cye{\bfL}^{p}(\Omega)},
+    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
     \quad 
@@
 \end{align}
-\cye{Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient},} 
-%
-\begin{align*}
-    \cye{C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.}
+Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient}, 
+\begin{align*}
+    C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.
 \end{align*}
@@
 Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| \cye{u}_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
 We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
@@
 \end{align*}
-\cye{Thus}, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    \cye{C_{\grad,\Omega,p}} \leq 2 \cye{\overline C_{\grad,\Omega,p}}.
-\end{align*}
-In the special case $p=2$, since the average \cye{becomes the} orthogonal projection, and this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
+\begin{align*}
+    \color{Emerald}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+    \leq 
+    2^{p-1} 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    +
+    2^{p-1} 
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    \leq 
+    2^{p} 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align*}
+\mwl{Via an application of the triangle inequality, }Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    C_{\grad,\Omega,p} \leq 2 \overline C_{\grad,\Omega,p}.
+\end{align*}
+In the special case $p=2$, taking the average is an orthogonal projection, 
+and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
 Hence,
 \begin{align*}
-    \cye{\overline C_{\grad,\Omega,2}} = \cye{C_{\grad,\Omega,2}}. 
-\end{align*}
-
-\cye{From~\eqref{math:aver_norm},} Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ \cye{as}
+    \overline C_{\grad,\Omega,2} = C_{\grad,\Omega,2}. 
+\end{align*}
+\mwl{
+This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+}
+From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
 \begin{align*}
@@
     u \in L^{p}(\Omega)
-    ,
-\end{align*}
-\cye{where we have also used} $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+    .
+\end{align*}
+Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
 The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
@@
 \begin{align}\label{math:p_vs_pf}
-    \cye{C_{\grad,\Omega,p}} \leq 2^{|2/p-1|} \cye{\overline C_{\grad,\Omega,p}}.
+    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} \overline C_{\grad,\Omega,p}.
 \end{align}
@@
 
+%%%%
+
+\subsection{Old : Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+
+We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
+We take the opportunity to discuss convex domains as a preparatory special case.
+This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
+\\
+
+Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
+Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
+We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
+
+We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
+if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
+for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:inequalitypf:gradient}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+Since $\Omega$ is connected, this is equivalent to  
+\begin{align*}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\PF,\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+\\
+
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
+Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
+we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
+if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
+% for all $u \in W^{1,p}(\Omega)$
+\begin{align*}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{{\rm P},\Omega,p} 
+    \| \nabla u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
+\begin{align*}
+    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
+\end{align*}
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\PF},\Omega,p} \leq C_{{\rm P},\Omega,p}$.
+
+There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
+We define the potential 
+\begin{align*}
+    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*}
+If there is a Poincar\'e--Friedrichs constant, then by definition
+\begin{align*}
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
+\end{align*}
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
+Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
+\begin{align*}
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    .
+\end{align*}
+A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
+\begin{align*}
+    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
+\\
+
+In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
+This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+
+\begin{remark}
+    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
+    We want to generalize the discussion to the curl and divergence operators. 
+    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
+    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
+    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
+    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
+    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
+    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
+\end{remark}
+
+% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+
 \subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over convex domains} \label{section: PX_convex}
@@
 We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} \cye{or \cite[Lemma~3.24]{ern2021finite}} 
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
 \begin{align}\label{math:acostaduran}
@@
 \end{align}
-\cye{where $\diam(\Omega)$ is the diameter of the domain $\Omega$.}
+where $\diam(\Omega)$ is the diameter of the domain $\Omega$.
 These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
@@
 \end{align*}
-Note that the last inequalities \cye{from~\eqref{math:p_vs_pf}} imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+Note that the last inequalities from~\eqref{math:p_vs_pf} imply, again when $1 < p < \infty$, the Poincar\'e inequalities
 \begin{align}\label{math:esposito:poincare}
@@
     % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant via~\eqref{math:p_vs_pf}. 
+    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
     Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
@@
 \begin{remark}
-    \cye{The above} Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    The above Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
     but individual convex domains may allow for better constants.
-    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for \cye{discussions};
+    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for discussions;
     for example, triangles allow the reduction of the constant by 20\%.
@@
 
-\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
-\\
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align*}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align*}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align*}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-% \begin{align*}
-%     \color{Emerald}
-%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p-1} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     +
-%     2^{p-1} 
-%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-%     \leq 
-%     2^{p} 
-%     \| u \|_{L^{p}(\Omega)}^{p}
-%     .
-% \end{align*}
-Via an application of the triangle inequality, 
-the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
-Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
-\end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-\\
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
-see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
-\begin{align}\label{math:acostaduran}
-    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{\diam(\Omega)}{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    ,
-    \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
-    \leq 
-    \frac{\diam(\Omega)}{\pi}
-    \| \nabla u \|_{L^{2}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,2}(\Omega)
-    .
-\end{align}
-These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
-\begin{align}\label{math:chuawheeden}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},{\rm CW},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where we use an upper bound by Chua and Wheeden:
-\begin{align*}
-    C_{{\rm P},{\rm CW},p} 
-    := 
-    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
-    \frac{ 
-        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
-    }{ 
-        \| \nabla v \|_{L^{p}([0,1])} 
-    }
-    \leq 
-    \sqrt[p]{p} 2^{1-\frac 1 p}
-    =
-    2
-    \left( \frac p 2 \right)^{\frac 1 p}
-    .
-\end{align*} % DONE: Theo : following sentence : which upper bound ?
-Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
-As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
-
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
-when $1 < p < \infty$, one can show that 
-\begin{align}\label{math:esposito:pf}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align*}
-    C_{\PF,{\rm EFNT},p}
-    :=
-    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
-    .
-\end{align*}
-Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
-\begin{align}\label{math:esposito:poincare}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
-\begin{align}\label{math:l1estimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{ \diam(\Omega) }{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    .
-\end{align}
-When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
-\begin{align}\label{math:lipschitzestimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{\infty}(\Omega)}
-    \leq 
-    \diam(\Omega)
-    \| \nabla u \|_{L^{\infty}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,\infty}(\Omega)
-    .
-\end{align}
-
-% DONT: Keep ?
-% \begin{example}
-%     We explain why \eqref{math:l1estimate} is optimal. 
-%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
-%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
-%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
-%     and $\Omega$ has diameter $2$. 
-%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
-%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
-%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
-% \end{example}
-
-\begin{remark}
-    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
-    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
-    In the case $2 \leq p$, 
-    \begin{align*}
-        2^{1-\frac 2 p}
-        C_{\PF,{\rm EFNT},p}
-        =
-        \frac{ 2^{1-\frac 2 p} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq 
-        4^{-\frac 1 p}
-        \leq
-        C_{{\rm P},{\rm CW},p} 
-        .
-    \end{align*}
-    In the case $2 \geq p$, 
-    \begin{align*}
-        2^{\frac 2 p - 1}
-        C_{\PF,{\rm EFNT},p}
-        =
-        \frac{ 2^{\frac 2 p - 1} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq
-        \frac{ 2^{\frac 2 p-1} }{2}
-        &
-        =
-        2^{\frac 2 p - 2}
-        \\&
-        =
-        4^{\frac 1 p - 1}
-        \leq
-        C_{{\rm P},{\rm CW},p} 
-%         % 
-%         .
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
-%         =
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
-%         \leq 
-%         \frac{1}{2}
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua Wheeden upper bound is not optimal!
-    % DONE: Theorem 1.2 in Chua Wheeden 
-% DONT: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
-%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-%         \leq 
-%         \frac{1}{2}
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{1}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,1}(\Omega)
-%         .
-%     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
-%     which implies the Poincar\'e inequality 
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,\infty}(\Omega)
-%         %
-%     \end{align*}
-%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
-%     % DONT: review this entire result 
-\end{remark}
-
-% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
-
-\begin{remark}
-    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
-    but individual convex domains may allow for better constants.
-    We refer to \cite{matculevich2016explicit} for an overview of some improved inequalities, such as for triangles.
-    % for example, triangles allow the reduction of the constant by 20\%.
-\end{remark}
-
-% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
-
 \section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
 
-In this section, we develop a stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
+In this section, we develop stepwise computable estimates of Poincar\'e--Friedrichs constants of triangulated domains. 
 The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
@@
         \leq 
-        C_{{\rm{PF}},T_1 \cup T_2,p}
+        C_{{\PF},T_1 \cup T_2,p}
         \| \nabla u \|_{L^{p}(U)}
@@
     \end{align*}
-    Here, $C_{{\rm{PF}},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
+    Here, $C_{{\PF},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
 \end{lemma}
@@
     \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
     \end{gather*}
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\rm{PF}},U_{F_m},p} 
+        C_{{\PF},U_{F_m},p} 
         \| \nabla u \|_{L^{p}(U_{F_m})} 
@@
     \begin{align}\label{math:wFm_inequality}
-        \| w_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\rm{PF}},U_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(U_{F_m})}.
+        \| w_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\PF},U_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(U_{F_m})}.
     \end{align}
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\rm{PF}},U_{F_\ell},p} 
+        C_{{\PF},U_{F_\ell},p} 
         ,
@@
         \volumeratio^{\frac m p}
-        C_{{\rm{PF}},T_{0},p}
+        C_{{\PF},T_{0},p}
         \| \nabla u \|_{L^{p}(T_{0})}
@@
 % Lemma 5.5
+
+\section{Review of vector calculus and exterior calculus}\label{section:calculus}
+
+% We discuss the Sobolev spaces of vector calculus and exterior calculus 
+% with particular emphasis on their transformation behavior. 
+% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
+% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
+% TODO: Fuse these two paragraphs
+
+We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
+We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
+
+Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
+
+\subsection{Vector calculus}
+
+\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
+\begin{gather*}
+    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
+\end{gather*}
+\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
+First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
+and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
+In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
+% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
+The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
+\begin{gather*}
+    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
+\end{gather*}
+The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
+and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
+\begin{gather*}
+    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
+    \\ 
+    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
+\end{gather*}}
+
+We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
+Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
+$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
+$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
+$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
+We also introduce 
+$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
+We define them 
+for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
+\begin{subequations}\label{eq_definition_piola}
+\begin{align*}
+    \phi^{\grad}(v) &= v \circ \phi, \\
+    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
+    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
+    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
+\end{align*}
+\end{subequations}
+Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
+These transformations are invertible. 
+Bounds on the Lebesgue norms will follow from a more general result below. 
+We use the commutativity relations 
+\begin{subequations}\label{eq_piola_commute}
+\begin{align}
+    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
+    \\
+    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
+    \\
+    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
+\end{align}
+\end{subequations}
+where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
+We summarize this as a commuting diagram:
+\begin{align*}
+    \begin{CD}
+        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
+        \\
+        @VV{\phi^{\grad}}V 
+        @VV{\phi^{\curl}}V 
+        @VV{\phi^{\divergence}}V 
+        @VV{\phi^{\rm b}}V 
+        \\
+        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
+    \end{CD}
+\end{align*}
+
+\begin{remark}
+    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
+    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
+    This definition is in accordance with the notion of pullback, which we will review shortly. 
+    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
+    The literature also knows the Piola transform in the direction of the original mapping. 
+\end{remark}
+
+\subsection{Exterior calculus}
+
+%\cye{We now move to} exterior calculus. 
+%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
+
+\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
+Let $V$ be a real vector space. 
+Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
+Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
+if 
+\begin{gather*} 
+    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
+    = 
+    \text{sign}(\pi) 
+    u( v_1, v_2, \ldots, v_k ) 
+\end{gather*}
+for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
+By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
+Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
+
+The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
+Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
+their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
+defined by the formula 
+\begin{gather*}
+    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
+    = 
+    \frac{1}{k! l!} 
+    % \sum_{ \pi \in S_{k+l}} 
+    \sum_{ \pi } 
+    \signum(\pi) 
+    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
+    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
+\end{gather*}
+for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
+Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
+% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
+The exterior product is bilinear and associative, and satisfies 
+\begin{align*}
+    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
+    \quad 
+    \forall u_1 \in \Alt^{k}(V),
+    \quad 
+    \forall u_2 \in \Alt^{l}(V).
+\end{align*}
+We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
+\begin{align*}
+    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
+    \quad 
+    \forall v_1, v_2, \ldots, v_{k-1} \in V.
+\end{align*}
+
+We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
+Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
+Moreover, this particular setting comes with a canonical basis. 
+We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
+This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
+To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
+we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
+and introduce the basic $k$-alternators 
+\begin{align*}
+    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
+    \quad 
+    \forall \sigma \in \Sigma(k,n). 
+\end{align*}
+These define a basis of $\Alt^{k}(\bbR^{n})$.
+Note that 
+$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
+In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
+% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
+
+We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
+which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
+The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
+
+\subsection{Smooth differential forms}
+
+We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
+which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
+The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
+to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
+Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
+\begin{gather*}
+    \omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \omega_{\sigma} \, 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
+\end{gather*}
+where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
+The exterior derivative \( \cartan\omega \) is defined by
+\begin{gather*}
+    \cartan\omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \sum_{j=1}^{n} 
+    \frac{\partial \omega_{\sigma}}{\partial x^j} 
+    \, \cartanx^j \wedge 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
+\end{gather*}
+The exterior derivative is linear and nilpotent, which means 
+\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
+Moreover, it satisfies the Leibniz rule:
+\begin{gather*} 
+    \cartan(\omega \wedge \eta) 
+    = 
+    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
+    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
+    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
+\end{gather*}
+
+\subsection{Sobolev spaces of differential forms}
+
+Let us now turn our attention to Sobolev spaces of differential forms. 
+Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
+We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
+such that its pointwise norm is $p$-integrable. 
+The exterior derivative is defined in the sense of distributions and we introduce 
+\begin{gather*}
+    W^{p}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
+    .
+\end{gather*}
+We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
+if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
+\begin{align*}
+    \int_{\Omega} \cartan v \wedge u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{\Omega} v \wedge f 
+    .
+\end{align*}
+% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
+% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
+% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
+Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
+Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
+We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
+such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+\begin{align*}
+    \int_{B_r(x)} \cartan v \wedge \tilde u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
+    .
+\end{align*}
+If that condition is satisfied, we also write 
+\begin{align*}
+    \trace_{\Gamma} u = 0
+    .
+\end{align*}
+Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
+Lastly, we introduce the closed subspaces 
+\begin{gather*}
+    W^{p}_{0}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
+    .
+\end{gather*}
+% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
+\mwl{This is a closed subspace.
+We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
+Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}
+
+\subsection{Transformations by bi-Lipschitz mappings}
+
+We are interested in transformations of Sobolev tensor fields from one domain onto another. 
+Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
+\begin{align} \label{equation:pullback}
+    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
+    := 
+    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
+\end{align}
+for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
+We cite an explicit transformation estimate~\cite{licht2019smoothed}.
+
+\begin{proposition} \label{proposition:pullbackestimate}
+ Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
+ Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
+ Then 
+ \begin{align}\label{math:pullbackestimate}
+  \begin{split}
+  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
+  &\leq 
+  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
+  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
+  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+  .
+  \end{split}
+ \end{align}
+\end{proposition}
+\notice{MWL:I have simplified the statement to what is needed later.}
+
+\begin{remark}
+    In three dimensions, 
+    the calculus of differential forms can be translated into classical vector calculus. 
+    This is expressed formally as the commuting diagram 
+    \begin{gather*}
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        @VV{\varpi^{3}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\, ,}
+    \end{gather*}
+    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
+    \begin{align*}
+     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
+     &= 
+     \left( u_1, u_2, u_3 \right), 
+     \\
+     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
+     &= 
+     \left( u_{23}, - u_{13}, u_{12} \right).   
+    \end{align*}
+    In two dimensions, 
+    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
+    To the authors' best knowledge, neither convention is dominant in the literature.
+    We summarize the situation in the following commuting diagram: 
+    \begin{gather*} 
+    \begin{CD}
+        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
+        \\
+        @AA{\varkappa^{0}}A 
+        @AA{\varkappa^{1}}A 
+        @AA{\varkappa^{2}}A 
+        \\
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\,.}
+    \end{gather*}
+    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
+We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
+    The other vertical arrows are the identity. 
+    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
+\end{remark}
+
+\subsection{Some approximation properties}
+
+We finally review a few approximation properties. 
+Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
+Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
+
+\begin{lemma}
+%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
+%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
+%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
+\end{lemma}
+
+% \begin{lemma} % TODO: possibly useful
+%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
+% \end{lemma}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
+    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
+\end{lemma}
+\begin{proof}
+    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
+    By the dominated convergence theorem and because $u$ has a weak derivative,
+    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
+    \begin{align*}
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
+        &= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
+        \\&= 
+        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
+        = 
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
+        .
+    \end{align*}
+    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
+
+    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
+    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
+    Define $\varphi_t(x) = tx$ for $t > 1$. 
+    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
+    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
+    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
+    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
+    The desired result follows. 
+\end{proof}
+
+\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
+
+We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
+We already know the optimal constants for the gradient operator over convex domains,
+and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
+We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
+
+\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
+For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
+We solve this for two special cases: 
+either the $L^{p}$ de~Rham complex without boundary conditions, 
+or the $L^{p}$ de~Rham with full boundary conditions. 
+either the $L^{p}$ de~Rham complex without boundary conditions, 
+or the $L^{p}$ de~Rham with full boundary conditions. 
+The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
+% 
+In comparison to their extensive work, our discussion is more modest:
+we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
+
+%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
+Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
+\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
+
+\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
+
+We begin with introducing the Costabel-McIntosh kernel.
+For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
+\begin{equation}\label{math:mainkernel}
+  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
+  ,
+\end{equation}
+where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
+Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
+we then define the integral operators
+\begin{align*}
+  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
+  \\
+  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
+\end{align*}
+We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.
+
+We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
+In order to analyze the properties of the potential operators,
+we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
+Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
+\begin{align*}
+    \calG_{\mia}(x,y) 
+    &= 
+    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \\
+    &= 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    .
+\end{align*}
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
+\begin{align*}
+    \calG_{\mia}(x,y) 
+    &= 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
+    \\
+    &= 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
+\end{align*}
+We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
+
+We begin with the Poincar\'e operator. 
+Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
+Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
+We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| \Poinc_{\mia} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+%     \\&\leq 
+%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
+    .
+\end{align*}
+We recall the radial integrals 
+\begin{align*}
+    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
+    &
+    =
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
+    \\&
+    =
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
+    =
+    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+    ,
+\end{align*}
+where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
+We compute 
+\begin{align}
+    &
+    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
+    \label{equation:A_Poinc}
+    .
+\end{align}
+Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
+and which is bounded by $2^{n-\mia}$. 
+In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
+    &
+    \leq 
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    \\&
+    \leq 
+    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
+Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\begin{gather*}
+    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
+\end{gather*}
+% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+%
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
+
+We analyze the Bogovski\u{\i} potential operator by similar means. 
+Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
+First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
+Consider now the case $x \in \overline\Omega$. 
+We estimate $\Bogov_{\mia} u(x)$ pointwise by 
+\begin{align*}
+    \left| \Bogov_{\mia} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+    \\&\leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
+    .
+\end{align*}
+Using once more the radial integrals discussed above, we compute 
+% We recall the radial integrals 
+% \begin{align*}
+%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
+%     =
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
+%     =
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
+%     =
+%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+%     .
+% \end{align*}
+% We compute 
+\begin{align*}
+    &
+    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
+    \label{equation:A_Bogov}
+    .
+\end{align*}
+Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
+and which is bounded by $2^{\mia-1}$. 
+In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
+    &
+    \leq 
+    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    \\&
+    \leq 
+    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u$ is essentially bounded.
+Since that space is dense in the Lebesgue spaces, a density argument yields: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\begin{gather*}
+    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
+\end{gather*}
+% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
+that is, the reconstructed potential has support contained within $\overline\Omega$. 
+\\
+
+\subsection{Additional properties}
+
+Additional properties of these operators become apparent after a change of variables. 
+We write down the full definition of these operators and perform two substitutions.
+For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
+leading to 
+\begin{align*}
+    \Poinc_{\mia} u(x) 
+    &= 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
+    \chi_{\Omega}\left(x+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
+    .
+\end{align*}
+For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+leading to 
+\begin{align*}
+    \Bogov_{\mia} u(x) 
+    &= 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
+    \chi_{\Omega}\left(y+t(x-y)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
+    .
+\end{align*}
+% We first discuss the support properties of this operator. 
+% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
+% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
+% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
+% 
+Given $a \in \Omega$, we introduce the potential operators 
+\begin{align*}
+    \Poinc_{\mia,a} u(x) 
+    &:= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
+    ,
+    \\
+    \Bogov_{\mia,a} u(x) 
+    &:= 
+    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
+    .
+\end{align*}
+By definition,
+\begin{align*}
+    \Poinc_{\mia} u(x) 
+    =
+    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
+    \quad 
+    \Bogov_{\mia} u(x) 
+    =
+    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
+    .
+\end{align*}
+We study the interaction of these potential operator with the exterior derivative in more detail.
+% 
+That discussion is classical and establishes the exactness of several de~Rham complexes. 
+We recapitulate these arguments since our variants of the regularized potential operators 
+are not yet included in the published literature.
+
+Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
+We rewrite the Poincar\'e potential,
+\begin{align*}
+    \Poinc_{\mia,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Poinc_{\mia,a} u(x) 
+    &= 
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    ,
+\end{align*}
+and apply the Poincar\'e potential operator to this result, which gives 
+\begin{align*}
+    \Poinc_{\mia+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
+    \,\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Poinc_{\mia,a} u(x)
+    +
+    \Poinc_{\mia+1,a} \cartan u(x)
+    \\&
+    =
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    u_{\sigma}(x) \,\cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+\mwl{What if $\mia = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x).
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
+
+The discussion for the Bogovski\u{\i} operator is almost analogous. 
+Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
+We rewrite the Bogovski\u{\i} potential,
+\begin{align*}
+    \Bogov_{\mia,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Bogov_{\mia,a} u(x) 
+    &= 
+    \mia 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    ,
+\end{align*}
+and apply the Bogovski\u{\i} potential operator to this result, which gives 
+\begin{align*}
+    \Bogov_{\mia+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Bogov_{\mia,a} u(x)
+    +
+    \Bogov_{\mia+1,a} \cartan u(x)
+    \\&
+    =
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    u_{\sigma}(x) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
+\\
+
+\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
+
+\mwl{We are in the position to establish the main results of this section.
+Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
+This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
+Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the dimension and the form degree enters the estimate.}
+
+We now state the main results of this section.
+\cye{Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\mia$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$}.
+
+\begin{theorem}\label{theorem:PF_EC}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
+    We have bounded operators 
+    \begin{align*}
+        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
+        ,
+        \qquad 
+        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
+        .
+    \end{align*}
+    They satisfy the operator norm bounds 
+    \begin{align*}
+        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
+        \| u \|_{L^{p}(\Omega)}
+        ,
+        \\
+        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
+        \| u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
+    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
+\end{theorem}
+
+\todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
+Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
+
+\begin{proof}
+    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\mia}(\Omega)$.
+
+    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Poinc_{\mia  } u$. 
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+
+    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Bogov_{\mia} u$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
+    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
+    it holds that 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+    This completes the proof. 
+\end{proof}
+
+% DONE: Density of C infty mit oder ohne c.
+
+% \begin{remark}
+%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
+%     while they are increasing for the Bogovski\u{\i} operator.
+%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
+% \end{remark}
+
+\begin{remark} \label{remark:reg_Poinc_Bog}
+    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    These potentials enable the analysis of de~Rham complexes without boundary conditions.
+    % 
+    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
+    % 
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they can study domains star-shaped with respect to a ball. 
+    Instead, we average over the entire domain, which requires a convex geometry. 
+    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
+    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
+
+    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
+    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
+
+    {\color{blue}
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they \cye{can} study domains star-shaped with respect to a ball. 
+    The\cye{ir} operators are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
+    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
+\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
+    }
+\end{remark}
 
@@
 
-\section{Review of vector calculus and exterior calculus}\label{section:calculus}
-
-% We discuss the Sobolev spaces of vector calculus and exterior calculus 
-% with particular emphasis on their transformation behavior. 
-% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-% TODO: Fuse these two paragraphs
-
-We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
-
-Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
-
-\subsection{Vector calculus}
-
-\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
-\begin{gather*}
-    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
-In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
-The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
-\begin{gather*}
-    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
-\begin{gather*}
-    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \\ 
-    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}}
-
-We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
-$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
-We also introduce 
-$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
-for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
-\begin{subequations}\label{eq_definition_piola}
-\begin{align*}
-    \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
-    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
-    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
-\end{align*}
-\end{subequations}
-Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
-These transformations are invertible. 
-Bounds on the Lebesgue norms will follow from a more general result below. 
-We use the commutativity relations 
-\begin{subequations}\label{eq_piola_commute}
-\begin{align}
-    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
-    \\
-    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
-\end{align}
-\end{subequations}
-where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
-We summarize this as a commuting diagram:
-\begin{align*}
-    \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
-        \\
-        @VV{\phi^{\grad}}V 
-        @VV{\phi^{\curl}}V 
-        @VV{\phi^{\divergence}}V 
-        @VV{\phi^{\rm b}}V 
-        \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
-    \end{CD}
-\end{align*}
-
-\begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
-\end{remark}
-
-\subsection{Exterior calculus}
-
-%\cye{We now move to} exterior calculus. 
-%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
-
-\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
-Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
-Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
-if 
-\begin{gather*} 
-    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
-    = 
-    \text{sign}(\pi) 
-    u( v_1, v_2, \ldots, v_k ) 
-\end{gather*}
-for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
-By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
-Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
-
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
-their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
-defined by the formula 
-\begin{gather*}
-    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
-    = 
-    \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\end{gather*}
-for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
-The exterior product is bilinear and associative, and satisfies 
-\begin{align*}
-    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
-    \quad 
-    \forall u_1 \in \Alt^{k}(V),
-    \quad 
-    \forall u_2 \in \Alt^{l}(V).
-\end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
-\begin{align*}
-    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
-    \quad 
-    \forall v_1, v_2, \ldots, v_{k-1} \in V.
-\end{align*}
-
-We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
-Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
-Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
-This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
-To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
-and introduce the basic $k$-alternators 
-\begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
-    \quad 
-    \forall \sigma \in \Sigma(k,n). 
-\end{align*}
-These define a basis of $\Alt^{k}(\bbR^{n})$.
-Note that 
-$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
-In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
-
-We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
-which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
-The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
-
-\subsection{Smooth differential forms}
-
-We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
-which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
-Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather*}
-    \omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather*}
-where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
-\begin{gather*}
-    \cartan\omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \sum_{j=1}^{n} 
-    \frac{\partial \omega_{\sigma}}{\partial x^j} 
-    \, \cartanx^j \wedge 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\end{gather*}
-The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
-Moreover, it satisfies the Leibniz rule:
-\begin{gather*} 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
-\end{gather*}
-
-\subsection{Sobolev spaces of differential forms}
-
-Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
-We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
-such that its pointwise norm is $p$-integrable. 
-The exterior derivative is defined in the sense of distributions and we introduce 
-\begin{gather*}
-    W^{p}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
-    .
-\end{gather*}
-We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
-% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
-% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
-Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
-Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
-\begin{align*}
-    \int_{B_r(x)} \cartan v \wedge \tilde u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
-    .
-\end{align*}
-If that condition is satisfied, we also write 
-\begin{align*}
-    \trace_{\Gamma} u = 0
-    .
-\end{align*}
-Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
-Lastly, we introduce the closed subspaces 
-\begin{gather*}
-    W^{p}_{0}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
-    .
-\end{gather*}
-% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
-\mwl{This is a closed subspace.
-We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}
-
-\subsection{Transformations by bi-Lipschitz mappings}
-
-We are interested in transformations of Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\begin{align} \label{equation:pullback}
-    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    := 
-    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\end{align}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
-We cite an explicit transformation estimate~\cite{licht2019smoothed}.
-
-\begin{proposition} \label{proposition:pullbackestimate}
- Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
- Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
- Then 
- \begin{align}\label{math:pullbackestimate}
-  \begin{split}
-  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-  &\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-  .
-  \end{split}
- \end{align}
-\end{proposition}
-\notice{MWL:I have simplified the statement to what is needed later.}
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms can be translated into classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \begin{gather*}
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\, ,}
-    \end{gather*}
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \begin{gather*} 
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\,.}
-    \end{gather*}
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
-
-\subsection{Some approximation properties}
-
-We finally review a few approximation properties. 
-Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\begin{lemma}
-%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
-%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
-%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
-\end{lemma}
-
-% \begin{lemma} % TODO: possibly useful
-%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-% \end{lemma}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
-\end{lemma}
-\begin{proof}
-    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
-    By the dominated convergence theorem and because $u$ has a weak derivative,
-    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
-    \begin{align*}
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
-        &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
-        = 
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
-        .
-    \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
-
-    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
-    Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
-    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
-    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
-    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
-    The desired result follows. 
-\end{proof}
-
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
-
-We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-We already know the optimal constants for the gradient operator over convex domains,
-and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
-
-\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
-For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: 
-either the $L^{p}$ de~Rham complex without boundary conditions, 
-or the $L^{p}$ de~Rham with full boundary conditions. 
-either the $L^{p}$ de~Rham complex without boundary conditions, 
-or the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their extensive work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
-
-%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
-\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
-
-\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
-
-We begin with introducing the Costabel-McIntosh kernel.
-For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{math:mainkernel}
-  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
-  ,
-\end{equation}
-where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
-we then define the integral operators
-\begin{align*}
-  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
-  \\
-  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align*}
-We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.
-
-We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
-    .
-\end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
-\end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
-
-We begin with the Poincar\'e operator. 
-Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
-We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    &
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
-    \\&
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    ,
-\end{align*}
-where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
-We compute 
-\begin{align}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
-    \label{equation:A_Poinc}
-    .
-\end{align}
-Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{n-\mia}$. 
-In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-%
-
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
-
-We analyze the Bogovski\u{\i} potential operator by similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\mia} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
-    .
-\end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-%     .
-% \end{align*}
-% We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
-    \label{equation:A_Bogov}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{\mia-1}$. 
-In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
-that is, the reconstructed potential has support contained within $\overline\Omega$. 
-\\
-
-\subsection{Additional properties}
-
-Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
-leading to 
-\begin{align*}
-    \Bogov_{\mia} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
-    \chi_{\Omega}\left(y+t(x-y)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-% We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
-% 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    ,
-    \\
-    \Bogov_{\mia,a} u(x) 
-    &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    .
-\end{align*}
-By definition,
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
-    \quad 
-    \Bogov_{\mia} u(x) 
-    =
-    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
-    .
-\end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-That discussion is classical and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators 
-are not yet included in the published literature.
-
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\mia,a} u(x) 
-    &= 
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    ,
-\end{align*}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
-    \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Poinc_{\mia,a} u(x)
-    +
-    \Poinc_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \,\cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-\mwl{What if $\mia = 0$ and $u$ is constant? The reconstruction is not complete for constants}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x).
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
-
-The discussion for the Bogovski\u{\i} operator is almost analogous. 
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \Bogov_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Bogov_{\mia,a} u(x) 
-    &= 
-    \mia 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    ,
-\end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \Bogov_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Bogov_{\mia,a} u(x)
-    +
-    \Bogov_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x)
-    .
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
-\\
-
-\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
-
-\mwl{We are in the position to establish the main results of this section.
-Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
-This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
-Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.}
-
-We now state the main results of this section.
-\cye{Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\mia$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$}.
-
-\begin{theorem}\label{theorem:PF_EC}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
-\end{theorem}
-
-\todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
-Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
-
-\begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\mia}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Poinc_{\mia  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\mia} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    This completes the proof. 
-\end{proof}
-
-% DONE: Density of C infty mit oder ohne c.
-
-% \begin{remark}
-%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-%     while they are increasing for the Bogovski\u{\i} operator.
-%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
-% \end{remark}
-
-\begin{remark} \label{remark:reg_Poinc_Bog}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % 
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-
-    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
-
-    {\color{blue}
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they \cye{can} study domains star-shaped with respect to a ball. 
-    The\cye{ir} operators are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
-    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
-\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
-    }
-\end{remark}
-
 \section{Reflections and Deformations on shellable stars}\label{section:extension}
@@
         \leq 
-        C_{{\rm{PF}},k,\Omega,p}
+        C_{{\PF},k,\Omega,p}
         \| \cartan u \|_{L^{p}(\Omega)}
@@
     \begin{align*}
-        C_{{\rm{PF}},k,\Omega,p} 
+        C_{{\PF},k,\Omega,p} 
         = 
@@
 Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
-Moreover, so far, all the constants $C_{{\rm{PF}},T,p}$, $C_{{\rm{PF}},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\rm{PF}},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
+Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
 Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
@@
     \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
     \end{gather*}

### 2024-10-01 main.tex
affiliations

@@
-\documentclass[10pt,letterpaper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
 \usepackage{fullpage}
-\usepackage[margin=0.1cm]{geometry}
+% \usepackage[margin=0.1cm]{geometry}
 \input{header}
@@
 \author{
-    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
-    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
+    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
+    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
     Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{martin.vohralik@inria.fr}

### 2024-10-02 main.tex
work on vector/exterior calculus section; improving (ongoing) the potential operators

@@
 We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalit\cye{ies} subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
+\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
@@
 \end{gather*}
-\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
+Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
+We recall $L^{p}(\Omega)$, the space of scalar-valued $p$-integrable functions defined on $\Omega$
 and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
 In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
 The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
@@
     \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}}
+\end{gather*}
 
@@
 
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
+The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra
+(see~Chapter 14 in \cite{lee2012smooth}). 
 Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
@@
 \end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
+The interior product is in some sense dual to the exterior product. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define the interior product $v \lrcorner u \in \Alt^{k-1}(V)$ via 
 \begin{align*}
@@
 
-We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
+We employ the exterior algebra only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
 Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
@@
 Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
+Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
 We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
@@
 for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
-We cite an explicit transformation estimate~\cite{licht2019smoothed}.
-
-\begin{proposition} \label{proposition:pullbackestimate}
+We cite an explicit transformation estimate~ (see~\cite{licht2019smoothed}) and a special estimate when the transformation is affine (see~Corollary~6~\cite{stern2013lp}).
+
+\begin{proposition}\label{proposition:pullbackestimate}
     Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
@@
     Then 
- \begin{align}\label{math:pullbackestimate}
-  \begin{split}
+    \begin{align}
         \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
@@
         .
-  \end{split}
+    \end{align}
+    If $\phi$ is affine and $\sigma_1 \geq \sigma_2 \geq \dots \geq \sigma_n$ are the singular values of $\Jacobian\phi$, then 
+    \begin{align}
+        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
+        &\leq 
+        \sigma_1 \sigma_2 \cdots \sigma_k \cdot 
+        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
+        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+        .
     \end{align}
 \end{proposition}
-\notice{MWL:I have simplified the statement to what is needed later.}
 
@@
     In three dimensions, 
-    the calculus of differential forms can be translated into classical vector calculus. 
+    the calculus of differential forms is in correspondence with classical vector calculus. 
     This is expressed formally as the commuting diagram 
@@
     the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant in the literature.
+    To the authors' best knowledge, neither convention is dominant over the other in the literature.
     We summarize the situation in the following commuting diagram: 
@@
 We finally review a few approximation properties. 
-Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
+Let $\mollifier$ be a non-negative scalar function whose integral equals one and whose support lies in the unit ball around the origin.
 Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
@@
     Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
+    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega) \subseteq W^{p}_{0}\Lambda^{k}(\Omega)$ 
     and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
@@
 
-We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-We already know the optimal constants for the gradient operator over convex domains,
-and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
-
-\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
-For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: 
-either the $L^{p}$ de~Rham complex without boundary conditions, 
-or the $L^{p}$ de~Rham with full boundary conditions. 
-either the $L^{p}$ de~Rham complex without boundary conditions, 
-or the $L^{p}$ de~Rham with full boundary conditions. 
+% We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
+% We already know the optimal constants for the gradient operator over convex domains,
+% and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
+% We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$. 
+% % 
+% We bound the norms of regularized potential operators for the exterior derivative over convex domains.
+% We solve this for two special cases:
+
+We now develop bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
+Here, we consider two special cases: 
+either the $L^{p}$ de~Rham complex without boundary conditions, or the $L^{p}$ de~Rham with full boundary conditions. 
 The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
@@
 we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
+However, our goal are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
 
@@
 Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
-\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
+
+% \todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
 
@@
 \end{align*}
-We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.
-
-We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
+We call $\Poinc_{\mia}$ the \emph{Poincar\'e operator} and $\Bogov_{\mia}$ the \emph{Bogovski\u{\i} operator}.
+
+We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually converge. 
 In order to analyze the properties of the potential operators,
@@
 Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
+First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$.
+Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
 Consider now the case $x \in \overline\Omega$. 
@@
 
-\subsection{Additional properties}
-
-Additional properties of these operators become apparent after a change of variables. 
+\subsection{Interaction of potential operators with the exterior derivative}
+
+More properties of these operators become apparent after a change of variables. 
 We write down the full definition of these operators and perform two substitutions.
@@
 % 
-That discussion is classical and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators 
-are not yet included in the published literature.
+The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
+We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.
+
+\mwl{Some of the notation here needs to be simplified or introducted: Sigma for all integers, possily empty. remove or add indices}
 
@@
     &= 
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
     \\&\qquad
@@
     \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
     ,
@@
     = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
     \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
@@
     \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\
+    &\text{ \mwl{if j wedge sigma is not too much in the first place}}
     .
@@
     =
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
     \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
@@
     =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     \int_{0}^{1} 
@@
     +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
     \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
@@
     \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
     =
     \sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \,\cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-\mwl{What if $\mia = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+    \left( u_{\sigma}(x) - 0^k u_{\sigma}(a) \right) \,\cartanx^{\sigma}
+    .
+\end{align*}
+We conclude that, 
+\begin{align*}
+    u(x) &= \cartan \Poinc_{0,a} u(x) - u(a)
+    \\
+    u(x) &= \cartan \Poinc_{\mia,a} u(x) + \Poinc_{\mia+1,a} \cartan u(x), \qquad 1 \leq \mia \leq n.
+\end{align*}
 In summary, after taking the average over $a \in \Omega$:
 \begin{align*}
-    u(x) = \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x).
+    u(x) &= \cartan \Poinc_{0} u(x) - \vol(\Omega)^{-1} \int_\Omega u(a)
+    \\
+    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
 \end{align*}
@@
     &= 
-    \mia 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
     \\&\qquad
@@
     = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
     \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
@@
     =
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
     \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
@@
     =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \sum_{\sigma \in \Sigma(\mia,n)} 
     \int_{1}^\infty 
@@
     +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
     \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
@@
     \\&
-    =
+    \mwl{=
     \sum_{\sigma \in \Sigma(\mia,n)} 
@@
     u(x)
-    .
+    .}
 \end{align*}

### 2024-10-02 main.tex
still ongoing rewrite

@@
 To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
+we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$, where $k, n \in \bbZ$, 
 and introduce the basic $k$-alternators 
@@
     + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     \int_{0}^{1} 
@@
     \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
+    =
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
     \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
@@
     (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
     \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
@@
     - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
+    %\sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
@@
     \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\
-    &\text{ \mwl{if j wedge sigma is not too much in the first place}}
     .
@@
     - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
@@
     \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&\qquad
+    + 
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
+    \int_{0}^{1} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     \\&
@@
 \begin{align*}
+    \minus 
     \Bogov_{\mia,a} u(x) 
@@
 \begin{align*}
+    \minus 
     \cartan \Bogov_{\mia,a} u(x) 
@@
 \begin{align*}
+    \minus 
     \Bogov_{\mia+1,a} \cartan u(x)
@@
     &
+    - 
     \cartan \Bogov_{\mia,a} u(x)
-    +
+    -
     \Bogov_{\mia+1,a} \cartan u(x)

### 2024-10-02 main.tex
triangulation, combinatorial; some macros

--- 2024-10-01 main.tex
@@
-\documentclass[10pt,a4paper]{article}
+\documentclass[10pt,letterpaper]{article}
 \usepackage[utf8]{inputenc}
 \usepackage{fullpage}
-% \usepackage[margin=0.1cm]{geometry}
+\usepackage[margin=0.1cm]{geometry}
 \input{header}
@@
 \begingroup
-    \color{blue}%
+    \color{red!35!yellow}%
     #1%
@@
 }
-% \color{red!35!yellow}
 
@@
 \author{
-    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
-    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{martin.vohralik@inria.fr}
+    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
+    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
+    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
 }
@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl, and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations in particular includes local patches (stars) in dimension two and three.
+    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
+    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
     The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
-    % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
+    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
     % 
@@
     %
-    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators where we can bound their operator norms.
+    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
+    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
     \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
-    Computational examples illustrate the theoretical findings.
+    \cye{Computational examples illustrate the theoretical findings.}
+    \\
+
+    We construct potentials for the gradient, the curl\cye{,} and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
+    This class of triangulations \cye{in particular} includes local \cye{patches (stars)} in dimension two and three.
+    \cye{We derive} computable bounds \cye{on} the operator norms of our potentials that only depend on the geometry.
+We thus obtain computable upper bounds for \cye{constants in} Poincar\'e--Friedrichs inequalities \cye{as well as} computable lower bounds for the eigenvalues of several vector Laplacians.
+    As a result with independent standing, we \cye{also} establish Poincar\'e--Friedrichs inequalities \cye{with computable constants} for the $L^{p}$ de~Rham complex over convex bounded domains.
+    This is achieved through \cye{a suitable construction of regularized} Poincar\'e and Bogovski\u{\i} potential operators \cye{where we can bound their operator norms}.
+    \cye{Computational examples illustrate the theoretical findings.}
 \end{abstract}
@@
 
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the\cye{se} potentials are upper bounds for the Poincar\'e--Friedrichs constants, which quantify the fundamental stability features of a variety of partial differential equations.
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant\cye{s} enter the stability and convergence theory and spectral bounds for \cye{stiffness} matrices.
-\cye{Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians}.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or \cye{more generally} the exterior derivative are \cye{largely unavailable}.
-
-\cye{Our main purpose here is to fill this gap.
-In the gradient case, we can go over with so-called face-connected triangulations.
-However, to proceed} in the \cye{general exterior derivative case, we are brought to} so-called shellable triangulations.
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards more general cases.
-\cye{Still, we cover most practical non-convex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
-\cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}
-
-Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be a bounded connected open set.
-Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
-Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
-
-%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{section:intro_grad}
-
-Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
-\begin{align} \label{equation:W1p}
-    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
-\end{align}
-For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
-Then,
-%
-\begin{align*}
-    \Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
-\end{align*}
-is the {\em potential operator}. A particular example of our interest is
-%
-\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
-    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
-\end{align}
-%
-Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
-
-\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
-\begin{align}\label{math:pot_grad_norm}
-    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
-\end{align}\end{subequations}}
-This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
-\begin{subequations}\label{math:PF_gradient}\begin{align} \label{math:PF_gradient_1}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
-\begin{align} \label{math:PF_gradient_2}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p}
-    \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}\end{subequations}
-We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
-\begin{align} \label{math:pot_PF_grad}
-    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
-    \| u \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\grad,\Omega,p}
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-for all $\bff \in \nabla W^{1,p}(\Omega)$.}
-
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
-Most research on optimal constants has addressed the case of convex domains.
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
-\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
-
-%\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
-
-Consider the vector-valued spaces
-\begin{subequations}\label{equation:W_curl_div_p} \begin{align}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align}\end{subequations}
-The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector  fields.
-
-\cye{Let a vector field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
-We are interested in constants for inequalities such as 
-\begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
-    ,
-    \\
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfu = f } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
-    ,
-\end{align}\end{subequations}
-and how these constants can be estimated by the operator norms of {\em linear} potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-The fundamental difference \cye{with respect to Section~\ref{section:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
-In Section~\ref{section:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
-It is thus trivially complemented for all $p$, with a canonical choice of projection.
-By contrast, in the Banach space case $p \neq 2$, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
-\cye{Actually,} the existence of a bounded linear potential operator here is a non-trivial fact even in the Hilbert space case $p = 2$.
-
-\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
-Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
-\begin{align}
-    \label{math:Weber}
-    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
-\end{align}
-for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
-Yet another writing is 
-\label{math:PF_orth} \begin{align}
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
-\end{align}
-for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
-Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
-However, that easy observation seems restricted to $p=2$.
-
-Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
-\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
-
-%\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
-
-Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
-This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
-\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $w \in W^{p}\Alt^{k}(\Omega)$, there exists $u \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
-\begin{align} \label{math:PF_DF} 
-    \| u \|_{L^{p}(\Omega} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
-\end{align} 
-}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparison with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
-
-In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
-\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
-
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
-\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
-Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-
-%\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
-
-\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
-\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
-Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
-\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
-\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
-
-%\subsection{\cye{Objectives and methodology}}
-
-The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
-\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
-
-% \subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
-
-Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
-For scalar-valued functions in the context of Section~\ref{section:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
-%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
-Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
-
-In the gradient case of Section~\ref{section:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-%\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
-
-For vector fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
-We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
-However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
-Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
-With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
-
-%\subsubsection{\cye{Analytical constants over convex domains}}
-
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
-Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
-In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
-The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
-
-%\subsubsection{\cye{Domains star-shaped with respect to a ball}}
-
-\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
-This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
-Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
-This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this \cye{in particular} occurs when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
-which contain local finite element patches \cye{that} are not star-shaped with respect to any ball.
-
-%\subsubsection{\cye{Potentials subject to partial boundary conditions}}
-
-\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalit\cye{ies} subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
-We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
-
-%\subsection{\cye{Main results}}
-
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.}
-\mwl{MV: remark from after Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} moved here.} 
-The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
-\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
-
-\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
-As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei}.}
-
-\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
-\cye{This is summarized in Theorem~\ref{theorem:PF_EC}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:PF_EC} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
-
-\section{Introduction}\label{section:intro}
-
+% DONE {Reformulate the first paragraph. } % 
 Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
@@
 which quantify the fundamental stability features of a variety of partial differential equations.
+% which serve a variety of purposes:
+% these constants quantify the fundamental stability properties of partial differential equations, imply lower bounds for the spectra of vector and Hodge Laplacians, and they . 
 However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-
+% We study potential operators in the special class of domains with shellable triangulations,
+% which include local stars in 2D and 3D. 
+% We bound the operator norms of our operators in terms of the shape regularity of the triangulation.
+
+% We contribute to the construction of potential operators in vector analysis and exterior calculus over triangulated domains. 
+% We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. 
+% The operator norms of these potentials will satisfy explicitly computable bounds in Lebesgue norms only in terms of the geometry. 
+% In particular, such operator norms bound yield computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians.
+
+% DONE : MV : remove 'For example' 
 We illustrate the subject of our discussion with the curl operator. 
+% One example application concerns the curl operator. 
 If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
@@
 The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
+%\color{blue}
 Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
+% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
 In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
+% \color{black}
 \\
@@
 The majority of estimates in the literature address only gradient potentials. 
+% We accomplish our results for a special class of triangulations, so-called shellable triangulations.
+% We accomplish this task in 
 We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
@@
 
+% DONE: MV : Be more didactical: write following as the existence of a potential. 
 Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
@@
 The different scalar potentials only differ by a constant. 
-Therefore, 
+Therefore, %when the domain is connected, then 
 this inequality is equivalent to the following statement: 
@@
 \end{align}
+% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
+% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
+% \begin{align}\label{math:intro:poincarefriedrichs:grad}
+%     \min\limits_{c\in\bbR}
+%     \| u - c \|_{L^{p}(\Omega)}
+%     \leq 
+%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
+%     \quad 
+%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
+%     .\tag{PF} 
+% \end{align}
 Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
@@
     u \in W^{1,p}(\Omega)
-    , \tag{P} 
+    , \tag{P} % DONE: tag Poincar\'e inequality 
 \end{align}
@@
 Most research on optimal constants has addressed the case of convex domains. 
+% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
 Notably, if the constants are required to depend on the convex domain only via its diameter, 
@@
 Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
+% even if the domain is convex, 
 This sharply contrasts to the study of the gradient operator. 
+%
+% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
 We can access some estimates from the literature in the formalism of exterior calculus. 
 We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
+% who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
 who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
@@
 By duality, that implies lower bounds for the case of full boundary conditions.
+% They also provide sequences of inequalities, such as the following in 3D smoothly bounded convex domains:
+% \begin{align}\label{math:intro:guerinisavo}
+%     C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
+% \end{align}
+% We emphasize that \cite{guerini2004eigenvalue} only addresses smoothly bounded domains, but the extension to convex domains is a technicality.
 
@@
 \\
+% DONE: cite Guzman and Salgado in a reasonable manner
 
@@
 and that difference can easily be removed to ensure continuity across that interface. 
+% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
 
@@
 
+% This construction of potentials requires triangulations with special conditions: 
+% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Such triangulations are called \textit{shellable}.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
+% In particular, local stars in 2D and 3D triangulations are shellable. 
+% \\
+
+% auxiliary problems 
+% We construct gradient potentials locally over convex domains or face patches. 
 Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
 Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
+% DONT: cite VVVV
 While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
@@
 
+% DONE: cite VVVV
 In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
 By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+% These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex smoothly bounded domains.
 
 However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy.
+% DONE: Theo : But -> However
 We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 We consider the latter outcome to be of independent interest. 
+% DONE \mwl{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.
 
@@
 we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
+% the curl of a vector field over a tetrahedron with vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential. % DONE : Theo : unclear sentence 
 We achieve this by constructing an auxiliary problem subject to full boundary conditions.
@@
 
+% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
 \mwl{What is the best place for this paragraph?}
@@
 The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
+%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
+% DONE: Theo : paragraph feels misplaced 
+\\
+
+% Future work % DONE: Theo : parts already mentioned ??? 
+% Computable reliable estimates are important: 
+% they quantify the fundamental stability properties of partial differential equations in vector analysis,
+% such as the Hodge Laplace equation. 
 There are several avenues for further research going from here. 
@@
 We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
 On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
@@
 
-\subsection{Organization of this manuscript}
-
 The remainder of this manuscript is structured as follows.
-We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
-We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.
 We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
-We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
-Our regularized potential operators over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
-giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
-We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
-and we construct an important geometric reflection operator in Section~\ref{section:extension}. 
-We finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}.
+We review Poincar\'e constants for the gradient over convex domains in~\ref{section:poincare}.
+We develop computable upper bounds for Poincar\'e--Friedrichs constants for the gradient over triangulated domains in Section~\ref{section:gradient}.
+We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
+We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
+Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
+We construct an important geometric reflection operator in Section~\ref{section:extension}
+and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+We present numerical examples in Section~\ref{section:numericalexamples}.
 
@@
 We call these points the \emph{vertices} of the simplex $T$.
+The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
+and its remaining points constitute the \textit{boundary} of the simplex.
 If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
@@
 
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
-
 A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$.
 We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is \sout{defined as} the union 
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
 \begin{align*}
@@
 Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
-% \begin{remark}
     Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
@@
     Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
-% \end{remark}
 }
@@
 \end{gather*}
-We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial structural observation is the following.~\footnote{\todo{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}}
+We also write $\Minako_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+A crucial structural observation is the following.
 
@@
 
-\subsection{...}
+\subsection{Shape measures and related quantities}
 
@@
 
-    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
+    Without loss of generality, $F$ lies in the hyerplane plane of the second to last coordinates,
     so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
@@
 
-\section{{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and {analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
-
-In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
-We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
-In particular, we take the opportunity to discuss convex domains as a special case.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
-
-\subsection{Nonlinear and linear potentials}
-
-In the Banach setting $p \neq 2$, finding a norm-minimizing potential such as $\Phi_{\grad}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$ is a nonlinear operation.
-Its existence may actually not be guaranteed unless $1 < p < \infty$.
-However, any \textit{linear} potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi_{\grad}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ has the operator norm that \cye{gives} the upper bound 
-\begin{align}\label{math:PF_P}
-    \mwl{C_{\grad,\Omega,p} = } 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
-    .
-\end{align}
-This explains our interest in the construction of {\em linear potential operators}.
-
-\subsection{Poincar\'e--Friedrichs and Poincar\'e inequalities}
-
-\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\grad}( \bff ) = \bff$ determines $\overline \Phi_{\grad}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
-\begin{align*}
-    \overline\Phi_{\grad}( \nabla u ) \cye{:}= u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_\Omega$ denotes the average of $u$ over the domain $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-This potential operator can also implicitly be defined by
-\begin{align*}
-    \overline \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the best constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
-\begin{align}\label{math:P_gradient}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    . 
-\end{align}
-Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient}, 
-\begin{align*}
-    C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.
-\end{align*}
-
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align} \label{math:aver_norm}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-\begin{align*}
-    \color{Emerald}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-    \leq 
-    2^{p-1} 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    +
-    2^{p-1} 
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    \leq 
-    2^{p} 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-\mwl{Via an application of the triangle inequality, }Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{\grad,\Omega,p} \leq 2 \overline C_{\grad,\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, 
-and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
-Hence,
-\begin{align*}
-    \overline C_{\grad,\Omega,2} = C_{\grad,\Omega,2}. 
-\end{align*}
-\mwl{
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-}
-From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} \overline C_{\grad,\Omega,p}.
-\end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-
-%%%%
-
-\subsection{Old : Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+\section{Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
 
@@
 \end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\PF},\Omega,p} \leq C_{{\rm P},\Omega,p}$.
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{{\rm P},\Omega,p}$. 
+Towards a converse inequality, 
+let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align*}
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
+    = 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align*}
+Here, we have used H\"older's or Jensen's inequality. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
+The triangle inequality now shows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)} 
+    \leq
+    2
+    \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+% \begin{align*}
+%     \color{Emerald}
+%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p-1} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     +
+%     2^{p-1} 
+%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+%     \leq 
+%     2^{p} 
+%     \| u \|_{L^{p}(\Omega)}^{p}
+%     .
+% \end{align*}
+Via an application of the triangle inequality, 
+the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
+\end{align*}
+In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$.
+Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$.
+This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}
+    \leq 
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| u \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
+We thus conclude 
+\begin{align}\label{math:p_vs_pf}
+    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.
+\end{align}
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
+\\
 
@@
 
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over convex domains} \label{section: PX_convex}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
+\subsection{Poincar\'e--Friedrichs inequalities over convex domains}
+
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
+see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
+Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
 \begin{align}\label{math:acostaduran}
@@
     u \in W^{1,2}(\Omega)
-    ,
+    .
 \end{align}
-where $\diam(\Omega)$ is the diameter of the domain $\Omega$.
 These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
@@
     .
-\end{align*} 
+\end{align*} % DONE: Theo : following sentence : which upper bound ?
 Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
@@
 
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}, \cite[Theorem~1.1]{esposito2013poincare}): 
+We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
 when $1 < p < \infty$, one can show that 
@@
 \end{align*}
-Note that the last inequalities from~\eqref{math:p_vs_pf} imply, again when $1 < p < \infty$, the Poincar\'e inequalities
+Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
 \begin{align}\label{math:esposito:poincare}
@@
     % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua Wheeden upper bound is not optimal!
+    % DONE: chua wheeden upper bound is not optimal!
     % DONE: Theorem 1.2 in Chua Wheeden 
@@
 \begin{remark}
-    The above Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
+    Any optimal Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
     but individual convex domains may allow for better constants.
-    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for discussions;
-    for example, triangles allow the reduction of the constant by 20\%.
+    We refer to \cite{matculevich2016explicit} for an overview of some improved inequalities, such as for triangles.
+    % for example, triangles allow the reduction of the constant by 20\%.
 \end{remark}
 
+% DONE: I imagine that $\Delta^n$ is a reference simplex, but this has not been introduced earlier.
+
 \section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
 
-In this section, we develop stepwise computable estimates of Poincar\'e--Friedrichs constants of triangulated domains. 
+In this section, we develop a stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
 The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
@@
 % 
-% {\color{blue}In this section, we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
+% {\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
 \cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
@@
 
-% While the underlying idea remains the same, they differ in the way the intermediate potentials are extended.
+% While the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
 % This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result. 
@@
         \leq 
-        C_{{\PF},T_1 \cup T_2,p}
+        C_{{\rm{PF}},T_1 \cup T_2,p}
         \| \nabla u \|_{L^{p}(U)}
@@
     \end{align*}
-    Here, $C_{{\PF},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
+    Here, $C_{{\rm{PF}},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
 \end{lemma}
@@
     \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
     \end{gather*}
@@
         C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(U_{F_m})} 
+        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
         ,
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},U_{F_m},p} 
-        \| \nabla u \|_{L^{p}(U_{F_m})} 
+        C_{{\rm{PF}},\Minako_{F_m},p} 
+        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
         . 
@@
     Suppose again that $1 \leq m \leq M$. 
-    Recall that we write $U_{F_m} := T_m \cup T_{m-1}$. 
-    We use the Poincar\'e--Friedrichs inequality over $U_{F_{m}}$,
+    Recall that we write $\Minako_{F_m} := T_m \cup T_{m-1}$. 
+    We use the Poincar\'e--Friedrichs inequality over $\Minako_{F_{m}}$,
     as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
-    to find $w_{F_m} \in W^{1,p}(U_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $U_{F_m}$ and 
+    to find $w_{F_m} \in W^{1,p}(\Minako_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Minako_{F_m}$ and 
     \begin{align}\label{math:wFm_inequality}
-        \| w_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\PF},U_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(U_{F_m})}.
+        \| w_{F_m} \|_{L^{p}(\Minako_{F_m})} \leq C_{{\rm{PF}},\Minako_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Minako_{F_m})}.
     \end{align}
-%     \cye{Since $\nabla (w_{|U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|U_{F_m}})$, 
+%     \cye{Since $\nabla (w_{|\Minako_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Minako_{F_m}})$, 
     We can define the constant
     \begin{align*}
-    c_{m} := w_{|U_{F_m}} - w_{F_{m}}.
+    c_{m} := w_{|\Minako_{F_m}} - w_{F_{m}}.
     \end{align*}
@@
         \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
+        \| w_{F_{m}} \|_{L^{p}(\Minako_{F_m})} 
         +
@@
         \right)
-        \| w_{F_m} \|_{L^{1}(U_{F_m})}
+        \| w_{F_m} \|_{L^{1}(\Minako_{F_m})}
         +
@@
         2
-        \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
+        \| w_{F_m} \|_{L^{\infty}(\Minako_{F_m})}
         +
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},U_{F_\ell},p} 
+        C_{{\rm{PF}},\Minako_{F_\ell},p} 
         ,
@@
         \right)
-        \| \nabla u \|_{L^{p}(U_{F_\ell})}
+        \| \nabla u \|_{L^{p}(\Minako_{F_\ell})}
         \\&
@@
         \volumeratio^{\frac m p}
-        C_{{\PF},T_{0},p}
+        C_{{\rm{PF}},T_{0},p}
         \| \nabla u \|_{L^{p}(T_{0})}
@@
     The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases.
-We hence target its use to local patches (stars), in particular non-convex boundary stars.
+We hence target its use to local patches (stars), in particular nonconvex boundary stars.
 The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ U_m \}$ with a face-connected path.
-The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ U_m \}$.
+Clearly, the same building principle applies whenever we have any nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ \Minako_m \}$ with a face-connected path.
+The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$.
 This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant.
@@
 % Lemma 5.5
-
-\section{Review of vector calculus and exterior calculus}\label{section:calculus}
-
-% We discuss the Sobolev spaces of vector calculus and exterior calculus 
-% with particular emphasis on their transformation behavior. 
-% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-% TODO: Fuse these two paragraphs
-
-We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
-
-Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
-
-\subsection{Vector calculus}
-
-\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
-\begin{gather*}
-    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
-In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
-The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
-\begin{gather*}
-    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
-\begin{gather*}
-    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \\ 
-    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}}
-
-We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
-$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
-We also introduce 
-$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
-for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
-\begin{subequations}\label{eq_definition_piola}
-\begin{align*}
-    \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
-    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
-    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
-\end{align*}
-\end{subequations}
-Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
-These transformations are invertible. 
-Bounds on the Lebesgue norms will follow from a more general result below. 
-We use the commutativity relations 
-\begin{subequations}\label{eq_piola_commute}
-\begin{align}
-    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
-    \\
-    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
-\end{align}
-\end{subequations}
-where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
-We summarize this as a commuting diagram:
-\begin{align*}
-    \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
-        \\
-        @VV{\phi^{\grad}}V 
-        @VV{\phi^{\curl}}V 
-        @VV{\phi^{\divergence}}V 
-        @VV{\phi^{\rm b}}V 
-        \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
-    \end{CD}
-\end{align*}
-
-\begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
-\end{remark}
-
-\subsection{Exterior calculus}
-
-%\cye{We now move to} exterior calculus. 
-%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
-
-\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
-Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
-Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
-if 
-\begin{gather*} 
-    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
-    = 
-    \text{sign}(\pi) 
-    u( v_1, v_2, \ldots, v_k ) 
-\end{gather*}
-for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
-By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
-Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
-
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
-their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
-defined by the formula 
-\begin{gather*}
-    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
-    = 
-    \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\end{gather*}
-for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
-The exterior product is bilinear and associative, and satisfies 
-\begin{align*}
-    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
-    \quad 
-    \forall u_1 \in \Alt^{k}(V),
-    \quad 
-    \forall u_2 \in \Alt^{l}(V).
-\end{align*}
-We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
-\begin{align*}
-    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
-    \quad 
-    \forall v_1, v_2, \ldots, v_{k-1} \in V.
-\end{align*}
-
-We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
-Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
-Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
-This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
-To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
-and introduce the basic $k$-alternators 
-\begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
-    \quad 
-    \forall \sigma \in \Sigma(k,n). 
-\end{align*}
-These define a basis of $\Alt^{k}(\bbR^{n})$.
-Note that 
-$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
-In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
-
-We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
-which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
-The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
-
-\subsection{Smooth differential forms}
-
-We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
-which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
-Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather*}
-    \omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather*}
-where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
-\begin{gather*}
-    \cartan\omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \sum_{j=1}^{n} 
-    \frac{\partial \omega_{\sigma}}{\partial x^j} 
-    \, \cartanx^j \wedge 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\end{gather*}
-The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
-Moreover, it satisfies the Leibniz rule:
-\begin{gather*} 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
-\end{gather*}
-
-\subsection{Sobolev spaces of differential forms}
-
-Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
-We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
-such that its pointwise norm is $p$-integrable. 
-The exterior derivative is defined in the sense of distributions and we introduce 
-\begin{gather*}
-    W^{p}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
-    .
-\end{gather*}
-We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
-% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
-% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
-Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
-Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
-\begin{align*}
-    \int_{B_r(x)} \cartan v \wedge \tilde u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
-    .
-\end{align*}
-If that condition is satisfied, we also write 
-\begin{align*}
-    \trace_{\Gamma} u = 0
-    .
-\end{align*}
-Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
-Lastly, we introduce the closed subspaces 
-\begin{gather*}
-    W^{p}_{0}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
-    .
-\end{gather*}
-% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
-\mwl{This is a closed subspace.
-We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}
-
-\subsection{Transformations by bi-Lipschitz mappings}
-
-We are interested in transformations of Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\begin{align} \label{equation:pullback}
-    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    := 
-    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\end{align}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
-We cite an explicit transformation estimate~\cite{licht2019smoothed}.
-
-\begin{proposition} \label{proposition:pullbackestimate}
- Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
- Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
- Then 
- \begin{align}\label{math:pullbackestimate}
-  \begin{split}
-  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-  &\leq 
-  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-  .
-  \end{split}
- \end{align}
-\end{proposition}
-\notice{MWL:I have simplified the statement to what is needed later.}
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms can be translated into classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \begin{gather*}
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\, ,}
-    \end{gather*}
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \begin{gather*} 
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\,.}
-    \end{gather*}
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
-
-\subsection{Some approximation properties}
-
-We finally review a few approximation properties. 
-Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\begin{lemma}
-%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
-%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
-%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
-\end{lemma}
-
-% \begin{lemma} % TODO: possibly useful
-%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-% \end{lemma}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
-\end{lemma}
-\begin{proof}
-    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
-    By the dominated convergence theorem and because $u$ has a weak derivative,
-    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
-    \begin{align*}
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
-        &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
-        = 
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
-        .
-    \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
-
-    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
-    Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
-    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
-    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
-    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
-    The desired result follows. 
-\end{proof}
-
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
-
-We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-We already know the optimal constants for the gradient operator over convex domains,
-and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
-
-\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
-For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
-We solve this for two special cases: 
-either the $L^{p}$ de~Rham complex without boundary conditions, 
-or the $L^{p}$ de~Rham with full boundary conditions. 
-either the $L^{p}$ de~Rham complex without boundary conditions, 
-or the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their extensive work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
-
-%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
-\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
-
-\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
-
-We begin with introducing the Costabel-McIntosh kernel.
-For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{math:mainkernel}
-  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
-  ,
-\end{equation}
-where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
-we then define the integral operators
-\begin{align*}
-  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
-  \\
-  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align*}
-We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.
-
-We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
-    .
-\end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
-\end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
-
-We begin with the Poincar\'e operator. 
-Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
-We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    &
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
-    \\&
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    ,
-\end{align*}
-where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
-We compute 
-\begin{align}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
-    \label{equation:A_Poinc}
-    .
-\end{align}
-Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{n-\mia}$. 
-In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-%
-
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
-
-We analyze the Bogovski\u{\i} potential operator by similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\mia} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
-    .
-\end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-%     .
-% \end{align*}
-% We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
-    \label{equation:A_Bogov}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{\mia-1}$. 
-In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
-that is, the reconstructed potential has support contained within $\overline\Omega$. 
-\\
-
-\subsection{Additional properties}
-
-Additional properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
-leading to 
-\begin{align*}
-    \Bogov_{\mia} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
-    \chi_{\Omega}\left(y+t(x-y)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-% We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
-% 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    ,
-    \\
-    \Bogov_{\mia,a} u(x) 
-    &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    .
-\end{align*}
-By definition,
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
-    \quad 
-    \Bogov_{\mia} u(x) 
-    =
-    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
-    .
-\end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-That discussion is classical and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators 
-are not yet included in the published literature.
-
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\mia,a} u(x) 
-    &= 
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    ,
-\end{align*}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
-    \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Poinc_{\mia,a} u(x)
-    +
-    \Poinc_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \,\cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-\mwl{What if $\mia = 0$ and $u$ is constant? The reconstruction is not complete for constants}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x).
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
-
-The discussion for the Bogovski\u{\i} operator is almost analogous. 
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \Bogov_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Bogov_{\mia,a} u(x) 
-    &= 
-    \mia 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    ,
-\end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \Bogov_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Bogov_{\mia,a} u(x)
-    +
-    \Bogov_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \mia
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    u(x)
-    .
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x)
-    .
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
-\\
-
-\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
-
-\mwl{We are in the position to establish the main results of this section.
-Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
-This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
-Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.}
-
-We now state the main results of this section.
-\cye{Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\mia$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$}.
-
-\begin{theorem}\label{theorem:PF_EC}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
-\end{theorem}
-
-\todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
-Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
-
-\begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\mia}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Poinc_{\mia  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\mia} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    This completes the proof. 
-\end{proof}
-
-% DONE: Density of C infty mit oder ohne c.
-
-% \begin{remark}
-%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-%     while they are increasing for the Bogovski\u{\i} operator.
-%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
-% \end{remark}
-
-\begin{remark} \label{remark:reg_Poinc_Bog}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % 
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-
-    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
-
-    {\color{blue}
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they \cye{can} study domains star-shaped with respect to a ball. 
-    The\cye{ir} operators are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
-    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
-\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
-    }
-\end{remark}
 
@@
     % The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
-    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the north pole without loss of generality, and a stereographic projection, 
+    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
     % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
@@
 We now collect important examples of shellable triangulations.
-Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, non-shellable situations can arise.
+Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, nonshellable situations can arise.
 Our main interest are local patches (stars) within triangulations: these are shellable up to three space dimensions, but not necessarily beyond.
@@
     Similarly, when $S$ is a boundary vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
-    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondence between the tetrahedra in $\calT$ and the triangles.
+    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondance between the tetrahedra in $\calT$ and the triangles.
     \footnote{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}
@@
 
+\section{Review of vector calculus and exterior calculus}\label{section:calculus}
+
+% We discuss the Sobolev spaces of vector calculus and exterior calculus 
+% with particular emphasis on their transformation behavior. 
+% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
+% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
+% TODO: Fuse these two paragraphs
+
+We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
+We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
+
+Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
+
+\subsection{Vector calculus}
+
+\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
+\begin{gather*}
+    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
+\end{gather*}
+\mwl{Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
+First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
+and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
+In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
+% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
+The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
+\begin{gather*}
+    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    .
+\end{gather*}
+The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
+and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
+\begin{gather*}
+    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
+    \\ 
+    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
+\end{gather*}}
+
+We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
+Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
+$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
+$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
+$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
+We also introduce 
+$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
+We define them 
+for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
+\begin{subequations}\label{eq_definition_piola}
+\begin{align*}
+    \phi^{\grad}(v) &= v \circ \phi, \\
+    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
+    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
+    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
+\end{align*}
+\end{subequations}
+Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
+These transformations are invertible. 
+Bounds on the Lebesgue norms will follow from a more general result below. 
+We use the commutativity relations 
+\begin{subequations}\label{eq_piola_commute}
+\begin{align}
+    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
+    \\
+    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
+    \\
+    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
+\end{align}
+\end{subequations}
+where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
+We summarize this as a commuting diagram:
+\begin{align*}
+    \begin{CD}
+        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
+        \\
+        @VV{\phi^{\grad}}V 
+        @VV{\phi^{\curl}}V 
+        @VV{\phi^{\divergence}}V 
+        @VV{\phi^{\rm b}}V 
+        \\
+        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
+    \end{CD}
+\end{align*}
+
+\begin{remark}
+    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
+    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
+    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
+    This definition is in accordance with the notion of pullback, which we will review shortly. 
+    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
+    The literature also knows the Piola transform in the direction of the original mapping. 
+\end{remark}
+
+\subsection{Exterior calculus}
+
+%\cye{We now move to} exterior calculus. 
+%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
+
+\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
+Let $V$ be a real vector space. 
+Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
+Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
+if 
+\begin{gather*} 
+    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
+    = 
+    \text{sign}(\pi) 
+    u( v_1, v_2, \ldots, v_k ) 
+\end{gather*}
+for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
+By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
+Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
+
+The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra. 
+Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
+their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
+defined by the formula 
+\begin{gather*}
+    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
+    = 
+    \frac{1}{k! l!} 
+    % \sum_{ \pi \in S_{k+l}} 
+    \sum_{ \pi } 
+    \signum(\pi) 
+    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
+    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
+\end{gather*}
+for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
+Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
+% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
+The exterior product is bilinear and associative, and satisfies 
+\begin{align*}
+    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
+    \quad 
+    \forall u_1 \in \Alt^{k}(V),
+    \quad 
+    \forall u_2 \in \Alt^{l}(V).
+\end{align*}
+We use the interior product, which is in some sense dual to the exterior product, in a special case. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define $v \lrcorner u \in \Alt^{k-1}(V)$ via 
+\begin{align*}
+    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
+    \quad 
+    \forall v_1, v_2, \ldots, v_{k-1} \in V.
+\end{align*}
+
+We are interested only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
+Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
+Moreover, this particular setting comes with a canonical basis. 
+We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
+This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
+To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
+we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$,
+and introduce the basic $k$-alternators 
+\begin{align*}
+    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
+    \quad 
+    \forall \sigma \in \Sigma(k,n). 
+\end{align*}
+These define a basis of $\Alt^{k}(\bbR^{n})$.
+Note that 
+$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
+In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
+% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
+
+We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
+which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
+The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
+
+\subsection{Smooth differential forms}
+
+We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
+which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
+The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
+to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
+Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
+\begin{gather*}
+    \omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \omega_{\sigma} \, 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
+\end{gather*}
+where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
+The exterior derivative \( \cartan\omega \) is defined by
+\begin{gather*}
+    \cartan\omega = 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \sum_{j=1}^{n} 
+    \frac{\partial \omega_{\sigma}}{\partial x^j} 
+    \, \cartanx^j \wedge 
+    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
+\end{gather*}
+The exterior derivative is linear and nilpotent, which means 
+\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
+Moreover, it satisfies the Leibniz rule:
+\begin{gather*} 
+    \cartan(\omega \wedge \eta) 
+    = 
+    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
+    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
+    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
+\end{gather*}
+
+\subsection{Sobolev spaces of differential forms}
+
+Let us now turn our attention to Sobolev spaces of differential forms. 
+Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, we can consider the pointwise norms of differential $k$-forms. 
+We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
+such that its pointwise norm is $p$-integrable. 
+The exterior derivative is defined in the sense of distributions and we introduce 
+\begin{gather*}
+    W^{p}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
+    .
+\end{gather*}
+We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
+if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
+\begin{align*}
+    \int_{\Omega} \cartan v \wedge u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{\Omega} v \wedge f 
+    .
+\end{align*}
+% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
+% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
+% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
+Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
+Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
+We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
+such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+\begin{align*}
+    \int_{B_r(x)} \cartan v \wedge \tilde u
+    &=
+    (-1)^{k(n-k)+1}
+    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
+    .
+\end{align*}
+If that condition is satisfied, we also write 
+\begin{align*}
+    \trace_{\Gamma} u = 0
+    .
+\end{align*}
+Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
+Lastly, we introduce the closed subspaces 
+\begin{gather*}
+    W^{p}_{0}\Alt^{k}(\Omega) 
+    := 
+    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
+    .
+\end{gather*}
+% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
+\mwl{This is a closed subspace.
+We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
+Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}
+
+\subsection{Transformations by bi-Lipschitz mappings}
+
+We are interested in transformations of Sobolev tensor fields from one domain onto another. 
+Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
+The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
+\begin{align} \label{equation:pullback}
+    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
+    := 
+    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
+\end{align}
+for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
+We cite an explicit transformation estimate~\cite{licht2019smoothed}.
+
+\begin{proposition} \label{proposition:pullbackestimate}
+ Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
+ Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
+ Then 
+ \begin{align}\label{math:pullbackestimate}
+  \begin{split}
+  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
+  &\leq 
+  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
+  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
+  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
+  .
+  \end{split}
+ \end{align}
+\end{proposition}
+\notice{MWL:I have simplified the statement to what is needed later.}
+
+\begin{remark}
+    In three dimensions, 
+    the calculus of differential forms can be translated into classical vector calculus. 
+    This is expressed formally as the commuting diagram 
+    \begin{gather*}
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        @VV{\varpi^{3}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\, ,}
+    \end{gather*}
+    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
+    \begin{align*}
+     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
+     &= 
+     \left( u_1, u_2, u_3 \right), 
+     \\
+     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
+     &= 
+     \left( u_{23}, - u_{13}, u_{12} \right).   
+    \end{align*}
+    In two dimensions, 
+    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
+    To the authors' best knowledge, neither convention is dominant in the literature.
+    We summarize the situation in the following commuting diagram: 
+    \begin{gather*} 
+    \begin{CD}
+        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
+        \\
+        @AA{\varkappa^{0}}A 
+        @AA{\varkappa^{1}}A 
+        @AA{\varkappa^{2}}A 
+        \\
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\,.}
+    \end{gather*}
+    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
+We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
+    The other vertical arrows are the identity. 
+    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
+\end{remark}
+
+\subsection{Some approximation properties}
+
+We finally review a few approximation properties. 
+Let $\mollifier$ be a non-negative scalar function supported in the unit ball around the origin and with unit integral.
+Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
+
+\begin{lemma}
+%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
+%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
+%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
+\end{lemma}
+
+% \begin{lemma} % TODO: possibly useful
+%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
+% \end{lemma}
+
+\begin{lemma}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
+    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
+    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
+\end{lemma}
+\begin{proof}
+    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
+    By the dominated convergence theorem and because $u$ has a weak derivative,
+    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
+    \begin{align*}
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
+        &= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
+        \\&= 
+        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
+        \\&= 
+        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
+        = 
+        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
+        .
+    \end{align*}
+    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
+
+    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
+    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
+    Define $\varphi_t(x) = tx$ for $t > 1$. 
+    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
+    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
+    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
+    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
+    The desired result follows. 
+\end{proof}
+
+\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
+
+We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
+We already know the optimal constants for the gradient operator over convex domains,
+and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
+We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.
+
+\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
+For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
+We solve this for two special cases: 
+either the $L^{p}$ de~Rham complex without boundary conditions, 
+or the $L^{p}$ de~Rham with full boundary conditions. 
+either the $L^{p}$ de~Rham complex without boundary conditions, 
+or the $L^{p}$ de~Rham with full boundary conditions. 
+The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
+% 
+In comparison to their extensive work, our discussion is more modest:
+we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
+
+%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
+Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
+\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
+
+\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
+
+We begin with introducing the Costabel-McIntosh kernel.
+For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
+\begin{equation}\label{math:mainkernel}
+  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
+  ,
+\end{equation}
+where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
+Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
+we then define the integral operators
+\begin{align*}
+  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
+  \\
+  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
+\end{align*}
+We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.
+
+We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
+In order to analyze the properties of the potential operators,
+we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
+Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
+\begin{align*}
+    \calG_{\mia}(x,y) 
+    &= 
+    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
+    \\
+    &= 
+    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
+    \\
+    &= 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
+    .
+\end{align*}
+If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
+\begin{align*}
+    \calG_{\mia}(x,y) 
+    &= 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
+    \\
+    &= 
+    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
+\end{align*}
+We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
+
+We begin with the Poincar\'e operator. 
+Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
+Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
+We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+\begin{align*}
+    \left| \Poinc_{\mia} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+%     \\&\leq 
+%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
+    .
+\end{align*}
+We recall the radial integrals 
+\begin{align*}
+    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
+    &
+    =
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
+    \\&
+    =
+    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
+    =
+    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+    ,
+\end{align*}
+where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
+We compute 
+\begin{align}
+    &
+    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
+    \label{equation:A_Poinc}
+    .
+\end{align}
+Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
+and which is bounded by $2^{n-\mia}$. 
+In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
+    &
+    \leq 
+    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    \\&
+    \leq 
+    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
+Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\begin{gather*}
+    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
+\end{gather*}
+% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+%
+
+\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
+
+We analyze the Bogovski\u{\i} potential operator by similar means. 
+Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
+First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
+Consider now the case $x \in \overline\Omega$. 
+We estimate $\Bogov_{\mia} u(x)$ pointwise by 
+\begin{align*}
+    \left| \Bogov_{\mia} u(x) \right|
+    &=
+    \left| 
+        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
+    \right| 
+    \\&\leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
+    \\&\leq 
+    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
+    .
+\end{align*}
+Using once more the radial integrals discussed above, we compute 
+% We recall the radial integrals 
+% \begin{align*}
+%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
+%     =
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
+%     =
+%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
+%     =
+%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+%     .
+% \end{align*}
+% We compute 
+\begin{align*}
+    &
+    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
+    \\&
+    =
+    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
+    %\\&
+    =
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
+    \label{equation:A_Bogov}
+    .
+\end{align*}
+Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
+and which is bounded by $2^{\mia-1}$. 
+In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
+So the convolution of $u$ is taken against an integrable function. 
+Young's convolution inequality now implies: 
+\begin{align*}
+    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
+    &
+    \leq 
+    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    \\&
+    \leq 
+    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    \diam(\Omega)
+    \| u \|_{L^{p}(\Omega)}
+    .
+\end{align*}
+We have assumed so far that $u$ is essentially bounded.
+Since that space is dense in the Lebesgue spaces, a density argument yields: 
+for any $1 \leq p \leq \infty$ we have a bounded linear operator 
+\begin{gather*}
+    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
+\end{gather*}
+% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
+that is, the reconstructed potential has support contained within $\overline\Omega$. 
+\\
+
+\subsection{Additional properties}
+
+Additional properties of these operators become apparent after a change of variables. 
+We write down the full definition of these operators and perform two substitutions.
+For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
+leading to 
+\begin{align*}
+    \Poinc_{\mia} u(x) 
+    &= 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
+    \chi_{\Omega}\left(x+t(y-x)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
+    .
+\end{align*}
+For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+leading to 
+\begin{align*}
+    \Bogov_{\mia} u(x) 
+    &= 
+    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
+    \chi_{\Omega}\left(y+t(x-y)\right) 
+    (x-y)\lrcorner u(y) \,dt\,dy 
+    \\
+    &=
+    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
+    .
+\end{align*}
+% We first discuss the support properties of this operator. 
+% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
+% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
+% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
+% 
+Given $a \in \Omega$, we introduce the potential operators 
+\begin{align*}
+    \Poinc_{\mia,a} u(x) 
+    &:= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
+    ,
+    \\
+    \Bogov_{\mia,a} u(x) 
+    &:= 
+    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
+    .
+\end{align*}
+By definition,
+\begin{align*}
+    \Poinc_{\mia} u(x) 
+    =
+    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
+    \quad 
+    \Bogov_{\mia} u(x) 
+    =
+    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
+    .
+\end{align*}
+We study the interaction of these potential operator with the exterior derivative in more detail.
+% 
+That discussion is classical and establishes the exactness of several de~Rham complexes. 
+We recapitulate these arguments since our variants of the regularized potential operators 
+are not yet included in the published literature.
+
+Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
+We rewrite the Poincar\'e potential,
+\begin{align*}
+    \Poinc_{\mia,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Poinc_{\mia,a} u(x) 
+    &= 
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    ,
+\end{align*}
+and apply the Poincar\'e potential operator to this result, which gives 
+\begin{align*}
+    \Poinc_{\mia+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
+    \,\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Poinc_{\mia,a} u(x)
+    +
+    \Poinc_{\mia+1,a} \cartan u(x)
+    \\&
+    =
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{0}^{1} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{0}^{1} 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    u_{\sigma}(x) \,\cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+\mwl{What if $\mia = 0$ and $u$ is constant? The reconstruction is not complete for constants}
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x).
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
+
+The discussion for the Bogovski\u{\i} operator is almost analogous. 
+Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
+We rewrite the Bogovski\u{\i} potential,
+\begin{align*}
+    \Bogov_{\mia,a} u(x) 
+    &= 
+    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    \\&
+    = 
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    ,
+\end{align*}
+and compute its exterior derivative:
+\begin{align*}
+    \cartan \Bogov_{\mia,a} u(x) 
+    &= 
+    \mia 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    .
+\end{align*}
+We write the exterior derivative of $u$ as 
+\begin{align*}
+    \cartan u(x)
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    ,
+\end{align*}
+and apply the Bogovski\u{\i} potential operator to this result, which gives 
+\begin{align*}
+    \Bogov_{\mia+1,a} \cartan u(x)
+    &=
+    (x-a)\lrcorner 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,\cartanx^{j} \wedge \cartanx^{\sigma}
+    \\&
+    = 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad 
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    .
+\end{align*}
+We add the exterior derivative of the potential and the potential of the exterior derivative.
+Taking into account cancellations, this gives the identity 
+\begin{align*}
+    &
+    \cartan \Bogov_{\mia,a} u(x)
+    +
+    \Bogov_{\mia+1,a} \cartan u(x)
+    \\&
+    =
+    \mia
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    + 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{1}^\infty 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \\&\qquad
+    - 
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    (-1)^{i-1}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
+    \int_{1}^\infty 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \\&\qquad
+    +
+    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    \\&
+    =
+    \sum_{\sigma \in \Sigma(\mia,n)} 
+    u_{\sigma}(x) \cartanx^{\sigma}
+    =
+    u(x)
+    .
+\end{align*}
+In summary, after taking the average over $a \in \Omega$:
+\begin{align*}
+    u(x) = \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x)
+    .
+\end{align*}
+In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
+\\
+
+\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
+
+\mwl{We are in the position to establish the main results of this section.
+Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
+This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
+Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the dimension and the form degree enters the estimate.}
+
+We now state the main results of this section.
+\cye{Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
+though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\mia$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$}.
+
+\begin{theorem}\label{theorem:PF_EC}
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
+    We have bounded operators 
+    \begin{align*}
+        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
+        ,
+        \qquad 
+        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
+        .
+    \end{align*}
+    They satisfy the operator norm bounds 
+    \begin{align*}
+        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
+        \| u \|_{L^{p}(\Omega)}
+        ,
+        \\
+        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
+        &\leq 
+        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
+        \| u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
+    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
+\end{theorem}
+
+\todo[inline]{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
+Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
+
+\begin{proof}
+    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\mia}(\Omega)$.
+
+    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Poinc_{\mia  } u$. 
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+
+    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    We write $w := \Bogov_{\mia} u$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
+    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
+    it holds that 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
+        .
+    \end{align*}
+    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+    This completes the proof. 
+\end{proof}
+
+% DONE: Density of C infty mit oder ohne c.
+
+% \begin{remark}
+%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
+%     while they are increasing for the Bogovski\u{\i} operator.
+%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
+% \end{remark}
+
+\begin{remark} \label{remark:reg_Poinc_Bog}
+    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    These potentials enable the analysis of de~Rham complexes without boundary conditions.
+    % 
+    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
+    % 
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they can study domains star-shaped with respect to a ball. 
+    Instead, we average over the entire domain, which requires a convex geometry. 
+    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
+    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
+
+    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
+    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
+
+    {\color{blue}
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they \cye{can} study domains star-shaped with respect to a ball. 
+    The\cye{ir} operators are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
+    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
+\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
+    }
+\end{remark}
+
 \section{Reflections and Deformations on shellable stars}\label{section:extension}
@@
         \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_{z}$,
         and that it equals $-z_{S'}$ when $x = z_{S'}$.
@@
         We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
-        that satisfies the desired mapping properties. 
+        that satifies the desired mapping properties. 
         It remains to analyze its Jacobian to get explicit estimates.
@@
         %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
+        %         From this obversation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
         %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
@@
 %         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
+%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
         The combination of the previous estimates for $\Psi$ and $\Theta$,
@@
         A similar argument applies to the triangulation $\calR'$. 
-        We conclude that $\Xi$ is bi-Lipschitz. 
+        We conclude that $\Xi$ is bi-Lipchitz. 
         \color{black}
@@
         \leq 
-        C_{{\PF},k,\Omega,p}
+        C_{{\rm{PF}},k,\Omega,p}
         \| \cartan u \|_{L^{p}(\Omega)}
@@
     \begin{align*}
-        C_{{\PF},k,\Omega,p} 
+        C_{{\rm{PF}},k,\Omega,p} 
         = 
@@
 Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
-Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
+Moreover, so far, all the constants $C_{{\rm{PF}},T,p}$, $C_{{\rm{PF}},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\rm{PF}},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
 Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
@@
 \begin{align*}
-    U_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
+    \Minako_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
 \end{align*}
@@
             \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-            \| \cartan u \|_{L^{p}(U_{m-1})}
+            \| \cartan u \|_{L^{p}(\Minako_{m-1})}
         \right)
@@
         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
-    \mwl{The notation $U_m$ should be settled in the definition of shellings.}
+        \| w \|_{L^{p}(\Minako_{m-1})}
+        .
+    \end{align*}
+    \mwl{The notation $\Minako_m$ should be settled in the definition of shellings.}
 \end{theorem}
@@
     \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
     \end{gather*}
@@
     By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $U_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
 
     We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
+    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
     as in Proposition~\ref{proposition:starreflection}. 
@@
         \cdot 
-        \| w_{m-1} \|_{L^{p}(U_{m-1})}
+        \| w_{m-1} \|_{L^{p}(\Minako_{m-1})}
         ,
@@
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(U_{m})} 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m})} 
         \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k+1}
         \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
-        .
-    \end{align*}
-    \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        \| \cartan w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        .
+    \end{align*}
+    \begin{align*}
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(U_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|U_{m-1}})) \|_{L^{p}(T_{m})}
+        \| w \|_{L^{p}(\Minako_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(U_{m-1})}
+        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
         ,
@@
     It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
-    where $U_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
+    where $\Minako_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
 
@@
     \begin{align} \label{equation:w''_ext_der}
-        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{U_{m-1}}),
+        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\Minako_{m-1}}),
     \end{align}
-    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
+    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
     as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
@@
         \leq  
-        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
-        + 
-        \| u - \Xi_{m}^{\ast}(u_{|U_{m-1}}) \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|U_{m-1}})) = 0$, we have
-    \begin{align*}
-        \| u - \Xi_{m}^{\ast}(u_{|U_{m-1}}) \|_{L^{p}(T_{m})} 
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
+        + 
+        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) = 0$, we have
+    \begin{align*}
+        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})} 
         &
@@
         C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
-        + \| \cartan (\Xi_{m}^{\ast}(u_{|U_{m-1}})) \|_{L^{p}(T_{m})} )
+        + \| \cartan (\Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})} )
         .
@@
     \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
         &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(U_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|U_{m-1}})) \|_{L^{p}(T_{m})}
+        \| w \|_{L^{p}(\Minako_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
         &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(U_{m-1})}
-        ,
-    \end{align*}
+        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
+        ,
+    \end{align*}
+    \mwl{MV: Which norms of the Jacobians and their determinants?}
     where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
@@
     In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
-    and we let $U_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
-    which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
+    and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow \Minako_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
+    which acts as the identity along $\partial \Minako_{m-1} \setminus \partial T$.
     By assumption, 
@@
 \end{proof}
-\todo{MV: Why a second theorem?
+\todo[inline]{MV: Why a second theorem?
 Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
@@
 Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the sprit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
 % We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.

### 2024-10-02 draft.tex

@@
 \begin{document}
+
+The remainder of this manuscript is structured as follows.
+We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}.
+We review basic notions of triangulations in Section~\ref{section:triangulations}.
+We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
+We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
+Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
+We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
+We construct an important geometric reflection operator in Section~\ref{section:extension}
+and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
+We present numerical examples in Section~\ref{section:numericalexamples}.
 

### 2024-10-02 main.tex

--- 2024-10-02 main.tex
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},U_{F_m},p} 
-        \| \nabla u \|_{L^{p}(U_{F_m})} 
+        C_{{\PF},\Minako_{F_m},p} 
+        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
         . 
@@
     Suppose again that $1 \leq m \leq M$. 
-    Recall that we write $U_{F_m} := T_m \cup T_{m-1}$. 
-    We use the Poincar\'e--Friedrichs inequality over $U_{F_{m}}$,
+    Recall that we write $\Minako_{F_m} := T_m \cup T_{m-1}$. 
+    We use the Poincar\'e--Friedrichs inequality over $\Minako_{F_{m}}$,
     as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
-    to find $w_{F_m} \in W^{1,p}(U_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $U_{F_m}$ and 
+    to find $w_{F_m} \in W^{1,p}(\Minako_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Minako_{F_m}$ and 
     \begin{align}\label{math:wFm_inequality}
-        \| w_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\PF},U_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(U_{F_m})}.
+        \| w_{F_m} \|_{L^{p}(\Minako_{F_m})} \leq C_{{\PF},\Minako_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Minako_{F_m})}.
     \end{align}
-%     \cye{Since $\nabla (w_{|U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|U_{F_m}})$, 
+%     \cye{Since $\nabla (w_{|\Minako_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Minako_{F_m}})$, 
     We can define the constant
     \begin{align*}
-    c_{m} := w_{|U_{F_m}} - w_{F_{m}}.
+    c_{m} := w_{|\Minako_{F_m}} - w_{F_{m}}.
     \end{align*}
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},U_{F_\ell},p} 
+        C_{{\PF},\Minako_{F_\ell},p} 
         ,
@@
 The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ U_m \}$ with a face-connected path.
-The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ U_m \}$.
+Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ \Minako_m \}$ with a face-connected path.
+The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$.
 This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant.
@@
 We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
+whose support lies in the open ball $B_r(x)$
+we have the integration by parts formula
 \begin{align*}
@@
 % \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
-\mwl{This is a closed subspace.
+This is a closed subspace.
 We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}
+Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
+We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega)$.
 
@@
     If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$. 
+	\mwl{If $\Omega$ is convex and $u \in W^{p}\Lambda^{n}(\Omega)$ has average zero, 
+	then $u$ is the limit in $W^{p}\Lambda^{k}(\Omega)$ of smooth compactly supported $n$-forms with average zero.}
 \end{lemma}
@@
     The desired result follows.
+
+	Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently msall radius. The proof is complete. 
 \end{proof}
@@
 
-The discussion for the Bogovski\u{\i} operator is almost analogous. 
+The discussion for the Bogovski\u{\i} operator is analogous. 
 Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
@@
     + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     \int_{1}^\infty 
@@
     \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    =
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
+    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
     ,
@@
     \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \int_{1}^{\infty} 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
     \\&\qquad
     + 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \int_{1}^{\infty} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
     \\&\qquad
@@
     \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
     \\&\qquad
     - 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
     (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
     \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
@@
     \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
+    \int_{1}^{\infty} 
+    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
     \\&\qquad
@@
     \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    \\&\qquad
+    + 
+    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
+    \int_{1}^{\infty} 
+    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma} \,dt 
     \\&
@@
     \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    \\&
-    \mwl{=
+    \int_{1}^{\infty} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    =
+    -
 	\sum_{\sigma \in \Sigma(\mia,n)} 
@@
     =
-    u(x)
-    .}
+    -u(x)
+    .
 \end{align*}
 In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) = \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x)
-    .
+\begin{align*}\label{math:hodgedecomposition:bogov}
+    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n.
 \end{align*}
 In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
-\\
+We remark that the apparent structural difference between \eqref{math:hodgedecomposition:poinc} and \eqref{math:hodgedecomposition:bogov} is due to our assumption that $u$ extends to a smooth function with support within $\overline\Omega$.
+This structural difference will disappear soon when we discuss operators between Sobolev spaces of differential forms.
 
@@
 
-\mwl{We are in the position to establish the main results of this section.
+We are now state the main results of this section. 
+% We are in the position to establish the main results of this section.
 Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
-This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
-Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the dimension and the form degree enters the estimate.}
-
-We now state the main results of this section.
-\cye{Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
-though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\mia$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$}.
+The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
+However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
+namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$.
 
 \begin{theorem}\label{theorem:PF_EC}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
+    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
     We have bounded operators 
@@
     \end{align*}
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
+    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$ and $\cartan u = 0$, 
+    then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
+    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$ and $\int_\Omega u = 0$ in the case $k=n$, 
+    then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
 \end{theorem}
 
-\todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
+% \todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
 Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
@@
 \begin{proof}
-    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\mia}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
+    It suffices to discuss the case $1 \leq p < \infty$, because taking the limit will then imply the inequality with $p = \infty$. 
+    The potential operators are linear and satisfy the stated bounds over $C^{\infty}_{c}\Alt^{\mia}(\Omega)$,
+    which is a dense subspace of $L^{p}\Alt^{\mia}(\Omega)$.
+
+    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$ and $\cartan u = 0$. 
     We write $w := \Poinc_{\mia  } u$. 
@@
     \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|U_{m-1}}) \|_{L^{p}(T_{m})}
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
         &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(U_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|U_{m-1}})) \|_{L^{p}(T_{m})}
+        \| w \|_{L^{p}(\Minako_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
         &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(U_{m-1})} 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(U_{m-1})}
+        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
         ,

### 2024-10-03 main.tex
reflection, ongoing

@@
 
-Two different variations of underlying idea are analyzed. 
+Two different variations of underlying idea are analyzed; the resulting estimates are only slightly different.  
 On the one hand, we extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that simplex.
@@
     then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
+
+    \mwl{
+    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
+    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
+    }
 \end{theorem}
@@
 \begin{proof}
-    It suffices to discuss the case $1 \leq p < \infty$, because taking the limit will then imply the inequality with $p = \infty$. 
+    It suffices to discuss the case $1 \leq p < \infty$, because the domain is bounded 
+    and taking the limit will then imply the inequality with $p = \infty$. 
     The potential operators are linear and satisfy the stated bounds over $C^{\infty}_{c}\Alt^{\mia}(\Omega)$,
@@
     By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+
+    \color{blue}
+    Let $u \in W^{p}_{ }\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$ and set $w = \Poinc_{\mia} \cartan u$.
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
+    \begin{align*}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        =
+        \int_{\Omega} v \wedge \cartan \Poinc_{\mia+1} \cartan u_{i}
+        =
+        \int_{\Omega} v \wedge \cartan u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge \cartan u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge w
+        .
+    \end{align*}
+    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+    \color{black}
 
@@
     This completes the proof.
+
+    \color{blue}
+    Let $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$ and set $w = \Bogov_{\mia} \cartan u$.
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, we verify 
+    \begin{align*}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        =
+        \int_{\Omega} v \wedge \cartan \Bogov_{\mia+1} \cartan u_{i}
+        =
+        \int_{\Omega} v \wedge \cartan u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge \cartan u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge w
+        .
+    \end{align*}
+    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
+    \color{black}
 \end{proof}
@@
     These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % 
+    % TODO: are these paragraphs in the introduction now?
     The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
@@
     {\color{blue}
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they \cye{can} study domains star-shaped with respect to a ball. 
-    The\cye{ir} operators are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight\cye{; this} proves boundedness of the operators between a variety of function spaces. 
+    Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
+    which is why they can study domains star-shaped with respect to a ball. 
+    Their operators are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight; this proves boundedness of the operators between a variety of function spaces. 
     Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been \cye{recently} contributed by Guzman and Salgado~\cite{guzman2021estimation}.\todo{MV: moved.}
-    Instead, we average over the entire domain, which requires a convex geometry, \cye{and we are only interested in boundedness in the Lebesgue $p$ norms.} This has not been established yet, to the best of our knowledge.
-\cye{Crucially, this exactly allows us to} establish \cye{computable bounds on the} Poincar\'e--Friedrichs constants.
+    have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
+    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
+    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
+    This had not been established yet, to the best of our knowledge. 
     }
@@
 Consider the situation where we have an $n$-dimensional local patch (star) around some simplex $S$ and some $n$-dimensional simplex $T$ within that local star. 
-We will need a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$,
+We construct a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$,
 similar to the two- and three-color maps in \cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}
-This homeomorphism is required to preserve the interface and we interpret it as a nonlinear reflection. 
-We ensure that the homeomorphism is bi-Lipschitz and we are particularly interested in the norms of its Jacobian.
+This homeomorphism, which we interpret as a nonlinear reflection, is required to preserve the interface. 
+We ensure that the homeomorphism is bi-Lipschitz, and we are particularly interested in the norms of its Jacobian.
 This nonlinear reflection will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms. 
@@
     Let $F, F'$ be the two subsimplices of $T$ with respective vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
-    Then $T$ lies on one side of the affine subspace
+    Then
     \begin{gather*}
@@
     \end{gather*}
-    Moreover, $F = T \cap A$.
+	is an affine subspace of dimension $n-1$, the simplex $T$ lies on one side of $A$,
+	and $F = T \cap A$.
 \end{lemma}
 \begin{proof}
-    Evidently, the linear spans 
+    Obviously, $F \subset A \cap T$. 
+    Suppose now that $x \in A \cap T$.
+    There exist $\lambda_1,\dots,\lambda_{n-1} \in \bbR$ such that 
+    \begin{align*}
+        x &= 
+        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
+        \\&
+        = 
+        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
+        + 
+        \sum_{i=1  }^{k  } \lambda_{i} v_i 
+        + 
+        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
+        + 
+        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
+        .
+    \end{align*}
+    This is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
+    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive and their sum is non-negative.
+    Hence $\lambda_{k+1} = \dots = \lambda_{n-1} = 0$, implying $x \in F$.
+    % 
+    Lastly, the linear spans 
     \begin{gather*}
@@
     \end{gather*}
-    intersect only at the origin, since otherwise the vertices of $T$ are not affinely independent. 
+    intersect only at the origin, since otherwise a non-trivial affine combination of the vertices of $T$ equals zero, 
+	contradicting their affine independence. %the vertices of $T$ are not affinely independent. 
     So $A$ has dimension $n-1$. 
-    Obviously, $F \subset A \cap T$. 
-    Suppose now that $x \in A \cap T$.
-    There exist $\lambda_1,\dots,\lambda_{n-1} \in \bbR$ such that 
-    \begin{align*}
-        x &= 
-        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
-        \\&
-        = 
-        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
-        + 
-        \sum_{i=1  }^{k  } \lambda_{i} v_i 
-        + 
-        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
-        + 
-        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
-        .
-    \end{align*}
-    This is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
-    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive.
-    But if $x \notin F$, then at least one of them must be negative,
-    and thus their sum must be negative, which is a contradiction. 
-    Hence $\lambda_{k+1} = \dots = \lambda_{n-1} = 0$, implying $x \in F$.
 \end{proof}
@@
 
-Next, we observe local stars can be subdivided to vertex stars.
-The shape regularity is controlled in that process.
+We state the simple observation that local stars can be subdivided to vertex stars.
+The shape regularity remains controlled in that process.
 
@@
 
-\mwl{TODO: Illustration}
+\mwl{TODO: Illustration. Extend to the more general case if needed later.}
 
@@
     \end{align*}
+	The following holds, where the constants on the right-hand sides are as stated in the proof. 
     \begin{enumerate}
@@
     \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap U$ and which satisfies the upper bounds 
+    which is the identity along ${\Gamma_1} = T \cap U$. 
+    Its singular values $\sigma_1 \geq \dots \geq \sigma_n$ satisfy 
+    \begin{align*}
+        \sigma_1 &\leq ...
+        \\
+        \sigma_i &\leq ..., \quad 2 \leq i \leq n-1,
+        \\
+        \sigma_n &\leq ...
+    \end{align*}
+    and which satisfies the upper bounds 
     \begin{gather*}
@@
         \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT),
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
     \end{gather*}
-    where the constants on the right-hand sides are as stated in the proof. 
     \item 
@@
     \begin{align*}
-        \Xi_{2} : \underlying{\star_{\calT}(S)} \rightarrow U
-    \end{align*}
-    which is the identity along $\partial U \setminus \partial T$ and which satisfies the upper bounds 
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U
+    \end{align*}
+    which is the identity along $\partial U \setminus \partial T$.
+    Its singular values $\sigma_1 \geq \dots \geq \sigma_n$ satisfy 
+    \begin{align*}
+        \sigma_1 &\leq ...
+        \\
+        \sigma_i &\leq ..., \quad 2 \leq i \leq n-1,
+        \\
+        \sigma_n &\leq ...
+    \end{align*}
+    and which satisfies the upper bounds 
     \begin{gather*}
@@
         \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT),
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
     \end{gather*}
-    where the constants on the right-hand sides are as stated in the proof. 
     \end{enumerate}
@@
             \\
-            \matnorm{ Jacobian \Xi_{2}^{-1} }
+            \matnorm{ \Jacobian \Xi_{2}^{-1} }
             &\leq  
@@
         This completes the desired estimates for $\Xi_{2}$. 
+    \end{itemize}
+    The proof is complete. 
+\end{proof}
+
+\begin{remark}
+    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
+    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
+    While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
+    it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
+\end{remark}
 
@@
 \end{comment}
-    \end{itemize}
-    The proof is complete. 
-\end{proof}
-
-\begin{remark}
-    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
-    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
-    While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
-    it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
-\end{remark}
 

### 2024-10-03 main.tex
reflection, ongoing

@@
 \usepackage{fullpage}
-% \usepackage[margin=0.1cm]{geometry}
+\usepackage[margin=0.1cm]{geometry}
 \input{header}
@@
         We let $z'_{S}$ be the midpoint of $S'$. 
-        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary simplex $S'$. 
-        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
+        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
+        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
 
         We define another simplicial complex $\calS^c$ as follows:
-        whenever $K \in \calS$ is an $n$-simplex, 
-        we replace the vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
-        giving us a simplex $K'$.
-
-        We let $\calS'$ be the union of $\calS$ and $\calS^c$. 
-        By construction, all these $n$-simplices contain $S$ as a subsimplex,
-        and they are disjoint except for their proper subsimplices. 
-        Hence $\calS'$ is indeed a triangulation. 
+        given any $n$-simplex $K \in \calS$, 
+        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
+        thus obtaining a new simplex $K'$. 
+        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.
+
+        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
+        By construction, all its $n$-simplices contain $S$ as a subsimplex,
+        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
         Moreover, $S$ is an inner subsimplex of that triangulation. 
@@
 
+        \mwl{Check that $\calS'$ is a triangulation...}
+
         \item 
-        In what follows, we also use $\calR'$, 
-        the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
-        Then $\calR'$ is the local star around the barycenter $z_S$,
-        and all $n$-simplices in $\calR'$ contain $z_{S}$. 
-        We let $\calR$ and $\calR^{c}$ be the corresponding refinements of $\calS$ and $\calS^{c}$, respectively.
-
-        The last simplicial complex that we introduce is called $\calK$,
-        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
+        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
+        Then $\calR'$ is its own local star around the barycenter $z_S$.
+        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
+        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
+        which we denote by $\calR$ and $\calR^{c}$, respectively.
+
+        Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
 
         \item 
-        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ as follows.
+        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ between the underlying sets as follows.
         Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
@@
         that agree on the vertices common to $K$ and $K'$.
-        We then define 
+        Then the mapping 
         \begin{align*}
@@
         % \end{align*}
-        By construction, the mapping preserves volumes:
+        preserves volumes:
         \begin{align*}
@@
         \end{align*}
+		Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
 		Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
@@
         \end{align*}
-        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
-        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
+        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
+        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
         whereas all its other singular values equal $1$.
@@
 %         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        By the definition of the tangent, $\tan(\beta) \leq \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$, and we know $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$. 
-        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
-        which is also a face of $T$. Then $(n-k) h_{z}$ is the height vector of $F_{z}$ in $T$. 
+        We develop explicit bounds for these singular values. 
+        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
+        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
+        % Obviously, $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$.
+
+        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
+        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
+        which must be contained in a face $F$ of $T$. 
+        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of $F$ in $T$. 
         Thus 
@@
             \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
             \leq 
@@
         This establishes bounds on the singular values of the transformation. 
-        We write 
+        We abbreviate 
         \begin{align*}

### 2024-10-03 main.tex
progress on reflection mapping

@@
         Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
-        which must be contained in a face $F$ of $T$. 
-        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of $F$ in $T$. 
+        which must be contained in some face of $T$. 
+        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
         Thus 
@@
         We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
-        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Phi$.
+        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
         We construct a bi-Lipschitz mapping 
         \begin{align*}
-            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}
-        \end{align*}
-        and analyze its properties. The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
-        will define the required mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
-        which will be bi-Lipschitz and the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
-
-        We write $h_{z}$ for the height of $z_{S'}$ within $K$.
-        Given $x \in K \cup K^{c}$, we have a unique representation
-        \begin{align*}
-            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c}.
-        \end{align*}
-        Notice that 
-        \begin{align*}
-            t = \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
+        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
+        Any $x \in K \cup K^{c}$ has a unique representation
+        \begin{align*}
+            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c},
+        \end{align*}
+        where we have 
+        \begin{align*}
+            t = t(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
             .
@@
         \begin{align*}
-            \Phi_{K}(x) := x - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
+            \Phi_{K}(x) 
+			:= 
+			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
+            = 
+			x^{\perp} - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
+            .
+        \end{align*}
+        We can write 
+        \begin{align*}
+            \Phi_{K}(x) 
+			:= 
+			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
+            = 
+			x^{\perp} + t(x) z_{S'} - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
+            = 
+			x - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
+            = 
+			x - t(x) z_{S'} - \frac 1 2 \left( 3 t(x) - 1 \right) z_{S'}
             .

### 2024-10-03 main.tex
rewriting reflection

@@
 %         \end{align*}
-        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$, then 
+        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
         \begin{align*}
@@
         Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
-        Any $x \in K \cup K^{c}$ has a unique representation
-        \begin{align*}
-            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c},
-        \end{align*}
-        where we have 
-        \begin{align*}
-            t = t(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
+        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
+        has a unique representation
+        \begin{align*}
+            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
+        \end{align*}
+        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+        \begin{align*}
+            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
             .
@@
             \Phi_{K}(x) 
+			&
 			:= 
-			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
-            = 
-			x^{\perp} - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
-            .
-        \end{align*}
-        We can write 
-        \begin{align*}
-            \Phi_{K}(x) 
-			:= 
-			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
-            = 
-			x^{\perp} + t(x) z_{S'} - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
-            = 
-			x - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
-            = 
-			x - t(x) z_{S'} - \frac 1 2 \left( 3 t(x) - 1 \right) z_{S'}
+            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
+            \\&
+            = 
+            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
+            = 
+            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
             .
@@
 
-        We have an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$.
+        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
         With that,
@@
             - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
+            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle }  
             z_{S'} \otimes h_{z}^{t}
@@
             - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
             h_{z} \otimes h_{z}^{t}
             - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
             b_{z} \otimes h_{z}^{t}
@@
             - 
-            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
+            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
             h_{z} \otimes h_{z}^{t}
             - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
             b_{z} \otimes h_{z}^{t}
@@
             - 
-            \frac{1}{ 2 } 
+            \frac{3}{ 2 } 
             \hat h_{z} \otimes \hat h_{z}^{t}
             - 
-            \frac{ \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
+            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
             \hat b_{z} \otimes \hat h_{z}^{t}
@@
         \end{align*}
+        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.
 		We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
@@
             C 
+            = 
+            \begin{pmatrix}
+                -\frac 1 2             & 0 
+                \\
+                -\frac 3 2 \tan(\beta) & 2 
+            \end{pmatrix}
 			= 
@@
                 \\
-                -\tan(\beta) & 2 
+                -3\tan(\beta) & 2 
             \end{pmatrix}
@@
         \end{align*}
-        These are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. 
-%         Upon close inspection, we see that 
-%         \begin{align*}
-%             \sigma_{\max} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-%             ,
-%             \\
-%             \sigma_{\min} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-%             .
-%         \end{align*}
-        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
-        Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
+        \begin{align*}
+            \sigma_{\max} 
+            = 
+            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
+            %=
+            %\frac 1 4 \sqrt{ 9 + 9\tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            =
+            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            ,
+            \\
+            \sigma_{\min} 
+            = 
+            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
+            =
+            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            .
+        \end{align*}
+        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
+        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
+        \begin{align*}
+            \det \Jacobian\Phi = \frac 1 2.
+        \end{align*}
         We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
@@
             \leq 
-            \frac 1 4 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
+            \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
             ,
@@
             \leq 
-            \frac 1 2 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
-            ,
-            \\
-            \det \Jacobian\Phi = \frac 1 2 
+            \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
             .
@@
         \item 
-        We prove another auxiliary result.
+        We continue with an auxiliary result.
         Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
@@
         This is defined away from the hyperplane orthogonal to $h_2$.
-        This is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
+        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
+        That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
         onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed,
-        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
 
         We identify the Lipschitz properties of this mapping by computing its Jacobian. 
-        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $h_2$, respectively, and the vector $x$.
+        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $x$ and between $h_2$ and $x$, respectively. 
         In what follows, $y \in \bbR^{n}$.
@@
             &=
+            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
+            x
+            - 
+            \frac{ \langle h_2, h_2 \rangle \langle h_2, y \rangle }{ \langle h_2, x \rangle^{2} }
+            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
+            x 
+            +
+            \frac{ \langle h_2, h_2 \rangle }{ \langle h_2, x \rangle }
+            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
+            y 
+            \\&=
             \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
@@
             +
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
             \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
@@
         We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
-        Notice that $a \perp \hat x$ by definition.
+        Notice that $a \perp \hat x$.
 The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
@@
         Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
-        We notice the obvious upper bound 
+        We thus consider the upper bound 
         \begin{align*}
@@
         \item 
+		\mwl{Continue proof reading here.}
         We introduce a bi-Lipschitz mapping 

### 2024-10-03 main.tex
reflection mapping...

@@
         \item 
-		\mwl{Continue proof reading here.}
-        We introduce a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|
-        \end{align*}
-        in the following manner.
+        We now describe the construction of a bi-Lipschitz mapping 
+        \begin{align*}
+            \Psi : |\calR'| \rightarrow |\calK|.
+        \end{align*}
+		Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,
+		so they must contain an open ball around the origin. 
+		\mwl{Here we need a particular result. }
 		Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
@@
 They define respective hyperplanes $H_{G}$ and $H_{K}$,
-        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
-        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
+        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$ for the corresponding faces. 
+        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$,
+        that is, the scalar product of $x$ with either height vector is positive. 
         We define 
@@
         \end{align*}
-        Our previous observations enable estimates for the Jacobians. 
-        We have the operator norm and determinant formulas 
+        We let $\alpha_K$ and $\alpha_{{G}}$ be the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
+        and let 
+        \begin{align*}
+            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
+            .
+        \end{align*}
+        The preceding auxiliary results now contribute all information on the singular values of these Jacobians:
         \begin{gather*}
@@
         \end{gather*}
-        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
-        and where 
-        \begin{align*}
-            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
-            .
-        \end{align*}
         We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
@@
 
-        The diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
+		\mwl{Continue proof reading here.}
+		We need further details to complete our estimates. 
+		We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
 The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
-        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of the origin in some simplex in $\calS'$
-        by scaling with $(k+1)^{-1}$.
-Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
+		That estimates the quotient $\| x_K \| / \| h_K \|$. 
+        % 
+        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
+        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
+        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
+        It follows again that $\|x_{G}\| \leq \diam(T)$. 
+        % 
+        It remains to find a lower bound for $\| h_{G} \|$.
+        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
+        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
+        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
 The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows that $\|x_{G}\| \leq \diam(T)$.
-
-        We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
-        \begin{align*}
-            \frac{\diam(T)}{ \|h_{F}\|}
-            \leq  
-            \aspectratio(T)
-            % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            .
-        \end{align*}
-        We conclude that 
-        \begin{gather*}
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
-            \leq 
+        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
+        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
+        %         
+%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
+%         \begin{align*}
+%             \frac{\diam(T)}{ \|h_{F}\|}
+%             \leq  
+%             \aspectratio(T)
+%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%             .
+%         \end{align*}
+        Putting all these technical observations together, we estimate 
+        \begin{align*}
+            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
+            &\leq 
             (k+1)B_{T}
@@
             \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
+            &\leq 
             (k+1)
@@
             .
-        \end{gather*}
+        \end{align*}
         \begin{gather*}
-            \frac{ \diam(K) }{ \| h_{{K}} \| }
+            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
             \leq 
@@
             \frac{\|x_{K}\|}{\|h_{K}\|} 
-            \\&
+            % \\&
             \leq 
@@
         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \mwl{TODO: not enough. Make this more explicit.}
+        \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
 
@@
         It preserves the interface from $T$ onto $U$. 
+		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
         % We briefly recapitulate why it is bi-Lipschitz.
@@
         It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
+		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
         The combination of the previous estimates for $\Psi$ and $\Phi$ now lead to 

### 2024-10-03 main.tex
reflection almost done

@@
 %         \end{align*}
-
-		\mwl{Continue proof reading here.}
 		We need further details to complete our estimates. 
@@
         \item 
+		\mwl{Continue proof reading here.}
         We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 

### 2024-10-04 draft.tex
some annotations in last section

@@
 We present numerical examples in Section~\ref{section:numericalexamples}.
+
+\begin{itemize}
+        \item 
+        We introduce a bi-Lipschitz mapping 
+        \begin{align*}
+            \Psi : |\calR'| \rightarrow |\calK|
+        \end{align*}
+        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
+        We define 
+        \begin{align*}
+            \Psi(x) 
+            = 
+            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
+            .
+        \end{align*}
+        One easily verifies that this defines a continuous mapping $\Psi$. 
+        By the same line of thought, we see that it is invertible with inverse 
+        \begin{align*}
+            \Psi^{-1}(x) 
+            = 
+            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x
+            .
+        \end{align*}
+        We analyze its Jacobian. 
+        First, by assumption,
+        \begin{align*}
+            \Psi(x) 
+            = 
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
+            .
+        \end{align*}
+        In what follows, $y \in \bbR^n$. We observe 
+        \begin{align*}
+            \Jacobian \Psi(x) \cdot y 
+            &= 
+            \frac{ 
+                ( A_{{G}}^{-t} \vecone \cdot y ) 
+                ( A_{K}^{-t} \vecone \cdot x )
+                -
+                ( A_{{G}}^{-t} \vecone \cdot x )
+                ( A_{K}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot x )^2
+            } 
+            x
+            + 
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
+            \\&= 
+            \frac{ 
+                ( A_{{G}}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot  x )
+            } 
+            x
+            -
+            \frac{ 
+                ( A_{{G}}^{-t} \vecone \cdot x )
+                ( A_{K}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot  x )^2
+            } 
+            x
+            + 
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
+            \\&= 
+            \frac{ 
+                ( A_{{G}}^{-t} \vecone \cdot y ) 
+            }{ 
+                ( A_{K}^{-t} \vecone \cdot  x )
+            } 
+            x
+            +
+            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
+            \left( 
+                y
+                -
+                \frac{ 
+                    ( A_{K}^{-t} \vecone \cdot y ) 
+                }{ 
+                    ( A_{K}^{-t} \vecone \cdot  x ) 
+                } 
+                x
+            \right)
+            .
+        \end{align*}
+        We see that the last summand is an oblique projection of $y$. 
+        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes.
+We conclude that
+        \[
+             A_{K}^{-t} \vecone \cdot x 
+             = 
+             \vecone \cdot A_{K}^{-1} x 
+             \geq 
+             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
+        \]
+        Together with the Xu-Zikatanov inequality, we obtain the upper bound 
+        \begin{align*}
+            \matnorm{ \Jacobian \Psi(x) }
+            &\leq 
+            \sqrt{n}
+            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
+            \left( 
+            1
+            + 
+            n
+            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
+            \right) 
+            .
+        \end{align*}
+        By completely analogous arguments, we find 
+        \begin{align*}
+            \matnorm{ \Jacobian \Psi^{-1}(x) }
+            &\leq 
+            \sqrt{n}
+            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-1} ) }
+            \left( 
+            1
+            + 
+            n
+            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-2} ) }
+            \right) 
+            .
+        \end{align*}
+        It follows that 
+        \begin{align*}
+            \Xi := \Psi \circ \Theta
+        \end{align*}
+        is a mapping from ${G}$ onto $U = \overline{\patch_{\calT}(S) \setminus {G}}$.
+        It preserves the interface from ${G}$ onto $U$.
+
+        \item 
+        \color{red}
+        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
+        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+        After application of a piecewise linear Lipschitz mapping, 
+        we can assume that $|\calK|$ is convex without loss of generality. 
+        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.
+
+        A similar argument applies to the triangulation $\calR'$. 
+        We conclude that $\Xi$ is bi-Lipschitz. 
+        \color{black}
+
+        \item 
+        \color{red}
+        We collect several geometric facts.
+
+        \item 
+        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
+        Each bisection step reduces the diameter by at most a factor of one half,
+        and it reduces the volume always by a factor of one half. 
+        We use the estimates in Lemma~\ref{lemma:measurerelationships}.
+        When $K \in \calK \cup \calS'r$, then 
+        \begin{align*}
+             \sigma_{\max}( A_{K}^{-1} )
+             &\leq 
+             \Czwei{n} \geometricshapemeasure(K) \diam(K)
+             \leq 
+             2 \Czwei{n} \geometricshapemeasure(\calT) \diam(K)^{-1}
+             \\
+             \sigma_{\min}( A_{K}^{-1} )^{-1}
+             &= 
+             \sigma_{\max}( A_{K} ) 
+             \leq 
+             \Ceins{n} \diam(K),
+             \\ 
+             \geometricshapemeasure( A_{K} )
+             &\leq 
+             \Cdrei{n} \geometricshapemeasure(K) \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+             .
+        \end{align*}
+        When ${G} \in \calR'$ is not our original simplex, then 
+        \begin{align*}
+             \sigma_{\max}( A_{{G}}^{-1} )
+             &\leq 
+             \Czwei{n} \geometricshapemeasure({G}) \diam({G})
+             \leq 
+             4 \Czwei{n} \geometricshapemeasure(\calT) \diam(G)^{-1},
+             \\
+             \sigma_{\min}( A_{{G}}^{-1} )^{-1}
+             &= 
+             \sigma_{\max}( A_{{G}} ) 
+             \leq 
+             \Ceins{n} \diam({G}),
+             \\ 
+             \geometricshapemeasure( A_{{G}} )
+             &\leq 
+             \Cdrei{n} \geometricshapemeasure({G}) \leq 4 \Cdrei{n} \geometricshapemeasure(\calT)
+             .
+        \end{align*}
+        All the diameters above are comparable up to a factor of $\diameterratio(\calT)$.
+        In summary,
+        \begin{gather*}
+            \matnorm{ \Jacobian \Theta_{|K}      } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+            ,
+            \qquad 
+            \matnorm{ \Jacobian \Theta_{|K}^{-1} } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
+            ,
+            \\
+            \matnorm{ \Jacobian \Xi(x) }
+            \leq 
+            \sqrt{n}
+            4 
+            \geometricshapemeasure(\calT) 
+            \Ceins{n} 
+            \Czwei{n} 
+            \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
+            \left( 
+                1
+                + 
+                n
+                2 \Cdrei{n} \geometricshapemeasure(\calT)
+                4 
+                \geometricshapemeasure(\calT) 
+                \Ceins{n} 
+                \Czwei{n} 
+                \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
+            \right) 
+            2 \Cdrei{n} \geometricshapemeasure(\calT)
+            ,
+            \\
+            \matnorm{ \Jacobian \Xi^{-1}(x) }
+            \leq 
+            \sqrt{n}
+            2 
+            \geometricshapemeasure(\calT) 
+            \Ceins{n} 
+            \Czwei{n} 
+            \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
+            \left( 
+                1
+                + 
+                n
+                2 \Cdrei{n} \geometricshapemeasure(\calT)
+                2 
+                \geometricshapemeasure(\calT) 
+                \Ceins{n} 
+                \Czwei{n} 
+                \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
+            \right) 
+            2 \Cdrei{n} \geometricshapemeasure(\calT)
+            .
+        \end{gather*}
+\end{itemize}
 

### 2024-10-04 main.tex
some annotations in last section

@@
 % \end{remark}
+
+These constants are generally not optimal. 
+For example, when $p=2$ and when only the divergence is considered, 
+we have the following improved estimate.
+
+\begin{lemma}\label{lemma:PFfordivergence}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
+    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
+    \begin{align*}
+        \| \bfw \|_{L^{2}(\Omega)} 
+        \leq 
+        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    This is a reduction to the Friedrichs inequality. 
+    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
+    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
+    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
+    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
+    which has the same smallest singular value. 
+\end{proof}
 
@@
         \item 
-		\mwl{Continue proof reading here.}
+		\mwl{Use interlacing inequalities.}
         We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
@@
 
-\begin{comment}
-        \item 
-        We introduce a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|
-        \end{align*}
-        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-        We define 
-        \begin{align*}
-            \Psi(x) 
-            = 
-            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
-            .
-        \end{align*}
-        One easily verifies that this defines a continuous mapping $\Psi$. 
-        By the same line of thought, we see that it is invertible with inverse 
-        \begin{align*}
-            \Psi^{-1}(x) 
-            = 
-            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x
-            .
-        \end{align*}
-        We analyze its Jacobian. 
-        First, by assumption,
-        \begin{align*}
-            \Psi(x) 
-            = 
-            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
-            .
-        \end{align*}
-        In what follows, $y \in \bbR^n$. We observe 
-        \begin{align*}
-            \Jacobian \Psi(x) \cdot y 
-            &= 
-            \frac{ 
-                ( A_{{G}}^{-t} \vecone \cdot y ) 
-                ( A_{K}^{-t} \vecone \cdot x )
-                -
-                ( A_{{G}}^{-t} \vecone \cdot x )
-                ( A_{K}^{-t} \vecone \cdot y ) 
-            }{ 
-                ( A_{K}^{-t} \vecone \cdot x )^2
-            } 
-            x
-            + 
-            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
-            \\&= 
-            \frac{ 
-                ( A_{{G}}^{-t} \vecone \cdot y ) 
-            }{ 
-                ( A_{K}^{-t} \vecone \cdot  x )
-            } 
-            x
-            -
-            \frac{ 
-                ( A_{{G}}^{-t} \vecone \cdot x )
-                ( A_{K}^{-t} \vecone \cdot y ) 
-            }{ 
-                ( A_{K}^{-t} \vecone \cdot  x )^2
-            } 
-            x
-            + 
-            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
-            \\&= 
-            \frac{ 
-                ( A_{{G}}^{-t} \vecone \cdot y ) 
-            }{ 
-                ( A_{K}^{-t} \vecone \cdot  x )
-            } 
-            x
-            +
-            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
-            \left( 
-                y
-                -
-                \frac{ 
-                    ( A_{K}^{-t} \vecone \cdot y ) 
-                }{ 
-                    ( A_{K}^{-t} \vecone \cdot  x ) 
-                } 
-                x
-            \right)
-            .
-        \end{align*}
-        We see that the last summand is an oblique projection of $y$. 
-        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes.
-We conclude that
-        \[
-             A_{K}^{-t} \vecone \cdot x 
-             = 
-             \vecone \cdot A_{K}^{-1} x 
-             \geq 
-             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
-        \]
-        Together with the Xu-Zikatanov inequality, we obtain the upper bound 
-        \begin{align*}
-            \matnorm{ \Jacobian \Psi(x) }
-            &\leq 
-            \sqrt{n}
-            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
-            \left( 
-            1
-            + 
-            n
-            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
-            \right) 
-            .
-        \end{align*}
-        By completely analogous arguments, we find 
-        \begin{align*}
-            \matnorm{ \Jacobian \Psi^{-1}(x) }
-            &\leq 
-            \sqrt{n}
-            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-1} ) }
-            \left( 
-            1
-            + 
-            n
-            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-2} ) }
-            \right) 
-            .
-        \end{align*}
-        It follows that 
-        \begin{align*}
-            \Xi := \Psi \circ \Theta
-        \end{align*}
-        is a mapping from ${G}$ onto $U = \overline{\patch_{\calT}(S) \setminus {G}}$.
-        It preserves the interface from ${G}$ onto $U$.
-
-        \item 
-        \color{red}
-        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-        After application of a piecewise linear Lipschitz mapping, 
-        we can assume that $|\calK|$ is convex without loss of generality. 
-        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.
-
-        A similar argument applies to the triangulation $\calR'$. 
-        We conclude that $\Xi$ is bi-Lipschitz. 
-        \color{black}
-
-        \item 
-        \color{red}
-        We collect several geometric facts.
-
-        \item 
-        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
-        Each bisection step reduces the diameter by at most a factor of one half,
-        and it reduces the volume always by a factor of one half. 
-        We use the estimates in Lemma~\ref{lemma:measurerelationships}.
-        When $K \in \calK \cup \calS'r$, then 
-        \begin{align*}
-             \sigma_{\max}( A_{K}^{-1} )
-             &\leq 
-             \Czwei{n} \geometricshapemeasure(K) \diam(K)
-             \leq 
-             2 \Czwei{n} \geometricshapemeasure(\calT) \diam(K)^{-1}
-             \\
-             \sigma_{\min}( A_{K}^{-1} )^{-1}
-             &= 
-             \sigma_{\max}( A_{K} ) 
-             \leq 
-             \Ceins{n} \diam(K),
-             \\ 
-             \geometricshapemeasure( A_{K} )
-             &\leq 
-             \Cdrei{n} \geometricshapemeasure(K) \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
-             .
-        \end{align*}
-        When ${G} \in \calR'$ is not our original simplex, then 
-        \begin{align*}
-             \sigma_{\max}( A_{{G}}^{-1} )
-             &\leq 
-             \Czwei{n} \geometricshapemeasure({G}) \diam({G})
-             \leq 
-             4 \Czwei{n} \geometricshapemeasure(\calT) \diam(G)^{-1},
-             \\
-             \sigma_{\min}( A_{{G}}^{-1} )^{-1}
-             &= 
-             \sigma_{\max}( A_{{G}} ) 
-             \leq 
-             \Ceins{n} \diam({G}),
-             \\ 
-             \geometricshapemeasure( A_{{G}} )
-             &\leq 
-             \Cdrei{n} \geometricshapemeasure({G}) \leq 4 \Cdrei{n} \geometricshapemeasure(\calT)
-             .
-        \end{align*}
-        All the diameters above are comparable up to a factor of $\diameterratio(\calT)$.
-        In summary,
-        \begin{gather*}
-            \matnorm{ \Jacobian \Theta_{|K}      } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
-            ,
-            \qquad 
-            \matnorm{ \Jacobian \Theta_{|K}^{-1} } \leq 2 \Cdrei{n} \geometricshapemeasure(\calT)
-            ,
-            \\
-            \matnorm{ \Jacobian \Xi(x) }
-            \leq 
-            \sqrt{n}
-            4 
-            \geometricshapemeasure(\calT) 
-            \Ceins{n} 
-            \Czwei{n} 
-            \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
-            \left( 
-                1
-                + 
-                n
-                2 \Cdrei{n} \geometricshapemeasure(\calT)
-                4 
-                \geometricshapemeasure(\calT) 
-                \Ceins{n} 
-                \Czwei{n} 
-                \diameterratio(\calT) % \frac{ \diam(K) }{ \diam(G) }
-            \right) 
-            2 \Cdrei{n} \geometricshapemeasure(\calT)
-            ,
-            \\
-            \matnorm{ \Jacobian \Xi^{-1}(x) }
-            \leq 
-            \sqrt{n}
-            2 
-            \geometricshapemeasure(\calT) 
-            \Ceins{n} 
-            \Czwei{n} 
-            \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
-            \left( 
-                1
-                + 
-                n
-                2 \Cdrei{n} \geometricshapemeasure(\calT)
-                2 
-                \geometricshapemeasure(\calT) 
-                \Ceins{n} 
-                \Czwei{n} 
-                \diameterratio(\calT) % \frac{ \diam(G) }{ \diam(K) }
-            \right) 
-            2 \Cdrei{n} \geometricshapemeasure(\calT)
-            .
-        \end{gather*}
-\end{comment}
-
 \section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
 
-We are now in the position to estimate Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions.
-The estimates require local Poincar\'e--Friedrichs constants over simplices, 
-with or without boundary conditions.
+We are now in the position to develop Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions.
+These results use local Poincar\'e--Friedrichs constants over simplices, 
+with or without boundary conditions, as subcomponents.
 
@@
     This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
-\end{proof}
-
-These constants are generally not optimal. 
-For example, when $p=2$ and when only the divergence is considered, 
-we have the following improved estimate.
-
-\begin{lemma}\label{lemma:PFfordivergence}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
-    \begin{align*}
-        \| \bfw \|_{L^{2}(\Omega)} 
-        \leq 
-        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This is a reduction to the Friedrichs inequality. 
-    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
-    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
-    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
-    which has the same smallest singular value. 
+	\mwl{check final form of result}
 \end{proof}
@@
         \Ceins{n}(T)^{k}
-        \diam(T)^{k} 
+        \diam(T)
         % \matnorm{\Jacobian \varphi}^{k}
@@
 \end{lemma}
-\todo{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
+\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
 Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
@@
 \begin{proof}
-    There exists $\varphi : \hat T \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
+    There exists an affine bijection $\varphi : \hat T \rightarrow T$ 
+	that maps the convex closure of the $n$ unit vectors onto the face $F_0$.
     We can also assume that the face of $\hat T$
@@
     Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes.
-    We define $\tilde g = \cartan \tilde u$
-    and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
+    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes,
+    and let $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
+    We observe $\tilde g = \cartan \tilde u$
     By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.
 
-    The bounds for the potential operators imply 
+    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:...} imply 
     the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
@@
     \end{align*}
-    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} \tilde w$.
+    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\hat T} )$.
     By construction, $\cartan w = \cartan u$,
@@
         \| \tilde w \|_{L^{p}(\hat T)}
-        \\&
-        \leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
-        \| \tilde w \|_{L^{p}(\tilde U)}
         ,
@@
         &\leq 
-        2^{\frac n p}
+        2^{\frac {n-\ell} p}
         \| \hat g \|_{L^{p}(\hat T)}
         \leq 
-        2^{\frac n p}
+        2^{\frac {n-\ell} p}
         |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
@@
     \end{align*}
-    \todo{MV: the norms of the Jacobians have to be fixed.}
-    The second inequality follows.
-    \todo{MV: Please a few more details.}
+    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. \mwl{Double check result}
 \end{proof}
 
+We settle the following notation for our main result. 
 Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
@@
 \end{align*}
-We settle the following notation for our main result. 
 Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
+\begin{align*}
+    \mwl{X_{m} := ...}
+\end{align*}
 For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
@@
         C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \diam(T)^{k} 
         \left( 
@@
 \begin{proof}
+    \mwl{Complete the proof.}
     This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
@@
         C_{\PF,T,k,p}(T_{0})
-        \prod_{i=0}^{m} 
+        \prod_{i=1}^{m} 
         C_{???}

### 2024-10-04 main.tex
Poincare section

@@
 \usepackage{fullpage}
-\usepackage[margin=0.1cm]{geometry}
+% \usepackage[margin=0.1cm]{geometry}
 \input{header}
@@
 
-\section{Basic notions of triangulations}\label{section:triangulations}
-
-We gather here basic notions and definitions concerning simplicial meshes.
-
-\subsection{A triangulation or a simplicial complex}
-
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
-We call these points the \emph{vertices} of the simplex $T$.
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
-If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
-
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
-(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
-\begin{align*}
-    \underlying{\calT} := \bigcup_{ T \in \calT } T
-    .
-\end{align*}
-We call any set triangulable if it is the underlying set of some triangulation. 
-\\
-
-\begin{comment}
-\begin{remark}
-    Our main interest in this manuscript are finite triangulations of compact sets. 
-    There is another reason why we insist on the triangulation being finite: 
-    if we do not require our simplicial complexes to be finite,
-    then a reasonable definition of simplicial complex would need additional topological conditions. 
-    % 
-    For example, if we modify our definition of simplicial complex to be infinite, 
-    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
-    %
-    A more interesting such example is this:
-    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
-    that underlies an ``infinite $0$-dimensional simplicial complex''.
-    If we place $\calC$ on the x-axis of a 2D coordinate system 
-    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
-    then the resulting set is still compact, even path-connected,  
-    but has an ``infinite $1$-dimensional triangulation''.
-    % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
-\end{remark}
-\end{comment}
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$,
-and $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
-
-Whenever $\calT$ is a simplicial complex, 
-the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
-In practice, we not always distinguish between points and singleton simplices.
-% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
-    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
-}
-% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
-We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
-Formally,
-\begin{gather*}
-    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
-    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
-    \qquad 
-    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
-\end{gather*}
-We also write $\Minako_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial structural observation is the following.
-
-\begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
- such that 
- \begin{align*}
-    \patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S''),
-    \qquad 
-    \Vertices(S) \cup \Vertices(S') = \Vertices(S'').
- \end{align*}
-\end{lemma}
-\begin{proof}
- Let $T \in \calT$ be $n$-dimensional.
- We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
- We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
- Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
- where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
-\end{proof}
-
-We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
-We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
-We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
-Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
-A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
-
-\subsection{Shape measures and related quantities}
-
-We shift gears and move from a combinatorial study of triangulations to an analytical study:
-we introduce quantitative measures for the geometric quality of triangulations. 
-These indicate of the regularity of simplex shapes. 
-All these quantities have in common that they can be computed from purely local information. 
-Most of such \emph{shape measures} in the literature are based on geometric features, 
-but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
-While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
-
-\mwl{MWL: The different geometric quantities in this section should really be just what is needed later.
-Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
-Any inequalities here should be as tight as possible.
-}
-
-We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
-where the height of a vertex is defined as the distance to the affine span of its opposing face.
-
-For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
-
-Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
-where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
-We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
-and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
-% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
-
-Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
-the \textit{aspect shape measure} $\aspectratio(T)$,
-and 
-the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
-by 
-\begin{align}\label{math:shapemeasure}
-    \geometricshapemeasure(T)
-    := 
-    \frac{ \diam(T)^{n} }{ n! \vol(T) }
-    ,
-    \qquad 
-    \aspectratio(T)
-    := 
-    \frac{ \diam(T) }{ \height(T) }
-    ,
-    \qquad 
-    \algebraicshapemeasure(T)
-    := 
-    \sup_{ \varphi : \Delta^n \rightarrow T } 
-    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
-%     \sup_{ \varphi : \Delta^n \rightarrow T } \matnorm{\Jacobian \varphi}_{\maxcol} \matnorm{ \Jacobian \varphi^{-1} }_{\maxcol}
-    ,
-\end{align}
-where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-
-When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
-\begin{align}\label{math:shapemeasure:triangulation}
-    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
-    ,
-    \quad 
-    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
-    ,
-    \quad 
-    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
-    .
-\end{align}
-We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
-
-We now gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
-
-\begin{lemma}\label{lemma:measurerelationships}
-    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{gather*}
-        \matnorm{\Jacobian \varphi}
-        \leq 
-        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
-        ,
-        \qquad 
-        \matnorm{ \Jacobian \varphi^{-1} }
-        \leq 
-        \Czwei{n} \cdot 
-        \geometricshapemeasure(T) 
-        \diam(T)^{-1}
-        ,
-        \\
-        \algebraicshapemeasure(T)
-        \leq 
-        \Cdrei{n}
-        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
-        \geometricshapemeasure(T)
-        ,
-        \qquad 
-        %         \geometricshapemeasure(T)^{\frac 1 n}
-        %         \leq 
-        \aspectratio(T)
-        \leq 
-        \geometricshapemeasure(T)
-        .
-    \end{gather*}
-    Here,
-    \begin{align*}
-        \Ceins{n} \leq \sqrt{n},
-        \quad 
-        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
-        \quad 
-        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
-        . 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
-%     except for the vertex $\varphi(0)$. It immediately follows that 
-%     \begin{align*}
-%         \matnorm{ \Jacobian \varphi^{-1} }_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
-%         .
-%     \end{align*}
-%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
-%     
-    We easily verify the first inequality.
-To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
-    The Jacobian determinant is the product of these singular values. 
-    By a result of Hong and Pan \cite{hong1992lower},
-    \begin{align*}
-        \sigma_{n}
-        &\geq 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
-        = 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
-        .
-    \end{align*}
-%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
-    The second inequality follows by taking the reciprocal. 
-    The definition of the condition number now gives the third inequalities. 
-    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
-    Finally, 
-    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
-    \begin{align*}
-        \frac{ \diam(T) }{ \height(T) }
-        \leq 
-        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
-        \leq 
-        \frac{ \diam(T)^{n} }{ n! \vol(T) }
-        .
-    \end{align*}
-%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
-%     \begin{align*}
-%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%         \leq 
-%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
-%         .
-%     \end{align*}
-    That shows the fourth and last of the inequalities. 
-\end{proof}
-
-\begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
-
-% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
-and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
-\begin{align}\label{math:volumeratio}
-    \volumeratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
-    \frac{ \vol(T) }{ \vol(T') }
-    ,
-\end{align}
-\begin{align}\label{math:diameterratio}
-    \diameterratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
-    \frac{ \diam(T) }{ \diam(T') }
-    .
-\end{align}
-Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
-that preserves $F$. We then define 
-\begin{align}\label{math:reflectionmeasure}
-    \reflectionestimate(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \matnorm{ \Jacobian \Xi_{T,T'} }
-\end{align}
-to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
-This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
-% we define the quantity 
-% \begin{align*}
-%     \geometricshapemeasure(T)
-%     := 
-%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%     .
-% \end{align*}
-
-\begin{lemma}\label{lemma:volumecomparison}
-    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \begin{align*}
-        \diam(T_1)
-        \leq 
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \diam(F)
-        % = 
-        \geometricshapemeasure(T_1)
-        \diam(F)
-        ,
-        \qquad 
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
-        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-        % \cdot 
-        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        % = 
-        \aspectratio(T_1) \aspectratio(T_2)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-        .
-    \end{align*}
-%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
-\end{lemma}
-
-% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
-% \begin{align*}
-%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
-%     \leq 
-%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-%     \cdot 
-%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-%     .
-% \end{align*}
-% DONE: REMOVE THE FACTORIAL?
-% DONE: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-% DONE: clarify the first of the following inequalities
-
-%     \begin{align*}
-%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
-%     \end{align*}
-%     Thus we establish the first estimate:
-
-%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-%     \begin{align*}
-%         \diam(F)
-%         \geq 
-%         h
-%         =
-%         n
-%         \frac{ \vol(T_1) }{ \vol(F') }
-%         \geq 
-%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
-%         \cdot 
-%         \diam(T_1)
-%         .
-%     \end{align*}
-%     That shows the second estimate.
-
-\begin{proof}
-    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
-%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
-%     \begin{align*}
-%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
-%     \end{align*}
-%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
-    Now, 
-    \begin{align*}
-%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
-        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
-    \end{align*}
-    The first estimate follows. 
-    As for the second estimate,
-    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
-    \begin{align*}
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        = 
-        \frac{ h_1 }{ h_2 }
-        \leq
-        \frac{ \diam(T_1) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \aspectratio(T_{2})
-        .
-    \end{align*}
-\begin{comment}
-    On the other hand, 
-    \begin{align*}
-        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
-%         \\
-%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        h_1 \leq \aspectratio(T_{1}) \diam(F),
-        \qquad 
-        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
-        .
-    \end{align*}
-    The second estimate follows. 
-    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
-    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
-    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }
-        \leq 
-        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \matnorm{ \Jacobian \Xi }
-%         &
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \diam(T_1)
-%         \diam(T_2)^{-1}
-%         \\&
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         \diam(F)
-%         \diam(T_2)^{-1}
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         .
-%     \end{align*}
-    All the desired results thus follow.
-\end{comment}
-    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    Writing $h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \left( 1 + \aspectratio(T_2) \right)
-        \aspectratio(T_1)
-        .
-    \end{align*}
-    The desired estimates are shown.
-\begin{comment}
-    \mwl{Tighter estimate via geometry}
-    Matrix inverse lemma:
-    \begin{align*}
-        A ( A + (z_2-z_1) e_1^t )^{-1}
-        =
-        \Id
-        - 
-        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        =
-        \Id
-        - 
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        .
-    \end{align*}
-    Putting in a multiple of $\alpha z_1$, we find 
-    \begin{align*}
-        \alpha z_1
-        -
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) 
-        .
-    \end{align*}
-
-    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
-    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
-    We can write 
-    \begin{align*}
-        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
-    \end{align*}
-    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
-    \begin{align*}
-        A = 
-        \begin{pmatrix}
-            b_1/a_1 & 0 & 0
-            \\
-            (b_2-a_2)/a_1 & 1 & 0
-            \\
-            b_3/a_1 & 0 & 1
-        \end{pmatrix}
-        =:
-        \begin{pmatrix}
-            c_1 & 0 & 0
-            \\
-            c_2 & 1 & 0
-            \\
-            c_3 & 0 & 1
-        \end{pmatrix}
-    \end{align*}
-    Its singular values are $1$ and 
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        +
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        =
-        \frac{1}{2}
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        +
-        \frac{1}{2}
-        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
-        \leq 
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        .
-    \end{align*}
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            -
-            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        -
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        .
-    \end{align*}
-
-    \begin{align*}
-        \sigma_{\max}
-        &= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            }
-        +
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        ,
-        \\
-        \sigma_{\min}
-        &=
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        -
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        .
-    \end{align*}
-    It follows that 
-    \begin{align*}
-        \det \Jacobian\Xi
-        &=
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-        +
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-        \\
-        \frac{1}{2} + \frac{1}{2} 
-        .
-    \end{align*}
-    Matrix determinant lemma:
-    \begin{align*}
-        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
-        =
-        \left( e_{n} A^{-1} z_2 \right) \det(A)
-        =
-        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
-        .
-    \end{align*}
-\end{comment}
-\end{proof}
-
-\begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diameterratio}}. 
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
-    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
-    If we have an upper estimate for the number of simplices sharing a given vertex, 
-    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
-\end{remark}
-%%%%%%%% END HERE
-
 \section{{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and {analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
@@
 
-\subsection{Old : Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+\section{Old : Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
+
+In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
+We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
+In particular, we take the opportunity to discuss bounded convex domains as a special case.
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
+
+It is generally easier to obtain upper bounds Constructing and analyzing a potential operator is generally easier if the potential is linear. 
+Constructing linear potential operators is generally easier 
+We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+
+% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
 
 We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
+We take the opportunity to discuss bounded convex domains as a preparatory special case.
 This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
@@
 
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
+Let $\Omega \subseteq \bbR^{n}$ be an open connected set. 
 Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
@@
 We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$.
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
+
+\mwl{Use Martin's notation for these constants}
+
+\subsection{Relationship with Poincar\'e inequalities}
+
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite[Remark~\mwl{todo}]{ern2021finite}.
+Given $p \in [1,\infty]$ and a domain $\Omega \subseteq \bbR^{n}$ of finite measure,
 we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
@@
 \end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\PF},\Omega,p} \leq C_{{\rm P},\Omega,p}$.
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
+Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have 
+\[
+	C_{{\PF},\Omega,p} \leq C_{{\rm P},\Omega,p}.
+\]
+Towards a converse inequality, 
+let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align} \label{math:aver_norm}
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
+    = 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align}
+Here, we have used H\"older's or Jensen's inequality. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
+The triangle inequality now shows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)} 
+    \leq
+    2
+    \| u \|_{L^{p}(\Omega)},
     \quad 
     \forall
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align}\label{math:p_is_smaller_than_pf}
+    C_{\grad,\Omega,p} \leq 2 \overline C_{\grad,\Omega,p}.
+\end{align}
+In the special case $p=2$, taking the average is an orthogonal projection, 
+and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
+Hence,
+\begin{align}\label{math:pf_equals_p_in_hilbertspace}
+    \overline C_{\grad,\Omega,2} = C_{\grad,\Omega,2}. 
+\end{align}
+% This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$. 
+THis improvement also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, from~\eqref{math:aver_norm} it now follows that 
+% From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}
+    \leq 
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| u \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| u \|_{L^{p}(\Omega)}
+    ,
     \quad 
     \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+We thus conclude 
+\begin{align}\label{math:p_vs_pf}
+    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} \overline C_{\grad,\Omega,p}.
+\end{align}
+In the limit cases $p = 1$ and $p = \infty$ we reproduce~\eqref{math:p_is_smaller_than_pf}, 
+and in the case $p = 2$ we achieve the identity~\eqref{math:pf_equals_p_in_hilbertspace} once again.
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the common notion of Poincar\'e constant, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
 
@@
 
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over convex domains} \label{section: PX_convex}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
+\subsection{Relationship with potential operators}
+
+There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
+We define the potential 
+\begin{align*}
+    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*}
+If there is a Poincar\'e--Friedrichs constant, then by definition
+\begin{align*}
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
+\end{align*}
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+
+Because $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$,
+any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
+\begin{align*}
+    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
+    .
+\end{align*}
+A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
+\begin{align*}
+    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align*}
+Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
+
+\begin{remark}
+    Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potential operators. 
+    We highlight this perspective because it seems to be most promising when generalizing the discussion to the curl and divergence operators. 
+\end{remark}
+
+\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains} \label{section: PX_convex}
+
+\mwl{Agree on a convention for these constants: diameter included or not.}
+
+We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of bounded convex domains. 
+We have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
 \begin{align}\label{math:acostaduran}
@@
 \end{remark}
+
+\section{Basic notions of triangulations}\label{section:triangulations}
+
+We gather here basic notions and definitions concerning simplicial meshes.
+
+\subsection{A triangulation or a simplicial complex}
+
+A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
+We call these points the \emph{vertices} of the simplex $T$.
+The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
+and its remaining points constitute the \textit{boundary} of the simplex.
+If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
+then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
+
+A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
+(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
+\begin{align*}
+    \underlying{\calT} := \bigcup_{ T \in \calT } T
+    .
+\end{align*}
+We call any set triangulable if it is the underlying set of some triangulation. 
+\\
+
+\begin{comment}
+\begin{remark}
+    Our main interest in this manuscript are finite triangulations of compact sets. 
+    There is another reason why we insist on the triangulation being finite: 
+    if we do not require our simplicial complexes to be finite,
+    then a reasonable definition of simplicial complex would need additional topological conditions. 
+    % 
+    For example, if we modify our definition of simplicial complex to be infinite, 
+    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
+    %
+    A more interesting such example is this:
+    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
+    that underlies an ``infinite $0$-dimensional simplicial complex''.
+    If we place $\calC$ on the x-axis of a 2D coordinate system 
+    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
+    then the resulting set is still compact, even path-connected,  
+    but has an ``infinite $1$-dimensional triangulation''.
+    % 
+    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
+\end{remark}
+\end{comment}
+
+Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$,
+and $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
+We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
+
+Whenever $\calT$ is a simplicial complex, 
+the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
+% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
+In practice, we not always distinguish between points and singleton simplices.
+% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
+Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
+    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
+    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
+    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
+}
+% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
+% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
+
+When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
+which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
+We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
+Formally,
+\begin{gather*}
+    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
+    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
+    \qquad 
+    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
+\end{gather*}
+We also write $\Minako_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+A crucial structural observation is the following.
+
+\begin{lemma}
+ Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
+ Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
+ such that 
+ \begin{align*}
+    \patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S''),
+    \qquad 
+    \Vertices(S) \cup \Vertices(S') = \Vertices(S'').
+ \end{align*}
+\end{lemma}
+\begin{proof}
+ Let $T \in \calT$ be $n$-dimensional.
+ We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
+ We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
+ Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
+ where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
+\end{proof}
+
+We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
+We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
+We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
+Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
+A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
+and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
+
+\subsection{Shape measures and related quantities}
+
+We shift gears and move from a combinatorial study of triangulations to an analytical study:
+we introduce quantitative measures for the geometric quality of triangulations. 
+These indicate of the regularity of simplex shapes. 
+All these quantities have in common that they can be computed from purely local information. 
+Most of such \emph{shape measures} in the literature are based on geometric features, 
+but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
+While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
+
+\mwl{MWL: The different geometric quantities in this section should really be just what is needed later.
+Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
+Any inequalities here should be as tight as possible.
+}
+
+We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
+Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
+where the height of a vertex is defined as the distance to the affine span of its opposing face.
+
+For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
+
+Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
+where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
+We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
+and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
+% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
+
+Whenever $T$ is any $n$-dimensional simplex $T$,
+we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
+the \textit{aspect shape measure} $\aspectratio(T)$,
+and 
+the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
+by 
+\begin{align}\label{math:shapemeasure}
+    \geometricshapemeasure(T)
+    := 
+    \frac{ \diam(T)^{n} }{ n! \vol(T) }
+    ,
+    \qquad 
+    \aspectratio(T)
+    := 
+    \frac{ \diam(T) }{ \height(T) }
+    ,
+    \qquad 
+    \algebraicshapemeasure(T)
+    := 
+    \sup_{ \varphi : \Delta^n \rightarrow T } 
+    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
+%     \sup_{ \varphi : \Delta^n \rightarrow T } \matnorm{\Jacobian \varphi}_{\maxcol} \matnorm{ \Jacobian \varphi^{-1} }_{\maxcol}
+    ,
+\end{align}
+where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
+% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
+
+When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
+\begin{align}\label{math:shapemeasure:triangulation}
+    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
+    ,
+    \quad 
+    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
+    ,
+    \quad 
+    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
+    .
+\end{align}
+We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
+
+We now gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
+
+\begin{lemma}\label{lemma:measurerelationships}
+    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
+    \begin{gather*}
+        \matnorm{\Jacobian \varphi}
+        \leq 
+        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
+        ,
+        \qquad 
+        \matnorm{ \Jacobian \varphi^{-1} }
+        \leq 
+        \Czwei{n} \cdot 
+        \geometricshapemeasure(T) 
+        \diam(T)^{-1}
+        ,
+        \\
+        \algebraicshapemeasure(T)
+        \leq 
+        \Cdrei{n}
+        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
+        \geometricshapemeasure(T)
+        ,
+        \qquad 
+        %         \geometricshapemeasure(T)^{\frac 1 n}
+        %         \leq 
+        \aspectratio(T)
+        \leq 
+        \geometricshapemeasure(T)
+        .
+    \end{gather*}
+    Here,
+    \begin{align*}
+        \Ceins{n} \leq \sqrt{n},
+        \quad 
+        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
+        \quad 
+        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
+        . 
+    \end{align*}
+\end{lemma}
+\begin{proof}
+%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
+%     except for the vertex $\varphi(0)$. It immediately follows that 
+%     \begin{align*}
+%         \matnorm{ \Jacobian \varphi^{-1} }_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
+%         .
+%     \end{align*}
+%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
+%     
+    We easily verify the first inequality.
+To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
+    The Jacobian determinant is the product of these singular values. 
+    By a result of Hong and Pan \cite{hong1992lower},
+    \begin{align*}
+        \sigma_{n}
+        &\geq 
+        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
+        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
+        = 
+        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
+        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
+        .
+    \end{align*}
+%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
+    The second inequality follows by taking the reciprocal. 
+    The definition of the condition number now gives the third inequalities. 
+    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
+    Finally, 
+    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
+    \begin{align*}
+        \frac{ \diam(T) }{ \height(T) }
+        \leq 
+        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
+        \leq 
+        \frac{ \diam(T)^{n} }{ n! \vol(T) }
+        .
+    \end{align*}
+%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
+%     \begin{align*}
+%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%         \leq 
+%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
+%         .
+%     \end{align*}
+    That shows the fourth and last of the inequalities. 
+\end{proof}
+
+\begin{remark}
+    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    In our convention, the reference simplex has unit shape measure.
+    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
+$\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
+
+% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
+    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
+    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
+    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
+    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
+    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
+% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
+\end{remark}
+
+We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
+and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
+\begin{align}\label{math:volumeratio}
+    \volumeratio(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
+    \frac{ \vol(T) }{ \vol(T') }
+    ,
+\end{align}
+\begin{align}\label{math:diameterratio}
+    \diameterratio(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
+    \frac{ \diam(T) }{ \diam(T') }
+    .
+\end{align}
+Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
+that preserves $F$. We then define 
+\begin{align}\label{math:reflectionmeasure}
+    \reflectionestimate(\calT) 
+    := 
+    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
+    \matnorm{ \Jacobian \Xi_{T,T'} }
+\end{align}
+to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
+This indicator quantifies how much reflection across the shared face distorts the geometry.
+
+% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
+% we define the quantity 
+% \begin{align*}
+%     \geometricshapemeasure(T)
+%     := 
+%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%     .
+% \end{align*}
+
+\begin{lemma}\label{lemma:volumecomparison}
+    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
+    \begin{align*}
+        \diam(T_1)
+        \leq 
+        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
+        % \diam(F)
+        % = 
+        \geometricshapemeasure(T_1)
+        \diam(F)
+        ,
+        \qquad 
+        \frac{ \vol(T_1) }{ \vol(T_2) }
+        \leq 
+        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
+        % \cdot 
+        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
+        % = 
+        \aspectratio(T_1) \aspectratio(T_2)
+        .
+    \end{align*}
+    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
+        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
+        .
+    \end{align*}
+%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
+\end{lemma}
+
+% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
+% \begin{align*}
+%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
+%     \leq 
+%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
+%     \cdot 
+%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
+%     .
+% \end{align*}
+% DONE: REMOVE THE FACTORIAL?
+% DONE: I am not 100% sure what that means.
+Is really the heights of F?
+I imagine this is rather the heights of simplices T_1 and T_2, isn't?
+Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
+(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
+% DONE: clarify the first of the following inequalities
+
+%     \begin{align*}
+%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
+%     \end{align*}
+%     Thus we establish the first estimate:
+
+%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
+%     \begin{align*}
+%         \diam(F)
+%         \geq 
+%         h
+%         =
+%         n
+%         \frac{ \vol(T_1) }{ \vol(F') }
+%         \geq 
+%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
+%         \cdot 
+%         \diam(T_1)
+%         .
+%     \end{align*}
+%     That shows the second estimate.
+
+\begin{proof}
+    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
+%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
+%     \begin{align*}
+%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
+%     \end{align*}
+%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
+    Now, 
+    \begin{align*}
+%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
+        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
+    \end{align*}
+    The first estimate follows. 
+    As for the second estimate,
+    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
+    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
+    \begin{align*}
+        \frac{ \vol(T_1) }{ \vol(T_2) }
+        = 
+        \frac{ h_1 }{ h_2 }
+        \leq
+        \frac{ \diam(T_1) }{ h_2 }
+        \leq
+        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
+        \leq
+        \aspectratio(T_{1}) \aspectratio(T_{2})
+        .
+    \end{align*}
+\begin{comment}
+    On the other hand, 
+    \begin{align*}
+        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
+%         \\
+%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
+        h_1 \leq \aspectratio(T_{1}) \diam(F),
+        \qquad 
+        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
+        .
+    \end{align*}
+    The second estimate follows. 
+    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
+    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
+    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }
+        \leq 
+        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
+        \leq 
+        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
+        \leq 
+        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
+        .
+    \end{align*}
+%     \begin{align*}
+%         \matnorm{ \Jacobian \Xi }
+%         &
+%         \leq 
+%         \Ceins{n}
+%         \Czwei{n}
+%         \geometricshapemeasure(T_2)
+%         \diam(T_1)
+%         \diam(T_2)^{-1}
+%         \\&
+%         \leq 
+%         \Ceins{n}
+%         \Czwei{n}
+%         \geometricshapemeasure(T_2)
+%         \geometricshapemeasure(T_1) 
+%         \diam(F)
+%         \diam(T_2)^{-1}
+%         \leq 
+%         \Ceins{n}
+%         \Czwei{n}
+%         \geometricshapemeasure(T_2)
+%         \geometricshapemeasure(T_1) 
+%         .
+%     \end{align*}
+    All the desired results thus follow.
+\end{comment}
+    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
+    Writing $h_0$ for the unit normal in direction $z_1$, we have 
+    \begin{align*}
+        \Xi(x) 
+        = 
+        x 
+        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
+        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
+        ,
+        \qquad 
+        x \in \bbR^{n}
+        .
+    \end{align*}
+    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
+    By the Xu-Zikanatov estimate,
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        \frac{ \diam(T_1) }{ \height(T_1) }
+        +
+        \frac{ \diam(T_2) }{ \height(T_1) }
+        \leq 
+        \left( 1 + \aspectratio(T_2) \right)
+        \aspectratio(T_1)
+        .
+    \end{align*}
+    The desired estimates are shown.
+\begin{comment}
+    \mwl{Tighter estimate via geometry}
+    Matrix inverse lemma:
+    \begin{align*}
+        A ( A + (z_2-z_1) e_1^t )^{-1}
+        =
+        \Id
+        - 
+        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
+        (z_2-z_1) e_1^t \cdot A^{-1}
+        =
+        \Id
+        - 
+        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
+        (z_2-z_1) e_1^t \cdot A^{-1}
+        .
+    \end{align*}
+    Putting in a multiple of $\alpha z_1$, we find 
+    \begin{align*}
+        \alpha z_1
+        -
+        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
+        (z_2-z_1) 
+        .
+    \end{align*}
+
+    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
+    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
+    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
+    We can write 
+    \begin{align*}
+        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
+    \end{align*}
+    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
+    \begin{align*}
+        A = 
+        \begin{pmatrix}
+            b_1/a_1 & 0 & 0
+            \\
+            (b_2-a_2)/a_1 & 1 & 0
+            \\
+            b_3/a_1 & 0 & 1
+        \end{pmatrix}
+        =:
+        \begin{pmatrix}
+            c_1 & 0 & 0
+            \\
+            c_2 & 1 & 0
+            \\
+            c_3 & 0 & 1
+        \end{pmatrix}
+    \end{align*}
+    Its singular values are $1$ and 
+    \begin{align*}
+        \sigma_{\max}
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            +
+            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
+        }
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            +
+            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        }
+        =
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+        +
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        =
+        \frac{1}{2}
+        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
+        +
+        \frac{1}{2}
+        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
+        \leq 
+        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
+        .
+    \end{align*}
+    \begin{align*}
+        \sigma_{\max}
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            -
+            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
+        }
+        =
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+        -
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        .
+    \end{align*}
+
+    \begin{align*}
+        \sigma_{\max}
+        &= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            }
+        +
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        ,
+        \\
+        \sigma_{\min}
+        &=
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        -
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        .
+    \end{align*}
+    It follows that 
+    \begin{align*}
+        \det \Jacobian\Xi
+        &=
+        \frac{1}{4}
+        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+        +
+        \frac{1}{4}
+        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+        \\
+        \frac{1}{2} + \frac{1}{2} 
+        .
+    \end{align*}
+    Matrix determinant lemma:
+    \begin{align*}
+        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
+        =
+        \left( e_{n} A^{-1} z_2 \right) \det(A)
+        =
+        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
+        .
+    \end{align*}
+\end{comment}
+\end{proof}
+
+\begin{remark}
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diameterratio}}. 
+    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
+    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
+    If we have an upper estimate for the number of simplices sharing a given vertex, 
+    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
+\end{remark}
+%%%%%%%% END HERE
 

### 2024-10-04 hyperplane.tex
various improvements

--- 2024-10-04 main.tex
@@
-\documentclass[10pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{fullpage}
-\usepackage[margin=0.1cm]{geometry}
-\input{header}
-
-\usepackage{comment}          % 
-\usepackage{hyperref}         % For hypertext links
-\usepackage{tikz-3dplot}      % 3d plots 
-\usepackage{enumitem}
-\setitemize[1]{left=0.0cm}
-
-% Added by MV 
-\usepackage{bm} % preferred version of bold symbols
-\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
-% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
-% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
-\newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
-\setlength{\marginparwidth}{2cm}
-
-\newcommand\cye[1]{%
-\protect\leavevmode
-\begingroup
-    \color{blue}%
-    #1%
-\endgroup
-}
-% \color{red!35!yellow}
-
-\newcommand{\mwl}[1]{{\color{red}#1}}
-\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
-\newcommand{\disk}{\cye{ball}}
-
-% Title, authors, and affiliations
-% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
-% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
-
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations}
-\author{
-    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
-    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{martin.vohralik@inria.fr}
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-    We construct potentials for the gradient, the curl, and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations in particular includes local patches (stars) in dimension two and three.
-    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
-    % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
-    % 
-    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
-    %     The main application that we envision are computable estimates over finite element patches. 
-    %
-    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators where we can bound their operator norms.
-    \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
-    Computational examples illustrate the theoretical findings.
-\end{abstract}
-
-\tableofcontents
-
-\section{Introduction}\label{section:intro}
-
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the\cye{se} potentials are upper bounds for the Poincar\'e--Friedrichs constants, which quantify the fundamental stability features of a variety of partial differential equations.
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant\cye{s} enter the stability and convergence theory and spectral bounds for \cye{stiffness} matrices.
-\cye{Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians}.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or \cye{more generally} the exterior derivative are \cye{largely unavailable}.
-
-\cye{Our main purpose here is to fill this gap.
-In the gradient case, we can go over with so-called face-connected triangulations.
-However, to proceed} in the \cye{general exterior derivative case, we are brought to} so-called shellable triangulations.
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards more general cases.
-\cye{Still, we cover most practical non-convex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
-\cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}
-
-Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be a bounded connected open set.
-Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
-Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
-
-%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{section:intro_grad}
-
-Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
-\begin{align} \label{equation:W1p}
-    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
-\end{align}
-For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
-Then,
-%
-\begin{align*}
-    \Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
-\end{align*}
-is the {\em potential operator}. A particular example of our interest is
-%
-\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
-    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
-\end{align}
-%
-Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
-
-\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
-\begin{align}\label{math:pot_grad_norm}
-    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
-\end{align}\end{subequations}}
-This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
-\begin{subequations}\label{math:PF_gradient}\begin{align} \label{math:PF_gradient_1}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
-\begin{align} \label{math:PF_gradient_2}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p}
-    \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}\end{subequations}
-We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
-\begin{align} \label{math:pot_PF_grad}
-    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
-    \| u \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\grad,\Omega,p}
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-for all $\bff \in \nabla W^{1,p}(\Omega)$.}
-
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
-Most research on optimal constants has addressed the case of convex domains.
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
-\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
-
-%\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
-
-Consider the vector-valued spaces
-\begin{subequations}\label{equation:W_curl_div_p} \begin{align}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align}\end{subequations}
-The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector  fields.
-
-\cye{Let a vector field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
-We are interested in constants for inequalities such as 
-\begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
-    ,
-    \\
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfu = f } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
-    ,
-\end{align}\end{subequations}
-and how these constants can be estimated by the operator norms of {\em linear} potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-The fundamental difference \cye{with respect to Section~\ref{section:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
-In Section~\ref{section:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
-It is thus trivially complemented for all $p$, with a canonical choice of projection.
-By contrast, in the Banach space case $p \neq 2$, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
-\cye{Actually,} the existence of a bounded linear potential operator here is a non-trivial fact even in the Hilbert space case $p = 2$.
-
-\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
-Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
-\begin{align}
-    \label{math:Weber}
-    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
-\end{align}
-for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
-Yet another writing is 
-\label{math:PF_orth} \begin{align}
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
-\end{align}
-for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
-Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
-However, that easy observation seems restricted to $p=2$.
-
-Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
-\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
-
-%\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
-
-Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
-This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
-\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $w \in W^{p}\Alt^{k}(\Omega)$, there exists $u \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
-\begin{align} \label{math:PF_DF} 
-    \| u \|_{L^{p}(\Omega} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
-\end{align} 
-}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparison with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
-
-In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
-\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
-
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
-\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
-Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-
-%\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
-
-\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
-\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
-Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
-\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
-\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
-
-%\subsection{\cye{Objectives and methodology}}
-
-The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
-\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
-
-% \subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
-
-Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
-For scalar-valued functions in the context of Section~\ref{section:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
-%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
-Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
-
-In the gradient case of Section~\ref{section:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-%\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
-
-For vector fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
-We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
-However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
-Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
-With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
-
-%\subsubsection{\cye{Analytical constants over convex domains}}
-
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
-Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
-In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
-The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
-
-%\subsubsection{\cye{Domains star-shaped with respect to a ball}}
-
-\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
-This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
-Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
-This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this \cye{in particular} occurs when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
-which contain local finite element patches \cye{that} are not star-shaped with respect to any ball.
-
-%\subsubsection{\cye{Potentials subject to partial boundary conditions}}
-
-\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
-We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
-
-%\subsection{\cye{Main results}}
-
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.}
-\mwl{MV: remark from after Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} moved here.} 
-The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
-\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
-
-\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
-As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei}.}
-
-\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
-\cye{This is summarized in Theorem~\ref{theorem:PF_EC}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:PF_EC} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
-
-\section{Introduction}\label{section:intro}
-
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-
-We illustrate the subject of our discussion with the curl operator. 
-If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
-Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
-    \leq 
-    C_{\curl}
-    \| \bff \|_{L^{2}(\Omega)}
-    .
-\end{align*}
-The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
-Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
-\\
-
-Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-The majority of estimates in the literature address only gradient potentials. 
-We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards the more general case. 
-For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
-Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
-\\
-
-Before we outline the main results of this exposition in more detail, 
-we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-
-Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
-for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:intro:inequalitypf:gradient} 
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The different scalar potentials only differ by a constant. 
-Therefore, 
-this inequality is equivalent to the following statement: 
-\begin{align}\label{math:intro:poincarefriedrichs:grad}
-    \min\limits_{c\in\bbR}
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
-    .\tag{PF} 
-\end{align}
-Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
-The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
-\begin{align*}
-    \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
-\begin{align}\label{math:intro:poincare:grad}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    , \tag{P} 
-\end{align}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
-
-Most research on optimal constants has addressed the case of convex domains. 
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence
-
-The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-We use the vector field spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align*}
-Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
-\begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
-    \qquad 
-    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
-\end{align*}
-The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
-We are interested in constants for inequalities such as 
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)}
-    ,
-    \\%\qquad 
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
-and how these constants can be estimated by the operator norms of linear potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-
-Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-This sharply contrasts to the study of the gradient operator. 
-We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
-who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
-thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
-By duality, that implies lower bounds for the case of full boundary conditions.
-
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
-follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-\\
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
-which contain finite element patches are not star-shaped with respect to any ball.
-
-Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
-However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
-We review some of the main outcomes. 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-% 
-The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted.
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here.
-The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
-Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the interfacing intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed to ensure continuity across that interface.
-
-While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
-we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
-We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
-which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
-We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
-
-% General outline 
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-\\
-
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable. 
-\\
-
-Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
-the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
-
-In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-
-However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
-We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
-In comparison to their exposition, our variants of the regularized potential operators are simplified:
-we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
-however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
-We consider the latter outcome to be of independent interest.
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-\mwl{What is the best place for this paragraph?}
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-There are several avenues for further research going from here. 
-The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
-There are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
-In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
-Better transformations or more careful estimates are likely possible, as are completely different approaches.
-For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
-
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
-These topics remain for future research.
-
-Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
-In particular, domains with shellable triangulations are contractible.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-\\
-
-\subsection{Organization of this manuscript}
-
-The remainder of this manuscript is structured as follows.
-We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
-We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.
-We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
-We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
-Our regularized potential operators over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
-giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
-We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
-and we construct an important geometric reflection operator in Section~\ref{section:extension}. 
-We finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}.
-
-\section{Basic notions of triangulations}\label{section:triangulations}
-
-We gather here basic notions and definitions concerning simplicial meshes.
-
-\subsection{A triangulation or a simplicial complex}
-
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
-We call these points the \emph{vertices} of the simplex $T$.
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
-If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
-
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
-(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
-\begin{align*}
-    \underlying{\calT} := \bigcup_{ T \in \calT } T
-    .
-\end{align*}
-We call any set triangulable if it is the underlying set of some triangulation. 
-\\
-
-\begin{comment}
-\begin{remark}
-    Our main interest in this manuscript are finite triangulations of compact sets. 
-    There is another reason why we insist on the triangulation being finite: 
-    if we do not require our simplicial complexes to be finite,
-    then a reasonable definition of simplicial complex would need additional topological conditions. 
-    % 
-    For example, if we modify our definition of simplicial complex to be infinite, 
-    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
-    %
-    A more interesting such example is this:
-    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
-    that underlies an ``infinite $0$-dimensional simplicial complex''.
-    If we place $\calC$ on the x-axis of a 2D coordinate system 
-    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
-    then the resulting set is still compact, even path-connected,  
-    but has an ``infinite $1$-dimensional triangulation''.
-    % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
-\end{remark}
-\end{comment}
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$,
-and $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
-
-Whenever $\calT$ is a simplicial complex, 
-the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
-In practice, we not always distinguish between points and singleton simplices.
-% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
-    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
-}
-% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
-We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
-Formally,
-\begin{gather*}
-    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
-    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
-    \qquad 
-    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
-\end{gather*}
-We also write $\Minako_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial structural observation is the following.
-
-\begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
- such that 
- \begin{align*}
-    \patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S''),
-    \qquad 
-    \Vertices(S) \cup \Vertices(S') = \Vertices(S'').
- \end{align*}
-\end{lemma}
-\begin{proof}
- Let $T \in \calT$ be $n$-dimensional.
- We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
- We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
- Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
- where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
-\end{proof}
-
-We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
-We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
-We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
-Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
-A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
-
-\subsection{Shape measures and related quantities}
-
-We shift gears and move from a combinatorial study of triangulations to an analytical study:
-we introduce quantitative measures for the geometric quality of triangulations. 
-These indicate of the regularity of simplex shapes. 
-All these quantities have in common that they can be computed from purely local information. 
-Most of such \emph{shape measures} in the literature are based on geometric features, 
-but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
-While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
-
-\mwl{MWL: The different geometric quantities in this section should really be just what is needed later.
-Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
-Any inequalities here should be as tight as possible.
-}
-
-We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
-where the height of a vertex is defined as the distance to the affine span of its opposing face.
-
-For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
-
-Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
-where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
-We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
-and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
-% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
-
-Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
-the \textit{aspect shape measure} $\aspectratio(T)$,
-and 
-the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
-by 
-\begin{align}\label{math:shapemeasure}
-    \geometricshapemeasure(T)
-    := 
-    \frac{ \diam(T)^{n} }{ n! \vol(T) }
-    ,
-    \qquad 
-    \aspectratio(T)
-    := 
-    \frac{ \diam(T) }{ \height(T) }
-    ,
-    \qquad 
-    \algebraicshapemeasure(T)
-    := 
-    \sup_{ \varphi : \Delta^n \rightarrow T } 
-    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
-%     \sup_{ \varphi : \Delta^n \rightarrow T } \matnorm{\Jacobian \varphi}_{\maxcol} \matnorm{ \Jacobian \varphi^{-1} }_{\maxcol}
-    ,
-\end{align}
-where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-
-When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
-\begin{align}\label{math:shapemeasure:triangulation}
-    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
-    ,
-    \quad 
-    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
-    ,
-    \quad 
-    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
-    .
-\end{align}
-We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
-
-We now gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
-
-\begin{lemma}\label{lemma:measurerelationships}
-    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{gather*}
-        \matnorm{\Jacobian \varphi}
-        \leq 
-        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
-        ,
-        \qquad 
-        \matnorm{ \Jacobian \varphi^{-1} }
-        \leq 
-        \Czwei{n} \cdot 
-        \geometricshapemeasure(T) 
-        \diam(T)^{-1}
-        ,
-        \\
-        \algebraicshapemeasure(T)
-        \leq 
-        \Cdrei{n}
-        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
-        \geometricshapemeasure(T)
-        ,
-        \qquad 
-        %         \geometricshapemeasure(T)^{\frac 1 n}
-        %         \leq 
-        \aspectratio(T)
-        \leq 
-        \geometricshapemeasure(T)
-        .
-    \end{gather*}
-    Here,
-    \begin{align*}
-        \Ceins{n} \leq \sqrt{n},
-        \quad 
-        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
-        \quad 
-        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
-        . 
-    \end{align*}
-\end{lemma}
-\begin{proof}
-%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
-%     except for the vertex $\varphi(0)$. It immediately follows that 
-%     \begin{align*}
-%         \matnorm{ \Jacobian \varphi^{-1} }_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
-%         .
-%     \end{align*}
-%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
-%     
-    We easily verify the first inequality.
-To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
-    The Jacobian determinant is the product of these singular values. 
-    By a result of Hong and Pan \cite{hong1992lower},
-    \begin{align*}
-        \sigma_{n}
-        &\geq 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
-        = 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
-        .
-    \end{align*}
-%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
-    The second inequality follows by taking the reciprocal. 
-    The definition of the condition number now gives the third inequalities. 
-    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
-    Finally, 
-    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
-    \begin{align*}
-        \frac{ \diam(T) }{ \height(T) }
-        \leq 
-        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
-        \leq 
-        \frac{ \diam(T)^{n} }{ n! \vol(T) }
-        .
-    \end{align*}
-%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
-%     \begin{align*}
-%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%         \leq 
-%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
-%         .
-%     \end{align*}
-    That shows the fourth and last of the inequalities. 
-\end{proof}
-
-\begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
-
-% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
-and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
-\begin{align}\label{math:volumeratio}
-    \volumeratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
-    \frac{ \vol(T) }{ \vol(T') }
-    ,
-\end{align}
-\begin{align}\label{math:diameterratio}
-    \diameterratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
-    \frac{ \diam(T) }{ \diam(T') }
-    .
-\end{align}
-Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
-that preserves $F$. We then define 
-\begin{align}\label{math:reflectionmeasure}
-    \reflectionestimate(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \matnorm{ \Jacobian \Xi_{T,T'} }
-\end{align}
-to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
-This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
-% we define the quantity 
-% \begin{align*}
-%     \geometricshapemeasure(T)
-%     := 
-%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%     .
-% \end{align*}
-
-\begin{lemma}\label{lemma:volumecomparison}
-    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \begin{align*}
-        \diam(T_1)
-        \leq 
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \diam(F)
-        % = 
-        \geometricshapemeasure(T_1)
-        \diam(F)
-        ,
-        \qquad 
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
-        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-        % \cdot 
-        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        % = 
-        \aspectratio(T_1) \aspectratio(T_2)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-        .
-    \end{align*}
-%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
-\end{lemma}
-
-% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
-% \begin{align*}
-%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
-%     \leq 
-%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-%     \cdot 
-%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-%     .
-% \end{align*}
-% DONE: REMOVE THE FACTORIAL?
-% DONE: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-% DONE: clarify the first of the following inequalities
-
-%     \begin{align*}
-%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
-%     \end{align*}
-%     Thus we establish the first estimate:
-
-%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-%     \begin{align*}
-%         \diam(F)
-%         \geq 
-%         h
-%         =
-%         n
-%         \frac{ \vol(T_1) }{ \vol(F') }
-%         \geq 
-%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
-%         \cdot 
-%         \diam(T_1)
-%         .
-%     \end{align*}
-%     That shows the second estimate.
-
-\begin{proof}
-    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
-%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
-%     \begin{align*}
-%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
-%     \end{align*}
-%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
-    Now, 
-    \begin{align*}
-%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
-        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
-    \end{align*}
-    The first estimate follows. 
-    As for the second estimate,
-    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
-    \begin{align*}
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        = 
-        \frac{ h_1 }{ h_2 }
-        \leq
-        \frac{ \diam(T_1) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \aspectratio(T_{2})
-        .
-    \end{align*}
-\begin{comment}
-    On the other hand, 
-    \begin{align*}
-        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
-%         \\
-%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        h_1 \leq \aspectratio(T_{1}) \diam(F),
-        \qquad 
-        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
-        .
-    \end{align*}
-    The second estimate follows. 
-    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
-    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
-    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }
-        \leq 
-        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \matnorm{ \Jacobian \Xi }
-%         &
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \diam(T_1)
-%         \diam(T_2)^{-1}
-%         \\&
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         \diam(F)
-%         \diam(T_2)^{-1}
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         .
-%     \end{align*}
-    All the desired results thus follow.
-\end{comment}
-    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    Writing $h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \left( 1 + \aspectratio(T_2) \right)
-        \aspectratio(T_1)
-        .
-    \end{align*}
-    The desired estimates are shown.
-\begin{comment}
-    \mwl{Tighter estimate via geometry}
-    Matrix inverse lemma:
-    \begin{align*}
-        A ( A + (z_2-z_1) e_1^t )^{-1}
-        =
-        \Id
-        - 
-        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        =
-        \Id
-        - 
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        .
-    \end{align*}
-    Putting in a multiple of $\alpha z_1$, we find 
-    \begin{align*}
-        \alpha z_1
-        -
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) 
-        .
-    \end{align*}
-
-    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
-    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
-    We can write 
-    \begin{align*}
-        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
-    \end{align*}
-    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
-    \begin{align*}
-        A = 
-        \begin{pmatrix}
-            b_1/a_1 & 0 & 0
-            \\
-            (b_2-a_2)/a_1 & 1 & 0
-            \\
-            b_3/a_1 & 0 & 1
-        \end{pmatrix}
-        =:
-        \begin{pmatrix}
-            c_1 & 0 & 0
-            \\
-            c_2 & 1 & 0
-            \\
-            c_3 & 0 & 1
-        \end{pmatrix}
-    \end{align*}
-    Its singular values are $1$ and 
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        +
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        =
-        \frac{1}{2}
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        +
-        \frac{1}{2}
-        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
-        \leq 
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        .
-    \end{align*}
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            -
-            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        -
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        .
-    \end{align*}
-
-    \begin{align*}
-        \sigma_{\max}
-        &= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            }
-        +
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        ,
-        \\
-        \sigma_{\min}
-        &=
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        -
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        .
-    \end{align*}
-    It follows that 
-    \begin{align*}
-        \det \Jacobian\Xi
-        &=
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-        +
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-        \\
-        \frac{1}{2} + \frac{1}{2} 
-        .
-    \end{align*}
-    Matrix determinant lemma:
-    \begin{align*}
-        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
-        =
-        \left( e_{n} A^{-1} z_2 \right) \det(A)
-        =
-        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
-        .
-    \end{align*}
-\end{comment}
-\end{proof}
-
-\begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diameterratio}}. 
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
-    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
-    If we have an upper estimate for the number of simplices sharing a given vertex, 
-    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
-\end{remark}
-%%%%%%%% END HERE
-
-\section{{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and {analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
-
-In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
-We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
-In particular, we take the opportunity to discuss convex domains as a special case.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
-
-\subsection{Nonlinear and linear potentials}
-
-In the Banach setting $p \neq 2$, finding a norm-minimizing potential such as $\Phi_{\grad}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$ is a nonlinear operation.
-Its existence may actually not be guaranteed unless $1 < p < \infty$.
-However, any \textit{linear} potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi_{\grad}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ has the operator norm that \cye{gives} the upper bound 
-\begin{align}\label{math:PF_P}
-    \mwl{C_{\grad,\Omega,p} = } 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
-    .
-\end{align}
-This explains our interest in the construction of {\em linear potential operators}.
-
-\subsection{Poincar\'e--Friedrichs and Poincar\'e inequalities}
-
-\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\grad}( \bff ) = \bff$ determines $\overline \Phi_{\grad}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
-\begin{align*}
-    \overline\Phi_{\grad}( \nabla u ) \cye{:}= u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_\Omega$ denotes the average of $u$ over the domain $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-This potential operator can also implicitly be defined by
-\begin{align*}
-    \overline \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the best constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
-\begin{align}\label{math:P_gradient}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    . 
-\end{align}
-Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient}, 
-\begin{align*}
-    C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.
-\end{align*}
-
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align} \label{math:aver_norm}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-\begin{align*}
-    \color{Emerald}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-    \leq 
-    2^{p-1} 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    +
-    2^{p-1} 
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    \leq 
-    2^{p} 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-\mwl{Via an application of the triangle inequality, }Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{\grad,\Omega,p} \leq 2 \overline C_{\grad,\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, 
-and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
-Hence,
-\begin{align*}
-    \overline C_{\grad,\Omega,2} = C_{\grad,\Omega,2}. 
-\end{align*}
-\mwl{
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-}
-From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} \overline C_{\grad,\Omega,p}.
-\end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-
-%%%%
-
-\subsection{Old : Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
-\\
-
-Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align*}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-\\
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite{ern2021finite}.
-Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure,
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align*}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\PF},\Omega,p} \leq C_{{\rm P},\Omega,p}$.
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
-Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
-\\
-
-In the light of these musings, we settle for the objective of constructing linear potential operators for the gradient operator.
-This task is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over convex domains} \label{section: PX_convex}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains. 
-Over convex bounded domains, we have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
-\begin{align}\label{math:acostaduran}
-    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{\diam(\Omega)}{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    ,
-    \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
-    \leq 
-    \frac{\diam(\Omega)}{\pi}
-    \| \nabla u \|_{L^{2}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,2}(\Omega)
-    ,
-\end{align}
-where $\diam(\Omega)$ is the diameter of the domain $\Omega$.
-These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
-\begin{align}\label{math:chuawheeden}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm P},{\rm CW},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where we use an upper bound by Chua and Wheeden:
-\begin{align*}
-    C_{{\rm P},{\rm CW},p} 
-    := 
-    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
-    \frac{ 
-        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
-    }{ 
-        \| \nabla v \|_{L^{p}([0,1])} 
-    }
-    \leq 
-    \sqrt[p]{p} 2^{1-\frac 1 p}
-    =
-    2
-    \left( \frac p 2 \right)^{\frac 1 p}
-    .
-\end{align*} 
-Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
-As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
-
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}, \cite[Theorem~1.1]{esposito2013poincare}): 
-when $1 < p < \infty$, one can show that 
-\begin{align}\label{math:esposito:pf}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\PF,{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align*}
-    C_{\PF,{\rm EFNT},p}
-    :=
-    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
-    .
-\end{align*}
-Note that the last inequalities from~\eqref{math:p_vs_pf} imply, again when $1 < p < \infty$, the Poincar\'e inequalities
-\begin{align}\label{math:esposito:poincare}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
-\begin{align}\label{math:l1estimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{ \diam(\Omega) }{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    .
-\end{align}
-When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
-\begin{align}\label{math:lipschitzestimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{\infty}(\Omega)}
-    \leq 
-    \diam(\Omega)
-    \| \nabla u \|_{L^{\infty}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,\infty}(\Omega)
-    .
-\end{align}
-
-% DONT: Keep ?
-% \begin{example}
-%     We explain why \eqref{math:l1estimate} is optimal. 
-%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
-%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
-%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
-%     and $\Omega$ has diameter $2$. 
-%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
-%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
-%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
-% \end{example}
-
-\begin{remark}
-    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
-    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
-    In the case $2 \leq p$, 
-    \begin{align*}
-        2^{1-\frac 2 p}
-        C_{\PF,{\rm EFNT},p}
-        =
-        \frac{ 2^{1-\frac 2 p} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq 
-        4^{-\frac 1 p}
-        \leq
-        C_{{\rm P},{\rm CW},p} 
-        .
-    \end{align*}
-    In the case $2 \geq p$, 
-    \begin{align*}
-        2^{\frac 2 p - 1}
-        C_{\PF,{\rm EFNT},p}
-        =
-        \frac{ 2^{\frac 2 p - 1} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq
-        \frac{ 2^{\frac 2 p-1} }{2}
-        &
-        =
-        2^{\frac 2 p - 2}
-        \\&
-        =
-        4^{\frac 1 p - 1}
-        \leq
-        C_{{\rm P},{\rm CW},p} 
-%         % 
-%         .
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
-%         =
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
-%         \leq 
-%         \frac{1}{2}
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua Wheeden upper bound is not optimal!
-    % DONE: Theorem 1.2 in Chua Wheeden 
-% DONT: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
-%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-%         \leq 
-%         \frac{1}{2}
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{1}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,1}(\Omega)
-%         .
-%     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
-%     which implies the Poincar\'e inequality 
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,\infty}(\Omega)
-%         %
-%     \end{align*}
-%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
-%     % DONT: review this entire result 
-\end{remark}
-
-% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
-
-\begin{remark}
-    The above Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
-    but individual convex domains may allow for better constants.
-    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for discussions;
-    for example, triangles allow the reduction of the constant by 20\%.
-\end{remark}
-
-\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
-
-In this section, we develop stepwise computable estimates of Poincar\'e--Friedrichs constants of triangulated domains. 
-The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-We perform a discrete analogue of this procedure over triangulated domains: 
-having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.
-%We construct a scalar potential for a given gradient vector field on larger and larger triangulated subdomains.
-We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face, thus constructing a scalar potential over larger and larger subdomains.
-This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-
-% We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
-We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells.
-We construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-% 
-% {\color{blue}In this section, we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
-\cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-% Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure.
-We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}.
-% We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
-% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-% }
-
-% While the underlying idea remains the same, they differ in the way the intermediate potentials are extended.
-% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result. 
-% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
-
-We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
-% This is inspired by the classical proof of what is often called the Friedrichs inequality.
-
-\begin{lemma}\label{lemma:mixedbconsimplex}
-    Let $T$ be an $n$-simplex with a face $F$ and $p \in [1,\infty]$. 
-    If $u \in W^{1,p}(T)$ with $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{\PF,T,F,p} \| \nabla u \|_{L^{p}(T)}
-        ,
-    \end{align*}
-    where $C_{\PF,T,F,p} = p^{-\frac 1 p} \diam(T)$ for $p < \infty$ and $C_{\PF,T,F,\infty} = \diam(T)$. 
-%     \begin{align*}
-%         C_{\PF,T,F,p}
-%         &\leq 
-%         C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
-%         \\
-%         C_{\PF,T,F,p}
-%         &\leq
-%         \frac{1}{\sqrt[p]{p}}
-%         \diam(T)
-%         .
-%     \end{align*}
-\end{lemma}
-\begin{proof}
-\begin{comment}
-    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
-    \begin{gather*}
-        \| w \|_{L^{p}(T)}
-        \leq 
-        C_{\PF,T,p} 
-        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
-        .
-    \end{gather*}
-    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
-    We use that 
-    \begin{gather*}
-        \| \gamma \|_{L^{p}(T)}
-        =
-        \gamma \vol(T)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \cdot 
-        \gamma 
-        \vol(F)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \| \gamma \|_{L^{p}(F)}
-        .
-    \end{gather*}
-    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
-    \begin{align*}
-        \| \gamma \|_{L^{p}(F)}^{p}
-        &
-        \leq 
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p}
-        +
-        p
-        \cdot 
-        \diam(T)
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p-1}
-        \| \nabla w \|_{L^{p}(T)}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot C_{\PF,T,p}^{p-1} \right) 
-        \diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right) 
-        %\diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        .
-    \end{align*}
-    Recall that $u = w - \gamma$. The first inequality follows. 
-\end{comment}
-    % The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Since the inequality follows from Rademacher's theorem in the limit case $p = \infty$,
-    we assume $1 \leq p < \infty$. 
-    Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
-    We extend $u$ by zero to a function over the entire $\bbR^{n}$.
-    Without loss of generality, 
-    the segment from the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
-    and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg$ for the trivial extension of $\nabla u$ over the entire $\bbR^{n}$.
-    %With the fundamental theorem of calculus and H\"older's inequality: 
-    Using the fundamental theorem of calculus and H\"older's inequality, 
-    \begin{align*}
-        \int_{T} |u(x)|^{p} \diff x \;dx
-        &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
-        \\&
-        \leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
-        \\&
-        \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
-        \\&
-        \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \;dx_1 
-        \cdot 
-        \int_{T} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
-        \leq
-        \frac{\diam(T)^{p}}{p} \int_{T} \left| \nabla u( x ) \right|^{p} \,dx
-        %
-%         \leq
-%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
-%         \leq 
-%         D^{p} 
-%         \int_{\Omega} |\nabla u|^{p} \,dx
-        .
-    \end{align*}
-    That $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
-    for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$. 
-    Very briefly verify that density argument: 
-    There exists affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ from the reference simplex onto $T$ that maps the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$.
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\Delta^{n}$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
-    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$ within the Banach space $W^{1,p}(T)$
-    and has the desired support property. 
-\end{proof}
-
-% \begin{remark}
-%     While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains.  
-% \end{remark}
-
-The next auxiliary result extends the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations.
-We emphasize that face patches are not necessarily convex.
-The following result is reasonably sharp when the two simplices have similar volumes and diameters.
-
-\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
-    Let $\calT$ be a triangulation.
-    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
-    Write $U := T_1 \cup T_2$. 
-    If $p \in [1,\infty]$ and $u \in W^{1,p}(\Omega)$,
-    then 
-    \begin{align*}
-        \min\limits_{ c \in \bbR }
-        \| u - c \|_{L^{p}(U)}
-        &
-%         \leq 
-%         2 \Ceins{n} C_{\PF,{\rm EFNT},p}
-%         \max\left( 
-%             \frac{ \vol(T_1) }{ \vol(T_2) }
-%             ,
-%             \frac{ \vol(T_2) }{ \vol(T_1) }
-%         \right)^{\frac 1 p}
-%         \\&\qquad\qquad 
-%         \cdot 
-%         \max\left( \diam(T_1), \diam(T_2) \right)
-%         \| \nabla u \|_{L^{p}(U)}
-%         \\&
-        \leq 
-        C_{{\PF},T_1 \cup T_2,p}
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    Here, $C_{{\PF},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
-\end{lemma}
-% \begin{remark}
-%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
-% \end{remark}
-\begin{proof}
-    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
-    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
-    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
-    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
-    be affine transformations that the origin to $v_0$, that map each unit vector $e_{i}$ to $v_{i}$ for $i = 1, \dots, n-1$,
-    and that satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
-    Write $\hat U := \Delta_1 \cup \Delta_2$.
-    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
-
-    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
-    We observe 
-%     \begin{align*}
-%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-%         &=
-%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-%         +
-%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-%         ,
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-%         &\leq 
-%         |\det(\Jacobian \varphi_1^{-1})|
-%         \cdot \matnorm{ \Jacobian \varphi_1 }^{p}
-%         \cdot 
-%         \| \nabla u \|_{L^{p}(T_1)}^{p}
-%         ,
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-%         &\leq 
-%         |\det(\Jacobian \varphi_2^{-1})|
-%         \cdot \matnorm{ \Jacobian \varphi_2 }^{p}
-%         \cdot 
-%         \| \nabla u \|_{L^{p}(T_2)}^{p}
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-%         &\leq 
-%         \max\left( 
-%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \matnorm{ \Jacobian \varphi_1 }^{p}
-%             ,
-%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \matnorm{ \Jacobian \varphi_2 }^{p}
-%         \right)
-%         \| \nabla u \|_{L^{p}(U)}^{p}
-%         .
-%     \end{align*}
-%     Hence 
-    \begin{align*}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}
-        &\leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_1 }
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_2 }
-        \right)
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    Notice that $\hat U$ has diameter $2$ and is (crucially) convex. 
-    Thus, due to Poincar\'e--Friedrichs inequality~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
-    \begin{align*}
-        \| \hat w \|_{L^{p}(\hat U)}
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}
-        .
-    \end{align*}
-    Next, setting $w := \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(U)}
-        \leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \| \hat w \|_{L^{p}(\hat U)}
-        .
-    \end{align*}
-    For both $i = 1,2$, we now recall the well-known equation $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$, 
-    % which we have already employed in~\eqref{equation:Hong_Pan}, 
-    and the estimate $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$, which is given in Lemma~\ref{lemma:measurerelationships}. We conclude the desired result.
-\begin{comment}
-    % DONE: that abbreviation is to close to the Jacobian / total derivative 
-    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
-    \begin{align*}
-        \| w \|_{L^{p}(U)}
-        &\leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \\&\qquad 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} 
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} 
-        \right)
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \\&\qquad 
-        \min\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)| 
-        \right)^{-\frac 1 p} 
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \max\left( 
-            \frac{ |\det(\Jacobian \varphi_1)| }{ |\det(\Jacobian \varphi_2)| }
-            ,
-            \frac{ |\det(\Jacobian \varphi_2)| }{ |\det(\Jacobian \varphi_1)| }
-        \right)^{\frac 1 p}
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{\PF,{\rm EFNT},p}
-        \max\left( 
-            \frac{ \vol(T_1) }{ \vol(T_2) }
-            ,
-            \frac{ \vol(T_2) }{ \vol(T_1) }
-        \right)^{\frac 1 p}
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    This gives the desired result. 
-\end{comment}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The main result of this section constructs a potential and gives an upper bound for the Poincar\'e--Friedrichs constant.  
-It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.
-The procedure serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-
-Two different variations of underlying idea are analyzed; the resulting estimates are only slightly different.  
-On the one hand, we extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that simplex.
-This auxiliary problem will be subject to partial boundary conditions.
-% We present an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex}, where we compute an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
-% We emphasize that this construction of potentials and bounding of Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-On the other hand, we can instead cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
-Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece by adjusting the local constants of integration.
-Both estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
-
-\begin{comment}
-For the remainder of this section, the following combinatorial notion of triangulations is used. 
-Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
-a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
-where for each index $1 \leq m \leq M$ we have a fixed index $0 \leq \iota(m) \leq m-1$ 
-such that $T_{m}$ and $T_{\iota(m)}$ are face-neighboring.
-We call $T_{\iota(m)}$ the \emph{precursor} of $T_{m}$ within the spanning tree. 
-The reader is referred to Figure~\ref{figure:spanningtree} for an illustration. 
-\end{comment}
-
-\begin{figure}[t]
-\begin{center}
-\begin{tikzpicture}[rotate=-60]
-    \coordinate (A) at (0,0);
-    \coordinate (B) at (2,0);
-    \coordinate (C) at (1,1.5);
-    \coordinate (D) at (3,1.5); 
-    \coordinate (E) at (3,3); 
-    \coordinate (F) at (4,0.25); 
-    \coordinate (X) at (1,-1.5);
-    \coordinate (Y) at (3,-1.5); 
-    \coordinate (T) at (5,2);
-
-    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
-    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
-    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
-    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
-    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
-    \coordinate (CentroidDFT) at ($(D)!0.3333!(F)!0.3333!(T)$);
-    \coordinate (CentroidDET) at ($(D)!0.3333!(E)!0.3333!(T)$);
-
-    \draw[fill=gray!10] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!10] (B) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!10] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!10] (B) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (A) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (E) -- cycle;
-
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
-    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET);
-
-%     \node at (A) [below left] {$A$};
-%     \node at (B) [below right] {$B$};
-%     \node at (C) [above] {$C$};
-%     \node at (D) [above right] {$D$};
-%     \node at (T) [above right] {$T$};
-\end{tikzpicture}
-\end{center}
-\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
-\label{figure:spanningtree}
-\end{figure}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\calT$ be a face-connected $n$-dimensional finite triangulation. 
-    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
-    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
-    Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
-    and satisfying the following estimates:
-    there exists an $n$-simplex $T_0 \in \calT$ with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    and whenever $T_0, T_1, \dots, T_M$ is a face path,
-    then for all $1 \leq m \leq$ we the following recursive estimates:
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{\iota(m)})} 
-        + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \left( 
-%             \| \nabla u \|_{L^{p}(T_{m})} 
-%             + 
-%             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-%             \| \nabla u \|_{L^{p}(T_{\iota(m)})}
-%         \right)
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
-        C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
-        ,
-        \\
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{{\iota(m)}})}
-        +
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Minako_{F_m},p} 
-        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
-        . 
-    \end{align*}
-    Here, for any $1 \leq m \leq M$, let $F_m = T_m \cap T_{m-1}$.
-\end{theorem}
-
-\begin{proof}
-    Let $u \in W^{1,p}(\Omega)$. 
-    We start with the Poincar\'e--Friedrichs inequality on the first simplex $T_{0}$. 
-    There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    In particular, $c_{0} := w_0 - u$ is a constant function. 
-    We then define 
-    \begin{align*}
-        w := u + c_0
-        .
-    \end{align*} 
-    Clearly, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
-    By construction $w_{|T_{0}} = w_0$. 
-    We verify that $w$ satisfies the two desired recursive estimates.
-    Suppose that $T_0, T_1, \dots, T_M$ is a face path in $\calT$
-    and that $1 \leq m \leq M$.
-    Recall that we write $F_m := T_m \cap T_{m-1}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$.
-
-    We proceed with showing the first recursive estimate. 
-    We define $w'_{m} := w_{|T_{m-1}} \circ \Xi \in W^{1,p}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
-    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
-    \begin{align*}
-        \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{|T_{m-1}}
-        .
-    \end{align*}
-    We now define $w''_{m} \in W^{1,p}(T_{m})$ via 
-    \begin{align}\label{equation:w''}
-        w''_{m} 
-        := 
-%         u_{|T_{m}} - w'_{m} + c_0 
-%         = 
-        w_{|T_{m}} - w'_{m} = u_{|T_{m}} - u_{|T_{m-1}} \circ \Xi.
-    \end{align}
-    We crucially note that $w''_{m}$ is trace-free along $F_{m}$ since
-    \begin{align*}
-        \trace_{F_{m}} w''_{m} 
-        = 
-        \trace_{F_{m}} \left( 
-            w_{|T_{m}} - w'_{m} 
-        \right) 
-        =
-        \trace_{F_{m}} w_{|T_{m}}
-        -
-        \trace_{F_{m}} w_{|T_{m-1}}
-        =
-        \trace_{F_{m}} u_{|T_{m}}
-        -
-        \trace_{F_{m}} u_{|T_{m-1}}
-%         = 
-%         \trace_{F_{m}} \left( 
-%             u_{|T_{m}} - w'_{m} + c_0 
-%         \right) 
-%         = 
-%         \trace_{F_{m}} \left( 
-%             u_{|T_{m-1}} - w_{|T_{m-1}} + c_0 
-%         \right) 
-        = 0.
-    \end{align*}
-    We apply Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''}, which gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla w \|_{L^{p}(T_{m})} 
-            + 
-            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        \leq 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{m})} 
-            + 
-            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        .
-    \end{align*}
-    Using Lemma~\ref{lemma:volumecomparison} as well as Definitions~\eqref{math:volumeratio} and~\eqref{math:reflectionmeasure}, we find 
-    \begin{align*}
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
-        &
-        \leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \matnorm{ \Jacobian \Xi }
-        \| \nabla w \|_{L^{p}(T_{m-1})}
-        \\&
-        \leq 
-        \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla w \|_{L^{p}(T_{m-1})}
-        \\&
-        =
-        \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla u \|_{L^{p}(T_{m-1})}
-        .
-    \end{align*}
-    % The second expression in~\eqref{equation:w''} shows $w_{|T_{m}} = w''_{m} + w'_{m}$. We finally find 
-    Since $w_{|T_{m}} = w''_{m} + w'_{m}$, we finally find 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{m})} 
-            + 
-            \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-        \| \nabla u \|_{L^{p}(T_{m-1})}
-        \right). 
-    \end{align*}
-    We now use H\"older's inequality. 
-    Therefrom, the first recursive estimate follows.
-
-    Now we discuss the second recursive estimate. 
-    Suppose again that $1 \leq m \leq M$. 
-    Recall that we write $\Minako_{F_m} := T_m \cup T_{m-1}$. 
-    We use the Poincar\'e--Friedrichs inequality over $\Minako_{F_{m}}$,
-    as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
-    to find $w_{F_m} \in W^{1,p}(\Minako_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Minako_{F_m}$ and 
-    \begin{align}\label{math:wFm_inequality}
-        \| w_{F_m} \|_{L^{p}(\Minako_{F_m})} \leq C_{{\PF},\Minako_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Minako_{F_m})}.
-    \end{align}
-%     \cye{Since $\nabla (w_{|\Minako_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Minako_{F_m}})$, 
-    We can define the constant
-    \begin{align*}
-    c_{m} := w_{|\Minako_{F_m}} - w_{F_{m}}.
-    \end{align*}
-    We now observe that 
-    \begin{gather*}
-        \| w \|_{L^{p}(T_m)}
-        \leq 
-        \| w_{F_m} \|_{L^{p}(T_m)}
-        +
-        \| c_{m} \|_{L^{p}(T_m)},
-        \\
-        \| c_{m} \|_{L^{p}(T_m)}
-        = 
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| c_{m} \|_{L^{p}(T_{{m-1}})},
-        \\ 
-        \| c_{m} \|_{L^{p}(T_{{m-1}})}
-        \leq 
-        \| w \|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
-        .
-    \end{gather*}
-    In combination, 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        &
-        \leq 
-        \| w_{F_m} \|_{L^{p}(T_m)}
-        \\&\qquad 
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{m-1}})}
-        .
-    \end{align*}
-    We sum the two integrals of $w_{F_m}$. 
-    % 
-    % 1/q = 1 - 1/p = (p-1)/p 
-    When $1 < p < \infty$, recalling the complementary exponent $q = p/(p-1) \in (1,\infty)$, 
-    we use H\"older's inequality to verify 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \left( 
-            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
-            +
-            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
-        \right)^{\frac 1 p}
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{m-1}})}
-        \\&\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \| w_{F_{m}} \|_{L^{p}(\Minako_{F_m})} 
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{m-1}})}
-        .
-    \end{align*}
-    In the special case $p=1$,
-    \begin{align*}
-        \| w\|_{L^{1}(T_m)}
-        \leq 
-        \max\left(
-            1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
-        \right)
-        \| w_{F_m} \|_{L^{1}(\Minako_{F_m})}
-        +
-        \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-        \| w \|_{L^{1}(T_{{m-1}})}
-        .
-    \end{align*}
-    In the limit case $p=\infty$, 
-    \begin{align*}
-        \| w \|_{L^{\infty}(T_m)}
-        \leq 
-        2
-        \| w_{F_m} \|_{L^{\infty}(\Minako_{F_m})}
-        +
-        \| w \|_{L^{\infty}(T_{{m-1}})}
-        .
-    \end{align*}
-    The local inequality~\eqref{math:wFm_inequality} now provides the second recursive estimate. 
-    The proof is complete.
-\end{proof}
-
-\begin{corollary}
-    Under the assumptions of Theorem~\ref{theorem:poincarefriedrichsestimate:grad},
-    whenever $T_0, T_1, \dots, T_m$ is a face-path of $n$-simplices in $\calT$,
-    we have 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \sum_{\ell=1}^{m} 
-        \volumeratio^{\frac{m-\ell}{p}}
-        \min\left( 
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Minako_{F_\ell},p} 
-        ,
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
-        C_{\PF,T_{\ell},F_{\ell},p} 
-        \right)
-        \| \nabla u \|_{L^{p}(\Minako_{F_\ell})}
-        \\&
-        \qquad 
-        \qquad 
-        +
-        \volumeratio^{\frac m p}
-        C_{{\PF},T_{0},p}
-        \| \nabla u \|_{L^{p}(T_{0})}
-        .
-    \end{align*}
-\end{corollary}
-\begin{proof}
-    This follows by repeated application of the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-\end{proof}
-
-\begin{remark}
-    The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases.
-We hence target its use to local patches (stars), in particular non-convex boundary stars.
-The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ \Minako_m \}$ with a face-connected path.
-The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$.
-This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant.
-\end{remark}
-
-% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
-% Lemma 5.5
-
-\section{Review of vector calculus and exterior calculus}\label{section:calculus}
-
-% We discuss the Sobolev spaces of vector calculus and exterior calculus 
-% with particular emphasis on their transformation behavior. 
-% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-% TODO: Fuse these two paragraphs
-
-We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
-
-Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
-
-\subsection{Vector calculus}
-
-\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
-\begin{gather*}
-    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-We recall $L^{p}(\Omega)$, the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
-In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
-\begin{gather*}
-    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
-\begin{gather*}
-    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \\ 
-    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}
-
-We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
-$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
-We also introduce 
-$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
-for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
-\begin{subequations}\label{eq_definition_piola}
-\begin{align*}
-    \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
-    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
-    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
-\end{align*}
-\end{subequations}
-Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
-These transformations are invertible. 
-Bounds on the Lebesgue norms will follow from a more general result below. 
-We use the commutativity relations 
-\begin{subequations}\label{eq_piola_commute}
-\begin{align}
-    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
-    \\
-    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
-\end{align}
-\end{subequations}
-where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
-We summarize this as a commuting diagram:
-\begin{align*}
-    \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
-        \\
-        @VV{\phi^{\grad}}V 
-        @VV{\phi^{\curl}}V 
-        @VV{\phi^{\divergence}}V 
-        @VV{\phi^{\rm b}}V 
-        \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
-    \end{CD}
-\end{align*}
-
-\begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
-\end{remark}
-
-\subsection{Exterior calculus}
-
-%\cye{We now move to} exterior calculus. 
-%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
-
-\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
-Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
-Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
-if 
-\begin{gather*} 
-    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
-    = 
-    \text{sign}(\pi) 
-    u( v_1, v_2, \ldots, v_k ) 
-\end{gather*}
-for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
-By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
-Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
-
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra
-(see~Chapter 14 in \cite{lee2012smooth}). 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
-their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
-defined by the formula 
-\begin{gather*}
-    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
-    = 
-    \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\end{gather*}
-for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
-The exterior product is bilinear and associative, and satisfies 
-\begin{align*}
-    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
-    \quad 
-    \forall u_1 \in \Alt^{k}(V),
-    \quad 
-    \forall u_2 \in \Alt^{l}(V).
-\end{align*}
-The interior product is in some sense dual to the exterior product. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define the interior product $v \lrcorner u \in \Alt^{k-1}(V)$ via 
-\begin{align*}
-    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
-    \quad 
-    \forall v_1, v_2, \ldots, v_{k-1} \in V.
-\end{align*}
-
-We employ the exterior algebra only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
-Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
-Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
-This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
-To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$, where $k, n \in \bbZ$, 
-and introduce the basic $k$-alternators 
-\begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
-    \quad 
-    \forall \sigma \in \Sigma(k,n). 
-\end{align*}
-These define a basis of $\Alt^{k}(\bbR^{n})$.
-Note that 
-$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
-In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
-
-We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
-which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
-The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
-
-\subsection{Smooth differential forms}
-
-We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
-which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
-Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather*}
-    \omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather*}
-where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
-\begin{gather*}
-    \cartan\omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \sum_{j=1}^{n} 
-    \frac{\partial \omega_{\sigma}}{\partial x^j} 
-    \, \cartanx^j \wedge 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\end{gather*}
-The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
-Moreover, it satisfies the Leibniz rule:
-\begin{gather*} 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
-\end{gather*}
-
-\subsection{Sobolev spaces of differential forms}
-
-Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
-We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
-such that its pointwise norm is $p$-integrable. 
-The exterior derivative is defined in the sense of distributions and we introduce 
-\begin{gather*}
-    W^{p}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
-    .
-\end{gather*}
-We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
-% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
-% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
-Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
-Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
-whose support lies in the open ball $B_r(x)$
-we have the integration by parts formula
-\begin{align*}
-    \int_{B_r(x)} \cartan v \wedge \tilde u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
-    .
-\end{align*}
-If that condition is satisfied, we also write 
-\begin{align*}
-    \trace_{\Gamma} u = 0
-    .
-\end{align*}
-Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
-Lastly, we introduce the closed subspaces 
-\begin{gather*}
-    W^{p}_{0}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
-    .
-\end{gather*}
-% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
-This is a closed subspace.
-We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
-We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega)$.
-
-\subsection{Transformations by bi-Lipschitz mappings}
-
-We are interested in transformations of Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
-\begin{align} \label{equation:pullback}
-    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    := 
-    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\end{align}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
-We cite an explicit transformation estimate~ (see~\cite{licht2019smoothed}) and a special estimate when the transformation is affine (see~Corollary~6~\cite{stern2013lp}).
-
-\begin{proposition}\label{proposition:pullbackestimate}
-    Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
-    Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
-    Then 
-    \begin{align}
-        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-        &\leq 
-        \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-        .
-    \end{align}
-    If $\phi$ is affine and $\sigma_1 \geq \sigma_2 \geq \dots \geq \sigma_n$ are the singular values of $\Jacobian\phi$, then 
-    \begin{align}
-        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-        &\leq 
-        \sigma_1 \sigma_2 \cdots \sigma_k \cdot 
-        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-        .
-    \end{align}
-\end{proposition}
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms is in correspondence with classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \begin{gather*}
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\, ,}
-    \end{gather*}
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant over the other in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \begin{gather*} 
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\,.}
-    \end{gather*}
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
-
-\subsection{Some approximation properties}
-
-We finally review a few approximation properties. 
-Let $\mollifier$ be a non-negative scalar function whose integral equals one and whose support lies in the unit ball around the origin.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\begin{lemma}
-%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
-%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
-%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
-\end{lemma}
-
-% \begin{lemma} % TODO: possibly useful
-%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-% \end{lemma}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$. 
-	\mwl{If $\Omega$ is convex and $u \in W^{p}\Lambda^{n}(\Omega)$ has average zero, 
-	then $u$ is the limit in $W^{p}\Lambda^{k}(\Omega)$ of smooth compactly supported $n$-forms with average zero.}
-\end{lemma}
-\begin{proof}
-    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
-    By the dominated convergence theorem and because $u$ has a weak derivative,
-    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
-    \begin{align*}
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
-        &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
-        = 
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
-        .
-    \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
-
-    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
-    Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega) \subseteq W^{p}_{0}\Lambda^{k}(\Omega)$ 
-    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
-    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
-    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
-    The desired result follows.
-
-	Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently msall radius. The proof is complete. 
-\end{proof}
-
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
-
-% We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-% We already know the optimal constants for the gradient operator over convex domains,
-% and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-% We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$. 
-% % 
-% We bound the norms of regularized potential operators for the exterior derivative over convex domains.
-% We solve this for two special cases:
-
-We now develop bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-Here, we consider two special cases: 
-either the $L^{p}$ de~Rham complex without boundary conditions, or the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their extensive work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our goal are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
-
-%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
-
-% \todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
-
-\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
-
-We begin with introducing the Costabel-McIntosh kernel.
-For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{math:mainkernel}
-  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
-  ,
-\end{equation}
-where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
-we then define the integral operators
-\begin{align*}
-  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
-  \\
-  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align*}
-We call $\Poinc_{\mia}$ the \emph{Poincar\'e operator} and $\Bogov_{\mia}$ the \emph{Bogovski\u{\i} operator}.
-
-We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually converge. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
-    .
-\end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
-\end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
-
-We begin with the Poincar\'e operator. 
-Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
-We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    &
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
-    \\&
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    ,
-\end{align*}
-where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
-We compute 
-\begin{align}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
-    \label{equation:A_Poinc}
-    .
-\end{align}
-Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{n-\mia}$. 
-In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-%
-
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
-
-We analyze the Bogovski\u{\i} potential operator by similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$.
-Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\mia} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
-    .
-\end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-%     .
-% \end{align*}
-% We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
-    \label{equation:A_Bogov}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{\mia-1}$. 
-In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
-that is, the reconstructed potential has support contained within $\overline\Omega$. 
-\\
-
-\subsection{Interaction of potential operators with the exterior derivative}
-
-More properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
-leading to 
-\begin{align*}
-    \Bogov_{\mia} u(x) 
-    &= 
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
-    \chi_{\Omega}\left(y+t(x-y)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-% We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
-% 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    ,
-    \\
-    \Bogov_{\mia,a} u(x) 
-    &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    .
-\end{align*}
-By definition,
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    =
-    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
-    \quad 
-    \Bogov_{\mia} u(x) 
-    =
-    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
-    .
-\end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.
-
-\mwl{Some of the notation here needs to be simplified or introducted: Sigma for all integers, possily empty. remove or add indices}
-
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\mia,a} u(x) 
-    &= 
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    =
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    ,
-\end{align*}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
-    \,\cartanx^{\sigma} 
-    \\&\qquad 
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    %\sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    \cartan \Poinc_{\mia,a} u(x)
-    +
-    \Poinc_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \left( u_{\sigma}(x) - 0^k u_{\sigma}(a) \right) \,\cartanx^{\sigma}
-    .
-\end{align*}
-We conclude that, 
-\begin{align*}
-    u(x) &= \cartan \Poinc_{0,a} u(x) - u(a)
-    \\
-    u(x) &= \cartan \Poinc_{\mia,a} u(x) + \Poinc_{\mia+1,a} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) &= \cartan \Poinc_{0} u(x) - \vol(\Omega)^{-1} \int_\Omega u(a)
-    \\
-    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
-
-The discussion for the Bogovski\u{\i} operator is analogous. 
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \minus 
-    \Bogov_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \minus 
-    \cartan \Bogov_{\mia,a} u(x) 
-    &= 
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    =
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    ,
-\end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \minus 
-    \Bogov_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    %\sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    - 
-    \cartan \Bogov_{\mia,a} u(x)
-    -
-    \Bogov_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^{\infty} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^{\infty} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^{\infty} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
-    \int_{1}^{\infty} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma} \,dt 
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^{\infty} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    =
-    -
-	\sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    -u(x)
-    .
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align*}\label{math:hodgedecomposition:bogov}
-    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n.
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
-We remark that the apparent structural difference between \eqref{math:hodgedecomposition:poinc} and \eqref{math:hodgedecomposition:bogov} is due to our assumption that $u$ extends to a smooth function with support within $\overline\Omega$.
-This structural difference will disappear soon when we discuss operators between Sobolev spaces of differential forms.
-
-\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
-
-We are now state the main results of this section. 
-% We are in the position to establish the main results of this section.
-Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
-The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
-However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
-namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$.
-
-\begin{theorem}\label{theorem:PF_EC}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$ and $\cartan u = 0$, 
-    then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$ and $\int_\Omega u = 0$ in the case $k=n$, 
-    then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
-
-    \mwl{
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
-    }
-\end{theorem}
-
-% \todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
-Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
-
-\begin{proof}
-    It suffices to discuss the case $1 \leq p < \infty$, because the domain is bounded 
-    and taking the limit will then imply the inequality with $p = \infty$. 
-    The potential operators are linear and satisfy the stated bounds over $C^{\infty}_{c}\Alt^{\mia}(\Omega)$,
-    which is a dense subspace of $L^{p}\Alt^{\mia}(\Omega)$.
-
-    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$ and $\cartan u = 0$. 
-    We write $w := \Poinc_{\mia  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-
-    \color{blue}
-    Let $u \in W^{p}_{ }\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$ and set $w = \Poinc_{\mia} \cartan u$.
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge \cartan u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge w
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    \color{black}
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\mia} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    This completes the proof.
-
-    \color{blue}
-    Let $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$ and set $w = \Bogov_{\mia} \cartan u$.
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge \cartan u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge w
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    \color{black}
-\end{proof}
-
-% DONE: Density of C infty mit oder ohne c.
-
-% \begin{remark}
-%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-%     while they are increasing for the Bogovski\u{\i} operator.
-%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
-% \end{remark}
-
-These constants are generally not optimal. 
-For example, when $p=2$ and when only the divergence is considered, 
-we have the following improved estimate.
-
-\begin{lemma}\label{lemma:PFfordivergence}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
-    \begin{align*}
-        \| \bfw \|_{L^{2}(\Omega)} 
-        \leq 
-        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This is a reduction to the Friedrichs inequality. 
-    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
-    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
-    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
-    which has the same smallest singular value. 
-\end{proof}
-
-\begin{remark} \label{remark:reg_Poinc_Bog}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % TODO: are these paragraphs in the introduction now?
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-
-    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
-
-    {\color{blue}
-    Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Their operators are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight; this proves boundedness of the operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
-    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
-    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
-    This had not been established yet, to the best of our knowledge. 
-    }
-\end{remark}
-
-\section{Shellable triangulations of manifolds}\label{section:advancedtriangulations}
-
-We return to the theory of triangulations,
-as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulate manifolds. 
-Our particular interest are manifold triangulations that are \emph{shellable}.
-Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
-Local patches (stars) within triangulations of dimension two and three are examples of such shellable complexes. 
-The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures} are our main references for this section. 
-We also refer to Lee's monograph~\cite{lee2011topological} for any further background on manifolds.
-
-\begin{figure}[h]
-\centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
-\caption{A manifold triangulation (left) and not a manifold triangulation (right)}
-\label{figure:not_manifold_triang}
-\end{figure}
-
-\subsection{Triangulations of manifolds}
-
-We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
-We recall that this means that for every $x \in \underlying{\calT}$
-% there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
-there exists an open neighborhood $U(x) \subseteq \underlying{\calT}$ and an embedding $\phi : U(x) \rightarrow \bbR^{n}$
-such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the open unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| < 1 \}$
-or onto the half-ball $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
-In the former case, $x$ is called an \emph{interior point}, and in the latter case $x$ is called a \emph{boundary point}. 
-Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional. 
-An example of a manifold triangulation and an example which is not a manifold triangulation are given in Figure~\ref{figure:not_manifold_triang}.
-
-The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball\mwl{, and we sometimes call this a \textit{$n$-disk} triangulation}.
-An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
-
-We know that any manifold $\calM$ has got a topological boundary $\partial\calM$, possibly empty. 
-If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$. 
-We gather a few helpful observations on how these notions relate to triangulations.
-While the reader might deem them obvious, we nevertheless include proofs.
-
-\begin{lemma}\label{lemma:boundarysimplices}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying set is a manifold $\calM$. 
-    \begin{itemize}
-        \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
-        \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
-        \item The simplices contained in the boundary constitute a triangulation of the boundary.
-        % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    We prove these statements in several steps.
-    \begin{enumerate}
-    \item 
-    Let $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
-    We will use the following fact:\footnote{To see this, one easily constructs a continuous deformation of $\calM$ into itself to move any chosen point on $S$ to any other chosen point on $S$.} if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$.
-    Since the boundary $\partial \calM$ is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
-
-    \item 
-    We recall an auxiliary result.
-    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    As a consequence of the Jordan--Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
-    we know that $Y \setminus X$ has got two connected components.
-
-    % \item 
-    % We prove an auxiliary result. 
-    % Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    % The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
-    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the north pole without loss of generality, and a stereographic projection, 
-    % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    % As a consequence of the Jordan--Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
-    % and thus $Y \setminus X$ has got two connected components.
-
-    \item
-    Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
-    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ 
-    homeomorphic to an $n$-dimensional ball 
-    so small that its closure $\overline{B_F}$ only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
-    Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
-    The intersection of any two of them is $F$, but their interiors are disjoint because otherwise they would coincide.
-
-    If $z_F$ is an interior point of $\calM$, 
-    then it follows by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
-    Consider $X = F \cap \partial \mathring B_F$.
-    If $n=1$, then $X$ is empty and $\partial \mathring B_F$ has $K$ distinct connected components. 
-    If $n > 1$, then $X$ is homeomorphic to a sphere of dimension $n-2$
-    and again $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
-    But by the auxiliary result above, $K = 2$. 
-    We conclude that $F$ is contained in two $n$-simplices of $\calT$.
-
-    Consider the case that $z_F$ lies on the boundary of $\calM$ and suppose that $F$ is contained in $K$ distinct $n$-simplices of $\calT$.
-    By adding at least one dimension, we can double\footnote{The reader is referred to Lee's textbook~\cite{lee2012smooth} for more background and the technicalities.} the manifold $\calM$ along the boundary and obtain the doubled manifold $\calM'$.
-    Similarly, we can construct a doubling of the triangulation $\calT'$ such that $F$ is contained in exactly $2K$ distinct $n$-simplices of $\calT'$. 
-    We know that $\calM'$ is a manifold without boundary, and hence $F$ is an interior simplex of $\calT'$.
-    This implies $K=1$.
-    So any boundary face can only be contained in one single $n$-simplex.
-
-    \item
-    Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
-    Every $x \in \calM$ is an inner point of some simplex $S \in \calT$. 
-    If $x \in \partial \calM$ is a boundary point, then $S$ must be a boundary simplex, 
-    so the boundary simplices triangulate all of $\partial \calM$.
-    \end{enumerate}
-    All desired results are thus proven. 
-\end{proof}
-
-Suppose that $\calT$ is an $n$-dimensional simplicial complex that triangulates a manifold. 
-Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
-% The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
-All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
-We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
-% We see that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
-% Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
-% Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
-% The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space.
-
-We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. This topics is surprisingly non-trivial and 
-we gather some results that are hard to find in the literature.
-
-We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{combinatorial}
-if for every vertex $V \in \calT$ the local star $\patch_{\calT}(V)$ is a simplicial ball of dimension $n$.
-
-\begin{lemma}\label{lemma:startopology}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    Suppose that $1 \leq n \leq 3$. Then the following holds:
-    \begin{itemize}
-        \item
-        If $S \in \calT$ is an inner simplex, 
-        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
-        \item
-        If $S \in \calT$ is a boundary subsimplex, 
-        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    The lemma is obvious if $n = 1$, so we assume $n \geq 2$ in what follows. 
-    We prove these statements in several steps. 
-    The reader is assumed to have some background in topology. 
-    \begin{enumerate}
-    \item 
-    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{S}$, and dimension $k$.
-    Let $\calS := \patch_{\calT}(S)$ be its star. 
-    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
-    has vertices $v_0, v_1, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$. 
-    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
-    $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
-%     \begin{align*}
-%         $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
-%     \end{align*}
-    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
-    that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS' = \patch_{\calS'}(z_{S})$. 
-    In particular, $z_{S}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
-    So it remains to study the topology of vertex stars.
-
-    \item 
-    Suppose that $2 \leq n \leq 3$ and that $\calM$ is a manifold without boundary. 
-    Under these assumptions, 
-    as explained in the proof of Theorem~1 in \cite{Siebenmann1979},
-    the set $\carapace(V)$ is a triangulation of a sphere of dimension $n-1$ for any inner vertex $V$. 
-    There exists a homeomorphism from the closed cone of $\underlying{\carapace(V)}$ onto the local star $\underlying{\patch_{\calT}(V)}$.
-    But then that closed cone and hence $\underlying{\patch_{\calT}(V)}$ are homeomorphic to an $n$-dimensional ball.
-
-    \item 
-    If $2 \leq n \leq 3$ and $\calM$ has a non-empty boundary, then we use an approach as in the proof of Lemma~\ref{lemma:boundarysimplices}: 
-    we let $\calM'$ denote the doubling of the manifold and $\calT'$ be the doubling of the triangulation $\calT$. 
-    Let $V \in \calT$ be a vertex. 
-    If $V$ is an inner vertex of $\calT$, then $\carapace(V) \subseteq \calT \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT \subseteq \calT'$ triangulates a ball of dimension $n$, as discussed above.
-    If $V$ is a boundary vertex of $\calT$, then it is an inner vertex of $\calT'$,
-    and so $\carapace_{\calT}(V) \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT'$ triangulates a ball of dimension $n$.
-    We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$.
-    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere. 
-    It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
-    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.
-
-%     Suppose that $S = \{z\}$ is a singleton simplex. 
-%     For $\delta > 0$ small enough, 
-%     \begin{align*}
-%         B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
-%         \quad 
-%         S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
-%     \end{align*}
-%     are compactly contained subsets of $|\patch_{\calT}(S)|$.
-%     For each simplex $K \in \patch_{\calT}(S)$ that contains the vertex $z$ and which has the opposite face $F_K$, 
-%     we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
-%     such that 
-%     $\phi_{K}(z) = z$, 
-%     such that 
-%     $\phi_{K}( K \cap S_{\delta}(z) ) = F_{K}$,
-%     such that 
-%     for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$,
-%     and such that 
-%     $\phi_{K}$ maps $[0,1]\cdot v$ linearly into $\bbR \cdot v$. 
-%     This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$. 
-%     Moreover, one easily verifies that $\phi$ is bi-Lipschitz.
-%     %     For $\delta > 0$ small enough, $B_{\delta}(z)$ is homeomorphic to the unit ball and that homeomorphism maps $S_{\delta}(z)$ onto the unit sphere. 
-%     \item 
-%     One sees that $\phi$ defines a mapping from the closed 
-%     homeomorphism between cone of link and ball 
-%     
-%     If $z$ is an inner vertex of $\calS'$, 
-%     then the boundary simplices of $\calS'$,
-%     which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
-%     
-%     Now suppose that $z$ is a boundary vertex of $\calS'$,
-%     which is the case if and only if $S$ is a boundary simplex. 
-%     Write 
-%     \[
-%         B_{H} = \left\{ x \in B_1(0) \suchthat* x_1 \leq 0 \right\},
-%         \quad 
-%         S_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 \leq 0 \right\}.
-%         \quad 
-%         D_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
-%     \]
-%     Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $D_H$,
-%     and which maps $z$ to the origin. 
-%         %
-%     It follows that $\phi'$ maps the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$ onto $S_H$.
-%         %
-%     Assuming that $\delta$ is small enough once more, 
-%     we now verify that $\phi^{-1}$ maps $|\carapace(S)|$ onto $S_{\delta}(z) \cap |\patch_{\calT}(S)|$.
-%     The latter equals the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$.
-%     It follows that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
-    % We let $\calM'$ be the doubling of the manifold and let $\calT'$ be the doubling of the present triangulation;
-    % we refer to Lee's textbook~\cite{lee2011topological} for details. 
-    % The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
-    % and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. 
-    % The underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ along $\phi$.
-    % The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
-    % and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. 
-    % Notice that 
-    % \begin{align*}
-    %     \partial\left( { B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)| \right)
-    %     =
-    %     S_{\delta}(z) \cap |\patch_{\calT}(S)|
-    %     \cup 
-    %     \overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|
-    %     .
-    % \end{align*}
-    % Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere.
-Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
-    % But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
-    \end{enumerate}
-    All relevant results are proven. 
-\end{proof}
-
-\begin{lemma}\label{lemma:connectivity}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    If the underlying space of $\calT$ is connected, then $\calT$ is face-connected.
-\end{lemma}
-\begin{proof}
-    We first show that each vertex star is face-connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are face-connected. 
-    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already face-connected if all simplicial $n$-balls and $n$-spheres are face-connected.
-    The induction argument implies that each vertex star in $\calT$ is face-connected.
-
-    If the underlying space $\underlying{\calT}$ is connected, 
-    then we easily see that the union of the $1$-simplices is path-connected.
-    Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
-    As each vertex star is face-connected, 
-    we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
-    is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-    This just means that $\calT$ is face-connected. 
-\end{proof}
-
-\begin{remark}
-    Triangulations with the property that all vertex stars are homeomorphic to a ball are also called \emph{combinatorial} \cite[Section~1]{Bagchi2005}.
-    All manifolds of dimension up to three admit smooth structures and smooth manifolds admit combinatorial triangulations. 
-    There are triangulations of manifolds in dimension higher than $3$ where not every vertex star is homeomorphic to a ball.
-
-    Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
-    Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
-    % Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. ~\cite{todo}
-    We therefore are not in pursuit of any easy combinatorial property that indicates whether a simplicial complex (without any further specific assumptions) triangulates a manifold.
-
-    Conversely, not all topological manifolds, even if compact, can be described as a triangulation. 
-    Such manifolds, some even compact and simply-connected, appear in dimension four and higher~\cite{akbulut2014casson}.
-%     For each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. 
-\end{remark}
-
-% 3. Shellability 
-\subsection{Shellable simplicial complexes}\label{subsection:shellability}
-
-The notions of shelling and shellable triangulation have been discussed widely in combinatorial topology and polytopal theory. 
-Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation of a manifold.
-This forces the intermediate triangulations to be particularly well-shaped. 
-We build upon the notion of shelling as introduced in~\cite[Definition 8.1]{ziegler1995lectures},
-where our definition of shelling is equivalent to the notion of the shellings of simplicial complexes, see also~\cite[Remark~8.3]{ziegler1995lectures}.
-
-% \mwl{Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-% by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-% the gluing interface is a triangulated submanifold of the boundary. 
-% This forces the intermediate triangulations to be particularly well-shaped. 
-% We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-%It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, as this enables the inductive method of proof.
-% }
-
-Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
-For any enumeration, we call 
-\begin{align*}
-    \Gamma_m 
-    := 
-    \big( 
-        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
-    \big) 
-    \cap 
-    T_{m+1}
-\end{align*}
-the $m$-th \textit{interface set}. 
-% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface set $\Gamma_m$ is a triangulated manifold of dimension $n-1$.
-
-\begin{remark}
-    We interpret a shelling as the construction of a triangulation 
-    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
-    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
-\end{remark}
-\begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
-    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
-    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
-\end{remark}
-
-The reason of our interest in shellable simplicial complexes is that they can be constructed via successive adhesion of simplices.
-The resulting succession of simplicial complexes consists of simplicial balls or spheres.
-
-\begin{lemma}\label{lemma:shell_triang_man}
-    Let $\calT$ be an $n$-dimensional simplicial complex 
-    with a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$,
-    such that each simplex of dimension $n-1$ is contained in at most two simplices. 
-    % DONE: what is non-branching?
-    Then
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}
-    $$ 
-    is a triangulated manifold with boundary for all $0 \leq m \leq M$.
-    % 
-    In particular, $X_{m}$ is a topological $n$-ball when $m < M$, 
-    and 
-    $X_{M}$ is either a topological $n$-ball or topological $n$-sphere. 
-\end{lemma}
-\begin{proof}  
-    We prove this claim by induction. 
-    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. Let $1 \leq m \leq M$ and suppose that 
-    \begin{align*}
-        X_{m-1} := T_{0} \cup T_{1} \cup \dots \cup T_{m-1}
-    \end{align*}
-    is a topological $n$-ball. Let $T_{m}$ is the next $n$-simplex in the shelling.
-    By definition, $\Gamma_{m} := X_{m-1} \cap T_{m}$ is a submanifold of $\partial T_{m}$,
-    and it is triangulated by some faces of $T_{m}$ and their subsimplices.
-
-    Let $F$ be such a face. 
-    By assumption, $F$ must be contained in exactly one $n$-simplex of $T_{0}, T_{1}, \dots, T_{m-1}$,
-    and $F$ is in the boundary of $X_{m-1}$. 
-    We conclude that $\Gamma_{m}$ triangulates a submanifold of the boundary of $X_{m-1}$.
-
-    On the one hand, 
-    if $\Gamma_{m}$ is the entire boundary of $T_{m}$, 
-    then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
-    Hence $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
-    which requires $m = M$.
-    On the other hand, 
-    if $\Gamma_{m}$ is a proper subset of the entire boundary of $T_{m}$, 
-    then $X_{m-1} \cup T_{m}$ is still a topological $n$-ball.
-\end{proof}
-
-We now collect important examples of shellable triangulations.
-Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, non-shellable situations can arise.
-Our main interest are local patches (stars) within triangulations: these are shellable up to three space dimensions, but not necessarily beyond.
-
-\begin{example}\label{example:shell_simpl}
-    Any simplex $T$ (trivially) has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
-    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling\mwl{; see Example 8.2.(iii) in~\cite{ziegler1995lectures}}.
-\end{example}
-\begin{example}
-    The standard triangulation of the $3$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable, as are its higher-dimensional generalizations.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
-\end{example}
-\begin{example}
-    There exists a non-shellable triangulation of a tetrahedron and of a cube in $n=3$, see~\cite[Example 8.9]{ziegler1995lectures}.
-\end{example}
-
-\begin{lemma}\label{lemma:shell_2D}
-    Any simplicial $2$-\disk\ is shellable.
-    Any simplicial $2$-sphere is shellable. 
-\end{lemma}
-\begin{proof}
-    First, 
-    let $\calS$ be any triangulation of a $2$-sphere. 
-    By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-\disk.
-    Any shelling of that \disk\ can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
-    So it remains to show that any triangulation $\calT$ of the two-dimensional \disk\ is shellable. 
-    We will construct the shelling in reverse.
-
-    Write $M = |\calT|$. 
-    There is nothing to show if $\calT$ contains only one triangle. 
-    We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
-    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
-    and a triangle is not good in $\calT$ if that intersection is either empty, only some of its vertices, or a vertex and the opposite edge.
-    % DONE: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
-    We show by an induction argument over the number of triangles that every triangulation of a $2$-\disk\ that contains at least two triangles also contains at least two good triangles.
-
-    Clearly, this is the case if the triangulation of the $2$-\disk\ contains two triangles. 
-    Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
-    and assume that $\calT$ includes $N+1$ triangles. 
-    There are at least two triangles with an edge on the boundary. 
-    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$.
-    Then there exists a triangle $T'$ that intersects $\partial M$ 
-    in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk.
-    By the induction assumption, each of those components contains at least two triangles 
-    that are good in the respective component. 
-    So each component has at least one triangle that is good in $\calT$. 
-    Hence $\calT$ contains two good triangles, which completes the induction step.
-
-    We conclude that whenever $\calT$ triangulates a $2$-\disk,
-    it contains a good triangle $T$. 
-    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
-    If $T$ intersects with the boundary in exactly one or two edges, 
-    then $\overline{M \setminus T}$ is still a topological $2$-\disk.
-    The triangulation $\calT'$ that is obtained by removing $T$
-    is a triangulation of some $2$-\disk\ that intersects $T$ only at either two or one edges.
-    Any shelling of $\calT'$ can in this way be extended to a shelling of $\calT$, and the proof is complete. 
-\end{proof}
-
-\begin{lemma}
-    Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
-    Then $\patch_{\calT}(S)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    The statement is trivially true if $S$ is a tetrahedron. 
-    The statement is clear if $S$ is an inner or boundary face of $\calT$,
-    where we only need to enumerate either one or two tetrahedra. 
-    The statement is still easily verified if $S$ is an inner or boundary edge of $\calT$:
-    one chooses a starting tetrahedron (with a boundary face if $S$ is a boundary edge) and rotates around the edge in a fixed direction to create a suitable enumeration. 
-    When $S$ is an inner vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-sphere.
-    Similarly, when $S$ is a boundary vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
-    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondence between the tetrahedra in $\calT$ and the triangles.
-    \footnote{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}
-\end{proof}
-
-\begin{lemma}\label{lemma:stars_are_shellable}
-    Let $\calT$ be a $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
-    Then $\patch_{\calT}(V)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    This is Lemma~8.7 in \cite{ziegler1995lectures}.
-%     Without loss of generality, $V$ is the origin. 
-%     Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
-%     We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
-%     which does not affect shellability. 
-%     The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
-%     and is thus shellable~\cite[Theorem~8.12]{ziegler1995lectures}. 
-\end{proof}
-
-\begin{remark}
-    Not all triangulable sets admit a triangulation that is shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations are be shellable.
-For example, if we extend the non-shellable triangulation of the tetrahedron from~\cite[Example 8.9]{ziegler1995lectures} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the space dimension $n$ is larger than three.
-\end{remark}
-\begin{remark}
-    Not all triangulable sets admit a triangulation that is also shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
-\end{remark}
-
-A major structural feature of shellable simplicial complexes is that each time an $n$-simplex is added, stars around lower-dimensional simplices gets completed.
-
-\begin{lemma}\label{lemma:existenceofstar}
-    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
-    For $0 \leq m \leq M$, write 
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}.
-    $$ 
-    For $1 \leq m \leq M$, write 
-    $$
-        \Gamma_{m} := X_{m-1} \cap T_{m}.
-    $$ 
-    Then $\Gamma_{m}$ is a union of $\ell$ different faces of $T_{m}$, $1 \leq k \leq n+1$.
-    If $m < M$, then the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-k$ that satisfies 
-    $$
-        \patch_{X_{m}}(S_{m}) = \patch_{\calT}(S_{m}).
-    $$
-\end{lemma}
-\begin{proof}
-    We know $\Gamma_{m}$ is a triangulated submanifold of the boundary of $T_{m}$, 
-    and so it must be a collection of $k$ faces of $T$, $1 \leq k \leq n+1$.
-    Note that $k = n + 1$ can only happen for the last enumerated simplex, $m = M$, if $\calT$ triangulates an $n$-sphere. 
-    $\Gamma_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-k$ in $\Gamma_{m}$.
-    By definition, $S_{m}$ is a boundary simplex of $X_{m}$, 
-    and it is an interior simplex of $X_{m+1}$. 
-    But then $S_{m}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
-    which means that $\patch_{X_{m+1}}(S_{m}) = \patch_{\calT}(S_{m})$. 
-\end{proof}
-
-\section{Reflections and Deformations on shellable stars}\label{section:extension}
-
-This section is devoted to geometric operations that are crucial for our main result in Section~\ref{section:poincarefriedrichs} below. 
-Consider the situation where we have an $n$-dimensional local patch (star) around some simplex $S$ and some $n$-dimensional simplex $T$ within that local star. 
-We construct a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$,
-similar to the two- and three-color maps in \cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}
-This homeomorphism, which we interpret as a nonlinear reflection, is required to preserve the interface. 
-We ensure that the homeomorphism is bi-Lipschitz, and we are particularly interested in the norms of its Jacobian.
-This nonlinear reflection will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms. 
-Additionally, this endeavor produces another geometric tool:
-we construct a bi-Lipschitz deformation which contracts the entire star into the complement of the newly completed star. 
-This deformation will enable additional estimates of Poincar\'e--Friedrichs constants.
-
 We begin with the following observation. 
@@
 \end{proof}
-
-% \begin{figure}
-% \tdplotsetmaincoords{60}{120}
-% \centering
-% \begin{tikzpicture}[tdplot_main_coords]
-% \coordinate (A) at (0, 0, 0);
-% \coordinate (B) at (2, 0, 0);
-% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
-% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
-% \coordinate (A) at (0, 0, 0);
-% \coordinate (B) at (2, 0, 0);
-% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
-% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
-% \draw[thick] (A) -- (B) 
-% \draw[] (B) -- (C) 
-% \draw[] (C) -- (A) 
-% \draw[] (A) -- (D);
-% \draw[thick] (B) -- (D);
-% \draw[] (C) -- (D);
-% \node at (A) [below left] {$A(0,0,0)$};
-% \node at (B) [below right] {$B(2,0,0)$};
-% \node at (C) [above right] {$C(1,\sqrt{3},0)$};
-% \node at (D) [above] {$D(1, \frac{1}{\sqrt{3}}, \sqrt{\frac{8}{3}})$};
-% \end{tikzpicture} 
-% \caption{test}
-% \end{figure}
-
-We state the simple observation that local stars can be subdivided to vertex stars.
-The shape regularity remains controlled in that process.
-
-% \begin{lemma}\label{lemma:stardivision}
-%     Let $\calT$ be an $n$-dimensional simplicial complex
-%     such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
-%     Let $z_S$ be the barycenter of $S$ 
-%     and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
-%     If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
-%     then $\vol(T^{\star}) = \vol(T) / n$.
-% \end{lemma}
-\begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$,
-    let $z_S$ be the barycenter of $S$, 
-    and let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ at $z_{S}$.
-    Then $\vol(T') = \vol(T) / n$. 
-\end{lemma}
-\begin{proof}
-    This is easy.
-\end{proof}
-
-\mwl{TODO: Illustration. Extend to the more general case if needed later.}
-
-We now provide the bi-Lipschitz nonlinear reflection across the interface between the selected simplex and the remainder of the local star
-as well as the bi-Lipschitz contraction from the local star onto the complement of the selected simplex.
-
-\begin{proposition}\label{proposition:starreflection}
-    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be a simplex of dimension $k < n$,
-    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
-    and let 
-    \begin{align*}
-        U := \overline{ |\patch_{\calT}(S)| \setminus T },
-        \qquad 
-        {\Gamma_1} := U \cap T,
-        \qquad 
-        {\Gamma_2} := \overline{ \partial T \setminus \partial U }.
-    \end{align*}
-	The following holds, where the constants on the right-hand sides are as stated in the proof. 
-    \begin{enumerate}
-    \item 
-    There exists a bi-Lipschitz mapping
-    \begin{align*}
-        \Xi_{1} : T \rightarrow U
-    \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap U$. 
-    Its singular values $\sigma_1 \geq \dots \geq \sigma_n$ satisfy 
-    \begin{align*}
-        \sigma_1 &\leq ...
-        \\
-        \sigma_i &\leq ..., \quad 2 \leq i \leq n-1,
-        \\
-        \sigma_n &\leq ...
-    \end{align*}
-    and which satisfies the upper bounds 
-    \begin{gather*}
-        \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
-        \quad 
-        \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
-        \\
-        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
-    \end{gather*}
-    \item 
-    There exists a bi-Lipschitz mapping
-    \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U
-    \end{align*}
-    which is the identity along $\partial U \setminus \partial T$.
-    Its singular values $\sigma_1 \geq \dots \geq \sigma_n$ satisfy 
-    \begin{align*}
-        \sigma_1 &\leq ...
-        \\
-        \sigma_i &\leq ..., \quad 2 \leq i \leq n-1,
-        \\
-        \sigma_n &\leq ...
-    \end{align*}
-    and which satisfies the upper bounds 
-    \begin{gather*}
-        \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
-        \quad 
-        \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
-        \\
-        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
-    \end{gather*}
-    \end{enumerate}
-\end{proposition}
-\mwl{TODO: throughout this manuscript, all vector and operator norms should indicate the exponent.}
-\begin{proof}
-    We derive the estimate in several steps. 
-    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
-    \begin{itemize}
-        \item 
-        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
-        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
-        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
-        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.
-
-        \item 
-        We let $z'_{S}$ be the midpoint of $S'$. 
-        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
-        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
-
-        We define another simplicial complex $\calS^c$ as follows:
-        given any $n$-simplex $K \in \calS$, 
-        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
-        thus obtaining a new simplex $K'$. 
-        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.
-
-        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
-        By construction, all its $n$-simplices contain $S$ as a subsimplex,
-        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
-        Moreover, $S$ is an inner subsimplex of that triangulation. 
-        In particular, $\calS'$ is its own star around $S$.
-
-        \mwl{Check that $\calS'$ is a triangulation...}
-
-        \item 
-        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
-        Then $\calR'$ is its own local star around the barycenter $z_S$.
-        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
-        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
-        which we denote by $\calR$ and $\calR^{c}$, respectively.
-
-        Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
-
-        \item 
-        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ between the underlying sets as follows.
-        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
-        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
-        be affine reference transformations
-        that agree on the vertices common to $K$ and $K'$.
-        Then the mapping 
-        \begin{align*}
-            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
-        \end{align*}
-        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
-        % \begin{align*}
-        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
-        %     \\
-        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
-        % \end{align*}
-        preserves volumes:
-        \begin{align*}
-            |\det( \Jacobian      \Theta_{|K} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|K} )|
-            =
-            1
-            .
-        \end{align*}
-        We want to characterize the singular values of this transform. 
-        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
-        We can write
-        \begin{align*}
-            \Theta_{|K}(x) 
-            = 
-            x
-            - 
-            2 \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            \hat z_{S'}
-            .
-        \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
-        and that it equals $-z_{S'}$ when $x = z_{S'}$.
-%         and when $x = z_{S'}$, then 
-%         \begin{align*}
-%             -z_{S'} 
-%             =
-%             z_{S'}
-%             - 
-%             2 \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-%             .
-%         \end{align*}
-        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
-        \begin{align*}
-            \Theta_{|K}( h_{z} ) 
-            &= 
-            h_{z}
-            - 
-            2 \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            = 
-            h_{z}
-            - 
-            2 \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            %\\&
-            = 
-            h_{z}
-            - 
-            2 z_{S'}
-            %\\&
-            = 
-            - h_{z}
-            - 
-            2 b_{z}
-            .
-        \end{align*}
-		Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
-		Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
-        We study the singular values of the matrix 
-        \begin{align*}
-            B 
-            := 
-            \begin{pmatrix}
-            -1                 & 0
-            \\ 
-            -2 \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
-            \end{pmatrix}
-            =
-            \begin{pmatrix}
-            -1             & 0
-            \\ 
-            -2 \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
-        Its square roots are the desired singular values of $B$:
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
-            ,
-            \\
-            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
-            .
-        \end{align*}
-        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
-        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
-        whereas all its other singular values equal $1$.
-
-%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        We develop explicit bounds for these singular values. 
-        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
-        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
-        % Obviously, $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$.
-
-        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
-        which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
-        Thus 
-        \begin{align*}
-            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
-            = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            \leq 
-            (n-k) \aspectratio(T)
-%             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
-%             \leq 
-%             \frac{ n-k }{n!}
-%             \cdot 
-%             \frac{ \diam(T)^{n} }{ \vol(T) }
-            .
-        \end{align*}
-        This establishes bounds on the singular values of the transformation. 
-        We abbreviate 
-        \begin{align*}
-            B_{T} 
-            := 
-%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
-%             \geq 
-            \sqrt{ 
-                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
-            } 
-            + 
-            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
-            .
-        \end{align*}
-
-        \item 
-        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
-        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
-        We construct a bi-Lipschitz mapping 
-        \begin{align*}
-            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
-        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
-        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
-        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
-        has a unique representation
-        \begin{align*}
-            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
-        \end{align*}
-        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
-        \begin{align*}
-            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
-            .
-        \end{align*}
-        Based on that observation, we define 
-        \begin{align*}
-            \Phi_{K}(x) 
-			&
-			:= 
-            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
-            \\&
-            = 
-            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
-            = 
-            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
-            .
-        \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
-        that satisfies the desired mapping properties. 
-        It remains to analyze its Jacobian to get explicit estimates.
-
-        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
-        With that,
-        \begin{align*}
-            \Jacobian \Phi_{K}(x)
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle }  
-            z_{S'} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
-            h_{z} \otimes h_{z}^{t}
-            - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
-            b_{z} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
-            h_{z} \otimes h_{z}^{t}
-            - 
-            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
-            b_{z} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 } 
-            \hat h_{z} \otimes \hat h_{z}^{t}
-            - 
-            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
-            \hat b_{z} \otimes \hat h_{z}^{t}
-            .
-        \end{align*}
-        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.
-		We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
-        \begin{align*}
-            C 
-            = 
-            \begin{pmatrix}
-                -\frac 1 2             & 0 
-                \\
-                -\frac 3 2 \tan(\beta) & 2 
-            \end{pmatrix}
-			= 
-			\frac 1 2 
-            \begin{pmatrix}
-                -1 & 0 
-                \\
-                -3\tan(\beta) & 2 
-            \end{pmatrix}
-        \end{align*}
-        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
-        \begin{align*}
-            \sigma_{\max} 
-            = 
-            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-            ,
-            \\
-            \sigma_{\min} 
-            = 
-            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-            .
-        \end{align*}
-        \begin{align*}
-            \sigma_{\max} 
-            = 
-            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
-            %=
-            %\frac 1 4 \sqrt{ 9 + 9\tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            =
-            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            ,
-            \\
-            \sigma_{\min} 
-            = 
-            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            .
-        \end{align*}
-        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
-        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
-        \begin{align*}
-            \det \Jacobian\Phi = \frac 1 2.
-        \end{align*}
-        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
-        Similar as above, we use the upper bound 
-        \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
-        \end{align*}
-        We conclude that 
-        \begin{gather*}
-            \matnorm{ \Jacobian\Phi_{K} } 
-            \leq 
-            \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            ,
-            \\
-            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
-            \leq 
-            \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            .
-        \end{gather*}
-        This finishes the discussion of the transformation $\Phi$.
-
-        \item 
-        We continue with an auxiliary result.
-        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
-        Define 
-        \begin{align*}
-            F(x) 
-            = 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
-            x
-            .
-        \end{align*}
-        This is defined away from the hyperplane orthogonal to $h_2$.
-        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
-        That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
-        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed,
-
-        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
-        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $x$ and between $h_2$ and $x$, respectively. 
-        In what follows, $y \in \bbR^{n}$.
-        \begin{align*}
-            \Jacobian F(x) \cdot y
-            &=
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
-            x
-            - 
-            \frac{ \langle h_2, h_2 \rangle \langle h_2, y \rangle }{ \langle h_2, x \rangle^{2} }
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            x 
-            +
-            \frac{ \langle h_2, h_2 \rangle }{ \langle h_2, x \rangle }
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            y 
-            \\&=
-            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
-            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            +
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
-            x
-            \\&=
-            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
-            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
-            +
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
-            \hat x
-            \\&=
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
-            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
-            +
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
-            \hat x
-            \\&=
-            \frac{ \| h_2 \| }{ \| h_1 \| }
-            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
-            \left( 
-                y 
-                - 
-                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
-                + 
-                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
-            \right)
-            .
-        \end{align*}
-        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
-        Notice that $a \perp \hat x$.
-The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
-Over that two-dimensional subspace, it can be represented by a triangular matrix.
-        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
-        %~\cite{blinn1996consider} 
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
-            \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
-        \end{align*}
-        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
-        We thus consider the upper bound 
-        \begin{align*}
-            \|a\| 
-            \leq 
-            2 \max_{1 \leq i \leq 2} 
-            \left( 
-                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
-            \right)
-            .
-        \end{align*}
-
-        \item 
-        We now describe the construction of a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|.
-        \end{align*}
-		Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,
-		so they must contain an open ball around the origin. 
-		\mwl{Here we need a particular result. }
-		Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
-There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively.
-They define respective hyperplanes $H_{G}$ and $H_{K}$,
-        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$ for the corresponding faces. 
-        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$,
-        that is, the scalar product of $x$ with either height vector is positive. 
-        We define 
-        \begin{align*}
-            \Psi(x) 
-            = 
-            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
-            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
-            x
-            .
-        \end{align*}
-        One easily verifies that this defines a continuous mapping $\Psi$. 
-        By the same line of thought, we see that it is invertible with inverse satisfying 
-        \begin{align*}
-            \Psi^{-1}(z) 
-            = 
-            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
-            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
-            z,
-            \qquad 
-            z = \Psi(x)
-            .
-        \end{align*}
-        We let $\alpha_K$ and $\alpha_{{G}}$ be the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
-        and let 
-        \begin{align*}
-            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
-            .
-        \end{align*}
-        The preceding auxiliary results now contribute all information on the singular values of these Jacobians:
-        \begin{gather*}
-            \matnorm{ \Jacobian\Psi(x) }
-            = 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
-            \right)
-            \\
-            \matnorm{ \Jacobian\Psi(z)^{-1} }
-            = 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
-            \right)^{-1},
-            \\
-            \det\Jacobian\Psi(x)
-            =
-            \left( 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \right)^{n},
-            \qquad
-            \det\Jacobian\Psi^{-1}(x)
-            =
-            \left( 
-            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
-            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
-            \right)^{n}
-        \end{gather*}
-        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
-        By the definition of the cosine, 
-        \begin{align*}
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \leq 
-            \frac{ \| x_K \| }{ \| h_{{G}} \| }
-            \leq 
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
-            ,
-            \qquad 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            \leq 
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
-            \frac{ \diam(G) }{ \| h_{K} \| }
-            .
-        \end{align*}
-%         \begin{align*}
-%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
-%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-%             \leq 
-%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
-%             .
-%         \end{align*}
-		We need further details to complete our estimates. 
-		We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
-The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
-		That estimates the quotient $\| x_K \| / \| h_K \|$. 
-        % 
-        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
-        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
-        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows again that $\|x_{G}\| \leq \diam(T)$. 
-        % 
-        It remains to find a lower bound for $\| h_{G} \|$.
-        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
-        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
-The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
-        %         
-%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
-%         \begin{align*}
-%             \frac{\diam(T)}{ \|h_{F}\|}
-%             \leq  
-%             \aspectratio(T)
-%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%             .
-%         \end{align*}
-        Putting all these technical observations together, we estimate 
-        \begin{align*}
-            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
-            &\leq 
-            (k+1)B_{T}
-            \frac{ \diam(K) }{ \| h_{T} \| }
-            \leq 
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \frac{ \diam(T) }{ \| h_{T} \| }
-            \leq 
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            ,
-            \\
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            &\leq 
-            (k+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(T) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \diameterratio(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \diameterratio(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-        \begin{gather*}
-            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
-            \leq 
-            (k+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            ,
-            \qquad 
-            \frac{ \| x_{G} \| }{ \| h_{G} \| }
-            \leq 
-            (k+1)B_{T}
-            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            .
-        \end{gather*}
-
-        %         To simplify that expression, we make another observation regarding the height vectors. 
-        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
-        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
-        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
-        %         with the factor $(k+1)^{-1}$.
-
-        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$.
-That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
-        We calculate 
-        \begin{align*}
-            \|a\|
-            = 
-            \left\|
-            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
-            - 
-            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
-            \right\|
-            &
-            \leq 
-            \frac{\|x_{G}\|}{\|h_{G}\|} 
-            + 
-            \frac{\|x_{K}\|}{\|h_{K}\|} 
-            % \\&
-            \leq 
-            (k+1) 
-            \left( 1 + B_{T} \right)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-
-        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
-        It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
-        Rademacher's theorem then shows that both have essentially bounded weak Jacobians.
-
-        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-        After application of a piecewise linear Lipschitz mapping, 
-        we can assume that $|\calK|$ is convex without loss of generality. 
-        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
-
-        \item 
-		\mwl{Use interlacing inequalities.}
-        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
-        \begin{align*}
-            \Xi_{1} := \Psi \circ \Theta.
-        \end{align*}
-        It preserves the interface from $T$ onto $U$. 
-		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
-        % We briefly recapitulate why it is bi-Lipschitz.
-%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-%         After application of a piecewise linear Lipschitz mapping, 
-%         we can assume that $|\calK|$ is convex without loss of generality. 
-%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
-        The combination of the previous estimates for $\Psi$ and $\Theta$,
-        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
-        provide 
-        \begin{align*}
-            \matnorm{ \Jacobian \Xi_{1} }
-            &\leq 
-            \Cfive{n}{k}(\calT)
-            :=
-            (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            B_{T}^{2}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            ,
-            \\
-            \matnorm{ \Jacobian \Xi_{1}^{-1} }
-            &\leq  
-            \Csechs{n}{k}(\calT)
-            :=
-            (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            B_{T}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            .
-        \end{align*}
-        We get the determinant estimates
-        \begin{align*}
-            |\det(\Xi_{1})|
-            &\leq 
-            \Cdetfive{n}{k}(\calT)
-            :=
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            B_{T}^{n}
-            \aspectratio(\calT)^{n}
-            ,
-            \\
-            |\det(\Xi_{1}^{-1})|
-            &\leq 
-            \Cdetsechs{n}{k}(\calT)
-            :=
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
-            .
-        \end{align*}
-        This completes the desired estimates for $\Xi_{1}$.
-
-        \item 
-        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U $ by setting 
-        \begin{align*}
-            \Xi_{2} := \Psi \circ \Phi.
-        \end{align*}
-        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
-		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
-        The combination of the previous estimates for $\Psi$ and $\Phi$ now lead to 
-        \begin{align*}
-            \matnorm{ \Jacobian \Xi_{2} }
-            &\leq 
-            \Csieb{n}{k}(\calT)
-            :=
-            \frac 1 4
-            % \left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
-            \left( 4 + (k+1) \aspectratio(T) \right)
-            \cdot 
-            (k+1) 
-            \aspectratio(\calT)
-            B_{T}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            \\
-            \matnorm{ \Jacobian \Xi_{2}^{-1} }
-            &\leq  
-            \Cacht{n}{k}(\calT)
-            :=
-            \frac 1 2
-            %\left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
-            \left( 4 + (k+1) \aspectratio(T) \right)
-            \cdot 
-            (k+1) 
-            \aspectratio(\calT)
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-        \end{align*}
-        We get the determinant estimate 
-        \begin{align*}
-            |\det(\Xi_{2})|
-            &\leq 
-            \Cdetsieb{n}{k}(\calT)
-            :=
-            \frac 1 2 
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            B_{T}^{n}
-            \aspectratio(\calT)^{n}
-            ,
-            \\
-            |\det(\Xi_{2}^{-1})|
-            &\leq 
-            \Cdetacht{n}{k}(\calT)
-            :=
-            2
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
-            .
-        \end{align*}
-        This completes the desired estimates for $\Xi_{2}$. 
-    \end{itemize}
-    The proof is complete. 
-\end{proof}
-
-\begin{remark}
-    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
-    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
-    While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
-    it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
-\end{remark}
-
-\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-We are now in the position to develop Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions.
-These results use local Poincar\'e--Friedrichs constants over simplices, 
-with or without boundary conditions, as subcomponents.
-
-The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator}
-implies the following estimate for Poincar\'e--Friedrichs constants over convex domains.
-
-\begin{lemma}\label{lemma:PFexteriorsimplex}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
-    Let $0 \leq k < n$. 
-    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
-    with $\cartan u = \cartan w$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        C_{{\PF},k,\Omega,p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    where 
-    \begin{align*}
-        C_{{\PF},k,\Omega,p} 
-        = 
-        n A_{\Poinc}(n,k+1) 
-        \vol_{n}(B_1(0)) 
-        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
-        \diam(\Omega)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This follows from the discussion in Section~\ref{section:potentialoperator}.
-    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
-	\mwl{check final form of result}
-\end{proof}
-
-We also need a Poincar\'e--Friedrichs inequality for differential forms over a simplex but subject to homogeneous boundary conditions along a collection of faces.
-
-\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
-    Let $T$ be an $n$-simplex 
-    and let $F_{0},\dots,F_{\ell}$ be $\ell+1$ different faces of $T$. 
-    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq \ell$.
-    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq \ell$
-    and  
-    \begin{align*}
-        \cartan w = \cartan u,
-        \quad 
-        \| w \|_{L^{p}(\Omega)} 
-        \leq 
-        C_{\PF,\Gamma,\ell,k,p}(T)
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    Here, $C_{\PF,\Gamma,\ell,k,p}(T) > 0$ is a constant such that 
-    \begin{align*}
-        C_{\PF,\Gamma,\ell,k,p}(T)
-        \leq 
-        2^{\frac n p}
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (\ell+1)/n! } 
-        \algebraicshapemeasure(T)^{k-1}
-        \Ceins{n}(T)^{k}
-        \diam(T)
-        % \matnorm{\Jacobian \varphi}^{k}
-        .
-    \end{align*}
-\end{lemma}
-\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
-Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
-Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
-Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
-We should unify.}
-\begin{proof}
-    There exists an affine bijection $\varphi : \hat T \rightarrow T$ 
-	that maps the convex closure of the $n$ unit vectors onto the face $F_0$.
-    We can also assume that the face of $\hat T$
-    orthogonal to the $i$-th coordinate axis is mapped 
-    onto the face $F_i$. 
-    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
-    We see that $\vol(\tilde U) = (l+1)/n!$
-
-    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
-    Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes,
-    and let $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
-    We observe $\tilde g = \cartan \tilde u$
-    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.
-
-    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:...} imply 
-    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
-    with $\cartan \tilde w = \cartan \tilde u$ and 
-    \begin{align*}
-        \| \tilde w \|_{L^{p}(\tilde U)}
-        &\leq 
-        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{ \vol(\tilde U) } 
-        2
-        \| \tilde g \|_{L^{p}(\tilde U)}
-        \\&\leq 
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
-        \| \tilde g \|_{L^{p}(\tilde U)}
-        .
-    \end{align*}
-    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\hat T} )$.
-    By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.
-
-    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
-    \begin{align*}
-        \| w \|_{L^{p}(T)}
-        &\leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
-        \| \tilde w \|_{L^{p}(\hat T)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\tilde U)}
-        &\leq 
-        2^{\frac {n-\ell} p}
-        \| \hat g \|_{L^{p}(\hat T)}
-        \leq 
-        2^{\frac {n-\ell} p}
-        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
-        \matnorm{\Jacobian \varphi}^{k}
-        \cdot 
-        \| \cartan u \|_{L^{p}(T)}
-        .
-    \end{align*}
-    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. \mwl{Double check result}
-\end{proof}
-
-We settle the following notation for our main result. 
-Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
-\begin{align*}
-    C_{\PF,\Gamma,k,p}(\calT) 
-    :=
-    \max\limits_{ \substack{ T \in \calT \\ \dim(T)=n \\ 0 \leq l \leq n } }
-    C_{\PF,\Gamma,l,k,p}(T)
-    .
-\end{align*}
-Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
-\begin{align*}
-    \mwl{X_{m} := ...}
-\end{align*}
-For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
-\begin{align*}
-    \Gamma_{m} := T_{m} \cap \left( T_{0} \cup \dots \cup T_{m-1} \right)
-\end{align*}
-According to Lemma~\ref{lemma:existenceofstar}, 
-there exists a simplex $S_{m} \in \calT$ 
-such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
-In particular, $\patch_{\calT}(S_{m})$ is already included in the union of the simplices up to $T_m$. 
-We write 
-\begin{align*}
-    \Minako_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
-\end{align*}
-for the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
-
-The main result of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorem.
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_M$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
-    and such that for each $T_{m} \in \calT$, $1 \leq m \leq M$, in the shelling
-    we have the following recursive estimate: 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \left( 
-            \| \cartan u      \|_{L^{p}(T_{m})} 
-            +
-            \Cfive{n}{k}(\calT)^{k+1} 
-            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-            \| \cartan u \|_{L^{p}(\Minako_{m-1})}
-        \right)
-        \\&\qquad
-        + 
-        \Cfive{n}{k}(\calT)^{k} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(\Minako_{m-1})}
-        .
-    \end{align*}
-    \mwl{The notation $\Minako_m$ should be settled in the definition of shellings.}
-\end{theorem}
-\begin{proof}
-    \mwl{Complete the proof.}
-    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $X_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.
-
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $X_{m-1}$. 
-    By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
-    as in Proposition~\ref{proposition:starreflection}. 
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        . 
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $X_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(X_{m})$ with $\cartan w_{m} = \cartan u$ over $X_{m}$.
-
-    We want to estimate norms. 
-    By construction,
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-    we can assume 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    We also employ Proposition~\ref{proposition:pullbackestimate} to find 
-    \begin{align*}
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|_{L^{\infty}(T_{m})}^{-\frac 1 p} 
-        \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k}
-        \cdot 
-        \| w_{m-1} \|_{L^{p}(\Minako_{m-1})}
-        ,
-        \\
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m})} 
-        \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k+1}
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(\Minako_{m-1})}
-        .
-    \end{align*}
-    \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(\Minako_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
-        ,
-    \end{align*}
-    We have assumed that $\cartan w_{m-1} = \cartan u_{|X_{m-1}}$. 
-    We use the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}. 
-    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-\begin{proof}
-    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
-    We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
-    For $0 < m \leq M$, by the definition of shellability in Section~\ref{section:shellability}, 
-    $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
-    where $\Minako_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
-
-    We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound. 
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex}, 
-    there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    We define $w_{|T_0} := w_0$. 
-    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
-    This is true for $m = 1$. 
-    We now define, as in Equations~(5.12) and~(5.14) of~\cite{ern2020stable} or Equations~(6.7) and~(6.9)~\cite{Chaum_Voh_p_rob_3D_H_curl_24},
-    \begin{align} \label{equation:w''_ext_der}
-        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\Minako_{m-1}}),
-    \end{align}
-    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
-    as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
-    Clearly, $w_{|T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
-    \begin{align*}
-        \trace_{\Gamma_{m}} w_{|T_m} = \trace_{\Gamma_{m}} w_{|X_{m-1}},
-    \end{align*}
-    since $u$ is trace continuous over $\Gamma_{m-1}$ and $\Xi_{m}$ is the identity along $\Gamma_{m-1}$, and
-    \begin{align*}
-        \cartan w = \cartan u \text{ over } T_m,
-    \end{align*}
-    since $\cartan w = \cartan u$ over $X_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
-    \begin{align*}
-        w_{|X_{m}} \in W^{p}\Alt^{k}(X_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } X_{m}. 
-    \end{align*}
-
-    We want to estimate norms. 
-    By construction,
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        \leq  
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        + 
-        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) = 0$, we have
-    \begin{align*}
-        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
-        + \| \cartan (\Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})} )
-        .
-    \end{align*}
-    We also use Proposition~\ref{proposition:pullbackestimate} to find 
-    \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(\Minako_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
-        ,
-    \end{align*}
-    where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
-    Using the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}, the desired recursive estimate follows. 
-\end{proof}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$.
-    Let $T_0, T_1, \dots, T_M$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
-    such that 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        \leq 
-        C_{\PF,T,k,p}(T_{0})
-        \prod_{i=1}^{m} 
-        C_{???}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-\end{theorem}
-\begin{proof}
-    We prove this via induction. 
-    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
-    Let us assume that the statement is true for some integer $m-1 \geq 0$.
-
-    We write $X_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
-    which is a triangulated $n$-dimensional submanifold with boundary.
-    By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
-    which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
-    and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow \Minako_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
-    which acts as the identity along $\partial \Minako_{m-1} \setminus \partial T$.
-    By assumption, 
-    there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
-    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
-    \begin{align*}
-        \| w_{m-1} \|_{L^{p}(T_{m})}
-        \leq 
-        C_{\PF,T,k,p}(T_{0})
-        \prod_{i=1}^{m} 
-        C_{???}
-        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    Because pullback and exterior derivative commute, 
-    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
-    Moreover, the desired estimate follow from Proposition~\ref{proposition:starreflection}.
-    The proof is complete. 
-\end{proof}
-\todo{MV: Why a second theorem?
-Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
-Which is better and when?
-Add more details to the estimates}
-
-\section{Numerical examples}\label{section:numericalexamples}
-
-We assess the ``efficiency'' of our upper bounds with a few numerical examples in dimension 2D and 3D, with focus on the Hilbert space case $p=2$. 
-Unless the Poincar\'e--Friedrichs constants are known explicitly, we use eigenvalue estimates on a refined mesh as a proxy for the exact value.
-We compare the (approximations of) the exact values with the upper bounds obtained via Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
-
-\subsection{Estimates for partial boundary conditions}
-
-We first assess the constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-which relies on estimates for the Bogovski\u{i} operator over an auxiliary reference domain.
-Our experiments over triangles and tetrahedra indicate we overestimate by several magnitudes.
-%
-We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
-Numerical examples indicate that this holds for $p=2$.
-
-\subsection{Two-dimensional examples}
-
-We consider the following example domains in two dimensions:
-the unit square $\Omega_Q$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{S}$:
-\begin{gather*}
-    \Omega_{Q}  = (-1,1)^2,
-    \qquad 
-    \Omega_{L}  = (-1,1)^2 \setminus (0,1)^2,
-    \\
-    \Omega_{S} = (-1,1)^2 \setminus ( [0,1) \times \{0\} ).
-\end{gather*}
-% Square 
-% L-shaped 
-% Slit
-
-\subsection{Three-dimensional examples}
-
-We consider the following example domains in two dimensions:
-the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
-\begin{gather*}
-    \Omega_{C}  = (-1,1)^3,
-    \qquad 
-    \Omega_{F}  = (-1,1)^3 \setminus [0,1)^3,
-    \\
-    \begin{aligned}
-    \Omega_{B} &= 
-    \left( (-1,0) \times (-1,0) \times (-1,1) \right)
-    \\&\qquad
-    \cup 
-    \left( (-1,0) \times (-1,1) \times (-1,0) \right)
-    \\&\qquad
-    \cup 
-    \left( (-1,1) \times (-1,0) \times (-1,0) \right)
-    .
-    \end{aligned}
-\end{gather*}
-% Cube 
-% Fichera
-% Crossed bricks
-
-\section{Outlook}\label{section:outlook}
-
-The most important outcome of this research have been computable upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches. 
-There are several avenues for further research going further from the results established in this manuscript.
-Our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), where there are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) \mwl{already} leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
-In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
-Better transformations or more careful estimates are likely possible, as are completely different approaches.
-For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
-
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
-
-Concerning the geometric setting, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to topological balls and spheres.
-In particular, domains with shellable triangulations are contractible.
-We expect that in the forthcoming works, these estimates will become subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-% Future work % DONE: Theo : parts already mentioned ??? 
-% Computable reliable estimates are important: 
-% they quantify the fundamental stability properties of partial differential equations in vector analysis,
-% such as the Hodge Laplace equation.
-
-\section*{Acknowledgments}
-
-MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
-
-\bibliographystyle{acm_mod}
-\bibliography{library}
-
-\end{document}

### 2024-10-04 main.tex
various improvements

@@
     Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{martin.vohralik@inria.fr}
+    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
 }
@@
     \leq 
-    C_{{\rm P},{\rm CW},p}
+    C_{{\rm CW},p}
     \diam(\Omega)
@@
 \begin{align*}
-    C_{{\rm P},{\rm CW},p} 
+    C_{{\rm CW},p} 
     := 
@@
 \end{align*} 
-Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
+Note that \eqref{math:chuawheeden} is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
 As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
@@
     \leq 
-    C_{\PF,{\rm EFNT},p}
+    C_{{\rm EFNT},p}
     \diam(\Omega)
@@
 \end{align}
-where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align*}
-    C_{\PF,{\rm EFNT},p}
+where $C_{{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
+\begin{align*}
+    C_{{\rm EFNT},p}
     :=
@@
     \leq 
-    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
+    2^{|1-\frac 2 p|}C_{{\rm EFNT},p}
     \diam(\Omega)
@@
 \end{align}
-When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
+When $p=1$, then the optimal Poincar\'e constant also bounds the Poincar\'e--Friedrichs constant:
 \begin{align}\label{math:l1estimate}
@@
     Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
-    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
-    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
+    Let us compare $C_{{\rm CW},p}$ for the Poincar\'e inequality
+    with $C_{{\rm EFNT},p}$ for the Poincar\'e--Friedrichs inequality. 
     In the case $2 \leq p$, 
@@
         2^{1-\frac 2 p}
-        C_{\PF,{\rm EFNT},p}
+        C_{{\rm EFNT},p}
         =
@@
         \leq
-        C_{{\rm P},{\rm CW},p} 
+        C_{{\rm CW},p} 
         .
@@
         2^{\frac 2 p - 1}
-        C_{\PF,{\rm EFNT},p}
+        C_{{\rm EFNT},p}
         =
@@
         \leq
-        C_{{\rm P},{\rm CW},p} 
+        C_{{\rm CW},p} 
 %         % 
@@
 % DONT: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
+%     In the limit as $p$ goes to $1$, the factor $C_{{\rm EFNT},p}$ converges to $1/2$,
 %     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
@@
 %     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
+%     In the limit as $p$ goes to infinity, the factor $C_{{\rm EFNT},p}$ converges to $1/2$, 
 %     which implies the Poincar\'e inequality 
@@
 
-In this section, we develop stepwise computable estimates of Poincar\'e--Friedrichs constants of triangulated domains. 
+In this section, we develop stepwise computable estimates for Poincar\'e--Friedrichs constants of triangulated domains. 
 The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
@@
 having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.
-%We construct a scalar potential for a given gradient vector field on larger and larger triangulated subdomains.
-We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face, thus constructing a scalar potential over larger and larger subdomains.
-This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+We always construct a gradient potential over the new simplex and fix the constant of integration using the value already known on the connecting face, thereby constructing a scalar potential over larger and larger subdomains.
+This basic idea has appeared in various forms before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
 
@@
     \end{align*}
-    That $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
-    for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$. 
-    Very briefly verify that density argument: 
-    There exists affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ from the reference simplex onto $T$ that maps the convex closure of the $n$ unit vectors onto the face $F$.
+    If $u \in W^{1,p}(T)$ has vanishing trace along $F$ but is not necessarily smooth, 
+	then we conclude $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
+    from approximation via members of $C^{\infty}(T)$ whose support is disjoint from $F$. 
+    We very briefly verify that density argument: 
+    There exists an affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ from the reference simplex onto $T$ that maps the convex closure of the $n$ unit vectors onto the face $F$.
     We let $\hat u := u \circ \varphi$.
@@
 
-The next auxiliary result extends the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations.
-We emphasize that face patches are not necessarily convex.
+The next auxiliary result establishes Poincar\'e--Friedrichs constants over face patches within simplicial triangulations. 
+We emphasize that face patches are not necessarily convex, but we can still extend the results on convex domains from Section~\ref{section: PX_convex}.
 The following result is reasonably sharp when the two simplices have similar volumes and diameters.
@@
 %         \leq 
-%         2 \Ceins{n} C_{\PF,{\rm EFNT},p}
+%         2 \Ceins{n} C_{{\rm EFNT},p}
 %         \max\left( 
@@
     \end{align*}
-    Here, $C_{{\PF},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
+    Here, $C_{{\PF},T_1 \cup T_2,p} = 2 \Ceins{n} C_{{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
 \end{lemma}
@@
     We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
-    be affine transformations that the origin to $v_0$, that map each unit vector $e_{i}$ to $v_{i}$ for $i = 1, \dots, n-1$,
+    be affine transformations 
+	that map the origin to $v_0$, that map each unit vector $e_{i}$ to $v_{i}$ for $i = 1, \dots, n-1$,
     and that satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
@@
         \leq 
-        2 C_{\PF,{\rm EFNT},p}
+        2 C_{{\rm EFNT},p}
         \| \nabla \hat u \|_{L^{p}(\hat U)}
@@
     % which we have already employed in~\eqref{equation:Hong_Pan}, 
-    and the estimate $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$, which is given in Lemma~\ref{lemma:measurerelationships}. We conclude the desired result.
+    and the estimate $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$, which is given in Lemma~\ref{lemma:measurerelationships}. We obtain the desired result.
 \begin{comment}
@@
         &\leq 
-        2 C_{\PF,{\rm EFNT},p}
+        2 C_{{\rm EFNT},p}
         \max\left( 
@@
         \leq 
-        2 C_{\PF,{\rm EFNT},p}
+        2 C_{{\rm EFNT},p}
         \max\left( 
@@
 The main result of this section constructs a potential and gives an upper bound for the Poincar\'e--Friedrichs constant.  
-It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.
-The procedure serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-
-Two different variations of underlying idea are analyzed; the resulting estimates are only slightly different.  
-On the one hand, we extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that simplex.
-This auxiliary problem will be subject to partial boundary conditions.
+It follows the same underlying principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.
+This procedure serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
+
+Two different variations of underlying idea are analyzed, yielding slighly different estimates. 
+On the one hand, we can extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that new simplex, subject to partial boundary conditions.
+On the other hand, we can instead cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
+Since these can only differ by constants at their overlaps, we assemble a global scalar potential piece by piece as we adjust the local constants of integration.
+Both estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
+
 % We present an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex}, where we compute an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
 % We emphasize that this construction of potentials and bounding of Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-On the other hand, we can instead cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
-Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece by adjusting the local constants of integration.
-Both estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
 
@@
 %             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
-%             \| \nabla u \|_{L^{p}(T_{\iota(m)})}
+%             \| \nabla u \|_{L^{p}(T_{m-1})}
 %         \right)
@@
         \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{{\iota(m)}})}
+        \| w \|_{L^{p}(T_{{m-1}})}
         +
@@
     and that $1 \leq m \leq M$.
-    Recall that we write $F_m := T_m \cap T_{m-1}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$.
-
-    We proceed with showing the first recursive estimate. 
+    Recall that we write $F_m := T_m \cap T_{m-1}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$,
+	and that we write $\Minako_{F_m} := T_m \cup T_{m-1}$.
+
+    We proceed with the first recursive estimate. 
     We define $w'_{m} := w_{|T_{m-1}} \circ \Xi \in W^{1,p}(T_{m})$,
@@
     Suppose again that $1 \leq m \leq M$. 
-    Recall that we write $\Minako_{F_m} := T_m \cup T_{m-1}$. 
     We use the Poincar\'e--Friedrichs inequality over $\Minako_{F_{m}}$,
@@
     \end{align*}
-    In the special case $p=1$,
+    Note that in the limit cases $p=1$ and $p=\infty$ we get, respectively, 
     \begin{align*}
         \| w\|_{L^{1}(T_m)}
-        \leq 
+        &\leq 
         \max\left(
@@
         \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-        \| w \|_{L^{1}(T_{{m-1}})}
-        .
-    \end{align*}
-    In the limit case $p=\infty$, 
-    \begin{align*}
+        \| w \|_{L^{1}(T_{{m-1}})},
+		\\
         \| w \|_{L^{\infty}(T_m)}
-        \leq 
+        &\leq 
         2
@@
 \begin{remark}
-    The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases.
-We hence target its use to local patches (stars), in particular non-convex boundary stars.
+    The Poincar\'e--Friedrichs constants obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimate the best one as number of $n$-simplices in the triangulation $\calT$ increases.
+We hence conceive their target application to be local patches (stars), in particular non-convex boundary stars.
 The latter occur inevitably at reentrant corners.
@@
 The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$.
-This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant.
+This may allow for partitions of $\overline \Omega$ with signficantly less elements, which enables a largely improved estimate of the best Poincar\'e--Friedrichs constant.
 \end{remark}
@@
 
-Throughout this section, we let $\Omega \subseteq \bbR^{3}$ be any bounded open set.
-
 \subsection{Vector calculus}
 
-\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ }
+\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ 
 \begin{gather*}
@@
     .
-\end{gather*}
+\end{gather*}}
 Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
@@
 \end{gather*}
-
 We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
@@
     This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
-    The literature also knows the Piola transform in the direction of the original mapping. 
+    One advantage of that definition is that it also makes sense whenever the transformation is not bijective. 
+    However, the literature also knows the Piola transform in the direction of the original mapping. 
 \end{remark}
@@
 
+We let $\Omega \subseteq \bbR^{n}$ be any bounded open set.
 We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
@@
     For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
-    $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
-%     \begin{align*}
 		  % $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
-%     \end{align*}
+    \begin{align*}
+        v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}. 
+    \end{align*}
     The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
@@
 
-We begin with the following observation. 
-Suppose that $T$ is any $n$-dimensional simplex with some proper subsimplex $F$.
-We find a hyperplane of codimension one that intersects $T$ only at the $F$ and such that $T$ is on only one side of the hyperplane.
-
-\begin{lemma}\label{lemma:oppositesubsimplex}
-    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
-    Let $F, F'$ be the two subsimplices of $T$ with respective vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
-    Then
-    \begin{gather*}
-        A 
-        := 
-        v_0 
-        + 
-        \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} 
-        +  
-        \operatorname{lin}\{ v_{k+1} - v_n, \dots, v_{n-1} - v_n \}.
-    \end{gather*}
-	is an affine subspace of dimension $n-1$, the simplex $T$ lies on one side of $A$,
-	and $F = T \cap A$.
-\end{lemma}
-\begin{proof}
-    Obviously, $F \subset A \cap T$. 
-    Suppose now that $x \in A \cap T$.
-    There exist $\lambda_1,\dots,\lambda_{n-1} \in \bbR$ such that 
-    \begin{align*}
-        x &= 
-        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
-        \\&
-        = 
-        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
-        + 
-        \sum_{i=1  }^{k  } \lambda_{i} v_i 
-        + 
-        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
-        + 
-        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
-        .
-    \end{align*}
-    This is the unique expression of $x$ as non-negative linear combination of the vertices of $T$.
-    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive and their sum is non-negative.
-    Hence $\lambda_{k+1} = \dots = \lambda_{n-1} = 0$, implying $x \in F$.
-    % 
-    Lastly, the linear spans 
-    \begin{gather*}
-        A_{0} := \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \},
-        \qquad 
-        A_{1} := \operatorname{lin}\{ v_{k+1} - v_n, \dots, v_{n-1} - v_n \}
-    \end{gather*}
-    intersect only at the origin, since otherwise a non-trivial affine combination of the vertices of $T$ equals zero, 
-	contradicting their affine independence. %the vertices of $T$ are not affinely independent. 
-    So $A$ has dimension $n-1$. 
-\end{proof}
-
 % \begin{figure}
@@
 \begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$,
-    let $z_S$ be the barycenter of $S$, 
-    and let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ at $z_{S}$.
-    Then $\vol(T') = \vol(T) / n$. 
+    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
+    Let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ in accordance with the barycentric subdivision of $S$ at $z_{S}$.
+	\begin{itemize}
+		\item $\vol(T') = \vol(T) / (k+1)$. 
+		\item The height vector of $v \in \Vertices(T) \setminus \Vertices(S)$ in $T'$ is the height vector $v$ in $T$.
+		\item The height vector of $z_S$ in $T'$ is the height vector of the single vertex $v \in \Vertices(T) \setminus \Vertices(T')$ in $T$,
+scaled by $(k+1)^{-1}$.
+	\end{itemize}
 \end{lemma}
@@
 
-\mwl{TODO: Illustration. Extend to the more general case if needed later.}
+\begin{figure}
+    \begin{center}
+    \begin{tikzpicture}
+        % Coordinates of the triangle
+        \coordinate (A) at (0,0); % Vertex A = v_0
+        \coordinate (B) at (4,0); % Vertex B = v_1
+        \coordinate (C) at (1,3); % Vertex C = v_2
+        \coordinate (M) at ($(A)!0.5!(B)$); % Midpoint M of AB
+        % Heights from each vertex
+        \coordinate (H_A) at ($(C)!(A)!(B)$); % Height from A to BC
+        \coordinate (H_B) at ($(C)!(B)!(A)$); % Height from B to AC
+        \coordinate (H_C) at ($(A)!(C)!(B)$); % Height from C to AB
+        \coordinate (H_M) at ($(B)!(M)!(C)$); % Height from M to BC
+        % Drawing the triangle
+        \draw[thick] (A) -- (B) -- (C) -- cycle;
+        % Drawing the bisector from C to AB and the height vectors 
+        %\draw[dashed] (C) -- (M);
+        \draw[] (C) -- (M);
+        \draw[dashed,->,line width=1.0pt,>=latex] (H_A) -- (A); % Height vector from A, original 
+        \draw[dashed,->,line width=1.0pt,>=latex] (H_M) -- (M); % Height vector from A, original 
+        \draw[dashed,->,line width=1.0pt,>=latex] (H_C) -- (C); % Height vector from C, unaffected
+        % Marking the height points
+        \node[above right] at (C) {$v_2$};  
+        \node[below left] at (A) {$v_0$};
+        \node[below right] at (B) {$v_1$};
+        \node[below] at (M) {$z_S$};
+    \end{tikzpicture}
+    \end{center}
+    \caption{Illustration of Lemma~\ref{lemma:stardivision}.
+The triangle $[ v_0, v_1, v_2 ]$ is bisected at the edge $[ v_0, v_1 ]$, leading to two new triangles.
+The height vector from $v_2$ in all three triangles remains the same.
+The height vector from $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector from $v_0$ in the original triangle.}
+\end{figure}
 
@@
 \end{proof}
-\todo{MV: Why a second theorem?
+\mwl{MV: Why a second theorem?
 Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?

### 2024-10-04 draft.tex
shape measures

@@
 We present numerical examples in Section~\ref{section:numericalexamples}.
+
+We shift gears and move from a combinatorial study of triangulations to an analytical study:
+we introduce quantitative measures for the geometric quality of triangulations. 
+These indicate of the regularity of simplex shapes. 
+All these quantities have in common that they can be computed from purely local information. 
+Most of such \emph{shape measures} in the literature are based on geometric features, 
+but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
+While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
 

### 2024-10-04 main.tex
shape measures

@@
 \\
+
+\paragraph{Notation}
+
+\mwl{Fix this}
+Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
+where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
+We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
+and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
+% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
 
@@
 
-We shift gears and move from a combinatorial study of triangulations to an analytical study:
-we introduce quantitative measures for the geometric quality of triangulations. 
-These indicate of the regularity of simplex shapes. 
-All these quantities have in common that they can be computed from purely local information. 
-Most of such \emph{shape measures} in the literature are based on geometric features, 
-but it will also be helpful to use indicators based on affine transformations associated with the mesh. %;this is because the properties of these transformations are what shows up in our estimates. 
-While there are many equivalent shape measures, we use the ones that most immediate appear in our proofs.
-
-\mwl{MWL: The different geometric quantities in this section should really be just what is needed later.
-Any shape measure should be locally measurable and close to what appears in the right-hand sides of the main results.
-Any inequalities here should be as tight as possible.
-}
+We introduce several quantities that measure the regularity of a triangulation. 
+% We quantify the quality of a triangulation via so-called \emph{shape measures}. 
+These have in common that they can be computed from purely local information.
 
@@
 where the height of a vertex is defined as the distance to the affine span of its opposing face.
-
 For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
 
-Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
-where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
-We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
-and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
-% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
-
 Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
-the \textit{aspect shape measure} $\aspectratio(T)$,
+we define the \textit{aspect shape measure} $\aspectratio(T)$,
 and 
@@
 \begin{align}\label{math:shapemeasure}
-    \geometricshapemeasure(T)
-    := 
-    \frac{ \diam(T)^{n} }{ n! \vol(T) }
-    ,
-    \qquad 
     \aspectratio(T)
@@
     \sup_{ \varphi : \Delta^n \rightarrow T } 
-    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
-%     \sup_{ \varphi : \Delta^n \rightarrow T } \matnorm{\Jacobian \varphi}_{\maxcol} \matnorm{ \Jacobian \varphi^{-1} }_{\maxcol}
+    % \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
+    \matnorm{\Jacobian \varphi} \matnorm{ \Jacobian \varphi^{-1} }
     ,
@@
 % DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
-
-When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
+When $\calT$ is an $n$-dimensional simplicial complex, we naturally define 
 \begin{align}\label{math:shapemeasure:triangulation}
-    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
-    ,
-    \quad 
     \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
@@
 \end{align}
-We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
-
-We now gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
+We call these the aspect and algebraic shape measure, respectively, of the triangulation.
+
+We gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
 
@@
     Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{gather*}
-        \matnorm{\Jacobian \varphi}
-        \leq 
-        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
-        ,
+    \begin{gather*} % First pair 
+        \matnorm{ \Jacobian \varphi } 
+        \leq 
+        \Ceins{n} \cdot \diam(T),
         \qquad 
@@
         \leq 
-        \Czwei{n} \cdot 
-        \geometricshapemeasure(T) 
-        \diam(T)^{-1}
-        ,
-        \\
-        \algebraicshapemeasure(T)
-        \leq 
-        \Cdrei{n}
-        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
-        \geometricshapemeasure(T)
-        ,
-        \qquad 
-        %         \geometricshapemeasure(T)^{\frac 1 n}
-        %         \leq 
-        \aspectratio(T)
-        \leq 
-        \geometricshapemeasure(T)
-        .
+        \Czwei{n} \cdot \aspectratio(T) \height(T)^{-1}
+        ,
+        \\
+        \frac{1}{\sqrt{2n}} \aspectratio(T) \leq \algebraicshapemeasure(T) \leq n \aspectratio(T).
     \end{gather*}
-    Here,
-    \begin{align*}
-        \Ceins{n} \leq \sqrt{n},
-        \quad 
-        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
-        \quad 
-        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
-        . 
-    \end{align*}
+    Here, $\Ceins{n} = \Czwei{n} = \sqrt n$. 
 \end{lemma}
 \begin{proof}
-%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
-%     except for the vertex $\varphi(0)$. It immediately follows that 
-%     \begin{align*}
-%         \matnorm{ \Jacobian \varphi^{-1} }_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
-%         .
-%     \end{align*}
-%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
-%     
-    We easily verify the first inequality.
-To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
-    The Jacobian determinant is the product of these singular values. 
-    By a result of Hong and Pan \cite{hong1992lower},
-    \begin{align*}
-        \sigma_{n}
-        &\geq 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
-        = 
-        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
-        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
-        .
-    \end{align*}
-%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
-    The second inequality follows by taking the reciprocal. 
-    The definition of the condition number now gives the third inequalities. 
-    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
-    Finally, 
-    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
-    \begin{align*}
-        \frac{ \diam(T) }{ \height(T) }
-        \leq 
-        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
-        \leq 
-        \frac{ \diam(T)^{n} }{ n! \vol(T) }
-        .
-    \end{align*}
-%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
-%     \begin{align*}
-%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%         \leq 
-%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
-%         .
-%     \end{align*}
-    That shows the fourth and last of the inequalities. 
+    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine transformation. 
+	We abbreviate $M := \Jacobian\phi$ for its Jacobian. 
+    We begin with observing that the largest $\ell^{2}$-norm of any column of $M$,
+    which here denote by $c_{\max}(M)$, 
+    equals the maximum of the quotient $\| M x \|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
+    We also know that the diameter of $T$ is the length of its longest edge. 
+    Our first pair of inequalities follows via standard comparisons of Euclidean norms:
+    \begin{align*}
+        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ M } \leq \sqrt{n} c_{\max}(M) \leq \sqrt{n} \diam(T).
+    \end{align*}
+    The columns of the matrix $M^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
+    except for the vertex $\varphi(0)$. It immediately follows that 
+    \begin{align*}
+        \matnorm{ M^{-1} } \leq \sqrt{n} c_{\max}(M^{-1}) \leq \sqrt{n} \cdot \height(T)^{-1}
+        .
+    \end{align*}
+    The smallest height in the reference simplex $\Delta^{n}$ is $\height_{\Delta} = 1/\sqrt{n}$, 
+    whence $\height(T) \geq \matnorm{M^{-1}}^{-1} / \sqrt{n}$. This yields our second pair of inequalities. 
+    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)$.
+    All relevant results follow.
 \end{proof}
 
-\begin{remark}
-    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    In our convention, the reference simplex has unit shape measure.
-    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions.
-$\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.
-
-% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
-    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
-    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}.
-    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
-    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
-    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
-% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
-and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
+We are interested in the maximal ratio of volumes between face-neighboring $n$-simplices, written $\volumeratio(\calT)$,
+and the ratio of the diameters of any intersecting simplices, written $\diameterratio(\calT)$. Formally, 
 \begin{align}\label{math:volumeratio}
@@
 
-% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
-% we define the quantity 
-% \begin{align*}
-%     \geometricshapemeasure(T)
-%     := 
-%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%     .
-% \end{align*}
-
 \begin{lemma}\label{lemma:volumecomparison}
@@
         % = 
-        \geometricshapemeasure(T_1)
+        \aspectratio(T_1)
         \diam(F)
@@
 
-% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
-% \begin{align*}
-%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
-%     \leq 
-%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-%     \cdot 
-%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-%     .
-% \end{align*}
-% DONE: REMOVE THE FACTORIAL?
-% DONE: I am not 100% sure what that means.
-Is really the heights of F?
-I imagine this is rather the heights of simplices T_1 and T_2, isn't?
-Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment!
-(I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
-% DONE: clarify the first of the following inequalities
-
-%     \begin{align*}
-%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
-%     \end{align*}
-%     Thus we establish the first estimate:
-
-%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
-%     \begin{align*}
-%         \diam(F)
-%         \geq 
-%         h
-%         =
-%         n
-%         \frac{ \vol(T_1) }{ \vol(F') }
-%         \geq 
-%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
-%         \cdot 
-%         \diam(T_1)
-%         .
-%     \end{align*}
-%     That shows the second estimate.
-
 \begin{proof}
-    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
-%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
-%     \begin{align*}
-%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
-%     \end{align*}
-%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
+    The diameter of $F$ is at least as large as the height $h_S$ of some other vertex of $F$ in $T_{1}$. 
     Now, 
@@
     \end{align*}
-\begin{comment}
-    On the other hand, 
-    \begin{align*}
-        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
-%         \\
-%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
-        h_1 \leq \aspectratio(T_{1}) \diam(F),
-        \qquad 
-        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
-        .
-    \end{align*}
-    The second estimate follows. 
-    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
-    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
-    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }
-        \leq 
-        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
-        \leq 
-        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \matnorm{ \Jacobian \Xi }
-%         &
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \diam(T_1)
-%         \diam(T_2)^{-1}
-%         \\&
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         \diam(F)
-%         \diam(T_2)^{-1}
-%         \leq 
-%         \Ceins{n}
-%         \Czwei{n}
-%         \geometricshapemeasure(T_2)
-%         \geometricshapemeasure(T_1) 
-%         .
-%     \end{align*}
-    All the desired results thus follow.
-\end{comment}
     Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
@@
 \begin{remark}
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diameterratio}}. 
-    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
-    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
-    If we have an upper estimate for the number of simplices sharing a given vertex, 
-    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
+    While we will utilize $\diameterratio(\calT)$ at numerous places throughout the manuscript, 
+	$\volumeratio(\calT)$ and $\reflectionestimate(\calT)$ will only be used throughout Section~\ref{section:gradient},
+	the following section.  
+	Lemma~\ref{lemma:volumecomparison} obviously shows that $\volumeratio(\calT)$ of~\eqref{math:volumeratio} is controlled by the shape measure.
+In a face-connected triangulation where we have an upper bound for the number of simplices sharing a vertex,
+    this Lemma also allows control of $\diameterratio(\calT)$ of~\eqref{math:diameterratio}.
 \end{remark}
-%%%%%%%% END HERE
 
@@
 %             + 
-%             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+%             \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
 %             \| \nabla u \|_{L^{p}(T_{m-1})}
 %         \right)
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \reflectionestimate(\calT)^{q} \right)^{\frac 1 q}
         C_{\PF,T_{m},F_{m},p} 
@@
         \leq 
-        \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
         \| \nabla w \|_{L^{p}(T_{m-1})}
@@
         =
-        \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
         \| \nabla u \|_{L^{p}(T_{m-1})}
@@
             + 
-            \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
+            \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
         \| \nabla u \|_{L^{p}(T_{m-1})}
@@
         ,
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
+        \left( 1 + \volumeratio(\calT)^{\frac q p} \reflectionestimate(\calT)^{q} \right)^{\frac 1 q}
         C_{\PF,T_{\ell},F_{\ell},p} 

### 2024-10-04 shape.tex
shape measures

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{align*} % First pair 
        \frac{\diam(T)}{\sqrt 2} 
        \leq 
        \matnorm{ \Jacobian \varphi } 
        \leq 
        \sqrt{n} \diam(T).
    \end{align*}
    \begin{align*} % Second pair
        \sqrt{n}^{-1} \height(T)^{-1} 
        \leq 
        \matnorm{ \Jacobian \varphi^{-1} } 
        \leq 
        \sqrt{n} \cdot \height(T)^{-1}
        .
    \end{align*}
    \begin{align*} % Third / fourth pair 
        \frac{ \height(T)    }{\sqrt{n}} \leq \matnorm{ A      } \leq \algebraicshapemeasure(A) \sqrt{n} \height(T),
        \quad 
        \frac{ \diam(T)^{-1} }{\sqrt{n}} \leq \matnorm{ A^{-1} } \leq \algebraicshapemeasure(A) \sqrt{2} \diam(T)^{-1}.
    \end{align*}
    \begin{align*}
        \frac{\aspectratio(T)}{\sqrt{2n}} \leq \algebraicshapemeasure(T) \leq n \aspectratio(T).
    \end{align*}

\end{lemma}
\begin{proof}
    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine transformation and let $M := \Jacobian\phi$ be its Jacobian. 
    We begin with observing that the largest $\ell^{2}$-norm of any column of $A$,
    which here denote by $c_{\max}(A)$, 
    equals the maximum of the quotient $\| A x\|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
    We also know that the diameter of $T$ is the length of its longest edge. 
    Our first pair of inequalities follows via standard comparisons of Euclidean norms
    \begin{align*}
        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ A } \leq \sqrt{n} c_{\max}(A) \leq \sqrt{n} \diam(T).
    \end{align*}
    The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
    except for the vertex $\varphi(0)$. It immediately follows that 
    \begin{align*}
        \matnorm{ \Jacobian \varphi^{-1} } \leq \sqrt{n} c_{\max}(A^{-1}) \leq \sqrt{n} \cdot \height(T)^{-1}
        .
    \end{align*}
    The smallest height in the reference simplex $\Delta^{n}$ is $\height_{\Delta} = 1/\sqrt{n}$, 
    whence $\height(T) \geq \matnorm{A^{-1}}^{-1} / \sqrt{n}$. This yields our second pair of inequalities. 
    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)$.
    All relevant results follow.

    Next, the above results also imply 
    \begin{align*}
        \matnorm{ A      } \geq \matnorm{ A^{-1} }^{-1} \geq \frac{ \height(T)    }{\sqrt{n}},
        \quad 
        \matnorm{ A^{-1} } \geq \matnorm{ A      }^{-1} \geq \frac{ \diam(T)^{-1} }{\sqrt{n}}.
    \end{align*}
    \begin{align*}
        \| A \| &\leq \algebraicshapemeasure(A) \matnorm{A^{-1}}^{-1} \leq \algebraicshapemeasure(A) \sqrt{n} \height(T),
        \\
        \| A^{-1} \| &\leq \algebraicshapemeasure(A) \matnorm{A}^{-1} \leq \algebraicshapemeasure(A) \sqrt{2} \diam(T)^{-1}.
    \end{align*}
    This shows the last two pairs of inequalities. The comparison of shape measures is a consequence. 
\end{proof}

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \matnorm{\Jacobian \varphi}
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \matnorm{ \Jacobian \varphi^{-1} }
        \leq 
        \Czwei{n} \cdot 
        \geometricshapemeasure(T) 
        \diam(T)^{-1}
        ,
        \\
        \algebraicshapemeasure(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \geometricshapemeasure(T)
        ,
        \qquad 
        %         \geometricshapemeasure(T)^{\frac 1 n}
        %         \leq 
        \aspectratio(T)
        \leq 
        \geometricshapemeasure(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
        \quad 
        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows by taking the reciprocal. 
    The definition of the condition number now gives the third inequalities. 
    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
    Finally, 
    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
    \begin{align*}
        \frac{ \diam(T) }{ \height(T) }
        \leq 
        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
        \leq 
        \frac{ \diam(T)^{n} }{ n! \vol(T) }
        .
    \end{align*}
%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
%     \begin{align*}
%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
%         \leq 
%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
%         .
%     \end{align*}
    That shows the fourth and last of the inequalities. 
\end{proof}

\begin{remark}
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions. $\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

\begin{comment}
    On the other hand, 
    \begin{align*}
        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
%         \\
%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        h_1 \leq \aspectratio(T_{1}) \diam(F),
        \qquad 
        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
    \begin{align*}
        \matnorm{ \Jacobian \Xi }
        \leq 
        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }
        \leq 
        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
        \leq 
        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
        \leq 
        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
        .
    \end{align*}
%     \begin{align*}
%         \matnorm{ \Jacobian \Xi }
%         &
%         \leq 
%         \Ceins{n}
%         \Czwei{n}
%         \geometricshapemeasure(T_2)
%         \diam(T_1)
%         \diam(T_2)^{-1}
%         \\&
%         \leq 
%         \Ceins{n}
%         \Czwei{n}
%         \geometricshapemeasure(T_2)
%         \geometricshapemeasure(T_1) 
%         \diam(F)
%         \diam(T_2)^{-1}
%         \leq 
%         \Ceins{n}
%         \Czwei{n}
%         \geometricshapemeasure(T_2)
%         \geometricshapemeasure(T_1) 
%         .
%     \end{align*}
    All the desired results thus follow.
\end{comment}

### 2024-10-04 main.tex
some clean up

@@
 \usepackage{comment}          % 
-\usepackage{hyperref}         % For hypertext links
+\usepackage[colorlinks=true]{hyperref}         % For hypertext links
+% Make the hyperlinks look similar to arXiv's
+\hypersetup{
+    colorlinks=true,
+    linkcolor=green,    % Color of internal links (sections)
+    citecolor=red,    % Color of citations
+    urlcolor=blue,     % Color for URLs
+    urlbordercolor={1 1 1},
+    pdfborder={0.5 0.5 0}  % Removes the border around the links
+}
 \usepackage{tikz-3dplot}      % 3d plots 
@@
 \end{align*} 
-Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
+Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
 \begin{align}\label{math:intro:poincare:grad}
@@
     \leq 
-    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
+    C_{\varnothing,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
     \quad 
@@
     \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: \overline C_{\grad,\Omega,p}}
+    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: C_{\varnothing,\Omega,p}}
     .
@@
 \end{align*} 
-Its operator norm is the best constant $\overline C_{\grad,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
+Its operator norm is the best constant $C_{\varnothing,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
 \begin{align}\label{math:P_gradient}
@@
     \leq 
-    \overline C_{\grad,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
+    C_{\varnothing,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
     \quad 
@@
 \begin{align*}
-    C_{\grad,\Omega,p} \leq \overline C_{\grad,\Omega,p}.
+    C_{\grad,\Omega,p} \leq C_{\varnothing,\Omega,p}.
 \end{align*}
@@
 \begin{align*}
-    C_{\grad,\Omega,p} \leq 2 \overline C_{\grad,\Omega,p}.
+    C_{\grad,\Omega,p} \leq 2 C_{\varnothing,\Omega,p}.
 \end{align*}
@@
 \begin{align*}
-    \overline C_{\grad,\Omega,2} = C_{\grad,\Omega,2}. 
+    C_{\varnothing,\Omega,2} = C_{\grad,\Omega,2}. 
 \end{align*}
@@
 \begin{align}\label{math:p_vs_pf}
-    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} \overline C_{\grad,\Omega,p}.
+    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} C_{\varnothing,\Omega,p}.
 \end{align}
@@
 We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
+if there exists a constant $C_{\grad,\Omega,p} \geq 0$ such that the following holds:
 for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
@@
     \leq 
-    C_{\PF,\Omega,p} 
+    C_{\grad,\Omega,p} 
     \| \bff \|_{L^{p}(\Omega)}
@@
     \leq 
-    C_{\PF,\Omega,p} 
+    C_{\grad,\Omega,p} 
     \| \nabla u \|_{L^{p}(\Omega)},
@@
 \end{align*}
-We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$.
-
-\mwl{Use Martin's notation for these constants}
+We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$.
 
@@
 we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{{{\rm P}},\Omega,p} \geq 0$ such that 
+if there exists $C_{\varnothing,\Omega,p} \geq 0$ such that 
 % for all $u \in W^{1,p}(\Omega)$
@@
     \leq 
-    C_{{\rm P},\Omega,p} 
+    C_{\varnothing,\Omega,p} 
     \| \nabla u \|_{L^{p}(\Omega)}
@@
 \[
-    C_{{\PF},\Omega,p} \leq C_{{\rm P},\Omega,p}.
+    C_{\grad,\Omega,p} \leq C_{\varnothing,\Omega,p}.
 \]
@@
 \begin{align}\label{math:p_is_smaller_than_pf}
-    C_{\grad,\Omega,p} \leq 2 \overline C_{\grad,\Omega,p}.
+    C_{\grad,\Omega,p} \leq 2 C_{\varnothing,\Omega,p}.
 \end{align}
@@
 \begin{align}\label{math:pf_equals_p_in_hilbertspace}
-    \overline C_{\grad,\Omega,2} = C_{\grad,\Omega,2}. 
+    C_{\varnothing,\Omega,2} = C_{\grad,\Omega,2}. 
 \end{align}
 % This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$. 
-THis improvement also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+This improvement also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
 Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
@@
 \begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\grad,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
+\end{align*}
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
@@
 \end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
+Its operator norm is just the optimal Poincar\'e constant $C_{\varnothing,\Omega,p}$.
 
@@
 \subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains} \label{section: PX_convex}
-
-\mwl{Agree on a convention for these constants: diameter included or not.}
 
@@
 where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
-% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
 When $\calT$ is an $n$-dimensional simplicial complex, we naturally define 
@@
 We call these the aspect and algebraic shape measure, respectively, of the triangulation.
+
+\begin{remark}
+    The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is instance of a so-called \emph{shape measure}.
+	For example, the reference triangle has aspect shape measure $1$ and the reference tetrahedron has aspect shape measure $\sqrt{3/2}$. 
+	Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
+	\cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here.
+	\cite[Definition~11.2]{ern2021finite}). 
+\end{remark}
 
@@
 In a face-connected triangulation where we have an upper bound for the number of simplices sharing a vertex,
-    this Lemma also allows control of $\diameterratio(\calT)$ of~\eqref{math:diameterratio}.
+    this Lemma also allows, at least in principle, control of $\diameterratio(\calT)$ of~\eqref{math:diameterratio}.
 \end{remark}
@@
 The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ \Minako_m \}$ with a face-connected path.
+Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches $\{ \Minako_m \}$ of $n$-simplices with an appropriate notion of connectivity.
 The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$.

### 2024-10-04 main.tex
minor polishment in first few sections

@@
 
+\mwl{
 In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
@@
 % Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-
-We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
-We take the opportunity to discuss bounded convex domains as a preparatory special case.
-This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
+}
+
+This section surveys variations of the Poincar\'e--Friedrichs inequalities for the gradient operator,
+with emphasis on analytical upper bounds over bounded convex domains. 
+We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potential operators.
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
 \\
@@
 and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
+Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$.
 
@@
 \end{align*}
-A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
+A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
+\begin{align*}
+    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
     \quad 
@@
 
-\subsection{A triangulation or a simplicial complex}
+% \subsection{A triangulation or a simplicial complex}
 
@@
     \begin{align*}
-        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ M } \leq \sqrt{n} c_{\max}(M) \leq \sqrt{n} \diam(T).
+        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ M } \leq \sqrt{n} \cdot c_{\max}(M) \leq \sqrt{n} \cdot \diam(T).
     \end{align*}
     The columns of the matrix $M^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
-    except for the vertex $\varphi(0)$. It immediately follows that 
+    except for the vertex $\varphi(0) \in T$. It immediately follows that 
     \begin{align*}
@@
     whence $\height(T) \geq \matnorm{M^{-1}}^{-1} / \sqrt{n}$. This yields our second pair of inequalities. 
-    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)$.
+    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)^{-1}$.
     All relevant results follow.
@@
 
-We are interested in the maximal ratio of volumes between face-neighboring $n$-simplices, written $\volumeratio(\calT)$,
+We will need the maximal ratio of volumes between face-neighboring $n$-simplices, written $\volumeratio(\calT)$,
 and the ratio of the diameters of any intersecting simplices, written $\diameterratio(\calT)$. Formally, 
@@
 
-\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ 
-\begin{gather*}
-    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}}
+% \cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ 
+% \begin{gather*}
+    % W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
+    % .
+% \end{gather*}}
 Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
@@
 Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
-We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega)$.
+We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega) = L^{p}(\Omega)$.
+We use the abbreviation $W^{1,p}_{0}(\Omega) := W^{p}\Lambda^{0}(\Omega)$.
 
@@
 
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}
+\subsection{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}
 
@@
 
-\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}
+\subsection{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}
 
@@
     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
+    % For each $u \in W^{1,2}_{0}(\Omega)$ there exists $w \in W^{1,p}_{0}(\Omega)$ with $\grad \bfw = \grad \bfu$ and 
+    % \begin{align*}
+        % \| w \|_{L^{2}(\Omega)} 
+        % \leq 
+        % \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
+        % .
+    % \end{align*}
+	For each $\bfu \in \bfW^{p}(\divergence,\Omega)$ there exists $\bfw \in \bfW^{p}(\divergence,\Omega)$ with $\divergence \bfw = \divergence \bfu$ and 
     \begin{align*}
@@
     This is a reduction to the Friedrichs inequality. 
-    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
+    The space $W^{1,2}_{0}(\Omega)$ is the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
     Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 

### 2024-10-04 draft.tex
further polishment

@@
 \begin{document}
+
+\section{{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and {analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
+
+\mwl{
+In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
+We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
+In particular, we take the opportunity to discuss bounded convex domains as a special case.
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
+
+It is generally easier to obtain upper bounds Constructing and analyzing a potential operator is generally easier if the potential is linear. 
+Constructing linear potential operators is generally easier 
+We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+
+% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
+}
+
+In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
+We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
+In particular, we take the opportunity to discuss convex domains as a special case.
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
+
+\subsection{Nonlinear and linear potentials}
+
+In the Banach setting $p \neq 2$, finding a norm-minimizing potential such as $\Phi_{\grad}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$ is a nonlinear operation.
+Its existence may actually not be guaranteed unless $1 < p < \infty$.
+However, any \textit{linear} potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+satisfying $\nabla \overline\Phi_{\grad}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ has the operator norm that \cye{gives} the upper bound 
+\begin{align}\label{math:PF_P}
+    \mwl{C_{\grad,\Omega,p} = } 
+    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }
+    \leq 
+    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: C_{\varnothing,\Omega,p}}
+    .
+\end{align}
+This explains our interest in the construction of {\em linear potential operators}.
+
+\subsection{Poincar\'e--Friedrichs and Poincar\'e inequalities}
+
+\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\grad}( \bff ) = \bff$ determines $\overline \Phi_{\grad}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
+\begin{align*}
+    \overline\Phi_{\grad}( \nabla u ) \cye{:}= u - u_{\Omega},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    ,
+\end{align*}
+where $u_\Omega$ denotes the average of $u$ over the domain $\Omega$, that is,
+\begin{align*}
+    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
+\end{align*}
+This potential operator can also implicitly be defined by
+\begin{align*}
+    \overline \Phi_{\grad}( \bff ) 
+    := 
+    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\fooL^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*} 
+Its operator norm is the best constant $C_{\varnothing,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
+\begin{align}\label{math:P_gradient}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\varnothing,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    . 
+\end{align}
+Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient}, 
+\begin{align*}
+    C_{\grad,\Omega,p} \leq C_{\varnothing,\Omega,p}.
+\end{align*}
+
+Towards a converse inequality, 
+let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
+\begin{align} \label{math:aver_norm}
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    = 
+    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
+    \leq 
+    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
+    = 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align}
+Here, we have used H\"older's or Jensen's inequality. 
+In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
+We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
+The triangle inequality now shows that 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)} 
+    \leq
+    2
+    \| u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+\begin{align*}
+    \color{Emerald}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
+    \leq 
+    2^{p-1} 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    +
+    2^{p-1} 
+    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
+    \leq 
+    2^{p} 
+    \| u \|_{L^{p}(\Omega)}^{p}
+    .
+\end{align*}
+\mwl{Via an application of the triangle inequality, }Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
+\begin{align*}
+    C_{\grad,\Omega,p} \leq 2 C_{\varnothing,\Omega,p}.
+\end{align*}
+In the special case $p=2$, taking the average is an orthogonal projection, 
+and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
+Hence,
+\begin{align*}
+    C_{\varnothing,\Omega,2} = C_{\grad,\Omega,2}. 
+\end{align*}
+\mwl{
+This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
+and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
+Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
+since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
+}
+From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
+\begin{align*}
+    \| u - u_\Omega \|_{L^{p}(\Omega)}
+    \leq 
+    \min\left( 2, 2^{|2/p-1|} \right)
+    \| u \|_{L^{p}(\Omega)}
+    = 
+    2^{|2/p-1|} 
+    \| u \|_{L^{p}(\Omega)}
+    ,
+    \quad 
+    \forall 
+    u \in L^{p}(\Omega)
+    .
+\end{align*}
+Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
+The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
+We thus conclude 
+\begin{align}\label{math:p_vs_pf}
+    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} C_{\varnothing,\Omega,p}.
+\end{align}
+In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
+
+%%%%
 

### 2024-10-04 main.tex
further polishment

@@
 
-\section{{Nonlinear and linear potentials, the Poincar\'e--Friedrichs and Poincar\'e inequalities, and {analytical} Poincar\'e--Friedrichs constants in the gradient case}} \label{section:poincare}
-
-In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
-We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
-In particular, we take the opportunity to discuss convex domains as a special case.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
-
-\subsection{Nonlinear and linear potentials}
-
-In the Banach setting $p \neq 2$, finding a norm-minimizing potential such as $\Phi_{\grad}( \bff )$ of~\eqref{math:pot_grad_def} for a given gradient $\bff$ is a nonlinear operation.
-Its existence may actually not be guaranteed unless $1 < p < \infty$.
-However, any \textit{linear} potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi_{\grad}( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ has the operator norm that \cye{gives} the upper bound 
-\begin{align}\label{math:PF_P}
-    \mwl{C_{\grad,\Omega,p} = } 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} } \cye{=: C_{\varnothing,\Omega,p}}
-    .
-\end{align}
-This explains our interest in the construction of {\em linear potential operators}.
-
-\subsection{Poincar\'e--Friedrichs and Poincar\'e inequalities}
-
-\cye{In the setting of Section~\ref{section:intro_grad}, when $\Omega$ is of finite measure,} a natural \cye{(and unique, since the gradient potential constraint $\nabla \overline \Phi_{\grad}( \bff ) = \bff$ determines $\overline \Phi_{\grad}( \bff )$ up to a constant)} choice \cye{for a linear potential operator} is the average-free potential operator $\overline\Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that is prescribed by
-\begin{align*}
-    \overline\Phi_{\grad}( \nabla u ) \cye{:}= u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_\Omega$ denotes the average of $u$ over the domain $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-This potential operator can also implicitly be defined by
-\begin{align*}
-    \overline \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \int_\Omega u = 0 } } \| \nabla u - \bff \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the best constant $C_{\varnothing,\Omega,p} > 0$ in the {\em Poincar\'e inequality} (or also Poincar\'e--Wirtinger inequality)
-\begin{align}\label{math:P_gradient}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\varnothing,\Omega,p} \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    . 
-\end{align}
-Thus, rephrasing~\eqref{math:PF_P} in terms of~\eqref{math:PF_gradient_2} and~\eqref{math:P_gradient}, 
-\begin{align*}
-    C_{\grad,\Omega,p} \leq C_{\varnothing,\Omega,p}.
-\end{align*}
-
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align} \label{math:aver_norm}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-\begin{align*}
-    \color{Emerald}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
-    \leq 
-    2^{p-1} 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    +
-    2^{p-1} 
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    \leq 
-    2^{p} 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align*}
-\mwl{Via an application of the triangle inequality, }Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align*}
-    C_{\grad,\Omega,p} \leq 2 C_{\varnothing,\Omega,p}.
-\end{align*}
-In the special case $p=2$, taking the average is an orthogonal projection, 
-and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
-Hence,
-\begin{align*}
-    C_{\varnothing,\Omega,2} = C_{\grad,\Omega,2}. 
-\end{align*}
-\mwl{
-This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$,
-and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
-}
-From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, where we reproduce the improved estimate for the Hilbert space case.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} C_{\varnothing,\Omega,p}.
-\end{align}
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-
-%%%%
-
-\section{Old : Review of Poincar\'e--Friedrichs constants}\label{section:poincare}
-
-\mwl{
-In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero.
-We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants.
-In particular, we take the opportunity to discuss bounded convex domains as a special case.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
-
-It is generally easier to obtain upper bounds Constructing and analyzing a potential operator is generally easier if the potential is linear. 
-Constructing linear potential operators is generally easier 
-We will extend that construction of the potential when we address Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-
-% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.
-}
+\section{Review of Poincar\'e and Poincar\'e--Friedrichs inequalities}\label{section:poincare}
 
@@
 Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
-    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
+    Our use of the term \textit{face} as is common in classical geometry and the finite element literature~\cite{brenner2008mathematical}
     and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
@@
     Let $\calT$ be a triangulation.
-    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
+    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
     Write $U := T_1 \cup T_2$. 
@@
 We now collect important examples of shellable triangulations.
-Essentially, in two space dimensions, interesting triangulations shellable, but starting from three space dimensions, non-shellable situations can arise.
+Essentially, in two space dimensions, interesting triangulations are shellable, but starting from three space dimensions, non-shellable situations can arise.
 Our main interest are local patches (stars) within triangulations: these are shellable up to three space dimensions, but not necessarily beyond.
@@
 
-We state the simple observation that local stars can be subdivided to vertex stars.
-The shape regularity remains controlled in that process.
+We will use the following observaton, which we state without proof, 
+that controls the volume and some heights when a simplex is partitioned via barycentric subdivision.
 
@@
 scaled by $(k+1)^{-1}$.
+	\hfill\qed
     \end{itemize}
 \end{lemma}
-\begin{proof}
-    This is easy.
-\end{proof}
 
@@
     \end{tikzpicture}
+    \begin{tikzpicture}
+
+        % Coordinates of the triangle
+        \coordinate (A) at (0,0); % Vertex A = v_0
+        \coordinate (B) at (4,0); % Vertex B = v_1
+        \coordinate (C) at (1,3); % Vertex C = v_2
+        % Barycenter (centroid) of the triangle
+        \coordinate (G) at ($(A)!1/3!(B)!1/3!(C)$);
+        % Drawing the triangle
+        \draw[thick] (A) -- (B) -- (C) -- cycle;
+        % Tripartitioning the triangle: draw lines from vertices to the barycenter
+        \draw[] (A) -- (G);
+        \draw[] (B) -- (G);
+        \draw[] (C) -- (G);
+        % Heights from the barycenter to the sides of the triangle
+        \coordinate (H_GA) at ($(B)!(G)!(C)$); % Height from G to BC
+        \coordinate (H_GB) at ($(A)!(G)!(C)$); % Height from G to AC
+        \coordinate (H_GC) at ($(A)!(G)!(B)$); % Height from G to AB
+
+        % Drawing the height vectors from the barycenter
+        \draw[dashed,->,line width=1.0pt,>=latex] (H_GA) -- (G); % Height from G to BC
+        \draw[dashed,->,line width=1.0pt,>=latex] (H_GB) -- (G); % Height from G to AC
+        \draw[dashed,->,line width=1.0pt,>=latex] (H_GC) -- (G); % Height from G to AB
+
+        % Marking the points
+        \node[above right] at (C) {$v_2$};  
+        \node[below left] at (A) {$v_0$};
+        \node[below right] at (B) {$v_1$};
+        \node[right] at (G) {$z_T$};
+    \end{tikzpicture}
     \end{center}
     \caption{Illustration of Lemma~\ref{lemma:stardivision}.
-The triangle $[ v_0, v_1, v_2 ]$ is bisected at the edge $[ v_0, v_1 ]$, leading to two new triangles.
+Left: the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles.
 The height vector from $v_2$ in all three triangles remains the same.
-The height vector from $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector from $v_0$ in the original triangle.}
+The height vector from $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector from $v_0$ in the original triangle.
+Right: the triangle $T$ is trisected, leading to three new triangles.
+The height of $z_T$ to from some edge is one third of the original height of that edge.}
 \end{figure}

### 2024-10-04 main.tex
additional graphics

@@
 \begin{figure}[h]
-\centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
-\caption{A manifold triangulation (left) and not a manifold triangulation (right)}
+% \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
+\centering
+\begin{tikzpicture}[scale=0.8]
+    % Coordinates of the main outer triangle
+    \coordinate (B0)  at (0,-1); % Bottom left
+    \coordinate (BL)  at (-3,0); % Bottom right
+    \coordinate (BR)  at (3,0); % Bottom right
+    \coordinate (CLL) at (-3,2); % Bottom left
+    \coordinate (CL)  at (-1,1); % Bottom right
+    \coordinate (CR)  at ( 1,1); % Bottom right
+    \coordinate (CRR) at ( 3,2); % Bottom right
+    \coordinate (Z)   at (0,3.5); % Top
+    \coordinate (ML) at  (-0.8,2.2);% ($(CL)!0.3!(Z)$);
+    \coordinate (MR) at  ( 0.8,2.2);% ($(CR)!0.6!(Z)$);
+    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
+    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
+    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
+    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
+    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
+    \draw[thick,fill=gray!25] (ML) -- (CL) -- (CLL) -- cycle;
+    \draw[thick,fill=gray!25] (MR) -- (CR) -- (CRR) -- cycle;
+    \draw[thick,fill=gray!25] (Z) -- (ML) -- (CLL) -- cycle;
+    \draw[thick,fill=gray!25] (Z) -- (MR) -- (CRR) -- cycle;
+    \draw[thick,fill=gray!25] (Z) -- (ML) -- (MR) -- cycle;
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[scale=0.8]
+    % Coordinates of the main outer triangle
+    \coordinate (B0)  at (0,-1); % Bottom left
+    \coordinate (BL)  at (-3,0); % Bottom right
+    \coordinate (BR)  at (3,0); % Bottom right
+    \coordinate (CLL) at (-3,2); % Bottom left
+    \coordinate (CL)  at (-1,1); % Bottom right
+    \coordinate (CR)  at ( 1,1); % Bottom right
+    \coordinate (CRR) at ( 3,2); % Bottom right
+    \coordinate (Z)   at (0,3.5); % Top
+    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
+    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
+    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
+    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
+    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
+    \draw[thick,fill=gray!25] (Z) -- (CL) -- (CLL) -- cycle;
+    \draw[thick,fill=gray!25] (Z) -- (CR) -- (CRR) -- cycle;
+\end{tikzpicture}
+
+\caption{Left: manifold triangulation of an anulus. Right: not a manifold triangulation.}
 \label{figure:not_manifold_triang}

### 2024-10-05 main.tex
proofreading the text

@@
 \begin{abstract}
-    We construct potentials for the gradient, the curl, and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. 
-    This class of triangulations in particular includes local patches (stars) in dimension two and three.
-    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
+    We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations. 
+    The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry. 
+    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
     % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
+    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
     % 
@@
     As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over convex bounded domains. 
-    This is achieved through a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators where we can bound their operator norms.
+    This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
     \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
@@
 The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-We perform a discrete analogue of this procedure over triangulated domains: 
+We perform a discrete analog of this procedure over triangulated domains: 
 having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.
@@
 
-Two different variations of underlying idea are analyzed, yielding slighly different estimates. 
+Two different variations of the underlying idea are analyzed, yielding slightly different estimates. 
 On the one hand, we can extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that new simplex, subject to partial boundary conditions.
@@
 \begin{remark}
-    The Poincar\'e--Friedrichs constants obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimate the best one as number of $n$-simplices in the triangulation $\calT$ increases.
-We hence conceive their target application to be local patches (stars), in particular non-convex boundary stars.
+    The Poincar\'e--Friedrichs constants obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimate the best one as the number of $n$-simplices in the triangulation $\calT$ increases.
+    Hence, we conceive their target application to be local patches (stars), in particular non-convex boundary stars. 
     The latter occur inevitably at reentrant corners.
@@
     The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$. 
-This may allow for partitions of $\overline \Omega$ with signficantly less elements, which enables a largely improved estimate of the best Poincar\'e--Friedrichs constant.
+    This may allow for partitions of $\overline \Omega$ with significantly fewer elements, which enables a largely improved estimate of the best Poincar\'e--Friedrichs constant. 
 \end{remark}
@@
     The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
     scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
@@
 we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our goal are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
+However, our goal is explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
 
@@
     Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for our purpose in establishing Poincar\'e--Friedrichs constants. 
+    The resulting potential operators are sufficient for establishing Poincar\'e--Friedrichs constants over bounded convex domains. 
     The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
@@
     The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight, and which proves boundedness of the operators between a variety of function spaces. 
+    because their averaging uses a smooth weight, and thus they are bounded operators between a variety of function spaces. 
     Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
@@
     Their operators are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight; this proves boundedness of the operators between a variety of function spaces. 
+    because their averaging uses a smooth weight; this proves that the operators are bounded between a variety of function spaces. 
     Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
@@
 Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
-Local patches (stars) within triangulations of dimension two and three are examples of such shellable complexes. 
+Local patches (stars) within triangulations of dimension two or three are examples of such shellable complexes. 
 The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures} are our main references for this section. 
@@
     \coordinate (CLL) at (-3,2); % Bottom left
-    \coordinate (CL)  at (-1,1); % Bottom right
-    \coordinate (CR)  at ( 1,1); % Bottom right
+    \coordinate (CL)  at (-1,0.8); % Bottom right
+    \coordinate (CR)  at ( 1,0.8); % Bottom right
     \coordinate (CRR) at ( 3,2); % Bottom right
@@
     Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying set is a manifold $\calM$. 
+    Then the simplices contained in the boundary constitute a triangulation of the boundary.
+    Moreover, if $F \in \calT$ is a face (i.e, $F$ has dimension $n-1$), then 
     \begin{itemize}
-        \item Any face $F \in \Faces(\calT)$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
-        \item Any face $F \in \Faces(\calT)$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
-        \item The simplices contained in the boundary constitute a triangulation of the boundary.
+        \item $F$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
+        \item $F$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
         % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
@@
     \item
-    Let $F \in \Faces(T)$ and let $z_F \in F$ be its barycenter. 
+    Let now $F \in \subsimplex_{n-1}(T)$ be a face and let $z_F \in F$ be its barycenter. 
     Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ 
@@
     All manifolds of dimension up to three admit smooth structures and smooth manifolds admit combinatorial triangulations. 
-    There are triangulations of manifolds in dimension higher than $3$ where not every vertex star is homeomorphic to a ball.
-
-    Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
+    There are triangulations of manifolds in more than three dimensions where not every vertex star is homeomorphic to a ball.
+
+    Not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
     When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
@@
 
-We now provide the bi-Lipschitz nonlinear reflection across the interface between the selected simplex and the remainder of the local star
-as well as the bi-Lipschitz contraction from the local star onto the complement of the selected simplex.
+We now provide the desired bi-Lipschitz transformation:
+on the one hand, the nonlinear reflection across the interface between the selected simplex and the remainder of the local star,
+and on the other hand, the bi-Lipschitz contraction from the local star onto the complement of the selected simplex. 
+We give detailed estimates for the singular values of their Jacobians.
 
@@
 
-The most important outcome of this research have been computable upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches. 
-There are several avenues for further research going further from the results established in this manuscript.
-Our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), where there are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) \mwl{already} leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
-In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
-Better transformations or more careful estimates are likely possible, as are completely different approaches.
-For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
-
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we employ now.
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest.
-
-Concerning the geometric setting, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to topological balls and spheres.
+The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions. 
+There are several avenues for further research.
+
+Our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), as there are at least two areas where the present techniques could see further improvement.
+First, we use local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) likely allow room for improvement.
+Second, our construction uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
+In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques could lead to better estimates.
+
+With regard to estimating Poincar\'e--Friedrichs constants over single simplices, we conjecture that the Guerini--Savo~\cite{guerini2004eigenvalue} estimates, hitherto only known when $p=2$ and over bounded convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and convex Lipschitz domains.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently employ.
+
+Lastly, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is restricted to topological balls and spheres. 
 In particular, domains with shellable triangulations are contractible. 
-We expect that in the forthcoming works, these estimates will become subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+We expect forthcoming works to utilize these estimates as subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
 
@@
 % such as the Hodge Laplace equation. 
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
 

### 2024-10-05 main.tex
singular values inserted

@@
 
-We return to the theory of triangulations,
-as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulate manifolds. 
-Our particular interest are manifold triangulations that are \emph{shellable}.
-Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. 
+We return to the theory of triangulations, as our main objective requires some further concepts.
+We are interested in simplicial complexes that triangulated domains and which are \emph{shellable}.
+Such simplicial complexes are constructed by successively adding simplices in a well-structured manner. 
 Local patches (stars) within triangulations of dimension two or three are examples of such shellable complexes. 
@@
 The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball\mwl{, and we sometimes call this a \textit{$n$-disk} triangulation}.
+an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball, and we sometimes call this an \textit{$n$-disk} triangulation.
 An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
@@
 we gather some results that are hard to find in the literature.
-
-We say that an $n$-dimensional manifold triangulation $\calT$ is \emph{combinatorial}
-if for every vertex $V \in \calT$ the local star $\patch_{\calT}(V)$ is a simplicial ball of dimension $n$.
 
@@
     Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
-    has vertices $v_0, v_1, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$. 
+    has vertices $v_0$, $v_1$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$. 
     For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
@@
 
-\begin{remark}
-    We interpret a shelling as the construction of a triangulation 
-    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
-    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
-\end{remark}
-\begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
-    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
-    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
-\end{remark}
-
 The reason of our interest in shellable simplicial complexes is that they can be constructed via successive adhesion of simplices.
@@
 \begin{example}\label{example:shell_simpl}
-    Any simplex $T$ (trivially) has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
-    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling\mwl{; see Example 8.2.(iii) in~\cite{ziegler1995lectures}}.
+    Any simplex $T$ (trivially) has a shelling, consisting only of $T$ itself. 
+	The boundary complex $\partial \calT(T)$ has a shelling:
+    any enumeration of the boundary faces of $T$ constitutes a shelling\mwl{; see Example 8.2.(iii) in~\cite{ziegler1995lectures}}.
 \end{example}
@@
     and assume that $\calT$ includes $N+1$ triangles. 
-    There are at least two triangles with an edge on the boundary. 
+	As we travel along the boundary, we traverse along edges of at least two simplices, 
+	and therefore there are at least two triangles with an edge on the boundary. 
     Suppose that $\calT$ does not have at least two triangles that are good in $\calT$.
@@
     in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk.
+    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk. % TODO: why are those two disks?
     By the induction assumption, each of those components contains at least two triangles 
     that are good in the respective component. 
-    So each component has at least one triangle that is good in $\calT$. 
+    So each component has at least one triangle that is also good in $\calT$. 
     Hence $\calT$ contains two good triangles, which completes the induction step.
@@
     Not all triangulable sets admit a triangulation that is shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations are be shellable.
+    Moreover, even if a set admits a shellable triangulation, not all of its triangulations are shellable.
 For example, if we extend the non-shellable triangulation of the tetrahedron from~\cite[Example 8.9]{ziegler1995lectures} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
@@
 \end{proof}
+
+\begin{remark}
+    We interpret a shelling as the construction of a triangulation 
+    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
+    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
+\end{remark}
+\begin{remark}
+    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
+    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
+    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
+\end{remark}
 
@@
 \begin{proposition}\label{proposition:starreflection}
-    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be a simplex of dimension $k < n$,
+    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
+    Let $S \in \calT$ be an inner simplex of dimension $k < n$,
     let $T \in \patch_{\calT}(S)$ be of dimension $n$,
@@
     which is the identity along ${\Gamma_1} = T \cap U$. 
-    Its singular values $\sigma_1 \geq \dots \geq \sigma_n$ satisfy 
-    \begin{align*}
-        \sigma_1 &\leq ...
-        \\
-        \sigma_i &\leq ..., \quad 2 \leq i \leq n-1,
-        \\
-        \sigma_n &\leq ...
-    \end{align*}
-    and which satisfies the upper bounds 
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
     \begin{gather*}
-        \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
+        \sigma_1 \leq \Cfive{n}{k}(\calT),
         \quad 
-        \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
-        \\
+        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{k}(\calT),
+        \quad 
         | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
+        \\
+        \sigma_n \leq \Csechs{n}{k}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{k}(\calT),
         \quad 
@@
     \end{gather*}
+%     and which satisfies the upper bounds 
+%     \begin{gather*}
+%         \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
+%         \quad 
+%         \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
+%         \\
+%         | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
+%         \quad 
+%         | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
+%     \end{gather*}
     \item 
@@
     which is the identity along $\partial U \setminus \partial T$.
-    Its singular values $\sigma_1 \geq \dots \geq \sigma_n$ satisfy 
-    \begin{align*}
-        \sigma_1 &\leq ...
-        \\
-        \sigma_i &\leq ..., \quad 2 \leq i \leq n-1,
-        \\
-        \sigma_n &\leq ...
-    \end{align*}
-    and which satisfies the upper bounds 
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
     \begin{gather*}
-        \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
+        \sigma_1 \leq \Csieb{n}{k}(\calT),
         \quad 
-        \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
-        \\
+        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{k}(\calT),
+        \quad 
         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
+        \\
+        \sigma_n \leq \Cacht{n}{k}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{k}(\calT),
         \quad 
@@
     \end{gather*}
+%     and which satisfies the upper bounds 
+%     \begin{gather*}
+%         \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
+%         \quad 
+%         \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
+%         \\
+%         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
+%         \quad 
+%         | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
+%     \end{gather*}
     \end{enumerate}
 \end{proposition}
-\mwl{TODO: throughout this manuscript, all vector and operator norms should indicate the exponent.}
 \begin{proof}
@@
 
-        \mwl{Check that $\calS'$ is a triangulation...}
+        % TODO Check that $\calS'$ is a triangulation...
 
@@
         Its square roots are the desired singular values of $B$:
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
-            ,
-            \\
-            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
-            .
-        \end{align*}
+        \begin{align}
+            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
+            ,
+            \\
+            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
+            .
+        \end{align}
         They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
@@
         We abbreviate 
-        \begin{align*}
+        \begin{align}\label{math:upper_bound_for_theta}
             B_{T} 
@@
             .
-        \end{align*}
+        \end{align}
 
@@
         We conclude that 
-        \begin{gather*}
+        \begin{gather}
             \matnorm{ \Jacobian\Phi_{K} } 
@@
             \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
+			\leq 
+            1 + \frac{3}{2} (k+1) \aspectratio(T) 
+			\label{math:phi_max}
             ,
@@
             \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            .
-        \end{gather*}
+            \leq 
+            2 + 3 (k+1) \aspectratio(T) 
+			\label{math:phi_min}
+            .
+        \end{gather}
         This finishes the discussion of the transformation $\Phi$.
@@
         \begin{align*}
-            \Psi : |\calR'| \rightarrow |\calK|.
+            \Psi : |\calR'| \rightarrow \underlying{\calK}.
         \end{align*}
@@
         so they must contain an open ball around the origin. 
-        \mwl{Here we need a particular result. }
+        % TODO \mwl{Here we need to show that it is indeed a ball. It must be a domain triangulation.}
         Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
@@
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            = 
+            \frac{ \| x_K \| }{ \| x_{{G}} \| }
             \leq 
@@
             \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
+            = 
+            \frac{ \| x_{G} \| }{ \| x_{K} \| }
             \leq 
@@
         \end{align*}
-
+        In summary, using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, we find the upper bounds 
+        \begin{align*}
+            \matnorm{ \Jacobian\Psi(x) }
+            &\leq  
+            (k+1)B_{T}
+            \diameterratio(\calT)
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \cdot 
+			\left( 
+                1 
+				+ 
+				(k+1) 
+				\left( 1 + B_{T} \right)
+				\aspectratio(\calT) 
+            \right)
+			,
+            \\
+            \matnorm{ \Jacobian\Psi(z)^{-1} }
+            &\leq  
+            (k+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \cdot 
+			\left( 
+                1 
+				+ 
+				(k+1) 
+				\left( 1 + B_{T} \right)
+				\aspectratio(\calT) 
+            \right)
+			,
+            \\
+            \det\Jacobian\Psi(x)
+            &\leq 
+            \left( 
+            (k+1)B_{T}
+            \diameterratio(\calT)
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \right)^{n},
+            \\
+            \det\Jacobian\Psi^{-1}(x)
+            &\leq 
+            \left( 
+            (k+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \right)^{n}
+        \end{align*}
         We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
-        It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
-        Rademacher's theorem then shows that both have essentially bounded weak Jacobians.
-
-        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-        After application of a piecewise linear Lipschitz mapping, 
-        we can assume that $|\calK|$ is convex without loss of generality. 
-        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-        \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
+        % It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
+        % Rademacher's theorem then shows that both have essentially bounded weak Jacobians. 
+        Every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $\underlying{\calK}$, since there exists a bi-Lipschitz transformation from $\underlying{\calK}$ onto the unit ball.
+        % We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+        % After application of a piecewise linear Lipschitz mapping, 
+        % we can assume that $\underlying{\calK}$ is convex without loss of generality. 
+        % Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $\underlying{\calK}$. 
+        % \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
 
         \item 
-        \mwl{Use interlacing inequalities.}
         We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
@@
         Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
-        % We briefly recapitulate why it is bi-Lipschitz.
-%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
-%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-%         After application of a piecewise linear Lipschitz mapping, 
-%         we can assume that $|\calK|$ is convex without loss of generality. 
-%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
-%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
-        The combination of the previous estimates for $\Psi$ and $\Theta$,
-        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
-        provide 
-        \begin{align*}
-            \matnorm{ \Jacobian \Xi_{1} }
+        Combining the previous estimates for $\Psi$ and $\Theta$ with interlacing inequalities for the singular values of product matrices provides 
+        \begin{align*}
+            \sigma_1(x) = \matnorm{ \Jacobian \Xi_{1} }
             &\leq 
@@
             \\
-            \matnorm{ \Jacobian \Xi_{1}^{-1} }
+            \sigma_2(x), \dots, \sigma_n(x) 
+            &\leq 
+            \Cfiveprime{n}{k}(\calT)
+            :=
+            (k+1)B_{T}
+            \diameterratio(\calT)
+            \aspectratio(T) 
+			\cdot 
+			B_T
+            \\
+            \sigma_n(x)^{-1} = \matnorm{ \Jacobian \Xi_{1}^{-1} }
             &\leq
@@
             \Big)
+            \\
+            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
+            &\leq 
+            \Csechsprime{n}{k}(\calT)
+            :=
+            (k+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \cdot 
+			B_T
             .
@@
         Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
-        The combination of the previous estimates for $\Psi$ and $\Phi$ now lead to 
-        \begin{align*}
+        The combination of the previous estimates for $\Psi$ and $\Phi$ with standard interlacing inequalities now lead to 
+        \begin{align*}
+            \sigma_1(x)
+            = 
             \matnorm{ \Jacobian \Xi_{2} }
@@
             :=
-            \frac 1 4
-            % \left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
-            \left( 4 + (k+1) \aspectratio(T) \right)
+            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
             \cdot 
@@
             \\
+            \sigma_2(x), \dots, \sigma_n(x) 
+            &\leq 
+            \Csiebprime{n}{k}(\calT)
+            :=
+            (k+1)B_{T}
+            \diameterratio(\calT)
+            \aspectratio(T) 
+			\cdot 
+			\left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            \\
+            \sigma_n(x)^{-1}
+            = 
             \matnorm{ \Jacobian \Xi_{2}^{-1} }
@@
             :=
-            \frac 1 2
-            %\left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
-            \left( 4 + (k+1) \aspectratio(T) \right)
+            \left( 2 + 3 (k+1) \aspectratio(T) \right)
             \cdot 
@@
             \Big)            
-        \end{align*}
-        We get the determinant estimate 
+            \\
+            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
+            &\leq 
+            \Cachtprime{n}{k}(\calT)
+            :=
+            (k+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \cdot 
+			\left( 2 + 3 (k+1) \aspectratio(T) \right)
+            .
+        \end{align*}
+        We get the determinant estimates 
         \begin{align*}
@@
 
+\begin{proof}
+    We begin with the following preparatory observations. 
+    Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
+    We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
+    That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
+    Then the mapping 
+    \begin{align}
+        F_T(x) 
+        = 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
+    \end{align}
+    maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
+    \begin{align}
+        F_T^{-1}(x) 
+        = 
+        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
+        .
+    \end{align}
+    We analyze its Lipschitz properties.
+    % 
+    In what follows, $y \in \bbR^{n}$. 
+    On the one hand, 
+    we compute the Jacobian at any $x \in \mathring T$:
+    \begin{align*}
+        \Jacobian F_T(x) \cdot y
+        &= 
+        \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
+        \left( \vecone \cdot A_{T}^{-1} x \right)
+        + 
+        \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
+        \\&= 
+        \left( \Id - \|x\|^{-2} x \otimes x^t \right)
+        \frac{ 1 }{ \|x\| } 
+        \left( \vecone \cdot A_{T}^{-1} x \right)
+        + 
+        \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        \left( \Id - \hat x \otimes \hat x^t \right) y
+        + 
+        \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+        .
+    \end{align*}
+    This is an orthogonal sum of two vectors. Its norm satisfies:
+\begin{align*}
+        \| \Jacobian F_T(x) \cdot y \|^{2}
+        &= 
+        \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
+        \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
+        + 
+        \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
+        .
+    \end{align*}
+    The Euclidean operator norm satisfies 
+    \begin{align*}
+        \| \Jacobian F_T(x) \| 
+        \leq 
+        \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
+        \leq 
+        \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
+        .
+    \end{align*}
+    On the other hand, we can rewrite the Jacobian as:
+    \begin{align*}
+        \Jacobian F_T(x) \cdot y
+        &= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        y
+        - 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        \left( \hat x \otimes \hat x^t \right) y
+        + 
+        \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        y
+        - 
+        \hat x 
+        \left( 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
+            -
+            \vecone^{t} A_{T}^{-1} 
+        \right) y
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        y
+        - 
+        \hat x 
+        \left( 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+            -
+            A_{T}^{-t} \vecone
+        \right)^{t} y
+        .
+    \end{align*}
+    Its inverse is found via the Woodbury formula: 
+    % Its inverse is easily verified to be:
+    \begin{align*}
+        \Jacobian F_T(x)^{-1}
+        &= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+        \Id
+        - 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
+        \hat x 
+        \left( 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+            -
+            A_{T}^{-t} \vecone
+        \right)^{t} 
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+        \left( 
+            \Id
+            - 
+            \hat x 
+            \left( 
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                \hat x
+                -
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                A_{T}^{-t} \vecone
+            \right)^{t}
+        \right)
+        \\&= 
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+        \left( 
+            \Id
+            - 
+            \hat x 
+            \left( 
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                \hat x
+                -
+                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                A_{T}^{-t} \vecone
+            \right)^{t}
+        \right)
+        \\&= 
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+        \left( 
+            \Id - \hat x \otimes \hat x^{t}
+            + 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \hat x \otimes \vecone^{t} A_{T}^{-1}
+        \right)
+        .
+    \end{align*}
+    The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
+    We notice the upper bound 
+    \begin{align*}
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+        &= 
+        \| A_{T}^{-1} \hat x \|^{-1}_{1}
+        \\&\leq  
+        \| A_{T}^{-1} \hat x \|^{-1}_{2}
+        \leq 
+        \sigma_{\min}( A_{T}^{-1} )^{-1}
+        = 
+        \sigma_{\max}( A_{T} )
+        .
+    \end{align*}
+    This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
+    %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
+    If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
+    \begin{align*}
+        \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
+        &\leq 
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left\| 
+%                 y
+%             \right\|^{2}
+%             +
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left| 
+%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+%                 \vecone^{t} A_{T}^{-1} y 
+%             \right|^{2}
+%             \\&\leq 
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+        \left\| 
+            y
+        \right\|^{2}
+        +
+        \frac{ 
+        \left| 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \vecone^{t} A_{T}^{-1} y 
+        \right|^{2}
+        }{
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
+        }
+        .
+    \end{align*}
+    The operator norm of that inverse is:
+    \begin{align*}
+        \| \Jacobian F_T(x)^{-1} \|
+        \leq 
+        \sigma_{\max}( A_{T} )
+        \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
+        .
+    \end{align*}
+    Since the domain and codomain of $F_{T}$ are convex, 
+    this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse. 
+\color{red}
+    On the one hand, given $x, y \in T$, 
+    where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
+    \begin{align*}
+        &
+        \left\| F_T(x) - F_T(y) \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+        \\&\qquad 
+        \leq 
+        2\sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
+        \left\| x - y \right\|_{2}
+        .
+    \end{align*}
+    On the one hand, given $x, y \in T$, 
+    where $\| x \|_{2} \leq \| y \|_{2}$ without loss of generality, we find 
+    \begin{align*}
+        &
+        \left\| F_T(x) - F_T(y) \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+        \frac{\|y\|}{\|x\|}
+        +
+        \|A_{T}^{-1} y\|_1 \|y\|_{2}
+        \left| \frac{1}{\|x\|} - \frac{1}{\|y\|} \right|
+        \\&\qquad 
+        \leq 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+        \frac{\|y\|}{\|x\|}
+        +
+        \|A_{T}^{-1} y\|_1 \|y\|_{2}
+        \left| \frac{ \|y\|_{2} - \|x\|_{2} }{\|x\|_{2} \|y\|_{2}} \right|
+        \\&\qquad 
+        \leq 
+        3 \sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
+        \left\| x - y \right\|_{2}
+        .
+    \end{align*}
+    On the other hand, given $x, y \in F_T(T)$, 
+    where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
+    \begin{align*}
+        &
+        \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|x\|_2 - \|y\|_2 \right|
+        \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} }
+        +
+        \|y\|_2^{2}
+        \left| 
+        \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} \| A_{T}^{-1} y \|_{1} }
+        \right|
+        \\&\qquad 
+        \leq 
+        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{2} } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|x\|_2 - \|y\|_2 \right|
+        \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{2} }
+        +
+        \|y\|_2^{2}
+        \left| 
+        \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{2} \| A_{T}^{-1} y \|_{2} }
+        \right|
+        \\&\qquad 
+        \leq 
+        \left( 2 + \sqrt{n} \frac{\sigma_{\max}(A_{T}^{-1}) }{ \sigma_{\min}(A_{T}^{-1}) } \right) \sigma_{\min}(A_{T}^{-1})^{-1} 
+        \left\| x - y \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left( 2 + \sqrt{n} \kappa(A_{T}) \right) \sigma_{\max}(A_{T})
+        \left\| x - y \right\|_{2}
+        .
+    \end{align*}
+    By convexity of the range of $F_T(T)$, 
+    we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
+    We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
+    \color{black}
+\end{proof}
+
 \end{document}

### 2024-10-06 main.tex
cleaning up the poincare section and some shellings

@@
 \begin{gather*}
-    \omega = 
+    \omega 
+	= 
+    \sum_{ \sigma \in \Sigma(k,n) } 
+    \omega_{\sigma} \, 
+    \cartanx^{\sigma}
+	= 
     \sum_{ \sigma \in \Sigma(k,n) } 
@@
     If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$. 
-    \mwl{If $\Omega$ is convex and $u \in W^{p}\Lambda^{n}(\Omega)$ has average zero, 
-    then $u$ is the limit in $W^{p}\Lambda^{k}(\Omega)$ of smooth compactly supported $n$-forms with average zero.}
+    %\mwl{If $\Omega$ is convex and $u \in W^{p}\Lambda^{n}(\Omega)$ has average zero, 
+    %then $u$ is the limit in $W^{p}\Lambda^{k}(\Omega)$ of smooth compactly supported $n$-forms with average zero.}
 \end{lemma}
@@
     The desired result follows. 
-
-    Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently msall radius. The proof is complete. 
+    % 
+    % Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently msall radius. The proof is complete. 
 \end{proof}
@@
 We compute 
-\begin{align}
+\begin{align*}
     &
@@
     .
-\end{align}
-Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{n-\mia}$. 
+\end{align*}
+% Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$. 
+Here we introduce the numerical constant 
+\begin{gather}\label{equation:A_Bogov}
+	A_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
+\end{gather}
+which depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$.
+
 In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
@@
     \leq 
-    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    n A_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
     \diam(\Omega)
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 %
@@
     \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
-    \label{equation:A_Bogov}
-    .
-\end{align*}
-Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
-and which is bounded by $2^{\mia-1}$. 
+    .
+\end{align*}
+% Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
+Here we introduce the numerical constant 
+\begin{gather}\label{equation:A_Bogov}
+	A_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
+\end{gather}
+which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
 In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
@@
     \leq 
-    n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    n A_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
     \diam(\Omega)
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
@@
     &= 
+    \vol(\Omega)^{-1}
 	\int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
@@
     &=
+    \vol(\Omega)^{-1}
 	\int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
@@
     &= 
+    \vol(\Omega)^{-1}
 	\int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
@@
     &=
-    - \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
+    - 
+	\vol(\Omega)^{-1}
+	\int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
     .
@@
     =
+    \vol(\Omega)^{-1}
 	\int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
@@
     =
+    \vol(\Omega)^{-1}
 	\int_{\Omega} \Bogov_{\mia,a} u(x) \,da
@@
 Taking into account cancellations, this gives the identity 
+\begingroup\allowdisplaybreaks
 \begin{align*}
@@
 \end{align*}
+\endgroup
 We conclude that, 
 \begin{align*}
-    u(x) &= \cartan \Poinc_{0,a} u(x) - u(a)
+    u(x) &= \Poinc_{1,a} \cartan u(x) - u(a), \qquad k = 0,
     \\
@@
 In summary, after taking the average over $a \in \Omega$:
-\begin{align*}
-    u(x) &= \cartan \Poinc_{0} u(x) - \vol(\Omega)^{-1} \int_\Omega u(a)
+\begin{align}\label{math:hodgedecomposition:poinc}
+    u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \,da, \qquad k = 0,
     \\
     u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
+\end{align}
 
@@
 \end{align*}
+We conclude that 
+\begin{align*}
+    u(x) &= \cartan \Bogov_{\mia,a} u(x) + \Bogov_{\mia+1,a} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
+    \\
+    u(x) &= \cartan \Bogov_{n,a} u(x) - \left( \int_{\Omega} u(a) \,da\right) \delta_a, \qquad k = n.
+\end{align*}
+Here, $\delta_a$ denotes the Dirac delta at $a$. 
 In summary, after taking the average over $a \in \Omega$:
-\begin{align*}\label{math:hodgedecomposition:bogov}
-    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n.
-\end{align*}
-In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
-We remark that the apparent structural difference between \eqref{math:hodgedecomposition:poinc} and \eqref{math:hodgedecomposition:bogov} is due to our assumption that $u$ extends to a smooth function with support within $\overline\Omega$.
-This structural difference will disappear soon when we discuss operators between Sobolev spaces of differential forms.
+\begin{align}\label{math:hodgedecomposition:bogov}
+    u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
+    \\
+    u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \,da\right) \chi_{\Omega}, \qquad k = n.
+\end{align}
 
@@
         &\leq 
-        n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        n A_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
         \diam(\Omega)
@@
         &\leq 
-        n A_{\Bogov}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        n A_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
         \diam(\Omega)
@@
     \end{align*}
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$ and $\cartan u = 0$, 
-    then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$ and $\int_\Omega u = 0$ in the case $k=n$, 
-    then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
-
-    \mwl{
-    If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
-    If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
-    }
+	For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
+	\begin{align}
+		u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a)
+		\label{math:theorem:PF_EC:poincare:zero}
+		\\
+		u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
+		\label{math:theorem:PF_EC:poincare:k}
+	\end{align}
+	In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
+
+	For any $u \in \bfW^{p}_{0}\Alt^{\mia}(\Omega)$ it holds that 
+	\begin{align}
+		u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
+		\label{math:theorem:PF_EC:bogov:k}
+		\\
+		u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \,da\right) \chi_{\Omega}.
+		\label{math:theorem:PF_EC:bogov:n}
+	\end{align}
+	In particular, if $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
+
+    % If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$ and $\cartan u = 0$, 
+    % then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
+    % If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$ and $\int_\Omega u = 0$ in the case $k=n$, 
+    % then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
+    % In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
+	% In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
+
 \end{theorem}
@@
 \begin{proof}
+    Consider the case $1 \leq p < \infty$.
+	%
+	Because the domain is bounded, 
+	the subspaces $C^{\infty}_{c}\Alt^{\mia}(\Omega)$ are dense in $L^{p}\Alt^{\mia}(\Omega)$,
+	and so the stated operator norm bounds follow by an approximation argument. 
+	% 
+	Taking the limit on both sides of equation then implies the inequality with $p = \infty$
+	because the $L^{\infty}$ norm is the limit of the Lebesgue norms as $p$ goes to infinity.
+
+	Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$. 
+    We write $\zeta := \Poinc_{\mia  } u$. 
+    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+		-
+		\int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u 
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u 
+        .
+    \end{align*}
+    By definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
+	This shows \eqref{math:theorem:PF_EC:poincare:k}, and \eqref{math:theorem:PF_EC:poincare:zero} follows by an approximation argument.
+
+	Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$. 
+    We write $\ := \Bogov_{\mia} u$. 
+    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
+    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
+    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
+    it holds that 
+    \begin{align*}
+        \int_{\Omega} v \wedge u_{i} 
+        &=
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
+        \\&=
+        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
+        +
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
+        .
+    \end{align*}
+    By the continuity of bounded linear functionals, we find 
+    \begin{align*}
+        \int_{\Omega} v \wedge u 
+        -
+		\int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u
+        &=
+        (-1)^{\mia(n-\mia)+1}
+        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u 
+        .
+    \end{align*}
+    By definition, $\zeta \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Bogov_{\mia+1} \cartan u$.
+    This shows \eqref{math:theorem:PF_EC:bogov:k}, and \eqref{math:theorem:PF_EC:bogov:n} follows by an approximation argument.
+
+	Everything else is now apparent, and the proof is complete. 
+\begin{comment}
     It suffices to discuss the case $1 \leq p < \infty$, because the domain is bounded 
@@
 
-    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$ and $\cartan u = 0$. 
-    We write $w := \Poinc_{\mia  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-
     \color{blue}
@@
 
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$. 
-    We write $w := \Bogov_{\mia} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    This completes the proof.
-
     \color{blue}
@@
     \color{black}
+\end{comment}
 \end{proof}
-
-% DONE: Density of C infty mit oder ohne c.
 
@@
     % \end{align*}
-	For each $\bfu \in \bfW^{p}(\divergence,\Omega)$ there exists $\bfw \in \bfW^{p}(\divergence,\Omega)$ with $\divergence \bfw = \divergence \bfu$ and 
+	For each $\bfu \in \bfW^{2}(\divergence,\Omega)$ there exists $\bfw \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfw = \divergence \bfu$ and 
     \begin{align*}
@@
     with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
-    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
+    The adjoint is the closed densely-defined linear operator $-\divergence : \bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
     which has the same smallest singular value. 
@@
     For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
-          % $v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}$.
-    \begin{align*}
-        v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}. 
-    \end{align*}
+    $v_0$, $\dots$, $v_{i-1}$, $z_{S}$, $v_{i+1}$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$.
+    % \begin{align*}
+        % v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}. 
+    % \end{align*}
     The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
@@
     We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$.
-    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere. 
+    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
+	by the topological Sch\"onfliess theorem. 
     It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
@@
     % \end{align*}
-    % Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap |\calT|$, which contains $z$, onto the unit sphere.
+    % Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap \underlying{\calT}$, which contains $z$, onto the unit sphere.
 Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
@@
 
+\begin{remark}
+    We interpret a shelling as the construction of a triangulation 
+    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
+    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
+\end{remark}
+\begin{remark}
+    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
+    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
+    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
+\end{remark}
+
 We now collect important examples of shellable triangulations.
@@
 
-    Write $M = |\calT|$. 
+    Write $M = \underlying{\calT}$. 
     There is nothing to show if $\calT$ contains only one triangle. 
@@
 \end{proof}
-
-\begin{remark}
-    We interpret a shelling as the construction of a triangulation 
-    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
-    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
-\end{remark}
-\begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
-    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
-    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
-\end{remark}
 
@@
     \begin{align*}
-        U := \overline{ |\patch_{\calT}(S)| \setminus T },
+        U := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
         \qquad 
@@
         \item 
-        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ between the underlying sets as follows.
+        We introduce a new mapping $\Theta : \underlying{\calR} \rightarrow \underlying{\calR^c}$ between the underlying sets as follows.
         Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
@@
         \begin{align*}
-            \Psi : |\calR'| \rightarrow \underlying{\calK}.
+            \Psi : \underlying{\calR'} \rightarrow \underlying{\calK}.
         \end{align*}
@@
         n A_{\Poinc}(n,k+1) 
-        \vol_{n}(B_1(0)) 
+        \vol_{}(B_1(0)) 
         \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
@@
     This follows from the discussion in Section~\ref{section:potentialoperator}.
-    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
+    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
     \mwl{check final form of result}
@@
         2^{\frac n p}
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (\ell+1)/n! } 
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
         \algebraicshapemeasure(T)^{k-1}
@@
         &\leq 
-        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{ \vol(\tilde U) } 
+        n A_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\tilde U) } 
         2
@@
         \\&\leq 
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
+        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
         \| \tilde g \|_{L^{p}(\tilde U)}

### 2024-10-06 main.tex
corrections

@@
 \cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
-\cye{This is summarized in Theorem~\ref{theorem:PF_EC}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:PF_EC} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
+\cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
 
@@
     \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
-    \label{equation:A_Poinc}
     .
@@
 Here we introduce the numerical constant 
-\begin{gather}\label{equation:A_Bogov}
+\begin{gather}\label{equation:A_Poinc}
 	A_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
@@
 
-\mwl{Some of the notation here needs to be simplified or introducted: Sigma for all integers, possily empty. remove or add indices}
+We make use of the following notation~\cite{licht2022basis}:
+for any mapping $\sigma \in \Sigma(k,n)$, we let $[\sigma] := \{ \sigma(1), \dots, \sigma(k) \}$ be its image. 
+When $p \in [\sigma]$, then the member of $\Sigma(k-1,n)$ with image $[\sigma] \setminus \{p\}$ is written $\sigma-p$.
 
@@
 
-\begin{theorem}\label{theorem:PF_EC}
+\begin{theorem}\label{theorem:bogovpoinc}
     Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
@@
 		u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a)
-		\label{math:theorem:PF_EC:poincare:zero}
+		\label{math:theorem:bogovpoinc:poincare:zero}
 		\\
 		u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
-		\label{math:theorem:PF_EC:poincare:k}
+		\label{math:theorem:bogovpoinc:poincare:k}
 	\end{align}
@@
 		u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
-		\label{math:theorem:PF_EC:bogov:k}
+		\label{math:theorem:bogovpoinc:bogov:k}
 		\\
 		u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \,da\right) \chi_{\Omega}.
-		\label{math:theorem:PF_EC:bogov:n}
+		\label{math:theorem:bogovpoinc:bogov:n}
 	\end{align}
@@
     By definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
-	This shows \eqref{math:theorem:PF_EC:poincare:k}, and \eqref{math:theorem:PF_EC:poincare:zero} follows by an approximation argument.
+	This shows \eqref{math:theorem:bogovpoinc:poincare:k}, and \eqref{math:theorem:bogovpoinc:poincare:zero} follows by an approximation argument.
 
@@
     By definition, $\zeta \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Bogov_{\mia+1} \cartan u$.
-    This shows \eqref{math:theorem:PF_EC:bogov:k}, and \eqref{math:theorem:PF_EC:bogov:n} follows by an approximation argument.
+    This shows \eqref{math:theorem:bogovpoinc:bogov:k}, and \eqref{math:theorem:bogovpoinc:bogov:n} follows by an approximation argument.
 
@@
 
-\subsection{Triangulations of manifolds}
+\subsection{Triangulations of manifolds}\label{subsection:manifoldtriangulation}
 
@@
 
-% \begin{lemma}\label{lemma:stardivision}
-%     Let $\calT$ be an $n$-dimensional simplicial complex
-%     such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
-%     Let $z_S$ be the barycenter of $S$ 
-%     and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
-%     If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
-%     then $\vol(T^{\star}) = \vol(T) / n$.
-% \end{lemma}
 \begin{lemma}\label{lemma:stardivision}
@@
         % Barycenter (centroid) of the triangle
-        \coordinate (G) at ($(A)!1/3!(B)!1/3!(C)$);
+        \coordinate (G) at (1.666666666,1); %($(A)!1/3!(B)!1/3!(C)$);
         % Drawing the triangle
@@
     This follows from the discussion in Section~\ref{section:potentialoperator}.
-    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
+    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
     \mwl{check final form of result}
@@
 
-    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:...} imply 
+    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
     the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
@@
 \begin{proof}
-    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
     By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
     We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
-    For $0 < m \leq M$, by the definition of shellability in Section~\ref{section:shellability}, 
+    For $0 < m \leq M$, by the definition of shellability in Section~\ref{subsection:shellability}, 
     $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 

### 2024-10-06 main.tex
more corrections

@@
 
-%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{section:intro_grad}
+%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}
 
@@
 \end{align*}
-The fundamental difference \cye{with respect to Section~\ref{section:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
-In Section~\ref{section:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
+The fundamental difference \cye{with respect to Section~\ref{subsection:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
+In Section~\ref{subsection:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
 It is thus trivially complemented for all $p$, with a canonical choice of projection.
@@
 Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
-For scalar-valued functions in the context of Section~\ref{section:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
+For scalar-valued functions in the context of Section~\ref{subsection:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
 %Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
@@
 
-In the gradient case of Section~\ref{section:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
+In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
 We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
@@
 
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.}
-\mwl{MV: remark from after Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} moved here.} 
+\cye{We treat specifically the gradient operator (the setting of Section~\ref{subsection:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
+Here, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} is our main results.}
+\mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
 The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
@@
 As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei}.}
+The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
 
@@
 
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains} \label{section: PX_convex}
+\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains} \label{subsection: PX_convex}
 
@@
 The next auxiliary result establishes Poincar\'e--Friedrichs constants over face patches within simplicial triangulations. 
-We emphasize that face patches are not necessarily convex, but we can still extend the results on convex domains from Section~\ref{section: PX_convex}.
+We emphasize that face patches are not necessarily convex, but we can still extend the results on convex domains from Section~\ref{subsection: PX_convex}.
 The following result is reasonably sharp when the two simplices have similar volumes and diameters.
@@
 
-The discussion for the Bogovski\u{\i} operator is analogous. 
+Even though the discussion for the Bogovski\u{\i} operator is large analogous, some modifications are needed. 
 Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
@@
     t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
+    .
 \end{align*}
@@
         \item 
-        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
+        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
         \begin{align*}
@@
 Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
-Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside.
+Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{subsection: PX_convex} have it outside.
 Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
@@
 Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
-\begin{align*}
-    \mwl{X_{m} := ...}
+For each $0 \leq m \leq M$, we write 
+\begin{align*}
+    X_{m} := T_0 \cup T_1 \cup \dots \cup T_{m}.
 \end{align*}
@@
 \begin{align*}
-    \Gamma_{m} := T_{m} \cap \left( T_{0} \cup \dots \cup T_{m-1} \right)
+    \Gamma_{m} := T_{m} \cap X_{m-1} %\left( T_{0} \cup \dots \cup T_{m-1} \right)
+	.
 \end{align*}
@@
 
-\begin{proof}
-    We begin with the following preparatory observations. 
-    Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
-    We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
-    That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
-    Then the mapping 
-    \begin{align}
-        F_T(x) 
-        = 
-        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
-    \end{align}
-    maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
-    \begin{align}
-        F_T^{-1}(x) 
-        = 
-        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
-        .
-    \end{align}
-    We analyze its Lipschitz properties.
-    % 
-    In what follows, $y \in \bbR^{n}$. 
-    On the one hand, 
-    we compute the Jacobian at any $x \in \mathring T$:
-    \begin{align*}
-        \Jacobian F_T(x) \cdot y
-        &= 
-        \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
-        \left( \vecone \cdot A_{T}^{-1} x \right)
-        + 
-        \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
-        \\&= 
-        \left( \Id - \|x\|^{-2} x \otimes x^t \right)
-        \frac{ 1 }{ \|x\| } 
-        \left( \vecone \cdot A_{T}^{-1} x \right)
-        + 
-        \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
-        \\&= 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-        \left( \Id - \hat x \otimes \hat x^t \right) y
-        + 
-        \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
-        .
-    \end{align*}
-    This is an orthogonal sum of two vectors. Its norm satisfies:
-\begin{align*}
-        \| \Jacobian F_T(x) \cdot y \|^{2}
-        &= 
-        \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
-        \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
-        + 
-        \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
-        .
-    \end{align*}
-    The Euclidean operator norm satisfies 
-    \begin{align*}
-        \| \Jacobian F_T(x) \| 
-        \leq 
-        \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
-        \leq 
-        \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
-        .
-    \end{align*}
-    On the other hand, we can rewrite the Jacobian as:
-    \begin{align*}
-        \Jacobian F_T(x) \cdot y
-        &= 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-        y
-        - 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-        \left( \hat x \otimes \hat x^t \right) y
-        + 
-        \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
-        \\&= 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-        y
-        - 
-        \hat x 
-        \left( 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
-            -
-            \vecone^{t} A_{T}^{-1} 
-        \right) y
-        \\&= 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
-        y
-        - 
-        \hat x 
-        \left( 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
-            -
-            A_{T}^{-t} \vecone
-        \right)^{t} y
-        .
-    \end{align*}
-    Its inverse is found via the Woodbury formula: 
-    % Its inverse is easily verified to be:
-    \begin{align*}
-        \Jacobian F_T(x)^{-1}
-        &= 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-        \Id
-        - 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
-        \hat x 
-        \left( 
-            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
-            -
-            A_{T}^{-t} \vecone
-        \right)^{t} 
-        \\&= 
-        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-        \left( 
-            \Id
-            - 
-            \hat x 
-            \left( 
-                % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-                % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
-                \hat x
-                -
-                \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-                A_{T}^{-t} \vecone
-            \right)^{t}
-        \right)
-        \\&= 
-        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-        \left( 
-            \Id
-            - 
-            \hat x 
-            \left( 
-                % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
-                % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
-                \hat x
-                -
-                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-                A_{T}^{-t} \vecone
-            \right)^{t}
-        \right)
-        \\&= 
-        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-        \left( 
-            \Id - \hat x \otimes \hat x^{t}
-            + 
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-            \hat x \otimes \vecone^{t} A_{T}^{-1}
-        \right)
-        .
-    \end{align*}
-    The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
-    We notice the upper bound 
-    \begin{align*}
-        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-        &= 
-        \| A_{T}^{-1} \hat x \|^{-1}_{1}
-        \\&\leq  
-        \| A_{T}^{-1} \hat x \|^{-1}_{2}
-        \leq 
-        \sigma_{\min}( A_{T}^{-1} )^{-1}
-        = 
-        \sigma_{\max}( A_{T} )
-        .
-    \end{align*}
-    This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
-    %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
-    If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
-    \begin{align*}
-        \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
-        &\leq 
-%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
-%             \left\| 
-%                 y
-%             \right\|^{2}
-%             +
-%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
-%             \left| 
-%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-%                 \vecone^{t} A_{T}^{-1} y 
-%             \right|^{2}
-%             \\&\leq 
-        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
-        \left\| 
-            y
-        \right\|^{2}
-        +
-        \frac{ 
-        \left| 
-            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
-            \vecone^{t} A_{T}^{-1} y 
-        \right|^{2}
-        }{
-        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
-        }
-        .
-    \end{align*}
-    The operator norm of that inverse is:
-    \begin{align*}
-        \| \Jacobian F_T(x)^{-1} \|
-        \leq 
-        \sigma_{\max}( A_{T} )
-        \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
-        .
-    \end{align*}
-    Since the domain and codomain of $F_{T}$ are convex, 
-    this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse. 
-\color{red}
-    On the one hand, given $x, y \in T$, 
-    where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
-    \begin{align*}
-        &
-        \left\| F_T(x) - F_T(y) \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left\| 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
-        \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left\| 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
-        \right\|_{2}
-        +
-        \left\| 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
-        \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
-        \left\| 
-            x - y
-        \right\|_{2}
-        +
-        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
-        \\&\qquad 
-        \leq 
-        2\sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
-        \left\| x - y \right\|_{2}
-        .
-    \end{align*}
-    On the one hand, given $x, y \in T$, 
-    where $\| x \|_{2} \leq \| y \|_{2}$ without loss of generality, we find 
-    \begin{align*}
-        &
-        \left\| F_T(x) - F_T(y) \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left\| 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
-        \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left\| 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
-        \right\|_{2}
-        +
-        \left\| 
-            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y
-        \right\|_{2}
-        +
-        \left\| 
-            \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
-        \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
-        \left\| 
-            x - y
-        \right\|_{2}
-        +
-        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
-        \frac{\|y\|}{\|x\|}
-        +
-        \|A_{T}^{-1} y\|_1 \|y\|_{2}
-        \left| \frac{1}{\|x\|} - \frac{1}{\|y\|} \right|
-        \\&\qquad 
-        \leq 
-        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
-        \left\| 
-            x - y
-        \right\|_{2}
-        +
-        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
-        \frac{\|y\|}{\|x\|}
-        +
-        \|A_{T}^{-1} y\|_1 \|y\|_{2}
-        \left| \frac{ \|y\|_{2} - \|x\|_{2} }{\|x\|_{2} \|y\|_{2}} \right|
-        \\&\qquad 
-        \leq 
-        3 \sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
-        \left\| x - y \right\|_{2}
-        .
-    \end{align*}
-    On the other hand, given $x, y \in F_T(T)$, 
-    where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
-    \begin{align*}
-        &
-        \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left\| 
-            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
-        \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left\| 
-            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
-        \right\|_{2}
-        +
-        \left\| 
-            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
-        \right\|_{2}
-        +
-        \left\| 
-            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
-        \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
-        \left\| 
-            x - y
-        \right\|_{2}
-        +
-        \left| \|x\|_2 - \|y\|_2 \right|
-        \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} }
-        +
-        \|y\|_2^{2}
-        \left| 
-        \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} \| A_{T}^{-1} y \|_{1} }
-        \right|
-        \\&\qquad 
-        \leq 
-        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{2} } 
-        \left\| 
-            x - y
-        \right\|_{2}
-        +
-        \left| \|x\|_2 - \|y\|_2 \right|
-        \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{2} }
-        +
-        \|y\|_2^{2}
-        \left| 
-        \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{2} \| A_{T}^{-1} y \|_{2} }
-        \right|
-        \\&\qquad 
-        \leq 
-        \left( 2 + \sqrt{n} \frac{\sigma_{\max}(A_{T}^{-1}) }{ \sigma_{\min}(A_{T}^{-1}) } \right) \sigma_{\min}(A_{T}^{-1})^{-1} 
-        \left\| x - y \right\|_{2}
-        \\&\qquad 
-        \leq 
-        \left( 2 + \sqrt{n} \kappa(A_{T}) \right) \sigma_{\max}(A_{T})
-        \left\| x - y \right\|_{2}
-        .
-    \end{align*}
-    By convexity of the range of $F_T(T)$, 
-    we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
-    We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
-    \color{black}
-\end{proof}
-
 \end{document}

### 2024-10-06 main.tex
bogovskii potential

@@
     &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt 
     \\&
@@
 We write the exterior derivative of $u$ as 
-\begin{align*}
+\begin{align}\label{math:exteriorderivative_of_u_in_hodgediscussion}
     \cartan u(x)
@@
     ,
-\end{align*}
+\end{align}
 and apply the Poincar\'e potential operator to this result, which gives 
@@
     &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;
+    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt 
     \\&
@@
 \end{align*}
-and compute its exterior derivative:
+We want to take its exterior derivative, but we can generally only do that in the distributional sense. 
+Away from the pivot point $a$, the form $\Bogov_{\mia,a} u(x)$ is differentiable in $x$, 
+and so we compute its exterior derivative over $\Omega \setminus \{a\}$:
 \begin{align*}
@@
 \end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align*}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    =
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    ,
-\end{align*}
+The derivative of $\Bogov_{\mia,a} u$ over the whole domain, which is what we need, can only be taken in the sense of distributions. 
+Let $\phi \in C^{\infty}\Alt^{n-\mia}(\Omega)$ be smooth and compactly supported over $\Omega$. 
+We let $\epsilon > 0$ and calculate 
+\begin{align*}
+    (-1)^{n(k-1)} % deg B u x deg phi = (k-1)(n-k) = nk-n-kk + k = nk - n = n(k-1)
+    \int_{ \Omega \setminus B_\epsilon(a) }
+    \Bogov_{\mia,a} u(x) \wedge \cartan \phi 
+    =
+    \int_{ S_\epsilon(a) }
+    \trace_{S_\epsilon(a)}{ \Bogov_{\mia,a} u(x) \wedge \phi } 
+    -
+    \int_{ \Omega \setminus B_\epsilon(a) }
+    \cartan \Bogov_{\mia,a} u(x) \wedge \phi 
+    ,
+\end{align*}
+where $\trace_{S_{\epsilon}(a)}$ denotes the trace onto the sphere $S_{\epsilon}(a)$. 
+In the limit as $\epsilon$ goes to zero, the two integrals over $\Omega \setminus B_\epsilon(a)$ in the above equation converge to the integrals of the respective integrands over $\Omega \setminus \{a\}$.
+To understand the derivative of $\Bogov_{\mia,a} u$ over the domain $\Omega$, 
+we study the remaining surface integral. 
+We apply several substitutions:
+\begin{align*}
+    &\int_{ S_\epsilon(a) }
+    \trace_{S_\epsilon(a)}{ \Bogov_{\mia,a} u(x) \wedge \phi(x) } 
+    \\&\quad 
+    =
+    % x = a + e n = a - e a + e a + e n = e ( a + n ) + (1-e) a
+    \epsilon^{n-1}
+    \int_{ S_1(a) }
+    \trace_{S_1(a)}{ \Bogov_{\mia,a} u( \epsilon x + a - \epsilon a ) \wedge \phi( \epsilon x + a - \epsilon a ) }
+    \\&\quad 
+    =
+    \epsilon^{n-1}
+    \int_{ S_1(a) }
+    \int_{1}^\infty 
+    \trace_{S_1(a)}{ 
+        \epsilon t^{\mia-1} (x-a)\lrcorner u\left( a + \epsilon t( x - a )\right) 
+        \wedge \phi( \epsilon (x-a) + a ) 
+    }
+    \,dt 
+    \\&\quad 
+    =
+    % s = \epsilon t 
+    \epsilon^{n-1}
+    \int_{ S_1(a) }
+    \int_{\epsilon}^\infty 
+    \trace_{S_1(a)}{ 
+        \epsilon^{-\mia+1} s^{\mia-1} (x-a)\lrcorner u\left( a + s( x - a )\right) 
+        \wedge \phi( \epsilon (x-a) + a ) 
+    }
+    \,ds 
+    \\&\quad 
+    =
+    % s = \epsilon t 
+    \epsilon^{n-\mia}
+    \int_{ S_1(a) }
+    \int_{\epsilon}^\infty 
+    \trace_{S_1(a)}{ 
+        s^{\mia-1} (x-a)\lrcorner u\left( a + s( x - a )\right) 
+        \wedge \phi( \epsilon (x-a) + a ) 
+    }
+    \,ds 
+    .
+\end{align*}
+We make a case distinction.
+When $k<n$, then the double integral itself is bounded uniformly in $\epsilon > 0$ and so the last expression vanishes as $\epsilon$ goes to zero.
+When instead $k=n$, then the last expression equals
+\begin{align*}
+	& 
+    \int_{ S_1(a) }
+    \int_{\epsilon}^\infty 
+    \trace_{S_1(a)}{ 
+        s^{n-1} (x-a)\lrcorner u\left( a + s( x - a )\right) 
+        \wedge \phi( \epsilon (x-a) + a ) 
+    }
+    \,ds 
+    \\&\quad 
+	=
+	\int_{\bbR^{n} \setminus B_{\epsilon}(0)}
+	    u\left( y \right) 
+        \wedge \phi\left( \epsilon \frac{y-a}{\|y-a\|} + a \right) 
+    \,dy 
+    .
+\end{align*}
+The limit of this is $\phi(a) \int_\Omega u(x)$ as $\epsilon$ goes to zero. 
+To complete the discussion, we write the exterior derivative of $u$ as in \eqref{math:exteriorderivative_of_u_in_hodgediscussion}, 
+% \begin{align*}
+    % \cartan u(x)
+    % =
+    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
+    % \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
+    % =
+    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
+    % \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
+    % ,
+% \end{align*}
 and apply the Bogovski\u{\i} potential operator to this result, which gives 
@@
 \end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begin{align*}
-    &
-    - 
-    \cartan \Bogov_{\mia,a} u(x)
-    -
-    \Bogov_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^{\infty} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^{\infty} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^{\infty} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
-    \int_{1}^{\infty} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma} \,dt 
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^{\infty} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    =
-    -
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    u_{\sigma}(x) \cartanx^{\sigma}
-    =
-    -u(x)
-    .
-\end{align*}
-We conclude that 
+We add the (distributional) exterior derivative of the potential and the potential of the exterior derivative.
+In a manner that fully analogous to the discussion of the averaged Poincar\'e operator save for the modification when $k=n$, 
+we come to the conclusion that 
+% Taking into account cancellations, this gives the identity 
+% \begingroup\allowdisplaybreaks
+% \begin{align*}
+    % &
+    % - 
+    % \cartan \Bogov_{\mia,a} u(x)
+    % -
+    % \Bogov_{\mia+1,a} \cartan u(x)
+    % \\&
+    % =
+    % \sum_{\sigma \in \Sigma(\mia,n)} 
+    % \int_{1}^{\infty} 
+    % \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
+    % \\&\qquad
+    % + 
+    % \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
+    % \int_{1}^{\infty} 
+    % t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
+    % \\&\qquad
+    % +
+    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
+    % \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
+    % \\&\qquad
+    % - 
+    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
+    % (-1)^{i-1}
+    % \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
+    % \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
+    % \\&
+    % =
+    % \sum_{\sigma \in \Sigma(\mia,n)} 
+    % \int_{1}^{\infty} 
+    % \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
+    % \\&\qquad
+    % +
+    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
+    % \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
+    % \\&\qquad
+    % + 
+    % \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
+    % \int_{1}^{\infty} 
+    % t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma} \,dt 
+    % \\&
+    % =
+    % \sum_{\sigma \in \Sigma(\mia,n)} 
+    % \int_{1}^{\infty} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
+    % =
+    % -
+    % \sum_{\sigma \in \Sigma(\mia,n)} 
+    % u_{\sigma}(x) \cartanx^{\sigma}
+    % =
+    % -u(x)
+    % .
+% \end{align*}
+% \endgroup
+% We conclude that 
 \begin{align*}
@@
     \\
-    u(x) &= \cartan \Bogov_{n,a} u(x) - \left( \int_{\Omega} u(a) \,da\right) \delta_a, \qquad k = n.
+    u(x) &= \cartan \Bogov_{n,a} u(x) - \left( \int_{\Omega} u(a) \right) \delta_a, \qquad k = n.
 \end{align*}
@@
     \\
-    u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \,da\right) \chi_{\Omega}, \qquad k = n.
+    u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}, \qquad k = n.
 \end{align}
@@
     \begin{align}
-		u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a)
+        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
         \label{math:theorem:bogovpoinc:poincare:zero}
@@
         \\
-		u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \,da\right) \chi_{\Omega}.
+        u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}.
         \label{math:theorem:bogovpoinc:bogov:n}

### 2024-10-06 draft.tex
singular values inserted
more corrections
first main result

@@
 \begin{document}
+
+\begin{proof}
+    By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
+    We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, 
+    which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
+    For $0 < m \leq M$, by the definition of shellability in Section~\ref{subsection:shellability}, 
+    $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
+    It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
+    where $\Minako_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
+
+    We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound. 
+    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
+    First, on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex}, 
+    there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
+    \begin{gather*}
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \end{gather*}
+    We define $w_{|T_0} := w_0$. 
+    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
+    This is true for $m = 1$. 
+    We now define, as in Equations~(5.12) and~(5.14) of~\cite{ern2020stable} or Equations~(6.7) and~(6.9)~\cite{Chaum_Voh_p_rob_3D_H_curl_24},
+    \begin{align} \label{equation:w''_ext_der}
+        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\Minako_{m-1}}),
+    \end{align}
+    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
+    as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
+    Clearly, $w_{|T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
+    \begin{align*}
+        \trace_{\Gamma_{m}} w_{|T_m} = \trace_{\Gamma_{m}} w_{|X_{m-1}},
+    \end{align*}
+    since $u$ is trace continuous over $\Gamma_{m-1}$ and $\Xi_{m}$ is the identity along $\Gamma_{m-1}$, and
+    \begin{align*}
+        \cartan w = \cartan u \text{ over } T_m,
+    \end{align*}
+    since $\cartan w = \cartan u$ over $X_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
+    \begin{align*}
+        w_{|X_{m}} \in W^{p}\Alt^{k}(X_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } X_{m}. 
+    \end{align*}
+
+    We want to estimate norms. 
+    By construction,
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        \leq  
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
+        + 
+        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) = 0$, we have
+    \begin{align*}
+        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
+        + \| \cartan (\Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})} )
+        .
+    \end{align*}
+    We also use Proposition~\ref{proposition:pullbackestimate} to find 
+    \begin{align*}
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
+        &\leq 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
+        \| w \|_{L^{p}(\Minako_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
+        &\leq 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
+        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
+        ,
+    \end{align*}
+	\begin{align*}
+        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
+        \| w \|_{L^{p}(\Minako_{m-1})}
+        ,
+        \\
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
+        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
+        ,
+    \end{align*}
+    where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
+    Using the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}, the desired recursive estimate follows. 
+\end{proof}
+
+\begin{proof}
+    We begin with the following preparatory observations. 
+    Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
+    We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
+    That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
+    Then the mapping 
+    \begin{align}
+        F_T(x) 
+        = 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
+    \end{align}
+    maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
+    \begin{align}
+        F_T^{-1}(x) 
+        = 
+        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
+        .
+    \end{align}
+    We analyze its Lipschitz properties.
+    % 
+    In what follows, $y \in \bbR^{n}$. 
+    On the one hand, 
+    we compute the Jacobian at any $x \in \mathring T$:
+    \begin{align*}
+        \Jacobian F_T(x) \cdot y
+        &= 
+        \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
+        \left( \vecone \cdot A_{T}^{-1} x \right)
+        + 
+        \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
+        \\&= 
+        \left( \Id - \|x\|^{-2} x \otimes x^t \right)
+        \frac{ 1 }{ \|x\| } 
+        \left( \vecone \cdot A_{T}^{-1} x \right)
+        + 
+        \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        \left( \Id - \hat x \otimes \hat x^t \right) y
+        + 
+        \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+        .
+    \end{align*}
+    This is an orthogonal sum of two vectors. Its norm satisfies:
+\begin{align*}
+        \| \Jacobian F_T(x) \cdot y \|^{2}
+        &= 
+        \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
+        \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
+        + 
+        \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
+        .
+    \end{align*}
+    The Euclidean operator norm satisfies 
+    \begin{align*}
+        \| \Jacobian F_T(x) \| 
+        \leq 
+        \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
+        \leq 
+        \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
+        .
+    \end{align*}
+    On the other hand, we can rewrite the Jacobian as:
+    \begin{align*}
+        \Jacobian F_T(x) \cdot y
+        &= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        y
+        - 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        \left( \hat x \otimes \hat x^t \right) y
+        + 
+        \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        y
+        - 
+        \hat x 
+        \left( 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
+            -
+            \vecone^{t} A_{T}^{-1} 
+        \right) y
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)
+        y
+        - 
+        \hat x 
+        \left( 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+            -
+            A_{T}^{-t} \vecone
+        \right)^{t} y
+        .
+    \end{align*}
+    Its inverse is found via the Woodbury formula: 
+    % Its inverse is easily verified to be:
+    \begin{align*}
+        \Jacobian F_T(x)^{-1}
+        &= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+        \Id
+        - 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
+        \hat x 
+        \left( 
+            \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
+            -
+            A_{T}^{-t} \vecone
+        \right)^{t} 
+        \\&= 
+        \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+        \left( 
+            \Id
+            - 
+            \hat x 
+            \left( 
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                \hat x
+                -
+                \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                A_{T}^{-t} \vecone
+            \right)^{t}
+        \right)
+        \\&= 
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+        \left( 
+            \Id
+            - 
+            \hat x 
+            \left( 
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
+                % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
+                \hat x
+                -
+                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+                A_{T}^{-t} \vecone
+            \right)^{t}
+        \right)
+        \\&= 
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+        \left( 
+            \Id - \hat x \otimes \hat x^{t}
+            + 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \hat x \otimes \vecone^{t} A_{T}^{-1}
+        \right)
+        .
+    \end{align*}
+    The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
+    We notice the upper bound 
+    \begin{align*}
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+        &= 
+        \| A_{T}^{-1} \hat x \|^{-1}_{1}
+        \\&\leq  
+        \| A_{T}^{-1} \hat x \|^{-1}_{2}
+        \leq 
+        \sigma_{\min}( A_{T}^{-1} )^{-1}
+        = 
+        \sigma_{\max}( A_{T} )
+        .
+    \end{align*}
+    This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
+    %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
+    If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
+    \begin{align*}
+        \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
+        &\leq 
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left\| 
+%                 y
+%             \right\|^{2}
+%             +
+%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+%             \left| 
+%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+%                 \vecone^{t} A_{T}^{-1} y 
+%             \right|^{2}
+%             \\&\leq 
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
+        \left\| 
+            y
+        \right\|^{2}
+        +
+        \frac{ 
+        \left| 
+            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
+            \vecone^{t} A_{T}^{-1} y 
+        \right|^{2}
+        }{
+        \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
+        }
+        .
+    \end{align*}
+    The operator norm of that inverse is:
+    \begin{align*}
+        \| \Jacobian F_T(x)^{-1} \|
+        \leq 
+        \sigma_{\max}( A_{T} )
+        \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
+        .
+    \end{align*}
+    Since the domain and codomain of $F_{T}$ are convex, 
+    this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse. 
+\color{red}
+    On the one hand, given $x, y \in T$, 
+    where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
+    \begin{align*}
+        &
+        \left\| F_T(x) - F_T(y) \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+        \\&\qquad 
+        \leq 
+        2\sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
+        \left\| x - y \right\|_{2}
+        .
+    \end{align*}
+    On the one hand, given $x, y \in T$, 
+    where $\| x \|_{2} \leq \| y \|_{2}$ without loss of generality, we find 
+    \begin{align*}
+        &
+        \left\| F_T(x) - F_T(y) \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+        \frac{\|y\|}{\|x\|}
+        +
+        \|A_{T}^{-1} y\|_1 \|y\|_{2}
+        \left| \frac{1}{\|x\|} - \frac{1}{\|y\|} \right|
+        \\&\qquad 
+        \leq 
+        \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
+        \frac{\|y\|}{\|x\|}
+        +
+        \|A_{T}^{-1} y\|_1 \|y\|_{2}
+        \left| \frac{ \|y\|_{2} - \|x\|_{2} }{\|x\|_{2} \|y\|_{2}} \right|
+        \\&\qquad 
+        \leq 
+        3 \sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
+        \left\| x - y \right\|_{2}
+        .
+    \end{align*}
+    On the other hand, given $x, y \in F_T(T)$, 
+    where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
+    \begin{align*}
+        &
+        \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left\| 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
+        \right\|_{2}
+        +
+        \left\| 
+            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
+        \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|x\|_2 - \|y\|_2 \right|
+        \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} }
+        +
+        \|y\|_2^{2}
+        \left| 
+        \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} \| A_{T}^{-1} y \|_{1} }
+        \right|
+        \\&\qquad 
+        \leq 
+        \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{2} } 
+        \left\| 
+            x - y
+        \right\|_{2}
+        +
+        \left| \|x\|_2 - \|y\|_2 \right|
+        \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{2} }
+        +
+        \|y\|_2^{2}
+        \left| 
+        \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{2} \| A_{T}^{-1} y \|_{2} }
+        \right|
+        \\&\qquad 
+        \leq 
+        \left( 2 + \sqrt{n} \frac{\sigma_{\max}(A_{T}^{-1}) }{ \sigma_{\min}(A_{T}^{-1}) } \right) \sigma_{\min}(A_{T}^{-1})^{-1} 
+        \left\| x - y \right\|_{2}
+        \\&\qquad 
+        \leq 
+        \left( 2 + \sqrt{n} \kappa(A_{T}) \right) \sigma_{\max}(A_{T})
+        \left\| x - y \right\|_{2}
+        .
+    \end{align*}
+    By convexity of the range of $F_T(T)$, 
+    we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
+    We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
+    \color{black}
+\end{proof}
 

### 2024-10-06 main.tex
first main result

@@
     =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
-    .
-\end{align*}
-% Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$. 
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
+    .
+\end{align*}
+% Here, $C_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$. 
 Here we introduce the numerical constant 
 \begin{gather}\label{equation:A_Poinc}
-    A_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
+    C_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
 \end{gather}
@@
     \leq 
-    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \vol_{n-1}(S_1) C_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
     \diam(\Omega)
@@
     \leq 
-    n A_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
     \diam(\Omega)
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+% Its operator norm is bounded by $n C_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 %
@@
     =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
-    .
-\end{align*}
-% Here, $A_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
+    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
+    .
+\end{align*}
+% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
 Here we introduce the numerical constant 
 \begin{gather}\label{equation:A_Bogov}
-    A_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
+    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
 \end{gather}
@@
     \leq 
-    n A_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
     \diam(\Omega)
@@
 \end{gather*}
-% Its operator norm is bounded by $n A_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
+% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
 Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
@@
 However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
-namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\mia)$ and $A_{\Bogov}(n,\mia)$.
+namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $C_{\Poinc}(n,\mia)$ and $C_{\Bogov}(n,\mia)$.
 
@@
         &\leq 
-        n A_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
         \diam(\Omega)
@@
         &\leq 
-        n A_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
         \diam(\Omega)
@@
     \begin{align*}
-        U := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
+        \Minako := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
         \qquad 
-        {\Gamma_1} := U \cap T,
+        {\Gamma_1} := \Minako \cap T,
         \qquad 
-        {\Gamma_2} := \overline{ \partial T \setminus \partial U }.
+        {\Gamma_2} := \overline{ \partial T \setminus \partial \Minako }.
     \end{align*}
@@
     \item 
-    There exists a bi-Lipschitz mapping
-    \begin{align*}
-        \Xi_{1} : T \rightarrow U
-    \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap U$. 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{1} : T \rightarrow \Minako
+    \end{align*}
+    which is the identity along ${\Gamma_1} = T \cap \Minako$. 
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \item 
-    There exists a bi-Lipschitz mapping
-    \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U
-    \end{align*}
-    which is the identity along $\partial U \setminus \partial T$.
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Minako
+    \end{align*}
+    which is the identity along $\partial \Minako \setminus \partial T$.
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
         Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
-        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
+        % Let $I := \Minako \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
         %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
@@
         Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.
+        whereas ${\Gamma_1} = \Minako \cap T$ is the union of exactly those faces of $T$ that contain $S$.
 
@@
         \item 
-        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
+        We define a mapping $ \Xi_{1} : T \rightarrow \Minako = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
         \begin{align*}
@@
         \end{align*}
-        It preserves the interface from $T$ onto $U$. 
+        It preserves the interface from $T$ onto $\Minako$. 
         Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
@@
         \item 
-        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U $ by setting 
+        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Minako $ by setting 
         \begin{align*}
@@
         = 
-        n A_{\Poinc}(n,k+1) 
+        n C_{\Poinc}(n,k+1) 
         \vol_{}(B_1(0)) 
@@
 \begin{proof}
-    This follows from the discussion in Section~\ref{section:potentialoperator}.
     This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
-    \mwl{check final form of result}
 \end{proof}
@@
     Let $T$ be an $n$-simplex 
-    and let $F_{0},\dots,F_{\ell}$ be $\ell+1$ different faces of $T$. 
+    and let $\Gamma = F_{0} \cup \dots \cup F_{\ell}$ be the union of $\ell+1$ different faces of $T$. 
     Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq \ell$.
+    $\trace_{T,\Gamma} u = 0$.
     Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq \ell$
+    $\trace_{T,\Gamma} w = 0$
     and  
@@
         \leq 
-        2^{\frac n p}
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
+        2^{\frac{n-\ell}{p}}
+        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
         \algebraicshapemeasure(T)^{k-1}
-        \Ceins{n}(T)^{k}
+        \Ceins{n}(T) 
         \diam(T)
-        % \matnorm{\Jacobian \varphi}^{k}
         .
@@
 \end{lemma}
-\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
-Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
-Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{subsection: PX_convex} have it outside.
-Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
-We should unify.}
 \begin{proof}
-    There exists an affine bijection $\varphi : \hat T \rightarrow T$ 
+    There exists an affine bijection $\varphi : \Delta^n \rightarrow T$ 
     that maps the convex closure of the $n$ unit vectors onto the face $F_0$.
-    We can also assume that the face of $\hat T$
+    We can also assume that the face of $\Delta^n$
     orthogonal to the $i$-th coordinate axis is mapped 
     onto the face $F_i$. 
-    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
-    We see that $\vol(\tilde U) = (l+1)/n!$
-
-    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    In what follows, we let $\widetilde \Minako$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
+    We see that $\vol(\widetilde \Minako) = (l+1)/n!$
+
+    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\Delta^n)$ via $\hat g := \cartan \varphi^{\ast} u$. 
     Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes,
-    and let $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
-    We observe $\tilde g = \cartan \tilde u$
-    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.
+    We let $\tilde u$ be the extension of $\hat u$ onto $\widetilde \Minako$ by reflection across the coordinate axes,
+    and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Minako$ by reflection across the coordinate axes. 
+    We observe $\tilde g = \cartan \tilde u$. 
+    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Minako)$.
 
     The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
-    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
+    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Minako)$
     with $\cartan \tilde w = \cartan \tilde u$ and 
     \begin{align*}
-        \| \tilde w \|_{L^{p}(\tilde U)}
+        \| \tilde w \|_{L^{p}(\widetilde \Minako)}
         &\leq 
-        n A_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\tilde U) } 
+        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Minako) } 
         2
-        \| \tilde g \|_{L^{p}(\tilde U)}
+        \| \tilde g \|_{L^{p}(\widetilde \Minako)}
         \\&\leq 
-        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
-        \| \tilde g \|_{L^{p}(\tilde U)}
-        .
-    \end{align*}
-    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\hat T} )$.
+        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
+        \| \tilde g \|_{L^{p}(\widetilde \Minako)}
+        .
+    \end{align*}
+    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\Delta^n} )$.
     By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.
+    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{l}$.
 
@@
         \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
-        \| \tilde w \|_{L^{p}(\hat T)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\tilde U)}
+        \| \tilde w \|_{L^{p}(\Delta^n)}
+        ,
+        \\
+        \| \tilde g \|_{L^{p}(\widetilde \Minako)}
+        \leq 
+        2^{\frac {n-\ell} p}
+        \| \hat g \|_{L^{p}(\Delta^n)}
         &\leq 
-        2^{\frac {n-\ell} p}
-        \| \hat g \|_{L^{p}(\hat T)}
-        \leq 
         2^{\frac {n-\ell} p}
@@
     \end{align*}
-    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. \mwl{Double check result}
+    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. 
 \end{proof}
 
-We settle the following notation for our main result. 
+We prepare some further notation for our main result. 
 Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
@@
 \end{align*}
-Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
+Suppose that $\calT$ is an $n$-dimensional triangulation and has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
 For each $0 \leq m \leq M$, we write 
@@
 such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
-In particular, $\patch_{\calT}(S_{m})$ is already included in the union of the simplices up to $T_m$. 
-We write 
-\begin{align*}
-    \Minako_{m} := \patch_{\calT}(S_{m}) \setminus T_{m}.
-\end{align*}
-for the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
+In particular, already $\patch_{\calT}(S_{m}) \subseteq X_{m}$. % is already included in the union of the simplices up to $T_m$.
+
+In addition to that, we introduce 
+\begin{align*}
+    \Minako_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}.
+\end{align*}
+for the complement $\Minako_{m-1} \subseteq X_{m-1}$ of the simplex $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
 
@@
     there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$
-    and such that for each $T_{m} \in \calT$, $1 \leq m \leq M$, in the shelling
-    we have the following recursive estimate: 
+	and such that the following estimates hold:
+	\begin{gather*}
+        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+    \end{gather*}
+    and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
     \begin{align*}
@@
             +
-            \Cfive{n}{k}(\calT)^{k+1} 
+            \Cfive{n}{k}(\calT)
+            \Cfiveprime{n}{k}(\calT)^{k} 
             \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
@@
         + 
-        \Cfive{n}{k}(\calT)^{k} 
+        \Cfive{n}{k}(\calT) 
+        \Cfiveprime{n}{k}(\calT)^{k-1} 
         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
@@
     \end{align*}
-    \mwl{The notation $\Minako_m$ should be settled in the definition of shellings.}
 \end{theorem}
 \begin{proof}
-    \mwl{Complete the proof.}
-    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
-    We write $X_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.
-
     Let $u \in W^{p}\Alt^{k}(\Omega)$. 
@@
     By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex, and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We define $w'_{m} :=  \Xi_{m}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$,
-    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
-    as in Proposition~\ref{proposition:starreflection}. 
+    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S_{m}$, 
+	and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Minako_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
+    We define $w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$. 
     By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
@@
 
-    We want to estimate norms. 
-    By construction,
+    We want to estimate norms. By the triangle inequality, 
     \begin{align*}
@@
     Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-    we can assume 
+    we can assume that $w''_{m}$ satisfies 
     \begin{align*}
@@
     \end{align*}
-    We also employ Proposition~\ref{proposition:pullbackestimate} to find 
+    Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} now show 
+    % \begin{align*}
+        % \| w'_{m} \|_{L^{p}(T_{m})}
+        % &\leq 
+        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k}
+        % \|\det \Jacobian \Xi_{1}^{-1}  \|_{L^{\infty}(\Minako_{m-1})}^{\frac 1 p} 
+        % \cdot 
+        % \| w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        % ,
+        % \\
+        % \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        % &\leq 
+        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k+1}
+        % \|\det \Jacobian \Xi_{1}^{-1}  \|^{\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        % \cdot 
+        % \| \cartan w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        % .
+    % \end{align*}
     \begin{align*}
@@
         &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|_{L^{\infty}(T_{m})}^{-\frac 1 p} 
-        \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k}
+        \Cfive{n}{k}(\calT)
+        \Cfiveprime{n}{k}(\calT)^{k-1}
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
         \cdot 
@@
         &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m})} 
-        \| \Jacobian \Xi_{m} \|_{L^{\infty}(T_{m})}^{k+1}
+        \Cfive{n}{k}(\calT)
+        \Cfiveprime{n}{k}(\calT)^{k}
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
         \cdot 
@@
     \end{align*}
-    \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(\Minako_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
-        ,
-    \end{align*}
     We have assumed that $\cartan w_{m-1} = \cartan u_{|X_{m-1}}$. 
-    We use the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}. 
     The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-\begin{proof}
-    By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
-    We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
-    For $0 < m \leq M$, by the definition of shellability in Section~\ref{subsection:shellability}, 
-    $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
-    where $\Minako_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
-
-    We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound. 
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex}, 
-    there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    We define $w_{|T_0} := w_0$. 
-    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
-    This is true for $m = 1$. 
-    We now define, as in Equations~(5.12) and~(5.14) of~\cite{ern2020stable} or Equations~(6.7) and~(6.9)~\cite{Chaum_Voh_p_rob_3D_H_curl_24},
-    \begin{align} \label{equation:w''_ext_der}
-        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\Minako_{m-1}}),
-    \end{align}
-    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
-    as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
-    Clearly, $w_{|T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
-    \begin{align*}
-        \trace_{\Gamma_{m}} w_{|T_m} = \trace_{\Gamma_{m}} w_{|X_{m-1}},
-    \end{align*}
-    since $u$ is trace continuous over $\Gamma_{m-1}$ and $\Xi_{m}$ is the identity along $\Gamma_{m-1}$, and
-    \begin{align*}
-        \cartan w = \cartan u \text{ over } T_m,
-    \end{align*}
-    since $\cartan w = \cartan u$ over $X_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
-    \begin{align*}
-        w_{|X_{m}} \in W^{p}\Alt^{k}(X_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } X_{m}. 
-    \end{align*}
-
-    We want to estimate norms. 
-    By construction,
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        \leq  
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        + 
-        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) = 0$, we have
-    \begin{align*}
-        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
-        + \| \cartan (\Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})} )
-        .
-    \end{align*}
-    We also use Proposition~\ref{proposition:pullbackestimate} to find 
-    \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(\Minako_{m-1})}
-        ,
-        \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
-        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
-        ,
-    \end{align*}
-    where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
-    Using the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}, the desired recursive estimate follows. 
 \end{proof}
@@
 
+\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
+Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
+Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{subsection: PX_convex} have it outside.
+Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
+We should unify.}
+
 \section{Numerical examples}\label{section:numericalexamples}

### 2024-10-06 main.tex
last theoretical section

@@
 
-We prepare some further notation for our main result. 
+We prepare some further notation for our two main results. 
 Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
@@
 \begin{align*}
-    X_{m} := T_0 \cup T_1 \cup \dots \cup T_{m}.
-\end{align*}
+    X_{m} := T_0 \cup T_1 \cup \dots \cup T_{m},
+\end{align*}
+which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
 For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
@@
 
-The main result of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorem.
+The two main results of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorems. 
+The first one is inspired by the recursive construction of gradient potentials in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+The second one is specific to the fact that shellable triangulations are contractible.
 
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
+    % Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
+	Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
     Let $T_0, T_1, \dots, T_M$ be a shelling.
@@
     \end{gather*}
-    %Suppose that claim is true when the domain has $m$ simplices of dimension $n$. 
     Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$.
+    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$. % CAUTION 
     Let $T_0, T_1, \dots, T_M$ be a shelling.
@@
         \leq 
-        C_{\PF,T,k,p}(T_{0})
-        \prod_{i=1}^{m} 
-        C_{???}
+        \left( 
+        \Cacht{n}{k}(\calT)
+        \Cachtprime{n}{k}(\calT)^{k} 
+        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \Csieb{n}{k}(\calT)
+        \Csiebprime{n}{k}(\calT)^{k-1} 
+        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \right)^{M}
+        C_{{\PF},k,T_{0},p}
         \| \cartan u \|_{L^{p}(\Omega)}
@@
     We prove this via induction. 
-    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
-    Let us assume that the statement is true for some integer $m-1 \geq 0$.
-
-    We write $X_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
-    which is a triangulated $n$-dimensional submanifold with boundary.
-    By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
-    which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
-    and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow \Minako_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
-    which acts as the identity along $\partial \Minako_{m-1} \setminus \partial T$.
-    By assumption, 
-    there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
-    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
-    \begin{align*}
-        \| w_{m-1} \|_{L^{p}(T_{m})}
-        \leq 
-        C_{\PF,T,k,p}(T_{0})
-        \prod_{i=1}^{m} 
-        C_{???}
-        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    Because pullback and exterior derivative commute, 
-    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
-    Moreover, the desired estimate follow from Proposition~\ref{proposition:starreflection}.
-    The proof is complete. 
+    The statement is clearly satisfied when $M=0$ because then we only consider a single simplex,
+    so that the Poincar\'e--Friedrichs inequality over a simplex can be used. 
+    Let us assume that the statement is true for some integer $M-1 \geq 0$.
+
+	Recall that $X_M$ is an $n$-dimensional submanifold with boundary with a triangulation that has a shelling $T_0, T_1, \dots, T_{M-1}$. 
+	Write $\Omega' \subseteq X_{M}$ for the interior domain of that manifold. 
+	By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
+	and we let $\Minako_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star.
+
+	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Minako_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
+	This mapping and its inverse are piecewiselinear, and it acts as the identity along $\partial \Minako_{M-1} \setminus \partial T$.
+    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.
+
+	Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
+    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
+    \begin{align*}
+        \| g' \|_{L^{p}(\Omega')}  
+        \leq 
+        \Cacht{n}{k}(\calT)
+        \Cachtprime{n}{k}(\calT)^{k} 
+        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \| g \|_{L^{p}(\Omega)}  
+        .
+    \end{align*}
+    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$ and 
+    \begin{align*}
+        \| w' \|_{L^{p}(\Omega')} 
+        \leq 
+        \left( 
+        \Cacht{n}{k}(\calT)
+        \Cachtprime{n}{k}(\calT)^{k} 
+        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \Csieb{n}{k}(\calT)
+        \Csiebprime{n}{k}(\calT)^{k-1} 
+        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \right)^{M-1}
+        C_{{\PF},k,T_{0},p}
+        \| g' \|_{L^{p}(\Omega')}  
+    \end{align*}
+    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
+    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}  
+        \leq 
+        \Csieb{n}{k}(\calT)
+        \Csiebprime{n}{k}(\calT)^{k-1} 
+        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \| w' \|_{L^{p}(\Omega')} 
+    \end{align*}
+    The induction step is complete, and the desired result follows. 
 \end{proof}
+
 \mwl{MV: Why a second theorem?
@@
 Add more details to the estimates}
-
 \mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?

### 2024-10-06 draft.tex
some clean up

@@
 \begin{document}
+
+\mwl{MV: Why a second theorem?
+Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
+Which is better and when?
+Add more details to the estimates}
+\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
+Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
+Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{subsection: PX_convex} have it outside.
+Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
+We should unify.}
 

### 2024-10-06 main.tex
some clean up

@@
 We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
-
+% 
 Whenever $\calT$ is a simplicial complex, 
@@
 }
+In practice, we do not always distinguish between points and singleton simplices. 
 % Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
@@
 \end{gather*}
+The integral of a differential $n$-form is uniquely defined via 
+\begin{gather*}
+    \int_{\Omega} \omega \cartanx^{1} \wedge \dots \wedge \cartanx^{n} = \int_{\Omega} \omega(x) \;dx
+    . 
+\end{gather*}
+
+\begin{remark}
+    In three dimensions, 
+    the calculus of differential forms is in correspondence with classical vector calculus. 
+    This is expressed formally as the commuting diagram 
+    \begin{gather*}
+    \begin{CD}
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        @VV{\varpi^{3}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\, ,}
+    \end{gather*}
+    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
+    \begin{align*}
+     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
+     &= 
+     \left( u_1, u_2, u_3 \right), 
+     \\
+     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
+     &= 
+     \left( u_{23}, - u_{13}, u_{12} \right).   
+    \end{align*}
+    In two dimensions, 
+    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
+    To the authors' best knowledge, neither convention is dominant over the other in the literature.
+    We summarize the situation in the following commuting diagram: 
+    \begin{gather*} 
+    \begin{CD}
+        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
+        \\
+        @AA{\varkappa^{0}}A 
+        @AA{\varkappa^{1}}A 
+        @AA{\varkappa^{2}}A 
+        \\
+        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
+        \\
+        @VV{\varpi^{0}}V 
+        @VV{\varpi^{1}}V 
+        @VV{\varpi^{2}}V 
+        \\
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
+    \end{CD}
+    \cye{\,.}
+    \end{gather*}
+    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
+We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
+    The other vertical arrows are the identity. 
+    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
+\end{remark}
 
@@
 Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
+The pullback of $u \in L^{p}\Alt^{k}(\Omega')$ along $\phi$ is the (measurable) differential form 
 \begin{align} \label{equation:pullback}
@@
 \end{align}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
-We cite an explicit transformation estimate~ (see~\cite{licht2019smoothed}) and a special estimate when the transformation is affine (see~Corollary~6~\cite{stern2013lp}).
+for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. 
+One can show that $\phi^{\ast}u \in L^{p}\Alt^{k}(\Omega)$ and the following estimates.
 
@@
     Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
-    Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
-    Then 
+    Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega')$. 
+    Then $\phi^{\ast} u \in L^{p}\Lambda^{k}(\Omega)$ and 
     \begin{align}
@@
     \end{align}
+	Moreover, if $u \in W^{p}\Lambda^{k}(\Omega')$, then $\phi^{\ast} u \in W^{p}\Lambda^{k}(\Omega)$ and $\cartan \phi^{\ast} u = \phi^{\ast} \cartan u$. 
 \end{proposition}
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms is in correspondence with classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \begin{gather*}
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\, ,}
-    \end{gather*}
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant over the other in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \begin{gather*} 
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\,.}
-    \end{gather*}
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
+\begin{proof}
+	See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}).
+\end{proof}
 
@@
 
-We finally review a few approximation properties. 
+We review a few approximation properties. 
 Let $\mollifier$ be a non-negative scalar function whose integral equals one and whose support lies in the unit ball around the origin.
@@
     $$ 
-    Then $\Gamma_{m}$ is a union of $\ell$ different faces of $T_{m}$, $1 \leq k \leq n+1$.
-    If $m < M$, then the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-k$ that satisfies 
+    Then $\Gamma_{m}$ is a union of $\ell$ different faces of $T_{m}$, $1 \leq \ell \leq n+1$.
+    If $m < M$, then the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-\ell$ that satisfies 
     $$
@@
     We know $\Gamma_{m}$ is a triangulated submanifold of the boundary of $T_{m}$, 
-    and so it must be a collection of $k$ faces of $T$, $1 \leq k \leq n+1$.
-    Note that $k = n + 1$ can only happen for the last enumerated simplex, $m = M$, if $\calT$ triangulates an $n$-sphere. 
-    $\Gamma_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-k$ in $\Gamma_{m}$.
+    and so it must be a collection of $\ell$ faces of $T$, $1 \leq \ell \leq n+1$.
+    Note that $\ell = n + 1$ can only happen for the last enumerated simplex, $m = M$, if $\calT$ triangulates an $n$-sphere. 
+    $\Gamma_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-\ell$ in $\Gamma_{m}$.
     By definition, $S_{m}$ is a boundary simplex of $X_{m}$, 
@@
     \end{center}
-    \caption{Illustration of Lemma~\ref{lemma:stardivision}.
-Left: the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles.
-The height vector from $v_2$ in all three triangles remains the same.
-The height vector from $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector from $v_0$ in the original triangle.
-Right: the triangle $T$ is trisected, leading to three new triangles.
-The height of $z_T$ to from some edge is one third of the original height of that edge.}
+    \caption{Illustration of Lemma~\ref{lemma:stardivision}. Left: 
+	the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles. 
+	The height vector to $v_2$ in all three triangles remains the same.
+The height vector to $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector to $v_0$ in the original triangle.
+	Right: 
+	the triangle $T$ is trisected, leading to three new triangles. 
+	The height vector to $z_T$ from the opposite edge in any triangle is one third of the original height vector of that edge.}
 \end{figure}
@@
 According to Lemma~\ref{lemma:existenceofstar}, 
-there exists a simplex $S_{m} \in \calT$ 
+there exists an interior simplex $S_{m} \in \calT$ 
 such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
@@
 
-\mwl{MV: Why a second theorem?
-Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}?
-Which is better and when?
-Add more details to the estimates}
-\mwl{MV: There is indeed $\diam(T)^{k}$, with the power $k$?
-Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}.
-Moreover, so far, all the constants $C_{{\PF},T,p}$, $C_{{\PF},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\PF},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{subsection: PX_convex} have it outside.
-Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous.
-We should unify.}
-
 \section{Numerical examples}\label{section:numericalexamples}

### 2024-10-06 main.tex
spell check

@@
     % 
-    % Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently msall radius. The proof is complete. 
+    % Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently small radius. The proof is complete. 
 \end{proof}
@@
 
-\caption{Left: manifold triangulation of an anulus. Right: not a manifold triangulation.}
+\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}
 \label{figure:not_manifold_triang}
@@
     The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
-    by the topological Sch\"onfliess theorem. 
+    by the topological Schoenflies theorem. 
     It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
@@
 
-We will use the following observaton, which we state without proof, 
+We will use the following observation, which we state without proof, 
 that controls the volume and some heights when a simplex is partitioned via barycentric subdivision.
@@
 	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Minako_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
-	This mapping and its inverse are piecewiselinear, and it acts as the identity along $\partial \Minako_{M-1} \setminus \partial T$.
+	This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Minako_{M-1} \setminus \partial T$.
     We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.

### 2024-10-06 main.tex
clean up

@@
 \end{gather*}
-We also write $\Minako_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
 A crucial structural observation is the following.
@@
 
-% \begin{remark}
-%     While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains.  
-% \end{remark}
-
 The next auxiliary result establishes Poincar\'e--Friedrichs constants over face patches within simplicial triangulations. 
@@
     \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET); 
-
-%     \node at (A) [below left] {$A$};
-%     \node at (B) [below right] {$B$};
-%     \node at (C) [above] {$C$};
-%     \node at (D) [above right] {$D$};
-%     \node at (T) [above right] {$T$};
 \end{tikzpicture}
@@
         C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
+        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
         ,
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Minako_{F_m},p} 
-        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
+        C_{{\PF},\Makoto_{F_m},p} 
+        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
         . 
@@
     Recall that we write $F_m := T_m \cap T_{m-1}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$,
-    and that we write $\Minako_{F_m} := T_m \cup T_{m-1}$.
+    and that we write $\Makoto_{F_m} := T_m \cup T_{m-1}$.
 
@@
     Suppose again that $1 \leq m \leq M$. 
-    We use the Poincar\'e--Friedrichs inequality over $\Minako_{F_{m}}$,
+    We use the Poincar\'e--Friedrichs inequality over $\Makoto_{F_{m}}$,
     as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
-    to find $w_{F_m} \in W^{1,p}(\Minako_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Minako_{F_m}$ and 
+    to find $w_{F_m} \in W^{1,p}(\Makoto_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Makoto_{F_m}$ and 
     \begin{align}\label{math:wFm_inequality}
-        \| w_{F_m} \|_{L^{p}(\Minako_{F_m})} \leq C_{{\PF},\Minako_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Minako_{F_m})}.
+        \| w_{F_m} \|_{L^{p}(\Makoto_{F_m})} \leq C_{{\PF},\Makoto_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Makoto_{F_m})}.
     \end{align}
-%     \cye{Since $\nabla (w_{|\Minako_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Minako_{F_m}})$, 
+%     \cye{Since $\nabla (w_{|\Makoto_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Makoto_{F_m}})$, 
     We can define the constant
     \begin{align*}
-    c_{m} := w_{|\Minako_{F_m}} - w_{F_{m}}.
+    c_{m} := w_{|\Makoto_{F_m}} - w_{F_{m}}.
     \end{align*}
@@
         \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \| w_{F_{m}} \|_{L^{p}(\Minako_{F_m})} 
+        \| w_{F_{m}} \|_{L^{p}(\Makoto_{F_m})} 
         +
@@
         \right)
-        \| w_{F_m} \|_{L^{1}(\Minako_{F_m})}
+        \| w_{F_m} \|_{L^{1}(\Makoto_{F_m})}
         +
@@
         2
-        \| w_{F_m} \|_{L^{\infty}(\Minako_{F_m})}
+        \| w_{F_m} \|_{L^{\infty}(\Makoto_{F_m})}
         +
@@
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Minako_{F_\ell},p} 
+        C_{{\PF},\Makoto_{F_\ell},p} 
         ,
@@
         \right)
-        \| \nabla u \|_{L^{p}(\Minako_{F_\ell})}
+        \| \nabla u \|_{L^{p}(\Makoto_{F_\ell})}
         \\&
@@
     The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches $\{ \Minako_m \}$ of $n$-simplices with an appropriate notion of connectivity.
-    The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$. 
+Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches $\{ \Makoto_m \}$ of $n$-simplices with an appropriate notion of connectivity.
+    The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Makoto_m \}$. 
     This may allow for partitions of $\overline \Omega$ with significantly fewer elements, which enables a largely improved estimate of the best Poincar\'e--Friedrichs constant. 
@@
 
+Our discussion requires some notions and results concerning triangulated manifolds. 
 We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
@@
     in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk. % TODO: why are those two disks?
+    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk. 
     By the induction assumption, each of those components contains at least two triangles 
@@
     \begin{align*}
-        \Minako := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
+        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
         \qquad 
-        {\Gamma_1} := \Minako \cap T,
+        {\Gamma_1} := \Makoto \cap T,
         \qquad 
-        {\Gamma_2} := \overline{ \partial T \setminus \partial \Minako }.
+        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
     \end{align*}
@@
     \begin{align*}
-        \Xi_{1} : T \rightarrow \Minako
-    \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap \Minako$. 
+        \Xi_{1} : T \rightarrow \Makoto
+    \end{align*}
+    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Minako
-    \end{align*}
-    which is the identity along $\partial \Minako \setminus \partial T$.
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto
+    \end{align*}
+    which is the identity along $\partial \Makoto \setminus \partial T$.
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
         Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
-        % Let $I := \Minako \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
+        % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
         %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
@@
         Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = \Minako \cap T$ is the union of exactly those faces of $T$ that contain $S$.
+        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
 
@@
         \item 
-        We define a mapping $ \Xi_{1} : T \rightarrow \Minako = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
+        We define a mapping $ \Xi_{1} : T \rightarrow \Makoto = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
         \begin{align*}
@@
         \end{align*}
-        It preserves the interface from $T$ onto $\Minako$. 
+        It preserves the interface from $T$ onto $\Makoto$. 
         Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
@@
         \item 
-        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Minako $ by setting 
+        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto $ by setting 
         \begin{align*}
@@
     onto the face $F_i$. 
-    In what follows, we let $\widetilde \Minako$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
-    We see that $\vol(\widetilde \Minako) = (l+1)/n!$
+    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
+    We see that $\vol(\widetilde \Makoto) = (l+1)/n!$
 
@@
     Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u$ be the extension of $\hat u$ onto $\widetilde \Minako$ by reflection across the coordinate axes,
-    and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Minako$ by reflection across the coordinate axes. 
+    We let $\tilde u$ be the extension of $\hat u$ onto $\widetilde \Makoto$ by reflection across the coordinate axes,
+    and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
     We observe $\tilde g = \cartan \tilde u$. 
-    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Minako)$.
+    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$.
 
     The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
-    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Minako)$
+    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
     with $\cartan \tilde w = \cartan \tilde u$ and 
     \begin{align*}
-        \| \tilde w \|_{L^{p}(\widetilde \Minako)}
+        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
         &\leq 
-        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Minako) } 
+        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 
         2
-        \| \tilde g \|_{L^{p}(\widetilde \Minako)}
+        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
         \\&\leq 
         2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
-        \| \tilde g \|_{L^{p}(\widetilde \Minako)}
+        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
         .
@@
         \\
-        \| \tilde g \|_{L^{p}(\widetilde \Minako)}
+        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
         \leq 
@@
 \begin{align*}
-    \Minako_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}.
-\end{align*}
-for the complement $\Minako_{m-1} \subseteq X_{m-1}$ of the simplex $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
+    \Makoto_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}.
+\end{align*}
+for the complement $\Makoto_{m-1} \subseteq X_{m-1}$ of the simplex $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
 
@@
             \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-            \| \cartan u \|_{L^{p}(\Minako_{m-1})}
+            \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
         \right)
@@
         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(\Minako_{m-1})}
+        \| w \|_{L^{p}(\Makoto_{m-1})}
         .
@@
     In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S_{m}$, 
-	and we let $\Minako_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Minako_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
+	and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
     We define $w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$. 
@@
         % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k}
-        % \|\det \Jacobian \Xi_{1}^{-1}  \|_{L^{\infty}(\Minako_{m-1})}^{\frac 1 p} 
+        % \|\det \Jacobian \Xi_{1}^{-1}  \|_{L^{\infty}(\Makoto_{m-1})}^{\frac 1 p} 
         % \cdot 
-        % \| w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        % \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
         % ,
@@
         % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k+1}
-        % \|\det \Jacobian \Xi_{1}^{-1}  \|^{\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        % \|\det \Jacobian \Xi_{1}^{-1}  \|^{\frac 1 p}_{L^{\infty}(\Makoto_{m-1})} 
         % \cdot 
-        % \| \cartan w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        % \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
         % .
@@
         \cdot 
-        \| w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
         ,
@@
         \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(\Minako_{m-1})}
+        \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
         .
@@
 	By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
-	and we let $\Minako_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star.
-
-	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Minako_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
-	This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Minako_{M-1} \setminus \partial T$.
+	and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star.
+
+	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Makoto_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
+	This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{M-1} \setminus \partial T$.
     We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.
@@
 which relies on estimates for the Bogovski\u{i} operator over an auxiliary reference domain.
-Our experiments over triangles and tetrahedra indicate we overestimate by several magnitudes.
+Our experiments over triangles and tetrahedra indicate that we overestimate the constant by several magnitudes.
 %
@@
 There are several avenues for further research. 
-
-Our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), as there are at least two areas where the present techniques could see further improvement.
-First, we use local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) likely allow room for improvement.
-Second, our construction uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
-In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques could lead to better estimates.
-
-With regard to estimating Poincar\'e--Friedrichs constants over single simplices, we conjecture that the Guerini--Savo~\cite{guerini2004eigenvalue} estimates, hitherto only known when $p=2$ and over bounded convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently employ.
+In particular, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), 
+as there are at least two areas where the present techniques could see further improvement.
+
+Firstly, we use local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) likely allow room for improvement.
+We conjecture that the Guerini--Savo~\cite{guerini2004eigenvalue} estimates, hitherto only known when $p=2$ and over bounded convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and convex Lipschitz domains.
+We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized Poincar\'e operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently employ.
+Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{i} operators.
+
+Secondly, our construction uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
+In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques could lead to better estimates,
+such as via trace and extension operators.
 
 Lastly, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is restricted to topological balls and spheres. 
-In particular, domains with shellable triangulations are contractible. 
-We expect forthcoming works to utilize these estimates as subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+In particular, the underlying set of any shellable triangulations is contractible. 
+We expect forthcoming works to utilize our estimates over local patches as subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
 

### 2024-10-06 main.tex
more clean up

@@
 
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite[Remark~\mwl{todo}]{ern2021finite}.
+We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite[Remark~3.32]{ern2021finite}.
 Given $p \in [1,\infty]$ and a domain $\Omega \subseteq \bbR^{n}$ of finite measure,
@@
 Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
+We introduce the gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
 $\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
@@
 
-\mwl{We now move the discussion to exterior calculus, beginning with exterior algebra.}
+We now move the discussion to exterior calculus, beginning with exterior algebra.
 Let $V$ be a real vector space. 
@@
     The boundary complex $\partial \calT(T)$ has a shelling:
-    any enumeration of the boundary faces of $T$ constitutes a shelling\mwl{; see Example 8.2.(iii) in~\cite{ziegler1995lectures}}.
+    any enumeration of the boundary faces of $T$ constitutes a shelling; see Example 8.2.(iii) in~\cite{ziegler1995lectures}.
 \end{example}
@@
 
-        % TODO Check that $\calS'$ is a triangulation...
+        % TODO Check that $\calS'$ is a triangulation
 

### 2024-10-06 main.tex
delete old paragraph

@@
 
-%\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}
+\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}
 
@@
 
-%\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
+\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
 
@@
 
-%\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
+\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
 
@@
 
-%\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
+\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
 
@@
 
-%\subsection{\cye{Objectives and methodology}}
+\subsection{\cye{Objectives and methodology}}
 
@@
 
-% \subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
+\subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
 
@@
 
-%\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
+\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
 
@@
 
-%\subsubsection{\cye{Analytical constants over convex domains}}
+\subsubsection{\cye{Analytical constants over convex domains}}
 
@@
 
-%\subsubsection{\cye{Domains star-shaped with respect to a ball}}
+\subsubsection{\cye{Domains star-shaped with respect to a ball}}
 
@@
 
-%\subsubsection{\cye{Potentials subject to partial boundary conditions}}
+\subsubsection{\cye{Potentials subject to partial boundary conditions}}
 
@@
 
-%\subsection{\cye{Main results}}
+\subsection{\cye{Main results}}
 
@@
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-There are several avenues for further research going from here. 
-The upper bounds in this manuscript are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches.
-There are at least two points where the present techniques can be improved further.
-First, we utilize local Poincar\'e--Friedrichs constants over single simplices, subject to various boundary conditions, but these local estimates over convex domains likely leave room for improvement.
-Second, our construction needs to extend differential forms onto a simplex from the complement of that simplex inside a local star.
-In the present manuscript, this is achieved via pullback along a bi-Lipschitz mapping.
-Better transformations or more careful estimates are likely possible, as are completely different approaches.
-For example, it is likely that further research on trace and extension operators on triangulations will enable better estimates.
-
-Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators.
-On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
-These topics remain for future research.
-
-Estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of disks and spheres.
-In particular, domains with shellable triangulations are contractible.
-However, these estimates are important partial results.
-Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
 \\

### 2024-10-06 main.tex
work on introduction

@@
     %
-    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over convex bounded domains. 
+    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains. 
     This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
@@
 Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance. 
-The operator norms of the\cye{se} potentials are upper bounds for the Poincar\'e--Friedrichs constants, which quantify the fundamental stability features of a variety of partial differential equations.
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant\cye{s} enter the stability and convergence theory and spectral bounds for \cye{stiffness} matrices.
-\cye{Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians}.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or \cye{more generally} the exterior derivative are \cye{largely unavailable}.
-
-\cye{Our main purpose here is to fill this gap.
-In the gradient case, we can go over with so-called face-connected triangulations.
-However, to proceed} in the \cye{general exterior derivative case, we are brought to} so-called shellable triangulations.
+The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
+which quantify the fundamental stability features of a variety of partial differential equations. 
+In numerical methods, estimates for the Poincar\'e--Friedrichs constants enter the stability and convergence theory and spectral bounds for stiffness matrices. 
+Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians. 
+However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
+quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.
+
+This manuscript aims to fill this gap.
+\cye{In the gradient case, we can go over with so-called face-connected triangulations.
+However, to proceed in the general exterior derivative case, we are brought to so-called shellable triangulations.}
 Even though only contractible domains can ever admit a shellable triangulation, 
 having computable upper bounds for such domains is an important stepping stone towards more general cases.
-\cye{Still, we cover most practical non-convex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions.
-\cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}
+\cye{We cover most practical non-convex and non-star-shaped triangulated domains,} and as a particular example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars), which are shellable in two and three spaces dimensions.
+Additionally, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
+
+% old
+Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
+The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
+which quantify the fundamental stability features of a variety of partial differential equations.
+However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
+
+We illustrate the subject of our discussion with the curl operator. 
+If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
+we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
+Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
+\begin{align*}
+    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
+    \leq 
+    C_{\curl}
+    \| \bff \|_{L^{2}(\Omega)}
+    .
+\end{align*}
+The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
+Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
+In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
+\\
+
+Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
+The majority of estimates in the literature address only gradient potentials. 
+We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
+Even though only contractible domains can ever admit a shellable triangulation, 
+having computable upper bounds for such domains is an important stepping stone towards the more general case. 
+For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
+Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
+\\
+
+\subsection{Conceptual overview: gradient}
+
+Before we outline the main results of this exposition in more detail, 
+we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
+We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
+
+Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
+we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
+for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
+such that $\nabla u = \bff$ and 
+\begin{align}\label{math:intro:inequalitypf:gradient} 
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p} 
+    \| \bff \|_{L^{p}(\Omega)}
+    .
+\end{align}
+We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+The different scalar potentials only differ by a constant. 
+Therefore, 
+this inequality is equivalent to the following statement: 
+\begin{align}\label{math:intro:poincarefriedrichs:grad}
+    \min\limits_{c\in\bbR}
+    \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall
+    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
+    .\tag{PF} 
+\end{align}
+Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
+The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
+% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
+One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
+\begin{align*}
+    \Phi_{\grad}( \bff ) 
+    := 
+    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    \bff \in \nabla W^{1,p}(\Omega)
+    .
+\end{align*} 
+Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
+\begin{align}\label{math:intro:poincare:grad}
+    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\varnothing,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    , \tag{P} 
+\end{align}
+where $u_\Omega$ denotes the average of $u$.
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
+
+Most research on optimal constants has addressed the case of convex domains. 
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+When the domain is not convex but star-shaped with respect to a ball,
+then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
+Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence
+
+\subsection{Conceptual overview: Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality} \label{subsection:intro_grad}
 
@@
 Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
-
-\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}
 
@@
 
-\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}
+\subsection{Conceptual overview: Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities} \label{section:intro_curl_div}
 
@@
 
-\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}
+\subsection{Conceptual overview: curl, divergence, exterior derivative}
+
+The situation is less clear cut when we study the curl or divergence operators in vector calculus.
+We use the vector field spaces
+\begin{align*}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
+    .
+\end{align*}
+Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
+This only requires that certain sums of distributional partial derivatives are integrable, 
+and hence these spaces are not classical Sobolev spaces of vector fields. 
+Our objective is to find bounded potentials for the operators 
+\begin{align*}
+    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
+    \qquad 
+    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
+\end{align*}
+The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
+In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
+The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
+We are interested in constants for inequalities such as 
+\begin{align*}
+    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
+    \| \bfv \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\curl,\Omega,p}
+    \| \bff \|_{L^{p}(\Omega)}
+    ,
+    \\%\qquad 
+    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
+    \| \bfv \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\divergence,\Omega,p}
+    \| f \|_{L^{p}(\Omega)}
+    ,
+\end{align*}
+and how these constants can be estimated by the operator norms of linear potential operators 
+\begin{align*}
+    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \\
+    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
+\end{align*}
+
+Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
+This sharply contrasts to the study of the gradient operator. 
+We can access some estimates from the literature in the formalism of exterior calculus. 
+We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
+who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
+thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
+By duality, that implies lower bounds for the case of full boundary conditions.
+
+\subsection{Conceptual overview: Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities} \label{section:intro_EC}
 
@@
 
-\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}
+\mwl{What is the best place for this paragraph?}
+Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
+Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
+Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
+The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
+For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
+\\
+
+\subsection{Review: Analytical constants over convex domains}
+
+\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
+Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
+In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
+The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms. 
+\\
+
+When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
+follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
+as mappings between Lebesgue spaces. 
+We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
+but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+\\
+
+\subsection{Review: Domains star-shaped with respect to a ball}
+
+\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
+This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
+Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
+This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this \cye{in particular} occurs when the domain has sharp reentrant corners.
+Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
+which contain local finite element patches \cye{that} are not star-shaped with respect to any ball. 
+\\
+
+The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
+Clearly, not all local stars describe convex subdomains. 
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
+which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
+However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
+This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
+which contain finite element patches are not star-shaped with respect to any ball.
+
+\subsection{Review: Potentials subject to partial boundary conditions}
+
+\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
+\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
+We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
+\\
+
+In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
+The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
+we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
+We achieve this by constructing an auxiliary problem subject to full boundary conditions.
+\\
+
+\subsection{Objectives: convex domains}
+
+Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
+Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
+While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
+the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
+
+In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+
+However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
+We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
+In comparison to their exposition, our variants of the regularized potential operators are simplified:
+we only study them over convex domains and use simpler (that is, constant) weight functions. 
+The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
+however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
+We consider the latter outcome to be of independent interest.
+
+\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}
 
@@
 
-\subsection{\cye{Objectives and methodology}}
+\subsection{Objectives and methodology}
 
@@
 
-\subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}
+\subsection{Combinatorial constants over face-connected triangulated domains}
 
@@
 
-\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}
+\subsection{Combinatorial constants over shellable triangulated domains}
 
@@
 
-\subsubsection{\cye{Analytical constants over convex domains}}
-
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
-Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
-In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
-The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
-
-\subsubsection{\cye{Domains star-shaped with respect to a ball}}
-
-\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
-This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
-Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
-This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this \cye{in particular} occurs when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
-which contain local finite element patches \cye{that} are not star-shaped with respect to any ball.
-
-\subsubsection{\cye{Potentials subject to partial boundary conditions}}
-
-\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
-We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
-
-\subsection{\cye{Main results}}
+\subsection{Main results}
 
@@
 
-\section{Introduction}\label{section:intro}
-
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-
-We illustrate the subject of our discussion with the curl operator. 
-If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
-Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
-    \leq 
-    C_{\curl}
-    \| \bff \|_{L^{2}(\Omega)}
-    .
-\end{align*}
-The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
-Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
-\\
-
-Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-The majority of estimates in the literature address only gradient potentials. 
-We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards the more general case. 
-For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
-Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
-\\
-
-Before we outline the main results of this exposition in more detail, 
-we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-
-Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
-for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:intro:inequalitypf:gradient} 
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The different scalar potentials only differ by a constant. 
-Therefore, 
-this inequality is equivalent to the following statement: 
-\begin{align}\label{math:intro:poincarefriedrichs:grad}
-    \min\limits_{c\in\bbR}
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
-    .\tag{PF} 
-\end{align}
-Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
-The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
-\begin{align*}
-    \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
-\begin{align}\label{math:intro:poincare:grad}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\varnothing,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    , \tag{P} 
-\end{align}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
-
-Most research on optimal constants has addressed the case of convex domains. 
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence
-
-The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-We use the vector field spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align*}
-Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
-\begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
-    \qquad 
-    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
-\end{align*}
-The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
-We are interested in constants for inequalities such as 
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)}
-    ,
-    \\%\qquad 
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
-and how these constants can be estimated by the operator norms of linear potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-
-Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-This sharply contrasts to the study of the gradient operator. 
-We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
-who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
-thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
-By duality, that implies lower bounds for the case of full boundary conditions.
-
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
-follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-\\
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
-which contain finite element patches are not star-shaped with respect to any ball.
+\subsection{Review: Triangulated domains}
 
@@
 Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-% 
+
 The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
@@
 
-% General outline 
+\subsection{Objective: sequential approach} 
 We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
@@
 
+\subsection{Objective: shellable triangulations}
 Shellable triangulations are defined by a special constructive property:
@@
 
-Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
-the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
-
-In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-
-However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
-We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
-In comparison to their exposition, our variants of the regularized potential operators are simplified:
-we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
-however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
-We consider the latter outcome to be of independent interest.
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-\mwl{What is the best place for this paragraph?}
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-\paragraph{Notation}
-
-\mwl{Fix this}
-Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
-where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
-We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
-and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
-% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.
+\subsection{Notation}
+
+Whenever $x \in \bbR^{n}$ is a vector, we write $\|x\| = \|x\|_{2}$ for its Euclidean norm, 
+and whenever $A \in \bbR^{n \times n}$, we let $\| A \|_{2}$ be its operator norm with respect to the Euclidean norm. 
+Furthermore, $\Jacobian F$ always denotes the Jacobian of any mapping $F$.
 
@@
 
-%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
+%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.}
+Let $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.
 
@@
 \begin{theorem}\label{theorem:bogovpoinc}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set and let $1 \leq p \leq \infty$. 
     We have bounded operators 
@@
 
-    {\color{blue}
+    \mwl{ 
     Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
@@
 \begin{lemma}\label{lemma:PFexteriorsimplex}
-    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set. 
     Let $0 \leq k < n$. 

### 2024-10-07 intro.tex
introduction, main theorems

--- 2024-10-06 main.tex
@@
-\documentclass[10pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{fullpage}
-% \usepackage[margin=0.1cm]{geometry}
-\input{header}
-
-\usepackage{comment}          % 
-\usepackage[colorlinks=true]{hyperref}         % For hypertext links
-% Make the hyperlinks look similar to arXiv's
-\hypersetup{
-    colorlinks=true,
-    linkcolor=green,    % Color of internal links (sections)
-    citecolor=red,    % Color of citations
-    urlcolor=blue,     % Color for URLs
-    urlbordercolor={1 1 1},
-    pdfborder={0.5 0.5 0}  % Removes the border around the links
-}
-\usepackage{tikz-3dplot}      % 3d plots 
-\usepackage{enumitem}
-\setitemize[1]{left=0.0cm}
-
-% Added by MV 
-\usepackage{bm} % preferred version of bold symbols
-\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
-% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
-% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
-\newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
-\setlength{\marginparwidth}{2cm}
-
-\newcommand\cye[1]{%
-\protect\leavevmode
-\begingroup
-    \color{blue}%
-    #1%
-\endgroup
-}
-% \color{red!35!yellow}
-
-\newcommand{\mwl}[1]{{\color{red}#1}}
-\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
-\newcommand{\disk}{\cye{ball}}
-
-% Title, authors, and affiliations
-% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
-% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
-
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations}
-\author{
-    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
-    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-    We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations. 
-    The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry. 
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
-    % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
-    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
-    % 
-    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
-    %     The main application that we envision are computable estimates over finite element patches. 
-    %
-    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains. 
-    This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
-    \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
-    Computational examples illustrate the theoretical findings.
-\end{abstract}
-
-\tableofcontents
-
-\section{Introduction}\label{section:intro}
-
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance. 
-The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations. 
-In numerical methods, estimates for the Poincar\'e--Friedrichs constants enter the stability and convergence theory and spectral bounds for stiffness matrices. 
-Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians. 
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
-quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.
-
-This manuscript aims to fill this gap.
-\cye{In the gradient case, we can go over with so-called face-connected triangulations.
-However, to proceed in the general exterior derivative case, we are brought to so-called shellable triangulations.}
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards more general cases.
-\cye{We cover most practical non-convex and non-star-shaped triangulated domains,} and as a particular example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars), which are shellable in two and three spaces dimensions.
-Additionally, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
-
-% old
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-
 We illustrate the subject of our discussion with the curl operator. 
@@
 
-\subsection{Conceptual overview: gradient}
-
 Before we outline the main results of this exposition in more detail, 
 we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains.
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-
-Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
-for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:intro:inequalitypf:gradient} 
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The different scalar potentials only differ by a constant. 
-Therefore, 
-this inequality is equivalent to the following statement: 
-\begin{align}\label{math:intro:poincarefriedrichs:grad}
-    \min\limits_{c\in\bbR}
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
-    .\tag{PF} 
-\end{align}
-Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
-The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
-\begin{align*}
-    \Phi_{\grad}( \bff ) 
-    := 
-    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*} 
-Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
-\begin{align}\label{math:intro:poincare:grad}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\varnothing,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    , \tag{P} 
-\end{align}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
 
@@
 
-\subsection{Conceptual overview: Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality} \label{subsection:intro_grad}
-
-Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be a bounded connected open set.
-Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
-Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
-
-Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
-\begin{align} \label{equation:W1p}
-    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
-\end{align}
-For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
-Then,
-%
-\begin{align*}
-    \Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
-\end{align*}
-is the {\em potential operator}. A particular example of our interest is
-%
-\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
-    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
-\end{align}
-%
-Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
-
-\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
-\begin{align}\label{math:pot_grad_norm}
-    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
-\end{align}\end{subequations}}
-This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
-\begin{subequations}\label{math:PF_gradient}\begin{align} \label{math:PF_gradient_1}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
-\begin{align} \label{math:PF_gradient_2}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p}
-    \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}\end{subequations}
-We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
-\begin{align} \label{math:pot_PF_grad}
-    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
-    \| u \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\grad,\Omega,p}
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-for all $\bff \in \nabla W^{1,p}(\Omega)$.}
-
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
-Most research on optimal constants has addressed the case of convex domains.
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
-\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
-
-\subsection{Conceptual overview: Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities} \label{section:intro_curl_div}
-
-Consider the vector-valued spaces
-\begin{subequations}\label{equation:W_curl_div_p} \begin{align}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align}\end{subequations}
-The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector  fields.
-
-\cye{Let a vector field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
-We are interested in constants for inequalities such as 
-\begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
-    ,
-    \\
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfu = f } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
-    ,
-\end{align}\end{subequations}
-and how these constants can be estimated by the operator norms of {\em linear} potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-The fundamental difference \cye{with respect to Section~\ref{subsection:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
-In Section~\ref{subsection:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
-It is thus trivially complemented for all $p$, with a canonical choice of projection.
-By contrast, in the Banach space case $p \neq 2$, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
-\cye{Actually,} the existence of a bounded linear potential operator here is a non-trivial fact even in the Hilbert space case $p = 2$.
-
-\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
-Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
-\begin{align}
-    \label{math:Weber}
-    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
-\end{align}
-for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
-Yet another writing is 
-\label{math:PF_orth} \begin{align}
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
-\end{align}
-for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
-Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
-However, that easy observation seems restricted to $p=2$.
-
-Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
-\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
-
-\subsection{Conceptual overview: curl, divergence, exterior derivative}
-
-The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-We use the vector field spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align*}
-Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
-\begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
-    \qquad 
-    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
-\end{align*}
-The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
-We are interested in constants for inequalities such as 
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)}
-    ,
-    \\%\qquad 
-    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
-    \| \bfv \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
-and how these constants can be estimated by the operator norms of linear potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-
-Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-This sharply contrasts to the study of the gradient operator. 
 We can access some estimates from the literature in the formalism of exterior calculus. 
@@
 
-\subsection{Conceptual overview: Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities} \label{section:intro_EC}
-
-Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
-This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
-\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $w \in W^{p}\Alt^{k}(\Omega)$, there exists $u \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
-\begin{align} \label{math:PF_DF} 
-    \| u \|_{L^{p}(\Omega} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
-\end{align} 
-}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparison with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
-
-In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
-\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
-
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
-\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
-Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-
-\mwl{What is the best place for this paragraph?}
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
-\\
-
-\subsection{Review: Analytical constants over convex domains}
-
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
-Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
-In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
-The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms. 
-\\
-
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
-follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-\\
-
-\subsection{Review: Domains star-shaped with respect to a ball}
-
-\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
-This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
-Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
-This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this \cye{in particular} occurs when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
-which contain local finite element patches \cye{that} are not star-shaped with respect to any ball. 
-\\
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
-which contain finite element patches are not star-shaped with respect to any ball.
-
-\subsection{Review: Potentials subject to partial boundary conditions}
-
-\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
-We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
-\\
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-\subsection{Objectives: convex domains}
-
-Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
-the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
-
-In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-
-However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
-We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
-In comparison to their exposition, our variants of the regularized potential operators are simplified:
-we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
-however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
-We consider the latter outcome to be of independent interest.
-
-\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}
-
-\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
-\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
-Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
-\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
-\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
-
-\subsection{Objectives and methodology}
-
-The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
-\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
-
-\subsection{Combinatorial constants over face-connected triangulated domains}
-
-Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
-For scalar-valued functions in the context of Section~\ref{subsection:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
-%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
-Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
-
-In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-\subsection{Combinatorial constants over shellable triangulated domains}
-
-For vector fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
-We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
-However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
-Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
-With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
-
-\subsection{Main results}
-
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{subsection:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} is our main results.}
-\mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
-The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
-\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
-
-\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
-As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-
-\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
-\cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
-
-\subsection{Review: Triangulated domains}
-
-Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
-However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
-We review some of the main outcomes. 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-
-The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
-The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
-Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the interfacing intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed to ensure continuity across that interface.
-
-While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
-we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
-We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
-which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
-We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
-
-\subsection{Objective: sequential approach} 
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-\\
-
-\subsection{Objective: shellable triangulations}
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable. 
-\\
-
-\subsection{Notation}
-
-Whenever $x \in \bbR^{n}$ is a vector, we write $\|x\| = \|x\|_{2}$ for its Euclidean norm, 
-and whenever $A \in \bbR^{n \times n}$, we let $\| A \|_{2}$ be its operator norm with respect to the Euclidean norm. 
-Furthermore, $\Jacobian F$ always denotes the Jacobian of any mapping $F$.
-
-\subsection{Organization of this manuscript}
-
-The remainder of this manuscript is structured as follows.
-We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
-We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.
-We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
-We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
-Our regularized potential operators over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
-giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
-We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
-and we construct an important geometric reflection operator in Section~\ref{section:extension}. 
-We finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}.
-
-\section{Review of Poincar\'e and Poincar\'e--Friedrichs inequalities}\label{section:poincare}
-
-This section surveys variations of the Poincar\'e--Friedrichs inequalities for the gradient operator,
-with emphasis on analytical upper bounds over bounded convex domains. 
-We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potential operators.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
-\\
-
-Let $\Omega \subseteq \bbR^{n}$ be an open connected set. 
-Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
-We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-% DONE: MV move this part to the introduction, as an alternative the first few paragraphs
-
-We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
-if there exists a constant $C_{\grad,\Omega,p} \geq 0$ such that the following holds:
-for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
-such that $\nabla u = \bff$ and 
-\begin{align}\label{math:inequalitypf:gradient}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{L^{p}(\Omega)}
-    .
-\end{align}
-Since $\Omega$ is connected, this is equivalent to  
-\begin{align*}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$.
-
-\subsection{Relationship with Poincar\'e inequalities}
-
-We wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known as Poincar\'e inequality (or also Poincar\'e--Wirtinger or Friedrichs inequality) in the literature~\cite[Remark~3.32]{ern2021finite}.
-Given $p \in [1,\infty]$ and a domain $\Omega \subseteq \bbR^{n}$ of finite measure,
-we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
-if there exists $C_{\varnothing,\Omega,p} \geq 0$ such that 
-% for all $u \in W^{1,p}(\Omega)$
-\begin{align*}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\varnothing,\Omega,p} 
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall u \in W^{1,p}(\Omega)
-    ,
-\end{align*}
-where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
-\begin{align*}
-    u_{\Omega} := \vol(\Omega)^{-1} \int_{\Omega} u(x) \;dx.
-\end{align*}
-Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have 
-\[
-    C_{\grad,\Omega,p} \leq C_{\varnothing,\Omega,p}.
-\]
-Towards a converse inequality, 
-let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align} \label{math:aver_norm}
-    \| u_\Omega \|_{L^{p}(\Omega)}^{p}
-    = 
-    \int_{\Omega} \left( \vol(\Omega)^{-1} \int_{\Omega} |u(x)| \;dx \right)^{p}
-    \leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \int_{\Omega} |u(x)|^{p} \;dx
-    = 
-    \| u \|_{L^{p}(\Omega)}^{p}
-    .
-\end{align}
-Here, we have used H\"older's or Jensen's inequality. 
-In the case $p = \infty$, any $u \in L^{\infty}(\Omega)$ satisfies $\| u_\Omega \|_{L^{\infty}(\Omega)} \leq \| u \|_{L^{\infty}(\Omega)}$. 
-We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 
-The triangle inequality now shows that 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)} 
-    \leq
-    2
-    \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-Thus, the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with 
-\begin{align}\label{math:p_is_smaller_than_pf}
-    C_{\grad,\Omega,p} \leq 2 C_{\varnothing,\Omega,p}.
-\end{align}
-In the special case $p=2$, taking the average is an orthogonal projection, 
-and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. 
-Hence,
-\begin{align}\label{math:pf_equals_p_in_hilbertspace}
-    C_{\varnothing,\Omega,2} = C_{\grad,\Omega,2}. 
-\end{align}
-% This improvement follows from the orthogonality of constant functions to average-free functions in $L^2(\Omega)$. 
-This improvement also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
-Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, from~\eqref{math:aver_norm} it now follows that 
-% From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
-\begin{align*}
-    \| u - u_\Omega \|_{L^{p}(\Omega)}
-    \leq 
-    \min\left( 2, 2^{|2/p-1|} \right)
-    \| u \|_{L^{p}(\Omega)}
-    = 
-    2^{|2/p-1|} 
-    \| u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in L^{p}(\Omega)
-    .
-\end{align*}
-Here, we have used $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
-We thus conclude 
-\begin{align}\label{math:p_vs_pf}
-    C_{\grad,\Omega,p} \leq 2^{|2/p-1|} C_{\varnothing,\Omega,p}.
-\end{align}
-In the limit cases $p = 1$ and $p = \infty$ we reproduce~\eqref{math:p_is_smaller_than_pf}, 
-and in the case $p = 2$ we achieve the identity~\eqref{math:pf_equals_p_in_hilbertspace} once again.
-In summary, our notion of Poincar\'e--Friedrichs constant is equivalent to the common notion of Poincar\'e constant, up to a numerical factor that only depends on $1 \leq p \leq \infty$ and that is at most $2$.
-
-\begin{remark}
-    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} suits our discussion better than the Poincar\'e inequality. 
-    We want to generalize the discussion to the curl and divergence operators. 
-    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
-    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
-    Hence, it is not even trivial whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
-    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
-    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
-    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
-\end{remark}
-
-\subsection{Relationship with potential operators}
-
-There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
-We define the potential 
-\begin{align*}
-    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
-    \quad 
-    \forall 
-    \bff \in \nabla W^{1,p}(\Omega)
-    .
-\end{align*}
-If there is a Poincar\'e--Friedrichs constant, then by definition
-\begin{align*}
-    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\grad,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
-\end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
-Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$.
-
-Because $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$,
-any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
-satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
-\begin{align*}
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    \leq 
-    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
-    .
-\end{align*}
-A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
-\begin{align*}
-    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align*}
-Its operator norm is just the optimal Poincar\'e constant $C_{\varnothing,\Omega,p}$.
-
-\begin{remark}
-    Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potential operators. 
-    We highlight this perspective because it seems to be most promising when generalizing the discussion to the curl and divergence operators. 
-\end{remark}
-
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains} \label{subsection: PX_convex}
-
-We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of bounded convex domains. 
-We have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
-\begin{align}\label{math:acostaduran}
-    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{\diam(\Omega)}{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    ,
-    \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
-    \leq 
-    \frac{\diam(\Omega)}{\pi}
-    \| \nabla u \|_{L^{2}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,2}(\Omega)
-    ,
-\end{align}
-where $\diam(\Omega)$ is the diameter of the domain $\Omega$.
-These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
-Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
-\begin{align}\label{math:chuawheeden}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm CW},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where we use an upper bound by Chua and Wheeden:
-\begin{align*}
-    C_{{\rm CW},p} 
-    := 
-    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
-    \frac{ 
-        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
-    }{ 
-        \| \nabla v \|_{L^{p}([0,1])} 
-    }
-    \leq 
-    \sqrt[p]{p} 2^{1-\frac 1 p}
-    =
-    2
-    \left( \frac p 2 \right)^{\frac 1 p}
-    .
-\end{align*} 
-Note that \eqref{math:chuawheeden} is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
-As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
-
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}, \cite[Theorem~1.1]{esposito2013poincare}): 
-when $1 < p < \infty$, one can show that 
-\begin{align}\label{math:esposito:pf}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    ,
-\end{align}
-where $C_{{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
-\begin{align*}
-    C_{{\rm EFNT},p}
-    :=
-    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
-    .
-\end{align*}
-Note that the last inequalities from~\eqref{math:p_vs_pf} imply, again when $1 < p < \infty$, the Poincar\'e inequalities
-\begin{align}\label{math:esposito:poincare}
-    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
-    \leq 
-    2^{|1-\frac 2 p|}C_{{\rm EFNT},p}
-    \diam(\Omega)
-    \| \nabla u \|_{L^{p}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-When $p=1$, then the optimal Poincar\'e constant also bounds the Poincar\'e--Friedrichs constant:
-\begin{align}\label{math:l1estimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{1}(\Omega)}
-    \leq 
-    \frac{ \diam(\Omega) }{2}
-    \| \nabla u \|_{L^{1}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,1}(\Omega)
-    .
-\end{align}
-When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
-\begin{align}\label{math:lipschitzestimate}
-    \min\limits_{ c \in \bbR }
-    \| u - c \|_{L^{\infty}(\Omega)}
-    \leq 
-    \diam(\Omega)
-    \| \nabla u \|_{L^{\infty}(\Omega)}
-    ,
-    \quad 
-    \forall 
-    u \in W^{1,\infty}(\Omega)
-    .
-\end{align}
-
-% DONT: Keep ?
-% \begin{example}
-%     We explain why \eqref{math:l1estimate} is optimal. 
-%     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
-%     that satisfy $u_{\epsilon}(0)=0$, $u_{\epsilon}({\epsilon}) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
-%     Obviously, $\| u_{\epsilon} \|_{L^{1}(\Omega)} = 2 - {\epsilon}$ and $\| u'_{\epsilon} \|_{L^{1}(\Omega)} = 2{\epsilon} \frac{2}{2{\epsilon}} = 2$,
-%     and $\Omega$ has diameter $2$. 
-%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
-%     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
-%     Since norms are convex, it follows that $u_{\epsilon}$ is the potential with minimal $L^1$ norm. 
-% \end{example}
-
-\begin{remark}
-    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
-    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
-    Let us compare $C_{{\rm CW},p}$ for the Poincar\'e inequality
-    with $C_{{\rm EFNT},p}$ for the Poincar\'e--Friedrichs inequality. 
-    In the case $2 \leq p$, 
-    \begin{align*}
-        2^{1-\frac 2 p}
-        C_{{\rm EFNT},p}
-        =
-        \frac{ 2^{1-\frac 2 p} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq 
-        4^{-\frac 1 p}
-        \leq
-        C_{{\rm CW},p} 
-        .
-    \end{align*}
-    In the case $2 \geq p$, 
-    \begin{align*}
-        2^{\frac 2 p - 1}
-        C_{{\rm EFNT},p}
-        =
-        \frac{ 2^{\frac 2 p - 1} }{2}
-        \frac{ \sin(\pi/p) }{ \pi/p }
-        \frac{ 1 }{ \sqrt[p]{p-1} }
-        \leq
-        \frac{ 2^{\frac 2 p-1} }{2}
-        &
-        =
-        2^{\frac 2 p - 2}
-        \\&
-        =
-        4^{\frac 1 p - 1}
-        \leq
-        C_{{\rm CW},p} 
-%         % 
-%         .
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
-%         =
-%         4^{\frac 1 p}
-%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
-%         \leq 
-%         \frac{1}{2}
-        .
-    \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
-    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua Wheeden upper bound is not optimal!
-    % DONE: Theorem 1.2 in Chua Wheeden 
-% DONT: Keep ?
-%     In the limit as $p$ goes to $1$, the factor $C_{{\rm EFNT},p}$ converges to $1/2$,
-%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
-%         \leq 
-%         \frac{1}{2}
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{1}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,1}(\Omega)
-%         .
-%     \end{align*}
-%     In the limit as $p$ goes to infinity, the factor $C_{{\rm EFNT},p}$ converges to $1/2$, 
-%     which implies the Poincar\'e inequality 
-%     \begin{align*}
-%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
-%         \leq 
-%         \diam(\Omega)
-%         \| \nabla u \|_{L^{\infty}(\Omega)}
-%         ,
-%         \quad
-%         \forall 
-%         u \in W^{1,\infty}(\Omega)
-%         %
-%     \end{align*}
-%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
-%     % DONT: review this entire result 
-\end{remark}
-
-% \notice{MWL: I have removed a few lines to shorten the discussion. We should discuss later how to set up this section and what results to present to keep a good flow.}
-
-\begin{remark}
-    The above Poincar\'e and Poincar\'e--Friedrichs constants are optimal for the class of convex domains, 
-    but individual convex domains may allow for better constants.
-    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for discussions;
-    for example, triangles allow the reduction of the constant by 20\%.
-\end{remark}
-
-\section{Basic notions of triangulations}\label{section:triangulations}
-
-We gather here basic notions and definitions concerning simplicial meshes.
-
-% \subsection{A triangulation or a simplicial complex}
-
-A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$.
-We call these points the \emph{vertices} of the simplex $T$.
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
-If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
-
-A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
-(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
-\begin{align*}
-    \underlying{\calT} := \bigcup_{ T \in \calT } T
-    .
-\end{align*}
-We call any set triangulable if it is the underlying set of some triangulation. 
-\\
-
-\begin{comment}
-\begin{remark}
-    Our main interest in this manuscript are finite triangulations of compact sets. 
-    There is another reason why we insist on the triangulation being finite: 
-    if we do not require our simplicial complexes to be finite,
-    then a reasonable definition of simplicial complex would need additional topological conditions. 
-    % 
-    For example, if we modify our definition of simplicial complex to be infinite, 
-    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
-    %
-    A more interesting such example is this:
-    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
-    that underlies an ``infinite $0$-dimensional simplicial complex''.
-    If we place $\calC$ on the x-axis of a 2D coordinate system 
-    and connect each member of $\calC$ to $(0,1) \in \bbR^{2}$ via a straight line segment, 
-    then the resulting set is still compact, even path-connected,  
-    but has an ``infinite $1$-dimensional triangulation''.
-    % 
-    However, none of these infinite families are infinite simplicial complexes in the sense of geometric topology~\cite{lee2011topological}. 
-\end{remark}
-\end{comment}
-
-Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$,
-and $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
-We write $\Vertices(T) := \subsimplex_{0}(T)$ for the set of vertices of $T$.
-% 
-Whenever $\calT$ is a simplicial complex, 
-the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
-% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively.
-In practice, we not always distinguish between points and singleton simplices.
-% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
-    Our use of the term \textit{face} as is common in classical geometry and the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
-}
-In practice, we do not always distinguish between points and singleton simplices. 
-% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
-% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}
-
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
-which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
-We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
-Formally,
-\begin{gather*}
-    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
-    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
-    \qquad 
-    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
-\end{gather*}
-We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
-A crucial structural observation is the following.
-
-\begin{lemma}
- Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
- such that 
- \begin{align*}
-    \patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(S''),
-    \qquad 
-    \Vertices(S) \cup \Vertices(S') = \Vertices(S'').
- \end{align*}
-\end{lemma}
-\begin{proof}
- Let $T \in \calT$ be $n$-dimensional.
- We have $T \in \patch_{\calT}(S )$ if and only if all vertices of $S $ are vertices of $T$.
- We have $T \in \patch_{\calT}(S')$ if and only if all vertices of $S'$ are vertices of $T$.
- Consequently, $T \in \patch_{\calT}(S) \cap \patch_{\calT}(S')$ if and only if $T \in \patch_{\calT}(S'')$,
- where $S'' \in \calT$ is the convex closure of $S$ and $S'$.
-\end{proof}
-
-We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
-We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
-We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
-Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
-A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
-and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
-
-\subsection{Shape measures and related quantities}
-
-We introduce several quantities that measure the regularity of a triangulation. 
-% We quantify the quality of a triangulation via so-called \emph{shape measures}. 
-These have in common that they can be computed from purely local information.
-
-We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
-where the height of a vertex is defined as the distance to the affine span of its opposing face.
-For the purpose of the usual scaling arguments, the \emph{$n$-dimensional reference simplex} $\Delta^n \subseteq \bbR^n$ is the convex closure of the origin and the $n$ canonical unit vectors.
-
-Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{aspect shape measure} $\aspectratio(T)$,
-and 
-the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
-by 
-\begin{align}\label{math:shapemeasure}
-    \aspectratio(T)
-    := 
-    \frac{ \diam(T) }{ \height(T) }
-    ,
-    \qquad 
-    \algebraicshapemeasure(T)
-    := 
-    \sup_{ \varphi : \Delta^n \rightarrow T } 
-    % \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
-    \matnorm{\Jacobian \varphi} \matnorm{ \Jacobian \varphi^{-1} }
-    ,
-\end{align}
-where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
-When $\calT$ is an $n$-dimensional simplicial complex, we naturally define 
-\begin{align}\label{math:shapemeasure:triangulation}
-    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
-    ,
-    \quad 
-    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
-    .
-\end{align}
-We call these the aspect and algebraic shape measure, respectively, of the triangulation.
-
-\begin{remark}
-    The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is instance of a so-called \emph{shape measure}.
-    For example, the reference triangle has aspect shape measure $1$ and the reference tetrahedron has aspect shape measure $\sqrt{3/2}$. 
-    Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
-    \cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here.
-    \cite[Definition~11.2]{ern2021finite}). 
-\end{remark}
-
-We gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
-
-\begin{lemma}\label{lemma:measurerelationships}
-    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
-    \begin{gather*} % First pair 
-        \matnorm{ \Jacobian \varphi } 
-        \leq 
-        \Ceins{n} \cdot \diam(T),
-        \qquad 
-        \matnorm{ \Jacobian \varphi^{-1} } 
-        \leq 
-        \Czwei{n} \cdot \aspectratio(T) \height(T)^{-1}
-        ,
-        \\
-        \frac{1}{\sqrt{2n}} \aspectratio(T) \leq \algebraicshapemeasure(T) \leq n \aspectratio(T).
-    \end{gather*}
-    Here, $\Ceins{n} = \Czwei{n} = \sqrt n$. 
-\end{lemma}
-\begin{proof}
-    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine transformation. 
-    We abbreviate $M := \Jacobian\phi$ for its Jacobian. 
-    We begin with observing that the largest $\ell^{2}$-norm of any column of $M$,
-    which here denote by $c_{\max}(M)$, 
-    equals the maximum of the quotient $\| M x \|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
-    We also know that the diameter of $T$ is the length of its longest edge. 
-    Our first pair of inequalities follows via standard comparisons of Euclidean norms:
-    \begin{align*}
-        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ M } \leq \sqrt{n} \cdot c_{\max}(M) \leq \sqrt{n} \cdot \diam(T).
-    \end{align*}
-    The columns of the matrix $M^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
-    except for the vertex $\varphi(0) \in T$. It immediately follows that 
-    \begin{align*}
-        \matnorm{ M^{-1} } \leq \sqrt{n} c_{\max}(M^{-1}) \leq \sqrt{n} \cdot \height(T)^{-1}
-        .
-    \end{align*}
-    The smallest height in the reference simplex $\Delta^{n}$ is $\height_{\Delta} = 1/\sqrt{n}$, 
-    whence $\height(T) \geq \matnorm{M^{-1}}^{-1} / \sqrt{n}$. This yields our second pair of inequalities. 
-    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)^{-1}$.
-    All relevant results follow.
-\end{proof}
-
-We will need the maximal ratio of volumes between face-neighboring $n$-simplices, written $\volumeratio(\calT)$,
-and the ratio of the diameters of any intersecting simplices, written $\diameterratio(\calT)$. Formally, 
-\begin{align}\label{math:volumeratio}
-    \volumeratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
-    \frac{ \vol(T) }{ \vol(T') }
-    ,
-\end{align}
-\begin{align}\label{math:diameterratio}
-    \diameterratio(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
-    \frac{ \diam(T) }{ \diam(T') }
-    .
-\end{align}
-Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
-that preserves $F$. We then define 
-\begin{align}\label{math:reflectionmeasure}
-    \reflectionestimate(\calT) 
-    := 
-    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
-    \matnorm{ \Jacobian \Xi_{T,T'} }
-\end{align}
-to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
-This indicator quantifies how much reflection across the shared face distorts the geometry.
-
-\begin{lemma}\label{lemma:volumecomparison}
-    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
-    \begin{align*}
-        \diam(T_1)
-        \leq 
-        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
-        % \diam(F)
-        % = 
-        \aspectratio(T_1)
-        \diam(F)
-        ,
-        \qquad 
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
-        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
-        % \cdot 
-        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
-        % = 
-        \aspectratio(T_1) \aspectratio(T_2)
-        .
-    \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-        .
-    \end{align*}
-%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
-\end{lemma}
-
-\begin{proof}
-    The diameter of $F$ is at least as large as the height $h_S$ of some other vertex of $F$ in $T_{1}$. 
-    Now, 
-    \begin{align*}
-%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
-        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
-    \end{align*}
-    The first estimate follows. 
-    As for the second estimate,
-    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
-    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
-    \begin{align*}
-        \frac{ \vol(T_1) }{ \vol(T_2) }
-        = 
-        \frac{ h_1 }{ h_2 }
-        \leq
-        \frac{ \diam(T_1) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
-        \leq
-        \aspectratio(T_{1}) \aspectratio(T_{2})
-        .
-    \end{align*}
-    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    Writing $h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \left( 1 + \aspectratio(T_2) \right)
-        \aspectratio(T_1)
-        .
-    \end{align*}
-    The desired estimates are shown.
-\begin{comment}
-    \mwl{Tighter estimate via geometry}
-    Matrix inverse lemma:
-    \begin{align*}
-        A ( A + (z_2-z_1) e_1^t )^{-1}
-        =
-        \Id
-        - 
-        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        =
-        \Id
-        - 
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        .
-    \end{align*}
-    Putting in a multiple of $\alpha z_1$, we find 
-    \begin{align*}
-        \alpha z_1
-        -
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) 
-        .
-    \end{align*}
-
-    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
-    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
-    We can write 
-    \begin{align*}
-        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
-    \end{align*}
-    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
-    \begin{align*}
-        A = 
-        \begin{pmatrix}
-            b_1/a_1 & 0 & 0
-            \\
-            (b_2-a_2)/a_1 & 1 & 0
-            \\
-            b_3/a_1 & 0 & 1
-        \end{pmatrix}
-        =:
-        \begin{pmatrix}
-            c_1 & 0 & 0
-            \\
-            c_2 & 1 & 0
-            \\
-            c_3 & 0 & 1
-        \end{pmatrix}
-    \end{align*}
-    Its singular values are $1$ and 
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        +
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        =
-        \frac{1}{2}
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        +
-        \frac{1}{2}
-        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
-        \leq 
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        .
-    \end{align*}
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            -
-            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        -
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        .
-    \end{align*}
-
-    \begin{align*}
-        \sigma_{\max}
-        &= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            }
-        +
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        ,
-        \\
-        \sigma_{\min}
-        &=
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        -
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        .
-    \end{align*}
-    It follows that 
-    \begin{align*}
-        \det \Jacobian\Xi
-        &=
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-        +
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-        \\
-        \frac{1}{2} + \frac{1}{2} 
-        .
-    \end{align*}
-    Matrix determinant lemma:
-    \begin{align*}
-        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
-        =
-        \left( e_{n} A^{-1} z_2 \right) \det(A)
-        =
-        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
-        .
-    \end{align*}
-\end{comment}
-\end{proof}
-
-\begin{remark}
-    While we will utilize $\diameterratio(\calT)$ at numerous places throughout the manuscript, 
-    $\volumeratio(\calT)$ and $\reflectionestimate(\calT)$ will only be used throughout Section~\ref{section:gradient},
-    the following section.  
-    Lemma~\ref{lemma:volumecomparison} obviously shows that $\volumeratio(\calT)$ of~\eqref{math:volumeratio} is controlled by the shape measure.
-In a face-connected triangulation where we have an upper bound for the number of simplices sharing a vertex,
-    this Lemma also allows, at least in principle, control of $\diameterratio(\calT)$ of~\eqref{math:diameterratio}.
-\end{remark}
-
-\section{Poincar\'e--Friedrichs inequalities over triangulated domains}\label{section:gradient}
-
-In this section, we develop stepwise computable estimates for Poincar\'e--Friedrichs constants of triangulated domains. 
-The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-We perform a discrete analog of this procedure over triangulated domains: 
-having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.
-We always construct a gradient potential over the new simplex and fix the constant of integration using the value already known on the connecting face, thereby constructing a scalar potential over larger and larger subdomains.
-This basic idea has appeared in various forms before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-
-% We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point.
-We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells.
-We construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-% 
-% {\color{blue}In this section, we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains.
-\cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-% Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure.
-We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}.
-% We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
-% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
-% }
-
-% While the underlying idea remains the same, they differ in the way the intermediate potentials are extended.
-% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result. 
-% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
-
-We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
-% This is inspired by the classical proof of what is often called the Friedrichs inequality.
-
-\begin{lemma}\label{lemma:mixedbconsimplex}
-    Let $T$ be an $n$-simplex with a face $F$ and $p \in [1,\infty]$. 
-    If $u \in W^{1,p}(T)$ with $\trace_{F} u = 0$, then 
-    \begin{align*}
-        \| u \|_{L^{p}(T)}
-        &
-        \leq 
-        C_{\PF,T,F,p} \| \nabla u \|_{L^{p}(T)}
-        ,
-    \end{align*}
-    where $C_{\PF,T,F,p} = p^{-\frac 1 p} \diam(T)$ for $p < \infty$ and $C_{\PF,T,F,\infty} = \diam(T)$. 
-%     \begin{align*}
-%         C_{\PF,T,F,p}
-%         &\leq 
-%         C_{\PF,T,p} + \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right)^{\frac 1 p},  
-%         \\
-%         C_{\PF,T,F,p}
-%         &\leq
-%         \frac{1}{\sqrt[p]{p}}
-%         \diam(T)
-%         .
-%     \end{align*}
-\end{lemma}
-\begin{proof}
-\begin{comment}
-    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
-    \begin{gather*}
-        \| w \|_{L^{p}(T)}
-        \leq 
-        C_{\PF,T,p} 
-        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
-        .
-    \end{gather*}
-    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
-    We use that 
-    \begin{gather*}
-        \| \gamma \|_{L^{p}(T)}
-        =
-        \gamma \vol(T)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \cdot 
-        \gamma 
-        \vol(F)^\frac{1}{p}
-        =
-        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
-        \| \gamma \|_{L^{p}(F)}
-        .
-    \end{gather*}
-    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
-    \begin{align*}
-        \| \gamma \|_{L^{p}(F)}^{p}
-        &
-        \leq 
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p}
-        +
-        p
-        \cdot 
-        \diam(T)
-        \frac{ \vol(F) }{ \vol(T) }
-        \| w \|_{L^{p}(T)}^{p-1}
-        \| \nabla w \|_{L^{p}(T)}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot C_{\PF,T,p}^{p-1} \right) 
-        \diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        \\&
-        \leq 
-        \left( \frac{ \vol(F) }{ \vol(T) } \right)
-        \left( C_{\PF,T,p}^{p} + p \cdot \diam(T) C_{\PF,T,p}^{p-1} \right) 
-        %\diam(T)^{p}
-        \| \nabla w \|_{L^{p}(T)}^{p}
-        .
-    \end{align*}
-    Recall that $u = w - \gamma$. The first inequality follows. 
-\end{comment}
-    % The second inequality follows from Rademacher's theorem when $p = \infty$.
-    Since the inequality follows from Rademacher's theorem in the limit case $p = \infty$,
-    we assume $1 \leq p < \infty$. 
-    Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
-    We extend $u$ by zero to a function over the entire $\bbR^{n}$.
-    Without loss of generality, 
-    the segment from the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
-    and the minimal first coordinate among all the points of $F$ equals $0$. 
-    We write $\bfg$ for the trivial extension of $\nabla u$ over the entire $\bbR^{n}$.
-    %With the fundamental theorem of calculus and H\"older's inequality: 
-    Using the fundamental theorem of calculus and H\"older's inequality, 
-    \begin{align*}
-        \int_{T} |u(x)|^{p} \diff x \;dx
-        &\leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
-        \\&
-        \leq
-        \int_{\bbR^{n-1}} \int_{0}^{\diam(T)} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
-        \\&
-        \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
-        \\&
-        \leq
-        \int_{0}^{\diam(T)} x_{1}^{p-1} \;dx_1 
-        \cdot 
-        \int_{T} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
-        \leq
-        \frac{\diam(T)^{p}}{p} \int_{T} \left| \nabla u( x ) \right|^{p} \,dx
-        %
-%         \leq
-%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
-%         \\&
-%         \leq
-%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
-%         \leq 
-%         D^{p} 
-%         \int_{\Omega} |\nabla u|^{p} \,dx
-        .
-    \end{align*}
-    If $u \in W^{1,p}(T)$ has vanishing trace along $F$ but is not necessarily smooth, 
-    then we conclude $\|u\|_{L^{p}(T)} \leq \diam(T) p^{-\frac 1 p} \|\nabla u\|_{L^{p}(T)}$ 
-    from approximation via members of $C^{\infty}(T)$ whose support is disjoint from $F$. 
-    We very briefly verify that density argument: 
-    There exists an affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ from the reference simplex onto $T$ that maps the convex closure of the $n$ unit vectors onto the face $F$.
-    We let $\hat u := u \circ \varphi$.
-    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\Delta^{n}$.
-    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
-    Then $\tilde u \in W^{1,p}_{0}(\hat U)$, and $\tilde u$ is the limit of a sequence $u_{m} \in C^{\infty}_{c}(\hat U)$.
-    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$ within the Banach space $W^{1,p}(T)$
-    and has the desired support property. 
-\end{proof}
-
-The next auxiliary result establishes Poincar\'e--Friedrichs constants over face patches within simplicial triangulations. 
-We emphasize that face patches are not necessarily convex, but we can still extend the results on convex domains from Section~\ref{subsection: PX_convex}.
-The following result is reasonably sharp when the two simplices have similar volumes and diameters.
-
-\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
-    Let $\calT$ be a triangulation.
-    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
-    Write $U := T_1 \cup T_2$. 
-    If $p \in [1,\infty]$ and $u \in W^{1,p}(\Omega)$,
-    then 
-    \begin{align*}
-        \min\limits_{ c \in \bbR }
-        \| u - c \|_{L^{p}(U)}
-        &
-%         \leq 
-%         2 \Ceins{n} C_{{\rm EFNT},p}
-%         \max\left( 
-%             \frac{ \vol(T_1) }{ \vol(T_2) }
-%             ,
-%             \frac{ \vol(T_2) }{ \vol(T_1) }
-%         \right)^{\frac 1 p}
-%         \\&\qquad\qquad 
-%         \cdot 
-%         \max\left( \diam(T_1), \diam(T_2) \right)
-%         \| \nabla u \|_{L^{p}(U)}
-%         \\&
-        \leq 
-        C_{{\PF},T_1 \cup T_2,p}
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    Here, $C_{{\PF},T_1 \cup T_2,p} = 2 \Ceins{n} C_{{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
-\end{lemma}
-% \begin{remark}
-%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
-% \end{remark}
-\begin{proof}
-    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
-    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
-    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
-    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
-    be affine transformations 
-    that map the origin to $v_0$, that map each unit vector $e_{i}$ to $v_{i}$ for $i = 1, \dots, n-1$,
-    and that satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
-    Write $\hat U := \Delta_1 \cup \Delta_2$.
-    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
-
-    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
-    We observe 
-%     \begin{align*}
-%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-%         &=
-%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-%         +
-%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-%         ,
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
-%         &\leq 
-%         |\det(\Jacobian \varphi_1^{-1})|
-%         \cdot \matnorm{ \Jacobian \varphi_1 }^{p}
-%         \cdot 
-%         \| \nabla u \|_{L^{p}(T_1)}^{p}
-%         ,
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
-%         &\leq 
-%         |\det(\Jacobian \varphi_2^{-1})|
-%         \cdot \matnorm{ \Jacobian \varphi_2 }^{p}
-%         \cdot 
-%         \| \nabla u \|_{L^{p}(T_2)}^{p}
-%         \\
-%         \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
-%         &\leq 
-%         \max\left( 
-%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \matnorm{ \Jacobian \varphi_1 }^{p}
-%             ,
-%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \matnorm{ \Jacobian \varphi_2 }^{p}
-%         \right)
-%         \| \nabla u \|_{L^{p}(U)}^{p}
-%         .
-%     \end{align*}
-%     Hence 
-    \begin{align*}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}
-        &\leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_1 }
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_2 }
-        \right)
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    Notice that $\hat U$ has diameter $2$ and is (crucially) convex. 
-    Thus, due to Poincar\'e--Friedrichs inequality~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
-    \begin{align*}
-        \| \hat w \|_{L^{p}(\hat U)}
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \| \nabla \hat u \|_{L^{p}(\hat U)}
-        .
-    \end{align*}
-    Next, setting $w := \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(U)}
-        \leq 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \| \hat w \|_{L^{p}(\hat U)}
-        .
-    \end{align*}
-    For both $i = 1,2$, we now recall the well-known equation $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$, 
-    % which we have already employed in~\eqref{equation:Hong_Pan}, 
-    and the estimate $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$, which is given in Lemma~\ref{lemma:measurerelationships}. We obtain the desired result.
-\begin{comment}
-    % DONE: that abbreviation is to close to the Jacobian / total derivative 
-    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
-    \begin{align*}
-        \| w \|_{L^{p}(U)}
-        &\leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \\&\qquad 
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} 
-            ,
-            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} 
-        \right)
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)|
-        \right)^{\frac 1 p}
-        \\&\qquad 
-        \min\left( 
-            |\det(\Jacobian \varphi_1)|
-            ,
-            |\det(\Jacobian \varphi_2)| 
-        \right)^{-\frac 1 p} 
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            \frac{ |\det(\Jacobian \varphi_1)| }{ |\det(\Jacobian \varphi_2)| }
-            ,
-            \frac{ |\det(\Jacobian \varphi_2)| }{ |\det(\Jacobian \varphi_1)| }
-        \right)^{\frac 1 p}
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        \\&
-        \leq 
-        2 C_{{\rm EFNT},p}
-        \max\left( 
-            \frac{ \vol(T_1) }{ \vol(T_2) }
-            ,
-            \frac{ \vol(T_2) }{ \vol(T_1) }
-        \right)^{\frac 1 p}
-        D
-        \| \nabla u \|_{L^{p}(U)}
-        .
-    \end{align*}
-    This gives the desired result. 
-\end{comment}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The main result of this section constructs a potential and gives an upper bound for the Poincar\'e--Friedrichs constant.  
-It follows the same underlying principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.
-This procedure serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-
-Two different variations of the underlying idea are analyzed, yielding slightly different estimates. 
-On the one hand, we can extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that new simplex, subject to partial boundary conditions.
-On the other hand, we can instead cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found.
-Since these can only differ by constants at their overlaps, we assemble a global scalar potential piece by piece as we adjust the local constants of integration.
-Both estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.
-
-% We present an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex}, where we compute an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary.
-% We emphasize that this construction of potentials and bounding of Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.
-
-\begin{comment}
-For the remainder of this section, the following combinatorial notion of triangulations is used. 
-Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
-a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
-where for each index $1 \leq m \leq M$ we have a fixed index $0 \leq \iota(m) \leq m-1$ 
-such that $T_{m}$ and $T_{\iota(m)}$ are face-neighboring.
-We call $T_{\iota(m)}$ the \emph{precursor} of $T_{m}$ within the spanning tree. 
-The reader is referred to Figure~\ref{figure:spanningtree} for an illustration. 
-\end{comment}
-
-\begin{figure}[t]
-\begin{center}
-\begin{tikzpicture}[rotate=-60]
-    \coordinate (A) at (0,0);
-    \coordinate (B) at (2,0);
-    \coordinate (C) at (1,1.5);
-    \coordinate (D) at (3,1.5); 
-    \coordinate (E) at (3,3); 
-    \coordinate (F) at (4,0.25); 
-    \coordinate (X) at (1,-1.5);
-    \coordinate (Y) at (3,-1.5); 
-    \coordinate (T) at (5,2);
-
-    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
-    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
-    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
-    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
-    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
-    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);
-    \coordinate (CentroidDFT) at ($(D)!0.3333!(F)!0.3333!(T)$);
-    \coordinate (CentroidDET) at ($(D)!0.3333!(E)!0.3333!(T)$);
-
-    \draw[fill=gray!10] (A) -- (B) -- (C) -- cycle; 
-    \draw[fill=gray!10] (B) -- (C) -- (D) -- cycle; 
-    \draw[fill=gray!10] (C) -- (D) -- (E) -- cycle; 
-    \draw[fill=gray!10] (B) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (A) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (X) -- cycle; 
-    \draw[fill=gray!10] (Y) -- (B) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (F) -- cycle; 
-    \draw[fill=gray!10] (T) -- (D) -- (E) -- cycle;
-
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
-    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
-    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET); 
-\end{tikzpicture}
-\end{center}
-\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
-\label{figure:spanningtree}
-\end{figure}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
-    Let $\calT$ be a face-connected $n$-dimensional finite triangulation. 
-    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
-    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
-    Then for any $u \in W^{1,p}(\Omega)$ 
-    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
-    and satisfying the following estimates:
-    there exists an $n$-simplex $T_0 \in \calT$ with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    and whenever $T_0, T_1, \dots, T_M$ is a face path,
-    then for all $1 \leq m \leq$ we the following recursive estimates:
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{m-1})} 
-        + 
-%         C_{\PF,T_{m},F_{m},p} 
-%         \left( 
-%             \| \nabla u \|_{L^{p}(T_{m})} 
-%             + 
-%             \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-%             \| \nabla u \|_{L^{p}(T_{m-1})}
-%         \right)
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \reflectionestimate(\calT)^{q} \right)^{\frac 1 q}
-        C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
-        ,
-        \\
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{{m-1}})}
-        +
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Makoto_{F_m},p} 
-        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
-        . 
-    \end{align*}
-    Here, for any $1 \leq m \leq M$, let $F_m = T_m \cap T_{m-1}$.
-\end{theorem}
-
-\begin{proof}
-    Let $u \in W^{1,p}(\Omega)$. 
-    We start with the Poincar\'e--Friedrichs inequality on the first simplex $T_{0}$. 
-    There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    In particular, $c_{0} := w_0 - u$ is a constant function. 
-    We then define 
-    \begin{align*}
-        w := u + c_0
-        .
-    \end{align*} 
-    Clearly, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
-    By construction $w_{|T_{0}} = w_0$. 
-    We verify that $w$ satisfies the two desired recursive estimates.
-    Suppose that $T_0, T_1, \dots, T_M$ is a face path in $\calT$
-    and that $1 \leq m \leq M$.
-    Recall that we write $F_m := T_m \cap T_{m-1}$, which is a face of dimension $n-1$ shared by the $n$-simplices $T_{m}$ and $T_{m-1}$,
-    and that we write $\Makoto_{F_m} := T_m \cup T_{m-1}$.
-
-    We proceed with the first recursive estimate. 
-    We define $w'_{m} := w_{|T_{m-1}} \circ \Xi \in W^{1,p}(T_{m})$,
-    where $\Xi : T_{m} \rightarrow T_{m-1}$ is the unique affine diffeomorphism that leaves $F_{m}$ invariant. 
-    By construction, $w'_{m} \in W^{1,p}(T_{m})$ with 
-    \begin{align*}
-        \trace_{F_{m}} w'_{m} = \trace_{F_{m}} w_{|T_{m-1}}
-        .
-    \end{align*}
-    We now define $w''_{m} \in W^{1,p}(T_{m})$ via 
-    \begin{align}\label{equation:w''}
-        w''_{m} 
-        := 
-%         u_{|T_{m}} - w'_{m} + c_0 
-%         = 
-        w_{|T_{m}} - w'_{m} = u_{|T_{m}} - u_{|T_{m-1}} \circ \Xi.
-    \end{align}
-    We crucially note that $w''_{m}$ is trace-free along $F_{m}$ since
-    \begin{align*}
-        \trace_{F_{m}} w''_{m} 
-        = 
-        \trace_{F_{m}} \left( 
-            w_{|T_{m}} - w'_{m} 
-        \right) 
-        =
-        \trace_{F_{m}} w_{|T_{m}}
-        -
-        \trace_{F_{m}} w_{|T_{m-1}}
-        =
-        \trace_{F_{m}} u_{|T_{m}}
-        -
-        \trace_{F_{m}} u_{|T_{m-1}}
-%         = 
-%         \trace_{F_{m}} \left( 
-%             u_{|T_{m}} - w'_{m} + c_0 
-%         \right) 
-%         = 
-%         \trace_{F_{m}} \left( 
-%             u_{|T_{m-1}} - w_{|T_{m-1}} + c_0 
-%         \right) 
-        = 0.
-    \end{align*}
-    We apply Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''}, which gives 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla w \|_{L^{p}(T_{m})} 
-            + 
-            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        \leq 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{m})} 
-            + 
-            \| \nabla w'_{m} \|_{L^{p}(T_{m})} 
-        \right) 
-        .
-    \end{align*}
-    Using Lemma~\ref{lemma:volumecomparison} as well as Definitions~\eqref{math:volumeratio} and~\eqref{math:reflectionmeasure}, we find 
-    \begin{align*}
-        \| \nabla w'_{m} \|_{L^{p}(T_{m})}
-        &
-        \leq 
-        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
-        \matnorm{ \Jacobian \Xi }
-        \| \nabla w \|_{L^{p}(T_{m-1})}
-        \\&
-        \leq 
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        \| \nabla w \|_{L^{p}(T_{m-1})}
-        \\&
-        =
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        \| \nabla u \|_{L^{p}(T_{m-1})}
-        .
-    \end{align*}
-    % The second expression in~\eqref{equation:w''} shows $w_{|T_{m}} = w''_{m} + w'_{m}$. We finally find 
-    Since $w_{|T_{m}} = w''_{m} + w'_{m}$, we finally find 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{m-1})} 
-        + 
-        C_{\PF,T_{m},F_{m},p} 
-        \left( 
-            \| \nabla u \|_{L^{p}(T_{m})} 
-            + 
-            \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-        \| \nabla u \|_{L^{p}(T_{m-1})}
-        \right). 
-    \end{align*}
-    We now use H\"older's inequality. 
-    Therefrom, the first recursive estimate follows.
-
-    Now we discuss the second recursive estimate. 
-    Suppose again that $1 \leq m \leq M$. 
-    We use the Poincar\'e--Friedrichs inequality over $\Makoto_{F_{m}}$,
-    as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
-    to find $w_{F_m} \in W^{1,p}(\Makoto_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Makoto_{F_m}$ and 
-    \begin{align}\label{math:wFm_inequality}
-        \| w_{F_m} \|_{L^{p}(\Makoto_{F_m})} \leq C_{{\PF},\Makoto_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Makoto_{F_m})}.
-    \end{align}
-%     \cye{Since $\nabla (w_{|\Makoto_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Makoto_{F_m}})$, 
-    We can define the constant
-    \begin{align*}
-    c_{m} := w_{|\Makoto_{F_m}} - w_{F_{m}}.
-    \end{align*}
-    We now observe that 
-    \begin{gather*}
-        \| w \|_{L^{p}(T_m)}
-        \leq 
-        \| w_{F_m} \|_{L^{p}(T_m)}
-        +
-        \| c_{m} \|_{L^{p}(T_m)},
-        \\
-        \| c_{m} \|_{L^{p}(T_m)}
-        = 
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| c_{m} \|_{L^{p}(T_{{m-1}})},
-        \\ 
-        \| c_{m} \|_{L^{p}(T_{{m-1}})}
-        \leq 
-        \| w \|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
-        .
-    \end{gather*}
-    In combination, 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        &
-        \leq 
-        \| w_{F_m} \|_{L^{p}(T_m)}
-        \\&\qquad 
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{m-1}})}
-        .
-    \end{align*}
-    We sum the two integrals of $w_{F_m}$. 
-    % 
-    % 1/q = 1 - 1/p = (p-1)/p 
-    When $1 < p < \infty$, recalling the complementary exponent $q = p/(p-1) \in (1,\infty)$, 
-    we use H\"older's inequality to verify 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \left( 
-            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
-            +
-            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
-        \right)^{\frac 1 p}
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{m-1}})}
-        \\&\leq 
-        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
-        \| w_{F_{m}} \|_{L^{p}(\Makoto_{F_m})} 
-        +
-        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
-        \| w \|_{L^{p}(T_{{m-1}})}
-        .
-    \end{align*}
-    Note that in the limit cases $p=1$ and $p=\infty$ we get, respectively, 
-    \begin{align*}
-        \| w\|_{L^{1}(T_m)}
-        &\leq 
-        \max\left(
-            1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
-        \right)
-        \| w_{F_m} \|_{L^{1}(\Makoto_{F_m})}
-        +
-        \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
-        \| w \|_{L^{1}(T_{{m-1}})},
-        \\
-        \| w \|_{L^{\infty}(T_m)}
-        &\leq 
-        2
-        \| w_{F_m} \|_{L^{\infty}(\Makoto_{F_m})}
-        +
-        \| w \|_{L^{\infty}(T_{{m-1}})}
-        .
-    \end{align*}
-    The local inequality~\eqref{math:wFm_inequality} now provides the second recursive estimate. 
-    The proof is complete.
-\end{proof}
-
-\begin{corollary}
-    Under the assumptions of Theorem~\ref{theorem:poincarefriedrichsestimate:grad},
-    whenever $T_0, T_1, \dots, T_m$ is a face-path of $n$-simplices in $\calT$,
-    we have 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \sum_{\ell=1}^{m} 
-        \volumeratio^{\frac{m-\ell}{p}}
-        \min\left( 
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Makoto_{F_\ell},p} 
-        ,
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \reflectionestimate(\calT)^{q} \right)^{\frac 1 q}
-        C_{\PF,T_{\ell},F_{\ell},p} 
-        \right)
-        \| \nabla u \|_{L^{p}(\Makoto_{F_\ell})}
-        \\&
-        \qquad 
-        \qquad 
-        +
-        \volumeratio^{\frac m p}
-        C_{{\PF},T_{0},p}
-        \| \nabla u \|_{L^{p}(T_{0})}
-        .
-    \end{align*}
-\end{corollary}
-\begin{proof}
-    This follows by repeated application of the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-\end{proof}
-
-\begin{remark}
-    The Poincar\'e--Friedrichs constants obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimate the best one as the number of $n$-simplices in the triangulation $\calT$ increases.
-    Hence, we conceive their target application to be local patches (stars), in particular non-convex boundary stars. 
-    The latter occur inevitably at reentrant corners.
-Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches $\{ \Makoto_m \}$ of $n$-simplices with an appropriate notion of connectivity.
-    The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Makoto_m \}$. 
-    This may allow for partitions of $\overline \Omega$ with significantly fewer elements, which enables a largely improved estimate of the best Poincar\'e--Friedrichs constant. 
-\end{remark}
-
-% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
-% Lemma 5.5
-
-\section{Review of vector calculus and exterior calculus}\label{section:calculus}
-
-% We discuss the Sobolev spaces of vector calculus and exterior calculus 
-% with particular emphasis on their transformation behavior. 
-% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-% TODO: Fuse these two paragraphs
-
-We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
-We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
-
-\subsection{Vector calculus}
-
-% \cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ 
-% \begin{gather*}
-    % W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    % .
-% \end{gather*}}
-Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
-We recall $L^{p}(\Omega)$, the space of scalar-valued $p$-integrable functions defined on $\Omega$
-and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
-In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
-The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
-\begin{gather*}
-    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
-    .
-\end{gather*}
-The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
-and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
-\begin{gather*}
-    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
-    \\ 
-    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
-\end{gather*}
-We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-We introduce the gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
-$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
-$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
-$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
-We also introduce 
-$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
-for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
-\begin{subequations}\label{eq_definition_piola}
-\begin{align*}
-    \phi^{\grad}(v) &= v \circ \phi, \\
-    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
-    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
-    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
-\end{align*}
-\end{subequations}
-Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
-These transformations are invertible. 
-Bounds on the Lebesgue norms will follow from a more general result below. 
-We use the commutativity relations 
-\begin{subequations}\label{eq_piola_commute}
-\begin{align}
-    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
-    \\
-    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
-    \\
-    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
-\end{align}
-\end{subequations}
-where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
-We summarize this as a commuting diagram:
-\begin{align*}
-    \begin{CD}
-        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
-        \\
-        @VV{\phi^{\grad}}V 
-        @VV{\phi^{\curl}}V 
-        @VV{\phi^{\divergence}}V 
-        @VV{\phi^{\rm b}}V 
-        \\
-        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
-    \end{CD}
-\end{align*}
-
-\begin{remark}
-    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
-    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
-    This definition is in accordance with the notion of pullback, which we will review shortly. 
-    One advantage of that definition is that it also makes sense whenever the transformation is not bijective. 
-    However, the literature also knows the Piola transform in the direction of the original mapping. 
-\end{remark}
-
-\subsection{Exterior calculus}
-
-%\cye{We now move to} exterior calculus. 
-%We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}.
-
-We now move the discussion to exterior calculus, beginning with exterior algebra.
-Let $V$ be a real vector space. 
-Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
-Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
-if 
-\begin{gather*} 
-    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
-    = 
-    \text{sign}(\pi) 
-    u( v_1, v_2, \ldots, v_k ) 
-\end{gather*}
-for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
-By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
-Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
-
-The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra
-(see~Chapter 14 in \cite{lee2012smooth}). 
-Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
-their wedge product \( u_1 \wedge u_2 \) is a member of $\Alt^{k+l}(V)$
-defined by the formula 
-\begin{gather*}
-    (u_1 \wedge u_2)(v_1, v_2, \ldots, v_{k+l}) 
-    = 
-    \frac{1}{k! l!} 
-    % \sum_{ \pi \in S_{k+l}} 
-    \sum_{ \pi } 
-    \signum(\pi) 
-    u_1( v_{\pi(  1)}, \ldots, v_{\pi(k  )} ) 
-    u_2( v_{\pi(k+1)}, \ldots, v_{\pi(k+l)} ),
-\end{gather*}
-for any \( v_1, v_2, \ldots, v_{k+l} \in V \).
-Here, the sum runs over all permutations $\pi$ of the index set \(\{ 1, 2, \ldots, k+l \}\).
-% Here, \( S_{k+l} \) denotes the symmetric group on \( k+l \) elements, and \( \signum(\pi) \) is the sign of the permutation \( \pi \). 
-The exterior product is bilinear and associative, and satisfies 
-\begin{align*}
-    u_1 \wedge u_2 = (-1)^{kl} u_2 \wedge u_1,
-    \quad 
-    \forall u_1 \in \Alt^{k}(V),
-    \quad 
-    \forall u_2 \in \Alt^{l}(V).
-\end{align*}
-The interior product is in some sense dual to the exterior product. Given $v \in V$ and $u \in \Alt^{k}(V)$, we define the interior product $v \lrcorner u \in \Alt^{k-1}(V)$ via 
-\begin{align*}
-    (v \lrcorner u)( v_1, v_2, \ldots, v_{k-1} ) = u( v, v_1, v_2, \ldots, v_{k-1} ),
-    \quad 
-    \forall v_1, v_2, \ldots, v_{k-1} \in V.
-\end{align*}
-
-We employ the exterior algebra only in the special case $V = \bbR^{n}$ of alternating forms over the $n$-dimensional Euclidean space. 
-Here, it is customary to identify $\Alt^{k}(V)$ with the space of antisymmetric tensors in $k$ indices. 
-Moreover, this particular setting comes with a canonical basis. 
-We let \(\{\cartanx^1, \cartanx^2, \ldots, \cartanx^{n}\}\) be the basis dual to the canonical unit vectors.
-This is a canonical basis of $\Alt^{1}(\bbR^{n})$. 
-To define a canonical basis of $\Alt^{k}(\bbR^{n})$, 
-we first introduce $\Sigma(k,n)$, the set of strictly ascending mappings $\sigma : \{1,\dots,k\} \rightarrow \{1,\dots,n\}$, where $k, n \in \bbZ$, 
-and introduce the basic $k$-alternators 
-\begin{align*}
-    \cartanx^{\sigma} := \cartanx^{\sigma(1)} \wedge \dots \wedge \cartanx^{\sigma(k)}, 
-    \quad 
-    \forall \sigma \in \Sigma(k,n). 
-\end{align*}
-These define a basis of $\Alt^{k}(\bbR^{n})$.
-Note that 
-$\dim \Alt^{k}(\bbR^{n}) = \binom{n}{k}$. 
-In particular, $\Alt^{k}(\bbR^{n})$ is the zero vector space whenever $k > n$.
-% The dimension of the space of \(k\)-forms, denoted \(\bigwedge^{k} V\), is given by the binomial coefficient \(\binom{n}{k}\).
-
-We notice that the canonical scalar product on $\bbR^{n}$ gives rise to a scalar product on $\Alt^{1}(\bbR^{n})$,
-which induces a scalar product on $\Alt^{k}(\bbR^{n})$.
-The basic $k$-alternators are an orthonormal basis of $\Alt^{k}(\bbR^{n})$ with respect to that inner product.
-
-\subsection{Smooth differential forms}
-
-We let $\Omega \subseteq \bbR^{n}$ be any bounded open set.
-We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
-which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
-The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
-to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
-Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather*}
-    \omega 
-    = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma}
-    = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \omega_{\sigma} \, 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather*}
-where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
-The exterior derivative \( \cartan\omega \) is defined by
-\begin{gather*}
-    \cartan\omega = 
-    \sum_{ \sigma \in \Sigma(k,n) } 
-    \sum_{j=1}^{n} 
-    \frac{\partial \omega_{\sigma}}{\partial x^j} 
-    \, \cartanx^j \wedge 
-    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
-\end{gather*}
-The exterior derivative is linear and nilpotent, which means 
-\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
-Moreover, it satisfies the Leibniz rule:
-\begin{gather*} 
-    \cartan(\omega \wedge \eta) 
-    = 
-    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
-    \qquad \forall \omega \in C^{\infty}\Alt^{k}(\Omega), 
-    \qquad \forall \eta \in C^{\infty}\Alt^{l}(\Omega).
-\end{gather*}
-The integral of a differential $n$-form is uniquely defined via 
-\begin{gather*}
-    \int_{\Omega} \omega \cartanx^{1} \wedge \dots \wedge \cartanx^{n} = \int_{\Omega} \omega(x) \;dx
-    . 
-\end{gather*}
-
-\begin{remark}
-    In three dimensions, 
-    the calculus of differential forms is in correspondence with classical vector calculus. 
-    This is expressed formally as the commuting diagram 
-    \begin{gather*}
-    \begin{CD}
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) @>{\cartan}>> C^\infty\Alt^3(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        @VV{\varpi^{3}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\, ,}
-    \end{gather*}
-    where $\varpi^{0}$ and $\varpi^{3}$ are the identity mappings and where 
-    \begin{align*}
-     \varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} + u_3 \cartanx^{3} \right) 
-     &= 
-     \left( u_1, u_2, u_3 \right), 
-     \\
-     \varpi^{2}\left( u_{12} \cartanx^{1} \wedge \cartanx^{2} + u_{13} \cartanx^{1} \wedge \cartanx^{3} + u_{23} \cartanx^{2} \wedge \cartanx^{3} \right) 
-     &= 
-     \left( u_{23}, - u_{13}, u_{12} \right).   
-    \end{align*}
-    In two dimensions, 
-    the calculus of differential forms can be translated into 2D vector calculus in two different ways. 
-    To the authors' best knowledge, neither convention is dominant over the other in the literature.
-    We summarize the situation in the following commuting diagram: 
-    \begin{gather*} 
-    \begin{CD}
-        C^\infty(\Omega) @>{\curl}>> C^\infty(\Omega)^{2} @>{\divergence}>> C^\infty(\Omega)
-        \\
-        @AA{\varkappa^{0}}A 
-        @AA{\varkappa^{1}}A 
-        @AA{\varkappa^{2}}A 
-        \\
-        C^\infty\Alt^0(\Omega) @>{\cartan}>> C^\infty\Alt^1(\Omega) @>{\cartan}>> C^\infty\Alt^2(\Omega) 
-        \\
-        @VV{\varpi^{0}}V 
-        @VV{\varpi^{1}}V 
-        @VV{\varpi^{2}}V 
-        \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
-    \end{CD}
-    \cye{\,.}
-    \end{gather*}
-    Here, $\varpi^{1}\left( u_1 \cartanx^{1} + u_2 \cartanx^{2} \right) = \left( u_1, u_2 \right)$ is the lower middle isomorphism.
-We introduce the rotation operator $J(x,y) = (y,-x)$ and define $\varkappa = J \varpi$ and $\rot = \divergence J$.
-    The other vertical arrows are the identity. 
-    The utility of exterior calculus is that the operators of vector calculus can be translated into a common framework that does not depend on the dimension.
-\end{remark}
-
-\subsection{Sobolev spaces of differential forms}
-
-Let us now turn our attention to Sobolev spaces of differential forms. 
-Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
-We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
-such that its pointwise norm is $p$-integrable. 
-The exterior derivative is defined in the sense of distributions and we introduce 
-\begin{gather*}
-    W^{p}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
-    .
-\end{gather*}
-We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
-\begin{align*}
-    \int_{\Omega} \cartan v \wedge u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{\Omega} v \wedge f 
-    .
-\end{align*}
-% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
-% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
-Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
-Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
-We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
-whose support lies in the open ball $B_r(x)$
-we have the integration by parts formula
-\begin{align*}
-    \int_{B_r(x)} \cartan v \wedge \tilde u
-    &=
-    (-1)^{k(n-k)+1}
-    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
-    .
-\end{align*}
-If that condition is satisfied, we also write 
-\begin{align*}
-    \trace_{\Gamma} u = 0
-    .
-\end{align*}
-Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
-Lastly, we introduce the closed subspaces 
-\begin{gather*}
-    W^{p}_{0}\Alt^{k}(\Omega) 
-    := 
-    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
-    .
-\end{gather*}
-% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
-This is a closed subspace.
-We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
-Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.
-We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega) = L^{p}(\Omega)$.
-We use the abbreviation $W^{1,p}_{0}(\Omega) := W^{p}\Lambda^{0}(\Omega)$.
-
-\subsection{Transformations by bi-Lipschitz mappings}
-
-We are interested in transformations of Sobolev tensor fields from one domain onto another. 
-Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
-The pullback of $u \in L^{p}\Alt^{k}(\Omega')$ along $\phi$ is the (measurable) differential form 
-\begin{align} \label{equation:pullback}
-    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
-    := 
-    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
-\end{align}
-for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. 
-One can show that $\phi^{\ast}u \in L^{p}\Alt^{k}(\Omega)$ and the following estimates.
-
-\begin{proposition}\label{proposition:pullbackestimate}
-    Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
-    Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega')$. 
-    Then $\phi^{\ast} u \in L^{p}\Lambda^{k}(\Omega)$ and 
-    \begin{align}
-        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-        &\leq 
-        \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
-        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-        .
-    \end{align}
-    If $\phi$ is affine and $\sigma_1 \geq \sigma_2 \geq \dots \geq \sigma_n$ are the singular values of $\Jacobian\phi$, then 
-    \begin{align}
-        \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
-        &\leq 
-        \sigma_1 \sigma_2 \cdots \sigma_k \cdot 
-        \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
-        \| u \|_{L^{p}\Lambda^{k}(\Omega')}
-        .
-    \end{align}
-	Moreover, if $u \in W^{p}\Lambda^{k}(\Omega')$, then $\phi^{\ast} u \in W^{p}\Lambda^{k}(\Omega)$ and $\cartan \phi^{\ast} u = \phi^{\ast} \cartan u$. 
-\end{proposition}
-\begin{proof}
-	See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}).
-\end{proof}
-
-\subsection{Some approximation properties}
-
-We review a few approximation properties. 
-Let $\mollifier$ be a non-negative scalar function whose integral equals one and whose support lies in the unit ball around the origin.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\begin{lemma}
-%     Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $u : \Omega \rightarrow \bbR$ be locally integrable.  
-%     Then $\mollifier_{\epsilon} \star u \rightarrow u$ almost everywhere. 
-%     If $u \in L^{p}(\Omega)$ for some $1 \leq p < \infty$, then $u_{\epsilon} \rightarrow u$ in $L^{p}(\Omega)$.
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    If $u \in L^{p}(\Omega)$, then the convolution $\mollifier_{\eps} \star u \rightarrow u$ in $L^{p}(\Omega)$ as $\epsilon \rightarrow 0$.
-\end{lemma}
-
-% \begin{lemma} % TODO: possibly useful
-%     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
-% \end{lemma}
-
-\begin{lemma}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
-    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
-    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$. 
-    %\mwl{If $\Omega$ is convex and $u \in W^{p}\Lambda^{n}(\Omega)$ has average zero, 
-    %then $u$ is the limit in $W^{p}\Lambda^{k}(\Omega)$ of smooth compactly supported $n$-forms with average zero.}
-\end{lemma}
-\begin{proof}
-    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
-    By the dominated convergence theorem and because $u$ has a weak derivative,
-    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
-    \begin{align*}
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
-        &= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
-        \\&= 
-        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
-        = 
-        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
-        .
-    \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
-
-    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
-    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
-    Define $\varphi_t(x) = tx$ for $t > 1$. 
-    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega) \subseteq W^{p}_{0}\Lambda^{k}(\Omega)$ 
-    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
-    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
-    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
-    The desired result follows. 
-    % 
-    % Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently small radius. The proof is complete. 
-\end{proof}
-
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
-
-% We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-% We already know the optimal constants for the gradient operator over convex domains,
-% and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
-% We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$. 
-% % 
-% We bound the norms of regularized potential operators for the exterior derivative over convex domains.
-% We solve this for two special cases:
-
-We now develop bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
-Here, we consider two special cases: 
-either the $L^{p}$ de~Rham complex without boundary conditions, or the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
-We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
-% 
-In comparison to their extensive work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
-However, our goal is explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
-
-%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.
-
-% \todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
-
-\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}
-
-We begin with introducing the Costabel-McIntosh kernel.
-For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
-\begin{equation}\label{math:mainkernel}
-  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
-  ,
-\end{equation}
-where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
-Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
-we then define the integral operators
-\begin{align*}
-  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
-  \\
-  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
-\end{align*}
-We call $\Poinc_{\mia}$ the \emph{Poincar\'e operator} and $\Bogov_{\mia}$ the \emph{Bogovski\u{\i} operator}.
-
-We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually converge. 
-In order to analyze the properties of the potential operators,
-we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
-Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
-    \\
-    &= 
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
-    .
-\end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
-\begin{align*}
-    \calG_{\mia}(x,y) 
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
-    \\
-    &= 
-    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
-\end{align*}
-We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
-
-\subsection{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}
-
-We begin with the Poincar\'e operator. 
-Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
-We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
-\begin{align*}
-    \left| \Poinc_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-%     \\&\leq 
-%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
-    .
-\end{align*}
-We recall the radial integrals 
-\begin{align*}
-    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    &
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
-    \\&
-    =
-    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
-    =
-    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    ,
-\end{align*}
-where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
-We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
-    .
-\end{align*}
-% Here, $C_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$. 
-Here we introduce the numerical constant 
-\begin{gather}\label{equation:A_Poinc}
-    C_{\Poinc}(n,\mia) := \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) },
-\end{gather}
-which depends only on $n$ and $\mia$ and which is bounded by $2^{n-\mia}$.
-
-In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) C_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
-Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n C_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-%
-
-\subsection{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}
-
-We analyze the Bogovski\u{\i} potential operator by similar means. 
-Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
-First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$.
-Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
-Consider now the case $x \in \overline\Omega$. 
-We estimate $\Bogov_{\mia} u(x)$ pointwise by 
-\begin{align*}
-    \left| \Bogov_{\mia} u(x) \right|
-    &=
-    \left| 
-        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
-    \right| 
-    \\&\leq 
-    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
-    \\&\leq 
-    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
-    .
-\end{align*}
-Using once more the radial integrals discussed above, we compute 
-% We recall the radial integrals 
-% \begin{align*}
-%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
-%     =
-%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
-%     =
-%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-%     .
-% \end{align*}
-% We compute 
-\begin{align*}
-    &
-    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
-    \\&
-    =
-    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
-    %\\&
-    =
-    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
-    .
-\end{align*}
-% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
-Here we introduce the numerical constant 
-\begin{gather}\label{equation:A_Bogov}
-    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
-\end{gather}
-which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
-In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
-Young's convolution inequality now implies: 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-    &
-    \leq 
-    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    \\&
-    \leq 
-    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-    \diam(\Omega)
-    \| u \|_{L^{p}(\Omega)}
-    .
-\end{align*}
-We have assumed so far that $u$ is essentially bounded.
-Since that space is dense in the Lebesgue spaces, a density argument yields: 
-for any $1 \leq p \leq \infty$ we have a bounded linear operator 
-\begin{gather*}
-    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
-\end{gather*}
-% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
-Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
-that is, the reconstructed potential has support contained within $\overline\Omega$. 
-\\
-
-\subsection{Interaction of potential operators with the exterior derivative}
-
-More properties of these operators become apparent after a change of variables. 
-We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
-leading to 
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    &= 
-    \vol(\Omega)^{-1}
-    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
-    \chi_{\Omega}\left(x+t(y-x)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    \vol(\Omega)^{-1}
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
-leading to 
-\begin{align*}
-    \Bogov_{\mia} u(x) 
-    &= 
-    \vol(\Omega)^{-1}
-    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
-    \chi_{\Omega}\left(y+t(x-y)\right) 
-    (x-y)\lrcorner u(y) \,dt\,dy 
-    \\
-    &=
-    - 
-    \vol(\Omega)^{-1}
-    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
-    .
-\end{align*}
-% We first discuss the support properties of this operator. 
-% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
-% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
-% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
-% 
-Given $a \in \Omega$, we introduce the potential operators 
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &:= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    ,
-    \\
-    \Bogov_{\mia,a} u(x) 
-    &:= 
-    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
-    .
-\end{align*}
-By definition,
-\begin{align*}
-    \Poinc_{\mia} u(x) 
-    =
-    \vol(\Omega)^{-1}
-    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
-    \quad 
-    \Bogov_{\mia} u(x) 
-    =
-    \vol(\Omega)^{-1}
-    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
-    .
-\end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
-% 
-The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
-We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.
-
-We make use of the following notation~\cite{licht2022basis}:
-for any mapping $\sigma \in \Sigma(k,n)$, we let $[\sigma] := \{ \sigma(1), \dots, \sigma(k) \}$ be its image. 
-When $p \in [\sigma]$, then the member of $\Sigma(k-1,n)$ with image $[\sigma] \setminus \{p\}$ is written $\sigma-p$.
-
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$.
-We rewrite the Poincar\'e potential,
-\begin{align*}
-    \Poinc_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt 
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{0}^{1} 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    ,
-\end{align*}
-and compute its exterior derivative:
-\begin{align*}
-    \cartan \Poinc_{\mia,a} u(x) 
-    &= 
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We write the exterior derivative of $u$ as 
-\begin{align}\label{math:exteriorderivative_of_u_in_hodgediscussion}
-    \cartan u(x)
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    =
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    ,
-\end{align}
-and apply the Poincar\'e potential operator to this result, which gives 
-\begin{align*}
-    \Poinc_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}
-    \,\cartanx^{\sigma} 
-    \\&\qquad 
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    %\sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
-Taking into account cancellations, this gives the identity 
-\begingroup\allowdisplaybreaks
-\begin{align*}
-    &
-    \cartan \Poinc_{\mia,a} u(x)
-    +
-    \Poinc_{\mia+1,a} \cartan u(x)
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&\qquad
-    +
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
-    \int_{0}^{1} 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    \\&
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{0}^{1} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    =
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \left( u_{\sigma}(x) - 0^k u_{\sigma}(a) \right) \,\cartanx^{\sigma}
-    .
-\end{align*}
-\endgroup
-We conclude that, 
-\begin{align*}
-    u(x) &= \Poinc_{1,a} \cartan u(x) - u(a), \qquad k = 0,
-    \\
-    u(x) &= \cartan \Poinc_{\mia,a} u(x) + \Poinc_{\mia+1,a} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align*}
-In summary, after taking the average over $a \in \Omega$:
-\begin{align}\label{math:hodgedecomposition:poinc}
-    u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \,da, \qquad k = 0,
-    \\
-    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align}
-
-Even though the discussion for the Bogovski\u{\i} operator is large analogous, some modifications are needed. 
-Suppose that $u \in C^{\infty}\Alt^{\mia}(\bbR^n)$ with $\supp u \subseteq \overline\Omega$.
-We rewrite the Bogovski\u{\i} potential,
-\begin{align*}
-    \minus 
-    \Bogov_{\mia,a} u(x) 
-    &= 
-    (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt 
-    \\&
-    = 
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&
-    = 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}
-    \int_{1}^\infty 
-    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} \,(x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-We want to take its exterior derivative, but we can generally only do that in the distributional sense. 
-Away from the pivot point $a$, the form $\Bogov_{\mia,a} u(x)$ is differentiable in $x$, 
-and so we compute its exterior derivative over $\Omega \setminus \{a\}$:
-\begin{align*}
-    \minus 
-    \cartan \Bogov_{\mia,a} u(x) 
-    &= 
-    \sum_{\sigma \in \Sigma(\mia,n)} 
-    \int_{1}^\infty 
-    \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    \\&\qquad
-    + 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    \int_{1}^\infty 
-    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    .
-\end{align*}
-The derivative of $\Bogov_{\mia,a} u$ over the whole domain, which is what we need, can only be taken in the sense of distributions. 
-Let $\phi \in C^{\infty}\Alt^{n-\mia}(\Omega)$ be smooth and compactly supported over $\Omega$. 
-We let $\epsilon > 0$ and calculate 
-\begin{align*}
-    (-1)^{n(k-1)} % deg B u x deg phi = (k-1)(n-k) = nk-n-kk + k = nk - n = n(k-1)
-    \int_{ \Omega \setminus B_\epsilon(a) }
-    \Bogov_{\mia,a} u(x) \wedge \cartan \phi 
-    =
-    \int_{ S_\epsilon(a) }
-    \trace_{S_\epsilon(a)}{ \Bogov_{\mia,a} u(x) \wedge \phi } 
-    -
-    \int_{ \Omega \setminus B_\epsilon(a) }
-    \cartan \Bogov_{\mia,a} u(x) \wedge \phi 
-    ,
-\end{align*}
-where $\trace_{S_{\epsilon}(a)}$ denotes the trace onto the sphere $S_{\epsilon}(a)$. 
-In the limit as $\epsilon$ goes to zero, the two integrals over $\Omega \setminus B_\epsilon(a)$ in the above equation converge to the integrals of the respective integrands over $\Omega \setminus \{a\}$.
-To understand the derivative of $\Bogov_{\mia,a} u$ over the domain $\Omega$, 
-we study the remaining surface integral. 
-We apply several substitutions:
-\begin{align*}
-    &\int_{ S_\epsilon(a) }
-    \trace_{S_\epsilon(a)}{ \Bogov_{\mia,a} u(x) \wedge \phi(x) } 
-    \\&\quad 
-    =
-    % x = a + e n = a - e a + e a + e n = e ( a + n ) + (1-e) a
-    \epsilon^{n-1}
-    \int_{ S_1(a) }
-    \trace_{S_1(a)}{ \Bogov_{\mia,a} u( \epsilon x + a - \epsilon a ) \wedge \phi( \epsilon x + a - \epsilon a ) }
-    \\&\quad 
-    =
-    \epsilon^{n-1}
-    \int_{ S_1(a) }
-    \int_{1}^\infty 
-    \trace_{S_1(a)}{ 
-        \epsilon t^{\mia-1} (x-a)\lrcorner u\left( a + \epsilon t( x - a )\right) 
-        \wedge \phi( \epsilon (x-a) + a ) 
-    }
-    \,dt 
-    \\&\quad 
-    =
-    % s = \epsilon t 
-    \epsilon^{n-1}
-    \int_{ S_1(a) }
-    \int_{\epsilon}^\infty 
-    \trace_{S_1(a)}{ 
-        \epsilon^{-\mia+1} s^{\mia-1} (x-a)\lrcorner u\left( a + s( x - a )\right) 
-        \wedge \phi( \epsilon (x-a) + a ) 
-    }
-    \,ds 
-    \\&\quad 
-    =
-    % s = \epsilon t 
-    \epsilon^{n-\mia}
-    \int_{ S_1(a) }
-    \int_{\epsilon}^\infty 
-    \trace_{S_1(a)}{ 
-        s^{\mia-1} (x-a)\lrcorner u\left( a + s( x - a )\right) 
-        \wedge \phi( \epsilon (x-a) + a ) 
-    }
-    \,ds 
-    .
-\end{align*}
-We make a case distinction.
-When $k<n$, then the double integral itself is bounded uniformly in $\epsilon > 0$ and so the last expression vanishes as $\epsilon$ goes to zero.
-When instead $k=n$, then the last expression equals
-\begin{align*}
-	& 
-    \int_{ S_1(a) }
-    \int_{\epsilon}^\infty 
-    \trace_{S_1(a)}{ 
-        s^{n-1} (x-a)\lrcorner u\left( a + s( x - a )\right) 
-        \wedge \phi( \epsilon (x-a) + a ) 
-    }
-    \,ds 
-    \\&\quad 
-	=
-	\int_{\bbR^{n} \setminus B_{\epsilon}(0)}
-	    u\left( y \right) 
-        \wedge \phi\left( \epsilon \frac{y-a}{\|y-a\|} + a \right) 
-    \,dy 
-    .
-\end{align*}
-The limit of this is $\phi(a) \int_\Omega u(x)$ as $\epsilon$ goes to zero. 
-To complete the discussion, we write the exterior derivative of $u$ as in \eqref{math:exteriorderivative_of_u_in_hodgediscussion}, 
-% \begin{align*}
-    % \cartan u(x)
-    % =
-    % \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    % \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} \,dt 
-    % =
-    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }}
-    % \frac{ \partial u }{\partial x_{j}}(x) \,\cartanx^{j} \wedge \cartanx^{\sigma} 
-    % ,
-% \end{align*}
-and apply the Bogovski\u{\i} potential operator to this result, which gives 
-\begin{align*}
-    \minus 
-    \Bogov_{\mia+1,a} \cartan u(x)
-    &=
-    (x-a)\lrcorner 
-    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    \,\cartanx^{j} \wedge \cartanx^{\sigma}
-    \\&
-    = 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    \\&\qquad 
-    - 
-    \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    %\sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}
-    (-1)^{i-1}
-    \int_{1}^\infty t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    (x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    .
-\end{align*}
-We add the (distributional) exterior derivative of the potential and the potential of the exterior derivative.
-In a manner that fully analogous to the discussion of the averaged Poincar\'e operator save for the modification when $k=n$, 
-we come to the conclusion that 
-% Taking into account cancellations, this gives the identity 
-% \begingroup\allowdisplaybreaks
-% \begin{align*}
-    % &
-    % - 
-    % \cartan \Bogov_{\mia,a} u(x)
-    % -
-    % \Bogov_{\mia+1,a} \cartan u(x)
-    % \\&
-    % =
-    % \sum_{\sigma \in \Sigma(\mia,n)} 
-    % \int_{1}^{\infty} 
-    % \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    % \\&\qquad
-    % + 
-    % \sum_{\substack{ \sigma \in \Sigma(\mia,n), \; 1 \leq i \leq \mia \\ 1 \leq j \leq n, \; j \notin [\sigma-\sigma(i)] }}
-    % \int_{1}^{\infty} 
-    % t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 
-    % \\&\qquad
-    % +
-    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    % \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
-    % \\&\qquad
-    % - 
-    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] \\ 1 \leq i \leq k }}
-    % (-1)^{i-1}
-    % \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 
-    % \,(x-a)_{\sigma(i)} \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)}
-    % \\&
-    % =
-    % \sum_{\sigma \in \Sigma(\mia,n)} 
-    % \int_{1}^{\infty} 
-    % \mia t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma} \,dt 
-    % \\&\qquad
-    % +
-    % \sum_{\substack{ \sigma \in \Sigma(\mia,n) \\ 1 \leq j \leq n, \; j \notin [\sigma] }} 
-    % \int_{1}^{\infty} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,(x-a)_{j} \,dt \,\cartanx^{\sigma}
-    % \\&\qquad
-    % + 
-    % \sum_{\substack{ \sigma \in \Sigma(\mia,n), \\ 1 \leq i \leq \mia }}
-    % \int_{1}^{\infty} 
-    % t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{\sigma(i)}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma(i)} \wedge \cartanx^{\sigma} \,dt 
-    % \\&
-    % =
-    % \sum_{\sigma \in \Sigma(\mia,n)} 
-    % \int_{1}^{\infty} \frac{\partial}{\partial t} \left( t^{\mia} u_{\sigma}\left(a+t(x-a)\right) \right) \,dt \,\cartanx^{\sigma}
-    % =
-    % -
-    % \sum_{\sigma \in \Sigma(\mia,n)} 
-    % u_{\sigma}(x) \cartanx^{\sigma}
-    % =
-    % -u(x)
-    % .
-% \end{align*}
-% \endgroup
-% We conclude that 
-\begin{align*}
-    u(x) &= \cartan \Bogov_{\mia,a} u(x) + \Bogov_{\mia+1,a} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
-    \\
-    u(x) &= \cartan \Bogov_{n,a} u(x) - \left( \int_{\Omega} u(a) \right) \delta_a, \qquad k = n.
-\end{align*}
-Here, $\delta_a$ denotes the Dirac delta at $a$. 
-In summary, after taking the average over $a \in \Omega$:
-\begin{align}\label{math:hodgedecomposition:bogov}
-    u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
-    \\
-    u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}, \qquad k = n.
-\end{align}
-
-\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}
-
-We are now state the main results of this section. 
-% We are in the position to establish the main results of this section.
-Recall that $\diam(\Omega) > 0$ is the diameter of $\Omega$ and that $B_{\diam(\Omega)}(0)$ is the $n$-dimensional ball centered at the origin.
-The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
-However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
-namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $C_{\Poinc}(n,\mia)$ and $C_{\Bogov}(n,\mia)$.
-
-\begin{theorem}\label{theorem:bogovpoinc}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set and let $1 \leq p \leq \infty$. 
-    We have bounded operators 
-    \begin{align*}
-        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
-        ,
-        \qquad 
-        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
-        .
-    \end{align*}
-    They satisfy the operator norm bounds 
-    \begin{align*}
-        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        ,
-        \\
-        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
-        &\leq 
-        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
-        \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
-    \begin{align}
-        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
-        \label{math:theorem:bogovpoinc:poincare:zero}
-        \\
-        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
-        \label{math:theorem:bogovpoinc:poincare:k}
-    \end{align}
-    In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
-
-    For any $u \in \bfW^{p}_{0}\Alt^{\mia}(\Omega)$ it holds that 
-    \begin{align}
-        u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
-        \label{math:theorem:bogovpoinc:bogov:k}
-        \\
-        u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}.
-        \label{math:theorem:bogovpoinc:bogov:n}
-    \end{align}
-    In particular, if $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
-
-    % If $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$ and $\cartan u = 0$, 
-    % then $\Poinc_{\mia} u \in W^{p}    \Alt^{\mia  }(\Omega)$ with $u = \cartan \Poinc_{\mia} u$.
-    % If $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $\cartan u = 0$ and $\int_\Omega u = 0$ in the case $k=n$, 
-    % then $\Bogov_{\mia} u \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $u = \cartan \Bogov_{\mia} u$.
-    % In particular, if $\cartan u = 0$, then $\cartan \Poinc_{\mia} u = u$.
-    % In particular, if $\cartan u = 0$, then $\cartan \Bogov_{\mia} u = u$.
-
-\end{theorem}
-
-% \todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
-Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
-
-\begin{proof}
-    Consider the case $1 \leq p < \infty$.
-    %
-    Because the domain is bounded, 
-    the subspaces $C^{\infty}_{c}\Alt^{\mia}(\Omega)$ are dense in $L^{p}\Alt^{\mia}(\Omega)$,
-    and so the stated operator norm bounds follow by an approximation argument. 
-    % 
-    Taking the limit on both sides of equation then implies the inequality with $p = \infty$
-    because the $L^{\infty}$ norm is the limit of the Lebesgue norms as $p$ goes to infinity.
-
-    Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$. 
-    We write $\zeta := \Poinc_{\mia  } u$. 
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        -
-        \int_{\Omega} v \wedge \Poinc_{\mia+1} \cartan u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia  } u 
-        .
-    \end{align*}
-    By definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
-    This shows \eqref{math:theorem:bogovpoinc:poincare:k}, and \eqref{math:theorem:bogovpoinc:poincare:zero} follows by an approximation argument.
-
-    Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$. 
-    We write $\ := \Bogov_{\mia} u$. 
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, 
-    which is the restriction of some member of $C^{\infty}\Alt^{n-\mia-1}(\bbR^{n})$, 
-    it holds that 
-    \begin{align*}
-        \int_{\Omega} v \wedge u_{i} 
-        &=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia  } u_{i}
-        \\&=
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        +
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge u 
-        -
-        \int_{\Omega} v \wedge \Bogov_{\mia+1} \cartan u
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia  } u 
-        .
-    \end{align*}
-    By definition, $\zeta \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Bogov_{\mia+1} \cartan u$.
-    This shows \eqref{math:theorem:bogovpoinc:bogov:k}, and \eqref{math:theorem:bogovpoinc:bogov:n} follows by an approximation argument.
-
-    Everything else is now apparent, and the proof is complete. 
-\begin{comment}
-    It suffices to discuss the case $1 \leq p < \infty$, because the domain is bounded 
-    and taking the limit will then imply the inequality with $p = \infty$. 
-    The potential operators are linear and satisfy the stated bounds over $C^{\infty}_{c}\Alt^{\mia}(\Omega)$,
-    which is a dense subspace of $L^{p}\Alt^{\mia}(\Omega)$.
-
-    \color{blue}
-    Let $u \in W^{p}_{ }\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$ and set $w = \Poinc_{\mia} \cartan u$.
-    There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}_{c}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} \cartan v \wedge \Poinc_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan \Poinc_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge \cartan u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge w
-        .
-    \end{align*}
-    By definition, $w \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    \color{black}
-
-    \color{blue}
-    Let $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$ and set $w = \Bogov_{\mia} \cartan u$.
-    There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
-    For any test form $v \in C^{\infty}\Alt^{n-\mia-1}(\Omega)$, we verify 
-    \begin{align*}
-        \int_{\Omega} \cartan v \wedge \Bogov_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan \Bogov_{\mia+1} \cartan u_{i}
-        =
-        \int_{\Omega} v \wedge \cartan u_{i}
-        .
-    \end{align*}
-    By the continuity of bounded linear functionals, we find 
-    \begin{align*}
-        \int_{\Omega} v \wedge \cartan u 
-        &=
-        (-1)^{\mia(n-\mia)+1}
-        \int_{\Omega} \cartan v \wedge w
-        .
-    \end{align*}
-    By definition, $w \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan w = u$.
-    \color{black}
-\end{comment}
-\end{proof}
-
-% \begin{remark}
-%     The operator norm bounds for the Poincar\'e operator are decreasing in the form degree,
-%     while they are increasing for the Bogovski\u{\i} operator.
-%     This echoes the Guerini--Savo theorem for the $L^{2}$ de~Rham complex over smoothly bounded convex domains~\cite{guerini2004eigenvalue}.
-% \end{remark}
-
-These constants are generally not optimal. 
-For example, when $p=2$ and when only the divergence is considered, 
-we have the following improved estimate.
-
-\begin{lemma}\label{lemma:PFfordivergence}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
-    % For each $u \in W^{1,2}_{0}(\Omega)$ there exists $w \in W^{1,p}_{0}(\Omega)$ with $\grad \bfw = \grad \bfu$ and 
-    % \begin{align*}
-        % \| w \|_{L^{2}(\Omega)} 
-        % \leq 
-        % \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
-        % .
-    % \end{align*}
-    For each $\bfu \in \bfW^{2}(\divergence,\Omega)$ there exists $\bfw \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfw = \divergence \bfu$ and 
-    \begin{align*}
-        \| \bfw \|_{L^{2}(\Omega)} 
-        \leq 
-        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This is a reduction to the Friedrichs inequality. 
-    The space $W^{1,2}_{0}(\Omega)$ is the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
-    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
-    The adjoint is the closed densely-defined linear operator $-\divergence : \bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
-    which has the same smallest singular value. 
-\end{proof}
-
-\begin{remark} \label{remark:reg_Poinc_Bog}
-    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % TODO: are these paragraphs in the introduction now?
-    The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for establishing Poincar\'e--Friedrichs constants over bounded convex domains. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-
-    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight, and thus they are bounded operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
-
-    \mwl{ 
-    Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Their operators are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight; this proves that the operators are bounded between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
-    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
-    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
-    This had not been established yet, to the best of our knowledge. 
-    }
-\end{remark}
-
-\section{Shellable triangulations of manifolds}\label{section:advancedtriangulations}
-
-We return to the theory of triangulations, as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulated domains and which are \emph{shellable}.
-Such simplicial complexes are constructed by successively adding simplices in a well-structured manner. 
-Local patches (stars) within triangulations of dimension two or three are examples of such shellable complexes. 
-The monographs by Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures} are our main references for this section. 
-We also refer to Lee's monograph~\cite{lee2011topological} for any further background on manifolds.
-
-\begin{figure}[h]
-% \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
-\centering
-\begin{tikzpicture}[scale=0.8]
-    % Coordinates of the main outer triangle
-    \coordinate (B0)  at (0,-1); % Bottom left
-    \coordinate (BL)  at (-3,0); % Bottom right
-    \coordinate (BR)  at (3,0); % Bottom right
-    \coordinate (CLL) at (-3,2); % Bottom left
-    \coordinate (CL)  at (-1,0.8); % Bottom right
-    \coordinate (CR)  at ( 1,0.8); % Bottom right
-    \coordinate (CRR) at ( 3,2); % Bottom right
-    \coordinate (Z)   at (0,3.5); % Top
-    \coordinate (ML) at  (-0.8,2.2);% ($(CL)!0.3!(Z)$);
-    \coordinate (MR) at  ( 0.8,2.2);% ($(CR)!0.6!(Z)$);
-    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
-    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
-    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
-    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
-    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
-    \draw[thick,fill=gray!25] (ML) -- (CL) -- (CLL) -- cycle;
-    \draw[thick,fill=gray!25] (MR) -- (CR) -- (CRR) -- cycle;
-    \draw[thick,fill=gray!25] (Z) -- (ML) -- (CLL) -- cycle;
-    \draw[thick,fill=gray!25] (Z) -- (MR) -- (CRR) -- cycle;
-    \draw[thick,fill=gray!25] (Z) -- (ML) -- (MR) -- cycle;
-\end{tikzpicture}
-\qquad
-\begin{tikzpicture}[scale=0.8]
-    % Coordinates of the main outer triangle
-    \coordinate (B0)  at (0,-1); % Bottom left
-    \coordinate (BL)  at (-3,0); % Bottom right
-    \coordinate (BR)  at (3,0); % Bottom right
-    \coordinate (CLL) at (-3,2); % Bottom left
-    \coordinate (CL)  at (-1,1); % Bottom right
-    \coordinate (CR)  at ( 1,1); % Bottom right
-    \coordinate (CRR) at ( 3,2); % Bottom right
-    \coordinate (Z)   at (0,3.5); % Top
-    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
-    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
-    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
-    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
-    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
-    \draw[thick,fill=gray!25] (Z) -- (CL) -- (CLL) -- cycle;
-    \draw[thick,fill=gray!25] (Z) -- (CR) -- (CRR) -- cycle;
-\end{tikzpicture}
-
-\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}
-\label{figure:not_manifold_triang}
-\end{figure}
-
-\subsection{Triangulations of manifolds}\label{subsection:manifoldtriangulation}
-
-Our discussion requires some notions and results concerning triangulated manifolds. 
-We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
-We recall that this means that for every $x \in \underlying{\calT}$
-% there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
-there exists an open neighborhood $U(x) \subseteq \underlying{\calT}$ and an embedding $\phi : U(x) \rightarrow \bbR^{n}$
-such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the open unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| < 1 \}$
-or onto the half-ball $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
-In the former case, $x$ is called an \emph{interior point}, and in the latter case $x$ is called a \emph{boundary point}. 
-Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional. 
-An example of a manifold triangulation and an example which is not a manifold triangulation are given in Figure~\ref{figure:not_manifold_triang}.
-
-The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball, and we sometimes call this an \textit{$n$-disk} triangulation.
-An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
-
-We know that any manifold $\calM$ has got a topological boundary $\partial\calM$, possibly empty. 
-If $\calM$ is $n$-dimensional, then the $\partial\calM$ is a topological manifold without boundary of dimension $n-1$. 
-We gather a few helpful observations on how these notions relate to triangulations.
-While the reader might deem them obvious, we nevertheless include proofs.
-
-\begin{lemma}\label{lemma:boundarysimplices}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying set is a manifold $\calM$. 
-    Then the simplices contained in the boundary constitute a triangulation of the boundary.
-    Moreover, if $F \in \calT$ is a face (i.e, $F$ has dimension $n-1$), then 
-    \begin{itemize}
-        \item $F$ is not contained in the boundary if and only if it is contained in exactly two $n$-simplices.
-        \item $F$ is contained in the boundary if and only if it is contained in exactly one $n$-simplex.
-        % \item $\calT$ is non-branching, that is, every $F \in \calT$ of dimension $n-1$ is contained in at most two $n$-simplices of $\calT$. 
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    We prove these statements in several steps.
-    \begin{enumerate}
-    \item 
-    Let $\mathring \calM := \calM \setminus \partial \calM$ denote the interior of the manifold. 
-    We will use the following fact:\footnote{To see this, one easily constructs a continuous deformation of $\calM$ into itself to move any chosen point on $S$ to any other chosen point on $S$.} if $S \in \calT$ has an inner point that lies on $\partial \calM$, then all inner points of $S$ are on $\partial \calM$.
-    Since the boundary $\partial \calM$ is closed, every $S \in \calT$ is either a subset of the boundary or all its inner points lie in the interior $\mathring \calM$ of the manifold.
-
-    \item 
-    We recall an auxiliary result.
-    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    As a consequence of the Jordan--Brouwer separation theorem~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, 
-    we know that $Y \setminus X$ has got two connected components.
-
-    % \item 
-    % We prove an auxiliary result. 
-    % Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
-    % The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
-    % Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the north pole without loss of generality, and a stereographic projection, 
-    % we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
-    % As a consequence of the Jordan--Brouwer separation theorem~\cite[Theorem IV.5.23]{mayer1989algebraische}~\cite[Corollary IV.5.24]{mayer1989algebraische}~\cite[Corollary VIII.6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
-    % and thus $Y \setminus X$ has got two connected components.
-
-    \item
-    Let now $F \in \subsimplex_{n-1}(T)$ be a face and let $z_F \in F$ be its barycenter. 
-    Since $\calT$ is finite, we let $\mathring B_F$ be an open neighborhood around $z_F$ 
-    homeomorphic to an $n$-dimensional ball 
-    so small that its closure $\overline{B_F}$ only intersects those $n$-simplices of $\calT$ that already contain $z_F$ and no faces other than $F$.
-    Suppose there are distinct $n$-simplices $T_1, T_2, \dots, T_K$ that contain $z_F$. 
-    The intersection of any two of them is $F$, but their interiors are disjoint because otherwise they would coincide.
-
-    If $z_F$ is an interior point of $\calM$, 
-    then it follows by our assumptions that $\mathring B_F$ is homeomorphic to an open $n$-ball and $\partial \mathring B_F$ is homeomorphic to a sphere of dimension $n-1$. 
-    Consider $X = F \cap \partial \mathring B_F$.
-    If $n=1$, then $X$ is empty and $\partial \mathring B_F$ has $K$ distinct connected components. 
-    If $n > 1$, then $X$ is homeomorphic to a sphere of dimension $n-2$
-    and again $\partial \mathring B_F \setminus X$ has $K$ distinct connected components. 
-    But by the auxiliary result above, $K = 2$. 
-    We conclude that $F$ is contained in two $n$-simplices of $\calT$.
-
-    Consider the case that $z_F$ lies on the boundary of $\calM$ and suppose that $F$ is contained in $K$ distinct $n$-simplices of $\calT$.
-    By adding at least one dimension, we can double\footnote{The reader is referred to Lee's textbook~\cite{lee2012smooth} for more background and the technicalities.} the manifold $\calM$ along the boundary and obtain the doubled manifold $\calM'$.
-    Similarly, we can construct a doubling of the triangulation $\calT'$ such that $F$ is contained in exactly $2K$ distinct $n$-simplices of $\calT'$. 
-    We know that $\calM'$ is a manifold without boundary, and hence $F$ is an interior simplex of $\calT'$.
-    This implies $K=1$.
-    So any boundary face can only be contained in one single $n$-simplex.
-
-    \item
-    Clearly, the simplices of $\calT$ contained in the boundary constitute a simplicial complex. 
-    Every $x \in \calM$ is an inner point of some simplex $S \in \calT$. 
-    If $x \in \partial \calM$ is a boundary point, then $S$ must be a boundary simplex, 
-    so the boundary simplices triangulate all of $\partial \calM$.
-    \end{enumerate}
-    All desired results are thus proven. 
-\end{proof}
-
-Suppose that $\calT$ is an $n$-dimensional simplicial complex that triangulates a manifold. 
-Those simplices of the manifold triangulation that are subsets of the boundary of the underlying manifold are called \emph{boundary simplices}. 
-% The simplices that lie in the boundary of the underlying set are called \emph{boundary simplices}.
-All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
-We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
-% We see that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
-% Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
-% Definitions imply that the boundary complex is a manifold triangulation of dimension $n-1$.
-% The boundary simplices of a manifold triangulation of dimension $n$ constitute a manifold triangulation themselves, of dimension $n-1$, which triangulate the boundary of the underlying space.
-
-We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. This topics is surprisingly non-trivial and 
-we gather some results that are hard to find in the literature.
-
-\begin{lemma}\label{lemma:startopology}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    Suppose that $1 \leq n \leq 3$. Then the following holds:
-    \begin{itemize}
-        \item
-        If $S \in \calT$ is an inner simplex, 
-        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
-        \item
-        If $S \in \calT$ is a boundary subsimplex, 
-        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    The lemma is obvious if $n = 1$, so we assume $n \geq 2$ in what follows. 
-    We prove these statements in several steps. 
-    The reader is assumed to have some background in topology. 
-    \begin{enumerate}
-    \item 
-    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{S}$, and dimension $k$.
-    Let $\calS := \patch_{\calT}(S)$ be its star. 
-    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
-    has vertices $v_0$, $v_1$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$. 
-    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
-    $v_0$, $\dots$, $v_{i-1}$, $z_{S}$, $v_{i+1}$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$.
-    % \begin{align*}
-        % v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}. 
-    % \end{align*}
-    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
-    that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS' = \patch_{\calS'}(z_{S})$. 
-    In particular, $z_{S}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
-    So it remains to study the topology of vertex stars.
-
-    \item 
-    Suppose that $2 \leq n \leq 3$ and that $\calM$ is a manifold without boundary. 
-    Under these assumptions, 
-    as explained in the proof of Theorem~1 in \cite{Siebenmann1979},
-    the set $\carapace(V)$ is a triangulation of a sphere of dimension $n-1$ for any inner vertex $V$. 
-    There exists a homeomorphism from the closed cone of $\underlying{\carapace(V)}$ onto the local star $\underlying{\patch_{\calT}(V)}$.
-    But then that closed cone and hence $\underlying{\patch_{\calT}(V)}$ are homeomorphic to an $n$-dimensional ball.
-
-    \item 
-    If $2 \leq n \leq 3$ and $\calM$ has a non-empty boundary, then we use an approach as in the proof of Lemma~\ref{lemma:boundarysimplices}: 
-    we let $\calM'$ denote the doubling of the manifold and $\calT'$ be the doubling of the triangulation $\calT$. 
-    Let $V \in \calT$ be a vertex. 
-    If $V$ is an inner vertex of $\calT$, then $\carapace(V) \subseteq \calT \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT \subseteq \calT'$ triangulates a ball of dimension $n$, as discussed above.
-    If $V$ is a boundary vertex of $\calT$, then it is an inner vertex of $\calT'$,
-    and so $\carapace_{\calT}(V) \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT'$ triangulates a ball of dimension $n$.
-    We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$.
-    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
-    by the topological Schoenflies theorem. 
-    It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
-    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.
-
-%     Suppose that $S = \{z\}$ is a singleton simplex. 
-%     For $\delta > 0$ small enough, 
-%     \begin{align*}
-%         B_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) \leq \delta \right\},
-%         \quad 
-%         S_{\delta}(z) = \left\{ x \in \calM \suchthat d(x,z) = \delta \right\},
-%     \end{align*}
-%     are compactly contained subsets of $|\patch_{\calT}(S)|$.
-%     For each simplex $K \in \patch_{\calT}(S)$ that contains the vertex $z$ and which has the opposite face $F_K$, 
-%     we easily find homeomorphisms $\phi_{K} : B_{\delta}(z) \cap K \rightarrow K$
-%     such that 
-%     $\phi_{K}(z) = z$, 
-%     such that 
-%     $\phi_{K}( K \cap S_{\delta}(z) ) = F_{K}$,
-%     such that 
-%     for all $K, K' \in \calT$ with $K' \subseteq K$ we have $\phi_{K|K'} = \phi_{K'}$,
-%     and such that 
-%     $\phi_{K}$ maps $[0,1]\cdot v$ linearly into $\bbR \cdot v$. 
-%     This is defines a homeomorphism $\phi : B_{\delta}(z) \rightarrow |\patch_{\calT}(S)|$. 
-%     Moreover, one easily verifies that $\phi$ is bi-Lipschitz.
-%     %     For $\delta > 0$ small enough, $B_{\delta}(z)$ is homeomorphic to the unit ball and that homeomorphism maps $S_{\delta}(z)$ onto the unit sphere. 
-%     \item 
-%     One sees that $\phi$ defines a mapping from the closed 
-%     homeomorphism between cone of link and ball 
-%     
-%     If $z$ is an inner vertex of $\calS'$, 
-%     then the boundary simplices of $\calS'$,
-%     which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
-%     
-%     Now suppose that $z$ is a boundary vertex of $\calS'$,
-%     which is the case if and only if $S$ is a boundary simplex. 
-%     Write 
-%     \[
-%         B_{H} = \left\{ x \in B_1(0) \suchthat* x_1 \leq 0 \right\},
-%         \quad 
-%         S_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 \leq 0 \right\}.
-%         \quad 
-%         D_{H} = \left\{ x \in \partial B_1(0) \suchthat* x_1 = 0 \right\}.
-%     \]
-%     Provided that $\delta > 0$ is small enough, there exists a homeomorphism $\phi'$ that maps $\overline{B_{\delta}(z)} \cap \calM$ onto $B_1(0)$, which maps $\overline{B_{\delta}(z)} \cap \partial\calM$ onto $D_H$,
-%     and which maps $z$ to the origin. 
-%         %
-%     It follows that $\phi'$ maps the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$ onto $S_H$.
-%         %
-%     Assuming that $\delta$ is small enough once more, 
-%     we now verify that $\phi^{-1}$ maps $|\carapace(S)|$ onto $S_{\delta}(z) \cap |\patch_{\calT}(S)|$.
-%     The latter equals the closure of $\partial{B_{\delta}(z)} \setminus \partial\calM$.
-%     It follows that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
-    % We let $\calM'$ be the doubling of the manifold and let $\calT'$ be the doubling of the present triangulation;
-    % we refer to Lee's textbook~\cite{lee2011topological} for details. 
-    % The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
-    % and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. 
-    % The underlying space of $\carapace(S)$ is homeomorphic to $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ along $\phi$.
-    % The vertex star around $z$ within the boundary triangulation $\partial\calT$ is homeomorphic to the ball of dimension $n-1$,
-    % and it is homeomorphic to $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi$. 
-    % Notice that 
-    % \begin{align*}
-    %     \partial\left( { B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)| \right)
-    %     =
-    %     S_{\delta}(z) \cap |\patch_{\calT}(S)|
-    %     \cup 
-    %     \overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|
-    %     .
-    % \end{align*}
-    % Necessarily, this homeomorphism maps the boundary of $\overline{B_{\delta}(z)} \cap \underlying{\calT}$, which contains $z$, onto the unit sphere.
-Since the image of $\overline{ B_{\delta}(z) } \cap |\partial\patch_{\calT}(S)|$ along $\phi'$ is still homeomorphic to a disk of dimension $n-1$, so must be the image of $S_{\delta}(z) \cap |\patch_{\calT}(S)|$ under $\phi'$.
-    % But that just means that $\carapace(S)$ triangulates a topological ball of dimension $n-1$. 
-    \end{enumerate}
-    All relevant results are proven. 
-\end{proof}
-
-\begin{lemma}\label{lemma:connectivity}
-    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
-    If the underlying space of $\calT$ is connected, then $\calT$ is face-connected.
-\end{lemma}
-\begin{proof}
-    We first show that each vertex star is face-connected via a short induction argument.
-    Clearly, any simplicial $1$-ball and simplicial $1$-sphere are face-connected. 
-    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already face-connected if all simplicial $n$-balls and $n$-spheres are face-connected.
-    The induction argument implies that each vertex star in $\calT$ is face-connected.
-
-    If the underlying space $\underlying{\calT}$ is connected, 
-    then we easily see that the union of the $1$-simplices is path-connected.
-    Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
-    As each vertex star is face-connected, 
-    we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
-    is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-    This just means that $\calT$ is face-connected. 
-\end{proof}
-
-\begin{remark}
-    Triangulations with the property that all vertex stars are homeomorphic to a ball are also called \emph{combinatorial} \cite[Section~1]{Bagchi2005}.
-    All manifolds of dimension up to three admit smooth structures and smooth manifolds admit combinatorial triangulations. 
-    There are triangulations of manifolds in more than three dimensions where not every vertex star is homeomorphic to a ball.
-
-    Not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
-    Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
-    % Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. ~\cite{todo}
-    We therefore are not in pursuit of any easy combinatorial property that indicates whether a simplicial complex (without any further specific assumptions) triangulates a manifold.
-
-    Conversely, not all topological manifolds, even if compact, can be described as a triangulation. 
-    Such manifolds, some even compact and simply-connected, appear in dimension four and higher~\cite{akbulut2014casson}.
-%     For each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. 
-\end{remark}
-
-% 3. Shellability 
-\subsection{Shellable simplicial complexes}\label{subsection:shellability}
-
-The notions of shelling and shellable triangulation have been discussed widely in combinatorial topology and polytopal theory. 
-Formally, a triangulation is shellable if its full-dimensional simplices can be enumerated such that each simplex intersects the union of the previously listed simplices in a codimension one triangulation of a manifold.
-This forces the intermediate triangulations to be particularly well-shaped. 
-We build upon the notion of shelling as introduced in~\cite[Definition 8.1]{ziegler1995lectures},
-where our definition of shelling is equivalent to the notion of the shellings of simplicial complexes, see also~\cite[Remark~8.3]{ziegler1995lectures}.
-
-% \mwl{Roughly speaking, a triangulation is shellable if the triangulation can be built, starting from a single simplex,
-% by successively gluing simplices to intermediate triangulations such that a combinatorial-geometric condition is satisfied:
-% the gluing interface is a triangulated submanifold of the boundary. 
-% This forces the intermediate triangulations to be particularly well-shaped. 
-% We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
-%It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex, as this enables the inductive method of proof.
-% }
-
-Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
-For any enumeration, we call 
-\begin{align*}
-    \Gamma_m 
-    := 
-    \big( 
-        T_{0} \cup T_{1} \cup \dots \cup T_{m} 
-    \big) 
-    \cap 
-    T_{m+1}
-\end{align*}
-the $m$-th \textit{interface set}. 
-% Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
-We call the enumeration a \emph{shelling} if each interface set $\Gamma_m$ is a triangulated manifold of dimension $n-1$.
-
-The reason of our interest in shellable simplicial complexes is that they can be constructed via successive adhesion of simplices.
-The resulting succession of simplicial complexes consists of simplicial balls or spheres.
-
-\begin{lemma}\label{lemma:shell_triang_man}
-    Let $\calT$ be an $n$-dimensional simplicial complex 
-    with a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$,
-    such that each simplex of dimension $n-1$ is contained in at most two simplices. 
-    % DONE: what is non-branching?
-    Then
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}
-    $$ 
-    is a triangulated manifold with boundary for all $0 \leq m \leq M$.
-    % 
-    In particular, $X_{m}$ is a topological $n$-ball when $m < M$, 
-    and 
-    $X_{M}$ is either a topological $n$-ball or topological $n$-sphere. 
-\end{lemma}
-\begin{proof}  
-    We prove this claim by induction. 
-    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. Let $1 \leq m \leq M$ and suppose that 
-    \begin{align*}
-        X_{m-1} := T_{0} \cup T_{1} \cup \dots \cup T_{m-1}
-    \end{align*}
-    is a topological $n$-ball. Let $T_{m}$ is the next $n$-simplex in the shelling.
-    By definition, $\Gamma_{m} := X_{m-1} \cap T_{m}$ is a submanifold of $\partial T_{m}$,
-    and it is triangulated by some faces of $T_{m}$ and their subsimplices.
-
-    Let $F$ be such a face. 
-    By assumption, $F$ must be contained in exactly one $n$-simplex of $T_{0}, T_{1}, \dots, T_{m-1}$,
-    and $F$ is in the boundary of $X_{m-1}$. 
-    We conclude that $\Gamma_{m}$ triangulates a submanifold of the boundary of $X_{m-1}$.
-
-    On the one hand, 
-    if $\Gamma_{m}$ is the entire boundary of $T_{m}$, 
-    then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
-    Hence $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
-    which requires $m = M$.
-    On the other hand, 
-    if $\Gamma_{m}$ is a proper subset of the entire boundary of $T_{m}$, 
-    then $X_{m-1} \cup T_{m}$ is still a topological $n$-ball.
-\end{proof}
-
-\begin{remark}
-    We interpret a shelling as the construction of a triangulation 
-    by successively attaching simplices such that the intermediate triangulations are well-behaved. 
-    Conversely, the reverse enumeration describes a successive decomposition of the triangulation, hence the name ``shelling''.
-\end{remark}
-\begin{remark}
-    Whether a simplicial complex is shellable can be checked, in principle, simply by trying out all the possible enumerations.
-    That we cannot do much better than this is captured in the result that testing for shellability is NP-complete~\cite{goaoc2019shellability}:
-    this complexity result is even true if we merely consider simplicial complexes of dimension two embedded in some Euclidean space.
-\end{remark}
-
-We now collect important examples of shellable triangulations.
-Essentially, in two space dimensions, interesting triangulations are shellable, but starting from three space dimensions, non-shellable situations can arise.
-Our main interest are local patches (stars) within triangulations: these are shellable up to three space dimensions, but not necessarily beyond.
-
-\begin{example}\label{example:shell_simpl}
-    Any simplex $T$ (trivially) has a shelling, consisting only of $T$ itself. 
-    The boundary complex $\partial \calT(T)$ has a shelling:
-    any enumeration of the boundary faces of $T$ constitutes a shelling; see Example 8.2.(iii) in~\cite{ziegler1995lectures}.
-\end{example}
-\begin{example}
-    The standard triangulation of the $3$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable, as are its higher-dimensional generalizations.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
-\end{example}
-\begin{example}
-    There exists a non-shellable triangulation of a tetrahedron and of a cube in $n=3$, see~\cite[Example 8.9]{ziegler1995lectures}.
-\end{example}
-
-\begin{lemma}\label{lemma:shell_2D}
-    Any simplicial $2$-\disk\ is shellable.
-    Any simplicial $2$-sphere is shellable. 
-\end{lemma}
-\begin{proof}
-    First, 
-    let $\calS$ be any triangulation of a $2$-sphere. 
-    By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-\disk.
-    Any shelling of that \disk\ can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
-    So it remains to show that any triangulation $\calT$ of the two-dimensional \disk\ is shellable. 
-    We will construct the shelling in reverse.
-
-    Write $M = \underlying{\calT}$. 
-    There is nothing to show if $\calT$ contains only one triangle. 
-    We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
-    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
-    and a triangle is not good in $\calT$ if that intersection is either empty, only some of its vertices, or a vertex and the opposite edge.
-    % DONE: I understand what it means from the rest of the proof, but I believe it could a bit more explicit.
-    We show by an induction argument over the number of triangles that every triangulation of a $2$-\disk\ that contains at least two triangles also contains at least two good triangles.
-
-    Clearly, this is the case if the triangulation of the $2$-\disk\ contains two triangles. 
-    Now suppose the induction claim is true when the triangulation includes at most $N$ triangles,
-    and assume that $\calT$ includes $N+1$ triangles. 
-    As we travel along the boundary, we traverse along edges of at least two simplices, 
-    and therefore there are at least two triangles with an edge on the boundary. 
-    Suppose that $\calT$ does not have at least two triangles that are good in $\calT$.
-    Then there exists a triangle $T'$ that intersects $\partial M$ 
-    in one edge and its opposite vertex.
-    Removing $T'$ splits the manifold into two face-connected components, each of which is a topological $2$-\disk. 
-    By the induction assumption, each of those components contains at least two triangles 
-    that are good in the respective component. 
-    So each component has at least one triangle that is also good in $\calT$. 
-    Hence $\calT$ contains two good triangles, which completes the induction step.
-
-    We conclude that whenever $\calT$ triangulates a $2$-\disk,
-    it contains a good triangle $T$. 
-    If $T$ has three edges in the boundary, then $T = M$ and we are trivially done. 
-    If $T$ intersects with the boundary in exactly one or two edges, 
-    then $\overline{M \setminus T}$ is still a topological $2$-\disk.
-    The triangulation $\calT'$ that is obtained by removing $T$
-    is a triangulation of some $2$-\disk\ that intersects $T$ only at either two or one edges.
-    Any shelling of $\calT'$ can in this way be extended to a shelling of $\calT$, and the proof is complete. 
-\end{proof}
-
-\begin{lemma}
-    Let $\calT$ be a $3$-dimensional manifold triangulation and $S \in \calT$.
-    Then $\patch_{\calT}(S)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    The statement is trivially true if $S$ is a tetrahedron. 
-    The statement is clear if $S$ is an inner or boundary face of $\calT$,
-    where we only need to enumerate either one or two tetrahedra. 
-    The statement is still easily verified if $S$ is an inner or boundary edge of $\calT$:
-    one chooses a starting tetrahedron (with a boundary face if $S$ is a boundary edge) and rotates around the edge in a fixed direction to create a suitable enumeration. 
-    When $S$ is an inner vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-sphere.
-    Similarly, when $S$ is a boundary vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
-    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondence between the tetrahedra in $\calT$ and the triangles.
-    \footnote{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}
-\end{proof}
-
-\begin{lemma}\label{lemma:stars_are_shellable}
-    Let $\calT$ be a $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
-    Then $\patch_{\calT}(V)$ is shellable. 
-\end{lemma}
-\begin{proof}
-    This is Lemma~8.7 in \cite{ziegler1995lectures}.
-%     Without loss of generality, $V$ is the origin. 
-%     Any ray starting at $V$ intersects at most one vertex of $\patch_{\calT}(V)$.
-%     We can also assume that all boundary vertices of $\patch_{\calT}(V)$ to be unit vectors,
-%     which does not affect shellability. 
-%     The simplicial boundary complex of $\calT$ is the boundary complex of a convex polytope,
-%     and is thus shellable~\cite[Theorem~8.12]{ziegler1995lectures}. 
-\end{proof}
-
-\begin{remark}
-    Not all triangulable sets admit a triangulation that is shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations are shellable.
-For example, if we extend the non-shellable triangulation of the tetrahedron from~\cite[Example 8.9]{ziegler1995lectures} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
-    This demonstrates that patches around boundary simplices are not necessarily shellable when the space dimension $n$ is larger than three.
-\end{remark}
-\begin{remark}
-    Not all triangulable sets admit a triangulation that is also shellable. 
-    Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
-\end{remark}
-
-A major structural feature of shellable simplicial complexes is that each time an $n$-simplex is added, stars around lower-dimensional simplices gets completed.
-
-\begin{lemma}\label{lemma:existenceofstar}
-    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
-    For $0 \leq m \leq M$, write 
-    $$
-        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m}.
-    $$ 
-    For $1 \leq m \leq M$, write 
-    $$
-        \Gamma_{m} := X_{m-1} \cap T_{m}.
-    $$ 
-    Then $\Gamma_{m}$ is a union of $\ell$ different faces of $T_{m}$, $1 \leq \ell \leq n+1$.
-    If $m < M$, then the intersection of those faces is an interior simplex $S_{m} \in \calT$ of dimension $n-\ell$ that satisfies 
-    $$
-        \patch_{X_{m}}(S_{m}) = \patch_{\calT}(S_{m}).
-    $$
-\end{lemma}
-\begin{proof}
-    We know $\Gamma_{m}$ is a triangulated submanifold of the boundary of $T_{m}$, 
-    and so it must be a collection of $\ell$ faces of $T$, $1 \leq \ell \leq n+1$.
-    Note that $\ell = n + 1$ can only happen for the last enumerated simplex, $m = M$, if $\calT$ triangulates an $n$-sphere. 
-    $\Gamma_{m}$ also constitutes a local patch (star) of $(n-1)$-dimensional simplices around some simplex $S_{m}$ of dimension $n-\ell$ in $\Gamma_{m}$.
-    By definition, $S_{m}$ is a boundary simplex of $X_{m}$, 
-    and it is an interior simplex of $X_{m+1}$. 
-    But then $S_{m}$ cannot be a subsimplex of any of the simplices $T_{m+1}, \dots, T_{M}$,
-    which means that $\patch_{X_{m+1}}(S_{m}) = \patch_{\calT}(S_{m})$. 
-\end{proof}
-
-\section{Reflections and Deformations on shellable stars}\label{section:extension}
-
-This section is devoted to geometric operations that are crucial for our main result in Section~\ref{section:poincarefriedrichs} below. 
-Consider the situation where we have an $n$-dimensional local patch (star) around some simplex $S$ and some $n$-dimensional simplex $T$ within that local star. 
-We construct a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$,
-similar to the two- and three-color maps in \cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}
-This homeomorphism, which we interpret as a nonlinear reflection, is required to preserve the interface. 
-We ensure that the homeomorphism is bi-Lipschitz, and we are particularly interested in the norms of its Jacobian.
-This nonlinear reflection will be used subsequently in generalizing the discussion in Section~\ref{section:gradient} to the setting of differential forms. 
-Additionally, this endeavor produces another geometric tool:
-we construct a bi-Lipschitz deformation which contracts the entire star into the complement of the newly completed star. 
-This deformation will enable additional estimates of Poincar\'e--Friedrichs constants.
-
-% \begin{figure}
-% \tdplotsetmaincoords{60}{120}
-% \centering
-% \begin{tikzpicture}[tdplot_main_coords]
-% \coordinate (A) at (0, 0, 0);
-% \coordinate (B) at (2, 0, 0);
-% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
-% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
-% \coordinate (A) at (0, 0, 0);
-% \coordinate (B) at (2, 0, 0);
-% \coordinate (C) at (1, 1.73, 0); % 1.73 = sqrt(3) for an equilateral triangle
-% \coordinate (D) at (1, 0.58, 1.63); % 1.63 = sqrt(8/3) for a regular tetrahedron
-% \draw[thick] (A) -- (B) 
-% \draw[] (B) -- (C) 
-% \draw[] (C) -- (A) 
-% \draw[] (A) -- (D);
-% \draw[thick] (B) -- (D);
-% \draw[] (C) -- (D);
-% \node at (A) [below left] {$A(0,0,0)$};
-% \node at (B) [below right] {$B(2,0,0)$};
-% \node at (C) [above right] {$C(1,\sqrt{3},0)$};
-% \node at (D) [above] {$D(1, \frac{1}{\sqrt{3}}, \sqrt{\frac{8}{3}})$};
-% \end{tikzpicture} 
-% \caption{test}
-% \end{figure}
-
-We will use the following observation, which we state without proof, 
-that controls the volume and some heights when a simplex is partitioned via barycentric subdivision.
-
-\begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
-    Let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ in accordance with the barycentric subdivision of $S$ at $z_{S}$.
-    \begin{itemize}
-        \item $\vol(T') = \vol(T) / (k+1)$. 
-        \item The height vector of $v \in \Vertices(T) \setminus \Vertices(S)$ in $T'$ is the height vector $v$ in $T$.
-        \item The height vector of $z_S$ in $T'$ is the height vector of the single vertex $v \in \Vertices(T) \setminus \Vertices(T')$ in $T$,
-scaled by $(k+1)^{-1}$.
-    \hfill\qed
-    \end{itemize}
-\end{lemma}
-
-\begin{figure}
-    \begin{center}
-    \begin{tikzpicture}
-        % Coordinates of the triangle
-        \coordinate (A) at (0,0); % Vertex A = v_0
-        \coordinate (B) at (4,0); % Vertex B = v_1
-        \coordinate (C) at (1,3); % Vertex C = v_2
-        \coordinate (M) at ($(A)!0.5!(B)$); % Midpoint M of AB
-        % Heights from each vertex
-        \coordinate (H_A) at ($(C)!(A)!(B)$); % Height from A to BC
-        \coordinate (H_B) at ($(C)!(B)!(A)$); % Height from B to AC
-        \coordinate (H_C) at ($(A)!(C)!(B)$); % Height from C to AB
-        \coordinate (H_M) at ($(B)!(M)!(C)$); % Height from M to BC
-        % Drawing the triangle
-        \draw[thick] (A) -- (B) -- (C) -- cycle;
-        % Drawing the bisector from C to AB and the height vectors 
-        %\draw[dashed] (C) -- (M);
-        \draw[] (C) -- (M);
-        \draw[dashed,->,line width=1.0pt,>=latex] (H_A) -- (A); % Height vector from A, original 
-        \draw[dashed,->,line width=1.0pt,>=latex] (H_M) -- (M); % Height vector from A, original 
-        \draw[dashed,->,line width=1.0pt,>=latex] (H_C) -- (C); % Height vector from C, unaffected
-        % Marking the height points
-        \node[above right] at (C) {$v_2$};  
-        \node[below left] at (A) {$v_0$};
-        \node[below right] at (B) {$v_1$};
-        \node[below] at (M) {$z_S$};
-    \end{tikzpicture}
-    \begin{tikzpicture}
-
-        % Coordinates of the triangle
-        \coordinate (A) at (0,0); % Vertex A = v_0
-        \coordinate (B) at (4,0); % Vertex B = v_1
-        \coordinate (C) at (1,3); % Vertex C = v_2
-        % Barycenter (centroid) of the triangle
-        \coordinate (G) at (1.666666666,1); %($(A)!1/3!(B)!1/3!(C)$);
-        % Drawing the triangle
-        \draw[thick] (A) -- (B) -- (C) -- cycle;
-        % Tripartitioning the triangle: draw lines from vertices to the barycenter
-        \draw[] (A) -- (G);
-        \draw[] (B) -- (G);
-        \draw[] (C) -- (G);
-        % Heights from the barycenter to the sides of the triangle
-        \coordinate (H_GA) at ($(B)!(G)!(C)$); % Height from G to BC
-        \coordinate (H_GB) at ($(A)!(G)!(C)$); % Height from G to AC
-        \coordinate (H_GC) at ($(A)!(G)!(B)$); % Height from G to AB
-
-        % Drawing the height vectors from the barycenter
-        \draw[dashed,->,line width=1.0pt,>=latex] (H_GA) -- (G); % Height from G to BC
-        \draw[dashed,->,line width=1.0pt,>=latex] (H_GB) -- (G); % Height from G to AC
-        \draw[dashed,->,line width=1.0pt,>=latex] (H_GC) -- (G); % Height from G to AB
-
-        % Marking the points
-        \node[above right] at (C) {$v_2$};  
-        \node[below left] at (A) {$v_0$};
-        \node[below right] at (B) {$v_1$};
-        \node[right] at (G) {$z_T$};
-    \end{tikzpicture}
-    \end{center}
-    \caption{Illustration of Lemma~\ref{lemma:stardivision}. Left: 
-	the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles. 
-	The height vector to $v_2$ in all three triangles remains the same.
-The height vector to $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector to $v_0$ in the original triangle.
-	Right: 
-	the triangle $T$ is trisected, leading to three new triangles. 
-	The height vector to $z_T$ from the opposite edge in any triangle is one third of the original height vector of that edge.}
-\end{figure}
-
-We now provide the desired bi-Lipschitz transformation:
-on the one hand, the nonlinear reflection across the interface between the selected simplex and the remainder of the local star,
-and on the other hand, the bi-Lipschitz contraction from the local star onto the complement of the selected simplex. 
-We give detailed estimates for the singular values of their Jacobians.
-
-\begin{proposition}\label{proposition:starreflection}
-    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be an inner simplex of dimension $k < n$,
-    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
-    and let 
-    \begin{align*}
-        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
-        \qquad 
-        {\Gamma_1} := \Makoto \cap T,
-        \qquad 
-        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
-    \end{align*}
-    The following holds, where the constants on the right-hand sides are as stated in the proof. 
-    \begin{enumerate}
-    \item 
-    There exists a bi-Lipschitz piecewise affine mapping
-    \begin{align*}
-        \Xi_{1} : T \rightarrow \Makoto
-    \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
-    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
-    \begin{gather*}
-        \sigma_1 \leq \Cfive{n}{k}(\calT),
-        \quad 
-        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{k}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
-        \\
-        \sigma_n \leq \Csechs{n}{k}(\calT),
-        \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{k}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
-    \end{gather*}
-%     and which satisfies the upper bounds 
-%     \begin{gather*}
-%         \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
-%         \quad 
-%         \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
-%         \\
-%         | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
-%         \quad 
-%         | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
-%     \end{gather*}
-    \item 
-    There exists a bi-Lipschitz piecewise affine mapping
-    \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto
-    \end{align*}
-    which is the identity along $\partial \Makoto \setminus \partial T$.
-    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
-    \begin{gather*}
-        \sigma_1 \leq \Csieb{n}{k}(\calT),
-        \quad 
-        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{k}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
-        \\
-        \sigma_n \leq \Cacht{n}{k}(\calT),
-        \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{k}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
-    \end{gather*}
-%     and which satisfies the upper bounds 
-%     \begin{gather*}
-%         \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
-%         \quad 
-%         \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
-%         \\
-%         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
-%         \quad 
-%         | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
-%     \end{gather*}
-    \end{enumerate}
-\end{proposition}
-\begin{proof}
-    We derive the estimate in several steps. 
-    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
-    \begin{itemize}
-        \item 
-        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
-        % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
-        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
-        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
-
-        \item 
-        We let $z'_{S}$ be the midpoint of $S'$. 
-        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
-        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
-
-        We define another simplicial complex $\calS^c$ as follows:
-        given any $n$-simplex $K \in \calS$, 
-        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
-        thus obtaining a new simplex $K'$. 
-        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.
-
-        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
-        By construction, all its $n$-simplices contain $S$ as a subsimplex,
-        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
-        Moreover, $S$ is an inner subsimplex of that triangulation. 
-        In particular, $\calS'$ is its own star around $S$.
-
-        % TODO Check that $\calS'$ is a triangulation
-
-        \item 
-        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
-        Then $\calR'$ is its own local star around the barycenter $z_S$.
-        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
-        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
-        which we denote by $\calR$ and $\calR^{c}$, respectively.
-
-        Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
-
-        \item 
-        We introduce a new mapping $\Theta : \underlying{\calR} \rightarrow \underlying{\calR^c}$ between the underlying sets as follows.
-        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
-        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
-        be affine reference transformations
-        that agree on the vertices common to $K$ and $K'$.
-        Then the mapping 
-        \begin{align*}
-            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
-        \end{align*}
-        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
-        % \begin{align*}
-        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
-        %     \\
-        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
-        % \end{align*}
-        preserves volumes:
-        \begin{align*}
-            |\det( \Jacobian      \Theta_{|K} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|K} )|
-            =
-            1
-            .
-        \end{align*}
-        We want to characterize the singular values of this transform. 
-        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
-        We can write
-        \begin{align*}
-            \Theta_{|K}(x) 
-            = 
-            x
-            - 
-            2 \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            \hat z_{S'}
-            .
-        \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
-        and that it equals $-z_{S'}$ when $x = z_{S'}$.
-%         and when $x = z_{S'}$, then 
-%         \begin{align*}
-%             -z_{S'} 
-%             =
-%             z_{S'}
-%             - 
-%             2 \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-%             .
-%         \end{align*}
-        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
-        \begin{align*}
-            \Theta_{|K}( h_{z} ) 
-            &= 
-            h_{z}
-            - 
-            2 \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            = 
-            h_{z}
-            - 
-            2 \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            %\\&
-            = 
-            h_{z}
-            - 
-            2 z_{S'}
-            %\\&
-            = 
-            - h_{z}
-            - 
-            2 b_{z}
-            .
-        \end{align*}
-        Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
-        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
-        We study the singular values of the matrix 
-        \begin{align*}
-            B 
-            := 
-            \begin{pmatrix}
-            -1                 & 0
-            \\ 
-            -2 \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
-            \end{pmatrix}
-            =
-            \begin{pmatrix}
-            -1             & 0
-            \\ 
-            -2 \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
-        Its square roots are the desired singular values of $B$:
-        \begin{align}
-            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
-            ,
-            \\
-            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
-            .
-        \end{align}
-        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
-        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
-        whereas all its other singular values equal $1$.
-
-%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        We develop explicit bounds for these singular values. 
-        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
-        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
-        % Obviously, $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$.
-
-        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
-        which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
-        Thus 
-        \begin{align*}
-            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
-            = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            \leq 
-            (n-k) \aspectratio(T)
-%             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
-%             \leq 
-%             \frac{ n-k }{n!}
-%             \cdot 
-%             \frac{ \diam(T)^{n} }{ \vol(T) }
-            .
-        \end{align*}
-        This establishes bounds on the singular values of the transformation. 
-        We abbreviate 
-        \begin{align}\label{math:upper_bound_for_theta}
-            B_{T} 
-            := 
-%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
-%             \geq 
-            \sqrt{ 
-                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
-            } 
-            + 
-            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
-            .
-        \end{align}
-
-        \item 
-        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
-        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
-        We construct a bi-Lipschitz mapping 
-        \begin{align*}
-            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
-        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
-        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
-        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
-        has a unique representation
-        \begin{align*}
-            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
-        \end{align*}
-        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
-        \begin{align*}
-            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
-            .
-        \end{align*}
-        Based on that observation, we define 
-        \begin{align*}
-            \Phi_{K}(x) 
-            &
-            := 
-            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
-            \\&
-            = 
-            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
-            = 
-            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
-            .
-        \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
-        that satisfies the desired mapping properties. 
-        It remains to analyze its Jacobian to get explicit estimates.
-
-        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
-        With that,
-        \begin{align*}
-            \Jacobian \Phi_{K}(x)
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle }  
-            z_{S'} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
-            h_{z} \otimes h_{z}^{t}
-            - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
-            b_{z} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
-            h_{z} \otimes h_{z}^{t}
-            - 
-            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
-            b_{z} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{3}{ 2 } 
-            \hat h_{z} \otimes \hat h_{z}^{t}
-            - 
-            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
-            \hat b_{z} \otimes \hat h_{z}^{t}
-            .
-        \end{align*}
-        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.
-        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
-        \begin{align*}
-            C 
-            = 
-            \begin{pmatrix}
-                -\frac 1 2             & 0 
-                \\
-                -\frac 3 2 \tan(\beta) & 2 
-            \end{pmatrix}
-            = 
-            \frac 1 2 
-            \begin{pmatrix}
-                -1 & 0 
-                \\
-                -3\tan(\beta) & 2 
-            \end{pmatrix}
-        \end{align*}
-        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
-        \begin{align*}
-            \sigma_{\max} 
-            = 
-            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-            ,
-            \\
-            \sigma_{\min} 
-            = 
-            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-            .
-        \end{align*}
-        \begin{align*}
-            \sigma_{\max} 
-            = 
-            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
-            %=
-            %\frac 1 4 \sqrt{ 9 + 9\tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            =
-            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            ,
-            \\
-            \sigma_{\min} 
-            = 
-            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            .
-        \end{align*}
-        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
-        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
-        \begin{align*}
-            \det \Jacobian\Phi = \frac 1 2.
-        \end{align*}
-        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
-        Similar as above, we use the upper bound 
-        \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
-        \end{align*}
-        We conclude that 
-        \begin{gather}
-            \matnorm{ \Jacobian\Phi_{K} } 
-            \leq 
-            \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            \leq 
-            1 + \frac{3}{2} (k+1) \aspectratio(T) 
-            \label{math:phi_max}
-            ,
-            \\
-            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
-            \leq 
-            \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            \leq 
-            2 + 3 (k+1) \aspectratio(T) 
-            \label{math:phi_min}
-            .
-        \end{gather}
-        This finishes the discussion of the transformation $\Phi$.
-
-        \item 
-        We continue with an auxiliary result.
-        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
-        Define 
-        \begin{align*}
-            F(x) 
-            = 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
-            x
-            .
-        \end{align*}
-        This is defined away from the hyperplane orthogonal to $h_2$.
-        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
-        That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
-        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed,
-
-        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
-        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $x$ and between $h_2$ and $x$, respectively. 
-        In what follows, $y \in \bbR^{n}$.
-        \begin{align*}
-            \Jacobian F(x) \cdot y
-            &=
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
-            x
-            - 
-            \frac{ \langle h_2, h_2 \rangle \langle h_2, y \rangle }{ \langle h_2, x \rangle^{2} }
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            x 
-            +
-            \frac{ \langle h_2, h_2 \rangle }{ \langle h_2, x \rangle }
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            y 
-            \\&=
-            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
-            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            +
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
-            x
-            \\&=
-            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
-            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
-            +
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
-            \hat x
-            \\&=
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
-            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
-            +
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
-            \hat x
-            \\&=
-            \frac{ \| h_2 \| }{ \| h_1 \| }
-            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
-            \left( 
-                y 
-                - 
-                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
-                + 
-                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
-            \right)
-            .
-        \end{align*}
-        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
-        Notice that $a \perp \hat x$.
-The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
-Over that two-dimensional subspace, it can be represented by a triangular matrix.
-        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
-        %~\cite{blinn1996consider} 
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
-            \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
-        \end{align*}
-        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
-        We thus consider the upper bound 
-        \begin{align*}
-            \|a\| 
-            \leq 
-            2 \max_{1 \leq i \leq 2} 
-            \left( 
-                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
-            \right)
-            .
-        \end{align*}
-
-        \item 
-        We now describe the construction of a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : \underlying{\calR'} \rightarrow \underlying{\calK}.
-        \end{align*}
-        Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,
-        so they must contain an open ball around the origin. 
-        % TODO \mwl{Here we need to show that it is indeed a ball. It must be a domain triangulation.}
-        Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
-There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively.
-They define respective hyperplanes $H_{G}$ and $H_{K}$,
-        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$ for the corresponding faces. 
-        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$,
-        that is, the scalar product of $x$ with either height vector is positive. 
-        We define 
-        \begin{align*}
-            \Psi(x) 
-            = 
-            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
-            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
-            x
-            .
-        \end{align*}
-        One easily verifies that this defines a continuous mapping $\Psi$. 
-        By the same line of thought, we see that it is invertible with inverse satisfying 
-        \begin{align*}
-            \Psi^{-1}(z) 
-            = 
-            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
-            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
-            z,
-            \qquad 
-            z = \Psi(x)
-            .
-        \end{align*}
-        We let $\alpha_K$ and $\alpha_{{G}}$ be the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
-        and let 
-        \begin{align*}
-            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
-            .
-        \end{align*}
-        The preceding auxiliary results now contribute all information on the singular values of these Jacobians:
-        \begin{gather*}
-            \matnorm{ \Jacobian\Psi(x) }
-            = 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
-            \right)
-            \\
-            \matnorm{ \Jacobian\Psi(z)^{-1} }
-            = 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
-            \right)^{-1},
-            \\
-            \det\Jacobian\Psi(x)
-            =
-            \left( 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \right)^{n},
-            \qquad
-            \det\Jacobian\Psi^{-1}(x)
-            =
-            \left( 
-            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
-            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
-            \right)^{n}
-        \end{gather*}
-        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
-        By the definition of the cosine, 
-        \begin{align*}
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            = 
-            \frac{ \| x_K \| }{ \| x_{{G}} \| }
-            \leq 
-            \frac{ \| x_K \| }{ \| h_{{G}} \| }
-            \leq 
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
-            ,
-            \qquad 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            = 
-            \frac{ \| x_{G} \| }{ \| x_{K} \| }
-            \leq 
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
-            \frac{ \diam(G) }{ \| h_{K} \| }
-            .
-        \end{align*}
-%         \begin{align*}
-%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
-%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-%             \leq 
-%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
-%             .
-%         \end{align*}
-        We need further details to complete our estimates. 
-        We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
-The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
-        That estimates the quotient $\| x_K \| / \| h_K \|$. 
-        % 
-        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
-        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
-        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows again that $\|x_{G}\| \leq \diam(T)$. 
-        % 
-        It remains to find a lower bound for $\| h_{G} \|$.
-        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
-        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
-The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
-        %         
-%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
-%         \begin{align*}
-%             \frac{\diam(T)}{ \|h_{F}\|}
-%             \leq  
-%             \aspectratio(T)
-%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%             .
-%         \end{align*}
-        Putting all these technical observations together, we estimate 
-        \begin{align*}
-            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
-            &\leq 
-            (k+1)B_{T}
-            \frac{ \diam(K) }{ \| h_{T} \| }
-            \leq 
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \frac{ \diam(T) }{ \| h_{T} \| }
-            \leq 
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            ,
-            \\
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            &\leq 
-            (k+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(T) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \diameterratio(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K) }{ \| h_{K} \| }
-            \leq 
-            (k+1)
-            \diameterratio(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-        \begin{gather*}
-            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
-            \leq 
-            (k+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            ,
-            \qquad 
-            \frac{ \| x_{G} \| }{ \| h_{G} \| }
-            \leq 
-            (k+1)B_{T}
-            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            .
-        \end{gather*}
-
-        %         To simplify that expression, we make another observation regarding the height vectors. 
-        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
-        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
-        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
-        %         with the factor $(k+1)^{-1}$.
-
-        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$.
-That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
-        We calculate 
-        \begin{align*}
-            \|a\|
-            = 
-            \left\|
-            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
-            - 
-            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
-            \right\|
-            &
-            \leq 
-            \frac{\|x_{G}\|}{\|h_{G}\|} 
-            + 
-            \frac{\|x_{K}\|}{\|h_{K}\|} 
-            % \\&
-            \leq 
-            (k+1) 
-            \left( 1 + B_{T} \right)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-        In summary, using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, we find the upper bounds 
-        \begin{align*}
-            \matnorm{ \Jacobian\Psi(x) }
-            &\leq  
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \cdot 
-            \left( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT) 
-            \right)
-            ,
-            \\
-            \matnorm{ \Jacobian\Psi(z)^{-1} }
-            &\leq  
-            (k+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \cdot 
-            \left( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT) 
-            \right)
-            ,
-            \\
-            \det\Jacobian\Psi(x)
-            &\leq 
-            \left( 
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \right)^{n},
-            \\
-            \det\Jacobian\Psi^{-1}(x)
-            &\leq 
-            \left( 
-            (k+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \right)^{n}
-        \end{align*}
-        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
-        % It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
-        % Rademacher's theorem then shows that both have essentially bounded weak Jacobians. 
-        Every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $\underlying{\calK}$, since there exists a bi-Lipschitz transformation from $\underlying{\calK}$ onto the unit ball.
-        % We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-        % After application of a piecewise linear Lipschitz mapping, 
-        % we can assume that $\underlying{\calK}$ is convex without loss of generality. 
-        % Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $\underlying{\calK}$. 
-        % \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
-
-        \item 
-        We define a mapping $ \Xi_{1} : T \rightarrow \Makoto = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
-        \begin{align*}
-            \Xi_{1} := \Psi \circ \Theta.
-        \end{align*}
-        It preserves the interface from $T$ onto $\Makoto$. 
-        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
-        Combining the previous estimates for $\Psi$ and $\Theta$ with interlacing inequalities for the singular values of product matrices provides 
-        \begin{align*}
-            \sigma_1(x) = \matnorm{ \Jacobian \Xi_{1} }
-            &\leq 
-            \Cfive{n}{k}(\calT)
-            :=
-            (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            B_{T}^{2}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            ,
-            \\
-            \sigma_2(x), \dots, \sigma_n(x) 
-            &\leq 
-            \Cfiveprime{n}{k}(\calT)
-            :=
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) 
-            \cdot 
-            B_T
-            \\
-            \sigma_n(x)^{-1} = \matnorm{ \Jacobian \Xi_{1}^{-1} }
-            &\leq
-            \Csechs{n}{k}(\calT)
-            :=
-            (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            B_{T}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)
-            \\
-            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
-            &\leq 
-            \Csechsprime{n}{k}(\calT)
-            :=
-            (k+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \cdot 
-            B_T
-            .
-        \end{align*}
-        We get the determinant estimates
-        \begin{align*}
-            |\det(\Xi_{1})|
-            &\leq 
-            \Cdetfive{n}{k}(\calT)
-            :=
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            B_{T}^{n}
-            \aspectratio(\calT)^{n}
-            ,
-            \\
-            |\det(\Xi_{1}^{-1})|
-            &\leq 
-            \Cdetsechs{n}{k}(\calT)
-            :=
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
-            .
-        \end{align*}
-        This completes the desired estimates for $\Xi_{1}$.
-
-        \item 
-        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto $ by setting 
-        \begin{align*}
-            \Xi_{2} := \Psi \circ \Phi.
-        \end{align*}
-        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
-        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
-        The combination of the previous estimates for $\Psi$ and $\Phi$ with standard interlacing inequalities now lead to 
-        \begin{align*}
-            \sigma_1(x)
-            = 
-            \matnorm{ \Jacobian \Xi_{2} }
-            &\leq 
-            \Csieb{n}{k}(\calT)
-            :=
-            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
-            \cdot 
-            (k+1) 
-            \aspectratio(\calT)
-            B_{T}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            \\
-            \sigma_2(x), \dots, \sigma_n(x) 
-            &\leq 
-            \Csiebprime{n}{k}(\calT)
-            :=
-            (k+1)B_{T}
-            \diameterratio(\calT)
-            \aspectratio(T) 
-            \cdot 
-            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
-            \\
-            \sigma_n(x)^{-1}
-            = 
-            \matnorm{ \Jacobian \Xi_{2}^{-1} }
-            &\leq  
-            \Cacht{n}{k}(\calT)
-            :=
-            \left( 2 + 3 (k+1) \aspectratio(T) \right)
-            \cdot 
-            (k+1) 
-            \aspectratio(\calT)
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
-            \\
-            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
-            &\leq 
-            \Cachtprime{n}{k}(\calT)
-            :=
-            (k+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \cdot 
-            \left( 2 + 3 (k+1) \aspectratio(T) \right)
-            .
-        \end{align*}
-        We get the determinant estimates 
-        \begin{align*}
-            |\det(\Xi_{2})|
-            &\leq 
-            \Cdetsieb{n}{k}(\calT)
-            :=
-            \frac 1 2 
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            B_{T}^{n}
-            \aspectratio(\calT)^{n}
-            ,
-            \\
-            |\det(\Xi_{2}^{-1})|
-            &\leq 
-            \Cdetacht{n}{k}(\calT)
-            :=
-            2
-            (k+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
-            .
-        \end{align*}
-        This completes the desired estimates for $\Xi_{2}$. 
-    \end{itemize}
-    The proof is complete. 
-\end{proof}
-
-\begin{remark}
-    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
-    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
-    While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
-    it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
-\end{remark}
-
-\section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
-
-We are now in the position to develop Poincar\'e--Friedrichs constants for the exterior derivative over domains with shellable triangulations; this includes the curl and divergence operators in three dimensions.
-These results use local Poincar\'e--Friedrichs constants over simplices, 
-with or without boundary conditions, as subcomponents.
-
-The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator}
-implies the following estimate for Poincar\'e--Friedrichs constants over convex domains.
-
-\begin{lemma}\label{lemma:PFexteriorsimplex}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set. 
-    Let $0 \leq k < n$. 
-    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
-    with $\cartan u = \cartan w$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        C_{{\PF},k,\Omega,p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    where 
-    \begin{align*}
-        C_{{\PF},k,\Omega,p} 
-        = 
-        n C_{\Poinc}(n,k+1) 
-        \vol_{}(B_1(0)) 
-        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
-        \diam(\Omega)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
-\end{proof}
-
-We also need a Poincar\'e--Friedrichs inequality for differential forms over a simplex but subject to homogeneous boundary conditions along a collection of faces.
-
-\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
-    Let $T$ be an $n$-simplex 
-    and let $\Gamma = F_{0} \cup \dots \cup F_{\ell}$ be the union of $\ell+1$ different faces of $T$. 
-    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,\Gamma} u = 0$.
-    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
-    $\trace_{T,\Gamma} w = 0$
-    and  
-    \begin{align*}
-        \cartan w = \cartan u,
-        \quad 
-        \| w \|_{L^{p}(\Omega)} 
-        \leq 
-        C_{\PF,\Gamma,\ell,k,p}(T)
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-    Here, $C_{\PF,\Gamma,\ell,k,p}(T) > 0$ is a constant such that 
-    \begin{align*}
-        C_{\PF,\Gamma,\ell,k,p}(T)
-        \leq 
-        2^{\frac{n-\ell}{p}}
-        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
-        \algebraicshapemeasure(T)^{k-1}
-        \Ceins{n}(T) 
-        \diam(T)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    There exists an affine bijection $\varphi : \Delta^n \rightarrow T$ 
-    that maps the convex closure of the $n$ unit vectors onto the face $F_0$.
-    We can also assume that the face of $\Delta^n$
-    orthogonal to the $i$-th coordinate axis is mapped 
-    onto the face $F_i$. 
-    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = (l+1)/n!$
-
-    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\Delta^n)$ via $\hat g := \cartan \varphi^{\ast} u$. 
-    Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u$ be the extension of $\hat u$ onto $\widetilde \Makoto$ by reflection across the coordinate axes,
-    and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
-    We observe $\tilde g = \cartan \tilde u$. 
-    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$.
-
-    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
-    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
-    with $\cartan \tilde w = \cartan \tilde u$ and 
-    \begin{align*}
-        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
-        &\leq 
-        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 
-        2
-        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        \\&\leq 
-        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
-        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        .
-    \end{align*}
-    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\Delta^n} )$.
-    By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{l}$.
-
-    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
-    \begin{align*}
-        \| w \|_{L^{p}(T)}
-        &\leq 
-        |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
-        \| \tilde w \|_{L^{p}(\Delta^n)}
-        ,
-        \\
-        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        \leq 
-        2^{\frac {n-\ell} p}
-        \| \hat g \|_{L^{p}(\Delta^n)}
-        &\leq 
-        2^{\frac {n-\ell} p}
-        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
-        \matnorm{\Jacobian \varphi}^{k}
-        \cdot 
-        \| \cartan u \|_{L^{p}(T)}
-        .
-    \end{align*}
-    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. 
-\end{proof}
-
-We prepare some further notation for our two main results. 
-Whenever $\calT$ is an $n$-dimensional triangulation, we use the abbreviation
-\begin{align*}
-    C_{\PF,\Gamma,k,p}(\calT) 
-    :=
-    \max\limits_{ \substack{ T \in \calT \\ \dim(T)=n \\ 0 \leq l \leq n } }
-    C_{\PF,\Gamma,l,k,p}(T)
-    .
-\end{align*}
-Suppose that $\calT$ is an $n$-dimensional triangulation and has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
-For each $0 \leq m \leq M$, we write 
-\begin{align*}
-    X_{m} := T_0 \cup T_1 \cup \dots \cup T_{m},
-\end{align*}
-which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
-For each $1 \leq m \leq M$, the interface of the new simplex to the previous intermediate triangulation is 
-\begin{align*}
-    \Gamma_{m} := T_{m} \cap X_{m-1} %\left( T_{0} \cup \dots \cup T_{m-1} \right)
-    .
-\end{align*}
-According to Lemma~\ref{lemma:existenceofstar}, 
-there exists an interior simplex $S_{m} \in \calT$ 
-such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $T_{m} \in \patch_{\calT}(S_{m})$.
-In particular, already $\patch_{\calT}(S_{m}) \subseteq X_{m}$. % is already included in the union of the simplices up to $T_m$.
-
-In addition to that, we introduce 
-\begin{align*}
-    \Makoto_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}.
-\end{align*}
-for the complement $\Makoto_{m-1} \subseteq X_{m-1}$ of the simplex $T_{m}$ in the star $\patch_{\calT}(S_{m})$.
-
-The two main results of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorems. 
-The first one is inspired by the recursive construction of gradient potentials in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-The second one is specific to the fact that shellable triangulations are contractible.
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
-    % Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
-	Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Let $T_0, T_1, \dots, T_M$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$
-	and such that the following estimates hold:
-	\begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \left( 
-            \| \cartan u      \|_{L^{p}(T_{m})} 
-            +
-            \Cfive{n}{k}(\calT)
-            \Cfiveprime{n}{k}(\calT)^{k} 
-            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-            \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
-        \right)
-        \\&\qquad
-        + 
-        \Cfive{n}{k}(\calT) 
-        \Cfiveprime{n}{k}(\calT)^{k-1} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(\Makoto_{m-1})}
-        .
-    \end{align*}
-\end{theorem}
-\begin{proof}
-    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
-    First, there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
-    \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
-    \end{gather*}
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $X_{m-1}$. 
-    By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
-    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S_{m}$, 
-	and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
-    We define $w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$. 
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        . 
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $X_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(X_{m})$ with $\cartan w_{m} = \cartan u$ over $X_{m}$.
-
-    We want to estimate norms. By the triangle inequality, 
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-    we can assume that $w''_{m}$ satisfies 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
-        \\&
-        \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
-        .
-    \end{align*}
-    Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} now show 
-    % \begin{align*}
-        % \| w'_{m} \|_{L^{p}(T_{m})}
-        % &\leq 
-        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k}
-        % \|\det \Jacobian \Xi_{1}^{-1}  \|_{L^{\infty}(\Makoto_{m-1})}^{\frac 1 p} 
-        % \cdot 
-        % \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
-        % ,
-        % \\
-        % \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        % &\leq 
-        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k+1}
-        % \|\det \Jacobian \Xi_{1}^{-1}  \|^{\frac 1 p}_{L^{\infty}(\Makoto_{m-1})} 
-        % \cdot 
-        % \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
-        % .
-    % \end{align*}
-    \begin{align*}
-        \| w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        \Cfive{n}{k}(\calT)
-        \Cfiveprime{n}{k}(\calT)^{k-1}
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
-        \cdot 
-        \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
-        ,
-        \\
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        &\leq 
-        \Cfive{n}{k}(\calT)
-        \Cfiveprime{n}{k}(\calT)^{k}
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
-        \cdot 
-        \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
-        .
-    \end{align*}
-    We have assumed that $\cartan w_{m-1} = \cartan u_{|X_{m-1}}$. 
-    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
-\end{proof}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$. % CAUTION 
-    Let $T_0, T_1, \dots, T_M$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
-    such that 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        \leq 
-        \left( 
-        \Cacht{n}{k}(\calT)
-        \Cachtprime{n}{k}(\calT)^{k} 
-        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-        \Csieb{n}{k}(\calT)
-        \Csiebprime{n}{k}(\calT)^{k-1} 
-        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-        \right)^{M}
-        C_{{\PF},k,T_{0},p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
-\end{theorem}
-\begin{proof}
-    We prove this via induction. 
-    The statement is clearly satisfied when $M=0$ because then we only consider a single simplex,
-    so that the Poincar\'e--Friedrichs inequality over a simplex can be used. 
-    Let us assume that the statement is true for some integer $M-1 \geq 0$.
-
-	Recall that $X_M$ is an $n$-dimensional submanifold with boundary with a triangulation that has a shelling $T_0, T_1, \dots, T_{M-1}$. 
-	Write $\Omega' \subseteq X_{M}$ for the interior domain of that manifold. 
-	By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
-	and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star.
-
-	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Makoto_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
-	This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{M-1} \setminus \partial T$.
-    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.
-
-	Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
-    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
-    \begin{align*}
-        \| g' \|_{L^{p}(\Omega')}  
-        \leq 
-        \Cacht{n}{k}(\calT)
-        \Cachtprime{n}{k}(\calT)^{k} 
-        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-        \| g \|_{L^{p}(\Omega)}  
-        .
-    \end{align*}
-    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$ and 
-    \begin{align*}
-        \| w' \|_{L^{p}(\Omega')} 
-        \leq 
-        \left( 
-        \Cacht{n}{k}(\calT)
-        \Cachtprime{n}{k}(\calT)^{k} 
-        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-        \Csieb{n}{k}(\calT)
-        \Csiebprime{n}{k}(\calT)^{k-1} 
-        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-        \right)^{M-1}
-        C_{{\PF},k,T_{0},p}
-        \| g' \|_{L^{p}(\Omega')}  
-    \end{align*}
-    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
-    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}  
-        \leq 
-        \Csieb{n}{k}(\calT)
-        \Csiebprime{n}{k}(\calT)^{k-1} 
-        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-        \| w' \|_{L^{p}(\Omega')} 
-    \end{align*}
-    The induction step is complete, and the desired result follows. 
-\end{proof}
-
-\section{Numerical examples}\label{section:numericalexamples}
-
-We assess the ``efficiency'' of our upper bounds with a few numerical examples in dimension 2D and 3D, with focus on the Hilbert space case $p=2$. 
-Unless the Poincar\'e--Friedrichs constants are known explicitly, we use eigenvalue estimates on a refined mesh as a proxy for the exact value.
-We compare the (approximations of) the exact values with the upper bounds obtained via Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
-
-\subsection{Estimates for partial boundary conditions}
-
-We first assess the constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-which relies on estimates for the Bogovski\u{i} operator over an auxiliary reference domain.
-Our experiments over triangles and tetrahedra indicate that we overestimate the constant by several magnitudes.
-%
-We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
-Numerical examples indicate that this holds for $p=2$.
-
-\subsection{Two-dimensional examples}
-
-We consider the following example domains in two dimensions:
-the unit square $\Omega_Q$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{S}$:
-\begin{gather*}
-    \Omega_{Q}  = (-1,1)^2,
-    \qquad 
-    \Omega_{L}  = (-1,1)^2 \setminus (0,1)^2,
-    \\
-    \Omega_{S} = (-1,1)^2 \setminus ( [0,1) \times \{0\} ).
-\end{gather*}
-% Square 
-% L-shaped 
-% Slit
-
-\subsection{Three-dimensional examples}
-
-We consider the following example domains in two dimensions:
-the unit cube $\Omega_C$, the Fichera corner domain $\Omega_F$, and the crossed bricks domain $\Omega_{B}$:
-\begin{gather*}
-    \Omega_{C}  = (-1,1)^3,
-    \qquad 
-    \Omega_{F}  = (-1,1)^3 \setminus [0,1)^3,
-    \\
-    \begin{aligned}
-    \Omega_{B} &= 
-    \left( (-1,0) \times (-1,0) \times (-1,1) \right)
-    \\&\qquad
-    \cup 
-    \left( (-1,0) \times (-1,1) \times (-1,0) \right)
-    \\&\qquad
-    \cup 
-    \left( (-1,1) \times (-1,0) \times (-1,0) \right)
-    .
-    \end{aligned}
-\end{gather*}
-% Cube 
-% Fichera
-% Crossed bricks
-
-\section{Outlook}\label{section:outlook}
-
-The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions. 
-There are several avenues for further research. 
-In particular, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), 
-as there are at least two areas where the present techniques could see further improvement.
-
-Firstly, we use local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) likely allow room for improvement.
-We conjecture that the Guerini--Savo~\cite{guerini2004eigenvalue} estimates, hitherto only known when $p=2$ and over bounded convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized Poincar\'e operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently employ.
-Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{i} operators.
-
-Secondly, our construction uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
-In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques could lead to better estimates,
-such as via trace and extension operators.
-
-Lastly, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is restricted to topological balls and spheres. 
-In particular, the underlying set of any shellable triangulations is contractible. 
-We expect forthcoming works to utilize our estimates over local patches as subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
-
-% Future work % DONE: Theo : parts already mentioned ??? 
-% Computable reliable estimates are important: 
-% they quantify the fundamental stability properties of partial differential equations in vector analysis,
-% such as the Hodge Laplace equation. 
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-
-\section*{Acknowledgments}
-
-MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
-
-\bibliographystyle{acm_mod}
-\bibliography{library}
-
-\end{document}
+Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.

### 2024-10-07 main.tex
introduction, main theorems

@@
     We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations. 
+    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
     The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry. 
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
+    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of vector Laplacians. 
     % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
-    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
     % 
@@
     This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
-    \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
+    {We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
     Computational examples illustrate the theoretical findings.
@@
 which quantify the fundamental stability features of a variety of partial differential equations. 
-In numerical methods, estimates for the Poincar\'e--Friedrichs constants enter the stability and convergence theory and spectral bounds for stiffness matrices. 
-Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians. 
+Estimates for the Poincar\'e--Friedrichs constants also enter the stability and convergence theory of numerical methods. 
+Computable upper bounds of the Poincar\'e--Friedrichs constants also provide computable lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
 However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
@@
 
-This manuscript aims to fill this gap.
-\cye{In the gradient case, we can go over with so-called face-connected triangulations.
-However, to proceed in the general exterior derivative case, we are brought to so-called shellable triangulations.}
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards more general cases.
-\cye{We cover most practical non-convex and non-star-shaped triangulated domains,} and as a particular example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars), which are shellable in two and three spaces dimensions.
-Additionally, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
-
-% old
-Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
-The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations.
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.
-
-We illustrate the subject of our discussion with the curl operator. 
-If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
-we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$.
-Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
-\begin{align*}
-    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
-    \leq 
-    C_{\curl}
-    \| \bff \|_{L^{2}(\Omega)}
-    .
-\end{align*}
-The constant in this inequality corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on that domain. 
-Broadly speaking, upper bounds for the Poincar\'e--Friedrichs constants correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacians.
-In numerical methods, estimates for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods, as well as spectral bounds for finite element matrices. 
-\\
-
-Finding a potential operator, whether linear or non-linear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
-The majority of estimates in the literature address only gradient potentials. 
-We carry out this endeavor in the special case where $\Omega$ admits a so-called \emph{shellable} triangulation. 
-Even though only contractible domains can ever admit a shellable triangulation, 
-having computable upper bounds for such domains is an important stepping stone towards the more general case. 
-For example, local stars around a simplex within a larger 2D or 3D triangulation are shellable.
-Poincar\'e--Friedrichs inequalities over local stars are our main goal in this exposition. 
-\\
+This manuscript aims to fill this gap. How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
+We apply the construction principle to the curl and divergence operators, as well as the exterior derivative. 
+However, to proceed in the general exterior derivative case, we restrict our efforts to so-called shellable triangulations. 
+Only contractible domains can ever admit a shellable triangulation, but having computable upper bounds for such domains is an important stepping stone towards more general situations. 
+The class of shellable of shellable triangulations includes practically relevant triangulations. 
+For example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
+Additionally, the study of regularized Poincar\'e and Bogovski\u{i} operators leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
 
@@
 
-Before we outline the main results of this exposition in more detail, 
-we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
-We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as our conceptual point of reference.
-
-Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
-we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
+We give a conceptual overview of the topic before we outline the known results in the literature and our contributions in more detail.
+Our conceptual point of reference is the Poincar\'e--Friedrichs inequality for the gradient of scalar functions.
+
+Let $\Omega \subseteq \bbR^n$ be a bounded connected open set.
+Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields, and $W^{1,p}(\Omega)$ denotes the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
+
+We search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
 for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
@@
 The different scalar potentials only differ by a constant. 
-Therefore, 
-this inequality is equivalent to the following statement: 
+This inequality is therefore equivalent to  
 \begin{align}\label{math:intro:poincarefriedrichs:grad}
@@
     \forall
-    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
+    u \in W^{1,p}(\Omega) 
     .\tag{PF} 
 \end{align}
-Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
+
+In the present setting, where $\Omega$ is connected and the potential of a gradient is thus already determined up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
+
+Finding a norm-minimizing potential of a given gradient $\nabla u$ is generally a nonlinear operation.
+\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
+    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+\end{align}
+\mwl{remove all references to poincare inequality from the introduction. emphasize the difference.}
 The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
-One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
-\begin{align*}
+One very simple example for such a bounded linear operator is the average-free potential: 
+\begin{align}\label{math:intro:poincarefriedrichs:gradientpotential}
     \Phi_{\grad}( \bff ) 
@@
     .
-\end{align*} 
+\end{align} 
 Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
@@
 Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
-
-Most research on optimal constants has addressed the case of convex domains. 
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence
+Computing a linear potential is generally easier than solving the nonlinear minimization problem~\eqref{math:intro:poincarefriedrichs:gradientpotential}. 
+%
+We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
 
@@
 \end{align}
-For a vector-valued field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
+For a vector field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
 Then,
@@
 
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
-Most research on optimal constants has addressed the case of convex domains.
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
 \cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
@@
 
-\subsection{Conceptual overview: curl, divergence, exterior derivative}
+\subsection{Conceptual overview: curl, divergence}
 
@@
 This sharply contrasts to the study of the gradient operator.
-We can access some estimates from the literature in the formalism of exterior calculus. 
-We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
-who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
-thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
-By duality, that implies lower bounds for the case of full boundary conditions.
 
@@
 This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
-\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $w \in W^{p}\Alt^{k}(\Omega)$, there exists $u \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
+\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
 \begin{align} \label{math:PF_DF} 
@@
 \end{align} 
-}\mwl{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparison with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
-
-In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
-\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
-
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
-\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
-Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-
+}
 \mwl{What is the best place for this paragraph?}
@@
 
+We review the literature on Poincar\'e--Friedrichs inequalities and identify the approaches that we want to generalize.
+
 \cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
@@
 \\
+
+In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
+\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
+
+Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
+\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
+Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+
+Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
+Most research on optimal constants has addressed the case of convex domains.
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+When the domain is not convex but star-shaped with respect to a ball,
+then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
+Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}.
 
@@
 In particular, local stars in 2D and 3D triangulations are shellable.
-\\
 
@@
 	Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Let $T_0, T_1, \dots, T_M$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
     there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$
@@
 	\begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
     \end{gather*}
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
-    Let $\Omega \subseteq \bbR^{n}$ be a domain with an $n$-dimensional shellable triangulation $\calT$. % CAUTION 
-    Let $T_0, T_1, \dots, T_M$ be a shelling.
-    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
+	Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
     there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
@@
 
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
+    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Let $1 \leq p \leq \infty$ and $\bfu \in \bfW^{p}(\Omega,\curl)$.
+    \begin{itemize}
+        \item 
+        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
+        and such that the following estimates hold:
+        \begin{gather*}
+            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}.
+        \end{gather*}
+        and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
+        \begin{align*}
+            \| \bfw \|_{L^{p}(T_{m})}
+            &
+            \leq  
+            C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
+            \left( 
+                \| \curl u      \|_{L^{p}(T_{m})} 
+                +
+                \Cfive{n}{1}(\calT)
+                \Cfiveprime{n}{1}(\calT)^{1} 
+                \Cdetsechs{n}{1}(\calT)^{\frac 1 p} 
+                \| \curl u \|_{L^{p}(\Makoto_{m-1})}
+            \right)
+            \\&\qquad
+            + 
+            \Cfive{n}{1}(\calT) 
+            \Cdetsechs{n}{1}(\calT)^{\frac 1 p} 
+            \| \bfw \|_{L^{p}(\Makoto_{m-1})}
+            .
+        \end{align*}
+        \item 
+        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
+        such that 
+        \begin{align*}
+            \| \bfw \|_{L^{p}(T_{m})}
+            \leq 
+            \left( 
+            \Cacht{n}{1}(\calT)
+            \Cachtprime{n}{1}(\calT) 
+            \Cdetsieb{n}{1}(\calT)^{\frac 1 p} 
+            \Csieb{n}{1}(\calT)
+            \Cdetacht{n}{1}(\calT)^{\frac 1 p} 
+            \right)^{M}
+            C_{{\PF},1,T_{0},p}
+            \| \curl \bfu \|_{L^{p}(\Omega)}
+            .
+        \end{align*}
+    \end{itemize}
+\end{theorem}
+
 \section{Numerical examples}\label{section:numericalexamples}

### 2024-10-07 main.tex
bugfix

@@
     This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
-    {We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
+    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
     Computational examples illustrate the theoretical findings.
@@
 \end{align}
-
-In the present setting, where $\Omega$ is connected and the potential of a gradient is thus already determined up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
+In the present setting, where $\Omega$ is connected and the potential of a gradient is thus already determined up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem.
 
 Finding a norm-minimizing potential of a given gradient $\nabla u$ is generally a nonlinear operation.
-\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
+\begin{align}\label{math:pot_grad_def}
     \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
@@
 %
-We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
+We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.
 
@@
 %
-\begin{subequations}\label{math:pot_grad}\begin{align}\label{math:pot_grad_def}
+\begin{align}\label{math:pot_grad_def}
     \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
@@
 %
-Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
-
-\cye{We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the {\em operator norm}
+Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem.
+
+We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the \emph{operator norm}
 \begin{align}\label{math:pot_grad_norm}
@@
     \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
-\end{align}\end{subequations}}
+\end{align}
 This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
-\begin{subequations}\label{math:PF_gradient}\begin{align} \label{math:PF_gradient_1}
+\begin{align} \label{math:PF_gradient_1}
     \| u \|_{L^{p}(\Omega)}
@@
     .
-\end{align}\end{subequations}
+\end{align}
 We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
@@
 Consider the vector-valued spaces
-\begin{subequations}\label{equation:W_curl_div_p} \begin{align}
+\begin{align}\label{equation:W_curl_div_p} 
     \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
@@
     .
-\end{align}\end{subequations}
+\end{align}
 The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
@@
 We are interested in constants for inequalities such as 
-\begin{subequations}\label{math:pot_PF_curl_div} \begin{align}
+\begin{align}\label{math:pot_PF_curl_div}
     \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
@@
     ,
-\end{align}\end{subequations}
+\end{align}
 and how these constants can be estimated by the operator norms of {\em linear} potential operators 

### 2024-10-07 intro.tex
part of introduction: conceptual overview

@@
 Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant\cye{, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem}.
+
+\subsection{Conceptual overview: Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality} \label{subsection:intro_grad}
+
+Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be a bounded connected open set.
+Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
+Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
+
+Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
+\begin{align} \label{equation:W1p}
+    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
+\end{align}
+For a vector field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} \emph{potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
+Then,
+%
+\begin{align*}
+    \Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
+\end{align*}
+is the \emph{potential operator}. A particular example of our interest is
+%
+\begin{align}\label{math:pot_grad_def}
+    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+\end{align}
+%
+Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem.
+
+We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the \emph{operator norm}
+\begin{align}\label{math:pot_grad_norm}
+    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
+\end{align}
+This operator norm is indeed finite and it equivalently turns out to be the best constant in the \emph{Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
+\begin{align} \label{math:PF_gradient_1}
+    \| u \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p} 
+    \| \bff \|_{\fooL^{p}(\Omega)}.
+\end{align}
+Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
+\begin{align} \label{math:PF_gradient_2}
+    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
+    \leq 
+    C_{\grad,\Omega,p}
+    \| \nabla u \|_{\fooL^{p}(\Omega)},
+    \quad 
+    \forall 
+    u \in W^{1,p}(\Omega)
+    .
+\end{align}
+We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
+\begin{align} \label{math:pot_PF_grad}
+    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
+    \| u \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\grad,\Omega,p}
+    \| \bff \|_{\fooL^{p}(\Omega)}.
+\end{align}
+for all $\bff \in \nabla W^{1,p}(\Omega)$.}
+
+\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
+
+\subsection{Conceptual overview: Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities} \label{section:intro_curl_div}
+
+Consider the vector-valued spaces
+\begin{align}\label{equation:W_curl_div_p} 
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in L^{p}(\Omega)^{3} \cye{\suchthat} \curl \bfu \in L^{p}(\Omega)^{3} \right\}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in L^{p}(\Omega)^{3} \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
+    .
+\end{align}
+The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
+This only requires that certain sums of distributional partial derivatives are integrable, 
+and hence these spaces are not classical Sobolev spaces of vector  fields.
+
+\cye{Let a vector field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
+We are interested in constants for inequalities such as 
+\begin{align}\label{math:pot_PF_curl_div}
+    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
+    \| \bfu \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\curl,\Omega,p}
+    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
+    ,
+    \\
+    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfu = f } } 
+    \| \bfu \|_{L^{p}(\Omega)}
+    &\leq 
+    C_{\divergence,\Omega,p}
+    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
+    ,
+\end{align}
+and how these constants can be estimated by the operator norms of \emph{linear} potential operators 
+\begin{align*}
+    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \\
+    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
+\end{align*}
+The fundamental difference \cye{with respect to Section~\ref{subsection:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
+In Section~\ref{subsection:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
+It is thus trivially complemented for all $p$, with a canonical choice of projection.
+By contrast, in the Banach space case $p \neq 2$, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
+\cye{Actually,} the existence of a bounded linear potential operator here is a non-trivial fact even in the Hilbert space case $p = 2$.
+
+\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
+Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
+\begin{align}
+    \label{math:Weber}
+    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
+\end{align}
+for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
+Yet another writing is 
+\label{math:PF_orth} \begin{align}
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
+\end{align}
+for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
+We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
+However, that easy observation seems restricted to $p=2$.
+
+Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
+\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}

### 2024-10-07 main.tex
part of introduction: conceptual overview

@@
 
-\subsection{Conceptual overview: gradient}
+\subsection{Conceptual overview}
 
 We give a conceptual overview of the topic before we outline the known results in the literature and our contributions in more detail. 
-Our conceptual point of reference is the Poincar\'e--Friedrichs inequality for the gradient of scalar functions.
-
-Let $\Omega \subseteq \bbR^n$ be a bounded connected open set.
-Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields, and $W^{1,p}(\Omega)$ denotes the first-order Sobolev space over $\Omega$ with integrability exponent $p$.
-
-We search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
-for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
+Our conceptual point of reference is the Poincar\'e--Friedrichs inequality for the gradient of scalar functions, 
+which has been subject to extensive research.
+\\
+
+For this illustration, we le $\Omega \subseteq \bbR^3$ be a bounded connected open set. 
+We let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $1 \leq p \leq \infty$, 
+and we write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$. 
+% we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields,
+
+We are interested in a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
+for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ 
+there exists a scalar potential $u \in W^{1,p}(\Omega)$
 such that $\nabla u = \bff$ and 
@@
 We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
-The different scalar potentials only differ by a constant. 
+The question is therefore whether we can always find a gradient potential of sufficiently small norm so this inequality holds. 
+One possible choice is the norm-minimizing potential 
+\begin{align}\label{math:pot_grad_def}
+    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+\end{align}
+In the present setting, where $\Omega$ is connected and the potential of the different gradient potentials can thus only differ by a constant, $\Phi_{\grad}( \bff )$ is a one-dimensional convex minimization problem.
 This inequality is therefore equivalent to  
@@
 \end{align}
-In the present setting, where $\Omega$ is connected and the potential of a gradient is thus already determined up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem.
-
-Finding a norm-minimizing potential of a given gradient $\nabla u$ is generally a nonlinear operation.
-\begin{align}\label{math:pot_grad_def}
-    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
+Such an inequality holds if we can bound the \emph{operator norm} of this gradient potential operator, and then the best constant is  
+%the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$.
+%Hence we want to evaluate the \emph{operator norm} of the potential operator 
+\begin{align}\label{math:pot_grad_norm}
+    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
+    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
 \end{align}
-\mwl{remove all references to poincare inequality from the introduction. emphasize the difference.}
-The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-One very simple example for such a bounded linear operator is the average-free potential: 
+Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally difficult. 
+Attention has been given to \emph{linear} potential operators
+Computing a linear potential is generally easier than solving the nonlinear minimization problem~\eqref{math:intro:poincarefriedrichs:gradientpotential}. 
+The operator norm of any linear potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
+One very simple example for such a bounded linear potential operator is the average-free potential, 
 \begin{align}\label{math:intro:poincarefriedrichs:gradientpotential}
-    \Phi_{\grad}( \bff ) 
+    \Phi_{\varnothing}( \bff ) 
     := 
@@
     \bff \in \nabla W^{1,p}(\Omega)
-    .
+    ,
 \end{align} 
-Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the Poincar\'e inequality 
+where the mean value of $u$ is fixed to zero. 
+Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the \emph{Poincar\'e inequality} 
 \begin{align}\label{math:intro:poincare:grad}
@@
 \end{align}
-where $u_\Omega$ denotes the average of $u$.
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
-Computing a linear potential is generally easier than solving the nonlinear minimization problem~\eqref{math:intro:poincarefriedrichs:gradientpotential}. 
-%
-We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.
-
-\subsection{Conceptual overview: Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality} \label{subsection:intro_grad}
-
-Let $\Omega \subseteq \bbR^n$, $n \geq 1$, be a bounded connected open set.
-Given any $1 \leq p \leq \infty$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$.
-Then $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ is the corresponding Lebesgue space of vector  fields.
-
-Let $W^{1,p}(\Omega)$ denote the first-order Sobolev space over $\Omega$ with integrability exponent $p$, 
-\begin{align} \label{equation:W1p}
-    W^{1,p}(\Omega) := \left\{u \in L^{p}(\Omega) \cye{\suchthat} \nabla u \in \bfL^{p}(\Omega) \right\}.
+where $u_\Omega$ denotes the average of $u$. We emphasize that the average-free potential is generally not the norm-minimizing potential unless $p = 2$.
+In particular, the Poincar\'e inequality and the Poincar\'e--Friedrichs inequality generally hold with different constants.  
+Considerable research effort has gone into computing (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
+Upper estimates for these constants also correspond to lower bounds for the spectra of Neumann--Laplacians over those domains.
+The relationship between the Poincar\'e constant and the Poincar\'e--Friedrichs constant will be elaborated upon in later sections of this manuscript. 
+% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.
+\\
+
+We study potential operators and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
+There are substantial changes and much less results are available in the literature. 
+We use the spaces of vector field 
+\begin{align}
+    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in L^{p}(\Omega)^{3} : \curl \bfu \in L^{p}(\Omega)^{3} \right\}
+	\eqref{math:pot_PF_curl}
+    ,
+    \\
+    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in L^{p}(\Omega)^{3} : \divergence \bfu \in L^{p}(\Omega) \right\}
+	\eqref{math:pot_PF_div}
+    .
 \end{align}
-For a vector field $\bff$ that is a distributional gradient of an object from $W^{1,p}(\Omega)$, $\bff \in \nabla W^{1,p}(\Omega)$, we are \cye{interested in} {\em potentials}, i.e., scalar-valued functions $\Phi_{\grad}( \bff ) \in W^{1,p}(\Omega)$ such that $\nabla \Phi_{\grad}( \bff ) = \bff$.
-Then,
-%
-\begin{align*}
-    \Phi_{\grad} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)
-\end{align*}
-is the {\em potential operator}. A particular example of our interest is
-%
-\begin{align}\label{math:pot_grad_def}
-    \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
-\end{align}
-%
-Actually, in the present gradient setting and since $\Omega$ is connected, already the gradient constraint determines $\Phi_{\grad}( \bff )$ up to a constant, so that~\eqref{math:pot_grad_def} is a one-dimensional minimization problem.
-
-We want to see whether the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$, i.e., we want to evaluate the \emph{operator norm}
-\begin{align}\label{math:pot_grad_norm}
-    C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
-    \frac{ \| \Phi_{\grad}(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{\fooL^{p}(\Omega)} }.
-\end{align}
-This operator norm is indeed finite and it equivalently turns out to be the best constant in the {\em Poincar\'e--Friedrichs inequality}: for every vector field $\bff \in \nabla W^{1,p}(\Omega)$, there exists $u \in W^{1,p}(\Omega)$ such that $\nabla u = \bff$ and
-\begin{align} \label{math:PF_gradient_1}
-    \| u \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p} 
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-Actually, \eqref{math:PF_gradient_1} is further equivalent to the more conventional writing
-\begin{align} \label{math:PF_gradient_2}
-    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
-    \leq 
-    C_{\grad,\Omega,p}
-    \| \nabla u \|_{\fooL^{p}(\Omega)},
-    \quad 
-    \forall 
-    u \in W^{1,p}(\Omega)
-    .
-\end{align}
-We call $C_{\grad,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} for the gradient operator with exponent $p$. \cye{A concise writing of all~\eqref{math:pot_grad}--\eqref{math:PF_gradient} is
-\begin{align} \label{math:pot_PF_grad}
-    \min\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } 
-    \| u \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\grad,\Omega,p}
-    \| \bff \|_{\fooL^{p}(\Omega)}.
-\end{align}
-for all $\bff \in \nabla W^{1,p}(\Omega)$.}
-
-\cye{We present a more profound discussion below in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.}
-
-\subsection{Conceptual overview: Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities} \label{section:intro_curl_div}
-
-Consider the vector-valued spaces
-\begin{align}\label{equation:W_curl_div_p} 
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) \cye{\suchthat} \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align}
-The members of these spaces are those vector fields whose distributional curls and divergences are \cye{respectively} in \cye{the} Lebesgue spaces \cye{$\bfL^{p}$ or $L^{p}(\Omega)$}.  
-This only requires that certain sums of distributional partial derivatives are integrable, 
-and hence these spaces are not classical Sobolev spaces of vector  fields.
-
-\cye{Let a vector field $\bff$ that is a distributional curl of an object from $\bfW^{p}(\curl,\Omega)$, $\bff \in \curl \bfW^{p}(\curl,\Omega)$, and scalar-valued field $f$ that is a distributional divergence of an object from $\bfW^{p}(\divergence,\Omega)$, $f \in \divergence \bfW^{p}(\divergence,\Omega)$, be given.}
-We are interested in constants for inequalities such as 
-\begin{align}\label{math:pot_PF_curl_div}
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\curl,\Omega) \\ \curl \bfu = \bff } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\curl,\Omega,p}
-    \| \bff \|_{L^{p}(\Omega)} \label{math:pot_PF_curl}
-    ,
-    \\
-    \min\limits_{ \substack{ \bfu \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfu = f } } 
-    \| \bfu \|_{L^{p}(\Omega)}
-    &\leq 
-    C_{\divergence,\Omega,p}
-    \| f \|_{L^{p}(\Omega)} \label{math:pot_PF_div}
-    ,
-\end{align}
-and how these constants can be estimated by the operator norms of {\em linear} potential operators 
-\begin{align*}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
-\end{align*}
-The fundamental difference \cye{with respect to Section~\ref{subsection:intro_grad}} is that the curl and divergence have infinite-dimensional kernels.
-In Section~\ref{subsection:intro_grad}, the kernel of the gradient is the one-dimensional space of constant functions.
-It is thus trivially complemented for all $p$, with a canonical choice of projection.
-By contrast, in the Banach space case $p \neq 2$, it is not immediately evident that the kernels of the curl and divergence operators are complemented, and a canonical projection only exists here in the Hilbert setting $p=2$.
-\cye{Actually,} the existence of a bounded linear potential operator here is a non-trivial fact even in the Hilbert space case $p = 2$.
-
-\cye{Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$.
-Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
-\begin{align}
-    \label{math:Weber}
-    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
-\end{align}
-for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
-Yet another writing is 
-\label{math:PF_orth} \begin{align}
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, \label{math:PF_orth_curl}\\
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)} \label{math:PF_orth_div}
-\end{align}
-for respectively all functions $\bfu$ from $\bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$ and all functions $\bfu$ from $\bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv$ from $\bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
-Still} in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with \cye{homogeneous} Dirichlet boundary conditions \cye{on $\partial \Omega$} implies, via duality~\eqref{math:pot_PF_div}.
-However, that easy observation seems restricted to $p=2$.
-
-Not much attention\cye{, however,} seems to have been given to the study of \cye{computable} constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex.
-\cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
-
-\subsection{Conceptual overview: curl, divergence}
-
-The situation is less clear cut when we study the curl or divergence operators in vector calculus.
-We use the vector field spaces
-\begin{align*}
-    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
-    ,
-    \\
-    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
-    .
-\end{align*}
-Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
-This only requires that certain sums of distributional partial derivatives are integrable, 
+Their members are those vector fields in Lebesgue spaces whose distributional curls and divergences, respectively, are in Lebesgue spaces. 
+In contrast to the gradient, this only requires that certain sums of distributional partial derivatives are integrable, 
 and hence these spaces are not classical Sobolev spaces of vector fields. 
@@
 \begin{align*}
-    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
+    \curl : \bfW^{p}(\curl,\Omega) \rightarrow L^{p}(\Omega)^{3},
     \qquad 
@@
 \end{align*}
-The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
-In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
-The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
 We are interested in constants for inequalities such as 
@@
 \end{align*}
-and how these constants can be estimated by the operator norms of linear potential operators 
+The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
+The kernel of the gradient is the one-dimensional space of constant functions, and it is thus trivially complemented for all $p$, with a canonical choice of projection. 
+By contrast, the kernels of the curl and divergence operators are generally infinite-dimensional. 
+Moreover, it is not immediately evident that the kernels of the curl and divergence operators are complemented in the Banach space case when $p \neq 2$, 
+and a canonical projection only exists here in the Hilbert setting $p=2$.
+
+In the Banach space case, it is not even trivial whether a norm-minimizing potential actually exists. 
+Our interest are linear potential operators 
 \begin{align*}
@@
 \end{align*}
-
-Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
-This sharply contrasts to the study of the gradient operator.
-
-\subsection{Conceptual overview: Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities} \label{section:intro_EC}
-
+and their operator norms. We remark that upper bounds for the Poincar\'e--Friedrichs inequality of the curl operator correspond to lower bounds for the so-called Maxwell eigenvalues. 
+In sharp contrast to the extensive research on gradient potentials, 
+not much attention seems to have been given to the study of computable constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
+\\
+
+Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus. 
 Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
-This formalism is independent of the \cye{space} dimension and highlights \cye{extends the} underlying geometric structures common to the gradient, curl, and divergence operators \cye{in three space dimensions}.
-\cye{In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: for every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is in detail fixed in Section~\ref{section:calculus} below)
+This formalism is independent of the spatial dimension and highlights extends the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
+% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}:
+for every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
 \begin{align} \label{math:PF_DF} 
-    \| u \|_{L^{p}(\Omega} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
+    \| u \|_{L^{p}(\Omega)} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
 \end{align} 
-}
-\mwl{What is the best place for this paragraph?}
-Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}.
-Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}.
-Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields.
-The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis.
-\\
+
+\subsection{Literature review}
+
+We review the literature on Poincar\'e--Friedrichs inequalities and identify the approaches that we want to generalize.
 
@@
 
-We review the literature on Poincar\'e--Friedrichs inequalities and identify the approaches that we want to generalize.
+Not much attention however seems to have been given to the study of computable constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex. 
+Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of the exterior calculus formalism, 
+but the Banach case $p \neq 2$ seems largely unexplored.
 
@@
 \\
+
+\subsection{General results}
+
+Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$. 
+Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
+\begin{align}
+    \label{math:Weber}
+    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
+\end{align}
+for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
+Yet another writing is 
+\label{math:PF_orth} \begin{align}
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, 
+	\label{math:PF_orth_curl}
+	\\
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)}, 
+	\label{math:PF_orth_div}
+\end{align}
+    where the former holds for all vector fields $\bfu \in \bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$,
+and where the latter holds for all functions $\bfu \in \bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
+We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+Still in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with homogeneous Dirichlet boundary conditions on $\partial \Omega$ implies, via duality~\eqref{math:pot_PF_div}.
+However, that easy observation seems restricted to $p=2$.
 

### 2024-10-07 intro.tex
conceptual overview

@@
 \cye{Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of} the exterior calculus formalism\cye{, but the Banach case $p \neq 2$ seems largely unexplored.}
+
+In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+
+There is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known.
+
+The literature is less extensive it comes to the estimates for the curl and divergence potentials.
+
+A conceptual approach to obtain computable estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of
+regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
+
+When the domain is star-shaped with respect to a ball, 
+then estimates for the Poincar\'e--Friedrichs constants 
+follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
+as mappings between Lebesgue spaces. 
+We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
+but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+\\
+
+\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are. 
+However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
+This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, 
+which contain finite element patches are not star-shaped with respect to any ball.
+
+One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball.

### 2024-10-07 main.tex
conceptual overview

@@
 \\
+
+\subsection{Potentials and Poincar\'e--Friedrichs inequalities for the gradient}
 
@@
 
+\subsection{Potentials and Poincar\'e--Friedrichs inequalities for the curl and divergence}
+
 We study potential operators and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
@@
 \\
+
+\subsection{Potentials and Poincar\'e--Friedrichs inequalities for the exterior derivative}
 
@@
 
-We review the literature on Poincar\'e--Friedrichs inequalities and identify the approaches that we want to generalize.
+We review the literature on Poincar\'e--Friedrichs inequalities. We also identify the obstructions of presently known results that we want to overcome with our contributions.
 
 \subsection{Review: Analytical constants over convex domains}
+
+% gradient over convex domains
+Considerable research effort has gone into computing explicit upper estimates for the constants in the Poincar\'e--Friedrichs inequalities over convex domains. 
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal gradient Poincar\'e--Friedrichs and Poincar\'e constants for the entire range of Lebesgue exponent $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+
+% Guerini Savo  
+The literature on Poincar\'e--Friedrichs constants and potentials of curls and divergences is less extensive than for potentials of gradients, even over convex domains.
+Guerini and Savo~\cite{guerini2004eigenvalue} provide explicit lower bounds for the spectrum of the Hodge--Laplace operator on bounded convex domains with smooth boundary in the Hilbert space case $p=2$.
+These bounds are only in terms of the dimension and diameter of the convex domain. 
+They thus give upper estimates for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence in particular for the curl and divergence operators.
+Additionally, a comparison result shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. 
+Using a duality argument, this also gives upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+However, these upper bounds are not necessarily optimal. 
+Moreover, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+
+\subsection{Review: Domains star-shaped with respect to a ball}
+
+When the domain is not convex but star-shaped with respect to a ball,
+then several estimates for Poincar\'e--Friedrichs constants are known. 
+Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
+Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
+We pay particular attention to the regularized Poincar\'e and Bogovski\u{i} potential operators for the exterior derivative,
+such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
+In principle, the operator norms of those potential operators as mapping between Lebesgue spaces of differential forms 
+are upper estimates for the Poincar\'e--Friedrichs constants of the domain. 
+Here, estimates for the higher-order seminorms of these potentials are available in~\cite{guzman2021estimation}, 
+but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+We particularly emphasize that these estimates for domains star-shaped with respect to a ball have in common that they rely on upper bounds for the \emph{eccentricity} of the domain.
+
+% Technical restriction of star-shaped domains
+
+Let us briefly discuss the practical limitations of the aforementioend estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
+Recall that the main objective of this manuscript is bounding these constants over local stars within triangulated domains. 
+Clearly, not all local stars describe convex subdomains, but most local stars are star-shaped with respect to a ball. 
+This observation would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
+However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
+This would not be as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+But the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this occurs most prominently when the domain has sharp reentrant corners.
+Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
+which contain local finite element patches that are not star-shaped with respect to any ball. 
+In view of this, we refrain from treating local patches (stars) in triangulations as domains star-staped with respect to a ball.
+
+\subsection{General results}
 
@@
 but the Banach case $p \neq 2$ seems largely unexplored.
-
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
-Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
-In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
-The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms. 
-\\
-
-When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constants 
-follow from bounds on the operator norms of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
-as mappings between Lebesgue spaces. 
-We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation} (see also~\cite{gallistl2023computational}),
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-\\
-
-In the Hilbert space case $p=2$, Guerini and Savo~\cite{guerini2004eigenvalue} provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence \cye{in particular} for the curl and divergence operators.
-\cye{A comparison result} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also \cye{gives} upper estimate\cye{s} of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
-
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} are known over \cye{(}convex\cye{)} \cye{(}Lipschitz\cye{)} domains and general Lebesgue exponents $1 \leq p \leq \infty$.
-\cye{A conceptual approach to obtain computable} estimates for the Poincar\'e--Friedrichs constants \cye{for any $1 \leq p \leq \infty$} and when the domain is star-shaped with respect to a ball is to bound operator norms of regularized Poincar\'e operators \cye{such as those of} Costabel and McIntosh~\cite{costabel2010bogovskiui} as mappings between Lebesgue spaces.
-Here, estimates for the higher-order seminorms of these potentials \cye{are available in}~\cite{guzman2021estimation}, but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-
-Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:pot_PF_grad}.
-Most research on optimal constants has addressed the case of convex domains.
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-When the domain is not convex but star-shaped with respect to a ball,
-then polynomial interpolation estimates already imply the Poincar\'e\cye{--Friedrichs} inequality~\cite{brenner2008mathematical,ern2021finite}. 
-Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}.
-
-\subsection{Review: Domains star-shaped with respect to a ball}
-
-\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are.
-This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}.
-Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
-This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this \cye{in particular} occurs when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
-which contain local finite element patches \cye{that} are not star-shaped with respect to any ball. 
-\\
-
-The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains. 
-One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
-which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser
-which contain finite element patches are not star-shaped with respect to any ball.
-
-\subsection{Review: Potentials subject to partial boundary conditions}
-
-\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
-We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
-\\
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-\subsection{General results}
 
@@
 \subsection{Objectives: convex domains}
-
-Estimating the norm of local potential operators over convex domains is an important subcomponent of our agenda. 
-Again, the situation is more complicated for potentials of curls and divergences than for potentials of gradients.
-While there is a wealth of literature for gradient Poincar\'e inequalities over convex domains, where optimal gradient Poincar\'e--Friedrichs constants for the entire range $1 \leq p < \infty$ are known,
-the literature is more sparse when it comes to the corresponding estimates for the curl and divergence potentials.
-
-In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
-By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-
-However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
+\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
+Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
+In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
+The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
+
+We rely on regularized potential operators as a remedy. 
 We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 We consider the latter outcome to be of independent interest.
+
+\subsection{Review: Potentials subject to partial boundary conditions}
+
+\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
+\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
+We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
+\\
+
+In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
+Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
+We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
+The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
+we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
+We achieve this by constructing an auxiliary problem subject to full boundary conditions.
+\\
+
+\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
+\cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
 
@@
 The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-
-\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
-\cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
 

### 2024-10-07 main.tex
reordering and clean up

@@
 For example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
-Additionally, the study of regularized Poincar\'e and Bogovski\u{i} operators leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
+Additionally, the study of regularized Poincar\'e and Bogovski\u{\i} operators leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
 
@@
 Additionally, a comparison result shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. 
-Using a duality argument, this also gives upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence \cye{operators} subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+Using a duality argument, this also gives upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
 However, these upper bounds are not necessarily optimal. 
@@
 Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
-We pay particular attention to the regularized Poincar\'e and Bogovski\u{i} potential operators for the exterior derivative,
+We pay particular attention to the regularized Poincar\'e and Bogovski\u{\i} potential operators for the exterior derivative,
 such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
@@
 
-\subsection{General results}
+\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}
+
+\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
+\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
+Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
+\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
+\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
+
+\subsection{Review: Triangulated domains}
+
+Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
+However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
+We review some of the main outcomes.
+
+Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
+Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
+
+The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
+starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
+That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface.
+
+We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
+which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
+However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
+We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
+
+\subsection{Review: Combinatorial constants over face-connected triangulated domains}
+
+Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
+For scalar-valued functions in the context of Section~\ref{subsection:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
+%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
+Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
+
+In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+\subsection{Review: General results}
 
@@
 
+\subsection{Objectives and methodology}
+
+The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
+\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
+
 \subsection{Objectives: convex domains}
@@
 
-\subsection{Review: Potentials subject to partial boundary conditions}
+\subsection{Objectives: Potentials subject to partial boundary conditions}
 
@@
 \cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
-
-\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}
-
-\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
-\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
-Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
-\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
-\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
-
-\subsection{Objectives and methodology}
-
-The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
-\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
-
-\subsection{Combinatorial constants over face-connected triangulated domains}
-
-Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
-For scalar-valued functions in the context of Section~\ref{subsection:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
-%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
-Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
-
-In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-\subsection{Combinatorial constants over shellable triangulated domains}
+\mwl{Of course, the eccentricity enters the estimate.}
+
+\subsection{Objective: Main results}
+
+\cye{We treat specifically the gradient operator (the setting of Section~\ref{subsection:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
+Here, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} is our main results.}
+\mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
+The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
+\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
+
+\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
+As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
+The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+
+\subsection{Objective: General}
+
+While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
+we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars.
+
+In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
+via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$.
+
+\subsection{Objective: sequential approach} 
+Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
+Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
+\\
+
+We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
+The basic inductive strategy remains the same.
+We start by constructing, say, a curl potential, over a single simplex.
+Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
+However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
+% 
+To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
+We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
+Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+\\
+
+\subsection{Objective: shellable triangulations}
+Shellable triangulations are defined by a special constructive property:
+we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D triangulations are shellable.
+
+\subsection{Objective: Combinatorial constants over shellable triangulated domains}
 
@@
 With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
-
-\subsection{Main results}
-
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{subsection:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} is our main results.}
-\mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
-The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
-\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
-
-\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
-As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-
-\subsection{Review: Triangulated domains}
-
-Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
-However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
-We review some of the main outcomes. 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-
-The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
-The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
-Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the interfacing intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed to ensure continuity across that interface.
-
-While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
-we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars. 
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$. 
-We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
-which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
-We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
-
-\subsection{Objective: sequential approach} 
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-\\
-
-\subsection{Objective: shellable triangulations}
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable.
 
@@
 
-    The bounds for the Bogovski\u{i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
+    The bounds for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
     the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
@@
 We first assess the constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-which relies on estimates for the Bogovski\u{i} operator over an auxiliary reference domain.
+which relies on estimates for the Bogovski\u{\i} operator over an auxiliary reference domain.
 Our experiments over triangles and tetrahedra indicate that we overestimate the constant by several magnitudes.
@@
 We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized Poincar\'e operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently employ.
-Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{i} operators.
+Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{\i} operators.
 

### 2024-10-07 main.tex
spellcheck

@@
 
-For this illustration, we le $\Omega \subseteq \bbR^3$ be a bounded connected open set. 
+For this illustration, we let $\Omega \subseteq \bbR^3$ be a bounded connected open set. 
 We let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $1 \leq p \leq \infty$, 
@@
 
-Let us briefly discuss the practical limitations of the aforementioend estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
+Let us briefly discuss the practical limitations of the aforementioned estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
 Recall that the main objective of this manuscript is bounding these constants over local stars within triangulated domains. 
@@
 which contain local finite element patches that are not star-shaped with respect to any ball. 
-In view of this, we refrain from treating local patches (stars) in triangulations as domains star-staped with respect to a ball.
+In view of this, we refrain from treating local patches (stars) in triangulations as domains star-shaped with respect to a ball.
 
@@
 \end{align*}
-For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+For the Bogovski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
 leading to 

### 2024-10-07 intro.tex
review of literature

@@
 One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball.
+
+\subsection{Review: Triangulated domains}
+
+% Intro DONE
+Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
+However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
+We review some of the main outcomes.
+
+% veeser and verfurth ... unknown DONE 
+Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
+Naturally, their estimates depend on the shape regularity of the mesh.
+
+% sequential approach 
+The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
+starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
+That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface.
+
+% sequential approach DONE
+Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
+For scalar-valued functions in the context of Section~\ref{subsection:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
+%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
+Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
+
+% eigenvalue and maxwell
+We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
+which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
+However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
+We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
+
+\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}
+
+Estimates for Laplacian eigenvalues over triangulated domains have received much attention. 
+The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$. 
+Similarly, the constant in~\eqref{math:pot_PF_curl} for $p=2$ corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$. 
+Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians and vice versa. 
+Prominent methods numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants upon solving a finite element system over a sufficiently fine triangulation and using some clever post-processing estimates.
+This technique is used for estimating scalar Laplacian eigenvalues~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} and vector Laplacian eigenvalues~\cite{gallistl2023computational}. 
+We remark that we wish to avoid the solution of (global) finite element systems in our computations. 
+% Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.

### 2024-10-07 main.tex
review of literature

@@
 
-\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}
-
-\cye{The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.} 
-\cye{Similarly, t}he constant \cye{in~\eqref{math:pot_PF_curl} for $p=2$} corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$.
-Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians \cye{and vice versa}. 
-\cye{This eigenvalues optics, upon employing a suitable numerical simulation} over a general triangulation \cye{and some clever post-processing estimates, enables to numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants, see~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} for~\eqref{math:pot_PF_grad} and~\cite{gallistl2023computational} for \eqref{math:pot_PF_curl}}.
-\cye{Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.}
-
 \subsection{Review: Triangulated domains}
 
-Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
-However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
+Geometric settings that admit finite triangulations offer further pathways to obtain Poincar\'e--Friedrichs inequalities. 
 We review some of the main outcomes.
 
-Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}.
-Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.
-
-The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step:
-starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
-That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
+Computable estimates for Laplacian eigenvalues over triangulated domains have received much attention. 
+The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$. 
+Similarly, the constant in~\eqref{math:pot_PF_curl} for $p=2$ corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$. 
+Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians and vice versa. 
+Prominent methods numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants upon solving a finite element system over a sufficiently fine triangulation and using some clever post-processing estimates.
+This has led to estimates for scalar Laplacian eigenvalues~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} and vector Laplacian eigenvalues~\cite{gallistl2023computational}. 
+We remark that for the purposes of this manuscript, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems. 
+% Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.
+
+% veeser and verfurth 
+% sequential methodology
+There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices. 
+Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
+Naturally, their estimates depend on the shape regularity of the mesh.
+Another class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
+% Starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
 The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
@@
 and that difference can easily be removed to ensure continuity across that interface. 
-
-We also remark that recent work~\cite{gallistl2023computational} addresses eigenvalues for the curl--curl operator over general triangulations,
-which gives rise to an estimate for the Poincar\'e--Friedrichs constant when $p=2$.
-However, the use case of these estimates are sequences of triangulations after sufficiently many levels of refinement, whereas our main application are estimates that work with fixed but small triangulations, such as local stars.
-We are not aware of any estimates for the curl operator, even in the Hilbert space situation.
-
-\subsection{Review: Combinatorial constants over face-connected triangulated domains}
-
-Domains that admit finite triangulations allow for techniques \cye{using some form of passing through the triangulation and construction of the potentials step-by-step}.
-For scalar-valued functions in the context of Section~\ref{subsection:intro_grad}, Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for \cye{vertex} stars.
-%Naturally, these estimates deteriorates when the shape regularity of the mesh deteriorates. 
-Such approaches were also previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-Triangle by triangle, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.
-
-In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
+The method is known in the finite element literature~\cite{ern2021finite}.
+It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+This sequential procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
+Importantly, these sequential estimates of Poincar\'e--Friedrichs constants generally circumvent the effect of low boundary regularity and only rely on the shape regularity.
 
@@
 \subsection{Objective: Main results}
+
+In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
 

### 2024-10-07 main.tex
some work on weber

@@
 Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance. 
-The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
-which quantify the fundamental stability features of a variety of partial differential equations. 
-Estimates for the Poincar\'e--Friedrichs constants also enter the stability and convergence theory of numerical methods. 
-Computable upper bounds of the Poincar\'e--Friedrichs constants also provide computable lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
+The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants.
+These quantify the fundamental stability properties of partial differential equations
+and enter the stability and convergence theory of numerical methods. 
+Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
 However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
@@
 
-This manuscript aims to fill this gap. How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
-We apply the construction principle to the curl and divergence operators, as well as the exterior derivative. 
+This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrich inequalities for the differential operators of vector calculus. 
+How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
+We apply this construction principle to the curl and divergence operators, as well as the exterior derivative. 
 However, to proceed in the general exterior derivative case, we restrict our efforts to so-called shellable triangulations. 
 Only contractible domains can ever admit a shellable triangulation, but having computable upper bounds for such domains is an important stepping stone towards more general situations. 
-The class of shellable of shellable triangulations includes practically relevant triangulations. 
-For example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
-Additionally, the study of regularized Poincar\'e and Bogovski\u{\i} operators leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
+The class of shellable triangulations includes practically relevant triangulations: 
+for example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
+Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
 
@@
 
-\subsection{Potentials and Poincar\'e--Friedrichs inequalities for the gradient}
+\subsubsection{Potentials and Poincar\'e--Friedrichs inequalities for the gradient}
 
@@
 One possible choice is the norm-minimizing potential 
-\begin{align}\label{math:pot_grad_def}
+\begin{align}\label{math:intro:gradientpotential}
     \Phi_{\grad}( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)}.
 \end{align}
-In the present setting, where $\Omega$ is connected and the potential of the different gradient potentials can thus only differ by a constant, $\Phi_{\grad}( \bff )$ is a one-dimensional convex minimization problem.
+In the present setting, where $\Omega$ is connected and the potential of the different gradient potentials can thus only differ by a constant, computing $\Phi_{\grad}( \bff )$ is a one-dimensional convex minimization problem.
 This inequality is therefore equivalent to  
@@
 %Hence we want to evaluate the \emph{operator norm} of the potential operator 
-\begin{align}\label{math:pot_grad_norm}
+\begin{align}\label{math:intro:gradient:potentialnorm}
     C_{\grad,\Omega,p} := \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
@@
 Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally difficult. 
-Attention has been given to \emph{linear} potential operators
-Computing a linear potential is generally easier than solving the nonlinear minimization problem~\eqref{math:intro:poincarefriedrichs:gradientpotential}. 
+Attention has been given to \emph{linear} potential operators instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}. 
 The operator norm of any linear potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
 One very simple example for such a bounded linear potential operator is the average-free potential, 
-\begin{align}\label{math:intro:poincarefriedrichs:gradientpotential}
+\begin{align}\label{math:intro:poincarepotential}
     \Phi_{\varnothing}( \bff ) 
@@
 where the mean value of $u$ is fixed to zero. 
-Its operator norm is the constant $C_{\varnothing,\Omega,p} > 0$ in the \emph{Poincar\'e inequality} 
+Its operator norm is the Poincar\'e constant $C_{\varnothing,\Omega,p} > 0$ that satisfies % for the \emph{Poincar\'e inequality} 
 \begin{align}\label{math:intro:poincare:grad}
@@
 where $u_\Omega$ denotes the average of $u$. We emphasize that the average-free potential is generally not the norm-minimizing potential unless $p = 2$.
-In particular, the Poincar\'e inequality and the Poincar\'e--Friedrichs inequality generally hold with different constants.  
-Considerable research effort has gone into computing (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
+Hence the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs differ in general. 
+Considerable research efforts have gone into determining constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
 Upper estimates for these constants also correspond to lower bounds for the spectra of Neumann--Laplacians over those domains.
 The relationship between the Poincar\'e constant and the Poincar\'e--Friedrichs constant will be elaborated upon in later sections of this manuscript. 
-% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:pot_grad_def}.
-\\
-
-\subsection{Potentials and Poincar\'e--Friedrichs inequalities for the curl and divergence}
+% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:intro:gradientpotential}.
+\\
+
+\subsubsection{Potentials and Poincar\'e--Friedrichs inequalities for the curl and divergence}
 
@@
     \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in L^{p}(\Omega)^{3} : \curl \bfu \in L^{p}(\Omega)^{3} \right\}
-	\eqref{math:pot_PF_curl}
+	\label{math:intro:Wcurl}
     ,
@@
     \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in L^{p}(\Omega)^{3} : \divergence \bfu \in L^{p}(\Omega) \right\}
-	\eqref{math:pot_PF_div}
+	\label{math:intro:Wdiv}
     .
@@
 \end{align*}
-We are interested in constants for inequalities such as 
-\begin{align*}
+We are interested in the natural analogues for the Poincar\'e--Friedrichs inequality of the gradient~\eqref{math:intro:poincarefriedrichs:grad},
+which for the curl and divergence are the inequalities 
+\begin{align}
     \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
@@
     \| \bff \|_{L^{p}(\Omega)}
+    \label{math:intro:Wcurl:pf}
     ,
@@
     \| f \|_{L^{p}(\Omega)}
-    ,
-\end{align*}
+    \label{math:intro:Wdiv:pf}
+    .
+\end{align}
 The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
@@
 and a canonical projection only exists here in the Hilbert setting $p=2$. 
+In that sense, there generally is no natural analogue to the Poincar\'e inequality~\eqref{math:intro:poincare:grad} for the curl and divergence.
 
 In the Banach space case, it is not even trivial whether a norm-minimizing potential actually exists. 
-Our interest are linear potential operators 
-\begin{align*}
+We are therefore interested in any potential operators 
+\begin{align}
     &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
@@
     .
-\end{align*}
+\end{align}
 and their operator norms. We remark that upper bounds for the Poincar\'e--Friedrichs inequality of the curl operator correspond to lower bounds for the so-called Maxwell eigenvalues. 
@@
 
-\subsection{Potentials and Poincar\'e--Friedrichs inequalities for the exterior derivative}
+\subsubsection{Potentials and Poincar\'e--Friedrichs inequalities for the exterior derivative}
 
@@
 for every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
-\begin{align} \label{math:PF_DF} 
+\begin{align} \label{math:intro:exterior:pf} 
     \| u \|_{L^{p}(\Omega)} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
@@
 
-We review the literature on Poincar\'e--Friedrichs inequalities. We also identify the obstructions of presently known results that we want to overcome with our contributions.
-
-\subsection{Review: Analytical constants over convex domains}
+We review the literature on Poincar\'e--Friedrichs inequalities. We also identify the obstructions inherent to presently known results that we wish to overcome with our contributions.
+
+\subsubsection{Review: Analytical constants over convex domains}
 
@@
 The literature on Poincar\'e--Friedrichs constants and potentials of curls and divergences is less extensive than for potentials of gradients, even over convex domains.
-Guerini and Savo~\cite{guerini2004eigenvalue} provide explicit lower bounds for the spectrum of the Hodge--Laplace operator on bounded convex domains with smooth boundary in the Hilbert space case $p=2$.
-These bounds are only in terms of the dimension and diameter of the convex domain. 
-They thus give upper estimates for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence in particular for the curl and divergence operators.
-Additionally, a comparison result shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. 
-Using a duality argument, this also gives upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-However, these upper bounds are not necessarily optimal. 
-Moreover, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
-
-\subsection{Review: Domains star-shaped with respect to a ball}
+Guerini and Savo~\cite{guerini2004eigenvalue} address the spectrum of the Hodge--Laplace operator on bounded convex domains with smooth boundary in the Hilbert space case $p=2$.
+Their results thus pertain to the Poincar\'e--Friedrichs constant of the exterior derivative, and hence in particular to the curl and divergence operators.
+They prove that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. 
+They also provide explicit (but not necessarily optimal) upper bounds for Poincar\'e--Friedrichs constants that depend only on the dimension and diameter of the convex domain. 
+A duality argument also yields upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+Unfortunately, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+
+\subsubsection{Review: Domains star-shaped with respect to a ball}
 
@@
 then several estimates for Poincar\'e--Friedrichs constants are known. 
-Poincar\'e--Friedrichs inequalities actually hold over merely star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
+Poincar\'e--Friedrichs inequalities actually hold over any star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
 Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
@@
 Let us briefly discuss the practical limitations of the aforementioned estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
-Recall that the main objective of this manuscript is bounding these constants over local stars within triangulated domains. 
-Clearly, not all local stars describe convex subdomains, but most local stars are star-shaped with respect to a ball. 
-This observation would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
-However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
+Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
+While not all local stars describe convex subdomains, most local stars are star-shaped with respect to a ball. 
+Even though that would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}, 
+the estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
 This would not be as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
@@
 
-\subsection{Review: Triangulated domains}
-
-Geometric settings that admit finite triangulations offer further pathways to obtain Poincar\'e--Friedrichs inequalities. 
+\subsubsection{Review: Triangulated domains}
+
+Geometric settings that admit finite triangulations enable different pathways to obtain Poincar\'e--Friedrichs inequalities. 
 We review some of the main outcomes.
@@
 Computable estimates for Laplacian eigenvalues over triangulated domains have received much attention. 
-The constant in~\eqref{math:pot_PF_grad} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$. 
-Similarly, the constant in~\eqref{math:pot_PF_curl} for $p=2$ corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$. 
+The constant in~\eqref{math:intro:inequalitypf:gradient} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.
+Similarly, the constant in~\eqref{math:intro:Wcurl:pf} for $p=2$ corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$. 
 Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians and vice versa. 
@@
 It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-This sequential procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
-Importantly, these sequential estimates of Poincar\'e--Friedrichs constants generally circumvent the effect of low boundary regularity and only rely on the shape regularity.
-
-\subsection{Review: General results}
-
-Not much attention however seems to have been given to the study of computable constants in~\eqref{math:pot_PF_curl_div}, even if the domain $\Omega$ is convex. 
+This sequential procedure applies to general triangulated domains, not only local stars, though the latter are our main interest here. 
+Most importantly, these sequential estimates of Poincar\'e--Friedrichs constants generally circumvent the effect of low boundary regularity and only rely on the shape regularity.
+
+\subsubsection{Review: General results}
+
+Not much attention however seems to have been given to the study of computable constants in~\eqref{math:intro:Wcurl_div}, even if the domain $\Omega$ is convex. 
 Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of the exterior calculus formalism, 
@@
 
-Let for a moment the topology of $\Omega$ be trivial, let $\Omega$ be weakly Lipschitz, and consider the Hilbert case $p=2$. 
-Then, \eqref{math:pot_PF_curl} is related to the so-called Poincar\'e--Friedrichs--Weber inequality
+Poincar\'e--Friedrich inequalities for vector fields have appeared under different names. 
+Let us assume for a moment that $\Omega$ is a weakly Lipschitz domain with trivial topology, and consider only the Hilbert case $p=2$. 
+Then the constant in \eqref{math:intro:Wcurl:pf} agrees with the constant in the so-called Poincar\'e--Friedrichs--Weber inequality
 \begin{align}
-    \label{math:Weber}
-    \| \bfu\|_{L^{2}(\Omega)} \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
+    \label{math:intro:weber}
+    \| \bfu\|_{L^{2}(\Omega)}   \leq C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)},
 \end{align}
-for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ with either the tangential or the normal trace zero on $\partial \Omega$ and $\divergence \bfu = 0$. 
-Yet another writing is 
+valid for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ that satisfy $\divergence \bfu = 0$ and have vanishing normal or vanishing tangential trace along $\partial \Omega$. 
+Equivalently, \eqref{math:intro:weber} is valid for all $\bfu \in \bfW^{2}(\curl,\Omega)$ that are $L^{2}$-orthogonal to the gradients of scalar fields in $W^{1,2}(\Omega)$
+or that have vanishing tangential trace and are $L^{2}$-orthogonal to the gradients of those scalar fields in $W^{1,2}(\Omega)$ that satisfy Dirichlet boundary conditions.
+
+% 
+Yet another rewriting is 
 \label{math:PF_orth} \begin{align}
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\curl,\Omega,p} \| \curl \bfu \|_{L^{2}(\Omega)}, 
+    \| \bfu\|_{L^{2}(\Omega)} & \leq C_{\curl,\Omega,2} \| \curl \bfu \|_{L^{2}(\Omega)}, 
 	\label{math:PF_orth_curl}
 	\\
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,p} \| \divergence \bfu \|_{L^{2}(\Omega)}, 
+    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,2} \| \divergence \bfu \|_{L^{2}(\Omega)}, 
 	\label{math:PF_orth_div}
@@
 We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
-Still in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with homogeneous Dirichlet boundary conditions on $\partial \Omega$ implies, via duality~\eqref{math:pot_PF_div}.
+Still in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with homogeneous Dirichlet boundary conditions on $\partial \Omega$ implies, via duality~\eqref{math:intro:Wdiv}.
 However, that easy observation seems restricted to $p=2$.
@@
 
-The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:PF_DF}}.
+The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:intro:exterior:pf}}.
 \cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
 
-\subsection{Objectives: convex domains}
+\subsubsection{Objectives: convex domains}
 \cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
@@
 
-\subsection{Objectives: Potentials subject to partial boundary conditions}
+\subsubsection{Objectives: Potentials subject to partial boundary conditions}
 
@@
 
-\subsection{Objective: Main results}
+\subsubsection{Objective: Main results}
 
@@
 
-\subsection{Objective: General}
+\subsubsection{Objective: General}
 
@@
 
-\subsection{Objective: sequential approach} 
+\subsubsection{Objective: sequential approach} 
 Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
@@
 
-\subsection{Objective: shellable triangulations}
+\subsubsection{Objective: shellable triangulations}
 Shellable triangulations are defined by a special constructive property:
@@
 
-\subsection{Objective: Combinatorial constants over shellable triangulated domains}
+\subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
 
@@
 The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point.
-We perform a discrete analog of this procedure over triangulated domains: 
+We perform a discrete analogue of this procedure over triangulated domains: 
 having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.

### 2024-10-07 main.tex
more work on weber

@@
 
+Still in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space
+with homogeneous Dirichlet boundary conditions on $\partial \Omega$ implies~\eqref{math:intro:Wdiv} via duality. 
+However, that easy observation seems restricted to $p=2$.
+
+The two
 Poincar\'e--Friedrich inequalities for vector fields have appeared under different names. 
@@
 or that have vanishing tangential trace and are $L^{2}$-orthogonal to the gradients of those scalar fields in $W^{1,2}(\Omega)$ that satisfy Dirichlet boundary conditions.
-
-% 
-Yet another rewriting is 
-\label{math:PF_orth} \begin{align}
-    \| \bfu\|_{L^{2}(\Omega)} & \leq C_{\curl,\Omega,2} \| \curl \bfu \|_{L^{2}(\Omega)}, 
-	\label{math:PF_orth_curl}
-	\\
-    \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,2} \| \divergence \bfu \|_{L^{2}(\Omega)}, 
-	\label{math:PF_orth_div}
-\end{align}
-where the former holds for all vector fields $\bfu \in \bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$,
-and where the latter holds for all functions $\bfu \in \bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in Gaffney~\cite{Gaff_Hilbert_harm_55}, Weber~\cite{Web_compact_Maxw_80}, \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
-Still in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with homogeneous Dirichlet boundary conditions on $\partial \Omega$ implies, via duality~\eqref{math:intro:Wdiv}.
-However, that easy observation seems restricted to $p=2$.
+% Yet another rewriting is 
+% \label{math:PF_orth} \begin{align}
+%     \| \bfu\|_{L^{2}(\Omega)} & \leq C_{\curl,\Omega,2} \| \curl \bfu \|_{L^{2}(\Omega)}, 
+% 	\label{math:PF_orth_curl}
+% 	\\
+%     \| \bfu\|_{L^{2}(\Omega)} & \leq \tilde C_{\divergence,\Omega,2} \| \divergence \bfu \|_{L^{2}(\Omega)}, 
+% 	\label{math:PF_orth_div}
+% \end{align}
+% where the former holds for all vector fields $\bfu \in \bfW^{2}(\curl,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\curl,\Omega)$ with $\curl \bfv = 0$,
+% and where the latter holds for all functions $\bfu \in \bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
+We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in \cite{Gaff_Hilbert_harm_55}, \cite{Web_compact_Maxw_80} as well as \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+The general case of $L^p$ differential forms over Lipschitz manifolds subject to partial boundary conditions is discussed in~\cite{goldshtein2011hodge}.
+
+However, while many of the above results rely on non-constructive estimates, 
+we are interested in practically computable upper bounds.
 

### 2024-10-07 main.tex
complete literature review for the time being

@@
 
-\subsubsection{Review: Analytical constants over convex domains}
-
-% gradient over convex domains
-Considerable research effort has gone into computing explicit upper estimates for the constants in the Poincar\'e--Friedrichs inequalities over convex domains. 
-Notably, if the constants are required to depend on the convex domain only via its diameter, 
-then the optimal gradient Poincar\'e--Friedrichs and Poincar\'e constants for the entire range of Lebesgue exponent $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
-
-% Guerini Savo  
-The literature on Poincar\'e--Friedrichs constants and potentials of curls and divergences is less extensive than for potentials of gradients, even over convex domains.
-Guerini and Savo~\cite{guerini2004eigenvalue} address the spectrum of the Hodge--Laplace operator on bounded convex domains with smooth boundary in the Hilbert space case $p=2$.
-Their results thus pertain to the Poincar\'e--Friedrichs constant of the exterior derivative, and hence in particular to the curl and divergence operators.
-They prove that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. 
-They also provide explicit (but not necessarily optimal) upper bounds for Poincar\'e--Friedrichs constants that depend only on the dimension and diameter of the convex domain. 
-A duality argument also yields upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
-
-\subsubsection{Review: Domains star-shaped with respect to a ball}
-
-When the domain is not convex but star-shaped with respect to a ball,
-then several estimates for Poincar\'e--Friedrichs constants are known. 
-Poincar\'e--Friedrichs inequalities actually hold over any star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
-Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
-We pay particular attention to the regularized Poincar\'e and Bogovski\u{\i} potential operators for the exterior derivative,
-such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
-In principle, the operator norms of those potential operators as mapping between Lebesgue spaces of differential forms 
-are upper estimates for the Poincar\'e--Friedrichs constants of the domain. 
-Here, estimates for the higher-order seminorms of these potentials are available in~\cite{guzman2021estimation}, 
-but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-We particularly emphasize that these estimates for domains star-shaped with respect to a ball have in common that they rely on upper bounds for the \emph{eccentricity} of the domain.
-
-% Technical restriction of star-shaped domains
-
-Let us briefly discuss the practical limitations of the aforementioned estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
-Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
-While not all local stars describe convex subdomains, most local stars are star-shaped with respect to a ball. 
-Even though that would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}, 
-the estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
-This would not be as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs most prominently when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
-which contain local finite element patches that are not star-shaped with respect to any ball. 
-In view of this, we refrain from treating local patches (stars) in triangulations as domains star-shaped with respect to a ball.
-
-\subsubsection{Review: Triangulated domains}
-
-Geometric settings that admit finite triangulations enable different pathways to obtain Poincar\'e--Friedrichs inequalities. 
-We review some of the main outcomes.
-
-Computable estimates for Laplacian eigenvalues over triangulated domains have received much attention. 
-The constant in~\eqref{math:intro:inequalitypf:gradient} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.
-Similarly, the constant in~\eqref{math:intro:Wcurl:pf} for $p=2$ corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$. 
-Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians and vice versa. 
-Prominent methods numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants upon solving a finite element system over a sufficiently fine triangulation and using some clever post-processing estimates.
-This has led to estimates for scalar Laplacian eigenvalues~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} and vector Laplacian eigenvalues~\cite{gallistl2023computational}. 
-We remark that for the purposes of this manuscript, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems. 
-% Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.
-
-% veeser and verfurth 
-% sequential methodology
-There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices. 
-Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
-Naturally, their estimates depend on the shape regularity of the mesh.
-Another class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
-% Starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
-The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
-Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
-along the interfacing intersection, the two potentials will only differ by a constant, 
-and that difference can easily be removed to ensure continuity across that interface. 
-Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
-The method is known in the finite element literature~\cite{ern2021finite}.
-It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-This sequential procedure applies to general triangulated domains, not only local stars, though the latter are our main interest here. 
-Most importantly, these sequential estimates of Poincar\'e--Friedrichs constants generally circumvent the effect of low boundary regularity and only rely on the shape regularity.
-
 \subsubsection{Review: General results}
 
-Not much attention however seems to have been given to the study of computable constants in~\eqref{math:intro:Wcurl_div}, even if the domain $\Omega$ is convex. 
-Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of the exterior calculus formalism, 
-but the Banach case $p \neq 2$ seems largely unexplored.
-
-Still in the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space
-with homogeneous Dirichlet boundary conditions on $\partial \Omega$ implies~\eqref{math:intro:Wdiv} via duality. 
-However, that easy observation seems restricted to $p=2$.
-
-The two
-Poincar\'e--Friedrich inequalities for vector fields have appeared under different names. 
+The qualitative existence of Poincar\'e--Friedrichs inequalities for the differential operators of vector calculus and exterior calculus is known for a large class of domains. 
+There is a particularly large body of literature on the Poincar\'e inequality for the gradient and its numerous variants,
+which may include weighted integrals or boundary terms. 
+These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem,
+and thus the resulting constants are not explicitly computable.
+
+% divergence 
+The divergence operator has received less attention. 
+In the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space
+with homogeneous Dirichlet boundary conditions along $\partial \Omega$ implies~\eqref{math:intro:Wdiv} via duality. 
+However, that easy duality argument, which yields an explicit upper bound proportional to the domain diameter, seems inherently restricted to $p=2$.
+
+% curl 
+The core challenges can be found in the discussion of the curl operator in three dimensions,
+where Poincar\'e--Friedrich inequalities have appeared under different names. 
 Let us assume for a moment that $\Omega$ is a weakly Lipschitz domain with trivial topology, and consider only the Hilbert case $p=2$. 
@@
 The general case of $L^p$ differential forms over Lipschitz manifolds subject to partial boundary conditions is discussed in~\cite{goldshtein2011hodge}.
-
 However, while many of the above results rely on non-constructive estimates, 
 we are interested in practically computable upper bounds.
+
+\subsubsection{Review: Analytical constants over convex domains}
+
+% gradient over convex domains
+Considerable research effort has gone into computing explicit upper estimates for the constants in the Poincar\'e--Friedrichs inequalities over convex domains. 
+Notably, if the constants are required to depend on the convex domain only via its diameter, 
+then the optimal gradient Poincar\'e--Friedrichs and Poincar\'e constants for the entire range of Lebesgue exponent $1 \leq p < \infty$ are known explicitly~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
+
+% Guerini Savo  
+The literature on Poincar\'e--Friedrichs constants and potentials of curls and divergences is less extensive than for potentials of gradients, even over convex domains.
+Guerini and Savo~\cite{guerini2004eigenvalue} address the spectrum of the Hodge--Laplace operator on bounded convex domains with smooth boundary in the Hilbert space case $p=2$.
+Their results thus pertain to the Poincar\'e--Friedrichs constant of the exterior derivative, and hence in particular to the curl and divergence operators.
+They prove that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. 
+They also provide explicit (but not necessarily optimal) upper bounds for Poincar\'e--Friedrichs constants that depend only on the dimension and diameter of the convex domain. 
+A duality argument also yields upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
+Unfortunately, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+
+\subsubsection{Review: Domains star-shaped with respect to a ball}
+
+When the domain is not convex but star-shaped with respect to a ball,
+then several estimates for Poincar\'e--Friedrichs constants are known. 
+Poincar\'e--Friedrichs inequalities actually hold over any star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
+Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
+We pay particular attention to the regularized Poincar\'e and Bogovski\u{\i} potential operators for the exterior derivative,
+such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
+In principle, the operator norms of those potential operators as mapping between Lebesgue spaces of differential forms 
+are upper estimates for the Poincar\'e--Friedrichs constants of the domain. 
+Here, estimates for the higher-order seminorms of these potentials are available in~\cite{guzman2021estimation}, 
+but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
+We particularly emphasize that these estimates for domains star-shaped with respect to a ball have in common that they rely on upper bounds for the \emph{eccentricity} of the domain.
+
+% Technical restriction of star-shaped domains
+
+Let us briefly discuss the practical limitations of the aforementioned estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
+Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
+While not all local stars describe convex subdomains, most local stars are star-shaped with respect to a ball. 
+Even though that would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}, 
+the estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
+This would not be as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
+But the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
+this occurs most prominently when the domain has sharp reentrant corners.
+Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
+which contain local finite element patches that are not star-shaped with respect to any ball. 
+In view of this, we refrain from treating local patches (stars) in triangulations as domains star-shaped with respect to a ball.
+
+\subsubsection{Review: Triangulated domains}
+
+Geometric settings that admit finite triangulations enable different pathways to obtain Poincar\'e--Friedrichs inequalities. 
+We review some of the main outcomes.
+
+Computable estimates for Laplacian eigenvalues over triangulated domains have received much attention. 
+The constant in~\eqref{math:intro:inequalitypf:gradient} for $p=2$ corresponds to a lower bound for the Laplace eigenvalues and quantifies the stability properties of the Laplacian on the domain $\Omega$.
+Similarly, the constant in~\eqref{math:intro:Wcurl:pf} for $p=2$ corresponds to a lower bound for the Maxwell eigenvalues and quantifies the stability properties of the Maxwell system on $\Omega$. 
+Thus, computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians and vice versa. 
+Prominent methods numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants upon solving a finite element system over a sufficiently fine triangulation and using some clever post-processing estimates.
+This has led to estimates for scalar Laplacian eigenvalues~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} and vector Laplacian eigenvalues~\cite{gallistl2023computational}. 
+We remark that for the purposes of this manuscript, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems. 
+% Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.
+
+% veeser and verfurth 
+% sequential methodology
+There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices. 
+Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
+Naturally, their estimates depend on the shape regularity of the mesh.
+Another class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
+% Starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface. 
+Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
+The method is known in the finite element literature~\cite{ern2021finite}.
+It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+This sequential procedure applies to general triangulated domains, not only local stars, though the latter are our main interest here. 
+Most importantly, these sequential estimates of Poincar\'e--Friedrichs constants generally circumvent the effect of low boundary regularity and only rely on the shape regularity.
 

### 2024-10-07 intro.tex
complete literature review for the time being
introduction

@@
 % Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.
+
+Important results in the Hilbert case $p=2$ can be found in~\cite{guerini2004eigenvalue, Paul_Vald_PF_grad_curl_div_20} that we discuss now in the broader setting of the exterior calculus formalism, 
+but the Banach case $p \neq 2$ seems largely unexplored.
+
+\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to convex domains.}
+
+\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
+Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
+In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
+The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
+
+our regularized potential operators are simplified in that we use constant weight functions and only study .
+
+We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
+
+In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, 
+the regularized potential operators we propose are simplified: 
+In comparison to their exposition, our variants of the regularized potential operators are simplified:
+we only study them over convex domains and use simpler (constant) weight functions. 
+The resulting operators feature generally lower regularity but their properties are sufficient for our purposes. 
+Crucially, this allows us to easily estimate their operator norms.
+
+We consider the latter outcome to be of independent interest.
+
+\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
+\cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
+\mwl{Of course, the eccentricity enters the estimate.}
+
+The main objective of this manuscript is the construction of potentials for the gradient, curl, and divergence, and more generally the exterior derivative.
+The operator norms of our potentials satisfy computable upper bounds, which are computable upper bounds of the Poincar\'e--Friedrichs constants.
+As we elaborate in what follows, we focus on domains with shellable triangulations.
+which include local patches (stars) in two and three dimensions as important special cases.
+\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
+
+Our main result for convex domains in the exterior calculus setting is the construction of regularized Poincar\'e and Bogovski\u{\i} potential operators with explicitly bounded operator norms.
+This is summarized in Theorem~\ref{theorem:bogovpoinc}.
+The  upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are bounded in terms of the domain's eccentricity.
+The bounds are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the space dimension and the form degree enter the estimates.
+
+The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is two-fold: 
+firstly, they are of evident independent interest, and secondly, we will need them as a component for our main results on triangulations. 
+We derive the Poincar\'e--Friedrichs inequalities via regularized Poincar\'e and Bogovski\u{\i}-type potential operators. 
+Here, we closely follow the general methodology of Costabel and McIntosh~\cite{costabel2010bogovskiui},
+who study these potential operators over domains star-shaped with respect to a ball,
+but the potential operators that we propose are simplified:
+we only study them over convex domains and use simpler (constant) weight functions. 
+While the resulting Poincar\'e and Bogovski\u{\i} potential operators feature generally lower regularity but are conductive for our purposes. 
+Crucially, this allows us to easily estimate their operator norms.
+
+Our main result for convex domains in the exterior calculus setting is the construction of regularized Poincar\'e and Bogovski\u{\i} potential operators with explicitly bounded operator norms. 
+This is summarized in Theorem~\ref{theorem:bogovpoinc}. 
+The upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are bounded in terms of the domain's eccentricity. 
+The bounds are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the space dimension and the form degree enter the estimates.
+
+The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is two-fold: 
+firstly, they are of evident independent interest, and secondly, we will need them as a component for our main results on triangulations.
+
+Our exposition of regularized Poincar\'e and Bogovski\u{\i}-type potential operators follows the general methodology of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
+By comparison, our variants of these operators are simplified: 
+we only study them over convex domains, instead of domains star-shaped with respect to a ball, 
+and we use simpler (constant) weight functions. 
+While the resulting potential operators feature generally lower regularity, 
+they are conductive for our purposes. 
+Crucially, this allows us to easily estimate their operator norms and thus bound Poincar\'e--Friedrichs constants.
+
+who study these potential operators over domains star-shaped with respect to a ball. 
+but the potential operators that we propose are simplified:
+we only study them over convex domains and use simpler (constant) weight functions. 
+While the resulting Poincar\'e and Bogovski\u{\i} potential operators feature generally lower regularity but are conductive for our purposes. 
+Crucially, this allows us to easily estimate their operator norms.
+
+In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
+\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions.
+We are not aware of explicit estimates or regularized potential operators for these boundary conditions in the published literature. 
+Our basic idea here is to reuse the Poincar\'e--Friedrichs inequalities subject to boundary conditions on the entire boundary in order to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
+For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
+we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
+
+We achieve this by constructing an auxiliary problem subject to full boundary conditions.
+We achieve this via an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra, 
+construction of an auxiliary problem subject to full boundary conditions, 
+and then affine ``folder'' map back to the tetrahedron.
+
+Again, we address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents and our Poincar\'e--Friedrichs constants are explicitly computable.
+
+% The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
+
+We achieve this via an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra, 
+construction of an auxiliary problem subject to full boundary conditions, 
+and then affine ``folder'' map back to the tetrahedron.

### 2024-10-07 main.tex
introduction

@@
 
-\tableofcontents
+% \tableofcontents
 
@@
 which has been subject to extensive research.
-\\
 
@@
 % We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:intro:gradientpotential}.
-\\
 
@@
 not much attention seems to have been given to the study of computable constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
-\\
 
@@
 However, that easy duality argument, which yields an explicit upper bound proportional to the domain diameter, seems inherently restricted to $p=2$.
+
+% In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, via duality, the Poincar\'e--Friedrichs inequality for the divergence operator.
+However, that easy observation seems restricted to the Hilbert space case $p=2$.
 
@@
 
+While we thus know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
+we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars.
+
 \subsection{Objectives and methodology}
 
-The main objective of this manuscript is the construction of linear potential operators with explicitly computable upper bounds on their operator norms (i.e., of computable bounds on the Poincar\'e--Friedrichs constants) for the gradient, curl, and divergence operators\cye{, and more broadly in the general case~\eqref{math:intro:exterior:pf}}.
-\cye{We consider not necessarily} convex subdomains and focus on \cye{local patches (stars) of simplicial elements within triangulated domains, but we will also devote an important effort specifically to} convex domains.
+The main objective of this manuscript is the construction of potentials for the gradient, curl, and divergence, and more generally the exterior derivative.
+The operator norms of our potentials satisfy computable upper bounds, which are computable upper bounds of the Poincar\'e--Friedrichs constants.
+As we elaborate in what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases.
+Towards that goal, we also devote an important effort specifically to convex domains.
 
 \subsubsection{Objectives: convex domains}
-\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains.
-Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators.
-In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions.
-The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.
-
-We rely on regularized potential operators as a remedy. 
-We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
-who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
-In comparison to their exposition, our variants of the regularized potential operators are simplified:
-we only study them over convex domains and use simpler (that is, constant) weight functions. 
-The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
-however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
-We consider the latter outcome to be of independent interest.
+
+Our main result for convex domains in the exterior calculus setting is the construction of regularized Poincar\'e and Bogovski\u{\i} potential operators with explicitly bounded operator norms. 
+This is summarized in Theorem~\ref{theorem:bogovpoinc}. 
+The upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are bounded in terms of the domain's eccentricity. 
+The bounds are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the space dimension and the form degree enter the estimates.
+
+The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is two-fold: 
+firstly, they are of evident independent interest, and secondly, we will need them as a component for our main results on triangulations. 
+Our exposition of regularized Poincar\'e and Bogovski\u{\i}-type potential operators follows the general methodology of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
+By comparison, our variants of these operators are simplified: 
+we only study them over convex domains, instead of domains star-shaped with respect to a ball, 
+and we use simpler (constant) weight functions. 
+While the resulting potential operators feature generally lower regularity, they are conductive for our purposes. 
+Crucially, this allows us to easily estimate their operator norms and thus bound Poincar\'e--Friedrichs constants.
 
@@
 
-\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions.
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
-\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces.
-We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
-\\
-
-In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
-Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
-We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
-The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions.
+We also address the construction of potential operators for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions.
+We are not aware of explicit estimates or regularized potential operators for these boundary conditions in the published literature. 
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
@@
 We achieve this by constructing an auxiliary problem subject to full boundary conditions.
-\\
-
-\cye{Finally, our main result for convex domains in the exterior calculus setting (Section~\ref{section:intro_EC}) is the construction} of regularized potential operators for the exterior derivative with explicitly bounded operator norms.
-\cye{This is summarized in Theorem~\ref{theorem:bogovpoinc}.} \mwl{MV: The discussion from before Theorem~\ref{theorem:bogovpoinc} resumed here.} \cye{The arising upper bounds for} the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the \cye{space} dimension and the form degree enter\cye{\sout{s}} the estimate\cye{s}.
-\mwl{Of course, the eccentricity enters the estimate.}
+so that we can build upon the regularized Bogovski\u{\i} operators and the Poincar\'e--Friedrichs inequalities subject to boundary conditions on the entire boundary.
+We thus obtain Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions. 
+Again, we address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents and our Poincar\'e--Friedrichs constants are explicitly computable.
 
@@
 
-\subsubsection{Objective: General}
-
-While we know Poincar\'e--Friedrichs constants over local stars for scalar-valued Sobolev spaces, 
-we are not aware of computable estimates for the case of $\bfW^{p}(\curl,\Omega)$ and $\bfW^{p}(\divergence,\Omega)$ over finite element stars.
-
-In the Hilbert space setting, with $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space with Dirichlet boundary conditions implies, 
-via duality, the Poincar\'e--Friedrichs inequality for the divergence operator. However, that easy observation seems restricted to the Hilbert space case $p=2$.
-
-\subsubsection{Objective: sequential approach} 
+\subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
+
 Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
@@
 We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-\\
-
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-\\
-
-\subsubsection{Objective: shellable triangulations}
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable.
-
-\subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
 
@@
 With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
+
+We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
+The basic inductive strategy remains the same.
+We start by constructing, say, a curl potential, over a single simplex.
+Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
+However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
+% 
+To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
+We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
+Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+
+Shellable triangulations are defined by a special constructive property:
+we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D triangulations are shellable.
 

### 2024-10-08 intro.tex
introduction, partially

@@
 and then affine ``folder'' map back to the tetrahedron.
+
+\subsubsection{Objective: Main results}
+
+% 1. intro paragraph 
+% 2. review of the gradient construction 
+% 3. hightlight the difficulty with the kernels
+% 4. introduce shellable
+% 5. Apply shellable triangulations
+% 6. Contractible 
+% [ ] remove face-connected completely
+
+Our main objective remains to compute Poincar\'e--Friedrichs constants for the differential operators of vector calculus and exterior calculus, including in particular the curl and divergence, over triangulated domains.
+
+In this work, we aim to construct linear potential operators for the gradient, curl, and divergence on triangulated domains, 
+providing explicitly computable upper bounds. Our approach extends to domains that may be non-convex and non-star-shaped, 
+focusing on triangulations that are face-connected or possess the special property of shellability.
+
+\subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
+
+Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
+Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
+
+For vector fields, new challenges arise because of the infinite-dimensional kernels. 
+We, however, overcome these challenges and succeed in generalizing the sequential construction of the potential operator for the gradient to vector potentials, including in particular the curl and divergence.
+The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. 
+Having already defined a potential operator over a set of simplices that we term a subtriangulation, 
+we then construct a potential over a simplex neighboring through some $(n-1)$-dimensional faces. 
+However, the potential on the new simplex might here not have the same tangential trace along the interface between the new simplex and the previous ones. 
+Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations. 
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
+With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
+
+We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
+The basic inductive strategy remains the same. 
+We start by constructing, say, a curl potential, over a single simplex. 
+Having already defined a potential operator over a subtriangulation, 
+we then construct a potential over a neighboring simplex. 
+However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex. 
+% 
+To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials. 
+We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, 
+we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions. 
+Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+
+Shellable triangulations are defined by a special constructive property:
+we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D triangulations are shellable.
+
+% seq construction 
+In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, 
+where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face. 
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, 
+formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.

### 2024-10-08 main.tex
introduction, partially

@@
 There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices. 
+% TODO V & V do the same sequential estimate 
 Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
@@
 
-In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{subsection:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} is our main results.}
-\mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
-The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
-\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
-
-\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
-As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+% 3. hightlight the difficulty with the kernels
+% 4. introduce shellable
+% 5. Apply shellable triangulations
+% 6. Contractible 
+% [ ] remove face-connected completely
+
+% 1. intro paragraph : outline what we will do and why
+
+Our main objective remains to find potential operators for the differential operators of vector calculus and exterior calculus, including in particular the curl and divergence, over triangulated domains.
+The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
+In light of the different approaches listed before, 
+we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
+and that do not depend on the boundary regularity of the domain.
+
+% In this work, we aim to construct linear potential operators for the gradient, curl, and divergence on triangulated domains, 
+% providing explicitly computable upper bounds. Our approach extends to domains that may be non-convex and non-star-shaped, 
+% focusing on triangulations that are face-connected or possess the special property of shellability.
+
+% 2. the gradient construction as blueprint 
+% outline the essential features
+
+\mwl{
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface. 
+Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
+}
+
+The sequential construction of potentials for gradient vector fields, as discussed above, 
+is well-known in the literature and serves as our conceptual blueprint.
+% TODO: improve the description here.
+We start by constructing a scalar potential over a single simplex
+and successively define scalar potentials over larger and larger intermediate subtriangulations until the full domain is finally exhausted.
+At each step, we construct a potential over some successive simplex that shares a face with one of the preceding simplices.
+The difference of the two scalar potentials along that interface is a constant,
+and we can easily fix the constant along the shared face to build the extend the scalar potential. 
+Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+
+% 
+For the gradient operator, our method involves a straightforward sequential traversal of the triangulation. 
+Each simplex is connected to the preceding ones via a shared (n?1)(n?1)-dimensional face. 
+We construct a gradient potential over each new simplex, and since the kernel of the gradient consists solely of constants, 
+we can fix the constant by matching the value on the shared face.
+
+% seq construction 
+In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, 
+where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face. 
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, 
+formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+Extending our method to vector fields—specifically for the curl and divergence operators introduces new challenges due to their infinite-dimensional kernels. 
+To address these challenges, we generalize the sequential construction used for the gradient to develop vector potentials. 
+The basic inductive strategy remains: 
+we start by constructing a potential over a single simplex and then extend it to neighboring simplices. 
+However, unlike in the gradient case, the potentials over adjacent simplices may not have matching tangential traces along their shared interfaces.
+
+To ensure the correct continuity properties of the vector potentials, we impose stronger conditions on the triangulations.
+We require that the intermediate subtriangulations formed during the sequential process are manifolds with boundary, and that the interface between the existing subtriangulation and the new simplex is a boundary submanifold of both.
+Under these conditions—which are satisfied by shellable triangulations—we can define well-posed auxiliary problems for the curl and divergence operators with partial boundary conditions.
+By iterating this procedure, we exhaust the entire triangulation and obtain the desired potentials.
+Our main results for the curl and divergence operators are presented in Theorems \ref{theorem:poincarefriedrichsestimate
+} and \ref{theorem:poincarefriedrichsestimate:exterior
+}.
+
+Shellability is a well-established concept in discrete geometry and combinatorics, referring to a property of simplicial or polytopal complexes that allows them to be built sequentially in a controlled manner.
+A triangulation is shellable if it can be assembled by adding one simplex at a time such that each new simplex shares a boundary submanifold with the existing complex.
+This property ensures that interfaces between simplices are well-behaved, which is crucial for the continuity of vector potentials.
+
+While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions—patches of simplices sharing a common vertex, edge, face, or nn-simplex.
+These local patches are inherently shellable, making our approach widely applicable.
+For more details on shellability, see Kozlov \cite{kozlov2008combinatorial} and Ziegler \cite{ziegler1995lectures}.
 
@@
 Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
+
 Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
@@
 
-For vector fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
-We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
-However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
+For vector fields, new challenges arise because of the infinite-dimensional kernels. 
+We, however, overcome these challenges and succeed in generalizing the sequential construction of the potential operator for the gradient to vector potentials, including in particular the curl and divergence.
+The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. 
+Having already defined a potential operator over a set of simplices that we term a subtriangulation, 
+we then construct a potential over a simplex neighboring through some $(n-1)$-dimensional faces. 
+However, the potential on the new simplex might here not have the same tangential trace along the interface between the new simplex and the previous ones. 
 Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
@@
 We start by constructing, say, a curl potential, over a single simplex. 
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
+Having already defined a potential operator over a subtriangulation, 
+we then construct a potential over a neighboring simplex. 
 However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex. 
@@
 We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, 
+we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions. 
 Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
@@
 In particular, local stars in 2D and 3D triangulations are shellable.
+
+% exterior PF 
+\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
+As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
+The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+
+\begin{remark}
+    % TODO: Reintegrate in that section
+    \mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
+    The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the given triangulation: 
+    the length of any traversal from the root simplex, the ratios of the volumes of any pair of adjacent simplices, 
+    and the Poincar\'e--Friedrichs constants on each face patch or each simplex. 
+    %, and the Poincar\'e--Friedrichs constant of the initial simplex. 
+    Here, Poincar\'e--Friedrichs constants on face patches are estimated in terms of shape regularity parameters of the triangulation; 
+    if the face patches of the triangulation are convex, then better estimates are possible. 
+\end{remark}
 
@@
 We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
-\begin{align*}
-    \underlying{\calT} := \bigcup_{ T \in \calT } T
-    .
-\end{align*}
+We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, 
+which is the union $\underlying{\calT} = \bigcup \calT$ of all simplices in $\calT$.
+% \begin{align*}
+    % \underlying{\calT} := \bigcup_{ T \in \calT } T
+    % .
+% \end{align*}
 We call any set triangulable if it is the underlying set of some triangulation.
-\\
 

### 2024-10-08 intro.tex
introduction

@@
 formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+% TODO: improve the description here.
+We start by constructing a scalar potential over a single simplex
+and successively define scalar potentials over larger and larger intermediate subtriangulations until the full domain is finally exhausted.
+At each step, we construct a potential over some successive simplex that shares a face with one of the preceding simplices.
+The difference of the two scalar potentials along that interface is a constant,
+and we can easily fix the constant along the shared face to build the extend the scalar potential. 
+We construct a potential over some successive simplex that shares a face with one of the preceding simplices.
+
+\mwl{
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface. 
+Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
+}
+
+% In this work, we aim to construct linear potential operators for the gradient, curl, and divergence on triangulated domains, 
+% providing explicitly computable upper bounds. Our approach extends to domains that may be non-convex and non-star-shaped, 
+% focusing on triangulations that are face-connected or possess the special property of shellability.
+
+For the gradient operator, our method involves a straightforward sequential traversal of the triangulation. 
+Each simplex is connected to the preceding ones via a shared (n?1)(n?1)-dimensional face. 
+We construct a gradient potential over each new simplex, and since the kernel of the gradient consists solely of constants, 
+we can fix the constant by matching the value on the shared face.
+
+% seq construction 
+In the gradient case of Section~\ref{subsection:intro_grad}, 
+it is possible to perform a simple pass through the triangulation, 
+where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face. 
+We always construct a gradient potential over the new simplex, 
+and since the gradient kernel is trivial, 
+formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+% we then construct a potential over a neighboring simplex that shares at least one face with the one of the preceding simplices. 
+% Of course, the potential on the new simplex and the existing intermediate potential may have different tangential traces along the interface between the new simplex and the existing intermediate subtriangulation.
+
+However, the potential on the new simplex might here not have the same tangential trace along the interface between the new simplex and the previous ones. 
+Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
+
+However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex. 
+To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials. 
+We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, 
+we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions. 
+Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+
+% Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
+% Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
+
+% For vector fields, new challenges arise because of the infinite-dimensional kernels. 
+% We, however, overcome these challenges and succeed in generalizing the sequential construction of the potential operator for the gradient to vector potentials, including in particular the curl and divergence.
+
+% We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
+% The basic inductive strategy remains the same. 
+% We start by constructing, say, a curl potential, over a single simplex. 
+% Having already defined a potential operator over a subtriangulation, 
+% we then construct a potential over a neighboring simplex that shares a face with the one of the preceding simplices.
+
+Shellable triangulations are defined by a special constructive property:
+we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D triangulations are shellable.
+
+\begin{remark} \label{remark:reg_Poinc_Bog}
+    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+	The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+
+    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    These potentials enable the analysis of de~Rham complexes without boundary conditions.
+    % TODO: are these paragraphs in the introduction now?
+    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
+    % 
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they can study domains star-shaped with respect to a ball. 
+    Instead, we average over the entire domain, which requires a convex geometry. 
+    The resulting potential operators are sufficient for establishing Poincar\'e--Friedrichs constants over bounded convex domains. 
+    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
+
+    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight, and thus they are bounded operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
+    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
+
+    The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+	The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+    Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
+    which is why they can study domains star-shaped with respect to a ball. 
+    Their operators are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight; this proves that the operators are bounded between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
+    Instead, we average over the entire domain, which requires a convex geometry, 
+	and we are interested in boundedness in the Lebesgue $p$-norms. 
+    We establish computable bounds on the Poincar\'e--Friedrichs constants,
+	which had not been established yet, to the best of our knowledge. 
+\end{remark}

### 2024-10-08 main.tex
introduction

--- 2024-10-07 main.tex
@@
 
-In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face\cye{; face-connected triangulations are sufficient here}.
-We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{subsection:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
-Here, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} is our main results.}
-\mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
-The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the \cye{given} triangulation: the length of any traversal from the root simplex, the ratios of the volumes of \cye{the} adjacent simplices, the Poincar\'e--Friedrichs constants on each face patch, and the Poincar\'e--Friedrichs constant of the initial simplex.
-\cye{Here,} the \cye{face patch} Poincar\'e--Friedrichs constants \cye{are} estimated in terms of shape \cye{regularity parameters of the triangulation}; if the face patches of the triangulation are convex, then better estimates are possible.
-
-\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
-As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
-The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
-
-\subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
-
-Towards our main objective of constructing linear potential operators for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-
-For vector fields, new challenges arise \cye{because of} the infinite-dimensional kernels.
-We, \cye{however, overcome these challenges and succeed in generalizing} the sequential construction of the potential operator for the gradient to vector potentials\cye{, including in particular} the curl and divergence.
+% 1. intro paragraph : outline what we will do and why
+
+Our main objective remains to find potential operators for the differential operators of vector calculus and exterior calculus, including the curl and the divergence, over triangulated domains. 
+The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
+In light of the different approaches listed before, we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, and that do not depend on the boundary regularity of the domain.
+
+% 2. the gradient construction as blueprint 
+% outline the essential features
+
+The sequential construction of potentials for gradient vector fields, as discussed above, is well-known in the literature and serves as our conceptual blueprint.
+Gradient potentials are easily computed over each individual simplex but the constants of integration will generally not match: the scalar piecewise potential will be a in broken Sobolev space. 
+In particular, the local potentials will only differ by a constant along the simplex boundary. 
+However, we can generate an actual potential in Sobolev spaces over larger and larger intermediate subdomains that we build up sequentially.
+At each step, the we choose a simplex that shares a face with one of the preceding simplices and adjust the constant of integration of the local potential. 
+The global potential is contructed cell by cell until the entire domain is exhausted. 
+Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+
+% 3. generalization to vector fields
+
+We generalize this sequential construction of potentials to curl, the divergence, and the exterior derivative. 
+However, we need to overcome new challenges here that are due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
 The basic inductive strategy remains the same. 
 We start by constructing, say, a curl potential, over a single simplex. 
-Having already defined a potential operator over a \cye{set of simplices that we term} a subtriangulation, we then construct a potential over a simplex \cye{neighboring through some $(n-1)$-dimensional faces}.
-However, the potential \cye{on the new simplex} might \cye{here} not have the same tangential trace along the interface between the new simplex and the previous ones.
-Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
-With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
-
-We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence.
-The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential, over a single simplex.
-Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex.
-However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex.
-% 
-To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials.
-We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
-Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions.
-Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-
-Shellable triangulations are defined by a special constructive property:
-we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
-Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
-Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
-In particular, local stars in 2D and 3D triangulations are shellable.
+Having already defined a potential operator over a subtriangulation, we choose a neighboring simplex whose intersection with the preceding simplices includes at least one common face. 
+We then construct a potential for the curl operator whose tangential traces along the intersection match the already existing potential.
+Repeating this procedure eventually completes the original triangulation and provides the desired potential.
+Here, Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} is our main result.
+
+% 4. hightlight the difficulty with the kernels
+
+However, unlike for the potential construction of the gradient, is not immediately evident whether the construction of local curl potential with given tangential traces is a well-posed auxiliary problem.
+For the case of the gradient, it was sufficient that the sequential traversal of the triangulation ensured that each new simplex shares at least one face with one of previous simplices was sufficient.
+For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive: 
+we ensure that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
+This allows us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex. 
+Whether a triangulation admits such a particular traversal is a non-trivial condition and defines the class of \emph{shellable} triangulations.
+
+% 4. introduce shellable
+
+Shellable simplicial complexes, and more generally polytopal complexes, are a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}, and the references therein.
+Any shellable simplicial complexes must necessarily triangulate a contractible space. 
+With respect to our main interest, local patches (stars) in 2D and 3D triangulations are shellable.
+
+% 5. Contractible 
+Inspired by contractibility of shellable triangulations, we pursuit an additional estimate for Poincar\'e--Friedrichs constants. 
+Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
+Their bi-Lipschitz constants are controlled by the shape regularity of the domain. 
+This reduces the construction of potentials over shellable triangulations to the construction of potentials over convex domains.
+We refer to Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} as the main result of this approach.
 
@@
 \begin{remark}
-    The Poincar\'e--Friedrichs constants obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimate the best one as the number of $n$-simplices in the triangulation $\calT$ increases.
+    The computable Poincar\'e--Friedrichs constants obtained in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} depend on only a few parameters of the given triangulation: 
+    the length of any traversal from the root simplex, 
+    the ratios of the volumes of any pair of adjacent simplices, 
+    and the Poincar\'e--Friedrichs constants on each face patch or each simplex. 
+    Poincar\'e--Friedrichs constants on face patches are estimated in terms of shape regularity parameters of the triangulation; 
+    if the face patches of the triangulation are convex, then better estimates are possible.
+
+    % obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}
+    These computable Poincar\'e--Friedrichs constants increasingly overestimate the best one as the number of $n$-simplices in the triangulation $\calT$ increases. 
     Hence, we conceive their target application to be local patches (stars), in particular non-convex boundary stars. 
@@
     The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
-    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
-    These potentials enable the analysis of de~Rham complexes without boundary conditions.
-    % TODO: are these paragraphs in the introduction now?
 	The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
-    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
-    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
-    % 
-    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
-    which is why they can study domains star-shaped with respect to a ball. 
-    Instead, we average over the entire domain, which requires a convex geometry. 
-    The resulting potential operators are sufficient for establishing Poincar\'e--Friedrichs constants over bounded convex domains. 
-    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
-
-    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
-    because their averaging uses a smooth weight, and thus they are bounded operators between a variety of function spaces. 
-    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
-    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
-    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
-
-    \mwl{ 
     Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
@@
     have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
-    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
-    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
-    This had not been established yet, to the best of our knowledge. 
-    }
+    Instead, we average over the entire domain, which requires a convex geometry, 
+	and we are interested in boundedness in the Lebesgue $p$-norms. 
+    We establish computable bounds on the Poincar\'e--Friedrichs constants,
+	which had not been established yet, to the best of our knowledge. 
 \end{remark}

### 2024-10-08 main.tex
spell check

@@
 
-This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrich inequalities for the differential operators of vector calculus. 
+This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrichs inequalities for the differential operators of vector calculus. 
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
@@
 The core challenges can be found in the discussion of the curl operator in three dimensions,
-where Poincar\'e--Friedrich inequalities have appeared under different names. 
+where Poincar\'e--Friedrichs inequalities have appeared under different names. 
 Let us assume for a moment that $\Omega$ is a weakly Lipschitz domain with trivial topology, and consider only the Hilbert case $p=2$. 
@@
 At each step, the we choose a simplex that shares a face with one of the preceding simplices and adjust the constant of integration of the local potential. 
-The global potential is contructed cell by cell until the entire domain is exhausted. 
+The global potential is constructed cell by cell until the entire domain is exhausted. 
 Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
@@
 
-% 4. hightlight the difficulty with the kernels
+% 4. highlight the difficulty with the kernels
 
@@
     % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by chua and Wheeden
-    % DONE: chua Wheeden upper bound is not optimal!
+    % DONT: insert the original inequality by Chua and Wheeden
+    % DONE: Chua Wheeden upper bound is not optimal!
     % DONE: Theorem 1.2 in Chua Wheeden 

### 2024-10-08 intro.tex
clean up

@@
 
+\cye{Computable constants for Lipschitz domains have recently been addressed in Pauly and Valdman~\cite{Paul_Vald_PF_grad_curl_div_20}, see also the references therein.}
+
+Extending our method to vector fields--specifically for the curl and divergence operators introduces new challenges due to their infinite-dimensional kernels. 
+To address these challenges, we generalize the sequential construction used for the gradient to develop vector potentials. 
+The basic inductive strategy remains: 
+we start by constructing a potential over a single simplex and then extend it to neighboring simplices. 
+However, unlike in the gradient case, the potentials over adjacent simplices may not have matching tangential traces along their shared interfaces.
+
+To ensure the correct continuity properties of the vector potentials, we impose stronger conditions on the triangulations.
+We require that the intermediate subtriangulations formed during the sequential process are manifolds with boundary, and that the interface between the existing subtriangulation and the new simplex is a boundary submanifold of both.
+Under these conditions--which are satisfied by shellable triangulations--we can define well-posed auxiliary problems for the curl and divergence operators with partial boundary conditions.
+By iterating this procedure, we exhaust the entire triangulation and obtain the desired potentials.
+Our main results for the curl and divergence operators are presented in Theorems \ref{theorem:poincarefriedrichsestimate} and \ref{theorem:poincarefriedrichsestimate:exterior}.
+
+Shellability is a well-established concept in discrete geometry and combinatorics, referring to a property of simplicial or polytopal complexes that allows them to be built sequentially in a controlled manner.
+A triangulation is shellable if it can be assembled by adding one simplex at a time such that each new simplex shares a boundary submanifold with the existing complex.
+This property ensures that interfaces between simplices are well-behaved, which is crucial for the continuity of vector potentials.
+
+While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions--patches of simplices sharing a common vertex, edge, face, or nn-simplex.
+These local patches are inherently shellable, making our approach widely applicable.
+For more details on shellability, see Kozlov \cite{kozlov2008combinatorial} and Ziegler \cite{ziegler1995lectures}.
+
 \begin{remark} \label{remark:reg_Poinc_Bog}

### 2024-10-08 main.tex
clean up

@@
 
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
 \author{
@@
 We remark that for the purposes of this manuscript, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems.
-% Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.
 
@@
 There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices. 
-% TODO V & V do the same sequential estimate 
 Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
 Naturally, their estimates depend on the shape regularity of the mesh.
-Another class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
-% Starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
+A whole class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
 The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
@@
 The main objective of this manuscript is the construction of potentials for the gradient, curl, and divergence, and more generally the exterior derivative. 
-The operator norms of our potentials satisfy computable upper bounds, which are computable upper bounds of the Poincar\'e--Friedrichs constants.
-As we elaborate in what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases.
-Towards that goal, we also devote an important effort specifically to convex domains.
+The operator norms of our potentials satisfy computable upper bounds, thus yielding computable upper estimates of the Poincar\'e--Friedrichs constants as well. 
+As we will elaborate in what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases. 
+To that end, we also devote an important effort specifically to convex domains.
 
@@
 
-The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is two-fold: 
+The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is twofold: 
 firstly, they are of evident independent interest, and secondly, we will need them as a component for our main results on triangulations. 
@@
 
-We also address the construction of potential operators for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions.
+We also address the construction of potential operators for the gradient, curl, divergence, and more generally the exterior derivative over a simplex subject to partial boundary conditions. 
 We are not aware of explicit estimates or regularized potential operators for these boundary conditions in the published literature. 
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions.
+we want to find the unique vector field potential that not only is a preimage under the curl operator but that also has vanishing tangential trace along the same three faces. 
+We achieve this by constructing an auxiliary problem subject to full boundary conditions,
 so that we can build upon the regularized Bogovski\u{\i} operators and the Poincar\'e--Friedrichs inequalities subject to boundary conditions on the entire boundary.
@@
 
-Our main objective remains to find potential operators for the differential operators of vector calculus and exterior calculus, including the curl and the divergence, over triangulated domains. 
-The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
-In light of the different approaches listed before, we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, and that do not depend on the boundary regularity of the domain.
-
+Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
+The operator norms of these potentials will serve as computable Poincar\'e--Friedrichs constants. 
+In light of the different approaches iscussed above, we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
 % 2. the gradient construction as blueprint 
@@
 
-The sequential construction of potentials for gradient vector fields, as discussed above, is well-known in the literature and serves as our conceptual blueprint.
-Gradient potentials are easily computed over each individual simplex but the constants of integration will generally not match: the scalar piecewise potential will be a in broken Sobolev space. 
-In particular, the local potentials will only differ by a constant along the simplex boundary. 
-However, we can generate an actual potential in Sobolev spaces over larger and larger intermediate subdomains that we build up sequentially.
-At each step, the we choose a simplex that shares a face with one of the preceding simplices and adjust the constant of integration of the local potential. 
-The global potential is constructed cell by cell until the entire domain is exhausted. 
-Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+The sequential construction of potentials for gradient vector fields, as discussed earlier, is well-established in the literature and serves as our conceptual blueprint. 
+Gradient potentials are easily computed over each individual simplex, but the constants of integration generally do not match: 
+the scalar piecewise potential will belong to a broken Sobolev space. 
+In particular, the local potentials will differ only by a constant along the simplex boundaries. 
+However, we can produce a potential in Sobolev spaces over increasingly larger intermediate subdomains, which we construct sequentially. 
+At each step, we select a simplex that shares a face with one of the previously processed simplices and adjust the constant of integration of the local potential. 
+The global potential is built cell by cell until the entire domain is covered. 
+Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate}.
 
@@
 
-We generalize this sequential construction of potentials to curl, the divergence, and the exterior derivative. 
-However, we need to overcome new challenges here that are due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
+We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
+However, we need to overcome new challenges that are arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
 The basic inductive strategy remains the same. 
-We start by constructing, say, a curl potential, over a single simplex. 
-Having already defined a potential operator over a subtriangulation, we choose a neighboring simplex whose intersection with the preceding simplices includes at least one common face. 
-We then construct a potential for the curl operator whose tangential traces along the intersection match the already existing potential.
-Repeating this procedure eventually completes the original triangulation and provides the desired potential.
+We start by constructing, say, a curl potential over a single simplex. 
+Having already defined a potential operator over a subtriangulation, we select a neighboring simplex whose intersection with the preceding simplices includes at least one common face. 
+We then construct a potential for the curl operator whose tangential traces along the intersection match those of the already existing potential.
+Repeating this procedure eventually exhausts the original triangulation. 
 Here, Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} is our main result.
@@
 
-However, unlike for the potential construction of the gradient, is not immediately evident whether the construction of local curl potential with given tangential traces is a well-posed auxiliary problem.
-For the case of the gradient, it was sufficient that the sequential traversal of the triangulation ensured that each new simplex shares at least one face with one of previous simplices was sufficient.
+However, unlike in the potential construction of the gradient, it is not immediately evident whether the construction of the local curl potential with given tangential traces is a well-posed auxiliary problem.
+For the case of the gradient, it is sufficient that the sequential traversal of the triangulation satisfies that each new simplex shares at least one face with one of the previous simplices. 
 For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive: 
@@
 
-% 4. introduce shellable
-
-Shellable simplicial complexes, and more generally polytopal complexes, are a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}, and the references therein.
-Any shellable simplicial complexes must necessarily triangulate a contractible space. 
+% 5. Shellable
+Shellable simplicial complexes, and more generally polytopal complexes, are a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures}, and the references therein.
+Any shellable simplicial complex must necessarily triangulate a contractible space. 
 With respect to our main interest, local patches (stars) in 2D and 3D triangulations are shellable.
 
-% 5. Contractible 
-Inspired by contractibility of shellable triangulations, we pursuit an additional estimate for Poincar\'e--Friedrichs constants. 
+% 6. Contractible 
+Inspired by the contractibility of shellable triangulations, we pursuit an additional estimate for Poincar\'e--Friedrichs constants. 
 Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 

### 2024-10-08 main.tex
Update on Overleaf.

@@
 
+\usepackage{xcolor}          % 
 \usepackage{comment}          % 
@@
     colorlinks=true,
-    linkcolor=green,    % Color of internal links (sections)
+    linkcolor=Maroon,    % Color of internal links (sections)
     citecolor=red,    % Color of citations
@@
 
-% \tableofcontents
+\tableofcontents
 
@@
 
-\subsubsection{Review: General results}
+\subsubsection{General results}
 
@@
 
-\subsubsection{Review: Analytical constants over convex domains}
+\subsubsection{Analytical constants over convex domains}
 
@@
 
-\subsubsection{Review: Domains star-shaped with respect to a ball}
+\subsubsection{Domains star-shaped with respect to a ball}
 
@@
 
-\subsubsection{Review: Triangulated domains}
+\subsubsection{Triangulated domains}
 
@@
 
-\subsubsection{Objectives: convex domains}
+\subsubsection{Convex domains}
 
@@
 
-\subsubsection{Objectives: Potentials subject to partial boundary conditions}
+\subsubsection{Potentials subject to partial boundary conditions}
 
@@
 
-\subsubsection{Objective: Main results}
+\subsubsection{Main results}
 
@@
 In light of the different approaches iscussed above, we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
+
 % 2. the gradient construction as blueprint 
@@
 The global potential is built cell by cell until the entire domain is covered. 
-Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate}.
+Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
 
@@
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
 We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, 
@@
     \end{CD}
-    \cye{\, ,}
+    \, ,
     \end{gather*}
@@
     \end{CD}
-    \cye{\,.}
+    \,.
     \end{gather*}

### 2024-10-09 main.tex
Update on Overleaf.

@@
     \leq 
-    \vol_{n-1}(S_1) A(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
+    \vol_{n-1}(S_1) C_{\Bogov}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
     \diam(\Omega)
@@
         \leq 
-        2^{\frac{n-\ell}{p}}
-        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
+        2^{\frac{n-\ell}{p} + n + 1}
+        %2^{n+1} 
+        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
         \algebraicshapemeasure(T)^{k-1}
@@
 which relies on estimates for the Bogovski\u{\i} operator over an auxiliary reference domain.
-Our experiments over triangles and tetrahedra indicate that we overestimate the constant by several magnitudes.
+We compare computed Poincar\'e--Friedrichs constants over the tetrahedron with tangential boundary conditions along a few faces.
+Our experiments and tetrahedra indicate that we overestimate the constant by several magnitudes.
 %
@@
 Numerical examples indicate that this holds for $p=2$.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c|c|c|c|c|c}
+        \hline
+        $\ell$ & simulation & theorem & ratio & GS & ratio \\
+        \hline
+        0 & 5.37161130e+00 & 6.96498956e+03 & 2.41385574e+02 & 1.34450672e+01 & 2.50298587e+00 \\ 
+        1 & 4.08721544e+00 & 2.46249567e+03 & 1.47407784e+02 & 1.90141963e+01 & 4.65211501e+00 \\
+        2 & 6.42794893e+00 & 8.20831891e+02 & 1.98659522e+01 & 2.68901344e+01 & 4.18331487e+00 \\
+        3 & 6.71227069e+00 & 6.15623918e+02 & 1.36639593e+01 & 3.80283927e+01 & 5.66550344e+00 \\
+        3 & 6.71227069e+00 & 2.51327412e+02 & 5.57828803e+00 & 7.76251317e+00 & 1.15646605e+00 \\
+        \hline
+    \end{tabular}
+    \caption{Estimated $L^2$ Poincar\'e--Friedrichs constants of the curl operator over the unit tetrahedron with tangential boundary conditions along $\ell$ faces. 
+    The first column contains estimates obtained by numerical simulation with lowest-order N\'ed\'elec elements, via solving an eigenvalue problem.
+    The second column contains estimates obtained via     Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} in the first four lines
+    and Theorem~\ref{theorem:bogovpoinc} in the last line. 
+    The fourth column uses the same type of estimate but replaces all applications of Theorem~\ref{theorem:bogovpoinc} with an estimate by Guerini and Savo~\cite{guerini2004eigenvalue}.
+    The last estimate, though clearly the most competitive, technically does not apply because the reference proves it only for bounded convex domains with smooth boundaries.
+    }
+    % Guerini savo : sqrt(3/2) exp(3/2) * D = 7.7625131735516560875716574146153971065689036068355180671108813262 > 6.71227069e+00
+\end{table}
 

### 2024-10-11 main.tex
remark on the recursive estimate

--- 2024-10-08 main.tex
@@
 }
+\date{}
 
@@
 \end{proof}
+
+\begin{remark}
+    \color{red}
+    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+    The potential $w$ for the gradient $\nabla u$ satisfies 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
+        \qquad 
+        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
+    \end{align*}
+    where $A_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
+    Unwrapping the recursion for the norm over the $m$-th simplex, we thus get
+    \begin{align}\label{math:fullrecursivesum}
+        \| w \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        \sum_{\ell=0}^{m} \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+        =:
+        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+        .
+    \end{align}
+    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \sum_{\ell=0}^{M} 
+        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+        \right)
+        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
+    \color{green}Hence 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \sum_{\ell=0}^{M} 
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+        \\&
+        \leq 
+        \max_{0 \leq \ell \leq M} \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \delta_{m,\ell} 
+        \right)
+        \cdot 
+        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        \\&
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)
+        \cdot 
+        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        .
+    \end{align}
+    Now, if $q \leq p$, that is, $2 \leq p$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \left(
+            \sum_{\ell'=0}^{M}
+            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
+        \right)^{\frac 1 q}
+        .
+    \end{align}
+    Instead if $p \leq q$, that is, $p \leq 2$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
+        .
+    \end{align}
+    So in any case, it is better than using the following Minkowski's inequality: 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
+        \\&
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
+        \| \nabla u \|_{L^{p}(\Omega)}
+        .
+    \end{align}
+\end{remark}
 

### 2024-10-11 main.tex
improved lemma

@@
     The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is instance of a so-called \emph{shape measure}.
-    For example, the reference triangle has aspect shape measure $1$ and the reference tetrahedron has aspect shape measure $\sqrt{3/2}$. 
+    For example, the reference triangle has aspect shape measure $2$ and the reference tetrahedron has aspect shape measure $\sqrt{6}$. 
     Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
@@
         \diam(F)
+        \leq 
+		\aspectratio(T_1)
+        \diam(T_2)
         ,
@@
     \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
+    If $\Xi : T_1 \rightarrow T_2$ is the affine diffeomorphism that is the identity over $F$, then 
     \begin{align*}
@@
         \leq 
-        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
+        \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2}
+        % ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
         % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
@@
     Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    Writing $h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \left( 1 + \aspectratio(T_2) \right)
-        \aspectratio(T_1)
-        .
-    \end{align*}
+    We estimate the Lipschitz constant of $\Xi$ as follows. 
+    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and contains the origin, 
+	and the unit height vector $h_0$ goes in the direction of the vertex $z_1$ is in the $n$-th coordinate direction.
+    Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha h_0$ and $x' = b' + \alpha' h_0$.
+    Since $\Xi(h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
+    \begin{align*}
+        \| \Xi(x) - \Xi(x') \|
+        \leq  
+        \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
+        \leq  
+        \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| h_0 \|
+        \leq 
+        \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
+        .
+    \end{align*}
+    % Writing $h_0$ for the unit normal in direction $z_1$, we have 
+    % \begin{align*}
+        % \Xi(x) 
+        % = 
+        % x 
+        % - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
+        % + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
+        % ,
+        % \qquad 
+        % x \in \bbR^{n}
+        % .
+    % \end{align*}
+    % Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
+    % By the Xu-Zikanatov estimate,
+    % \begin{align*}
+        % \matnorm{ \Jacobian \Xi }
+        % \leq 
+        % \frac{ \diam(T_1) }{ \height(T_1) }
+        % +
+        % \frac{ \diam(T_2) }{ \height(T_1) }
+        % \leq 
+        % \left( 1 + \aspectratio(T_2) \right)
+        % \aspectratio(T_1)
+        % .
+    % \end{align*}
     The desired estimates are shown.
@@
 
-\begin{remark}
+\begin{remark}\label{remark:fullrecursivesum}
     \color{red}
@@
         \qquad 
-        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
-    \end{align*}
-    where $A_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
-    Unwrapping the recursion for the norm over the $m$-th simplex, we thus get
+        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
+        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
+    \end{align*}
+    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
+    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
     \begin{align}\label{math:fullrecursivesum}
@@
         \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+        +
+        \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
         =:
@@
         \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
+        % \\&
         \leq 
@@
     In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
+    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
+    % \begin{align*}
+        % \| w \|_{L^{p}(\Omega)}^{p}
+        % &
+        % \leq 
+        % \sum_{m=0}^{M}
+        % \| w \|_{L^{p}(T_{m})}^{p}
+        % \\&
+        % \leq 
+        % \sum_{m=0}^{M}
+        % L^{\frac p q}
+        % \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+        % \leq 
+        % L^{\frac p q}
+        % \sum_{m=0}^{M} 
+        % \max_{ 0 \leq \ell \leq M }
+        % C_{m,\ell}^{p} 
+        % \cdot 
+        % \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        % ,
+    % \end{align*}
+
     \color{green}Hence 

### 2024-10-19 draft.tex
some proofreading, potential operators, mixed bc pf inequality

@@
 We should unify.}
+
+\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
+    Let $T$ be an $n$-simplex 
+    and let $\Gamma = F_{1} \cup \dots \cup F_{\ell}$ be the union of $\ell+1$ different faces of $T$. 
+    Suppose that $u \in W^{2}\Lambda^{k}(T)$ such that 
+    $\trace_{T,\Gamma} u = 0$.
+    Then there exists $w \in W^{2}\Lambda^{k}(T)$ such that 
+    $\trace_{T,\Gamma} w = 0$
+    and  
+    \begin{align*}
+        \cartan w = \cartan u,
+        \quad 
+        \| w \|_{L^{2}(\Omega)} 
+        \leq 
+        C_{\PF,\Gamma,\ell,k,2}(T)
+        \| \cartan u \|_{L^{2}(\Omega)}
+        .
+    \end{align*}
+    Here, $C_{\PF,\Gamma,\ell,k,2}(T) > 0$ is a constant such that 
+    \begin{align*}
+        C_{\PF,\Gamma,\ell,k,2}(T)
+        \leq 
+        \diam(T)
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    If $\ell = n$, then the Poincar\'e--Friedrichs constant is obtained via duality from the case without boundary conditions, 
+    so we only consider the case $\ell < n$.
+    There exists an affine bijection $\varphi : \Delta^n \rightarrow T$ 
+    that maps 
+    the face of $\Delta^n$
+    orthogonal to the $i$-th coordinate axis, written $\hat F_{i} \subseteq \Delta^n$ here, is mapped onto the face $F_{i-1}$ for $1 \leq i \leq \ell+1$.
+    We write $\hat \Gamma := \hat F_{1} \cup \dots \cup \hat F_{\ell+1}$.
+    Note that $\hat\Gamma$ does not include the face of the reference simplex whose vertices are the $n$ canonical unit vectors.
+
+    Let $\hat u \in W^{2}\Lambda^{k}(\hat T)$ such that $\trace_{\hat T,\hat\Gamma} u = 0$.
+    By exactness of the de~Rham complex over the reference with simplex 
+    with tangential boundary conditions along $\hat\Gamma$, which is a topological ball, 
+    we conclude that there exists $w \in W^{2}\Lambda^{k}(T)$ satisfying the conditions $\trace_{T,\Gamma} w = 0$
+    and $\cartan w = \cartan u$ and such that $w$ has minimal norm among the members of $W^{2}\Lambda^{k}(T)$ satisfying these two conditions.
+    Under these conditions, we have the Gaffney inequality 
+    \begin{align}\color{red}
+        \| \nabla \hat w \|_{L^{2}(\Delta^{n})}
+        \leq 
+        C_{??}
+        \| \cartan \hat w \|_{L^{2}(\Delta^{n})}
+        .
+    \end{align}
+    We write $w$ as in \eqref{math:canonicalrepresentation},
+    \begin{gather}
+        w
+        = 
+        \sum_{ \sigma \in \Sigma(k,n) } 
+        w_{\sigma} \, 
+        \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
+    \end{gather}
+    If $\sigma \in \Sigma(k,n)$ and its range does not contain some $1 \leq i \leq \ell+1$,
+    then the boundary conditions imply that $\trace_{T,F_{i}} w_{\sigma} = 0$.
+    Then Friedrichs inequality with partial boundary conditions, Lemma~\ref{lemma:mixedbconsimplex},
+    implies 
+    \begin{align*}
+        \| w_{\sigma} \|_{L^{2}(T)}
+        &
+        \leq 
+        \frac{\diam(T)}{\sqrt{2}}
+        \| \nabla w \|_{L^{2}(T)}
+        .
+    \end{align*}
+    We then define $w'_{\sigma} := w_{\sigma}$.
+
+    If $\sigma \in \Sigma(k,n)$ and its range does not contain any $1 \leq i \leq \ell+1$,
+    then no boundary conditions are imposed on that component but the classical Poincar\'e--Friedrichs inequality implies 
+    \begin{align*}
+        \| w_{\sigma} - w_{\sigma,\Omega} \|_{L^{2}(T)}
+        &
+        \leq 
+        \frac{\diam(T)}{\pi}
+        \| \nabla w \|_{L^{2}(T)}
+        .
+    \end{align*}
+    We then define $w'_{\sigma} = w_{\sigma} - w_{\sigma,\Omega}$.
+
+    This defines a new differential form 
+    \begin{gather}
+        w'
+        = 
+        \sum_{ \sigma \in \Sigma(k,n) } 
+        w'_{\sigma} \, 
+        \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}
+        \in
+        W^{2}\Lambda^{k-1}(\Omega)
+    \end{gather}
+    that satisfies $\cartan w' = \cartan u$ and $\trace_{\hat T,\hat\Gamma} w' = 0$. By construction, 
+    \begin{align*}
+        \| w' \|_{L^{2}(\hat T)}
+        \leq 
+        \| w \|_{L^{2}(\hat T)}
+        \leq 
+        2^{-\frac 1 2}
+        \| \nabla w \|_{L^{2}(\hat T)}
+        \leq 
+        2^{-\frac 1 2}
+        C_{??} % TODO
+        \| \cartan u \|_{L^{2}(\hat T)}
+        .
+    \end{align*}
+
+    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
+    \begin{align*}
+        \| w \|_{L^{p}(T)}
+        &\leq 
+        |\det(\Jacobian \varphi)|^{\frac 1 p} 
+        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
+        \| \tilde w \|_{L^{p}(\Delta^n)}
+        ,
+        \\
+        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
+        \leq 
+        2^{\frac {n-\ell} p}
+        \| \hat g \|_{L^{p}(\Delta^n)}
+        &\leq 
+        2^{\frac {n-\ell} p}
+        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
+        \matnorm{\Jacobian \varphi}^{k}
+        \cdot 
+        \| \cartan u \|_{L^{p}(T)}
+        .
+    \end{align*}
+    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. 
+\end{proof}
 

### 2024-10-19 main.tex
some proofreading, potential operators, mixed bc pf inequality

--- 2024-10-11 main.tex
@@
 \usepackage{fullpage}
-\usepackage[margin=0.1cm]{geometry}
+% \usepackage[margin=0.1cm]{geometry}
 \input{header}
 
-\usepackage{xcolor}          % 
 \usepackage{comment}          % 
@@
     colorlinks=true,
-    linkcolor=Maroon,    % Color of internal links (sections)
+    linkcolor=green,    % Color of internal links (sections)
     citecolor=red,    % Color of citations
@@
 
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations}
 \author{
@@
 }
-\date{}
 
@@
 Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
+However, while potentials and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
 quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.
 
-This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrichs inequalities for the differential operators of vector calculus. 
+This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrich inequalities for the differential operators of vector calculus. 
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
@@
 Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally difficult. 
-Attention has been given to \emph{linear} potential operators instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}. 
+Attention has been given to \emph{linear} potentials instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}. 
 The operator norm of any linear potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
@@
 The relationship between the Poincar\'e constant and the Poincar\'e--Friedrichs constant will be elaborated upon in later sections of this manuscript. 
-% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:intro:gradientpotential}.
+% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potentials to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potentials such as~\eqref{math:intro:gradientpotential}.
 
@@
 
-We study potential operators and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
+We study potentials and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
 There are substantial changes and much less results are available in the literature. 
@@
 In the Banach space case, it is not even trivial whether a norm-minimizing potential actually exists. 
-We are therefore interested in any potential operators 
+We are therefore interested in any potentials 
 \begin{align}
@@
 
-\subsubsection{General results}
+\subsubsection{Review: General results}
 
@@
 The core challenges can be found in the discussion of the curl operator in three dimensions,
-where Poincar\'e--Friedrichs inequalities have appeared under different names. 
+where Poincar\'e--Friedrich inequalities have appeared under different names. 
 Let us assume for a moment that $\Omega$ is a weakly Lipschitz domain with trivial topology, and consider only the Hilbert case $p=2$. 
@@
 
-\subsubsection{Analytical constants over convex domains}
+\subsubsection{Review: Analytical constants over convex domains}
 
@@
 
-\subsubsection{Domains star-shaped with respect to a ball}
+\subsubsection{Review: Domains star-shaped with respect to a ball}
 
@@
 such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
-In principle, the operator norms of those potential operators as mapping between Lebesgue spaces of differential forms 
+In principle, the operator norms of those potentials as mapping between Lebesgue spaces of differential forms 
 are upper estimates for the Poincar\'e--Friedrichs constants of the domain. 
@@
 
-\subsubsection{Triangulated domains}
+\subsubsection{Review: Triangulated domains}
 
@@
 We remark that for the purposes of this manuscript, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems. 
+% Our approaches, in contrast, are either analytical or combinatorial, and in any case we only employ the given geometry but no computer simulation.
 
@@
 There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices. 
+% TODO V & V do the same sequential estimate 
 Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
 Naturally, their estimates depend on the shape regularity of the mesh.
-A whole class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
+Another class of upper bounds for Poincar\'e--Friedrichs inequalities uses some form of passing through the triangulation and constructs the potentials step-by-step. 
+% Starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
 The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
@@
 The main objective of this manuscript is the construction of potentials for the gradient, curl, and divergence, and more generally the exterior derivative.
-The operator norms of our potentials satisfy computable upper bounds, thus yielding computable upper estimates of the Poincar\'e--Friedrichs constants as well. 
-As we will elaborate in what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases. 
-To that end, we also devote an important effort specifically to convex domains.
-
-\subsubsection{Convex domains}
+The operator norms of our potentials satisfy computable upper bounds, which are computable upper bounds of the Poincar\'e--Friedrichs constants.
+As we elaborate in what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases.
+Towards that goal, we also devote an important effort specifically to convex domains.
+
+\subsubsection{Objectives: convex domains}
 
@@
 
-The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is twofold: 
+The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is two-fold: 
 firstly, they are of evident independent interest, and secondly, we will need them as a component for our main results on triangulations. 
@@
 and we use simpler (constant) weight functions. 
-While the resulting potential operators feature generally lower regularity, they are conductive for our purposes. 
+While the resulting potentials feature generally lower regularity, they are conductive for our purposes. 
 Crucially, this allows us to easily estimate their operator norms and thus bound Poincar\'e--Friedrichs constants.
 
-\subsubsection{Potentials subject to partial boundary conditions}
-
-We also address the construction of potential operators for the gradient, curl, divergence, and more generally the exterior derivative over a simplex subject to partial boundary conditions. 
-We are not aware of explicit estimates or regularized potential operators for these boundary conditions in the published literature. 
+\subsubsection{Objectives: Potentials subject to partial boundary conditions}
+
+We also address the construction of potentials for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions. 
+We are not aware of explicit estimates or regularized potentials for these boundary conditions in the published literature. 
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that not only is a preimage under the curl operator but that also has vanishing tangential trace along the same three faces. 
-We achieve this by constructing an auxiliary problem subject to full boundary conditions,
+we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
+We achieve this by constructing an auxiliary problem subject to full boundary conditions.
 so that we can build upon the regularized Bogovski\u{\i} operators and the Poincar\'e--Friedrichs inequalities subject to boundary conditions on the entire boundary.
@@
 
-\subsubsection{Main results}
+\subsubsection{Objective: Main results}
+
+% 3. hightlight the difficulty with the kernels
+% 4. introduce shellable
+% 5. Apply shellable triangulations
+% 6. Contractible 
+% [ ] remove face-connected completely
 
@@
 
-Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
-The operator norms of these potentials will serve as computable Poincar\'e--Friedrichs constants. 
-In light of the different approaches iscussed above, we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
+Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, including in particular the curl and divergence, over triangulated domains. 
+The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
+In light of the different approaches listed before, 
+we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
+and that do not depend on the boundary regularity of the domain.
+
+% In this work, we aim to construct linear potentials for the gradient, curl, and divergence on triangulated domains, 
+% providing explicitly computable upper bounds. Our approach extends to domains that may be non-convex and non-star-shaped, 
+% focusing on triangulations that are face-connected or possess the special property of shellability.
 
@@
 
-The sequential construction of potentials for gradient vector fields, as discussed earlier, is well-established in the literature and serves as our conceptual blueprint. 
-Gradient potentials are easily computed over each individual simplex, but the constants of integration generally do not match: 
-the scalar piecewise potential will belong to a broken Sobolev space. 
-In particular, the local potentials will differ only by a constant along the simplex boundaries. 
-However, we can produce a potential in Sobolev spaces over increasingly larger intermediate subdomains, which we construct sequentially. 
-At each step, we select a simplex that shares a face with one of the previously processed simplices and adjust the constant of integration of the local potential. 
-The global potential is built cell by cell until the entire domain is covered. 
+\mwl{
+The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
+Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
+along the interfacing intersection, the two potentials will only differ by a constant, 
+and that difference can easily be removed to ensure continuity across that interface. 
+Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
+}
+
+The sequential construction of potentials for gradient vector fields, as discussed above, 
+is well-known in the literature and serves as our conceptual blueprint.
+% TODO: improve the description here.
+We start by constructing a scalar potential over a single simplex
+and successively define scalar potentials over larger and larger intermediate subtriangulations until the full domain is finally exhausted.
+At each step, we construct a potential over some successive simplex that shares a face with one of the preceding simplices.
+The difference of the two scalar potentials along that interface is a constant,
+and we can easily fix the constant along the shared face to build the extend the scalar potential. 
 Our main result in this context is Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
 
-% 3. generalization to vector fields
-
-We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
-However, we need to overcome new challenges that are arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
+% 
+For the gradient operator, our method involves a straightforward sequential traversal of the triangulation. 
+Each simplex is connected to the preceding ones via a shared (n?1)(n?1)-dimensional face. 
+We construct a gradient potential over each new simplex, and since the kernel of the gradient consists solely of constants, 
+we can fix the constant by matching the value on the shared face.
+
+% seq construction 
+In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, 
+where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face. 
+We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, 
+formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+Extending our method to vector fields, specifically for the curl and divergence operators introduces new challenges due to their infinite-dimensional kernels. 
+To address these challenges, we generalize the sequential construction used for the gradient to develop vector potentials. 
+The basic inductive strategy remains: 
+we start by constructing a potential over a single simplex and then extend it to neighboring simplices. 
+However, unlike in the gradient case, the potentials over adjacent simplices may not have matching tangential traces along their shared interfaces.
+
+To ensure the correct continuity properties of the vector potentials, we impose stronger conditions on the triangulations.
+We require that the intermediate subtriangulations formed during the sequential process are manifolds with boundary, and that the interface between the existing subtriangulation and the new simplex is a boundary submanifold of both.
+Under these conditions, which are satisfied by shellable triangulations, we can define well-posed auxiliary problems for the curl and divergence operators with partial boundary conditions.
+By iterating this procedure, we exhaust the entire triangulation and obtain the desired potentials.
+Our main results for the curl and divergence operators are presented in Theorems \ref{theorem:poincarefriedrichsestimate
+} and \ref{theorem:poincarefriedrichsestimate:exterior
+}.
+
+Shellability is a well-established concept in discrete geometry and combinatorics, referring to a property of simplicial or polytopal complexes that allows them to be built sequentially in a controlled manner.
+A triangulation is shellable if it can be assembled by adding one simplex at a time such that each new simplex shares a boundary submanifold with the existing complex.
+This property ensures that interfaces between simplices are well-behaved, which is crucial for the continuity of vector potentials.
+
+While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions, patches of simplices sharing a common vertex, edge, face, or nn-simplex.
+These local patches are inherently shellable, making our approach widely applicable.
+For more details on shellability, see Kozlov \cite{kozlov2008combinatorial} and Ziegler \cite{ziegler1995lectures}.
+
+\subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
+
+Towards our main objective of constructing linear potentials for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
+
+Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
+
+For vector fields, new challenges arise because of the infinite-dimensional kernels. 
+We, however, overcome these challenges and succeed in generalizing the sequential construction of the potential operator for the gradient to vector potentials, including in particular the curl and divergence.
+The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. 
+Having already defined a potential operator over a set of simplices that we term a subtriangulation, 
+we then construct a potential over a simplex neighboring through some $(n-1)$-dimensional faces. 
+However, the potential on the new simplex might here not have the same tangential trace along the interface between the new simplex and the previous ones. 
+Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations. 
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
+With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
+
+We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
 The basic inductive strategy remains the same. 
-We start by constructing, say, a curl potential over a single simplex. 
-Having already defined a potential operator over a subtriangulation, we select a neighboring simplex whose intersection with the preceding simplices includes at least one common face. 
-We then construct a potential for the curl operator whose tangential traces along the intersection match those of the already existing potential.
-Repeating this procedure eventually exhausts the original triangulation. 
-Here, Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} is our main result.
-
-% 4. highlight the difficulty with the kernels
-
-However, unlike in the potential construction of the gradient, it is not immediately evident whether the construction of the local curl potential with given tangential traces is a well-posed auxiliary problem.
-For the case of the gradient, it is sufficient that the sequential traversal of the triangulation satisfies that each new simplex shares at least one face with one of the previous simplices. 
-For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive: 
-we ensure that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
-This allows us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex. 
-Whether a triangulation admits such a particular traversal is a non-trivial condition and defines the class of \emph{shellable} triangulations.
-
-% 5. Shellable
-Shellable simplicial complexes, and more generally polytopal complexes, are a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures}, and the references therein.
-Any shellable simplicial complex must necessarily triangulate a contractible space. 
-With respect to our main interest, local patches (stars) in 2D and 3D triangulations are shellable.
-
-% 6. Contractible 
-Inspired by the contractibility of shellable triangulations, we pursuit an additional estimate for Poincar\'e--Friedrichs constants. 
-Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
-Their bi-Lipschitz constants are controlled by the shape regularity of the domain. 
-This reduces the construction of potentials over shellable triangulations to the construction of potentials over convex domains.
-We refer to Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} as the main result of this approach.
+We start by constructing, say, a curl potential, over a single simplex. 
+Having already defined a potential operator over a subtriangulation, 
+we then construct a potential over a neighboring simplex. 
+However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex. 
+% 
+To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials. 
+We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex.
+Under those conditions, which are met by so-called \textit{shellable} triangulations, 
+we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions. 
+Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+
+Shellable triangulations are defined by a special constructive property:
+we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
+Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
+Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case.
+In particular, local stars in 2D and 3D triangulations are shellable.
+
+% exterior PF 
+\cye{Our main result for the curl and divergence operators (Section~\ref{section:intro_curl_div}) and more generally in the exterior calculus setting (Section~\ref{section:intro_EC}) for triangulated domains are Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} and~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+They treat triangulated domains that can be non-convex and non-star-shaped but where the triangulation is shellable.
+As discussed above, though this is slightly less generic than merely face-connected triangulations, this namely covers patches of simplices sharing a given vertex, edge, face, or $n$-simplex (stars) in two and three space dimensions, since these local patches are shellable.
+The dependencies of the obtained computable Poincar\'e--Friedrichs constants are similar to those of the gradient operator in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
+
+\begin{remark}
+    % TODO: Reintegrate in that section
+    \mwl{MV: remark from after Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.} 
+    The computable Poincar\'e--Friedrichs constants obtained here depend on only a few parameters of the given triangulation: 
+    the length of any traversal from the root simplex, the ratios of the volumes of any pair of adjacent simplices, 
+    and the Poincar\'e--Friedrichs constants on each face patch or each simplex. 
+    %, and the Poincar\'e--Friedrichs constant of the initial simplex. 
+    Here, Poincar\'e--Friedrichs constants on face patches are estimated in terms of shape regularity parameters of the triangulation; 
+    if the face patches of the triangulation are convex, then better estimates are possible. 
+\end{remark}
 
@@
 We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
-We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.
+We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potentials.
 We review basic notions of triangulations in Section~\ref{section:triangulations}.
@@
 We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
-Our regularized potential operators over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
+Our regularized potentials over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
 giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
@@
 with emphasis on analytical upper bounds over bounded convex domains. 
-We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potential operators.
+We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potentials.
 This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
@@
 
-\subsection{Relationship with potential operators}
+\subsection{Relationship with potentials}
 
@@
 \begin{remark}
-    Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potential operators. 
+    Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potentials. 
     We highlight this perspective because it seems to be most promising when generalizing the discussion to the curl and divergence operators. 
@@
     % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
-    % DONT: insert the original inequality by Chua and Wheeden
-    % DONE: Chua Wheeden upper bound is not optimal!
+    % DONT: insert the original inequality by chua and Wheeden
+    % DONE: chua Wheeden upper bound is not optimal!
     % DONE: Theorem 1.2 in Chua Wheeden 
@@
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
+We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.}
 We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, 
@@
 \begin{remark}
-    \color{red}
-    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    The potential $w$ for the gradient $\nabla u$ satisfies 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
-        \qquad 
-        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
-    \end{align*}
-    where $A_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
-    Unwrapping the recursion for the norm over the $m$-th simplex, we thus get
-    \begin{align}\label{math:fullrecursivesum}
-        \| w \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        \sum_{\ell=0}^{m} \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
-        =:
-        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
-        .
-    \end{align}
-    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \sum_{\ell=0}^{M} 
-        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
-        \right)
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
-    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
-    \color{green}Hence 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \sum_{\ell=0}^{M} 
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        \\&
-        \leq 
-        \max_{0 \leq \ell \leq M} \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \delta_{m,\ell} 
-        \right)
-        \cdot 
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        \\&
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)
-        \cdot 
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        .
-    \end{align}
-    Now, if $q \leq p$, that is, $2 \leq p$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \left(
-            \sum_{\ell'=0}^{M}
-            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
-        \right)^{\frac 1 q}
-        .
-    \end{align}
-    Instead if $p \leq q$, that is, $p \leq 2$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
-        .
-    \end{align}
-    So in any case, it is better than using the following Minkowski's inequality: 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
-        \\&
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
-        \| \nabla u \|_{L^{p}(\Omega)}
-        .
-    \end{align}
-\end{remark}
-
-\begin{remark}
-    The computable Poincar\'e--Friedrichs constants obtained in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} depend on only a few parameters of the given triangulation: 
-    the length of any traversal from the root simplex, 
-    the ratios of the volumes of any pair of adjacent simplices, 
-    and the Poincar\'e--Friedrichs constants on each face patch or each simplex. 
-    Poincar\'e--Friedrichs constants on face patches are estimated in terms of shape regularity parameters of the triangulation; 
-    if the face patches of the triangulation are convex, then better estimates are possible.
-
-    % obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}
-    These computable Poincar\'e--Friedrichs constants increasingly overestimate the best one as the number of $n$-simplices in the triangulation $\calT$ increases. 
+    The Poincar\'e--Friedrichs constants obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimate the best one as the number of $n$-simplices in the triangulation $\calT$ increases.
     Hence, we conceive their target application to be local patches (stars), in particular non-convex boundary stars. 
@@
 Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather*}
+\begin{gather}\label{math:canonicalrepresentation}
     \omega 
@@
     \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather*}
+\end{gather}
 where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
@@
     \end{CD}
-    \, ,
+    \cye{\, ,}
     \end{gather*}
@@
     \end{CD}
-    \,.
+    \cye{\,.}
     \end{gather*}
@@
 
-\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
+\section{Regularized potentials over convex sets}\label{section:potentialoperator}
 
@@
 % % 
-% We bound the norms of regularized potential operators for the exterior derivative over convex domains.
+% We bound the norms of regularized potentials for the exterior derivative over convex domains.
 % We solve this for two special cases:
@@
 either the $L^{p}$ de~Rham complex without boundary conditions, or the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+The corresponding linear potentials are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
 We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 In comparison to their extensive work, our discussion is more modest:
-we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+we study potentials merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
 However, our goal is explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
@@
 We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually converge. 
-In order to analyze the properties of the potential operators,
+In order to analyze the properties of the potentials,
 we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
@@
 
-\subsection{Interaction of potential operators with the exterior derivative}
+\subsection{Interaction of potentials with the exterior derivative}
 
@@
 % 
-Given $a \in \Omega$, we introduce the potential operators 
+Given $a \in \Omega$, we introduce the potentials 
 \begin{align*}
@@
     The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
+    To the best of our knowledge, the work of Costabel and McIntosh~\cite{costabel2010bogovskiui} was the first to propose a regularized Poincar\'e operator (regularized via averaging).
+    These potentials enable the analysis of de~Rham complexes without boundary conditions.
+    % TODO: are these paragraphs in the introduction now?
     The Bogovski\u{\i}-type operators were first studied for the divergence operator and are a staple in the mathematics of hydrodynamics~\cite{bogovskii1979solution}.
+    Their generalization to differential forms was again first discussed by Costabel and McIntosh~\cite{costabel2010bogovskiui}. 
+    In some sense dual to the regularized Poincar\'e operators, they establish the exactness of the $L^{p}$ de~Rham complex with full boundary conditions.
+    % 
+    Costabel and McIntosh regularize the potentials by smoothly averaging over pivot points within an interior ball, 
+    which is why they can study domains star-shaped with respect to a ball. 
+    Instead, we average over the entire domain, which requires a convex geometry. 
+    The resulting potential operators are sufficient for establishing Poincar\'e--Friedrichs constants over bounded convex domains. 
+    The $L^{p}$ continuity constants of the regularized potential operators have not yet been established, to the best of our knowledge.
+
+    The operators discussed by Costabel and McIntosh are pseudo-differential operators of negative order, 
+    because their averaging uses a smooth weight, and thus they are bounded operators between a variety of function spaces. 
+    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
+    have been contributed by Guzman and Salgado~\cite{guzman2021estimation}. % DONE: THEO That requires more comments 
+    % Guzman and Salgado have estimated the operator norm. \mwl{Describe Guzman and Salgado's contribution in more detail.}
+
+    \mwl{ 
     Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
@@
     have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
-    Instead, we average over the entire domain, which requires a convex geometry, 
-	and we are interested in boundedness in the Lebesgue $p$-norms. 
-    We establish computable bounds on the Poincar\'e--Friedrichs constants,
-	which had not been established yet, to the best of our knowledge. 
+    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
+    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
+    This had not been established yet, to the best of our knowledge. 
+    }
 \end{remark}
@@
         \leq 
-        2^{\frac{n-\ell}{p}}
         2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
@@
     and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
-    We observe $\tilde g = \cartan \tilde u$. 
-    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$.
-
-    The bounds for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
-    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
-    with $\cartan \tilde w = \cartan \tilde u$ and 
-    \begin{align*}
-        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
+    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$ with $\tilde g = \cartan \tilde u$.
+    We observe 
+    \begin{align*}
+        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
+        \leq 
+        2^{\frac {n-\ell} p}
+        \| \hat g \|_{L^{p}(\Delta^n)}
+        .
+    \end{align*}
+    \color{red}
+    The bounds for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc}, imply 
+    the existence of $\mathring w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
+    with $\cartan \mathring w = \cartan \tilde u$ and 
+    \begin{align*}
+        \| \mathring w \|_{L^{p}(\widetilde \Makoto)}
         &\leq 
@@
     \end{align*}
+    \color{blue}
+    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $l+1$ through $n$. Thus,
+    \begin{align*}
+        \| \tilde w \|_{L^{p}(\Delta^{n})}
+        =
+        2^{-\frac{n-\ell}{p}}
+        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
+        .
+    \end{align*}
+    Since $\tilde g$ has got the same symmetries, $\cartan \tilde w = \tilde g$.
+    \color{black}
+
     We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\Delta^n} )$.
@@
         \\
-        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        \leq 
-        2^{\frac {n-\ell} p}
         \| \hat g \|_{L^{p}(\Delta^n)}
         &\leq 
-        2^{\frac {n-\ell} p}
         |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 

### 2024-10-19 main.tex

--- 2024-10-11 main.tex
@@
 Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
-However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
+However, while potentials and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
 quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.
@@
 and we use simpler (constant) weight functions. 
-While the resulting potential operators feature generally lower regularity, they are conductive for our purposes. 
+While the resulting potentials feature generally lower regularity, they are conductive for our purposes. 
 Crucially, this allows us to easily estimate their operator norms and thus bound Poincar\'e--Friedrichs constants.
@@
 
-We also address the construction of potential operators for the gradient, curl, divergence, and more generally the exterior derivative over a simplex subject to partial boundary conditions. 
-We are not aware of explicit estimates or regularized potential operators for these boundary conditions in the published literature. 
+We also address the construction of potentials for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions. 
+We are not aware of explicit estimates or regularized potentials for these boundary conditions in the published literature. 
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
@@
 
-Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
-The operator norms of these potentials will serve as computable Poincar\'e--Friedrichs constants. 
-In light of the different approaches iscussed above, we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
+Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, including the curl and divergence in particular, over triangulated domains. 
+The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
+In light of the different approaches listed before, 
+we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
+and that do not depend on the boundary regularity of the domain.
+
+% TODO: Figure out whether to use the following paragraph.
+% Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
+% The operator norms of these potentials will serve as computable Poincar\'e--Friedrichs constants. 
+% In light of the different approaches listed before, 
+% we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
+
+% In this work, we aim to construct linear potentials for the gradient, curl, and divergence on triangulated domains, 
+% providing explicitly computable upper bounds. Our approach extends to domains that may be non-convex and non-star-shaped, 
+% focusing on triangulations that are face-connected or possess the special property of shellability.
 
@@
 
+% TODO: check whether introduction is readable
+% In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, 
+% where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face. 
+% We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, 
+% formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
+
+% Extending our method to vector fields, specifically for the curl and divergence operators introduces new challenges due to their infinite-dimensional kernels. 
+% To address these challenges, we generalize the sequential construction used for the gradient to develop vector potentials. 
+% The basic inductive strategy remains: 
+% we start by constructing a potential over a single simplex and then extend it to neighboring simplices. 
+% However, unlike in the gradient case, the potentials over adjacent simplices may not have matching tangential traces along their shared interfaces.
+
+% To ensure the correct continuity properties of the vector potentials, we impose stronger conditions on the triangulations.
+We require that the intermediate subtriangulations formed during the sequential process are manifolds with boundary, and that the interface between the existing subtriangulation and the new simplex is a boundary submanifold of both.
+Under these conditions, which are satisfied by shellable triangulations, we can define well-posed auxiliary problems for the curl and divergence operators with partial boundary conditions.
+By iterating this procedure, we exhaust the entire triangulation and obtain the desired potentials.
+Our main results for the curl and divergence operators are presented in Theorems \ref{theorem:poincarefriedrichsestimate
+% } and \ref{theorem:poincarefriedrichsestimate:exterior}.
+
+% Shellability is a well-established concept in discrete geometry and combinatorics, referring to a property of simplicial or polytopal complexes that allows them to be built sequentially in a controlled manner.
+A triangulation is shellable if it can be assembled by adding one simplex at a time such that each new simplex shares a boundary submanifold with the existing complex.
+This property ensures that interfaces between simplices are well-behaved, which is crucial for the continuity of vector potentials.
+
+% While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions, patches of simplices sharing a common vertex, edge, face, or nn-simplex.
+These local patches are inherently shellable, making our approach widely applicable.
+For more details on shellability, see Kozlov \cite{kozlov2008combinatorial} and Ziegler \cite{ziegler1995lectures}.
+
+% \subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
+
+% Towards our main objective of constructing linear potentials for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
+
+% Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
+We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
+
+% For vector fields, new challenges arise because of the infinite-dimensional kernels. 
+% We, however, overcome these challenges and succeed in generalizing the sequential construction of the potential operator for the gradient to vector potentials, including in particular the curl and divergence.
+% The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. 
+% Having already defined a potential operator over a set of simplices that we term a subtriangulation, 
+% we then construct a potential over a simplex neighboring through some $(n-1)$-dimensional faces. 
+% However, the potential on the new simplex might here not have the same tangential trace along the interface between the new simplex and the previous ones. 
+% Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
+% Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
+% These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations. 
+% Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
+% With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
+
+% We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
 We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
@@
         \leq 
-        2^{\frac{n-\ell}{p} + n + 1}
-        %2^{n+1} 
+        2^{n+1} 
         n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
@@
 \begin{table}[h!]
-    \centering
+    \centering % TODO: recompute all those numbers
     \begin{tabular}{c|c|c|c|c|c}

### 2024-12-06 draft.tex
minor updates

@@
 \end{proof}
+
+    Lastly, we show a modification of this prove when $p=2$. 
+    We choose $\mathring w \in W^{2}\Lambda^{k}(\widetilde \Makoto)$ to have minimum norm among those members of $W^{2}\Lambda^{k}(\widetilde \Makoto)$ whose exterior derivative equals $\cartan \tilde u$.
+Since then $\tilde w \in W^{2}\Lambda^{k}(\widetilde \Makoto)$ has the same properties,
+    it follows that $\tilde w = \mathring w$.
+
+    Under these conditions, we can use Gaffney's inequality: % TODO: cite specific inequality 
+    $\tilde w \in W^{1,2}(\Omega) \otimes \Alt^{k}(\bbR^{n})$ with 
+    \begin{align}\color{red}
+        \| \nabla \tilde w \|_{L^{2}(\Delta^{n})}
+        \leq 
+        \| \cartan \tilde w \|_{L^{2}(\Delta^{n})}
+        .
+    \end{align} % TODO: what exactly is the norm being measured on the left hand side?
 

### 2024-12-06 main.tex
replace some tabs
minor updates

@@
     \end{align*}
-    % Writing $h_0$ for the unit normal in direction $z_1$, we have 
-    % \begin{align*}
-        % \Xi(x) 
-        % = 
-        % x 
-        % - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        % + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
-        % ,
-        % \qquad 
-        % x \in \bbR^{n}
-        % .
-    % \end{align*}
-    % Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    % By the Xu-Zikanatov estimate,
-    % \begin{align*}
-        % \matnorm{ \Jacobian \Xi }
-        % \leq 
-        % \frac{ \diam(T_1) }{ \height(T_1) }
-        % +
-        % \frac{ \diam(T_2) }{ \height(T_1) }
-        % \leq 
-        % \left( 1 + \aspectratio(T_2) \right)
-        % \aspectratio(T_1)
-        % .
-    % \end{align*}
+    \color{red}
+    Writing $h_0$ for the unit normal in direction $z_1$, we have 
+    \begin{align*}
+        \Xi(x) 
+        = 
+        x 
+        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
+        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
+        ,
+        \qquad 
+        x \in \bbR^{n}
+        .
+    \end{align*}
+    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
+    By the Xu-Zikanatov estimate,
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        \frac{ \diam(T_1) }{ \height(T_1) }
+        +
+        \frac{ \diam(T_2) }{ \height(T_1) }
+        \leq 
+        \left( 1 + \aspectratio(T_2) \right)
+        \aspectratio(T_1)
+        .
+    \end{align*}
     The desired estimates are shown.
@@
 \end{theorem}
+\begin{proof}\color{blue}
+    We first fix some notation. 
+    Recall that for any $1 \leq m \leq M$, 
+    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
+    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
+    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
+    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We introduce the deformation mapping $\Xi_{2,m} : \patch_{\calT}(S_m) \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
+    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{m-1} \setminus \partial T$.
+    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{m} \rightarrow X_{m-1}$ 
+    by letting it be the identity over $X_{m-1} \setminus A_{m-1}$.
+
+    For each $T \in \calT$ of dimension $n$, there exists a sequence $1 \leq m_{T,1},\dots,m_{T,K} \leq M$, for some $1 \leq K \leq M$,
+    such over the simplex $T$ we have the identity 
+    \begin{align*}
+        ...
+    \end{align*}
+\end{proof}
 \begin{proof}
@@
 \end{proof}
+
+\begin{remark}\label{remark:fullrecursivesum:exterior}
+    \color{red}
+    We provide a similar discussion as in Remark~\ref{remark:fullrecursivesum}, 
+    this time geared towards the application of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
+        \| \cartan u      \|_{L^{p}(T_{m})} 
+        \\&\qquad
+        +
+        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
+        \Cfive{n}{k}(\calT)
+        \Cfiveprime{n}{k}(\calT)^{k} 
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
+        \\&\qquad
+        + 
+        \Cfive{n}{k}(\calT) 
+        \Cfiveprime{n}{k}(\calT)^{k-1} 
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(\Makoto_{m-1})}
+        .
+    \end{align*}
+    Unwrapping the recursion for the norm over the $m$-th simplex, 
+    we find an estimate of the form 
+    \begin{align}\label{math:fullrecursivesum:exterior}
+        \| w \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
+        .
+    \end{align}
+    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
+    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        % \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \sum_{\ell=0}^{M} 
+        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+        \right)
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        L^{\frac p q}
+        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
+        \leq 
+        L^{\frac p q}
+        \sum_{m=0}^{M} 
+        \max_{ 0 \leq \ell \leq M }
+        C_{m,\ell}^{p} 
+        \cdot 
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+
+    Hence 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \sum_{\ell=0}^{M} 
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \delta_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
+        \\&
+        \leq 
+        \max_{0 \leq \ell \leq M} \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \delta_{m,\ell} 
+        \right)
+        \cdot 
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        \\&
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)
+        \cdot 
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        .
+    \end{align}
+    Now, if $q \leq p$, that is, $2 \leq p$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \left(
+            \sum_{\ell'=0}^{M}
+            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
+        \right)^{\frac 1 q}
+        .
+    \end{align}
+    Instead if $p \leq q$, that is, $p \leq 2$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
+        .
+    \end{align}
+    So in any case, it is better than using the following Minkowski's inequality: 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
+        \\&
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align}
+\end{remark}
 

### 2024-12-08 main.tex
notes on improved estimates for potential operators

@@
 
-In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
-So the convolution of $u$ is taken against an integrable function. 
+In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$
+and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
 Young's convolution inequality now implies: 
@@
 which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
-In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
-So the convolution of $u$ is taken against an integrable function. 
+Similar as above,
+the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$
+and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
 Young's convolution inequality now implies: 
@@
 
+\color{blue}
 \subsection{Interaction of potentials with the exterior derivative}
@@
 \end{align*}
-We study the interaction of these potential operator with the exterior derivative in more detail.
+On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
+These do not depend on the eccentricity of the domain.
+
+We begin with the Poincar\'e operator. 
+By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
+\begin{align*}
+    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
+    &
+    \leq 
+    \diam(\Omega)^{p}
+    \vol(\Omega)^{-1}
+    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
+    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{0}^{1} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{0}^{1} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{\Omega} 
+    |u( z )|^{p}
+    \int_{0}^{1} 
+    \vol\left(\left\{ 
+        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
+    \right\}\right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \,dt \,dz 
+    .
+\end{align*}
+\color{red}
+A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
+\begin{align*}
+    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
+    &
+    \leq 
+    \diam(\Omega)^{p}
+    \vol(\Omega)^{-1}
+    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
+    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{1}^{\infty} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{1}^{\infty} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{\Omega} 
+    |u( z )|^{p}
+    \int_{1}^{\infty} 
+    \vol\left(\left\{ 
+        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
+    \right\}\right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \,dt \,dz 
+    .
+\end{align*}
+\color{blue}
+We estimate 
+\begin{align*}
+    \int_{0}^{1}
+    \vol\left(\left\{ 
+        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
+    \right\}\right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \ dt
+    &
+    \leq 
+    \int_{0}^{1}
+    \min\left( 
+        \vol\left(\Omega\right), 
+        \vol\left( \tfrac{t}{1-t} \Omega \right) 
+    \right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \ dt
+    \\&
+    \leq 
+    \int_{0}^{1}
+    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
+    t^{p(k-1)} 
+    \ dt
+    \\&
+    \leq 
+    \int_{0}^{1}
+    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
+    t^{k-1} 
+    \ dt
+    .
+\end{align*}
+We estimate the last integral via the basic observations
+\begin{align*}
+    \int_{0}^{\frac 1 2} 
+    \frac{ t^{k-1} }{ (1-t)^{n} }
+    \ dt
+    \leq 
+    \int_{0}^{\frac 1 2} 
+    (1-t)^{-n+k-1}
+    \ dt
+    =
+    \int_{\frac 1 2}^{1} 
+    t^{-n+k-1}
+    \ dt
+    =
+    \begin{cases}
+        \ln(2)                 & \text{$n=k$}
+        \\
+        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
+    \end{cases}
+\end{align*}
+
+\subsection{Interaction of potentials with the exterior derivative}
+\color{black}
+We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
 % 
-The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
+The main arguments are well-known and establish the exactness of several de~Rham complexes. 
 We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.

### 2024-12-09 main.tex
notes on improved estimates for potential operators
another estimate

@@
         \frac{ \vol(T_1) }{ \vol(T_2) }
-        \leq 
         % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
@@
         % = 
+        \leq 
+        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
+        \leq 
         \aspectratio(T_1) \aspectratio(T_2)
@@
     If $\Xi : T_1 \rightarrow T_2$ is the affine diffeomorphism that is the identity over $F$, then 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi }
-        \leq 
-        \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2}
-        % ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-        .
-    \end{align*}
-%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
+%     \begin{align*}
+%         \matnorm{ \Jacobian \Xi }
+%         \leq 
+%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2}
+%         % ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
+%         % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
+%         .
+%     \end{align*}
+    \begin{gather*}
+        \matnorm{ \Jacobian \Xi^{  } } \leq \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
+        \quad 
+        \matnorm{ \Jacobian \Xi^{-1} } \leq \aspectratio(T_2) + \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_1),
+        \\
+        \det(\Jacobian \Xi)            \leq \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
+    \end{gather*}
 \end{lemma}
-
 \begin{proof}
@@
         \aspectratio(T_{1}) \aspectratio(T_{2})
-        .
-    \end{align*}
+        ,
+        \qquad 
+        \frac{ \diam(T_1) }{ h_2 }
+        \leq
+        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2})
+        .
+    \end{align*}
+    \color{blue}
     Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    We estimate the Lipschitz constant of $\Xi$ as follows. 
-    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and contains the origin, 
-    and the unit height vector $h_0$ goes in the direction of the vertex $z_1$ is in the $n$-th coordinate direction.
-    Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha h_0$ and $x' = b' + \alpha' h_0$.
-    Since $\Xi(h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
-    \begin{align*}
-        \| \Xi(x) - \Xi(x') \|
-        \leq  
-        \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
-        \leq  
-        \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| h_0 \|
-        \leq 
-        \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
-        .
-    \end{align*}
+    To estimate the Lipschitz constant of $\Xi$, we study the singular values of its Jacobian. 
+    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and contains the origin. 
+    Write $z_1 \in T_1$ and $z_2 \in T_2$ for the two vertices not contained in $F$.
+    There exists a unit height vector $\hat h_0$ that goes in the direction of the vertex $z_1$. 
+    Without loss of generality, $\hat h_0$ is in the $n$-th coordinate direction.
+    Suppose that $b_1, b_2 \in F$ such that $z_1 = b_1 + h_1 \hat h_0$ and $x_2 = b_2 + h_2 \hat h_0$.
+    The mapping $\Xi$ is linear, being the identity over $F$ and mapping $z_1$ to $z_2$. Hence,
+    \begin{align*}
+        \Xi( \hat h_0 ) = h_1^{-1} ( b_2 - b_1 ) + h_2 h_{1}^{-1} \hat h_0.
+    \end{align*}
+    We see that $\Xi$ equals the identity over the orthogonal complement of the span of $\hat h_0$ and $b_2 - b_1$.
+    The only singular values of its Jacobian are the two singular values $\sigma_{-} \leq 1 \leq \sigma_{+}$ of the matrix 
+    \begin{align*}
+        \begin{pmatrix}
+            a & 0 
+            \\
+            c & 1
+        \end{pmatrix},
+        \qquad 
+        a = h_2 / h_1,
+        \qquad 
+        c = \|b_2-b_1\| / h_1
+        .
+    \end{align*}
+    These are 
+    \begin{align*}
+        \sigma_{\pm} 
+        &
+        = 
+        \frac{1}{\sqrt{2}} \sqrt{ 1 + a^2 + c^2 \pm \sqrt{ \left( 1 + a^2 + c^2 \right)^{2} - 4a^{2} } } 
+        \\&
+        =
+        \frac{1}{\sqrt{2}} \sqrt{ 1 + a^2 + c^2 \pm \sqrt{ \left( (1+a)^2 + c^2 \right)\left( (1-a)^2 + c^2 \right) } } 
+        \\&
+        =
+        \frac{1}{2} 
+        \left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        .
+    \end{align*}
+%     This implies the determinant identity and estimate 
+%     \begin{align*}
+%         \det( \Jacobian \Xi ) 
+%         = 
+%         \frac 1 4 \left( (1+a)^2 - (1-a)^2 \right) 
+%         &
+%         = 
+%         a
+%         \leq 
+%         \aspectratio(T_{1}) \aspectratio(T_{2}) 
+%         .
+%     \end{align*}
+    We remark that this provides the upper bound 
+    \begin{align}
+        \sigma_{+} 
+        &\leq 
+        \sqrt{ \left( 1 + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) \right)^{2} + \aspectratio(T_{1})^{2} }
+        .
+    \end{align}
+%     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
+%     Since $\Xi(\hat h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
+%     \begin{align*}
+%         \| \Xi(x) - \Xi(x') \|
+%         \leq  
+%         \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
+%         \leq  
+%         \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| \hat h_0 \|
+%         \leq 
+%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
+%         .
+%     \end{align*}
     \color{red}
-    Writing $h_0$ for the unit normal in direction $z_1$, we have 
+    The linear mapping $\Xi$ takes the form Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
     \begin{align*}
@@
         x 
-        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
-        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
+        - \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_1
+        + \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_2
         ,
@@
     \begin{align*}
-        \matnorm{ \Jacobian \Xi }
+        % \matnorm{ \Jacobian \Xi }
+        \sigma_{+} 
         \leq 
@@
         \leq 
-        \left( 1 + \aspectratio(T_2) \right)
-        \aspectratio(T_1)
-        .
-    \end{align*}
+        \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
+        .
+    \end{align*}
+    Analogous upper bound holds for $\sigma^{-1}_{-}$.
+%     \begin{align}
+%         \sigma_{-}^{-1} \leq \left( 1 + \aspectratio(T_1) \right) \aspectratio(T_2)
+%     \end{align}
     The desired estimates are shown.
-\begin{comment}
+% \begin{comment}
+    \color{Mulberry}
     \mwl{Tighter estimate via geometry}
@@
     \end{align*}
-\end{comment}
+% \end{comment}
 \end{proof}
@@
 \end{align*}
-We estimate the last integral via the basic observations
-\begin{align*}
+\begin{align*}
+    \int_{\frac 1 2}^{1}
+    t^{-n+k-1}
+    \ dt
+    =
+    \frac{2^{n-k}-1}{n-k}
+    \\
     \int_{0}^{\frac 1 2} 
@@
     =
-    \int_{\frac 1 2}^{1} 
-    t^{-n+k-1}
-    \ dt
-    =
-    \begin{cases}
-        \ln(2)                 & \text{$n=k$}
-        \\
-        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
-    \end{cases}
+    \frac{2^{n-k}-1}{n-k}
+    .
 \end{align*}

### 2024-12-10 main.tex
update the geometric transformation estimates

@@
     % \end{align*}
-    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
+    The collection $\calS^\ast$ of these simplices and their subsimplices constitute a simplicial complex 
     that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS' = \patch_{\calS'}(z_{S})$. 
-    In particular, $z_{S}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
+    Moreover, $\calS^\ast = \patch_{\calS^\ast}(z_{S})$. 
+    In particular, $z_{S}$ is a boundary vertex of $\calS^\ast$ if and only if $S$ is a boundary simplex of $\calS$. 
     So it remains to study the topology of vertex stars.
@@
 %     
-%     If $z$ is an inner vertex of $\calS'$, 
-%     then the boundary simplices of $\calS'$,
+%     If $z$ is an inner vertex of $\calS^\ast$, 
+%     then the boundary simplices of $\calS^\ast$,
 %     which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
 %     
-%     Now suppose that $z$ is a boundary vertex of $\calS'$,
+%     Now suppose that $z$ is a boundary vertex of $\calS^\ast$,
 %     which is the case if and only if $S$ is a boundary simplex. 
@@
 
+\clearpage
 We now provide the desired bi-Lipschitz transformation:
@@
         \\
-        \sigma_n \leq \Csechs{n}{k}(\calT),
+        \sigma_n^{-1} \leq \Csechs{n}{k}(\calT),
         \quad 
@@
     \end{gather*}
-%     and which satisfies the upper bounds 
-%     \begin{gather*}
-%         \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
-%         \quad 
-%         \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
-%         \\
-%         | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
-%         \quad 
-%         | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
-%     \end{gather*}
     \item 
@@
         \\
-        \sigma_n \leq \Cacht{n}{k}(\calT),
+        \sigma_n^{-1} \leq \Cacht{n}{k}(\calT),
         \quad 
@@
     \end{gather*}
-%     and which satisfies the upper bounds 
-%     \begin{gather*}
-%         \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
-%         \quad 
-%         \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
-%         \\
-%         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
-%         \quad 
-%         | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
-%     \end{gather*}
     \end{enumerate}
@@
         \item 
-        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
+        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin. 
         % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
@@
         %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
-        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
+        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
         whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
@@
         \item 
-        We let $z'_{S}$ be the midpoint of $S'$. 
-        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
-        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
-
-        We define another simplicial complex $\calS^c$ as follows:
-        given any $n$-simplex $K \in \calS$, 
+        We let $z_{S'}$ be the midpoint of $S'$. 
+        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calD$ of the underlying set $\underlying{T}$. 
+        Obviously, all $n$-simplices in $\calD$ contain $S$ and $z_{S'}$.
+
+        We define another simplicial complex $\calD^c$ as follows:
+        given any $n$-simplex $K \in \calD$, 
         we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
-        thus obtaining a new simplex $K'$. 
-        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.
-
-        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
+        thus obtaining a new simplex $K^{c}$. 
+        Indeed, that $\calD^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
+
+        We let the simplicial complex $\calD^\ast$ be the union of $\calD$ and $\calD^c$. 
         By construction, all its $n$-simplices contain $S$ as a subsimplex,
-        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
+        % Indeed, $\calD^\ast$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
         Moreover, $S$ is an inner subsimplex of that triangulation. 
-        In particular, $\calS'$ is its own star around $S$.
-
-        % TODO Check that $\calS'$ is a triangulation
+        In particular, $\calD^\ast$ is its own star around $S$.
+
+        % TODO Check that $\calD^\ast$ is a triangulation
 
         \item 
-        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
-        Then $\calR'$ is its own local star around the barycenter $z_S$.
-        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
-        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
-        which we denote by $\calR$ and $\calR^{c}$, respectively.
+        As additional step, we introduce another simplicial complex $\calG^\ast$ from $\calD^\ast$ via barycentric subdivision of $S$.
+        Then $\calG^\ast$ is its own local star around the barycenter $z_S$.
+        In particular, all $n$-simplices in $\calG^\ast$ contain $z_{S}$. 
+        The simplicial complex $\calG^\ast$ also contains as subcomplexes the corresponding refinements of $\calD$ and $\calD^{c}$, 
+        which we denote by $\calG$ and $\calG^{c}$, respectively.
+        Given any $n$-simplex in $\calG$, replacing its vertex $z_{S}$ with its opposite $-z_{S}$ gives an associated $n$-simplex in $\calG^{c}$.
 
@@
         \item 
-        We introduce a new mapping $\Theta : \underlying{\calR} \rightarrow \underlying{\calR^c}$ between the underlying sets as follows.
-        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
-        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
+        % Notice that $A_{G^{c}}$ and $A_{G}$ have the same singular values. Thus
+        % \begin{align*}
+        %     \matnorm{ \Jacobian \Theta_{|G}      } &\leq \| A_{G^{c}} \| \cdot \| A_{G}^{-1} \| \leq \geometricshapemeasure(A_{G}),
+        %     \\
+        %     \matnorm{ \Jacobian \Theta_{|G}^{-1} } &\leq \| A_{G^{c}}^{-1} \| \cdot \| A_{G} \| \leq \geometricshapemeasure(A_{G}).
+        % \end{align*}
+        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
+        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
+        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
         be affine reference transformations
-        that agree on the vertices common to $K$ and $K'$.
+        that agree on the vertices common to $G$ and $G^{c}$.
         Then the mapping 
         \begin{align*}
-            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
-        \end{align*}
-        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
-        % \begin{align*}
-        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
-        %     \\
-        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
-        % \end{align*}
+            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}
+        \end{align*}
         preserves volumes:
         \begin{align*}
-            |\det( \Jacobian      \Theta_{|K} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|K} )|
+            |\det( \Jacobian      \Theta_{|G} )|
+            = 
+            |\det( \Jacobian^{-1} \Theta_{|G} )|
             =
@@
         We want to characterize the singular values of this transform. 
-        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
+        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
         We can write
         \begin{align*}
-            \Theta_{|K}(x) 
+            \Theta_{|G}(x) 
             = 
@@
         \begin{align*}
-            \Theta_{|K}( h_{z} ) 
+            \Theta_{|G}( h_{z} ) 
             &= 
@@
         \end{align*}
-        Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
+        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
@@
         \begin{align*}
-            B 
+            M_{\Theta,G} 
             := 
@@
         \end{align*}
-        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
-        Its square roots are the desired singular values of $B$:
+        We compute the eigenvalues of the symmetric matrix $M_{\Theta,G}^{\ast} M_{\Theta,G}$. 
+        Its square roots are the desired singular values of $M_{\Theta,G}$:
         \begin{align}
-            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
-            ,
-            \\
-            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
+            \sigma_{\max}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
+            ,
+            \\
+            \sigma_{\min}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
             .
@@
         They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
-        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
+        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,
         whereas all its other singular values equal $1$.
@@
 
-        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
+        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
+        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
         which must be contained in some face of $T$. 
@@
         \begin{align}\label{math:upper_bound_for_theta}
-            B_{T} 
+            \mu_{T,k} 
             := 
@@
         \end{align}
-
+        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
+        \begin{align}
+            \sigma_{1}(\Theta,x) \leq \mu_{T,k},
+            \quad 
+            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
+            \quad 
+            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,k}.
+        \end{align}
         \item 
-        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
-        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
+        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
+        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
         We construct a bi-Lipschitz mapping 
         \begin{align*}
-            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
-        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
-        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
-        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
+            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
+        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
+        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
+        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
         has a unique representation
         \begin{align*}
-            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
-        \end{align*}
-        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
+        \end{align*}
+        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
         \begin{align*}
@@
         \begin{align*}
-            \Phi_{K}(x) 
+            \Phi_{G}(x) 
             &
             := 
-            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
+            \mu x_{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
             \\&
@@
         \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
+        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
         that satisfies the desired mapping properties. 
@@
         \begin{align*}
-            \Jacobian \Phi_{K}(x)
+            \Jacobian \Phi_{G}(x)
             &=
@@
         \begin{align*}
-            C 
+            M_{\Phi,G} 
             = 
@@
         \end{align*}
-        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
-        \begin{align*}
-            \sigma_{\max} 
-            = 
+        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
+        we obtain the singular values 
+        \begin{align*}
+            \sigma_{\max}(\Phi,G) 
+            := 
             \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
@@
             \\
-            \sigma_{\min} 
-            = 
+            \sigma_{\min}(\Phi,G)
+            := 
             \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
@@
         \begin{align*}
-            \sigma_{\max} 
-            = 
+            \sigma_{\max}(\Phi,G) 
+            := 
             \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
@@
             \\
-            \sigma_{\min} 
-            = 
+            \sigma_{\min}(\Phi,G) 
+            := 
             \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
@@
         \end{align*}
-        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
         These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
+        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
+        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$. 
+        Therefore,
         \begin{align*}
@@
         \end{align*}
-        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
         Similar as above, we use the upper bound 
@@
         \end{align*}
-        We conclude that 
+        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
         \begin{gather}
-            \matnorm{ \Jacobian\Phi_{K} } 
+            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
             \leq 
@@
             \\
-            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
+            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
+            \\
+            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
             \leq 
@@
         \begin{align*}
-            \Psi : \underlying{\calR'} \rightarrow \underlying{\calK}.
-        \end{align*}
-        Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,
+            \Psi : \underlying{\calG^\ast} \rightarrow \underlying{\calK}.
+        \end{align*}
+        Recall that $\calG^\ast$ and $\calK$ are their own respective stars around the origin,
         so they must contain an open ball around the origin. 
         % TODO \mwl{Here we need to show that it is indeed a ball. It must be a domain triangulation.}
-        Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
+        Let ${G} \in \calG^\ast$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
 There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
@@
         \begin{gather*}
-            \matnorm{ \Jacobian\Psi(x) }
+            % \matnorm{ \Jacobian\Psi(x) }
+            \sigma_{1}( \Jacobian\Psi(x) )
             = 
@@
             \right)
-            \\
-            \matnorm{ \Jacobian\Psi(z)^{-1} }
+            ,
+            \\
+            % \matnorm{ \Jacobian\Psi(z)^{-1} }
+            \sigma_{1}( \Jacobian\Psi(z)^{-1} )
             = 
@@
             \\
+            \sigma_{2}( \Jacobian\Psi(x) ) = \dots = \sigma_{n-1}( \Jacobian\Psi(x) )
+            =
+            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            ,
+            \\
             \det\Jacobian\Psi(x)
@@
             \qquad
-            \det\Jacobian\Psi^{-1}(x)
+            \det\Jacobian\Psi^{-1}(z)
             =
@@
             \right)^{n}
+            .
         \end{gather*}
@@
         % 
-        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
-        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
+        In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
         that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
@@
         It remains to find a lower bound for $\| h_{G} \|$.
-        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
-        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
-The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
+        Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
+        by scaling with $(k+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
+        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,k}$.
+The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
         %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
@@
             &\leq 
-            (k+1)B_{T}
+            (k+1)\mu_{T,k}
             \frac{ \diam(K) }{ \| h_{T} \| }
             \leq 
-            (k+1)B_{T}
+            (k+1)\mu_{T,k}
             \diameterratio(\calT)
@@
             \leq 
-            (k+1)B_{T}
+            (k+1)
             \diameterratio(\calT)
             \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \mu_{T,k}
             ,
@@
             \leq 
-            (k+1)B_{T}
-            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (k+1)
+            \aspectratio({G}) \mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
         %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
+        %         From this observation we infer that the height vectors at the origin of the simplices in $\calG^\ast$ and $\calK$
+        %         are obtained by rescaling the height vectors in $\calD^\ast$ and $\patch_{\calT}(S)$
         %         with the factor $(k+1)^{-1}$.
@@
             (k+1) 
-            \left( 1 + B_{T} \right)
+            \left( 1 + \mu_{T,k} \right)
             \sup_{ K \in \patch_{\calT}(S) }
@@
         \end{align*}
-        In summary, using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, we find the upper bounds 
-        \begin{align*}
-            \matnorm{ \Jacobian\Psi(x) }
+        We define 
+        \begin{align}
+            \nu_{T,k} := \sqrt{ 1 + \frac{ (k+1)^{2}\left( 1 + \mu_{T,k} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (k+1)\left( 1 + \mu_{T,k} \right) \aspectratio(\calT) }{2}
+            .
+        \end{align}
+        In summary, 
+        the singular values of the Jacobian of $\Psi$ at almost every $x$ satisfy 
+        % using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, 
+        \begin{align}
+            \sigma_{1}(\Psi,x) % \matnorm{ \Jacobian\Psi(x) }
             &\leq  
-            (k+1)B_{T}
+            (k+1)
             \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T)\mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \cdot 
-            \left( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT) 
-            \right)
-            ,
-            \\
-            \matnorm{ \Jacobian\Psi(z)^{-1} }
+            \nu_{T,k}
+            ,
+            \\
+            \sigma_{n}(\Psi,x)^{-1} % \matnorm{ \Jacobian\Psi(z)^{-1} }
             &\leq  
@@
             \cdot 
-            \left( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT) 
-            \right)
+            \nu_{T,k}
+            ,
+            \\
+            \sigma_{  2}(\Psi,x) 
+            &= 
+            \dots
+            =
+            \sigma_{n-1}(\Psi,x) 
+            \leq 
+            (k+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,k}
             ,
@@
             \left( 
-            (k+1)B_{T}
+            (k+1)
             \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T)\mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \right)^{n},
@@
             \right)^{n}
-        \end{align*}
+            .
+        \end{align}
         We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
@@
             \aspectratio(\calT)
-            B_{T}^{2}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
+            \mu_{T,k}^{2}
+            \nu_{T,k}           
             ,
@@
             :=
-            (k+1)B_{T}
+            (k+1)
             \diameterratio(\calT)
-            \aspectratio(T) 
-            \cdot 
-            B_T
+            \aspectratio(T) \mu_{T,k}^{2}
+            ,
             \\
@@
             \aspectratio(\calT)
-            B_{T}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)
+            \mu_{T,k}
+            \nu_{T,k}
+            ,
             \\
@@
             \cdot 
-            B_T
+            \mu_{T,k}
             .
@@
             \diameterratio(\calT)^{n}
-            B_{T}^{n}
+            \mu_{T,k}^{n}
             \aspectratio(\calT)^{n}
@@
             :=
-            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
-            \cdot 
             (k+1) 
             \aspectratio(\calT)
-            B_{T}
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
+            \diameterratio(\calT)
+            \mu_{T,k}
+            \nu_{T,k}         
+            \cdot 
+            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            ,
             \\
@@
             :=
-            (k+1)B_{T}
+            (k+1)
             \diameterratio(\calT)
-            \aspectratio(T) 
+            \aspectratio(T)\mu_{T,k} 
             \cdot 
             \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            ,
             \\
@@
             :=
+            (k+1) 
+            \diameterratio(\calT)
+            \aspectratio(\calT)
+            \nu_{T,k}           
+            \cdot 
             \left( 2 + 3 (k+1) \aspectratio(T) \right)
-            \cdot 
-            (k+1) 
-            \aspectratio(\calT)
-            \Big( 
-                1 
-                + 
-                (k+1) 
-                \left( 1 + B_{T} \right)
-                \aspectratio(\calT)
-            \Big)            
+            ,
             \\
@@
     \end{itemize}
-    The proof is complete. 
+    Having shown all the desired estimates, and the proof is complete. 
 \end{proof}

### 2024-12-10 main.tex
further improvement of geometric estimates; spellcheck and grammar

@@
 
+% LTeX: enabled=false
 % Title, authors, and affiliations
@@
 \date{}
+% LTeX: enabled=true
 
@@
 
-This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrichs inequalities for the differential operators of vector calculus. 
+This manuscript contributes to the theory of computable estimates for Poincar\'e--Friedrichs inequalities for the differential operators of vector calculus. 
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
@@
 \end{align}
-We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+This inequality is called \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
 The question is therefore whether we can always find a gradient potential of sufficiently small norm so this inequality holds. 
@@
 %the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$.
-%Hence we want to evaluate the \emph{operator norm} of the potential operator 
+%Hence, we want to evaluate the \emph{operator norm} of the potential operator 
 \begin{align}\label{math:intro:gradient:potentialnorm}
@@
 where $u_\Omega$ denotes the average of $u$. We emphasize that the average-free potential is generally not the norm-minimizing potential unless $p = 2$.
-Hence the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs differ in general. 
+Hence, the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs differ in general. 
 Considerable research efforts have gone into determining constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
@@
 We study potentials and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
-There are substantial changes and much less results are available in the literature. 
+There are substantial changes and much fewer results are available in the literature. 
 We use the spaces of vector field 
@@
     &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-    .
 \end{align}
@@
 This formalism is independent of the spatial dimension and highlights extends the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
-% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}:
-for every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
+% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
+% In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: 
+For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
 \begin{align} \label{math:intro:exterior:pf} 
@@
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that not only is a preimage under the curl operator but that also has vanishing tangential trace along the same three faces. 
+we want to find the unique vector field potential that not only is a preimage under the curl operator but also has vanishing tangential trace along the same three faces. 
 We achieve this by constructing an auxiliary problem subject to full boundary conditions,
@@
 We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
-However, we need to overcome new challenges that are arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
+However, we need to overcome new challenges that arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
 The basic inductive strategy remains the same. 
@@
 % 6. Contractible 
-Inspired by the contractibility of shellable triangulations, we pursuit an additional estimate for Poincar\'e--Friedrichs constants. 
+Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
 Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
@@
 
+% LTeX: enabled=false
 The remainder of this manuscript is structured as follows.
@@
 Our regularized potentials over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
-giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
+giving rise to computable Poincar\'e--Friedrichs constants as their operator norms. 
 We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
@@
 We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}. 
+% LTeX: enabled=true
 
@@
 We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potentials.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
-\\
-
-Let $\Omega \subseteq \bbR^{n}$ be an open connected set. 
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below, but we believe it is also of independent interest.
+\\
+
+Let $\Omega \subseteq \bbR^{n}$ be a connected open set. 
 Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
@@
 Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a the projection onto the constants functions with unit norm, from~\eqref{math:aver_norm} it now follows that 
+since taking the average is a projection onto the constants functions with unit norm, from~\eqref{math:aver_norm} it now follows that 
 % From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
@@
 \end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is the smallest possible constant in \eqref{math:inequalitypf:gradient}. 
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$.
@@
 % \end{align*}
-We call any set triangulable if it is the underlying set of some triangulation.
+One calls any set triangulable if it is the underlying set of some triangulation.
 
@@
 % Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
+Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, members with codimension one) of this triangulation.\footnote{
     Our use of the term \textit{face} as is common in classical geometry and the finite element literature~\cite{brenner2008mathematical}
@@
 
+% LTeX: enabled=false
 We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
@@
 and we call $\calT$ \emph{face-connected} if it has only one face-connected component. 
+% LTeX: enabled=true
 
@@
 We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
+Moreover, $\height(T)$ refers to the smallest height of any vertex of the simplex $T$,
 where the height of a vertex is defined as the distance to the affine span of its opposing face.
@@
     equals the maximum of the quotient $\| M x \|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
-    We also know that the diameter of $T$ is the length of its longest edge. 
+    The diameter of $T$ is the length of its longest edge. 
     Our first pair of inequalities follows via standard comparisons of Euclidean norms:
@@
 %     \end{align*}
-%     Hence 
+%     Hence, 
     \begin{align*}
@@
     \end{gather*}
-    and whenever $T_0, T_1, \dots, T_M$ is a face path,
-    then for all $1 \leq m \leq$ we the following recursive estimates:
+    Whenever $T_0, T_1, \dots, T_M$ is a face path,
+    then for all $1 \leq m \leq$ the following recursive estimates:
     \begin{align*}
@@
     \end{align*}
-    We apply Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''}, which gives 
+    An application of Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''} gives 
     \begin{align*}
@@
     \end{align*}
-    We now observe that 
+    Now we observe that 
     \begin{gather*}
@@
 
-    \color{green}Hence 
+    \color{green}Hence, 
     \begin{align}
@@
     \end{align}
-    Instead if $p \leq q$, that is, $p \leq 2$, then 
+    Instead, if $p \leq q$, that is, $p \leq 2$, then 
     \begin{align}
@@
 $\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-We define them 
+These are defined 
 for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
@@
 We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
+if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration-by-parts formula
 \begin{align*}
@@
 We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration-by-parts formula
 such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
 whose support lies in the open ball $B_r(x)$
-we have the integration by parts formula
+we have the integration-by-parts formula
 \begin{align*}
@@
 \begin{proof}
-    See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}).
+    See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}.
 \end{proof}
@@
     \end{align*}
-    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
+    Hence, $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
 
@@
 Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
-We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+We estimate $\Poinc_{\mia} u(x)$ pointwise for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
 \begin{align*}
@@
 where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
-We compute 
+One computes 
 \begin{align*}
@@
 First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$.
-Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
+Hence, $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
 Consider now the case $x \in \overline\Omega$. 
@@
 We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
+For the Poincar\'e operator, we substitute $a = x + t(y-x)$, and then we substitute $s = (t-1)/t$,
 leading to 
@@
 \end{align*}
-For the Bogovski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
+For the Bogovski\u{\i} operator, we first substitute $a = y + t(x-y)$, and then we substitute $s = t/(t-1)$,
 leading to 
@@
 \end{align*}
-We add the exterior derivative of the potential and the potential of the exterior derivative.
+Next, we add the exterior derivative of the potential and the potential of the exterior derivative.
 Taking into account cancellations, this gives the identity 
@@
     Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
+    whose smallest singular value is bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
     The adjoint is the closed densely-defined linear operator $-\divergence : \bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
@@
 All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
+We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifold's boundary. 
 We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
@@
 
-We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. This topics is surprisingly non-trivial and 
-we gather some results that are hard to find in the literature.
+We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. 
+This topic is surprisingly non-trivial. We only gather some results that are hard to find in the literature.
 
@@
 
-Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
+Suppose that $\calT$ is an $n$-dimensional simplicial complex and that we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
 For any enumeration, we call 
@@
     then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
-    Hence $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
+    Hence, $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
     which requires $m = M$.
@@
     We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
-    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
+    Hence, a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
     and a triangle is not good in $\calT$ if that intersection is either empty, only some of its vertices, or a vertex and the opposite edge.
@@
     So each component has at least one triangle that is also good in $\calT$. 
-    Hence $\calT$ contains two good triangles, which completes the induction step.
+    Hence, $\calT$ contains two good triangles, which completes the induction step.
 
@@
 \begin{lemma}\label{lemma:stars_are_shellable}
-    Let $\calT$ be a $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
+    Let $\calT$ be an $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
     Then $\patch_{\calT}(V)$ is shellable. 
@@
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
+    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an example of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
 \end{remark}
@@
         We want to characterize the singular values of this transform. 
-        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
-        We can write
+        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
+        We verify that 
         \begin{align*}
@@
         \end{align}
-        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
+        They are mutual reciprocals of each other, and they are monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
         We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,
@@
         Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
-        Thus 
+        Thus, 
         \begin{align*}
@@
         \end{align}
+        \color{red}It is also evident that the eigenvalues of the Jacobian almost everywhere have magnitude $1$.\color{black}
+
         \item 
@@
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
+        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
         \begin{align*}
@@
                 -3\tan(\beta) & 2 
+            \end{pmatrix}
+            \\
+            \color{red}
+            M_{\Phi,G} 
+            = 
+            \begin{pmatrix}
+                -\frac 1 2             & 0 
+                \\
+                -\frac 3 2 \tan(\beta) & 1 
+            \end{pmatrix}
+            = 
+            \frac 1 2 
+            \begin{pmatrix}
+                -1 & 0 
+                \\
+                -3\tan(\beta) & 1 
             \end{pmatrix}
@@
         \end{align*}
-        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
         Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
@@
         \end{gather}
+        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $-\tfrac 1 2$ with multiplicity $1$.\color{black}
         This finishes the discussion of the transformation $\Phi$.
@@
         \end{align*}
-        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
+        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\|a\|$.
         We thus consider the upper bound 
@@
         \end{align*}
+        \color{red}Lastly, the matrix $\Id + \hat x \otimes a^{t}$ has the eigenvalue $1$ with multiplicity $n-1$ and a trace of $n + \langle a, \hat x \rangle$,
+        so it has one eigenvalue $1 + \langle a, \hat x \rangle$.\color{black}
 
@@
 There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively.
+We let $h_{{G}}$ and $h_{K}$ be the normal vectors of the origin within ${G}$ and $K$, respectively.
 They define respective hyperplanes $H_{G}$ and $H_{K}$,
@@
         % 
-        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
+        In order to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
         In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
@@
         \| \cartan u \|_{L^{p}(\Omega)}
-        .
+        ,
     \end{align*}
@@
 \begin{align*}
-    \Makoto_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}.
+    \Makoto_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}
 \end{align*}
@@
     \begin{gather*}
-        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
+        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}
+        ,
     \end{gather*}
@@
 
-    Hence 
+    Hence, 
     \begin{align}
@@
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
-    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
-    Let $1 \leq p \leq \infty$ and $\bfu \in \bfW^{p}(\Omega,\curl)$.
+    Let $\calT$ be a shellable $n$-dimensional triangulation, 
+    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
     \begin{itemize}
@@
         \begin{gather*}
-            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}.
+            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
         \end{gather*}
@@
 \section*{Acknowledgments}
-
-MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
+% LTeX: enabled=false
+MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, by John M.\ Lee, and G\"unther M.\ Ziegler.
+% LTeX: enabled=true
 

### 2024-12-10 main.tex

--- 2024-12-09 main.tex
@@
     If $\Xi : T_1 \rightarrow T_2$ is the affine diffeomorphism that is the identity over $F$, then 
+    at least $n-2$ of its Jacobian's singular values equal $1$, and we have 
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi^{  } } 
+        &
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) + 1 \right)^{2} + \aspectratio(T_{1})^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) - 1 \right)^{2} + \aspectratio(T_{1})^{2} }
+        ,
+        \\
+        \matnorm{ \Jacobian \Xi^{-1} } 
+        &
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2}) + 1 \right)^{2} + \aspectratio(T_{2})^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2}) - 1 \right)^{2} + \aspectratio(T_{2})^{2} }
+        ,
+        \\
+        \det(\Jacobian \Xi)
+        &\leq 
+        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
+        .
+    \end{align*}
 %     \begin{align*}
@@
 %     \end{align*}
-    \begin{gather*}
-        \matnorm{ \Jacobian \Xi^{  } } \leq \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
-        \quad 
-        \matnorm{ \Jacobian \Xi^{-1} } \leq \aspectratio(T_2) + \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_1),
-        \\
-        \det(\Jacobian \Xi)            \leq \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
-    \end{gather*}
+%     \begin{gather*}
+%         \matnorm{ \Jacobian \Xi^{  } } 
+%         \leq 
+%         \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
+%         \quad 
+%         \matnorm{ \Jacobian \Xi^{-1} } \leq \aspectratio(T_2) + \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_1),
+%         \\
+%         \det(\Jacobian \Xi)            \leq \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2),
+%     \end{gather*}
 \end{lemma}
@@
     \end{align*}
-    \color{blue}
     Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
@@
     \end{align*}
+    We remark that this provides the upper bound 
+    \begin{align*}
+        \sigma_{+} 
+        &
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) + 1 \right)^{2} + \aspectratio(T_{1})^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) - 1 \right)^{2} + \aspectratio(T_{1})^{2} }
+        .
+    \end{align*}
+    The desired estimates are shown.
 %     This implies the determinant identity and estimate 
@@
 %     \end{align*}
-    We remark that this provides the upper bound 
-    \begin{align}
-        \sigma_{+} 
-        &\leq 
-        \sqrt{ \left( 1 + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) \right)^{2} + \aspectratio(T_{1})^{2} }
-        .
-    \end{align}
+%     % Now we see that if $a \leq 1$, then $\sigma_{+} \leq 1 + c$, and if $a \geq 1$, then $\sigma_{+} \leq a + c$.
 %     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
@@
 %     \end{align*}
+    \color{blue}
     \color{red}
-    The linear mapping $\Xi$ takes the form Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
+    The linear mapping $\Xi$ takes the form 
+    % Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
     \begin{align*}
@@
 %     \end{align}
-    The desired estimates are shown.
 % \begin{comment}
@@
 \color{blue}
-\subsection{Interaction of potentials with the exterior derivative}
+\subsection{Rewriting the potentials operators}
 
@@
 \end{align*}
-\begin{align*}
+The last integral is handled via the basic observations
+\begin{align*}
+    \int_{0}^{\frac 1 2} 
+    \frac{ t^{k-1} }{ (1-t)^{n} }
+    \ dt
+    \leq 
+    \int_{0}^{\frac 1 2} 
+    (1-t)^{-n+k-1}
+    \ dt
+    =
     \int_{\frac 1 2}^{1} 
@@
     =
-    \frac{2^{n-k}-1}{n-k}
-    \\
-    \int_{0}^{\frac 1 2} 
-    \frac{ t^{k-1} }{ (1-t)^{n} }
-    \ dt
-    \leq 
-    \int_{0}^{\frac 1 2} 
-    (1-t)^{-n+k-1}
-    \ dt
-    =
-    \frac{2^{n-k}-1}{n-k}
-    .
+    \begin{cases}
+        \ln(2)                 & \text{$n=k$}
+        \\
+        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
+    \end{cases}
 \end{align*}
@@
 
+\begin{remark}\label{remark:improved_starreflection}
+    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
+    Some improvements are immediately possible if $k=n-1$. 
+    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
+    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
+    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
+    %     \begin{gather*}
+    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
+    %         \quad 
+    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
+    %         \quad 
+    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
+    %         \\ 
+    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
+    %         \quad 
+    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
+    %     \end{gather*}
+    \begin{gather*} 
+        | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
+        \quad 
+        | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT),
+        \\
+        \sigma_{1}
+        %&
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        ,
+        \\
+        \sigma_{n}^{-1}
+        %&
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        ,
+        \\
+        \sigma_2,\dots,\sigma_{n-1} \leq 1.
+        %         \det(\Jacobian \Xi) &\leq \diameterratio(\calT) \aspectratio(T_2)
+    \end{gather*}
+    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
+    We believe that better estimates can be computed from the geometric data also in the other cases.
+\end{remark}
+
 \section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}

### 2024-12-10 main.tex

--- 2024-12-10 main.tex
@@
 \begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
+    Let $T$ be an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
     Let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ in accordance with the barycentric subdivision of $S$ at $z_{S}$.
     \begin{itemize}
-        \item $\vol(T') = \vol(T) / (k+1)$. 
+        \item $\vol(T') = \vol(T) / (\ell+1)$. 
         \item The height vector of $v \in \Vertices(T) \setminus \Vertices(S)$ in $T'$ is the height vector $v$ in $T$.
         \item The height vector of $z_S$ in $T'$ is the height vector of the single vertex $v \in \Vertices(T) \setminus \Vertices(T')$ in $T$,
-scaled by $(k+1)^{-1}$.
+scaled by $(\ell+1)^{-1}$.
     \hfill\qed
@@
     Let $\calT$ be a triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be an inner simplex of dimension $k < n$,
+    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
     let $T \in \patch_{\calT}(S)$ be of dimension $n$,
@@
     \begin{gather*}
-        \sigma_1 \leq \Cfive{n}{k}(\calT),
+        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
         \quad 
-        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{k}(\calT),
+        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Csechs{n}{k}(\calT),
+        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
         \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{k}(\calT),
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
     \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
+        \leq 
+        \Cfivetrafo{n}{k}{\ell}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
+        \leq 
+        \Csechstrafo{n}{k}{\ell}(\calT).
+    \end{align*}
+
     \item 
@@
     \begin{gather*}
-        \sigma_1 \leq \Csieb{n}{k}(\calT),
+        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
         \quad 
-        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{k}(\calT),
+        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Cacht{n}{k}(\calT),
+        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
         \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{k}(\calT),
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
     \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+        \leq 
+        \Csiebtrafo{n}{k}{\ell}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
+        \leq 
+        \Cachttrafo{n}{k}{\ell}(\calT).
+    \end{align*}
     \end{enumerate}
@@
         Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin. 
-        % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
-        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
+        % Let $I := \Makoto \cap T$, which is the union of $\ell$ different faces of $T$, with $1 \leq \ell \leq n$.
+        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-\ell$ faces of $T$.
         %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
@@
         which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
+        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
         Thus, 
@@
             = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
-            \leq 
-            (n-k) \aspectratio(T)
+            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
+            \leq 
+            (n-\ell) \aspectratio(T)
 %             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
+%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
 %             \leq 
-%             \frac{ n-k }{n!}
+%             \frac{ n-\ell }{n!}
 %             \cdot 
@@
         \begin{align}\label{math:upper_bound_for_theta}
-            \mu_{T,k} 
+            \mu_{T,\ell} 
             := 
@@
             \sqrt{ 
-                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+                1 + (n-\ell)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
             } 
             + 
-            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
+            (n-\ell) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
             .
@@
         \begin{align}
-            \sigma_{1}(\Theta,x) \leq \mu_{T,k},
+            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
             \quad 
@@
             \quad 
-            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,k}.
+            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell}.
         \end{align}
@@
                 \\
-                -\frac 3 2 \tan(\beta) & 2 
-            \end{pmatrix}
-            = 
-            \frac 1 2 
-            \begin{pmatrix}
-                -1 & 0 
-                \\
-                -3\tan(\beta) & 2 
-            \end{pmatrix}
-            \\
-            \color{red}
-            M_{\Phi,G} 
-            = 
-            \begin{pmatrix}
-                -\frac 1 2             & 0 
-                \\
                 -\frac 3 2 \tan(\beta) & 1 
             \end{pmatrix}
-            = 
-            \frac 1 2 
-            \begin{pmatrix}
-                -1 & 0 
-                \\
-                -3\tan(\beta) & 1 
-            \end{pmatrix}
+%             = 
+%             \frac 1 2 
+%             \begin{pmatrix}
+%                 -1 & 0 
+%                 \\
+%                 -3\tan(\beta) & 2 
+%             \end{pmatrix}
+            .
         \end{align*}
@@
             \sigma_{\max}(\Phi,G) 
-            := 
-            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            &
+            =
+%             \frac{1}{2} 
+%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+%             \frac{1}{2} 
+%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
             ,
@@
             \sigma_{\min}(\Phi,G) 
-            := 
-            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
-            .
-        \end{align*}
-        \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            := 
-            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
-            %=
-            %\frac 1 4 \sqrt{ 9 + 9\tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            =
-            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
-            ,
-            \\
-            \sigma_{\min}(\Phi,G) 
-            := 
-            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
-            =
-            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            &
+            =
+%             \frac{1}{2} 
+%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+%             \frac{1}{2} 
+%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
             .
@@
         Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
-        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$. 
-        Therefore,
+        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$ and 
         \begin{align*}
@@
         \end{align*}
-        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
         Similar as above, we use the upper bound 
         \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
+            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
         \end{align*}
@@
             \leq 
-            \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            \leq 
-            1 + \frac{3}{2} (k+1) \aspectratio(T) 
+            \frac 3 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            1 + \frac{3}{2} (\ell+1) \aspectratio(T) 
             \label{math:phi_max}
@@
             \leq 
-            \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
-            \leq 
-            2 + 3 (k+1) \aspectratio(T) 
+            \frac 3 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            2 + 3 (\ell+1) \aspectratio(T) 
             \label{math:phi_min}
@@
         Notice that these are strictly monotonically increasing or decreasing, respectively, in $\|a\|$.
-        We thus consider the upper bound 
-        \begin{align*}
-            \|a\| 
-            \leq 
-            2 \max_{1 \leq i \leq 2} 
-            \left( 
-                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
-            \right)
-            .
-        \end{align*}
+%         We thus consider the upper bound 
+%         \begin{align*}
+%             \|a\| 
+%             \leq 
+%             2 \max_{1 \leq i \leq 2} 
+%             \left( 
+%                 \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
+%             \right)
+%             .
+%         \end{align*}
         \color{red}Lastly, the matrix $\Id + \hat x \otimes a^{t}$ has the eigenvalue $1$ with multiplicity $n-1$ and a trace of $n + \langle a, \hat x \rangle$,
@@
         We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
-The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
+The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(\ell+1)^{-1}$.
         That estimates the quotient $\| x_K \| / \| h_K \|$. 
@@
         Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
-        by scaling with $(k+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,k}$.
+        by scaling with $(\ell+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
+        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,\ell}$.
 The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
@@
             &\leq 
-            (k+1)\mu_{T,k}
+            (\ell+1)\mu_{T,\ell}
             \frac{ \diam(K) }{ \| h_{T} \| }
             \leq 
-            (k+1)\mu_{T,k}
+            (\ell+1)\mu_{T,\ell}
             \diameterratio(\calT)
@@
             \leq 
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
             \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \mu_{T,k}
+            \mu_{T,\ell}
             ,
@@
             &\leq 
-            (k+1)
+            (\ell+1)
             \sup_{ K \in \patch_{\calT}(S) }
@@
             \leq 
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
@@
             \leq 
-            (k+1)
+            (\ell+1)
             \sup_{ K \in \patch_{\calT}(S) }
@@
             \leq 
-            (k+1)
-            \aspectratio({G}) \mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (\ell+1)
+            \aspectratio({G}) \mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
         %         To simplify that expression, we make another observation regarding the height vectors. 
-        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
+        %         when $T$ is an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S \subseteq T$,
         %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
-        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
+        %         then the barycenter $z_S$ of $S$ has distance $h/(\ell+1)$ from the face $F$. 
         %         From this observation we infer that the height vectors at the origin of the simplices in $\calG^\ast$ and $\calK$
         %         are obtained by rescaling the height vectors in $\calD^\ast$ and $\patch_{\calT}(S)$
-        %         with the factor $(k+1)^{-1}$.
+        %         with the factor $(\ell+1)^{-1}$.
 
@@
             \leq 
-            (k+1) 
-            \left( 1 + \mu_{T,k} \right)
+            (\ell+1) 
+            \left( 1 + \mu_{T,\ell} \right)
             \sup_{ K \in \patch_{\calT}(S) }
@@
         \begin{align}
-            \nu_{T,k} := \sqrt{ 1 + \frac{ (k+1)^{2}\left( 1 + \mu_{T,k} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (k+1)\left( 1 + \mu_{T,k} \right) \aspectratio(\calT) }{2}
+            \nu_{T,\ell} := \sqrt{ 1 + \frac{ (\ell+1)^{2}\left( 1 + \mu_{T,\ell} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (\ell+1)\left( 1 + \mu_{T,\ell} \right) \aspectratio(\calT) }{2}
             .
@@
             &\leq  
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \cdot 
-            \nu_{T,k}
+            \nu_{T,\ell}
             ,
@@
             &\leq  
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
@@
             \cdot 
-            \nu_{T,k}
+            \nu_{T,\ell}
             ,
@@
             \leq 
-            (k+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,k}
+            (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell}
+            ,
+            \\
+            \sigma_{n-1}(\Psi,x)^{-1} 
+            &= 
+            \dots
+            =
+            \sigma_{  2}(\Psi,x)^{-1} 
+            \leq 
+            (\ell+1) \diameterratio(\calT) \aspectratio(T) 
             ,
@@
             \left( 
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \right)^{n},
@@
             \left( 
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
@@
             &\leq 
-            \Cfive{n}{k}(\calT)
+            \Cfive{n}{\ell}(\calT)
             :=
-            (k+1) 
+            (\ell+1) 
             \diameterratio(\calT)
             \aspectratio(\calT)
-            \mu_{T,k}^{2}
-            \nu_{T,k}           
+            \mu_{T,\ell}^{2}
+            \nu_{T,\ell}           
             ,
@@
             &\leq 
-            \Cfiveprime{n}{k}(\calT)
+            \Cfiveprime{n}{\ell}(\calT)
             :=
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
-            \aspectratio(T) \mu_{T,k}^{2}
+            \aspectratio(T) \mu_{T,\ell}^{2}
             ,
@@
             &\leq
-            \Csechs{n}{k}(\calT)
+            \Csechs{n}{\ell}(\calT)
             :=
-            (k+1) 
+            (\ell+1) 
             \diameterratio(\calT)
             \aspectratio(\calT)
-            \mu_{T,k}
-            \nu_{T,k}
+            \mu_{T,\ell}
+            \nu_{T,\ell}
             ,
@@
             &\leq 
-            \Csechsprime{n}{k}(\calT)
+            \Csechsprime{n}{\ell}(\calT)
             :=
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
@@
             \cdot 
-            \mu_{T,k}
+            \mu_{T,\ell}
             .
@@
             &\leq 
-            \Cdetfive{n}{k}(\calT)
+            \Cdetfive{n}{\ell}(\calT)
             :=
-            (k+1)^{n}
+            (\ell+1)^{n}
             \diameterratio(\calT)^{n}
-            \mu_{T,k}^{n}
+            \mu_{T,\ell}^{n}
             \aspectratio(\calT)^{n}
@@
             &\leq 
-            \Cdetsechs{n}{k}(\calT)
+            \Cdetsechs{n}{\ell}(\calT)
             :=
-            (k+1)^{n}
+            (\ell+1)^{n}
             \diameterratio(\calT)^{n}
@@
         \end{align*}
+        \color{blue}
+        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
+        \begin{align*}
+            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
+            &
+            \leq 
+            \Cfivetrafo{n}{k}{\ell}(\calT)
+            \\&
+            :=
+            \left( 
+            % Theta max 
+            \mu_{T,\ell} 
+            % Psi max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p}
+            ,
+            \\
+            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
+            &
+            \leq 
+            \Csechstrafo{n}{k}{\ell}(\calT)
+            \\&
+            :=
+            \left(
+            % Theta^{-1} max 
+            \mu_{T,\ell} 
+            % Psi^{-1} max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p}            
+            .
+        \end{align*}
         This completes the desired estimates for $\Xi_{1}$. 
+        \color{black}
 
@@
             &\leq 
-            \Csieb{n}{k}(\calT)
+            \Csieb{n}{\ell}(\calT)
             :=
-            (k+1) 
+            (\ell+1) 
             \aspectratio(\calT)
             \diameterratio(\calT)
-            \mu_{T,k}
-            \nu_{T,k}         
+            \mu_{T,\ell}
+            \nu_{T,\ell}         
             \cdot 
-            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)
             ,
@@
             &\leq 
-            \Csiebprime{n}{k}(\calT)
+            \Csiebprime{n}{\ell}(\calT)
             :=
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,k} 
+            \aspectratio(T)\mu_{T,\ell} 
             \cdot 
-            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)
             ,
@@
             &\leq  
-            \Cacht{n}{k}(\calT)
+            \Cacht{n}{\ell}(\calT)
             :=
-            (k+1) 
+            (\ell+1) 
             \diameterratio(\calT)
             \aspectratio(\calT)
-            \nu_{T,k}           
+            \nu_{T,\ell}           
             \cdot 
-            \left( 2 + 3 (k+1) \aspectratio(T) \right)
+            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
             ,
@@
             &\leq 
-            \Cachtprime{n}{k}(\calT)
+            \Cachtprime{n}{\ell}(\calT)
             :=
-            (k+1)
+            (\ell+1)
             \diameterratio(\calT)
@@
             \cdot 
-            \left( 2 + 3 (k+1) \aspectratio(T) \right)
+            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
             .
@@
             &\leq 
-            \Cdetsieb{n}{k}(\calT)
+            \Cdetsieb{n}{\ell}(\calT)
             :=
             \frac 1 2 
-            (k+1)^{n}
+            (\ell+1)^{n}
             \diameterratio(\calT)^{n}
-            \mu_{T,k}^{n}
+            \mu_{T,\ell}^{n}
             \aspectratio(\calT)^{n}
@@
             &\leq 
-            \Cdetacht{n}{k}(\calT)
+            \Cdetacht{n}{\ell}(\calT)
             :=
             2
-            (k+1)^{n}
+            (\ell+1)^{n}
             \diameterratio(\calT)^{n}
@@
         \end{align*}
+        \color{blue}
+        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
+        \begin{align*}
+            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+            &
+            \leq 
+            \Csiebtrafo{n}{k}{\ell}(\calT)
+            \\&
+            :=
+            \left( 
+            % Phi max 
+            \left( 1 + \frac 3 2 ( \ell+1 )\aspectratio(\calT) \right)
+            % Psi max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p} 2^{\frac n p}
+            ,
+            \\
+            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
+            &
+            \leq 
+            \Cachttrafo{n}{k}{\ell}(\calT)
+            \\&
+            :=
+            \left(
+            % Phi^{-1} max 
+            \left( 2 + 3 ( \ell+1 )\aspectratio(\calT) \right)
+            % Psi^{-1} max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p} 2^{\frac n p}            
+            .
+        \end{align*}
+        \color{black}
         This completes the desired estimates for $\Xi_{2}$. 
@@
     it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
+\end{remark}
+
+\begin{remark}\label{remark:improved_starreflection}
+    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
+    Some improvements are immediately possible if $\ell=n-1$. 
+    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
+    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
+    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
+    %     \begin{gather*}
+    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
+    %         \quad 
+    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
+    %         \quad 
+    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
+    %         \\ 
+    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
+    %         \quad 
+    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
+    %     \end{gather*}
+    \begin{gather*} 
+        | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
+        \quad 
+        | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT),
+        \\
+        \sigma_{1}
+        %&
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        ,
+        \\
+        \sigma_{n}^{-1}
+        %&
+        \leq 
+        \frac{1}{2} 
+        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        +
+        \frac{1}{2} 
+        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        ,
+        \\
+        \sigma_2,\dots,\sigma_{n-1} \leq 1.
+        %         \det(\Jacobian \Xi) &\leq \diameterratio(\calT) \aspectratio(T_2)
+    \end{gather*}
+    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
+    We believe that better estimates can be computed from the geometric data also in the other cases.
 \end{remark}

### 2024-12-11 main.tex
minor corrections

--- 2024-12-10 main.tex
@@
     Let $0 \leq k < n$. 
-    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
+    For each $u \in W^{p}\Lambda^{k}(\Omega)$ 
     there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
@@
         \leq 
-        C_{{\PF},k,\Omega,p}
+        C_{{\PF},\Poinc,k,\Omega,p}
         \| \cartan u \|_{L^{p}(\Omega)}
@@
     \end{align*}
+    and for each $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ 
+    there exists $w \in W^{p}_{0}\Lambda^{k}(\Omega)$ 
+    with $\cartan u = \cartan w$ and 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        C_{{\PF},\Bogov,k,\Omega,p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        ,
+    \end{align*}
     where 
     \begin{align*}
-        C_{{\PF},k,\Omega,p} 
+        C_{{\PF},\Poinc,k,\Omega,p} 
         = 
         n C_{\Poinc}(n,k+1) 
+        \vol_{}(B_1(0)) 
+        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
+        \diam(\Omega)
+        \\
+        C_{{\PF},\Bogov,k,\Omega,p} 
+        = 
+        n C_{\Bogov}(n,k+1) 
         \vol_{}(B_1(0)) 
@@
     onto the face $F_i$. 
-    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = (l+1)/n!$
+    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $\ell+1$ through $n$. 
+    We see that $\vol(\widetilde \Makoto) = (\ell+1)/n!$
 
@@
         \\&\leq 
-        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
+        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
@@
     \color{blue}
-    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $l+1$ through $n$. Thus,
+    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $\ell+1$ through $n$. Thus,
     \begin{align*}
@@
     By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{l}$.
+    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{\ell}$.
 

### 2024-12-12 draft.tex

@@
 We should unify.}
+
+This implies the following estimate for Poincar\'e--Friedrichs constants over convex domains.
+
+\begin{lemma}\label{lemma:PFexteriorsimplex}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set. 
+    Let $0 \leq k < n$. 
+    For each $u \in W^{p}\Lambda^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
+    with $\cartan u = \cartan w$ and 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        C_{{\PF},\Poinc,k,\Omega,p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        ,
+    \end{align*}
+    and for each $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ 
+    there exists $w \in W^{p}_{0}\Lambda^{k}(\Omega)$ 
+    with $\cartan u = \cartan w$ and 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        C_{{\PF},\Bogov,k,\Omega,p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        ,
+    \end{align*}
+    where 
+    \begin{align*}
+        C_{{\PF},\Poinc,k,\Omega,p} 
+        = 
+        n C_{\Poinc}(n,k+1) 
+        \vol_{}(B_1(0)) 
+        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
+        \diam(\Omega)
+        \\
+        C_{{\PF},\Bogov,k,\Omega,p} 
+        = 
+        n C_{\Bogov}(n,k+1) 
+        \vol_{}(B_1(0)) 
+        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
+        \diam(\Omega)
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
+\end{proof}
 

### 2024-12-12 main.tex

--- 2024-12-10 main.tex
@@
         &\leq 
-        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
+        % n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{1}(0)) }{\vol(\Omega)} 
+        C_{{\PF},\Poinc,k,\Omega,p}
         \| u \|_{L^{p}(\Omega)}
@@
         &\leq 
-        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        \diam(\Omega)
+        % n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        C_{{\PF},\Bogov,k,\Omega,p}
         \| u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
+        ,
+    \end{align*}
+    where 
+    \begin{align}
+        C_{{\PF},\Poinc,k,\Omega,p} := C_{\Poinc}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
+        ,
+        \quad 
+        C_{{\PF},\Bogov,k,\Omega,p} := C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
+        .
+    \end{align}
     For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
@@
     Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$. 
-    We write $\ := \Bogov_{\mia} u$. 
+    We write $\zeta := \Bogov_{\mia} u$. 
     There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
@@
 
-The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator}
-implies the following estimate for Poincar\'e--Friedrichs constants over convex domains.
-
-\begin{lemma}\label{lemma:PFexteriorsimplex}
-    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set. 
-    Let $0 \leq k < n$. 
-    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
-    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
-    with $\cartan u = \cartan w$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        C_{{\PF},k,\Omega,p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        ,
-    \end{align*}
-    where 
-    \begin{align*}
-        C_{{\PF},k,\Omega,p} 
-        = 
-        n C_{\Poinc}(n,k+1) 
-        \vol_{}(B_1(0)) 
-        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
-        \diam(\Omega)
-        .
-    \end{align*}
-\end{lemma}
-\begin{proof}
-    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
-\end{proof}
-
+The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator} has produced Poincar\'e--Friedrichs constants for convex domains and their analogues for the case of full boundary conditions.
 We also need a Poincar\'e--Friedrichs inequality for differential forms over a simplex but subject to homogeneous boundary conditions along a collection of faces.
@@
         \leq 
-        2^{n+1} 
-        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
+        n! \cdot 2^{\ell+1} 
+        C_{\Bogov}(n,k+1) 
+        \vol_{n-1}(S_1(0))
+        \cdot 
         \algebraicshapemeasure(T)^{k-1}
@@
     onto the face $F_i$. 
-    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = (l+1)/n!$
-
-    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\Delta^n)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $\ell+1$ through $n$. 
+    We see that $\vol(\widetilde \Makoto) = 2^{n-\ell}/n!$
+
+    We let $\hat u := \varphi^{\ast} u \in W^{p}\Lambda^{k}(\Delta^n)$ and define $\hat g \in L^{p}\Lambda^{k+1}(\Delta^n)$ via $\hat g := \cartan \varphi^{\ast} u$. 
     Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u$ be the extension of $\hat u$ onto $\widetilde \Makoto$ by reflection across the coordinate axes,
-    and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
+    We let $\tilde u \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be the extension of $\hat u$ onto $\widetilde \Makoto$ by reflection across the coordinate axes,
+    and let $\tilde g \in L^{p}\Lambda^{k+1}(\widetilde \Makoto)$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
     By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$ with $\tilde g = \cartan \tilde u$.
@@
     \end{align*}
-    \color{red}
-    The bounds for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc}, imply 
+    The analysis for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc}, imply 
     the existence of $\mathring w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
-    with $\cartan \mathring w = \cartan \tilde u$ and 
+    with $\cartan \mathring w = \cartan \tilde u$ satisfying the bounds 
     \begin{align*}
@@
         &\leq 
-        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 
-        2
+        C_{{\PF},\Poinc,k,\widetilde \Makoto,p}
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        \\&\leq 
-        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
+        %\\&
+        \leq 
+        % n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 2
+        % 2^n n   C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0))    }{ \vol(\widetilde \Makoto) } 2
+        % 2^n     C_{\Bogov}(n,k+1) \frac{ \vol_{n-1}(S_1(0)) }{ \vol(\widetilde \Makoto) } 2
+        % 2^{n+1} C_{\Bogov}(n,k+1) \frac{ \vol_{n-1}(S_1(0)) }{ \vol(\widetilde \Makoto) }
+        % 2^{n+1} C_{\Bogov}(n,k+1) \frac{ \vol_{n-1}(S_1(0)) }{ 2^{n-\ell}/n! }
+        %
+        % n! 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
+        %
+        n! 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
@@
     \end{align*}
-    \color{blue}
-    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $l+1$ through $n$. Thus,
+    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $\ell+1$ through $n$. Thus,
     \begin{align*}
@@
         \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
+        ,
+        \qquad 
+        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
+        \leq 
+        \| \mathring w \|_{L^{p}(\widetilde \Makoto)}
         .
@@
     Since $\tilde g$ has got the same symmetries, $\cartan \tilde w = \tilde g$.
+    \color{red}
+    \color{blue}
     \color{black}
@@
     By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{l}$.
-
-    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
+    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{\ell}$.
+
+    To complete the discussion, we recall by Proposition~\ref{proposition:pullbackestimate} that 
     \begin{align*}

### 2024-12-13 main.tex
correction
main

@@
         \leq 
-        \Cfivetrafo{n}{k}{\ell}(\calT),
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
         \qquad 
@@
         \leq 
-        \Csechstrafo{n}{k}{\ell}(\calT).
+        \Csechstrafo{n}{k}{\ell}{p}(\calT).
     \end{align*}
@@
         \leq 
-        \Csiebtrafo{n}{k}{\ell}(\calT),
+        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
         \qquad 
@@
         \leq 
-        \Cachttrafo{n}{k}{\ell}(\calT).
+        \Cachttrafo{n}{k}{\ell}{p}(\calT).
     \end{align*}
@@
             \leq 
-            \Cfivetrafo{n}{k}{\ell}(\calT)
+            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
             \\&
@@
             \leq 
-            \Csechstrafo{n}{k}{\ell}(\calT)
+            \Csechstrafo{n}{k}{\ell}{p}(\calT)
             \\&
@@
             \leq 
-            \Csiebtrafo{n}{k}{\ell}(\calT)
+            \Csiebtrafo{n}{k}{\ell}{p}(\calT)
             \\&
@@
             \leq 
-            \Cachttrafo{n}{k}{\ell}(\calT)
+            \Cachttrafo{n}{k}{\ell}{p}(\calT)
             \\&
@@
         %
-        n! 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
+        n! \cdot 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
@@
             +
-            \Cfive{n}{k}(\calT)
-            \Cfiveprime{n}{k}(\calT)^{k} 
-            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+            % \Cfive{n}{k}(\calT)
+            % \Cfiveprime{n}{k}(\calT)^{k} 
+            % \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
             \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
         \right)
-        \\&\qquad
+        %\\&\qquad
         + 
-        \Cfive{n}{k}(\calT) 
-        \Cfiveprime{n}{k}(\calT)^{k-1} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+        % \Cfive{n}{k}(\calT) 
+        % \Cfiveprime{n}{k}(\calT)^{k-1} 
+        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
         \| w \|_{L^{p}(\Makoto_{m-1})}
-        .
-    \end{align*}
+        ,
+    \end{align*}
+    where $0 \leq \ell < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices. 
 \end{theorem}
@@
     and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star. 
+    We write $\ell$ for the dimension of $S_{m}$.
 
@@
         &\leq 
-        \Cfive{n}{k}(\calT)
-        \Cfiveprime{n}{k}(\calT)^{k-1}
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+        % \Cfive{n}{k}(\calT)
+        % \Cfiveprime{n}{k}(\calT)^{k-1}
+        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
         \cdot 
@@
         &\leq 
-        \Cfive{n}{k}(\calT)
-        \Cfiveprime{n}{k}(\calT)^{k}
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+        % \Cfive{n}{k}{\ell}(\calT)
+        % \Cfiveprime{n}{k}(\calT)^{k}
+        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
         \cdot 
@@
     \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        \leq 
+        \| w \|_{L^{p}(\Omega)}
+        \leq 
+%         \left( 
+%             \Cachttrafo{n}{k}{\ell}(\calT)
+            % \Cacht{n}{k}(\calT)
+            % \Cachtprime{n}{k}(\calT)^{k} 
+            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+%             \Csiebtrafo{n}{k}{\ell}(\calT)
+            % \Csieb{n}{k}(\calT)
+            % \Csiebprime{n}{k}(\calT)^{k-1} 
+            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+%         \right)^{M}
         \left( 
-        \Cacht{n}{k}(\calT)
-        \Cachtprime{n}{k}(\calT)^{k} 
-        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-        \Csieb{n}{k}(\calT)
-        \Csiebprime{n}{k}(\calT)^{k-1} 
-        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-        \right)^{M}
+        \prod_{m=1}^{M}
+            \Cachttrafo{n}{k}{\ell_{m}}{p}(\calT)
+            \Csiebtrafo{n}{k}{\ell_{m}}{p}(\calT)
+        \right)
         C_{{\PF},k,T_{0},p}
         \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align*}
+        ,
+    \end{align*}
+    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices.
 \end{theorem}
@@
     and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star. 
+    We let $\ell_{M}$ be the dimension of $S_{M}$.
 
@@
         \leq 
-        \Cacht{n}{k}(\calT)
-        \Cachtprime{n}{k}(\calT)^{k} 
-        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
+        %\Cacht{n}{k}(\calT)
+        %\Cachtprime{n}{k}(\calT)^{k} 
+        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
         \| g \|_{L^{p}(\Omega)}  
@@
     \end{align*}
-    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$ and 
-    \begin{align*}
-        \| w' \|_{L^{p}(\Omega')} 
-        \leq 
-        \left( 
-        \Cacht{n}{k}(\calT)
-        \Cachtprime{n}{k}(\calT)^{k} 
-        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-        \Csieb{n}{k}(\calT)
-        \Csiebprime{n}{k}(\calT)^{k-1} 
-        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-        \right)^{M-1}
-        C_{{\PF},k,T_{0},p}
-        \| g' \|_{L^{p}(\Omega')}  
-    \end{align*}
+    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
+%     We have 
+%     \begin{align*}
+%         \| w' \|_{L^{p}(\Omega')} 
+%         \leq 
+%         \left( 
+%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
+%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
+%         \right)^{M-1}
+%         C_{{\PF},k,T_{0},p}
+%         \| g' \|_{L^{p}(\Omega')}  
+%     \end{align*}
     Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
@@
         \leq 
-        \Csieb{n}{k}(\calT)
-        \Csiebprime{n}{k}(\calT)^{k-1} 
-        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
+        %\Csieb{n}{k}(\calT)
+        %\Csiebprime{n}{k}(\calT)^{k-1} 
+        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
         \| w' \|_{L^{p}(\Omega')} 
     \end{align*}
-    The induction step is complete, and the desired result follows. 
+    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
 \end{proof}
@@
         C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \Cfive{n}{k}(\calT)
-        \Cfiveprime{n}{k}(\calT)^{k} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT)
+%         \Cfiveprime{n}{k}(\calT)^{k} 
+%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
         \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
@@
         + 
-        \Cfive{n}{k}(\calT) 
-        \Cfiveprime{n}{k}(\calT)^{k-1} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT) 
+%         \Cfiveprime{n}{k}(\calT)^{k-1} 
+%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
         \| w \|_{L^{p}(\Makoto_{m-1})}
@@
     \end{align*}
-
     Hence, 
@@
     Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
+    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell$ faces with the previous simplices.
     \begin{itemize}
@@
                 +
-                \Cfive{n}{1}(\calT)
-                \Cfiveprime{n}{1}(\calT)^{1} 
-                \Cdetsechs{n}{1}(\calT)^{\frac 1 p} 
+                \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
                 \| \curl u \|_{L^{p}(\Makoto_{m-1})}
@@
             + 
-            \Cfive{n}{1}(\calT) 
-            \Cdetsechs{n}{1}(\calT)^{\frac 1 p} 
+            \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
             \| \bfw \|_{L^{p}(\Makoto_{m-1})}
@@
             \left( 
-            \Cacht{n}{1}(\calT)
-            \Cachtprime{n}{1}(\calT) 
-            \Cdetsieb{n}{1}(\calT)^{\frac 1 p} 
-            \Csieb{n}{1}(\calT)
-            \Cdetacht{n}{1}(\calT)^{\frac 1 p} 
-            \right)^{M}
+            \prod_{i=1}^{M}
+            \Cachttrafo{n}{1}{\ell_{m}}{p}(\calT)
+            \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)
+            \right)
             C_{{\PF},1,T_{0},p}

### 2024-12-13 main.tex
tables

--- 2024-12-11 main.tex
@@
 
-% LTeX: enabled=false
 % Title, authors, and affiliations
@@
 \date{}
-% LTeX: enabled=true
 
@@
 
-This manuscript contributes to the theory of computable estimates for Poincar\'e--Friedrichs inequalities for the differential operators of vector calculus. 
+This manuscript contributes to the theory of computable estimates for Poincar\'--Friedrichs inequalities for the differential operators of vector calculus. 
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
@@
 \end{align}
-This inequality is called \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
+We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
 The question is therefore whether we can always find a gradient potential of sufficiently small norm so this inequality holds. 
@@
 %the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$.
-%Hence, we want to evaluate the \emph{operator norm} of the potential operator 
+%Hence we want to evaluate the \emph{operator norm} of the potential operator 
 \begin{align}\label{math:intro:gradient:potentialnorm}
@@
 where $u_\Omega$ denotes the average of $u$. We emphasize that the average-free potential is generally not the norm-minimizing potential unless $p = 2$.
-Hence, the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs differ in general. 
+Hence the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs differ in general. 
 Considerable research efforts have gone into determining constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
@@
 We study potentials and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
-There are substantial changes and much fewer results are available in the literature. 
+There are substantial changes and much less results are available in the literature. 
 We use the spaces of vector field 
@@
     &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+    .
 \end{align}
@@
 This formalism is independent of the spatial dimension and highlights extends the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
-% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-% In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: 
-For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
+% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}:
+for every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
 \begin{align} \label{math:intro:exterior:pf} 
@@
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that not only is a preimage under the curl operator but also has vanishing tangential trace along the same three faces. 
+we want to find the unique vector field potential that not only is a preimage under the curl operator but that also has vanishing tangential trace along the same three faces. 
 We achieve this by constructing an auxiliary problem subject to full boundary conditions,
@@
 We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
-However, we need to overcome new challenges that arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
+However, we need to overcome new challenges that are arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
 The basic inductive strategy remains the same. 
@@
 % 6. Contractible 
-Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
+Inspired by the contractibility of shellable triangulations, we pursuit an additional estimate for Poincar\'e--Friedrichs constants. 
 Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
@@
 
-% LTeX: enabled=false
 The remainder of this manuscript is structured as follows.
@@
 Our regularized potentials over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
-giving rise to computable Poincar\'e--Friedrichs constants as their operator norms. 
+giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
 We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
@@
 We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}.
-% LTeX: enabled=true
 
@@
 We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potentials.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below, but we believe it is also of independent interest.
-\\
-
-Let $\Omega \subseteq \bbR^{n}$ be a connected open set. 
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
+\\
+
+Let $\Omega \subseteq \bbR^{n}$ be an open connected set. 
 Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
@@
 Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:
-since taking the average is a projection onto the constants functions with unit norm, from~\eqref{math:aver_norm} it now follows that 
+since taking the average is a the projection onto the constants functions with unit norm, from~\eqref{math:aver_norm} it now follows that 
 % From~\eqref{math:aver_norm}, Stern's generalized projection estimate~\cite[Theorem~4.1, Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$ as 
@@
 \end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is the smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$.
@@
 % \end{align*}
-One calls any set triangulable if it is the underlying set of some triangulation.
+We call any set triangulable if it is the underlying set of some triangulation.
 
@@
 % Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
-Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, members with codimension one) of this triangulation.\footnote{
+Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
     Our use of the term \textit{face} as is common in classical geometry and the finite element literature~\cite{brenner2008mathematical}
@@
 
-% LTeX: enabled=false
 We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
@@
 and we call $\calT$ \emph{face-connected} if it has only one face-connected component.
-% LTeX: enabled=true
 
@@
 We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any vertex of the simplex $T$,
+Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$,
 where the height of a vertex is defined as the distance to the affine span of its opposing face.
@@
     equals the maximum of the quotient $\| M x \|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
-    The diameter of $T$ is the length of its longest edge. 
+    We also know that the diameter of $T$ is the length of its longest edge. 
     Our first pair of inequalities follows via standard comparisons of Euclidean norms:
@@
         \frac{ \vol(T_1) }{ \vol(T_2) }
+        \leq 
         % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
@@
         % = 
-        \leq 
-        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
-        \leq 
         \aspectratio(T_1) \aspectratio(T_2)
@@
     If $\Xi : T_1 \rightarrow T_2$ is the affine diffeomorphism that is the identity over $F$, then 
-%     \begin{align*}
-%         \matnorm{ \Jacobian \Xi }
-%         \leq 
-%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2}
-%         % ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-%         % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-%         .
-%     \end{align*}
-    \begin{gather*}
-        \matnorm{ \Jacobian \Xi^{  } } \leq \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
-        \quad 
-        \matnorm{ \Jacobian \Xi^{-1} } \leq \aspectratio(T_2) + \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_1),
-        \\
-        \det(\Jacobian \Xi)            \leq \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
-    \end{gather*}
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2}
+        % ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
+        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
+        .
+    \end{align*}
+%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
 \end{lemma}
+
 \begin{proof}
@@
         \aspectratio(T_{1}) \aspectratio(T_{2})
-        ,
-        \qquad 
-        \frac{ \diam(T_1) }{ h_2 }
-        \leq
-        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2})
-        .
-    \end{align*}
-    \color{blue}
+        .
+    \end{align*}
     Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    To estimate the Lipschitz constant of $\Xi$, we study the singular values of its Jacobian. 
-    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and contains the origin. 
-    Write $z_1 \in T_1$ and $z_2 \in T_2$ for the two vertices not contained in $F$.
-    There exists a unit height vector $\hat h_0$ that goes in the direction of the vertex $z_1$. 
-    Without loss of generality, $\hat h_0$ is in the $n$-th coordinate direction.
-    Suppose that $b_1, b_2 \in F$ such that $z_1 = b_1 + h_1 \hat h_0$ and $x_2 = b_2 + h_2 \hat h_0$.
-    The mapping $\Xi$ is linear, being the identity over $F$ and mapping $z_1$ to $z_2$. Hence,
-    \begin{align*}
-        \Xi( \hat h_0 ) = h_1^{-1} ( b_2 - b_1 ) + h_2 h_{1}^{-1} \hat h_0.
-    \end{align*}
-    We see that $\Xi$ equals the identity over the orthogonal complement of the span of $\hat h_0$ and $b_2 - b_1$.
-    The only singular values of its Jacobian are the two singular values $\sigma_{-} \leq 1 \leq \sigma_{+}$ of the matrix 
-    \begin{align*}
-        \begin{pmatrix}
-            a & 0 
-            \\
-            c & 1
-        \end{pmatrix},
-        \qquad 
-        a = h_2 / h_1,
-        \qquad 
-        c = \|b_2-b_1\| / h_1
-        .
-    \end{align*}
-    These are 
-    \begin{align*}
-        \sigma_{\pm} 
-        &
-        = 
-        \frac{1}{\sqrt{2}} \sqrt{ 1 + a^2 + c^2 \pm \sqrt{ \left( 1 + a^2 + c^2 \right)^{2} - 4a^{2} } } 
-        \\&
-        =
-        \frac{1}{\sqrt{2}} \sqrt{ 1 + a^2 + c^2 \pm \sqrt{ \left( (1+a)^2 + c^2 \right)\left( (1-a)^2 + c^2 \right) } } 
-        \\&
-        =
-        \frac{1}{2} 
-        \left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
-        .
-    \end{align*}
-%     This implies the determinant identity and estimate 
+    We estimate the Lipschitz constant of $\Xi$ as follows. 
+    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and contains the origin, 
+    and the unit height vector $h_0$ goes in the direction of the vertex $z_1$ is in the $n$-th coordinate direction.
+    Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha h_0$ and $x' = b' + \alpha' h_0$.
+    Since $\Xi(h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
+    \begin{align*}
+        \| \Xi(x) - \Xi(x') \|
+        \leq  
+        \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
+        \leq  
+        \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| h_0 \|
+        \leq 
+        \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
+        .
+    \end{align*}
+    % Writing $h_0$ for the unit normal in direction $z_1$, we have 
     % \begin{align*}
-%         \det( \Jacobian \Xi ) 
+        % \Xi(x) 
         % = 
-%         \frac 1 4 \left( (1+a)^2 - (1-a)^2 \right) 
-%         &
-%         = 
-%         a
-%         \leq 
-%         \aspectratio(T_{1}) \aspectratio(T_{2}) 
+        % x 
+        % - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
+        % + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
+        % ,
+        % \qquad 
+        % x \in \bbR^{n}
         % .
     % \end{align*}
-    We remark that this provides the upper bound 
-    \begin{align}
-        \sigma_{+} 
-        &\leq 
-        \sqrt{ \left( 1 + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) \right)^{2} + \aspectratio(T_{1})^{2} }
-        .
-    \end{align}
-%     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
-%     Since $\Xi(\hat h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
+    % Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
+    % By the Xu-Zikanatov estimate,
     % \begin{align*}
-%         \| \Xi(x) - \Xi(x') \|
+        % \matnorm{ \Jacobian \Xi }
         % \leq 
-%         \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
+        % \frac{ \diam(T_1) }{ \height(T_1) }
+        % +
+        % \frac{ \diam(T_2) }{ \height(T_1) }
         % \leq 
-%         \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| \hat h_0 \|
-%         \leq 
-%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
+        % \left( 1 + \aspectratio(T_2) \right)
+        % \aspectratio(T_1)
         % .
     % \end{align*}
-    \color{red}
-    The linear mapping $\Xi$ takes the form Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_1
-        + \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
-    \begin{align*}
-        % \matnorm{ \Jacobian \Xi }
-        \sigma_{+} 
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
-        .
-    \end{align*}
-    Analogous upper bound holds for $\sigma^{-1}_{-}$.
-%     \begin{align}
-%         \sigma_{-}^{-1} \leq \left( 1 + \aspectratio(T_1) \right) \aspectratio(T_2)
-%     \end{align}
     The desired estimates are shown.
-% \begin{comment}
-    \color{Mulberry}
+\begin{comment}
     \mwl{Tighter estimate via geometry}
@@
     \end{align*}
-% \end{comment}
+\end{comment}
 \end{proof}
@@
 %     \end{align*}
-%     Hence, 
+%     Hence 
     \begin{align*}
@@
     \end{gather*}
-    Whenever $T_0, T_1, \dots, T_M$ is a face path,
-    then for all $1 \leq m \leq$ the following recursive estimates:
+    and whenever $T_0, T_1, \dots, T_M$ is a face path,
+    then for all $1 \leq m \leq$ we the following recursive estimates:
     \begin{align*}
@@
     \end{align*}
-    An application of Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''} gives 
+    We apply Lemma~\ref{lemma:mixedbconsimplex} to the first expression in~\eqref{equation:w''}, which gives 
     \begin{align*}
@@
     \end{align*}
-    Now we observe that 
+    We now observe that 
     \begin{gather*}
@@
 
-    \color{green}Hence, 
+    \color{green}Hence 
     \begin{align}
@@
     \end{align}
-    Instead, if $p \leq q$, that is, $p \leq 2$, then 
+    Instead if $p \leq q$, that is, $p \leq 2$, then 
     \begin{align}
@@
 $\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
-These are defined 
+We define them 
 for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
@@
 We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
-if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration-by-parts formula
+if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
 \begin{align*}
@@
 We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration-by-parts formula
+% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
 such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
 whose support lies in the open ball $B_r(x)$
-we have the integration-by-parts formula
+we have the integration by parts formula
 \begin{align*}
@@
 \begin{proof}
-    See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}.
+    See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}).
 \end{proof}
@@
     \end{align*}
-    Hence, $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
+    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.
 
@@
 Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
-We estimate $\Poinc_{\mia} u(x)$ pointwise for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
+We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
 \begin{align*}
@@
 where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
-One computes 
+We compute 
 \begin{align*}
@@
 
-In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$
-and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
+In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
+So the convolution of $u$ is taken against an integrable function. 
 Young's convolution inequality now implies: 
@@
 First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$.
-Hence, $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
+Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
 Consider now the case $x \in \overline\Omega$. 
@@
 which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
-Similar as above,
-the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$
-and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
+In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
+So the convolution of $u$ is taken against an integrable function. 
 Young's convolution inequality now implies: 
@@
 
-\color{blue}
 \subsection{Interaction of potentials with the exterior derivative}
@@
 We write down the full definition of these operators and perform two substitutions.
-For the Poincar\'e operator, we substitute $a = x + t(y-x)$, and then we substitute $s = (t-1)/t$,
+For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
 leading to 
@@
 \end{align*}
-For the Bogovski\u{\i} operator, we first substitute $a = y + t(x-y)$, and then we substitute $s = t/(t-1)$,
+For the Bogovski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
 leading to 
@@
 \end{align*}
-On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
-These do not depend on the eccentricity of the domain.
-
-We begin with the Poincar\'e operator. 
-By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
-    &
-    \leq 
-    \diam(\Omega)^{p}
-    \vol(\Omega)^{-1}
-    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
-    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{0}^{1} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{0}^{1} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{\Omega} 
-    |u( z )|^{p}
-    \int_{0}^{1} 
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \,dt \,dz 
-    .
-\end{align*}
-\color{red}
-A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
-    &
-    \leq 
-    \diam(\Omega)^{p}
-    \vol(\Omega)^{-1}
-    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
-    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{1}^{\infty} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{1}^{\infty} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{\Omega} 
-    |u( z )|^{p}
-    \int_{1}^{\infty} 
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \,dt \,dz 
-    .
-\end{align*}
-\color{blue}
-We estimate 
-\begin{align*}
-    \int_{0}^{1}
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \ dt
-    &
-    \leq 
-    \int_{0}^{1}
-    \min\left( 
-        \vol\left(\Omega\right), 
-        \vol\left( \tfrac{t}{1-t} \Omega \right) 
-    \right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \ dt
-    \\&
-    \leq 
-    \int_{0}^{1}
-    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
-    t^{p(k-1)} 
-    \ dt
-    \\&
-    \leq 
-    \int_{0}^{1}
-    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
-    t^{k-1} 
-    \ dt
-    .
-\end{align*}
-\begin{align*}
-    \int_{\frac 1 2}^{1}
-    t^{-n+k-1}
-    \ dt
-    =
-    \frac{2^{n-k}-1}{n-k}
-    \\
-    \int_{0}^{\frac 1 2} 
-    \frac{ t^{k-1} }{ (1-t)^{n} }
-    \ dt
-    \leq 
-    \int_{0}^{\frac 1 2} 
-    (1-t)^{-n+k-1}
-    \ dt
-    =
-    \frac{2^{n-k}-1}{n-k}
-    .
-\end{align*}
-
-\subsection{Interaction of potentials with the exterior derivative}
-\color{black}
-We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
+We study the interaction of these potential operator with the exterior derivative in more detail.
 % 
-The main arguments are well-known and establish the exactness of several de~Rham complexes. 
+The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
 We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.
@@
 \end{align*}
-Next, we add the exterior derivative of the potential and the potential of the exterior derivative.
+We add the exterior derivative of the potential and the potential of the exterior derivative.
 Taking into account cancellations, this gives the identity 
@@
     Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
-    whose smallest singular value is bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
+    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
     The adjoint is the closed densely-defined linear operator $-\divergence : \bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
@@
 All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifold's boundary. 
+We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifolds boundary. 
 We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
@@
 
-We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. 
-This topic is surprisingly non-trivial. We only gather some results that are hard to find in the literature.
+We continue with a few more observations about the topology of local patches (stars) of manifold triangulations. This topics is surprisingly non-trivial and 
+we gather some results that are hard to find in the literature.
 
@@
     % \end{align*}
-    The collection $\calS^\ast$ of these simplices and their subsimplices constitute a simplicial complex 
+    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
     that triangulates the same underlying set as $\calS$.
-    Moreover, $\calS^\ast = \patch_{\calS^\ast}(z_{S})$. 
-    In particular, $z_{S}$ is a boundary vertex of $\calS^\ast$ if and only if $S$ is a boundary simplex of $\calS$. 
+    Moreover, $\calS' = \patch_{\calS'}(z_{S})$. 
+    In particular, $z_{S}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
     So it remains to study the topology of vertex stars.
@@
 %     
-%     If $z$ is an inner vertex of $\calS^\ast$, 
-%     then the boundary simplices of $\calS^\ast$,
+%     If $z$ is an inner vertex of $\calS'$, 
+%     then the boundary simplices of $\calS'$,
 %     which are the boundary simplices of $\calS$, triangulate a topological sphere of dimension $n-1$.
 %     
-%     Now suppose that $z$ is a boundary vertex of $\calS^\ast$,
+%     Now suppose that $z$ is a boundary vertex of $\calS'$,
 %     which is the case if and only if $S$ is a boundary simplex. 
@@
 
-Suppose that $\calT$ is an $n$-dimensional simplicial complex and that we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
+Suppose that $\calT$ is an $n$-dimensional simplicial complex and we have an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$.
 For any enumeration, we call 
@@
     then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
-    Hence, $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
+    Hence $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
     which requires $m = M$.
@@
     We call a triangle $T \in \calT$ \emph{good in $\calT$} if it intersects the boundary $\partial M$ in a non-empty union of edges. 
-    Hence, a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
+    Hence a triangle is good in $\calT$ if its intersection with $\partial M$ is either one, two, or three edges,
     and a triangle is not good in $\calT$ if that intersection is either empty, only some of its vertices, or a vertex and the opposite edge.
@@
     So each component has at least one triangle that is also good in $\calT$. 
-    Hence, $\calT$ contains two good triangles, which completes the induction step.
+    Hence $\calT$ contains two good triangles, which completes the induction step.
 
@@
 \begin{lemma}\label{lemma:stars_are_shellable}
-    Let $\calT$ be an $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
+    Let $\calT$ be a $n$-dimensional shellable triangulation and $V \in \Vertices(\calT)$ be a vertex.
     Then $\patch_{\calT}(V)$ is shellable. 
@@
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations might be shellable. 
-    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an example of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
+    We refer to~\cite[Example 8.9]{ziegler1995lectures} for an examples of non-shellable triangulations of cubes and tetrahedra in three dimensions. 
 \end{remark}
@@
 
-\clearpage
 We now provide the desired bi-Lipschitz transformation:
@@
         \\
-        \sigma_n^{-1} \leq \Csechs{n}{k}(\calT),
+        \sigma_n \leq \Csechs{n}{k}(\calT),
         \quad 
@@
         \\
-        \sigma_n^{-1} \leq \Cacht{n}{k}(\calT),
+        \sigma_n \leq \Cacht{n}{k}(\calT),
         \quad 
@@
     \end{gather*}
+%     and which satisfies the upper bounds 
+%     \begin{gather*}
+%         \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
+%         \quad 
+%         \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
+%         \\
+%         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
+%         \quad 
+%         | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
+%     \end{gather*}
     \end{enumerate}
@@
         \item 
-        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin. 
+        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
         % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
@@
         %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
-        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
+        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
         whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
@@
         \item 
-        We let $z_{S'}$ be the midpoint of $S'$. 
-        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calD$ of the underlying set $\underlying{T}$. 
-        Obviously, all $n$-simplices in $\calD$ contain $S$ and $z_{S'}$.
-
-        We define another simplicial complex $\calD^c$ as follows:
-        given any $n$-simplex $K \in \calD$, 
+        We let $z'_{S}$ be the midpoint of $S'$. 
+        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
+        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.
+
+        We define another simplicial complex $\calS^c$ as follows:
+        given any $n$-simplex $K \in \calS$, 
         we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
-        thus obtaining a new simplex $K^{c}$. 
-        Indeed, that $\calD^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
-
-        We let the simplicial complex $\calD^\ast$ be the union of $\calD$ and $\calD^c$. 
+        thus obtaining a new simplex $K'$. 
+        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.
+
+        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
         By construction, all its $n$-simplices contain $S$ as a subsimplex,
-        % Indeed, $\calD^\ast$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
+        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
         Moreover, $S$ is an inner subsimplex of that triangulation. 
-        In particular, $\calD^\ast$ is its own star around $S$.
-
-        % TODO Check that $\calD^\ast$ is a triangulation
+        In particular, $\calS'$ is its own star around $S$.
+
+        % TODO Check that $\calS'$ is a triangulation
 
         \item 
-        As additional step, we introduce another simplicial complex $\calG^\ast$ from $\calD^\ast$ via barycentric subdivision of $S$.
-        Then $\calG^\ast$ is its own local star around the barycenter $z_S$.
-        In particular, all $n$-simplices in $\calG^\ast$ contain $z_{S}$. 
-        The simplicial complex $\calG^\ast$ also contains as subcomplexes the corresponding refinements of $\calD$ and $\calD^{c}$, 
-        which we denote by $\calG$ and $\calG^{c}$, respectively.
-        Given any $n$-simplex in $\calG$, replacing its vertex $z_{S}$ with its opposite $-z_{S}$ gives an associated $n$-simplex in $\calG^{c}$.
+        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
+        Then $\calR'$ is its own local star around the barycenter $z_S$.
+        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
+        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
+        which we denote by $\calR$ and $\calR^{c}$, respectively.
 
@@
         \item 
-        % Notice that $A_{G^{c}}$ and $A_{G}$ have the same singular values. Thus
+        We introduce a new mapping $\Theta : \underlying{\calR} \rightarrow \underlying{\calR^c}$ between the underlying sets as follows.
+        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
+        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
+        be affine reference transformations
+        that agree on the vertices common to $K$ and $K'$.
+        Then the mapping 
+        \begin{align*}
+            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
+        \end{align*}
+        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
         % \begin{align*}
-        %     \matnorm{ \Jacobian \Theta_{|G}      } &\leq \| A_{G^{c}} \| \cdot \| A_{G}^{-1} \| \leq \geometricshapemeasure(A_{G}),
+        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
         %     \\
-        %     \matnorm{ \Jacobian \Theta_{|G}^{-1} } &\leq \| A_{G^{c}}^{-1} \| \cdot \| A_{G} \| \leq \geometricshapemeasure(A_{G}).
+        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
         % \end{align*}
-        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
-        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
-        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
-        be affine reference transformations
-        that agree on the vertices common to $G$ and $G^{c}$.
-        Then the mapping 
-        \begin{align*}
-            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}
-        \end{align*}
         preserves volumes:
         \begin{align*}
-            |\det( \Jacobian      \Theta_{|G} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|G} )|
+            |\det( \Jacobian      \Theta_{|K} )|
+            = 
+            |\det( \Jacobian^{-1} \Theta_{|K} )|
             =
@@
         We want to characterize the singular values of this transform. 
-        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
-        We verify that 
-        \begin{align*}
-            \Theta_{|G}(x) 
+        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
+        We can write
+        \begin{align*}
+            \Theta_{|K}(x) 
             = 
@@
         \begin{align*}
-            \Theta_{|G}( h_{z} ) 
+            \Theta_{|K}( h_{z} ) 
             &= 
@@
         \end{align*}
-        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
+        Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
@@
         \begin{align*}
-            M_{\Theta,G} 
+            B 
             := 
@@
         \end{align*}
-        We compute the eigenvalues of the symmetric matrix $M_{\Theta,G}^{\ast} M_{\Theta,G}$. 
-        Its square roots are the desired singular values of $M_{\Theta,G}$:
+        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
+        Its square roots are the desired singular values of $B$:
         \begin{align}
-            \sigma_{\max}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
+            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
             ,
             \\
-            \sigma_{\min}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
+            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
             .
         \end{align}
-        They are mutual reciprocals of each other, and they are monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
-        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,
+        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
+        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
         whereas all its other singular values equal $1$.
@@
 
-        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
+        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
+        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
         which must be contained in some face of $T$. 
         Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
-        Thus, 
+        Thus 
         \begin{align*}
@@
         \begin{align}\label{math:upper_bound_for_theta}
-            \mu_{T,k} 
+            B_{T} 
             := 
@@
         \end{align}
-        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
-        \begin{align}
-            \sigma_{1}(\Theta,x) \leq \mu_{T,k},
-            \quad 
-            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
-            \quad 
-            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,k}.
-        \end{align}
-        \color{red}It is also evident that the eigenvalues of the Jacobian almost everywhere have magnitude $1$.\color{black}
 
         \item 
-        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
-        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
+        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
+        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
         We construct a bi-Lipschitz mapping 
         \begin{align*}
-            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
-        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
-        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
-        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
+            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
+        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
+        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
+        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
         has a unique representation
         \begin{align*}
-            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
-        \end{align*}
-        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
+        \end{align*}
+        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
         \begin{align*}
@@
         \begin{align*}
-            \Phi_{G}(x) 
+            \Phi_{K}(x) 
             &
             := 
-            \mu x_{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
+            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
             \\&
@@
         \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
+        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
         that satisfies the desired mapping properties. 
@@
         \begin{align*}
-            \Jacobian \Phi_{G}(x)
+            \Jacobian \Phi_{K}(x)
             &=
@@
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
-        \begin{align*}
-            M_{\Phi,G} 
+        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
+        \begin{align*}
+            C 
             = 
@@
             \end{pmatrix}
-            \\
-            \color{red}
-            M_{\Phi,G} 
-            = 
-            \begin{pmatrix}
-                -\frac 1 2             & 0 
-                \\
-                -\frac 3 2 \tan(\beta) & 1 
-            \end{pmatrix}
-            = 
-            \frac 1 2 
-            \begin{pmatrix}
-                -1 & 0 
-                \\
-                -3\tan(\beta) & 1 
-            \end{pmatrix}
-        \end{align*}
-        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
-        we obtain the singular values 
-        \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            := 
+        \end{align*}
+        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
+        \begin{align*}
+            \sigma_{\max} 
+            = 
             \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
@@
             \\
-            \sigma_{\min}(\Phi,G)
-            := 
+            \sigma_{\min} 
+            = 
             \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
@@
         \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            := 
+            \sigma_{\max} 
+            = 
             \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
@@
             \\
-            \sigma_{\min}(\Phi,G) 
-            := 
+            \sigma_{\min} 
+            = 
             \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
@@
         \end{align*}
-        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
-        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$. 
-        Therefore,
+        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
+        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
         \begin{align*}
@@
         \end{align*}
-        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
         Similar as above, we use the upper bound 
@@
         \end{align*}
-        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
+        We conclude that 
         \begin{gather}
-            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
+            \matnorm{ \Jacobian\Phi_{K} } 
             \leq 
@@
             \\
-            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
-            \\
-            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
+            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
             \leq 
@@
         \end{gather}
-        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $-\tfrac 1 2$ with multiplicity $1$.\color{black}
         This finishes the discussion of the transformation $\Phi$.
@@
         \end{align*}
-        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\|a\|$.
+        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
         We thus consider the upper bound 
@@
         \end{align*}
-        \color{red}Lastly, the matrix $\Id + \hat x \otimes a^{t}$ has the eigenvalue $1$ with multiplicity $n-1$ and a trace of $n + \langle a, \hat x \rangle$,
-        so it has one eigenvalue $1 + \langle a, \hat x \rangle$.\color{black}
 
@@
         \begin{align*}
-            \Psi : \underlying{\calG^\ast} \rightarrow \underlying{\calK}.
-        \end{align*}
-        Recall that $\calG^\ast$ and $\calK$ are their own respective stars around the origin,
+            \Psi : \underlying{\calR'} \rightarrow \underlying{\calK}.
+        \end{align*}
+        Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,
         so they must contain an open ball around the origin. 
         % TODO \mwl{Here we need to show that it is indeed a ball. It must be a domain triangulation.}
-        Let ${G} \in \calG^\ast$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
+        Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
 There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-We let $h_{{G}}$ and $h_{K}$ be the normal vectors of the origin within ${G}$ and $K$, respectively.
+We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively.
 They define respective hyperplanes $H_{G}$ and $H_{K}$,
@@
         \begin{gather*}
-            % \matnorm{ \Jacobian\Psi(x) }
-            \sigma_{1}( \Jacobian\Psi(x) )
+            \matnorm{ \Jacobian\Psi(x) }
             = 
@@
             \right)
-            ,
-            \\
-            % \matnorm{ \Jacobian\Psi(z)^{-1} }
-            \sigma_{1}( \Jacobian\Psi(z)^{-1} )
+            \\
+            \matnorm{ \Jacobian\Psi(z)^{-1} }
             = 
@@
             \\
-            \sigma_{2}( \Jacobian\Psi(x) ) = \dots = \sigma_{n-1}( \Jacobian\Psi(x) )
-            =
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            ,
-            \\
             \det\Jacobian\Psi(x)
@@
             \qquad
-            \det\Jacobian\Psi^{-1}(z)
+            \det\Jacobian\Psi^{-1}(x)
             =
@@
             \right)^{n}
-            .
         \end{gather*}
@@
         % 
-        In order to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
-        In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
+        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
         that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
@@
         It remains to find a lower bound for $\| h_{G} \|$.
-        Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
-        by scaling with $(k+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,k}$.
-The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
+        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
+        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
+        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
+The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
         %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
@@
             &\leq 
-            (k+1)\mu_{T,k}
+            (k+1)B_{T}
             \frac{ \diam(K) }{ \| h_{T} \| }
             \leq 
-            (k+1)\mu_{T,k}
+            (k+1)B_{T}
             \diameterratio(\calT)
@@
             \leq 
-            (k+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
             \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \mu_{T,k}
             ,
@@
             \leq 
-            (k+1)
-            \aspectratio({G}) \mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (k+1)B_{T}
+            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
         %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calG^\ast$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calD^\ast$ and $\patch_{\calT}(S)$
+        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
+        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
         %         with the factor $(k+1)^{-1}$.
@@
             (k+1) 
-            \left( 1 + \mu_{T,k} \right)
+            \left( 1 + B_{T} \right)
             \sup_{ K \in \patch_{\calT}(S) }
@@
         \end{align*}
-        We define 
-        \begin{align}
-            \nu_{T,k} := \sqrt{ 1 + \frac{ (k+1)^{2}\left( 1 + \mu_{T,k} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (k+1)\left( 1 + \mu_{T,k} \right) \aspectratio(\calT) }{2}
-            .
-        \end{align}
-        In summary, 
-        the singular values of the Jacobian of $\Psi$ at almost every $x$ satisfy 
-        % using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, 
-        \begin{align}
-            \sigma_{1}(\Psi,x) % \matnorm{ \Jacobian\Psi(x) }
+        In summary, using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, we find the upper bounds 
+        \begin{align*}
+            \matnorm{ \Jacobian\Psi(x) }
             &\leq  
+            (k+1)B_{T}
+            \diameterratio(\calT)
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \cdot 
+            \left( 
+                1 
+                + 
                 (k+1) 
-            \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \cdot 
-            \nu_{T,k}
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT) 
+            \right)
             ,
             \\
-            \sigma_{n}(\Psi,x)^{-1} % \matnorm{ \Jacobian\Psi(z)^{-1} }
+            \matnorm{ \Jacobian\Psi(z)^{-1} }
             &\leq  
@@
             \cdot 
-            \nu_{T,k}
-            ,
-            \\
-            \sigma_{  2}(\Psi,x) 
-            &= 
-            \dots
-            =
-            \sigma_{n-1}(\Psi,x) 
-            \leq 
-            (k+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,k}
+            \left( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT) 
+            \right)
             ,
@@
             \left( 
-            (k+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,k} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \right)^{n},
@@
             \right)^{n}
-            .
-        \end{align}
+        \end{align*}
         We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
@@
             \aspectratio(\calT)
-            \mu_{T,k}^{2}
-            \nu_{T,k}           
+            B_{T}^{2}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)            
             ,
@@
             :=
-            (k+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T) \mu_{T,k}^{2}
-            ,
+            \aspectratio(T) 
+            \cdot 
+            B_T
             \\
@@
             \aspectratio(\calT)
-            \mu_{T,k}
-            \nu_{T,k}
-            ,
+            B_{T}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)
             \\
@@
             \cdot 
-            \mu_{T,k}
+            B_T
             .
@@
             \diameterratio(\calT)^{n}
-            \mu_{T,k}^{n}
+            B_{T}^{n}
             \aspectratio(\calT)^{n}
@@
             :=
+            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            \cdot 
             (k+1) 
             \aspectratio(\calT)
-            \diameterratio(\calT)
-            \mu_{T,k}
-            \nu_{T,k}         
-            \cdot 
-            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
-            ,
+            B_{T}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)            
             \\
@@
             :=
-            (k+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,k} 
+            \aspectratio(T) 
             \cdot 
             \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
-            ,
             \\
@@
             :=
+            \left( 2 + 3 (k+1) \aspectratio(T) \right)
+            \cdot 
             (k+1) 
-            \diameterratio(\calT)
             \aspectratio(\calT)
-            \nu_{T,k}           
-            \cdot 
-            \left( 2 + 3 (k+1) \aspectratio(T) \right)
-            ,
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)            
             \\
@@
     \end{itemize}
-    Having shown all the desired estimates, and the proof is complete. 
+    The proof is complete. 
 \end{proof}
@@
     Let $0 \leq k < n$. 
-    For each $u \in W^{p}\Lambda^{k}(\Omega)$ 
+    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
     there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
@@
         \leq 
-        C_{{\PF},\Poinc,k,\Omega,p}
+        C_{{\PF},k,\Omega,p}
         \| \cartan u \|_{L^{p}(\Omega)}
-        ,
-    \end{align*}
-    and for each $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ 
-    there exists $w \in W^{p}_{0}\Lambda^{k}(\Omega)$ 
-    with $\cartan u = \cartan w$ and 
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        C_{{\PF},\Bogov,k,\Omega,p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        ,
+        .
     \end{align*}
@@
     \begin{align*}
-        C_{{\PF},\Poinc,k,\Omega,p} 
+        C_{{\PF},k,\Omega,p} 
         = 
         n C_{\Poinc}(n,k+1) 
-        \vol_{}(B_1(0)) 
-        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
-        \diam(\Omega)
-        \\
-        C_{{\PF},\Bogov,k,\Omega,p} 
-        = 
-        n C_{\Bogov}(n,k+1) 
         \vol_{}(B_1(0)) 
@@
     onto the face $F_i$. 
-    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $\ell+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = (\ell+1)/n!$
+    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
+    We see that $\vol(\widetilde \Makoto) = (l+1)/n!$
 
@@
         \\&\leq 
-        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
+        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
@@
     \color{blue}
-    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $\ell+1$ through $n$. Thus,
+    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $l+1$ through $n$. Thus,
     \begin{align*}
@@
     By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{\ell}$.
+    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{l}$.
 
@@
 \begin{align*}
-    \Makoto_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}
+    \Makoto_{m-1} := \patch_{\calT}(S_{m}) \setminus T_{m}.
 \end{align*}
@@
     \begin{gather*}
-        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}
-        ,
+        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
     \end{gather*}
@@
 \end{theorem}
-\begin{proof}\color{blue}
-    We first fix some notation. 
-    Recall that for any $1 \leq m \leq M$, 
-    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
-    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
-    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
-    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We introduce the deformation mapping $\Xi_{2,m} : \patch_{\calT}(S_m) \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
-    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{m-1} \setminus \partial T$.
-    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{m} \rightarrow X_{m-1}$ 
-    by letting it be the identity over $X_{m-1} \setminus A_{m-1}$.
-
-    For each $T \in \calT$ of dimension $n$, there exists a sequence $1 \leq m_{T,1},\dots,m_{T,K} \leq M$, for some $1 \leq K \leq M$,
-    such over the simplex $T$ we have the identity 
-    \begin{align*}
-        ...
-    \end{align*}
-\end{proof}
 \begin{proof}
@@
 
-\begin{remark}\label{remark:fullrecursivesum:exterior}
-    \color{red}
-    We provide a similar discussion as in Remark~\ref{remark:fullrecursivesum}, 
-    this time geared towards the application of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \| \cartan u      \|_{L^{p}(T_{m})} 
-        \\&\qquad
-        +
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \Cfive{n}{k}(\calT)
-        \Cfiveprime{n}{k}(\calT)^{k} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
-        \\&\qquad
-        + 
-        \Cfive{n}{k}(\calT) 
-        \Cfiveprime{n}{k}(\calT)^{k-1} 
-        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(\Makoto_{m-1})}
-        .
-    \end{align*}
-    Unwrapping the recursion for the norm over the $m$-th simplex, 
-    we find an estimate of the form 
-    \begin{align}\label{math:fullrecursivesum:exterior}
-        \| w \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
-        .
-    \end{align}
-    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
-    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \sum_{\ell=0}^{M} 
-        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
-        \right)
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
-    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        L^{\frac p q}
-        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        L^{\frac p q}
-        \sum_{m=0}^{M} 
-        \max_{ 0 \leq \ell \leq M }
-        C_{m,\ell}^{p} 
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-
-    Hence, 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \sum_{\ell=0}^{M} 
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \delta_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \\&
-        \leq 
-        \max_{0 \leq \ell \leq M} \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \delta_{m,\ell} 
-        \right)
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        \\&
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        .
-    \end{align}
-    Now, if $q \leq p$, that is, $2 \leq p$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \left(
-            \sum_{\ell'=0}^{M}
-            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
-        \right)^{\frac 1 q}
-        .
-    \end{align}
-    Instead, if $p \leq q$, that is, $p \leq 2$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
-        .
-    \end{align}
-    So in any case, it is better than using the following Minkowski's inequality: 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
-        \\&
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align}
-\end{remark}
-
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
-    Let $\calT$ be a shellable $n$-dimensional triangulation, 
-    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
+    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Let $1 \leq p \leq \infty$ and $\bfu \in \bfW^{p}(\Omega,\curl)$.
     \begin{itemize}
@@
         \begin{gather*}
-            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
+            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}.
         \end{gather*}
@@
 
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    Domain & Exact PF & Approximate PF & Ratio 
+    \\ 
+    \hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    \hline
+    \end{tabular}
+    \caption{Example table with text and formulas.}
+    \label{tab:example}
+\end{table}
+
 \subsection{Three-dimensional examples}
@@
 
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    Domain & Exact PF & Approximate PF & Ratio 
+    \\ 
+    \hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    \hline
+    \end{tabular}
+    \caption{Example table with text and formulas.}
+    \label{tab:example}
+\end{table}
+
 \section{Outlook}\label{section:outlook}
@@
 \section*{Acknowledgments}
-% LTeX: enabled=false
-MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, by John M.\ Lee, and G\"unther M.\ Ziegler.
-% LTeX: enabled=true
+
+MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
 

### 2024-12-17 main.tex
alternative geometric construction, sketch of proof

--- 2024-12-13 main.tex
@@
         \begin{align*}
-            \Phi_{G}(x) 
+            \Phi_{G}(x) % TODO : Sign error. Check values for 0 and 1. Then proceed from there ... 
             &
             := 
-            \mu x_{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
+            \mu x_{Q} + \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
             \\&
             = 
-            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
-            = 
-            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
+            x - \lambda(x) z_{S'} + \frac{ \lambda(x)}{ 2 } z_{S'} - \frac{ 1 }{ 2 } z_{S'}
+            \\&
+            = 
+            x - \frac{ \lambda(x) }{2} z_{S'} - \frac{ 1 }{ 2 } z_{S'}
+            \\&
+            = 
+            x - \frac{\langle h_{z},x\rangle}{2\langle h_{z},z_{S'}\rangle} z_{S'} - \frac 1 2 z_{S'}
             .
@@
             - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle }  
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
             z_{S'} \otimes h_{z}^{t}
@@
             - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
             h_{z} \otimes h_{z}^{t}
             - 
-            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
             b_{z} \otimes h_{z}^{t}
@@
             - 
-            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
+            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
             h_{z} \otimes h_{z}^{t}
             - 
-            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
+            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
             b_{z} \otimes h_{z}^{t}
@@
             - 
-            \frac{3}{ 2 } 
+            \frac{1}{ 2 } 
             \hat h_{z} \otimes \hat h_{z}^{t}
             - 
-            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
+            \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
             \hat b_{z} \otimes \hat h_{z}^{t}
@@
         \end{align*}
-        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.
+        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
+        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
+        We verify that 
+        \begin{align}
+            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z},
+            \qquad 
+            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac 1 2 h_{z} - \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } \hat b_{z}
+            .
+        \end{align}
+        It remains to study the singular values of the matrix 
         \begin{align*}
@@
             \begin{pmatrix}
-                -\frac 1 2             & 0 
-                \\
-                -\frac 3 2 \tan(\beta) & 1 
+                 \frac 1 2             & 0 
+                \\
+                -\frac 1 2 \tan(\beta) & 1 
             \end{pmatrix}
@@
             =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
+            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
             ,
@@
             =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
+            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
             .
@@
             \leq 
-            \frac 3 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            1 + \frac{3}{2} (\ell+1) \aspectratio(T) 
+            \frac 1 4 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            1 + \frac{1}{2} (\ell+1) \aspectratio(T) 
             \label{math:phi_max}
@@
             \leq 
-            \frac 3 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            2 + 3 (\ell+1) \aspectratio(T) 
+            \frac 1 2 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            2 + (\ell+1) \aspectratio(T) 
             \label{math:phi_min}
@@
         \end{gather}
-        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $-\tfrac 1 2$ with multiplicity $1$.\color{black}
+        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $\tfrac 1 2$ with multiplicity $1$.\color{black}
         This finishes the discussion of the transformation $\Phi$.
@@
             \cdot 
-            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)
+            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)
             ,
@@
             \cdot 
-            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
+            \left( 2 + (\ell+1) \aspectratio(T) \right)
             ,
@@
             \cdot 
-            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
+            \left( 2 + (\ell+1) \aspectratio(T) \right)
             .
@@
             % Phi max 
-            \left( 1 + \frac 3 2 ( \ell+1 )\aspectratio(\calT) \right)
+            \left( 1 + \frac 1 2 ( \ell+1 )\aspectratio(\calT) \right)
             % Psi max 
@@
             % Phi^{-1} max 
-            \left( 2 + 3 ( \ell+1 )\aspectratio(\calT) \right)
+            \left( 2 + ( \ell+1 )\aspectratio(\calT) \right)
             % Psi^{-1} max 
@@
         \\
-        \sigma_{1}
+        \sigma_{1}, \sigma_{n}^{-1}
         %&
@@
         \\
-        \sigma_{n}^{-1}
-        %&
-        \leq 
-        \frac{1}{2} 
-        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
-        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
-        +
-        \frac{1}{2} 
-        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
-        ,
-        \\
         \sigma_2,\dots,\sigma_{n-1} \leq 1.
@@
 \end{remark}
+
+\begin{proof}\color{magenta}
+    We derive the estimate in several steps. 
+    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
+    \begin{itemize}
+        \item 
+        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.
+
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
+        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
+        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$. 
+        We let $z_{S'}$ be the midpoint of $S'$.
+
+        We apply barycentric refinement to the simplex $S$ and then the complementary simplex $S'$.
+        This produces a triangulation $\calG$ of $\underlying{|T|}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.
+
+        \item 
+        There exists $\varrho > 0$ such that $\patch_{\calT}(S)$ is star-shaped with respect to the closed ball $\overline{\Ball_{\varrho}(z_S)}$.
+        % TODO: prove this observation
+
+        \item
+
+        Let us write $\rho = \min(1,\varrho)$. 
+        We define $y = - \rho \hat z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho$. 
+        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
+        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.
+
+        We define another triangulation $\calG^{c}$ as follows:
+        given any $n$-simplex $G \in \calG$, 
+        we replace its vertex $z_{S}'$ by the vertex $y$ at the opposite position,
+        thus obtaining a new $n$-simplex $G^{c}$. 
+        Indeed, that $\calG^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
+
+        We let the simplicial complex $\calG^\ast$ be the union of $\calG$ and $\calG^c$. 
+        By construction, all its $n$-simplices contain $z_{S}$ as a subsimplex, which is an inner vertex of that triangulation. 
+        In particular, $\calD^\ast$ is its own star around $z_{S}$.
+
+        \item 
+        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
+        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
+        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
+        be affine reference transformations
+        that agree on the vertices common to $G$ and $G^{c}$.
+        We then define the piecewise affine mapping 
+        \begin{align*}
+            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}.
+        \end{align*}
+        It follows that 
+        \begin{align*}
+            |\det( \Jacobian      \Theta_{|G} )| = \frac{\vol(G^{c})}{\vol(G)}
+            .
+        \end{align*}
+        We want to further characterize the singular values of this transform. 
+        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
+        We verify that 
+        \begin{align*}
+            \Theta_{|G}(x) 
+            = 
+            x
+            - 
+            (1+\rho) \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+            \hat z_{S'}
+            .
+        \end{align*}
+        Indeed, the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
+        and when $x = z_{S'}$, then 
+        \begin{align*}
+            y 
+            =
+            z_{S'}
+            - 
+            (1+\rho) \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+            =
+            z_{S'}
+            - 
+            (1+\rho) \hat z_{S'} \vecnorm{z_{S'}}
+            =
+            - z_{S'}
+            .
+        \end{align*}
+        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
+        \begin{align*}
+            \Theta_{|G}( h_{z} ) 
+            &= 
+            h_{z}
+            - 
+            (1+\rho) \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            \\&
+            = 
+            h_{z}
+            - 
+            (1+\rho) \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            %\\&
+            = 
+            h_{z}
+            - 
+            (1+\rho) z_{S'}
+            %\\&
+            = 
+            - \rho h_{z}
+            - 
+            (1+\rho) b_{z}
+            .
+        \end{align*}
+        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
+        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
+        We study the singular values of the matrix 
+        \begin{align*}
+            M_{\Theta,G} 
+            := 
+            \begin{pmatrix}
+            -\rho                                         & 0
+            \\ 
+            -(1+\rho) \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            -\rho                 & 0
+            \\ 
+            -(1+\rho) \tan(\beta) & 1
+            \end{pmatrix}
+            .
+        \end{align*}
+        Its two singular values are:
+        \begin{align}
+            \sigma_{\max}(\Theta,G) 
+            := 
+            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } + \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
+            \label{math:theta_max}
+            ,
+            \\
+            \sigma_{\min}(\Theta,G) 
+            = 
+            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } - \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
+            \label{math:theta_min}
+            .
+        \end{align}
+        All other singular values of $\Jacobian\Theta_{|G}$ equal $1$. 
+        The singular value $\sigma_{\max}(\Theta,G) \geq 1$ is monotonically increasing in $\tan(\beta)$ and must hence be the maximal singular value of $\Jacobian\Theta_{|G}$.
+        Moreover, $\sigma_{\min}(\Theta,G) = \rho / \sigma_{\max}(\Theta,G) \leq \rho \leq 1$ must be the smallest singular value of $\Jacobian\Theta_{|G}$.
+        It is evident that $\rho = \vol(G^{c}) / \vol(G)$.
+
+        We develop explicit bounds for these singular values. 
+        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
+        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
+
+        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
+        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
+        which must be contained in some face of $T$. 
+        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
+        Thus, 
+        \begin{align*}
+            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
+            = 
+            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
+            \leq 
+            (n-\ell) \aspectratio(T)
+%             = 
+%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
+%             \leq 
+%             \frac{ n-\ell }{n!}
+%             \cdot 
+%             \frac{ \diam(T)^{n} }{ \vol(T) }
+            .
+        \end{align*}
+        We abbreviate 
+        \begin{align}\label{math:upper_bound_for_theta}
+            \mu_{T,\ell} 
+            := 
+            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
+            + 
+            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
+            .
+        \end{align}
+        This establishes bounds on the singular values of the transformation. 
+        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
+        \begin{align}
+            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
+            \quad 
+            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
+            \quad 
+            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell} / \rho.
+        \end{align}
+
+        \item 
+        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
+        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
+        We construct a bi-Lipschitz mapping 
+        \begin{align*}
+            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
+        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
+        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $y$ in $G^{c}$.
+        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
+        has a unique representation
+        \begin{align*}
+            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
+        \end{align*}
+        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+        \begin{align*}
+            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+            .
+        \end{align*}
+        Based on that observation, we define 
+        \begin{align*}
+            \Phi_{G}(x) 
+            &
+            := 
+            \mu x_{Q} + \frac{\rho}{\rho+1} \left( \lambda(x) - 1 \right) z_{S'}
+            \\&
+            = 
+            \mu x_{Q} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            \\&
+            = 
+            x - \frac{\rho+1}{\rho+1} \lambda(x) z_{S'} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            \\&
+            = 
+            x - \frac{1}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            \\&
+            = 
+            x - \frac{1}{\rho+1} \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            .
+        \end{align*}
+        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
+        that satisfies the desired mapping properties. 
+        It remains to analyze its Jacobian and get explicit estimates for its singular values.
+
+        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
+        With that,
+        \begin{align*}
+            \Jacobian \Phi_{G}(x)
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},z_{S'}\rangle }  
+            \\
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle }  
+            \\
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ h_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ b_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
+            \\
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \hat h_{z} \otimes \hat h_{z}^{t}
+            - 
+            \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho }  
+            \hat b_{z} \otimes \hat h_{z}^{t}
+            .
+        \end{align*}
+        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
+        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
+        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
+        Direct computation shows 
+        \begin{align}
+            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z}
+            ,
+            \qquad 
+            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac{ \rho }{ 1 + \rho } \hat h_{z} - \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho } \hat b_{z}
+            .
+        \end{align}
+        It remains to study the singular values of the matrix 
+        \begin{align*}
+            M_{\Phi,G} 
+            = 
+            \begin{pmatrix}
+                 \frac{ \rho }{ 1 + \rho }    & 0 
+                \\
+                -\frac{ \tan(\beta) }{1+\rho} & 1 
+            \end{pmatrix}
+            .
+        \end{align*}
+        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
+        we obtain the singular values 
+        \begin{align*}
+            \sigma_{\max}(\Phi,G) 
+            &
+            =
+            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } + \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
+            ,
+            \\
+            \sigma_{\min}(\Phi,G) 
+            &
+            =
+            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } - \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
+            .
+        \end{align*}
+        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
+        Notice that 
+        \begin{align*}
+            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2}.
+        \end{align*}
+        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        Similar as above, we use the upper bound 
+        \begin{align*}
+            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
+        \end{align*}
+        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
+        \begin{gather}
+            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
+            \leq 
+            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
+            + 
+            \frac{1}{2(1+\rho)} \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \label{math:phi_max}
+            ,
+            \\
+            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
+            \\
+            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
+            \leq 
+            % \frac{(1+\rho)^2}{\rho(1+\rho)}
+            % \frac{1}{2(1+\rho)} 
+            \frac{1}{2\rho}
+            \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
+            + 
+            % \frac{(1+\rho)^2}{\rho(1+\rho)}
+            % \frac{1}{2(1+\rho)} 
+            \frac{1}{2\rho}
+            \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \label{math:phi_min}
+            .
+        \end{gather}
+        This finishes the discussion of the transformation $\Phi$. 
+    \end{itemize}
+    Having shown all the desired estimates, and the proof is complete. 
+\end{proof}
 

### 2024-12-18 main.tex
corrections

@@
 \begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
+    Let $T$ be an $n$-dimensional simplex with an $\ell$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
     Let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ in accordance with the barycentric subdivision of $S$ at $z_{S}$.
@@
 
-\begin{proof}\color{magenta}
+\color{magenta}
+\begin{proposition}\label{proposition:starreflection}
+    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
+    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
+    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
+    and let 
+    \begin{align*}
+        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
+        \qquad 
+        {\Gamma_1} := \Makoto \cap T,
+        \qquad 
+        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
+    \end{align*}
+    The following holds, where the constants on the right-hand sides are as stated in the proof. 
+    \begin{enumerate}
+    \item 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{1} : T \rightarrow \Xi_{1}(T) \subseteq \Makoto 
+    \end{align*}
+    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
+    \begin{gather*}
+        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
+        \quad 
+        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
+    \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
+        \leq 
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
+        \leq 
+        \Csechstrafo{n}{k}{\ell}{p}(\calT).
+    \end{align*}
+
+    \item 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Xi_{2}( \underlying{\patch_{\calT}(S)} ) \subseteq \Makoto
+    \end{align*}
+    which is the identity along $\partial \Makoto \setminus \partial T$.
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
+    \begin{gather*}
+        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
+        \quad 
+        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
+    \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+        \leq 
+        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
+        \leq 
+        \Cachttrafo{n}{k}{\ell}{p}(\calT).
+    \end{align*}
+    \end{enumerate}
+\end{proposition}
+\begin{proof}
     We derive the estimate in several steps. 
@@
         We apply barycentric refinement to the simplex $S$ and then the complementary simplex $S'$.
-        This produces a triangulation $\calG$ of $\underlying{|T|}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.
+        This produces a triangulation $\calG$ of $\underlying{T}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.
 
@@
         There exists $\varrho > 0$ such that $\patch_{\calT}(S)$ is star-shaped with respect to the closed ball $\overline{\Ball_{\varrho}(z_S)}$.
+        We show that, if we let $\calK$ denote the simplicial complex obtained by barycentric refinement of $S$,
+        then the minimum height of $z_{S}$ in any $n$-simplex $K \in \calK$ is a possible choice of $\varrho$.
+        Given any $n$-simplex $K \in \calK$, the face $F \subseteq K$ opposite to $z_{S}$ is some boundary face of $\patch_{\calT}(S)$.
+        The height of $F$ in $K$ is the height of $F$ in the original simplex $T \in \patch_{\calT}(S)$ with $K \subseteq T$ scaled by $(\ell+1)^{-1}$.
+
+        Assuming that $\varrho > 0$ is at most the minimum height of $z_{S}$ in any $n$-simplex $K \in \calK$,
+        suppose that $z \in \Ball_{\varrho}(z_S)$. 
+        Let $x \in \patch_{\calT}(S)$ be in the interior of the local patch. 
+        If the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$, 
+        then $I$ passes through a boundary face $F \subseteq K$ of the local patch,
+        and $z$ and $x$ are contained on different sides of the hyperplane $H$ spanned by $F$. 
+        Then $x$ and $z_{S}$ are the same side of $H$, since otherwise the straight line segment from $x$ to $z_{S}$ would not be contained in the patch. 
+        This means, however, that $z_{S}$ and $z$ are on different sides of $H$, contradicting that $\varrho$ is at most the height of $z_S \in K$.
+
         % TODO: prove this observation
@@
         \begin{align*}
-            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2}.
+            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2} = \frac{\rho}{1+\rho}.
         \end{align*}
@@
 \end{proof}
+\color{black}
 
@@
             +
-            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+            \Cfivetrafo{n}{k+1}{\ell}{p}(\calT)
             % \Cfive{n}{k}(\calT)
@@
     and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star. 
-    We write $\ell$ for the dimension of $S_{m}$.
+    Write $\ell$ for the dimension of $S_{m}$.
 
     We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
-    We define $w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m})$. 
+    We define 
+    \begin{align*}
+        w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m}).
+    \end{align*}
     By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
@@
         &\leq 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+        \Cfivetrafo{n}{k+1}{\ell}{p}(\calT)
         % \Cfive{n}{k}{\ell}(\calT)
@@
         C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT)
+        \Cfivetrafo{n}{k+1}{\ell_{m}}{p}(\calT)
 %         \Cfiveprime{n}{k}(\calT)^{k} 

### 2024-12-18 main.tex
correction

--- 2024-12-17 main.tex
@@
         \begin{align*}
-            \Phi_{G}(x) % TODO : Sign error. Check values for 0 and 1. Then proceed from there ... 
+            \Phi_{G}(x) 
             &
             := 
-            \mu x_{Q} + \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
+            \mu x_{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
             \\&
             = 
-            x - \lambda(x) z_{S'} + \frac{ \lambda(x)}{ 2 } z_{S'} - \frac{ 1 }{ 2 } z_{S'}
-            \\&
-            = 
-            x - \frac{ \lambda(x) }{2} z_{S'} - \frac{ 1 }{ 2 } z_{S'}
-            \\&
-            = 
-            x - \frac{\langle h_{z},x\rangle}{2\langle h_{z},z_{S'}\rangle} z_{S'} - \frac 1 2 z_{S'}
+            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
+            = 
+            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
             .
@@
             - 
-            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
+            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
             h_{z} \otimes h_{z}^{t}
             - 
-            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
+            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
             b_{z} \otimes h_{z}^{t}
@@
             - 
-            \frac{1}{ 2 } 
+            \frac{3}{ 2 } 
             \hat h_{z} \otimes \hat h_{z}^{t}
             - 
-            \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
+            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
             \hat b_{z} \otimes \hat h_{z}^{t}
@@
         \end{align*}
-        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
+        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.
         We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
-        We verify that 
-        \begin{align}
-            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z},
-            \qquad 
-            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac 1 2 h_{z} - \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } \hat b_{z}
-            .
-        \end{align}
-        It remains to study the singular values of the matrix 
+        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
         \begin{align*}
@@
             \begin{pmatrix}
-                 \frac 1 2             & 0 
-                \\
-                -\frac 1 2 \tan(\beta) & 1 
+                -\frac 1 2             & 0 
+                \\
+                -\frac 3 2 \tan(\beta) & 1 
             \end{pmatrix}
@@
             =
-            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
+%             \frac{1}{2} 
+%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+%             \frac{1}{2} 
+%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
             ,
@@
             =
-            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
+%             \frac{1}{2} 
+%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+%             \frac{1}{2} 
+%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
+%             \\&
+%             =
+            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
             .
@@
             \leq 
-            \frac 1 4 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            1 + \frac{1}{2} (\ell+1) \aspectratio(T) 
+            \frac 3 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            1 + \frac{3}{2} (\ell+1) \aspectratio(T) 
             \label{math:phi_max}
@@
             \leq 
-            \frac 1 2 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            2 + (\ell+1) \aspectratio(T) 
+            \frac 3 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            2 + 3 (\ell+1) \aspectratio(T) 
             \label{math:phi_min}
@@
         \end{gather}
-        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $\tfrac 1 2$ with multiplicity $1$.\color{black}
+        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $-\tfrac 1 2$ with multiplicity $1$.\color{black}
         This finishes the discussion of the transformation $\Phi$.
@@
             \cdot 
-            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)
+            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)
             ,
@@
             \cdot 
-            \left( 2 + (\ell+1) \aspectratio(T) \right)
+            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
             ,
@@
             \cdot 
-            \left( 2 + (\ell+1) \aspectratio(T) \right)
+            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
             .
@@
             % Phi max 
-            \left( 1 + \frac 1 2 ( \ell+1 )\aspectratio(\calT) \right)
+            \left( 1 + \frac 3 2 ( \ell+1 )\aspectratio(\calT) \right)
             % Psi max 
@@
             % Phi^{-1} max 
-            \left( 2 + ( \ell+1 )\aspectratio(\calT) \right)
+            \left( 2 + 3 ( \ell+1 )\aspectratio(\calT) \right)
             % Psi^{-1} max 
@@
     \begin{gather*} 
-        | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
-        \quad 
-        | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT),
-        \\
-        \sigma_{1}, \sigma_{n}^{-1}
-        %&
+        | \det\Jacobian\Xi^{  } |      \leq \volumeratio(\calT),
+        \\
+        \sigma_{1}
         \leq 
         \frac{1}{2} 
-        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
         \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
@@
         \\
-        \sigma_2,\dots,\sigma_{n-1} \leq 1.
-        %         \det(\Jacobian \Xi) &\leq \diameterratio(\calT) \aspectratio(T_2)
+        \sigma_2,\dots,\sigma_{n-1},\sigma_{n} \leq 1.
     \end{gather*}
+    In particular,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+        \leq 
+        \left( 
+            \frac{1}{2} 
+            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
+            +
+            \frac{1}{2} 
+            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
+        \right)
+        \volumeratio(\calT)^{\frac 1 p}
+        .
+    \end{align*}
     These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
@@
 \end{remark}
-
-\begin{proof}\color{magenta}
-    We derive the estimate in several steps. 
-    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
-    \begin{itemize}
-        \item 
-        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.
-
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
-        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$. 
-        We let $z_{S'}$ be the midpoint of $S'$.
-
-        We apply barycentric refinement to the simplex $S$ and then the complementary simplex $S'$.
-        This produces a triangulation $\calG$ of $\underlying{|T|}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.
-
-        \item 
-        There exists $\varrho > 0$ such that $\patch_{\calT}(S)$ is star-shaped with respect to the closed ball $\overline{\Ball_{\varrho}(z_S)}$.
-        % TODO: prove this observation
-
-        \item
-
-        Let us write $\rho = \min(1,\varrho)$. 
-        We define $y = - \rho \hat z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho$. 
-        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
-        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.
-
-        We define another triangulation $\calG^{c}$ as follows:
-        given any $n$-simplex $G \in \calG$, 
-        we replace its vertex $z_{S}'$ by the vertex $y$ at the opposite position,
-        thus obtaining a new $n$-simplex $G^{c}$. 
-        Indeed, that $\calG^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
-
-        We let the simplicial complex $\calG^\ast$ be the union of $\calG$ and $\calG^c$. 
-        By construction, all its $n$-simplices contain $z_{S}$ as a subsimplex, which is an inner vertex of that triangulation. 
-        In particular, $\calD^\ast$ is its own star around $z_{S}$.
-
-        \item 
-        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
-        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
-        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
-        be affine reference transformations
-        that agree on the vertices common to $G$ and $G^{c}$.
-        We then define the piecewise affine mapping 
-        \begin{align*}
-            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}.
-        \end{align*}
-        It follows that 
-        \begin{align*}
-            |\det( \Jacobian      \Theta_{|G} )| = \frac{\vol(G^{c})}{\vol(G)}
-            .
-        \end{align*}
-        We want to further characterize the singular values of this transform. 
-        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
-        We verify that 
-        \begin{align*}
-            \Theta_{|G}(x) 
-            = 
-            x
-            - 
-            (1+\rho) \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            \hat z_{S'}
-            .
-        \end{align*}
-        Indeed, the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
-        and when $x = z_{S'}$, then 
-        \begin{align*}
-            y 
-            =
-            z_{S'}
-            - 
-            (1+\rho) \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            =
-            z_{S'}
-            - 
-            (1+\rho) \hat z_{S'} \vecnorm{z_{S'}}
-            =
-            - z_{S'}
-            .
-        \end{align*}
-        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
-        \begin{align*}
-            \Theta_{|G}( h_{z} ) 
-            &= 
-            h_{z}
-            - 
-            (1+\rho) \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            \\&
-            = 
-            h_{z}
-            - 
-            (1+\rho) \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            %\\&
-            = 
-            h_{z}
-            - 
-            (1+\rho) z_{S'}
-            %\\&
-            = 
-            - \rho h_{z}
-            - 
-            (1+\rho) b_{z}
-            .
-        \end{align*}
-        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
-        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
-        We study the singular values of the matrix 
-        \begin{align*}
-            M_{\Theta,G} 
-            := 
-            \begin{pmatrix}
-            -\rho                                         & 0
-            \\ 
-            -(1+\rho) \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
-            \end{pmatrix}
-            =
-            \begin{pmatrix}
-            -\rho                 & 0
-            \\ 
-            -(1+\rho) \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        Its two singular values are:
-        \begin{align}
-            \sigma_{\max}(\Theta,G) 
-            := 
-            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } + \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
-            \label{math:theta_max}
-            ,
-            \\
-            \sigma_{\min}(\Theta,G) 
-            = 
-            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } - \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
-            \label{math:theta_min}
-            .
-        \end{align}
-        All other singular values of $\Jacobian\Theta_{|G}$ equal $1$. 
-        The singular value $\sigma_{\max}(\Theta,G) \geq 1$ is monotonically increasing in $\tan(\beta)$ and must hence be the maximal singular value of $\Jacobian\Theta_{|G}$.
-        Moreover, $\sigma_{\min}(\Theta,G) = \rho / \sigma_{\max}(\Theta,G) \leq \rho \leq 1$ must be the smallest singular value of $\Jacobian\Theta_{|G}$.
-        It is evident that $\rho = \vol(G^{c}) / \vol(G)$.
-
-        We develop explicit bounds for these singular values. 
-        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
-        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
-
-        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
-        which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
-        Thus, 
-        \begin{align*}
-            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
-            = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
-            \leq 
-            (n-\ell) \aspectratio(T)
-%             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
-%             \leq 
-%             \frac{ n-\ell }{n!}
-%             \cdot 
-%             \frac{ \diam(T)^{n} }{ \vol(T) }
-            .
-        \end{align*}
-        We abbreviate 
-        \begin{align}\label{math:upper_bound_for_theta}
-            \mu_{T,\ell} 
-            := 
-            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
-            + 
-            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
-            .
-        \end{align}
-        This establishes bounds on the singular values of the transformation. 
-        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
-        \begin{align}
-            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
-            \quad 
-            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
-            \quad 
-            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell} / \rho.
-        \end{align}
-
-        \item 
-        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
-        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
-        We construct a bi-Lipschitz mapping 
-        \begin{align*}
-            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
-        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
-        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $y$ in $G^{c}$.
-        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
-        has a unique representation
-        \begin{align*}
-            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
-        \end{align*}
-        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
-        \begin{align*}
-            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
-            .
-        \end{align*}
-        Based on that observation, we define 
-        \begin{align*}
-            \Phi_{G}(x) 
-            &
-            := 
-            \mu x_{Q} + \frac{\rho}{\rho+1} \left( \lambda(x) - 1 \right) z_{S'}
-            \\&
-            = 
-            \mu x_{Q} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            \\&
-            = 
-            x - \frac{\rho+1}{\rho+1} \lambda(x) z_{S'} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            \\&
-            = 
-            x - \frac{1}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            \\&
-            = 
-            x - \frac{1}{\rho+1} \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            .
-        \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
-        that satisfies the desired mapping properties. 
-        It remains to analyze its Jacobian and get explicit estimates for its singular values.
-
-        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
-        With that,
-        \begin{align*}
-            \Jacobian \Phi_{G}(x)
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},z_{S'}\rangle }  
-            \\
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle }  
-            \\
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ h_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ b_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
-            \\
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \hat h_{z} \otimes \hat h_{z}^{t}
-            - 
-            \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho }  
-            \hat b_{z} \otimes \hat h_{z}^{t}
-            .
-        \end{align*}
-        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
-        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
-        Direct computation shows 
-        \begin{align}
-            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z}
-            ,
-            \qquad 
-            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac{ \rho }{ 1 + \rho } \hat h_{z} - \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho } \hat b_{z}
-            .
-        \end{align}
-        It remains to study the singular values of the matrix 
-        \begin{align*}
-            M_{\Phi,G} 
-            = 
-            \begin{pmatrix}
-                 \frac{ \rho }{ 1 + \rho }    & 0 
-                \\
-                -\frac{ \tan(\beta) }{1+\rho} & 1 
-            \end{pmatrix}
-            .
-        \end{align*}
-        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
-        we obtain the singular values 
-        \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            &
-            =
-            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } + \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
-            ,
-            \\
-            \sigma_{\min}(\Phi,G) 
-            &
-            =
-            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } - \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
-            .
-        \end{align*}
-        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
-        Notice that 
-        \begin{align*}
-            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2}.
-        \end{align*}
-        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
-        Similar as above, we use the upper bound 
-        \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
-        \end{align*}
-        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
-        \begin{gather}
-            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
-            \leq 
-            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
-            + 
-            \frac{1}{2(1+\rho)} \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \label{math:phi_max}
-            ,
-            \\
-            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
-            \\
-            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
-            \leq 
-            % \frac{(1+\rho)^2}{\rho(1+\rho)}
-            % \frac{1}{2(1+\rho)} 
-            \frac{1}{2\rho}
-            \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
-            + 
-            % \frac{(1+\rho)^2}{\rho(1+\rho)}
-            % \frac{1}{2(1+\rho)} 
-            \frac{1}{2\rho}
-            \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \label{math:phi_min}
-            .
-        \end{gather}
-        This finishes the discussion of the transformation $\Phi$. 
-    \end{itemize}
-    Having shown all the desired estimates, and the proof is complete. 
-\end{proof}
 
@@
         \prod_{m=1}^{M}
-            \Cachttrafo{n}{k}{\ell_{m}}{p}(\calT)
-            \Csiebtrafo{n}{k}{\ell_{m}}{p}(\calT)
+            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
+            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
         \right)
@@
         \leq 
-        \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
+        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
         %\Cacht{n}{k}(\calT)
@@
     Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
-    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell$ faces with the previous simplices.
+    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell_{m}$ faces with the previous simplices.
     \begin{itemize}
@@
             \left( 
-                \| \curl u      \|_{L^{p}(T_{m})} 
+                \| \curl \bfu      \|_{L^{p}(T_{m})} 
                 +
                 \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
-                \| \curl u \|_{L^{p}(\Makoto_{m-1})}
+                \| \curl \bfu \|_{L^{p}(\Makoto_{m-1})}
             \right)
@@
             \prod_{i=1}^{M}
-            \Cachttrafo{n}{1}{\ell_{m}}{p}(\calT)
+            \Cachttrafo{n}{2}{\ell_{m}}{p}(\calT)
             \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)

### 2024-12-18 main.tex

--- 2024-12-17 main.tex
@@
     \begin{gather*} 
-        | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
-        \quad 
-        | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT),
+        | \det\Jacobian\Xi^{  } |      \leq \volumeratio(\calT),
         \\
         \sigma_{1}, \sigma_{n}^{-1}
-        %&
         \leq 
         \frac{1}{2} 
-        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
         \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }

### 2024-12-26 main.tex
fix estimate

@@
         \item 
-
-        Let us write $\rho = \min(1,\varrho)$. 
-        We define $y = - \rho \hat z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho$. 
+        Let $\rho \in (0,1]$, yet to be determined. 
+        We define $y = - \rho z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho \|z_{S'}\|$. 
+        Henceforth, we assume $\rho \leq \varrho / \|z_{S'}\|$ so that $y \in \overline{\Ball_{\varrho}(z_S)}$.  
         By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
@@
         We want to further characterize the singular values of this transform. 
-        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
+        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$,
+        that is, the vector pointing to $z_{S'}$ and standing orthogonally on the affine hull of the face $G$ that opposes $z_{S'}$
         We verify that 
@@
         \begin{align*}
-            y 
+            \Theta_{|G}\left( z_{S'} \right) 
+            &
             =
@@
             (1+\rho) \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+            \\&
             =
@@
             =
-            - z_{S'}
+            z_{S'}
+            - 
+            (1+\rho) z_{S'} 
+            =
+            - \rho z_{S'} = y
             .
@@
             \sigma_{\min}(\Theta,G) 
-            = 
+            := 
             \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } - \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
@@
         All other singular values of $\Jacobian\Theta_{|G}$ equal $1$. 
-        The singular value $\sigma_{\max}(\Theta,G) \geq 1$ is monotonically increasing in $\tan(\beta)$ and must hence be the maximal singular value of $\Jacobian\Theta_{|G}$.
-        Moreover, $\sigma_{\min}(\Theta,G) = \rho / \sigma_{\max}(\Theta,G) \leq \rho \leq 1$ must be the smallest singular value of $\Jacobian\Theta_{|G}$.
+        The singular values $\sigma_{\max}(\Theta,G) \geq 1$ and $\sigma_{\min}(\Theta,G) \leq 1$ is monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
+Hence they must the extremal maximal singular values of $\Jacobian\Theta_{|G}$.
         It is evident that $\rho = \vol(G^{c}) / \vol(G)$.
@@
 
-        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
-        which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
+        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions: 
+        first at $z_{S}$, leading to some intermediate $n$-simplex $T'$, and then at $z_{S'}$, leading to $G \subseteq T'$. 
+        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$, which is some face of $T'$.
+        Now, the height of $F_{z}$ in $G$ is $(n-\ell)$-th of the height of $F_{z}$ in $T'$
+        since $S'$ has dimension $n-\ell-1$. 
+        The height of $F_{z}$ in $T'$ is just the height of the its opposing vertex, which lies in $S'$,
+        and which equals the height of that vertex in $T$.
+%         which must be contained in some face of $T$ containing $S$. 
+%         The height vector $h_{z}$ is orthogonal to $F_{z}$. 
+%         Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$,
+%         pointing to some vertex of $S'$ and standing orthogonally on the face opposite to that vertex. 
         Thus, 
@@
             \quad 
-            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell} / \rho.
+            \sigma_{n}(\Theta,x)^{-1} = \frac{ \sigma_{1}(\Theta,x) }{ \left| \det \Jacobian\Theta_{|G} \right| } \leq \mu_{T,\ell} / \rho.
         \end{align}
@@
             \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
+            =
+            \frac{ \sigma_{1}(\Phi,x) }{ \left| \det \Jacobian\Phi \right| }
             \leq 

### 2024-12-29 tcf/main.tex

--- 2024-12-18 main.tex
@@
 \usepackage{enumitem}
-\setitemize[1]{left=0.0cm}
+% \setitemize[1]{left=0.0cm}
 
@@
 \begingroup
-    \color{blue}%
+    \color{red!30!yellow}%
     #1%
@@
 
-% LTeX: enabled=false
+\newcommand{\cred}[1]{{\color{red} #1}}
+\newcommand{\tcf}[1]{{\color{blue} #1}}
+\newcommand{\tcfsays}[1]{{\color{blue} [TCF: #1]}}
+
 % Title, authors, and affiliations
@@
 }
-\date{}
-% LTeX: enabled=true
 
@@
 The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants.
-These quantify the fundamental stability properties of partial differential equations
+These quantify the fundamental stability properties of \tcf{certain} partial differential equations
 and enter the stability and convergence theory of numerical methods. 
-Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
-However, while potentials and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
+Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians \tcf{\sout{and the eigenvalues of finite element matrices}} \tcfsays{This is not true in general I believe}.
+However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
 quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.
 
-This manuscript contributes to the theory of computable estimates for Poincar\'e--Friedrichs inequalities for the differential operators of vector calculus. 
+This manuscript contributes to the theory of computable estimates for Poincar\tcf{\'e}--Friedrichs inequalities for the differential operators of vector calculus. 
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
-We apply this construction principle to the curl and divergence operators, as well as the exterior derivative. 
+\tcf{Here, we extend this idea} % We apply this construction principle
+to the curl and divergence operators, as well as the exterior derivative.
 However, to proceed in the general exterior derivative case, we restrict our efforts to so-called shellable triangulations. 
@@
 The class of shellable triangulations includes practically relevant triangulations: 
-for example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
+for example, local triangulations around a simplex \tcfsays{Is it really true if the simlex is of highest dimension, e.g., a tetrahedron in 3D?} within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three.
 Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
@@
 Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally difficult. 
-Attention has been given to \emph{linear} potentials instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}. 
+Attention has been given to \emph{linear} potential operators instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}. 
 The operator norm of any linear potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
@@
 The relationship between the Poincar\'e constant and the Poincar\'e--Friedrichs constant will be elaborated upon in later sections of this manuscript. 
-% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potentials to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potentials such as~\eqref{math:intro:gradientpotential}.
+% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potential operators to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potential operators such as~\eqref{math:intro:gradientpotential}.
 
@@
 
-We study potentials and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
-There are substantial changes and much fewer results are available in the literature. 
+We study potential operators and Poincar\'e--Friedrichs inequalities for the curl or divergence operators in vector calculus.
+There are substantial changes and much less results are available in the literature. 
 We use the spaces of vector field 
@@
 and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
+Our objective is to find bounded potentials \tcf{(i.e. left inverses)} for the operators 
 \begin{align*}
@@
 In the Banach space case, it is not even trivial whether a norm-minimizing potential actually exists. 
-We are therefore interested in any potentials 
+We are therefore interested in any potential operators 
 \begin{align}
@@
 Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
-This formalism is independent of the spatial dimension and highlights extends the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
-% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-% In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: 
-For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
+This formalism is independent of the spatial dimension and highlights \tcf{\sout{extends}} the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
+% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}:
+\tcf{F}or every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
 \begin{align} \label{math:intro:exterior:pf} 
@@
 which may include weighted integrals or boundary terms. 
-These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem,
+These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem \tcfsays{I believe this is often refered to as the Tartare-Petree theorem},
 and thus the resulting constants are not explicitly computable.
@@
 In the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space
-with homogeneous Dirichlet boundary conditions along $\partial \Omega$ implies~\eqref{math:intro:Wdiv} via duality. 
-However, that easy duality argument, which yields an explicit upper bound proportional to the domain diameter, seems inherently restricted to $p=2$.
+with homogeneous Dirichlet boundary conditions along $\partial \Omega$ implies~\tcf{\eqref{math:intro:Wdiv:pf}}
+\tcf{by}  %% via
+duality. However, that easy duality argument, which yields an explicit upper bound proportional to the domain diameter, seems inherently restricted to $p=2$.
 
@@
 % and where the latter holds for all functions $\bfu \in \bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in \cite{Gaff_Hilbert_harm_55}, \cite{Web_compact_Maxw_80} as well as \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+We refer to~\cite[Equation~(5)]{Fried_diff_forms_55}, \cite[Equation~(2)]{Gaff_Hilbert_harm_55}, \cite{Web_compact_Maxw_80} as well as \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
 The general case of $L^p$ differential forms over Lipschitz manifolds subject to partial boundary conditions is discussed in~\cite{goldshtein2011hodge}.
@@
 A duality argument also yields upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+Unfortunately, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$ \tcfsays{We might want to obtain with ML's recent preprint.}.
 
@@
 then several estimates for Poincar\'e--Friedrichs constants are known. 
-Poincar\'e--Friedrichs inequalities actually hold over any star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
-Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
+Poincar\'e--Friedrichs inequalities actually hold over any star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare} \tcfsays{I don't exactly get the point of this sentence.}. 
+Polynomial interpolation estimates already imply the \tcf{gradient} Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
 We pay particular attention to the regularized Poincar\'e and Bogovski\u{\i} potential operators for the exterior derivative,
 such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
-In principle, the operator norms of those potentials as mapping between Lebesgue spaces of differential forms 
+In principle, the operator norms of those potential operators as mapping between Lebesgue spaces of differential forms 
 are upper estimates for the Poincar\'e--Friedrichs constants of the domain. 
@@
 Let us briefly discuss the practical limitations of the aforementioned estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
-Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
+Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over
+\tcf{domains with shellable triangulations, with a key application being} local stars within triangulated domains. 
 While not all local stars describe convex subdomains, most local stars are star-shaped with respect to a ball. 
@@
 Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
-The method is known in the finite element literature~\cite{ern2021finite}.
+The method is known in the finite element literature~\cite{ern2021finite} \tcfsays{Could you reference a particular theorem or chapter?}.
 It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
-This sequential procedure applies to general triangulated domains, not only local stars, though the latter are our main interest here. 
+This sequential procedure applies to general triangulated domains, not only local stars\tcf{\sout{, though the latter are our main interest here}}. 
 Most importantly, these sequential estimates of Poincar\'e--Friedrichs constants generally circumvent the effect of low boundary regularity and only rely on the shape regularity.
@@
 and we use simpler (constant) weight functions. 
-While the resulting potentials feature generally lower regularity, they are conductive for our purposes. 
+While the resulting potential operators feature generally lower regularity, they are conductive for our purposes. 
 Crucially, this allows us to easily estimate their operator norms and thus bound Poincar\'e--Friedrichs constants.
@@
 
-We also address the construction of potentials for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions. 
-We are not aware of explicit estimates or regularized potentials for these boundary conditions in the published literature. 
+We also address the construction of potential operators for the gradient, curl, divergence, and more generally the exterior derivative over a simplex subject to partial boundary conditions. 
+We are not aware of explicit estimates or regularized potential operators for these boundary conditions in the published literature. 
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
-we want to find the unique vector field potential that not only is a preimage under the curl operator but also has vanishing tangential trace along the same three faces. 
+we want to find the unique vector field potential that not only is a preimage under the curl operator but that also has vanishing tangential trace along the same three faces. 
 We achieve this by constructing an auxiliary problem subject to full boundary conditions,
@@
 
-Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, including the curl and divergence in particular, over triangulated domains. 
-The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
-In light of the different approaches listed before, 
-we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
-and that do not depend on the boundary regularity of the domain.
-
-% TODO: Figure out whether to use the following paragraph.
-% Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
-% The operator norms of these potentials will serve as computable Poincar\'e--Friedrichs constants. 
-% In light of the different approaches listed before, 
-% we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
-
-% In this work, we aim to construct linear potentials for the gradient, curl, and divergence on triangulated domains, 
-% providing explicitly computable upper bounds. Our approach extends to domains that may be non-convex and non-star-shaped, 
-% focusing on triangulations that are face-connected or possess the special property of shellability.
+Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
+The operator norms of these potentials will serve as computable Poincar\'e--Friedrichs constants. 
+In light of the different approaches \tcf{d}iscussed above, we seek constants that can be explicitly computed in terms of the mesh geometry, that do not require solving global finite element problems, and that are independent of the boundary regularity of the domain.
 
@@
 
-% TODO: check whether introduction is readable
-% In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, 
-% where merely each subsequent simplex has to be connected to the previous ones by a $(n-1)$-dimensional face. 
-% We always construct a gradient potential over the new simplex, and since the gradient kernel is trivial, 
-% formed merely by constants, it is enough to fix this constant using the value already known on the $(n-1)$-dimensional face.
-
-% Extending our method to vector fields, specifically for the curl and divergence operators introduces new challenges due to their infinite-dimensional kernels. 
-% To address these challenges, we generalize the sequential construction used for the gradient to develop vector potentials. 
-% The basic inductive strategy remains: 
-% we start by constructing a potential over a single simplex and then extend it to neighboring simplices. 
-% However, unlike in the gradient case, the potentials over adjacent simplices may not have matching tangential traces along their shared interfaces.
-
-% To ensure the correct continuity properties of the vector potentials, we impose stronger conditions on the triangulations.
-We require that the intermediate subtriangulations formed during the sequential process are manifolds with boundary, and that the interface between the existing subtriangulation and the new simplex is a boundary submanifold of both.
-Under these conditions, which are satisfied by shellable triangulations, we can define well-posed auxiliary problems for the curl and divergence operators with partial boundary conditions.
-By iterating this procedure, we exhaust the entire triangulation and obtain the desired potentials.
-Our main results for the curl and divergence operators are presented in Theorems \ref{theorem:poincarefriedrichsestimate
-% } and \ref{theorem:poincarefriedrichsestimate:exterior}.
-
-% Shellability is a well-established concept in discrete geometry and combinatorics, referring to a property of simplicial or polytopal complexes that allows them to be built sequentially in a controlled manner.
-A triangulation is shellable if it can be assembled by adding one simplex at a time such that each new simplex shares a boundary submanifold with the existing complex.
-This property ensures that interfaces between simplices are well-behaved, which is crucial for the continuity of vector potentials.
-
-% While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions, patches of simplices sharing a common vertex, edge, face, or nn-simplex.
-These local patches are inherently shellable, making our approach widely applicable.
-For more details on shellability, see Kozlov \cite{kozlov2008combinatorial} and Ziegler \cite{ziegler1995lectures}.
-
-% \subsubsection{Objective: Combinatorial constants over shellable triangulated domains}
-
-% Towards our main objective of constructing linear potentials for the gradient, curl, and divergence, satisfying explicitly computable upper bounds, we closely follow the philosophy of the aforementioned sequential approach.
-
-% Transitioning to vector fields incurs new challenges due to the infinite-dimensional kernels.
-We overcome these challenges on a special class of triangulated domains, namely domains with so-called \emph{shellable} triangulations.
-
-% For vector fields, new challenges arise because of the infinite-dimensional kernels. 
-% We, however, overcome these challenges and succeed in generalizing the sequential construction of the potential operator for the gradient to vector potentials, including in particular the curl and divergence.
-% The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. 
-% Having already defined a potential operator over a set of simplices that we term a subtriangulation, 
-% we then construct a potential over a simplex neighboring through some $(n-1)$-dimensional faces. 
-% However, the potential on the new simplex might here not have the same tangential trace along the interface between the new simplex and the previous ones. 
-% Actually, the passage through the triangulation has to be such that the intermediate subtriangulations are manifolds with boundary and the interface is a boundary submanifold of the intermediate subtriangulation and the new simplex.
-% Then, we can define a well-posed \cye{mapping from the already visited simplices.} Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
-% These stronger conditions on the triangulations are exactly those of a so-called \emph{shellable} triangulations. 
-% Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} or Ziegler~\cite{ziegler1995lectures}.
-% With respect to our main interest, local \cye{patches} (stars) in 2D and 3D triangulations are shellable.
-
-% We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
-We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
-However, we need to overcome new challenges that arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
+We generalize this sequential construction of potentials to the curl, the divergence, and \tcf{more generally,} the exterior derivative. 
+However, we need to overcome new challenges that are arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
 The basic inductive strategy remains the same. 
@@
 For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive: 
-we ensure that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
+we \tcf{require} %% ensure
+that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
 This allows us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex. 
@@
 % 6. Contractible 
-Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
+Inspired by the contractibility of shellable triangulations, we \tcf{pursue} %% pursuit
+an additional estimate for Poincar\'e--Friedrichs constants. 
 Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
@@
 
-% LTeX: enabled=false
 The remainder of this manuscript is structured as follows.
 We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
-We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potentials.
+We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potential operators.
 We review basic notions of triangulations in Section~\ref{section:triangulations}.
 We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
-We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
-Our regularized potentials over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
-giving rise to computable Poincar\'e--Friedrichs constants as their operator norms. 
+We \tcf{recap} %% move on to the
+Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
+Our regularized potential operators over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
+giving rise to to computable Poincar\'e--Friedrichs constants as their operator norms. 
 We subsequently review shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations},
@@
 with emphasis on analytical upper bounds over bounded convex domains. 
-We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potentials.
-This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below, but we believe it is also of independent interest.
-\\
-
-Let $\Omega \subseteq \bbR^{n}$ be a connected open set. 
+We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potential operators.
+This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
+\\
+
+Let $\Omega \subseteq \bbR^{n}$ be an open connected set. 
 Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields.
@@
 
-\subsection{Relationship with potentials}
+\subsection{Relationship with potential operators}
 
@@
 \begin{remark}
-    Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potentials. 
+    Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potential operators. 
     We highlight this perspective because it seems to be most promising when generalizing the discussion to the curl and divergence operators. 
@@
 % \end{align*}
-One calls any set triangulable if it is the underlying set of some triangulation.
+We call any set triangulable if it is the underlying set of some triangulation. 
+\tcfsays{Should we be worried that $\underlying{\calT}$ is a closed set when working
+with open domains?}
 
@@
 \end{gather*}
-We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch
+\tcfsays{Should this be the interior of the underyling set?}.
 A crucial structural observation is the following.
@@
  Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
+ Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint \tcfsays{We should probably define presicely what this is.} or there exists $S'' \in \calT$
  such that 
@@
 \begin{remark}
-    The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is instance of a so-called \emph{shape measure}.
-    For example, the reference triangle has aspect shape measure $2$ and the reference tetrahedron has aspect shape measure $\sqrt{6}$. 
+    The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is \tcf{an} instance of a so-called \emph{shape measure}.
+    For example, the reference triangle has aspect shape measure $1$ and the reference tetrahedron has aspect shape measure $\sqrt{3/2}$. 
     Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
@@
 
+\tcfsays{I have removed the the subscripts from the $\|{\cdot}\|_2$ norm below, since the notation $\|{\cdot}\| = \|{\cdot}\|_2$ was introduced above.}
+
+\tcfsays{I have changed the macros for {\tt \textbackslash Ceins\{n\}} and {\tt \textbackslash Czwei\{n\}} to immedtiatly print $\sqrt{n}$.}
+
 \begin{lemma}\label{lemma:measurerelationships}
@@
         \matnorm{ \Jacobian \varphi^{-1} } 
-        \leq 
-        \Czwei{n} \cdot \aspectratio(T) \height(T)^{-1}
+        \tcf{\leq \Czwei{n} \cdot \height(T)^{-1}}
+        \leq
+        \Czwei{n} \cdot \aspectratio(T) \cred{\diam}(T)^{-1}
         ,
@@
     \end{gather*}
-    Here, $\Ceins{n} = \Czwei{n} = \sqrt n$. 
+    %% Here, $\Ceins{n} = \Czwei{n} = \sqrt n$. 
 \end{lemma}
@@
         \diam(F)
-        \leq 
-        \aspectratio(T_1)
-        \diam(T_2)
         ,
@@
     \end{align*}
-    If $\Xi : T_1 \rightarrow T_2$ is the affine diffeomorphism that is the identity over $F$, then 
-    at least $n-2$ of its Jacobian's singular values equal $1$, and we have 
-    \begin{align*}
-        \matnorm{ \Jacobian \Xi^{  } } 
-        &
-        \leq 
-        \frac{1}{2} 
-        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
-        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) + 1 \right)^{2} + \aspectratio(T_{1})^{2} }
-        +
-        \frac{1}{2} 
-        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) - 1 \right)^{2} + \aspectratio(T_{1})^{2} }
-        ,
-        \\
-        \matnorm{ \Jacobian \Xi^{-1} } 
-        &
-        \leq 
-        \frac{1}{2} 
-        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
-        \sqrt{ \left( \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2}) + 1 \right)^{2} + \aspectratio(T_{2})^{2} }
-        +
-        \frac{1}{2} 
-        \sqrt{ \left( \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2}) - 1 \right)^{2} + \aspectratio(T_{2})^{2} }
-        ,
-        \\
-        \det(\Jacobian \Xi)
-        &\leq 
-        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
-        .
-    \end{align*}
-%     \begin{align*}
-%         \matnorm{ \Jacobian \Xi }
-%         \leq 
-%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2}
-%         % ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
-%         % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
-%         .
-%     \end{align*}
-%     \begin{gather*}
-%         \matnorm{ \Jacobian \Xi^{  } } 
-%         \leq 
-%         \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
-%         \quad 
-%         \matnorm{ \Jacobian \Xi^{-1} } \leq \aspectratio(T_2) + \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_1),
-%         \\
-%         \det(\Jacobian \Xi)            \leq \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2),
-%     \end{gather*}
+    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
+    \begin{align*}
+        \matnorm{ \Jacobian \Xi }
+        \leq 
+        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
+        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
+        .
+    \end{align*}
+%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
 \end{lemma}
+
 \begin{proof}
@@
         \aspectratio(T_{1}) \aspectratio(T_{2})
-        ,
-        \qquad 
-        \frac{ \diam(T_1) }{ h_2 }
-        \leq
-        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_{2})
-        .
-    \end{align*}
+        .
+    \end{align*}
+
+	\tcfsays{What are $z_1$ and $z_2$? I can imagine this are the vertices of $T_1$ and $T_2$ not contained in $F$, but this should be written.
+             What is the Xu-Zikanato estimates?}
+
     Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
-    To estimate the Lipschitz constant of $\Xi$, we study the singular values of its Jacobian. 
-    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and contains the origin. 
-    Write $z_1 \in T_1$ and $z_2 \in T_2$ for the two vertices not contained in $F$.
-    There exists a unit height vector $\hat h_0$ that goes in the direction of the vertex $z_1$. 
-    Without loss of generality, $\hat h_0$ is in the $n$-th coordinate direction.
-    Suppose that $b_1, b_2 \in F$ such that $z_1 = b_1 + h_1 \hat h_0$ and $x_2 = b_2 + h_2 \hat h_0$.
-    The mapping $\Xi$ is linear, being the identity over $F$ and mapping $z_1$ to $z_2$. Hence,
-    \begin{align*}
-        \Xi( \hat h_0 ) = h_1^{-1} ( b_2 - b_1 ) + h_2 h_{1}^{-1} \hat h_0.
-    \end{align*}
-    We see that $\Xi$ equals the identity over the orthogonal complement of the span of $\hat h_0$ and $b_2 - b_1$.
-    The only singular values of its Jacobian are the two singular values $\sigma_{-} \leq 1 \leq \sigma_{+}$ of the matrix 
-    \begin{align*}
-        \begin{pmatrix}
-            a & 0 
-            \\
-            c & 1
-        \end{pmatrix},
-        \qquad 
-        a = h_2 / h_1,
-        \qquad 
-        c = \|b_2-b_1\| / h_1
-        .
-    \end{align*}
-    These are 
-    \begin{align*}
-        \sigma_{\pm} 
-        &
-        = 
-        \frac{1}{\sqrt{2}} \sqrt{ 1 + a^2 + c^2 \pm \sqrt{ \left( 1 + a^2 + c^2 \right)^{2} - 4a^{2} } } 
-        \\&
-        =
-        \frac{1}{\sqrt{2}} \sqrt{ 1 + a^2 + c^2 \pm \sqrt{ \left( (1+a)^2 + c^2 \right)\left( (1-a)^2 + c^2 \right) } } 
-        \\&
-        =
-        \frac{1}{2} 
-        \left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
-        .
-    \end{align*}
-    We remark that this provides the upper bound 
-    \begin{align*}
-        \sigma_{+} 
-        &
-        \leq 
-        \frac{1}{2} 
-        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
-        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) + 1 \right)^{2} + \aspectratio(T_{1})^{2} }
-        +
-        \frac{1}{2} 
-        \sqrt{ \left( \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_{1}) - 1 \right)^{2} + \aspectratio(T_{1})^{2} }
-        .
-    \end{align*}
-    The desired estimates are shown.
-%     This implies the determinant identity and estimate 
-%     \begin{align*}
-%         \det( \Jacobian \Xi ) 
-%         = 
-%         \frac 1 4 \left( (1+a)^2 - (1-a)^2 \right) 
-%         &
-%         = 
-%         a
-%         \leq 
-%         \aspectratio(T_{1}) \aspectratio(T_{2}) 
-%         .
-%     \end{align*}
-%     % Now we see that if $a \leq 1$, then $\sigma_{+} \leq 1 + c$, and if $a \geq 1$, then $\sigma_{+} \leq a + c$.
-%     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
-%     Since $\Xi(\hat h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
-%     \begin{align*}
-%         \| \Xi(x) - \Xi(x') \|
-%         \leq  
-%         \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
-%         \leq  
-%         \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| \hat h_0 \|
-%         \leq 
-%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
-%         .
-%     \end{align*}
-    \color{blue}
-    \color{red}
-    The linear mapping $\Xi$ takes the form 
-    % Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
+    Writing $h_0$ for the unit normal in direction $z_1$, we have 
     \begin{align*}
@@
         x 
-        - \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_1
-        + \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_2
+        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
+        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
         ,
@@
     \begin{align*}
-        % \matnorm{ \Jacobian \Xi }
-        \sigma_{+} 
+        \matnorm{ \Jacobian \Xi }
         \leq 
@@
         \leq 
-        \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
-        .
-    \end{align*}
-    Analogous upper bound holds for $\sigma^{-1}_{-}$.
-%     \begin{align}
-%         \sigma_{-}^{-1} \leq \left( 1 + \aspectratio(T_1) \right) \aspectratio(T_2)
-%     \end{align}
-% \begin{comment}
-    \color{Mulberry}
+        \left( 1 + \aspectratio(T_2) \right)
+        \aspectratio(T_1)
+        .
+    \end{align*}
+    The desired estimates are shown.
+\begin{comment}
     \mwl{Tighter estimate via geometry}
@@
     Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
-    We extend $u$ by zero to a function over the entire $\bbR^{n}$.
+    We extend $u$ by zero to a function over the entire $\bbR^{n}$ \tcfsays{How is that done? $u$ does not vanish on the whole boundary.}.
     Without loss of generality, 
@@
 
-\begin{remark}\label{remark:fullrecursivesum}
-    \color{red}
-    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    The potential $w$ for the gradient $\nabla u$ satisfies 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
-        \qquad 
-        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
-        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
-    \end{align*}
-    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
-    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
-    \begin{align}\label{math:fullrecursivesum}
-        \| w \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
-        +
-        \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
-        =:
-        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
-        .
-    \end{align}
-    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \sum_{\ell=0}^{M} 
-        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
-        \right)
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
-    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
-    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
-    % \begin{align*}
-        % \| w \|_{L^{p}(\Omega)}^{p}
-        % &
-        % \leq 
-        % \sum_{m=0}^{M}
-        % \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
-        % \leq 
-        % \sum_{m=0}^{M}
-        % L^{\frac p q}
-        % \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        % \leq 
-        % L^{\frac p q}
-        % \sum_{m=0}^{M} 
-        % \max_{ 0 \leq \ell \leq M }
-        % C_{m,\ell}^{p} 
-        % \cdot 
-        % \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        % ,
-    % \end{align*}
-
-    \color{green}Hence, 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \sum_{\ell=0}^{M} 
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        \\&
-        \leq 
-        \max_{0 \leq \ell \leq M} \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \delta_{m,\ell} 
-        \right)
-        \cdot 
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        \\&
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)
-        \cdot 
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        .
-    \end{align}
-    Now, if $q \leq p$, that is, $2 \leq p$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \left(
-            \sum_{\ell'=0}^{M}
-            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
-        \right)^{\frac 1 q}
-        .
-    \end{align}
-    Instead, if $p \leq q$, that is, $p \leq 2$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
-        .
-    \end{align}
-    So in any case, it is better than using the following Minkowski's inequality: 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
-        \\&
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
-        \| \nabla u \|_{L^{p}(\Omega)}
-        .
-    \end{align}
-\end{remark}
-
 \begin{remark}
@@
 Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
-\begin{gather}\label{math:canonicalrepresentation}
+\begin{gather*}
     \omega 
@@
     \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
-\end{gather}
+\end{gather*}
 where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
@@
 We use the abbreviation $W^{1,p}_{0}(\Omega) := W^{p}\Lambda^{0}(\Omega)$.
+
+\tcfsays{Is the definition of trace satisfactory for matching traces across simplicies?}
 
@@
 \begin{proof}
-    See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}.
+	See~\cite{licht2019smoothed} and Corollary~6 in~\cite{stern2013lp}).
 \end{proof}
@@
 Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
+
+\tcfsays{It is a bit pedantic, but shouldn't we say that $u$ is extended by zero to define the convolution below?}
 
@@
 
-\section{Regularized potentials over convex sets}\label{section:potentialoperator}
+\section{Regularized potential operators over convex sets}\label{section:potentialoperator}
 
@@
 % % 
-% We bound the norms of regularized potentials for the exterior derivative over convex domains.
+% We bound the norms of regularized potential operators for the exterior derivative over convex domains.
 % We solve this for two special cases:
@@
 either the $L^{p}$ de~Rham complex without boundary conditions, or the $L^{p}$ de~Rham with full boundary conditions. 
-The corresponding linear potentials are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
+The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
 We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
@@
 In comparison to their extensive work, our discussion is more modest:
-we study potentials merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
+we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
 However, our goal is explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.
@@
 %\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.
+\tcf{In the remainder of this section,} $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.
 
@@
 
-We begin with introducing the Costabel-McIntosh kernel.
+We begin \tcf{by} introducing the Costabel-McIntosh kernel.
 For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
@@
 We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually converge. 
-In order to analyze the properties of the potentials,
+In order to analyze the properties of the potential operators,
 we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
@@
 
+\tcfsays{I guess the way we remove the $\chi_\Omega$ is beause we somehow have a convex (if $r \leq \delta(\Omega)$) conbination
+of $x,y$, correct? It would be nice poiting it out explicitly.}
+
 \subsection{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}
@@
 
-\color{blue}
-\subsection{Rewriting the potentials operators}
+\subsection{Interaction of potential operators with the exterior derivative}
 
@@
 % 
-Given $a \in \Omega$, we introduce the potentials 
+Given $a \in \Omega$, we introduce the potential operators 
 \begin{align*}
@@
 \end{align*}
-On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
-These do not depend on the eccentricity of the domain.
-
-We begin with the Poincar\'e operator. 
-By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
-    &
-    \leq 
-    \diam(\Omega)^{p}
-    \vol(\Omega)^{-1}
-    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
-    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{0}^{1} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{0}^{1} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{\Omega} 
-    |u( z )|^{p}
-    \int_{0}^{1} 
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \,dt \,dz 
-    .
-\end{align*}
-\color{red}
-A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
-    &
-    \leq 
-    \diam(\Omega)^{p}
-    \vol(\Omega)^{-1}
-    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
-    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{1}^{\infty} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{1}^{\infty} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{\Omega} 
-    |u( z )|^{p}
-    \int_{1}^{\infty} 
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \,dt \,dz 
-    .
-\end{align*}
-\color{blue}
-We estimate 
-\begin{align*}
-    \int_{0}^{1}
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \ dt
-    &
-    \leq 
-    \int_{0}^{1}
-    \min\left( 
-        \vol\left(\Omega\right), 
-        \vol\left( \tfrac{t}{1-t} \Omega \right) 
-    \right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \ dt
-    \\&
-    \leq 
-    \int_{0}^{1}
-    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
-    t^{p(k-1)} 
-    \ dt
-    \\&
-    \leq 
-    \int_{0}^{1}
-    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
-    t^{k-1} 
-    \ dt
-    .
-\end{align*}
-The last integral is handled via the basic observations
-\begin{align*}
-    \int_{0}^{\frac 1 2} 
-    \frac{ t^{k-1} }{ (1-t)^{n} }
-    \ dt
-    \leq 
-    \int_{0}^{\frac 1 2} 
-    (1-t)^{-n+k-1}
-    \ dt
-    =
-    \int_{\frac 1 2}^{1} 
-    t^{-n+k-1}
-    \ dt
-    =
-    \begin{cases}
-        \ln(2)                 & \text{$n=k$}
-        \\
-        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
-    \end{cases}
-\end{align*}
-
-\subsection{Interaction of potentials with the exterior derivative}
-\color{black}
-We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
+We study the interaction of these potential operator with the exterior derivative in more detail.
 % 
-The main arguments are well-known and establish the exactness of several de~Rham complexes. 
+The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
 We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.
@@
 
-We are now state the main results of this section. 
+We are now \tcf{ready to} state the main results of this section. 
 % We are in the position to establish the main results of this section.
@@
 The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
-However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
+However, \tcf{\sout{though}} the space dimension $n$ and the form degree $\mia$ enter the estimates, 
 namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $C_{\Poinc}(n,\mia)$ and $C_{\Bogov}(n,\mia)$.
@@
         &\leq 
-        % n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{1}(0)) }{\vol(\Omega)} 
-        C_{{\PF},\Poinc,k,\Omega,p}
+        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
         \| u \|_{L^{p}(\Omega)}
@@
         &\leq 
-        % n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
-        C_{{\PF},\Bogov,k,\Omega,p}
+        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
+        \diam(\Omega)
         \| u \|_{L^{p}(\Omega)}
-        ,
-    \end{align*}
-    where 
-    \begin{align}
-        C_{{\PF},\Poinc,k,\Omega,p} := C_{\Poinc}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
-        ,
-        \quad 
-        C_{{\PF},\Bogov,k,\Omega,p} := C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
-        .
-    \end{align}
+        .
+    \end{align*}
     For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
@@
         \\
-        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
+        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n\tcf{,}
         \label{math:theorem:bogovpoinc:poincare:k}
     \end{align}
-    In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
+    \tcf{for a.e. $x \in \Omega$.} In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
 
@@
         \\
-        u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}.
+        u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}\tcf{,}
         \label{math:theorem:bogovpoinc:bogov:n}
     \end{align}
-    In particular, if $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
+    \tcf{for a.e. $x \in \Omega$.} In particular, if $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
 
@@
     Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$. 
-    We write $\zeta := \Poinc_{\mia  } u$. 
+    \tcf{\sout{We write $\zeta := \Poinc_{\mia  } u$.}}
     There exists a sequence $u_{i} \in C^{\infty}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
@@
     \end{align*}
-    By definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
+    \tcf{Hence b}y definition, $\tcf{\Poinc_{\mia} u} \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \tcf{\Poinc_{\mia} u} = u - \Poinc_{\mia+1} \cartan u$.
     This shows \eqref{math:theorem:bogovpoinc:poincare:k}, and \eqref{math:theorem:bogovpoinc:poincare:zero} follows by an approximation argument.
@@
     Analogously, suppose that $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$. 
-    We write $\zeta := \Bogov_{\mia} u$. 
+    \tcf{\sout{We write $\ := \Bogov_{\mia} u$. }}
     There exists a sequence $u_{i} \in C^{\infty}_{c}\Alt^{\mia}(\overline\Omega)$ that converges to $u$ in $W^{p}\Alt^{\mia}(\Omega)$. 
@@
     \end{align*}
-    By definition, $\zeta \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Bogov_{\mia+1} \cartan u$.
+    By definition, $\tcf{\Bogov_{\mia} u} \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan \tcf{\Bogov_{\mia} u} = u - \Bogov_{\mia+1} \cartan u$.
     This shows \eqref{math:theorem:bogovpoinc:bogov:k}, and \eqref{math:theorem:bogovpoinc:bogov:n} follows by an approximation argument.
@@
 We return to the theory of triangulations, as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulated domains and which are \emph{shellable}.
+We are interested in simplicial complexes that triangulate\tcf{\sout{d}} domains and which are \emph{shellable}.
 Such simplicial complexes are constructed by successively adding simplices in a well-structured manner. 
@@
 All other simplices of the manifold triangulation are called \emph{inner simplices}. 
-We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifold's boundary. 
+We have seen that the boundary simplices of a manifold triangulation constitute a triangulation of the manifold\tcf{'}s boundary. 
 We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
@@
         then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-\tcf{\sout{ball}sphere?}.
     \end{itemize}
@@
     The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
-    by the topological Schoenflies theorem. 
+    by the topological Schoenflies theorem \tcfsays{Reference here?}.
     It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
@@
 
+	\tcfsays{I could not really follow the paragraph above. Let's talk about it when we can!}
+
     If the underlying space $\underlying{\calT}$ is connected, 
-    then we easily see that the union of the $1$-simplices is path-connected.
+    then we easily see that the union of the $1$-simplices is path-connected. \tcfsays{Why?}
     Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
+    we can thus choose a sequence of $\tcf{S = \hat S_0},\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
     As each vertex star is face-connected, 
@@
     Not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
+    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, \tcf{can} decide\tcf{\sout{s}} whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
     Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.
+	\tcfsays{To make sure I properly understood: In the former case, you say that given a triangulation and a manifold, you cannot decides whether it triangulates it. In the second case,
+	you say that it is not possible to decide whether a triangulation triangulates some manifold (without specifying what it is, neither as input nor output). Correct?}
     % Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. ~\cite{todo}
@@
     then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
-    Hence, $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
-    which requires $m = M$.
+    Hence $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
+    which requires $m = M$. \tcfsays{I don't understand why $X_M$ couldn't be a topological $n$-ball.}
     On the other hand, 
@@
     By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-\disk.
-    Any shelling of that \disk\ can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    Any shelling of \tcf{$\calT$} can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
     So it remains to show that any triangulation $\calT$ of the two-dimensional \disk\ is shellable. 
@@
 \begin{lemma}\label{lemma:stardivision}
-    Let $T$ be an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
+    Let $T$ be an $n$-dimensional simplex with a $k$-dimensional subsimplex $S$ and let $z_S$ be the barycenter of $S$. 
     Let $T'$ be one of the $n$-dimensional simplices obtained by splitting $T$ in accordance with the barycentric subdivision of $S$ at $z_{S}$.
     \begin{itemize}
-        \item $\vol(T') = \vol(T) / (\ell+1)$. 
+        \item $\vol(T') = \vol(T) / (k+1)$. 
         \item The height vector of $v \in \Vertices(T) \setminus \Vertices(S)$ in $T'$ is the height vector $v$ in $T$.
         \item The height vector of $z_S$ in $T'$ is the height vector of the single vertex $v \in \Vertices(T) \setminus \Vertices(T')$ in $T$,
-scaled by $(\ell+1)^{-1}$.
+scaled by $(k+1)^{-1}$.
     \hfill\qed
@@
 
+\tcfsays{If the mappings are piecewise affine below, I guess that their actual norms
+could be exactly computed rather than estimated as below. It might reduce the resulting
+PF constants.}
+
 \begin{proposition}\label{proposition:starreflection}
     Let $\calT$ be a triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
+    Let $S \in \calT$ be an inner simplex of dimension $k < n$,
     let $T \in \patch_{\calT}(S)$ be of dimension $n$,
@@
     \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
+    which is the identity along \tcf{$\Gamma_1$ [--].} %${\Gamma_1} = T \cap \Makoto$. 
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
     \begin{gather*}
-        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
+        \sigma_1 \leq \Cfive{n}{k}(\calT),
         \quad 
-        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
+        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{k}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
+        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
+        \\
+        \sigma_n \leq \Csechs{n}{k}(\calT),
         \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{k}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
     \end{gather*}
-    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
-        \leq 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
-        \qquad 
-        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
-        \leq 
-        \Csechstrafo{n}{k}{\ell}{p}(\calT).
-    \end{align*}
-
+%     and which satisfies the upper bounds 
+%     \begin{gather*}
+%         \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
+%         \quad 
+%         \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
+%         \\
+%         | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
+%         \quad 
+%         | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
+%     \end{gather*}
     \item 
@@
     \begin{gather*}
-        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
+        \sigma_1 \leq \Csieb{n}{k}(\calT),
         \quad 
-        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
+        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{k}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
+        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
+        \\
+        \sigma_n \leq \Cacht{n}{k}(\calT),
         \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{k}(\calT),
         \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
     \end{gather*}
-    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
-        \leq 
-        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
-        \qquad 
-        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
-        \leq 
-        \Cachttrafo{n}{k}{\ell}{p}(\calT).
-    \end{align*}
+%     and which satisfies the upper bounds 
+%     \begin{gather*}
+%         \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
+%         \quad 
+%         \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
+%         \\
+%         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
+%         \quad 
+%         | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
+%     \end{gather*}
     \end{enumerate}
+\tcfsays{Should $\sigma_n$ be $\sigma_n^{-1}$ in the second line of both statements?}
 \end{proposition}
@@
         \item 
-        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin. 
-        % Let $I := \Makoto \cap T$, which is the union of $\ell$ different faces of $T$, with $1 \leq \ell \leq n$.
-        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-\ell$ faces of $T$.
+        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
+        % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
+        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
         %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
-        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
+        We fix the subsimplex $S' \subseteq T$ that is complementary \tcfsays{What does that mean?} to $S$.
+        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
         whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
@@
 
+		\tcfsays{A picture would be very nice to visualize what's going on here.}
+
         \item 
-        % Notice that $A_{G^{c}}$ and $A_{G}$ have the same singular values. Thus
+        We introduce a new mapping $\Theta : \underlying{\calR} \rightarrow \underlying{\calR^c}$ between the underlying sets as follows.
+        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
+        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
+        be affine reference transformations
+        that agree on the vertices common to $K$ and $K'$.
+        Then the mapping 
+        \begin{align*}
+            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
+        \end{align*}
+        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
         % \begin{align*}
-        %     \matnorm{ \Jacobian \Theta_{|G}      } &\leq \| A_{G^{c}} \| \cdot \| A_{G}^{-1} \| \leq \geometricshapemeasure(A_{G}),
+        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
         %     \\
-        %     \matnorm{ \Jacobian \Theta_{|G}^{-1} } &\leq \| A_{G^{c}}^{-1} \| \cdot \| A_{G} \| \leq \geometricshapemeasure(A_{G}).
+        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).
         % \end{align*}
-        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
-        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
-        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
-        be affine reference transformations
-        that agree on the vertices common to $G$ and $G^{c}$.
-        Then the mapping 
-        \begin{align*}
-            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}
-        \end{align*}
         preserves volumes:
         \begin{align*}
-            |\det( \Jacobian      \Theta_{|G} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|G} )|
+            |\det( \Jacobian      \Theta_{|K} )|
+            = 
+            |\det( \Jacobian^{-1} \Theta_{|K} )|
             =
@@
         We want to characterize the singular values of this transform. 
-        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
-        We verify that 
-        \begin{align*}
-            \Theta_{|G}(x) 
+        We \tcf{let} $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
+        We can write
+        \begin{align*}
+            \Theta_{|K}(x) 
             = 
@@
         \end{align*}
-        We compute the eigenvalues of the symmetric matrix $M_{\Theta,G}^{\ast} M_{\Theta,G}$. 
-        Its square roots are the desired singular values of $M_{\Theta,G}$:
+        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
+        Its square roots are the desired singular values of $B$:
         \begin{align}
-            \sigma_{\max}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
-            ,
-            \\
-            \sigma_{\min}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
+            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
+            ,
+            \\
+            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
             .
         \end{align}
-        They are mutual reciprocals of each other, and they are monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
-        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,
+        They are mutual reciprocals of each other and they monotonely increasing and decreasing, respectively, in $\tan(\beta)$.
+        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
         whereas all its other singular values equal $1$.
@@
 
-        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
+        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
+        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
         which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
-        Thus, 
+        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
+        Thus 
         \begin{align*}
@@
             = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
-            \leq 
-            (n-\ell) \aspectratio(T)
+            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
+            \leq 
+            (n-k) \aspectratio(T)
 %             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
+%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
 %             \leq 
-%             \frac{ n-\ell }{n!}
+%             \frac{ n-k }{n!}
 %             \cdot 
@@
         \begin{align}\label{math:upper_bound_for_theta}
-            \mu_{T,\ell} 
+            B_{T} 
             := 
@@
             \sqrt{ 
-                1 + (n-\ell)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
             } 
             + 
-            (n-\ell) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
+            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
             .
         \end{align}
-        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
-        \begin{align}
-            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
-            \quad 
-            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
-            \quad 
-            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell}.
-        \end{align}
-        \color{red}It is also evident that the eigenvalues of the Jacobian almost everywhere have magnitude $1$.\color{black}
 
         \item 
-        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
-        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
+        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
+        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
         We construct a bi-Lipschitz mapping 
         \begin{align*}
-            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
-        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
-        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
-        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
+            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
+        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
+        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
+        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
         has a unique representation
         \begin{align*}
-            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
-        \end{align*}
-        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
+        \end{align*}
+        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
         \begin{align*}
@@
                 \\
-                -\frac 3 2 \tan(\beta) & 1 
+                -\frac 3 2 \tan(\beta) & 2 
             \end{pmatrix}
-%             = 
-%             \frac 1 2 
-%             \begin{pmatrix}
-%                 -1 & 0 
-%                 \\
-%                 -3\tan(\beta) & 2 
-%             \end{pmatrix}
-            .
-        \end{align*}
-        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
-        we obtain the singular values 
-        \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            &
-            =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
-            ,
-            \\
-            \sigma_{\min}(\Phi,G) 
-            &
-            =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-%             \frac{1}{2} 
-%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
-%             \\&
-%             =
-            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 
-            .
-        \end{align*}
-        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
-        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$ and 
+            = 
+            \frac 1 2 
+            \begin{pmatrix}
+                -1 & 0 
+                \\
+                -3\tan(\beta) & 2 
+            \end{pmatrix}
+        \end{align*}
+        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
+        \begin{align*}
+            \sigma_{\max} 
+            = 
+            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
+            =
+            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            ,
+            \\
+            \sigma_{\min} 
+            = 
+            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
+            =
+            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
+            .
+        \end{align*}
+        \begin{align*}
+            \sigma_{\max} 
+            = 
+            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
+            %=
+            %\frac 1 4 \sqrt{ 9 + 9\tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            =
+            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            ,
+            \\
+            \sigma_{\min} 
+            = 
+            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
+            =
+            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
+            .
+        \end{align*}
+        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
+        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
         \begin{align*}
@@
         \end{align*}
-        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
         Similar as above, we use the upper bound 
         \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
-        \end{align*}
-        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
+            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
+        \end{align*}
+        We conclude that 
         \begin{gather}
-            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
-            \leq 
-            \frac 3 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            1 + \frac{3}{2} (\ell+1) \aspectratio(T) 
+            \matnorm{ \Jacobian\Phi_{K} } 
+            \leq 
+            \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
+            \leq 
+            1 + \frac{3}{2} (k+1) \aspectratio(T) 
             \label{math:phi_max}
@@
             \\
-            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
-            \\
-            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
-            \leq 
-            \frac 3 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            2 + 3 (\ell+1) \aspectratio(T) 
+            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
+            \leq 
+            \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
+            \leq 
+            2 + 3 (k+1) \aspectratio(T) 
             \label{math:phi_min}
@@
         \end{align*}
-        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\|a\|$.
-%         We thus consider the upper bound 
-%         \begin{align*}
-%             \|a\| 
-%             \leq 
-%             2 \max_{1 \leq i \leq 2} 
-%             \left( 
-%                 \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
-%             \right)
-%             .
-%         \end{align*}
-        \color{red}Lastly, the matrix $\Id + \hat x \otimes a^{t}$ has the eigenvalue $1$ with multiplicity $n-1$ and a trace of $n + \langle a, \hat x \rangle$,
-        so it has one eigenvalue $1 + \langle a, \hat x \rangle$.\color{black}
+        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
+        We thus consider the upper bound 
+        \begin{align*}
+            \|a\| 
+            \leq 
+            2 \max_{1 \leq i \leq 2} 
+            \left( 
+                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
+            \right)
+            .
+        \end{align*}
 
@@
         We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
-The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(\ell+1)^{-1}$.
+The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
         That estimates the quotient $\| x_K \| / \| h_K \|$. 
         % 
-        In order to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
-        In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
+        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
         that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
@@
         It remains to find a lower bound for $\| h_{G} \|$.
-        Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
-        by scaling with $(\ell+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,\ell}$.
-The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
+        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
+        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
+        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$.
+The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
         %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
@@
             &\leq 
-            (\ell+1)\mu_{T,\ell}
+            (k+1)B_{T}
             \frac{ \diam(K) }{ \| h_{T} \| }
             \leq 
-            (\ell+1)\mu_{T,\ell}
+            (k+1)B_{T}
             \diameterratio(\calT)
@@
             \leq 
-            (\ell+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
             \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \mu_{T,\ell}
             ,
@@
             &\leq 
-            (\ell+1)
+            (k+1)
             \sup_{ K \in \patch_{\calT}(S) }
@@
             \leq 
-            (\ell+1)
+            (k+1)
             \diameterratio(\calT)
@@
             \leq 
-            (\ell+1)
+            (k+1)
             \sup_{ K \in \patch_{\calT}(S) }
@@
             \leq 
-            (\ell+1)
-            \aspectratio({G}) \mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            (k+1)B_{T}
+            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             .
@@
         %         To simplify that expression, we make another observation regarding the height vectors. 
-        %         when $T$ is an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S \subseteq T$,
+        %         when $T$ is an $n$-dimensional simplex with a $k$-dimensional subsimplex $S \subseteq T$,
         %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
-        %         then the barycenter $z_S$ of $S$ has distance $h/(\ell+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calG^\ast$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calD^\ast$ and $\patch_{\calT}(S)$
-        %         with the factor $(\ell+1)^{-1}$.
+        %         then the barycenter $z_S$ of $S$ has distance $h/(k+1)$ from the face $F$. 
+        %         From this observation we infer that the height vectors at the origin of the simplices in $\calR'$ and $\calK$
+        %         are obtained by rescaling the height vectors in $\calS'$ and $\patch_{\calT}(S)$
+        %         with the factor $(k+1)^{-1}$.
 
@@
             \leq 
-            (\ell+1) 
-            \left( 1 + \mu_{T,\ell} \right)
+            (k+1) 
+            \left( 1 + B_{T} \right)
             \sup_{ K \in \patch_{\calT}(S) }
@@
         \end{align*}
-        We define 
-        \begin{align}
-            \nu_{T,\ell} := \sqrt{ 1 + \frac{ (\ell+1)^{2}\left( 1 + \mu_{T,\ell} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (\ell+1)\left( 1 + \mu_{T,\ell} \right) \aspectratio(\calT) }{2}
-            .
-        \end{align}
-        In summary, 
-        the singular values of the Jacobian of $\Psi$ at almost every $x$ satisfy 
-        % using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, 
-        \begin{align}
-            \sigma_{1}(\Psi,x) % \matnorm{ \Jacobian\Psi(x) }
+        In summary, using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, we find the upper bounds 
+        \begin{align*}
+            \matnorm{ \Jacobian\Psi(x) }
             &\leq  
-            (\ell+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \cdot 
-            \nu_{T,\ell}
-            ,
-            \\
-            \sigma_{n}(\Psi,x)^{-1} % \matnorm{ \Jacobian\Psi(z)^{-1} }
+            \left( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT) 
+            \right)
+            ,
+            \\
+            \matnorm{ \Jacobian\Psi(z)^{-1} }
             &\leq  
-            (\ell+1)
+            (k+1)
             \diameterratio(\calT)
@@
             \cdot 
-            \nu_{T,\ell}
-            ,
-            \\
-            \sigma_{  2}(\Psi,x) 
-            &= 
-            \dots
-            =
-            \sigma_{n-1}(\Psi,x) 
-            \leq 
-            (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell}
-            ,
-            \\
-            \sigma_{n-1}(\Psi,x)^{-1} 
-            &= 
-            \dots
-            =
-            \sigma_{  2}(\Psi,x)^{-1} 
-            \leq 
-            (\ell+1) \diameterratio(\calT) \aspectratio(T) 
+            \left( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT) 
+            \right)
             ,
@@
             \left( 
-            (\ell+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
             \right)^{n},
@@
             \left( 
-            (\ell+1)
+            (k+1)
             \diameterratio(\calT)
@@
             &\leq 
-            \Cfive{n}{\ell}(\calT)
+            \Cfive{n}{k}(\calT)
             :=
-            (\ell+1) 
+            (k+1) 
             \diameterratio(\calT)
             \aspectratio(\calT)
-            \mu_{T,\ell}^{2}
-            \nu_{T,\ell}           
+            B_{T}^{2}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)            
             ,
@@
             &\leq 
-            \Cfiveprime{n}{\ell}(\calT)
+            \Cfiveprime{n}{k}(\calT)
             :=
-            (\ell+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T) \mu_{T,\ell}^{2}
-            ,
+            \aspectratio(T) 
+            \cdot 
+            B_T
             \\
@@
             &\leq
-            \Csechs{n}{\ell}(\calT)
+            \Csechs{n}{k}(\calT)
             :=
-            (\ell+1) 
+            (k+1) 
             \diameterratio(\calT)
             \aspectratio(\calT)
-            \mu_{T,\ell}
-            \nu_{T,\ell}
-            ,
+            B_{T}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)
             \\
@@
             &\leq 
-            \Csechsprime{n}{\ell}(\calT)
+            \Csechsprime{n}{k}(\calT)
             :=
-            (\ell+1)
+            (k+1)
             \diameterratio(\calT)
@@
             \cdot 
-            \mu_{T,\ell}
+            B_T
             .
@@
             &\leq 
-            \Cdetfive{n}{\ell}(\calT)
+            \Cdetfive{n}{k}(\calT)
             :=
-            (\ell+1)^{n}
+            (k+1)^{n}
             \diameterratio(\calT)^{n}
-            \mu_{T,\ell}^{n}
+            B_{T}^{n}
             \aspectratio(\calT)^{n}
@@
             &\leq 
-            \Cdetsechs{n}{\ell}(\calT)
+            \Cdetsechs{n}{k}(\calT)
             :=
-            (\ell+1)^{n}
+            (k+1)^{n}
             \diameterratio(\calT)^{n}
@@
         \end{align*}
-        \color{blue}
-        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
-        \begin{align*}
-            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
-            &
-            \leq 
-            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left( 
-            % Theta max 
-            \mu_{T,\ell} 
-            % Psi max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p}
-            ,
-            \\
-            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
-            &
-            \leq 
-            \Csechstrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left(
-            % Theta^{-1} max 
-            \mu_{T,\ell} 
-            % Psi^{-1} max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p}            
-            .
-        \end{align*}
         This completes the desired estimates for $\Xi_{1}$.
-        \color{black}
 
@@
             &\leq 
-            \Csieb{n}{\ell}(\calT)
+            \Csieb{n}{k}(\calT)
             :=
-            (\ell+1) 
+            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
+            \cdot 
+            (k+1) 
             \aspectratio(\calT)
-            \diameterratio(\calT)
-            \mu_{T,\ell}
-            \nu_{T,\ell}         
-            \cdot 
-            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)
-            ,
+            B_{T}
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)            
             \\
@@
             &\leq 
-            \Csiebprime{n}{\ell}(\calT)
+            \Csiebprime{n}{k}(\calT)
             :=
-            (\ell+1)
+            (k+1)B_{T}
             \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,\ell} 
+            \aspectratio(T) 
             \cdot 
-            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)
-            ,
+            \left( 1 + \frac{3}{2} (k+1) \aspectratio(T) \right)
             \\
@@
             &\leq  
-            \Cacht{n}{\ell}(\calT)
+            \Cacht{n}{k}(\calT)
             :=
-            (\ell+1) 
-            \diameterratio(\calT)
+            \left( 2 + 3 (k+1) \aspectratio(T) \right)
+            \cdot 
+            (k+1) 
             \aspectratio(\calT)
-            \nu_{T,\ell}           
-            \cdot 
-            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
-            ,
+            \Big( 
+                1 
+                + 
+                (k+1) 
+                \left( 1 + B_{T} \right)
+                \aspectratio(\calT)
+            \Big)            
             \\
@@
             &\leq 
-            \Cachtprime{n}{\ell}(\calT)
+            \Cachtprime{n}{k}(\calT)
             :=
-            (\ell+1)
+            (k+1)
             \diameterratio(\calT)
@@
             \cdot 
-            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)
+            \left( 2 + 3 (k+1) \aspectratio(T) \right)
             .
@@
             &\leq 
-            \Cdetsieb{n}{\ell}(\calT)
+            \Cdetsieb{n}{k}(\calT)
             :=
             \frac 1 2 
-            (\ell+1)^{n}
+            (k+1)^{n}
             \diameterratio(\calT)^{n}
-            \mu_{T,\ell}^{n}
+            B_{T}^{n}
             \aspectratio(\calT)^{n}
@@
             &\leq 
-            \Cdetacht{n}{\ell}(\calT)
+            \Cdetacht{n}{k}(\calT)
             :=
             2
-            (\ell+1)^{n}
+            (k+1)^{n}
             \diameterratio(\calT)^{n}
@@
         \end{align*}
-        \color{blue}
-        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
-        \begin{align*}
-            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
-            &
-            \leq 
-            \Csiebtrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left( 
-            % Phi max 
-            \left( 1 + \frac 3 2 ( \ell+1 )\aspectratio(\calT) \right)
-            % Psi max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p} 2^{\frac n p}
-            ,
-            \\
-            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
-            &
-            \leq 
-            \Cachttrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left(
-            % Phi^{-1} max 
-            \left( 2 + 3 ( \ell+1 )\aspectratio(\calT) \right)
-            % Psi^{-1} max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p} 2^{\frac n p}            
-            .
-        \end{align*}
-        \color{black}
         This completes the desired estimates for $\Xi_{2}$. 
     \end{itemize}
-    Having shown all the desired estimates, and the proof is complete. 
+    The proof is complete. 
 \end{proof}
 
-\begin{remark}
-    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
-    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
-    While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
-    it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
-\end{remark}
-
-\begin{remark}\label{remark:improved_starreflection}
-    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
-    Some improvements are immediately possible if $\ell=n-1$. 
-    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
-    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
-    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
-    %     \begin{gather*}
-    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
-    %         \quad 
-    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
-    %         \quad 
-    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
-    %         \\ 
-    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
-    %         \quad 
-    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
-    %     \end{gather*}
-    \begin{gather*} 
-        | \det\Jacobian\Xi^{  } |      \leq \volumeratio(\calT),
-        \\
-        \sigma_{1}
-        \leq 
-        \frac{1}{2} 
-        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
-        +
-        \frac{1}{2} 
-        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
-        ,
-        \\
-        \sigma_2,\dots,\sigma_{n-1},\sigma_{n} \leq 1.
-    \end{gather*}
-    In particular,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
-        \leq 
-        \left( 
-            \frac{1}{2} 
-            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
-            +
-            \frac{1}{2} 
-            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
-        \right)
-        \volumeratio(\calT)^{\frac 1 p}
-        .
-    \end{align*}
-    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
-    We believe that better estimates can be computed from the geometric data also in the other cases.
-\end{remark}
+\tcf{[--]}
+
+%%%   \begin{remark}
+%%%       We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
+%%%       where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
+%%%       While the reflection and deformation mappings in Proposition~\ref{proposition:starreflection} serve our purpose,
+%%%       it might be possible to improve the analysis or construction and lower the Jacobian estimates. 
+%%%   \end{remark}
 
@@
 
-The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator} has produced Poincar\'e--Friedrichs constants for convex domains and their analogues for the case of full boundary conditions.
+The analysis of the Poincar\'e potential operators in Section~\ref{section:potentialoperator}
+implies the following estimate for Poincar\'e--Friedrichs constants over convex domains.
+
+\begin{lemma}\label{lemma:PFexteriorsimplex}
+    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set. 
+    Let $0 \leq k < n$. 
+    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
+    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
+    with $\cartan u = \cartan w$ and 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        C_{{\PF},k,\Omega,p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align*}
+    where 
+    \begin{align*}
+        C_{{\PF},k,\Omega,p} 
+        = 
+        n C_{\Poinc}(n,k+1) 
+        \vol_{}(B_1(0)) 
+        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
+        \diam(\Omega)
+        .
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
+\end{proof}
+
 We also need a Poincar\'e--Friedrichs inequality for differential forms over a simplex but subject to homogeneous boundary conditions along a collection of faces.
@@
         \leq 
-        n! \cdot 2^{\ell+1} 
-        C_{\Bogov}(n,k+1) 
-        \vol_{n-1}(S_1(0))
-        \cdot 
+        2^{\frac{n-\ell}{p} + n + 1}
+        %2^{n+1} 
+        n^{\tcf{3/2}} C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (\ell+1)/n! } 
         \algebraicshapemeasure(T)^{k-1}
-        \Ceins{n}(T) 
+        % \Ceins{n}(T) 
         \diam(T)
@@
     onto the face $F_i$. 
-    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $\ell+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = 2^{n-\ell}/n!$
-
-    We let $\hat u := \varphi^{\ast} u \in W^{p}\Lambda^{k}(\Delta^n)$ and define $\hat g \in L^{p}\Lambda^{k+1}(\Delta^n)$ via $\hat g := \cartan \varphi^{\ast} u$. 
+    In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $l+1$ through $n$. 
+    We see that $\vol(\widetilde \Makoto) = (l+1)/n!$
+
+    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\Delta^n)$ via $\hat g := \cartan \varphi^{\ast} u$. 
     Then $\cartan \hat u = \hat g$. 
-    We let $\tilde u \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be the extension of $\hat u$ onto $\widetilde \Makoto$ by reflection across the coordinate axes,
-    and let $\tilde g \in L^{p}\Lambda^{k+1}(\widetilde \Makoto)$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
-    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$ with $\tilde g = \cartan \tilde u$.
-    We observe 
-    \begin{align*}
+    We let $\tilde u$ be the extension of $\hat u$ onto $\widetilde \Makoto$ by reflection across the coordinate axes,
+    and let $\tilde g$ is the extension of $\hat g$ onto $\widetilde \Makoto$ by reflection across the coordinate axes. 
+    We observe $\tilde g = \cartan \tilde u$. 
+    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$.
+
+    The bounds for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc} imply 
+    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
+    with $\cartan \tilde w = \cartan \tilde u$ and 
+    \begin{align*}
+        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
+        &\leq 
+        n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 
+        2
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        \leq 
-        2^{\frac {n-\ell} p}
-        \| \hat g \|_{L^{p}(\Delta^n)}
-        .
-    \end{align*}
-    The analysis for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc}, imply 
-    the existence of $\mathring w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
-    with $\cartan \mathring w = \cartan \tilde u$ satisfying the bounds 
-    \begin{align*}
-        \| \mathring w \|_{L^{p}(\widetilde \Makoto)}
-        &\leq 
-        C_{{\PF},\Poinc,k,\widetilde \Makoto,p}
+        \\&\leq 
+        2^{n+1} n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0)) }{ (l+1)/n! } 
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        %\\&
-        \leq 
-        % n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 2
-        % 2^n n   C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_1(0))    }{ \vol(\widetilde \Makoto) } 2
-        % 2^n     C_{\Bogov}(n,k+1) \frac{ \vol_{n-1}(S_1(0)) }{ \vol(\widetilde \Makoto) } 2
-        % 2^{n+1} C_{\Bogov}(n,k+1) \frac{ \vol_{n-1}(S_1(0)) }{ \vol(\widetilde \Makoto) }
-        % 2^{n+1} C_{\Bogov}(n,k+1) \frac{ \vol_{n-1}(S_1(0)) }{ 2^{n-\ell}/n! }
-        %
-        % n! 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
-        %
-        n! \cdot 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
-        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        .
-    \end{align*}
-    We let $\tilde w \in W^{p}\Lambda^{k}(\widetilde \Makoto)$ be defined by averaging the $2^{n - \ell}$ reflections of $\mathring w$ along the coordinate axes $\ell+1$ through $n$. Thus,
-    \begin{align*}
-        \| \tilde w \|_{L^{p}(\Delta^{n})}
-        =
-        2^{-\frac{n-\ell}{p}}
-        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
-        ,
-        \qquad 
-        \| \tilde w \|_{L^{p}(\widetilde \Makoto)}
-        \leq 
-        \| \mathring w \|_{L^{p}(\widetilde \Makoto)}
-        .
-    \end{align*}
-    Since $\tilde g$ has got the same symmetries, $\cartan \tilde w = \tilde g$.
-    \color{red}
-    \color{blue}
-    \color{black}
-
+        .
+    \end{align*}
     We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} ( \tilde w_{|\Delta^n} )$.
     By construction, $\cartan w = \cartan u$,
-    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{\ell}$.
-
-    To complete the discussion, we recall by Proposition~\ref{proposition:pullbackestimate} that 
+    and $w$ has vanishing trace along $F_{0} \cup \dots \cup F_{l}$.
+
+    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
     \begin{align*}
@@
         \\
+        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
+        \leq 
+        2^{\frac {n-\ell} p}
         \| \hat g \|_{L^{p}(\Delta^n)}
         &\leq 
+        2^{\frac {n-\ell} p}
         |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
@@
 
+\tcf
+{
+\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative:p2n3}
+We make the same assumption as in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
+but additionally require that $p=2$ and $d=3$. Then, for all 
+$u \in W^{p}\Lambda^{k}(T)$ with $\trace_{T,\Gamma} u = 0$,
+there exists $w \in W^{p}\Lambda^{k}(T)$ such that $\trace_{T,\Gamma} w = 0$,
+$\cartan w = \cartan u$, and  
+\begin{align*}
+\| w \|_{L^{p}(\Omega)} 
+\leq 
+\dots
+\| \cartan u \|_{L^{p}(\Omega)}.
+\end{align*}
+\end{lemma}
+
+\tcfsays{I am currently working on the proof.}
+
+%%%   \begin{proof}
+%%%   We present in detail the case where $k=2$ and $\cartan = \curl$.
+%%%   We set
+%%%   \begin{equation*}
+%%%   w
+%%%   :=
+%%%   \arg \min_{\substack{w \in W^{p}\Lambda^{k}(T) \\ \trace_{T,\Gamma} w = 0}} \|\phi\|.
+%%%   \end{equation*}
+%%%   
+%%%   Here, we first assume that $T$ is the reference tetrahedron.
+%%%   We observe that $w \in H^1(T)$. To see that, observe that $w$ solves a boundary
+%%%   value problem in $T$. We can classically reflect $w$ into $\widetilde w$ across all
+%%%   the faces of $T$ that are aligned with the coordinate axis (the reflection is ``odd''
+%%%   or ``even'' depending on the boundary condition of the face, and this process is done
+%%%   iteratively). The resulting $\widetilde w$ satifies $\widetilde w|_T = w$ and solves the
+%%%   same PDE than $w$ in the reflected patch $D$ (it is a convex ``diamond'') with the boundary
+%%%   condition satisfied by $w$ onto the face not aligned with the coordinate axis on the
+%%%   whole boundary of the resulting domain. In other words, $\widetilde w$ solves a
+%%%   curl-div PDE on a convex domain with one set of boundary conditions only, and therefore,
+%%%   $\widetilde w \in H^1(D)$, so that in particular $w \in H^1(T)$.
+%%%   \end{proof}
+}
+
 We prepare some further notation for our two main results. 
@@
 \end{align*}
+\tcfsays{I don't really understand what $\Gamma$ is in the formula above.}
 Suppose that $\calT$ is an $n$-dimensional triangulation and has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
@@
 	\begin{gather*}
-        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}
-        ,
+        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
     \end{gather*}
@@
             +
-            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
-            % \Cfive{n}{k}(\calT)
-            % \Cfiveprime{n}{k}(\calT)^{k} 
-            % \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+            \Cfive{n}{k}(\calT)
+            \Cfiveprime{n}{k}(\calT)^{k} 
+            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
             \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
         \right)
-        %\\&\qquad
+        \\&\qquad
         + 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
-        % \Cfive{n}{k}(\calT) 
-        % \Cfiveprime{n}{k}(\calT)^{k-1} 
-        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \Cfive{n}{k}(\calT) 
+        \Cfiveprime{n}{k}(\calT)^{k-1} 
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
         \| w \|_{L^{p}(\Makoto_{m-1})}
-        ,
-    \end{align*}
-    where $0 \leq \ell < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices. 
+        .
+    \end{align*}
 \end{theorem}
@@
 	and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-    We write $\ell$ for the dimension of $S_{m}$.
 
@@
     \end{align*}
+	\tcfsays{As pointed out above, I don't think this makes sense for our definition of trace.}
     There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
@@
         &\leq 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
-        % \Cfive{n}{k}(\calT)
-        % \Cfiveprime{n}{k}(\calT)^{k-1}
-        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
+        \Cfive{n}{k}(\calT)
+        \Cfiveprime{n}{k}(\calT)^{k-1}
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
         \cdot 
@@
         &\leq 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
-        % \Cfive{n}{k}{\ell}(\calT)
-        % \Cfiveprime{n}{k}(\calT)^{k}
-        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
+        \Cfive{n}{k}(\calT)
+        \Cfiveprime{n}{k}(\calT)^{k}
+        \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
         \cdot 
@@
     \begin{align*}
-        \| w \|_{L^{p}(\Omega)}
-        \leq 
-%         \left( 
-%             \Cachttrafo{n}{k}{\ell}(\calT)
-            % \Cacht{n}{k}(\calT)
-            % \Cachtprime{n}{k}(\calT)^{k} 
-            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-%             \Csiebtrafo{n}{k}{\ell}(\calT)
-            % \Csieb{n}{k}(\calT)
-            % \Csiebprime{n}{k}(\calT)^{k-1} 
-            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-%         \right)^{M}
+        \| w \|_{L^{p}(T_{m})}
+        \leq 
         \left( 
-        \prod_{m=1}^{M}
-            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
-            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
-        \right)
+        \Cacht{n}{k}(\calT)
+        \Cachtprime{n}{k}(\calT)^{k} 
+        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \Csieb{n}{k}(\calT)
+        \Csiebprime{n}{k}(\calT)^{k-1} 
+        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \right)^{M}
         C_{{\PF},k,T_{0},p}
         \| \cartan u \|_{L^{p}(\Omega)}
-        ,
-    \end{align*}
-    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices.
+        .
+    \end{align*}
 \end{theorem}
-\begin{proof}\color{blue}
-    We first fix some notation. 
-    Recall that for any $1 \leq m \leq M$, 
-    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
-    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
-    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
-    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
-
-    We introduce the deformation mapping $\Xi_{2,m} : \patch_{\calT}(S_m) \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
-    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{m-1} \setminus \partial T$.
-    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{m} \rightarrow X_{m-1}$ 
-    by letting it be the identity over $X_{m-1} \setminus A_{m-1}$.
-
-    For each $T \in \calT$ of dimension $n$, there exists a sequence $1 \leq m_{T,1},\dots,m_{T,K} \leq M$, for some $1 \leq K \leq M$,
-    such over the simplex $T$ we have the identity 
-    \begin{align*}
-        ...
-    \end{align*}
-\end{proof}
 \begin{proof}
@@
 	and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star.
-    We let $\ell_{M}$ be the dimension of $S_{M}$.
 
@@
         \leq 
-        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
-        %\Cacht{n}{k}(\calT)
-        %\Cachtprime{n}{k}(\calT)^{k} 
-        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \Cacht{n}{k}(\calT)
+        \Cachtprime{n}{k}(\calT)^{k} 
+        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
         \| g \|_{L^{p}(\Omega)}  
@@
     \end{align*}
-    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
-%     We have 
-%     \begin{align*}
-%         \| w' \|_{L^{p}(\Omega')} 
-%         \leq 
-%         \left( 
-%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
-%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
-%         \right)^{M-1}
-%         C_{{\PF},k,T_{0},p}
-%         \| g' \|_{L^{p}(\Omega')}  
-%     \end{align*}
+    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$ and 
+    \begin{align*}
+        \| w' \|_{L^{p}(\Omega')} 
+        \leq 
+        \left( 
+        \Cacht{n}{k}(\calT)
+        \Cachtprime{n}{k}(\calT)^{k} 
+        \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \Csieb{n}{k}(\calT)
+        \Csiebprime{n}{k}(\calT)^{k-1} 
+        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \right)^{M-1}
+        C_{{\PF},k,T_{0},p}
+        \| g' \|_{L^{p}(\Omega')}  
+    \end{align*}
     Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
@@
         \leq 
-        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
-        %\Csieb{n}{k}(\calT)
-        %\Csiebprime{n}{k}(\calT)^{k-1} 
-        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \Csieb{n}{k}(\calT)
+        \Csiebprime{n}{k}(\calT)^{k-1} 
+        \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
         \| w' \|_{L^{p}(\Omega')} 
     \end{align*}
-    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
+    The induction step is complete, and the desired result follows. 
 \end{proof}
 
-\begin{remark}\label{remark:fullrecursivesum:exterior}
-    \color{red}
-    We provide a similar discussion as in Remark~\ref{remark:fullrecursivesum}, 
-    this time geared towards the application of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \| \cartan u      \|_{L^{p}(T_{m})} 
-        \\&\qquad
-        +
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT)
-%         \Cfiveprime{n}{k}(\calT)^{k} 
-%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
-        \\&\qquad
-        + 
-        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT) 
-%         \Cfiveprime{n}{k}(\calT)^{k-1} 
-%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(\Makoto_{m-1})}
-        .
-    \end{align*}
-    Unwrapping the recursion for the norm over the $m$-th simplex, 
-    we find an estimate of the form 
-    \begin{align}\label{math:fullrecursivesum:exterior}
-        \| w \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
-        .
-    \end{align}
-    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
-    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \sum_{\ell=0}^{M} 
-        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
-        \right)
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
-    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        L^{\frac p q}
-        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        L^{\frac p q}
-        \sum_{m=0}^{M} 
-        \max_{ 0 \leq \ell \leq M }
-        C_{m,\ell}^{p} 
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    Hence, 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \sum_{\ell=0}^{M} 
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \delta_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \\&
-        \leq 
-        \max_{0 \leq \ell \leq M} \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \delta_{m,\ell} 
-        \right)
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        \\&
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        .
-    \end{align}
-    Now, if $q \leq p$, that is, $2 \leq p$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \left(
-            \sum_{\ell'=0}^{M}
-            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
-        \right)^{\frac 1 q}
-        .
-    \end{align}
-    Instead, if $p \leq q$, that is, $p \leq 2$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
-        .
-    \end{align}
-    So in any case, it is better than using the following Minkowski's inequality: 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
-        \\&
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align}
-\end{remark}
-
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
-    Let $\calT$ be a shellable $n$-dimensional triangulation, 
-    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
-    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell_{m}$ faces with the previous simplices.
-    \begin{itemize}
-        \item 
-        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
-        and such that the following estimates hold:
-        \begin{gather*}
-            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
-        \end{gather*}
-        and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
-        \begin{align*}
-            \| \bfw \|_{L^{p}(T_{m})}
-            &
-            \leq  
-            C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
-            \left( 
-                \| \curl \bfu      \|_{L^{p}(T_{m})} 
-                +
-                \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
-                \| \curl \bfu \|_{L^{p}(\Makoto_{m-1})}
-            \right)
-            \\&\qquad
-            + 
-            \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
-            \| \bfw \|_{L^{p}(\Makoto_{m-1})}
-            .
-        \end{align*}
-        \item 
-        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
-        such that 
-        \begin{align*}
-            \| \bfw \|_{L^{p}(T_{m})}
-            \leq 
-            \left( 
-            \prod_{i=1}^{M}
-            \Cachttrafo{n}{2}{\ell_{m}}{p}(\calT)
-            \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)
-            \right)
-            C_{{\PF},1,T_{0},p}
-            \| \curl \bfu \|_{L^{p}(\Omega)}
-            .
-        \end{align*}
-    \end{itemize}
-\end{theorem}
+\tcfsays{I have removed theorem specific to curl. I feel like the ones above stated with
+the exterior derivatives are sufficiently clear.}
+
+%%%   \begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
+%%%       Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+%%%       Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+%%%       Let $1 \leq p \leq \infty$ and $\bfu \in \bfW^{p}(\Omega,\curl)$.
+%%%       \begin{itemize}
+%%%           \item 
+%%%           There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
+%%%           and such that the following estimates hold:
+%%%           \begin{gather*}
+%%%               \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}.
+%%%           \end{gather*}
+%%%           and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
+%%%           \begin{align*}
+%%%               \| \bfw \|_{L^{p}(T_{m})}
+%%%               &
+%%%               \leq  
+%%%               C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
+%%%               \left( 
+%%%                   \| \curl u      \|_{L^{p}(T_{m})} 
+%%%                   +
+%%%                   \Cfive{n}{1}(\calT)
+%%%                   \Cfiveprime{n}{1}(\calT)^{1} 
+%%%                   \Cdetsechs{n}{1}(\calT)^{\frac 1 p} 
+%%%                   \| \curl u \|_{L^{p}(\Makoto_{m-1})}
+%%%               \right)
+%%%               \\&\qquad
+%%%               + 
+%%%               \Cfive{n}{1}(\calT) 
+%%%               \Cdetsechs{n}{1}(\calT)^{\frac 1 p} 
+%%%               \| \bfw \|_{L^{p}(\Makoto_{m-1})}
+%%%               .
+%%%           \end{align*}
+%%%           \item 
+%%%           There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
+%%%           such that 
+%%%           \begin{align*}
+%%%               \| \bfw \|_{L^{p}(T_{m})}
+%%%               \leq 
+%%%               \left( 
+%%%               \Cacht{n}{1}(\calT)
+%%%               \Cachtprime{n}{1}(\calT) 
+%%%               \Cdetsieb{n}{1}(\calT)^{\frac 1 p} 
+%%%               \Csieb{n}{1}(\calT)
+%%%               \Cdetacht{n}{1}(\calT)^{\frac 1 p} 
+%%%               \right)^{M}
+%%%               C_{{\PF},1,T_{0},p}
+%%%               \| \curl \bfu \|_{L^{p}(\Omega)}
+%%%               .
+%%%           \end{align*}
+%%%       \end{itemize}
+%%%   \end{theorem}
 
@@
 \begin{table}[h!]
-    \centering % TODO: recompute all those numbers
+    \centering
     \begin{tabular}{c|c|c|c|c|c}
@@
 
-The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions. 
+The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low \tcf{(i.e.
+$n=2$ or $3$)} dimensions.
 There are several avenues for further research. 
@@
 Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{\i} operators.
+
+\tcfsays{We might want to change above paragraph.}
 

### 2025-01-13 main.tex
add all of explicit notes by TCF to the reader.

@@
 % \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
-\newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
+% \newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
 \setlength{\marginparwidth}{2cm}
@@
 \newcommand{\disk}{\cye{ball}}
+\newcommand{\todo}[1]{{\color{RedOrange}\textbf{#1}}}
 
@@
 The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants.
-These quantify the fundamental stability properties of partial differential equations
+These quantify the fundamental stability properties of \todo{numerous} partial differential equations
 and enter the stability and convergence theory of numerical methods. 
-Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians and the eigenvalues of finite element matrices. 
+Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians \todo{and the eigenvalues of finite element matrices.
+(doubtful statement?)}
 However, while potentials and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
@@
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature. 
-We apply this construction principle to the curl and divergence operators, as well as the exterior derivative. 
+Here, we extend this construction to the curl and divergence operators, as well as the exterior derivative. 
 However, to proceed in the general exterior derivative case, we restrict our efforts to so-called shellable triangulations. 
@@
 The class of shellable triangulations includes practically relevant triangulations: 
-for example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
+for example, local triangulations around a simplex \todo{[TCF: Is it really
+true if the simlex is of highest dimension, e.g., a tetrahedron in 3D?]} within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
 Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
@@
 and hence these spaces are not classical Sobolev spaces of vector fields. 
-Our objective is to find bounded potentials for the operators 
+Our objective is to find bounded potentials (i.e., right inverses) for the operators 
 \begin{align*}
@@
 Exterior calculus~\cite{greub1967multilinear,lee2012smooth} is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite, gross2004electromagnetic, arnold2006finite, arnold2009geometric, arnold2010finite, demlow2014posteriori, licht2021local, arnold2021complexes}.
-This formalism is independent of the spatial dimension and highlights extends the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
-% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
-% In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}: 
+This formalism is independent of the spatial dimension and highlights the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
 For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
@@
 For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
+% This formalism is independent of the spatial dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
+% In this setting, the common writing of the Poincar\'e--Friedrichs inequalities we are interested in is just as~\eqref{math:PF_gradient_1}:
 
@@
 which may include weighted integrals or boundary terms. 
-These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem,
+These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem, \todo{[TCF: I believe this is often refered to as the Tartare-Petree theorem]}
 and thus the resulting constants are not explicitly computable.
@@
 In the Hilbert space case $p=2$, the Friedrichs inequality~\cite{burenkov1998sobolev} over the Sobolev space
-with homogeneous Dirichlet boundary conditions along $\partial \Omega$ implies~\eqref{math:intro:Wdiv} via duality. 
+with homogeneous Dirichlet boundary conditions along $\partial \Omega$ implies~\eqref{math:intro:Wdiv} by duality. 
 However, that easy duality argument, which yields an explicit upper bound proportional to the domain diameter, seems inherently restricted to $p=2$.
@@
 A duality argument also yields upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-Unfortunately, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+Their inequalities hold in convex Lipschitz domains, too, still in the Hilbert space setting~\cite{licht2024geometry}.
+However, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
+%\todo{ [TCF: We might want to obtain with ML's recent preprint.].}
 
@@
 then several estimates for Poincar\'e--Friedrichs constants are known. 
-Poincar\'e--Friedrichs inequalities actually hold over any star-shaped open bounded sets~\cite[Theorem~3.1]{hurri1988poincare}. 
-Polynomial interpolation estimates already imply the Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
+In fact, Poincar\'e--Friedrichs inequalities even hold over any star-shaped open bounded set~\cite[Theorem~3.1]{hurri1988poincare}. \todo{[TCF: I don’t exactly get the point of this sentence.].}
+Polynomial interpolation estimates already imply the gradient Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
 We pay particular attention to the regularized Poincar\'e and Bogovski\u{\i} potential operators for the exterior derivative,
@@
 Let us briefly discuss the practical limitations of the aforementioned estimates for Poincar\'e--Friedrichs constants for convex domains or domains that are star-shaped with respect to a ball. 
-Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
+Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over domains with shellable triangulations, with a key application being local stars within triangulated domains.
 While not all local stars describe convex subdomains, most local stars are star-shaped with respect to a ball. 
@@
 Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
-The method is known in the finite element literature~\cite{ern2021finite}.
-It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+The method is known in the finite element literature~\cite{ern2021finite}. \todo{[TCF: Could you reference a particular theorem or
+chapter?]} It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
 This sequential procedure applies to general triangulated domains, not only local stars, though the latter are our main interest here. 
@@
 The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
-In light of the different approaches listed before, 
-we aim for constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
+In light of the different approaches discussed above, 
+we seek constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
 and that do not depend on the boundary regularity of the domain.
@@
 % We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
-We generalize this sequential construction of potentials to the curl, the divergence, and the exterior derivative. 
+We generalize this sequential construction of potentials to the curl, the divergence, and more generally, the exterior derivative. 
 However, we need to overcome new challenges that arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail. 
@@
 For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive: 
-we ensure that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
+we require that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
 This allows us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex. 
@@
 We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
-We move on to the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
+We recap Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
 Our regularized potentials over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
@@
 Because $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$,
-any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
+any \emph{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
 satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
@@
 We call these points the \emph{vertices} of the simplex $T$.
-The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
-and its remaining points constitute the \textit{boundary} of the simplex.
+The strictly positive convex combinations of the vertices of the simplex constitute the \emph{ interior} of the simplex,
+and its remaining points constitute the \emph{boundary} of the simplex.
 If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
-then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.
+then we call $S$ a \emph{subsimplex} of $T$ and call $T$ a \emph{supersimplex} of $S$.
 
@@
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
-We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, 
+We say that a simplicial complex $\calT$ has \emph{dimension $n$} or is \emph{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
+We also write $\underlying{\calT}$ for the \emph{underlying set} of the simplicial complex $\calT$, 
 which is the union $\underlying{\calT} = \bigcup \calT$ of all simplices in $\calT$.
@@
 One calls any set triangulable if it is the underlying set of some triangulation. 
+\todo{Settle the issue that triangulations are closed but that domains are open sets.}
 
@@
 Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, members with codimension one) of this triangulation.\footnote{
-    Our use of the term \textit{face} as is common in classical geometry and the finite element literature~\cite{brenner2008mathematical}
-    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
-    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
+    Our use of the term \emph{face} as is common in classical geometry and the finite element literature~\cite{brenner2008mathematical}
+    and is synonymous with \emph{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
+    Notably, this terminology differs from the uses \emph{face} and \emph{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
 }
@@
 
-When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
+When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \emph{local star} of $T$, 
 which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
@@
 \end{gather*}
-We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
+We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the closed underlying set of the local patch. 
+\todo{Should that rather be a closed set?}
 A crucial structural observation is the following.
@@
  Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
+ \todo{Be more explicit and avoid measure theory}
  Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
@@
 Whenever $T$ is any $n$-dimensional simplex $T$,
-we define the \textit{aspect shape measure} $\aspectratio(T)$,
+we define the \emph{aspect shape measure} $\aspectratio(T)$,
 and 
-the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
+the \emph{algebraic shape measure} $\algebraicshapemeasure(T)$
 by 
@@
 \begin{remark}
-    The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is instance of a so-called \emph{shape measure}.
+    The ratio $\aspectratio(T)$ measures the ``shape quality'' of an $n$-dimensional simplex $T$ and is an instance of a so-called \emph{shape measure}.
     For example, the reference triangle has aspect shape measure $2$ and the reference tetrahedron has aspect shape measure $\sqrt{6}$. 
@@
 We gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
+\todo{Settle the subscripts of the vector norm.}
+\todo{Replace the constant Ceins and Czwei by the square root of n immediately.}
 
@@
     Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate,
+    By the Xu-Zikanatov estimate~\cite{xu2003some},
     \begin{align*}
@@
     Let $u \in C^{\infty}(T)$ have support disjoint from $F$.
-    We extend $u$ by zero to a function over the entire $\bbR^{n}$.
+    We tacitly extend this by zero to a function $u \in \Lebesgue^{\infty}(\bbR^{n})$. 
+    \todo{Is this readable?}
     Without loss of generality, 
@@
 
+\todo{TCF: Is the definition of trace satisfactory for matching traces across simplicies?}
+
 \subsection{Transformations by bi-Lipschitz mappings}
@@
 Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
+
+\todo{TCF: It is a bit pedantic, but shouldn’t we say that u is extended by zero to define the convolution
+below?}
 
@@
 %\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.}
-Let $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.
+In the remainder of this section, $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.
 
@@
 
-We begin with introducing the Costabel-McIntosh kernel.
+We begin by introducing the Costabel-McIntosh kernel.
 For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
@@
 We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.
+
+\todo{I guess the way we remove the $\chi_\Omega$ is beause we somehow have a convex (if $r \leq \delta(\Omega)$) conbination
+of $x,y$, correct? It would be nice poiting it out explicitly.}
 
@@
 
-We are now state the main results of this section. 
+We are now ready to state the main results of this section. 
 % We are in the position to establish the main results of this section.
@@
 The following upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$.
-However, though the space dimension $n$ and the form degree $\mia$ enter the estimates, 
+However, the space dimension $n$ and the form degree $\mia$ enter the estimates, 
 namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $C_{\Poinc}(n,\mia)$ and $C_{\Bogov}(n,\mia)$.
@@
         \label{math:theorem:bogovpoinc:poincare:k}
+    \todo{for a.e.\ $x \in \Omega$ (commas)}
     \end{align}
@@
         \label{math:theorem:bogovpoinc:bogov:n}
+    \todo{for a.e.\ $x \in \Omega$ (commas)}
     \end{align}
@@
     because the $L^{\infty}$ norm is the limit of the Lebesgue norms as $p$ goes to infinity. 
+    \todo{Get rid of the auxiliary zeta?}
 
     Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$. 
+    \todo{\sout{We write $\zeta := \Poinc_{\mia  } u$.}}
     We write $\zeta := \Poinc_{\mia  } u$. 
@@
     \end{align*}
-    By definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
+    Hence, by definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
     This shows \eqref{math:theorem:bogovpoinc:poincare:k}, and \eqref{math:theorem:bogovpoinc:poincare:zero} follows by an approximation argument.
@@
 We return to the theory of triangulations, as our main objective requires some further concepts.
-We are interested in simplicial complexes that triangulated domains and which are \emph{shellable}.
+We are interested in simplicial complexes that triangulate domains and which are \emph{shellable}.
 Such simplicial complexes are constructed by successively adding simplices in a well-structured manner. 
@@
 The following special cases receive particular interest:
-an \textit{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball, and we sometimes call this an \textit{$n$-disk} triangulation.
-An \textit{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
+an \emph{$n$-ball triangulation} is any triangulation of a topological (closed) $n$-ball, and we sometimes call this an \emph{$n$-disk} triangulation.
+An \emph{$n$-sphere triangulation} is any triangulation of a topological $n$-sphere.
 
@@
 We call this simplicial complex the \emph{boundary complex}. It has dimension $n-1$. 
-% We see that the family of boundary faces constitute a simplicial complex, which we call \textit{boundary complex}.
+% We see that the family of boundary faces constitute a simplicial complex, which we call \emph{boundary complex}.
 % Any point on the boundary lies within some boundary simplex, and hence the boundary complex is a triangulation of the boundary. 
@@
         then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball. \todo{sphere?}
     \end{itemize}
@@
     The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
-    by the topological Schoenflies theorem. 
+    by the topological Schoenflies theorem. \todo{reference}
     It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
@@
 
+    \todo{TCF: I could not really follow the paragraph above. Let's talk about it when we can!}
+
     If the underlying space $\underlying{\calT}$ is connected, 
-    then we easily see that the union of the $1$-simplices is path-connected.
+    then we easily see that the union of the $1$-simplices is path-connected. \todo{Maybe not that easy.}
     Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $\hat S_0=S,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
+    we can thus choose a sequence of $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
     As each vertex star is face-connected, 
@@
     Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
+    \todo{TCF: To make sure I properly understood: In the former case, you say that given a triangulation and a manifold, you cannot decides
+    whether it triangulates it.
+In the second case, you say that it is not possible to decide whether a triangulation triangulates some manifold (without specifying what it is, neither as input nor output).
+Correct?}
     % Whether a simplicial complex is the triangulation of a manifold is algorithmically undecidable. ~\cite{todo}
@@
 \end{align*}
-the $m$-th \textit{interface set}. 
+the $m$-th \emph{interface set}. 
 % Note that this intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$.
@@
     which requires $m = M$.
+    \todo{TCF: I don’t understand why XM couldn’t be a topological n-ball.}
     On the other hand, 
@@
     By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-\disk.
-    Any shelling of that \disk\ can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    Any shelling of that \disk\ \todo{$\calT$} can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
     So it remains to show that any triangulation $\calT$ of the two-dimensional \disk\ is shellable. 
@@
     \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
+    which is the identity along ${\Gamma_1}$. 
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \end{align*}
-    which is the identity along $\partial \Makoto \setminus \partial T$.
+    which is the identity along $\partial \Makoto \setminus \partial T$. \todo{Use some name for this intersection?}
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \end{align*}
+    \todo{TCF: Should $\sigma_n$ be $\sigma_n^{-1}$ in the second line of both statements?}
     \end{enumerate}
@@
         %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$. \todo{What is the complementary subsimplex?}
         Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
@@
         In particular, $\calD^\ast$ is its own star around $S$.
+
+        \todo{Picture?}
 
@@
 \begin{remark}\label{remark:improved_starreflection}
-    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
+    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \emph{proof-of-concept} but not as optimal in any sense.
     Some improvements are immediately possible if $\ell=n-1$. 
@@
     \end{align*}
+    \todo{Double check the constant}
 \end{lemma}
@@
 
+% TODO: Keep this theorem? 
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
@@
 
-The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions. 
+The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e.\ $n=2$ or $n=3$).
 There are several avenues for further research. 
@@
 Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{\i} operators.
+\todo{The above needs to be updated.}
 

### 2025-01-14 main.tex
partial update

@@
 The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants.
-These quantify the fundamental stability properties of \todo{numerous} partial differential equations
+These quantify the fundamental stability properties of {numerous} partial differential equations % DONE
 and enter the stability and convergence theory of numerical methods. 
-Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians \todo{and the eigenvalues of finite element matrices.
-(doubtful statement?)}
+Upper bounds of the Poincar\'e--Friedrichs constants also provide lower bounds of the eigenvalues of the associated Laplacians.
+% DONE {and the eigenvalues of finite element matrices. (doubtful statement?)}
 However, while potentials and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
@@
 The class of shellable triangulations includes practically relevant triangulations: 
-for example, local triangulations around a simplex \todo{[TCF: Is it really
-true if the simlex is of highest dimension, e.g., a tetrahedron in 3D?]} within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three. 
+for example, local triangulations around a simplex 
+% \todo{[TCF: Is it really true if the simlex is of highest dimension, e.g., a tetrahedron in 3D?]} 
+within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three; see also Figure~\ref{figure:patches}. 
 Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
@@
 A duality argument also yields upper estimates of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary.
-Their inequalities hold in convex Lipschitz domains, too, still in the Hilbert space setting~\cite{licht2024geometry}.
+Their inequalities hold in convex Lipschitz domains, too~\cite{licht2024geometry}.
 However, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$.
@@
 When the domain is not convex but star-shaped with respect to a ball,
-then several estimates for Poincar\'e--Friedrichs constants are known. 
-In fact, Poincar\'e--Friedrichs inequalities even hold over any star-shaped open bounded set~\cite[Theorem~3.1]{hurri1988poincare}. \todo{[TCF: I don’t exactly get the point of this sentence.].}
+then several estimates for Poincar\'e--Friedrichs constants are known.\footnote{In fact, Poincar\'e--Friedrichs inequalities even hold over any star-shaped open bounded set; see~\cite[Theorem~3.1]{hurri1988poincare}.}
+% \todo{[TCF: I don’t exactly get the point of this sentence.].}
 Polynomial interpolation estimates already imply the gradient Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
@@
 We also write $\Makoto_T := | \patch_{\calT}(T) |$ for the closed underlying set of the local patch. 
-\todo{Should that rather be a closed set?}
+% DONE {Should that rather be a closed set?} {No, it's easier to keep it like that.}
 A crucial structural observation is the following.
+
+\begin{figure}[t]
+\centering
+\begin{tabular}{ccc}
+  \begin{tikzpicture}
+    % [line join=bevel,z={( 3.85mm, -3.85mm)}]
+    [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]
+
+    % TODO: Change colors to grey scale
+
+    \coordinate (O) at (  0.0,  0.0, 0.0);
+    \coordinate (A) at (  1.0,  0.0, 0.0);
+    \coordinate (B) at (  0.3,  1.0, 0.0);
+    \coordinate (C) at ( -0.6,  0.8, 0.0);
+    \coordinate (D) at ( -0.6, -0.7, 0.0);
+    \coordinate (E) at (  0.3, -1.0, 0.0);
+    \coordinate (F) at (  0.3, -1.0, 0.0);
+
+    \draw (O) -- (A) -- (B) -- cycle;
+    \draw (O) -- (B) -- (C) -- cycle;
+    \draw (O) -- (C) -- (D) -- cycle;
+    \draw (O) -- (D) -- (E) -- cycle;
+    \draw (O) -- (E) -- (A) -- cycle;
+    \draw (A) -- (B) -- (C) -- (D) -- (E) -- cycle;
+    \draw (0,0) circle[radius=2pt];
+    \fill (0,0) circle[radius=2pt];
+  \end{tikzpicture}%
+  \qquad&\qquad
+  \begin{tikzpicture}
+    % [line join=bevel,z={( 3.85mm, -3.85mm)}]
+    [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]
+
+    % TODO: Change colors to grey scale
+
+    \coordinate (O) at (  0.0,  0.0, 0.0);
+    \coordinate (A) at (  1.0,  0.0, 0.0);
+    \coordinate (B) at (  0.3,  1.0, 0.0);
+    \coordinate (C) at ( -0.6,  0.8, 0.0);
+    \coordinate (D) at ( -0.6, -0.7, 0.0);
+    \coordinate (E) at (  0.3, -1.0, 0.0);
+    \coordinate (F) at (  0.3, -1.0, 0.0);
+
+    \draw (O) -- (A) -- (B) -- cycle;
+    \draw (O) -- (E) -- (A) -- cycle;
+    \draw[line width=0.1cm] (O) -- (A);
+  \end{tikzpicture}%
+  \qquad&\qquad
+  \begin{tikzpicture}
+    % [line join=bevel,z={( 3.85mm, -3.85mm)}]
+    [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]
+
+    % TODO: Change colors to grey scale
+
+    \coordinate (O) at (  0.0,  0.0, 0.0);
+    \coordinate (A) at (  1.0,  0.0, 0.0);
+    \coordinate (B) at (  0.3,  1.0, 0.0);
+    \coordinate (C) at ( -0.6,  0.8, 0.0);
+    \coordinate (D) at ( -0.6, -0.7, 0.0);
+    \coordinate (E) at (  0.3, -1.0, 0.0);
+    \coordinate (F) at (  0.3, -1.0, 0.0);
+
+    \draw[line width=0.1cm] (O) -- (A) -- (E) -- cycle;
+  \end{tikzpicture}
+\end{tabular} 
+\caption{From left to right: local patches around a vertex, and edge, and a triangle.
+The local patch of a full-dimensional simplex is the only the simplex itself (and its subsimplices).}\label{figure:patches}
+\end{figure}
 
@@
  Let $\calT$ be an $n$-dimensional simplicial complex and let $S,S' \in \calT$.
- \todo{Be more explicit and avoid measure theory}
- Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ are essentially disjoint or there exists $S'' \in \calT$
+ % DONE {Be more explicit and avoid measure theory}
+ Then either $\patch_{\calT}(S)$ and $\patch_{\calT}(S')$ 
+ only intersect in simplices of dimension at most $n-1$ % are essentially disjoint 
+ or there exists $S'' \in \calT$
  such that 
@@
 Let $\mollifier$ be a non-negative scalar function whose integral equals one and whose support lies in the unit ball around the origin.
-Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We review the following approximation results.
-
-\todo{TCF: It is a bit pedantic, but shouldn’t we say that u is extended by zero to define the convolution
-below?}
+Define $\mollifier_{\eps}(x) := \eps^{-n} \mollifier(x/\eps)$. We collect several approximation results that involve convolution with a mollifier.
+In what follows, convolutions of functions defined over domains tacitly assume that these functions have been extended by zero to all of Euclidean space.
+
+% \todo{TCF: It is a bit pedantic, but shouldn’t we say that u is extended by zero to define the convolution below?}
 
@@
     \begin{align}
-        C_{{\PF},\Poinc,k,\Omega,p} := C_{\Poinc}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
-        ,
-        \quad 
-        C_{{\PF},\Bogov,k,\Omega,p} := C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
+        C_{{\PF},\Poinc,k,\Omega,p} &:= C_{\Poinc}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
+        ,
+        \\
+        C_{{\PF},\Bogov,k,\Omega,p} &:= C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\Omega)^{n}}{\vol(\Omega)} \diam(\Omega)
         .
     \end{align}
-    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
+    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds for a.e.\ $x \in \Omega$ that 
     \begin{align}
@@
         \label{math:theorem:bogovpoinc:poincare:k}    
-    \todo{for a.e.\ $x \in \Omega$ (commas)}
     \end{align}
@@
 
-    For any $u \in \bfW^{p}_{0}\Alt^{\mia}(\Omega)$ it holds that 
+    For any $u \in \bfW^{p}_{0}\Alt^{\mia}(\Omega)$ it holds for a.e.\ $x \in \Omega$ that 
     \begin{align}
@@
         \label{math:theorem:bogovpoinc:bogov:n}
-    \todo{for a.e.\ $x \in \Omega$ (commas)}
     \end{align}
@@
     because the $L^{\infty}$ norm is the limit of the Lebesgue norms as $p$ goes to infinity. 
-    \todo{Get rid of the auxiliary zeta?}
+    % DONE \todo{Get rid of the auxiliary zeta?} {no}
 
     Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$. 
-    \todo{\sout{We write $\zeta := \Poinc_{\mia  } u$.}}
+    % \todo{\sout{We write $\zeta := \Poinc_{\mia  } u$.}}
     We write $\zeta := \Poinc_{\mia  } u$. 
@@
         then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
-        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball. \todo{sphere?}
+        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball. % DONE {sphere?}
     \end{itemize}
@@
     Clearly, any simplicial $1$-ball and simplicial $1$-sphere are face-connected. 
-    Now, if $n \geq 1$, then any vertex star in any $(n+1)$-dimensional manifold triangulation is already face-connected if all simplicial $n$-balls and $n$-spheres are face-connected.
+    Now, if $n \geq 1$ and $V \in \calT$,
+    then the $n$-simplices in $\patch_{\calT}(V)$ are in correspondence to the $(n-1)$-simplices in $\carapace_{\calT}(V)$.
+    Hence $\patch_{\calT}(V)$, a triangulation of dimension $n-1$, is face-connected if and only if $\carapace_{\calT}(V)$, a triangulation of dimension $n-1$, is face-connected.
+    % then any vertex star in any $(n+1)$-dimensional manifold triangulation is already face-connected if all simplicial $n$-balls and $n$-spheres are face-connected.
     The induction argument implies that each vertex star in $\calT$ is face-connected.
 
-    \todo{TCF: I could not really follow the paragraph above. Let's talk about it when we can!}
+    % \todo{TCF: I could not really follow the paragraph above. Let's talk about it when we can!}
+
+    \todo{
+    We assume that the underlying space $\underlying{\calT}$ is connected. 
+    Given $n$-simplices $S,S' \in \calT$, 
+    there exists a path $\gamma : [0,1] \rightarrow \underlying{\calT}$ from the barycenter of $S$ to the barycenter of $S'$.
+    We can choose a sequence of $n$-simplices $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ that cover the path and whose intersections with the path are homeomorphic to $[0,1]$.
+    }
 
@@
     \end{align*}
-    which is the identity along $\partial \Makoto \setminus \partial T$. \todo{Use some name for this intersection?}
+    which is the identity along $\Gamma_2$. \todo{Include a picture of the situation?}
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
         %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$. \todo{What is the complementary subsimplex?}
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$. 
+        In other words, the vertices of $S'$ are the vertices of $T$ that are not vertices of $S$. 
         Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,

### 2025-01-14 main.tex
some proof

@@
     \todo{
-    We assume that the underlying space $\underlying{\calT}$ is connected. 
+    We assume that the underlying space $\underlying{\calT}$ is connected, and hence path-connected. 
     Given $n$-simplices $S,S' \in \calT$, 
     there exists a path $\gamma : [0,1] \rightarrow \underlying{\calT}$ from the barycenter of $S$ to the barycenter of $S'$.
-    We can choose a sequence of $n$-simplices $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ that cover the path and whose intersections with the path are homeomorphic to $[0,1]$.
+    We can choose a sequence of $n$-simplices $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ without repetitions 
+    that cover the path and whose intersections with the path are homeomorphic to $[0,1]$.
+    The intersections $\gamma([0,1]) \cap S_{i}$ and $\gamma([0,1]) \cap S_{i+1}$ intersect at one point that lies in a common subsimplex of $S_{i}$ and $S_{i+1}$.
+    We deduce that each two consecutive simplices in the sequence $\hat S_0,\hat S_1,\dots,\hat S_m$ have at least one vertex in common. 
+    As each vertex star is face-connected, 
+    there exists a  sequence $S=T_0,T_1,\dots,T_{m}=S' \in \calT$ 
+    where $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+    This just means that $\calT$ is face-connected. 
     }
 
+    \tode{
+    We assume that the underlying space \(\underlying{\calT}\) is connected, and hence path-connected. 
+    Given \(n\)-simplices \(S, S' \in \calT\), 
+    there exists a path \(\gamma : [0,1] \rightarrow \underlying{\calT}\) from the barycenter of \(S\) to the barycenter of \(S'\).
+    We can choose a sequence of \(n\)-simplices \(\hat S_0, \hat S_1, \dots, \hat S_m \in \calT\) (with \(\hat S_0 = S\) and \(\hat S_m = S'\)), without repetitions, 
+    that covers the path and whose intersections with the path are homeomorphic to \([0,1]\).
+    The sets \(\gamma([0,1]) \cap \hat S_{i}\) and \(\gamma([0,1]) \cap \hat S_{i+1}\) intersect at exactly one point, which lies in a common subsimplex of \(\hat S_{i}\) and \(\hat S_{i+1}\).
+    We deduce that any two consecutive simplices in the sequence \(\hat S_0, \hat S_1, \dots, \hat S_m\) share at least one vertex. 
+    As each vertex star is face-connected, 
+    there exists another sequence of \(n\)-simplices \(T_0, T_1, \dots, T_m \in \calT\) (with \(T_0 = S\) and \(T_m = S'\)) 
+    such that \(T_{i} \cap T_{i-1}\) is a face of both \(T_{i}\) and \(T_{i-1}\) for all \(1 \le i \le m\).
+    This shows that \(\calT\) is face-connected.
+    }
     If the underlying space $\underlying{\calT}$ is connected, 
-    then we easily see that the union of the $1$-simplices is path-connected. \todo{Maybe not that easy.}
+    then we easily see that the union of the $1$-simplices is path-connected. 
     Given $n$-simplices $S,S' \in \calT$, 

### 2025-01-14 main.tex
more of Theo's remarks

--- 2025-01-14 main.tex
@@
 \end{align*}
-If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
+If $x \in \Omega$ and $x \neq y$, 
+then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
 \begin{align*}
@@
 
-\todo{I guess the way we remove the $\chi_\Omega$ is beause we somehow have a convex (if $r \leq \delta(\Omega)$) conbination
-of $x,y$, correct? It would be nice poiting it out explicitly.}
+% DONE {I guess the way we remove the $\chi_\Omega$ is beause we somehow have a convex (if $r \leq \delta(\Omega)$) conbination of $x,y$, correct? It would be nice poiting it out explicitly.}
 
@@
     Not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
-    When the dimension is at least five, then there is no computer algorithm that, given a finite simplicial complex as input, decides whether the input is the triangulation of some fixed manifold~\cite{chernavsky2006unrecognizability}.
-    Going further, it has been shown that deciding whether a simplicial complex is the triangulation of a manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
-    \todo{TCF: To make sure I properly understood: In the former case, you say that given a triangulation and a manifold, you cannot decides
-    whether it triangulates it.
+    When the dimension is at least five, then there are manifolds for which no computer algorithm, given a finite simplicial complex as input, decides whether the input is the triangulation of that manifold~\cite{chernavsky2006unrecognizability}.
+    Going further, it has been shown that deciding whether a simplicial complex triangulates \emph{any} manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
+%     \todo{TCF: To make sure I properly understood: In the former case, you say that given a triangulation and a manifold, you cannot decides whether it triangulates it.
 In the second case, you say that it is not possible to decide whether a triangulation triangulates some manifold (without specifying what it is, neither as input nor output).
@@
 We conjecture that the Guerini--Savo~\cite{guerini2004eigenvalue} estimates, hitherto only known when $p=2$ and over bounded convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and convex Lipschitz domains.
-We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized Poincar\'e operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently employ.
+The case $p=2$ was discussed recently~\cite{licht2024geometry}.
+Such estimates would likely improve on the Poincar\'e--Friedrichs constants than the regularized Poincar\'e operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently use.
 Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{\i} operators.
-\todo{The above needs to be updated.}
+% DONE {The above needs to be updated.}
 

### 2025-01-14 revision/main.tex
first batch of changes
process changes to vector calculus section

@@
 \end{align} 
-}\todo[inline]{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparsion with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
+}\todo[inline]{MV: The roles of $u$ and $w$ are flipped in the various parts of the paper, see~\eqref{math:PF_DF} in comparison with Lemma~\ref{lemma:PFexteriorsimplex}. It would be great to unify.}
 
@@
 
-\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be nonconvex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
+\cye{We treat specifically the gradient operator (the setting of Section~\ref{section:intro_grad}) on triangulated domains that can be non-convex and non-star-shaped but where the triangulations are face connected (though not necessarily shellable).
 Here, Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} are our main results.} \todo{MV: remark from after Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:gradzwei} moved here.}
@@
 In practice, we not always distinguish between points and singleton simplices. 
-Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
+Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, members of codimension one) of this triangulation.\footnote{
     Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
@@
 We write $\diam(T)$ and $\vol(T)$ for the diameter and $n$-dimensional volume of any $n$-simplex $T$.
-Moreover, $\height(T)$ refers to the smallest height of any of the vertices of the simplex $T$.
+Moreover, $\height(T)$ refers to the smallest height of any vertex of the simplex $T$.
 
@@
 The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} overestimates the best one increasingly with increasing number of $n$-simplices in the triangulation $\calT$.
-For this reason, we target its use to local patches (stars), in particular nonconvex boundary stars such as that of Figure~\ref{figure:exhausting}.
-Clearly, the same building principle applies when we can obtain a nonoverlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a  face-connected path.
+For this reason, we target its use to local patches (stars), in particular non-convex boundary stars such as that of Figure~\ref{figure:exhausting}.
+Clearly, the same building principle applies when we can obtain a non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $U_m$ with a  face-connected path.
 The proof proceeds verbatim, where we merely replace the simplices $T_{m}$ by the convex local patches $U_m$.
@@
 We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
-such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
+such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration-by-parts formula
 \begin{align*}
@@
 and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m\cye{-1}})$. 
-The main result of this manuscript \cye{for nonconvex and non-star-shaped triangulated domains} is the following theorem.
+The main result of this manuscript \cye{for non-convex and non-star-shaped triangulated domains} is the following theorem.
 

### 2025-01-15 main.tex
fix
update vector norm notation

--- 2025-01-14 main.tex
@@
 The class of shellable triangulations includes practically relevant triangulations: 
-for example, local triangulations around a simplex 
-% \todo{[TCF: Is it really true if the simlex is of highest dimension, e.g., a tetrahedron in 3D?]} 
-within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three; see also Figure~\ref{figure:patches}. 
+for example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three; see also Figure~\ref{figure:patches}.
+% DONE {[TCF: Is it really true if the simplex is of highest dimension, e.g., a tetrahedron in 3D?]} 
 Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
@@
 which may include weighted integrals or boundary terms. 
-These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem, \todo{[TCF: I believe this is often refered to as the Tartare-Petree theorem]}
+These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem, 
+% TODO {[TCF: I believe this is often refered to as the Tartare-Petree theorem]}
 and thus the resulting constants are not explicitly computable.
@@
 However, no results as those of~\cite{guerini2004eigenvalue} are known over bounded convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$. 
-%\todo{ [TCF: We might want to obtain with ML's recent preprint.].}
+%DONE { [TCF: We might want to obtain with ML's recent preprint.].}
 
@@
 then several estimates for Poincar\'e--Friedrichs constants are known.\footnote{In fact, Poincar\'e--Friedrichs inequalities even hold over any star-shaped open bounded set; see~\cite[Theorem~3.1]{hurri1988poincare}.}
-% \todo{[TCF: I don’t exactly get the point of this sentence.].}
+% DONE {[TCF: I don't exactly get the point of this sentence.].}
 Polynomial interpolation estimates already imply the gradient Poincar\'e--Friedrichs inequality~\cite{brenner2008mathematical,ern2021finite}. 
@@
 Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
-The method is known in the finite element literature~\cite{ern2021finite}. \todo{[TCF: Could you reference a particular theorem or
-chapter?]} It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
+The method is known in the finite element literature~\cite{ern2021finite}. 
+% TODO {[TCF: Could you reference a particular theorem or chapter?]} 
+It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
 This sequential procedure applies to general triangulated domains, not only local stars, though the latter are our main interest here. 
@@
 One calls any set triangulable if it is the underlying set of some triangulation. 
-\todo{Settle the issue that triangulations are closed but that domains are open sets.}
+% DONE {Settle the issue that triangulations are closed but that domains are open sets.}
 
@@
 We gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
-\todo{Settle the subscripts of the vector norm.}
-\todo{Replace the constant Ceins and Czwei by the square root of n immediately.}
+% \todo{Settle the subscripts of the vector norm.}
+% TODO {Replace the constant Ceins and Czwei by the square root of n immediately.}
 
@@
         \qquad 
-        c = \|b_2-b_1\| / h_1
+        c = \vecnorm{ b_2-b_1 } / h_1
         .
@@
 %     \begin{align*}
-%         \| \Xi(x) - \Xi(x') \|
+%         \vecnorm{ \Xi(x) - \Xi(x') }
 %         \leq  
-%         \| b - b' \| + | \alpha - \alpha' | \cdot \| z_2 \|
+%         \vecnorm{ b - b' } + | \alpha - \alpha' | \cdot \vecnorm{ z_2 }
 %         \leq  
-%         \| b - b' \| + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \| \hat h_0 \|
+%         \vecnorm{ b - b' } + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \vecnorm{ \hat h_0 }
 %         \leq 
-%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \| x-x' \|
+%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \vecnorm{ x-x' }
 %         .
@@
     We tacitly extend this by zero to a function $u \in \Lebesgue^{\infty}(\bbR^{n})$. 
-    \todo{Is this readable?}
+    % DONE {Is this readable?}
     Without loss of generality, 
@@
 % \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
-% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
+% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }} DONE {MV: repeated below.}
 Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
@@
 \end{gather*}
-% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
+% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.} DONE {MV: Moved here.}
 This is a closed subspace.
@@
 
-\todo{TCF: Is the definition of trace satisfactory for matching traces across simplicies?}
+% DONE {TCF: Is the definition of trace satisfactory for matching traces across simplicies?}
 
@@
 
-% \todo{TCF: It is a bit pedantic, but shouldn’t we say that u is extended by zero to define the convolution below?}
+% DONE {TCF: It is a bit pedantic, but shouldn't we say that u is extended by zero to define the convolution below?}
 
@@
 
-% \todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
+% DONE {MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:
 
@@
         u\left( y \right) 
-        \wedge \phi\left( \epsilon \frac{y-a}{\|y-a\|} + a \right) 
+        \wedge \phi\left( \epsilon \frac{y-a}{ \vecnorm{y-a} } + a \right) 
     \,dy 
@@
 
-% \todo{MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
+% DONE {MV: Do $\Poinc_{\mia}$ and $\Bogov_{\mia}$ still map piecewise polynomials to piecewise polynomials?
 Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}
@@
     because the $L^{\infty}$ norm is the limit of the Lebesgue norms as $p$ goes to infinity. 
-    % DONE \todo{Get rid of the auxiliary zeta?} {no}
+    % DONT {Get rid of the auxiliary zeta?} {no}
 
     Consider now $u \in W^{p}\Alt^{\mia}(\Omega)$ with $1 \leq k \leq n$. 
-    % \todo{\sout{We write $\zeta := \Poinc_{\mia  } u$.}}
     We write $\zeta := \Poinc_{\mia  } u$. 
@@
 
-    % \todo{TCF: I could not really follow the paragraph above. Let's talk about it when we can!}
-
-    \todo{
-    We assume that the underlying space $\underlying{\calT}$ is connected. 
+    % DONE {TCF: I could not really follow the paragraph above. Let's talk about it when we can!}
+
+    We assume that the underlying space $\underlying{\calT}$ is connected, and hence path-connected. 
     Given $n$-simplices $S,S' \in \calT$, 
     there exists a path $\gamma : [0,1] \rightarrow \underlying{\calT}$ from the barycenter of $S$ to the barycenter of $S'$.
-    We can choose a sequence of $n$-simplices $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ that cover the path and whose intersections with the path are homeomorphic to $[0,1]$.
-    }
-
-    If the underlying space $\underlying{\calT}$ is connected, 
-    then we easily see that the union of the $1$-simplices is path-connected. \todo{Maybe not that easy.}
-    Given $n$-simplices $S,S' \in \calT$, 
-    we can thus choose a sequence of $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, and so each two consecutive simplices in that sequence have at least one vertex in common.
+    We can choose a sequence of $n$-simplices $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ without repetitions 
+    that cover the path and whose intersections with the path are homeomorphic to $[0,1]$.
+    For any index $1 \leq i \leq m$, 
+    the intersection $\gamma([0,1]) \cap S_{i}$ and $\gamma([0,1]) \cap S_{i+1}$ intersect at one point lying in a common subsimplex of $S_{i}$ and $S_{i+1}$.
+    We deduce that each two consecutive simplices in the sequence $\hat S_0,\hat S_1,\dots,\hat S_m$ will have at least one vertex in common. 
     As each vertex star is face-connected, 
-    we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
-    is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+    there exists a sequence $S=S_0,S_1,\dots,S_{m}=S' \in \calT$ 
+    where $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
     This just means that $\calT$ is face-connected.
+
+%     If the underlying space $\underlying{\calT}$ is connected, 
+%     then we easily see that the union of the $1$-simplices is path-connected. 
+%     Given $n$-simplices $S,S' \in \calT$, 
+%     we can thus choose a sequence of $S = \hat S_0,\hat S_1,\dots,\hat S_m=S' \in \calT$ 
+%     such that $\hat S_{i} \cap \hat S_{i-1} \neq \emptyset$ for all $1 \leq i \leq m$, 
+%     and so each two consecutive simplices in that sequence have at least one vertex in common. 
+%     As each vertex star is face-connected, 
+%     we can thus assume without loss of generality that the sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ 
+%     is such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+%     This just means that $\calT$ is face-connected. 
 \end{proof}
@@
     Going further, it has been shown that deciding whether a simplicial complex triangulates \emph{any} manifold cannot be decided by any computer algorithm~\cite{poonen2014undecidable}.     
-%     \todo{TCF: To make sure I properly understood: In the former case, you say that given a triangulation and a manifold, you cannot decides whether it triangulates it.
+%     DONE {TCF: To make sure I properly understood: In the former case, you say that given a triangulation and a manifold, you cannot decides whether it triangulates it.
 In the second case, you say that it is not possible to decide whether a triangulation triangulates some manifold (without specifying what it is, neither as input nor output).
@@
     which requires $m = M$.
-    \todo{TCF: I don’t understand why XM couldn’t be a topological n-ball.}
+    % TODO {TCF: I don't understand why XM couldn't be a topological n-ball.}
     On the other hand, 
@@
     \end{align*}
-    which is the identity along $\Gamma_2$. \todo{Include a picture of the situation?}
+    which is the identity along $\Gamma_2$. 
+    \todo{Include a picture of the situation?}
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
             = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
+            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
             \leq 
@@
             = 
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
+            \frac{ \vecnorm{h_2}^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, x \rangle }{ \vecnorm{ h_1 }^{2} }
             x
@@
         This is defined away from the hyperplane orthogonal to $h_2$.
-        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
+        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \vecnorm{ h_1 }^{2}$, then $\langle F(x), h_2 \rangle = \vecnorm{ h_2 }^{2}$.
         That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
@@
             &=
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
+            \frac{ \vecnorm{ h_2 }^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \vecnorm{ h_1 }^{2} }
             x
@@
             \\&=
-            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
+            \frac{ \langle h_2, h_2 \rangle }{ \vecnorm{ h_2 } \vecnorm{x} \cos(\alpha_2) }
             \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
@@
             +
-            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
+            \frac{ \vecnorm{ h_2 }^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \vecnorm{ h_1 }^{2} }
             x
@@
             +
-            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
+            \frac{ \vecnorm{ h_2 } }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \langle \hat h_1, y \rangle }{ \vecnorm{ h_1 } }
             \hat x
             \\&=
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
+            \frac{ \vecnorm{ h_2 } }{ \cos(\alpha_2) }
             \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
-            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
+            \frac{ \cos(\alpha_1) }{ \vecnorm{ h_1 } }
             +
-            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
-            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
+            \frac{ \vecnorm{ h_2 } }{ \cos(\alpha_2) }
+            \frac{ \langle \hat h_1, y \rangle }{ \vecnorm{ h_1 } }
             \hat x
             \\&=
-            \frac{ \| h_2 \| }{ \| h_1 \| }
+            \frac{ \vecnorm{ h_2 } }{ \vecnorm{ h_1 } }
             \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
@@
         \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
+            \sigma_{\max} = \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } + \frac{ \vecnorm{a} }{2},
             \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
-        \end{align*}
-        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\|a\|$.
+            \sigma_{\min} = \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } - \frac{ \vecnorm{a} }{2}.     
+        \end{align*}
+        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\vecnorm{a}$.
 %         We thus consider the upper bound 
 %         \begin{align*}
-%             \|a\| 
+%             \vecnorm{a} 
 %             \leq 
@@
             = 
-            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
-            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
+            \frac{ \vecnorm{ h_K }^{2} }{ \langle h_K, x \rangle }
+            \frac{ \langle h_{{G}}, x \rangle }{ \vecnorm{ h_{{G}} }^{2} }
             x
@@
             = 
-            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
-            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
+            \frac{ \vecnorm{ h_{{G}} }^{2} }{ \langle h_{{G}}, z \rangle }
+            \frac{ \langle h_K, z \rangle }{ \vecnorm{ h_K }^{2} }
             z,
@@
             = 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
             \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
+                \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } + \frac{ \vecnorm{a} }{2}
             \right)
@@
             = 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
+            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_K } }
             \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
             \left( 
-                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
+                \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } - \frac{ \vecnorm{a} }{2}
             \right)^{-1},
@@
             =
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
@@
             \left( 
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
@@
             \left( 
-            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
+            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_{K} } }
             \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
@@
         \begin{align*}
-            \frac{ \| h_K \| }{ \| h_{{G}} \| }
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
             = 
-            \frac{ \| x_K \| }{ \| x_{{G}} \| }
-            \leq 
-            \frac{ \| x_K \| }{ \| h_{{G}} \| }
-            \leq 
-            \frac{ \diam(K) }{ \| h_{{G}} \| }
+            \frac{ \vecnorm{ x_K } }{ \vecnorm{ x_{{G}} } }
+            \leq 
+            \frac{ \vecnorm{ x_K } }{ \vecnorm{ h_{{G}} } }
+            \leq 
+            \frac{ \diam(K) }{ \vecnorm{ h_{{G}} } }
             ,
             \qquad 
-            \frac{ \| h_{{G}} \| }{ \| h_K \| }
+            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_K } }
             \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
             = 
-            \frac{ \| x_{G} \| }{ \| x_{K} \| }
-            \leq 
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
-            \leq 
-            \frac{ \diam(G) }{ \| h_{K} \| }
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ x_{K} } }
+            \leq 
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{K} } }
+            \leq 
+            \frac{ \diam(G) }{ \vecnorm{ h_{K} } }
             .
@@
 %         \begin{align*}
-%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
+%             \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
 %             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
 %             \leq 
-%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
+%             \frac{ \vecnorm{ x_K } }{ \vecnorm{ x_{{G}} } }
 %             .
@@
         We need further details to complete our estimates. 
-        We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
+        We know that $\vecnorm{ x_K } \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
 The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(\ell+1)^{-1}$.
-        That estimates the quotient $\| x_K \| / \| h_K \|$. 
+        That estimates the quotient $\vecnorm{ x_K } / \vecnorm{ h_K }$. 
         % 
-        In order to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
+        In order to estimate $\vecnorm{ h_{G} }$, we first notice the case $G \in \calG$ implies $\vecnorm{ h_{G} } \leq \diam(G) \leq \diam(T)$. 
         In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
@@
         The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows again that $\|x_{G}\| \leq \diam(T)$. 
+        It follows again that $\vecnorm{ h_{G} } \leq \diam(T)$. 
         % 
-        It remains to find a lower bound for $\| h_{G} \|$.
+        It remains to find a lower bound for $\vecnorm{ h_{G} }$.
         Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
@@
 The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        %         In oder to estimate $\vecnorm{ h_{G} }$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
         %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
+        %         It follows that $\vecnorm{ x_{G} } \leq \diam(T)$. 
         %         
@@
 %         \begin{align*}
-%             \frac{\diam(T)}{ \|h_{F}\|}
+%             \frac{\diam(T)}{ \vecnorm{ h_{F} }}
 %             \leq  
@@
         \begin{align*}
-            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
+            \frac{ \vecnorm{ x_{K} } }{ \vecnorm{ h_{{G}} } }
             &\leq 
             (\ell+1)\mu_{T,\ell}
-            \frac{ \diam(K) }{ \| h_{T} \| }
+            \frac{ \diam(K) }{ \vecnorm{ h_{T} } }
             \leq 
@@
             \diameterratio(\calT)
-            \frac{ \diam(T) }{ \| h_{T} \| }
+            \frac{ \diam(T) }{ \vecnorm{ h_{T} } }
             \leq 
@@
             \\
-            \frac{ \| x_{G} \| }{ \| h_{K} \| }
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{K} } }
             &\leq 
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(T) }{ \| h_{K} \| }
+            \frac{ \diam(T) }{ \vecnorm{ h_{K} } }
             \leq 
@@
             \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K) }{ \| h_{K} \| }
+            \frac{ \diam(K) }{ \vecnorm{ h_{K} } }
             \leq 
@@
         \begin{gather*}
-            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
+            \frac{ \vecnorm{ x_{K} } }{ \vecnorm{ h_{{K}} } }
             \leq 
@@
             \qquad 
-            \frac{ \| x_{G} \| }{ \| h_{G} \| }
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{G} } }
             \leq 
@@
         \begin{align*}
-            \|a\|
+            \vecnorm{a}
             = 
             \left\|
-            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
+            \frac{\vecnorm{ x_{G} }}{\vecnorm{ h_{G} }} \hat h_{{G}} 
             - 
-            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
+            \frac{\vecnorm{ x_{K} }}{\vecnorm{ h_{K} }} \hat h_K
             \right\|
@@
             \leq 
-            \frac{\|x_{G}\|}{\|h_{G}\|} 
+            \frac{\vecnorm{ x_{G} }}{\vecnorm{ h_{G} }} 
             + 
-            \frac{\|x_{K}\|}{\|h_{K}\|} 
+            \frac{\vecnorm{ x_{K} }}{\vecnorm{ h_{K} }} 
             % \\&
@@
         Let $\rho \in (0,1]$, yet to be determined. 
-        We define $y = - \rho z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho \|z_{S'}\|$. 
-        Henceforth, we assume $\rho \leq \varrho / \|z_{S'}\|$ so that $y \in \overline{\Ball_{\varrho}(z_S)}$.  
+        We define $y = - \rho z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho \vecnorm{ z_{S'} }$. 
+        Henceforth, we assume $\rho \leq \varrho / \vecnorm{ z_{S'} }$ so that $y \in \overline{\Ball_{\varrho}(z_S)}$.  
         By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,

### 2025-01-15 main.tex
all Theo's remarks

@@
 We gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.
-% \todo{Settle the subscripts of the vector norm.}
+% DONE {Settle the subscripts of the vector norm.}
 % TODO {Replace the constant Ceins and Czwei by the square root of n immediately.}
@@
     The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
-    by the topological Schoenflies theorem. \todo{reference}
+    by the topological Schoenflies theorem~\cite{Moise1977geometric}
     It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
@@
     By removing any triangle $S \in \calS$, we obtain a triangulation $\calT$ of a $2$-\disk.
-    Any shelling of that \disk\ \todo{$\calT$} can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
-    So it remains to show that any triangulation $\calT$ of the two-dimensional \disk\ is shellable. 
+    Any shelling of that triangulation $\calT$ can be extended to a shelling of $\calS$ by re-inserting the first triangle $S$.
+    So it remains to show that any triangulation $\calT$ of a two-dimensional \disk\ is shellable. 
     We will construct the shelling in reverse.
@@
     which is the identity along $\Gamma_2$. 
-    \todo{Include a picture of the situation?}
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \end{align*}
-    \todo{TCF: Should $\sigma_n$ be $\sigma_n^{-1}$ in the second line of both statements?}
+    % DONE {TCF: Should $\sigma_n$ be $\sigma_n^{-1}$ in the second line of both statements?}
     \end{enumerate}
@@
 
-        \todo{Picture?}
-
         % TODO Check that $\calD^\ast$ is a triangulation
@@
         Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
+
+        \begin{figure}[t]
+            \centering
+            \begin{tabular}{ccc}
+            \begin{tikzpicture}
+                % [line join=bevel,z={( 3.85mm, -3.85mm)}]
+                [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]
+
+                \coordinate (O) at (  0.0,  0.0, 0.0);
+                \coordinate (A) at (  1.0,  0.0, 0.0);
+                \coordinate (B) at (  0.3,  1.0, 0.0);
+                \coordinate (C) at ( -0.6,  0.8, 0.0);
+                \coordinate (D) at ( -0.6, -0.7, 0.0);
+                \coordinate (E) at (  0.3, -1.0, 0.0);
+                \coordinate (F) at (  0.3, -1.0, 0.0);
+
+                \fill[gray!30] (A) -- (B) -- (O) -- cycle;
+
+                \node at (-0.15, -0.5) {$A$};
+                \node at (0.4, 0.35) {$T$};
+                \node at (0.45, -0.2) {$\Gamma_1$};
+                \node at (-0.75, 0) {$\Gamma_2$};
+
+                \draw[dotted] (O) -- (A); % THIS ONE 
+                \draw[dotted] (O) -- (B); % THIS ONE 
+                \draw[] (A) -- (B); % THIS ONE 
+%                 \draw (O) -- (C);
+%                 \draw (O) -- (D);
+%                 \draw (O) -- (E);
+                \draw[line width=0.2em] (B) -- (C) -- (D) -- (E) -- (A);
+            \end{tikzpicture}%
+            \end{tabular} 
+            \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.}\label{figure:geometricconstruction}
+        \end{figure}
 
@@
 The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        %         In oder to estimate $\vecnorm{ h_{G} }$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        %         In oder to estimate $\vecnorm{ x_{G} }$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
         %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
@@
     \end{align*}
-    \todo{Double check the constant}
+    % DONE {Double check the constant}
 \end{lemma}
@@
     In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $\ell+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = 2^{n-\ell}/n!$
+    We see that $\vol(\widetilde \Makoto) = 2^{n-\ell} \vol(\Delta^n) = 2^{n-\ell}/n!$
 
@@
     \end{align*}
-    The analysis for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc}, imply 
-    the existence of $\mathring w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
+    By the analysis for the Bogovski\u{\i} potential operators, Theorem~\ref{theorem:bogovpoinc}, 
+    there exists $\mathring w \in W^{p}_{0}\Lambda^{k}(\widetilde \Makoto)$
     with $\cartan \mathring w = \cartan \tilde u$ satisfying the bounds 
@@
         &\leq 
-        C_{{\PF},\Poinc,k,\widetilde \Makoto,p}
+        C_{{\PF},\Bogov,k,\widetilde \Makoto,p}
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
@@
         \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
+        .
+    \end{align*}
+    Here,
+    \begin{align*}
+        C_{{\PF},\Bogov,k,\widetilde \Makoto,p} 
+        &
+        = 
+        C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\widetilde \Makoto)^{n}}{\vol(\widetilde \Makoto)} \diam(\widetilde \Makoto)
+        \\&
+        = 
+        C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{2^{n}}{2^{n-\ell}/n!} 2
+        = 
+        C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \cdot n! 2^{\ell+1} 
         .

### 2025-01-15 main.tex
further TODOs done

@@
 These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem, 
-% TODO {[TCF: I believe this is often refered to as the Tartare-Petree theorem]}
+% DONT {[TCF: I believe this is often refered to as the Tartare-Petree theorem]}
 and thus the resulting constants are not explicitly computable.
@@
 The method is known in the finite element literature~\cite{ern2021finite}. 
-% TODO {[TCF: Could you reference a particular theorem or chapter?]} 
+% DONE {[TCF: Could you reference a particular theorem or chapter?]} 
 It was previously used in the context of finite volume methods~\cite{Eym_Gal_Her_00}, broken (weakly continuous) Sobolev spaces~\cite{vohralik2005discrete}, or more recently in continuous--discrete comparison results~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24,  Voh_loc_glob_H1_24}.
@@
 
-% TODO: Figure out whether to use the following paragraph.
+% DONE: Figure out whether to use the following paragraph.
 % Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, such as the curl and divergence, over triangulated domains. 
@@
 
-% TODO: check whether introduction is readable
+% DONE: check whether introduction is readable
 % In the gradient case of Section~\ref{subsection:intro_grad}, it is possible to perform a simple pass through the triangulation, 
@@
 
-    % TODO: Change colors to grey scale
-
     \coordinate (O) at (  0.0,  0.0, 0.0);
@@
 \caption{From left to right: local patches around a vertex, and edge, and a triangle.
-The local patch of a full-dimensional simplex is the only the simplex itself (and its subsimplices).}\label{figure:patches}
+The local patch of any full-dimensional simplex only consists of that simplex itself (and its subsimplices).}\label{figure:patches}
 \end{figure}
@@
     Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
-    \cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here.
+    {\cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here in the final version or figure out how to fix the display in the editor.
     \cite[Definition~11.2]{ern2021finite}). 
@@
 % DONE {Settle the subscripts of the vector norm.}
-% TODO {Replace the constant Ceins and Czwei by the square root of n immediately.}
+% DONT {Replace the constant Ceins and Czwei by the square root of n immediately.}
 
@@
 
-% We discuss the Sobolev spaces of vector calculus and exterior calculus 
-% with particular emphasis on their transformation behavior. 
-% We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
-% Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.
-% TODO: Fuse these two paragraphs
-
-We review in this section the Sobolev spaces of vector and exterior calculus and their transformation behavior.
+We review in this section the Sobolev spaces of vector and exterior calculus with particular emphasis on their transformation behavior. 
 We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for background material on Sobolev vector analysis and to Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth} for exterior algebra and exterior products.
@@
 
-% \begin{lemma} % TODO: possibly useful
+% \begin{lemma} % DONT: possibly useful
 %     Let $1 \leq p < \infty$. A sequence converges to $u \in L^{p}$ if and only if it converges locally by measure and the $L^{p}$ norms converge.
@@
     then the $n$-simplices in $\patch_{\calT}(V)$ are in correspondence to the $(n-1)$-simplices in $\carapace_{\calT}(V)$.
-    Hence $\patch_{\calT}(V)$, a triangulation of dimension $n-1$, is face-connected if and only if $\carapace_{\calT}(V)$, a triangulation of dimension $n-1$, is face-connected.
+    Hence, $\patch_{\calT}(V)$, a triangulation of dimension $n-1$, is face-connected if and only if $\carapace_{\calT}(V)$, a triangulation of dimension $n-1$, is face-connected.
     % then any vertex star in any $(n+1)$-dimensional manifold triangulation is already face-connected if all simplicial $n$-balls and $n$-spheres are face-connected.
@@
     We prove this claim by induction. 
-    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. Let $1 \leq m \leq M$ and suppose that 
+    Certainly, if $\calT$ contains only one single $n$-simplex, then it is a shellable triangulation of a topological $n$-ball. 
+    Next, let $1 \leq m \leq M$ and suppose that
     \begin{align*}
@@
     \end{align*}
-    is a topological $n$-ball. Let $T_{m}$ is the next $n$-simplex in the shelling.
+    is already known to be a topological $n$-ball. Let $T_{m}$ be the next $n$-simplex in the shelling.
     By definition, $\Gamma_{m} := X_{m-1} \cap T_{m}$ is a submanifold of $\partial T_{m}$,
-    and it is triangulated by some faces of $T_{m}$ and their subsimplices.
+    triangulated by some faces of $T_{m}$ and their subsimplices.
 
@@
 
-    On the one hand, 
-    if $\Gamma_{m}$ is the entire boundary of $T_{m}$, 
-    then it must also be the boundary of the topological $n$-ball $X_{m-1}$. 
-    Hence, $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
-    which requires $m = M$.
-    % TODO {TCF: I don't understand why XM couldn't be a topological n-ball.}
+    On the one hand, if $\Gamma_{m}$ is the entire boundary of $T_{m}$, then it is a topological sphere of dimension $n-1$. 
+    Since $\Gamma_{m}$ is a submanifold of the boundary of $X_{m-1}$, which by induction assumption is also a topological sphere of dimension $n-1$,
+    we conclude that $\Gamma_{m}$ is the whole boundary of $X_{m}$.
+    By basic geometric topology, $X_{m}$ is a topological $n$-sphere, and $T_{m}$ can only be the last simplex in the shelling, $m=M$.
+%     then it must also be the boundary of $X_{m-1}$, which is a topological $n$-ball by the induction assumption. 
+%     Hence, $\Gamma_{m} = \partial X_{m-1}$ is a topological sphere of dimension $n-1$, 
+%     which requires $\partial X_{m-1} \cap \partial T_{m}$ by assumption. 
+%     Hence, $X_{m-1} \cup T_{m}$ must be a topological $n$-sphere and thus a manifold without boundary, 
+%     which requires $m = M$.
+    % DONE{TCF: I don't understand why XM couldn't be a topological n-ball.}
     On the other hand, 
@@
         % Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $\underlying{\calK}$. 
-        % \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
+        % \mwl{DONE: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
 
@@
         The singular values $\sigma_{\max}(\Theta,G) \geq 1$ and $\sigma_{\min}(\Theta,G) \leq 1$ is monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
-Hence they must the extremal maximal singular values of $\Jacobian\Theta_{|G}$.
+Hence, they must the extremal maximal singular values of $\Jacobian\Theta_{|G}$.
         It is evident that $\rho = \vol(G^{c}) / \vol(G)$.
@@
         since $S'$ has dimension $n-\ell-1$. 
-        The height of $F_{z}$ in $T'$ is just the height of the its opposing vertex, which lies in $S'$,
+        The height of the face $F_{z}$ in $T'$ is just the height of its opposing vertex, which lies in $S'$,
         and which equals the height of that vertex in $T$.

### 2025-01-15 draft.tex
fix; clean up face reflection

@@
-\documentclass[a4paper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
 \usepackage{fullpage}
-\usepackage{hyperref}         % For hypertext links
-
+% \usepackage[margin=0.1cm]{geometry}
 \input{header}
 
+\usepackage{xcolor}          % 
+\usepackage{comment}          % 
+\usepackage[colorlinks=true]{hyperref}         % For hypertext links
+% Make the hyperlinks look similar to arXiv's
+\hypersetup{
+    colorlinks=true,
+    linkcolor=Maroon,    % Color of internal links (sections)
+    citecolor=red,    % Color of citations
+    urlcolor=blue,     % Color for URLs
+    urlbordercolor={1 1 1},
+    pdfborder={0.5 0.5 0}  % Removes the border around the links
+}
+\usepackage{tikz-3dplot}      % 3d plots 
+\usepackage{enumitem}
+\setitemize[1]{left=0.0cm}
+
+% Added by MV 
+\usepackage{bm} % preferred version of bold symbols
+\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
+% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
+% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
+% \newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
+\setlength{\marginparwidth}{2cm}
+
+\newcommand\cye[1]{%
+\protect\leavevmode
+\begingroup
+    \color{blue}%
+    #1%
+\endgroup
+}
+% \color{red!35!yellow}
+
+\newcommand{\mwl}[1]{{\color{red}#1}}
+\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
+\newcommand{\disk}{\cye{ball}}
+\newcommand{\todo}[1]{{\color{RedOrange}\textbf{#1}}}
+
+% LTeX: enabled=false
+% Title, authors, and affiliations
+% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
+% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
+
+\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
+\author{
+    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
+    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
+    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
+}
+\date{}
+% LTeX: enabled=true
+
 \begin{document}
+
+\tableofcontents
+
+\section{Draft of the Reflection along faces in one of the first sections}
+
+\begin{proof}
+    %     This implies the determinant identity and estimate 
+%     \begin{align*}
+%         \det( \Jacobian \Xi ) 
+%         = 
+%         \frac 1 4 \left( (1+a)^2 - (1-a)^2 \right) 
+%         &
+%         = 
+%         a
+%         \leq 
+%         \aspectratio(T_{1}) \aspectratio(T_{2}) 
+%         .
+%     \end{align*}
+%     % Now we see that if $a \leq 1$, then $\sigma_{+} \leq 1 + c$, and if $a \geq 1$, then $\sigma_{+} \leq a + c$.
+%     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
+%     Since $\Xi(\hat h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
+%     \begin{align*}
+%         \vecnorm{ \Xi(x) - \Xi(x') }
+%         \leq  
+%         \vecnorm{ b - b' } + | \alpha - \alpha' | \cdot \vecnorm{ z_2 }
+%         \leq  
+%         \vecnorm{ b - b' } + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \vecnorm{ \hat h_0 }
+%         \leq 
+%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \vecnorm{ x-x' }
+%         .
+%     \end{align*}
+    \color{blue}
+    \color{red}
+    The linear mapping $\Xi$ takes the form 
+    % Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
+    \begin{align*}
+        \Xi(x) 
+        = 
+        x 
+        - \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_1
+        + \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_2
+        ,
+        \qquad 
+        x \in \bbR^{n}
+        .
+    \end{align*}
+    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
+    By the Xu-Zikanatov estimate~\cite{xu2003some},
+    \begin{align*}
+        % \matnorm{ \Jacobian \Xi }
+        \sigma_{+} 
+        \leq 
+        \frac{ \diam(T_1) }{ \height(T_1) }
+        +
+        \frac{ \diam(T_2) }{ \height(T_1) }
+        \leq 
+        \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
+        .
+    \end{align*}
+    Analogous upper bound holds for $\sigma^{-1}_{-}$.
+%     \begin{align}
+%         \sigma_{-}^{-1} \leq \left( 1 + \aspectratio(T_1) \right) \aspectratio(T_2)
+%     \end{align}
+% \begin{comment}
+    \color{Mulberry}
+    \mwl{Tighter estimate via geometry}
+    Matrix inverse lemma:
+    \begin{align*}
+        A ( A + (z_2-z_1) e_1^t )^{-1}
+        =
+        \Id
+        - 
+        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
+        (z_2-z_1) e_1^t \cdot A^{-1}
+        =
+        \Id
+        - 
+        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
+        (z_2-z_1) e_1^t \cdot A^{-1}
+        .
+    \end{align*}
+    Putting in a multiple of $\alpha z_1$, we find 
+    \begin{align*}
+        \alpha z_1
+        -
+        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
+        (z_2-z_1) 
+        .
+    \end{align*}
+
+    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
+    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
+    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
+    We can write 
+    \begin{align*}
+        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
+    \end{align*}
+    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
+    \begin{align*}
+        A = 
+        \begin{pmatrix}
+            b_1/a_1 & 0 & 0
+            \\
+            (b_2-a_2)/a_1 & 1 & 0
+            \\
+            b_3/a_1 & 0 & 1
+        \end{pmatrix}
+        =:
+        \begin{pmatrix}
+            c_1 & 0 & 0
+            \\
+            c_2 & 1 & 0
+            \\
+            c_3 & 0 & 1
+        \end{pmatrix}
+    \end{align*}
+    Its singular values are $1$ and 
+    \begin{align*}
+        \sigma_{\max}
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            +
+            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
+        }
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            +
+            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        }
+        =
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+        +
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        =
+        \frac{1}{2}
+        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
+        +
+        \frac{1}{2}
+        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
+        \leq 
+        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
+        .
+    \end{align*}
+    \begin{align*}
+        \sigma_{\max}
+        =
+        \frac{1}{\sqrt 2}
+        \sqrt{
+            1 + c_1^2 + c_2^2 + c_3^2 
+            -
+            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
+        }
+        =
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
+        -
+        \frac{1}{2}
+        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
+        .
+    \end{align*}
+
+    \begin{align*}
+        \sigma_{\max}
+        &= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            } }
+        \\&= 
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+            }
+        +
+        \frac{1}{\sqrt 2}
+        \sqrt{ 
+            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        +
+        \frac{1}{2}
+        \sqrt{ 
+            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
+            }
+        ,
+        \\
+        \sigma_{\min}
+        &=
+        \frac{1}{\sqrt 2}
+        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
+        \\&= 
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
+            }
+        -
+        \frac{1}{2}
+        \sqrt{ 
+            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
+            }
+        .
+    \end{align*}
+    It follows that 
+    \begin{align*}
+        \det \Jacobian\Xi
+        &=
+        \frac{1}{4}
+        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
+        +
+        \frac{1}{4}
+        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
+        \\
+        \frac{1}{2} + \frac{1}{2} 
+        .
+    \end{align*}
+    Matrix determinant lemma:
+    \begin{align*}
+        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
+        =
+        \left( e_{n} A^{-1} z_2 \right) \det(A)
+        =
+        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
+        .
+    \end{align*}
+% \end{comment}
+\end{proof}
+
+\section{Material}
 
@@
     It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
-    where $\Minako_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
+    where $\frakM_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.
 
@@
     \begin{align} \label{equation:w''_ext_der}
-        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\Minako_{m-1}}),
+        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\frakM_{m-1}}),
     \end{align}
-    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
+    where $\Xi_{m} : T_{m} \rightarrow \frakM_{m-1}$ is the reflection mapping
     as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
@@
         \leq  
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        + 
-        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        .
-    \end{align*}
-    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) = 0$, we have
-    \begin{align*}
-        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})} 
+        \| \Xi_{m}^{\ast}(w_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
+        + 
+        \| u - \Xi_{m}^{\ast}(u_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\frakM_{m-1}})) = 0$, we have
+    \begin{align*}
+        \| u - \Xi_{m}^{\ast}(u_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})} 
         &
@@
         C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
-        + \| \cartan (\Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})} )
+        + \| \cartan (\Xi_{m}^{\ast}(u_{|\frakM_{m-1}})) \|_{L^{p}(T_{m})} )
         .
@@
     \begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \Xi_{m}^{\ast}(w_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
+        &\leq 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(\Minako_{m-1})}
+        \| w \|_{L^{p}(\frakM_{m-1})}
         ,
         \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
-        &\leq 
-        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\frakM_{m-1}})) \|_{L^{p}(T_{m})}
+        &\leq 
+        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
+        \| \cartan u \|_{L^{p}(\frakM_{m-1})}
         ,
@@
 	\begin{align*}
-        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \Xi_{m}^{\ast}(w_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
-        \| w \|_{L^{p}(\Minako_{m-1})}
+        \| w \|_{L^{p}(\frakM_{m-1})}
         ,
         \\
-        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
-        &\leq 
-        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
+        \| \cartan (\Xi_{m}^{\ast}(w_{|\frakM_{m-1}})) \|_{L^{p}(T_{m})}
+        &\leq 
+        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
         \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
-        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
+        \| \cartan u \|_{L^{p}(\frakM_{m-1})}
         ,
@@
 
+\begin{itemize}
         \item 
@@
         \color{black}
+\item 
+\end{itemize}
 

### 2025-01-15 main.tex
fix; clean up face reflection

@@
     Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
-    {\cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here in the final version or figure out how to fix the display in the editor.
+    \cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here in the final version or figure out how to fix the display in the editor.
     \cite[Definition~11.2]{ern2021finite}). 
@@
         \det(\Jacobian \Xi)
-        &\leq 
-        \frac{ \diam(T_1) }{ \diam(T_2) } \aspectratio(T_2)
+        &
+        =
+        \frac{ \vol(T_2) }{ \vol(T_1) }
+        \leq 
+        \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_1)
         .
@@
     The desired estimates are shown.
-%     This implies the determinant identity and estimate 
-%     \begin{align*}
-%         \det( \Jacobian \Xi ) 
-%         = 
-%         \frac 1 4 \left( (1+a)^2 - (1-a)^2 \right) 
-%         &
-%         = 
-%         a
-%         \leq 
-%         \aspectratio(T_{1}) \aspectratio(T_{2}) 
-%         .
-%     \end{align*}
-%     % Now we see that if $a \leq 1$, then $\sigma_{+} \leq 1 + c$, and if $a \geq 1$, then $\sigma_{+} \leq a + c$.
-%     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
-%     Since $\Xi(\hat h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
-%     \begin{align*}
-%         \vecnorm{ \Xi(x) - \Xi(x') }
-%         \leq  
-%         \vecnorm{ b - b' } + | \alpha - \alpha' | \cdot \vecnorm{ z_2 }
-%         \leq  
-%         \vecnorm{ b - b' } + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \vecnorm{ \hat h_0 }
-%         \leq 
-%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \vecnorm{ x-x' }
-%         .
-%     \end{align*}
-    \color{blue}
-    \color{red}
-    The linear mapping $\Xi$ takes the form 
-    % Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
-    \begin{align*}
-        \Xi(x) 
-        = 
-        x 
-        - \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_1
-        + \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_2
-        ,
-        \qquad 
-        x \in \bbR^{n}
-        .
-    \end{align*}
-    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
-    By the Xu-Zikanatov estimate~\cite{xu2003some},
-    \begin{align*}
-        % \matnorm{ \Jacobian \Xi }
-        \sigma_{+} 
-        \leq 
-        \frac{ \diam(T_1) }{ \height(T_1) }
-        +
-        \frac{ \diam(T_2) }{ \height(T_1) }
-        \leq 
-        \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
-        .
-    \end{align*}
-    Analogous upper bound holds for $\sigma^{-1}_{-}$.
-%     \begin{align}
-%         \sigma_{-}^{-1} \leq \left( 1 + \aspectratio(T_1) \right) \aspectratio(T_2)
-%     \end{align}
-% \begin{comment}
-    \color{Mulberry}
-    \mwl{Tighter estimate via geometry}
-    Matrix inverse lemma:
-    \begin{align*}
-        A ( A + (z_2-z_1) e_1^t )^{-1}
-        =
-        \Id
-        - 
-        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        =
-        \Id
-        - 
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) e_1^t \cdot A^{-1}
-        .
-    \end{align*}
-    Putting in a multiple of $\alpha z_1$, we find 
-    \begin{align*}
-        \alpha z_1
-        -
-        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
-        (z_2-z_1) 
-        .
-    \end{align*}
-
-    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
-    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
-    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
-    We can write 
-    \begin{align*}
-        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
-    \end{align*}
-    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
-    \begin{align*}
-        A = 
-        \begin{pmatrix}
-            b_1/a_1 & 0 & 0
-            \\
-            (b_2-a_2)/a_1 & 1 & 0
-            \\
-            b_3/a_1 & 0 & 1
-        \end{pmatrix}
-        =:
-        \begin{pmatrix}
-            c_1 & 0 & 0
-            \\
-            c_2 & 1 & 0
-            \\
-            c_3 & 0 & 1
-        \end{pmatrix}
-    \end{align*}
-    Its singular values are $1$ and 
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            +
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        +
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        =
-        \frac{1}{2}
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        +
-        \frac{1}{2}
-        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
-        \leq 
-        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
-        .
-    \end{align*}
-    \begin{align*}
-        \sigma_{\max}
-        =
-        \frac{1}{\sqrt 2}
-        \sqrt{
-            1 + c_1^2 + c_2^2 + c_3^2 
-            -
-            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
-        }
-        =
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
-        -
-        \frac{1}{2}
-        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
-        .
-    \end{align*}
-
-    \begin{align*}
-        \sigma_{\max}
-        &= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            } }
-        \\&= 
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-            }
-        +
-        \frac{1}{\sqrt 2}
-        \sqrt{ 
-            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        +
-        \frac{1}{2}
-        \sqrt{ 
-            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
-            }
-        ,
-        \\
-        \sigma_{\min}
-        &=
-        \frac{1}{\sqrt 2}
-        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
-        \\&= 
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
-            }
-        -
-        \frac{1}{2}
-        \sqrt{ 
-            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
-            }
-        .
-    \end{align*}
-    It follows that 
-    \begin{align*}
-        \det \Jacobian\Xi
-        &=
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
-        +
-        \frac{1}{4}
-        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
-        \\
-        \frac{1}{2} + \frac{1}{2} 
-        .
-    \end{align*}
-    Matrix determinant lemma:
-    \begin{align*}
-        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
-        =
-        \left( e_{n} A^{-1} z_2 \right) \det(A)
-        =
-        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
-        .
-    \end{align*}
-% \end{comment}
 \end{proof}

### 2025-01-15 draft.tex
clean up

@@
 \end{proof}
+
+\section{Alternative attempt at getting a Poincare constant estimate for the scalar potential}
+
+\color{green}
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        L^{\frac p q}
+        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+        \leq 
+        L^{\frac p q}
+        \sum_{m=0}^{M} 
+        \max_{ 0 \leq \ell \leq M }
+        C_{m,\ell}^{p} 
+        \cdot 
+        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+
+    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
+    Hence, 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \sum_{\ell=0}^{M} 
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+        \\&
+        \leq 
+        \max_{0 \leq \ell \leq M} \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \delta_{m,\ell} 
+        \right)
+        \cdot 
+        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        \\&
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)
+        \cdot 
+        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+        .
+    \end{align}
+    Now, if $q \leq p$, that is, $2 \leq p$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \left(
+            \sum_{\ell'=0}^{M}
+            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
+        \right)^{\frac 1 q}
+        .
+    \end{align}
+    Instead, if $p \leq q$, that is, $p \leq 2$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
+        .
+    \end{align}
+    So in any case, it is better than using the following Minkowski's inequality: 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
+        \\&
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
+        \| \nabla u \|_{L^{p}(\Omega)}
+        .
+    \end{align}
+
+\subsection{Failed uppr bound for potential operators}
+On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
+These do not depend on the eccentricity of the domain.
+
+We begin with the Poincar\'e operator. 
+By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
+\begin{align*}
+    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
+    &
+    \leq 
+    \diam(\Omega)^{p}
+    \vol(\Omega)^{-1}
+    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
+    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{0}^{1} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{0}^{1} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{\Omega} 
+    |u( z )|^{p}
+    \int_{0}^{1} 
+    \vol\left(\left\{ 
+        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
+    \right\}\right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \,dt \,dz 
+    .
+\end{align*}
+\color{red}
+A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
+\begin{align*}
+    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
+    &
+    \leq 
+    \diam(\Omega)^{p}
+    \vol(\Omega)^{-1}
+    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
+    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{1}^{\infty} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{1}^{\infty} 
+    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
+    \vol(t\Omega)^{-1}
+    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
+    \\&
+    = 
+    \diam(\Omega)^{p}
+    \int_{\Omega} 
+    |u( z )|^{p}
+    \int_{1}^{\infty} 
+    \vol\left(\left\{ 
+        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
+    \right\}\right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \,dt \,dz 
+    .
+\end{align*}
+\color{blue}
+We estimate 
+\begin{align*}
+    \int_{0}^{1}
+    \vol\left(\left\{ 
+        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
+    \right\}\right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \ dt
+    &
+    \leq 
+    \int_{0}^{1}
+    \min\left( 
+        \vol\left(\Omega\right), 
+        \vol\left( \tfrac{t}{1-t} \Omega \right) 
+    \right)
+    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
+    \ dt
+    \\&
+    \leq 
+    \int_{0}^{1}
+    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
+    t^{p(k-1)} 
+    \ dt
+    \\&
+    \leq 
+    \int_{0}^{1}
+    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
+    t^{k-1} 
+    \ dt
+    .
+\end{align*}
+The last integral is handled via the basic observations
+\begin{align*}
+    \int_{0}^{\frac 1 2} 
+    \frac{ t^{k-1} }{ (1-t)^{n} }
+    \ dt
+    \leq 
+    \int_{0}^{\frac 1 2} 
+    (1-t)^{-n+k-1}
+    \ dt
+    =
+    \int_{\frac 1 2}^{1} 
+    t^{-n+k-1}
+    \ dt
+    =
+    \begin{cases}
+        \ln(2)                 & \text{$n=k$}
+        \\
+        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
+    \end{cases}
+\end{align*}
+
+\subsection{Attempted proof for deformation-based estimate}
+
+\begin{proof}\color{blue}
+    We first fix some notation. 
+    Recall that for any $1 \leq m \leq M$, 
+    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
+    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
+    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
+    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
+
+    We introduce the deformation mapping $\Xi_{2,m} : \patch_{\calT}(S_m) \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
+    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{m-1} \setminus \partial T$.
+    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{m} \rightarrow X_{m-1}$ 
+    by letting it be the identity over $X_{m-1} \setminus A_{m-1}$.
+
+    For each $T \in \calT$ of dimension $n$, there exists a sequence $1 \leq m_{T,1},\dots,m_{T,K} \leq M$, for some $1 \leq K \leq M$,
+    such over the simplex $T$ we have the identity 
+    \begin{align*}
+        ...
+    \end{align*}
+\end{proof}
+
+\section{Attempted global upper bound: exterior derivative case}
+
+Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        L^{\frac p q}
+        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
+        \leq 
+        L^{\frac p q}
+        \sum_{m=0}^{M} 
+        \max_{ 0 \leq \ell \leq M }
+        C_{m,\ell}^{p} 
+        \cdot 
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+    Hence, 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \sum_{\ell=0}^{M} 
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \delta_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
+        \\&
+        \leq 
+        \max_{0 \leq \ell \leq M} \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \delta_{m,\ell} 
+        \right)
+        \cdot 
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        \\&
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)
+        \cdot 
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        .
+    \end{align}
+    Now, if $q \leq p$, that is, $2 \leq p$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \left(
+            \sum_{\ell'=0}^{M}
+            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
+        \right)^{\frac 1 q}
+        .
+    \end{align}
+    Instead, if $p \leq q$, that is, $p \leq 2$, then 
+    \begin{align}
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
+        .
+    \end{align}
+    So in any case, it is better than using the following Minkowski's inequality: 
+    \begin{align}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
+        \\&
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
+        \leq 
+        \sum_{\ell=0}^{M}
+        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        .
+    \end{align}
+
+\section{}
 

### 2025-01-15 main.tex
clean up

@@
     In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
-    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
-    % \begin{align*}
-        % \| w \|_{L^{p}(\Omega)}^{p}
-        % &
-        % \leq 
-        % \sum_{m=0}^{M}
-        % \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
-        % \leq 
-        % \sum_{m=0}^{M}
-        % L^{\frac p q}
-        % \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        % \leq 
-        % L^{\frac p q}
-        % \sum_{m=0}^{M} 
-        % \max_{ 0 \leq \ell \leq M }
-        % C_{m,\ell}^{p} 
-        % \cdot 
-        % \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        % ,
-    % \end{align*}
-
-    \color{green}Hence, 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \sum_{\ell=0}^{M} 
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-        \\&
-        \leq 
-        \max_{0 \leq \ell \leq M} \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \delta_{m,\ell} 
-        \right)
-        \cdot 
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        \\&
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)
-        \cdot 
-        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-        .
-    \end{align}
-    Now, if $q \leq p$, that is, $2 \leq p$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \left(
-            \sum_{\ell'=0}^{M}
-            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
-        \right)^{\frac 1 q}
-        .
-    \end{align}
-    Instead, if $p \leq q$, that is, $p \leq 2$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
-        .
-    \end{align}
-    So in any case, it is better than using the following Minkowski's inequality: 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
-        \\&
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
-        \| \nabla u \|_{L^{p}(\Omega)}
-        .
-    \end{align}
 \end{remark}
@@
 that is, the reconstructed potential has support contained within $\overline\Omega$.
-\\
-
-\color{blue}
+
 \subsection{Rewriting the potentials operators}
@@
 \end{align*}
-On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
-These do not depend on the eccentricity of the domain.
-
-We begin with the Poincar\'e operator. 
-By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
-\begin{align*}
-    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
-    &
-    \leq 
-    \diam(\Omega)^{p}
-    \vol(\Omega)^{-1}
-    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
-    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{0}^{1} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{0}^{1} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{\Omega} 
-    |u( z )|^{p}
-    \int_{0}^{1} 
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \,dt \,dz 
-    .
-\end{align*}
-\color{red}
-A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
-\begin{align*}
-    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
-    &
-    \leq 
-    \diam(\Omega)^{p}
-    \vol(\Omega)^{-1}
-    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
-    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{1}^{\infty} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{1}^{\infty} 
-    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
-    \vol(t\Omega)^{-1}
-    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
-    \\&
-    = 
-    \diam(\Omega)^{p}
-    \int_{\Omega} 
-    |u( z )|^{p}
-    \int_{1}^{\infty} 
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \,dt \,dz 
-    .
-\end{align*}
-\color{blue}
-We estimate 
-\begin{align*}
-    \int_{0}^{1}
-    \vol\left(\left\{ 
-        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
-    \right\}\right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \ dt
-    &
-    \leq 
-    \int_{0}^{1}
-    \min\left( 
-        \vol\left(\Omega\right), 
-        \vol\left( \tfrac{t}{1-t} \Omega \right) 
-    \right)
-    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
-    \ dt
-    \\&
-    \leq 
-    \int_{0}^{1}
-    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
-    t^{p(k-1)} 
-    \ dt
-    \\&
-    \leq 
-    \int_{0}^{1}
-    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
-    t^{k-1} 
-    \ dt
-    .
-\end{align*}
-The last integral is handled via the basic observations
-\begin{align*}
-    \int_{0}^{\frac 1 2} 
-    \frac{ t^{k-1} }{ (1-t)^{n} }
-    \ dt
-    \leq 
-    \int_{0}^{\frac 1 2} 
-    (1-t)^{-n+k-1}
-    \ dt
-    =
-    \int_{\frac 1 2}^{1} 
-    t^{-n+k-1}
-    \ dt
-    =
-    \begin{cases}
-        \ln(2)                 & \text{$n=k$}
-        \\
-        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
-    \end{cases}
-\end{align*}
 
 \subsection{Interaction of potentials with the exterior derivative}
-\color{black}
+
 We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
@@
 We give detailed estimates for the singular values of their Jacobians.
+
+\begin{figure}[t]
+    \centering
+    \begin{tabular}{ccc}
+    \begin{tikzpicture}
+        % [line join=bevel,z={( 3.85mm, -3.85mm)}]
+        [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]
+
+        \coordinate (O) at (  0.0,  0.0, 0.0);
+        \coordinate (A) at (  1.0,  0.0, 0.0);
+        \coordinate (B) at (  0.3,  1.0, 0.0);
+        \coordinate (C) at ( -0.6,  0.8, 0.0);
+        \coordinate (D) at ( -0.6, -0.7, 0.0);
+        \coordinate (E) at (  0.3, -1.0, 0.0);
+        \coordinate (F) at (  0.3, -1.0, 0.0);
+
+        \fill[gray!30] (A) -- (B) -- (O) -- cycle;
+
+        \node at (-0.15, -0.5) {$A$};
+        \node at (0.4, 0.35) {$T$};
+        \node at (0.45, -0.2) {$\Gamma_1$};
+        \node at (-0.75, 0) {$\Gamma_2$};
+
+        \draw[dotted] (O) -- (A); % THIS ONE 
+        \draw[dotted] (O) -- (B); % THIS ONE 
+        \draw[] (A) -- (B); % THIS ONE 
+%                 \draw (O) -- (C);
+%                 \draw (O) -- (D);
+%                 \draw (O) -- (E);
+        \draw[line width=0.2em] (B) -- (C) -- (D) -- (E) -- (A);
+    \end{tikzpicture}%
+    \end{tabular} 
+    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.}\label{figure:geometricconstruction}
+\end{figure}
 
@@
         Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
-
-        \begin{figure}[t]
-            \centering
-            \begin{tabular}{ccc}
-            \begin{tikzpicture}
-                % [line join=bevel,z={( 3.85mm, -3.85mm)}]
-                [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]
-
-                \coordinate (O) at (  0.0,  0.0, 0.0);
-                \coordinate (A) at (  1.0,  0.0, 0.0);
-                \coordinate (B) at (  0.3,  1.0, 0.0);
-                \coordinate (C) at ( -0.6,  0.8, 0.0);
-                \coordinate (D) at ( -0.6, -0.7, 0.0);
-                \coordinate (E) at (  0.3, -1.0, 0.0);
-                \coordinate (F) at (  0.3, -1.0, 0.0);
-
-                \fill[gray!30] (A) -- (B) -- (O) -- cycle;
-
-                \node at (-0.15, -0.5) {$A$};
-                \node at (0.4, 0.35) {$T$};
-                \node at (0.45, -0.2) {$\Gamma_1$};
-                \node at (-0.75, 0) {$\Gamma_2$};
-
-                \draw[dotted] (O) -- (A); % THIS ONE 
-                \draw[dotted] (O) -- (B); % THIS ONE 
-                \draw[] (A) -- (B); % THIS ONE 
-%                 \draw (O) -- (C);
-%                 \draw (O) -- (D);
-%                 \draw (O) -- (E);
-                \draw[line width=0.2em] (B) -- (C) -- (D) -- (E) -- (A);
-            \end{tikzpicture}%
-            \end{tabular} 
-            \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.}\label{figure:geometricconstruction}
-        \end{figure}
 
@@
 
+\color{magenta}
+\begin{proposition}\label{proposition:starreflection}
+    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
+    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
+    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
+    and let 
+    \begin{align*}
+        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
+        \qquad 
+        {\Gamma_1} := \Makoto \cap T,
+        \qquad 
+        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
+    \end{align*}
+    The following holds, where the constants on the right-hand sides are as stated in the proof. 
+    \begin{enumerate}
+    \item 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{1} : T \rightarrow \Xi_{1}(T) \subseteq \Makoto 
+    \end{align*}
+    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
+    \begin{gather*}
+        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
+        \quad 
+        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
+    \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
+        \leq 
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
+        \leq 
+        \Csechstrafo{n}{k}{\ell}{p}(\calT).
+    \end{align*}
+
+    \item 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Xi_{2}( \underlying{\patch_{\calT}(S)} ) \subseteq \Makoto
+    \end{align*}
+    which is the identity along $\partial \Makoto \setminus \partial T$.
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
+    \begin{gather*}
+        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
+        \quad 
+        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
+    \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+        \leq 
+        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
+        \leq 
+        \Cachttrafo{n}{k}{\ell}{p}(\calT).
+    \end{align*}
+    \end{enumerate}
+\end{proposition}
+\begin{proof}
+    We derive the estimate in several steps. 
+    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
+    \begin{itemize}
+        \item 
+        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.
+
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
+        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
+        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$. 
+        We let $z_{S'}$ be the midpoint of $S'$.
+
+        We apply barycentric refinement to the simplex $S$ and then the complementary simplex $S'$.
+        This produces a triangulation $\calG$ of $\underlying{T}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.
+
+        \item 
+        There exists $\varrho > 0$ such that $\patch_{\calT}(S)$ is star-shaped with respect to the closed ball $\overline{\Ball_{\varrho}(z_S)}$.
+        We show that, if we let $\calK$ denote the simplicial complex obtained by barycentric refinement of $S$,
+        then the minimum height of $z_{S}$ in any $n$-simplex $K \in \calK$ is a possible choice of $\varrho$.
+        Given any $n$-simplex $K \in \calK$, the face $F \subseteq K$ opposite to $z_{S}$ is some boundary face of $\patch_{\calT}(S)$.
+        The height of $F$ in $K$ is the height of $F$ in the original simplex $T \in \patch_{\calT}(S)$ with $K \subseteq T$ scaled by $(\ell+1)^{-1}$.
+
+        Assuming that $\varrho > 0$ is at most the minimum height of $z_{S}$ in any $n$-simplex $K \in \calK$,
+        suppose that $z \in \Ball_{\varrho}(z_S)$. 
+        Let $x \in \patch_{\calT}(S)$ be in the interior of the local patch. 
+        If the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$, 
+        then $I$ passes through a boundary face $F \subseteq K$ of the local patch,
+        and $z$ and $x$ are contained on different sides of the hyperplane $H$ spanned by $F$. 
+        Then $x$ and $z_{S}$ are the same side of $H$, since otherwise the straight line segment from $x$ to $z_{S}$ would not be contained in the patch. 
+        This means, however, that $z_{S}$ and $z$ are on different sides of $H$, contradicting that $\varrho$ is at most the height of $z_S \in K$.
+
+        % TODO: prove this observation
+
+        \item 
+        Let $\rho \in (0,1]$, yet to be determined. 
+        We define $y = - \rho z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho \vecnorm{ z_{S'} }$. 
+        Henceforth, we assume $\rho \leq \varrho / \vecnorm{ z_{S'} }$ so that $y \in \overline{\Ball_{\varrho}(z_S)}$.  
+        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
+        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.
+
+        We define another triangulation $\calG^{c}$ as follows:
+        given any $n$-simplex $G \in \calG$, 
+        we replace its vertex $z_{S}'$ by the vertex $y$ at the opposite position,
+        thus obtaining a new $n$-simplex $G^{c}$. 
+        Indeed, that $\calG^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
+
+        We let the simplicial complex $\calG^\ast$ be the union of $\calG$ and $\calG^c$. 
+        By construction, all its $n$-simplices contain $z_{S}$ as a subsimplex, which is an inner vertex of that triangulation. 
+        In particular, $\calD^\ast$ is its own star around $z_{S}$.
+
+        \item 
+        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
+        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
+        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
+        be affine reference transformations
+        that agree on the vertices common to $G$ and $G^{c}$.
+        We then define the piecewise affine mapping 
+        \begin{align*}
+            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}.
+        \end{align*}
+        It follows that 
+        \begin{align*}
+            |\det( \Jacobian      \Theta_{|G} )| = \frac{\vol(G^{c})}{\vol(G)}
+            .
+        \end{align*}
+        We want to further characterize the singular values of this transform. 
+        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$,
+        that is, the vector pointing to $z_{S'}$ and standing orthogonally on the affine hull of the face $G$ that opposes $z_{S'}$
+        We verify that 
+        \begin{align*}
+            \Theta_{|G}(x) 
+            = 
+            x
+            - 
+            (1+\rho) \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+            \hat z_{S'}
+            .
+        \end{align*}
+        Indeed, the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
+        and when $x = z_{S'}$, then 
+        \begin{align*}
+            \Theta_{|G}\left( z_{S'} \right) 
+            &
+            =
+            z_{S'}
+            - 
+            (1+\rho) \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+            \\&
+            =
+            z_{S'}
+            - 
+            (1+\rho) \hat z_{S'} \vecnorm{z_{S'}}
+            =
+            z_{S'}
+            - 
+            (1+\rho) z_{S'} 
+            =
+            - \rho z_{S'} = y
+            .
+        \end{align*}
+        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
+        \begin{align*}
+            \Theta_{|G}( h_{z} ) 
+            &= 
+            h_{z}
+            - 
+            (1+\rho) \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            \\&
+            = 
+            h_{z}
+            - 
+            (1+\rho) \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            %\\&
+            = 
+            h_{z}
+            - 
+            (1+\rho) z_{S'}
+            %\\&
+            = 
+            - \rho h_{z}
+            - 
+            (1+\rho) b_{z}
+            .
+        \end{align*}
+        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
+        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
+        We study the singular values of the matrix 
+        \begin{align*}
+            M_{\Theta,G} 
+            := 
+            \begin{pmatrix}
+            -\rho                                         & 0
+            \\ 
+            -(1+\rho) \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            -\rho                 & 0
+            \\ 
+            -(1+\rho) \tan(\beta) & 1
+            \end{pmatrix}
+            .
+        \end{align*}
+        Its two singular values are:
+        \begin{align}
+            \sigma_{\max}(\Theta,G) 
+            := 
+            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } + \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
+            \label{math:theta_max}
+            ,
+            \\
+            \sigma_{\min}(\Theta,G) 
+            := 
+            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } - \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
+            \label{math:theta_min}
+            .
+        \end{align}
+        All other singular values of $\Jacobian\Theta_{|G}$ equal $1$. 
+        The singular values $\sigma_{\max}(\Theta,G) \geq 1$ and $\sigma_{\min}(\Theta,G) \leq 1$ is monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
+Hence, they must the extremal maximal singular values of $\Jacobian\Theta_{|G}$.
+        It is evident that $\rho = \vol(G^{c}) / \vol(G)$.
+
+        We develop explicit bounds for these singular values. 
+        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
+        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
+
+        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions: 
+        first at $z_{S}$, leading to some intermediate $n$-simplex $T'$, and then at $z_{S'}$, leading to $G \subseteq T'$. 
+        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$, which is some face of $T'$.
+        Now, the height of $F_{z}$ in $G$ is $(n-\ell)$-th of the height of $F_{z}$ in $T'$
+        since $S'$ has dimension $n-\ell-1$. 
+        The height of the face $F_{z}$ in $T'$ is just the height of its opposing vertex, which lies in $S'$,
+        and which equals the height of that vertex in $T$.
+%         which must be contained in some face of $T$ containing $S$. 
+%         The height vector $h_{z}$ is orthogonal to $F_{z}$. 
+%         Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$,
+%         pointing to some vertex of $S'$ and standing orthogonally on the face opposite to that vertex. 
+        Thus, 
+        \begin{align*}
+            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
+            = 
+            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
+            \leq 
+            (n-\ell) \aspectratio(T)
+%             = 
+%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
+%             \leq 
+%             \frac{ n-\ell }{n!}
+%             \cdot 
+%             \frac{ \diam(T)^{n} }{ \vol(T) }
+            .
+        \end{align*}
+        We abbreviate 
+        \begin{align}\label{math:upper_bound_for_theta}
+            \mu_{T,\ell} 
+            := 
+            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
+            + 
+            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
+            .
+        \end{align}
+        This establishes bounds on the singular values of the transformation. 
+        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
+        \begin{align}
+            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
+            \quad 
+            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
+            \quad 
+            \sigma_{n}(\Theta,x)^{-1} = \frac{ \sigma_{1}(\Theta,x) }{ \left| \det \Jacobian\Theta_{|G} \right| } \leq \mu_{T,\ell} / \rho.
+        \end{align}
+
+        \item 
+        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
+        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
+        We construct a bi-Lipschitz mapping 
+        \begin{align*}
+            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
+        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
+        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $y$ in $G^{c}$.
+        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
+        has a unique representation
+        \begin{align*}
+            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
+        \end{align*}
+        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+        \begin{align*}
+            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+            .
+        \end{align*}
+        Based on that observation, we define 
+        \begin{align*}
+            \Phi_{G}(x) 
+            &
+            := 
+            \mu x_{Q} + \frac{\rho}{\rho+1} \left( \lambda(x) - 1 \right) z_{S'}
+            \\&
+            = 
+            \mu x_{Q} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            \\&
+            = 
+            x - \frac{\rho+1}{\rho+1} \lambda(x) z_{S'} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            \\&
+            = 
+            x - \frac{1}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            \\&
+            = 
+            x - \frac{1}{\rho+1} \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} z_{S'} - \frac{\rho}{\rho+1} z_{S'}
+            .
+        \end{align*}
+        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
+        that satisfies the desired mapping properties. 
+        It remains to analyze its Jacobian and get explicit estimates for its singular values.
+
+        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
+        With that,
+        \begin{align*}
+            \Jacobian \Phi_{G}(x)
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},z_{S'}\rangle }  
+            \\
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle }  
+            \\
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ h_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \frac{ b_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
+            \\
+            &=
+            \Id 
+            - 
+            \frac{ 1 }{ 1 + \rho }  
+            \hat h_{z} \otimes \hat h_{z}^{t}
+            - 
+            \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho }  
+            \hat b_{z} \otimes \hat h_{z}^{t}
+            .
+        \end{align*}
+        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
+        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
+        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
+        Direct computation shows 
+        \begin{align}
+            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z}
+            ,
+            \qquad 
+            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac{ \rho }{ 1 + \rho } \hat h_{z} - \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho } \hat b_{z}
+            .
+        \end{align}
+        It remains to study the singular values of the matrix 
+        \begin{align*}
+            M_{\Phi,G} 
+            = 
+            \begin{pmatrix}
+                 \frac{ \rho }{ 1 + \rho }    & 0 
+                \\
+                -\frac{ \tan(\beta) }{1+\rho} & 1 
+            \end{pmatrix}
+            .
+        \end{align*}
+        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
+        we obtain the singular values 
+        \begin{align*}
+            \sigma_{\max}(\Phi,G) 
+            &
+            =
+            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } + \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
+            ,
+            \\
+            \sigma_{\min}(\Phi,G) 
+            &
+            =
+            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } - \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
+            .
+        \end{align*}
+        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
+        Notice that 
+        \begin{align*}
+            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2} = \frac{\rho}{1+\rho}.
+        \end{align*}
+        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        Similar as above, we use the upper bound 
+        \begin{align*}
+            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
+        \end{align*}
+        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
+        \begin{gather}
+            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
+            \leq 
+            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
+            + 
+            \frac{1}{2(1+\rho)} \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \label{math:phi_max}
+            ,
+            \\
+            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
+            \\
+            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
+            =
+            \frac{ \sigma_{1}(\Phi,x) }{ \left| \det \Jacobian\Phi \right| }
+            \leq 
+            % \frac{(1+\rho)^2}{\rho(1+\rho)}
+            % \frac{1}{2(1+\rho)} 
+            \frac{1}{2\rho}
+            \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
+            + 
+            % \frac{(1+\rho)^2}{\rho(1+\rho)}
+            % \frac{1}{2(1+\rho)} 
+            \frac{1}{2\rho}
+            \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \label{math:phi_min}
+            .
+        \end{gather}
+        This finishes the discussion of the transformation $\Phi$. 
+    \end{itemize}
+    Having shown all the desired estimates, and the proof is complete. 
+\end{proof}
+\color{black}
+
 \begin{remark}
@@
 
-\color{magenta}
-\begin{proposition}\label{proposition:starreflection}
-    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
-    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
-    and let 
-    \begin{align*}
-        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
-        \qquad 
-        {\Gamma_1} := \Makoto \cap T,
-        \qquad 
-        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
-    \end{align*}
-    The following holds, where the constants on the right-hand sides are as stated in the proof. 
-    \begin{enumerate}
-    \item 
-    There exists a bi-Lipschitz piecewise affine mapping
-    \begin{align*}
-        \Xi_{1} : T \rightarrow \Xi_{1}(T) \subseteq \Makoto 
-    \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
-    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
-    \begin{gather*}
-        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
-        \quad 
-        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
-        \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
-    \end{gather*}
-    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
-        \leq 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
-        \qquad 
-        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
-        \leq 
-        \Csechstrafo{n}{k}{\ell}{p}(\calT).
-    \end{align*}
-
-    \item 
-    There exists a bi-Lipschitz piecewise affine mapping
-    \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Xi_{2}( \underlying{\patch_{\calT}(S)} ) \subseteq \Makoto
-    \end{align*}
-    which is the identity along $\partial \Makoto \setminus \partial T$.
-    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
-    \begin{gather*}
-        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
-        \quad 
-        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
-        \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
-    \end{gather*}
-    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
-        \leq 
-        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
-        \qquad 
-        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
-        \leq 
-        \Cachttrafo{n}{k}{\ell}{p}(\calT).
-    \end{align*}
-    \end{enumerate}
-\end{proposition}
-\begin{proof}
-    We derive the estimate in several steps. 
-    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
-    \begin{itemize}
-        \item 
-        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.
-
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
-        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$. 
-        We let $z_{S'}$ be the midpoint of $S'$.
-
-        We apply barycentric refinement to the simplex $S$ and then the complementary simplex $S'$.
-        This produces a triangulation $\calG$ of $\underlying{T}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.
-
-        \item 
-        There exists $\varrho > 0$ such that $\patch_{\calT}(S)$ is star-shaped with respect to the closed ball $\overline{\Ball_{\varrho}(z_S)}$.
-        We show that, if we let $\calK$ denote the simplicial complex obtained by barycentric refinement of $S$,
-        then the minimum height of $z_{S}$ in any $n$-simplex $K \in \calK$ is a possible choice of $\varrho$.
-        Given any $n$-simplex $K \in \calK$, the face $F \subseteq K$ opposite to $z_{S}$ is some boundary face of $\patch_{\calT}(S)$.
-        The height of $F$ in $K$ is the height of $F$ in the original simplex $T \in \patch_{\calT}(S)$ with $K \subseteq T$ scaled by $(\ell+1)^{-1}$.
-
-        Assuming that $\varrho > 0$ is at most the minimum height of $z_{S}$ in any $n$-simplex $K \in \calK$,
-        suppose that $z \in \Ball_{\varrho}(z_S)$. 
-        Let $x \in \patch_{\calT}(S)$ be in the interior of the local patch. 
-        If the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$, 
-        then $I$ passes through a boundary face $F \subseteq K$ of the local patch,
-        and $z$ and $x$ are contained on different sides of the hyperplane $H$ spanned by $F$. 
-        Then $x$ and $z_{S}$ are the same side of $H$, since otherwise the straight line segment from $x$ to $z_{S}$ would not be contained in the patch. 
-        This means, however, that $z_{S}$ and $z$ are on different sides of $H$, contradicting that $\varrho$ is at most the height of $z_S \in K$.
-
-        % TODO: prove this observation
-
-        \item 
-        Let $\rho \in (0,1]$, yet to be determined. 
-        We define $y = - \rho z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho \vecnorm{ z_{S'} }$. 
-        Henceforth, we assume $\rho \leq \varrho / \vecnorm{ z_{S'} }$ so that $y \in \overline{\Ball_{\varrho}(z_S)}$.  
-        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
-        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.
-
-        We define another triangulation $\calG^{c}$ as follows:
-        given any $n$-simplex $G \in \calG$, 
-        we replace its vertex $z_{S}'$ by the vertex $y$ at the opposite position,
-        thus obtaining a new $n$-simplex $G^{c}$. 
-        Indeed, that $\calG^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
-
-        We let the simplicial complex $\calG^\ast$ be the union of $\calG$ and $\calG^c$. 
-        By construction, all its $n$-simplices contain $z_{S}$ as a subsimplex, which is an inner vertex of that triangulation. 
-        In particular, $\calD^\ast$ is its own star around $z_{S}$.
-
-        \item 
-        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
-        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
-        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
-        be affine reference transformations
-        that agree on the vertices common to $G$ and $G^{c}$.
-        We then define the piecewise affine mapping 
-        \begin{align*}
-            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}.
-        \end{align*}
-        It follows that 
-        \begin{align*}
-            |\det( \Jacobian      \Theta_{|G} )| = \frac{\vol(G^{c})}{\vol(G)}
-            .
-        \end{align*}
-        We want to further characterize the singular values of this transform. 
-        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$,
-        that is, the vector pointing to $z_{S'}$ and standing orthogonally on the affine hull of the face $G$ that opposes $z_{S'}$
-        We verify that 
-        \begin{align*}
-            \Theta_{|G}(x) 
-            = 
-            x
-            - 
-            (1+\rho) \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            \hat z_{S'}
-            .
-        \end{align*}
-        Indeed, the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
-        and when $x = z_{S'}$, then 
-        \begin{align*}
-            \Theta_{|G}\left( z_{S'} \right) 
-            &
-            =
-            z_{S'}
-            - 
-            (1+\rho) \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            \\&
-            =
-            z_{S'}
-            - 
-            (1+\rho) \hat z_{S'} \vecnorm{z_{S'}}
-            =
-            z_{S'}
-            - 
-            (1+\rho) z_{S'} 
-            =
-            - \rho z_{S'} = y
-            .
-        \end{align*}
-        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
-        \begin{align*}
-            \Theta_{|G}( h_{z} ) 
-            &= 
-            h_{z}
-            - 
-            (1+\rho) \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            \\&
-            = 
-            h_{z}
-            - 
-            (1+\rho) \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            %\\&
-            = 
-            h_{z}
-            - 
-            (1+\rho) z_{S'}
-            %\\&
-            = 
-            - \rho h_{z}
-            - 
-            (1+\rho) b_{z}
-            .
-        \end{align*}
-        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
-        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
-        We study the singular values of the matrix 
-        \begin{align*}
-            M_{\Theta,G} 
-            := 
-            \begin{pmatrix}
-            -\rho                                         & 0
-            \\ 
-            -(1+\rho) \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
-            \end{pmatrix}
-            =
-            \begin{pmatrix}
-            -\rho                 & 0
-            \\ 
-            -(1+\rho) \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        Its two singular values are:
-        \begin{align}
-            \sigma_{\max}(\Theta,G) 
-            := 
-            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } + \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
-            \label{math:theta_max}
-            ,
-            \\
-            \sigma_{\min}(\Theta,G) 
-            := 
-            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } - \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
-            \label{math:theta_min}
-            .
-        \end{align}
-        All other singular values of $\Jacobian\Theta_{|G}$ equal $1$. 
-        The singular values $\sigma_{\max}(\Theta,G) \geq 1$ and $\sigma_{\min}(\Theta,G) \leq 1$ is monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
-Hence, they must the extremal maximal singular values of $\Jacobian\Theta_{|G}$.
-        It is evident that $\rho = \vol(G^{c}) / \vol(G)$.
-
-        We develop explicit bounds for these singular values. 
-        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
-        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
-
-        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions: 
-        first at $z_{S}$, leading to some intermediate $n$-simplex $T'$, and then at $z_{S'}$, leading to $G \subseteq T'$. 
-        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$, which is some face of $T'$.
-        Now, the height of $F_{z}$ in $G$ is $(n-\ell)$-th of the height of $F_{z}$ in $T'$
-        since $S'$ has dimension $n-\ell-1$. 
-        The height of the face $F_{z}$ in $T'$ is just the height of its opposing vertex, which lies in $S'$,
-        and which equals the height of that vertex in $T$.
-%         which must be contained in some face of $T$ containing $S$. 
-%         The height vector $h_{z}$ is orthogonal to $F_{z}$. 
-%         Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$,
-%         pointing to some vertex of $S'$ and standing orthogonally on the face opposite to that vertex. 
-        Thus, 
-        \begin{align*}
-            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
-            = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
-            \leq 
-            (n-\ell) \aspectratio(T)
-%             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
-%             \leq 
-%             \frac{ n-\ell }{n!}
-%             \cdot 
-%             \frac{ \diam(T)^{n} }{ \vol(T) }
-            .
-        \end{align*}
-        We abbreviate 
-        \begin{align}\label{math:upper_bound_for_theta}
-            \mu_{T,\ell} 
-            := 
-            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
-            + 
-            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
-            .
-        \end{align}
-        This establishes bounds on the singular values of the transformation. 
-        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
-        \begin{align}
-            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
-            \quad 
-            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
-            \quad 
-            \sigma_{n}(\Theta,x)^{-1} = \frac{ \sigma_{1}(\Theta,x) }{ \left| \det \Jacobian\Theta_{|G} \right| } \leq \mu_{T,\ell} / \rho.
-        \end{align}
-
-        \item 
-        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
-        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
-        We construct a bi-Lipschitz mapping 
-        \begin{align*}
-            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
-        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
-        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $y$ in $G^{c}$.
-        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
-        has a unique representation
-        \begin{align*}
-            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
-        \end{align*}
-        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
-        \begin{align*}
-            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
-            .
-        \end{align*}
-        Based on that observation, we define 
-        \begin{align*}
-            \Phi_{G}(x) 
-            &
-            := 
-            \mu x_{Q} + \frac{\rho}{\rho+1} \left( \lambda(x) - 1 \right) z_{S'}
-            \\&
-            = 
-            \mu x_{Q} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            \\&
-            = 
-            x - \frac{\rho+1}{\rho+1} \lambda(x) z_{S'} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            \\&
-            = 
-            x - \frac{1}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            \\&
-            = 
-            x - \frac{1}{\rho+1} \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} z_{S'} - \frac{\rho}{\rho+1} z_{S'}
-            .
-        \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
-        that satisfies the desired mapping properties. 
-        It remains to analyze its Jacobian and get explicit estimates for its singular values.
-
-        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
-        With that,
-        \begin{align*}
-            \Jacobian \Phi_{G}(x)
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},z_{S'}\rangle }  
-            \\
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle }  
-            \\
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ h_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \frac{ b_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
-            \\
-            &=
-            \Id 
-            - 
-            \frac{ 1 }{ 1 + \rho }  
-            \hat h_{z} \otimes \hat h_{z}^{t}
-            - 
-            \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho }  
-            \hat b_{z} \otimes \hat h_{z}^{t}
-            .
-        \end{align*}
-        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
-        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
-        Direct computation shows 
-        \begin{align}
-            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z}
-            ,
-            \qquad 
-            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac{ \rho }{ 1 + \rho } \hat h_{z} - \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho } \hat b_{z}
-            .
-        \end{align}
-        It remains to study the singular values of the matrix 
-        \begin{align*}
-            M_{\Phi,G} 
-            = 
-            \begin{pmatrix}
-                 \frac{ \rho }{ 1 + \rho }    & 0 
-                \\
-                -\frac{ \tan(\beta) }{1+\rho} & 1 
-            \end{pmatrix}
-            .
-        \end{align*}
-        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
-        we obtain the singular values 
-        \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            &
-            =
-            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } + \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
-            ,
-            \\
-            \sigma_{\min}(\Phi,G) 
-            &
-            =
-            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } - \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
-            .
-        \end{align*}
-        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
-        Notice that 
-        \begin{align*}
-            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2} = \frac{\rho}{1+\rho}.
-        \end{align*}
-        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
-        Similar as above, we use the upper bound 
-        \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
-        \end{align*}
-        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
-        \begin{gather}
-            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
-            \leq 
-            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
-            + 
-            \frac{1}{2(1+\rho)} \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \label{math:phi_max}
-            ,
-            \\
-            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
-            \\
-            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
-            =
-            \frac{ \sigma_{1}(\Phi,x) }{ \left| \det \Jacobian\Phi \right| }
-            \leq 
-            % \frac{(1+\rho)^2}{\rho(1+\rho)}
-            % \frac{1}{2(1+\rho)} 
-            \frac{1}{2\rho}
-            \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
-            + 
-            % \frac{(1+\rho)^2}{\rho(1+\rho)}
-            % \frac{1}{2(1+\rho)} 
-            \frac{1}{2\rho}
-            \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \label{math:phi_min}
-            .
-        \end{gather}
-        This finishes the discussion of the transformation $\Phi$. 
-    \end{itemize}
-    Having shown all the desired estimates, and the proof is complete. 
-\end{proof}
-\color{black}
-
 \section{Constructive estimates of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
@@
     where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
-    Alternatively, when $L$ denotes the longest path, then a different application of H\"older's inequality shows:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        L^{\frac p q}
-        \sum_{\ell=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        L^{\frac p q}
-        \sum_{m=0}^{M} 
-        \max_{ 0 \leq \ell \leq M }
-        C_{m,\ell}^{p} 
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    Hence, 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \sum_{\ell=0}^{M} 
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \delta_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \\&
-        \leq 
-        \max_{0 \leq \ell \leq M} \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \delta_{m,\ell} 
-        \right)
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        \\&
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)
-        \cdot 
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        .
-    \end{align}
-    Now, if $q \leq p$, that is, $2 \leq p$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \left(
-            \sum_{\ell'=0}^{M}
-            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
-        \right)^{\frac 1 q}
-        .
-    \end{align}
-    Instead, if $p \leq q$, that is, $p \leq 2$, then 
-    \begin{align}
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \right)^{\frac 1 p}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
-        .
-    \end{align}
-    So in any case, it is better than using the following Minkowski's inequality: 
-    \begin{align}
-        \| w \|_{L^{p}(\Omega)}
-        &
-        \leq 
-        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
-        \\&
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \cartan u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
-        \leq 
-        \sum_{\ell=0}^{M}
-        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
-        \| \cartan u \|_{L^{p}(\Omega)}
-        .
-    \end{align}
 \end{remark}

### 2025-01-15 main.tex
remove old version of geometric estimate; more clean up

@@
         \node at (0.45, -0.2) {$\Gamma_1$};
-        \node at (-0.75, 0) {$\Gamma_2$};
+        \node at (-0.80, 0) {$\Gamma_2$};
 
@@
     \end{tabular} 
-    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.}\label{figure:geometricconstruction}
+    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.
+    The triangle $T$ completes the star around an interior vertex. $A$ is the complement of the triangle within the star. 
+    $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
+    $\Gamma_2$ is left invariant by the deformation.}\label{figure:geometricconstruction}
 \end{figure}
@@
     \begin{align*}
-        \Xi_{1} : T \rightarrow \Makoto
-    \end{align*}
-    which is the identity along ${\Gamma_1}$. 
+        \Xi_{1} : T \rightarrow \Xi_{1}(T) \subseteq \Makoto 
+    \end{align*}
+    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto
-    \end{align*}
-    which is the identity along $\Gamma_2$. 
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Xi_{2}( \underlying{\patch_{\calT}(S)} ) \subseteq \Makoto
+    \end{align*}
+    which is the identity along $\partial \Makoto \setminus \partial T$.
     At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
@@
     \end{align*}
-    % DONE {TCF: Should $\sigma_n$ be $\sigma_n^{-1}$ in the second line of both statements?}
     \end{enumerate}
@@
         Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.
-        % Let $I := \Makoto \cap T$, which is the union of $\ell$ different faces of $T$, with $1 \leq \ell \leq n$.
-        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-\ell$ faces of $T$.
-        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
-        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$. 
-        In other words, the vertices of $S'$ are the vertices of $T$ that are not vertices of $S$. 
-        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
-        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
-
-        \item 
-        We let $z_{S'}$ be the midpoint of $S'$. 
-        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calD$ of the underlying set $\underlying{T}$. 
-        Obviously, all $n$-simplices in $\calD$ contain $S$ and $z_{S'}$.
-
-        We define another simplicial complex $\calD^c$ as follows:
-        given any $n$-simplex $K \in \calD$, 
-        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
-        thus obtaining a new simplex $K^{c}$. 
-        Indeed, that $\calD^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
-
-        We let the simplicial complex $\calD^\ast$ be the union of $\calD$ and $\calD^c$. 
-        By construction, all its $n$-simplices contain $S$ as a subsimplex,
-        % Indeed, $\calD^\ast$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
-        Moreover, $S$ is an inner subsimplex of that triangulation. 
-        In particular, $\calD^\ast$ is its own star around $S$.
-
-        % TODO Check that $\calD^\ast$ is a triangulation
-
-        \item 
-        As additional step, we introduce another simplicial complex $\calG^\ast$ from $\calD^\ast$ via barycentric subdivision of $S$.
-        Then $\calG^\ast$ is its own local star around the barycenter $z_S$.
-        In particular, all $n$-simplices in $\calG^\ast$ contain $z_{S}$. 
-        The simplicial complex $\calG^\ast$ also contains as subcomplexes the corresponding refinements of $\calD$ and $\calD^{c}$, 
-        which we denote by $\calG$ and $\calG^{c}$, respectively.
-        Given any $n$-simplex in $\calG$, replacing its vertex $z_{S}$ with its opposite $-z_{S}$ gives an associated $n$-simplex in $\calG^{c}$.
-
-        Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
-
-        \item 
-        % Notice that $A_{G^{c}}$ and $A_{G}$ have the same singular values. Thus
-        % \begin{align*}
-        %     \matnorm{ \Jacobian \Theta_{|G}      } &\leq \| A_{G^{c}} \| \cdot \| A_{G}^{-1} \| \leq \geometricshapemeasure(A_{G}),
-        %     \\
-        %     \matnorm{ \Jacobian \Theta_{|G}^{-1} } &\leq \| A_{G^{c}}^{-1} \| \cdot \| A_{G} \| \leq \geometricshapemeasure(A_{G}).
-        % \end{align*}
-        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
-        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
-        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
-        be affine reference transformations
-        that agree on the vertices common to $G$ and $G^{c}$.
-        Then the mapping 
-        \begin{align*}
-            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}
-        \end{align*}
-        preserves volumes:
-        \begin{align*}
-            |\det( \Jacobian      \Theta_{|G} )|
-            = 
-            |\det( \Jacobian^{-1} \Theta_{|G} )|
-            =
-            1
-            .
-        \end{align*}
-        We want to characterize the singular values of this transform. 
-        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
-        We verify that 
-        \begin{align*}
-            \Theta_{|G}(x) 
-            = 
-            x
-            - 
-            2 \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-            \hat z_{S'}
-            .
-        \end{align*}
-        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
-        and that it equals $-z_{S'}$ when $x = z_{S'}$.
-%         and when $x = z_{S'}$, then 
-%         \begin{align*}
-%             -z_{S'} 
-%             =
-%             z_{S'}
-%             - 
-%             2 \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
-%             .
-%         \end{align*}
-        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
-        \begin{align*}
-            \Theta_{|G}( h_{z} ) 
-            &= 
-            h_{z}
-            - 
-            2 \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            = 
-            h_{z}
-            - 
-            2 \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
-            %\\&
-            = 
-            h_{z}
-            - 
-            2 z_{S'}
-            %\\&
-            = 
-            - h_{z}
-            - 
-            2 b_{z}
-            .
-        \end{align*}
-        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
-        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
-        We study the singular values of the matrix 
-        \begin{align*}
-            M_{\Theta,G} 
-            := 
-            \begin{pmatrix}
-            -1                 & 0
-            \\ 
-            -2 \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
-            \end{pmatrix}
-            =
-            \begin{pmatrix}
-            -1             & 0
-            \\ 
-            -2 \tan(\beta) & 1
-            \end{pmatrix}
-            .
-        \end{align*}
-        We compute the eigenvalues of the symmetric matrix $M_{\Theta,G}^{\ast} M_{\Theta,G}$. 
-        Its square roots are the desired singular values of $M_{\Theta,G}$:
-        \begin{align}
-            \sigma_{\max}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
-            ,
-            \\
-            \sigma_{\min}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
-            .
-        \end{align}
-        They are mutual reciprocals of each other, and they are monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
-        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,
-        whereas all its other singular values equal $1$.
-
-%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
-        We develop explicit bounds for these singular values. 
-        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
-        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
-        % Obviously, $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$.
-
-        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
-        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
-        which must be contained in some face of $T$. 
-        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
-        Thus, 
-        \begin{align*}
-            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
-            = 
-            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
-            = 
-            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
-            \leq 
-            (n-\ell) \aspectratio(T)
-%             = 
-%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
-%             \leq 
-%             \frac{ n-\ell }{n!}
-%             \cdot 
-%             \frac{ \diam(T)^{n} }{ \vol(T) }
-            .
-        \end{align*}
-        This establishes bounds on the singular values of the transformation. 
-        We abbreviate 
-        \begin{align}\label{math:upper_bound_for_theta}
-            \mu_{T,\ell} 
-            := 
-%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
-%             \geq 
-            \sqrt{ 
-                1 + (n-\ell)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
-            } 
-            + 
-            (n-\ell) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
-            .
-        \end{align}
-        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
-        \begin{align}
-            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
-            \quad 
-            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
-            \quad 
-            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell}.
-        \end{align}
-        \color{red}It is also evident that the eigenvalues of the Jacobian almost everywhere have magnitude $1$.\color{black}
-
-        \item 
-        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
-        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
-        We construct a bi-Lipschitz mapping 
-        \begin{align*}
-            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
-        \end{align*}
-        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
-        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
-        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
-
-        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
-        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
-        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
-        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
-        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
-        has a unique representation
-        \begin{align*}
-            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
-        \end{align*}
-        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
-        \begin{align*}
-            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
-            .
-        \end{align*}
-        Based on that observation, we define 
-        \begin{align*}
-            \Phi_{G}(x) % TODO : Sign error. Check values for 0 and 1. Then proceed from there ... 
-            &
-            := 
-            \mu x_{Q} + \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
-            \\&
-            = 
-            x - \lambda(x) z_{S'} + \frac{ \lambda(x)}{ 2 } z_{S'} - \frac{ 1 }{ 2 } z_{S'}
-            \\&
-            = 
-            x - \frac{ \lambda(x) }{2} z_{S'} - \frac{ 1 }{ 2 } z_{S'}
-            \\&
-            = 
-            x - \frac{\langle h_{z},x\rangle}{2\langle h_{z},z_{S'}\rangle} z_{S'} - \frac 1 2 z_{S'}
-            .
-        \end{align*}
-        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
-        that satisfies the desired mapping properties. 
-        It remains to analyze its Jacobian to get explicit estimates.
-
-        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
-        With that,
-        \begin{align*}
-            \Jacobian \Phi_{G}(x)
-            &=
-            \Id 
-            - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
-            z_{S'} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
-            h_{z} \otimes h_{z}^{t}
-            - 
-            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
-            b_{z} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
-            h_{z} \otimes h_{z}^{t}
-            - 
-            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
-            b_{z} \otimes h_{z}^{t}
-            \\
-            &=
-            \Id 
-            - 
-            \frac{1}{ 2 } 
-            \hat h_{z} \otimes \hat h_{z}^{t}
-            - 
-            \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
-            \hat b_{z} \otimes \hat h_{z}^{t}
-            .
-        \end{align*}
-        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
-        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
-        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
-        We verify that 
-        \begin{align}
-            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z},
-            \qquad 
-            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac 1 2 h_{z} - \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } \hat b_{z}
-            .
-        \end{align}
-        It remains to study the singular values of the matrix 
-        \begin{align*}
-            M_{\Phi,G} 
-            = 
-            \begin{pmatrix}
-                 \frac 1 2             & 0 
-                \\
-                -\frac 1 2 \tan(\beta) & 1 
-            \end{pmatrix}
-%             = 
-%             \frac 1 2 
-%             \begin{pmatrix}
-%                 -1 & 0 
-%                 \\
-%                 -3\tan(\beta) & 2 
-%             \end{pmatrix}
-            .
-        \end{align*}
-        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
-        we obtain the singular values 
-        \begin{align*}
-            \sigma_{\max}(\Phi,G) 
-            &
-            =
-            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
-            ,
-            \\
-            \sigma_{\min}(\Phi,G) 
-            &
-            =
-            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
-            .
-        \end{align*}
-        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
-        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
-        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$ and 
-        \begin{align*}
-            \det \Jacobian\Phi = \frac 1 2.
-        \end{align*}
-        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
-        Similar as above, we use the upper bound 
-        \begin{align*}
-            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
-        \end{align*}
-        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
-        \begin{gather}
-            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
-            \leq 
-            \frac 1 4 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            1 + \frac{1}{2} (\ell+1) \aspectratio(T) 
-            \label{math:phi_max}
-            ,
-            \\
-            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
-            \\
-            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
-            \leq 
-            \frac 1 2 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
-            \leq 
-            2 + (\ell+1) \aspectratio(T) 
-            \label{math:phi_min}
-            .
-        \end{gather}
-        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $\tfrac 1 2$ with multiplicity $1$.\color{black}
-        This finishes the discussion of the transformation $\Phi$.
-
-        \item 
-        We continue with an auxiliary result.
-        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
-        Define 
-        \begin{align*}
-            F(x) 
-            = 
-            \frac{ \vecnorm{h_2}^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, x \rangle }{ \vecnorm{ h_1 }^{2} }
-            x
-            .
-        \end{align*}
-        This is defined away from the hyperplane orthogonal to $h_2$.
-        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \vecnorm{ h_1 }^{2}$, then $\langle F(x), h_2 \rangle = \vecnorm{ h_2 }^{2}$.
-        That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
-        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed,
-
-        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
-        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $x$ and between $h_2$ and $x$, respectively. 
-        In what follows, $y \in \bbR^{n}$.
-        \begin{align*}
-            \Jacobian F(x) \cdot y
-            &=
-            \frac{ \vecnorm{ h_2 }^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \vecnorm{ h_1 }^{2} }
-            x
-            - 
-            \frac{ \langle h_2, h_2 \rangle \langle h_2, y \rangle }{ \langle h_2, x \rangle^{2} }
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            x 
-            +
-            \frac{ \langle h_2, h_2 \rangle }{ \langle h_2, x \rangle }
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            y 
-            \\&=
-            \frac{ \langle h_2, h_2 \rangle }{ \vecnorm{ h_2 } \vecnorm{x} \cos(\alpha_2) }
-            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
-            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
-            +
-            \frac{ \vecnorm{ h_2 }^{2} }{ \langle h_2, x \rangle }
-            \frac{ \langle h_1, y \rangle }{ \vecnorm{ h_1 }^{2} }
-            x
-            \\&=
-            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
-            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
-            +
-            \frac{ \vecnorm{ h_2 } }{ \langle \hat h_2, \hat x \rangle }
-            \frac{ \langle \hat h_1, y \rangle }{ \vecnorm{ h_1 } }
-            \hat x
-            \\&=
-            \frac{ \vecnorm{ h_2 } }{ \cos(\alpha_2) }
-            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
-            \frac{ \cos(\alpha_1) }{ \vecnorm{ h_1 } }
-            +
-            \frac{ \vecnorm{ h_2 } }{ \cos(\alpha_2) }
-            \frac{ \langle \hat h_1, y \rangle }{ \vecnorm{ h_1 } }
-            \hat x
-            \\&=
-            \frac{ \vecnorm{ h_2 } }{ \vecnorm{ h_1 } }
-            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
-            \left( 
-                y 
-                - 
-                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
-                + 
-                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
-            \right)
-            .
-        \end{align*}
-        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
-        Notice that $a \perp \hat x$.
-The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
-Over that two-dimensional subspace, it can be represented by a triangular matrix.
-        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
-        %~\cite{blinn1996consider} 
-        \begin{align*}
-            \sigma_{\max} = \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } + \frac{ \vecnorm{a} }{2},
-            \qquad 
-            \sigma_{\min} = \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } - \frac{ \vecnorm{a} }{2}.     
-        \end{align*}
-        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\vecnorm{a}$.
-%         We thus consider the upper bound 
-%         \begin{align*}
-%             \vecnorm{a} 
-%             \leq 
-%             2 \max_{1 \leq i \leq 2} 
-%             \left( 
-%                 \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
-%             \right)
-%             .
-%         \end{align*}
-        \color{red}Lastly, the matrix $\Id + \hat x \otimes a^{t}$ has the eigenvalue $1$ with multiplicity $n-1$ and a trace of $n + \langle a, \hat x \rangle$,
-        so it has one eigenvalue $1 + \langle a, \hat x \rangle$.\color{black}
-
-        \item 
-        We now describe the construction of a bi-Lipschitz mapping 
-        \begin{align*}
-            \Psi : \underlying{\calG^\ast} \rightarrow \underlying{\calK}.
-        \end{align*}
-        Recall that $\calG^\ast$ and $\calK$ are their own respective stars around the origin,
-        so they must contain an open ball around the origin. 
-        % TODO \mwl{Here we need to show that it is indeed a ball. It must be a domain triangulation.}
-        Let ${G} \in \calG^\ast$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
-There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
-We let $h_{{G}}$ and $h_{K}$ be the normal vectors of the origin within ${G}$ and $K$, respectively.
-They define respective hyperplanes $H_{G}$ and $H_{K}$,
-        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$ for the corresponding faces. 
-        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$,
-        that is, the scalar product of $x$ with either height vector is positive. 
-        We define 
-        \begin{align*}
-            \Psi(x) 
-            = 
-            \frac{ \vecnorm{ h_K }^{2} }{ \langle h_K, x \rangle }
-            \frac{ \langle h_{{G}}, x \rangle }{ \vecnorm{ h_{{G}} }^{2} }
-            x
-            .
-        \end{align*}
-        One easily verifies that this defines a continuous mapping $\Psi$. 
-        By the same line of thought, we see that it is invertible with inverse satisfying 
-        \begin{align*}
-            \Psi^{-1}(z) 
-            = 
-            \frac{ \vecnorm{ h_{{G}} }^{2} }{ \langle h_{{G}}, z \rangle }
-            \frac{ \langle h_K, z \rangle }{ \vecnorm{ h_K }^{2} }
-            z,
-            \qquad 
-            z = \Psi(x)
-            .
-        \end{align*}
-        We let $\alpha_K$ and $\alpha_{{G}}$ be the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
-        and let 
-        \begin{align*}
-            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
-            .
-        \end{align*}
-        The preceding auxiliary results now contribute all information on the singular values of these Jacobians:
-        \begin{gather*}
-            % \matnorm{ \Jacobian\Psi(x) }
-            \sigma_{1}( \Jacobian\Psi(x) )
-            = 
-            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \left( 
-                \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } + \frac{ \vecnorm{a} }{2}
-            \right)
-            ,
-            \\
-            % \matnorm{ \Jacobian\Psi(z)^{-1} }
-            \sigma_{1}( \Jacobian\Psi(z)^{-1} )
-            = 
-            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_K } }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            \left( 
-                \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } - \frac{ \vecnorm{a} }{2}
-            \right)^{-1},
-            \\
-            \sigma_{2}( \Jacobian\Psi(x) ) = \dots = \sigma_{n-1}( \Jacobian\Psi(x) )
-            =
-            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            ,
-            \\
-            \det\Jacobian\Psi(x)
-            =
-            \left( 
-            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            \right)^{n},
-            \qquad
-            \det\Jacobian\Psi^{-1}(z)
-            =
-            \left( 
-            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_{K} } }
-            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
-            \right)^{n}
-            .
-        \end{gather*}
-        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
-        By the definition of the cosine, 
-        \begin{align*}
-            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
-            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-            = 
-            \frac{ \vecnorm{ x_K } }{ \vecnorm{ x_{{G}} } }
-            \leq 
-            \frac{ \vecnorm{ x_K } }{ \vecnorm{ h_{{G}} } }
-            \leq 
-            \frac{ \diam(K) }{ \vecnorm{ h_{{G}} } }
-            ,
-            \qquad 
-            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_K } }
-            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
-            = 
-            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ x_{K} } }
-            \leq 
-            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{K} } }
-            \leq 
-            \frac{ \diam(G) }{ \vecnorm{ h_{K} } }
-            .
-        \end{align*}
-%         \begin{align*}
-%             \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
-%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
-%             \leq 
-%             \frac{ \vecnorm{ x_K } }{ \vecnorm{ x_{{G}} } }
-%             .
-%         \end{align*}
-        We need further details to complete our estimates. 
-        We know that $\vecnorm{ x_K } \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
-The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(\ell+1)^{-1}$.
-        That estimates the quotient $\vecnorm{ x_K } / \vecnorm{ h_K }$. 
-        % 
-        In order to estimate $\vecnorm{ h_{G} }$, we first notice the case $G \in \calG$ implies $\vecnorm{ h_{G} } \leq \diam(G) \leq \diam(T)$. 
-        In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
-        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        It follows again that $\vecnorm{ h_{G} } \leq \diam(T)$. 
-        % 
-        It remains to find a lower bound for $\vecnorm{ h_{G} }$.
-        Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
-        by scaling with $(\ell+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
-        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,\ell}$.
-The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
-        %         In oder to estimate $\vecnorm{ x_{G} }$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
-        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
-        %         It follows that $\vecnorm{ x_{G} } \leq \diam(T)$. 
-        %         
-%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
-%         \begin{align*}
-%             \frac{\diam(T)}{ \vecnorm{ h_{F} }}
-%             \leq  
-%             \aspectratio(T)
-%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
-%             .
-%         \end{align*}
-        Putting all these technical observations together, we estimate 
-        \begin{align*}
-            \frac{ \vecnorm{ x_{K} } }{ \vecnorm{ h_{{G}} } }
-            &\leq 
-            (\ell+1)\mu_{T,\ell}
-            \frac{ \diam(K) }{ \vecnorm{ h_{T} } }
-            \leq 
-            (\ell+1)\mu_{T,\ell}
-            \diameterratio(\calT)
-            \frac{ \diam(T) }{ \vecnorm{ h_{T} } }
-            \leq 
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \mu_{T,\ell}
-            ,
-            \\
-            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{K} } }
-            &\leq 
-            (\ell+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(T) }{ \vecnorm{ h_{K} } }
-            \leq 
-            (\ell+1)
-            \diameterratio(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \frac{ \diam(K) }{ \vecnorm{ h_{K} } }
-            \leq 
-            (\ell+1)
-            \diameterratio(\calT)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-        \begin{gather*}
-            \frac{ \vecnorm{ x_{K} } }{ \vecnorm{ h_{{K}} } }
-            \leq 
-            (\ell+1)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            ,
-            \qquad 
-            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{G} } }
-            \leq 
-            (\ell+1)
-            \aspectratio({G}) \mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            .
-        \end{gather*}
-
-        %         To simplify that expression, we make another observation regarding the height vectors. 
-        %         when $T$ is an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S \subseteq T$,
-        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
-        %         then the barycenter $z_S$ of $S$ has distance $h/(\ell+1)$ from the face $F$. 
-        %         From this observation we infer that the height vectors at the origin of the simplices in $\calG^\ast$ and $\calK$
-        %         are obtained by rescaling the height vectors in $\calD^\ast$ and $\patch_{\calT}(S)$
-        %         with the factor $(\ell+1)^{-1}$.
-
-        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$.
-That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
-        We calculate 
-        \begin{align*}
-            \vecnorm{a}
-            = 
-            \left\|
-            \frac{\vecnorm{ x_{G} }}{\vecnorm{ h_{G} }} \hat h_{{G}} 
-            - 
-            \frac{\vecnorm{ x_{K} }}{\vecnorm{ h_{K} }} \hat h_K
-            \right\|
-            &
-            \leq 
-            \frac{\vecnorm{ x_{G} }}{\vecnorm{ h_{G} }} 
-            + 
-            \frac{\vecnorm{ x_{K} }}{\vecnorm{ h_{K} }} 
-            % \\&
-            \leq 
-            (\ell+1) 
-            \left( 1 + \mu_{T,\ell} \right)
-            \sup_{ K \in \patch_{\calT}(S) }
-            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
-            .
-        \end{align*}
-        We define 
-        \begin{align}
-            \nu_{T,\ell} := \sqrt{ 1 + \frac{ (\ell+1)^{2}\left( 1 + \mu_{T,\ell} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (\ell+1)\left( 1 + \mu_{T,\ell} \right) \aspectratio(\calT) }{2}
-            .
-        \end{align}
-        In summary, 
-        the singular values of the Jacobian of $\Psi$ at almost every $x$ satisfy 
-        % using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, 
-        \begin{align}
-            \sigma_{1}(\Psi,x) % \matnorm{ \Jacobian\Psi(x) }
-            &\leq  
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \cdot 
-            \nu_{T,\ell}
-            ,
-            \\
-            \sigma_{n}(\Psi,x)^{-1} % \matnorm{ \Jacobian\Psi(z)^{-1} }
-            &\leq  
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \cdot 
-            \nu_{T,\ell}
-            ,
-            \\
-            \sigma_{  2}(\Psi,x) 
-            &= 
-            \dots
-            =
-            \sigma_{n-1}(\Psi,x) 
-            \leq 
-            (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell}
-            ,
-            \\
-            \sigma_{n-1}(\Psi,x)^{-1} 
-            &= 
-            \dots
-            =
-            \sigma_{  2}(\Psi,x)^{-1} 
-            \leq 
-            (\ell+1) \diameterratio(\calT) \aspectratio(T) 
-            ,
-            \\
-            \det\Jacobian\Psi(x)
-            &\leq 
-            \left( 
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
-            \right)^{n},
-            \\
-            \det\Jacobian\Psi^{-1}(x)
-            &\leq 
-            \left( 
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \right)^{n}
-            .
-        \end{align}
-        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
-        % It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
-        % Rademacher's theorem then shows that both have essentially bounded weak Jacobians. 
-        Every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $\underlying{\calK}$, since there exists a bi-Lipschitz transformation from $\underlying{\calK}$ onto the unit ball.
-        % We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
-        % After application of a piecewise linear Lipschitz mapping, 
-        % we can assume that $\underlying{\calK}$ is convex without loss of generality. 
-        % Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $\underlying{\calK}$. 
-        % \mwl{DONE: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
-
-        \item 
-        We define a mapping $ \Xi_{1} : T \rightarrow \Makoto = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
-        \begin{align*}
-            \Xi_{1} := \Psi \circ \Theta.
-        \end{align*}
-        It preserves the interface from $T$ onto $\Makoto$. 
-        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
-        Combining the previous estimates for $\Psi$ and $\Theta$ with interlacing inequalities for the singular values of product matrices provides 
-        \begin{align*}
-            \sigma_1(x) = \matnorm{ \Jacobian \Xi_{1} }
-            &\leq 
-            \Cfive{n}{\ell}(\calT)
-            :=
-            (\ell+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            \mu_{T,\ell}^{2}
-            \nu_{T,\ell}           
-            ,
-            \\
-            \sigma_2(x), \dots, \sigma_n(x) 
-            &\leq 
-            \Cfiveprime{n}{\ell}(\calT)
-            :=
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(T) \mu_{T,\ell}^{2}
-            ,
-            \\
-            \sigma_n(x)^{-1} = \matnorm{ \Jacobian \Xi_{1}^{-1} }
-            &\leq
-            \Csechs{n}{\ell}(\calT)
-            :=
-            (\ell+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            \mu_{T,\ell}
-            \nu_{T,\ell}
-            ,
-            \\
-            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
-            &\leq 
-            \Csechsprime{n}{\ell}(\calT)
-            :=
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \cdot 
-            \mu_{T,\ell}
-            .
-        \end{align*}
-        We get the determinant estimates
-        \begin{align*}
-            |\det(\Xi_{1})|
-            &\leq 
-            \Cdetfive{n}{\ell}(\calT)
-            :=
-            (\ell+1)^{n}
-            \diameterratio(\calT)^{n}
-            \mu_{T,\ell}^{n}
-            \aspectratio(\calT)^{n}
-            ,
-            \\
-            |\det(\Xi_{1}^{-1})|
-            &\leq 
-            \Cdetsechs{n}{\ell}(\calT)
-            :=
-            (\ell+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
-            .
-        \end{align*}
-        \color{blue}
-        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
-        \begin{align*}
-            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
-            &
-            \leq 
-            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left( 
-            % Theta max 
-            \mu_{T,\ell} 
-            % Psi max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p}
-            ,
-            \\
-            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
-            &
-            \leq 
-            \Csechstrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left(
-            % Theta^{-1} max 
-            \mu_{T,\ell} 
-            % Psi^{-1} max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p}            
-            .
-        \end{align*}
-        This completes the desired estimates for $\Xi_{1}$. 
-        \color{black}
-
-        \item 
-        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto $ by setting 
-        \begin{align*}
-            \Xi_{2} := \Psi \circ \Phi.
-        \end{align*}
-        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
-        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
-        The combination of the previous estimates for $\Psi$ and $\Phi$ with standard interlacing inequalities now lead to 
-        \begin{align*}
-            \sigma_1(x)
-            = 
-            \matnorm{ \Jacobian \Xi_{2} }
-            &\leq 
-            \Csieb{n}{\ell}(\calT)
-            :=
-            (\ell+1) 
-            \aspectratio(\calT)
-            \diameterratio(\calT)
-            \mu_{T,\ell}
-            \nu_{T,\ell}         
-            \cdot 
-            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)
-            ,
-            \\
-            \sigma_2(x), \dots, \sigma_n(x) 
-            &\leq 
-            \Csiebprime{n}{\ell}(\calT)
-            :=
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(T)\mu_{T,\ell} 
-            \cdot 
-            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)
-            ,
-            \\
-            \sigma_n(x)^{-1}
-            = 
-            \matnorm{ \Jacobian \Xi_{2}^{-1} }
-            &\leq  
-            \Cacht{n}{\ell}(\calT)
-            :=
-            (\ell+1) 
-            \diameterratio(\calT)
-            \aspectratio(\calT)
-            \nu_{T,\ell}           
-            \cdot 
-            \left( 2 + (\ell+1) \aspectratio(T) \right)
-            ,
-            \\
-            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
-            &\leq 
-            \Cachtprime{n}{\ell}(\calT)
-            :=
-            (\ell+1)
-            \diameterratio(\calT)
-            \aspectratio(\calT) 
-            \cdot 
-            \left( 2 + (\ell+1) \aspectratio(T) \right)
-            .
-        \end{align*}
-        We get the determinant estimates 
-        \begin{align*}
-            |\det(\Xi_{2})|
-            &\leq 
-            \Cdetsieb{n}{\ell}(\calT)
-            :=
-            \frac 1 2 
-            (\ell+1)^{n}
-            \diameterratio(\calT)^{n}
-            \mu_{T,\ell}^{n}
-            \aspectratio(\calT)^{n}
-            ,
-            \\
-            |\det(\Xi_{2}^{-1})|
-            &\leq 
-            \Cdetacht{n}{\ell}(\calT)
-            :=
-            2
-            (\ell+1)^{n}
-            \diameterratio(\calT)^{n}
-            \aspectratio(\calT)^{n}
-            .
-        \end{align*}
-        \color{blue}
-        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
-        \begin{align*}
-            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
-            &
-            \leq 
-            \Csiebtrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left( 
-            % Phi max 
-            \left( 1 + \frac 1 2 ( \ell+1 )\aspectratio(\calT) \right)
-            % Psi max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p} 2^{\frac n p}
-            ,
-            \\
-            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
-            &
-            \leq 
-            \Cachttrafo{n}{k}{\ell}{p}(\calT)
-            \\&
-            :=
-            \left(
-            % Phi^{-1} max 
-            \left( 2 + ( \ell+1 )\aspectratio(\calT) \right)
-            % Psi^{-1} max 
-            \nu_{T,\ell}
-            \right)
-            % Det 
-            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p} 2^{\frac n p}            
-            .
-        \end{align*}
-        \color{black}
-        This completes the desired estimates for $\Xi_{2}$. 
-    \end{itemize}
-    Having shown all the desired estimates, and the proof is complete. 
-\end{proof}
-
-\color{magenta}
-\begin{proposition}\label{proposition:starreflection}
-    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
-    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
-    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
-    and let 
-    \begin{align*}
-        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
-        \qquad 
-        {\Gamma_1} := \Makoto \cap T,
-        \qquad 
-        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
-    \end{align*}
-    The following holds, where the constants on the right-hand sides are as stated in the proof. 
-    \begin{enumerate}
-    \item 
-    There exists a bi-Lipschitz piecewise affine mapping
-    \begin{align*}
-        \Xi_{1} : T \rightarrow \Xi_{1}(T) \subseteq \Makoto 
-    \end{align*}
-    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
-    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
-    \begin{gather*}
-        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
-        \quad 
-        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
-        \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
-    \end{gather*}
-    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
-        \leq 
-        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
-        \qquad 
-        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
-        \leq 
-        \Csechstrafo{n}{k}{\ell}{p}(\calT).
-    \end{align*}
-
-    \item 
-    There exists a bi-Lipschitz piecewise affine mapping
-    \begin{align*}
-        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Xi_{2}( \underlying{\patch_{\calT}(S)} ) \subseteq \Makoto
-    \end{align*}
-    which is the identity along $\partial \Makoto \setminus \partial T$.
-    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
-    \begin{gather*}
-        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
-        \quad 
-        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
-        \\
-        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
-        \quad 
-        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
-        \quad 
-        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
-    \end{gather*}
-    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
-    \begin{align*}
-        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
-        \leq 
-        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
-        \qquad 
-        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
-        \leq 
-        \Cachttrafo{n}{k}{\ell}{p}(\calT).
-    \end{align*}
-    \end{enumerate}
-\end{proposition}
-\begin{proof}
-    We derive the estimate in several steps. 
-    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
-    \begin{itemize}
-        \item 
-        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.
 
@@
         This means, however, that $z_{S}$ and $z$ are on different sides of $H$, contradicting that $\varrho$ is at most the height of $z_S \in K$. 
-
-        % TODO: prove this observation
+        % TODO: The above argument seems to rely on convexity. Generalise it to avoid that difficulty.
 
@@
 \end{proof}
-\color{black}
 
@@
     Since $\tilde g$ has got the same symmetries, $\cartan \tilde w = \tilde g$.
-    \color{red}
-    \color{blue}
-    \color{black}
 
@@
 
-% TODO: Keep this theorem? 
+% TODO: Keep this theorem in favor of a broad audience? Or toss it?
 \begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}

### 2025-01-17 main.tex
some text on numerical experiments

@@
     We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations. 
-    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
+    Notably, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
     The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry. 
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of vector Laplacians. 
+    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of vector Laplacians. 
     % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
@@
     %
-    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains. 
-    This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
-    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
+    As an additional result with independent standing, we establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains. 
+    This is achieved via regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
+    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operators as its particular instances. 
     Computational examples illustrate the theoretical findings.
@@
 We give a conceptual overview of the topic before we outline the known results in the literature and our contributions in more detail. 
-Our conceptual point of reference is the Poincar\'e--Friedrichs inequality for the gradient of scalar functions, 
-which has been subject to extensive research.
+Our conceptual point of reference is the Poincar\'e--Friedrichs inequality for the gradient of scalar functions, which has been subject to extensive research.
 
@@
 The relationship between the Poincar\'e constant and the Poincar\'e--Friedrichs constant will be elaborated upon in later sections of this manuscript.
-% We present a more profound discussion further below and also in Section~\ref{section:poincare}, where we also discuss the difference with the Poincar\'e inequality, where the mean value of $u$ is fixed to zero, and address why we later employ linear potentials to estimate the Poincar\'e--Friedrichs constant and not directly the minimizing but nonlinear (for $p \neq 2$) potentials such as~\eqref{math:intro:gradientpotential}.
 
@@
 These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem, 
-% DONT {[TCF: I believe this is often refered to as the Tartare-Petree theorem]}
 and thus the resulting constants are not explicitly computable. 
-
-% divergence 
+% DONT {[TCF: I believe this is often referred to as the Tartare-Petree theorem]}
+
 The divergence operator has received less attention. 
@@
     This just means that $\calT$ is face-connected. 
-
+\end{proof}
 %     If the underlying space $\underlying{\calT}$ is connected, 
@@
 %     This just means that $\calT$ is face-connected.
-\end{proof}
 
@@
 
+\begin{remark}\label{remark:mixedbconsimplex:exteriorderivative:hilbert}
+    Under the assumptions of Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, 
+    the special case $p=2$ allows for the following improvement:
+    there exists $w \in W^{2}\Lambda^{k}(T)$ such that 
+    $\trace_{T,\Gamma} w = 0$
+    and  
+    \begin{align*}
+        \cartan w = \cartan u,
+        \quad 
+        \| w \|_{L^{p}(\Omega)} 
+        \leq 
+        C_{\PF,\Gamma,\ell,k,2}(T)
+        \| \cartan u \|_{L^{p}(\Omega)}
+        ,
+    \end{align*}
+    where 
+    \begin{align*}
+        C_{\PF,\Gamma,\ell,k,p}(T)
+        \leq 
+        \frac{1}{\pi}
+        \algebraicshapemeasure(T)^{k-1}
+        \Ceins{n}(T) 
+        \diam(T)
+        .
+    \end{align*}
+    This follows from the results in \cite{licht2024geometry} as simplices are Lipschitz domains.
+    We conjecture that the constant can be improved further, to be independent of the tetrahedron's eccentricity.
+\end{remark}
+
 We prepare some further notation for our two main results. 
@@
 We assess the ``efficiency'' of our upper bounds with a few numerical examples in dimension 2D and 3D, with focus on the Hilbert space case $p=2$. 
-Unless the Poincar\'e--Friedrichs constants are known explicitly, we use eigenvalue estimates on a refined mesh as a proxy for the exact value.
-We compare the (approximations of) the exact values with the upper bounds obtained via Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+Unless the Poincar\'e--Friedrichs constants are known explicitly, we use reference eigenvalue estimates as a proxy for the exact value, which we obtain using a finite element method on refined mesh. 
+We compare the (approximations of) the exact values with the upper bounds given by Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
 
@@
 We compare computed Poincar\'e--Friedrichs constants over the tetrahedron with tangential boundary conditions along a few faces. 
-Our experiments and tetrahedra indicate that we overestimate the constant by several magnitudes.
-%
-We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
+% We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
 Numerical examples indicate that this holds for $p=2$.
 
-\begin{table}[h!]
+\begin{table}[t]
     \centering % TODO: recompute all those numbers
@@
         \hline
-        $\ell$ & simulation & theorem & ratio & GS & ratio \\
+        $\ell$ & simulation & theorem & ratio \\
         \hline
-        0 & 5.37161130e+00 & 6.96498956e+03 & 2.41385574e+02 & 1.34450672e+01 & 2.50298587e+00 \\ 
-        1 & 4.08721544e+00 & 2.46249567e+03 & 1.47407784e+02 & 1.90141963e+01 & 4.65211501e+00 \\
-        2 & 6.42794893e+00 & 8.20831891e+02 & 1.98659522e+01 & 2.68901344e+01 & 4.18331487e+00 \\
-        3 & 6.71227069e+00 & 6.15623918e+02 & 1.36639593e+01 & 3.80283927e+01 & 5.66550344e+00 \\
-        3 & 6.71227069e+00 & 2.51327412e+02 & 5.57828803e+00 & 7.76251317e+00 & 1.15646605e+00 \\
+        0 & 5.37161130e+00 & 1.34450672e+01 & 2.50298587e+00 \\ 
+        1 & 4.08721544e+00 & 1.90141963e+01 & 4.65211501e+00 \\
+        2 & 6.42794893e+00 & 2.68901344e+01 & 4.18331487e+00 \\
+        3 & 6.71227069e+00 & 3.80283927e+01 & 5.66550344e+00 \\
+        3 & 6.71227069e+00 & 7.76251317e+00 & 1.15646605e+00 \\
         \hline
@@
     The second column contains estimates obtained via Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} in the first four lines
-    and Theorem~\ref{theorem:bogovpoinc} in the last line. 
-    The fourth column uses the same type of estimate but replaces all applications of Theorem~\ref{theorem:bogovpoinc} with an estimate by Guerini and Savo~\cite{guerini2004eigenvalue}.
-    The last estimate, though clearly the most competitive, technically does not apply because the reference proves it only for bounded convex domains with smooth boundaries.
+    and Theorem~\ref{theorem:bogovpoinc} in the last line, where we use Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} for improvement. 
     }
@@
 \end{gather*}
-% Square 
-% L-shaped 
-% Slit
+We consider the triangulations: 
+\begin{itemize}
+    \item $\calT_{Q}$: square triangulation with two triangles
+    \item $\calT_{L}$: L-shaped domain triangulation with four triangles
+    \item $\calT_{S}$: Slit domain triangulation, five triangles 
+\end{itemize}
+
+Only two differential operators appear in the two-dimensional de~Rham complexes,
+and their Poincar\'e--Friedrichs constants are the inverse square roots of the smallest non-zero Dirichlet and Neumann Laplacians. 
+Standard finite element eigenvalue computations on a sufficiently refined mesh (four steps of uniform refinement) provide reference values for these.
+
+We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+A brufe-force search easily enumerates all the shortest face-paths that start from a given triangle, so we use the best possible estimate that this method provides.
+
+We compare the reference Neumann and Dirichlet eigenvalues with the bounds in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
+Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
+so the best possible estimate with that method can be obtained.
+
+% Because much easier estimates are known for those, applying our estimates in the two-dimensional situation has only demonstrative purpose.
 
@@
 \end{gather*}
-% Cube 
-% Fichera
-% Crossed bricks
+We consider the triangulations: 
+\begin{itemize}
+    \item $\calT_{C}$: cube triangulation with five tetrahedra
+    \item $\calT_{K}$: Kuhn triangulation of the cube, consisting of six tetrahedra
+    \item $\calT_{F}$: Fichera corner, $24$ simplices 
+    \item $\calT_{B}$: crossed bricks, $24$ simplices 
+\end{itemize}
+
+The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex and a sufficiently refined mesh (four steps of uniform refinement).
+As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+
+Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
+Brute-force enumeration of all shellings seems infeasible, though. 
+Instead,
+
+\todo{1. be explicit whether/that a shortest path tree is needed. 2. introduce face shortest-path tree 3. how to enumerate shellings}
 
@@
 There are several avenues for further research. 
-In particular, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars), 
-as there are at least two areas where the present techniques could see further improvement.
+In particular, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars) and further improvement seems possible.
 
@@
 
+Thirdly, the present results can be generalized to shellable polytopal complexes. 
+This extension may also pertain for simplicial triangulation: 
+since the estimates deteriorate if the number of simplices increases, 
+we might improve our estimates if we lump simplices of a triangulation together into a few polytopal subdomains for which the Poincar\'e--Friedrichs constants are controlable.
+
 Lastly, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is restricted to topological balls and spheres. 

### 2025-01-17 main.tex
clarifying a proof

--- 2025-01-15 main.tex
@@
 We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
-We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
-We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
+We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i}$ and $S_{i-1}$ are face-neighboring for all $1 \leq i \leq m$.
+Such a sequence is called a \emph{face path} from $S$ to $S'$ in $\calT$. 
 Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
@@
     $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
-    $\Gamma_2$ is left invariant by the deformation.}\label{figure:geometricconstruction}
+    $\Gamma_2$ is left invariant by the deformation.
+    $\Xi_{1}$ maps $T$ into $A$ while preserving the interface $\Gamma_1$,
+    and 
+    $\Xi_{2}$ maps the whole patch into $A$ while preserving the boundary $\Gamma_2$.
+    }\label{figure:geometricconstruction}
 \end{figure}
@@
         Let $x \in \patch_{\calT}(S)$ be in the interior of the local patch. 
-        If the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$, 
-        then $I$ passes through a boundary face $F \subseteq K$ of the local patch,
-        and $z$ and $x$ are contained on different sides of the hyperplane $H$ spanned by $F$. 
-        Then $x$ and $z_{S}$ are the same side of $H$, since otherwise the straight line segment from $x$ to $z_{S}$ would not be contained in the patch. 
-        This means, however, that $z_{S}$ and $z$ are on different sides of $H$, contradicting that $\varrho$ is at most the height of $z_S \in K$. 
-        % TODO: The above argument seems to rely on convexity. Generalise it to avoid that difficulty.
+        Suppose that the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$. 
+        Then $I$ intersects with a boundary face $F \subseteq K$ of the local patch.
+        The straight line segment from $z_{S}$ to $x$ lies within one open half-space defined by the affine hull of $F$.
+        Since $I$ intersects with $F$, this open-half space cannot contain $z$ but it must contain $\Ball_{\varrho}(z_S)$.
+        That is a contradiction. Hence, the straight line segment from $z$ to $x$ bust lie within the interior of the local patch. 
+        We deduce that $\patch_{\calT}(S)$ is star-shaped with respect to $\Ball_{\varrho}(z_S)$.
 

### 2025-01-17 main.tex
some clean up and new writing

@@
 We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-A brufe-force search easily enumerates all the shortest face-paths that start from a given triangle, so we use the best possible estimate that this method provides.
-
-We compare the reference Neumann and Dirichlet eigenvalues with the bounds in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+A brufe-force search easily enumerates all the (reptition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.
+
+We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
 Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
 Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
-so the best possible estimate with that method can be obtained.
+allowing us to compute the best possible of these bounds.
 
@@
 
-The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex and a sufficiently refined mesh (four steps of uniform refinement).
-As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-
-Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
+The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
+Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+
+The computation becomes more demanding in dimension three. 
+Enumerating all the paths between tetrahedra in our example triangulations is feasible but takes considerably longer. 
 Brute-force enumeration of all shellings seems infeasible, though. 
@@
 
-\todo{1. be explicit whether/that a shortest path tree is needed. 2. introduce face shortest-path tree 3. how to enumerate shellings}
+\todo{How to select shellings}
 

### 2025-01-17 draft.tex

@@
 \tableofcontents
+
+\section{Previous geometric deformation estimate}
+
+\begin{proposition}\label{proposition:starreflection}
+    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
+    Let $S \in \calT$ be an inner simplex of dimension $\ell < n$,
+    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
+    and let 
+    \begin{align*}
+        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
+        \qquad 
+        {\Gamma_1} := \Makoto \cap T,
+        \qquad 
+        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
+    \end{align*}
+    The following holds, where the constants on the right-hand sides are as stated in the proof. 
+    \begin{enumerate}
+    \item 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{1} : T \rightarrow \Makoto
+    \end{align*}
+    which is the identity along ${\Gamma_1}$. 
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
+    \begin{gather*}
+        \sigma_1 \leq \Cfive{n}{\ell}(\calT),
+        \quad 
+        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Csechs{n}{\ell}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{\ell}(\calT).
+    \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
+        \leq 
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
+        \leq 
+        \Csechstrafo{n}{k}{\ell}{p}(\calT).
+    \end{align*}
+
+    \item 
+    There exists a bi-Lipschitz piecewise affine mapping
+    \begin{align*}
+        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto
+    \end{align*}
+    which is the identity along $\Gamma_2$. 
+    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
+    \begin{gather*}
+        \sigma_1 \leq \Csieb{n}{\ell}(\calT),
+        \quad 
+        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{\ell}(\calT),
+        \\
+        \sigma_n^{-1} \leq \Cacht{n}{\ell}(\calT),
+        \quad 
+        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{\ell}(\calT),
+        \quad 
+        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{\ell}(\calT).
+    \end{gather*}
+    Moreover, for any $0 \leq k \leq n$ and $p \in [1,\infty]$,
+    \begin{align*}
+        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+        \leq 
+        \Csiebtrafo{n}{k}{\ell}{p}(\calT),
+        \qquad 
+        \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
+        \leq 
+        \Cachttrafo{n}{k}{\ell}{p}(\calT).
+    \end{align*}
+    % DONE {TCF: Should $\sigma_n$ be $\sigma_n^{-1}$ in the second line of both statements?}
+    \end{enumerate}
+\end{proposition}
+\begin{proof}
+    We derive the estimate in several steps. 
+    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
+    \begin{itemize}
+        \item 
+        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin. 
+        % Let $I := \Makoto \cap T$, which is the union of $\ell$ different faces of $T$, with $1 \leq \ell \leq n$.
+        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-\ell$ faces of $T$.
+        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
+        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$. 
+        In other words, the vertices of $S'$ are the vertices of $T$ that are not vertices of $S$. 
+        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
+        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.
+
+        \item 
+        We let $z_{S'}$ be the midpoint of $S'$. 
+        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calD$ of the underlying set $\underlying{T}$. 
+        Obviously, all $n$-simplices in $\calD$ contain $S$ and $z_{S'}$.
+
+        We define another simplicial complex $\calD^c$ as follows:
+        given any $n$-simplex $K \in \calD$, 
+        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
+        thus obtaining a new simplex $K^{c}$. 
+        Indeed, that $\calD^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.
+
+        We let the simplicial complex $\calD^\ast$ be the union of $\calD$ and $\calD^c$. 
+        By construction, all its $n$-simplices contain $S$ as a subsimplex,
+        % Indeed, $\calD^\ast$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
+        Moreover, $S$ is an inner subsimplex of that triangulation. 
+        In particular, $\calD^\ast$ is its own star around $S$.
+
+        % TODO Check that $\calD^\ast$ is a triangulation
+
+        \item 
+        As additional step, we introduce another simplicial complex $\calG^\ast$ from $\calD^\ast$ via barycentric subdivision of $S$.
+        Then $\calG^\ast$ is its own local star around the barycenter $z_S$.
+        In particular, all $n$-simplices in $\calG^\ast$ contain $z_{S}$. 
+        The simplicial complex $\calG^\ast$ also contains as subcomplexes the corresponding refinements of $\calD$ and $\calD^{c}$, 
+        which we denote by $\calG$ and $\calG^{c}$, respectively.
+        Given any $n$-simplex in $\calG$, replacing its vertex $z_{S}$ with its opposite $-z_{S}$ gives an associated $n$-simplex in $\calG^{c}$.
+
+        Lastly, we introduce one more simplicial complex $\calK$ obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.
+
+        \item 
+        % Notice that $A_{G^{c}}$ and $A_{G}$ have the same singular values. Thus
+        % \begin{align*}
+        %     \matnorm{ \Jacobian \Theta_{|G}      } &\leq \| A_{G^{c}} \| \cdot \| A_{G}^{-1} \| \leq \geometricshapemeasure(A_{G}),
+        %     \\
+        %     \matnorm{ \Jacobian \Theta_{|G}^{-1} } &\leq \| A_{G^{c}}^{-1} \| \cdot \| A_{G} \| \leq \geometricshapemeasure(A_{G}).
+        % \end{align*}
+        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
+        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
+        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$
+        be affine reference transformations
+        that agree on the vertices common to $G$ and $G^{c}$.
+        Then the mapping 
+        \begin{align*}
+            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}
+        \end{align*}
+        preserves volumes:
+        \begin{align*}
+            |\det( \Jacobian      \Theta_{|G} )|
+            = 
+            |\det( \Jacobian^{-1} \Theta_{|G} )|
+            =
+            1
+            .
+        \end{align*}
+        We want to characterize the singular values of this transform. 
+        Let $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.
+        We verify that 
+        \begin{align*}
+            \Theta_{|G}(x) 
+            = 
+            x
+            - 
+            2 \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+            \hat z_{S'}
+            .
+        \end{align*}
+        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
+        and that it equals $-z_{S'}$ when $x = z_{S'}$.
+%         and when $x = z_{S'}$, then 
+%         \begin{align*}
+%             -z_{S'} 
+%             =
+%             z_{S'}
+%             - 
+%             2 \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
+%             .
+%         \end{align*}
+        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 
+        \begin{align*}
+            \Theta_{|G}( h_{z} ) 
+            &= 
+            h_{z}
+            - 
+            2 \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            = 
+            h_{z}
+            - 
+            2 \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
+            %\\&
+            = 
+            h_{z}
+            - 
+            2 z_{S'}
+            %\\&
+            = 
+            - h_{z}
+            - 
+            2 b_{z}
+            .
+        \end{align*}
+        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 
+        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        Then $\vecnorm{ h_{z} } = \cos(\beta) \vecnorm{ z_{S'} }$ and $\vecnorm{ b_{z} } = \sin(\beta) \vecnorm{ z_{S'} }$. 
+        We study the singular values of the matrix 
+        \begin{align*}
+            M_{\Theta,G} 
+            := 
+            \begin{pmatrix}
+            -1                 & 0
+            \\ 
+            -2 \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
+            \end{pmatrix}
+            =
+            \begin{pmatrix}
+            -1             & 0
+            \\ 
+            -2 \tan(\beta) & 1
+            \end{pmatrix}
+            .
+        \end{align*}
+        We compute the eigenvalues of the symmetric matrix $M_{\Theta,G}^{\ast} M_{\Theta,G}$. 
+        Its square roots are the desired singular values of $M_{\Theta,G}$:
+        \begin{align}
+            \sigma_{\max}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
+            ,
+            \\
+            \sigma_{\min}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}
+            .
+        \end{align}
+        They are mutual reciprocals of each other, and they are monotonically increasing and decreasing, respectively, in $\tan(\beta)$.
+        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,
+        whereas all its other singular values equal $1$.
+
+%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
+        We develop explicit bounds for these singular values. 
+        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
+        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.
+        % Obviously, $\vecnorm{ b_{z} } \leq \vecnorm{ z_{S'} }$.
+
+        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
+        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
+        which must be contained in some face of $T$. 
+        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
+        Thus, 
+        \begin{align*}
+            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
+            = 
+            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
+            = 
+            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \vecnorm{ (n-\ell) h_{z} } }
+            \leq 
+            (n-\ell) \aspectratio(T)
+%             = 
+%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
+%             \leq 
+%             \frac{ n-\ell }{n!}
+%             \cdot 
+%             \frac{ \diam(T)^{n} }{ \vol(T) }
+            .
+        \end{align*}
+        This establishes bounds on the singular values of the transformation. 
+        We abbreviate 
+        \begin{align}\label{math:upper_bound_for_theta}
+            \mu_{T,\ell} 
+            := 
+%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
+%             \geq 
+            \sqrt{ 
+                1 + (n-\ell)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
+            } 
+            + 
+            (n-\ell) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
+            .
+        \end{align}
+        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
+        \begin{align}
+            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
+            \quad 
+            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
+            \quad 
+            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell}.
+        \end{align}
+        \color{red}It is also evident that the eigenvalues of the Jacobian almost everywhere have magnitude $1$.\color{black}
+
+        \item 
+        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
+        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
+        We construct a bi-Lipschitz mapping 
+        \begin{align*}
+            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
+        \end{align*}
+        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
+        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
+        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.
+
+        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
+        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
+        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
+        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
+        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
+        has a unique representation
+        \begin{align*}
+            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
+        \end{align*}
+        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
+        \begin{align*}
+            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
+            .
+        \end{align*}
+        Based on that observation, we define 
+        \begin{align*}
+            \Phi_{G}(x) % TODO : Sign error. Check values for 0 and 1. Then proceed from there ... 
+            &
+            := 
+            \mu x_{Q} + \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
+            \\&
+            = 
+            x - \lambda(x) z_{S'} + \frac{ \lambda(x)}{ 2 } z_{S'} - \frac{ 1 }{ 2 } z_{S'}
+            \\&
+            = 
+            x - \frac{ \lambda(x) }{2} z_{S'} - \frac{ 1 }{ 2 } z_{S'}
+            \\&
+            = 
+            x - \frac{\langle h_{z},x\rangle}{2\langle h_{z},z_{S'}\rangle} z_{S'} - \frac 1 2 z_{S'}
+            .
+        \end{align*}
+        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
+        that satisfies the desired mapping properties. 
+        It remains to analyze its Jacobian to get explicit estimates.
+
+        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
+        With that,
+        \begin{align*}
+            \Jacobian \Phi_{G}(x)
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
+            z_{S'} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            h_{z} \otimes h_{z}^{t}
+            - 
+            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
+            b_{z} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
+            h_{z} \otimes h_{z}^{t}
+            - 
+            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
+            b_{z} \otimes h_{z}^{t}
+            \\
+            &=
+            \Id 
+            - 
+            \frac{1}{ 2 } 
+            \hat h_{z} \otimes \hat h_{z}^{t}
+            - 
+            \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
+            \hat b_{z} \otimes \hat h_{z}^{t}
+            .
+        \end{align*}
+        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
+        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
+        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
+        We verify that 
+        \begin{align}
+            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z},
+            \qquad 
+            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac 1 2 h_{z} - \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } \hat b_{z}
+            .
+        \end{align}
+        It remains to study the singular values of the matrix 
+        \begin{align*}
+            M_{\Phi,G} 
+            = 
+            \begin{pmatrix}
+                 \frac 1 2             & 0 
+                \\
+                -\frac 1 2 \tan(\beta) & 1 
+            \end{pmatrix}
+%             = 
+%             \frac 1 2 
+%             \begin{pmatrix}
+%                 -1 & 0 
+%                 \\
+%                 -3\tan(\beta) & 2 
+%             \end{pmatrix}
+            .
+        \end{align*}
+        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
+        we obtain the singular values 
+        \begin{align*}
+            \sigma_{\max}(\Phi,G) 
+            &
+            =
+            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
+            ,
+            \\
+            \sigma_{\min}(\Phi,G) 
+            &
+            =
+            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 
+            .
+        \end{align*}
+        These are monotonically increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
+        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
+        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$ and 
+        \begin{align*}
+            \det \Jacobian\Phi = \frac 1 2.
+        \end{align*}
+        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(\ell+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
+        Similar as above, we use the upper bound 
+        \begin{align*}
+            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (\ell+1) \aspectratio(T).
+        \end{align*}
+        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 
+        \begin{gather}
+            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 
+            \leq 
+            \frac 1 4 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            1 + \frac{1}{2} (\ell+1) \aspectratio(T) 
+            \label{math:phi_max}
+            ,
+            \\
+            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
+            \\
+            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 
+            \leq 
+            \frac 1 2 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
+            \leq 
+            2 + (\ell+1) \aspectratio(T) 
+            \label{math:phi_min}
+            .
+        \end{gather}
+        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $\tfrac 1 2$ with multiplicity $1$.\color{black}
+        This finishes the discussion of the transformation $\Phi$.
+
+        \item 
+        We continue with an auxiliary result.
+        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
+        Define 
+        \begin{align*}
+            F(x) 
+            = 
+            \frac{ \vecnorm{h_2}^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, x \rangle }{ \vecnorm{ h_1 }^{2} }
+            x
+            .
+        \end{align*}
+        This is defined away from the hyperplane orthogonal to $h_2$.
+        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \vecnorm{ h_1 }^{2}$, then $\langle F(x), h_2 \rangle = \vecnorm{ h_2 }^{2}$.
+        That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
+        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed,
+
+        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
+        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $x$ and between $h_2$ and $x$, respectively. 
+        In what follows, $y \in \bbR^{n}$.
+        \begin{align*}
+            \Jacobian F(x) \cdot y
+            &=
+            \frac{ \vecnorm{ h_2 }^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \vecnorm{ h_1 }^{2} }
+            x
+            - 
+            \frac{ \langle h_2, h_2 \rangle \langle h_2, y \rangle }{ \langle h_2, x \rangle^{2} }
+            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
+            x 
+            +
+            \frac{ \langle h_2, h_2 \rangle }{ \langle h_2, x \rangle }
+            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
+            y 
+            \\&=
+            \frac{ \langle h_2, h_2 \rangle }{ \vecnorm{ h_2 } \vecnorm{x} \cos(\alpha_2) }
+            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
+            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
+            +
+            \frac{ \vecnorm{ h_2 }^{2} }{ \langle h_2, x \rangle }
+            \frac{ \langle h_1, y \rangle }{ \vecnorm{ h_1 }^{2} }
+            x
+            \\&=
+            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
+            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
+            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
+            +
+            \frac{ \vecnorm{ h_2 } }{ \langle \hat h_2, \hat x \rangle }
+            \frac{ \langle \hat h_1, y \rangle }{ \vecnorm{ h_1 } }
+            \hat x
+            \\&=
+            \frac{ \vecnorm{ h_2 } }{ \cos(\alpha_2) }
+            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
+            \frac{ \cos(\alpha_1) }{ \vecnorm{ h_1 } }
+            +
+            \frac{ \vecnorm{ h_2 } }{ \cos(\alpha_2) }
+            \frac{ \langle \hat h_1, y \rangle }{ \vecnorm{ h_1 } }
+            \hat x
+            \\&=
+            \frac{ \vecnorm{ h_2 } }{ \vecnorm{ h_1 } }
+            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
+            \left( 
+                y 
+                - 
+                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
+                + 
+                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
+            \right)
+            .
+        \end{align*}
+        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
+        Notice that $a \perp \hat x$.
+The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$.
+Over that two-dimensional subspace, it can be represented by a triangular matrix.
+        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
+        %~\cite{blinn1996consider} 
+        \begin{align*}
+            \sigma_{\max} = \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } + \frac{ \vecnorm{a} }{2},
+            \qquad 
+            \sigma_{\min} = \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } - \frac{ \vecnorm{a} }{2}.     
+        \end{align*}
+        Notice that these are strictly monotonically increasing or decreasing, respectively, in $\vecnorm{a}$.
+%         We thus consider the upper bound 
+%         \begin{align*}
+%             \vecnorm{a} 
+%             \leq 
+%             2 \max_{1 \leq i \leq 2} 
+%             \left( 
+%                 \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
+%             \right)
+%             .
+%         \end{align*}
+        \color{red}Lastly, the matrix $\Id + \hat x \otimes a^{t}$ has the eigenvalue $1$ with multiplicity $n-1$ and a trace of $n + \langle a, \hat x \rangle$,
+        so it has one eigenvalue $1 + \langle a, \hat x \rangle$.\color{black}
+
+        \item 
+        We now describe the construction of a bi-Lipschitz mapping 
+        \begin{align*}
+            \Psi : \underlying{\calG^\ast} \rightarrow \underlying{\calK}.
+        \end{align*}
+        Recall that $\calG^\ast$ and $\calK$ are their own respective stars around the origin,
+        so they must contain an open ball around the origin. 
+        % TODO \mwl{Here we need to show that it is indeed a ball. It must be a domain triangulation.}
+        Let ${G} \in \calG^\ast$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero.
+There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
+We let $h_{{G}}$ and $h_{K}$ be the normal vectors of the origin within ${G}$ and $K$, respectively.
+They define respective hyperplanes $H_{G}$ and $H_{K}$,
+        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$ for the corresponding faces. 
+        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$,
+        that is, the scalar product of $x$ with either height vector is positive. 
+        We define 
+        \begin{align*}
+            \Psi(x) 
+            = 
+            \frac{ \vecnorm{ h_K }^{2} }{ \langle h_K, x \rangle }
+            \frac{ \langle h_{{G}}, x \rangle }{ \vecnorm{ h_{{G}} }^{2} }
+            x
+            .
+        \end{align*}
+        One easily verifies that this defines a continuous mapping $\Psi$. 
+        By the same line of thought, we see that it is invertible with inverse satisfying 
+        \begin{align*}
+            \Psi^{-1}(z) 
+            = 
+            \frac{ \vecnorm{ h_{{G}} }^{2} }{ \langle h_{{G}}, z \rangle }
+            \frac{ \langle h_K, z \rangle }{ \vecnorm{ h_K }^{2} }
+            z,
+            \qquad 
+            z = \Psi(x)
+            .
+        \end{align*}
+        We let $\alpha_K$ and $\alpha_{{G}}$ be the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
+        and let 
+        \begin{align*}
+            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
+            .
+        \end{align*}
+        The preceding auxiliary results now contribute all information on the singular values of these Jacobians:
+        \begin{gather*}
+            % \matnorm{ \Jacobian\Psi(x) }
+            \sigma_{1}( \Jacobian\Psi(x) )
+            = 
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            \left( 
+                \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } + \frac{ \vecnorm{a} }{2}
+            \right)
+            ,
+            \\
+            % \matnorm{ \Jacobian\Psi(z)^{-1} }
+            \sigma_{1}( \Jacobian\Psi(z)^{-1} )
+            = 
+            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_K } }
+            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
+            \left( 
+                \sqrt{ 1 + \frac{ \vecnorm{a}^{2} }{ 4 } } - \frac{ \vecnorm{a} }{2}
+            \right)^{-1},
+            \\
+            \sigma_{2}( \Jacobian\Psi(x) ) = \dots = \sigma_{n-1}( \Jacobian\Psi(x) )
+            =
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            ,
+            \\
+            \det\Jacobian\Psi(x)
+            =
+            \left( 
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            \right)^{n},
+            \qquad
+            \det\Jacobian\Psi^{-1}(z)
+            =
+            \left( 
+            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_{K} } }
+            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
+            \right)^{n}
+            .
+        \end{gather*}
+        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
+        By the definition of the cosine, 
+        \begin{align*}
+            \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
+            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+            = 
+            \frac{ \vecnorm{ x_K } }{ \vecnorm{ x_{{G}} } }
+            \leq 
+            \frac{ \vecnorm{ x_K } }{ \vecnorm{ h_{{G}} } }
+            \leq 
+            \frac{ \diam(K) }{ \vecnorm{ h_{{G}} } }
+            ,
+            \qquad 
+            \frac{ \vecnorm{ h_{{G}} } }{ \vecnorm{ h_K } }
+            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
+            = 
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ x_{K} } }
+            \leq 
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{K} } }
+            \leq 
+            \frac{ \diam(G) }{ \vecnorm{ h_{K} } }
+            .
+        \end{align*}
+%         \begin{align*}
+%             \frac{ \vecnorm{ h_K } }{ \vecnorm{ h_{{G}} } }
+%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
+%             \leq 
+%             \frac{ \vecnorm{ x_K } }{ \vecnorm{ x_{{G}} } }
+%             .
+%         \end{align*}
+        We need further details to complete our estimates. 
+        We know that $\vecnorm{ x_K } \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
+The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(\ell+1)^{-1}$.
+        That estimates the quotient $\vecnorm{ x_K } / \vecnorm{ h_K }$. 
+        % 
+        In order to estimate $\vecnorm{ h_{G} }$, we first notice the case $G \in \calG$ implies $\vecnorm{ h_{G} } \leq \diam(G) \leq \diam(T)$. 
+        In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
+        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
+        It follows again that $\vecnorm{ h_{G} } \leq \diam(T)$. 
+        % 
+        It remains to find a lower bound for $\vecnorm{ h_{G} }$.
+        Every height of the origin in some simplex of $\calG^\ast$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calD^\ast$
+        by scaling with $(\ell+1)^{-1}$. If $G \in \calG$, then that original height was already a height of a vertex of $S$ in $T$. 
+        If instead $G \notin \calG$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calD$, multiplied by $\mu_{T,\ell}$.
+The height of any vertex of $S$ in some simplex of $\calD$ is the same as the height $h_T$ of that vertex in the original simplex $T$.
+        %         In oder to estimate $\vecnorm{ x_{G} }$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
+        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
+        %         It follows that $\vecnorm{ x_{G} } \leq \diam(T)$. 
+        %         
+%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
+%         \begin{align*}
+%             \frac{\diam(T)}{ \vecnorm{ h_{F} }}
+%             \leq  
+%             \aspectratio(T)
+%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
+%             .
+%         \end{align*}
+        Putting all these technical observations together, we estimate 
+        \begin{align*}
+            \frac{ \vecnorm{ x_{K} } }{ \vecnorm{ h_{{G}} } }
+            &\leq 
+            (\ell+1)\mu_{T,\ell}
+            \frac{ \diam(K) }{ \vecnorm{ h_{T} } }
+            \leq 
+            (\ell+1)\mu_{T,\ell}
+            \diameterratio(\calT)
+            \frac{ \diam(T) }{ \vecnorm{ h_{T} } }
+            \leq 
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \mu_{T,\ell}
+            ,
+            \\
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{K} } }
+            &\leq 
+            (\ell+1)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \frac{ \diam(T) }{ \vecnorm{ h_{K} } }
+            \leq 
+            (\ell+1)
+            \diameterratio(\calT)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \frac{ \diam(K) }{ \vecnorm{ h_{K} } }
+            \leq 
+            (\ell+1)
+            \diameterratio(\calT)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            .
+        \end{align*}
+        \begin{gather*}
+            \frac{ \vecnorm{ x_{K} } }{ \vecnorm{ h_{{K}} } }
+            \leq 
+            (\ell+1)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            ,
+            \qquad 
+            \frac{ \vecnorm{ x_{G} } }{ \vecnorm{ h_{G} } }
+            \leq 
+            (\ell+1)
+            \aspectratio({G}) \mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            .
+        \end{gather*}
+
+        %         To simplify that expression, we make another observation regarding the height vectors. 
+        %         when $T$ is an $n$-dimensional simplex with a $\ell$-dimensional subsimplex $S \subseteq T$,
+        %         and $h > 0$ is the height of some vertex $v \in S$ opposite to a face $F$,
+        %         then the barycenter $z_S$ of $S$ has distance $h/(\ell+1)$ from the face $F$. 
+        %         From this observation we infer that the height vectors at the origin of the simplices in $\calG^\ast$ and $\calK$
+        %         are obtained by rescaling the height vectors in $\calD^\ast$ and $\patch_{\calT}(S)$
+        %         with the factor $(\ell+1)^{-1}$.
+
+        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$.
+That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
+        We calculate 
+        \begin{align*}
+            \vecnorm{a}
+            = 
+            \left\|
+            \frac{\vecnorm{ x_{G} }}{\vecnorm{ h_{G} }} \hat h_{{G}} 
+            - 
+            \frac{\vecnorm{ x_{K} }}{\vecnorm{ h_{K} }} \hat h_K
+            \right\|
+            &
+            \leq 
+            \frac{\vecnorm{ x_{G} }}{\vecnorm{ h_{G} }} 
+            + 
+            \frac{\vecnorm{ x_{K} }}{\vecnorm{ h_{K} }} 
+            % \\&
+            \leq 
+            (\ell+1) 
+            \left( 1 + \mu_{T,\ell} \right)
+            \sup_{ K \in \patch_{\calT}(S) }
+            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
+            .
+        \end{align*}
+        We define 
+        \begin{align}
+            \nu_{T,\ell} := \sqrt{ 1 + \frac{ (\ell+1)^{2}\left( 1 + \mu_{T,\ell} \right)^{2} \aspectratio(\calT)^{2} }{4} } + \frac{ (\ell+1)\left( 1 + \mu_{T,\ell} \right) \aspectratio(\calT) }{2}
+            .
+        \end{align}
+        In summary, 
+        the singular values of the Jacobian of $\Psi$ at almost every $x$ satisfy 
+        % using that $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$, 
+        \begin{align}
+            \sigma_{1}(\Psi,x) % \matnorm{ \Jacobian\Psi(x) }
+            &\leq  
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \cdot 
+            \nu_{T,\ell}
+            ,
+            \\
+            \sigma_{n}(\Psi,x)^{-1} % \matnorm{ \Jacobian\Psi(z)^{-1} }
+            &\leq  
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \cdot 
+            \nu_{T,\ell}
+            ,
+            \\
+            \sigma_{  2}(\Psi,x) 
+            &= 
+            \dots
+            =
+            \sigma_{n-1}(\Psi,x) 
+            \leq 
+            (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell}
+            ,
+            \\
+            \sigma_{n-1}(\Psi,x)^{-1} 
+            &= 
+            \dots
+            =
+            \sigma_{  2}(\Psi,x)^{-1} 
+            \leq 
+            (\ell+1) \diameterratio(\calT) \aspectratio(T) 
+            ,
+            \\
+            \det\Jacobian\Psi(x)
+            &\leq 
+            \left( 
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(T)\mu_{T,\ell} % \frac{ \diam(T)^{n} }{ n! \vol(T) }
+            \right)^{n},
+            \\
+            \det\Jacobian\Psi^{-1}(x)
+            &\leq 
+            \left( 
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \right)^{n}
+            .
+        \end{align}
+        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz with respect to some essentially disjoint closed partitions over their respective domains.
+        % It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
+        % Rademacher's theorem then shows that both have essentially bounded weak Jacobians. 
+        Every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $\underlying{\calK}$, since there exists a bi-Lipschitz transformation from $\underlying{\calK}$ onto the unit ball.
+        % We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
+        % After application of a piecewise linear Lipschitz mapping, 
+        % we can assume that $\underlying{\calK}$ is convex without loss of generality. 
+        % Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $\underlying{\calK}$. 
+        % \mwl{DONE: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}
+
+        \item 
+        We define a mapping $ \Xi_{1} : T \rightarrow \Makoto = \overline{ \underlying{ \patch_{\calT}(S) } \setminus T}$ by setting 
+        \begin{align*}
+            \Xi_{1} := \Psi \circ \Theta.
+        \end{align*}
+        It preserves the interface from $T$ onto $\Makoto$. 
+        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
+        Combining the previous estimates for $\Psi$ and $\Theta$ with interlacing inequalities for the singular values of product matrices provides 
+        \begin{align*}
+            \sigma_1(x) = \matnorm{ \Jacobian \Xi_{1} }
+            &\leq 
+            \Cfive{n}{\ell}(\calT)
+            :=
+            (\ell+1) 
+            \diameterratio(\calT)
+            \aspectratio(\calT)
+            \mu_{T,\ell}^{2}
+            \nu_{T,\ell}           
+            ,
+            \\
+            \sigma_2(x), \dots, \sigma_n(x) 
+            &\leq 
+            \Cfiveprime{n}{\ell}(\calT)
+            :=
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(T) \mu_{T,\ell}^{2}
+            ,
+            \\
+            \sigma_n(x)^{-1} = \matnorm{ \Jacobian \Xi_{1}^{-1} }
+            &\leq
+            \Csechs{n}{\ell}(\calT)
+            :=
+            (\ell+1) 
+            \diameterratio(\calT)
+            \aspectratio(\calT)
+            \mu_{T,\ell}
+            \nu_{T,\ell}
+            ,
+            \\
+            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
+            &\leq 
+            \Csechsprime{n}{\ell}(\calT)
+            :=
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \cdot 
+            \mu_{T,\ell}
+            .
+        \end{align*}
+        We get the determinant estimates
+        \begin{align*}
+            |\det(\Xi_{1})|
+            &\leq 
+            \Cdetfive{n}{\ell}(\calT)
+            :=
+            (\ell+1)^{n}
+            \diameterratio(\calT)^{n}
+            \mu_{T,\ell}^{n}
+            \aspectratio(\calT)^{n}
+            ,
+            \\
+            |\det(\Xi_{1}^{-1})|
+            &\leq 
+            \Cdetsechs{n}{\ell}(\calT)
+            :=
+            (\ell+1)^{n}
+            \diameterratio(\calT)^{n}
+            \aspectratio(\calT)^{n}
+            .
+        \end{align*}
+        \color{blue}
+        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
+        \begin{align*}
+            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{1} |^{-\frac 1 p}
+            &
+            \leq 
+            \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+            \\&
+            :=
+            \left( 
+            % Theta max 
+            \mu_{T,\ell} 
+            % Psi max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p}
+            ,
+            \\
+            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{1} |^{\frac 1 p}
+            &
+            \leq 
+            \Csechstrafo{n}{k}{\ell}{p}(\calT)
+            \\&
+            :=
+            \left(
+            % Theta^{-1} max 
+            \mu_{T,\ell} 
+            % Psi^{-1} max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p}            
+            .
+        \end{align*}
+        This completes the desired estimates for $\Xi_{1}$. 
+        \color{black}
+
+        \item 
+        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto $ by setting 
+        \begin{align*}
+            \Xi_{2} := \Psi \circ \Phi.
+        \end{align*}
+        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
+        Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
+        The combination of the previous estimates for $\Psi$ and $\Phi$ with standard interlacing inequalities now lead to 
+        \begin{align*}
+            \sigma_1(x)
+            = 
+            \matnorm{ \Jacobian \Xi_{2} }
+            &\leq 
+            \Csieb{n}{\ell}(\calT)
+            :=
+            (\ell+1) 
+            \aspectratio(\calT)
+            \diameterratio(\calT)
+            \mu_{T,\ell}
+            \nu_{T,\ell}         
+            \cdot 
+            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)
+            ,
+            \\
+            \sigma_2(x), \dots, \sigma_n(x) 
+            &\leq 
+            \Csiebprime{n}{\ell}(\calT)
+            :=
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(T)\mu_{T,\ell} 
+            \cdot 
+            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)
+            ,
+            \\
+            \sigma_n(x)^{-1}
+            = 
+            \matnorm{ \Jacobian \Xi_{2}^{-1} }
+            &\leq  
+            \Cacht{n}{\ell}(\calT)
+            :=
+            (\ell+1) 
+            \diameterratio(\calT)
+            \aspectratio(\calT)
+            \nu_{T,\ell}           
+            \cdot 
+            \left( 2 + (\ell+1) \aspectratio(T) \right)
+            ,
+            \\
+            \sigma_1(x)^{-1}, \dots, \sigma_{n-1}(x)^{-1}
+            &\leq 
+            \Cachtprime{n}{\ell}(\calT)
+            :=
+            (\ell+1)
+            \diameterratio(\calT)
+            \aspectratio(\calT) 
+            \cdot 
+            \left( 2 + (\ell+1) \aspectratio(T) \right)
+            .
+        \end{align*}
+        We get the determinant estimates 
+        \begin{align*}
+            |\det(\Xi_{2})|
+            &\leq 
+            \Cdetsieb{n}{\ell}(\calT)
+            :=
+            \frac 1 2 
+            (\ell+1)^{n}
+            \diameterratio(\calT)^{n}
+            \mu_{T,\ell}^{n}
+            \aspectratio(\calT)^{n}
+            ,
+            \\
+            |\det(\Xi_{2}^{-1})|
+            &\leq 
+            \Cdetacht{n}{\ell}(\calT)
+            :=
+            2
+            (\ell+1)^{n}
+            \diameterratio(\calT)^{n}
+            \aspectratio(\calT)^{n}
+            .
+        \end{align*}
+        \color{blue}
+        Let $p \in [1,\infty]$ and $0 < k < n$. Using inequalities for the product of singular values, we find 
+        \begin{align*}
+            \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
+            &
+            \leq 
+            \Csiebtrafo{n}{k}{\ell}{p}(\calT)
+            \\&
+            :=
+            \left( 
+            % Phi max 
+            \left( 1 + \frac 1 2 ( \ell+1 )\aspectratio(\calT) \right)
+            % Psi max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T)\mu_{T,\ell} \right)^{k-\frac n p} 2^{\frac n p}
+            ,
+            \\
+            \sigma_{n}^{-1}\cdots\sigma_{n-k+1}^{-1} | \det\Jacobian\Xi_{2} |^{\frac 1 p}
+            &
+            \leq 
+            \Cachttrafo{n}{k}{\ell}{p}(\calT)
+            \\&
+            :=
+            \left(
+            % Phi^{-1} max 
+            \left( 2 + ( \ell+1 )\aspectratio(\calT) \right)
+            % Psi^{-1} max 
+            \nu_{T,\ell}
+            \right)
+            % Det 
+            \left( (\ell+1) \diameterratio(\calT) \aspectratio(T) \right)^{k-\frac n p} 2^{\frac n p}            
+            .
+        \end{align*}
+        \color{black}
+        This completes the desired estimates for $\Xi_{2}$. 
+    \end{itemize}
+    Having shown all the desired estimates, and the proof is complete. 
+\end{proof}
 
@@
     \end{align}
-
-\section{}
 

### 2025-01-17 draft.tex

@@
 \tableofcontents
+
+\section{Old type}
+
+\begin{table}[t]
+    \centering % TODO: recompute all those numbers
+    \begin{tabular}{c|c|c|c|c|c}
+        \hline
+        $\ell$ & simulation & theorem & ratio \\
+        \hline
+        0 & 5.37161130e+00 & 1.34450672e+01 & 2.50298587e+00 \\ 
+        1 & 4.08721544e+00 & 1.90141963e+01 & 4.65211501e+00 \\
+        2 & 6.42794893e+00 & 2.68901344e+01 & 4.18331487e+00 \\
+        3 & 6.71227069e+00 & 3.80283927e+01 & 5.66550344e+00 \\
+        3 & 6.71227069e+00 & 7.76251317e+00 & 1.15646605e+00 \\
+        \hline
+    \end{tabular}
+    \caption{Estimated $L^2$ Poincar\'e--Friedrichs constants of the curl operator over the unit tetrahedron with tangential boundary conditions along $\ell$ faces. 
+    The first column contains estimates obtained by numerical simulation with lowest-order N\'ed\'elec elements, via solving an eigenvalue problem.
+    The second column contains estimates obtained via Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} in the first four lines
+    and Theorem~\ref{theorem:bogovpoinc} in the last line, where we use Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} for improvement. 
+    }
+    % Guerini savo : sqrt(3/2) exp(3/2) * D = 7.7625131735516560875716574146153971065689036068355180671108813262 > 6.71227069e+00
+\end{table}
 

### 2025-01-17 main.tex
add sentence

@@
         The straight line segment from $z_{S}$ to $x$ lies within one open half-space defined by the affine hull of $F$.
-        Since $I$ intersects with $F$, this open-half space cannot contain $z$ but it must contain $\Ball_{\varrho}(z_S)$.
+        Since $I$ intersects with $F$, this open-half space cannot contain $z$, but it must contain $\Ball_{\varrho}(z_S)$.
         That is a contradiction. Hence, the straight line segment from $z$ to $x$ bust lie within the interior of the local patch. 
@@
 which relies on estimates for the Bogovski\u{\i} operator over an auxiliary reference domain.
-We compare computed Poincar\'e--Friedrichs constants over the tetrahedron with tangential boundary conditions along a few faces. 
+We compare computed Poincar\'e--Friedrichs constants over the reference tetrahedron with tangential boundary conditions along a few faces. 
 % We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
@@
 \begin{table}[t]
-    \centering % TODO: recompute all those numbers
-    \begin{tabular}{c|c|c|c|c|c}
+    \centering
+    \begin{tabular}{|c|c|c|c|}
         \hline
-        $\ell$ & simulation & theorem & ratio \\
-        \hline
-        0 & 5.37161130e+00 & 1.34450672e+01 & 2.50298587e+00 \\ 
-        1 & 4.08721544e+00 & 1.90141963e+01 & 4.65211501e+00 \\
-        2 & 6.42794893e+00 & 2.68901344e+01 & 4.18331487e+00 \\
-        3 & 6.71227069e+00 & 3.80283927e+01 & 5.66550344e+00 \\
-        3 & 6.71227069e+00 & 7.76251317e+00 & 1.15646605e+00 \\
-        \hline
+                           & $\grad$           & $\curl$           & $\divergence$   \\ \hline
+        $l=0$              & 0.08625017654     & 0.1453729386      & 0.2601720480    \\ \hline
+        $l=1$              & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
+        $l=2$              & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
+        $l=3$              & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
+        $\Gamma=\emptyset$ & 0.2631059409      & 0.1458215887      & 0.08740665548   \\ \hline
     \end{tabular}
-    \caption{Estimated $L^2$ Poincar\'e--Friedrichs constants of the curl operator over the unit tetrahedron with tangential boundary conditions along $\ell$ faces. 
-    The first column contains estimates obtained by numerical simulation with lowest-order N\'ed\'elec elements, via solving an eigenvalue problem.
-    The second column contains estimates obtained via Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} in the first four lines
-    and Theorem~\ref{theorem:bogovpoinc} in the last line, where we use Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} for improvement. 
-    }
-    % Guerini savo : sqrt(3/2) exp(3/2) * D = 7.7625131735516560875716574146153971065689036068355180671108813262 > 6.71227069e+00
+    \caption{
+    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
+    where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
+    Computed via lowest-order finite element methods. The upper bound in Lemma~\ref{} is $0.45015815807$.
+    }\label{table:referencepoincarefriedrichs}
 \end{table}
@@
 % Because much easier estimates are known for those, applying our estimates in the two-dimensional situation has only demonstrative purpose.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    Domain & Exact PF & Approximate PF & Ratio 
+    \\ 
+    \hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    \hline
+    \end{tabular}
+    \caption{Example table with text and formulas.}
+    \label{tab:example}
+\end{table}
 
@@
 Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    Domain & Exact PF & Approximate PF & Ratio 
+    \\ 
+    \hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    %\hline
+    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
+    \\ 
+    \hline
+    \end{tabular}
+    \caption{Example table with text and formulas.}
+    \label{tab:example}
+\end{table}
+The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex and a sufficiently refined mesh (four steps of uniform refinement).
+As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
 

### 2025-01-17 main.tex
table for PF constants with mixed boundary conditions

@@
 
-We first assess the constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-which relies on estimates for the Bogovski\u{\i} operator over an auxiliary reference domain.
-We compare computed Poincar\'e--Friedrichs constants over the reference tetrahedron with tangential boundary conditions along a few faces. 
+We first assess the Poincar\'e--Friedrichs constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
+where tangential boundary conditions hold along a few faces. 
+We tabulate reference Poincar\'e--Friedrichs constants over the reference tetrahedron in Table~\ref{table:referencepoincarefriedrichs},
+which are computed via a higher-order finite element method over a mesh after three iterations of uniform refinement.
+
+The aforementioned lemma gives an upper bound of $\sqrt{2}/\pi \approx 0.45015815807$,
+which is an overestimate of at most a factor of six.
+We take this as an indication that the estimate is within feasible range. 
+We expect the bound to deteriorate as the eccentricity of the tetrahedron increases.
+
 % We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
@@
     where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
-    Computed via lowest-order finite element methods. The upper bound in Lemma~\ref{} is $0.45015815807$.
+    Computed via lowest-order finite element methods. The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $0.45015815807$.
     }\label{table:referencepoincarefriedrichs}

### 2025-01-18 main.tex
more text

--- 2025-01-17 main.tex
@@
 We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
-We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i}$ and $S_{i-1}$ are face-neighboring for all $1 \leq i \leq m$.
-Such a sequence is called a \emph{face path} from $S$ to $S'$ in $\calT$. 
+We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$.
+We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
 Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
@@
     $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
-    $\Gamma_2$ is left invariant by the deformation.
-    $\Xi_{1}$ maps $T$ into $A$ while preserving the interface $\Gamma_1$,
-    and 
-    $\Xi_{2}$ maps the whole patch into $A$ while preserving the boundary $\Gamma_2$.
-    }\label{figure:geometricconstruction}
+    $\Gamma_2$ is left invariant by the deformation.}\label{figure:geometricconstruction}
 \end{figure}
@@
         Let $x \in \patch_{\calT}(S)$ be in the interior of the local patch. 
-        Suppose that the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$. 
-        Then $I$ intersects with a boundary face $F \subseteq K$ of the local patch.
-        The straight line segment from $z_{S}$ to $x$ lies within one open half-space defined by the affine hull of $F$.
-        Since $I$ intersects with $F$, this open-half space cannot contain $z$ but it must contain $\Ball_{\varrho}(z_S)$.
-        That is a contradiction. Hence, the straight line segment from $z$ to $x$ bust lie within the interior of the local patch. 
-        We deduce that $\patch_{\calT}(S)$ is star-shaped with respect to $\Ball_{\varrho}(z_S)$.
+        If the line segment $I$ from $z$ to $x$ is not wholly contained in $\patch_{\calT}(S)$, 
+        then $I$ passes through a boundary face $F \subseteq K$ of the local patch,
+        and $z$ and $x$ are contained on different sides of the hyperplane $H$ spanned by $F$. 
+        Then $x$ and $z_{S}$ are the same side of $H$, since otherwise the straight line segment from $x$ to $z_{S}$ would not be contained in the patch. 
+        This means, however, that $z_{S}$ and $z$ are on different sides of $H$, contradicting that $\varrho$ is at most the height of $z_S \in K$. 
+        % TODO: The above argument seems to rely on convexity. Generalise it to avoid that difficulty.
 
@@
 We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-A brufe-force search easily enumerates all the (reptition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.
-
-We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+A brufe-force search easily enumerates all the shortest face-paths that start from a given triangle, so we use the best possible estimate that this method provides.
+
+We compare the reference Neumann and Dirichlet eigenvalues with the bounds in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
 Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
 Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
-allowing us to compute the best possible of these bounds.
+so the best possible estimate with that method can be obtained.
 
@@
 
-The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
-Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-
-The computation becomes more demanding in dimension three. 
-Enumerating all the paths between tetrahedra in our example triangulations is feasible but takes considerably longer. 
-Brute-force enumeration of all shellings seems infeasible, though. 
-Instead,
-
-\todo{How to select shellings}
+The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex and a sufficiently refined mesh (four steps of uniform refinement).
+As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+
+Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
+Brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
+Instead, we perform a greedy backtracking search: 
+starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
+Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
+We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
+It is imperative for the improvement of our upper bounds that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations, thus avoiding overtly pessimistic blanket estimates.
+
+This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found before the last iteration. 
+Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
+We repeat this for a possible choices of initial simplex, and pick the optimal among those.
+The candidate shellings that we obtain in this manner allow for estimates that differ by a factor of about $2$.
 

### 2025-01-18 main.tex

--- 2025-01-17 main.tex
@@
 The computation becomes more demanding in dimension three. 
-Enumerating all the paths between tetrahedra in our example triangulations is feasible but takes considerably longer. 
-Brute-force enumeration of all shellings seems infeasible, though. 
-Instead,
+Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
+Brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
+Instead, we perform a greedy backtracking search: 
+starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
+Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
+We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
+It is imperative for the improvement of our upper bounds that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations, thus avoiding overtly pessimistic blanket estimates.
+
+This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found before the last iteration. 
+Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
+We repeat this for a possible choices of initial simplex, and pick the optimal among those.
+The candidate shellings that we obtain in this manner allow for estimates that differ by a factor of about $2$.
 

### 2025-01-20 main.tex
corrections

@@
     Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
-    \cite[p.97, Definition 4.2.16 ]{brenner2008mathematical}, % TODO: add brackets here in the final version or figure out how to fix the display in the editor.
+    \cite[p.97, Definition {\char`\(}4.2.16{\char`\)} ]{brenner2008mathematical}, % DONE: add brackets here in the final version or figure out how to fix the display in the editor.
     \cite[Definition~11.2]{ern2021finite}). 
@@
         = 
-        C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{\diam(\widetilde \Makoto)^{n}}{\vol(\widetilde \Makoto)} \diam(\widetilde \Makoto)
+        C_{\Bogov}(n,\mia+1) \vol_{n-1}(S_{1}(0)) \frac{\diam(\widetilde \Makoto)^{n}}{\vol(\widetilde \Makoto)} \diam(\widetilde \Makoto)
         \\&
         = 
-        C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \frac{2^{n}}{2^{n-\ell}/n!} 2
-        = 
-        C_{\Bogov}(n,\mia) \vol_{n-1}(S_{1}(0)) \cdot n! 2^{\ell+1} 
+        C_{\Bogov}(n,\mia+1) \vol_{n-1}(S_{1}(0)) \frac{2^{n}}{2^{n-\ell}/n!} 2
+        = 
+        C_{\Bogov}(n,\mia+1) \vol_{n-1}(S_{1}(0)) \cdot n! 2^{\ell+1} 
         .
@@
         \leq 
-        \frac{1}{\pi}
+        \frac{2}{\pi}
         \algebraicshapemeasure(T)^{k-1}
@@
 
-% TODO: Keep this theorem in favor of a broad audience? Or toss it?
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
-    Let $\calT$ be a shellable $n$-dimensional triangulation, 
-    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
-    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell_{m}$ faces with the previous simplices.
-    \begin{itemize}
-        \item 
-        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
-        and such that the following estimates hold:
-        \begin{gather*}
-            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
-        \end{gather*}
-        and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
-        \begin{align*}
-            \| \bfw \|_{L^{p}(T_{m})}
-            &
-            \leq  
-            C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
-            \left( 
-                \| \curl \bfu      \|_{L^{p}(T_{m})} 
-                +
-                \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
-                \| \curl \bfu \|_{L^{p}(\Makoto_{m-1})}
-            \right)
-            \\&\qquad
-            + 
-            \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
-            \| \bfw \|_{L^{p}(\Makoto_{m-1})}
-            .
-        \end{align*}
-        \item 
-        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
-        such that 
-        \begin{align*}
-            \| \bfw \|_{L^{p}(T_{m})}
-            \leq 
-            \left( 
-            \prod_{i=1}^{M}
-            \Cachttrafo{n}{2}{\ell_{m}}{p}(\calT)
-            \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)
-            \right)
-            C_{{\PF},1,T_{0},p}
-            \| \curl \bfu \|_{L^{p}(\Omega)}
-            .
-        \end{align*}
-    \end{itemize}
-\end{theorem}
-
 \section{Numerical examples}\label{section:numericalexamples}
@@
     where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
-    Computed via lowest-order finite element methods. The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $0.45015815807$.
+    Computed via lowest-order finite element methods. 
+    Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
+    The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $0.45015815807$.
     }\label{table:referencepoincarefriedrichs}
@@
 % Because much easier estimates are known for those, applying our estimates in the two-dimensional situation has only demonstrative purpose.
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-    Domain & Exact PF & Approximate PF & Ratio 
-    \\ 
-    \hline
-    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
-    \\ 
-    %\hline
-    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
-    \\ 
-    %\hline
-    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
-    \\ 
-    \hline
-    \end{tabular}
-    \caption{Example table with text and formulas.}
-    \label{tab:example}
-\end{table}
 
@@
 Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-    Domain & Exact PF & Approximate PF & Ratio 
-    \\ 
-    \hline
-    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
-    \\ 
-    %\hline
-    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
-    \\ 
-    %\hline
-    $\Omega$ & $1.0$ & $1.0$ & $1.0$ 
-    \\ 
-    \hline
-    \end{tabular}
-    \caption{Example table with text and formulas.}
-    \label{tab:example}
-\end{table}
-The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex and a sufficiently refined mesh (four steps of uniform refinement).
-As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+
+% The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
+% As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
 
@@
 
-This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found before the last iteration. 
+This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found until all shellings have been produced.
+However, finding all shellings seems practically infeasible. 
 Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
-We repeat this for a possible choices of initial simplex, and pick the optimal among those.
+We repeat this for a possible choices of initial simplex, and pick the optimal shelling among those found.
 The candidate shellings that we obtain in this manner allow for estimates that differ by a factor of about $2$.
-
-\todo{How to select shellings}
 

### 2025-01-20 main.tex
minor fix

--- 2025-01-18 main.tex
@@
 We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-A brufe-force search easily enumerates all the (reptition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.
+A brufe-force search easily enumerates all the (repetition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.
 
@@
 The computation becomes more demanding in dimension three. 
-Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
-Brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
-Instead, we perform a greedy backtracking search: 
-starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
-Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
-We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
-It is imperative for the improvement of our upper bounds that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations, thus avoiding overtly pessimistic blanket estimates.
-
-This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found before the last iteration. 
-Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
-We repeat this for a possible choices of initial simplex, and pick the optimal among those.
-The candidate shellings that we obtain in this manner allow for estimates that differ by a factor of about $2$.
+Enumerating all the paths between tetrahedra in our example triangulations is feasible but takes considerably longer. 
+Brute-force enumeration of all shellings seems infeasible, though. 
+Instead,
 

### 2025-01-20 draft.tex

@@
 \tableofcontents
+
+\section{Additional formulation for the curl-operator}
+
+% TODO: Keep this theorem in favor of a broad audience? Or toss it?
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
+    Let $\calT$ be a shellable $n$-dimensional triangulation, 
+    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
+    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell_{m}$ faces with the previous simplices.
+    \begin{itemize}
+        \item 
+        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
+        and such that the following estimates hold:
+        \begin{gather*}
+            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
+        \end{gather*}
+        and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
+        \begin{align*}
+            \| \bfw \|_{L^{p}(T_{m})}
+            &
+            \leq  
+            C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
+            \left( 
+                \| \curl \bfu      \|_{L^{p}(T_{m})} 
+                +
+                \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
+                \| \curl \bfu \|_{L^{p}(\Makoto_{m-1})}
+            \right)
+            \\&\qquad
+            + 
+            \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
+            \| \bfw \|_{L^{p}(\Makoto_{m-1})}
+            .
+        \end{align*}
+        \item 
+        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
+        such that 
+        \begin{align*}
+            \| \bfw \|_{L^{p}(T_{m})}
+            \leq 
+            \left( 
+            \prod_{i=1}^{M}
+            \Cachttrafo{n}{2}{\ell_{m}}{p}(\calT)
+            \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)
+            \right)
+            C_{{\PF},1,T_{0},p}
+            \| \curl \bfu \|_{L^{p}(\Omega)}
+            .
+        \end{align*}
+    \end{itemize}
+\end{theorem}
 

### 2025-01-20 draft.tex
work on the tables

@@
 \tableofcontents
+
+\section{Original 2D table}
+
+\begin{table}[t]
+    \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+        \hline
+                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio      & $\grad$ est & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
+        \hline
+        $\calT_{Q}$     & 0.318309563  &             &                    & 1.559393582 & 3.141595843441268  & 0.2250565284       & 1.559393592        &  6.928897176872058 \\ 
+        \hline
+        $\calT_{L}$     & 0.8226899867 &             &                    & 2.382013071 & 2.895395724002629  & 0.3221078945       & 2.382013071        &  7.402266766215750 \\ 
+        \hline
+        $\calT_{S}$     & 0.9781817319 &             &                    & 2.917358296 & 2.982429747636027  & 0.3465088853       & 2.917358296        &  8.419288566306699 \\ 
+        \hline
+        $\calT_{S'}$    & 0.9781817319 &             &                    & 4.764026134 & 4.870287369552950  & 0.3465088853       & 4.764026134        & 13.748640615306034 \\ 
+        \hline
+    \end{tabular}
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
+    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
+    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column)
+    where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
+    Computed via lowest-order finite element methods. 
+    Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
+    The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $0.45015815807$.
+    }\label{table:referencepoincarefriedrichs}
+\end{table}
 

### 2025-01-20 main.tex
initiate table
2D table using recursive estimate
work on the tables

@@
 where tangential boundary conditions hold along a few faces. 
+This constant appears repeatedly within our main result.
+
 We tabulate reference Poincar\'e--Friedrichs constants over the reference tetrahedron in Table~\ref{table:referencepoincarefriedrichs},
@@
 which is an overestimate of at most a factor of six.
-We take this as an indication that the estimate is within feasible range. 
+We take this as an indication that the estimate is within feasible range, at least on simplices with good shape regularity. 
 We expect the bound to deteriorate as the eccentricity of the tetrahedron increases.
+
+However, the results indicate significant room for improvement. 
+Future estimates should tighten the gap towards the actual computed values,
+including for ill-shaped simplices.
 
@@
     Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
-    The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $0.45015815807$.
+    The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $2/\pi \approx 0.45015815807$.
     }\label{table:referencepoincarefriedrichs}
@@
     \item $\calT_{S}$:  Slit domain triangulation, five triangles 
+    \item $\calT_{S'}$: Slit domain triangulation, 8 triangles, four of which touch the origin.
 \end{itemize}
@@
 % Because much easier estimates are known for those, applying our estimates in the two-dimensional situation has only demonstrative purpose.
+
+\begin{table}[t]
+    \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+        \hline
+                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio & $\grad$ est & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
+        \hline
+        $\calT_{Q}$     & 0.318        &             &               & 1.559       & 3.141              & 0.225              & 1.559              &  6.928              \\ 
+        \hline
+        $\calT_{L}$     & 0.822        &             &               & 2.382       & 2.895              & 0.322              & 2.382              &  7.402              \\ 
+        \hline
+        $\calT_{S}$     & 0.978        &             &               & 2.917       & 2.982              & 0.346              & 2.917              &  8.419              \\ 
+        \hline
+        $\calT_{S'}$    & 0.978        &             &               & 4.764       & 4.870              & 0.346              & 4.764              & 13.748              \\ 
+        \hline
+    \end{tabular}
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
+    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
+    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
+    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
+    }\label{table:estimates2D}
+\end{table}
 
@@
 
+\begin{table}[t]
+    \color{red}
+    \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+        \hline
+                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio      & $\grad$ est & $\grad$ ratio       \\ 
+        \hline
+        $\calT_{C}$     & 0.3177997026 &             &                    &  1.147682616 & 3.611339490040196  \\ 
+        \hline
+        $\calT_{K}$     & 0.3179254398 &             &                    & 12.73827122  & 91.66905966662563  \\ 
+        \hline
+        $\calT_{C,5}$     &              &             &                    & 36.7821067   &                    \\ 
+        \hline
+    \end{tabular}
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
+    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
+    }\label{table:estimates3D:grad}
+\end{table}
+
+\begin{table}[t]
+    \color{red}
+    \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+        \hline
+                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
+        \hline
+        $\calT_{C}$     & 0.2250695032 & 1.147682616 & 5.099236457042005 & 0.1837881324      & 1.5265605865      &  8.30608900893      \\ 
+        \hline
+        $\calT_{K}$     & 0.2250062929 & 29.14392611 & 129.5249378629681 & 0.1837655124      & 25.68030786       & 139.7449800105412   \\ 
+        \hline
+        $\calT_{C,5}$   &              & 160.0052039 &                   & 36.7821067        & 160.7339833       &                     \\ 
+        \hline
+    \end{tabular}
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
+    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
+    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
+    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
+    }\label{table:estimates3D:curldiv}
+\end{table}
+
+36.7821067  160.0052039 160.7339833
+
 \section{Outlook}\label{section:outlook}

### 2025-01-22 main.tex
more data
more info on the data

@@
     with $\cartan \mathring w = \cartan \tilde u$ satisfying the bounds 
-    \begin{align*}
+    \begin{align}\label{math:mixedbconsimplex:exteriorderivative:internalconstant}
         \| \mathring w \|_{L^{p}(\widetilde \Makoto)}
@@
         %\\&
-        \leq 
+        % \leq 
         % n C_{\Bogov}(n,k+1) \frac{ \vol_{}(B_2(0)) }{ \vol(\widetilde \Makoto) } 2
@@
         %
-        n! \cdot 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
-        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
-        .
-    \end{align*}
+        % n! \cdot 2^{\ell+1} C_{\Bogov}(n,k+1) \vol_{n-1}(S_1(0)) 
+        % \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
+        .
+    \end{align}
     Here,
@@
     Under the assumptions of Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, 
-    the special case $p=2$ allows for the following improvement:
+    the special case $p=2$ allows to improve the preceding lemma.
+    Specifically, we use a better estimate for the auxiliary constant in \eqref{math:mixedbconsimplex:exteriorderivative:internalconstant}.
+    This follows from the results in \cite{licht2024geometry} as simplices are Lipschitz domains.
+    The complete inequality then reads: 
     there exists $w \in W^{2}\Lambda^{k}(T)$ such that 
@@
     \end{align*}
-    This follows from the results in \cite{licht2024geometry} as simplices are Lipschitz domains.
-    We conjecture that the constant can be improved further, to be independent of the tetrahedron's eccentricity.
+    We conjecture that the constant can be improved further, to be independent of the tetrahedron's eccentricity,
+    and that the result can be extended to Lebesgue exponents $1 \leq p \leq \infty$.
 \end{remark}
@@
 
-We assess the ``efficiency'' of our upper bounds with a few numerical examples in dimension 2D and 3D, with focus on the Hilbert space case $p=2$. 
-Unless the Poincar\'e--Friedrichs constants are known explicitly, we use reference eigenvalue estimates as a proxy for the exact value, which we obtain using a finite element method on refined mesh. 
-We compare the (approximations of) the exact values with the upper bounds given by Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+We assess the practical quality of our upper bounds with a few numerical examples in dimension 2D and 3D, with exclusive focus on the Hilbert space case $p=2$. 
+We want to compare the exact Poincar\'e--Friedrichs constants with the upper bounds given by Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+In lieu of the exact value, finite element computations on a refined mesh provide reference eigenvalues as a proxy for the exact value.
+We have multiple estimates for the gradient potential, and the Poincar\'e--Friedrichs constant of the divergence can always be estimated by the diameter,
+hence our main interest is the curl operator.
 
@@
 
-We first assess the Poincar\'e--Friedrichs constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
-where tangential boundary conditions hold along a few faces. 
-This constant appears repeatedly within our main result.
-
-We tabulate reference Poincar\'e--Friedrichs constants over the reference tetrahedron in Table~\ref{table:referencepoincarefriedrichs},
-which are computed via a higher-order finite element method over a mesh after three iterations of uniform refinement.
-
-The aforementioned lemma gives an upper bound of $\sqrt{2}/\pi \approx 0.45015815807$,
-which is an overestimate of at most a factor of six.
+We first assess the Poincar\'e--Friedrichs constant over the reference simplex where boundary conditions hold along a few faces. 
+This is of interest because the constant appears repeatedly within our main result.
+
+For the purpose of comparison, we compute reference Poincar\'e--Friedrichs constants over the reference tetrahedron via a higher-order finite element method over a mesh after three iterations of uniform refinement.
+These data are tabulated in Table~\ref{table:referencepoincarefriedrichs}.
+
+Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and the subequent remark (using $p=2$) give an upper bound of $2/\pi \approx 0.45015815807$,
+which is an overestimate by a factor of at most six.
 We take this as an indication that the estimate is within feasible range, at least on simplices with good shape regularity. 
@@
     \centering
-    \begin{tabular}{|c|c|c|c|}
+    \begin{tabular}{|l|c|c|c|}
         \hline
                                                   & $\grad$           & $\curl$           & $\divergence$   \\ \hline
-        $l=0$              & 0.08625017654     & 0.1453729386      & 0.2601720480    \\ \hline
-        $l=1$              & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
-        $l=2$              & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
-        $l=3$              & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
-        $\Gamma=\emptyset$ & 0.2631059409      & 0.1458215887      & 0.08740665548   \\ \hline
+        $\Gamma = F_0 \cup F_1 \cup F_2 \cup F_3$ & 0.08625017654     & 0.1453729386      & 0.2601720480    \\ \hline
+        $\Gamma =          F_1 \cup F_2 \cup F_3$ & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
+        $\Gamma =                   F_2 \cup F_3$ & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
+        $\Gamma =                            F_3$ & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
+        $\Gamma =                      \emptyset$ & 0.2631059409      & 0.1458215887      & 0.08740665548   \\ \hline
     \end{tabular}
@@
     Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
-    where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
-    Computed via lowest-order finite element methods. 
+    where boundary conditions are imposed along the boundary part $\Gamma$, 
+    computed via lowest-order finite element methods on a refined mesh. 
     Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
-    The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $2/\pi \approx 0.45015815807$.
+    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} 
+    give the improved upper bound $2/\pi \approx 0.45015815807$.
     }\label{table:referencepoincarefriedrichs}
@@
 \begin{gather*}
-    \Omega_{Q} = (-1,1)^2,
+    \Omega_{Q} = ( 0,1)^2,
     \qquad 
@@
 \begin{gather*}
-    \Omega_{C}  = (-1,1)^3,
+    \Omega_{C}  = ( 0,1)^3,
     \qquad 
@@
 The computation becomes more demanding in dimension three. 
-Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
-Brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
+Enumerating all the shortest-path trees of the triangulations above is still feasible but takes considerably longer. 
+However, brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
 Instead, we perform a greedy backtracking search: 
@@
 We repeat this for a possible choices of initial simplex, and pick the optimal shelling among those found.
-The candidate shellings that we obtain in this manner allow for estimates that differ by a factor of about $2$.
+The candidate shellings that we obtain in this manner lead to different quantitative estimates.
+In the case of more complicated triangulations, such as of the Fichera corner, they may differ by a factor of $20$.
+For that reason, optimizing the estimate induced by the shelling is an important computational subproblem.
 
@@
 
-36.7821067  160.0052039 160.7339833
-
 \section{Outlook}\label{section:outlook}

### 2025-01-30 main.tex
further data
Update on Overleaf.

@@
 
+\begin{remark}\label{remark:mixedbconsimplex:hilbert}
+    We can improve Lemma~\ref{lemma:mixedbconsimplex} in the special case $p=2$.
+    The variational formulation of the Poincar\'e constant over a convex domain reveals that $C_{\PF,T,F,p}$ lies between the the Poincar\'e constant without boundary conditions and with full boundary conditions.
+    In particular,
+    \begin{align*}
+        C_{\PF,T,F,2} 
+        \leq 
+        \frac{ \diam(T) }{ \pi }
+    \end{align*}
+    is an improved Poincar\'e inequality.
+\end{remark}
+
 The next auxiliary result establishes Poincar\'e--Friedrichs constants over face patches within simplicial triangulations. 
@@
     \begin{gather*}
-        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
+        \| w \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
     \end{gather*}
-    Whenever $T_0, T_1, \dots, T_M$ is a face path,
-    then for all $1 \leq m \leq$ the following recursive estimates:
+    For any $n$-simplex $T_M \in \calT$ there exists a face path $T_0, T_1, \dots, T_M$
+    such that for all $1 \leq m \leq$ we have one of the following recursive estimates:
     \begin{align*}
@@
         \leq  
-        \volumeratio(\calT)^{\frac 1 p} 
+        A_{m}
         \| w \|_{L^{p}(T_{m-1})} 
         +
-%         C_{\PF,T_{m},F_{m},p} 
-%         \left( 
-%             \| \nabla u \|_{L^{p}(T_{m})} 
-%             + 
-%             \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
-%             \| \nabla u \|_{L^{p}(T_{m-1})}
-%         \right)
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \reflectionestimate(\calT)^{q} \right)^{\frac 1 q}
+        B'_{m}
+        \| \nabla u \|_{L^{p}(T_{m  })} 
+        + 
+        B''_{m}
+        \| \nabla u \|_{L^{p}(T_{m-1})} 
+        ,
+        \\
+        \| w \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        A_{m}
+        \| w \|_{L^{p}(T_{m-1})} 
+        +
+        B^\star_{m}
+        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
+        , 
+    \end{align*}
+    where 
+    \begin{gather*}
+        A_{m} 
+        \leq
+        \volumeratio(\calT)^{\frac 1 p} 
+        ,
+        \quad 
+        B'_{m} 
+        \leq 
         C_{\PF,T_{m},F_{m},p} 
-        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
-        ,
-        \\
-        \| w \|_{L^{p}(T_m)}
-        &\leq 
-        \volumeratio(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(T_{{m-1}})}
-        +
+        ,
+        \quad 
+        B''_{m} 
+        \leq 
+        C_{\PF,T_{m},F_{m},p} \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT) 
+        ,
+        \\
+        B_{m}^\star
+        \leq 
         \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Makoto_{F_m},p} 
-        \| \nabla u \|_{L^{p}(\Makoto_{F_m})} 
-        . 
-    \end{align*}
+        C_{{\PF},\Makoto_{F_\ell},p} 
+        .
+    \end{gather*}
     Here, for any $1 \leq m \leq M$, let $F_m = T_m \cap T_{m-1}$.
@@
     By construction $w_{|T_{0}} = w_0$. 
-    We verify that $w$ satisfies the two desired recursive estimates.
+    We verify that $w$ can be chosen such that it satisfies the desired recursive estimates.
     Suppose that $T_0, T_1, \dots, T_M$ is a face path in $\calT$
@@
 
-    We proceed with the first recursive estimate. 
+    We study two constructions, beginning as follows. 
     We define $w'_{m} := w_{|T_{m-1}} \circ \Xi \in W^{1,p}(T_{m})$,
@@
         \right) 
+        \\&
         \leq 
@@
         \leq 
-        \volumeratio(\calT)^{\frac 1 p} \reflectionestimate(\calT)
+        \left( \frac{ \vol(T_m) }{ \vol(T_{m-1}) } \right)^{\frac 1 p}
+        \reflectionestimate(\calT)
         \| \nabla w \|_{L^{p}(T_{m-1})}
-        \\&
+        %\\&
         =
@@
     \end{align*}
-    We now use H\"older's inequality. 
     Therefrom, the first recursive estimate follows.
@@
         \| w \|_{L^{p}(T_m)}
-        &\leq 
+        &
+        \leq 
         \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
@@
         \| w \|_{L^{p}(T_{{m-1}})}
-        \\&\leq 
+        \\&
+        = 
         \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
@@
 
-\begin{corollary}
-    Under the assumptions of Theorem~\ref{theorem:poincarefriedrichsestimate:grad},
-    whenever $T_0, T_1, \dots, T_m$ is a face-path of $n$-simplices in $\calT$,
-    we have 
-    \begin{align*}
-        \| w \|_{L^{p}(T_m)}
+The recursive construction of a gradient potential in the previous theorem, marching from simplex to simplex, can be associated with a concept of graph theory.
+Indeed, the face-neighbor relationship between adjacent $n$-simplices gives rise to an undirected graph that we call \emph{face-connection graph}.
+If the potential is constructed starting from an initial $n$-simplex $T_0$, then the sequence of simplices corresponds to a path in that graph.
+In practice, we will pick a spanning tree for the undirected graph to describe the construction of the potentials.
+
+We use that formalism to describe an estimate for the Poincar\'e--Friedrichs constant of the gradient potential, unwrapping the recursion.
+
+\begin{theorem}\label{theorem:globalestimate:gradient}
+    Let $\calT$ be a face-connected $n$-dimensional finite triangulation
+    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
+    Let $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
+    and suppose that $u, w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
+
+    Suppose that $n$-simplices are enumerated as $T_0, T_1, \dots, T_M$,
+    and that with each $n$-simplex $T_{m} \in \calT$ 
+    we have a sequence of indices 
+    \begin{gather*}
+        0 = \imath_{m,0}, \; \imath_{m,1}, \; \dots, \; \imath_{m,L_m} = m
+    \end{gather*}
+    such that for each $0 \leq m \leq M$ we have estimates of the following form:
+    \begin{align*}
+        \| w \|_{L^{p}(T_{0})} &\leq A_{m,0} \| \nabla u \|_{L^{p}(T_{0})}
+        ,
+        \\
+        \| w \|_{L^{p}(T_{m,\ell})}
         &\leq  
-        \sum_{\ell=1}^{m} 
-        \volumeratio^{\frac{m-\ell}{p}}
-        \min\left( 
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
-        C_{{\PF},\Makoto_{F_\ell},p} 
-        ,
-        \left( 1 + \volumeratio(\calT)^{\frac q p} \reflectionestimate(\calT)^{q} \right)^{\frac 1 q}
-        C_{\PF,T_{\ell},F_{\ell},p} 
-        \right)
-        \| \nabla u \|_{L^{p}(\Makoto_{F_\ell})}
-        \\&
-        \qquad 
-        \qquad 
+        A_{m,\ell}
+        \| w \|_{L^{p}(T_{m,\ell-1})} 
         +
-        \volumeratio^{\frac m p}
-        C_{{\PF},T_{0},p}
-        \| \nabla u \|_{L^{p}(T_{0})}
-        .
-    \end{align*}
-\end{corollary}
+        B'_{m,\ell}
+        \| \nabla u \|_{L^{p}(T_{m,\ell  })} 
+        + 
+        B''_{m,\ell}
+        \| \nabla u \|_{L^{p}(T_{m,\ell-1})}, 
+        \qquad 1 \leq \ell \leq L_m
+        .
+    \end{align*}
+    % TODO: complete here. We need a spanning tree. 
+\end{theorem}
 \begin{proof}
-    This follows by repeated application of the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-\end{proof}
-
-\begin{remark}\label{remark:fullrecursivesum}
-    \color{red}
-    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    The potential $w$ for the gradient $\nabla u$ satisfies 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
-        \qquad 
-        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
-        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
-    \end{align*}
-    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
     Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
     \begin{align}\label{math:fullrecursivesum}
+        \begin{split}
             \| w \|_{L^{p}(T_{m})} 
@@
             \leq 
-        \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+            \sum_{\ell=0}^{m}   \left( B_{m,m} \cdots B_{m,\ell+1} \right) A_{m,\ell} \| \nabla u \|_{L^{p}(T_{m,\ell})}
             +
-        \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
+            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) A'_{m,\ell+1} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \\&
+            = 
+            A_{m,m} \| \nabla u \|_{L^{p}(T_{m,m})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) \left( B_{m,\ell+1} A_{m,\ell} + A'_{m,\ell+1} \right) \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \\&
             =:
@@
             .
+        \end{split}
     \end{align}
     Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    By definition, $C_{m,0} = A_0$, and 
+    \begin{align}
+        C_{m,}
+    \end{align}
+
     The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
     \begin{align*}
+        \begin{split}
             \| w \|_{L^{p}(\Omega)}^{p}
@@
             \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
+            \\&
+            \leq 
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p}
+            \\&
             \leq 
@@
             ,
+        \end{split}
     \end{align*}
     where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+\end{proof}
+
+\begin{remark}\label{remark:fullrecursivesum}
+    \color{red}
+    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+    The potential $w$ for the gradient $\nabla u$ satisfies 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
+        \qquad 
+        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
+        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
+    \end{align*}
+    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
+
+    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
+    \begin{align}\label{math:fullrecursivesum}
+        \begin{split}
+            \| w \|_{L^{p}(T_{m})} 
+            &
+            \leq 
+            \sum_{\ell=0}^{m}   \left( B_{m,m} \cdots B_{m,\ell+1} \right) A_{m,\ell} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) A'_{m,\ell+1} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \\&
+            = 
+            A_{m,m} \| \nabla u \|_{L^{p}(T_{m,m})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) \left( B_{m,\ell+1} A_{m,\ell} + A'_{m,\ell+1} \right) \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \\&
+            =:
+            \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+            .
+        \end{split}
+    \end{align}
+    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    By definition, $C_{m,0} = A_0$, and 
+    \begin{align}
+        C_{m,}
+    \end{align}
+
+    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \begin{split}
+            \| w \|_{L^{p}(\Omega)}^{p}
+            &
+            \leq 
+            \sum_{m=0}^{M}
+            \| w \|_{L^{p}(T_{m})}^{p}
+            \\&
+            \leq 
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p}
+            \\&
+            \leq 
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \sum_{\ell=0}^{M} 
+            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+            \leq 
+            \left(
+                \sum_{m=0}^{M}
+                \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+            \right)
+            \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+            ,
+        \end{split}
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$.
+
     In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
@@
                                                   & $\grad$           & $\curl$           & $\divergence$   \\ \hline
-        $\Gamma = F_0 \cup F_1 \cup F_2 \cup F_3$ & 0.08625017654     & 0.1453729386      & 0.2601720480    \\ \hline
+        $\Gamma = F_0 \cup F_1 \cup F_2 \cup F_3$ & 0.0862501765      & 0.1453729386      & 0.2601720480    \\ \hline
         $\Gamma =          F_1 \cup F_2 \cup F_3$ & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
@@
         $\Gamma =                            F_3$ & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
-        $\Gamma =                      \emptyset$ & 0.2631059409      & 0.1458215887      & 0.08740665548   \\ \hline
+        $\Gamma =                      \emptyset$ & 0.2631059409      & 0.1458215887      & 0.0874066554    \\ \hline
     \end{tabular}
@@
     Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} 
-    give the improved upper bound $2/\pi \approx 0.45015815807$.
+    give the upper bound $2/\pi \cdot \diam(\Delta^3) \approx 0.90031631615$.
     }\label{table:referencepoincarefriedrichs}
@@
         \hline
-        $\calT_{Q}$     & 0.318        &             &               & 1.559       & 3.141              & 0.225              & 1.559              &  6.928              \\ 
+        $\calT_{Q}$     & 0.318        & 1.684337597 &               & 1.684337582       & 3.141        & 0.225              & 1.684337545        &  6.928              \\ 
         \hline
-        $\calT_{L}$     & 0.822        &             &               & 2.382       & 2.895              & 0.322              & 2.382              &  7.402              \\ 
+        $\calT_{L}$     & 0.822        & 5.079960342 &               & 2.382       & 2.895              & 0.322              & 2.382              &  7.402              \\ 
         \hline
@@
         \hline
-        $\calT_{C,5}$     &              &             &                    & 36.7821067   &                    \\ 
+        $\calT_{B,5}$   & 1.022627161  &             &                    & 36.7821067   & 35.96824737574127  \\ 
+        \hline
+        $\calT_{B}$     & 1.022627161  &             &                    & 62.40578125  & 61.02495966269372  \\ 
+        \hline
+        $\calT_{F}$     & 0.7117133306 &             &                    & 325.7340627  & 18796.92616132183  \\ 
         \hline
@@
         \hline
-        $\calT_{C,5}$   &              & 160.0052039 &                   & 36.7821067        & 160.7339833       &                     \\ 
+        $\calT_{B,5}$   & 0.3315710272 & 160.0052039 & 482.5669036190229 & 0.2330604743      & 160.7339833       & 689.6664212985330   \\ 
+        \hline
+        $\calT_{B}$     & 0.3315710272 & 572.3519405 & 1726.182004903473 & 0.2330604743      & 510.806374        & 2191.733177984011   \\ 
+        \hline
+        $\calT_{F}$     & 0.5549678737 & 13378.02292 & 24105.94118711908 & 0.3106774562      & 11705.58269       & 37677.60567703448   \\ 
         \hline

### 2025-01-30 draft.tex
items on TODO list

@@
 \tableofcontents
+
+\section{Remark on global estimate: gradient}
+
+\begin{remark}\label{remark:fullrecursivesum}
+    \color{red}
+    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+    The potential $w$ for the gradient $\nabla u$ satisfies 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
+        \qquad 
+        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
+        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
+    \end{align*}
+    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
+    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
+    \begin{align}\label{math:fullrecursivesum}
+        \begin{split}
+            \| w \|_{L^{p}(T_{m})} 
+            &
+            \leq 
+            \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
+            \\&
+            \leq 
+            A_{m} \| \nabla u \|_{L^{p}(T_{m})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) \left( B_{\ell+1} A_{\ell} + A'_{\ell+1} \right) \| \nabla u \|_{L^{p}(T_{\ell})}
+            \\&
+            =:
+            \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+            .
+        \end{split}
+    \end{align}
+    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    By definition, $C_{m,0} = A_0$, and 
+    \begin{align}
+        C_{m,}
+    \end{align}
+
+    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \begin{split}
+            \| w \|_{L^{p}(\Omega)}^{p}
+            &
+            \leq 
+            \sum_{m=0}^{M}
+            \| w \|_{L^{p}(T_{m})}^{p}
+            \\&
+            \leq 
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \sum_{\ell=0}^{M} 
+            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+            \leq 
+            \left(
+                \sum_{m=0}^{M}
+                \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+            \right)
+            \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+            ,
+        \end{split}
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
+\end{remark}
+
+\section{Old contraction results, now turned into a remark}
+
+% 6. Contractible 
+Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
+Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
+Their bi-Lipschitz constants are controlled by the shape regularity of the domain. 
+This reduces the construction of potentials over shellable triangulations to the construction of potentials over convex domains.
+We refer to Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} as the main result of this approach.
+
+\color{red}
+\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
+    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
+    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
+    such that 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
+        \leq 
+%         \left( 
+%             \Cachttrafo{n}{k}{\ell}(\calT)
+            % \Cacht{n}{k}(\calT)
+            % \Cachtprime{n}{k}(\calT)^{k} 
+            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+%             \Csiebtrafo{n}{k}{\ell}(\calT)
+            % \Csieb{n}{k}(\calT)
+            % \Csiebprime{n}{k}(\calT)^{k-1} 
+            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+%         \right)^{M}
+        \left( 
+        \prod_{m=1}^{M}
+            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
+            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
+        \right)
+        C_{{\PF},k,T_{0},p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        ,
+    \end{align*}
+    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell_{m}$ faces in common with the previous simplices.
+\end{theorem}
+\begin{proof}
+    We prove this via induction. 
+    The statement is clearly satisfied when $M=0$ because then we only consider a single simplex,
+    so that the Poincar\'e--Friedrichs inequality over a simplex can be used. 
+    Let us assume that the statement is true for some integer $M-1 \geq 0$.
+
+    Recall that $X_M$ is an $n$-dimensional submanifold with boundary with a triangulation that has a shelling $T_0, T_1, \dots, T_{M-1}$. 
+    Write $\Omega' \subseteq X_{M}$ for the interior domain of that manifold. 
+    By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
+    and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star. 
+    We let $\ell_{M}$ be the dimension of $S_{M}$.
+
+    We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Makoto_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
+    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{M-1} \setminus \partial T$.
+    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.
+
+    Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
+    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
+    \begin{align*}
+        \| g' \|_{L^{p}(\Omega')}  
+        \leq 
+        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
+        %\Cacht{n}{k}(\calT)
+        %\Cachtprime{n}{k}(\calT)^{k} 
+        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
+        \| g \|_{L^{p}(\Omega)}  
+        .
+    \end{align*}
+    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
+%     We have 
+%     \begin{align*}
+%         \| w' \|_{L^{p}(\Omega')} 
+%         \leq 
+%         \left( 
+%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
+%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
+%         \right)^{M-1}
+%         C_{{\PF},k,T_{0},p}
+%         \| g' \|_{L^{p}(\Omega')}  
+%     \end{align*}
+    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
+    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}  
+        \leq 
+        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
+        %\Csieb{n}{k}(\calT)
+        %\Csiebprime{n}{k}(\calT)^{k-1} 
+        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
+        \| w' \|_{L^{p}(\Omega')} 
+    \end{align*}
+    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
+\end{proof}
+\color{black}
 

### 2025-01-30 main.tex
items on TODO list

--- 2025-01-22 main.tex
@@
 With respect to our main interest, local patches (stars) in 2D and 3D triangulations are shellable.
-
-% 6. Contractible 
-Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
-Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
-Their bi-Lipschitz constants are controlled by the shape regularity of the domain. 
-This reduces the construction of potentials over shellable triangulations to the construction of potentials over convex domains.
-We refer to Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} as the main result of this approach.
 
@@
     \begin{align}\label{math:fullrecursivesum}
+        \begin{split}
             \| w \|_{L^{p}(T_{m})} 
@@
             \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
+            \\&
+            \leq 
+            A_{m} \| \nabla u \|_{L^{p}(T_{m})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) \left( B_{\ell+1} A_{\ell} + A'_{\ell+1} \right) \| \nabla u \|_{L^{p}(T_{\ell})}
+            \\&
             =:
@@
             \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
+            \\&
             \leq 
@@
             ,
+        \end{split}
     \end{align*}
@@
 %
+
+\begin{remark}
+    As already explained in the original paper~\cite{costabel2010bogovskiui}, the operators $\Poinc_{\mia}$ preserve polynomial differential forms. 
+\end{remark}
 
@@
 
-\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
+\begin{remark}\label{remark:poincarefriedrichsestimate:exterior:contraction}
+    We would like to point out an alternative application of Proposition~\ref{proposition:starreflection},
+    using the second class of transformations. 
+    Those transformations are a sequence of contractions.
+    Here, we take inspiration from the topological observation that domains with shellable triangulations are contractible. 
+    More specifically, we have seen that every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations, and their bi-Lipschitz constants are controlled by the shape regularity of the triangulation.
+
+    Using successive pullbacks along those contractions, the original problem of finding a potential over the domain is reduced to finding a potential for some right-hand side over the first simplex of the shelling.
+    The potential over that first simplex is then extended along successive reverse pullbacks to the whole domain. 
+    Using the Poincar\'e--Friedrichs constant over the first simplex and pullback estimates (Proposition~\ref{proposition:pullbackestimate}),
+    one obtains the following estimate.
+
     Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
-    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$
+    and let $0 \leq \ell_{m} < n$, for $1 \leq m \leq M$, be such that $T_{m}$ has $n - \ell_{m}$ faces in common with the previous simplices.
     Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
@@
         \| \cartan u \|_{L^{p}(\Omega)}
-        ,
-    \end{align*}
-    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices.
-\end{theorem}
-\begin{proof}
-    We prove this via induction. 
-    The statement is clearly satisfied when $M=0$ because then we only consider a single simplex,
-    so that the Poincar\'e--Friedrichs inequality over a simplex can be used. 
-    Let us assume that the statement is true for some integer $M-1 \geq 0$.
-
-    Recall that $X_M$ is an $n$-dimensional submanifold with boundary with a triangulation that has a shelling $T_0, T_1, \dots, T_{M-1}$. 
-    Write $\Omega' \subseteq X_{M}$ for the interior domain of that manifold. 
-    By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
-    and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star. 
-    We let $\ell_{M}$ be the dimension of $S_{M}$.
-
-    We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Makoto_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
-    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{M-1} \setminus \partial T$.
-    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.
-
-    Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
-    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
-    \begin{align*}
-        \| g' \|_{L^{p}(\Omega')}  
-        \leq 
-        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
-        %\Cacht{n}{k}(\calT)
-        %\Cachtprime{n}{k}(\calT)^{k} 
-        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
-        \| g \|_{L^{p}(\Omega)}  
-        .
-    \end{align*}
-    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
-%     We have 
-%     \begin{align*}
-%         \| w' \|_{L^{p}(\Omega')} 
-%         \leq 
-%         \left( 
-%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
-%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
-%         \right)^{M-1}
-%         C_{{\PF},k,T_{0},p}
-%         \| g' \|_{L^{p}(\Omega')}  
-%     \end{align*}
-    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
-    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}  
-        \leq 
-        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
-        %\Csieb{n}{k}(\calT)
-        %\Csiebprime{n}{k}(\calT)^{k-1} 
-        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
-        \| w' \|_{L^{p}(\Omega')} 
-    \end{align*}
-    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
-\end{proof}
+        .
+    \end{align*}
+    However, in our numerical examples (see Section~\ref{section:numericalexamples}), 
+    the estimate performs significantly worse than the estimate derived in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior},
+    which is why we choose to not deploy this method in our computations. 
+\end{remark}
 
@@
 These data are tabulated in Table~\ref{table:referencepoincarefriedrichs}. 
+This example conforms to the well-known fact that the eigenvalues of the scalar Laplacian with mixed boundary conditions are between the Neumann and Dirichlet eigenvalues, which follows from a known variational principle.
+However, such an enclosure does not seem to hold for the vector Laplacians with mixed boundary conditions.
 
@@
 
-However, the results indicate significant room for improvement. 
+However, the results indicate room for improvement. 
 Future estimates should tighten the gap towards the actual computed values,
@@
 
-We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
+We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
 Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
@@
 The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
-Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
 

### 2025-01-30 draft.tex
explicit potential in main theorem

@@
 \tableofcontents
+
+\section{....}
+
+\begin{proof}
+    We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
+    We define 
+    \begin{align*}
+        w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m}).
+    \end{align*}
+    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
+    \begin{align*}
+        \trace_F w_{m-1} = \trace_F w'_{m}
+        . 
+    \end{align*}
+    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
+    \begin{align*}
+        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
+        \quad 
+        \trace_{\Gamma_{m}} w''_{m} = 0.
+    \end{align*}
+    Indeed, such $w''_{m}$ exists because 
+    \begin{align*}
+        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
+        &= 
+        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
+        \\&= 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
+        = 
+        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
+        = 
+        0
+        .
+    \end{align*}
+    Setting $w_{m} := w_{m-1}$ over $X_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
+    we find 
+    \begin{gather*}
+        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
+        \\
+        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
+    \end{gather*}
+    That means that $w_{m} \in W^{p}\Alt^{k}(X_{m})$ with $\cartan w_{m} = \cartan u$ over $X_{m}$.
+
+    We want to estimate norms. By the triangle inequality, 
+    \begin{align*}
+        \| w_{m} \|_{L^{p}(T_{m})}
+        \leq  
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        + 
+        \| w''_{m} \|_{L^{p}(T_{m})}
+        .
+    \end{align*}
+    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
+    we can assume that $w''_{m}$ satisfies 
+    \begin{align*}
+        \| w''_{m} \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
+        \\&
+        \leq 
+        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
+        + 
+        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        .
+    \end{align*}
+    Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} now show 
+    % \begin{align*}
+        % \| w'_{m} \|_{L^{p}(T_{m})}
+        % &\leq 
+        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k}
+        % \|\det \Jacobian \Xi_{1}^{-1}  \|_{L^{\infty}(\Makoto_{m-1})}^{\frac 1 p} 
+        % \cdot 
+        % \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
+        % ,
+        % \\
+        % \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        % &\leq 
+        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k+1}
+        % \|\det \Jacobian \Xi_{1}^{-1}  \|^{\frac 1 p}_{L^{\infty}(\Makoto_{m-1})} 
+        % \cdot 
+        % \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
+        % .
+    % \end{align*}
+    \begin{align*}
+        \| w'_{m} \|_{L^{p}(T_{m})}
+        &\leq 
+        \Cfivetrafo{n}{k}{\ell}{p}(\calT)
+        % \Cfive{n}{k}(\calT)
+        % \Cfiveprime{n}{k}(\calT)^{k-1}
+        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
+        \cdot 
+        \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
+        ,
+        \\
+        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        &\leq 
+        \Cfivetrafo{n}{k+1}{\ell}{p}(\calT)
+        % \Cfive{n}{k}{\ell}(\calT)
+        % \Cfiveprime{n}{k}(\calT)^{k}
+        % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
+        \cdot 
+        \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
+        .
+    \end{align*}
+    We have assumed that $\cartan w_{m-1} = \cartan u_{|X_{m-1}}$. 
+    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
+\end{proof}
 

### 2025-01-30 main.tex
explicit potential in main theorem

@@
     \end{gather*}
-    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ 
-    with $\cartan w_{m-1} = \cartan u$ over $X_{m-1}$. 
+    Suppose that $0 < m \leq M$ such that there exists $w_{m-1} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w_{m-1} = \cartan u$ over $X_{m-1}$. 
+    This is already true for $m = 1$.
     By assumption, $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
@@
 
-    We introduce the reflection mapping $\Xi_{1} : T_{m} \rightarrow \Makoto_{m-1}$ of Proposition~\ref{proposition:starreflection}. 
-    We define 
-    \begin{align*}
-        w'_{m} :=  \Xi_{1}^{\ast} w_{m-1} \in W^{p}\Alt^{k}(T_{m}).
-    \end{align*}
-    By construction, $w'_{m} \in W^{p}\Alt^{k}(T_{m})$ with 
-    \begin{align*}
-        \trace_F w_{m-1} = \trace_F w'_{m}
-        . 
-    \end{align*}
-    There exists $w''_{m} \in W^{p}\Alt^{k}(T_{m})$ satisfying 
-    \begin{align*}
-        \cartan w''_{m} = \cartan u - \cartan w'_{m}, 
-        \quad 
-        \trace_{\Gamma_{m}} w''_{m} = 0.
-    \end{align*}
-    Indeed, such $w''_{m}$ exists because 
-    \begin{align*}
-        \trace_{\Gamma_{m}}( \cartan u - \cartan w'_{m} ) 
-        &= 
-        \trace_{\Gamma_{m}} \cartan u - \trace_{\Gamma_{m}} \cartan w'_{m}
-        \\&= 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w'_{m}
-        = 
-        \cartan \trace_{\Gamma_{m}} u - \cartan \trace_{\Gamma_{m}} w_{m-1}
-        = 
-        0
-        .
-    \end{align*}
-    Setting $w_{m} := w_{m-1}$ over $X_{m-1}$ and $w_{m} := w'_{m} + w''_{m}$ over $T_{m}$, 
-    we find 
-    \begin{gather*}
-        \cartan w_{m} = \cartan w'_{m} + \cartan w''_{m} = \cartan w'_{m} + \cartan u - \cartan w'_{m} = \cartan u,
-        \\
-        \trace_{\Gamma_{m}} w_{m} = \trace_{\Gamma_{m}} w'_{m} = \trace_{\Gamma_{m}} w_{m-1}.
-    \end{gather*}
-    That means that $w_{m} \in W^{p}\Alt^{k}(X_{m})$ with $\cartan w_{m} = \cartan u$ over $X_{m}$.
-
-    We want to estimate norms. By the triangle inequality, 
-    \begin{align*}
-        \| w_{m} \|_{L^{p}(T_{m})}
-        \leq  
-        \| w'_{m} \|_{L^{p}(T_{m})}
+    We now define, as in~\cite[Equations~{\char`\(}5.12{\char`\)} and~{\char`\(}5.14{\char`\)}]{ern2020stable} or~\cite[equations~{\char`\(}6.7{\char`\)} and~{\char`\(}6.9{\char`\)}]{Chaum_Voh_p_rob_3D_H_curl_24}, the field $\widetilde w_{m} \in W^{p}\Alt^{k}(T_{m})$ via
+    \begin{align} \label{equation:w''_ext_der}
+        {\widetilde w}_{m} := u_{|T_m} + \Xi_{1}^{\ast}\left( (w_{m-1} - u)_{|\Makoto_{m-1} } \right).
+    \end{align}
+    One verifies that 
+    \begin{align*}
+        \trace_F {\widetilde w}_{m} 
+        &
+        = 
+        \trace_F u_{|T_m} + \trace_F \Xi_{1}^{\ast} w_{m-1|\Makoto_{m-1} } - \trace_F \Xi_{1}^{\ast} u_{|\Makoto_{m-1} } 
+        \\&
+        = 
+        \trace_F u_{|T_m} + \trace_F \Xi_{1}^{\ast} w_{m-1|\Makoto_{m-1} } - \trace_F \Xi_{1}^{\ast} u_{|\Makoto_{m-1} } 
+        \\&
+        = 
+        \trace_F \Xi_{1}^{\ast} w_{m-1|\Makoto_{m-1} }
+        \\&
+        = 
+        \trace_F w_{m-1|\Makoto_{m-1}}
+        .
+    \end{align*}
+    Moreover, 
+    \begin{align*}
+        \cartan {\widetilde w}_{m} 
+        &
+        = 
+        \cartan u_{|T_m} + \cartan \Xi_{1}^{\ast} w_{m-1|\Makoto_{m-1} } - \cartan \Xi_{1}^{\ast} u_{|\Makoto_{m-1} } 
+        \\&
+        = 
+        \cartan u_{|T_m} + \Xi_{1}^{\ast} \cartan w_{m-1|\Makoto_{m-1} } - \Xi_{1}^{\ast} \cartan u_{|\Makoto_{m-1} } 
+        = 
+        \cartan u_{|T_m}
+        .
+    \end{align*}
+    Setting $w_{m} := w_{m-1}$ over $X_{m-1}$ and $w_{m} := {\widetilde w}_{m} + w''_{m}$ over $T_{m}$, 
+    we thus verify $w_{m} \in W^{p}\Alt^{k}(X_{m})$ with $\cartan w_{m} = \cartan u$ over $X_{m}$.
+
+    We want to estimate norms. 
+    By construction,
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        \leq  
+        \| \Xi_{1}^{\ast} w_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})}
         + 
-        \| w''_{m} \|_{L^{p}(T_{m})}
+        \| u - \Xi_{1}^{\ast} u_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})}
         .
@@
     Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, 
-    we can assume that $w''_{m}$ satisfies 
-    \begin{align*}
-        \| w''_{m} \|_{L^{p}(T_{m})} 
+    which applies since $\trace_{\Gamma_{m}} \left( u_{|T_m} - \Xi_{1}^{\ast} u_{|\Makoto_{m-1}} \right) = 0$, 
+    we have
+    \begin{align*}
+        \| u - \Xi_{1}^{\ast} u_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})} 
         &
         \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
+        C_{\PF,T_{m},\Gamma_{m-1},k,p} 
+        \left( 
+            \| \cartan u \|_{L^{p}(T_{m})} + \| \cartan \Xi_{1}^{\ast} u_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})} 
+        \right)
         \\&
         \leq 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
-        + 
-        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
+        C_{\PF,T_{m},\Gamma_{m-1},k,p} 
+        \left( 
+            \| \cartan u \|_{L^{p}(T_{m})} + \| \Xi_{1}^{\ast} \cartan u_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})} 
+        \right)
         .
@@
     Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} now show 
-    % \begin{align*}
-        % \| w'_{m} \|_{L^{p}(T_{m})}
-        % &\leq 
-        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k}
-        % \|\det \Jacobian \Xi_{1}^{-1}  \|_{L^{\infty}(\Makoto_{m-1})}^{\frac 1 p} 
-        % \cdot 
-        % \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
-        % ,
-        % \\
-        % \| \cartan w'_{m} \|_{L^{p}(T_{m})}
-        % &\leq 
-        % \| \Jacobian \Xi_{1} \|_{L^{\infty}(T_{m})}^{k+1}
-        % \|\det \Jacobian \Xi_{1}^{-1}  \|^{\frac 1 p}_{L^{\infty}(\Makoto_{m-1})} 
-        % \cdot 
-        % \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
-        % .
-    % \end{align*}
-    \begin{align*}
-        \| w'_{m} \|_{L^{p}(T_{m})}
+    \begin{align*}
+        \| \Xi_{1}^{\ast} w_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})}
         &\leq 
@@
         % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
-        \cdot 
         \| w_{m-1} \|_{L^{p}(\Makoto_{m-1})}
@@
         \\
-        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
+        \| \Xi_{1}^{\ast} \cartan u_{|\Makoto_{m-1}} \|_{L^{p}(T_{m})}
         &\leq 
@@
         % \Cdetsechs{n}{k}(\calT)^{\frac 1 p}
-        \cdot 
         \| \cartan w_{m-1} \|_{L^{p}(\Makoto_{m-1})}

### 2025-01-31 main.tex
recursive estimate

@@
 We use that formalism to describe an estimate for the Poincar\'e--Friedrichs constant of the gradient potential, unwrapping the recursion.
+While the notation is a bit technical, the underlying idea is this:
+Unrolling the recursion gives estimates for the potential over a simplex in terms of the potential over previous simplices. 
+The final constant can be estimated by a norm of the vector of the coefficients that appear in the recursion.
 
@@
     \begin{gather*}
-        0 = \imath_{m,0}, \; \imath_{m,1}, \; \dots, \; \imath_{m,L_m} = m
+        0 = \imath(m,0), \; \imath(m,1), \; \dots, \; \imath(m,L_m) = m
     \end{gather*}
@@
         ,
-        \\
-        \| w \|_{L^{p}(T_{m,\ell})}
+    \end{align*}
+    \begin{align*}
+        \| w \|_{ L^{p}(T_{\imath(m,\ell)}) }
         &\leq  
-        A_{m,\ell}
-        \| w \|_{L^{p}(T_{m,\ell-1})} 
+        A_{m,\imath(m,\ell)}
+        \| w \|_{ L^{p}(T_{\imath(m,\ell-1)}) }
+        \\&\qquad 
         +
-        B'_{m,\ell}
-        \| \nabla u \|_{L^{p}(T_{m,\ell  })} 
+        B'_{m,\imath(m,\ell)}
+        \| \nabla u \|_{ L^{p}(T_{\imath(m,\ell)}) }
         + 
-        B''_{m,\ell}
-        \| \nabla u \|_{L^{p}(T_{m,\ell-1})}, 
-        \qquad 1 \leq \ell \leq L_m
+        B''_{m,\imath(m,\ell)}
+        \| \nabla u \|_{ L^{p}(T_{\imath(m,\ell-1)}) }
+        ,
+        \quad 1 \leq \ell \leq L_m
+        .
+    \end{align*}
+    Then 
+    \begin{gather*}
+        \| w \|_{ L^{p}(\Omega) }
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{L_m} D_{m,\ell}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \| \nabla u \|_{ L^{p}(\Omega) }
+        ,
+    \end{gather*}
+    where 
+    \begin{gather*}
+        D_{m,L_m} = A_{m,m},
+        \\
+        D_{m,\ell} 
+        = 
+        \left( B_{m,\imath(m,L_m)} \cdots B_{m,\imath(m,\ell+2)} \right) 
+        \left( B_{m,\imath(m,\ell+1)} A_{m,\imath(m,\ell)} + A'_{m,\imath(m,\ell+1)} \right) 
+        ,
+        \qquad 
+        1 \leq \ell \leq L_{m}-1
         .
@@
     Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
-    \begin{align}\label{math:fullrecursivesum}
+    \begin{align*}%\label{math:fullrecursivesum}
         \begin{split}
@@
             \leq 
-            \sum_{\ell=0}^{m}   \left( B_{m,m} \cdots B_{m,\ell+1} \right) A_{m,\ell} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \sum_{\ell=0}^{L_m}   \left( B_{m,\imath(m,L_m)} \cdots B_{m,\imath(m,\ell+1)} \right) A_ {m,\imath(m,\ell  )} \| \nabla u \|_{L^{p}(T_{\imath(m,\ell)})}
+            \\&\qquad 
             +
-            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) A'_{m,\ell+1} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \sum_{\ell=0}^{L_m-1} \left( B_{m,\imath(m,L_m)} \cdots B_{m,\imath(m,\ell+2)} \right) A'_{m,\imath(m,\ell+1)} \| \nabla u \|_{L^{p}(T_{\imath(m,\ell)})}
             \\&
             = 
-            A_{m,m} \| \nabla u \|_{L^{p}(T_{m,m})}
+            A_{m,m} \| \nabla u \|_{L^{p}(T_{\imath(m,L_m)})}
+            \\&\qquad 
             +
-            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) \left( B_{m,\ell+1} A_{m,\ell} + A'_{m,\ell+1} \right) \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \sum_{\ell=0}^{L_m-1} 
+            \left( B_{m,\imath(m,L_m)} \cdots B_{m,\imath(m,\ell+2)} \right) 
+            \left( B_{m,\imath(m,\ell+1)} A_{m,\imath(m,\ell)} + A'_{m,\imath(m,\ell+1)} \right) 
+            \| \nabla u \|_{L^{p}(T_{\imath(m,\ell)})}
             \\&
@@
         \end{split}
-    \end{align}
+    \end{align*}
     Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    By definition, $C_{m,0} = A_0$, and 
-    \begin{align}
-        C_{m,}
-    \end{align}
-
     The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
@@
             \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \sum_{\ell=0}^{M} 
-            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+            \sum_{\ell'=0}^{M} \| \nabla u \|_{L^{p}(T_{\ell'})}^{p} 
             \leq 

### 2025-01-31 main.tex
recursive estimate

@@
 
-\begin{theorem}\label{theorem:globalestimate:gradient}
+\begin{theorem}\label{theorem:fullrecursivesum:grad}
     Let $\calT$ be a face-connected $n$-dimensional finite triangulation
@@
         .
-    \end{align*}
-    % TODO: complete here. We need a spanning tree. 
+    \end{gather*}
 \end{theorem}
@@
 \end{proof}
-
-\begin{remark}\label{remark:fullrecursivesum}
-    \color{red}
-    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    The potential $w$ for the gradient $\nabla u$ satisfies 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
-        \qquad 
-        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
-        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
-    \end{align*}
-    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
-
-    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
-    \begin{align}\label{math:fullrecursivesum}
-        \begin{split}
-            \| w \|_{L^{p}(T_{m})} 
-            &
-            \leq 
-            \sum_{\ell=0}^{m}   \left( B_{m,m} \cdots B_{m,\ell+1} \right) A_{m,\ell} \| \nabla u \|_{L^{p}(T_{m,\ell})}
-            +
-            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) A'_{m,\ell+1} \| \nabla u \|_{L^{p}(T_{m,\ell})}
-            \\&
-            = 
-            A_{m,m} \| \nabla u \|_{L^{p}(T_{m,m})}
-            +
-            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) \left( B_{m,\ell+1} A_{m,\ell} + A'_{m,\ell+1} \right) \| \nabla u \|_{L^{p}(T_{m,\ell})}
-            \\&
-            =:
-            \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
-            .
-        \end{split}
-    \end{align}
-    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    By definition, $C_{m,0} = A_0$, and 
-    \begin{align}
-        C_{m,}
-    \end{align}
-
-    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
-    \begin{align*}
-        \begin{split}
-            \| w \|_{L^{p}(\Omega)}^{p}
-            &
-            \leq 
-            \sum_{m=0}^{M}
-            \| w \|_{L^{p}(T_{m})}^{p}
-            \\&
-            \leq 
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p}
-            \\&
-            \leq 
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-            \sum_{\ell=0}^{M} 
-            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
-            \leq 
-            \left(
-                \sum_{m=0}^{M}
-                \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
-            \right)
-            \| \nabla u \|_{L^{p}(\Omega)}^{p} 
-            ,
-        \end{split}
-    \end{align*}
-    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$.
-
-    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
-\end{remark}
 
@@
 
-    We now define, as in~\cite[Equations~{\char`\(}5.12{\char`\)} and~{\char`\(}5.14{\char`\)}]{ern2020stable} or~\cite[equations~{\char`\(}6.7{\char`\)} and~{\char`\(}6.9{\char`\)}]{Chaum_Voh_p_rob_3D_H_curl_24}, the field $\widetilde w_{m} \in W^{p}\Alt^{k}(T_{m})$ via
+    We now define, as in~\cite[Equations~{\char`\(}5.12{\char`\)} and~{\char`\(}5.14{\char`\)}]{ern2020stable} or~\cite[Equations~{\char`\(}6.7{\char`\)} and~{\char`\(}6.9{\char`\)}]{Chaum_Voh_p_rob_3D_H_curl_24}, the field $\widetilde w_{m} \in W^{p}\Alt^{k}(T_{m})$ via
     \begin{align} \label{equation:w''_ext_der}
@@
 
+We derive an estimate for the Poincar\'e--Friedrichs constant, in analogy to Theorem~\ref{theorem:fullrecursivesum:grad}, though the generalization to the exterior derivative faces a more complicated recursive structure.
+For ease of discussion, we choose to present the result for a general class of recursive estimates.
+Of course, implementations should make use of the simplifications warranted by the specific recursive structure,
+such as the recursion presented in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+
+\begin{theorem}\label{theorem:fullrecursivesum:exterior}
+    % Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable $n$-dimensional triangulation $\calT$.
+    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
+    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
+    Suppose that $u, w \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
+    such that $\cartan w = \cartan u$ and the following recursive estimate holds:
+    \begin{gather*}
+        \| w \|_{L^{p}(T_{0})} 
+        \leq 
+        A_{0,0}
+        \| \cartan u \|_{L^{p}(T_{0})}
+        ,
+    \end{gather*}
+    and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        \sum_{\ell=0}^{m} A_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})} 
+        +
+        \sum_{\ell=0}^{m-1} B_{m,\ell} \| w \|_{L^{p}(T_{\ell})} 
+        .
+    \end{align*}
+    Then we have an inequality of the form 
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}
+        &
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+        \right)^{\frac 1 p}
+        \| \cartan u \|_{L^{p}(\Omega)}
+        ,
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+    Here, 
+    \begin{align*}
+        C_{m,\ell} = \sum_{ m = i_L > \dots > i_1 \geq \ell } B_{i_{L},i_{L-1}} \cdots B_{i_{2},i_{1}} A_{i_{1},\ell}.
+    \end{align*}
+\end{theorem}
+\begin{proof}    
+    %     The discussion is similar as in the proof of Theorem~\ref{theorem:fullrecursivesum:grad}.
+    %     this time geared towards the application of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+    Unwrapping the recursion, we obtain an estimate of the form 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})} 
+        \leq 
+        \sum_{\ell = 0}^{m}
+        \underbrace{ 
+            \left( 
+                \sum_{ m = i_L > \dots > i_1 \geq \ell }
+                B_{i_{L},i_{L-1}} \cdots B_{i_{2},i_{1}} A_{i_{1},\ell}
+            \right)
+        }_{ =: C_{m,\ell} }
+        \| \cartan u \|_{L^{p}(T_{\ell})} 
+    \end{align*}
+    Here, $C_{m,\ell}$ denotes the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
+    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    Once again, The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        % \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+        \sum_{\ell'=0}^{M} \| \cartan u \|_{L^{p}(T_{\ell'})}^{p} 
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+        \right)
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+    where $q \in [1,\infty]$ is as described above. The proof is complete. 
+    % where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+\end{proof}
+
+\begin{remark}\label{remark:fullrecursivesum:exterior}
+    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{m})}
+        &
+        \leq  
+        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
+        \| \cartan u      \|_{L^{p}(T_{m})} 
+        \\&\qquad
+        +
+        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
+        \Cfivetrafo{n}{k+1}{\ell_{m}}{p}(\calT)
+%         \Cfiveprime{n}{k}(\calT)^{k} 
+%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
+        \\&\qquad
+        + 
+        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT) 
+%         \Cfiveprime{n}{k}(\calT)^{k-1} 
+%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
+        \| w \|_{L^{p}(\Makoto_{m-1})}
+        .
+    \end{align*}
+    Unwrapping the recursion for the norm over the $m$-th simplex, 
+    we find an estimate of the form 
+    \begin{align}\label{math:fullrecursivesum:exterior}
+        \| w \|_{L^{p}(T_{m})} 
+        &
+        \leq 
+        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
+        .
+    \end{align}
+    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
+    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \| w \|_{L^{p}(\Omega)}^{p}
+        &
+        \leq 
+        \sum_{m=0}^{M}
+        \| w \|_{L^{p}(T_{m})}^{p}
+        % \\&
+        \leq 
+        \sum_{m=0}^{M}
+        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+        \sum_{\ell=0}^{M} 
+        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
+        \leq 
+        \left(
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+        \right)
+        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
+        ,
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
+\end{remark}
+
 \begin{remark}\label{remark:poincarefriedrichsestimate:exterior:contraction}
-    We would like to point out an alternative application of Proposition~\ref{proposition:starreflection},
+    While our main interest in this manuscript, we point out an alternative application of Proposition~\ref{proposition:starreflection},
     using the second class of transformations. 
@@
 
-\begin{remark}\label{remark:fullrecursivesum:exterior}
-    \color{red}
-    We provide a similar discussion as in Remark~\ref{remark:fullrecursivesum}, 
-    this time geared towards the application of Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
-    \begin{align*}
-        \| w \|_{L^{p}(T_{m})}
-        &
-        \leq  
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \| \cartan u      \|_{L^{p}(T_{m})} 
-        \\&\qquad
-        +
-        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
-        \Cfivetrafo{n}{k+1}{\ell_{m}}{p}(\calT)
-%         \Cfiveprime{n}{k}(\calT)^{k} 
-%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
-        \\&\qquad
-        + 
-        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT) 
-%         \Cfiveprime{n}{k}(\calT)^{k-1} 
-%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
-        \| w \|_{L^{p}(\Makoto_{m-1})}
-        .
-    \end{align*}
-    Unwrapping the recursion for the norm over the $m$-th simplex, 
-    we find an estimate of the form 
-    \begin{align}\label{math:fullrecursivesum:exterior}
-        \| w \|_{L^{p}(T_{m})} 
-        &
-        \leq 
-        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
-        .
-    \end{align}
-    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
-    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
-    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
-    \begin{align*}
-        \| w \|_{L^{p}(\Omega)}^{p}
-        &
-        \leq 
-        \sum_{m=0}^{M}
-        \| w \|_{L^{p}(T_{m})}^{p}
-        % \\&
-        \leq 
-        \sum_{m=0}^{M}
-        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
-        \sum_{\ell=0}^{M} 
-        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
-        \leq 
-        \left(
-            \sum_{m=0}^{M}
-            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
-        \right)
-        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
-        ,
-    \end{align*}
-    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
-\end{remark}
-
 \section{Numerical examples}\label{section:numericalexamples}
@@
 We expect the bound to deteriorate as the eccentricity of the tetrahedron increases.
-
 However, the results indicate room for improvement. 

### 2025-01-31 draft.tex
recursive estimate
rewriting algorithms

@@
 
+For the purpose of comparison, we compute reference Poincar\'e--Friedrichs constants over the reference tetrahedron via a higher-order finite element method over a mesh after three iterations of uniform refinement.
+These data are tabulated in Table~\ref{table:referencepoincarefriedrichs}. 
+This example conforms to the well-known fact that the eigenvalues of the scalar Laplacian with mixed boundary conditions are between the Neumann and Dirichlet eigenvalues, which follows from a known variational principle.
+However, such an enclosure does not seem to hold for the vector Laplacians with mixed boundary conditions.
+
+We overestimate by a factor of at most six.
+We take this as an indication that the estimate is within feasible range, at least on simplices with good shape regularity. 
+We expect the bound to deteriorate as the eccentricity of the tetrahedron increases.
+However, the results indicate room for improvement. 
+Future estimates should tighten the gap towards the actual computed values,
+including for ill-shaped simplices.
+
 \section{....}
+
+\begin{remark}\label{remark:fullrecursivesum}
+    \color{red}
+    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+    The potential $w$ for the gradient $\nabla u$ satisfies 
+    \begin{align*}
+        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
+        \qquad 
+        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
+        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
+    \end{align*}
+    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
+
+    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
+    \begin{align}\label{math:fullrecursivesum}
+        \begin{split}
+            \| w \|_{L^{p}(T_{m})} 
+            &
+            \leq 
+            \sum_{\ell=0}^{m}   \left( B_{m,m} \cdots B_{m,\ell+1} \right) A_{m,\ell} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) A'_{m,\ell+1} \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \\&
+            = 
+            A_{m,m} \| \nabla u \|_{L^{p}(T_{m,m})}
+            +
+            \sum_{\ell=0}^{m-1} \left( B_{m,m} \cdots B_{m,\ell+2} \right) \left( B_{m,\ell+1} A_{m,\ell} + A'_{m,\ell+1} \right) \| \nabla u \|_{L^{p}(T_{m,\ell})}
+            \\&
+            =:
+            \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
+            .
+        \end{split}
+    \end{align}
+    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
+    By definition, $C_{m,0} = A_0$, and 
+    \begin{align}
+        C_{m,}
+    \end{align}
+
+    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
+    \begin{align*}
+        \begin{split}
+            \| w \|_{L^{p}(\Omega)}^{p}
+            &
+            \leq 
+            \sum_{m=0}^{M}
+            \| w \|_{L^{p}(T_{m})}^{p}
+            \\&
+            \leq 
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p}
+            \\&
+            \leq 
+            \sum_{m=0}^{M}
+            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
+            \sum_{\ell=0}^{M} 
+            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
+            \leq 
+            \left(
+                \sum_{m=0}^{M}
+                \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
+            \right)
+            \| \nabla u \|_{L^{p}(\Omega)}^{p} 
+            ,
+        \end{split}
+    \end{align*}
+    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$.
+
+    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
+\end{remark}
 

### 2025-01-31 main.tex
Update on Overleaf.
rewriting algorithms

@@
 
-We assess the practical quality of our upper bounds with a few numerical examples in dimension 2D and 3D, with exclusive focus on the Hilbert space case $p=2$. 
-We want to compare the exact Poincar\'e--Friedrichs constants with the upper bounds given by Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
-In lieu of the exact value, finite element computations on a refined mesh provide reference eigenvalues as a proxy for the exact value.
-We have multiple estimates for the gradient potential, and the Poincar\'e--Friedrichs constant of the divergence can always be estimated by the diameter,
-hence our main interest is the curl operator.
+We wish to assess the practical quality of our upper bounds, with exclusive focus on the Hilbert space case $p=2$. 
+To that end, we compare our estimates for the Poincar\'e--Friedrichs constants with the exact constants of a few examples domains in dimension 2 and 3. 
+In lieu of the exact values, finite element eigenvalue computations on a refined mesh provide reference values as a proxy for the exact value.
+We study the
+
+Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} gives estimates for the gradient, curl and divergence Poincar\'e--Friedrichs constants. 
+In addition, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} provides anotherr upper bound for the Poincar\'e constant.
+We remark that the Poincar\'e--Friedrichs constant for the divergence can always be estimated by less than the diameter of the domain (see Lemma~\ref{lemma:mixedbconsimplex}), so our recursive estimates are of no practical interest in that case.
+
+\subsection{Software and algorithms}
+
+% TODO: write about the software and the algorithms
+
+% spanning trees 
+Computing the upper bound for the Poincar\'e constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires to find paths between simplices.
+One easily sees that the estimate is minimized by a spanning tree of the face-connection graph.
+We choose a depth-first search that attempts to minimize the resulting constant. 
+While this does not take much time on small two-dimensional examples, the computation takes considerably in our three dimensional examples.
+
+% shelling
+Computing the upper bound for the Poincar\'e--Friedrichs constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires the construction of shellings. 
+While a brute-force enumeration of shellings is still feasible for small two-dimensional triangulations, it becomes unfeasible in dimension three due to the combinatorial explosion of the number of possible shellings.
+Instead, we perform a greedy backtracking search: 
+starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
+Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
+We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}.
+
+This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found until all shellings have been produced.
+However, finding all shellings seems practically infeasible. 
+Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
+We repeat this for a possible choices of initial simplex, and pick the optimal shelling among those found.
+The candidate shellings that we obtain in this manner lead to different quantitative estimates.
+In the case of more complicated 3D triangulations, such as of the Fichera corner, they may differ by a factor of $20$.
+For that reason, optimizing the estimate induced by the shelling is an important computational subproblem.
+
+For tight estimates, it is imperative that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations.
+The estimates that we use are slightly tighter than the ones stated in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:exterior},
+namely the calculations used in the proofs.
 
@@
 
+The Poincar\'e--Friedrichs constants over simplices enter our estimates.
+They are subject to boundary conditions that hold along a few faces. 
+Since those constants appear so frequently, we prefer to have tight upper estimates for them.
+
+Specifically, and subject to different boundary conditions 
 We first assess the Poincar\'e--Friedrichs constant over the reference simplex where boundary conditions hold along a few faces. 
@@
 
+Whenever $T$ is a simplex, the Poincar\'e--Friedrichs constants have upper bounds of the form $C \diam(T)$ for some numerical constant $C > 0$.
+Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and the subequent remark (using $p=2$) have established that $C = 2/\pi \approx 0.45015815807$.
+In the special case of the gradient potential, where the Poincar\'e constant can be characterized variationally, the Poincar\'e constant without boundary conditions is already an upper bound for the Poincar\'e constant with boundary conditions, and one can choose $C = 1/\pi \approx 0.31830988618$.
+This conforms to the well-known fact that the eigenvalues of the scalar Laplacian with mixed boundary conditions are between the Neumann and Dirichlet eigenvalues.
+Finally, the factor $1/\pi$ in the previous two estimates has a known improvement when the simplex is a triangle:
+then we can replace the factor by $1/j_{1,1} \approx 0.2609803592$, where $j_{1,1}$ is the zero of a Bessel function; see~\cite{todo}.
+
 For the purpose of comparison, we compute reference Poincar\'e--Friedrichs constants over the reference tetrahedron via a higher-order finite element method over a mesh after three iterations of uniform refinement.
 These data are tabulated in Table~\ref{table:referencepoincarefriedrichs}.
-This example conforms to the well-known fact that the eigenvalues of the scalar Laplacian with mixed boundary conditions are between the Neumann and Dirichlet eigenvalues, which follows from a known variational principle.
-However, such an enclosure does not seem to hold for the vector Laplacians with mixed boundary conditions.
-
-Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and the subequent remark (using $p=2$) give an upper bound of $2/\pi \approx 0.45015815807$,
-which is an overestimate by a factor of at most six.
+
+We overestimate by a factor of at most six.
 We take this as an indication that the estimate is within feasible range, at least on simplices with good shape regularity. 
@@
 including for ill-shaped simplices.
-
-% We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex.
-Numerical examples indicate that this holds for $p=2$.
 
@@
 
-We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
+We compare the reference Poincar\'e constants with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
 A brufe-force search easily enumerates all the (repetition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem. 
-
-We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
-Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
-Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
-allowing us to compute the best possible of these bounds.
+%
+Moreover, we compare the reference Poincar\'e--Friedrichs constants with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
+Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection}.
+% (with Remark~\ref{remark:improved_starreflection}).
+Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations, allowing us to compute the best possible of these bounds.
 

### 2025-02-01 main.tex
numerics and outlook

@@
 
-% TODO: write about the software and the algorithms
-
-% spanning trees 
+All computations have been implemented with an in-house C++ code developed specifically for implementing finite element exterior calculus. 
+The reference Poincar\'e constants are the inverse square roots of reference eigenvalues.
+We compute the latter by solving finite element eigenvalue problems that involve mixed formulations of the vector Laplacian over sufficiently refined meshes.
+
 Computing the upper bound for the Poincar\'e constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires to find paths between simplices.
-One easily sees that the estimate is minimized by a spanning tree of the face-connection graph.
+One quickly sees that a spanning tree of the face-connection graph minimizes the estimate.
 We choose a depth-first search that attempts to minimize the resulting constant. 
-While this does not take much time on small two-dimensional examples, the computation takes considerably in our three dimensional examples.
-
-% shelling
+While this does not take much time for small two-dimensional examples, the computation takes considerably for our three-dimensional examples.
+
 Computing the upper bound for the Poincar\'e--Friedrichs constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires the construction of shellings. 
+Finding a shelling that optimizes a geometric target quantity is a challenging problem in computational geometry and theoretical computer science. 
 While a brute-force enumeration of shellings is still feasible for small two-dimensional triangulations, it becomes unfeasible in dimension three due to the combinatorial explosion of the number of possible shellings.
 Instead, we perform a greedy backtracking search: 
-starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
-Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
-We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}.
-
-This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found until all shellings have been produced.
-However, finding all shellings seems practically infeasible. 
+Starting with a single simplex, we successively add simplices to the partial shellings until a complete shelling is found. 
+This backtracking algorithm does generally not find the optimal shelling until all shellings have been checked.
+However, enumerating and checking all shellings seems practically infeasible.
+
+Therefore, we need a practical heuristic to find shellings that induce small constants.
+Indeed, our computations show that the Poincar\'e--Friedrichs estimates depend on the shelling and can differ by orders of magnitudes.
 Our implementation starts with a fixed simplex and generates up to $10$ shellings.
-We repeat this for a possible choices of initial simplex, and pick the optimal shelling among those found.
-The candidate shellings that we obtain in this manner lead to different quantitative estimates.
-In the case of more complicated 3D triangulations, such as of the Fichera corner, they may differ by a factor of $20$.
-For that reason, optimizing the estimate induced by the shelling is an important computational subproblem.
-
-For tight estimates, it is imperative that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations.
+We repeat this for all possible initial simplices and pick the optimal shelling among those found.
+We use a greedy strategy: Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
+We moreover prioritize the completion of face stars since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
+In other words, we defer the completion of non-face stars in order to not introduce large factors early into the recursion.
+
+For tight estimates, we must compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each geometric transformation.
 The estimates that we use are slightly tighter than the ones stated in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:exterior},
-namely the calculations used in the proofs.
+as we directly implement the calculations used in the proofs.
 
@@
 Finally, the factor $1/\pi$ in the previous two estimates has a known improvement when the simplex is a triangle:
-then we can replace the factor by $1/j_{1,1} \approx 0.2609803592$, where $j_{1,1}$ is the zero of a Bessel function; see~\cite{todo}.
+then we can replace the factor $1/\pi$ by $1/j_{1,1} \approx 0.2609803592$, where $j_{1,1}$ is the zero of a Bessel function; see~\cite{laugesen2010minimizing}.
 
@@
 We compare the reference Poincar\'e constants with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
-A brufe-force search easily enumerates all the (repetition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem. 
 %
@@
 % (with Remark~\ref{remark:improved_starreflection}).
-Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations, allowing us to compute the best possible of these bounds.
-
-% Because much easier estimates are known for those, applying our estimates in the two-dimensional situation has only demonstrative purpose.
 
@@
     \centering
-    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
         \hline
@@
         \hline
-        $\calT_{L}$     & 0.822        & 5.079960342 &               & 2.382       & 2.895              & 0.322              & 2.382              &  7.402              \\ 
+        $\calT_{L}$     & 0.822        & 2.904309304 &               & 1.733455376       & 2.895              & 0.322              & 1.733455385              &  7.402              \\ 
         \hline
-        $\calT_{S}$     & 0.978        &             &               & 2.917       & 2.982              & 0.346              & 2.917              &  8.419              \\ 
+        $\calT_{S}$     & 0.978        & 3.357380776 &               & 2.170240475       & 2.982              & 0.346              & 2.170240474              &  8.419              \\ 
         \hline
-        $\calT_{S'}$    & 0.978        &             &               & 4.764       & 4.870              & 0.346              & 4.764              & 13.748              \\ 
+        $\calT_{S'}$    & 0.978        & 3.368675195 &               & 3.368675191       & 4.870              & 0.346              & 3.368675191              & 13.748              \\ 
         \hline
@@
 % As in the two-dimensional case outlined above, we again compare these reference values with estimates obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad}, Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
-
-The computation becomes more demanding in dimension three. 
-Enumerating all the shortest-path trees of the triangulations above is still feasible but takes considerably longer. 
-However, brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
-Instead, we perform a greedy backtracking search: 
-starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
-Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
-We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
-It is imperative for the improvement of our upper bounds that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations, thus avoiding overtly pessimistic blanket estimates.
-
-This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found until all shellings have been produced.
-However, finding all shellings seems practically infeasible. 
-Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
-We repeat this for a possible choices of initial simplex, and pick the optimal shelling among those found.
-The candidate shellings that we obtain in this manner lead to different quantitative estimates.
-In the case of more complicated triangulations, such as of the Fichera corner, they may differ by a factor of $20$.
-For that reason, optimizing the estimate induced by the shelling is an important computational subproblem.
 
@@
 
-The most important outcome of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e.\ $n=2$ or $n=3$).
-There are several avenues for further research. 
-In particular, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars) and further improvement seems possible.
-
-Firstly, we use local Poincar\'e--Friedrichs inequalities over single simplices, subject to various boundary conditions, but these local estimates over simplices (and, more generally, convex domains) likely allow room for improvement.
-We conjecture that the Guerini--Savo~\cite{guerini2004eigenvalue} estimates, hitherto only known when $p=2$ and over bounded convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and convex Lipschitz domains.
-The case $p=2$ was discussed recently~\cite{licht2024geometry}.
-Such estimates would likely improve on the Poincar\'e--Friedrichs constants than the regularized Poincar\'e operators in the spirit of Costabel and McIntosh~\cite{costabel2010bogovskiui} that we currently use.
-Similarly, Poincar\'e--Friedrichs constants subject to boundary conditions allow for upper bounds tighter than what we currently achieve via regularized Bogovski\u{\i} operators.
-% DONE {The above needs to be updated.}
-
-Secondly, our construction uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
-In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques could lead to better estimates,
-such as via trace and extension operators.
-
-Thirdly, the present results can be generalized to shellable polytopal complexes. 
-This extension may also pertain for simplicial triangulation: 
-since the estimates deteriorate if the number of simplices increases, 
-we might improve our estimates if we lump simplices of a triangulation together into a few polytopal subdomains for which the Poincar\'e--Friedrichs constants are controlable.
+The most important contribution of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., \ $n=2$ or $n=3$).
+However, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars). There are several avenues for further research and improvement.
+
+We use local Poincar\'e--Friedrichs inequalities over single simplices, subject to boundary conditions along some faces.
+As mentioned earlier, the Poincar\'e constant over triangles admits a sharper upper bound than for general convex domains.
+We conjecture that tetrahedra permit a similar improvement.
+
+The gradient Poincar\'e--Friedrichs constant already dominates the Poincar\'e--Friedrichs constants of the $\Lebesgue^2$ de~Rham complex without boundary conditions (or with full boundary conditions) over convex domains~\cite{guerini2004eigenvalue,licht2024geometry}.
+We believe that this generalizes to the entire range of Lebesgue exponents $1 \leq p \leq \infty$
+Such estimates would likely improve on the Poincar\'e--Friedrichs constants derived via the regularized Poincar\'e and Bogovski\u{\i} operators.
+
+Our method uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
+In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques, such as via trace and extension operators, could lead to better estimates.
+
+There is little research on practical algorithms that construct shellings.
+Checking whether a general triangulation has a shelling is computationally infeasible.
+While the literature knows a few theoretical results, there is interest in algorithms that attempt to shell practically relevant triangulations while optimizing geometric target heuristics.
+
+We expect the present results to generalize to shellable polytopal complexes. 
+Apart from the intrinsic interest in polytopal simplicial complexes, this extension is also relevant for any simplicial triangulation:
+As a rule of thumb, the estimates deteriorate as the number of simplices increases.
+We might improve our estimates by lumping simplices into a few polytopal subdomains for which the Poincar\'e--Friedrichs constants are controllable.
+For example, the crossed bricks domain easily partitions into four quadrilaterals.
 

### 2025-02-03 main.tex
Update on Overleaf.

@@
 
+The shelling-based estimate for the Poincar\'e constant of the gradient potential outperforms the estimate in Section~\ref{section:gradient} in our examples where the triangles are not all congruent to each other.
+That is a result of our implementation, where the face-based reflections are not necessarily onto, which allows for some improved estimates.
+
 \begin{table}[t]
@@
         \hline
-        $\calT_{Q}$     & 0.318        & 1.684337597 &               & 1.684337582       & 3.141        & 0.225              & 1.684337545        &  6.928              \\ 
+        $\calT_{Q}$     & 0.318        & 0.9040624834 &               & 0.904062477       & 3.141        & 0.225              & 1.380978233              &  6.928              \\ 
         \hline
-        $\calT_{L}$     & 0.822        & 2.904309304 &               & 1.733455376       & 2.895              & 0.322              & 1.733455385              &  7.402              \\ 
+        $\calT_{L}$     & 0.822        & 2.381225711 &               & 1.421249625       & 2.895              & 0.322              & 2.978885552         &  7.402              \\ 
         \hline
-        $\calT_{S}$     & 0.978        & 3.357380776 &               & 2.170240475       & 2.982              & 0.346              & 2.170240474              &  8.419              \\ 
+        $\calT_{L'}$     & 0.822        & 2.391924501 &               & 2.391924492       & 2.895              & 0.322              & 4.208181795        &  7.402              \\ 
         \hline
-        $\calT_{S'}$    & 0.978        & 3.368675195 &               & 3.368675191       & 4.870              & 0.346              & 3.368675191              & 13.748              \\ 
+        $\calT_{S,5}$     & 0.978        & 2.752696283 &               & 1.779367097       & 2.982              & 0.346              & 3.717588832       &  8.419              \\ 
+        \hline % non-centered
+        $\calT_{S'}$    & 0.978        & 2.761956509 &               & 2.761956506       & 4.870              & 0.346              & 4.840464511         & 13.748              \\ 
+        \hline % non-centered
+        $\calT_{S''}$   & 0.978        & 3.131764309 &               & 3.131764307       & 4.870              & 0.346              & 5.669944609         & 13.748              \\ 
         \hline

### 2025-02-03 main.tex
correction
Update on Overleaf.
some constants

--- 2025-02-01 main.tex
@@
         |\det(\Jacobian \varphi)|^{\frac 1 p} 
-        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
+        \matnorm{ \Jacobian \varphi^{-1} }^{k}
         \| \tilde w \|_{L^{p}(\Delta^n)}
@@
         |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
-        \matnorm{\Jacobian \varphi}^{k}
-        \cdot 
+        \matnorm{\Jacobian \varphi}^{k+1}
         \| \cartan u \|_{L^{p}(T)}
@@
     \item $\calT_{S}$:  Slit domain triangulation, five triangles 
-    \item $\calT_{S'}$: Slit domain triangulation, 8 triangles, four of which touch the origin.
+    \item $\calT_{S'}$: Slit domain triangulation, 8 triangles, all of which touch the origin.
+    \item $\calT_{S''}$: Slit domain triangulation, 8 triangles, four of which touch the origin.
 \end{itemize}
@@
 % (with Remark~\ref{remark:improved_starreflection}).
+
+The shelling-based estimate for the Poincar\'e constant of the gradient potential outperforms the estimate in Section~\ref{section:gradient} in our examples where the triangles are not all congruent to each other ($\calT_{L}$ and $\calT_{S,5}$).
+That is a result of our implementation, where the face-based reflections are not necessarily onto, which allows for some improved estimates.
 
@@
         \hline
-        $\calT_{Q}$     & 0.318        & 1.684337597 &               & 1.684337582       & 3.141        & 0.225              & 1.684337545        &  6.928              \\ 
+        $\calT_{Q}$     & 0.318        & 0.9040624834 &               & 0.904062477        & 3.141        & 0.225              & 1.339553527              &  6.928              \\
         \hline
-        $\calT_{L}$     & 0.822        & 2.904309304 &               & 1.733455376       & 2.895              & 0.322              & 1.733455385              &  7.402              \\ 
+        $\calT_{L}$     & 0.822        & 2.381225711 &               & 1.421249625        & 2.895              & 0.322              & 2.505543143         &  7.402              \\
         \hline
-        $\calT_{S}$     & 0.978        & 3.357380776 &               & 2.170240475       & 2.982              & 0.346              & 2.170240474              &  8.419              \\ 
+        $\calT_{L'}$     & 0.822        & 2.391924501 &               & 2.391924492        & 2.895              & 0.322              & 4.053039867        &  7.402              \\
         \hline
-        $\calT_{S'}$    & 0.978        & 3.368675195 &               & 3.368675191       & 4.870              & 0.346              & 3.368675191              & 13.748              \\ 
+        $\calT_{S,5}$     & 0.978        & 2.752696283 &               & 1.779367097       & 2.982              & 0.346              & 3.717588832       &  8.419              \\ 
+        \hline % centered
+        $\calT_{S'}$    & 0.978        & 3.131764309 &               & 3.131764307       & 4.870              & 0.346              & 5.453759801         & 13.748              \\
+        \hline % non-centered
+        $\calT_{S''}$   & 0.978        & 2.761956509 &               & 2.761956506       & 4.870              & 0.346              & 4.662992222         & 13.748              \\
         \hline
@@
         \hline
-        $\calT_{C}$     & 0.3177997026 &             &                    &  1.147682616 & 3.611339490040196  \\ 
+        $\calT_{C,5}$   & 0.3179254398 & 4.31776537   &                    & 3.246136642  & 91.66905966662563  \\
         \hline
-        $\calT_{K}$     & 0.3179254398 &             &                    & 12.73827122  & 91.66905966662563  \\ 
+        $\calT_{C,K}$   & 0.3041392027 & 0.3177997026 &                    & 11.03485346 & 3.611339490040196  \\
         \hline
-        $\calT_{B,5}$   & 1.022627161  &             &                    & 36.7821067   & 35.96824737574127  \\ 
+        $\calT_{B,5}$   & 1.022627161  & 7.698889039  &                    & 25.97226447  & 35.96824737574127  \\
         \hline
-        $\calT_{B}$     & 1.022627161  &             &                    & 62.40578125  & 61.02495966269372  \\ 
+        $\calT_{B,K}$   & 1.022627161  & 10.10602558  &                    & 53.76320901  & 61.02495966269372  \\
         \hline
@@
         \hline
-        $\calT_{C}$     & 0.2250695032 & 1.147682616 & 5.099236457042005 & 0.1837881324      & 1.5265605865      &  8.30608900893      \\ 
+        $\calT_{K,5}$   & 0.2250062929 & 141.1488115 & 129.5249378629681 & 0.1837655124      & 3.391164992       & 139.7449800105412   \\
         \hline
-        $\calT_{K}$     & 0.2250062929 & 29.14392611 & 129.5249378629681 & 0.1837655124      & 25.68030786       & 139.7449800105412   \\ 
+        $\calT_{C,K}$   & 0.2250695032 & 12.15727753 & 5.099236457042005 & 0.1837881324      & 25.89943821       &  8.30608900893      \\
         \hline
-        $\calT_{B,5}$   & 0.3315710272 & 160.0052039 & 482.5669036190229 & 0.2330604743      & 160.7339833       & 689.6664212985330   \\ 
+        $\calT_{B,5}$   & 0.3315710272 & 113.0845771 & 482.5669036190229 & 0.2330604743      & 152.8861269       &    \\
         \hline
-        $\calT_{B}$     & 0.3315710272 & 572.3519405 & 1726.182004903473 & 0.2330604743      & 510.806374        & 2191.733177984011   \\ 
+        $\calT_{B,K}$   & 0.3315710272 & 162.6872182 & 1726.182004903473 & 0.2330604743      & 512.2731352       & 2191.733177984011   \\
         \hline

### 2025-02-03 draft.tex
new table entries, completed, abbreviated

@@
 \color{black}
+
+\section{Updated Tables}
+
+\begin{table}[t]
+    \centering
+    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
+        \hline
+                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio       & $\grad$ est   & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
+        \hline
+        $\calT_{Q}$     & 0.318        & 0.9040624834 & 2.842963784        & 0.904062477   & 2.84296376         & 0.225              & 1.339553527        & 5.95357123111   \\
+        \hline
+        $\calT_{L}$     & 0.822        & 2.381225711 & 2.896868261         & 1.421249625   & 1.72901414234      & 0.322              & 2.505543143        & 7.78118988509   \\
+        \hline
+        $\calT_{L'}$    & 0.822        & 2.391924501 & 2.909883821         & 2.391924492   & 2.90988381022      & 0.322              & 4.053039867        & 12.5870803323   \\
+        \hline
+        $\calT_{S,5}$   & 0.978        & 2.752696283 & 2.81461787627       & 1.779367097   & 1.81939375971      & 0.346              & 3.717588832        & 10.7444763931   \\ 
+        \hline % centered
+        $\calT_{S'}$    & 0.978        & 3.131764309 & 3.2022129948        & 3.131764307   & 3.20221299284      & 0.346              & 5.453759801        & 15.7623115636   \\
+        \hline % non-centered
+        $\calT_{S''}$   & 0.978        & 2.761956509 & 2.82408641002       & 2.761956506   & 2.82408640695      & 0.346              & 4.662992222        & 13.4768561329   \\
+        \hline
+    \end{tabular}
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
+    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
+    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
+    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
+    }\label{table:estimates2D}
+\end{table}
+
+\begin{table}[t]
+    \color{red}
+    \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+        \hline
+                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est & $\grad$ ratio  \\
+        \hline
+        $\calT_{C,5}$   & 0.3179254398 & 4.31776537   & 13.5810628200       & 3.246136642  & 10.214410571  \\
+        \hline
+        $\calT_{C,K}$   & 0.3177997026 & 3.571616557  &  11.238577405       & 11.03485346  & 34.722667673  \\
+        \hline
+        $\calT_{B,5}$   & 1.022627161  & 7.698889039  & 7.52853956223       & 25.97226447  & 25.397589131  \\
+        \hline
+        $\calT_{B,K}$   & 1.022627161  & 10.10602558  & 9.88241459391       & 53.76320901  & 52.573617306  \\
+        \hline
+        $\calT_{F}$     & 0.7117133306 & 10.62410979  & 14.9275127122       & 269.5329306  & 378.70996511  \\ 
+        \hline
+    \end{tabular} 
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
+    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
+    }\label{table:estimates3D:grad}
+\end{table}
+
+\begin{table}[t]
+    \color{red}
+    \centering
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+        \hline
+                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
+        \hline
+        $\calT_{K,5}$   & 0.2250062929 & 141.1488115 & 627.310506212     & 0.1837655124      & 3.391164992       & 18.4537617952   \\
+        \hline
+        $\calT_{C,K}$   & 0.2250695032 & 12.15727753 & 54.0308334194     & 0.1837881324      & 25.89943821       & 140.920079397   \\
+        \hline
+        $\calT_{B,5}$   & 0.3315710272 & 113.0845771 & 341.056871148     & 0.2330604743      & 152.8861269       & 655.993374077   \\
+        \hline
+        $\calT_{B,K}$   & 0.3315710272 & 162.6872182 & 490.655711308     & 0.2330604743      & 512.2731352       & 2198.02665698   \\
+        \hline
+        $\calT_{F}$     & 0.5549678737 & 25752.34203 & 46403.3023359     & 0.3106774562      & 8958.467291       & 28835.2666478   \\ 
+        \hline
+    \end{tabular}
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
+    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
+    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
+    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
+    }\label{table:estimates3D:curldiv}
+\end{table}
 

### 2025-02-03 main.tex
new table entries, completed, abbreviated
outlook

@@
     \centering
-    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
+    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
         \hline
@@
         \hline
-        $\calT_{Q}$     & 0.318        & 0.9040624834 &               & 0.904062477        & 3.141        & 0.225              & 1.339553527              &  6.928              \\
+        $\calT_{Q}$     & 0.318        & 0.904       & 2.842               & 0.904         & 2.842              & 0.225              & 1.339              &  5.953         \\
         \hline
-        $\calT_{L}$     & 0.822        & 2.381225711 &               & 1.421249625        & 2.895              & 0.322              & 2.505543143         &  7.402              \\
+        $\calT_{L}$     & 0.822        & 2.381       & 2.896               & 1.421         & 1.729              & 0.322              & 2.505              &  7.781         \\
         \hline
-        $\calT_{L'}$     & 0.822        & 2.391924501 &               & 2.391924492        & 2.895              & 0.322              & 4.053039867        &  7.402              \\
+        $\calT_{L'}$    & 0.822        & 2.391       & 2.909               & 2.391         & 2.909              & 0.322              & 4.053              & 12.587         \\
         \hline
-        $\calT_{S,5}$     & 0.978        & 2.752696283 &               & 1.779367097       & 2.982              & 0.346              & 3.717588832       &  8.419              \\ 
+        $\calT_{S,5}$   & 0.978        & 2.752       & 2.814               & 1.779         & 1.819              & 0.346              & 3.717              & 10.744         \\ 
         \hline % centered
-        $\calT_{S'}$    & 0.978        & 3.131764309 &               & 3.131764307       & 4.870              & 0.346              & 5.453759801         & 13.748              \\
+        $\calT_{S'}$    & 0.978        & 3.131       & 3.202               & 3.131         & 3.202              & 0.346              & 5.453              & 15.762         \\
         \hline % non-centered
-        $\calT_{S''}$   & 0.978        & 2.761956509 &               & 2.761956506       & 4.870              & 0.346              & 4.662992222         & 13.748              \\
+        $\calT_{S''}$   & 0.978        & 2.761       & 2.824               & 2.761         & 2.824              & 0.346              & 4.662              & 13.476         \\
         \hline
@@
 \begin{itemize}
-    \item $\calT_{C}$: cube triangulation with five tetrahedra
-    \item $\calT_{K}$: Kuhn triangulation of the cube, consisting of six tetrahedra
+    \item $\calT_{C,5}$: cube triangulation with five tetrahedra
+    \item $\calT_{C,K}$: Kuhn triangulation of the cube, consisting of six tetrahedra
+    \item $\calT_{B,5}$: crossed bricks, four copies of $\calT_{C,5}$
+    \item $\calT_{B,K}$: crossed bricks, four copies of $\calT_{C,K}$
     \item $\calT_{F}$: Fichera corner, $24$ simplices 
-    \item $\calT_{B}$: crossed bricks, $24$ simplices 
 \end{itemize}
@@
     \centering
-    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
         \hline
@@
         \hline
-        $\calT_{C,5}$   & 0.3179254398 & 4.31776537   &                    & 3.246136642  & 91.66905966662563  \\
+        $\calT_{C,5}$   & 0.317        & 4.317        & 13.581              & 3.246        & 10.214         \\
         \hline
-        $\calT_{C,K}$   & 0.3041392027 & 0.3177997026 &                    & 11.03485346 & 3.611339490040196  \\
+        $\calT_{C,K}$   & 0.317        & 3.571        &  11.23              & 11.034       & 34.722         \\
         \hline
-        $\calT_{B,5}$   & 1.022627161  & 7.698889039  &                    & 25.97226447  & 35.96824737574127  \\
+        $\calT_{B,5}$   & 1.022        & 7.698        & 7.5285              & 25.972       & 25.397         \\
         \hline
-        $\calT_{B,K}$   & 1.022627161  & 10.10602558  &                    & 53.76320901  & 61.02495966269372  \\
+        $\calT_{B,K}$   & 1.022        & 10.106       & 9.8824              & 53.763       & 52.573         \\
         \hline
-        $\calT_{F}$     & 0.7117133306 &              &                    & 325.7340627  & 18796.92616132183  \\
+        $\calT_{F}$     & 0.711        & 10.622       & 14.927              &  268.071     & 377.033        \\ 
         \hline
@@
     \centering
-    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+    \begin{tabular}{|r||r|r|r||r|r|r|}
         \hline
@@
         \hline
-        $\calT_{K,5}$   & 0.2250062929 & 141.1488115 & 129.5249378629681 & 0.1837655124      & 3.391164992       & 139.7449800105412   \\
+        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310506212          & 0.183             & 3.391             & 18.453          \\
         \hline
-        $\calT_{C,K}$   & 0.2250695032 & 12.15727753 & 5.099236457042005 & 0.1837881324      & 25.89943821       &  8.30608900893      \\
+        $\calT_{C,K}$   & 0.225        & 12.157      & 54.0308334194          & 0.183             & 25.899            & 140.920         \\
         \hline
-        $\calT_{B,5}$   & 0.3315710272 & 113.0845771 & 482.5669036190229 & 0.2330604743      & 152.8861269       &    \\
+        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056871148          & 0.233             & 152.886           & 655.993         \\
         \hline
-        $\calT_{B,K}$   & 0.3315710272 & 162.6872182 & 1726.182004903473 & 0.2330604743      & 512.2731352       & 2191.733177984011   \\
+        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655711308          & 0.233             & 512.273           & 2198.026        \\
         \hline
-        $\calT_{F}$     & 0.5549678737 & 13378.02292 & 24105.94118711908 & 0.3106774562      & 11705.58269       & 37677.60567703448   \\ 
+        $\calT_{F}$     & 0.554        & 25752.342   & 46403.3023359          & 0.310             & 8958.467          & 28835.266       \\ 
         \hline
@@
 The most important contribution of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., \ $n=2$ or $n=3$).
-However, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars). There are several avenues for further research and improvement.
+However, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars).
+There are several avenues for further research and improvement, both in the analytical tools and the implementations.
 
 We use local Poincar\'e--Friedrichs inequalities over single simplices, subject to boundary conditions along some faces. 
-As mentioned earlier, the Poincar\'e constant over triangles admits a sharper upper bound than for general convex domains.
-We conjecture that tetrahedra permit a similar improvement.
-
+The estimates would improve considerably from sharper bounds on the local Poincar\'e constants. 
+However, not many specific results seem to be available for the various special cases. 
 The gradient Poincar\'e--Friedrichs constant already dominates the Poincar\'e--Friedrichs constants of the $\Lebesgue^2$ de~Rham complex without boundary conditions (or with full boundary conditions) over convex domains~\cite{guerini2004eigenvalue,licht2024geometry}.
@@
 Such estimates would likely improve on the Poincar\'e--Friedrichs constants derived via the regularized Poincar\'e and Bogovski\u{\i} operators. 
+As mentioned in the manuscript, the Poincar\'e constant over triangles admits a sharper upper bound than for general convex domains. We conjecture that tetrahedra permit a similar improvement.
 

### 2025-02-03 main.tex
Update on Overleaf.

@@
 
+\begin{comment}
 \begin{remark}\label{remark:fullrecursivesum:exterior}
@@
 \end{remark}
+\end{comment}
 
@@
 \begin{table}[t]
-    \color{red}
     \centering
@@
 \begin{table}[t]  
-    \color{red}
     \centering
@@
         \hline
-        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310506212          & 0.183             & 3.391             & 18.453          \\
+        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310                & 0.183             & 3.391             & 18.453          \\
         \hline
-        $\calT_{C,K}$   & 0.225        & 12.157      & 54.0308334194          & 0.183             & 25.899            & 140.920         \\
+        $\calT_{C,K}$   & 0.225        & 12.157      & 54.030                 & 0.183             & 25.899            & 140.920         \\
         \hline
-        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056871148          & 0.233             & 152.886           & 655.993         \\
+        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056                & 0.233             & 152.886           & 655.993         \\
         \hline
-        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655711308          & 0.233             & 512.273           & 2198.026        \\
+        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655                & 0.233             & 512.273           & 2198.026        \\
         \hline
-        $\calT_{F}$     & 0.554        & 25752.342   & 46403.3023359          & 0.310             & 8958.467          & 28835.266       \\ 
+        $\calT_{F}$     & 0.554        & 25752.342   & 46403.302              & 0.310             & 8958.467          & 28835.266       \\ 
         \hline
@@
     Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
-    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
+    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=1$ (3rd and 4th column) and with $k=2$ (5th and 6th column).
     Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.

### 2025-02-12 main.tex
tweaks and language

--- 2025-02-03 main.tex
@@
 
-\newcommand{\mwl}[1]{{\color{red}#1}}
-\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
-\newcommand{\disk}{\cye{ball}}
-\newcommand{\todo}[1]{{\color{RedOrange}\textbf{#1}}}
-
 % LTeX: enabled=false
@@
     The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry.
-    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of vector Laplacians. 
+    We thus compute upper bounds for constants in Poincar\'e--Friedrichs inequalities and lower bounds for the eigenvalues of vector Laplacians.
     % We derive computable bound on the operator norms of our potentials that only depend on the geometry.
@@
     %
-    As an additional result with independent standing, we establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains. 
-    This is achieved via regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
-    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operators as its particular instances. 
+    As an additional result with independent standing, we establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains, derived as explicit operator norms of regularized Poincar\'e and Bogovski\u{\i} potential operators.
+    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operators as instances of the exterior derivative.
     Computational examples illustrate the theoretical findings.
@@
 However, while potentials and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
-quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.
+quantifiable results regarding the curl and divergence operators, or more generally, the exterior derivative, are largely unavailable.
 
@@
 How to construct potentials for the gradient over triangulated domains is well-documented in the literature.
-Here, we extend this construction to the curl and divergence operators, as well as the exterior derivative. 
+Here, we extend this construction to the curl and divergence operators, treating them as instances of the exterior derivative.
 However, to proceed in the general exterior derivative case, we restrict our efforts to so-called shellable triangulations.
-Only contractible domains can ever admit a shellable triangulation, but having computable upper bounds for such domains is an important stepping stone towards more general situations. 
 The class of shellable triangulations includes practically relevant triangulations:
-for example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three; see also Figure~\ref{figure:patches}.
+for example, local triangulations around simplices within a larger triangulation (the so-called local patches or stars) are shellable in dimensions two and three; see also Figure~\ref{figure:patches}.
+Only contractible domains can ever admit a shellable triangulation, but having computable upper bounds for such domains is an important stepping stone toward more general situations.
+Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
 % DONE {[TCF: Is it really true if the simplex is of highest dimension, e.g., a tetrahedron in 3D?]}
-Additionally, we include a study of regularized Poincar\'e and Bogovski\u{\i} operators that leads to new Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.
 
@@
 Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally difficult. 
-Attention has been given to \emph{linear} potentials instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}. 
+Attention has focused on \emph{linear} potentials instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}.
 The operator norm of any linear potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
-One very simple example for such a bounded linear potential operator is the average-free potential, 
+One straightforward example for such a bounded linear potential operator is the average-free potential,
 \begin{align}\label{math:intro:poincarepotential}
@@
 \end{align} 
-where the mean value of $u$ is fixed to zero. 
+whose mean value is fixed to zero.
 Its operator norm is the Poincar\'e constant $C_{\varnothing,\Omega,p} > 0$ that satisfies % for the \emph{Poincar\'e inequality} 
@@
 where $u_\Omega$ denotes the average of $u$. We emphasize that the average-free potential is generally not the norm-minimizing potential unless $p = 2$.
-Hence, the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs differ in general. 
+Hence, the optimal Poincar\'e constant and the optimal Poincar\'e--Friedrichs generally differ.
 Considerable research efforts have gone into determining constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.
@@
     \qquad 
-    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
+    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega).
 \end{align*}
@@
 and a canonical projection only exists here in the Hilbert setting $p=2$.
-In that sense, there generally is no natural analogue to the Poincar\'e inequality~\eqref{math:intro:poincare:grad} for the curl and divergence.
+In that sense, there generally is no natural analog to the Poincar\'e inequality~\eqref{math:intro:poincare:grad} for the curl and divergence.
 
@@
 For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
-\begin{align} \label{math:intro:exterior:pf} 
-    \| u \|_{L^{p}(\Omega)} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
+\begin{align}\label{math:intro:exterior:pf} 
+    \| w \|_{L^{p}(\Omega)} \leq  C_{k,\Omega,p} \| \cartan w \|_{L^{p}(\Omega)}.
 \end{align} 
@@
 The qualitative existence of Poincar\'e--Friedrichs inequalities for the differential operators of vector calculus and exterior calculus is known for a large class of domains.
-There is a particularly large body of literature on the Poincar\'e inequality for the gradient and its numerous variants,
+There is a vast body of literature on the Poincar\'e inequality for the gradient and its numerous variants,
 which may include weighted integrals or boundary terms.
-These Poincar\'e-type inequalities are often derived via non-constructive arguments, such as the Rellich embedding theorem, 
-and thus the resulting constants are not explicitly computable. 
+We emphasize that non-constructive arguments, such as the Rellich embedding theorem, generally do not yield explicitly computable constants.
 % DONT {[TCF: I believe this is often referred to as the Tartare-Petree theorem]}
@@
 Let us assume for a moment that $\Omega$ is a weakly Lipschitz domain with trivial topology, and consider only the Hilbert case $p=2$. 
-Then the constant in \eqref{math:intro:Wcurl:pf} agrees with the constant in the so-called Poincar\'e--Friedrichs--Weber inequality
+Then the constant in~\eqref{math:intro:Wcurl:pf} agrees with the constant in the so-called Poincar\'e--Friedrichs--Weber inequality
 \begin{align}
@@
 valid for all $\bfu \in \bfW^{2}(\curl,\Omega) \cap \bfW^{2}(\divergence,\Omega)$ that satisfy $\divergence \bfu = 0$ and have vanishing normal or vanishing tangential trace along $\partial \Omega$. 
-Equivalently, \eqref{math:intro:weber} is valid for all $\bfu \in \bfW^{2}(\curl,\Omega)$ that are $L^{2}$-orthogonal to the gradients of scalar fields in $W^{1,2}(\Omega)$
+Equivalently,~\eqref{math:intro:weber} is valid for all $\bfu \in \bfW^{2}(\curl,\Omega)$ that are $L^{2}$-orthogonal to the gradients of scalar fields in $W^{1,2}(\Omega)$
 or that have vanishing tangential trace and are $L^{2}$-orthogonal to the gradients of those scalar fields in $W^{1,2}(\Omega)$ that satisfy Dirichlet boundary conditions.
@@
 % and where the latter holds for all functions $\bfu \in \bfW^{2}(\divergence,\Omega)$ such that $\int_{\Omega} \bfu(x) \cdot \bfv(x) \;dx = 0$ for all $\bfv \in \bfW^{2}(\divergence,\Omega)$ with $\divergence \bfv = 0$.
-We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in \cite{Gaff_Hilbert_harm_55}, \cite{Web_compact_Maxw_80} as well as \cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86}, \cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
+We refer to Equation~(5) in~\cite{Fried_diff_forms_55}, Equation~(2) in~\cite{Gaff_Hilbert_harm_55},~\cite{Web_compact_Maxw_80} as well as~\cite[Lemmas~3.4 and~3.6]{Gir_Rav_NS_86},~\cite[Proposition~7.4]{Fer_Gil_Maxw_BC_97}, and the references therein.
 The general case of $L^p$ differential forms over Lipschitz manifolds subject to partial boundary conditions is discussed in~\cite{goldshtein2011hodge}.
@@
 such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
-In principle, the operator norms of those potentials as mapping between Lebesgue spaces of differential forms 
-are upper estimates for the Poincar\'e--Friedrichs constants of the domain. 
-Here, estimates for the higher-order seminorms of these potentials are available in~\cite{guzman2021estimation}, 
+In principle, if we conceive these potentials as mappings between Lebesgue spaces of differential forms, then their operator norms are upper estimates for the Poincar\'e--Friedrichs constants of the domain.
+We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation},
 but estimates in Lebesgue norms have not been made explicit in the literature yet, to the best of our knowledge.
-We particularly emphasize that these estimates for domains star-shaped with respect to a ball have in common that they rely on upper bounds for the \emph{eccentricity} of the domain.
+We particularly emphasize that all these estimates for domains star-shaped with respect to a ball have in common that they rely on upper bounds for the \emph{eccentricity} of the domain.
 
@@
 Recall that the main objective of this manuscript is bounding Poincar\'e--Friedrichs constants over domains with shellable triangulations, with a key application being local stars within triangulated domains.
-While not all local stars describe convex subdomains, most local stars are star-shaped with respect to a ball. 
-Even though that would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}, 
+Not all local stars describe convex subdomains.
+Even if the local stars are star-shaped with respect to a ball,
+which would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui},
 the estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
-This would not be as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
-But the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
-this occurs most prominently when the domain has sharp reentrant corners.
-Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
+While this is not as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation, the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the triangulation displays decent shape regularity.
+This occurs most prominently when the domain has sharp reentrant corners, illustrative limit cases including the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed},
 which contain local finite element patches that are not star-shaped with respect to any ball.
@@
 Geometric settings that admit finite triangulations enable different pathways to obtain Poincar\'e--Friedrichs inequalities.
-We review some of the main outcomes.
+We review the main outcomes.
 
@@
 Prominent methods numerically compute guaranteed upper bounds on the Poincar\'e--Friedrichs constants upon solving a finite element system over a sufficiently fine triangulation and using some clever post-processing estimates.
-This has led to estimates for scalar Laplacian eigenvalues~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} and vector Laplacian eigenvalues~\cite{gallistl2023computational}. 
-We remark that for the purposes of this manuscript, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems.
+This approach has led to estimates for scalar Laplacian eigenvalues~\cite{Cars_Ged_LB_eigs_14,Liu_fram_eigs_15} and vector Laplacian eigenvalues~\cite{gallistl2023computational}.
+For the purposes of this manuscript, however, we aim for computable upper bounds that do not rely on the solution of (global) finite element systems.
 
@@
 There are numerous estimates for Poincar\'e--Friedrichs constants that only rely on locally computable geometric quantities, such as the diameter and volumes of simplices.
-Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for vertex stars.
+Veeser and Verf\"urth~\cite{veeser2012poincare} provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with a focus on efficient estimates for vertex stars.
 Naturally, their estimates depend on the shape regularity of the mesh.
@@
 and that difference can easily be removed to ensure continuity across that interface.
-Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections, until the entire domain is exhausted.  
+Cell by cell, the potential is constructed over increasing subdomains, matching along the interfacing intersections until the entire domain is exhausted.
 The method is known in the finite element literature~\cite{ern2021finite}.
@@
 The operator norms of our potentials satisfy computable upper bounds, thus yielding computable upper estimates of the Poincar\'e--Friedrichs constants as well.
-As we will elaborate in what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases. 
+In what follows, we focus on domains with shellable triangulations, which include local patches (stars) in two and three dimensions as important special cases.
 To that end, we also devote an important effort specifically to convex domains.
@@
 
-Our main result for convex domains in the exterior calculus setting is the construction of regularized Poincar\'e and Bogovski\u{\i} potential operators with explicitly bounded operator norms. 
-This is summarized in Theorem~\ref{theorem:bogovpoinc}. 
-The upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are bounded in terms of the domain's eccentricity. 
+Our main result for convex domains in the exterior calculus setting is the construction of regularized Poincar\'e and Bogovski\u{\i} potential operators with explicitly bounded operator norms, as summarized in Theorem~\ref{theorem:bogovpoinc}.
+These upper bounds for the Poincar\'e--Friedrichs constants are proportional to the domain diameter and are bounded in terms of the domain's eccentricity.
 The bounds are independent of the Lebesgue exponent $1 \leq p \leq \infty$, though the space dimension and the form degree enter the estimates.
 
-The reasons for our study of Poincar\'e--Friedrichs constants over convex domains is twofold: 
+The reason for our study of Poincar\'e--Friedrichs constants over convex domains is twofold:
 firstly, they are of evident independent interest, and secondly, we will need them as a component for our main results on triangulations.
 Our exposition of regularized Poincar\'e and Bogovski\u{\i}-type potential operators follows the general methodology of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
-By comparison, our variants of these operators are simplified: 
-we only study them over convex domains, instead of domains star-shaped with respect to a ball, 
-and we use simpler (constant) weight functions. 
-While the resulting potentials feature generally lower regularity, they are conductive for our purposes. 
-Crucially, this allows us to easily estimate their operator norms and thus bound Poincar\'e--Friedrichs constants.
+By comparison, we simplify the potential operators:
+we only study them over convex domains instead of domains star-shaped with respect to a ball. Moreover, we use simpler (constant) weight functions.
+While the resulting potentials feature generally lower regularity, they are conducive to our purposes.
+Crucially, this allows us to estimate their operator norms easily and thus bound Poincar\'e--Friedrichs constants.
 
@@
 For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces,
-we want to find the unique vector field potential that not only is a preimage under the curl operator but also has vanishing tangential trace along the same three faces. 
+we want to find the unique vector field potential that not only is a preimage under the curl operator but also has a vanishing tangential trace along the same three faces.
 We achieve this by constructing an auxiliary problem subject to full boundary conditions,
@@
 In light of the different approaches discussed above,
-we seek constants that be explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems, 
+we seek constants that are explicitly computed in terms of mesh geometry, that do not require the solution of global finite element problems,
 and that do not depend on the boundary regularity of the domain.
@@
 
-The sequential construction of potentials for gradient vector fields, as discussed earlier, is well-established in the literature and serves as our conceptual blueprint. 
-Gradient potentials are easily computed over each individual simplex, but the constants of integration generally do not match: 
-the scalar piecewise potential will belong to a broken Sobolev space. 
-In particular, the local potentials will differ only by a constant along the simplex boundaries. 
-However, we can produce a potential in Sobolev spaces over increasingly larger intermediate subdomains, which we construct sequentially. 
-At each step, we select a simplex that shares a face with one of the previously processed simplices and adjust the constant of integration of the local potential. 
+As discussed earlier, the sequential construction of potentials for gradient vector fields is well-established in the literature and serves as our conceptual blueprint.
+Gradient potentials are easily computed over each individual simplex, but the constants of integration generally do not match, so the scalar piecewise potential will belong to a broken Sobolev space.
+However, the local potentials will differ only by a constant along the simplex boundaries.
+We can sequentially construct a potential in Sobolev spaces over increasingly larger intermediate subdomains: at each step, we select a simplex that shares a face with one of the previously processed simplices and adjust the constant integration of the local potential.
 The global potential is built cell by cell until the entire domain is covered.
@@
 These local patches are inherently shellable, making our approach widely applicable.
-For more details on shellability, see Kozlov \cite{kozlov2008combinatorial} and Ziegler \cite{ziegler1995lectures}.
+For more details on shellability, see Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures}.
 
@@
 % We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. 
-We generalize this sequential construction of potentials to the curl, the divergence, and more generally, the exterior derivative. 
+We generalize this sequential construction of potentials to the curl, the divergence, and, more generally, the exterior derivative.
 However, we need to overcome new challenges that arise due to the infinite-dimensional kernels of these differential operators, as we now explain in more detail.
 The basic inductive strategy remains the same.
-We start by constructing, say, a curl potential over a single simplex. 
-Having already defined a potential operator over a subtriangulation, we select a neighboring simplex whose intersection with the preceding simplices includes at least one common face. 
-We then construct a potential for the curl operator whose tangential traces along the intersection match those of the already existing potential.
+We start by constructing, for instance, a curl potential over a single simplex.
+Having already defined a potential operator over a subtriangulation, we select a neighboring simplex that shares at least one face with the preceding simplices.
+We then construct a potential for the curl operator whose tangential traces along the shared faces match those of the already existing potential.
 Repeating this procedure eventually exhausts the original triangulation.
-Here, Theorems~\ref{theorem:poincarefriedrichsestimate:exterior} is our main result.
+Our main result here is Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}.
 
@@
 For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive:
-we require that the new simplex intersects with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold.
-This allows us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex. 
+we require the new simplex to intersect with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold, allowing us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex.
 Whether a triangulation admits such a particular traversal is a non-trivial condition and defines the class of \emph{shellable} triangulations.
@@
 % 5. Shellable
-Shellable simplicial complexes, and more generally polytopal complexes, are a well-established notion in discrete geometry and combinatorics, see, e.g., Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures}, and the references therein.
+Shellable simplicial complexes, and more generally polytopal complexes, are a well-established notion in discrete geometry and combinatorics; see, e.g., Kozlov~\cite{kozlov2008combinatorial} and Ziegler~\cite{ziegler1995lectures}, and the references therein.
 Any shellable simplicial complex must necessarily triangulate a contractible space.
-With respect to our main interest, local patches (stars) in 2D and 3D triangulations are shellable.
+Concerning our main interest, local patches (stars) in 2D and 3D triangulations are shellable.
 
@@
 let us first observe that the average of any $u \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
-\begin{align} \label{math:aver_norm}
+\begin{align}\label{math:aver_norm}
     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
@@
 \end{align*}
-and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is the smallest possible constant in \eqref{math:inequalitypf:gradient}. 
+and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is the smallest possible constant in~\eqref{math:inequalitypf:gradient}. 
 Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$.
@@
 
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains} \label{subsection: PX_convex}
+\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains}\label{subsection: PX_convex}
 
 We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of bounded convex domains. 
-We have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or \cite[Lemma~3.24]{ern2021finite}) 
+We have the Poincar\'e inequalities~\cite{Pay_Wei_Poin_conv_60,bebendorf2003note,acosta2004optimal} (or~\cite[Lemma~3.24]{ern2021finite}) 
 \begin{align}\label{math:acostaduran}
@@
     \\
-    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
+    \| u - u_{\Omega} \|_{L^{2}(\Omega)}\label{math:bebendorf}
     \leq 
@@
 \end{align*} 
-Note that \eqref{math:chuawheeden} is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
+Note that~\eqref{math:chuawheeden} is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
 As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.
 
-We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}, \cite[Theorem~1.1]{esposito2013poincare}): 
+We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark},~\cite[Theorem~1.1]{esposito2013poincare}): 
 when $1 < p < \infty$, one can show that 
@@
 % \begin{example}
-%     We explain why \eqref{math:l1estimate} is optimal. 
+%     We explain why~\eqref{math:l1estimate} is optimal. 
 %     Let $\Omega = (-1,1)$ and consider the family of odd function $u_{\epsilon} : \Omega \rightarrow \bbR$ for ${\epsilon} \in (0,1)$ 
@@
 %     and $\Omega$ has diameter $2$. 
-%     Since $u_{\epsilon}$ has average zero, this example shows that \eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
+%     Since $u_{\epsilon}$ has average zero, this example shows that~\eqref{math:acostaduran} is optimal among the constants that only depend on the diameter of the domain. 
 %     At the same time, for any constant $c \in \bbR$ we have $\| u_{\epsilon} - c \|_{L^1(\Omega)} = \| u_{\epsilon} + c \|_{L^1(\Omega)}$.
@@
     \end{align*}
-    In the case $2 \geq p$, 
+    In the case $p \leq 2$,
     \begin{align*}
@@
         2^{\frac 2 p - 2}
-        \\&
+        %\\&
         =
@@
     \end{align*}
-    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
+    It follows that~\eqref{math:esposito:poincare} is generally a tighter estimate than~\eqref{math:chuawheeden} for $1 < p < \infty$.
     % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
@@
 %     In the limit as $p$ goes to $1$, the factor $C_{{\rm EFNT},p}$ converges to $1/2$,
-%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
+%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality~\eqref{math:acostaduran}
 %     \begin{align*}
@@
     but individual convex domains may allow for better constants.
-    We refer to \cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for discussions;
+    We refer to~\cite{Liu_Kik_interp_10, Cars_Ged_Rim_expl_cnst_12, matculevich2016explicit} for discussions;
     for example, triangles allow the reduction of the constant by 20\%.
@@
 (i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
-We say that a simplicial complex $\calT$ has \emph{dimension $n$} or is \emph{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
+We say that a simplicial complex $\calT$ has \emph{dimension $n$} or is \emph{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.~\cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
 We also write $\underlying{\calT}$ for the \emph{underlying set} of the simplicial complex $\calT$, 
@@
     Numerous alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices (see~\cite[p.61, Definition 5.1]{braess2001finite},
-    \cite[p.97, Definition {\char`\(}4.2.16{\char`\)} ]{brenner2008mathematical}, % DONE: add brackets here in the final version or figure out how to fix the display in the editor.
-    \cite[Definition~11.2]{ern2021finite}). 
+   ~\cite[p.97, Definition {\char`\(}4.2.16{\char`\)} ]{brenner2008mathematical}, % DONE: add brackets here in the final version or figure out how to fix the display in the editor.
+   ~\cite[Definition~11.2]{ern2021finite}). 
 \end{remark}
@@
 We always construct a gradient potential over the new simplex and fix the constant of integration using the value already known on the connecting face, thereby constructing a scalar potential over larger and larger subdomains.
-This basic idea has appeared in various forms before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+This basic idea has appeared in various forms before, for instance recently in~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
 
@@
 We construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods.
-% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+% This basic idea has appeared in the different variants before, for instance recently in~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
 % 
@@
 % We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
-% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
+% This basic idea has appeared in the different variants before, for instance recently in~\cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
 % }
@@
 \begin{proof}
-    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
+    Unwrapping the recursion for the norm over the $m$-th simplex, the total expression takes the form
     \begin{align*}%\label{math:fullrecursivesum}
@@
 The wedge product (or exterior product) of alternating multilinear forms is a fundamental operation in exterior algebra
-(see~Chapter 14 in \cite{lee2012smooth}). 
+(see~Chapter 14 in~\cite{lee2012smooth}). 
 Given two alternating multilinear forms \( u_1 \in \Alt^{k}(V) \) and \( u_2 \in \Alt^{l}(V) \), 
@@
         \\
-        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega)
+        C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{3} @>{\curl}>> C^\infty(\Omega)^{3} @>{\divergence}>> C^\infty(\Omega),
     \end{CD}
-    \, ,
+    % \, ,
     \end{gather*}
@@
         C^\infty(\Omega) @>{\grad}>> C^\infty(\Omega)^{2} @>{\rot}>> C^\infty(\Omega)
+        .
     \end{CD}
-    \,.
+    % \,.
     \end{gather*}
@@
 The pullback of $u \in L^{p}\Alt^{k}(\Omega')$ along $\phi$ is the (measurable) differential form 
-\begin{align} \label{equation:pullback}
+\begin{align}\label{equation:pullback}
     \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
@@
     \end{align}
-    If $\phi$ is affine and $\sigma_1 \geq \sigma_2 \geq \dots \geq \sigma_n$ are the singular values of $\Jacobian\phi$, then 
+    If $\phi$ is affine and $\sigma_1 \geq \sigma_2 \geq \cdots \geq \sigma_n$ are the singular values of $\Jacobian\phi$, then 
     \begin{align}
@@
 
-We begin by introducing the Costabel-McIntosh kernel.
+We begin by introducing the Costabel--McIntosh kernel.
 For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
@@
 In order to analyze the properties of the potentials,
-we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
+we first rewrite the Costabel--McIntosh kernel $\calG_{\mia}$.
 Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
@@
 We conclude that, 
-\begin{align*}
-    u(x) &= \Poinc_{1,a} \cartan u(x) - u(a), \qquad k = 0,
-    \\
-    u(x) &= \cartan \Poinc_{\mia,a} u(x) + \Poinc_{\mia+1,a} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align*}
+\begin{alignat*}{4}
+    u(x) &= \Poinc_{1,a} \cartan u(x) - u(a), \qquad                              && k = 0,
+    \\
+    u(x) &= \cartan \Poinc_{\mia,a} u(x) + \Poinc_{\mia+1,a} \cartan u(x), \qquad && 1 \leq \mia \leq n.
+\end{alignat*}
+% \begin{align*}
+%     u(x) &= \Poinc_{1,a} \cartan u(x) - u(a), \qquad k = 0,
+%     \\
+%     u(x) &= \cartan \Poinc_{\mia,a} u(x) + \Poinc_{\mia+1,a} \cartan u(x), \qquad 1 \leq \mia \leq n.
+% \end{align*}
 In summary, after taking the average over $a \in \Omega$:
-\begin{align}\label{math:hodgedecomposition:poinc}
-    u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \,da, \qquad k = 0,
-    \\
-    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
-\end{align}
+\begin{alignat}{4}\label{math:hodgedecomposition:poinc}
+    u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \,da,  \qquad && k = 0,
+    \\
+    u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x),          \qquad && 1 \leq \mia \leq n.
+\end{alignat}
+% \begin{align}\label{math:hodgedecomposition:poinc}
+%     u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \,da, \qquad k = 0,
+%     \\
+%     u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
+% \end{align}
 
@@
 The limit of this is $\phi(a) \int_\Omega u(x)$ as $\epsilon$ goes to zero. 
-To complete the discussion, we write the exterior derivative of $u$ as in \eqref{math:exteriorderivative_of_u_in_hodgediscussion}, 
+To complete the discussion, we write the exterior derivative of $u$ as in~\eqref{math:exteriorderivative_of_u_in_hodgediscussion}, 
 % \begin{align*}
@@
 % We conclude that 
-\begin{align*}
-    u(x) &= \cartan \Bogov_{\mia,a} u(x) + \Bogov_{\mia+1,a} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
-    \\
-    u(x) &= \cartan \Bogov_{n,a} u(x) - \left( \int_{\Omega} u(a) \right) \delta_a, \qquad k = n.
-\end{align*}
+\begin{alignat*}{4}
+    u(x) &= \cartan \Bogov_{\mia,a} u(x) + \Bogov_{\mia+1,a} \cartan u(x),          \qquad && 0 \leq \mia \leq n-1,
+    \\
+    u(x) &= \cartan \Bogov_{n,a} u(x) - \left( \int_{\Omega} u(a) \right) \delta_a, \qquad && k = n.
+\end{alignat*}
 Here, $\delta_a$ denotes the Dirac delta at $a$. 
 In summary, after taking the average over $a \in \Omega$:
-\begin{align}\label{math:hodgedecomposition:bogov}
-    u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
-    \\
-    u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}, \qquad k = n.
-\end{align}
+\begin{alignat}{4}\label{math:hodgedecomposition:bogov}
+    u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x),                                   \qquad && 0 \leq \mia \leq n-1,
+    \\
+    u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}, \qquad && k = n.
+\end{alignat}
 
@@
     For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds for a.e.\ $x \in \Omega$ that 
-    \begin{align}
-        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
+    \begin{alignat}{4}
+        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da, && \qquad k = 0,
         \label{math:theorem:bogovpoinc:poincare:zero}
         \\
-        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
+        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x),        && \qquad 1 \leq \mia \leq n.
         \label{math:theorem:bogovpoinc:poincare:k}    
-    \end{align}
+    \end{alignat}
     In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
@@
     For any $u \in \bfW^{p}_{0}\Alt^{\mia}(\Omega)$ it holds for a.e.\ $x \in \Omega$ that 
-    \begin{align}
-        u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x), \qquad 0 \leq \mia \leq n-1,
+    \begin{alignat}{4}
+        u(x) &= \cartan \Bogov_{\mia} u(x) + \Bogov_{\mia+1} \cartan u(x),
+        \qquad && 0 \leq \mia \leq n-1,
         \label{math:theorem:bogovpoinc:bogov:k}
         \\
-        u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega}.
+        u(x) &= \cartan \Bogov_{n} u(x) - \left( \vol(\Omega)^{-1} \int_{\Omega} u(a) \right) \chi_{\Omega},
+        \qquad && k=n.
         \label{math:theorem:bogovpoinc:bogov:n}
-    \end{align}
+    \end{alignat}
     In particular, if $u \in W^{p}_{0}\Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Bogov_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.
@@
     Hence, by definition, $\zeta \in W^{p}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Poinc_{\mia+1} \cartan u$.
-    This shows \eqref{math:theorem:bogovpoinc:poincare:k}, and \eqref{math:theorem:bogovpoinc:poincare:zero} follows by an approximation argument.
+    This shows~\eqref{math:theorem:bogovpoinc:poincare:k}, and~\eqref{math:theorem:bogovpoinc:poincare:zero} follows by an approximation argument.
 
@@
     By definition, $\zeta \in W^{p}_{0}\Alt^{\mia-1}(\Omega)$ with $\cartan \zeta = u - \Bogov_{\mia+1} \cartan u$.
-    This shows \eqref{math:theorem:bogovpoinc:bogov:k}, and \eqref{math:theorem:bogovpoinc:bogov:n} follows by an approximation argument.
+    This shows~\eqref{math:theorem:bogovpoinc:bogov:k}, and~\eqref{math:theorem:bogovpoinc:bogov:n} follows by an approximation argument.
 
@@
 
-\begin{remark} \label{remark:reg_Poinc_Bog}
+\begin{remark}\label{remark:reg_Poinc_Bog}
     The classical Poincar\'e operator is known for its role in proving the exactness of the smooth de~Rham complex over star-shaped domains~\cite{lee2012smooth}.
@@
     Under these assumptions, 
-    as explained in the proof of Theorem~1 in \cite{Siebenmann1979},
+    as explained in the proof of Theorem~1 in~\cite{Siebenmann1979},
     the set $\carapace(V)$ is a triangulation of a sphere of dimension $n-1$ for any inner vertex $V$. 
@@
 \begin{remark}
-    Triangulations with the property that all vertex stars are homeomorphic to a ball are also called \emph{combinatorial} \cite[Section~1]{Bagchi2005}.
+    Triangulations with the property that all vertex stars are homeomorphic to a ball are also called \emph{combinatorial}~\cite[Section~1]{Bagchi2005}.
     All manifolds of dimension up to three admit smooth structures and smooth manifolds admit combinatorial triangulations. 
@@
     Similarly, when $S$ is a boundary vertex, then the faces (triangles) of $\patch_{\calT}(S)$ that do not contain $V$ constitute a simplicial $2$-\disk.
-    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondence between the tetrahedra in $\calT$ and the triangles.
-    \footnote{For $S$ an inner vertex, \cite[Lemma~B.1]{ern2020stable} also yields the claim.}
+    Both these $2$-dimensional complexes are shellable by Lemma~\ref{lemma:shell_2D}, and any such shelling immediately yields a shelling of $\patch_{\calT}(S)$ since there is a one-to-one correspondence between the tetrahedra in $\calT$ and the triangles.\footnote{For $S$ an inner vertex,~\cite[Lemma~B.1]{ern2020stable} also yields the claim.}
 \end{proof}
@@
 \begin{proof}
-    This is Lemma~8.7 in \cite{ziegler1995lectures}.
+    This is Lemma~8.7 in~\cite{ziegler1995lectures}.
 %     Without loss of generality, $V$ is the origin. 
@@
     Moreover, even if a set admits a shellable triangulation, not all of its triangulations are shellable.
-For example, if we extend the non-shellable triangulation of the tetrahedron from~\cite[Example 8.9]{ziegler1995lectures} to a triangulation of a hypertetrahedron by suspending it from a new point $v_\star$, then the resulting new triangulation is non-shellable and coincides with the patch around $v_\star$.
+For example, if we extend the non-shellable triangulation of the tetrahedron from~\cite[Example 8.9]{ziegler1995lectures} to a triangulation of a hypertetrahedron by suspending it from a new point $v^\star$, then the resulting new triangulation is non-shellable and coincides with the patch around $v^\star$.
     This demonstrates that patches around boundary simplices are not necessarily shellable when the space dimension $n$ is larger than three.
@@
 We construct a homeomorphism going from the simplex $T$ onto its complement within the local star around $S$,
-similar to the two- and three-color maps in \cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}
+similar to the two- and three-color maps in~\cite[Sections~5.3 and~6.3]{ern2020stable} and the symmetrization maps in~\cite[Section~7.6]{Chaum_Voh_p_rob_3D_H_curl_24}
 This homeomorphism, which we interpret as a nonlinear reflection, is required to preserve the interface. 
@@
         \begin{align*}
-            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
+            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q.
         \end{align*}
@@
         \end{align*}
-        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
+        Computing the eigenvalues of the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$,
         we obtain the singular values 
@@
     Under the assumptions of Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, 
-    the special case $p=2$ allows to improve the preceding lemma.
-    Specifically, we use a better estimate for the auxiliary constant in \eqref{math:mixedbconsimplex:exteriorderivative:internalconstant}.
-    This follows from the results in \cite{licht2024geometry} as simplices are Lipschitz domains.
+    the special case $p=2$ allows improving the preceding lemma.
+    Specifically, we use a better estimate for the auxiliary constant in~\eqref{math:mixedbconsimplex:exteriorderivative:internalconstant}.
+    This follows from the results in~\cite{licht2024geometry} as simplices are Lipschitz domains.
     The complete inequality then reads: 
@@
     We now define, as in~\cite[Equations~{\char`\(}5.12{\char`\)} and~{\char`\(}5.14{\char`\)}]{ern2020stable} or~\cite[Equations~{\char`\(}6.7{\char`\)} and~{\char`\(}6.9{\char`\)}]{Chaum_Voh_p_rob_3D_H_curl_24}, the field $\widetilde w_{m} \in W^{p}\Alt^{k}(T_{m})$ via
-    \begin{align} \label{equation:w''_ext_der}
+    \begin{align}\label{equation:w''_ext_der}
         {\widetilde w}_{m} := u_{|T_m} + \Xi_{1}^{\ast}\left( (w_{m-1} - u)_{|\Makoto_{m-1} } \right).
@@
 Whenever $T$ is a simplex, the Poincar\'e--Friedrichs constants have upper bounds of the form $C \diam(T)$ for some numerical constant $C > 0$.
-Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and the subequent remark (using $p=2$) have established that $C = 2/\pi \approx 0.45015815807$.
+Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and the subsequent remark (using $p=2$) have established that $C = 2/\pi \approx 0.45015815807$.
 In the special case of the gradient potential, where the Poincar\'e constant can be characterized variationally, the Poincar\'e constant without boundary conditions is already an upper bound for the Poincar\'e constant with boundary conditions, and one can choose $C = 1/\pi \approx 0.31830988618$.
@@
 
-The most important contribution of this manuscript is the computation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., \ $n=2$ or $n=3$).
-However, our upper bounds are hardly the last word on estimating the Poincar\'e--Friedrichs constants over local patches (stars).
-There are several avenues for further research and improvement, both in the analytical tools and the implementations.
+The primary contribution of this manuscript is the derivation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., $n=2$ or $n=3$).
+However, we believe there are ample opportunities for refining our estimates of Poincar\'e--Friedrichs constants and extending the technique to further applications.
 
 We use local Poincar\'e--Friedrichs inequalities over single simplices, subject to boundary conditions along some faces.
-The estimates would improve considerably from sharper bounds on the local Poincar\'e constants. 
-However, not many specific results seem to be available for the various special cases. 
+We believe that tighter estimates of these are achievable.
+In particular, we conjecture that the improvements for triangles~\cite{laugesen2010minimizing} have analogs for tetrahedra.
+
 The gradient Poincar\'e--Friedrichs constant already dominates the Poincar\'e--Friedrichs constants of the $\Lebesgue^2$ de~Rham complex without boundary conditions (or with full boundary conditions) over convex domains~\cite{guerini2004eigenvalue,licht2024geometry}.
-We believe that this generalizes to the entire range of Lebesgue exponents $1 \leq p \leq \infty$
-Such estimates would likely improve on the Poincar\'e--Friedrichs constants derived via the regularized Poincar\'e and Bogovski\u{\i} operators. 
-As mentioned in the manuscript, the Poincar\'e constant over triangles admits a sharper upper bound than for general convex domains. We conjecture that tetrahedra permit a similar improvement.
-
-Our method uses the extension of differential forms onto a simplex from the complement of that simplex within a local star. 
-In the present manuscript, this extension is via pullback along a bi-Lipschitz mapping, but different techniques, such as via trace and extension operators, could lead to better estimates.
-
-There is little research on practical algorithms that construct shellings.
-Checking whether a general triangulation has a shelling is computationally infeasible.
-While the literature knows a few theoretical results, there is interest in algorithms that attempt to shell practically relevant triangulations while optimizing geometric target heuristics.
-
-We expect the present results to generalize to shellable polytopal complexes. 
-Apart from the intrinsic interest in polytopal simplicial complexes, this extension is also relevant for any simplicial triangulation:
+We believe that this relationship extends to the entire range of Lebesgue exponents $1 \leq p \leq \infty$,
+improving on the Poincar\'e--Friedrichs constants derived via the regularized Poincar\'e and Bogovski\u{\i} operators.
+
+Our method hinges on extending differential forms onto a simplex from the complement of that simplex within a local star.
+Whilst the present manuscript realizes this extension via pullback along a bi-Lipschitz mapping, better estimates might be possible via different techniques, e.g., carefully analyzing trace and extension theorems.
+
+On the algorithmic part, even though merely checking whether a general triangulation has a shelling is known to be computationally infeasible,
+there might be more efficient algorithms for constructing shellings for practically relevant triangulations while optimizing geometric target heuristics.
+
+We anticipate the present results to generalize to shellable polytopal complexes.
+Apart from the intrinsic interest in polytopal simplicial complexes, such extensions are already relevant for simplicial triangulation:
 As a rule of thumb, the estimates deteriorate as the number of simplices increases.
-We might improve our estimates by lumping simplices into a few polytopal subdomains for which the Poincar\'e--Friedrichs constants are controllable.
+Lumping simplices into a few polytopal subdomains for which the Poincar\'e--Friedrichs constants are controllable could improve the estimates.
 For example, the crossed bricks domain easily partitions into four quadrilaterals.
 
-Lastly, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is restricted to topological balls and spheres. 
-In particular, the underlying set of any shellable triangulations is contractible. 
-We expect forthcoming works to utilize our estimates over local patches as subcomponents in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds.
+Lastly, estimating Poincar\'e--Friedrichs constants over domains and manifolds with shellable triangulations is fundamentally restricted to topological balls and spheres.
+However, we expect our estimates over local patches to serve as subcomponents in estimating Poincar\'e--Friedrichs constants of general $n$-dimensional triangulated manifolds.
 
@@
 % such as the Hodge Laplace equation. 
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
+% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in~\eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
 
@@
 % LTeX: enabled=false
-MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, by John M.\ Lee, and G\"unther M.\ Ziegler.
+MWL appreciates helpful remarks by Abdellatif Aitelhad, Martin Costabel, John M.\ Lee, and G\"unther M.\ Ziegler.
 % LTeX: enabled=true

### 2025-02-12 main.tex

@@
 The primary contribution of this manuscript is the derivation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., $n=2$ or $n=3$).
-However, we believe there are ample opportunities for refining our estimates of Poincar\'e--Friedrichs constants and extending the technique to further applications.
+However, we believe there are ample opportunities for refining our estimates of Poincar\'e--Friedrichs constants, both conceptually and algorithmically, and extending the technique to further applications.
 

### 2025-02-12 main.tex
main

@@
 For the differential operators of vector calculus and exterior calculus, we choose to be more restrictive:
-we require the new simplex to intersect with the existing subtriangulation along an $(n-1)$-dimensional boundary submanifold, allowing us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex.
+we require the new simplex to intersect with the existing subtriangulation along a boundary submanifold of dimension $n-1$, allowing us to define a well-posed auxiliary problem and to extend the existing curl potential to the new simplex.
 Whether a triangulation admits such a particular traversal is a non-trivial condition and defines the class of \emph{shellable} triangulations.
@@
 The remainder of this manuscript is structured as follows.
-We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}. 
-We also discuss there the difference with the Poincar\'e inequality and motivate our interest in linear potentials.
+We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare},
+where we also discuss the difference with the Poincar\'e inequality and motivate our interest in linear potentials.
 We review basic notions of triangulations in Section~\ref{section:triangulations}.
-We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
-We recap Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}. 
-Our regularized potentials over convex sets are then introduced in Section~\ref{section:potentialoperator}, 
+Subsequently, we develop the computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
+Sobolev spaces in vector calculus and the calculus of differential forms are reviewed in Section~\ref{section:calculus}. 
+We then introduce our regularized potentials over convex sets in Section~\ref{section:potentialoperator}, 
 giving rise to computable Poincar\'e--Friedrichs constants as their operator norms. 
@@
 and we construct an important geometric reflection operator in Section~\ref{section:extension}. 
-We finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
-We present numerical examples in Section~\ref{section:numericalexamples} and conclude by some outlook in Section~\ref{section:outlook}. 
+Finally, we provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs} and present numerical examples in Section~\ref{section:numericalexamples}.
+We conclude with an outlook in Section~\ref{section:outlook}. 
 % LTeX: enabled=true
@@
     We can improve Lemma~\ref{lemma:mixedbconsimplex} in the special case $p=2$.
-    The variational formulation of the Poincar\'e constant over a convex domain reveals that $C_{\PF,T,F,p}$ lies between the the Poincar\'e constant without boundary conditions and with full boundary conditions.
+    The variational formulation of the Poincar\'e constant over a convex domain reveals that $C_{\PF,T,F,p}$ lies between the Poincar\'e constant without boundary conditions and with full boundary conditions.
     In particular,
@@
 Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} gives estimates for the gradient, curl and divergence Poincar\'e--Friedrichs constants. 
-In addition, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} provides anotherr upper bound for the Poincar\'e constant.
+In addition, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} provides another upper bound for the Poincar\'e constant.
 We remark that the Poincar\'e--Friedrichs constant for the divergence can always be estimated by less than the diameter of the domain (see Lemma~\ref{lemma:mixedbconsimplex}), so our recursive estimates are of no practical interest in that case.
@@
 All computations have been implemented with an in-house C++ code developed specifically for implementing finite element exterior calculus. 
-The reference Poincar\'e constants are the inverse square roots of reference eigenvalues.
-We compute the latter by solving finite element eigenvalue problems that involve mixed formulations of the vector Laplacian over sufficiently refined meshes.
-
-Computing the upper bound for the Poincar\'e constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires to find paths between simplices.
-One quickly sees that a spanning tree of the face-connection graph minimizes the estimate.
+The reference Poincar\'e constants are the inverse square roots of reference eigenvalues,
+the latter being computed as solutions of finite element eigenvalue problems in mixed formulation over sufficiently refined meshes.
+
+Computing the upper bound for the Poincar\'e constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires computing paths between simplices. 
+One quickly sees that a spanning tree of the face-connection graph provides paths that minimize the estimate.  
 We choose a depth-first search that attempts to minimize the resulting constant. 
-While this does not take much time for small two-dimensional examples, the computation takes considerably for our three-dimensional examples.
-
-Computing the upper bound for the Poincar\'e--Friedrichs constant of Theorem~\ref{theorem:fullrecursivesum:grad} requires the construction of shellings. 
+While this does not take much time for small two-dimensional examples, the computation takes considerably longer for our three-dimensional examples.
+
+We require a shelling to apply Theorem~\ref{theorem:fullrecursivesum:grad} and estimate the upper bound for the Poincar\'e--Friedrichs constant. 
 Finding a shelling that optimizes a geometric target quantity is a challenging problem in computational geometry and theoretical computer science. 
-While a brute-force enumeration of shellings is still feasible for small two-dimensional triangulations, it becomes unfeasible in dimension three due to the combinatorial explosion of the number of possible shellings.
-Instead, we perform a greedy backtracking search: 
+While a brute-force enumeration of shellings is still feasible for small two-dimensional triangulations, it becomes practically infeasible in dimension three due to the combinatorial explosion of the number of possible shellings.
+Instead, we perform a backtracking search guided by a greedy strategy: 
 Starting with a single simplex, we successively add simplices to the partial shellings until a complete shelling is found. 
-This backtracking algorithm does generally not find the optimal shelling until all shellings have been checked.
-However, enumerating and checking all shellings seems practically infeasible.
-
-Therefore, we need a practical heuristic to find shellings that induce small constants.
-Indeed, our computations show that the Poincar\'e--Friedrichs estimates depend on the shelling and can differ by orders of magnitudes.
-Our implementation starts with a fixed simplex and generates up to $10$ shellings.
-We repeat this for all possible initial simplices and pick the optimal shelling among those found.
-We use a greedy strategy: Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
-We moreover prioritize the completion of face stars since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
-In other words, we defer the completion of non-face stars in order to not introduce large factors early into the recursion.
-
-For tight estimates, we must compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each geometric transformation.
-The estimates that we use are slightly tighter than the ones stated in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:exterior},
-as we directly implement the calculations used in the proofs.
+% 
+% 
+In choosing among the possible candidates for the next simplex, our practical heuristic prefers those that introduce the smallest possible geometric constants, and we further prioritize the completion of face stars because then the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}.
+% 
+% 
+We repeat this backtracking approach for all possible initial simplices, producing up to $10$ shellings each time, and pick the optimal shelling among those found. 
+We have observed in our computations that the Poincar\'e--Friedrichs estimates depend on the shelling and may differ by orders of magnitudes;
+the method might not necessarily produce the global optimum.
+
+In order to ensure tight estimates, we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each local star.
+These estimates are numerically tighter than the ones stated in Theorems~\ref{theorem:poincarefriedrichsestimate:grad} and~\ref{theorem:poincarefriedrichsestimate:exterior}, as we directly implement the calculations used in the proofs.
+
+% and pick the optimal shelling among those found.
+% This backtracking algorithm does generally not find the optimal shelling until all shellings have been checked.
+% However, enumerating and checking all shellings seems practically infeasible. 
+% Therefore, we need a practical heuristic to find shellings that induce small constants. 
+% Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
+% We repeat this for all possible initial simplices and pick the optimal shelling among those found.
+% We use a greedy strategy: Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
+% We moreover prioritize the completion of face stars since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
+% In other words, we defer the completion of non-face stars in order to not introduce large factors early into the recursion.
 
@@
 
-We overestimate by a factor of at most six.
-We take this as an indication that the estimate is within feasible range, at least on simplices with good shape regularity. 
-We expect the bound to deteriorate as the eccentricity of the tetrahedron increases.
-However, the results indicate room for improvement. 
-Future estimates should tighten the gap towards the actual computed values,
-including for ill-shaped simplices.
+With an overestimate by a factor of at most six,
+the estimate seems within practical range, at least on simplices with good shape regularity. 
+However, the results indicate room for improvement, and we expect the overestimate to worsen as the eccentricity of the tetrahedron increases.
+Future estimates should tighten the gap towards the actual computed values, including for ill-shaped simplices.
 

### 2025-02-14 main.tex
more proofreading

@@
 
-For this illustration, we let $\Omega \subseteq \bbR^3$ be a bounded connected open set. 
+For the purpose of illustration, we let $\Omega \subseteq \bbR^3$ be a bounded connected open set.
 We let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $1 \leq p \leq \infty$, 
@@
 \end{align}
-Such an inequality holds if we can bound the \emph{operator norm} of this gradient potential operator, and then the best constant is  
+Such an inequality holds if we can bound the \emph{operator norm} of this gradient potential operator. Then the best constant is
 %the $L^{p}(\Omega)$ norm of the potential $\Phi_{\grad}( \bff )$ is bounded in terms of the $\bfL^{p}(\Omega)$ norm of the source field $\bff$.
@@
 \end{align}
-Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally difficult. 
+Finding the norm-minimizing potential and the optimal Poincar\'e--Friedrichs constant is generally tricky.
 Attention has focused on \emph{linear} potentials instead of the norm-minimizing nonlinear potential~\eqref{math:intro:gradientpotential}.
@@
 
-In the Banach space case, it is not even trivial whether a norm-minimizing potential actually exists.
+In the Banach space case, not even the existence of norm-minimizing potentials is trivial.
 We are therefore interested in any potentials 
-\begin{align}
-    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
-    ,
-    \\
-    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
-\end{align}
+\begin{gather}
+    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
+    ,
+    \\
+    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
+\end{gather}
 and their operator norms. We remark that upper bounds for the Poincar\'e--Friedrichs inequality of the curl operator correspond to lower bounds for the so-called Maxwell eigenvalues. 
 In sharp contrast to the extensive research on gradient potentials, 
-not much attention seems to have been given to the study of computable constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators.
+not much research seems available on computable constants in such Poincar\'e--Friedrichs inequalities for the curl operators.
 
@@
 This formalism is independent of the spatial dimension and highlights the underlying geometric structures common to the gradient, curl, and divergence operators in three space dimensions.
-For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ and such that (all the notation is fixed in detail in Section~\ref{section:calculus} later)
+For every $u \in W^{p}\Alt^{k}(\Omega)$, there exists $w \in W^{p}\Alt^{k}(\Omega)$ with the sam exterior derivative $\cartan w = \cartan u$ and such that\footnote{All the notation is fixed in detail in Section~\ref{section:calculus} later.}
 \begin{align}\label{math:intro:exterior:pf} 
@@
 % curl 
-The core challenges can be found in the discussion of the curl operator in three dimensions,
+The core challenges are found in the discussion of the curl operator in three dimensions,
 where Poincar\'e--Friedrichs inequalities have appeared under different names.
-Let us assume for a moment that $\Omega$ is a weakly Lipschitz domain with trivial topology, and consider only the Hilbert case $p=2$. 
+Let us assume momentarily that $\Omega$ is a weakly Lipschitz domain with trivial topology and consider only the Hilbert case $p=2$.
 Then the constant in~\eqref{math:intro:Wcurl:pf} agrees with the constant in the so-called Poincar\'e--Friedrichs--Weber inequality
@@
 Guerini and Savo~\cite{guerini2004eigenvalue} address the spectrum of the Hodge--Laplace operator on bounded convex domains with smooth boundary in the Hilbert space case $p=2$.
-Their results thus pertain to the Poincar\'e--Friedrichs constant of the exterior derivative, and hence in particular to the curl and divergence operators.
-They prove that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
+Among their results is the observation that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators.
 They also provide explicit (but not necessarily optimal) upper bounds for Poincar\'e--Friedrichs constants that depend only on the dimension and diameter of the convex domain.
@@
 
-When the domain is not convex but star-shaped with respect to a ball,
+When the domain is not necessarily convex but star-shaped with respect to a ball,
 then several estimates for Poincar\'e--Friedrichs constants are known.\footnote{In fact, Poincar\'e--Friedrichs inequalities even hold over any star-shaped open bounded set; see~\cite[Theorem~3.1]{hurri1988poincare}.}
@@
 such as those of Costabel and McIntosh~\cite{costabel2010bogovskiui}.
-In principle, if we conceive these potentials as mappings between Lebesgue spaces of differential forms, then their operator norms are upper estimates for the Poincar\'e--Friedrichs constants of the domain.
+If we conceive these potentials as mappings between Lebesgue spaces of differential forms, then their operator norms are upper estimates for the Poincar\'e--Friedrichs constants of the domain.
 We are aware of estimates for the higher-order seminorms of these potentials~\cite{guzman2021estimation},
@@
 which would enable, e.g., the averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui},
-the estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter.
+the estimates that rely on this geometric condition deteriorate when the aforementioned ball has a radius much smaller than the domain diameter.
 While this is not as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation, the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the triangulation displays decent shape regularity.
@@
 
-The main objective of this manuscript is the construction of potentials for the gradient, curl, and divergence, and more generally the exterior derivative.
+The main objective of this manuscript is the construction of potentials for the gradient, curl, and divergence, as well as, more generally, the exterior derivative.
 The operator norms of our potentials satisfy computable upper bounds, thus yielding computable upper estimates of the Poincar\'e--Friedrichs constants as well.
@@
 
-We also address the construction of potentials for the gradient, curl, and divergence operators, and in general the exterior derivative, over a simplex subject to partial boundary conditions.
+We also address the construction of potentials for the gradient, curl, and divergence operators, being special cases of the exterior derivative, over a simplex subject to partial boundary conditions.
 We are not aware of explicit estimates or regularized potentials for these boundary conditions in the published literature.
@@
 We thus obtain Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions.
-Again, we address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents and our Poincar\'e--Friedrichs constants are explicitly computable.
+Again, we address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents, and our Poincar\'e--Friedrichs constants are explicitly computable.
 
@@
 
-Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, including the curl and divergence in particular, over triangulated domains.
+Our main objective remains to find potentials for the differential operators of vector calculus and exterior calculus, including the curl and divergence over triangulated domains.
 The operator norms of these potentials will serve as our computable Poincar\'e--Friedrichs constants.
@@
 
-This section surveys variations of the Poincar\'e--Friedrichs inequalities for the gradient operator,
-with emphasis on analytical upper bounds over bounded convex domains. 
+This section surveys variations of the Poincar\'e--Friedrichs inequalities for the gradient operator, with emphasis on analytical upper bounds over bounded convex domains.
 We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potentials.
@@
     Upper bounds for Poincar\'e--Friedrichs constants~\eqref{math:inequalitypf:gradient} are easily obtained from linear potentials.
-    We highlight this perspective because it seems to be most promising when generalizing the discussion to the curl and divergence operators. 
+    We highlight this perspective because it is our theoretical backbone when generalizing the discussion to the curl and divergence operators.
 \end{remark}
 
-\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains}\label{subsection: PX_convex}
+\subsection{Analytical constants in Poincar\'e--Friedrichs inequalities over bounded convex domains}\label{subsection:PX_convex}
 
@@
 
-We gather here basic notions and definitions concerning simplicial meshes.
-
-% \subsection{A triangulation or a simplicial complex}
+We gather basic notions and definitions concerning simplicial meshes.
 
@@
 A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions:
-(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
+(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each.
 We say that a simplicial complex $\calT$ has \emph{dimension $n$} or is \emph{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.~\cite{ziegler1995lectures}) and simply ``simplicial meshes'' in the finite element literature.}
@@
 which is the union $\underlying{\calT} = \bigcup \calT$ of all simplices in $\calT$.
+One calls any set triangulable if it is the underlying set of some triangulation.
 % \begin{align*}
@@
 % \end{align*}
-One calls any set triangulable if it is the underlying set of some triangulation. 
 % DONE {Settle the issue that triangulations are closed but that domains are open sets.}
@@
 The next auxiliary result establishes Poincar\'e--Friedrichs constants over face patches within simplicial triangulations. 
-We emphasize that face patches are not necessarily convex, but we can still extend the results on convex domains from Section~\ref{subsection: PX_convex}.
+We emphasize that face patches are not necessarily convex, but we can still extend the results on convex domains from Section~\ref{subsection:PX_convex}.
 The following result is reasonably sharp when the two simplices have similar volumes and diameters.
@@
     In what follows, we let $\widetilde \Makoto$ be the convex set obtained from reflecting $\Delta^n$ along the coordinate axes $\ell+1$ through $n$. 
-    We see that $\vol(\widetilde \Makoto) = 2^{n-\ell} \vol(\Delta^n) = 2^{n-\ell}/n!$
+    We see that $\vol(\widetilde \Makoto) = 2^{n-\ell} \vol(\Delta^n) = 2^{n-\ell}/(n!)$
 
@@
 
-Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} gives estimates for the gradient, curl and divergence Poincar\'e--Friedrichs constants. 
+Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} estimates the gradient, curl and divergence Poincar\'e--Friedrichs constants.
 In addition, Theorem~\ref{theorem:poincarefriedrichsestimate:grad} provides another upper bound for the Poincar\'e constant.
@@
 All computations have been implemented with an in-house C++ code developed specifically for implementing finite element exterior calculus.
-The reference Poincar\'e constants are the inverse square roots of reference eigenvalues,
-the latter being computed as solutions of finite element eigenvalue problems in mixed formulation over sufficiently refined meshes.
+The reference Poincar\'e constants are the inverse square roots of reference eigenvalues, the latter computed as solutions of finite element eigenvalue problems in mixed formulation over sufficiently refined meshes.
 
@@
 % We moreover prioritize the completion of face stars since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}.
-% In other words, we defer the completion of non-face stars in order to not introduce large factors early into the recursion.
+% In other words, we defer the completion of non-face stars to postpone large factors to the end of the recursion.
 
@@
 
-Specifically, and subject to different boundary conditions 
-We first assess the Poincar\'e--Friedrichs constant over the reference simplex where boundary conditions hold along a few faces. 
-This is of interest because the constant appears repeatedly within our main result.
+% Specifically, and subject to different boundary conditions
+We first assess the Poincar\'e--Friedrichs constant over the reference simplex where boundary conditions hold along a few faces
+because that constant appears repeatedly within our main result.
 
@@
 However, the results indicate room for improvement, and we expect the overestimate to worsen as the eccentricity of the tetrahedron increases.
-Future estimates should tighten the gap towards the actual computed values, including for ill-shaped simplices.
+Future estimates should tighten the gap towards the practically observed values, including for ill-shaped simplices.
 
@@
 The primary contribution of this manuscript is the derivation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., $n=2$ or $n=3$).
-However, we believe there are ample opportunities for refining our estimates of Poincar\'e--Friedrichs constants, both conceptually and algorithmically, and extending the technique to further applications.
+However, we believe there are ample opportunities to refine our estimates of Poincar\'e--Friedrichs constants, both conceptually and algorithmically, and extend the technique to further applications.
 
@@
 
-On the algorithmic part, even though merely checking whether a general triangulation has a shelling is known to be computationally infeasible,
+On the algorithmic part, even though merely checking whether a general triangulation has a shelling is known to be computationally infeasible \cite{goaoc2019shellability},
 there might be more efficient algorithms for constructing shellings for practically relevant triangulations while optimizing geometric target heuristics.

### 2025-02-14 main.tex
minor tweaks
Update on Overleaf.
reorder some tex for clarity

@@
+% \documentclass[sn-mathphys-num]{sn-jnl}
 \documentclass[10pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{fullpage}
-% \usepackage[margin=0.1cm]{geometry}
+
 \input{header}
-
-\usepackage{xcolor}          % 
-\usepackage{comment}          % 
-\usepackage[colorlinks=true]{hyperref}         % For hypertext links
-% Make the hyperlinks look similar to arXiv's
-\hypersetup{
-    colorlinks=true,
-    linkcolor=Maroon,    % Color of internal links (sections)
-    citecolor=red,    % Color of citations
-    urlcolor=blue,     % Color for URLs
-    urlbordercolor={1 1 1},
-    pdfborder={0.5 0.5 0}  % Removes the border around the links
-}
-\usepackage{tikz-3dplot}      % 3d plots 
-\usepackage{enumitem}
-\setitemize[1]{left=0.0cm}
-
-% Added by MV 
-\usepackage{bm} % preferred version of bold symbols
-\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
-% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
-% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
-% \newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
-\setlength{\marginparwidth}{2cm}
-
-\newcommand\cye[1]{%
-\protect\leavevmode
-\begingroup
-    \color{blue}%
-    #1%
-\endgroup
-}
-% \color{red!35!yellow}
 
@@
 % \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
-
 \title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
@@
     We thus compute upper bounds for constants in Poincar\'e--Friedrichs inequalities and lower bounds for the eigenvalues of vector Laplacians.
-    % We derive computable bound on the operator norms of our potentials that only depend on the geometry.
-    % 
-    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
-    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
-    %     The main application that we envision are computable estimates over finite element patches. 
-    %
     As an additional result with independent standing, we establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains, derived as explicit operator norms of regularized Poincar\'e and Bogovski\u{\i} potential operators.
@@
 
-% While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions, patches of simplices sharing a common vertex, edge, face, or nn-simplex.
+% While shellable triangulations are slightly less general than merely face-connected ones, they encompass important cases such as local stars in two and three dimensions, patches of simplices sharing a common vertex, edge, face, or $n$-simplex.
 These local patches are inherently shellable, making our approach widely applicable.
@@
 
-% DONE {TCF: Is the definition of trace satisfactory for matching traces across simplicies?}
+% DONE {TCF: Is the definition of trace satisfactory for matching traces across simplices?}
 
@@
 
-% DONE {I guess the way we remove the $\chi_\Omega$ is beause we somehow have a convex (if $r \leq \delta(\Omega)$) conbination of $x,y$, correct? It would be nice poiting it out explicitly.}
+% DONE {I guess the way we remove the $\chi_\Omega$ is because we somehow have a convex (if $r \leq \delta(\Omega)$) combination of $x,y$, correct? It would be nice pointing it out explicitly.}
 

### 2025-02-14 main.tex
latex tweaks of main files

@@
 \input{header}
+
+\usepackage[colorlinks=true]{hyperref}         % For hypertext links
+% Make the hyperlinks look similar to arXiv's
+\hypersetup{
+    colorlinks=true,
+    linkcolor=Maroon,    % Color of internal links (sections)
+    citecolor=red,    % Color of citations
+    urlcolor=blue,     % Color for URLs
+    urlbordercolor={1 1 1},
+    pdfborder={0.5 0.5 0}  % Removes the border around the links
+}
 
@@
 \begin{figure}[t]
+\caption{From left to right: local patches around a vertex, and edge, and a triangle.
+The local patch of any full-dimensional simplex only consists of that simplex itself (and its subsimplices).}\label{figure:patches}
 \centering
@@
 \end{tabular} 
-\caption{From left to right: local patches around a vertex, and edge, and a triangle.
-The local patch of any full-dimensional simplex only consists of that simplex itself (and its subsimplices).}\label{figure:patches}
 \end{figure}
@@
 \begin{figure}[t]
+\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}\label{figure:spanningtree}
 \begin{center}
@@
 \end{center}
-\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
-\label{figure:spanningtree}
 \end{figure}
@@
 \begin{figure}[h]
+\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}\label{figure:not_manifold_triang}
 % \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
@@
 \end{tikzpicture}
-
-\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}
-\label{figure:not_manifold_triang}
 \end{figure}
@@
 \begin{figure}
+    \caption{Illustration of Lemma~\ref{lemma:stardivision}. Left: 
+    the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles. 
+    The height vector to $v_2$ in all three triangles remains the same.
+The height vector to $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector to $v_0$ in the original triangle.
+    Right: 
+    the triangle $T$ is trisected, leading to three new triangles. 
+    The height vector to $z_T$ from the opposite edge in any triangle is one third of the original height vector of that edge.}
     \begin{center}
@@
     \end{center}
-    \caption{Illustration of Lemma~\ref{lemma:stardivision}. Left: 
-    the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles. 
-    The height vector to $v_2$ in all three triangles remains the same.
-The height vector to $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector to $v_0$ in the original triangle.
-    Right: 
-    the triangle $T$ is trisected, leading to three new triangles. 
-    The height vector to $z_T$ from the opposite edge in any triangle is one third of the original height vector of that edge.}
 \end{figure}
@@
 \begin{figure}[t]
+    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.
+    The triangle $T$ completes the star around an interior vertex. $A$ is the complement of the triangle within the star. 
+    $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
+    $\Gamma_2$ is left invariant by the deformation.
+    $\Xi_{1}$ maps $T$ into $A$ while preserving the interface $\Gamma_1$,
+    and 
+    $\Xi_{2}$ maps the whole patch into $A$ while preserving the boundary $\Gamma_2$.
+    }\label{figure:geometricconstruction}
     \centering
@@
     \end{tabular} 
-    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.
-    The triangle $T$ completes the star around an interior vertex. $A$ is the complement of the triangle within the star. 
-    $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
-    $\Gamma_2$ is left invariant by the deformation.
-    $\Xi_{1}$ maps $T$ into $A$ while preserving the interface $\Gamma_1$,
-    and 
-    $\Xi_{2}$ maps the whole patch into $A$ while preserving the boundary $\Gamma_2$.
-    }\label{figure:geometricconstruction}
 \end{figure}
@@
 \begin{table}[t]
+    \caption{
+    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
+    where boundary conditions are imposed along the boundary part $\Gamma$, 
+    computed via lowest-order finite element methods on a refined mesh. 
+    Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
+    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} 
+    give the upper bound $2/\pi \cdot \diam(\Delta^3) \approx 0.90031631615$.
+    }\label{table:referencepoincarefriedrichs}
     \centering
@@
     \end{tabular}
-    \caption{
-    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
-    where boundary conditions are imposed along the boundary part $\Gamma$, 
-    computed via lowest-order finite element methods on a refined mesh. 
-    Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
-    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} 
-    give the upper bound $2/\pi \cdot \diam(\Delta^3) \approx 0.90031631615$.
-    }\label{table:referencepoincarefriedrichs}
 \end{table}
@@
 \begin{table}[t]
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
+    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
+    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
+    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
+    }\label{table:estimates2D}
     \centering
@@
     \end{tabular}
-    \caption{
-    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
-    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
-    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
-    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
-    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
-    }\label{table:estimates2D}
 \end{table}
@@
 \begin{table}[t]
+    \caption{
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
+    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
+    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
+    }\label{table:estimates3D:grad}
     \centering
@@
     \end{tabular} 
+\end{table}
+
+\begin{table}[t]  
     \caption{
-    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
-    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
-    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
-    }\label{table:estimates3D:grad}
-\end{table}
-
-\begin{table}[t]  
+    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
+    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
+    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=1$ (3rd and 4th column) and with $k=2$ (5th and 6th column).
+    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
+    }\label{table:estimates3D:curldiv}
     \centering
@@
     \end{tabular}
-    \caption{
-    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
-    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
-    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=1$ (3rd and 4th column) and with $k=2$ (5th and 6th column).
-    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
-    }\label{table:estimates3D:curldiv}
 \end{table}

### 2025-02-14 focm_02_2025/sn-article.tex
add FoCM (Springer) subfolder

--- 2025-02-14 main.tex
@@
-% \documentclass[sn-mathphys-num]{sn-jnl}
-\documentclass[10pt,a4paper]{article}
-
-\input{header}
-
-% LTeX: enabled=false
-% Title, authors, and affiliations
-% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
-% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}
-\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
-\author{
-    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
-    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
-    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
-}
-\date{}
-% LTeX: enabled=true
+\documentclass[sn-mathphys-num]{sn-jnl}
+
+\input{../header}
+
+% \theoremstyle{thmstyleone}%
+% \newtheorem{theorem}{Theorem}%  meant for continuous numbers
+% %\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+% % optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+% \newtheorem{proposition}[theorem]{Proposition}% 
+% %\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+% 
+% \theoremstyle{thmstyletwo}%
+% \newtheorem{example}{Example}%
+% \newtheorem{remark}{Remark}%
+% 
+% \theoremstyle{thmstylethree}%
+% \newtheorem{definition}{Definition}%
+
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
 
@@
 
-\maketitle
-
-\begin{abstract}
-    We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations.
+\title[Computable PF over shellable triangulations]{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
+
+%%=============================================================%%
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% \author*[1,2]{\fnm{Joergen W.} \spfx{van der} \sur{Ploeg} 
+%%  \sfx{IV}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author[1]{\fnm{Th\'eophile} \sur{Chaumont-Frelet}}\email{theophile.chaumont@inria.fr}
+\equalcont{These authors contributed equally to this work.}
+
+\author*[2]{\fnm{Martin Werner} \sur{Licht}}\email{martin.licht@epfl.ch}
+
+\author[3,4]{\fnm{Martin} \sur{Vohral\'ik}}\email{martin.vohralik@inria.fr}
+\equalcont{These authors contributed equally to this work.}
+
+\affil[1]{\orgname{Inria Univ. Lille and Laboratoire Paul Painlev\'e}, \orgaddress{\city{Villeneuve-d'Ascq}, \postcode{59655}, \country{France}}}
+
+\affil*[2]{\orgname{\'Ecole Polytechnique F\'ed\'erale de Lausanne}, \orgaddress{\city{Lausanne}, \postcode{CH-1015}, \state{VD}, \country{Switzerland}}}
+
+\affil[3]{\orgname{Inria}, \orgaddress{\street{48 rue Barrault}, \city{Paris}, \postcode{75647}, \state{State}, \country{France}}}
+\affil[4]{\orgname{CERMICS, Ecole des Ponts}, \orgaddress{\city{Marne-la-Vall\'ee}, \postcode{77455}, \state{State}, \country{France}}}
+
+%%==================================%%
+%% Sample for unstructured abstract %%
+%%==================================%%
+
+\abstract{We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations.
     Notably, the class of shellable triangulations includes local patches (stars) in two or three dimensions.
@@
     We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operators as instances of the exterior derivative.
-    Computational examples illustrate the theoretical findings.
-\end{abstract}
-
-% \tableofcontents
+    Computational examples illustrate the theoretical findings.}
+
+\keywords{Bogovski\u{\i}--Poincar\'e potential operator, Hodge--Laplace eigenvalues, Poincar\'e--Friedrichs constants, shellable triangulations, }
+
+%%\pacs[JEL Classification]{D8, H51}
+
+\pacs[MSC Classification]{58A10, 35A23, 65N30, 57Q99, 57Q05, 05E45}
+
+\maketitle
 
@@
 \begin{figure}[t]
+  \caption{From left to right: local patches around a vertex, and edge, and a triangle.
+The local patch of any full-dimensional simplex only consists of that simplex itself (and its subsimplices).}\label{figure:patches}
   \centering
@@
 \begin{figure}[t]
+\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
+\label{figure:spanningtree}
 \begin{center}
@@
 \begin{figure}[h]
+\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}
+\label{figure:not_manifold_triang}
 % \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
@@
 
-% Future work % DONE: Theo : parts already mentioned ??? 
-% Computable reliable estimates are important: 
-% they quantify the fundamental stability properties of partial differential equations in vector analysis,
-% such as the Hodge Laplace equation. 
-% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in~\eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex.
-
-\section*{Acknowledgments}
-% LTeX: enabled=false
-MWL appreciates helpful remarks by Abdellatif Aitelhad, Martin Costabel, John M.\ Lee, and G\"unther M.\ Ziegler.
-% LTeX: enabled=true
-
-\bibliographystyle{acm_mod}
-\bibliography{library}
+\begin{comment}
+\section*{Declarations}
+
+Some journals require declarations to be submitted in a standardised format.
+Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section.
+If yes, your manuscript must contain the following sections under the heading `Declarations':
+
+\begin{itemize}
+\item Funding
+\item Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
+\item Ethics approval and consent to participate
+\item Consent for publication
+\item Data availability 
+\item Materials availability
+\item Code availability 
+\item Author contribution
+\end{itemize}
+
+\noindent
+If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.
+
+%%===================================================%%
+%% For presentation purpose, we have included        %%
+%% \bigskip command. Please ignore this.             %%
+%%===================================================%%
+\bigskip
+\begin{flushleft}%
+Editorial Policies for:
+
+\bigskip\noindent
+Springer journals and proceedings: \url{https://www.springer.com/gp/editorial-policies}
+
+\bigskip\noindent
+Nature Portfolio journals: \url{https://www.nature.com/nature-research/editorial-policies}
+
+\bigskip\noindent
+\textit{Scientific Reports}: \url{https://www.nature.com/srep/journal-policies/editorial-policies}
+
+\bigskip\noindent
+BMC journals: \url{https://www.biomedcentral.com/getpublished/editorial-policies}
+\end{flushleft}
+\end{comment}
+
+% \bibliographystyle{sn-mathphys-num}
+\bibliography{../library}% common bib file
+%% if required, the content of .bbl file can be included here once bbl is generated
+% \input sn-article.bbl
 
